### 2017-09-29 article.tex
Init

\RequirePackage[l2tabu, orthodox]{nag}
\RequirePackage{silence}\WarningFilter{fmtcount}{\ordinal already defined use \FCordinal instead}
\documentclass[version=last, pagesize, twoside=semi, DIV=calc, bibliography=totoc, 12pt, a4paper, french, english]{scrartcl}
\input{preamble/packages}
\input{preamble/math_basics}
\input{preamble/math_mine}
\input{preamble/redac}
\input{preamble/draw}
\input{preamble/acronyms}

\begin{document}
\title{The title}
\author{Olivier Cailloux}
\makeatletter
	\hypersetup{
		pdfsubject={Epistemology},
		pdfkeywords={Decision aiding, Decision making, Argumentation}
	}
\makeatother
\maketitle

\section{Overview}
Looking for possibilities (weak acceptance). Those propositions that are in the reflexive preferences in a large sense: there is no strong enough reason to reject those propositions, though their contrary may hold as well.
\begin{itemize}
	\item All alternatives $\allalts$.
	\item Topic $\alltopic$ = $\Set{\prop_\alt, \alt \in \allalts} ∪ \Set{\prop_{¬\alt}, \alt \in \allalts}$. Denoted simply $\alt$ and $¬\alt$. We define $¬\prop$, with $\prop = \prop_\alt$, as equal to $\prop_{¬\alt}$ and $¬\prop$, with $\prop = \prop_{¬\alt}$, as equal to $\prop_{\alt}$.
	\item All possible arguments: $\allargs$, the set of all strings.
	\item $\ar' \ibeatsed_\prop \ar$: strong rejection attack; $\ar'$ renders $\ar$ invalid (with $\ar$ supporting $\prop$, $\ar'$ claims that $¬\prop$ is a certainty, thus $\ar$ can’t be used even to say that $\prop$ is a possibility, thus $\ar'$ supports that $\prop$ is not weakly accepted). Thus we have only attacks between contradictory propositions. Suffices that the attack occurs at least once over the considered time frame and unstability factors (such as submitting $i$ to other counter-arguments). Here we do not condition on $\ar'$ surviving: $\ar'$ is declared incorrect, with no necessity of pursuing the debate and no hope of reinstatement. Example: $\ar'$ has already been taken into account and countered in $\ar$. (TODO exploit the fact that we probably only need the negation, $¬(\ar' \ibeatsed_\prop \ar)$, which is pretty clear as further attacks to $\ar'$ have no impact.)
	\item Define $\ileadsto$, decisive support, as $\ar \ileadsto \prop$ iff $i$ declares that $\ar$ is a definitive argument in that weakly supports $\prop$: there are no $\ar'$ that changes her position (once she has heard about $\ar$), in the sense of weak acceptancy, thus, no $\ar'$ attacking $\ar$ in the sense of strong rejection attack.
\end{itemize}

\begin{definition}[Clear-cut]
	Define a situation $(\alltopic, \allargs, \ileadsto)$. It is clear-cut iff $\forall \alt \in \allalts: \ileadstoinv(\{\prop_\alt, \prop_{¬\alt}\}) ≠ \emptyset$.
\end{definition}

We want to prove that, under suitable assumptions (justifiable unstability, and so on): situation is clear cut iff a model (with no cycles) exist.

\section{Models}
$D$ a DAG over $(s, p)$ pairs.

Given $(\ar_2, \prop), (\ar_1, ¬\prop) \in D$, define $\ar_2 \wibeatse_{¬\prop} \ar_1$ iff $\forall \ar \suchthat (\ar, \prop) \in D: [¬(\ar_1 \ibeatsed_\prop \ar) ∨ ¬(\ar_1 \ibeatsed_\prop (\ar + \ar_2)) ∨ \ar_2 \text{ is itself attacked}]$.
Can perhaps be queried directly by asking (in the context of some $\ar_1 \ibeatsed_\prop \ar$): “assume $\ar_2$ survives, then does $\ar_2$ counter $\ar_1$?” (In the sense that $\ar_2$ is sufficiently convincing that $\prop$ holds perhaps, to cancel the argument $\ar_1$ according to which $¬\prop$ surely holds.)

Given $(\ar_3, ¬\prop), (\ar_2, \prop) \in D$, define $\ar_3 \ibeatse_\prop \ar_2$ iff $\forall (\ar_1, ¬\prop) \in D: [¬(\ar_2 \wibeatse^\text{dec}_{¬\prop} \ar_1) ∨ ¬(\ar_2 \wibeatse^\text{dec}_{¬\prop} (\ar_1 + \ar_3)) ∨ \ar_3 \text{ is itself attacked}]$.

Define $¬(\ar_2 \wibeatse^\text{dec}_{¬\prop} \ar_1) = ¬(\ar_2 \wibeatse_{¬\prop} \ar_1)$. Then,
$(\ar_3, ¬\prop) \ibeatse (\ar_2, \prop)$ iff $\forall (\ar_1, ¬\prop): [(\ar_1 \ibeatsed_\prop \ar_2) ∨ ((\ar_1 + \ar_3) \ibeatsed_\prop \ar_2) ∨ \ar_3 \text{ is itself attacked}]$.

\subsection{Perhaps equivalent and better}
Let $D$ be a DAG over $(\ar, \prop)$ pairs, such that $\forall \ar: (\ar, \prop) \notin D ∨ (\ar, ¬\prop) \notin D$, thus, a given argument is never used both with $\prop$ and with $¬\prop$.

Define $\ibeats^D_\prop$ as follows.
\begin{itemize}
	\item $\ar_2 \ibeats^D_\prop \ar_1$ iff $(\ar_2 \ibeatsed_\prop \ar_1)$ when $(\ar_1, \prop), (\ar_2, ¬\prop) \in D$,
	\item $\ar_2 \ibeats^D_\prop \ar_1$ iff $¬(\ar_1 \ibeatsed_\prop \ar_2)$ when $(\ar_2, \prop), (\ar_1, ¬\prop) \in D$, 
	\item $\ar_2 \ibeats^D_\prop \ar_1$ not defined otherwise.
\end{itemize}
Thus, $\ar_2 \ibeats^D_{¬\prop} \ar_1$ iff $¬(\ar_1 \ibeatsed_{¬\prop} \ar_2)$ when $(\ar_1, \prop), (\ar_2, ¬\prop) \in D$.

Given $(\ar_3, ¬\prop), (\ar_2, \prop) \in D$, define $\ar_3 \ibeatse_\prop \ar_2$ iff $\forall (\ar_1, ¬\prop) \in D: [¬(\ar_2 \ibeats^D_\prop \ar_1) ∨ ¬(\ar_2 \ibeats^D_\prop (\ar_1 + \ar_3)) ∨ \ar_3 \text{ is itself attacked}]$.

Given $(\ar_3, \prop), (\ar_2, ¬\prop) \in D$, define $\ar_3 \wibeatse_{¬\prop} \ar_2$ iff $\forall (\ar_1, \prop) \in D: [¬(\ar_2 \ibeatsed_\prop \ar_1) ∨ ¬(\ar_2 \ibeatsed_\prop (\ar_1 + \ar_3)) ∨ \ar_3 \text{ is itself attacked}]$.

\subsection{Newer try}
$s' ntepd s$ (for not triangle exists p d) iff $¬(s' tepd s)$, iff it is sure that $s'$ has no impact on $s$, even assuming that $s'$ would in turn resist all counter-arguments to it.

$s2 naenp s1$ iff it is sure that $s2$ has no sufficient impact on $s1$, even assuming that $s2$ survives, more precisely, iff for some $s$, where $¬(s1 ntepd s)$: $¬(s1 ntepd (s+s2))$.

\section{Models - try}
Additionally.
\begin{itemize}
	\item Propositions weakly self-supported $\topic \subseteq \alltopic$: weakly accepted if no arg is given. Examples: $m$ = “eat miam”; $¬b$ = “beurk is to exclude”; or, in a problem where there’s no particularly good aliments, both $a$ = “eat this” and $¬a$.
%	\item $\ar' \nibeatse_\prop \ar$: existence of an absence of strong rejection attack.
	\item $\ar' \wibeatse_\prop \ar$: weak attack; $\ar'$ renders $\ar$ invalid because too strong (with $\ar$ supporting $\prop$, $\ar'$ claims that $¬\prop$ is a possibility, thus $\ar$ can’t be used to say that $\prop$ is a certainty, thus $\ar'$ supports that $¬\prop$ is weakly accepted). Assuming $\ar'$ survives. This is a relation on the arguments that defend $\prop$ times the arguments that defend $¬\prop$, union the converse, union on all propositions. Thus we have only attacks between contradictory propositions.
\end{itemize}

When given $(\ar, \prop)$, $i$ may say: $\ar$ does not survive; or: assuming $\ar$ survives, then $\ar$ supports $\prop$, or, assuming $\ar$ survives, then $\ar$ does not support $\prop$ anyway.

When given $\ar'$ against $\ar$, $i$ may say: $\ar'$ does not survive, or: assuming $\ar'$ survives, then $\ar'$ supports $¬\prop$, …

We might use the following hyp. (We can dispense of it?) (TODO what does that mean?)
\begin{definition}[Completeness of $\topic$]
	At least one of $\alt$ and $¬\alt$ is in $\topic$, for each alternative.
\end{definition}
If none, we should assume the DM means that both are (which can be done if falsifying against observed choices).

I think we need a primitive definition of $(s, p)$ attacked by $s1$.

Then we can define: $s_{cc}$ attacks $s_c$ iff [$(p + s_{cc}, p)$ not attacked by $s_c$, or $s_{cc}$ not decisive].

Except this is maybe not well defined in case of circularities! (But this should not be a problem as we will not need this definition in that case.)

\begin{definition}
	Given 
\end{definition}

\appendix
\section{Certainties}
Looking for certainties. Those propositions that are in the reflexive preferences in a demanding sense: there is a strong enough reason to prefer it than its contrary.
\begin{itemize}
	\item $\ar' \wibeatse \ar$: weak attack; $\ar'$ renders $\ar$ invalid (can’t be used to say that $t$ holds for sure) (assuming $\ar'$ survives)
	\item Propositions strongly self-supported: strongly accepted if no arg is given. Examples: $m$ = “eat miam”; $¬b$ = “beurk is to exclude”. We might have neither $c$ nor $¬c$ in that set.
\end{itemize}

%\bibliography{mybib}

\end{document}

### 2017-10-12 article.tex
Models and conds

@@
 We define $¬\prop$, with $\prop = \prop_\alt$, as equal to $\prop_{¬\alt}$ and $¬\prop$, with $\prop = \prop_{¬\alt}$, as equal to $\prop_{\alt}$.
-	\item All possible arguments: $\allargs$, the set of all strings.
-	\item $\ar' \ibeatsed_\prop \ar$: strong rejection attack; $\ar'$ renders $\ar$ invalid (with $\ar$ supporting $\prop$, $\ar'$ claims that $¬\prop$ is a certainty, thus $\ar$ can’t be used even to say that $\prop$ is a possibility, thus $\ar'$ supports that $\prop$ is not weakly accepted).
+	\item All possible arguments: $\allargs$, the set of all strings. It can be chosen differently, but must be non empty as it contains at least $\emptyset$, the empty argument.
+	\item $\ar' \nibeatsst[\prop] \ar$: absence, all the time, of strong rejection attack; $\ar'$ does not render $\ar$ invalid; it is sure that $\ar'$ has no impact on $\ar$, even assuming that $\ar'$ would in turn resist all counter-arguments to it.
+This is an hypothesized relation, unobservable, used to define the deliberated preferences of $i$ (it is clear we can’t observe it, thus, as we can’t observe the DP).
+With $\ar$ supporting $\prop$, $\ar'$ claims that $¬\prop$ is a certainty, thus $\ar'$ supports that $\prop$ is not weakly accepted, thus $\ar$, if rebutted, can’t be used even to say that $\prop$ is a possibility.
 Thus we have only attacks between contradictory propositions.
-Suffices that the attack occurs at least once over the considered time frame and unstability factors (such as submitting $i$ to other counter-arguments).
+Suffices that the attack occurs at least once over the considered time frame and unstability factors (such as submitting $i$ to other counter-arguments) to negate $\ar' \nibeatsst[\prop] \ar$.
 Here we do not condition on $\ar'$ surviving: $\ar'$ is declared incorrect, with no necessity of pursuing the debate and no hope of reinstatement.
-Example: $\ar'$ has already been taken into account and countered in $\ar$.
-(TODO exploit the fact that we probably only need the negation, $¬(\ar' \ibeatsed_\prop \ar)$, which is pretty clear as further attacks to $\ar'$ have no impact.)
-	\item Define $\ileadsto$, decisive support, as $\ar \ileadsto \prop$ iff $i$ declares that $\ar$ is a definitive argument in that weakly supports $\prop$: there are no $\ar'$ that changes her position (once she has heard about $\ar$), in the sense of weak acceptancy, thus, no $\ar'$ attacking $\ar$ in the sense of strong rejection attack.
+Example: $\ar'$ has already been taken into account and countered in $\ar$; or $\ar'$ does not talk about $\ar$ at all; or is not understood by $i$.
+Note that when $\ar' \nibeatsst[\prop] \ar$, further attacks to $\ar'$ have no chance to change that fact (assuming some properties over the way $i$ reason).
+The negation of this should read: $\ar'$ may attack $\ar$ in at least some cases.
+For example, $¬ (\ar' \nibeatsst[\prop] \ar)$ ($\ar'$ may attack $\ar$) in case $i$ suspects that $\ar'$ is invalid (because of some counter-argument $\ar_2$ to $\ar'$ that $i$ has in mind) but wants to leave the door open to reinstatement of $\ar'$.
+	\item Define $¬ (\ar' \nibeatsst[\prop] \ar)$ iff $\ar' \ibeatse[\prop] \ar$.
+	\item Define $\ar \ibeatse[¬\prop, \text{sure}] \ar'$ iff $\ar$ may attack $\ar'$, where $\ar$ has a weak claim ($\prop$ is possible) and $\ar'$ has a strong claim ($¬\prop$ is sure).
+Similarly, $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$ is a constant absence of attack.
+	\item Require (as an axiom) that $\ar' \ibeatse[\prop] \ar ∨ \ar \ibeatse[¬\prop, \text{sure}] \ar'$.
+Equivalently: $¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar' ∧ \ar' \nibeatsst[\prop] \ar)$; $¬(\ar' \ibeatsst[\prop] \ar ∧ \ar' \nibeatsst[\prop] \ar)$; $\ar' \ibeatsst[\prop] \ar ⇒ \ar' \ibeatse[\prop] \ar$.
+\end{itemize}
+It seems that knowledge of the poss rels is insufficient to know the sure rel: assume $¬(\ar' \ibeatse[\prop] \ar)$ and $\ar \ibeatse[¬\prop] \ar'$.
+Thus, 1.
+$\ar$ is sufficient for $\prop$ possible, $\ar'$ not sufficient for $¬\prop$ sure; and 2.
+$\ar$ may be sufficient for $\prop$ sure, $\ar'$ insuff for $\prop$.
+But is $\ar$ sufficient for $\prop$ sure?
+Thus, $\ar' \ibeatse[\prop, \text{sure}] \ar$?
+Equivalently: $\ar \nibeatse[¬\prop] \ar'$?
+To know this we need to know whether $¬\prop \in T_i$.
+Or can we use $¬(\ar' \ibeatse[\prop] \ar) ⇒ \ar' \nibeatse[\prop] \ar$?
+
+Previously:
+\begin{itemize}
+	\item $¬ (\ar' \ibeatsst[\prop] \ar) ⇔ \ar' \nibeatse[\prop] \ar ⇔ \ar \ibeatse[¬\prop, \text{sure}] \ar' ⇔ ¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar')$.
+	\item Require (as an axiom) that $\ar' \ibeatse[\prop] \ar ∨ \ar' \nibeatse[\prop] \ar$. This yields $¬ (\ar' \ibeatsst[\prop] \ar ∧ \ar' \nibeatsst[\prop] \ar)$.
 \end{itemize}
 
+Define $T_i \subseteq \alltopic$ as the set of propositions that are weakly accepted.
+\begin{definition}[Weak acceptance]
+	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$.
+A proposition $\prop \in \alltopic$ is weakly accepted, $\prop \in T_i$, iff $\exists \ar \in \allargs \suchthat \forall \ar' \in \allargs: \ar' \nibeatsst[\prop] \ar$.
+\end{definition}
+It follows that $¬\prop \notin T_i$ iff $\forall \ar: \exists \ar' \suchthat \ar' \ibeatse[¬\prop] \ar$.
+
+\begin{definition}[Strong rejection]
+	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$.
+A proposition $¬\prop \in \alltopic$ is strongly rejected iff $\forall \ar \in \allargs, \exists \ar' \in \allargs \suchthat \ar \nibeatsst[\prop, \text{sure}] \ar'$.
+\end{definition}
+Thus, strong rejection mandates $\ar'$ such that $\ar' \ibeatsst[¬\prop] \ar$.
+
+If $¬\prop$ is strongly rejected, then it is not weakly accepted ($¬\prop \notin T_i$) as $\ar' \ibeatsst[¬\prop] \ar ⇒ \ar' \ibeatse[¬\prop] \ar$.
+
 \begin{definition}[Clear-cut]
-	Define a situation $(\alltopic, \allargs, \ileadsto)$. It is clear-cut iff $\forall \alt \in \allalts: \ileadstoinv(\{\prop_\alt, \prop_{¬\alt}\}) ≠ \emptyset$.
+	A situation is clear-cut iff $¬\prop \notin T_i ⇒ ¬\prop$ is strongly rejected.
 \end{definition}
 
-We want to prove that, under suitable assumptions (justifiable unstability, and so on): situation is clear cut iff a model (with no cycles) exist.
+First, we want that if situation is CC, 1) exists a valid model, 2) any valid model has the right $T_i$.
+A model is valid if: a) can correctly get reinstatement; b) i is justifiably unstable; c) finite arguments; d) model is convincing.
+
+Second, we want that given a situation, if there exists a valid model, then the situation is CC.
+
+Third, perhaps we get as a bonus that there exists a valid model ⇔ the situation is CC3. CC1: ¬p not in wa ⇔ ¬p s rej. CC2: ¬p s rej ⇒ p w acc. CC3: ¬p s rej ⇒ p is sure.
 
 \section{Models}
-$D$ a DAG over $(s, p)$ pairs.
+$\mbeats$ a (possibly infinite!) DAG over $(s, p)$ pairs, $+$ defined over arguments in $\mbeats$: $(\ar_1, \prop) + (\ar_3, \prop) = (\ar', \prop)$ for some $(\ar', \prop) \in \mbeats$.
+Define $D' \subseteq \clargs$ as a subset of arguments (those supporting propositions).
+Define $\clargs \subseteq \allargs$ as the set of arguments used in $\mbeats$.
+Assume it can be represented by $≥$, a weak order defined on the basis of $\mbeats$, defining at most $k$ equivalence classes, so that our recursive definitions make sense.
+(TODO make this correct and precise.)
 
-Given $(\ar_2, \prop), (\ar_1, ¬\prop) \in D$, define $\ar_2 \wibeatse_{¬\prop} \ar_1$ iff $\forall \ar \suchthat (\ar, \prop) \in D: [¬(\ar_1 \ibeatsed_\prop \ar) ∨ ¬(\ar_1 \ibeatsed_\prop (\ar + \ar_2)) ∨ \ar_2 \text{ is itself attacked}]$.
-Can perhaps be queried directly by asking (in the context of some $\ar_1 \ibeatsed_\prop \ar$): “assume $\ar_2$ survives, then does $\ar_2$ counter $\ar_1$?” (In the sense that $\ar_2$ is sufficiently convincing that $\prop$ holds perhaps, to cancel the argument $\ar_1$ according to which $¬\prop$ surely holds.)
+$\mbeats(\ar_2)$: arguments that $\ar_2$ attacks, $\ar_1 \in \mbeats(\ar_2) ⇔ \ar_2 \mbeats \ar_1$.
 
-Given $(\ar_3, ¬\prop), (\ar_2, \prop) \in D$, define $\ar_3 \ibeatse_\prop \ar_2$ iff $\forall (\ar_1, ¬\prop) \in D: [¬(\ar_2 \wibeatse^\text{dec}_{¬\prop} \ar_1) ∨ ¬(\ar_2 \wibeatse^\text{dec}_{¬\prop} (\ar_1 + \ar_3)) ∨ \ar_3 \text{ is itself attacked}]$.
+Given $\ar_1 \in D'$, define $\ar_2 \wibeatse \ar_1$ iff $\ar_2 \ibeatse \ar_1$.
 
-Define $¬(\ar_2 \wibeatse^\text{dec}_{¬\prop} \ar_1) = ¬(\ar_2 \wibeatse_{¬\prop} \ar_1)$. Then,
-$(\ar_3, ¬\prop) \ibeatse (\ar_2, \prop)$ iff $\forall (\ar_1, ¬\prop): [(\ar_1 \ibeatsed_\prop \ar_2) ∨ ((\ar_1 + \ar_3) \ibeatsed_\prop \ar_2) ∨ \ar_3 \text{ is itself attacked}]$.
+Given $\ar_1 \in D'$, define $\ar_2 \nwibeatse \ar_1$ iff $\ar_1 \ibeatse[\text{sure}] \ar_2$.
 
-\subsection{Perhaps equivalent and better}
-Let $D$ be a DAG over $(\ar, \prop)$ pairs, such that $\forall \ar: (\ar, \prop) \notin D ∨ (\ar, ¬\prop) \notin D$, thus, a given argument is never used both with $\prop$ and with $¬\prop$.
+Define $\ar_1 \wibeatse[\text{sure}] \ar_2$ ⇔ $\ar_2 \nwibeatse \ar_1$.
 
-Define $\ibeats^D_\prop$ as follows.
+$\ar_1$ root in $\mbeats$ $⇒$ $\ar_1 \in D'$. $\ar_1 \in D' ⇒ \ar_3 + \ar_1 \in D'$.
+
+Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin D'$: $\ar_3 \wibeatse \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse \ar_1 ∧ \ar_2 \nwibeatse \ar_3 + \ar_1$.
+
+Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin D'$: $\ar_3 \nwibeatse \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse \ar_1 ∧ \ar_2 \wibeatse \ar_3 + \ar_1$.
+
+Check: For $\ar_4, \ar_3, \ar_3 \notin D'$: $\ar_4 \wibeatse \ar_3$ iff $\exists \ar_2 \suchthat  \ar_3 \wibeatse \ar_2 ∧ \ar_3 \nwibeatse \ar_4 + \ar_2$.
+Thus, $\exists \ar_2 \suchthat  \ar_3 \wibeatse \ar_2 ∧ \exists \ar_1 \suchthat (\ar_4 + \ar_2) \wibeatse \ar_1 ∧ (\ar_4 + \ar_2) \wibeatse \ar_3 + \ar_1$.
+
+Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse \ar_1$, we have: $\ar_3 \wibeatse \ar_2 ∨ \ar_3 \nwibeatse \ar_2$.
+
+Define $\wibeatsst = ¬\nwibeatse$. Hence, $¬(\ar \wibeatse[\text{sure}] \ar') ⇔ \ar \nwibeatsst[\text{sure}] \ar' ⇔ ¬(\ar' \nwibeatse \ar) ⇔ \ar' \wibeatsst \ar$.
+
+Define $\nwibeatsst = ¬\wibeatse$.
+
+Hence, given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin D'$: $\ar_3 \wibeatsst \ar_2$ iff $\forall \ar_1 \in \mbeats(\ar_2) ∩ \wibeatse(\ar_2): \ar_2 \nwibeatsst \ar_3 + \ar_1$.
+
+\section{Conditions}
+\begin{definition}[Reinstatement]
+	Given a model $\mu = (\mbeats, D')$ and a decision situation $(\allalts, \allargs, \ibeatse)$, given $\ar_1 \in D', \ar_2 \mbeats \ar_1, \ar_2 \wibeatse \ar_1, \ar_3 \wibeatse \ar_2, \mbeatsinv(\ar_3) = \emptyset$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_1 + \ar_3) ∧ \mbeatsinv(\ar_1 + \ar_3) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
+\end{definition}
+
+\begin{definition}[Observable validity]
+	Given as above, the model is observably valid iff $\forall \ar_2 \mbeats \ar: ¬(\ar_2 \wibeatse \ar) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse \ar_2$.
+\end{definition}
+
+\begin{definition}[Justifiable unstability]
+	Given as above…
+\end{definition}
+
+\appendix
+\section{Todo}
+Road map.
 \begin{itemize}
-	\item $\ar_2 \ibeats^D_\prop \ar_1$ iff $(\ar_2 \ibeatsed_\prop \ar_1)$ when $(\ar_1, \prop), (\ar_2, ¬\prop) \in D$,
-	\item $\ar_2 \ibeats^D_\prop \ar_1$ iff $¬(\ar_1 \ibeatsed_\prop \ar_2)$ when $(\ar_2, \prop), (\ar_1, ¬\prop) \in D$, 
-	\item $\ar_2 \ibeats^D_\prop \ar_1$ not defined otherwise.
+	\item P1: $p_a$ is w-a or $p_{¬a}$ is w-a
+	\item Define $p_{a}$ is strongly accepted; $p_{¬a}$ is strongly rejected, so that they are equivalent.
+	\item P2: $p_a$ is w-a or $p_{¬a}$ is strongly accepted.
 \end{itemize}
-Thus, $\ar_2 \ibeats^D_{¬\prop} \ar_1$ iff $¬(\ar_1 \ibeatsed_{¬\prop} \ar_2)$ when $(\ar_1, \prop), (\ar_2, ¬\prop) \in D$.
 
-Given $(\ar_3, ¬\prop), (\ar_2, \prop) \in D$, define $\ar_3 \ibeatse_\prop \ar_2$ iff $\forall (\ar_1, ¬\prop) \in D: [¬(\ar_2 \ibeats^D_\prop \ar_1) ∨ ¬(\ar_2 \ibeats^D_\prop (\ar_1 + \ar_3)) ∨ \ar_3 \text{ is itself attacked}]$.
+Other todos.
+\begin{itemize}
+	\item If $i$ does not consider $\ar$ as supporting $\prop$, it also works: if $\prop$ is not weakly acceptable by default, then any $\ar'$ is considered by $i$ as a better argument than $\ar$ in favor of certain $¬\prop$, and so on.
+In fact, whether $\emptyset \ibeatse[\prop] \emptyset$ determines whether $\prop$ is weakly supported by default.
+	\item I should define $\ar' (□\ibeatse[\prop]) \ar$ as an observable: “Assuming $\ar'$ would survive, do you consider $\ar'$ as leading to certainty of $¬\prop$, even when considering $\ar$?”.
+It distinguishes our knowledge and the truth: $\ar' (□\ibeatse[\prop]) \ar ⇒ \ar' \ibeatse[\prop] \ar$, thus, implies $¬ (\ar' \nibeatsst[\prop] \ar)$.
+But out of $¬ (\ar' (□\ibeatse[\prop]) \ar)$, nothing.
+	\item Partition (objectively) $\allargs$ (or $\allargs × \alltopic$) into arguments in favor of $\prop, \text{sure}$, $¬\prop, \text{sure}$, and similarly for possible.
+Use only one rel $\ibeatse$, defined on contradictory arguments only, instead of $\ibeatse[\prop, \text{sure}]$ and others.
+Define $\ar' \ibeatse[\prop] \ar$ equals no when $¬(\ar' \ileadsto ¬\prop, \text{sure})$, equals $\ibeatse$ for adequate arguments, and equals yes when $¬(\ar \ileadsto \prop, \text{possible})$ and $\ar' \ileadsto ¬\prop, \text{sure}$, with probably some complications needed for the argument $\emptyset$ (and related default attitude towards $\prop$).
+\end{itemize}
 
-Given $(\ar_3, \prop), (\ar_2, ¬\prop) \in D$, define $\ar_3 \wibeatse_{¬\prop} \ar_2$ iff $\forall (\ar_1, \prop) \in D: [¬(\ar_2 \ibeatsed_\prop \ar_1) ∨ ¬(\ar_2 \ibeatsed_\prop (\ar_1 + \ar_3)) ∨ \ar_3 \text{ is itself attacked}]$.
+Questions:
+Q1. Relationship with $\ar \ibeatse[\prop] \ar$?
 
-\subsection{Newer try}
-$s' ntepd s$ (for not triangle exists p d) iff $¬(s' tepd s)$, iff it is sure that $s'$ has no impact on $s$, even assuming that $s'$ would in turn resist all counter-arguments to it.
+We want to exclude: $s$ supports $p$ perhaps, attacked by $s2$ (supporting $¬p$ sure), but then $s2$ is attacked by $s$.
+Exclude $\ar' \ibeatse[\prop] \ar$ and $\ar \ibeatse[¬\prop, \text{sure}] \ar'$.
+Require to assume that this situation implies another argument $\ar_3$ “attacking” $\ar'$, thus, such that $\ar_3 + \ar$ is no more attacked by $\ar_2$.
 
-$s2 naenp s1$ iff it is sure that $s2$ has no sufficient impact on $s1$, even assuming that $s2$ survives, more precisely, iff for some $s$, where $¬(s1 ntepd s)$: $¬(s1 ntepd (s+s2))$.
-
-\section{Models - try}
-Additionally.
-\begin{itemize}
-	\item Propositions weakly self-supported $\topic \subseteq \alltopic$: weakly accepted if no arg is given.
+\section{To think}
+Propositions weakly self-supported $\topic \subseteq \alltopic$: weakly accepted if no arg is given.
 Examples: $m$ = “eat miam”; $¬b$ = “beurk is to exclude”; or, in a problem where there’s no particularly good aliments, both $a$ = “eat this” and $¬a$.
-%	\item $\ar' \nibeatse_\prop \ar$: existence of an absence of strong rejection attack.
-	\item $\ar' \wibeatse_\prop \ar$: weak attack; $\ar'$ renders $\ar$ invalid because too strong (with $\ar$ supporting $\prop$, $\ar'$ claims that $¬\prop$ is a possibility, thus $\ar$ can’t be used to say that $\prop$ is a certainty, thus $\ar'$ supports that $¬\prop$ is weakly accepted).
-Assuming $\ar'$ survives.
-This is a relation on the arguments that defend $\prop$ times the arguments that defend $¬\prop$, union the converse, union on all propositions.
-Thus we have only attacks between contradictory propositions.
-\end{itemize}
 
@@
 
-We might use the following hyp. (We can dispense of it?) (TODO what does that mean?)
-\begin{definition}[Completeness of $\topic$]
-	At least one of $\alt$ and $¬\alt$ is in $\topic$, for each alternative.
-\end{definition}
-If none, we should assume the DM means that both are (which can be done if falsifying against observed choices).
+Given $(\ar_2, \prop), (\ar_1, ¬\prop) \in D$, define $¬(\ar_2 \wibeatse^\text{neg}_{¬\prop} \ar_1)$ iff for some $(\ar, \prop) \in D$, where $\ar_1 \ibeatse[\prop] \ar$: $\ar_1 \ibeatse[\prop] \ar + \ar_2$.
+Equivalently: $\ar_2 \wibeatse^\text{neg}_{¬\prop} \ar_1$ iff for all $\ar$, where $\ar_1 \ibeatse[\prop] \ar$: $¬(\ar_1 \ibeatse[\prop] \ar + \ar_2)$.
+(This does not seem right: if given $\ar_3$ attacking $\ar_2$, and not given $\ar_4$ which would convincingly rebut $\ar_3$, then temporarily it may hold again that $\ar_1 \ibeatse[\prop] \ar + \ar2$ (in the sense that $\ar_1 + \ar_3 \ibeatse[\prop] \ar + \ar_2$).)
 
-I think we need a primitive definition of $(s, p)$ attacked by $s1$.
+$\ar_2 \wibeatse_{¬\prop} \ar_1$ can perhaps be queried directly by asking (in the context of some $\ar_1 \ibeatse[\prop] \ar$): “assume $\ar_2$ survives, then does $\ar_2$ counter $\ar_1$?” (In the sense that $\ar_2$ is sufficiently convincing that $\prop$ holds perhaps, to cancel the argument $\ar_1$ according to which $¬\prop$ surely holds.)
 
-Then we can define: $s_{cc}$ attacks $s_c$ iff [$(p + s_{cc}, p)$ not attacked by $s_c$, or $s_{cc}$ not decisive].
-
-Except this is maybe not well defined in case of circularities! (But this should not be a problem as we will not need this definition in that case.)
-
-\begin{definition}
-	Given 
-\end{definition}
-
-\appendix
 \section{Certainties}
@@
 
+\begin{definition}[Sure acceptance]
+	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$.
+A proposition $\prop \in \alltopic$ is accepted as sure iff $\exists \ar' \in \allargs \suchthat \forall \ar \in \allargs: \ar \nibeatsst[\prop, \text{sure}] \ar'$.
+\end{definition}
+
+Assume we use rather: if $p$ is not sure, then $¬p$ is weakly accepted (by def).
+Then we have never problems of inconsistency!
+But we could be in a situation where $p$ is not accepted as sure but nobody can tell why because it is fundamentally unstable (sometimes $p$ being accepted, sometimes not).
+
+\section{Example}
+s2 argues in favor of p against s1: s "le monde n’est pas fiable".
+s1 "le monde est fiable, bhl l’a dit".
+s2 "bhl est un clown, il s’est planté sur l’Irak".
+s3 "il avait raison sur l’Irak : l’Irak a des ADM".
+s4 "l’Irak n’a pas d’ADM, Bush l’a reconnu".
+Does s4 attack s3?
+"bhl est un clown, il s’est planté sur l’irak" + "l’irak n’a pas d’ADM, Bush l’a reconnu" VS "il avait raison sur l’Irak : l’Irak a des ADM" !
+
+Measure problem?
+
 %\bibliography{mybib}

### 2017-11-02 article.tex
Plenty

@@
 	\item Define $¬ (\ar' \nibeatsst[\prop] \ar)$ iff $\ar' \ibeatse[\prop] \ar$.
+	\item Define $\args^\prop$ as the decisive arguments in favor of $\prop$: $\ar \in \args^\prop ⇔ \nexists \ar' \ibeatse[\prop] \ar ⇔ \ar' \nibeatsst[\prop] \ar$.
 	\item Define $\ar \ibeatse[¬\prop, \text{sure}] \ar'$ iff $\ar$ may attack $\ar'$, where $\ar$ has a weak claim ($\prop$ is possible) and $\ar'$ has a strong claim ($¬\prop$ is sure).
 Similarly, $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$ is a constant absence of attack.
-	\item Require (as an axiom) that $\ar' \ibeatse[\prop] \ar ∨ \ar \ibeatse[¬\prop, \text{sure}] \ar'$.
-Equivalently: $¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar' ∧ \ar' \nibeatsst[\prop] \ar)$; $¬(\ar' \ibeatsst[\prop] \ar ∧ \ar' \nibeatsst[\prop] \ar)$; $\ar' \ibeatsst[\prop] \ar ⇒ \ar' \ibeatse[\prop] \ar$.
+	\item Define $\args^{¬\prop, \text{sure}}$ as the decisive arguments in favor of $¬\prop, \text{sure}$: $\ar' \in \args^{¬\prop, \text{sure}} ⇔ \nexists \ar \ibeatse[¬\prop, \text{sure}] \ar' ⇔ \ar \nibeatsst[¬\prop, \text{sure}] \ar'$.
+	\item Require (axiom A1) that $\ar' \ibeatse[\prop] \ar ∨ \ar \ibeatse[¬\prop, \text{sure}] \ar'$.
+Equivalently: $¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar' ∧ \ar' \nibeatsst[\prop] \ar)$; $\ar \nibeatsst[¬\prop, \text{sure}] \ar' ⇒ \ar' \ibeatse[\prop] \ar$.
+	\item Axiom A2: $\ar \nibeatsst[¬\prop, \text{sure}] \ar' ⇒ \ar \nibeatsst[¬\prop] \ar'$. Equivalently: $\ar \ibeatse[¬\prop] \ar' ⇒ \ar \ibeatse[¬\prop, \text{sure}] \ar'$.
+	\footnote{A3: $[\exists \ar \suchthat (\ar' \ibeatse[\prop] \ar ∧ \ar \ibeatse[¬\prop, \text{sure}] \ar')] ⇒ \exists \ar_2 \suchthat \ar_2 \ibeatse[¬\prop] \ar'$.
+Equivalently: $\ar_2 \nibeatsst[¬\prop] \ar', \forall \ar_2$ implies that for all $\ar$, $(\ar' \nibeatsst[\prop] \ar ∨ \ar \nibeatsst[¬\prop, \text{sure}] \ar')$.
+A1, A2 and A3 are equivalent to: $\ar \nibeatsst[¬\prop, \text{sure}] \ar' ⇔ \ar \nibeatsst[¬\prop] \ar' ∧ \ar' \ibeatse[\prop] \ar$.}
+	\footnote{Having A1 and A2, can we have $\ar \nibeatsst[¬\prop] \ar' ∧ \ar' \ibeatse[\prop] \ar ∧ \ar \ibeatse[¬\prop, \text{sure}] \ar'$?
+Consider $(\ar', ¬\prop) \succeq (\ar, \prop) \sim (\ar', ¬\prop, \text{sure}) \succeq (\ar, \prop, \text{sure})$.}
 \end{itemize}
+
 It seems that knowledge of the poss rels is insufficient to know the sure rel: assume $¬(\ar' \ibeatse[\prop] \ar)$ and $\ar \ibeatse[¬\prop] \ar'$.
@@
 Equivalently: $\ar \nibeatse[¬\prop] \ar'$?
-To know this we need to know whether $¬\prop \in T_i$.
+To know this we need to know whether $¬\prop \in \iposs$.
 Or can we use $¬(\ar' \ibeatse[\prop] \ar) ⇒ \ar' \nibeatse[\prop] \ar$?
@@
 	\item $¬ (\ar' \ibeatsst[\prop] \ar) ⇔ \ar' \nibeatse[\prop] \ar ⇔ \ar \ibeatse[¬\prop, \text{sure}] \ar' ⇔ ¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar')$.
-	\item Require (as an axiom) that $\ar' \ibeatse[\prop] \ar ∨ \ar' \nibeatse[\prop] \ar$. This yields $¬ (\ar' \ibeatsst[\prop] \ar ∧ \ar' \nibeatsst[\prop] \ar)$.
 \end{itemize}
 
-Define $T_i \subseteq \alltopic$ as the set of propositions that are weakly accepted.
+Define $\iposs \subseteq \alltopic$ as the set of propositions that are weakly accepted.
 \begin{definition}[Weak acceptance]
 	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$.
-A proposition $\prop \in \alltopic$ is weakly accepted, $\prop \in T_i$, iff $\exists \ar \in \allargs \suchthat \forall \ar' \in \allargs: \ar' \nibeatsst[\prop] \ar$.
+A proposition $\prop \in \alltopic$ is weakly accepted, $\prop \in \iposs$, iff $\exists \ar \in \allargs \suchthat \forall \ar' \in \allargs: \ar' \nibeatsst[\prop] \ar$.
 \end{definition}
-It follows that $¬\prop \notin T_i$ iff $\forall \ar: \exists \ar' \suchthat \ar' \ibeatse[¬\prop] \ar$.
+It follows that $¬\prop \notin \iposs$ iff $\forall \ar: \exists \ar' \suchthat \ar' \ibeatse[¬\prop] \ar$. Equivalently, $¬\prop \notin \iposs ⇔ \ibeatse[¬\prop](\allargs) = \allargs$.
 
-\begin{definition}[Strong rejection]
-	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$.
-A proposition $¬\prop \in \alltopic$ is strongly rejected iff $\forall \ar \in \allargs, \exists \ar' \in \allargs \suchthat \ar \nibeatsst[\prop, \text{sure}] \ar'$.
+\begin{definition}[Sure acceptance]
+	$¬\prop \in \isure$ iff $\exists \ar' \in \allargs \suchthat \forall \ar \in \allargs: \ar \nibeatsst[¬\prop, \text{sure}] \ar'$.\footnote{Instead of accepting $¬\prop$ for sure, it is tempting to define strong rejection of $t$ as follows.
+A proposition $\prop \in \alltopic$ is strongly rejected iff $\forall \ar_0 \in \allargs, \exists \ar' \in \allargs \suchthat \ar_0 \nibeatsst[¬\prop, \text{sure}] \ar'$.
+But this is too weak: we want $\ar'$ to be also decisive, thus $\ar \nibeatsst[¬\prop, \text{sure}] \ar', \forall \ar$.
+Hence the definition becomes $\exists \ar' \in \allargs \suchthat \ar \nibeatsst[¬\prop, \text{sure}] \ar'$.}
 \end{definition}
-Thus, strong rejection mandates $\ar'$ such that $\ar' \ibeatsst[¬\prop] \ar$.
+If $¬\prop \in \isure$, then $\prop \notin \iposs$: with $\ar' \in \args^{¬\prop, \text{sure}}$, given any $\ar$, $\ar' \ibeatse[\prop] \ar$ (because $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$, see A1).
 
-If $¬\prop$ is strongly rejected, then it is not weakly accepted ($¬\prop \notin T_i$) as $\ar' \ibeatsst[¬\prop] \ar ⇒ \ar' \ibeatse[¬\prop] \ar$.
+If $¬\prop \in \isure$, then $¬\prop \in \iposs$: from $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$ we obtain $\ar \nibeatsst[¬\prop] \ar'$ using A2.
 
 \begin{definition}[Clear-cut]
-	A situation is clear-cut iff $¬\prop \notin T_i ⇒ ¬\prop$ is strongly rejected.
+	A situation is clear-cut iff $\prop \notin \iposs ⇒ ¬\prop \in \isure$.
+\end{definition}
+Here is an example of a non clear-cut situation. $\allargs = \{\emptyset\}, \alltopic = \{\prop\}, \emptyset \ibeatse[\prop] \emptyset, \emptyset \ibeatse[¬\prop, \text{sure}] \emptyset$.
+
+\section{Models}
+$\mbeats$ an acyclic binary relation over $\allargs$ (by which we mean that its transitive closure is irreflexive).
+$\mleadsto \subseteq \allargs × \alltopic$.
+Define $\clargs \subseteq \allargs$ as the set of arguments used in $\mbeats ∪ \mleadsto$.
+Let $+$ be defined over arguments used in the model: $\ar_3 + \ar_1 = \ar'$ for some $\ar' \in \clargs$, for any $\ar_3, \ar_1 \in \clargs$.
+
+Requirements. The maximum length of a path in $\mbeats$ is finite.
+$\ar_3 \mbeats \ar_2 \mbeats \ar_1 ⇒ \ar_2 \mbeats \ar_3 + \ar_1$.\footnote{Necessary for definition of $\ar_3 \wibeatse \ar_2$.}
+
+Notation. Let $\mleadstoinv(\alltopic) \subseteq \clargs$ denote the subset of arguments supporting propositions. 
+$\mbeats(\ar_2)$: arguments that $\ar_2$ attacks, $\ar_1 \in \mbeats(\ar_2) ⇔ \ar_2 \mbeats \ar_1$.
+We write $\args \mbeats \ar$ to mean that $\forall \ar' \in \args: \ar' \mbeats \ar$, and similarly for other binary relations.
+
+Given a decision situation, define $\wibeatse \subseteq \mbeats$ as follows.
+
+Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ \ar_3 \ibeatse[\prop] \ar_2]$.
+
+Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \nwibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ \ar_2 \ibeatse[¬\prop, \text{sure}] \ar_3]$.
+\footnote{Check: Given $\ar_4 \mbeats \ar_3, \ar_3 \notin \mleadstoinv(\alltopic)$, with $\ar_2 \in \mbeats(\ar_3)$ ⇒ ($\ar_2$ and $\ar_4 + \ar_2$ $\mbeats$-attack only root nodes and do not support any proposition): $\ar_4 \wibeatse[\prop] \ar_3$ iff
+\begin{itemize}
+	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\ar_3 \wibeatse[\prop] \ar_2) ∧ (\ar_3 \nwibeatse[\prop] \ar_4 + \ar_2)]$ iff 
+	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_4 + \ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_4 + \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)]$ iff
+	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_1 \ileadsto t ∧ \ar_2 \ibeatse[\prop] \ar_1 ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ \ar_3 + \ar_1 \ibeatse[¬\prop, \text{sure}] \ar_2) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_1 \mleadsto \prop ∧ \ar_4 + \ar_2 \ibeatse[\prop] \ar_1 ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ \ar_4 + \ar_2 \ibeatse[\prop] \ar_3 + \ar_1)]$.
+\end{itemize}
+}
+
+TODO this is well-defined because associate to each $\ar \in \clargs$ $d(\ar)$, the distance to the farthest root (a root is an argument that $\mbeats$-attacks nobody).
+Then $\wibeatse$ is defined for all attacks from $d(.)=1$ nodes (because those nodes attack only $d(.)=0$ nodes), and thus is defined for all nodes $2$, I suppose, …
+
+Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop] \ar_1$, we have: $\ar_3 \wibeatse[\prop] \ar_2 ∨ \ar_3 \nwibeatse[\prop] \ar_2$.
+
+Define $\ar_2 \wibeatse \ar_1 ⇔ \exists \prop \in \alltopic \suchthat \ar_2 \wibeatse[\prop] \ar_1$.
+
+Define $\wibeatsst = ¬\nwibeatse$. Define $\nwibeatsst = ¬\wibeatse$.
+
+Hence, given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic)$: $\ar_3 \wibeatsst \ar_2$ iff $\forall \ar_1 \in \mbeats(\ar_2) ∩ \wibeatse(\ar_2): \ar_2 \nwibeatsst \ar_3 + \ar_1$.
+
+\subsection{Certainties}
+Assume we define $\ar_1 \wibeatse[¬\prop, \text{sure}] \ar_2$ ⇔ $\ar_2 \nwibeatse[\prop] \ar_1$.
+Then, indeed, given $\ar_1 \mleadsto \prop$, $\ar_2 \wibeatse[¬\prop, \text{sure}] \ar_1$ ⇔ $\ar_2 \ibeatse[¬\prop, \text{sure}] \ar_1$.
+But it gives the wrong conclusion.
+For $\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto t: \ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\ar_2 \nwibeatse[¬\prop] \ar_3$ iff $\exists \ar_1 \in \mbeats(\ar_3) \suchthat \ar_3 \wibeatse[¬\prop] \ar_1 ∧ \ar_3 \wibeatse[¬\prop] \ar_2 + \ar_1$.
+
+Given $\ar_1 \mleadsto \prop$, define $\ar_2 \wibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_2 \ibeatse[\prop, \text{sure}] \ar_1$.
+
+Given $\ar_1 \mleadsto \prop$, define $\ar_2 \nwibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_1 \ibeatse[¬\prop] \ar_2$.
+
+Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \nwibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.
+
+Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \nwibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \wibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.
+
+\section{Conditions}
+All these conditions assume that a decision situation $(\allalts, \allargs, \{\ibeatse[\prop]\})$ and a model $\eta = (\mbeats, \mleadsto, +)$ are given.
+
+Define $\argsdec = \clargs \setminus \text{im}(\wibeatse)$ the decisive arguments according to $\wibeatse$, or $\wibeatse$-decisive arguments for short: $\ar \in \argsdec ⇔ \wibeatseinv(\ar) = \emptyset$.
+
+\begin{definition}[Reinstatement]
+	Given $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3 \in \argsdec$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
+	\footnote{TODO the condition must be $\wibeatseinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$ to allow $\ar_5 \mbeats \ar_4 \mbeats \ar_3 \mbeats \ar_2 \mbeats \ar_1$ and $\ar_5 \mbeats \ar_4 \mbeats \ar_3 + \ar_1$, considering that possibly $\ar_3$ is $\wibeatse$-decisive.
+This should not invalidate the conditions, but it does currently.
+But it’s not a problem: the model would actually not be built this way.
+In this scenario the argument $\ar_3 + \ar_1$ is useful only in case $\ar_3$ is decisive, thus $\ar_4 \mbeats \ar_3 + \ar_1$ must not be planned.
+Rather $\ar_5 + \ar_3$ decisive, then $(\ar_5 + \ar_3) + \ar_1$.
+Alternatively, also $\ar_4 \mbeats \ar_1$ and then no problem as well.}
+\footnote{The stronger condition mandating $\mbeatsinv(\ar_3 + \ar_1) \subseteq \wibeatseinv(\ar_1) \setminus \mbeats(\ar_3)$ would be more difficult to check: when some $\ar_2 \wibeatse \ar_3 + \ar_1$, we’d need to check not only that $\ar_2 \mbeats \ar_1$ but also $\ar_2 \wibeatse \ar_1$.}
 \end{definition}
 
-First, we want that if situation is CC, 1) exists a valid model, 2) any valid model has the right $T_i$.
-A model is valid if: a) can correctly get reinstatement; b) i is justifiably unstable; c) finite arguments; d) model is convincing.
+\begin{definition}[Justifiable unstability]
+	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse \ar_1, \ar_2 \nwibeatse \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse \ar_2$.
+\end{definition}
 
-Second, we want that given a situation, if there exists a valid model, then the situation is CC.
+\begin{definition}[Finite defense]
+	If $\wibeatseinv(\ar) \subseteq \wibeatse(\argsdec)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse(\args)$.
+\footnote{Define Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec as: $\wibeatseinv(\ar) \subseteq \wibeatse(\clargs \setminus \text{im}(\mbeats)) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args)$.
+Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is insufficient to provide $T_\eta = \iposs$.
+Define $\ar' \mbeats^\text{fail} \ar$ iff $\ar' \mbeats \ar ∧ ¬(\ar' \wibeatse \ar)$.
+Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_4 \mbeats^\text{fail} \{\ar_3, \ar_3', …\}$.
+Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is artificially satisfied because the antecedent fails to trigger.}
+\footnote{Define Finite defense-$\wibeatse$-$\wibeatse$-subsets as: $\wibeatseinv(\ar) \subseteq \wibeatse(\args) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args')$.
+Finite defense-$\wibeatse$-$\wibeatse$-subsets is insufficient to provide $T_\eta = \iposs$.
+This is because Reinstatement allows for new attacks in $\wibeatse$ (it only forbids new attacks in $\mbeats$), thus we can forever transform previously failing attacks to new attacks, hence always satisfying Finite defense (always finite cover of $\wibeatse$, but infinite cover of $\mbeats$) but still not converging.
+Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3' \wibeatse \ar_2' \mbeats^\text{fail} \ar_1$, and so on; and $\ar_3' \wibeatse \ar_2' \wibeatse \ar_3 + \ar_1, \ar_3'' \wibeatse \ar_2'' \mbeats^\text{fail} \ar_3 + \ar_1$, and so on.}
+\footnote{Define Finite defense-$\mbeats$-$\wibeatse$-startdec as: $\mbeatsinv(\ar) \subseteq \wibeatse(\argsdec) ⇒ \mbeatsinv(\ar) \subseteq \wibeatse(\args)$.
+Finite defense-$\mbeats$-$\wibeatse$-startdec is insufficient to provide $T_\eta = \iposs$.
+Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_5 \mbeats^\text{fail} \ar_4 \mbeats^\text{fail} \ar_1$.
+Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\mbeats$-$\wibeatse$-startdec is satisfied as there is no cover of the $\mbeats$ attacks to $\ar_1$.}
+\footnote{Define Finite defense-$\mbeats$-$\mbeats$-startdec as: $\mbeatsinv(\ar) \subseteq \mbeats(\argsdec) ⇒ \mbeatsinv(\ar) \subseteq \mbeats(\args)$.
+Finite defense-$\mbeats$-$\mbeats$-startdec is insufficient to provide $T_\eta = \iposs$.
+Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar \mbeats^\text{fail} \{\ar_2, \ar_2', …\}$.
+Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\mbeats$-$\mbeats$-startdec is artificially satisfied because of $\ar$.
+Define Finite defense-$\mbeats$-$\mbeats$-subsets as: $\mbeatsinv(\ar) \subseteq \mbeats(\args) ⇒ \mbeatsinv(\ar) \subseteq \mbeats(\args')$ (for any $\args \subseteq \argsdec$).
+Finite defense-$\mbeats$-$\mbeats$-subsets is (rightly) non satisfied in this example.}
+\footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check).
+But it may be interesting to not limit it and declare that the model has specific replies to any counter-argument, but promises to use only a few rebuttals and that afterwards, the dm will stop using those kind of arguments (but we don’t know in advance which ones will be chosen).}
+\footnote{Define Finite defense-$\wibeatse$-$\wibeatse$-subsets as: $\wibeatseinv(\ar) \subseteq \wibeatse(\args) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args')$.
+Finite defense-$\mbeats$-$\wibeatse$-subsets $⇏$ Finite defense-$\wibeatse$-$\wibeatse$-subsets.
+Consider $\ar_2 \mbeats^\text{fail} \ar_1$ (to be continued…)}
+\end{definition}
+Thus, if the attackers of $\ar$ are attacked by decisive arguments, then $j$ defenders are enough to defend $\ar$.
 
-Third, perhaps we get as a bonus that there exists a valid model ⇔ the situation is CC3. CC1: ¬p not in wa ⇔ ¬p s rej. CC2: ¬p s rej ⇒ p w acc. CC3: ¬p s rej ⇒ p is sure.
-
-\section{Models}
-$\mbeats$ a (possibly infinite!) DAG over $(s, p)$ pairs, $+$ defined over arguments in $\mbeats$: $(\ar_1, \prop) + (\ar_3, \prop) = (\ar', \prop)$ for some $(\ar', \prop) \in \mbeats$.
-Define $D' \subseteq \clargs$ as a subset of arguments (those supporting propositions).
-Define $\clargs \subseteq \allargs$ as the set of arguments used in $\mbeats$.
-Assume it can be represented by $≥$, a weak order defined on the basis of $\mbeats$, defining at most $k$ equivalence classes, so that our recursive definitions make sense.
-(TODO make this correct and precise.)
-
-$\mbeats(\ar_2)$: arguments that $\ar_2$ attacks, $\ar_1 \in \mbeats(\ar_2) ⇔ \ar_2 \mbeats \ar_1$.
-
-Given $\ar_1 \in D'$, define $\ar_2 \wibeatse \ar_1$ iff $\ar_2 \ibeatse \ar_1$.
-
-Given $\ar_1 \in D'$, define $\ar_2 \nwibeatse \ar_1$ iff $\ar_1 \ibeatse[\text{sure}] \ar_2$.
-
-Define $\ar_1 \wibeatse[\text{sure}] \ar_2$ ⇔ $\ar_2 \nwibeatse \ar_1$.
-
-$\ar_1$ root in $\mbeats$ $⇒$ $\ar_1 \in D'$. $\ar_1 \in D' ⇒ \ar_3 + \ar_1 \in D'$.
-
-Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin D'$: $\ar_3 \wibeatse \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse \ar_1 ∧ \ar_2 \nwibeatse \ar_3 + \ar_1$.
-
-Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin D'$: $\ar_3 \nwibeatse \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse \ar_1 ∧ \ar_2 \wibeatse \ar_3 + \ar_1$.
-
-Check: For $\ar_4, \ar_3, \ar_3 \notin D'$: $\ar_4 \wibeatse \ar_3$ iff $\exists \ar_2 \suchthat  \ar_3 \wibeatse \ar_2 ∧ \ar_3 \nwibeatse \ar_4 + \ar_2$.
-Thus, $\exists \ar_2 \suchthat  \ar_3 \wibeatse \ar_2 ∧ \exists \ar_1 \suchthat (\ar_4 + \ar_2) \wibeatse \ar_1 ∧ (\ar_4 + \ar_2) \wibeatse \ar_3 + \ar_1$.
-
-Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse \ar_1$, we have: $\ar_3 \wibeatse \ar_2 ∨ \ar_3 \nwibeatse \ar_2$.
-
-Define $\wibeatsst = ¬\nwibeatse$. Hence, $¬(\ar \wibeatse[\text{sure}] \ar') ⇔ \ar \nwibeatsst[\text{sure}] \ar' ⇔ ¬(\ar' \nwibeatse \ar) ⇔ \ar' \wibeatsst \ar$.
-
-Define $\nwibeatsst = ¬\wibeatse$.
-
-Hence, given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin D'$: $\ar_3 \wibeatsst \ar_2$ iff $\forall \ar_1 \in \mbeats(\ar_2) ∩ \wibeatse(\ar_2): \ar_2 \nwibeatsst \ar_3 + \ar_1$.
-
-\section{Conditions}
-\begin{definition}[Reinstatement]
-	Given a model $\mu = (\mbeats, D')$ and a decision situation $(\allalts, \allargs, \ibeatse)$, given $\ar_1 \in D', \ar_2 \mbeats \ar_1, \ar_2 \wibeatse \ar_1, \ar_3 \wibeatse \ar_2, \mbeatsinv(\ar_3) = \emptyset$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_1 + \ar_3) ∧ \mbeatsinv(\ar_1 + \ar_3) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
+Define $R$, the reinstates relation, as follows: $\ar_3 R \ar_1$ iff $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$ (for some $\ar_2$), $\ar_3 \in \argsdec$.
+Define $\gdargs$ as the transitive closure of $\mleadstoinv(\alltopic)$ under $R$.
+\begin{definition}[Covering]
+	$\forall \ar \in \gdargs, \ar' \in \allargs: \ar' \ibeatse \ar ⇒ \ar' \mbeats \ar$. \footnote{Specify $\ibeatse$.}
 \end{definition}
@@
 \begin{definition}[Observable validity]
-	Given as above, the model is observably valid iff $\forall \ar_2 \mbeats \ar: ¬(\ar_2 \wibeatse \ar) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse \ar_2$.
+	$\forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$.
+Furthermore, if $¬(\clargs \mleadsto ¬\prop), \forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop, \text{sure}] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop, \text{sure}] \ar_2$.
 \end{definition}
 
-\begin{definition}[Justifiable unstability]
-	Given as above…
-\end{definition}
+\section{Example}
+The general conditions are Reinstatement, Justifiable unstability, Finite defense and Covering.
+A general model is a model that claims it satisfies the general conditions.
+
+TODO give up general models.
+In this example, $\ar_1$ would need to be planned as attacking sometimes $\ar_2$.
+Better consider an instanciation mechanism.
+An instantiated model is particular, and can be tested (especially against another one).
+\begin{example}
+	$\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto \prop$, $\ar_2 \mleadsto ¬\prop$; $\ar_3 + \ar_1 \mleadsto \prop$.
+\end{example}
+This model is compatible (meaning that it satisfies the general conditions) with the following decision situations. We describe $\ibeatse$ fully (no attack iff not mentioned).
+\begin{itemize}
+	\item Sure of $\prop$: $\ar_1 \mleadsto \prop$; $\ar_3 \ibeatse \ar_2$ (the rest is implied, for example $\forall \ar_4 \in \allargs: \ar_1 \ibeatse[¬\prop] \ar_4$ because of covering).
+	\item Sure of $\prop$ with reinstatement: $\ar_3 \ibeatse[\prop] \ar_2 \ibeatse[\prop] \ar_1 \mleadsto \prop$; $\ar_1 + \ar_3 \mleadsto \prop$; $\ar_3 \ibeatse[¬\prop] \ar_2$
+	\item Sure of $¬\prop$: $\ar_2 \mleadsto ¬\prop$; $\ar_2 \ibeatse \ar_1$
+	\item Both: $¬(\ar_2 \ibeatse \ar_1), \ar_1 \mleadsto \prop$, $¬(\ar_3 \ibeatse \ar_2), \ar_2 \mleadsto ¬\prop$
+\end{itemize}
+This situation falsifies the model. $\ar_4 \ibeatse \ar_1$, $\ar_4$ not attacked.
+
+\section{Theorem}
+\subsection{Main}
+\begin{theorem}[Validity]
+	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iposs$.
+\end{theorem}
+\begin{proof}
+Define $\wibeatse^\text{ext} \subseteq \allargs × \allargs$ as: $\ar' \wibeatse^\text{ext} \ar$ iff $\ar' \wibeatse \ar ∨ (\ar \in \mleadstoinv ∧ \ar' \ibeatse \ar)$.
+
+$\ar$ is defended iff its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments.
+Sketch:
+\begin{enumerate}
+	\item $\ar_1$ defended implies $\ar_1$ replaceable by some $\wibeatse$-decisive $\ar$
+	\item $\ar_1$ has its $\wibeatse$-attackers $\wibeatse$-attacked by defended arguments implies $\ar_1$ defended
+	\item Hence, $\ar_1$ has its $\wibeatse$-attackers $\wibeatse$-attacked by defended arguments implies $\ar_1$ replaceable by $\wibeatse$-decisive
+	\item If $\ar_1$ is not defended, it is $\wibeatse$-attacked by no $\ar_2$ decisive [Obs valid], hence, $\ar_1$ is attacked by no $\ar_2$ defended (otherwise there would be a decisive attacker).
+TODO clarify how we take into account attacks from outside of $\wibeatse$ (simply $\ibeatse$) coming from arguments out of $\clargs$.
+	\item If $\ar_1$ is not defended, it is attacked by some $\ar_2$ attacked by no $\ar_3$ decisive (otherwise, $\ar_1$ defended).
+	\item Hence, if $\ar_1$ is not defended, it is attacked by some $\ar_2$ not defended, itself attacked by no $\ar_3$ decisive. And we can hopefully recurse.
+	\item In short: $\ar_1$ not defended by dec, attacked by some $\ar_2$ not defended by dec, implies $\ar_2$ attacked by some $\ar_3$ not defended by decisive.
+\end{enumerate}
+First, we want to prove that $\ar_1$ defended implies $\ar_1$ replaceable by some $\wibeatse$-decisive $\ar$, and if $\ar_1 \in \gdargs$, then its replacer $\ar$ is in $\gdargs$ as well.
+
+By hypothesis, $\wibeatseinv(\ar_1) \subseteq \wibeatse(\argsdec)$. Thus, $\exists \args \subseteq \argsdec \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse(\args)$, $\args$ finite [Finite defense].
+
+Pick any $\ar_{3, 1} \in \args$ such that $\ar_{3, 1} \wibeatse \ar_2 \wibeatse \ar_1$ (if there’s none, $\ar_1 \in \argsdec$ and we’re done).
+$\ar_{3, 1} + \ar_1$ replaces $\ar_1$, and $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_{3, 1})$ [Reinstatement].
+Hence, $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \wibeatse(\args) \setminus \mbeats(\ar_{3, 1})$.
+Iterate by picking any $\ar_{3, 2} \in \args$ such that $\ar_{3, 2} \wibeatse \ar_2 \wibeatse \ar_{3, 1} + \ar_1$ (if there’s none, $\ar_{3, 1} + \ar_1 \in \argsdec$ and we’re done) and obtaining $\ar_{3, 2} + (\ar_{3, 1} + \ar_1)$ replacing $\ar_{3, 1} + \ar_1$ (hence, replacing $\ar_1$) with $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \mbeatsinv(\ar_{3, 1} + \ar_1) \setminus \mbeats(\ar_{3, 2})$.
+Hence, $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \wibeatse(\args) \setminus \mbeats(\ar_{3, 1}) \setminus \mbeats(\ar_{3, 2})$.
+Iterating in such a way over the finite set $\args$ will finally yield an element that is $\wibeatse$-decisive.
+The last point, $\ar_1 \in \gdargs ⇒ \ar \in \gdargs$, follows from the definition of $\gdargs$.
+
+Second, we want to prove that if $\ar_1$ not defended and has no decisive $\wibeatse$-attackers (meaning that $\wibeatseinv(\ar_1) \subseteq \overline{\argsdec}$), then $\ar_1$ is $\wibeatse$-attacked by some $\ar_2$ that is not defended and has no decisive $\wibeatse$-attacker.
+
+Consider $\ar_1$ not defended and having no decisive $\wibeatse$-attackers.
+Because $\ar_1$ is not defended, by definition, it is $\wibeatse$-attacked by some $\ar_2$ that has no decisive $\wibeatse$-attacker.
+Because $\ar_1$ has no decisive attacker, $\ar_2$ is not decisive.
+If $\ar_2$ was defended, by the first part of this proof, it would be replaceable by a decisive argument, and $\ar_1$ would have a decisive attacker.
+Thus, $\ar_2$ is not defended.
+
+TODO do not mandate that $\ar_3 + \ar_1 \ileadsto \prop$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice).
+We obtain that some argument exists that support $\prop$, but not necessarily one that the model claims supports it.
+We need: Obs applies to restricted supports (one per prop decided by model); Covering applies to extended supports (restricted supports plus those obtained by reinstatement).
+Replacement-1 applies to all and requires attack at least as large; Replacement-2 applies to restricted supports and requires no new $\ibeatse$-attacks.
+
+Third, consider an argument $\ar_1 \in \mleadstoinv(\alltopic)$.
+It has no decisive $\ibeatse$-attacker: as $\ar_1 \in \gdargs$, any $\ibeatse$-attack is a $\wibeatse$-attack [Covering], and $\ar_1$ has no decisive $\wibeatse$-attacker [Obs val].
+Also, $\ar_1$ is defended: assume it is not, then by our second point in this proof some $\ar_2 \wibeatse \ar_1$, with $\ar_2$ not defended and with no decisive $\wibeatse$-attacker, and iterating and using finiteness of $\wibeatse$ leads to a contradiction.
+Hence, by our first point in this proof, $\ar_1$ is replaceable by some $\wibeatse$-decisive $\ar \in \gdargs$.
+As $\ar \in \gdargs$, any $\ibeatse$-attack is a $\wibeatse$-attack [Covering], thus $\ar$ is $\ibeatse$-decisive.
+\end{proof}
+
+\subsection{Bonus}
+A model $\eta' = (\mbeats', \mleadsto', +')$ particularizes a model $\eta = (\mbeats, \mleadsto, +)$ iff $\mbeats' = \mbeats, \mleadsto' \subseteq \mleadsto, +' = +$.
+\begin{theorem}[Instanciation]
+	Given a decision situation and a model $\eta$ and a model particularization $\eta'$, if $\eta$ satisfies the general conditions, then $\eta'$ satisfies the general conditions.
+\end{theorem}
 
@@
 \section{To think}
-Propositions weakly self-supported $\topic \subseteq \alltopic$: weakly accepted if no arg is given.
+Propositions weakly self-supported $T \subseteq \alltopic$: weakly accepted if no arg is given.
 Examples: $m$ = “eat miam”; $¬b$ = “beurk is to exclude”; or, in a problem where there’s no particularly good aliments, both $a$ = “eat this” and $¬a$.

### 2017-11-02 article.tex
Removed bonus theorem about model instanciation
Moved example in appendix

@@
 
-\section{Example}
-The general conditions are Reinstatement, Justifiable unstability, Finite defense and Covering.
-A general model is a model that claims it satisfies the general conditions.
-
-TODO give up general models.
-In this example, $\ar_1$ would need to be planned as attacking sometimes $\ar_2$.
-Better consider an instanciation mechanism.
-An instantiated model is particular, and can be tested (especially against another one).
-\begin{example}
-	$\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto \prop$, $\ar_2 \mleadsto ¬\prop$; $\ar_3 + \ar_1 \mleadsto \prop$.
-\end{example}
-This model is compatible (meaning that it satisfies the general conditions) with the following decision situations. We describe $\ibeatse$ fully (no attack iff not mentioned).
-\begin{itemize}
-	\item Sure of $\prop$: $\ar_1 \mleadsto \prop$; $\ar_3 \ibeatse \ar_2$ (the rest is implied, for example $\forall \ar_4 \in \allargs: \ar_1 \ibeatse[¬\prop] \ar_4$ because of covering).
-	\item Sure of $\prop$ with reinstatement: $\ar_3 \ibeatse[\prop] \ar_2 \ibeatse[\prop] \ar_1 \mleadsto \prop$; $\ar_1 + \ar_3 \mleadsto \prop$; $\ar_3 \ibeatse[¬\prop] \ar_2$
-	\item Sure of $¬\prop$: $\ar_2 \mleadsto ¬\prop$; $\ar_2 \ibeatse \ar_1$
-	\item Both: $¬(\ar_2 \ibeatse \ar_1), \ar_1 \mleadsto \prop$, $¬(\ar_3 \ibeatse \ar_2), \ar_2 \mleadsto ¬\prop$
-\end{itemize}
-This situation falsifies the model. $\ar_4 \ibeatse \ar_1$, $\ar_4$ not attacked.
-
 \section{Theorem}
-\subsection{Main}
 \begin{theorem}[Validity]
@@
 \end{proof}
-
-\subsection{Bonus}
-A model $\eta' = (\mbeats', \mleadsto', +')$ particularizes a model $\eta = (\mbeats, \mleadsto, +)$ iff $\mbeats' = \mbeats, \mleadsto' \subseteq \mleadsto, +' = +$.
-\begin{theorem}[Instanciation]
-	Given a decision situation and a model $\eta$ and a model particularization $\eta'$, if $\eta$ satisfies the general conditions, then $\eta'$ satisfies the general conditions.
-\end{theorem}
 
@@
 
-\section{Example}
+\section{Example about model instanciation}
+The general conditions are Reinstatement, Justifiable unstability, Finite defense and Covering.
+A general model is a model that claims it satisfies the general conditions.
+
+TODO give up general models.
+In this example, $\ar_1$ would need to be planned as attacking sometimes $\ar_2$.
+Better consider an instanciation mechanism.
+An instantiated model is particular, and can be tested (especially against another one).
+\begin{example}
+	$\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto \prop$, $\ar_2 \mleadsto ¬\prop$; $\ar_3 + \ar_1 \mleadsto \prop$.
+\end{example}
+This model is compatible (meaning that it satisfies the general conditions) with the following decision situations. We describe $\ibeatse$ fully (no attack iff not mentioned).
+\begin{itemize}
+	\item Sure of $\prop$: $\ar_1 \mleadsto \prop$; $\ar_3 \ibeatse \ar_2$ (the rest is implied, for example $\forall \ar_4 \in \allargs: \ar_1 \ibeatse[¬\prop] \ar_4$ because of covering).
+	\item Sure of $\prop$ with reinstatement: $\ar_3 \ibeatse[\prop] \ar_2 \ibeatse[\prop] \ar_1 \mleadsto \prop$; $\ar_1 + \ar_3 \mleadsto \prop$; $\ar_3 \ibeatse[¬\prop] \ar_2$
+	\item Sure of $¬\prop$: $\ar_2 \mleadsto ¬\prop$; $\ar_2 \ibeatse \ar_1$
+	\item Both: $¬(\ar_2 \ibeatse \ar_1), \ar_1 \mleadsto \prop$, $¬(\ar_3 \ibeatse \ar_2), \ar_2 \mleadsto ¬\prop$
+\end{itemize}
+This situation falsifies the model. $\ar_4 \ibeatse \ar_1$, $\ar_4$ not attacked.
+
+\section{Example about default arguments}
 s2 argues in favor of p against s1: s "le monde n’est pas fiable".

### 2017-11-02 article.tex
Start thm about isure
Removed proof sketch

@@
 Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ \ar_3 \ibeatse[\prop] \ar_2]$.
+\footnote{Or $\ar_2 \ileadsto \prop ∧ ¬\prop \notin \mleadsto(\allargs) ∧ \ar_3 \ibeatse[\prop, \text{sure}] \ar_2$.}
 
@@
 	$\forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$.
-Furthermore, if $¬(\clargs \mleadsto ¬\prop), \forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop, \text{sure}] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop, \text{sure}] \ar_2$.
+Furthermore, if $¬(\clargs \mleadsto \prop), \forall \ar_1 \mleadsto ¬\prop, \ar \in \allargs: \ar_1 \ibeatse[\prop] \ar$.
+	\footnote{If the model claims $¬\prop \in \isure$, this requires clear-cut (for that prop), so we must mandate it (hopefully A3 or an equivalent such as Justifiable unstability fits).
+Thus we only need to prove $\prop \notin \iposs$, for which $\ar_1 \ibeatse[\prop] \ar$ suffices.}
 \end{definition}
@@
 	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iposs$.
+Furthermore, if $¬\prop \in \mleadsto(\clargs) ∧ \prop \notin \mleadstoinv(\clargs)$, $¬\prop \in \isure$.
 \end{theorem}
 \begin{proof}
-Define $\wibeatse^\text{ext} \subseteq \allargs × \allargs$ as: $\ar' \wibeatse^\text{ext} \ar$ iff $\ar' \wibeatse \ar ∨ (\ar \in \mleadstoinv ∧ \ar' \ibeatse \ar)$.
+$\ar$ is defended iff its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments.
 
-$\ar$ is defended iff its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments.
-Sketch:
-\begin{enumerate}
-	\item $\ar_1$ defended implies $\ar_1$ replaceable by some $\wibeatse$-decisive $\ar$
-	\item $\ar_1$ has its $\wibeatse$-attackers $\wibeatse$-attacked by defended arguments implies $\ar_1$ defended
-	\item Hence, $\ar_1$ has its $\wibeatse$-attackers $\wibeatse$-attacked by defended arguments implies $\ar_1$ replaceable by $\wibeatse$-decisive
-	\item If $\ar_1$ is not defended, it is $\wibeatse$-attacked by no $\ar_2$ decisive [Obs valid], hence, $\ar_1$ is attacked by no $\ar_2$ defended (otherwise there would be a decisive attacker).
-TODO clarify how we take into account attacks from outside of $\wibeatse$ (simply $\ibeatse$) coming from arguments out of $\clargs$.
-	\item If $\ar_1$ is not defended, it is attacked by some $\ar_2$ attacked by no $\ar_3$ decisive (otherwise, $\ar_1$ defended).
-	\item Hence, if $\ar_1$ is not defended, it is attacked by some $\ar_2$ not defended, itself attacked by no $\ar_3$ decisive. And we can hopefully recurse.
-	\item In short: $\ar_1$ not defended by dec, attacked by some $\ar_2$ not defended by dec, implies $\ar_2$ attacked by some $\ar_3$ not defended by decisive.
-\end{enumerate}
 First, we want to prove that $\ar_1$ defended implies $\ar_1$ replaceable by some $\wibeatse$-decisive $\ar$, and if $\ar_1 \in \gdargs$, then its replacer $\ar$ is in $\gdargs$ as well.

### 2017-11-02 article.tex
Moved footnotes alternative definitions of Finite defense in appendix

@@
 	\footnote{The stronger condition mandating $\mbeatsinv(\ar_3 + \ar_1) \subseteq \wibeatseinv(\ar_1) \setminus \mbeats(\ar_3)$ would be more difficult to check: when some $\ar_2 \wibeatse \ar_3 + \ar_1$, we’d need to check not only that $\ar_2 \mbeats \ar_1$ but also $\ar_2 \wibeatse \ar_1$.}
+	\footnote{We do not mandate that $\ar_3 + \ar_1 \ileadsto \prop$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice).
+We need: Obs applies to restricted supports (one per prop decided by model); Covering applies to extended supports (restricted supports plus those obtained by reinstatement).
+Replacement-1 applies to all and requires attack at least as large; Replacement-2 applies to restricted supports and requires no new $\ibeatse$-attacks.}
 \end{definition}
@@
 	If $\wibeatseinv(\ar) \subseteq \wibeatse(\argsdec)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse(\args)$.
-\footnote{Define Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec as: $\wibeatseinv(\ar) \subseteq \wibeatse(\clargs \setminus \text{im}(\mbeats)) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args)$.
-Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is insufficient to provide $T_\eta = \iposs$.
-Define $\ar' \mbeats^\text{fail} \ar$ iff $\ar' \mbeats \ar ∧ ¬(\ar' \wibeatse \ar)$.
-Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_4 \mbeats^\text{fail} \{\ar_3, \ar_3', …\}$.
-Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is artificially satisfied because the antecedent fails to trigger.}
-\footnote{Define Finite defense-$\wibeatse$-$\wibeatse$-subsets as: $\wibeatseinv(\ar) \subseteq \wibeatse(\args) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args')$.
-Finite defense-$\wibeatse$-$\wibeatse$-subsets is insufficient to provide $T_\eta = \iposs$.
-This is because Reinstatement allows for new attacks in $\wibeatse$ (it only forbids new attacks in $\mbeats$), thus we can forever transform previously failing attacks to new attacks, hence always satisfying Finite defense (always finite cover of $\wibeatse$, but infinite cover of $\mbeats$) but still not converging.
-Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3' \wibeatse \ar_2' \mbeats^\text{fail} \ar_1$, and so on; and $\ar_3' \wibeatse \ar_2' \wibeatse \ar_3 + \ar_1, \ar_3'' \wibeatse \ar_2'' \mbeats^\text{fail} \ar_3 + \ar_1$, and so on.}
-\footnote{Define Finite defense-$\mbeats$-$\wibeatse$-startdec as: $\mbeatsinv(\ar) \subseteq \wibeatse(\argsdec) ⇒ \mbeatsinv(\ar) \subseteq \wibeatse(\args)$.
-Finite defense-$\mbeats$-$\wibeatse$-startdec is insufficient to provide $T_\eta = \iposs$.
-Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_5 \mbeats^\text{fail} \ar_4 \mbeats^\text{fail} \ar_1$.
-Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\mbeats$-$\wibeatse$-startdec is satisfied as there is no cover of the $\mbeats$ attacks to $\ar_1$.}
-\footnote{Define Finite defense-$\mbeats$-$\mbeats$-startdec as: $\mbeatsinv(\ar) \subseteq \mbeats(\argsdec) ⇒ \mbeatsinv(\ar) \subseteq \mbeats(\args)$.
-Finite defense-$\mbeats$-$\mbeats$-startdec is insufficient to provide $T_\eta = \iposs$.
-Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar \mbeats^\text{fail} \{\ar_2, \ar_2', …\}$.
-Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\mbeats$-$\mbeats$-startdec is artificially satisfied because of $\ar$.
-Define Finite defense-$\mbeats$-$\mbeats$-subsets as: $\mbeatsinv(\ar) \subseteq \mbeats(\args) ⇒ \mbeatsinv(\ar) \subseteq \mbeats(\args')$ (for any $\args \subseteq \argsdec$).
-Finite defense-$\mbeats$-$\mbeats$-subsets is (rightly) non satisfied in this example.}
 \footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check).
 But it may be interesting to not limit it and declare that the model has specific replies to any counter-argument, but promises to use only a few rebuttals and that afterwards, the dm will stop using those kind of arguments (but we don’t know in advance which ones will be chosen).}
-\footnote{Define Finite defense-$\wibeatse$-$\wibeatse$-subsets as: $\wibeatseinv(\ar) \subseteq \wibeatse(\args) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args')$.
-Finite defense-$\mbeats$-$\wibeatse$-subsets $⇏$ Finite defense-$\wibeatse$-$\wibeatse$-subsets.
-Consider $\ar_2 \mbeats^\text{fail} \ar_1$ (to be continued…)}
 \end{definition}
@@
 Thus, $\ar_2$ is not defended.
-
-TODO do not mandate that $\ar_3 + \ar_1 \ileadsto \prop$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice).
-We obtain that some argument exists that support $\prop$, but not necessarily one that the model claims supports it.
-We need: Obs applies to restricted supports (one per prop decided by model); Covering applies to extended supports (restricted supports plus those obtained by reinstatement).
-Replacement-1 applies to all and requires attack at least as large; Replacement-2 applies to restricted supports and requires no new $\ibeatse$-attacks.
 
@@
 
+\section{Alternative definitions of finite defense}
+Define Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec as: $\wibeatseinv(\ar) \subseteq \wibeatse(\clargs \setminus \text{im}(\mbeats)) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args)$.
+Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is insufficient to provide $T_\eta = \iposs$.
+Define $\ar' \mbeats^\text{fail} \ar$ iff $\ar' \mbeats \ar ∧ ¬(\ar' \wibeatse \ar)$.
+Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_4 \mbeats^\text{fail} \{\ar_3, \ar_3', …\}$.
+Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is artificially satisfied because the antecedent fails to trigger.
+
+Define Finite defense-$\wibeatse$-$\wibeatse$-subsets as: $\wibeatseinv(\ar) \subseteq \wibeatse(\args) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args')$.
+Finite defense-$\wibeatse$-$\wibeatse$-subsets is insufficient to provide $T_\eta = \iposs$.
+This is because Reinstatement allows for new attacks in $\wibeatse$ (it only forbids new attacks in $\mbeats$), thus we can forever transform previously failing attacks to new attacks, hence always satisfying Finite defense (always finite cover of $\wibeatse$, but infinite cover of $\mbeats$) but still not converging.
+Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3' \wibeatse \ar_2' \mbeats^\text{fail} \ar_1$, and so on; and $\ar_3' \wibeatse \ar_2' \wibeatse \ar_3 + \ar_1, \ar_3'' \wibeatse \ar_2'' \mbeats^\text{fail} \ar_3 + \ar_1$, and so on.
+
+Define Finite defense-$\mbeats$-$\wibeatse$-startdec as: $\mbeatsinv(\ar) \subseteq \wibeatse(\argsdec) ⇒ \mbeatsinv(\ar) \subseteq \wibeatse(\args)$.
+Finite defense-$\mbeats$-$\wibeatse$-startdec is insufficient to provide $T_\eta = \iposs$.
+Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_5 \mbeats^\text{fail} \ar_4 \mbeats^\text{fail} \ar_1$.
+Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\mbeats$-$\wibeatse$-startdec is satisfied as there is no cover of the $\mbeats$ attacks to $\ar_1$.
+
+Define Finite defense-$\mbeats$-$\mbeats$-startdec as: $\mbeatsinv(\ar) \subseteq \mbeats(\argsdec) ⇒ \mbeatsinv(\ar) \subseteq \mbeats(\args)$.
+Finite defense-$\mbeats$-$\mbeats$-startdec is insufficient to provide $T_\eta = \iposs$.
+Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar \mbeats^\text{fail} \{\ar_2, \ar_2', …\}$.
+Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\mbeats$-$\mbeats$-startdec is artificially satisfied because of $\ar$.
+Define Finite defense-$\mbeats$-$\mbeats$-subsets as: $\mbeatsinv(\ar) \subseteq \mbeats(\args) ⇒ \mbeatsinv(\ar) \subseteq \mbeats(\args')$ (for any $\args \subseteq \argsdec$).
+Finite defense-$\mbeats$-$\mbeats$-subsets is (rightly) non satisfied in this example.
+
+Define Finite defense-$\wibeatse$-$\wibeatse$-subsets as: $\wibeatseinv(\ar) \subseteq \wibeatse(\args) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args')$.
+Finite defense-$\mbeats$-$\wibeatse$-subsets $⇏$ Finite defense-$\wibeatse$-$\wibeatse$-subsets.
+Consider $\ar_2 \mbeats^\text{fail} \ar_1$ (to be continued…)
+
 %\bibliography{mybib}

### 2017-11-02 article.tex
Moved model certainties in appendix
Some cleanup in text

@@
 
-\section{Overview}
-Looking for possibilities (weak acceptance).
-Those propositions that are in the reflexive preferences in a large sense: there is no strong enough reason to reject those propositions, though their contrary may hold as well.
+\section{Decision situation}
+Here is the definition of a decision situation.
 \begin{itemize}
@@
 We define $¬\prop$, with $\prop = \prop_\alt$, as equal to $\prop_{¬\alt}$ and $¬\prop$, with $\prop = \prop_{¬\alt}$, as equal to $\prop_{\alt}$.
-	\item All possible arguments: $\allargs$, the set of all strings. It can be chosen differently, but must be non empty as it contains at least $\emptyset$, the empty argument.
-	\item $\ar' \nibeatsst[\prop] \ar$: absence, all the time, of strong rejection attack; $\ar'$ does not render $\ar$ invalid; it is sure that $\ar'$ has no impact on $\ar$, even assuming that $\ar'$ would in turn resist all counter-arguments to it.
-This is an hypothesized relation, unobservable, used to define the deliberated preferences of $i$ (it is clear we can’t observe it, thus, as we can’t observe the DP).
-With $\ar$ supporting $\prop$, $\ar'$ claims that $¬\prop$ is a certainty, thus $\ar'$ supports that $\prop$ is not weakly accepted, thus $\ar$, if rebutted, can’t be used even to say that $\prop$ is a possibility.
-Thus we have only attacks between contradictory propositions.
+	\item All possible arguments: $\allargs$.
+It contains at least $\emptyset$, the empty argument.
+It contains all the arguments and more.
+As an example, $\allargs$ could be the set of all strings (assuming all arguments can be transmitted textually).
+	\item $\ar' \nibeatsst[\prop] \ar$: read $\ar'$, supporting $¬\prop$ sure, never attacks $\ar$, supporting $\prop$.
+We show arguments $\ar$ and $\ar'$ to $i$ and ask whether $\prop$ is considered as a possibility by $i$ (meaning $i$ would consider picking $\alt$, if $\prop = \prop_\alt$) or rather $¬\prop$ is sure (meaning $i$ would not consider picking $\alt$ as a choice).
+$\ar' \nibeatsst[\prop] \ar$ denotes a stable preference for $\prop$, in the sense that $\ar'$ does not render $\ar$ invalid; it is sure that $\ar'$ has no impact on $\ar$, even assuming that $\ar'$ would in turn resist all counter-arguments to it.
+This is an hypothesized relation, unobservable, used to define the deliberated preferences of $i$.
 Suffices that the attack occurs at least once over the considered time frame and unstability factors (such as submitting $i$ to other counter-arguments) to negate $\ar' \nibeatsst[\prop] \ar$.
-Here we do not condition on $\ar'$ surviving: $\ar'$ is declared incorrect, with no necessity of pursuing the debate and no hope of reinstatement.
-Example: $\ar'$ has already been taken into account and countered in $\ar$; or $\ar'$ does not talk about $\ar$ at all; or is not understood by $i$.
+We do not condition on $\ar'$ surviving: $\ar'$ is declared incorrect, with no necessity of pursuing the debate and no hope of reinstatement.
+Example: $\ar'$ has already been taken into account and countered in $\ar$; or $\ar'$ does not talk about $\prop$ at all; or is not understood by $i$.
 Note that when $\ar' \nibeatsst[\prop] \ar$, further attacks to $\ar'$ have no chance to change that fact (assuming some properties over the way $i$ reason).
@@
 For example, $¬ (\ar' \nibeatsst[\prop] \ar)$ ($\ar'$ may attack $\ar$) in case $i$ suspects that $\ar'$ is invalid (because of some counter-argument $\ar_2$ to $\ar'$ that $i$ has in mind) but wants to leave the door open to reinstatement of $\ar'$.
-	\item Define $¬ (\ar' \nibeatsst[\prop] \ar)$ iff $\ar' \ibeatse[\prop] \ar$.
-	\item Define $\args^\prop$ as the decisive arguments in favor of $\prop$: $\ar \in \args^\prop ⇔ \nexists \ar' \ibeatse[\prop] \ar ⇔ \ar' \nibeatsst[\prop] \ar$.
+	\item Define $\ar' \ibeatse[\prop] \ar$ iff $¬ (\ar' \nibeatsst[\prop] \ar)$.
+Note that $\ar$ or $\ar'$ (or both) may equal $\emptyset$, which is useful to query the attitude of $i$ towards an argument against her own knowledge or her default attitude when no argument is given.
 	\item Define $\ar \ibeatse[¬\prop, \text{sure}] \ar'$ iff $\ar$ may attack $\ar'$, where $\ar$ has a weak claim ($\prop$ is possible) and $\ar'$ has a strong claim ($¬\prop$ is sure).
 Similarly, $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$ is a constant absence of attack.
-	\item Define $\args^{¬\prop, \text{sure}}$ as the decisive arguments in favor of $¬\prop, \text{sure}$: $\ar' \in \args^{¬\prop, \text{sure}} ⇔ \nexists \ar \ibeatse[¬\prop, \text{sure}] \ar' ⇔ \ar \nibeatsst[¬\prop, \text{sure}] \ar'$.
+	\footnote{Previously: $¬ (\ar' \ibeatsst[\prop] \ar) ⇔ \ar' \nibeatse[\prop] \ar ⇔ \ar \ibeatse[¬\prop, \text{sure}] \ar' ⇔ ¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar')$.}
 	\item Require (axiom A1) that $\ar' \ibeatse[\prop] \ar ∨ \ar \ibeatse[¬\prop, \text{sure}] \ar'$.
@@
 Consider $(\ar', ¬\prop) \succeq (\ar, \prop) \sim (\ar', ¬\prop, \text{sure}) \succeq (\ar, \prop, \text{sure})$.}
-\end{itemize}
-
-It seems that knowledge of the poss rels is insufficient to know the sure rel: assume $¬(\ar' \ibeatse[\prop] \ar)$ and $\ar \ibeatse[¬\prop] \ar'$.
-Thus, 1.
-$\ar$ is sufficient for $\prop$ possible, $\ar'$ not sufficient for $¬\prop$ sure; and 2.
-$\ar$ may be sufficient for $\prop$ sure, $\ar'$ insuff for $\prop$.
-But is $\ar$ sufficient for $\prop$ sure?
-Thus, $\ar' \ibeatse[\prop, \text{sure}] \ar$?
-Equivalently: $\ar \nibeatse[¬\prop] \ar'$?
-To know this we need to know whether $¬\prop \in \iposs$.
-Or can we use $¬(\ar' \ibeatse[\prop] \ar) ⇒ \ar' \nibeatse[\prop] \ar$?
-
-Previously:
-\begin{itemize}
-	\item $¬ (\ar' \ibeatsst[\prop] \ar) ⇔ \ar' \nibeatse[\prop] \ar ⇔ \ar \ibeatse[¬\prop, \text{sure}] \ar' ⇔ ¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar')$.
 \end{itemize}
@@
 \end{definition}
-If $¬\prop \in \isure$, then $\prop \notin \iposs$: with $\ar' \in \args^{¬\prop, \text{sure}}$, given any $\ar$, $\ar' \ibeatse[\prop] \ar$ (because $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$, see A1).
+If $¬\prop \in \isure$, then $\prop \notin \iposs$: with $\ar'$ decisive for $¬\prop, \text{sure}$, given any $\ar$, $\ar' \ibeatse[\prop] \ar$ (because $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$, see A1).
 
@@
 \section{Models}
+A model is a triple $(\mbeats, \mleadsto, +)$ defined as follows and satisfying the constraints as indicated here.
+
 $\mbeats$ an acyclic binary relation over $\allargs$ (by which we mean that its transitive closure is irreflexive).
@@
 
-Define $\wibeatsst = ¬\nwibeatse$. Define $\nwibeatsst = ¬\wibeatse$.
-
-Hence, given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic)$: $\ar_3 \wibeatsst \ar_2$ iff $\forall \ar_1 \in \mbeats(\ar_2) ∩ \wibeatse(\ar_2): \ar_2 \nwibeatsst \ar_3 + \ar_1$.
-
-\subsection{Certainties}
-Assume we define $\ar_1 \wibeatse[¬\prop, \text{sure}] \ar_2$ ⇔ $\ar_2 \nwibeatse[\prop] \ar_1$.
-Then, indeed, given $\ar_1 \mleadsto \prop$, $\ar_2 \wibeatse[¬\prop, \text{sure}] \ar_1$ ⇔ $\ar_2 \ibeatse[¬\prop, \text{sure}] \ar_1$.
-But it gives the wrong conclusion.
-For $\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto t: \ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\ar_2 \nwibeatse[¬\prop] \ar_3$ iff $\exists \ar_1 \in \mbeats(\ar_3) \suchthat \ar_3 \wibeatse[¬\prop] \ar_1 ∧ \ar_3 \wibeatse[¬\prop] \ar_2 + \ar_1$.
-
-Given $\ar_1 \mleadsto \prop$, define $\ar_2 \wibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_2 \ibeatse[\prop, \text{sure}] \ar_1$.
-
-Given $\ar_1 \mleadsto \prop$, define $\ar_2 \nwibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_1 \ibeatse[¬\prop] \ar_2$.
-
-Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \nwibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.
-
-Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \nwibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \wibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.
+Hence, given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic)$: $¬ (\ar_3 \nwibeatse \ar_2)$ iff $\forall \ar_1 \in \mbeats(\ar_2) ∩ \wibeatse(\ar_2): ¬ (\ar_2 \wibeatse \ar_3 + \ar_1)$.
 
 \section{Conditions}
-All these conditions assume that a decision situation $(\allalts, \allargs, \{\ibeatse[\prop]\})$ and a model $\eta = (\mbeats, \mleadsto, +)$ are given.
+All these conditions assume that a decision situation $(\allalts, \allargs, \{\ibeatse[\prop]\}, \{\ibeatse[\prop, \text{sure}]\})$ and a model $\eta = (\mbeats, \mleadsto, +)$ are given.
 
@@
 
+\section{Model certainties}
+Assume we define $\ar_1 \wibeatse[¬\prop, \text{sure}] \ar_2$ ⇔ $\ar_2 \nwibeatse[\prop] \ar_1$.
+Then, indeed, given $\ar_1 \mleadsto \prop$, $\ar_2 \wibeatse[¬\prop, \text{sure}] \ar_1$ ⇔ $\ar_2 \ibeatse[¬\prop, \text{sure}] \ar_1$.
+But it gives the wrong conclusion.
+For $\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto t: \ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\ar_2 \nwibeatse[¬\prop] \ar_3$ iff $\exists \ar_1 \in \mbeats(\ar_3) \suchthat \ar_3 \wibeatse[¬\prop] \ar_1 ∧ \ar_3 \wibeatse[¬\prop] \ar_2 + \ar_1$.
+
+Given $\ar_1 \mleadsto \prop$, define $\ar_2 \wibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_2 \ibeatse[\prop, \text{sure}] \ar_1$.
+
+Given $\ar_1 \mleadsto \prop$, define $\ar_2 \nwibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_1 \ibeatse[¬\prop] \ar_2$.
+
+Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \nwibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.
+
+Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \nwibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \wibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.
+
 \section{Example about default arguments}

### 2017-11-02 article.tex
Removed old todos
Intro

@@
 \begin{document}
-\title{The title}
-\author{Olivier Cailloux}
+\title{Simple models of deliberated preference}
+\author{Olivier Cailloux \and Yves Meinard}
 \makeatletter
@@
 \maketitle
+
+\section{Motivation}
+We define the deliberated preference of an individual.
+We are interested in a context of a choice of a subset of alternatives from a set of possible alternatives given a priori.
+We define a model of the DP and give conditions and a validation procedure that ensure that what the model claims is in the DP is indeed.
+We want in particular to allow for the model to be applicable to various individuals that start with different knowledge: the model may use different counter-arguments to convince different individuals.
+
+More in detail.
+A full-blown proof may be so long that nobody would read it.
+(That’s why mathematicians do not write their proofs in set-theoretic bare notation.) Hence, shortcuts are taken, which rely on the individual knowing stuff already.
+More generally, assume you want to convince someone of fact $F$ with a text (we call this an argument), in our case, we want to convince a person that such alternative from the set is a good choice for her.
+The argument may assume the reader knows already why such or such possible counter-arguments are invalid, and the argument will thus not delve into the details of some points.
+When shown in interactive mode (our context here), an individual may however question some points (which we call a counter-argument).
+The argumenter should then be able to provide an answer to the query (a counter-counter-argument).
+
+This article aims at defining such a procedure and conditions of its validity.
 
@@
 \section{Todo}
-Road map.
-\begin{itemize}
-	\item P1: $p_a$ is w-a or $p_{¬a}$ is w-a
-	\item Define $p_{a}$ is strongly accepted; $p_{¬a}$ is strongly rejected, so that they are equivalent.
-	\item P2: $p_a$ is w-a or $p_{¬a}$ is strongly accepted.
-\end{itemize}
-
-Other todos.
 \begin{itemize}

### 2017-11-06 article.tex
¬YM
Started improving basic defs

@@
 \input{preamble/acronyms}
+\addtokomafont{labelinglabel}{\sffamily\bfseries}
 
@@
 \title{Simple models of deliberated preference}
-\author{Olivier Cailloux \and Yves Meinard}
+\author{Olivier Cailloux}
 \makeatletter
@@
 Here is an example of a non clear-cut situation. $\allargs = \{\emptyset\}, \alltopic = \{\prop\}, \emptyset \ibeatse[\prop] \emptyset, \emptyset \ibeatse[¬\prop, \text{sure}] \emptyset$.
+
+\subsection{Possible outcomes}
+We know $\prop \in \isure ⇒ ¬\prop \notin \iposs$ and $\prop \in \isure ⇒ \prop \in \iposs$.
+
+Here are the remaining possibilities, considering the four pairs $(\prop, \iposs)$, $(\prop, \isure)$, $(¬\prop, \iposs)$, $(¬\prop, \isure)$.
+(A pair $(\prop, T)$ not mentioned means $\prop \notin T$.)
+\begin{labeling}{Unstability with $¬\prop$ possible}
+	\item[All poss] $\prop \in \iposs$, $¬\prop \in \iposs$
+	\item[$\prop$ sure] $\prop \in \iposs$, $\prop \in \isure$
+	\item[$¬\prop$ sure] (symmetric)
+	\item[Unstability with $\prop$ possible] $\prop \in \iposs$ (oddity: $¬\prop \notin \iposs$ should imply $\prop \in \isure$)
+	\item[Unstability with $¬\prop$ possible] (symmetric)
+	\item[Strong unstability] (both oddities above)
+\end{labeling}
 
@@
 \appendix
+\section{Better definitions}
+Define $f_\prop$ from any unordered pair of arguments $(\ar, \ar')$ into $\{$ $\prop$ sure, $¬\prop$ sure, both possible, unstable$\}$.
+We present both arguments to $i$ and ask which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind, where the first three are when $i$ always declares the same answer and the last one is used if $i$ sometimes wobble (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason).
+
+We can also use $\emptyset$ as one or both of the arguments.
+
+We write $(\ar, \ar') \ileadsto \prop$ (respectively $¬\prop$, $b$, $\emptyset$) for $f_\prop(\ar, \ar') = \prop \text{ sure}$ (respectively $¬\prop$ sure, both possible, unstable).
+
+To encode this data efficiently, we can define two binary relations $\prop^+$ and $\prop^−$: $(\ar, \ar') \in \prop^+$ ⇔ $(\ar, \ar')$ always supports $\prop$ sure or always supports both ⇔ $(\ar, \ar') \ileadsto \prop ∨ (\ar, \ar') \ileadsto b$; and $(\ar, \ar') \in \prop^− ⇔ (\ar, \ar') \ileadsto ¬\prop ∨ (\ar, \ar') \ileadsto b$.
+
+This is indeed equivalent:
+\begin{itemize}
+	\item $(\ar, \ar') \ileadsto \prop ⇔ (\ar, \ar') \in \prop^+ ∧ (\ar, \ar') \notin \prop^−$
+	\item $(\ar, \ar') \ileadsto ¬\prop ⇔ (\ar, \ar') \notin \prop^+ ∧ (\ar, \ar') \in \prop^−$
+	\item $(\ar, \ar') \ileadsto b ⇔ (\ar, \ar') \in \prop^+ ∧ (\ar, \ar') \in \prop^−$
+	\item $(\ar, \ar') \ileadsto \emptyset ⇔ (\ar, \ar') \notin \prop^+ ∧ (\ar, \ar') \notin \prop^−$
+\end{itemize}
+
+We can now define $\ipossp, \ipossm \subseteq \alltopic$:
+\begin{itemize}
+	\item $\prop \in \ipossp ⇔ \exists \ar \suchthat \forall \ar': [(\ar, \ar') \ileadsto \prop] ∨ [(\ar, \ar') \ileadsto b]$. 
+	\item $\prop \in \ipossm ⇔ \exists \ar \suchthat \forall \ar': [(\ar, \ar') \ileadsto ¬\prop] ∨ [(\ar, \ar') \ileadsto b]$. 
+	\item $\prop$ strongly possible ⇔ $[\exists \ar \suchthat \forall \ar': (\ar, \ar') \ileadsto \prop] ∨ [\exists \ar \suchthat \forall \ar': (\ar, \ar') \ileadsto b]$. 
+\end{itemize}
+
+Here is a case where $\prop$ is possible but not strongly possible: $\exists (\ar_1, \ar) \ileadsto \prop$, $\exists (\ar_2, \ar) \ileadsto b$, $\nexists (\ar', \ar) \ileadsto ¬\prop$, $\nexists (\ar', \ar) \ileadsto \emptyset$.
+However this case is odd as just after showing $\ar_2$ to $i$ we could ask again about $\ar_1$ … (TODO)
+
+Now do we have $\prop \in \isure ⇔ \exists \ar \suchthat \forall \ar': (\ar, \ar') \ileadsto \prop$?
 \section{Todo}

### 2017-11-08 article.tex
Better basic definitions, in appendix

@@
 \section{Better definitions}
-Define $f_\prop$ from any unordered pair of arguments $(\ar, \ar')$ into $\{$ $\prop$ sure, $¬\prop$ sure, both possible, unstable$\}$.
-We present both arguments to $i$ and ask which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind, where the first three are when $i$ always declares the same answer and the last one is used if $i$ sometimes wobble (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason).
-
+Define $f_\prop$ from any unordered pair of arguments $(\ar, \ar')$ into $\powerset{\prop\text{-sure}, ¬\prop\text{-sure}, b)}$ (where $b$ means both possible).
+We present both arguments to $i$ and ask which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind.
+The set designates all cumulated answers over time, thus allowing $i$ to be unstable (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason).
+We assume $b$ is observable as well.
 We can also use $\emptyset$ as one or both of the arguments.
 
-We write $(\ar, \ar') \ileadsto \prop$ (respectively $¬\prop$, $b$, $\emptyset$) for $f_\prop(\ar, \ar') = \prop \text{ sure}$ (respectively $¬\prop$ sure, both possible, unstable).
+We define two binary relations $\prop^+$ (always supports $\propposs$) and $\prop^−$ (always supports $¬\propsure$) on $\allargs$.
+We define $(\ar, \ar') \in \prop^+ ⇔ (\ar, \ar') \ileadstopst \prop ⇔ \ar' \nibeatsst[\prop] \ar ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, and $(\ar, \ar') \in \prop^− ⇔ (\ar, \ar') \ileadstosst ¬\prop ⇔ \ar \nibeatsst[¬\propsure] \ar' ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$.
+Hence, $(\ar, \ar') \notin \prop^+ ⇔ (\ar, \ar') \ileadstose ¬\prop ⇔ \ar' \ibeatse[\prop] \ar ⇔ ¬(\ar' \nibeatsst[\prop] \ar) ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\}$, and $(\ar, \ar') \notin \prop^− ⇔ (\ar, \ar') \ileadstope \prop ⇔ \ar \ibeatse[¬\propsure] \ar' ⇔ ¬(\ar \nibeatsst[¬\propsure] \ar') ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\}$.
+
+When $\prop$ is fixed, or if it can be deduced from the output set, we write $(\ar, \ar') \ileadsto O$ or $\ileadsto(\ar, \ar') = O$ instead of $f_\prop(\ar, \ar') = O$.
+
+Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on, together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
+\footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.}
+and (A2) that $\ileadstosst \subseteq \ileadstopst$ 
+\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}
+and the fact that the relations $\prop^+$ and $\prop^−$ are symmetric. 
+\footnote{Unclear where we use the fact that the relations $\prop^+$ and $\prop^−$ are symmetric.}
+
+We say $(\ar, \ar')$ is $\prop$-unstable iff $(\ar, \ar') \ileadstose \prop ∧ (\ar, \ar') \ileadstose ¬\prop$.
+
+$\ar$ is 
+\begin{itemize}
+	\item $\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$
+	\item $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$
+\end{itemize}
+
+We can now define $\iposs, \isure \subseteq \alltopic$:
+\begin{itemize}
+	\item $\prop \in \iposs ⇔ \exists \ar \ \proppossdec$. 
+\footnote{\label{ft:notposs}$\prop \notin \iposs ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstose ¬\prop$.}
+	\item $\prop \in \isure ⇔ \exists \ar \ \propsuredec$. 
+\footnote{\label{ft:notsure}$¬\prop \notin \isure ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstope \prop$.}
+\end{itemize}
+
+We say that severe $\prop$-unstability happens iff $\forall \ar, [\exists \ar^+ \suchthat (\ar, \ar^+) \ileadstose \prop] ∧ [\exists \ar^− \suchthat (\ar, \ar^−) \ileadstose ¬\prop]$.
+\footnote{Severe $\prop$-unstability happens iff severe $¬\prop$-unstability happens.}
+
+\begin{theorem}
+	If $\prop \notin \iposs ∧ ¬\prop \notin \iposs$, severe $\prop$-unstability happens.
+\end{theorem}
+The proof follows from \cref{ft:notposs}.
+
+\begin{theorem}
+	$\prop \in \isure ⇒ ¬\prop \notin \iposs$.
+\end{theorem}
+This is because $\ar^+$ is $\propsuredec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstosst \prop$ hence $(\ar^+, \ar^−) \ileadstose \prop$ (using A1).
+
+\begin{theorem}
+	$\prop \in \isure ⇒ \prop \in \iposs$.
+\end{theorem}
+The proof follows from (A2).
+
+Something like Axiom JU should be sufficient for CC.
+JU: If $(\ar, \ar')$ is $\prop$-unstable, then $\exists \ar_2 \in \allargs$ such that for $(\ar_1, \ar_0) = (\ar, \ar')$ or for $(\ar_1, \ar_0) = (\ar', \ar)$, $\ar_2$ attacks decisively $\ar_1$, where we mean by this that $\ar_2$ combined with $\ar_0$ is decisive.
+Means that if not CC, then not JU.
+Hence, infinite discussion happens, or irreducible unstability.
+Or, the memory buffer of $i$ is too short to hold adequate reinstated arguments, in which case our approach based on decisive arguments is not adequate.
+
+\subsection{Encoding (non-intuitive)}
+TODO…
 
@@
 	\item $(\ar, \ar') \ileadsto \emptyset ⇔ (\ar, \ar') \notin \prop^+ ∧ (\ar, \ar') \notin \prop^−$
-\end{itemize}
-
-We can now define $\ipossp, \ipossm \subseteq \alltopic$:
-\begin{itemize}
-	\item $\prop \in \ipossp ⇔ \exists \ar \suchthat \forall \ar': [(\ar, \ar') \ileadsto \prop] ∨ [(\ar, \ar') \ileadsto b]$. 
-	\item $\prop \in \ipossm ⇔ \exists \ar \suchthat \forall \ar': [(\ar, \ar') \ileadsto ¬\prop] ∨ [(\ar, \ar') \ileadsto b]$. 
-	\item $\prop$ strongly possible ⇔ $[\exists \ar \suchthat \forall \ar': (\ar, \ar') \ileadsto \prop] ∨ [\exists \ar \suchthat \forall \ar': (\ar, \ar') \ileadsto b]$. 
 \end{itemize}

### 2017-11-08 article.tex
Removed old incorrect basic encoding

@@
 
-\subsection{Encoding (non-intuitive)}
-TODO…
-
-To encode this data efficiently, we can define two binary relations $\prop^+$ and $\prop^−$: $(\ar, \ar') \in \prop^+$ ⇔ $(\ar, \ar')$ always supports $\prop$ sure or always supports both ⇔ $(\ar, \ar') \ileadsto \prop ∨ (\ar, \ar') \ileadsto b$; and $(\ar, \ar') \in \prop^− ⇔ (\ar, \ar') \ileadsto ¬\prop ∨ (\ar, \ar') \ileadsto b$.
-
-This is indeed equivalent:
-\begin{itemize}
-	\item $(\ar, \ar') \ileadsto \prop ⇔ (\ar, \ar') \in \prop^+ ∧ (\ar, \ar') \notin \prop^−$
-	\item $(\ar, \ar') \ileadsto ¬\prop ⇔ (\ar, \ar') \notin \prop^+ ∧ (\ar, \ar') \in \prop^−$
-	\item $(\ar, \ar') \ileadsto b ⇔ (\ar, \ar') \in \prop^+ ∧ (\ar, \ar') \in \prop^−$
-	\item $(\ar, \ar') \ileadsto \emptyset ⇔ (\ar, \ar') \notin \prop^+ ∧ (\ar, \ar') \notin \prop^−$
-\end{itemize}
-
-Here is a case where $\prop$ is possible but not strongly possible: $\exists (\ar_1, \ar) \ileadsto \prop$, $\exists (\ar_2, \ar) \ileadsto b$, $\nexists (\ar', \ar) \ileadsto ¬\prop$, $\nexists (\ar', \ar) \ileadsto \emptyset$.
-However this case is odd as just after showing $\ar_2$ to $i$ we could ask again about $\ar_1$ … (TODO)
-
-Now do we have $\prop \in \isure ⇔ \exists \ar \suchthat \forall \ar': (\ar, \ar') \ileadsto \prop$?
 \section{Todo}

### 2017-12-07 article.tex
Much!

@@
 \RequirePackage[l2tabu, orthodox]{nag}
-\RequirePackage{silence}\WarningFilter{fmtcount}{\ordinal already defined use \FCordinal instead}
-\documentclass[version=last, pagesize, twoside=semi, DIV=calc, bibliography=totoc, 12pt, a4paper, french, english]{scrartcl}
+\RequirePackage{silence}\WarningFilter{typearea}{Maybe no optimal type area settings}
+\documentclass[version=last, pagesize, twocolumn, twoside=off, bibliography=totoc, 12pt, a4paper, french, english]{scrartcl}
 \input{preamble/packages}
@@
 
+%printer margin: I take 0.5 inches = 1,27 cm to be safe. 21 cm - (2 × 1.27 cm) = 18.46 cm. 29.7 cm − 0.9 cm − (2 × 1.27 cm) = 26.26 cm
+\areaset{18.46cm}{26.26cm}
+\setlength{\footskip}{9mm}
 \begin{document}
@@
 As an example, $\allargs$ could be the set of all strings (assuming all arguments can be transmitted textually).
-	\item $\ar' \nibeatsst[\prop] \ar$: read $\ar'$, supporting $¬\prop$ sure, never attacks $\ar$, supporting $\prop$.
-We show arguments $\ar$ and $\ar'$ to $i$ and ask whether $\prop$ is considered as a possibility by $i$ (meaning $i$ would consider picking $\alt$, if $\prop = \prop_\alt$) or rather $¬\prop$ is sure (meaning $i$ would not consider picking $\alt$ as a choice).
-$\ar' \nibeatsst[\prop] \ar$ denotes a stable preference for $\prop$, in the sense that $\ar'$ does not render $\ar$ invalid; it is sure that $\ar'$ has no impact on $\ar$, even assuming that $\ar'$ would in turn resist all counter-arguments to it.
-This is an hypothesized relation, unobservable, used to define the deliberated preferences of $i$.
-Suffices that the attack occurs at least once over the considered time frame and unstability factors (such as submitting $i$ to other counter-arguments) to negate $\ar' \nibeatsst[\prop] \ar$.
-We do not condition on $\ar'$ surviving: $\ar'$ is declared incorrect, with no necessity of pursuing the debate and no hope of reinstatement.
-Example: $\ar'$ has already been taken into account and countered in $\ar$; or $\ar'$ does not talk about $\prop$ at all; or is not understood by $i$.
-Note that when $\ar' \nibeatsst[\prop] \ar$, further attacks to $\ar'$ have no chance to change that fact (assuming some properties over the way $i$ reason).
-The negation of this should read: $\ar'$ may attack $\ar$ in at least some cases.
-For example, $¬ (\ar' \nibeatsst[\prop] \ar)$ ($\ar'$ may attack $\ar$) in case $i$ suspects that $\ar'$ is invalid (because of some counter-argument $\ar_2$ to $\ar'$ that $i$ has in mind) but wants to leave the door open to reinstatement of $\ar'$.
-	\item Define $\ar' \ibeatse[\prop] \ar$ iff $¬ (\ar' \nibeatsst[\prop] \ar)$.
-Note that $\ar$ or $\ar'$ (or both) may equal $\emptyset$, which is useful to query the attitude of $i$ towards an argument against her own knowledge or her default attitude when no argument is given.
-	\item Define $\ar \ibeatse[¬\prop, \text{sure}] \ar'$ iff $\ar$ may attack $\ar'$, where $\ar$ has a weak claim ($\prop$ is possible) and $\ar'$ has a strong claim ($¬\prop$ is sure).
-Similarly, $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$ is a constant absence of attack.
-	\footnote{Previously: $¬ (\ar' \ibeatsst[\prop] \ar) ⇔ \ar' \nibeatse[\prop] \ar ⇔ \ar \ibeatse[¬\prop, \text{sure}] \ar' ⇔ ¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar')$.}
-	\item Require (axiom A1) that $\ar' \ibeatse[\prop] \ar ∨ \ar \ibeatse[¬\prop, \text{sure}] \ar'$.
-Equivalently: $¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar' ∧ \ar' \nibeatsst[\prop] \ar)$; $\ar \nibeatsst[¬\prop, \text{sure}] \ar' ⇒ \ar' \ibeatse[\prop] \ar$.
-	\item Axiom A2: $\ar \nibeatsst[¬\prop, \text{sure}] \ar' ⇒ \ar \nibeatsst[¬\prop] \ar'$. Equivalently: $\ar \ibeatse[¬\prop] \ar' ⇒ \ar \ibeatse[¬\prop, \text{sure}] \ar'$.
-	\footnote{A3: $[\exists \ar \suchthat (\ar' \ibeatse[\prop] \ar ∧ \ar \ibeatse[¬\prop, \text{sure}] \ar')] ⇒ \exists \ar_2 \suchthat \ar_2 \ibeatse[¬\prop] \ar'$.
-Equivalently: $\ar_2 \nibeatsst[¬\prop] \ar', \forall \ar_2$ implies that for all $\ar$, $(\ar' \nibeatsst[\prop] \ar ∨ \ar \nibeatsst[¬\prop, \text{sure}] \ar')$.
-A1, A2 and A3 are equivalent to: $\ar \nibeatsst[¬\prop, \text{sure}] \ar' ⇔ \ar \nibeatsst[¬\prop] \ar' ∧ \ar' \ibeatse[\prop] \ar$.}
-	\footnote{Having A1 and A2, can we have $\ar \nibeatsst[¬\prop] \ar' ∧ \ar' \ibeatse[\prop] \ar ∧ \ar \ibeatse[¬\prop, \text{sure}] \ar'$?
-Consider $(\ar', ¬\prop) \succeq (\ar, \prop) \sim (\ar', ¬\prop, \text{sure}) \succeq (\ar, \prop, \text{sure})$.}
 \end{itemize}
 
-Define $\iposs \subseteq \alltopic$ as the set of propositions that are weakly accepted.
-\begin{definition}[Weak acceptance]
-	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$.
-A proposition $\prop \in \alltopic$ is weakly accepted, $\prop \in \iposs$, iff $\exists \ar \in \allargs \suchthat \forall \ar' \in \allargs: \ar' \nibeatsst[\prop] \ar$.
-\end{definition}
-It follows that $¬\prop \notin \iposs$ iff $\forall \ar: \exists \ar' \suchthat \ar' \ibeatse[¬\prop] \ar$. Equivalently, $¬\prop \notin \iposs ⇔ \ibeatse[¬\prop](\allargs) = \allargs$.
+Define $f_\prop$ from any unordered pair of arguments $(\ar, \ar')$ into $\powerset{\prop\text{-sure}, ¬\prop\text{-sure}, b)}$ (where $b$ means both possible).
+We present both arguments to $i$ and ask which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind.
+The set designates all cumulated answers over time, thus allowing $i$ to be unstable (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason).
+We assume $b$ is observable as well.
+We can also use $\emptyset$ as one or both of the arguments.
 
-\begin{definition}[Sure acceptance]
-	$¬\prop \in \isure$ iff $\exists \ar' \in \allargs \suchthat \forall \ar \in \allargs: \ar \nibeatsst[¬\prop, \text{sure}] \ar'$.\footnote{Instead of accepting $¬\prop$ for sure, it is tempting to define strong rejection of $t$ as follows.
-A proposition $\prop \in \alltopic$ is strongly rejected iff $\forall \ar_0 \in \allargs, \exists \ar' \in \allargs \suchthat \ar_0 \nibeatsst[¬\prop, \text{sure}] \ar'$.
-But this is too weak: we want $\ar'$ to be also decisive, thus $\ar \nibeatsst[¬\prop, \text{sure}] \ar', \forall \ar$.
-Hence the definition becomes $\exists \ar' \in \allargs \suchthat \ar \nibeatsst[¬\prop, \text{sure}] \ar'$.}
-\end{definition}
-If $¬\prop \in \isure$, then $\prop \notin \iposs$: with $\ar'$ decisive for $¬\prop, \text{sure}$, given any $\ar$, $\ar' \ibeatse[\prop] \ar$ (because $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$, see A1).
+We define two binary relations $\prop^+$ (always supports $\propposs$) and $\prop^−$ (always supports $¬\propsure$) on $\allargs$.
+We define $(\ar, \ar') \in \prop^+ ⇔ (\ar, \ar') \ileadstopst \prop ⇔ \ar' \nibeatsst[\prop] \ar ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, and $(\ar, \ar') \in \prop^− ⇔ (\ar, \ar') \ileadstosst ¬\prop ⇔ \ar \nibeatsst[¬\propsure] \ar' ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$.
+Hence, $(\ar, \ar') \notin \prop^+ ⇔ (\ar, \ar') \ileadstose ¬\prop ⇔ \ar' \ibeatse[\prop] \ar ⇔ ¬(\ar' \nibeatsst[\prop] \ar) ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\}$, and $(\ar, \ar') \notin \prop^− ⇔ (\ar, \ar') \ileadstope \prop ⇔ \ar \ibeatse[¬\propsure] \ar' ⇔ ¬(\ar \nibeatsst[¬\propsure] \ar') ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\}$.
 
-If $¬\prop \in \isure$, then $¬\prop \in \iposs$: from $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$ we obtain $\ar \nibeatsst[¬\prop] \ar'$ using A2.
+When $\prop$ is fixed, or if it can be deduced from the output set, we write $(\ar, \ar') \ileadsto O$ or $\ileadsto(\ar, \ar') = O$ instead of $f_\prop(\ar, \ar') = O$.
+
+Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on, together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
+\footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.}
+and (A2) that $\ileadstosst \subseteq \ileadstopst$ 
+\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}
+and the fact that the relations $\prop^+$ and $\prop^−$ are symmetric. 
+\footnote{Unclear where we use the fact that the relations $\prop^+$ and $\prop^−$ are symmetric.}
+
+We say $(\ar, \ar')$ is $\prop$-unstable iff $(\ar, \ar') \ileadstose \prop ∧ (\ar, \ar') \ileadstose ¬\prop$.
+
+$\ar$ is 
+\begin{itemize}
+	\item $\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$
+	\item $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$
+\end{itemize}
+
+We can now define $\iposs, \isure \subseteq \alltopic$:
+\begin{itemize}
+	\item $\prop \in \iposs ⇔ \exists \ar \ \proppossdec$. 
+\footnote{\label{ft:notposs}$\prop \notin \iposs ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstose ¬\prop$.}
+	\item $\prop \in \isure ⇔ \exists \ar \ \propsuredec$. 
+\footnote{\label{ft:notsure}$¬\prop \notin \isure ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstope \prop$.}
+\end{itemize}
+
+We say that severe $\prop$-unstability happens iff $\forall \ar, [\exists \ar^+ \suchthat (\ar, \ar^+) \ileadstose \prop] ∧ [\exists \ar^− \suchthat (\ar, \ar^−) \ileadstose ¬\prop]$.
+\footnote{Severe $\prop$-unstability happens iff severe $¬\prop$-unstability happens.}
+\footnote{Here is an example of severe $\prop$-unstability. $\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstose \prop$.}
+
+\begin{theorem}
+	If $\prop \notin \iposs ∧ ¬\prop \notin \iposs$, severe $\prop$-unstability happens.
+\end{theorem}
+The proof follows from \cref{ft:notposs}.
+
+\begin{theorem}
+	$\prop \in \isure ⇒ ¬\prop \notin \iposs$.
+\end{theorem}
+This is because $\ar^+$ is $\propsuredec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstosst \prop$ hence $(\ar^+, \ar^−) \ileadstose \prop$ (using A1).
+
+\begin{theorem}
+	$\prop \in \isure ⇒ \prop \in \iposs$.
+\end{theorem}
+The proof follows from (A2).
 
 \begin{definition}[Clear-cut]
-	A situation is clear-cut iff $\prop \notin \iposs ⇒ ¬\prop \in \isure$.
+	A situation is $\prop$-clear-cut iff $\prop \notin \iposs ⇒ ¬\prop \in \isure$.
+\footnote{Here is an example of non $\prop$-clear-cut situation with no severe $\prop$-unstability.
+$\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstope \prop, (\ar, \ar') \ileadstopst ¬\prop$.}
+\footnote{Something like Axiom JU should be sufficient for CC.
+JU: If $(\ar, \ar')$ is $\prop$-unstable, then $\exists \ar_2 \in \allargs$ such that for $(\ar_1, \ar_0) = (\ar, \ar')$ or for $(\ar_1, \ar_0) = (\ar', \ar)$, $\ar_2$ attacks decisively $\ar_1$, where we mean by this that $\ar_2$ combined with $\ar_0$ is decisive.
+Means that if not CC, then not JU.
+Hence, infinite discussion happens, or irreducible unstability.
+Or, the memory buffer of $i$ is too short to hold adequate reinstated arguments, in which case our approach based on decisive arguments is not adequate.}
 \end{definition}
-Here is an example of a non clear-cut situation. $\allargs = \{\emptyset\}, \alltopic = \{\prop\}, \emptyset \ibeatse[\prop] \emptyset, \emptyset \ibeatse[¬\prop, \text{sure}] \emptyset$.
 
@@
 (A pair $(\prop, T)$ not mentioned means $\prop \notin T$.)
-\begin{labeling}{Unstability with $¬\prop$ possible}
+\begin{labeling}{Unstability, $¬\prop$ poss}
 	\item[All poss] $\prop \in \iposs$, $¬\prop \in \iposs$
@@
 	\item[$¬\prop$ sure] (symmetric)
-	\item[Unstability with $\prop$ possible] $\prop \in \iposs$ (oddity: $¬\prop \notin \iposs$ should imply $\prop \in \isure$)
-	\item[Unstability with $¬\prop$ possible] (symmetric)
+	\item[Unstability, $\prop$ poss] $\prop \in \iposs$ (oddity: $¬\prop \notin \iposs$ should imply $\prop \in \isure$)
+	\item[Unstability, $¬\prop$ poss] (symmetric)
 	\item[Strong unstability] (both oddities above)
@@
 
-$\mbeats$ an acyclic binary relation over $\allargs$ (by which we mean that its transitive closure is irreflexive).
+$\mbeats$ a binary relation over $\allargs$.
 $\mleadsto \subseteq \allargs × \alltopic$.
@@
 
-Requirements. The maximum length of a path in $\mbeats$ is finite.
+Requirements. The maximum length of a path in $\mbeats$ is finite (which implies that $\mbeats$ is acyclic).
 $\ar_3 \mbeats \ar_2 \mbeats \ar_1 ⇒ \ar_2 \mbeats \ar_3 + \ar_1$.\footnote{Necessary for definition of $\ar_3 \wibeatse \ar_2$.}
@@
 
-Given a decision situation, define $\wibeatse \subseteq \mbeats$ as follows.
+Given a decision situation, define $\wibeatse[\prop], \nwibeatse[¬\prop] \subseteq \mbeats$ as follows.
 
-Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ \ar_3 \ibeatse[\prop] \ar_2]$.
-\footnote{Or $\ar_2 \ileadsto \prop ∧ ¬\prop \notin \mleadsto(\allargs) ∧ \ar_3 \ibeatse[\prop, \text{sure}] \ar_2$.}
+Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
+\footnote{Or $\ar_2 \ileadsto \prop ∧ ¬\prop \notin \mleadsto(\allargs) ∧ (\ar_3, \ar_2) \ileadstope ¬\prop$.}
 
-Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \nwibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ \ar_2 \ibeatse[¬\prop, \text{sure}] \ar_3]$.
-\footnote{Check: Given $\ar_4 \mbeats \ar_3, \ar_3 \notin \mleadstoinv(\alltopic)$, with $\ar_2 \in \mbeats(\ar_3)$ ⇒ ($\ar_2$ and $\ar_4 + \ar_2$ $\mbeats$-attack only root nodes and do not support any proposition): $\ar_4 \wibeatse[\prop] \ar_3$ iff
+Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \nwibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstope \prop]$.
+
+This is well defined thanks to the following construction.
+Given a model. 
+\begin{itemize}
+	\item Define a root as an argument that $\mbeats$-attacks nobody. 
+	\item Associate to each $\ar \in \clargs$ its depth $d(\ar)$, the distance to the farthest root: $d(\ar) = 0$ iff $\ar$ is a root and $d(\ar) = k+1$ iff $\ar$ $\mbeats$-attacks some $\ar'$ of depth $k$ and $\mbeats$-attacks no $\ar'$ of depth superior to $k$ (thus $d(\ar) = 1$ iff $\ar$ attacks some and only root nodes; $d(\ar) = 2$ iff $\ar$ attacks some node of depth 1 and only nodes of depth 1 or 0; and so on).
+	\item Observe that if $\ar_3 \mbeats \ar_2$ and $d(\ar_3) = k+1$, then $d(\ar_2) ≤ k$. 
+	\item Define $\wibeatse[\prop]_{(0)} = \nwibeatse[\prop]_{(0)} = \emptyset$. %as $\ar_3 \wibeatse[\prop]_{(1)} \ar_2$ iff $d(\ar_3) = 1 ∧ \ar_2 \ileadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop$. 
+%	\item Define $\nwibeatse[\prop]_{(1)}$ as $\ar_3 \nwibeatse[\prop]_{(1)} \ar_2$ iff $d(\ar_3) = 1 ∧ \ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstope \prop$. 
+	\item Define $\wibeatse[\prop]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\prop]_{(k+1)} \ar_2$ iff, first, $d(\ar_3) = k+1$, and second, $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\prop]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
+Proceed similarly for $\nwibeatse[\prop]_{(k+1)}$.
+	\item Define $\wibeatse[\prop] = \bigcup_{k ≥ 0} \wibeatse[\prop]_{(k)}$, and similarly for $\nwibeatse[\prop]$.
+\end{itemize}
+
+{Check: Given $\ar_4 \mbeats \ar_3, \ar_3 \notin \mleadstoinv(\alltopic)$, with $\ar_2 \in \mbeats(\ar_3)$ ⇒ ($\ar_2$ and $\ar_4 + \ar_2$ $\mbeats$-attack only root nodes and do not support any proposition): $\ar_4 \wibeatse[\prop] \ar_3$ iff
 \begin{itemize}
@@
 	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_4 + \ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_4 + \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)]$ iff
-	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_1 \ileadsto t ∧ \ar_2 \ibeatse[\prop] \ar_1 ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ \ar_3 + \ar_1 \ibeatse[¬\prop, \text{sure}] \ar_2) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_1 \mleadsto \prop ∧ \ar_4 + \ar_2 \ibeatse[\prop] \ar_1 ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ \ar_4 + \ar_2 \ibeatse[\prop] \ar_3 + \ar_1)]$.
+	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_1 \ileadsto t ∧ (\ar_2, \ar_1) \ileadstose ¬\prop ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ (\ar_3 + \ar_1, \ar_2) \ileadstope \prop ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_1 \mleadsto \prop ∧ (\ar_4 + \ar_2, \ar_1) \ileadstose ¬\prop ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ (\ar_4 + \ar_2, \ar_3 + \ar_1) \ileadstose ¬\prop)]$.
 \end{itemize}
 }
-
-TODO this is well-defined because associate to each $\ar \in \clargs$ $d(\ar)$, the distance to the farthest root (a root is an argument that $\mbeats$-attacks nobody).
-Then $\wibeatse$ is defined for all attacks from $d(.)=1$ nodes (because those nodes attack only $d(.)=0$ nodes), and thus is defined for all nodes $2$, I suppose, …
 
@@
 \appendix
-\section{Better definitions}
-Define $f_\prop$ from any unordered pair of arguments $(\ar, \ar')$ into $\powerset{\prop\text{-sure}, ¬\prop\text{-sure}, b)}$ (where $b$ means both possible).
-We present both arguments to $i$ and ask which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind.
-The set designates all cumulated answers over time, thus allowing $i$ to be unstable (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason).
-We assume $b$ is observable as well.
-We can also use $\emptyset$ as one or both of the arguments.
-
-We define two binary relations $\prop^+$ (always supports $\propposs$) and $\prop^−$ (always supports $¬\propsure$) on $\allargs$.
-We define $(\ar, \ar') \in \prop^+ ⇔ (\ar, \ar') \ileadstopst \prop ⇔ \ar' \nibeatsst[\prop] \ar ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, and $(\ar, \ar') \in \prop^− ⇔ (\ar, \ar') \ileadstosst ¬\prop ⇔ \ar \nibeatsst[¬\propsure] \ar' ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$.
-Hence, $(\ar, \ar') \notin \prop^+ ⇔ (\ar, \ar') \ileadstose ¬\prop ⇔ \ar' \ibeatse[\prop] \ar ⇔ ¬(\ar' \nibeatsst[\prop] \ar) ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\}$, and $(\ar, \ar') \notin \prop^− ⇔ (\ar, \ar') \ileadstope \prop ⇔ \ar \ibeatse[¬\propsure] \ar' ⇔ ¬(\ar \nibeatsst[¬\propsure] \ar') ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\}$.
-
-When $\prop$ is fixed, or if it can be deduced from the output set, we write $(\ar, \ar') \ileadsto O$ or $\ileadsto(\ar, \ar') = O$ instead of $f_\prop(\ar, \ar') = O$.
-
-Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on, together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
-\footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.}
-and (A2) that $\ileadstosst \subseteq \ileadstopst$ 
-\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}
-and the fact that the relations $\prop^+$ and $\prop^−$ are symmetric. 
-\footnote{Unclear where we use the fact that the relations $\prop^+$ and $\prop^−$ are symmetric.}
-
-We say $(\ar, \ar')$ is $\prop$-unstable iff $(\ar, \ar') \ileadstose \prop ∧ (\ar, \ar') \ileadstose ¬\prop$.
-
-$\ar$ is 
-\begin{itemize}
-	\item $\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$
-	\item $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$
-\end{itemize}
-
-We can now define $\iposs, \isure \subseteq \alltopic$:
-\begin{itemize}
-	\item $\prop \in \iposs ⇔ \exists \ar \ \proppossdec$. 
-\footnote{\label{ft:notposs}$\prop \notin \iposs ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstose ¬\prop$.}
-	\item $\prop \in \isure ⇔ \exists \ar \ \propsuredec$. 
-\footnote{\label{ft:notsure}$¬\prop \notin \isure ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstope \prop$.}
-\end{itemize}
-
-We say that severe $\prop$-unstability happens iff $\forall \ar, [\exists \ar^+ \suchthat (\ar, \ar^+) \ileadstose \prop] ∧ [\exists \ar^− \suchthat (\ar, \ar^−) \ileadstose ¬\prop]$.
-\footnote{Severe $\prop$-unstability happens iff severe $¬\prop$-unstability happens.}
-
-\begin{theorem}
-	If $\prop \notin \iposs ∧ ¬\prop \notin \iposs$, severe $\prop$-unstability happens.
-\end{theorem}
-The proof follows from \cref{ft:notposs}.
-
-\begin{theorem}
-	$\prop \in \isure ⇒ ¬\prop \notin \iposs$.
-\end{theorem}
-This is because $\ar^+$ is $\propsuredec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstosst \prop$ hence $(\ar^+, \ar^−) \ileadstose \prop$ (using A1).
-
-\begin{theorem}
-	$\prop \in \isure ⇒ \prop \in \iposs$.
-\end{theorem}
-The proof follows from (A2).
-
-Something like Axiom JU should be sufficient for CC.
-JU: If $(\ar, \ar')$ is $\prop$-unstable, then $\exists \ar_2 \in \allargs$ such that for $(\ar_1, \ar_0) = (\ar, \ar')$ or for $(\ar_1, \ar_0) = (\ar', \ar)$, $\ar_2$ attacks decisively $\ar_1$, where we mean by this that $\ar_2$ combined with $\ar_0$ is decisive.
-Means that if not CC, then not JU.
-Hence, infinite discussion happens, or irreducible unstability.
-Or, the memory buffer of $i$ is too short to hold adequate reinstated arguments, in which case our approach based on decisive arguments is not adequate.
-
 \section{Todo}
@@
 Require to assume that this situation implies another argument $\ar_3$ “attacking” $\ar'$, thus, such that $\ar_3 + \ar$ is no more attacked by $\ar_2$.
+
+\subsection{Attack rel}
+Given $\prop$, define a (symmetric) strong attack rel, $Q_\prop$, as $\ar Q_\prop \ar'$ iff $(\ar, \ar') \ileadstosst ¬\prop$.
+
+Define a (symmetric) weak attack rel, $R_\prop$, as $\ar R_\prop \ar'$ iff $(\ar, \ar') \ileadstopst ¬\prop$.
+
+Given $\prop$, we want to check the arguments that defend it. We want to build an asymmetric attack relation.
+$\ar_1 M \ar_0$, and not the converse, iff $\ar_1$ attacks $\ar_0$ and, would $\ar_1$ be attacked, $\ar_0$ reinstated would defend $\prop$.
+$\ar_1$ should be able to support a sub-claim $\prop'$, and then $\ar_2$ attack $\ar_1$ on that sub-claim precisely.
+$\ar_2$ decisive on this sub-claim and $\ar_0 + \ar_2$ decisive implies $\ar_1$ attacks $\ar_0$ and not conversely.
+
+Or simply. $\ar_1$ decisive for $¬\prop$ means $\ar_1$ attacks $\ar_0$ and not conversely.
+
+Then define $i$’s DJ in terms of argumentation semantics.
 

### 2018-01-27 simple.tex
Various impr

--- 2017-12-07 article.tex
@@
 \RequirePackage[l2tabu, orthodox]{nag}
-\RequirePackage{silence}\WarningFilter{typearea}{Maybe no optimal type area settings}
-\documentclass[version=last, pagesize, twocolumn, twoside=off, bibliography=totoc, 12pt, a4paper, french, english]{scrartcl}
+\documentclass[version=last, pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=14pt, a4paper, french, english]{scrartcl}
 \input{preamble/packages}
@@
 
-%printer margin: I take 0.5 inches = 1,27 cm to be safe. 21 cm - (2 × 1.27 cm) = 18.46 cm. 29.7 cm − 0.9 cm − (2 × 1.27 cm) = 26.26 cm
-\areaset{18.46cm}{26.26cm}
-\setlength{\footskip}{9mm}
 \begin{document}
@@
 \author{Olivier Cailloux}
+\affil{Université Paris-Dauphine, PSL Research University, CNRS, LAMSADE, 75016 PARIS, FRANCE\\
+	\href{mailto:olivier.cailloux@dauphine.fr}{olivier.cailloux@dauphine.fr}
+}
 \makeatletter
@@
 
-We define two binary relations $\prop^+$ (always supports $\propposs$) and $\prop^−$ (always supports $¬\propsure$) on $\allargs$.
-We define $(\ar, \ar') \in \prop^+ ⇔ (\ar, \ar') \ileadstopst \prop ⇔ \ar' \nibeatsst[\prop] \ar ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, and $(\ar, \ar') \in \prop^− ⇔ (\ar, \ar') \ileadstosst ¬\prop ⇔ \ar \nibeatsst[¬\propsure] \ar' ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$.
-Hence, $(\ar, \ar') \notin \prop^+ ⇔ (\ar, \ar') \ileadstose ¬\prop ⇔ \ar' \ibeatse[\prop] \ar ⇔ ¬(\ar' \nibeatsst[\prop] \ar) ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\}$, and $(\ar, \ar') \notin \prop^− ⇔ (\ar, \ar') \ileadstope \prop ⇔ \ar \ibeatse[¬\propsure] \ar' ⇔ ¬(\ar \nibeatsst[¬\propsure] \ar') ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\}$.
-
 When $\prop$ is fixed, or if it can be deduced from the output set, we write $(\ar, \ar') \ileadsto O$ or $\ileadsto(\ar, \ar') = O$ instead of $f_\prop(\ar, \ar') = O$.
 
-Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on, together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
+We define $(\ar, \ar') \ileadstopst \prop ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, $(\ar, \ar') \ileadstosst ¬\prop ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$, $(\ar, \ar') \ileadstose ¬\prop ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\} ⇔ ¬((\ar, \ar') \ileadstopst \prop)$, and $(\ar, \ar') \ileadstope \prop  ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\} ⇔ ¬((\ar, \ar') \ileadstosst ¬\prop)$.
+
+TODO do everything with only one relation.
+Define for each prop: $\prop^{s}$ and $\prop^p$, and define $¬(\prop^s) = (¬\prop)^p$, and we can do everything with $(\ar, \ar') \ileadsto \prop^p$ (defined as $\ileadstopst \prop$) and $(\ar, \ar') \ileadsto \prop^s$ (defined as $\ileadstosst \prop$).
+
+Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on (and their negations $\ileadstose$ and $\ileadstope$), together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
 \footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.}
 and (A2) that $\ileadstosst \subseteq \ileadstopst$
-\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}
-and the fact that the relations $\prop^+$ and $\prop^−$ are symmetric. 
-\footnote{Unclear where we use the fact that the relations $\prop^+$ and $\prop^−$ are symmetric.}
-
-We say $(\ar, \ar')$ is $\prop$-unstable iff $(\ar, \ar') \ileadstose \prop ∧ (\ar, \ar') \ileadstose ¬\prop$.
+\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}, 
+the pair $(\ar, \ar')$ being understood as unordered (thus not different than $(\ar', \ar)$).
 
@@
 
-We say that severe $\prop$-unstability happens iff $\forall \ar, [\exists \ar^+ \suchthat (\ar, \ar^+) \ileadstose \prop] ∧ [\exists \ar^− \suchthat (\ar, \ar^−) \ileadstose ¬\prop]$.
-\footnote{Severe $\prop$-unstability happens iff severe $¬\prop$-unstability happens.}
-\footnote{Here is an example of severe $\prop$-unstability. $\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstose \prop$.}
+We say that a situation is $(\prop, ¬\prop)\text{-unstable}$ iff $\forall \ar, [\exists \ar^+ \suchthat (\ar, \ar^+) \ileadstose \prop] ∧ [\exists \ar^− \suchthat (\ar, \ar^−) \ileadstose ¬\prop]$.
+\footnote{Example of $(\prop, ¬\prop)\text{-unstable}$: $\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstose \prop$.}
 
 \begin{theorem}
-	If $\prop \notin \iposs ∧ ¬\prop \notin \iposs$, severe $\prop$-unstability happens.
+	$\prop \notin \iposs ∧ ¬\prop \notin \iposs ⇔ (\prop, ¬\prop)\text{-unstable}$.
 \end{theorem}
@@
 \end{theorem}
-This is because $\ar^+$ is $\propsuredec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstosst \prop$ hence $(\ar^+, \ar^−) \ileadstose \prop$ (using A1).
+This is because some $\ar^+$ is $\propsuredec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstosst \prop$ hence $(\ar^+, \ar^−) \ileadstose \prop$ (using A1).
 
@@
 	A situation is $\prop$-clear-cut iff $\prop \notin \iposs ⇒ ¬\prop \in \isure$.
-\footnote{Here is an example of non $\prop$-clear-cut situation with no severe $\prop$-unstability.
-$\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstope \prop, (\ar, \ar') \ileadstopst ¬\prop$.}
+A situation is $(\prop, ¬\prop)$-clear-cut iff $\prop \notin \isure ∧ ¬\prop \notin \isure ⇒ \prop \in \iposs ∧ ¬\prop \in \iposs$.
+\footnote{$\prop\text{-CC} ∧ ¬\prop\text{-CC} ⇔ (¬\prop \in \isure ∨ \prop \in \iposs) ∧ (\prop \in \isure ∨ ¬\prop \in \iposs) ⇔ (¬\prop \in \isure ∧ \prop \in \isure) ∨ (¬\prop \in \isure) ∨ (\prop \in \isure) ∨ (\prop \in \iposs ∧ ¬\prop \in \iposs) ⇔ (\prop, ¬\prop)\text{-CC}$.}
+\footnote{$\overline{\prop\text{-CC}} ∧ \overline{¬\prop\text{-CC}} ⇔ (\prop, ¬\prop)$-unstability.}
+\footnote{Example of $\overline{¬\prop\text{-CC}} ∧ \prop \in \iposs$ (thus with $\prop\text{-CC}$ and no $(\prop, ¬\prop)$-unstability): $\forall (\ar, \ar'), (\ar, \ar') \ileadstose \prop, (\ar, \ar') \ileadstope ¬\prop, (\ar, \ar') \ileadstopst \prop$.
+In such a situation, it is unclear whether $\prop$ holds rather than $¬\prop$ or both $\prop$ and $¬\prop$.}
+\footnote{Hence (with possible meaning merely possible and not sure), for a given pair $(t, ¬t)$, either both are possible, or one is sure, or only $¬\prop$-CC and $¬t \in \iposs$ and $t \notin \iposs$, or only $\prop$-CC and $t \in \iposs$ and $¬t \notin \iposs$, or no CC and $(\prop, ¬\prop)$-unstable.}
 \footnote{Something like Axiom JU should be sufficient for CC.
+We say $(\ar, \ar')$ is $\prop$-unstable iff $(\ar, \ar') \ileadstose \prop ∧ (\ar, \ar') \ileadstose ¬\prop$.
 JU: If $(\ar, \ar')$ is $\prop$-unstable, then $\exists \ar_2 \in \allargs$ such that for $(\ar_1, \ar_0) = (\ar, \ar')$ or for $(\ar_1, \ar_0) = (\ar', \ar)$, $\ar_2$ attacks decisively $\ar_1$, where we mean by this that $\ar_2$ combined with $\ar_0$ is decisive.
@@
 
-\subsection{Possible outcomes}
-We know $\prop \in \isure ⇒ ¬\prop \notin \iposs$ and $\prop \in \isure ⇒ \prop \in \iposs$.
-
-Here are the remaining possibilities, considering the four pairs $(\prop, \iposs)$, $(\prop, \isure)$, $(¬\prop, \iposs)$, $(¬\prop, \isure)$.
-(A pair $(\prop, T)$ not mentioned means $\prop \notin T$.)
-\begin{labeling}{Unstability, $¬\prop$ poss}
-	\item[All poss] $\prop \in \iposs$, $¬\prop \in \iposs$
-	\item[$\prop$ sure] $\prop \in \iposs$, $\prop \in \isure$
-	\item[$¬\prop$ sure] (symmetric)
-	\item[Unstability, $\prop$ poss] $\prop \in \iposs$ (oddity: $¬\prop \notin \iposs$ should imply $\prop \in \isure$)
-	\item[Unstability, $¬\prop$ poss] (symmetric)
-	\item[Strong unstability] (both oddities above)
-\end{labeling}
+$\prop$ is provably possible, $\prop \in \ipposs$, iff $\prop \in \iposs ∧ ¬\prop\text{-CC}$.
+\footnote{$\prop \in \ipposs ⇔ \prop \in \iposs ∧ (\prop, ¬\prop)\text{-CC}$ (because $\prop \in \iposs ⇒ \prop\text{-CC}$).}
+\footnote{
+\begin{itemize}
+	\item $\prop \in \ipposs ∧ ¬\prop \in \ipposs ⇔ \prop \in \iposs ∧ ¬\prop \in \iposs ⇔ \prop \in \iposs ∧ ¬\prop \in \iposs ∧ (\prop, ¬\prop)\text{-CC} ⇔ \prop \notin \isure ∧ ¬\prop \notin \isure ∧ (\prop, ¬\prop)\text{-CC}$
+	\item $\prop \in \ipposs ∧ ¬\prop \notin \ipposs ⇔ \prop \in \iposs ∧ (\prop, ¬\prop)\text{-CC} ∧ ¬\prop \notin \iposs ⇔ \prop \in \isure$
+	\item $\prop \notin \ipposs ∧ ¬\prop \notin \ipposs ⇔ \overline{\prop\text{-CC}} ∨ \overline{¬\prop\text{-CC}}$.
+\end{itemize}
+}
 
 \section{Models}
-A model is a triple $(\mbeats, \mleadsto, +)$ defined as follows and satisfying the constraints as indicated here.
+A model is a triple $(\mbeats, \mleadsto, +)$ defined as follows and satisfying the following constraints.
 
@@
 Notation. Let $\mleadstoinv(\alltopic) \subseteq \clargs$ denote the subset of arguments supporting propositions. 
-$\mbeats(\ar_2)$: arguments that $\ar_2$ attacks, $\ar_1 \in \mbeats(\ar_2) ⇔ \ar_2 \mbeats \ar_1$.
-We write $\args \mbeats \ar$ to mean that $\forall \ar' \in \args: \ar' \mbeats \ar$, and similarly for other binary relations.
+$\mbeats(\args)$: arguments that $\args$ attacks, $\ar_1 \in \mbeats(\args) ⇔ \exists \ar_2 \in \args \suchthat \ar_2 \mbeats \ar_1$; $\mbeatsinv(\ar)$: arguments attacking $\ar$, $\ar_2 \in \mbeatsinv(\ar) ⇔ \ar_2 \mbeats \ar$.
 
-Given a decision situation, define $\wibeatse[\prop], \nwibeatse[¬\prop] \subseteq \mbeats$ as follows.
+Given a decision situation, we define the relations $\wibeatse[\prop], \nwibeatse[¬\prop] \subseteq \mbeats$ in order to obtain the following result.
 
-Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
+Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
 \footnote{Or $\ar_2 \ileadsto \prop ∧ ¬\prop \notin \mleadsto(\allargs) ∧ (\ar_3, \ar_2) \ileadstope ¬\prop$.}
@@
 
-This is well defined thanks to the following construction.
+This is done with the following construction.
 Given a model. 
 \begin{itemize}
-	\item Define a root as an argument that $\mbeats$-attacks nobody. 
-	\item Associate to each $\ar \in \clargs$ its depth $d(\ar)$, the distance to the farthest root: $d(\ar) = 0$ iff $\ar$ is a root and $d(\ar) = k+1$ iff $\ar$ $\mbeats$-attacks some $\ar'$ of depth $k$ and $\mbeats$-attacks no $\ar'$ of depth superior to $k$ (thus $d(\ar) = 1$ iff $\ar$ attacks some and only root nodes; $d(\ar) = 2$ iff $\ar$ attacks some node of depth 1 and only nodes of depth 1 or 0; and so on).
+	\item Define a root as an argument that $\mbeats$-attacks nothing. 
+	\item Associate to each $\ar \in \clargs$ its depth $d(\ar)$, the distance to the farthest root: $d(\ar) = 0$ iff $\ar$ is a root and $d(\ar) = k+1$ iff $\ar$ $\mbeats$-attacks some $\ar'$ of depth $k$ and $\mbeats$-attacks no $\ar'$ of depth superior to $k$.
+\footnote{Thus $d(\ar) = 1$ iff $\ar$ attacks some and only root nodes; $d(\ar) = 2$ iff $\ar$ attacks some node of depth 1 and only nodes of depth 1 or 0; and so on.}
 	\item Observe that if $\ar_3 \mbeats \ar_2$ and $d(\ar_3) = k+1$, then $d(\ar_2) ≤ k$. 
-	\item Define $\wibeatse[\prop]_{(0)} = \nwibeatse[\prop]_{(0)} = \emptyset$. %as $\ar_3 \wibeatse[\prop]_{(1)} \ar_2$ iff $d(\ar_3) = 1 ∧ \ar_2 \ileadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop$. 
-%	\item Define $\nwibeatse[\prop]_{(1)}$ as $\ar_3 \nwibeatse[\prop]_{(1)} \ar_2$ iff $d(\ar_3) = 1 ∧ \ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstope \prop$. 
-	\item Define $\wibeatse[\prop]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\prop]_{(k+1)} \ar_2$ iff, first, $d(\ar_3) = k+1$, and second, $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\prop]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
+	\item Define $\wibeatse[\prop]_{(0)} = \nwibeatse[\prop]_{(0)} = \emptyset$. 
+	\item Define $\wibeatse[\prop]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\prop]_{(k+1)} \ar_2$ iff $\ar_3 \mbeats \ar_2$, $d(\ar_3) = k+1$, and: $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\prop]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
 Proceed similarly for $\nwibeatse[\prop]_{(k+1)}$.
@@
 \section{Conditions}
-All these conditions assume that a decision situation $(\allalts, \allargs, \{\ibeatse[\prop]\}, \{\ibeatse[\prop, \text{sure}]\})$ and a model $\eta = (\mbeats, \mleadsto, +)$ are given.
+All these conditions assume that a decision situation $(\allalts, \allargs, …)$ and a model $\eta = (\mbeats, \mleadsto, +)$ are given.
 
-Define $\argsdec = \clargs \setminus \text{im}(\wibeatse)$ the decisive arguments according to $\wibeatse$, or $\wibeatse$-decisive arguments for short: $\ar \in \argsdec ⇔ \wibeatseinv(\ar) = \emptyset$.
+Define $\argsdec^\prop = \clargs \setminus \text{im}(\wibeatse[\prop])$ the decisive arguments according to $\wibeatse[\prop]$, or $\wibeatse[\prop]$-decisive arguments for short: $\ar \in \argsdec ⇔ \wibeatseinv[\prop](\ar) = \emptyset$.
 
 \begin{definition}[Reinstatement]
-	Given $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3 \in \argsdec$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
+	Given $\ar_3 \wibeatse[\prop] \ar_2 \wibeatse[\prop] \ar_1, \ar_3 \in \argsdec^\prop$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
 	\footnote{TODO the condition must be $\wibeatseinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$ to allow $\ar_5 \mbeats \ar_4 \mbeats \ar_3 \mbeats \ar_2 \mbeats \ar_1$ and $\ar_5 \mbeats \ar_4 \mbeats \ar_3 + \ar_1$, considering that possibly $\ar_3$ is $\wibeatse$-decisive.
@@
 Replacement-1 applies to all and requires attack at least as large; Replacement-2 applies to restricted supports and requires no new $\ibeatse$-attacks.}
+	\footnote{Is Reinf equivalent to Justifiable unstability?
+Define $\ar_3 \wibeatsst[\prop] \ar_2 ⇔ \ar_3 \wibeatse[\prop] \ar_2 ∧ ¬(\ar_3 \nwibeatse[\prop] \ar_2)$.
+Prove that $\ar_3 \wibeatsst[\prop] \ar_2 \wibeatse[\prop] \ar_2 ⇒ ¬(\ar_2 \wibeatse[\prop] \ar_3 + \ar_1)$.}
 \end{definition}
@@
 \begin{definition}[Justifiable unstability]
-	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse \ar_1, \ar_2 \nwibeatse \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse \ar_2$.
+	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse[\prop] \ar_1, \ar_2 \nwibeatse[\prop] \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$.
 \end{definition}
 
+$\ar$ is $\prop$-defended iff $\wibeatseinv[\prop](\ar) \subseteq \wibeatse[\prop](\argsdec^\prop)$ (its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments).
+
 \begin{definition}[Finite defense]
-	If $\wibeatseinv(\ar) \subseteq \wibeatse(\argsdec)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse(\args)$.
+	If $\wibeatseinv[\prop](\ar) \subseteq \wibeatse[\prop](\argsdec^\prop)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse[\prop](\args)$.
 \footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check).
@@
 
-Define $R$, the reinstates relation, as follows: $\ar_3 R \ar_1$ iff $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$ (for some $\ar_2$), $\ar_3 \in \argsdec$.
-Define $\gdargs$ as the transitive closure of $\mleadstoinv(\alltopic)$ under $R$.
+Define $R^\prop$, the reinstates relation, as follows: $(\ar_3 + \ar_1) R^\prop \ar_1$ iff $\ar_3 \wibeatse[\prop] \ar_2 \wibeatse[\prop] \ar_1$ (for some $\ar_2, \prop$), $\ar_3 \in \argsdec^\prop$.
+Define $\gdargs^\prop$ as the transitive closure of $\mleadstoinv(\alltopic)$ under $R^\prop$.
+Given $\prop, \ar \in \gdargs^\prop, \ar' \in \allargs$, define $\ar' \ibeatse[\prop] \ar ⇔ (\ar', \ar) \ileadstose ¬\prop$.
 \begin{definition}[Covering]
-	$\forall \ar \in \gdargs, \ar' \in \allargs: \ar' \ibeatse \ar ⇒ \ar' \mbeats \ar$. \footnote{Specify $\ibeatse$.}
+	$\forall \prop, \ar \in \gdargs^\prop, \ar' \in \allargs: \ar' \ibeatse[\prop] \ar ⇒ \ar' \mbeats \ar$. 
 \end{definition}
@@
 	$\forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$.
-Furthermore, if $¬(\clargs \mleadsto \prop), \forall \ar_1 \mleadsto ¬\prop, \ar \in \allargs: \ar_1 \ibeatse[\prop] \ar$.
+Furthermore, if $¬(\clargs \mleadsto \prop), \forall \ar_1 \mleadsto ¬\prop, \ar \in \allargs: (\ar_1, \ar) \ileadstose ¬\prop$.
 	\footnote{If the model claims $¬\prop \in \isure$, this requires clear-cut (for that prop), so we must mandate it (hopefully A3 or an equivalent such as Justifiable unstability fits).
-Thus we only need to prove $\prop \notin \iposs$, for which $\ar_1 \ibeatse[\prop] \ar$ suffices.}
+Thus we only need to prove $\prop \notin \iposs$, for which $(\ar_1, \ar) \ileadstose ¬\prop$ suffices.}
 \end{definition}
@@
 \begin{proof}
-$\ar$ is defended iff its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments.
+First, we want to prove that $\ar_1$ $\prop$-defended implies $\ar_1$ replaceable by some $\wibeatse[\prop]$-decisive $\ar$, and if $\ar_1 \in \gdargs$, then its replacer $\ar$ is in $\gdargs$ as well.
 
-First, we want to prove that $\ar_1$ defended implies $\ar_1$ replaceable by some $\wibeatse$-decisive $\ar$, and if $\ar_1 \in \gdargs$, then its replacer $\ar$ is in $\gdargs$ as well.
-
-By hypothesis, $\wibeatseinv(\ar_1) \subseteq \wibeatse(\argsdec)$. Thus, $\exists \args \subseteq \argsdec \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse(\args)$, $\args$ finite [Finite defense].
+Because $\ar_1$ is $\prop$-defended, $\exists \args \subseteq \argsdec^\prop \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse[\prop](\args)$, $\args$ finite [Finite defense].
 
@@
 $\ar_{3, 1} + \ar_1$ replaces $\ar_1$, and $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_{3, 1})$ [Reinstatement].
-Hence, $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \wibeatse(\args) \setminus \mbeats(\ar_{3, 1})$.
+Hence, $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \wibeatse[\prop](\args) \setminus \mbeats(\ar_{3, 1})$.
 Iterate by picking any $\ar_{3, 2} \in \args$ such that $\ar_{3, 2} \wibeatse \ar_2 \wibeatse \ar_{3, 1} + \ar_1$ (if there’s none, $\ar_{3, 1} + \ar_1 \in \argsdec$ and we’re done) and obtaining $\ar_{3, 2} + (\ar_{3, 1} + \ar_1)$ replacing $\ar_{3, 1} + \ar_1$ (hence, replacing $\ar_1$) with $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \mbeatsinv(\ar_{3, 1} + \ar_1) \setminus \mbeats(\ar_{3, 2})$.
-Hence, $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \wibeatse(\args) \setminus \mbeats(\ar_{3, 1}) \setminus \mbeats(\ar_{3, 2})$.
-Iterating in such a way over the finite set $\args$ will finally yield an element that is $\wibeatse$-decisive.
+Hence, $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \wibeatse[\prop](\args) \setminus \mbeats(\ar_{3, 1}) \setminus \mbeats(\ar_{3, 2})$.
+Iterating in such a way over the finite set $\args$ will finally yield an element that is $\wibeatse[\prop]$-decisive.
 The last point, $\ar_1 \in \gdargs ⇒ \ar \in \gdargs$, follows from the definition of $\gdargs$.
 
-Second, we want to prove that if $\ar_1$ not defended and has no decisive $\wibeatse$-attackers (meaning that $\wibeatseinv(\ar_1) \subseteq \overline{\argsdec}$), then $\ar_1$ is $\wibeatse$-attacked by some $\ar_2$ that is not defended and has no decisive $\wibeatse$-attacker.
+Second, we want to prove that if $\ar_1$ is not $\prop$-defended and has no decisive $\wibeatse[\prop]$-attackers (meaning that $\wibeatseinv[\prop](\ar_1) \subseteq \overline{\argsdec^\prop}$), then $\ar_1$ is $\wibeatse[\prop]$-attacked by some $\ar_2$ that is not $\prop$-defended and has no decisive $\wibeatse[\prop]$-attacker.
 
-Consider $\ar_1$ not defended and having no decisive $\wibeatse$-attackers.
-Because $\ar_1$ is not defended, by definition, it is $\wibeatse$-attacked by some $\ar_2$ that has no decisive $\wibeatse$-attacker.
+Consider $\ar_1$ not $\prop$-defended and having no decisive $\wibeatse[\prop]$-attackers.
+Because $\ar_1$ is not $\prop$-defended, by definition, it is $\wibeatse[\prop]$-attacked by some $\ar_2$ that has no decisive $\wibeatse[\prop]$-attacker.
 Because $\ar_1$ has no decisive attacker, $\ar_2$ is not decisive.
@@
 
+We conclude from this second point that if $\wibeatseinv[\prop](\ar_1) \subseteq \overline{\argsdec^\prop}$, then $\ar_1$ is $\prop$-defended.
+Otherwise, it is attacked by some $\ar_2$, on which the condition applies in turn, thus attacked by some $\ar_3$, on which the condition applies, and iterating in this way and using finiteness of $\wibeatse[\prop]$ leads to a contradiction.
+
 Third, consider an argument $\ar_1 \in \mleadstoinv(\alltopic)$.
-It has no decisive $\ibeatse$-attacker: as $\ar_1 \in \gdargs$, any $\ibeatse$-attack is a $\wibeatse$-attack [Covering], and $\ar_1$ has no decisive $\wibeatse$-attacker [Obs val].
-Also, $\ar_1$ is defended: assume it is not, then by our second point in this proof some $\ar_2 \wibeatse \ar_1$, with $\ar_2$ not defended and with no decisive $\wibeatse$-attacker, and iterating and using finiteness of $\wibeatse$ leads to a contradiction.
-Hence, by our first point in this proof, $\ar_1$ is replaceable by some $\wibeatse$-decisive $\ar \in \gdargs$.
-As $\ar \in \gdargs$, any $\ibeatse$-attack is a $\wibeatse$-attack [Covering], thus $\ar$ is $\ibeatse$-decisive.
+If some $\ar_2 \wibeatse[\prop] \ar_1$ then $\ar_3 \wibeatse[\prop] \ar_2$ [Obs val].
+Thus, $\wibeatseinv[\prop](\ar_1) \subseteq \overline{\argsdec^\prop}$.
+Thus, $\ar_1$ is $\prop$-defended, by our second point.
+Hence, by our first point in this proof, $\ar_1$ is replaceable by some $\wibeatse[\prop]$-decisive $\ar \in \gdargs$.
+We obtain that $\forall \ar' \in \allargs: ¬(\ar' \wibeatse[\prop] \ar)$.
+As $\ar \in \gdargs$, $\ar' \ibeatse[\prop] \ar ⇒ \ar' \wibeatse[\prop] \ar$ [Covering], thus we obtain $¬(\ar' \ibeatse[\prop] \ar)$, hence $\ar$ is $\prop$-poss-dec and $\prop \in \iposs$.
 \end{proof}
@@
 \section{Todo}
+We define $(\ar, \ar') \ileadstopst \prop ⇔ \ar' \nibeatsst[\prop] \ar ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, and $(\ar, \ar') \ileadstosst ¬\prop ⇔ \ar \nibeatsst[¬\propsure] \ar' ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$.
+Hence, $(\ar, \ar') \ileadstose ¬\prop ⇔ \ar' \ibeatse[\prop] \ar ⇔ ¬(\ar' \nibeatsst[\prop] \ar) ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\}$, and $(\ar, \ar') \ileadstope \prop ⇔ \ar \ibeatse[¬\propsure] \ar' ⇔ ¬(\ar \nibeatsst[¬\propsure] \ar') ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\}$.
+
 \begin{itemize}

### 2018-01-27 simple.tex
Started using alternative notation with phi

@@
 
-$\ar$ is 
-\begin{itemize}
-	\item $\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$
-	\item $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$
-\end{itemize}
+We also define $\Phi = \alltopic × \set{\text{possible}, \text{sure}}$, and $\forall \phi = (\prop, \text{possible}) \in \Phi: (\ar, \ar') \ileadstost \phi ⇔ (\ar, \ar') \ileadstopst \prop$ and $\forall \phi = (\prop, \text{sure}) \in \Phi: (\ar, \ar') \ileadstost \phi ⇔ (\ar, \ar') \ileadstosst \prop$.
+We define the negation operator $¬$ over $\Phi$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
+It follows that $¬¬\phi = \phi$.
+We write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$.
+\footnote{From (A1) and (A2) we can write, using this notation, $(\ar, \ar') \ileadstost \phi ⇒ (\ar, \ar') \nileadstost ¬\phi$.}
+
+$\ar$ is $\phi\text{-dec} ⇔ \forall \ar': (\ar', \ar) \ileadstost \prop$. We also say that $\ar$ is $\propsuredec$ or $\proppossdec$ when $\phi=(\prop, \text{sure})$ or $\phi=(\prop, \text{possible}$.
+\footnote{$\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$, $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$.}
 

### 2018-01-28 simple.tex
Intro with phi’s

@@
 
-TODO do everything with only one relation.
-Define for each prop: $\prop^{s}$ and $\prop^p$, and define $¬(\prop^s) = (¬\prop)^p$, and we can do everything with $(\ar, \ar') \ileadsto \prop^p$ (defined as $\ileadstopst \prop$) and $(\ar, \ar') \ileadsto \prop^s$ (defined as $\ileadstosst \prop$).
-
 Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on (and their negations $\ileadstose$ and $\ileadstope$), together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
@@
 \footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}, 
-the pair $(\ar, \ar')$ being understood as unordered (thus not different than $(\ar', \ar)$).
+the pair $(\ar, \ar')$ being understood as unordered (thus $(\ar, \ar') \ileadstosst \prop ⇔ (\ar', \ar) \ileadstosst \prop$, and similarly for $\ileadstopst$).
 
@@
 It follows that $¬¬\phi = \phi$.
-We write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$.
-\footnote{From (A1) and (A2) we can write, using this notation, $(\ar, \ar') \ileadstost \phi ⇒ (\ar, \ar') \nileadstost ¬\phi$.}
+We write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstost ¬\phi$.
+\footnote{\label{ft:sttoe}From (A1) and (A2) we can write, using this notation, $(\ar, \ar') \ileadstost \phi ⇒ (\ar, \ar') \ileadstoe \phi$.}
 
-$\ar$ is $\phi\text{-dec} ⇔ \forall \ar': (\ar', \ar) \ileadstost \prop$. We also say that $\ar$ is $\propsuredec$ or $\proppossdec$ when $\phi=(\prop, \text{sure})$ or $\phi=(\prop, \text{possible}$.
-\footnote{$\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$, $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$.}
+$\ar$ is $\phi\text{-dec} ⇔ \forall \ar': (\ar', \ar) \ileadstost \phi$. 
+\footnote{Equivalently: $\ar \ \phidec ⇔ \exists \ar \suchthat [\ileadstostinv(\phi)](\ar) = \allargs$.}
+\footnote{We also say that $\ar$ is $\propsuredec$ or $\proppossdec$ when $\phi=(\prop, \text{sure})$ or $\phi=(\prop, \text{possible})$.
+$\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$, $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$.}
 
-We can now define $\iposs, \isure \subseteq \alltopic$:
-\begin{itemize}
-	\item $\prop \in \iposs ⇔ \exists \ar \ \proppossdec$. 
-\footnote{\label{ft:notposs}$\prop \notin \iposs ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstose ¬\prop$.}
-	\item $\prop \in \isure ⇔ \exists \ar \ \propsuredec$. 
-\footnote{\label{ft:notsure}$¬\prop \notin \isure ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstope \prop$.}
-\end{itemize}
+We can now define $\iPhi \subseteq \Phi$: $\phi \in \iPhi ⇔  \exists \ar \ \phi\text{-dec}$.
+\footnote{Equivalently: $\iPhi = \bigcup_{\ar \in \allargs} \bigcap{\ar' \in \allargs} \ileadstost(\ar', \ar)$.}
+\footnote{$\phi \in \iPhi ⇔ \exists \ar \suchthat \allargs × \{\ar\} \ileadstost \phi$.}
+\footnote{\label{ft:notposs}$\prop \in \iposs ⇔ \exists \ar \ \proppossdec$ and $\prop \notin \iposs ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstose ¬\prop$.}
+\footnote{\label{ft:notsure}$\prop \in \isure ⇔ \exists \ar \ \propsuredec$ and $¬\prop \notin \isure ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstope \prop$.}
 
@@
 \begin{theorem}
-	$\prop \in \isure ⇒ ¬\prop \notin \iposs$.
+	$\phi \in \iPhi ⇒ ¬\phi \notin \iPhi$.
 \end{theorem}
-This is because some $\ar^+$ is $\propsuredec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstosst \prop$ hence $(\ar^+, \ar^−) \ileadstose \prop$ (using A1).
+This is because some $\ar^+$ is $\phidec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstost \phi$ hence $(\ar^+, \ar^−) \ileadstoe \phi$ (using \cref{ft:sttoe}).
 
 \begin{theorem}
-	$\prop \in \isure ⇒ \prop \in \iposs$.
+	$(\prop, \text{sure}) \in \iPhi ⇒ (\prop, \text{possible}) \in \iPhi$.
 \end{theorem}
@@
 \begin{definition}[Clear-cut]
-	A situation is $\prop$-clear-cut iff $\prop \notin \iposs ⇒ ¬\prop \in \isure$.
-A situation is $(\prop, ¬\prop)$-clear-cut iff $\prop \notin \isure ∧ ¬\prop \notin \isure ⇒ \prop \in \iposs ∧ ¬\prop \in \iposs$.
+	A situation is $\prop$-clear-cut iff $(\prop, \text{sure}) \notin \iPhi ⇒ (¬\prop, \text{possible}) \in \iPhi$.
+A situation is $(\prop, ¬\prop)$-clear-cut iff $\prop \notin \isure ∧ ¬\prop \notin \isure ⇒ \prop \in \iposs ∧ ¬\prop \in \iposs$, equivalently, $\phi \notin \iPhi ⇔ ¬\phi \in \iPhi$.
 \footnote{$\prop\text{-CC} ∧ ¬\prop\text{-CC} ⇔ (¬\prop \in \isure ∨ \prop \in \iposs) ∧ (\prop \in \isure ∨ ¬\prop \in \iposs) ⇔ (¬\prop \in \isure ∧ \prop \in \isure) ∨ (¬\prop \in \isure) ∨ (\prop \in \isure) ∨ (\prop \in \iposs ∧ ¬\prop \in \iposs) ⇔ (\prop, ¬\prop)\text{-CC}$.}
@@
 $\mbeats(\args)$: arguments that $\args$ attacks, $\ar_1 \in \mbeats(\args) ⇔ \exists \ar_2 \in \args \suchthat \ar_2 \mbeats \ar_1$; $\mbeatsinv(\ar)$: arguments attacking $\ar$, $\ar_2 \in \mbeatsinv(\ar) ⇔ \ar_2 \mbeats \ar$.
+We write $\ar \mleadsto (\prop, \text{possible})$ for $\ar \mleadsto \prop$ and $\ar \mleadsto (\prop, \text{sure})$ for $\ar \mleadsto \prop ∧ (¬\prop \notin \mleadsto(\allargs))$.
 

### 2018-01-29 simple.tex
Finished refactor with \phi

@@
 We can now define $\iPhi \subseteq \Phi$: $\phi \in \iPhi ⇔  \exists \ar \ \phi\text{-dec}$.
-\footnote{Equivalently: $\iPhi = \bigcup_{\ar \in \allargs} \bigcap{\ar' \in \allargs} \ileadstost(\ar', \ar)$.}
+\footnote{Equivalently: $\iPhi = \bigcup_{\ar \in \allargs} \bigcap_{\ar' \in \allargs} \ileadstost(\ar', \ar)$.}
 \footnote{$\phi \in \iPhi ⇔ \exists \ar \suchthat \allargs × \{\ar\} \ileadstost \phi$.}
@@
 
-Given a decision situation, we define the relations $\wibeatse[\prop], \nwibeatse[¬\prop] \subseteq \mbeats$ in order to obtain the following result.
+Given a decision situation, we define the relations $\wibeatse[\phi], \nwibeatse[¬\phi] \subseteq \mbeats$ in order to obtain the following result.
 
-Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
-\footnote{Or $\ar_2 \ileadsto \prop ∧ ¬\prop \notin \mleadsto(\allargs) ∧ (\ar_3, \ar_2) \ileadstope ¬\prop$.}
+Given $\ar_3 \mbeats \ar_2, \phi \in \Phi$: $\ar_3 \wibeatse[\phi] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \nwibeatse[\phi] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe ¬\phi]$.
 
-Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \nwibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstope \prop]$.
+Given $\ar_3 \mbeats \ar_2, \phi \in \iPhi$: $\ar_3 \nwibeatse[\phi] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \wibeatse[\phi] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe \phi]$.
 
@@
 	\item Observe that if $\ar_3 \mbeats \ar_2$ and $d(\ar_3) = k+1$, then $d(\ar_2) ≤ k$. 
-	\item Define $\wibeatse[\prop]_{(0)} = \nwibeatse[\prop]_{(0)} = \emptyset$. 
-	\item Define $\wibeatse[\prop]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\prop]_{(k+1)} \ar_2$ iff $\ar_3 \mbeats \ar_2$, $d(\ar_3) = k+1$, and: $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\prop]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
-Proceed similarly for $\nwibeatse[\prop]_{(k+1)}$.
-	\item Define $\wibeatse[\prop] = \bigcup_{k ≥ 0} \wibeatse[\prop]_{(k)}$, and similarly for $\nwibeatse[\prop]$.
+	\item Define $\wibeatse[\phi]_{(0)} = \nwibeatse[\phi]_{(0)} = \emptyset$. 
+	\item Define $\wibeatse[\phi]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\phi]_{(k+1)} \ar_2$ iff $\ar_3 \mbeats \ar_2$, $d(\ar_3) = k+1$, and: $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\phi]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe ¬\phi]$.
+Proceed similarly for $\nwibeatse[\phi]_{(k+1)}$.
+	\item Define $\wibeatse[\phi] = \bigcup_{k ≥ 0} \wibeatse[\phi]_{(k)}$, and similarly for $\nwibeatse[\phi]$.
 \end{itemize}
 
-{Check: Given $\ar_4 \mbeats \ar_3, \ar_3 \notin \mleadstoinv(\alltopic)$, with $\ar_2 \in \mbeats(\ar_3)$ ⇒ ($\ar_2$ and $\ar_4 + \ar_2$ $\mbeats$-attack only root nodes and do not support any proposition): $\ar_4 \wibeatse[\prop] \ar_3$ iff
+{Check: Given $\ar_4 \mbeats \ar_3, \ar_3 \notin \mleadstoinv(\alltopic)$, with $\ar_2 \in \mbeats(\ar_3)$ ⇒ ($\ar_2$ and $\ar_4 + \ar_2$ $\mbeats$-attack only root nodes and do not support any proposition): $\ar_4 \wibeatse[\phi] \ar_3$ iff
 \begin{itemize}
-	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\ar_3 \wibeatse[\prop] \ar_2) ∧ (\ar_3 \nwibeatse[\prop] \ar_4 + \ar_2)]$ iff 
-	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_4 + \ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_4 + \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)]$ iff
-	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_1 \ileadsto t ∧ (\ar_2, \ar_1) \ileadstose ¬\prop ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ (\ar_3 + \ar_1, \ar_2) \ileadstope \prop ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_1 \mleadsto \prop ∧ (\ar_4 + \ar_2, \ar_1) \ileadstose ¬\prop ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ (\ar_4 + \ar_2, \ar_3 + \ar_1) \ileadstose ¬\prop)]$.
+	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\ar_3 \wibeatse[\phi] \ar_2) ∧ (\ar_3 \nwibeatse[\phi] \ar_4 + \ar_2)]$ iff 
+	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \nwibeatse[\phi] \ar_3 + \ar_1) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_4 + \ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_4 + \ar_2 \wibeatse[\phi] \ar_3 + \ar_1)]$ iff
+	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_1 \ileadsto t ∧ (\ar_2, \ar_1) \ileadstose ¬\phi ∧ \ar_3 + \ar_1 \ileadsto \phi ∧ (\ar_3 + \ar_1, \ar_2) \ileadstope \phi ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_1 \mleadsto \phi ∧ (\ar_4 + \ar_2, \ar_1) \ileadstose ¬\phi ∧ \ar_3 + \ar_1 \ileadsto \phi ∧ (\ar_4 + \ar_2, \ar_3 + \ar_1) \ileadstose ¬\phi)]$.
 \end{itemize}
@@
 
-Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop] \ar_1$, we have: $\ar_3 \wibeatse[\prop] \ar_2 ∨ \ar_3 \nwibeatse[\prop] \ar_2$.
+Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\phi] \ar_1$, we have: $\ar_3 \wibeatse[\phi] \ar_2 ∨ \ar_3 \nwibeatse[\phi] \ar_2$.
 
-Define $\ar_2 \wibeatse \ar_1 ⇔ \exists \prop \in \alltopic \suchthat \ar_2 \wibeatse[\prop] \ar_1$.
+Define $\ar_2 \wibeatse \ar_1 ⇔ \exists \phi \in \alltopic \suchthat \ar_2 \wibeatse[\phi] \ar_1$.
 
@@
 
-Define $\argsdec^\prop = \clargs \setminus \text{im}(\wibeatse[\prop])$ the decisive arguments according to $\wibeatse[\prop]$, or $\wibeatse[\prop]$-decisive arguments for short: $\ar \in \argsdec ⇔ \wibeatseinv[\prop](\ar) = \emptyset$.
+Define $\argsdec^\phi = \clargs \setminus \text{im}(\wibeatse[\phi])$ the decisive arguments according to $\wibeatse[\phi]$, or $\wibeatse[\phi]$-decisive arguments for short: $\ar \in \argsdec^\phi ⇔ \wibeatseinv[\phi](\ar) = \emptyset$.
+
+We say that $\ar$ replaces $\ar_1$ iff $\mbeats(\ar_1) \subseteq \mbeats(\ar)$.
 
 \begin{definition}[Reinstatement]
-	Given $\ar_3 \wibeatse[\prop] \ar_2 \wibeatse[\prop] \ar_1, \ar_3 \in \argsdec^\prop$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
+	Given $\ar_3 \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1, \ar_3 \in \argsdec^\phi$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
 	\footnote{TODO the condition must be $\wibeatseinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$ to allow $\ar_5 \mbeats \ar_4 \mbeats \ar_3 \mbeats \ar_2 \mbeats \ar_1$ and $\ar_5 \mbeats \ar_4 \mbeats \ar_3 + \ar_1$, considering that possibly $\ar_3$ is $\wibeatse$-decisive.
@@
 	\footnote{The stronger condition mandating $\mbeatsinv(\ar_3 + \ar_1) \subseteq \wibeatseinv(\ar_1) \setminus \mbeats(\ar_3)$ would be more difficult to check: when some $\ar_2 \wibeatse \ar_3 + \ar_1$, we’d need to check not only that $\ar_2 \mbeats \ar_1$ but also $\ar_2 \wibeatse \ar_1$.}
-	\footnote{We do not mandate that $\ar_3 + \ar_1 \ileadsto \prop$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice).
-We need: Obs applies to restricted supports (one per prop decided by model); Covering applies to extended supports (restricted supports plus those obtained by reinstatement).
-Replacement-1 applies to all and requires attack at least as large; Replacement-2 applies to restricted supports and requires no new $\ibeatse$-attacks.}
+	\footnote{We do not mandate that $\ar_3 + \ar_1 \ileadsto \phi$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice).}
 	\footnote{Is Reinf equivalent to Justifiable unstability?
-Define $\ar_3 \wibeatsst[\prop] \ar_2 ⇔ \ar_3 \wibeatse[\prop] \ar_2 ∧ ¬(\ar_3 \nwibeatse[\prop] \ar_2)$.
-Prove that $\ar_3 \wibeatsst[\prop] \ar_2 \wibeatse[\prop] \ar_2 ⇒ ¬(\ar_2 \wibeatse[\prop] \ar_3 + \ar_1)$.}
+Define $\ar_3 \wibeatsst[\phi] \ar_2 ⇔ \ar_3 \wibeatse[\phi] \ar_2 ∧ ¬(\ar_3 \nwibeatse[\phi] \ar_2)$.
+Prove that $\ar_3 \wibeatsst[\phi] \ar_2 \wibeatse[\phi] \ar_2 ⇒ ¬(\ar_2 \wibeatse[\phi] \ar_3 + \ar_1)$.}
 \end{definition}
@@
 \begin{definition}[Justifiable unstability]
-	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse[\prop] \ar_1, \ar_2 \nwibeatse[\prop] \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$.
+	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse[\phi] \ar_1, \ar_2 \nwibeatse[\phi] \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\phi] \ar_2$.
 \end{definition}
 
-$\ar$ is $\prop$-defended iff $\wibeatseinv[\prop](\ar) \subseteq \wibeatse[\prop](\argsdec^\prop)$ (its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments).
+$\ar$ is $\phi$-defended iff $\wibeatseinv[\phi](\ar) \subseteq \wibeatse[\phi](\argsdec^\phi)$ (its $\wibeatse[\phi]$-attackers are $\wibeatse[\phi]$-attacked by $\wibeatse[\phi]$-decisive arguments).
 
 \begin{definition}[Finite defense]
-	If $\wibeatseinv[\prop](\ar) \subseteq \wibeatse[\prop](\argsdec^\prop)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse[\prop](\args)$.
+	If $\wibeatseinv[\phi](\ar) \subseteq \wibeatse[\phi](\argsdec^\phi)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse[\phi](\args)$.
 \footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check).
@@
 
-Define $R^\prop$, the reinstates relation, as follows: $(\ar_3 + \ar_1) R^\prop \ar_1$ iff $\ar_3 \wibeatse[\prop] \ar_2 \wibeatse[\prop] \ar_1$ (for some $\ar_2, \prop$), $\ar_3 \in \argsdec^\prop$.
-Define $\gdargs^\prop$ as the transitive closure of $\mleadstoinv(\alltopic)$ under $R^\prop$.
-Given $\prop, \ar \in \gdargs^\prop, \ar' \in \allargs$, define $\ar' \ibeatse[\prop] \ar ⇔ (\ar', \ar) \ileadstose ¬\prop$.
+Define $R^\phi$, the reinstates relation, as follows: $(\ar_3 + \ar_1) R^\phi \ar_1$ iff $\ar_3 \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1$ (for some $\ar_2, \phi$), $\ar_3 \in \argsdec^\phi$.
+Define $\gdargs^\phi$ as the transitive closure of $\mleadstoinv(\Phi)$ under $R^\phi$.
+Given $\phi, \ar \in \gdargs^\phi, \ar' \in \allargs$, define $\ar' \ibeatse[\phi] \ar ⇔ (\ar', \ar) \ileadstoe ¬\phi$.
 \begin{definition}[Covering]
-	$\forall \prop, \ar \in \gdargs^\prop, \ar' \in \allargs: \ar' \ibeatse[\prop] \ar ⇒ \ar' \mbeats \ar$. 
+	$\forall \phi, \ar \in \gdargs^\phi, \ar' \in \allargs: \ar' \ibeatse[\phi] \ar ⇒ \ar' \mbeats \ar$. 
 \end{definition}
@@
 \begin{definition}[Observable validity]
-	$\forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$.
-Furthermore, if $¬(\clargs \mleadsto \prop), \forall \ar_1 \mleadsto ¬\prop, \ar \in \allargs: (\ar_1, \ar) \ileadstose ¬\prop$.
+	$\forall \ar_2 \mbeats \ar_1 \mleadsto \phi: ¬(\ar_2 \wibeatse[\phi] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\phi] \ar_2$.
 	\footnote{If the model claims $¬\prop \in \isure$, this requires clear-cut (for that prop), so we must mandate it (hopefully A3 or an equivalent such as Justifiable unstability fits).
-Thus we only need to prove $\prop \notin \iposs$, for which $(\ar_1, \ar) \ileadstose ¬\prop$ suffices.}
+Thus we only need to prove $\prop \notin \iposs$, for which $(\ar_1, \ar) \ileadstose ¬\prop$, for each $\ar$, suffices.
+In fact, from $\ar_1$ in the model arguing for $\phi$ and $(\ar_1, \ar) \ileadstoe \phi \forall \ar \in \allargs$, we should probably be able, using the argument in the theorem about finite chains, to deduce that this is enough to conclude that $\ar_1$ is $\phidec$.}
 \end{definition}
@@
 \begin{theorem}[Validity]
-	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iposs$.
-Furthermore, if $¬\prop \in \mleadsto(\clargs) ∧ \prop \notin \mleadstoinv(\clargs)$, $¬\prop \in \isure$.
+	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iPhi$.
 \end{theorem}
 \begin{proof}
-First, we want to prove that $\ar_1$ $\prop$-defended implies $\ar_1$ replaceable by some $\wibeatse[\prop]$-decisive $\ar$, and if $\ar_1 \in \gdargs$, then its replacer $\ar$ is in $\gdargs$ as well.
+First, we want to prove that $\ar_1$ $\phi$-defended implies $\ar_1$ replaceable by some $\wibeatse[\phi]$-decisive $\ar$, and if $\ar_1 \in \gdargs^\phi$, then its replacer $\ar$ is in $\gdargs^\phi$ as well.
 
-Because $\ar_1$ is $\prop$-defended, $\exists \args \subseteq \argsdec^\prop \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse[\prop](\args)$, $\args$ finite [Finite defense].
+Because $\ar_1$ is $\phi$-defended, $\exists \args \subseteq \argsdec^\phi \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse[\phi](\args)$, $\args$ finite [Finite defense].
 
-Pick any $\ar_{3, 1} \in \args$ such that $\ar_{3, 1} \wibeatse \ar_2 \wibeatse \ar_1$ (if there’s none, $\ar_1 \in \argsdec$ and we’re done).
+Pick any $\ar_{3, 1} \in \args$ such that $\ar_{3, 1} \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1$ (if there’s none, $\ar_1 \in \argsdec^\phi$ and we’re done).
 $\ar_{3, 1} + \ar_1$ replaces $\ar_1$, and $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_{3, 1})$ [Reinstatement].
-Hence, $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \wibeatse[\prop](\args) \setminus \mbeats(\ar_{3, 1})$.
-Iterate by picking any $\ar_{3, 2} \in \args$ such that $\ar_{3, 2} \wibeatse \ar_2 \wibeatse \ar_{3, 1} + \ar_1$ (if there’s none, $\ar_{3, 1} + \ar_1 \in \argsdec$ and we’re done) and obtaining $\ar_{3, 2} + (\ar_{3, 1} + \ar_1)$ replacing $\ar_{3, 1} + \ar_1$ (hence, replacing $\ar_1$) with $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \mbeatsinv(\ar_{3, 1} + \ar_1) \setminus \mbeats(\ar_{3, 2})$.
-Hence, $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \wibeatse[\prop](\args) \setminus \mbeats(\ar_{3, 1}) \setminus \mbeats(\ar_{3, 2})$.
-Iterating in such a way over the finite set $\args$ will finally yield an element that is $\wibeatse[\prop]$-decisive.
-The last point, $\ar_1 \in \gdargs ⇒ \ar \in \gdargs$, follows from the definition of $\gdargs$.
+Hence, $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \wibeatse[\phi](\args) \setminus \mbeats(\ar_{3, 1})$.
+Iterate by picking any $\ar_{3, 2} \in \args$ such that $\ar_{3, 2} \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_{3, 1} + \ar_1$ (if there’s none, $\ar_{3, 1} + \ar_1 \in \argsdec^\phi$ and we’re done) and obtaining $\ar_{3, 2} + (\ar_{3, 1} + \ar_1)$ replacing $\ar_{3, 1} + \ar_1$ (hence, replacing $\ar_1$) with $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \mbeatsinv(\ar_{3, 1} + \ar_1) \setminus \mbeats(\ar_{3, 2})$.
+Hence, $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \wibeatse[\phi](\args) \setminus \mbeats(\ar_{3, 1}) \setminus \mbeats(\ar_{3, 2})$.
+Iterating in such a way over the finite set $\args$ will finally yield an element that is $\wibeatse[\phi]$-decisive.
+The last point, $\ar_1 \in \gdargs^\phi ⇒ \ar \in \gdargs^\phi$, follows from the definition of $\gdargs^\phi$.
 
-Second, we want to prove that if $\ar_1$ is not $\prop$-defended and has no decisive $\wibeatse[\prop]$-attackers (meaning that $\wibeatseinv[\prop](\ar_1) \subseteq \overline{\argsdec^\prop}$), then $\ar_1$ is $\wibeatse[\prop]$-attacked by some $\ar_2$ that is not $\prop$-defended and has no decisive $\wibeatse[\prop]$-attacker.
+Second, we want to prove that if $\ar_1$ is not $\phi$-defended and has no decisive $\wibeatse[\phi]$-attackers (meaning that $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$), then $\ar_1$ is $\wibeatse[\phi]$-attacked by some $\ar_2$ that is not $\phi$-defended and has no decisive $\wibeatse[\phi]$-attacker.
 
-Consider $\ar_1$ not $\prop$-defended and having no decisive $\wibeatse[\prop]$-attackers.
-Because $\ar_1$ is not $\prop$-defended, by definition, it is $\wibeatse[\prop]$-attacked by some $\ar_2$ that has no decisive $\wibeatse[\prop]$-attacker.
+Consider $\ar_1$ not $\phi$-defended and having no decisive $\wibeatse[\phi]$-attackers.
+Because $\ar_1$ is not $\phi$-defended, by definition, it is $\wibeatse[\phi]$-attacked by some $\ar_2$ that has no decisive $\wibeatse[\phi]$-attacker.
 Because $\ar_1$ has no decisive attacker, $\ar_2$ is not decisive.
@@
 
-We conclude from this second point that if $\wibeatseinv[\prop](\ar_1) \subseteq \overline{\argsdec^\prop}$, then $\ar_1$ is $\prop$-defended.
-Otherwise, it is attacked by some $\ar_2$, on which the condition applies in turn, thus attacked by some $\ar_3$, on which the condition applies, and iterating in this way and using finiteness of $\wibeatse[\prop]$ leads to a contradiction.
+We conclude from this second point that if $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$, then $\ar_1$ is $\phi$-defended.
+Otherwise, it would be attacked by some $\ar_2$, on which the condition would apply in turn, thus which would be attacked by some $\ar_3$, on which the condition would apply, and iterating in this way would build an infinite chain in $\wibeatse[\phi]$, a contradiction.
 
-Third, consider an argument $\ar_1 \in \mleadstoinv(\alltopic)$.
-If some $\ar_2 \wibeatse[\prop] \ar_1$ then $\ar_3 \wibeatse[\prop] \ar_2$ [Obs val].
-Thus, $\wibeatseinv[\prop](\ar_1) \subseteq \overline{\argsdec^\prop}$.
-Thus, $\ar_1$ is $\prop$-defended, by our second point.
-Hence, by our first point in this proof, $\ar_1$ is replaceable by some $\wibeatse[\prop]$-decisive $\ar \in \gdargs$.
-We obtain that $\forall \ar' \in \allargs: ¬(\ar' \wibeatse[\prop] \ar)$.
-As $\ar \in \gdargs$, $\ar' \ibeatse[\prop] \ar ⇒ \ar' \wibeatse[\prop] \ar$ [Covering], thus we obtain $¬(\ar' \ibeatse[\prop] \ar)$, hence $\ar$ is $\prop$-poss-dec and $\prop \in \iposs$.
+Third, consider an argument $\ar_1 \in \mleadstoinv(\Phi)$.
+If some $\ar_2 \wibeatse[\phi] \ar_1$ then $\ar_3 \wibeatse[\phi] \ar_2$ [Obs val].
+Thus, $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$.
+Thus, $\ar_1$ is $\phi$-defended, by our second point.
+Hence, by our first point in this proof, $\ar_1$ is replaceable by some $\wibeatse[\phi]$-decisive $\ar \in \gdargs$.
+We obtain that $\forall \ar' \in \allargs: ¬(\ar' \wibeatse[\phi] \ar)$.
+As $\ar \in \gdargs$, $\ar' \ibeatse[\phi] \ar ⇒ \ar' \wibeatse[\phi] \ar$ [Covering], thus we obtain $¬(\ar' \ibeatse[\phi] \ar)$, hence $\ar$ is $\phidec$ and $\phi \in \iPhi$.
 \end{proof}

### 2018-01-30 simple.tex
Theories, and started refactor with t possible more demanding

@@
 \addtokomafont{labelinglabel}{\sffamily\bfseries}
+\renewcommand{\phi}{\varphi}
 
@@
 
+\begin{definition}[Decision situation]
+	A decision situation is a topic $\Phi$, a set of arguments $\allargs$, an arbiter relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$.
+\end{definition}
+
 $\ar$ is $\phi\text{-dec} ⇔ \forall \ar': (\ar', \ar) \ileadstost \phi$. 
@@
 
-We can now define $\iPhi \subseteq \Phi$: $\phi \in \iPhi ⇔  \exists \ar \ \phi\text{-dec}$.
+TODO.
+Mandate that some $\ar$ be “both-decisive” for having both decisive.
+Equivalently, (to be defined as a derivative) $t$ poss must require $t sure$ or both $(t, poss)$-dec and $(¬t, poss)$-dec.
+Stick to the model producing both arguments for $t$ poss and $¬t$ poss in that case (that’s useful for falsifying other theories that claim $t$ sure).
+
+When “both” is not observable, only the sets \{$\prop$-sure, both\} and \{$¬\prop$-sure, both\} can be observed, and there’s only $\phi=\prop$ and $¬\phi=¬\prop$.
+Accepting $\prop$ requires an arg that always leads to \{$\prop$-sure, both\}.
+
+The deliberated judgment of $i$ maps any pair $(\prop, ¬\prop)$ to one of four possibilities: $\prop$ is sure, $¬\prop$ is sure, both are possible, or undecided.
+$\prop$ is sure iff $\exists \ar \ (\prop, \text{sure})\text{-dec}$; both are possible iff $\exists \ar \ (\prop, \text{possible})\text{-dec}$ and $\exists \ar \ (¬\prop, \text{possible})\text{-dec}$; and undecided is when neither of the other three cases hold.
+To deal easily with $i$’s deliberated judgment, we define $\iPhi \subseteq \Phi$ to contain the propositions in $i$’s deliberated judgment, as follows.
+$(\prop, \text{sure}) \in \iPhi ⇔ \exists \ar \ (\prop, \text{sure}\text{-dec}$; $(\prop, \text{possible}) \in \iPhi ⇔  \exists \ar \ (\prop, \text{possible}\text{-dec} ∧ (\exists \ar \ (\prop, \text{sure}\text{-dec} ∨ \exists \ar \ (¬\prop, \text{possible}\text{-dec})$.
+NB footnotes (and all the rest) should be updated.
 \footnote{Equivalently: $\iPhi = \bigcup_{\ar \in \allargs} \bigcap_{\ar' \in \allargs} \ileadstost(\ar', \ar)$.}
@@
 
+\section{Theories proposing decisive argument}
+In most situations, there are too many arguments to exhaustively test whether any $\ar$ is a decisive argument for any $\phi$.
+Furthermore, it is impossible to confirm definitely that $(\ar, \ar') \ileadstost \phi$, whenever $(\ar, \ar') \ileadstost \phi$.
+We rather propose to introduce theories, and expose them to falsification.
+
+A theory $T$ proposing decisive arguments describes a set $D_T$ of decision situations to which it applies, and proposes, for any situation $d = (\Phi, \allargs, \ileadstost) \in D_T$, a subset $\Phi_{d, T} \subseteq \Phi$ and a mapping $f_{d, T}: \Phi_{d, T} → \allargs$.
+The theory claims that it knows the deliberated judgment of $i$ (the individual described by $\ileadstost$ in $d$) about the propositions in $\Phi_{d, T}$, and claims that $f_{d, T}(\phi)$ is a decisive argument for $\phi$.
+
+A falsification instance of $T$ is a triplet $(d, \ar', \phi) \in D_T × \allargs × \Phi_{d, T}$ such that $(f_{d, T}(\phi), \ar') \ileadstoe ¬\phi$.
+A theory $T$ is said to be falsified iff such a triplet is found.
+
+Note that if $(\prop, \text{sure}) \in \Phi_{d, T}$, then including $(\prop, \text{possible})$ in $\Phi_{d, T}$ does not augment the set of falsification instances, thus we suppose $(\prop, \text{sure}) \in \Phi_{d, T} ⇒ (\prop, \text{possible}) \in \Phi_{d, T}$ in what follows.
+
+As is usual in science, falsification procedures should not be considered as ways of definitely validating a theory, but rather as ways of confronting theories.
+We say that two theories $T, T'$ disagree on $\phi$ (or equivalently, on $¬\phi$) iff $\phi \in \Phi_{d, T}$ and $¬\phi \in \Phi_{d, T'}$ in some situation $d \in D_T ∪ D_{T'}$.
+We say that $T$ and $T'$ disagree iff they disagree on some $d \in D_T ∪ D_{T'}$ and $\phi \in \Phi$.
+To confront a theory $T$ to a disagreeing theory $T'$, suffice to test, for any $\phi$ such that $\phi \in \Phi_T, ¬\phi \in \Phi_{T'}$, whether $(f_T(\phi), f_{T'}(¬\phi)) \ileadstoe \phi$.
+Observe that such a test necessarily falsifies one of the theories.
+Observe also that this applies to a single theory $T$, that disagrees with itself, if $\Phi_{d, T}$ contains both $\phi$ and $¬\phi$ for some $d$ and some $\phi$.
+
+The following proposition shows that this notion of falsification is sufficient to test the claims of the theory.
+\begin{proposition}
+	A theory $T$ proposing decisive arguments has no falsification instances iff $\forall d \in D_T, \phi \in \Phi_{d, T}: f_{d, T}(\phi)$ is $\phidec$.
+Furthermore, if a theory $T$ proposing decisive arguments has no falsification instances, then $\Phi_{d, T} \subseteq \iPhi$, $\forall d \in D_T$.
+\end{proposition}
+
 \section{Models}
@@
 Requirements. The maximum length of a path in $\mbeats$ is finite (which implies that $\mbeats$ is acyclic).
-$\ar_3 \mbeats \ar_2 \mbeats \ar_1 ⇒ \ar_2 \mbeats \ar_3 + \ar_1$.\footnote{Necessary for definition of $\ar_3 \wibeatse \ar_2$.}
+$\ar_3 \mbeats \ar_2 \mbeats \ar_1 ⇒ \ar_2 \mbeats \ar_3 + \ar_1$.\footnote{Necessary for definition of $\ar_3 \wibeatse[\phi] \ar_2$.
+TODO remove this condition, define $\wibeatse[\phi]$ more largely and never valid when not in $\mbeats$.}
 
@@
 
-Given a decision situation, we define the relations $\wibeatse[\phi], \nwibeatse[¬\phi] \subseteq \mbeats$ in order to obtain the following result.
+Given a decision situation, we define the relations $\wibeatse[\phi], \nwibeatse[\phi] \subseteq \allargs × \allargs$ in order to obtain the following result, and with $\wibeatse[\phi], \nwibeatse[\phi] \subseteq \mbeats$.
 
@@
 
-Given $\ar_3 \mbeats \ar_2, \phi \in \iPhi$: $\ar_3 \nwibeatse[\phi] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \wibeatse[\phi] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe \phi]$.
+Given $\ar_3 \mbeats \ar_2, \phi \in \Phi$: $\ar_3 \nwibeatse[\phi] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \wibeatse[\phi] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe \phi]$.
 
@@
 \end{itemize}
-
-{Check: Given $\ar_4 \mbeats \ar_3, \ar_3 \notin \mleadstoinv(\alltopic)$, with $\ar_2 \in \mbeats(\ar_3)$ ⇒ ($\ar_2$ and $\ar_4 + \ar_2$ $\mbeats$-attack only root nodes and do not support any proposition): $\ar_4 \wibeatse[\phi] \ar_3$ iff
-\begin{itemize}
-	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\ar_3 \wibeatse[\phi] \ar_2) ∧ (\ar_3 \nwibeatse[\phi] \ar_4 + \ar_2)]$ iff 
-	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \nwibeatse[\phi] \ar_3 + \ar_1) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_4 + \ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_4 + \ar_2 \wibeatse[\phi] \ar_3 + \ar_1)]$ iff
-	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_1 \ileadsto t ∧ (\ar_2, \ar_1) \ileadstose ¬\phi ∧ \ar_3 + \ar_1 \ileadsto \phi ∧ (\ar_3 + \ar_1, \ar_2) \ileadstope \phi ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_1 \mleadsto \phi ∧ (\ar_4 + \ar_2, \ar_1) \ileadstose ¬\phi ∧ \ar_3 + \ar_1 \ileadsto \phi ∧ (\ar_4 + \ar_2, \ar_3 + \ar_1) \ileadstose ¬\phi)]$.
-\end{itemize}
-}
 
@@
 \begin{definition}[Covering]
-	$\forall \phi, \ar \in \gdargs^\phi, \ar' \in \allargs: \ar' \ibeatse[\phi] \ar ⇒ \ar' \mbeats \ar$. 
+	$\forall \phi, \ar \in \gdargs^\phi, \ar' \in \allargs: \ar' \ibeatse[\phi] \ar ⇒ \ar' \wibeatse[\phi] \ar$. 
 \end{definition}

### 2018-01-30 simple.tex
Finished refactor sec 2 with t poss requires CC

@@
 We write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstost ¬\phi$.
+We say $\phi$ is about $\prop$ iff $\phi \in \{\prop, ¬\prop\} × \{\text{possible}, \text{sure}\}$.
 \footnote{\label{ft:sttoe}From (A1) and (A2) we can write, using this notation, $(\ar, \ar') \ileadstost \phi ⇒ (\ar, \ar') \ileadstoe \phi$.}
@@
 \footnote{Equivalently: $\ar \ \phidec ⇔ \exists \ar \suchthat [\ileadstostinv(\phi)](\ar) = \allargs$.}
-\footnote{We also say that $\ar$ is $\propsuredec$ or $\proppossdec$ when $\phi=(\prop, \text{sure})$ or $\phi=(\prop, \text{possible})$.
+\footnote{We also say that $\ar$ is $\propsuredec$, $\proppossdec$, or $¬\proppossdec$, when $\phi=(\prop, \text{sure})$, $\phi=(\prop, \text{possible})$, or $\phi=(¬\prop, \text{possible})$, respectively.
 $\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$, $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$.}
@@
 TODO.
-Mandate that some $\ar$ be “both-decisive” for having both decisive.
-Equivalently, (to be defined as a derivative) $t$ poss must require $t sure$ or both $(t, poss)$-dec and $(¬t, poss)$-dec.
-Stick to the model producing both arguments for $t$ poss and $¬t$ poss in that case (that’s useful for falsifying other theories that claim $t$ sure).
-
 When “both” is not observable, only the sets \{$\prop$-sure, both\} and \{$¬\prop$-sure, both\} can be observed, and there’s only $\phi=\prop$ and $¬\phi=¬\prop$.
@@
 The deliberated judgment of $i$ maps any pair $(\prop, ¬\prop)$ to one of four possibilities: $\prop$ is sure, $¬\prop$ is sure, both are possible, or undecided.
-$\prop$ is sure iff $\exists \ar \ (\prop, \text{sure})\text{-dec}$; both are possible iff $\exists \ar \ (\prop, \text{possible})\text{-dec}$ and $\exists \ar \ (¬\prop, \text{possible})\text{-dec}$; and undecided is when neither of the other three cases hold.
-To deal easily with $i$’s deliberated judgment, we define $\iPhi \subseteq \Phi$ to contain the propositions in $i$’s deliberated judgment, as follows.
-$(\prop, \text{sure}) \in \iPhi ⇔ \exists \ar \ (\prop, \text{sure}\text{-dec}$; $(\prop, \text{possible}) \in \iPhi ⇔  \exists \ar \ (\prop, \text{possible}\text{-dec} ∧ (\exists \ar \ (\prop, \text{sure}\text{-dec} ∨ \exists \ar \ (¬\prop, \text{possible}\text{-dec})$.
-NB footnotes (and all the rest) should be updated.
-\footnote{Equivalently: $\iPhi = \bigcup_{\ar \in \allargs} \bigcap_{\ar' \in \allargs} \ileadstost(\ar', \ar)$.}
-\footnote{$\phi \in \iPhi ⇔ \exists \ar \suchthat \allargs × \{\ar\} \ileadstost \phi$.}
-\footnote{\label{ft:notposs}$\prop \in \iposs ⇔ \exists \ar \ \proppossdec$ and $\prop \notin \iposs ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstose ¬\prop$.}
-\footnote{\label{ft:notsure}$\prop \in \isure ⇔ \exists \ar \ \propsuredec$ and $¬\prop \notin \isure ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstope \prop$.}
-
-We say that a situation is $(\prop, ¬\prop)\text{-unstable}$ iff $\forall \ar, [\exists \ar^+ \suchthat (\ar, \ar^+) \ileadstose \prop] ∧ [\exists \ar^− \suchthat (\ar, \ar^−) \ileadstose ¬\prop]$.
-\footnote{Example of $(\prop, ¬\prop)\text{-unstable}$: $\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstose \prop$.}
-
-\begin{theorem}
-	$\prop \notin \iposs ∧ ¬\prop \notin \iposs ⇔ (\prop, ¬\prop)\text{-unstable}$.
-\end{theorem}
-The proof follows from \cref{ft:notposs}.
-
-\begin{theorem}
-	$\phi \in \iPhi ⇒ ¬\phi \notin \iPhi$.
-\end{theorem}
-This is because some $\ar^+$ is $\phidec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstost \phi$ hence $(\ar^+, \ar^−) \ileadstoe \phi$ (using \cref{ft:sttoe}).
-
-\begin{theorem}
-	$(\prop, \text{sure}) \in \iPhi ⇒ (\prop, \text{possible}) \in \iPhi$.
-\end{theorem}
-The proof follows from (A2).
-
-\begin{definition}[Clear-cut]
-	A situation is $\prop$-clear-cut iff $(\prop, \text{sure}) \notin \iPhi ⇒ (¬\prop, \text{possible}) \in \iPhi$.
-A situation is $(\prop, ¬\prop)$-clear-cut iff $\prop \notin \isure ∧ ¬\prop \notin \isure ⇒ \prop \in \iposs ∧ ¬\prop \in \iposs$, equivalently, $\phi \notin \iPhi ⇔ ¬\phi \in \iPhi$.
-\footnote{$\prop\text{-CC} ∧ ¬\prop\text{-CC} ⇔ (¬\prop \in \isure ∨ \prop \in \iposs) ∧ (\prop \in \isure ∨ ¬\prop \in \iposs) ⇔ (¬\prop \in \isure ∧ \prop \in \isure) ∨ (¬\prop \in \isure) ∨ (\prop \in \isure) ∨ (\prop \in \iposs ∧ ¬\prop \in \iposs) ⇔ (\prop, ¬\prop)\text{-CC}$.}
-\footnote{$\overline{\prop\text{-CC}} ∧ \overline{¬\prop\text{-CC}} ⇔ (\prop, ¬\prop)$-unstability.}
+$\prop$ is sure iff $\exists \ar \ \propsuredec$; both are possible iff $\exists \ar \ \proppossdec$ and $\exists \ar \ ¬\proppossdec$; and undecided is when none of the other three cases hold.
+For easier treatment, we summarize $i$’s deliberated judgment in a single set $\iPhi \subseteq \Phi$, as follows: $(\prop, \text{possible}) \in \iPhi ∧ (¬\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$ iff $(\prop, ¬\prop)$ maps to both possible; $(\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \in \iPhi ∧ (¬\prop, \text{possible}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$ iff $(\prop, ¬\prop)$ maps to $\prop$ is sure, $\phi \notin \iPhi$ for all $\phi$ about $\prop$ iff $(\prop, ¬\prop)$ maps to undecided.
+\footnote{Example of $(\prop, ¬\prop)\text{-undecided}$: $\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstose \prop$.}
 \footnote{Example of $\overline{¬\prop\text{-CC}} ∧ \prop \in \iposs$ (thus with $\prop\text{-CC}$ and no $(\prop, ¬\prop)$-unstability): $\forall (\ar, \ar'), (\ar, \ar') \ileadstose \prop, (\ar, \ar') \ileadstope ¬\prop, (\ar, \ar') \ileadstopst \prop$.
 In such a situation, it is unclear whether $\prop$ holds rather than $¬\prop$ or both $\prop$ and $¬\prop$.}
-\footnote{Hence (with possible meaning merely possible and not sure), for a given pair $(t, ¬t)$, either both are possible, or one is sure, or only $¬\prop$-CC and $¬t \in \iposs$ and $t \notin \iposs$, or only $\prop$-CC and $t \in \iposs$ and $¬t \notin \iposs$, or no CC and $(\prop, ¬\prop)$-unstable.}
 \footnote{Something like Axiom JU should be sufficient for CC.
@@
 Or, the memory buffer of $i$ is too short to hold adequate reinstated arguments, in which case our approach based on decisive arguments is not adequate.}
-\end{definition}
 
-$\prop$ is provably possible, $\prop \in \ipposs$, iff $\prop \in \iposs ∧ ¬\prop\text{-CC}$.
-\footnote{$\prop \in \ipposs ⇔ \prop \in \iposs ∧ (\prop, ¬\prop)\text{-CC}$ (because $\prop \in \iposs ⇒ \prop\text{-CC}$).}
-\footnote{
-\begin{itemize}
-	\item $\prop \in \ipposs ∧ ¬\prop \in \ipposs ⇔ \prop \in \iposs ∧ ¬\prop \in \iposs ⇔ \prop \in \iposs ∧ ¬\prop \in \iposs ∧ (\prop, ¬\prop)\text{-CC} ⇔ \prop \notin \isure ∧ ¬\prop \notin \isure ∧ (\prop, ¬\prop)\text{-CC}$
-	\item $\prop \in \ipposs ∧ ¬\prop \notin \ipposs ⇔ \prop \in \iposs ∧ (\prop, ¬\prop)\text{-CC} ∧ ¬\prop \notin \iposs ⇔ \prop \in \isure$
-	\item $\prop \notin \ipposs ∧ ¬\prop \notin \ipposs ⇔ \overline{\prop\text{-CC}} ∨ \overline{¬\prop\text{-CC}}$.
-\end{itemize}
-}
+Observe that (thanks to A2) $(\prop, \text{possible}) \in \iPhi$ iff $\exists \ar \ \proppossdec ∧ (\exists \ar \ \propsuredec ∨ \exists \ar \ ¬\proppossdec)$.
+
+\begin{proposition}
+	a) $\phi \in \iPhi ⇒ ¬\phi \notin \iPhi$.
+b) $(\prop, ¬\prop)$ maps to undecided $⇔ \phi \notin \iPhi ∧ ¬\phi \notin \iPhi$ for some $\phi$ about $\prop$.
+c) If $\phi \in \iPhi$ for some $\phi$ about $\prop$, then $\phi \in \iPhi ⇔ ¬\phi \notin \iPhi$ for all $\phi$ about $\prop$.
+\end{proposition}
+\begin{proof}
+	a) is because some $\ar^+$ is then $\phidec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstost \phi$ hence $(\ar^+, \ar^−) \ileadstoe \phi$ (using \cref{ft:sttoe}).
+\end{proof}
 

### 2018-02-25 simple.tex
Nicer pres and intro

@@
 \begin{document}
-\title{Simple models of deliberated preference}
+\title{Theories of deliberated preference}
 \author{Olivier Cailloux}
@@
 
+\begin{abstract}
+	In decision theory and economy in general, preferences are generally considered as “intuitive”, as originating from an “immediate sensation”, as famously written by \citeauthor{von_neumann_theory_2004}.
+This conception is insufficient to study the positions that individuals adopt towards difficult decision problems after careful thinking.
+This article introduces, and defines formally, the concept of deliberated preferences to fill this gap: the deliberated preferences of an individual about a given decision problem represent the position of that individual towards that problem that is stable facing counter-arguments.
+As defined, deliberated preferences are only indirectly observable.
+To make it possible to model deliberated preferences, the article also defines formally the notion of a theory of deliberated preferences, together with a protocol of falsification of such a theory.
+The proposed falsification protocol involves only observations similar to those used in classical theories of revealed preferences.
+It is shown that a theory of deliberated preference captures effectively a known subset of the deliberated preferences if and only if it is not falsifiable.
+\end{abstract}
+
 \section{Motivation}
-We define the deliberated preference of an individual.
-We are interested in a context of a choice of a subset of alternatives from a set of possible alternatives given a priori.
-We define a model of the DP and give conditions and a validation procedure that ensure that what the model claims is in the DP is indeed.
-We want in particular to allow for the model to be applicable to various individuals that start with different knowledge: the model may use different counter-arguments to convince different individuals.
+In decision theory and economy in general, preferences are generally considered as “intuitive”, as originating from an “immediate sensation”, following the terms used by \citet{von_neumann_theory_2004} (vNM) \citep{fishburn_retrospective_1989, cailloux_reasons_2017}.
+Though appropriate when studying the everyday behavior of individuals, this conception is insufficient to study the positions that individuals adopt towards difficult decision problems after careful thinking.
+In this article I define the concept of deliberated preferences to fill this gap: the deliberated preferences of an individual about a given decision problem represent the position of that individual towards that problem that is stable facing counter-arguments.
 
-More in detail.
-A full-blown proof may be so long that nobody would read it.
-(That’s why mathematicians do not write their proofs in set-theoretic bare notation.) Hence, shortcuts are taken, which rely on the individual knowing stuff already.
-More generally, assume you want to convince someone of fact $F$ with a text (we call this an argument), in our case, we want to convince a person that such alternative from the set is a good choice for her.
-The argument may assume the reader knows already why such or such possible counter-arguments are invalid, and the argument will thus not delve into the details of some points.
-When shown in interactive mode (our context here), an individual may however question some points (which we call a counter-argument).
-The argumenter should then be able to provide an answer to the query (a counter-counter-argument).
+After having defined this concept formally, I define the notion of a theory pretending to capture the deliberated preferences of a set of individuals about some topic, I propose an empirical procedure to attempt to falsify such a theory, and I show that such a theory tells the truth whenever it is not falsifiable by that procedure.
 
-This article aims at defining such a procedure and conditions of its validity.
+This article does not attempt to propose a concrete theory of deliberated preferences.
+It is more preliminarly.
+It proposes formal definitions for 1) the kind of object that are to be studied for capturing “more reflexive” preferences than considered usually, 2) what theories of such preferences should look like, 3) how to falsify such theories and using which information.
+Therefore, it proposes a research program rather than a direct solution to the problem of capturing reflexive preferences.
+
+Before delving into the formalism, let me present a bit of motivation for considering deliberated preferences as an interesting object to study.
+Being able to capture deliberated preferences can help provide a better understanding of human preferences in the large sense and may improve policy making (though this article does not explore issues of group decision).
+Besides this very broad goal, here are three example of contexts in which this notion is useful, which may give it a more concrete interest and serve to introduce this concept informally by indicating the kinds of things that it should be able to help understand.
+
+First, decision theory has produced several models of how an individual ought to decide, such as the seminal one of vNM.
+(The following remarks apply equally well to other normative models such as the one of \citet{savage_foundations_1972}, \citet{keeney_decisions_1993} or more recent ones.) Those models can be used to help individuals take “good” decisions, as opposed to predict their behavior (for which other models, taking into account cognitive limitations, are more appropriate \citep{wakker_prospect_2010}).
+But it is unclear how to validate recommendations obtained on the basis of such models.
+Some researchers have opposed the norms on which some of those models are based \citep{ellsberg_risk_1961, allais_so-called_1979}.
+As \citet{raiffa_back_1985} points out, while it is the case that some sophisticated decision makers may consciously refuse to abide by the vNM axioms (or others), it is also true that some decision makers simply fail to comply with them because of insufficient reflexion.
+However, no general proposal, as far as I know, has been described yet to test whether, for a given individual and context, those axioms would, after careful thinking, reveal acceptable.
+Psychologists have tried to test the convincing power of those axioms \citep{slovic_who_1974, maccrimmon_utility_1979}.
+Their conclusions inevitably depend on how axioms have been presented to the individuals and on whether counter-arguments have been presented, as \citet{slovic_who_1974} themselves point out.
+But lacking a systematic approach to determine stability facing counter-arguments, those conclusions only shed very partial light on the question of acceptance of specific norms by the general public.
+The notion of deliberated preferences can help confront different possible norms for normative decision theory by seeing them as constituents of theories of deliberated preferences and using the procedure described in this article to confront theories.
+
+Second, the concept of nudge \citep{thaler_nudge:_2009} has been tremendously popular in the recent past, but has also been vastly criticized: the risk of manipulation is particularly high whenever it is unsure that the individual would indeed have adopted the decision that the nudge suggests after careful thinking.
+
+Third, analytical philosophy has presented very elaborated and diverging views about the concept of justice.
+\citet{rawls_theory_1999}, in particular, suggests that the appropriate conception of justice is one that individuals would arrive at in a state of reflexive equilibrium (a concept borrowed from \citet{goodman_fact_1983}).
+\citeauthor{rawls_theory_1999} and \citeauthor{goodman_fact_1983} insist that individuals must not only accept principles, when thinking about difficult notions such as justice, but also think about consequences of those principles: sometimes, principles that appear intuitively acceptable yield consequences that do not appear intuitively acceptable, in which case something must give.
+The state of reflexive equilibrium is a state where accepted principles yield acceptable consequences only.
+The concept of deliberated preferences may be considered as defining that state of reflexive equilibrium, or to be a path towards such a goal (an important difference is that it does not explicitly model the difference between principles and consequences).
+One way to go beyond philosophers disagreement about the right conception of justice, then, is to ask non-philosophers about what they think is right and so use these laymen as arbiters of the competition between views of justice.
+Similar empirical studies have started to be conducted recently \citep{gaertner_empirical_2012}.
+But those studies are conducted by asking individuals only which distribution of goods they consider intuitively right in various circumstances.
+Thus, they do not try to capture their well-considered judgments for justice, where different reasonings in favor of different conceptions of justice would be presented to the individuals together with the distributions.
+Hence, this does not test appropriately whether laymen would accept, after thinking carefully, the sophisticated conceptions of justice presented by a given philosopher or economist.
+A more appropriate way of testing the convincing power of elaborated claims about justice may be considered to require, here again, to present his conception of justice to the individual and submit it to counter-arguments (possibly coming from other sophisticated thinkers).
+
+The first and third contexts of usage come together when it is desired to test whether an individual accepts some axiom as representing an acceptable way of reasoning for him.
+One simple way is to explain axioms individually and ask the individual whether they appear acceptable.
+But this fails to make sure the individual understands and accepts the consequences of the union of the axioms accepted by such a procedure \citep{meinard_justification_2018}.
+(Note that probably nobody is able to mentally deduce all consequences of a union of non trivial axioms.) As an example, in a context of trying to determine the voting rule that best represents someone’s notion of justice, the tested individual could accept the axioms of universal domain, independence of irrelevant alternatives, and pareto dominance, without realizing that he has just accepted dictatorship \citep{arrow_social_1963}.
 
 \section{Decision situation}
-Here is the definition of a decision situation.
-\begin{itemize}
-	\item All alternatives $\allalts$.
-	\item Topic $\alltopic$ = $\Set{\prop_\alt, \alt \in \allalts} ∪ \Set{\prop_{¬\alt}, \alt \in \allalts}$.
-Denoted simply $\alt$ and $¬\alt$.
-We define $¬\prop$, with $\prop = \prop_\alt$, as equal to $\prop_{¬\alt}$ and $¬\prop$, with $\prop = \prop_{¬\alt}$, as equal to $\prop_{\alt}$.
-	\item All possible arguments: $\allargs$.
-It contains at least $\emptyset$, the empty argument.
-It contains all the arguments and more.
-As an example, $\allargs$ could be the set of all strings (assuming all arguments can be transmitted textually).
-\end{itemize}
+The object of study in a given decision situation is the deliberated preferences of a given individual $i$, about a topic $\alltopic$, given a set of arguments $\allargs$, given a certain query protocol, and over a certain time frame.
+
+A decision situation is defined as a triple $(\alltopic, \allargs, \ileadstost)$.
+It concerns a specific individual $i$, whose deliberated preferences are studied, and whose reactions to arguments is modeled by $\ileadstost$, as will be defined shortly.
+
+The decision situation contains a topic denoted by $\alltopic$, which is a set of propositions $\prop \in \alltopic$ about which we are interested of knowing the deliberated preferences of $i$.
+Propositions are not described further, but are supposedly understandable by $i$ (for example, they could be sentences in some natural language).
+Alternatively, in the case of an analyst helping $i$ to make a decision, $\alltopic$ is a set of propositions about which $i$ is interested to know his own deliberated preferences.
+I assume $\alltopic$ is closed under negation and introduce a symbol $¬$ for negating a proposition: if $\prop \in \alltopic$, then $¬\prop \in \alltopic$, and $¬(¬\prop) = \prop$.
+
+With the decision situation comes also a set of all arguments $\allargs$.
+This set contains all the arguments that may possibly be considered relevant by $i$ for his decision problem, and possibly more.
+Importantly, the notion of deliberated preferences does not require to constrain a priori $\allargs$ to some set of arguments that would fit some precise notion of relevancy, coherence, or even well-formedness.
+This permits to avoid introducing inadequate normative principles into the deliberated preferences: only the individual $i$ is then considered legitimate to dictate what is a relevant argument.
+Under that view, $\allargs$ may contain anything that can possibly be considered as an argument by anyone, under the widest possible conception of an argument.
+The notion of deliberated judgment can however also be applied when considering a restricted set of arguments, for example, the arguments that have been put forward by some specific set of experts when talking about the topic $\alltopic$.
+
+The set $\allargs$ may be infinite or very large: as we will see, thanks to our falsificationist approach, there is no need to be able to explore it entirely.
+The set of arguments contains at least the empty argument, denoted by $\zar$.
+
+\begin{example}
+	Consider a decision problem where a set of alternatives $\allalts$ is given, food products among which $i$ would like to form a deliberated preference (taking into account the effects of food on health, price, pleasure, morality issues related to the production process, and so on).
+The topic could be defined as $\alltopic$ = $\Set{\prop_\alt, ¬\prop_\alt, \forall \alt \in \allalts}$, where $\prop_\alt$ is the proposition according to which $\alt$ is one of the best alternatives among $\allalts$ (there is no strictly better alternatives among $\allalts$, from $i$’s point of view), and $¬\prop_\alt$ is the proposition according to which $\alt$ is not one of the best alternatives among $\allalts$ (some $\alt' \in \allalts$ is a strictly better alternative, from $i$’s point of view).
+	The set $\allargs$ is defined as the set of all strings, because in this example it is considered acceptable to restrict arguments to those that can take a textual form.
+\end{example}
+
+As vNM aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher.” The fundamental element here is the reaction of $i$ to arguments.
+Given a proposition $\prop$ and two arguments $\ar, \ar' \in \allargs$, a query consists in presenting both arguments to $i$ and observing which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind: is it that $\prop$ holds, that $¬\prop$ holds, or that both are possible?
+The third possibility allows for the case where no argument appears more decisive than the other one.
+
+It is also necessary to capture the evolution of the position of $i$ towards arguments over time: a repeated query using a given pair of arguments may yield different answers, for example because the repeated question has been interleaved with another query containing other arguments (which $i$ may still have in mind when answering the second repetition), or for any other known or unknown reason.
+The important information for us is the \emph{set} of answers that $i$ could give to a query involving two given arguments and a given topic, among the set $\{\prop, ¬\prop, \text{both}\}$.
+Hence, given $\prop \in \alltopic$, define a relation $\ileadsto^\prop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadsto^\prop C$, with $C \subseteq \Set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind.
+The querying protocol is supposedly made so that for any $\prop \in \alltopic$, $\ileadsto^\prop = \ileadsto^{¬\prop}$.
+
+This information is only indirectly observable: for example, if $(\ar, \ar') \ileadsto^\prop \{\prop\}$, a querier will never know more than $(\ar, \ar') \ileadsto^\prop C$ with $\prop \in C \subseteq \Set{\prop, ¬\prop, \text{both}}$.
+This limitation of our observation will not be a problem for the results of this article.
+Intuitively, this bears on the fact that if a theory claims that $(\ar, \ar') \ileadsto^\prop \{\prop\}$, then either this claim is correct, or it is falsifiable, in the sense that there is a possibility of observing a contradiction to its claim.
+
+I voluntarily leave the querying protocol not precisely specified, as multiple reasonable choices are possible and the results of this article depend only on specific assumptions that will be made clear shortly.
+One possible choice, when arguments and propositions are strings, is to read both arguments to $i$, together with $\prop$, and ask $i$ to verbally report the choice he opts for among the three possibilities.
+Another is to present both arguments and ask $i$ to pick an item among some choice set and make the choice correspond to a validation of $\prop$ or $¬\prop$, possibly even letting the choice engage $i$, for example telling $i$ that she may keep the object of choice (this is illustrated in \cref{ex:pick}).
+This second possibility is especially interesting as it makes the protocol partially observable in the restricted sense usually appreciated in revealed preferences approaches.
+Note that depending on the protocol, the choice “both” is not necessarily observable (more about this below).
+%In that case, the semantics of $\prop$ and $¬\prop$ relatedly change: instead of meaning that $\prop$ is definitely the 
+%Indeed, \citet{tversky_intransitivity_1969} note that individuals “are not perfectly consistent in their choices.
+When faced with repeated choices between x and y, people often choose x in some instances and y in others.
+Furthermore, such inconsistencies are observed even in the absence of systematic changes in the decision maker’s taste which might be due to learning or sequential effects.
+It seems, therefore, that the observed inconsistencies reflect inherent variability or momentary fluctuation in the evaluative process.” This is an accepted fact of experimental psychology \citep{luce_utility_2000}.
+However, it is reasonable to suspect that fluctuations occur less often, if at all, for some choices.
+For example, facing a choice between tea or coffee, I would virtually never pick tea (all other things being equal).
+We are interested in capturing precisely those kind of preferences.
+
+One can also use $\zar$ as one or both of the arguments, in which case the protocol queries the preference of $i$ given only one or given no argument.
+
+\begin{example}[cont.]
+	\label{ex:pick}
+	Continuing the example, define the querying protocol as, given $\prop_\alt$, presenting two arguments to $i$ and let $i$ choose an item among $\allalts$. $i$ may keep the chosen item. 
+	If $i$ chooses $\alt$, it is considered that $i$ has validated $\prop_\alt$, otherwise, $¬\prop_\alt$. The option “both” is not observable.
+%	Queries are separated by one week at least, which (as supposed in this example) is enough to ensure that no effect of pleasure for variability enter into play. 
+\end{example}
+
+To summarize this information, define $\Phi = \alltopic × \set{\text{possible}, \text{sure}}$, and define a single relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$, pronounced “always leads to”.
+Elements in $\Phi$ will also be called propositions, which should create no ambiguity.
+Define $\forall \phi = (\prop, \text{possible}) \in \Phi: (\ar, \ar') \ileadstost \phi ⇔ (\ar, \ar') \ileadsto^\prop C$ with $C \subseteq \Set{\prop, \text{both}}$; and $\forall \phi = (\prop, \text{sure}) \in \Phi: (\ar, \ar') \ileadstost \phi ⇔ (\ar, \ar') \ileadsto^\prop \set{\prop}$.
+The semantics are that whenever $(\ar, \ar') \ileadstost (\prop, \text{sure})$, $i$ always considers that $\prop$ is sure (meaning that $¬\prop$ is excluded), when presented with these two arguments, and whenever $(\ar, \ar') \ileadstost (\prop, \text{possible})$, $i$ always considers that $\prop$ is “at least” possible (meaning that $¬\prop$ may be possible as well), when presented with these two arguments.
+
+Define the negation operator $¬$ over $\Phi$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
+It follows that $¬¬\phi = \phi$.
+Write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstost ¬\phi$.
+The relation $\ileadstoe$ is pronounced “sometimes leads to”.
+A proposition $\phi$ is about $\prop$ iff $\phi \in \{\prop, ¬\prop\} × \{\text{possible}, \text{sure}\}$. 
+\footnote{\label{ft:sttoe}From (A1) and (A2) we can write, using this notation, $(\ar, \ar') \ileadstost \phi ⇒ (\ar, \ar') \ileadstoe \phi$.}
 
 Define $f_\prop$ from any unordered pair of arguments $(\ar, \ar')$ into $\powerset{\prop\text{-sure}, ¬\prop\text{-sure}, b)}$ (where $b$ means both possible).
-We present both arguments to $i$ and ask which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind.
-The set designates all cumulated answers over time, thus allowing $i$ to be unstable (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason).
+We The set designates all cumulated answers over time, thus allowing $i$ to be unstable (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason).
 We assume $b$ is observable as well.
-We can also use $\emptyset$ as one or both of the arguments.
 
@@
 
+When “both” is not observable, the same definitions hold, with $f_t(\ar, \ar') ≠ b$.
+It follows that $\ileadstopst = \ileadstosst$.
+We say in this case that $\ileadstost$ does not distinguish sure from possible.
+Thus, elements $\phi \in \Phi$ may be considered as simply equal to $\prop$ or $¬\prop$, as $(\prop, \text{sure})$ is treated exactly as $(\prop, \text{possible})$.
+
 \begin{definition}[Decision situation]
@@
 
-TODO.
-When “both” is not observable, only the sets \{$\prop$-sure, both\} and \{$¬\prop$-sure, both\} can be observed, and there’s only $\phi=\prop$ and $¬\phi=¬\prop$.
-Accepting $\prop$ requires an arg that always leads to \{$\prop$-sure, both\}.
+The following proposition follows from the fact that when $\ar^+$ is $\phidec$, given any $\ar^−$, $(\ar^+, \ar^−) \ileadstost \phi$ hence $(\ar^+, \ar^−) \ileadstoe \phi$ (using \cref{ft:sttoe}).
+\begin{proposition}
+	\label{thm:nocontrdec}
+	$\exists \ar \ \phidec ⇒ \nexists \ar' \ ¬\phidec.$
+\end{proposition}
 
-The deliberated judgment of $i$ maps any pair $(\prop, ¬\prop)$ to one of four possibilities: $\prop$ is sure, $¬\prop$ is sure, both are possible, or undecided.
-$\prop$ is sure iff $\exists \ar \ \propsuredec$; both are possible iff $\exists \ar \ \proppossdec$ and $\exists \ar \ ¬\proppossdec$; and undecided is when none of the other three cases hold.
-For easier treatment, we summarize $i$’s deliberated judgment in a single set $\iPhi \subseteq \Phi$, as follows: $(\prop, \text{possible}) \in \iPhi ∧ (¬\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$ iff $(\prop, ¬\prop)$ maps to both possible; $(\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \in \iPhi ∧ (¬\prop, \text{possible}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$ iff $(\prop, ¬\prop)$ maps to $\prop$ is sure, $\phi \notin \iPhi$ for all $\phi$ about $\prop$ iff $(\prop, ¬\prop)$ maps to undecided.
+The deliberated judgment of $i$ maps any unordered pair $(\prop, ¬\prop)$ to one of four possibilities.
+For easier treatment, we summarize $i$’s deliberated judgment in a single set $\iPhi \subseteq \Phi$, as follows.
+(Interpretation is given in parenthesis.)
+\begin{itemize}
+	\item $(\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \in \iPhi ∧ (¬\prop, \text{possible}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$ iff $\exists \ar \ \propsuredec$ ($\prop$ is sure)
+	\item $(\prop, \text{possible}) \in \iPhi ∧ (¬\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$ iff $\exists \ar \ \proppossdec$ and $\exists \ar \ ¬\proppossdec$ (both $\prop$ and $¬\prop$ are possible)
+	\item $\phi \notin \iPhi$ for all $\phi$ about $\prop$ iff neither $\prop$ is sure, nor $¬\prop$ is sure, nor both are possible ($(\prop, ¬\prop)$ is undecided).
+\end{itemize}
+\Cref{thm:nocontrdec} shows that the second case is separate from the first.
 \footnote{Example of $(\prop, ¬\prop)\text{-undecided}$: $\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstose \prop$.}
@@
 
-Observe that (thanks to A2) $(\prop, \text{possible}) \in \iPhi$ iff $\exists \ar \ \proppossdec ∧ (\exists \ar \ \propsuredec ∨ \exists \ar \ ¬\proppossdec)$.
-
 \begin{proposition}
-	a) $\phi \in \iPhi ⇒ ¬\phi \notin \iPhi$.
-b) $(\prop, ¬\prop)$ maps to undecided $⇔ \phi \notin \iPhi ∧ ¬\phi \notin \iPhi$ for some $\phi$ about $\prop$.
-c) If $\phi \in \iPhi$ for some $\phi$ about $\prop$, then $\phi \in \iPhi ⇔ ¬\phi \notin \iPhi$ for all $\phi$ about $\prop$.
+	a) $\phi \in \iPhi ⇒$ some $\ar$ is $\phidec$.
+b) $(\prop, \text{possible}) \in \iPhi$ iff $\exists \ar \ \proppossdec ∧ (\exists \ar \ \propsuredec ∨ \exists \ar \ ¬\proppossdec)$.
+c) $(\prop, \text{sure}) \in \iPhi ⇒ (\prop, \text{possible}) \in \iPhi$.
+d) $\phi \in \iPhi ⇒ ¬\phi \notin \iPhi$.
+e) $(\prop, ¬\prop)$ undecided $⇔ \phi \notin \iPhi ∧ ¬\phi \notin \iPhi$ for some $\phi$ about $\prop$.
+f) If $\phi \in \iPhi$ for some $\phi$ about $\prop$, then $\phi \in \iPhi ⇔ ¬\phi \notin \iPhi$ for all $\phi$ about $\prop$.
+g) If $\ileadstost$ does not distinguish sure from possible, no pair of proposition is mapped to “both are possible”.
 \end{proposition}
 \begin{proof}
-	a) is because some $\ar^+$ is then $\phidec$, thus given any $\ar^−$, $(\ar^+, \ar^−) \ileadstost \phi$ hence $(\ar^+, \ar^−) \ileadstoe \phi$ (using \cref{ft:sttoe}).
+	a) is a consequence of A2.
+b) and c) follow from the definition of $\iPhi$.
+d) is obtained using a), \cref{thm:nocontrdec}, and the contrapositive of a).
+About e), we must show that $\phi \notin \iPhi ∧ ¬\phi \notin \iPhi$ for some $\phi$ about $\prop$ implies $\phi' \notin \iPhi$ for all $\phi'$ about $\prop$.
+Assume $\phi=(l, \text{possible})$ and $¬\phi = (¬l, \text{sure})$ are not in $\iPhi$, with $l = t$ or $l = ¬t$.
+We need to prove that $(l, \text{sure})$ and $(¬l, \text{possible})$ are not in $\iPhi$ either.
+We obtain $(l, \text{sure}) \notin \iPhi$ using the contrapositive of c).
+And $(¬l, \text{possible}) \notin \iPhi$ because $(¬l, \text{possible}) \in \iPhi$ would require another $\phi'$ about $\prop$ to be present in $\iPhi$, as can be checked from the definition of $\iPhi$.
+f) follows from d) together with the fact that $(\prop, ¬\prop)$ is (by definition) not undecided when $\phi \in \iPhi$ for some $\phi$ about $\prop$, hence, from e), $\phi \in \iPhi ∨ ¬\phi \in \iPhi$.
+Finally, g) is because in that case, $\exists \ar \ \proppossdec ⇔ \exists \ar \ \propsuredec$, thus using \cref{thm:nocontrdec}, $\exists \ar \ \proppossdec ⇒ \nexists \ar' \ ¬\proppossdec$.
 \end{proof}
 
-\section{Theories proposing decisive argument}
+\section{Theories proposing decisive arguments}
 In most situations, there are too many arguments to exhaustively test whether any $\ar$ is a decisive argument for any $\phi$.
@@
 Observe that such a test necessarily falsifies one of the theories.
-Observe also that this applies to a single theory $T$, that disagrees with itself, if $\Phi_{d, T}$ contains both $\phi$ and $¬\phi$ for some $d$ and some $\phi$.
 
-The following proposition shows that this notion of falsification is sufficient to test the claims of the theory.
+The following proposition shows that this notion of falsification adequately tests the claims of the theory.
 \begin{proposition}
@@
 
-%\bibliography{mybib}
+\bibliography{simple}
 

### 2018-02-25 simple.tex
Rephr (minor)

@@
 The important information for us is the \emph{set} of answers that $i$ could give to a query involving two given arguments and a given topic, among the set $\{\prop, ¬\prop, \text{both}\}$.
+The set designates all possible answers over time and over different order of asking the queries.
 Hence, given $\prop \in \alltopic$, define a relation $\ileadsto^\prop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadsto^\prop C$, with $C \subseteq \Set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind.
@@
 Define $f_\prop$ from any unordered pair of arguments $(\ar, \ar')$ into $\powerset{\prop\text{-sure}, ¬\prop\text{-sure}, b)}$ (where $b$ means both possible).
-We The set designates all cumulated answers over time, thus allowing $i$ to be unstable (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason).
+We , thus allowing $i$ to be unstable (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason).
 We assume $b$ is observable as well.

### 2018-02-25 simple.tex
Removed old defs with leadsto_f and co

@@
 
-Define $f_\prop$ from any unordered pair of arguments $(\ar, \ar')$ into $\powerset{\prop\text{-sure}, ¬\prop\text{-sure}, b)}$ (where $b$ means both possible).
-We , thus allowing $i$ to be unstable (because she has learnt new things in between two questioning, or just because of time passing, or for any known or unknown reason).
-We assume $b$ is observable as well.
-
-When $\prop$ is fixed, or if it can be deduced from the output set, we write $(\ar, \ar') \ileadsto O$ or $\ileadsto(\ar, \ar') = O$ instead of $f_\prop(\ar, \ar') = O$.
-
-We define $(\ar, \ar') \ileadstopst \prop ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, $(\ar, \ar') \ileadstosst ¬\prop ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$, $(\ar, \ar') \ileadstose ¬\prop ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\} ⇔ ¬((\ar, \ar') \ileadstopst \prop)$, and $(\ar, \ar') \ileadstope \prop  ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\} ⇔ ¬((\ar, \ar') \ileadstosst ¬\prop)$.
-
 Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on (and their negations $\ileadstose$ and $\ileadstope$), together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
@@
 the pair $(\ar, \ar')$ being understood as unordered (thus $(\ar, \ar') \ileadstosst \prop ⇔ (\ar', \ar) \ileadstosst \prop$, and similarly for $\ileadstopst$).
-
-We also define $\Phi = \alltopic × \set{\text{possible}, \text{sure}}$, and $\forall \phi = (\prop, \text{possible}) \in \Phi: (\ar, \ar') \ileadstost \phi ⇔ (\ar, \ar') \ileadstopst \prop$ and $\forall \phi = (\prop, \text{sure}) \in \Phi: (\ar, \ar') \ileadstost \phi ⇔ (\ar, \ar') \ileadstosst \prop$.
-We define the negation operator $¬$ over $\Phi$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
-It follows that $¬¬\phi = \phi$.
-We write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstost ¬\phi$.
-We say $\phi$ is about $\prop$ iff $\phi \in \{\prop, ¬\prop\} × \{\text{possible}, \text{sure}\}$.
-\footnote{\label{ft:sttoe}From (A1) and (A2) we can write, using this notation, $(\ar, \ar') \ileadstost \phi ⇒ (\ar, \ar') \ileadstoe \phi$.}
 

### 2018-02-25 simple.tex
Def minimal dec sit

@@
 
-Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on (and their negations $\ileadstose$ and $\ileadstope$), together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
+As defined, $\ileadstost$ has the following properties. (A1) $\ileadstopst \subseteq \ileadstope$
 \footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.}
@@
 \footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}, 
-the pair $(\ar, \ar')$ being understood as unordered (thus $(\ar, \ar') \ileadstosst \prop ⇔ (\ar', \ar) \ileadstosst \prop$, and similarly for $\ileadstopst$).
+and the pair $(\ar, \ar')$ is to be understood as unordered (thus $(\ar, \ar') \ileadstosst \prop ⇔ (\ar', \ar) \ileadstosst \prop$).
 
+Note that these properties follow from the way the querying protocol is presented above, but actually these are the only properties required, thus any querying protocol that satisfies those qualify.
 When “both” is not observable, the same definitions hold, with $f_t(\ar, \ar') ≠ b$.

### 2018-02-27 simple.tex
First part done (simple theories with decisive arguments).

--- 2018-02-25 simple.tex
@@
 \section{Decision situation}
-The object of study in a given decision situation is the deliberated preferences of a given individual $i$, about a topic $\alltopic$, given a set of arguments $\allargs$, given a certain query protocol, and over a certain time frame.
+The object of study in a given decision situation is the deliberated preferences of a given individual $i$. 
+A decision situation concerns a topic $\alltopic$, given a set of arguments $\allargs$, given a certain query protocol, and over a certain time frame.
+The relation $\ileadstost$, to be defined shortly, models the reaction of $i$ to arguments about the topic.
+The decision situation will be defined as a triple $(\alltopic, \allargs, \ileadstost)$ satisfying some conditions to be defined after having presented those three fundamental elements.
 
-A decision situation is defined as a triple $(\alltopic, \allargs, \ileadstost)$.
-It concerns a specific individual $i$, whose deliberated preferences are studied, and whose reactions to arguments is modeled by $\ileadstost$, as will be defined shortly.
-
-The decision situation contains a topic denoted by $\alltopic$, which is a set of propositions $\prop \in \alltopic$ about which we are interested of knowing the deliberated preferences of $i$.
+The decision situation relates to a topic denoted by $\alltopic$, which is a set of propositions $\prop \in \alltopic$ about which we are interested of knowing the deliberated preferences of $i$.
 Propositions are not described further, but are supposedly understandable by $i$ (for example, they could be sentences in some natural language).
@@
 \begin{example}
-	Consider a decision problem where a set of alternatives $\allalts$ is given, food products among which $i$ would like to form a deliberated preference (taking into account the effects of food on health, price, pleasure, morality issues related to the production process, and so on).
+	Consider a decision problem where a set of alternatives $\allalts$ is given, containing food products among which $i$ would like to form a deliberated preference (taking into account the effects of food on health, price, pleasure, morality issues related to the production process, and so on).
 The topic could be defined as $\alltopic$ = $\Set{\prop_\alt, ¬\prop_\alt, \forall \alt \in \allalts}$, where $\prop_\alt$ is the proposition according to which $\alt$ is one of the best alternatives among $\allalts$ (there is no strictly better alternatives among $\allalts$, from $i$’s point of view), and $¬\prop_\alt$ is the proposition according to which $\alt$ is not one of the best alternatives among $\allalts$ (some $\alt' \in \allalts$ is a strictly better alternative, from $i$’s point of view).
@@
 
-As vNM aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher.” The fundamental element here is the reaction of $i$ to arguments.
+Define $\Phi = \alltopic × \set{\text{possible}, \text{sure}}$. Elements in $\Phi$ will also be called propositions, which should create no ambiguity. 
+The relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$, pronounced “always leads to”, has the following semantics.
+Whenever $(\ar, \ar') \ileadstost (\prop, \text{sure})$, $i$ always considers that $\prop$ is sure (meaning that $¬\prop$ is excluded), when presented with these two arguments, and whenever $(\ar, \ar') \ileadstost (\prop, \text{possible})$, $i$ always considers that $\prop$ is “at least” possible (meaning that $¬\prop$ may be possible as well), when presented with these two arguments.
+In both cases, the term “always” means that the consideration is stable over time, including after having presented other arguments to $i$.
+Two query protocols presented below will illustrate how these semantics might be satisfied. 
+However, I voluntarily leave the querying protocol not precisely specified in general, as multiple reasonable choices are possible.
+The results of this article depend only on assumptions about $\ileadstost$.
+
+Define the negation operator $¬$ over $\Phi$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
+It follows that $¬¬\phi = \phi$.
+Write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstost ¬\phi$.
+The relation $\ileadstoe$ is pronounced “sometimes leads to”.
+A proposition $\phi$ is about $\prop$ iff $\phi \in \{\prop, ¬\prop\} × \{\text{possible}, \text{sure}\}$.
+
+The pair $(\ar, \ar')$ is to be understood as unordered (thus $(\ar, \ar') \ileadstost \prop ⇔ (\ar', \ar) \ileadstost \prop$).
+
+The relation $\ileadstost$ must satisfy the two following properties, or axioms. (A1) $\ileadstost \subseteq \ileadstoe$
+\footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $\ileadstopst \subseteq \ileadstope$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.}
+and (A2) $\forall \prop \in \alltopic: (\ar, \ar') \ileadstost (\prop, \text{sure}) ⇒ (\ar, \ar') \ileadstost (\prop, \text{possible})$
+\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}. 
+Observe that (A1) can equivalently be formulated as $\forall \prop \in \alltopic: [(\ar, \ar') \ileadstost (\prop, \text{sure}) ⇒ (\ar, \ar') \ileadstoe (\prop, \text{sure})]$, or equivalently, $\forall \prop \in \alltopic: [(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇒ (\ar, \ar') \ileadstoe (\prop, \text{possible})]$, and (A2) is equivalent to $\forall \prop \in \alltopic: [(\ar, \ar') \ileadstoe (\prop, \text{sure}) ⇒ (\ar, \ar') \ileadstoe (\prop, \text{possible})]$.
+
+\begin{definition}[Decision situation]
+	A decision situation is a topic $\alltopic$ closed under negation, a set of arguments $\allargs$, an “always leads to” relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$ satisfying (A1) and (A2) and using unordered pairs of arguments, $\Phi$ being the set of propositions $\alltopic × \set{\text{sure}, \text{possible}}$.
+\end{definition}
+
+\subsection{Query protocols}
+As vNM aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher.” The fundamental element here is the reaction of $i$ to arguments, which will serve as the informational basis to define $\ileadstost$.
 Given a proposition $\prop$ and two arguments $\ar, \ar' \in \allargs$, a query consists in presenting both arguments to $i$ and observing which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind: is it that $\prop$ holds, that $¬\prop$ holds, or that both are possible?
@@
 This information is only indirectly observable: for example, if $(\ar, \ar') \ileadsto^\prop \{\prop\}$, a querier will never know more than $(\ar, \ar') \ileadsto^\prop C$ with $\prop \in C \subseteq \Set{\prop, ¬\prop, \text{both}}$.
+Also, it may be only possible to test one ordering of the queries (assuming that $i$ forgets over time might permit to test different orderings, but this assumption might be unrealistic).
+In some cases, it may even be only possible to test a single query with a given individual.
 This limitation of our observation will not be a problem for the results of this article.
-Intuitively, this bears on the fact that if a theory claims that $(\ar, \ar') \ileadsto^\prop \{\prop\}$, then either this claim is correct, or it is falsifiable, in the sense that there is a possibility of observing a contradiction to its claim.
+Intuitively, this bears on the fact that, first, theories apply to multiple individuals, and second, if a theory claims that $(\ar, \ar') \ileadsto^\prop \{\prop\}$, then either this claim is correct, or it is falsifiable, in the sense that there is a possibility of observing a contradiction to its claim.
 
-I voluntarily leave the querying protocol not precisely specified, as multiple reasonable choices are possible and the results of this article depend only on specific assumptions that will be made clear shortly.
-One possible choice, when arguments and propositions are strings, is to read both arguments to $i$, together with $\prop$, and ask $i$ to verbally report the choice he opts for among the three possibilities.
+To be more concrete, one possible choice of a query protocol, when arguments and propositions are strings, is to read both arguments to $i$, together with $\prop$, and ask $i$ to verbally report the choice he opts for among the three possibilities.
 Another is to present both arguments and ask $i$ to pick an item among some choice set and make the choice correspond to a validation of $\prop$ or $¬\prop$, possibly even letting the choice engage $i$, for example telling $i$ that she may keep the object of choice (this is illustrated in \cref{ex:pick}).
@@
 
-To summarize this information, define $\Phi = \alltopic × \set{\text{possible}, \text{sure}}$, and define a single relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$, pronounced “always leads to”.
-Elements in $\Phi$ will also be called propositions, which should create no ambiguity.
-Define $\forall \phi = (\prop, \text{possible}) \in \Phi: (\ar, \ar') \ileadstost \phi ⇔ (\ar, \ar') \ileadsto^\prop C$ with $C \subseteq \Set{\prop, \text{both}}$; and $\forall \phi = (\prop, \text{sure}) \in \Phi: (\ar, \ar') \ileadstost \phi ⇔ (\ar, \ar') \ileadsto^\prop \set{\prop}$.
-The semantics are that whenever $(\ar, \ar') \ileadstost (\prop, \text{sure})$, $i$ always considers that $\prop$ is sure (meaning that $¬\prop$ is excluded), when presented with these two arguments, and whenever $(\ar, \ar') \ileadstost (\prop, \text{possible})$, $i$ always considers that $\prop$ is “at least” possible (meaning that $¬\prop$ may be possible as well), when presented with these two arguments.
+Define $\ileadstost$ from $\ileadsto^\prop$ as follows, for any $\prop \in \alltopic$: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadsto^\prop C$ with $C \subseteq \Set{\prop, \text{both}}$; and $(\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadsto^\prop \set{\prop}$.
 
-Define the negation operator $¬$ over $\Phi$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
-It follows that $¬¬\phi = \phi$.
-Write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstost ¬\phi$.
-The relation $\ileadstoe$ is pronounced “sometimes leads to”.
-A proposition $\phi$ is about $\prop$ iff $\phi \in \{\prop, ¬\prop\} × \{\text{possible}, \text{sure}\}$. 
-\footnote{\label{ft:sttoe}From (A1) and (A2) we can write, using this notation, $(\ar, \ar') \ileadstost \phi ⇒ (\ar, \ar') \ileadstoe \phi$.}
+Note that (A1) and (A2) hold.
 
-Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on (and their negations $\ileadstose$ and $\ileadstope$), together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
-\footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.}
-and (A2) that $\ileadstosst \subseteq \ileadstopst$
-\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}, 
-the pair $(\ar, \ar')$ being understood as unordered (thus $(\ar, \ar') \ileadstosst \prop ⇔ (\ar', \ar) \ileadstosst \prop$, and similarly for $\ileadstopst$).
-
-When “both” is not observable, the same definitions hold, with $f_t(\ar, \ar') ≠ b$.
-It follows that $\ileadstopst = \ileadstosst$.
+When “both” is not observable, $\ileadstost$ is defined as: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadsto^\prop \set{\prop}$.
+(A1) and (A2) still hold.
 We say in this case that $\ileadstost$ does not distinguish sure from possible.
@@
 
-\begin{definition}[Decision situation]
-	A decision situation is a topic $\Phi$, a set of arguments $\allargs$, an arbiter relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$.
-\end{definition}
+\subsection{Deliberated preference}
+The following important definition is required in order to define the deliberated preference of $i$.
+An argument $\ar$ is decisive for $\phi$, in short, $\phi\text{-dec}$ iff $\forall \ar' \in \allargs: (\ar', \ar) \ileadstost \phi$.
+\footnote{Equivalently: $\ar \ \phidec ⇔ [\ileadstostinv(\phi)](\ar) = \allargs$, and $\exists \ar \ \phidec ⇔ [\ileadstostinv(\phi)]^{-1}(\allargs) ≠ \emptyset$.}
+I also say that $\ar$ is $\propsuredec$, $\proppossdec$, or $¬\proppossdec$, when $\phi=(\prop, \text{sure})$, $\phi=(\prop, \text{possible})$, or $\phi=(¬\prop, \text{possible})$, respectively.
+\footnote{$\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$, $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$.}
 
-$\ar$ is $\phi\text{-dec} ⇔ \forall \ar': (\ar', \ar) \ileadstost \phi$. 
-\footnote{Equivalently: $\ar \ \phidec ⇔ \exists \ar \suchthat [\ileadstostinv(\phi)](\ar) = \allargs$.}
-\footnote{We also say that $\ar$ is $\propsuredec$, $\proppossdec$, or $¬\proppossdec$, when $\phi=(\prop, \text{sure})$, $\phi=(\prop, \text{possible})$, or $\phi=(¬\prop, \text{possible})$, respectively.
-$\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$, $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$.}
-
-The following proposition follows from the fact that when $\ar^+$ is $\phidec$, given any $\ar^−$, $(\ar^+, \ar^−) \ileadstost \phi$ hence $(\ar^+, \ar^−) \ileadstoe \phi$ (using \cref{ft:sttoe}).
 \begin{proposition}
 	\label{thm:nocontrdec}
-	$\exists \ar \ \phidec ⇒ \nexists \ar' \ ¬\phidec.$
+	For any decision situation, a) $\exists \ar \ \phidec ⇒ \nexists \ar' \ ¬\phidec$ and b) $\exists \ar \ \propsuredec ⇒ \nexists \ar' \ ¬\propsuredec$.
 \end{proposition}
+\begin{proof}
+	About a), when $\ar$ is $\phidec$, given any $\ar'$, $(\ar, \ar') \ileadstost \phi$ hence $(\ar, \ar') \ileadstoe \phi$ (using (A1)), hence $(\ar, \ar') \nileadstost ¬\phi$.
+b) obtains similarly using (A2).
+\end{proof}
 
-The deliberated judgment of $i$ maps any unordered pair $(\prop, ¬\prop)$ to one of four possibilities.
-For easier treatment, we summarize $i$’s deliberated judgment in a single set $\iPhi \subseteq \Phi$, as follows.
-(Interpretation is given in parenthesis.)
-\begin{itemize}
-	\item $(\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \in \iPhi ∧ (¬\prop, \text{possible}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$ iff $\exists \ar \ \propsuredec$ ($\prop$ is sure)
-	\item $(\prop, \text{possible}) \in \iPhi ∧ (¬\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$ iff $\exists \ar \ \proppossdec$ and $\exists \ar \ ¬\proppossdec$ (both $\prop$ and $¬\prop$ are possible)
-	\item $\phi \notin \iPhi$ for all $\phi$ about $\prop$ iff neither $\prop$ is sure, nor $¬\prop$ is sure, nor both are possible ($(\prop, ¬\prop)$ is undecided).
-\end{itemize}
-\Cref{thm:nocontrdec} shows that the second case is separate from the first.
-\footnote{Example of $(\prop, ¬\prop)\text{-undecided}$: $\forall (\ar, \ar'), (\ar, \ar') \ileadstose ¬\prop, (\ar, \ar') \ileadstose \prop$.}
+The deliberated preference of $i$ maps each pair $(\prop, ¬\prop)$ to one among four possibilities, depending on the existence of decisive arguments supporting the propositions about $\prop$.
+The mapping is defined as follows.
+\begin{description}
+	\item[$\prop$ is sure] iff $\exists \ar \ \propsuredec$
+	\item[$¬\prop$ is sure] iff $\exists \ar \ ¬\propsuredec$
+	\item[both $\prop$ and $¬\prop$ are possible] iff $\exists \ar \ \proppossdec$ and $\exists \ar \ ¬\proppossdec$
+	\item[$(\prop, ¬\prop)$ is undecided] iff neither $\prop$ is sure, nor $¬\prop$ is sure, nor both are possible.
+\end{description}
+\Cref{thm:nocontrdec} shows that the cases are separate.
+\footnote{Example of $(\prop, ¬\prop)\text{-undecided}$: $\forall (\ar, \ar'), (\ar, \ar') \ileadstoe (¬\prop, \text{sure}), (\ar, \ar') \ileadstoe (\prop, \text{sure})$.}
 \footnote{Example of $\overline{¬\prop\text{-CC}} ∧ \prop \in \iposs$ (thus with $\prop\text{-CC}$ and no $(\prop, ¬\prop)$-unstability): $\forall (\ar, \ar'), (\ar, \ar') \ileadstose \prop, (\ar, \ar') \ileadstope ¬\prop, (\ar, \ar') \ileadstopst \prop$.
@@
 
+It should be clear that the validity of the conclusions obtained from any theory of deliberated preference rests on the acceptance of this just given normative definition, namely, it is to be considered meaningful that the deliberated preference of $i$ be defined in such a way, given the query protocol used for defining $\ileadstost$ in a particular application.
+
+This information is summarized by defining a subset $\iPhi \subseteq \Phi$ of propositions that represent $i$’s deliberated preference, defined as follows.
+\begin{description}
+	\item[$\prop$ is sure] ⇒ $(\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \in \iPhi ∧ (¬\prop, \text{possible}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$
+	\item[both $\prop$ and $¬\prop$ are possible] ⇒ $(\prop, \text{possible}) \in \iPhi ∧ (¬\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$
+	\item[$(\prop, ¬\prop)$ is undecided] ⇒ $\phi \notin \iPhi$ for all $\phi$ about $\prop$.
+\end{description}
+Because this defines unequivocally the membership of every proposition about $\prop$ for every $\prop \in \alltopic$, this suffices to define $\iPhi$; and it follows that the reverse implications hold as well.
+
+The following propositions can help get convinced that the proposed definition of deliberated preference makes sense.
 \begin{proposition}
@@
 
+It is important to remark that when the query protocol does not admit observation of “both”, thus, when $\ileadstost$ does not distinguish sure from possible, it does \emph{not} follow that $i$ is sure of either $\prop$ or $¬\prop$ for every pair of proposition: the “undecided” case will hold whenever $i$ considers no argument as sufficiently strong to determine a decisive preference (assuming that in that case, $i$ at least sometimes alternates his choice).
+Admittedly, it might also happen that $i$ is really indifferent between $\prop$ and $¬\prop$ but still systematically chooses, say, $\prop$ over $¬\prop$, in which case it will be (somewhat) erroneously concluded that $\prop \in \iPhi$.
+This is the price to pay for using protocols that do not allow to observe indifference.
+Observe however that (depending on the application) this error might be considered not harmful, as the obtained model will be faithful to $i$’s behavior after deliberation.
+
 \section{Theories proposing decisive arguments}
-In most situations, there are too many arguments to exhaustively test whether any $\ar$ is a decisive argument for any $\phi$.
-Furthermore, it is impossible to confirm definitely that $(\ar, \ar') \ileadstost \phi$, whenever $(\ar, \ar') \ileadstost \phi$.
-We rather propose to introduce theories, and expose them to falsification.
+In most situations, there are too many arguments to attempt to exhaustively test whether any $\ar$ is a decisive argument for any $\phi$.
+And most importantly, it is impossible to confirm definitely that $(\ar, \ar') \ileadstost \phi$, whenever $(\ar, \ar') \ileadstost \phi$.
+This is why falsifiable theories are needed.
 
 A theory $T$ proposing decisive arguments describes a set $D_T$ of decision situations to which it applies, and proposes, for any situation $d = (\Phi, \allargs, \ileadstost) \in D_T$, a subset $\Phi_{d, T} \subseteq \Phi$ and a mapping $f_{d, T}: \Phi_{d, T} → \allargs$.
-The theory claims that it knows the deliberated judgment of $i$ (the individual described by $\ileadstost$ in $d$) about the propositions in $\Phi_{d, T}$, and claims that $f_{d, T}(\phi)$ is a decisive argument for $\phi$.
+The theory claims that it knows the deliberated preference of $i$ (the individual described by $\ileadstost$ in $d$) about the propositions in $\Phi_{d, T}$, and claims that $f_{d, T}(\phi)$ is a decisive argument for $\phi$.
+The theory $T$ is said to have a position about $\prop$ if $(\prop, \text{sure}) \in \Phi_{d, T} ∨ (¬\prop, \text{possible}) \in \Phi_{d, T}$.
+In order for the claims of the theory to be interpretable, it is requested that if $T$ has a position about $\prop$, then it must have a position about $¬\prop$.
+This forces $T$, for each pair $(\prop, ¬\prop)$, to either claim that one is sure, claim that both are possible, or have no claim about the pair.
 
@@
 
-Note that if $(\prop, \text{sure}) \in \Phi_{d, T}$, then including $(\prop, \text{possible})$ in $\Phi_{d, T}$ does not augment the set of falsification instances, thus we suppose $(\prop, \text{sure}) \in \Phi_{d, T} ⇒ (\prop, \text{possible}) \in \Phi_{d, T}$ in what follows.
-
 As is usual in science, falsification procedures should not be considered as ways of definitely validating a theory, but rather as ways of confronting theories.
-We say that two theories $T, T'$ disagree on $\phi$ (or equivalently, on $¬\phi$) iff $\phi \in \Phi_{d, T}$ and $¬\phi \in \Phi_{d, T'}$ in some situation $d \in D_T ∪ D_{T'}$.
-We say that $T$ and $T'$ disagree iff they disagree on some $d \in D_T ∪ D_{T'}$ and $\phi \in \Phi$.
-To confront a theory $T$ to a disagreeing theory $T'$, suffice to test, for any $\phi$ such that $\phi \in \Phi_T, ¬\phi \in \Phi_{T'}$, whether $(f_T(\phi), f_{T'}(¬\phi)) \ileadstoe \phi$.
-Observe that such a test necessarily falsifies one of the theories.
+Two theories $T, T'$ are said to disagree on $\phi$ iff $\phi \in \Phi_{d, T}$ and $¬\phi \in \Phi_{d, T'}$ in some situation $d \in D_T ∪ D_{T'}$.
+$T$ and $T'$ are said to disagree iff they disagree on some $\phi \in \Phi$.
+To confront a theory $T$ to a disagreeing theory $T'$, suffice to test, for any situation $d \in D_T ∪ D_{T'}$ and $\phi$ such that $\phi \in \Phi_{d, T}, ¬\phi \in \Phi_{d, T'}$, whether $(f_{d, T}(\phi), f_{d, T'}(¬\phi)) \ileadstoe \phi$.
+Such a test necessarily falsifies one of the theories.
 
@@
 \begin{proposition}
-	A theory $T$ proposing decisive arguments has no falsification instances iff $\forall d \in D_T, \phi \in \Phi_{d, T}: f_{d, T}(\phi)$ is $\phidec$.
+	\label{thm:fals}
+	A theory $T$ proposing decisive arguments has no falsification instances iff $\forall d \in D_T, \forall \phi \in \Phi_{d, T}: f_{d, T}(\phi)$ is $\phidec$.
 Furthermore, if a theory $T$ proposing decisive arguments has no falsification instances, then $\Phi_{d, T} \subseteq \iPhi$, $\forall d \in D_T$.
 \end{proposition}
+
+\begin{example}[(cont.)]
+	Returning to the previous example, a theory $T$ could claim that, for all individuals that belong to some given socio-economic situation and that have some given degree (described by the theory in sufficient details that it is possible to determine precisely to which kind of individuals it applies), $(\prop_a, \text{sure})$ is in the deliberated preferences of the individuals, for a given alternative $\alt$ also described by $T$.
+The theory also suggests some argument $\ar$, a text that (according to $T$) will convince any individual (fitting the description) that $\prop_\alt$ holds, thus, that $\alt$ is a “good” food product for him.
+The theory can be put to the test by picking an individual fitting the description, presenting the argument together with any other argument (for example, proposed by another theory), and observing whether $i$ is convinced.
+$T$ resists to such a falsification test if $i$ is convinced.
+According to \cref{thm:fals}, $T$ tells the truth if it would resist to any possible falsification test.
+(This is impossible to definitely make sure of.)
+\end{example}
+This example illustrates a difference between this proposal and the classical revealed approach: it could be that $T$ tells the truth even though its claim does not correspond to the revealed preference of some individuals, thus that, given no argument, some individuals would consider $a$ as dominated by another alternative in the set considered.
+It also illustrates a difference between this proposal and persuasion: the goal of $T$ is not merely to convince $i$ (possibly by using its lack of knowledge of any counter-argument to what $T$ says), but to resist any falsification attempt.
+Thus, $T$ should be confronted to arguments coming from as varied perspectives as possible, in order to give confidence that it tells the truth.
+
+\bibliography{simple}
+\end{document}
 

### 2020-04-15 simple.tex
Started rework with two stages

@@
 \begin{document}
-\title{Theories of deliberated preference}
+%\title{Theories of deliberated preference}
+\title{Testable normative theories}
 \author{Olivier Cailloux}
@@
 \section{Motivation}
+TODO The model should be: (m, s) leadsto (t, sure) where m can be for example: after having presented s0, s1, s2, present s3, and tell the individual to wait for one week.
+
 In decision theory and economy in general, preferences are generally considered as “intuitive”, as originating from an “immediate sensation”, following the terms used by \citet{von_neumann_theory_2004} (vNM) \citep{fishburn_retrospective_1989, cailloux_reasons_2017}.
@@
 (Note that probably nobody is able to mentally deduce all consequences of a union of non trivial axioms.) As an example, in a context of trying to determine the voting rule that best represents someone’s notion of justice, the tested individual could accept the axioms of universal domain, independence of irrelevant alternatives, and pareto dominance, without realizing that he has just accepted dictatorship \citep{arrow_social_1963}.
+
+\section{General normative theories}
+A general normative theory is a tuple $(\alltopic, \allargs, I, (\ileadsto, i \in I), \gargs, \gleadsto)$.
+
+TODO: theorist proposes theory $\gamma$.
+Contains set $\allargs$.
+The theory must exhibit a limited number of candidates $s_c$ when $s'$ sometimes trumps $s$ and $s'$ sometimes does not trump $s$ (valid for all $i$): that’s falsifiable, and then permits validation of $\eta$.
+Also, $\gamma$ must exhibit a replacer $s$ of $s_3, s_1$ against $s_2$, or a set of candidate replacers.
+The replacer (or candidates) may depend on $s_3$ and $s_1$, but not on $i$.
+This is falsifiable again.
+And $\gamma$ must fix bounds of width and breadth.
+And $\gamma$ must indicate how an $s \notin \args_\gamma$ is unnecessary, by exhibiting resistant [not trumped by any decisive argument in $\args_\gamma$] candidates from $\args_\gamma$ such that at least one trump $s$ or replace $s$.
+
+A counter-theory may propose $\args^\text{ext}$ with some arguments not in $\allargs$ (or, more generally, may propose to enlarge the conditions for considering that $s', s \ileadsto t$: if DM has eaten a pancake or has eaten no pancake, must be stable).
+Then they either can exhibit a plausible argument in $\args^\text{ext}$ not in $\allargs$ (and indeed $\allargs$ is rejected), or not, and then both theories are equivalent, better keep the simpler one.
+
+Thus, $\gamma$ takes positions only on those things true for all $i$.
+
+Then a theorist can propose a mapping $i$ to $\eta_i$. If $\gamma$ is valid, then it is easy to validate $\eta_i$.
+
+More generally, I need a set of possible situations, and an operation defined by the theory $\gamma$, that brings a situation to another situation, that is normatively better for taking a decision (or innocuous?).
+The operation is: adding an argument.
+This operation corresponds to forming the pair $(s', s)$: from a situation $s'$, we add the argument $s$ and bring $i$ in the situation $(s', s)$ where she has heard two arguments.
+
+Then the normative criterion is: $t$ in DJ of $i$ when $\exists s \suchthat \forall s': (s', s) \ileadstost^i t$ (the theory provides a part of this guarantee under falsification, claiming for all $i$, the model makes the rest under validation for this $i$).
 
@@
 I also say that $\ar$ is $\propsuredec$, $\proppossdec$, or $¬\proppossdec$, when $\phi=(\prop, \text{sure})$, $\phi=(\prop, \text{possible})$, or $\phi=(¬\prop, \text{possible})$, respectively.
-\footnote{$\propsuredec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstosst \prop$, $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$.}
+\footnote{$\propsuredec ⇔ \forall \ar': (\ar', \ar) \ileadstosst \prop ⇔ \forall \ar': ¬[(\ar', \ar) \ileadstope ¬\prop]$, $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$.
+Note that “both” ≠ “we donno”: in case “both”, we know how to prove that both are reasonable options, in the sense that neither is certain.
+We have excluded some possibilities (and some other model could disagree with the “both” conclusion).}
 
@@
 It should be clear that the validity of the conclusions obtained from any theory of deliberated preference rests on the acceptance of this just given normative definition, namely, it is to be considered meaningful that the deliberated preference of $i$ be defined in such a way, given the query protocol used for defining $\ileadstost$ in a particular application.
+
+\commentOC{TODO}
+We want to leave “undecided” as an option: the model takes no position, does not know about $(t, ¬t)$.
+But we want to exclude $t$ possible and $¬t$ unknown.
+Thus $t$ possible should imply $¬t$ possible or $t$ sure.
+If this holds, we can simplify the status of the propositions: only determine whether $t$ is possible for all $t \in \alltopic$, and from there, we know everything.
+This result can be obtained with: assume $s$ decisive for $t$ poss and no $s$ is decisive for $¬t$ poss, then, for some $(s_1, s)$ leading to $t$ sure and $(s_2, s)$ leading to $\set{t, ¬t}$, it is possible to form $(s_2, s_1, s)$, and if this leads to $t$ sure, it should imply that $s + s_1$ is decisive for $t$ sure; and if this leads to $¬t$ possible, then this should imply that $s+s_2$ is decisive for $¬t$ possible.
 
@@
 \bibliography{simple}
-\end{document}
 

### 2020-04-15 simple.tex
Switched to new canvas

@@
 \RequirePackage[l2tabu, orthodox]{nag}
-\documentclass[version=last, pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=14pt, a4paper, french, english]{scrartcl}
+\documentclass[version=last, pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=12pt, a4paper, french, english]{scrartcl}
 \input{preamble/packages}
@@
 \input{preamble/redac}
-\input{preamble/draw}
-\input{preamble/acronyms}
+%\input{preamble/draw}
+%\input{preamble/acronyms}
 \addtokomafont{labelinglabel}{\sffamily\bfseries}
 \renewcommand{\phi}{\varphi}
+
+%I find these settings useful in draft mode. Should be removed for final versions.
+	%Which line breaks are chosen: accept worse lines, therefore reducing risk of overfull lines. Default = 200.
+		\tolerance=2000
+	%Accept overfull hbox up to...
+		\hfuzz=2cm
+	%Reduces verbosity about the bad line breaks.
+		\hbadness 5000
+	%Reduces verbosity about the underful vboxes.
+		\vbadness=1300
 
@@
 	Consider a decision problem where a set of alternatives $\allalts$ is given, containing food products among which $i$ would like to form a deliberated preference (taking into account the effects of food on health, price, pleasure, morality issues related to the production process, and so on).
-The topic could be defined as $\alltopic$ = $\Set{\prop_\alt, ¬\prop_\alt, \forall \alt \in \allalts}$, where $\prop_\alt$ is the proposition according to which $\alt$ is one of the best alternatives among $\allalts$ (there is no strictly better alternatives among $\allalts$, from $i$’s point of view), and $¬\prop_\alt$ is the proposition according to which $\alt$ is not one of the best alternatives among $\allalts$ (some $\alt' \in \allalts$ is a strictly better alternative, from $i$’s point of view).
+The topic could be defined as $\alltopic$ = $\set{\prop_\alt, ¬\prop_\alt, \forall \alt \in \allalts}$, where $\prop_\alt$ is the proposition according to which $\alt$ is one of the best alternatives among $\allalts$ (there is no strictly better alternatives among $\allalts$, from $i$’s point of view), and $¬\prop_\alt$ is the proposition according to which $\alt$ is not one of the best alternatives among $\allalts$ (some $\alt' \in \allalts$ is a strictly better alternative, from $i$’s point of view).
 	The set $\allargs$ is defined as the set of all strings, because in this example it is considered acceptable to restrict arguments to those that can take a textual form.
@@
 The set designates all possible answers over time and over different order of asking the queries.
-Hence, given $\prop \in \alltopic$, define a relation $\ileadsto^\prop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadsto^\prop C$, with $C \subseteq \Set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind.
+Hence, given $\prop \in \alltopic$, define a relation $\ileadsto^\prop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadsto^\prop C$, with $C \subseteq \set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind.
 The querying protocol is supposedly made so that for any $\prop \in \alltopic$, $\ileadsto^\prop = \ileadsto^{¬\prop}$.
 
-This information is only indirectly observable: for example, if $(\ar, \ar') \ileadsto^\prop \{\prop\}$, a querier will never know more than $(\ar, \ar') \ileadsto^\prop C$ with $\prop \in C \subseteq \Set{\prop, ¬\prop, \text{both}}$.
+This information is only indirectly observable: for example, if $(\ar, \ar') \ileadsto^\prop \{\prop\}$, a querier will never know more than $(\ar, \ar') \ileadsto^\prop C$ with $\prop \in C \subseteq \set{\prop, ¬\prop, \text{both}}$.
 Also, it may be only possible to test one ordering of the queries (assuming that $i$ forgets over time might permit to test different orderings, but this assumption might be unrealistic).
@@
 
-Define $\ileadstost$ from $\ileadsto^\prop$ as follows, for any $\prop \in \alltopic$: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadsto^\prop C$ with $C \subseteq \Set{\prop, \text{both}}$; and $(\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadsto^\prop \set{\prop}$.
+Define $\ileadstost$ from $\ileadsto^\prop$ as follows, for any $\prop \in \alltopic$: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadsto^\prop C$ with $C \subseteq \set{\prop, \text{both}}$; and $(\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadsto^\prop \set{\prop}$.
 
@@
 I also say that $\ar$ is $\propsuredec$, $\proppossdec$, or $¬\proppossdec$, when $\phi=(\prop, \text{sure})$, $\phi=(\prop, \text{possible})$, or $\phi=(¬\prop, \text{possible})$, respectively.
-\footnote{$\propsuredec ⇔ \forall \ar': (\ar', \ar) \ileadstosst \prop ⇔ \forall \ar': ¬[(\ar', \ar) \ileadstope ¬\prop]$, $\proppossdec$ ⇔ $\forall \ar': (\ar', \ar) \ileadstopst \prop$.
-Note that “both” ≠ “we donno”: in case “both”, we know how to prove that both are reasonable options, in the sense that neither is certain.
+\footnote{$\propsuredec ⇔ \forall \ar': (\ar', \ar) \ileadstosst \prop ⇔ \forall \ar': ¬[(\ar', \ar) \ileadstope ¬\prop]$, $\proppossdec ⇔ \forall \ar': (\ar', \ar) \ileadstopst \prop$.
+Note that “both” $≠$ “we donno”: in case “both”, we know how to prove that both are reasonable options, in the sense that neither is certain.
 We have excluded some possibilities (and some other model could disagree with the “both” conclusion).}
@@
 \bibliography{simple}
+\end{document}
 
@@
 \section{Model certainties}
-Assume we define $\ar_1 \wibeatse[¬\prop, \text{sure}] \ar_2$ ⇔ $\ar_2 \nwibeatse[\prop] \ar_1$.
-Then, indeed, given $\ar_1 \mleadsto \prop$, $\ar_2 \wibeatse[¬\prop, \text{sure}] \ar_1$ ⇔ $\ar_2 \ibeatse[¬\prop, \text{sure}] \ar_1$.
+Assume we define $\ar_1 \wibeatse[¬\prop, \text{sure}] \ar_2 ⇔ \ar_2 \nwibeatse[\prop] \ar_1$.
+Then, indeed, given $\ar_1 \mleadsto \prop$, $\ar_2 \wibeatse[¬\prop, \text{sure}] \ar_1 ⇔ \ar_2 \ibeatse[¬\prop, \text{sure}] \ar_1$.
 But it gives the wrong conclusion.

### 2020-04-18 simple.tex
minor
Reworked for one simple model overall

@@
 \section{Motivation}
-TODO The model should be: (m, s) leadsto (t, sure) where m can be for example: after having presented s0, s1, s2, present s3, and tell the individual to wait for one week.
-
 In decision theory and economy in general, preferences are generally considered as “intuitive”, as originating from an “immediate sensation”, following the terms used by \citet{von_neumann_theory_2004} (vNM) \citep{fishburn_retrospective_1989, cailloux_reasons_2017}.
@@
 
-\section{General normative theories}
-A general normative theory is a tuple $(\alltopic, \allargs, I, (\ileadsto, i \in I), \gargs, \gleadsto)$.
+\section{Normative theories}
+Sketch: define normative models, using questions, and making claims about DJ.
+A problem is that models specific to a narrow situation will not offer enough means for falsification.
+Then define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.
+BUT what about a model for only one situation?
+Then we need to accept that $q$ can’t be falsified, and accept that it defines the individual (or just assume without proof that it does not).
+
+A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstost[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats)$,
+with $\gargs \subseteq \allargs$, ${\ileadstost[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
+where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$.
+
+To lighten notations, $\ileadstost[i]$ will generally be denoted by $\ileadstost$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$.
+When the symbol $i$ is used in a formula without being bound, the binding $\forall i \in I$ is implied.
+
+As usual, $(\ar', \ar) \nileadstost \phi$ means $¬[(\ar', \ar) \ileadstost \phi]$.
+
+The symbol $¬$ is a negation operator on $\allprops$, such that $\forall \prop \in \allprops: ¬¬\prop = \prop$ (this article also uses this symbol to negate classical logic propositions and as a negation operator on $\Phi$, which should create no confusion).
+Define $¬$ on $\Phi$ as follows, $\forall \prop \in \allprops$: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
+Observe that $¬¬\phi = \phi$.
+
+Abusing notation, given $\ar \in \allargs$ and $\phi \in \Phi$, I write $\ar \ileadstost \phi$ to mean $[\forall \ar' \in \allargs: (\ar', \ar) \ileadstost \phi]$.
+
+The set $\iphi \subseteq \Phi$ is the set of interest. 
+When $(\prop, \text{possible}) \in \iphi$, $\prop$ is considered as a possibility in the deliberated judgment of $i$ (it is not rejected), and when $(\prop, \text{sure}) \in \iPhi$, $\prop$ is considered as a certainty in the deliberated judgment of $i$.
+TODO we should have $(\prop, \text{sure}) \in \iPhi ⇒ (¬\prop, \text{possible}) \notin \iPhi$.
+Part of the content of $\Phi$ is known as a result of a correct normative and empirical analysis.
+
+To ease intuition, let $(\ar', \ar) \ileadstoe \phi$ be equivalent to $(\ar', \ar) \nileadstost ¬\phi$, $\forall \ar', \ar, \phi$.
+
+Given $\phi \in {\gleadsto}(\allargs)$, an argument $\ar \in \allargs$ is \emph{in favor of $\phi$}, $\ar \in \gargs[\phi]$, iff $\ar \in [\gbeatsinv]^{2k}({\gleadstoinv}(\phi))$ for some $k \in \N$, where $R^\alpha$ denotes $\alpha$ times the composition of the relation $R$ with itself.
+(Throughout the article, $\N$ includes zero.) Define $\gargs = \cup_{\phi \in {\gleadstoinv}(\allargs)} \gargs[\phi]$.
+
+Define ${\ibeatse} \subseteq \allargs × \gargs$ such that $\ar' \ibeatse \ar$ iff $\exists \phi \suchthat \ar \in \gargs[\phi] \text{ and } (\ar', \ar) \ileadstoe ¬\phi$. 
+Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[\phi]} \subseteq \allargs × \gargs[\phi]$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$. 
+Define ${\ibeatsst} \subseteq \gargs × \allargs$ such that $\ar' \ibeatsst \ar$ iff $\forall \phi \suchthat \ar' \in \gargs[\phi]: (\ar', \ar) \ileadstost \phi$.
+\footnote{When both $\ar_1, \ar_2 \in \gargs$, the relationship is as follows.
+$\ar_2 \ibeatse \ar_1 ⇒ \ar_2 \nibeatsst \ar_1$, the converse failing only if $\ar_2$ has some claims that $\ar_1$ does not have (thus $\exists \phi \suchthat \ar_2 \in \gargs[\phi] \land \ar_1 \notin \gargs[\phi]$): $\ar_2 \nibeatsst \ar_1$ exactly when $\ar_2$ fails to argue decisively for some of its claims, and $\ar_2 \nibeatse \ar_1$ exactly when $\ar_1$ argues decisively for all of its claims.}
+
+A normative theory starts with an axiom stating its normative adequacy.
+\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$]
+	A general normative theory is \emph{normatively adequate} iff $\forall \phi \in \Phi$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ 
+		\begin{cases}
+			\phi \in \iphi,\\
+			\lnot\phi \notin \iphi.
+		\end{cases}
+	\end{equation}
+\end{axiom}
+
+This notation is justified only if it is impossible that both $\phi \in \iphi$ and $\phi \notin \iphi$ be implied. \commentOC{TODO clarify.} The following conditions permit to obtain this result.
+
+\begin{condition}[Always implies sometimes]
+	\label{cl:ais}
+	${\ileadstost} \subseteq {\ileadstoe}$.
+\end{condition}
+
+\begin{condition}[Sure implies possible]
+	\label{cl:sip}
+	$\forall \ar', \ar \in \allargs, t \in \allprops: (\ar', \ar) \ileadstost (\prop, \text{sure}) ⇒ (\ar', \ar) \ileadstost (\prop, \text{possible})$.
+\end{condition}
+
+\begin{proposition}
+	$\forall \phi \in \Phi$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi],
+	\end{equation}
+	and $\forall \prop \in \allprops$:
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost (\prop, \text{sure})] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost (¬\prop, \text{sure})].
+	\end{equation}
+\end{proposition}
+\begin{proof}
+	The first result obtains because $\ar \ileadstost \phi$ means that given any $\ar'$, $(\ar, \ar') \ileadstost \phi$, hence $(\ar, \ar') \ileadstoe \phi$ (using \cref{cl:ais}), or equivalently, $(\ar, \ar') \nileadstost ¬\phi$, thus no $\ar' \in \allargs$ satisfies $\ar' \ileadstost ¬\phi$.
+For the second one, a similar reasoning yields that $(\ar, \ar') \nileadstost (¬\prop, \text{possible})$, and using the contrapositive of \cref{cl:sip}, $(\ar, \ar') \nileadstost (¬\prop, \text{sure})$, thus no $\ar' \in \allargs$ satisfies $\ar' \ileadstost (¬\prop, \text{sure})$.
+\end{proof}
+
+\begin{definition}[Validity]
+	A theory is \emph{valid} iff ${\gleadsto}(\allargs) \subseteq \iphi$.
+\end{definition}
+
+The following condition mandates that if the arguments used by the theory are not decisive, it knows a reason.
+\begin{definition}[Answerability]
+	$\forall \phi \in \Phi, \ar_1 \in \allargs, \ar_2 \in \gargs[\phi] \cap {\gbeatsinv}(\ar_1): (\ar_2, \ar_1) \ileadstoe ¬\phi ⇒ [\exists \ar_3 \in {\gbeatsinv}(\ar_2) \suchthat (\ar_3, \ar_2) \ileadstoe \phi]$.
+\end{definition}
+
+\begin{definition}[Bounded width]
+	$\forall \ar \in \gargs: \card{\ibeatseinv(\ar)} ≤ b_w$.
+\end{definition}
+
+\begin{definition}[Bounded length]
+	$\forall n \in \N$, if $n > b_l$, there is no sequence of arguments $(\ar_k)_{0 ≤ k < n}$ such that $[\exists \phi \suchthat \forall (0 ≤ k < 2n): \ar_{2k} \in \gargs[\phi]]$ and $(\ar_{k + 1}, \ar_k) \ileadstoe \phi$ and $(\ar_{k + 1}, \ar_k) \ileadstoe ¬\phi$.
+\end{definition}
+
+\begin{definition}[Reinstatement]
+	A theory satisfies \emph{reinstatement} iff $\forall \ar_1, \ar_3 \in \gargs[\phi], \ar_2 \in \allargs: [\ar_1 \ileadstoe \phi, (\ar_2, \ar_1) \ileadstoe ¬\phi, (\ar_3, \ar_2) \ileadstost \phi] ⇒ (\ar_1 + \ar_3, \ar_2) \ileadstost \phi$.
+\end{definition}
+
+\begin{definition}[Operational validity]
+	A theory is \emph{operationally valid} iff $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ [\ar_1 \gbeats \ar_0] \land [\exists \ar_2 \in {\gbeatsinv}(\ar_1) \suchthat (\ar_2, \ar_1) \ileadstoe \phi]$.
+\end{definition}
+
+\begin{theorem}
+	If a theory is answerable, satisfies reinstatement, has bounded width and length, and is operationally valid, it is valid.
+\end{theorem}
+\begin{proof}
+	Given $\phi \in {\gleadsto}(\allargs), \args_2, \args_0 \subseteq \gargs$, define $\args_2$ as \emph{$\phi$-defending} $\args_0$ iff $\forall \ar_1 \in \allargs: [\exists \ar_0 \in \args_0 \suchthat (\ar_1, \ar_0) \ileadstoe ¬\phi] ⇒ [\exists \ar_2 \in \args_2 \suchthat (\ar_2, \ar_1) \ileadstoe \phi]$.
+Define $\args_2$ as \emph{decisively $\phi$-defending} $\args_0$ iff $\forall \ar_1 \in \allargs: [\exists \ar_0 \in \args_0 \suchthat (\ar_1, \ar_0) \ileadstoe ¬\phi] ⇒ [\exists \ar_2 \in \args_2 \suchthat (\ar_2, \ar_1) \ileadstost \phi]$.
+
+	Fix $\phi \in {\gleadsto}(\allargs)$. For all $k \in \N$, define $\gargs[k] = [\gbeatsinv]^{2k}({\gleadstoinv}(\phi))$.
+	Note that $\ar \in \gargs[\phi] ⇔ \exists k \in \N \suchthat \ar \in \gargs[k]$.
+
+	Lemma: $\gargs[k+2]$ $\phi$-defends $\gargs[k]$.
+To prove this, fix $\ar_1 \in \allargs, \ar_0 \in \gargs[k] \suchthat (\ar_1, \ar_0) \ileadstoe ¬\phi$.
+We need to exhibit $\ar_2 \in \gargs[k+2] \suchthat (\ar_2, \ar_1) \ileadstoe \phi$.
+Indeed, we know that $\ar_1 \ibeatse[\phi] \ar_0$, and we can use Operational validity as $\ar_0 \in \gargs[\phi]$, thus, $\ar_1 \gbeats \ar_0$ and $\exists \ar_2 \in {\gbeatsinv}(\ar_1) \suchthat (\ar_2, \ar_1) \ileadstoe \phi$.
+
+	\commentOC{I suppose that, therefore, $\gargs$ $\phi$-defends itself!}
+
+	Pick any even $b > b_l$. Lemma: $\gargs[b] = \emptyset$, and $\gargs[b]$ defends $\gargs[b-2]$, thus, $\gargs[b-2]$ has no attacker.
+
+	Th: $\gargs[4]$ decisively defends $\gargs[2]$ (easy if $j = 4$).
+	Then: if $\gargs[4]$ decisively defends $\gargs[2]$, then anything $\gargs[2]$ defends, it decisively defends.
+\end{proof}
+
+Model: for a given $i$.
+Defends $\prop$.
+$\exists \ar_1 \in \args_\eta \suchthat \ar_1 \ileadstoe \prop$.
+Then, $\forall \ar_2 \in \gargs \suchthat (\ar_2, \ar_1) \ileadstoe ¬\prop: \exists \ar_3 \in \args_\eta \suchthat (\ar_3, \ar_2) \ileadstoe \prop.$
 
@@
 
-Then the normative criterion is: $t$ in DJ of $i$ when $\exists s \suchthat \forall s': (s', s) \ileadstost^i t$ (the theory provides a part of this guarantee under falsification, claiming for all $i$, the model makes the rest under validation for this $i$).
+Then the normative criterion is: $t$ in DJ of $i$ when $\exists s \suchthat \forall s': (s', s) \ileadstost t$ (the theory provides a part of this guarantee under falsification, claiming for all $i$, the model makes the rest under validation for this $i$).
+
+\commentOC{Say that a theory supposedly draws on general principles, which justifies that it talks about multiple $\phi$, even though at this level, there is no connection between them.}
 
@@
 The pair $(\ar, \ar')$ is to be understood as unordered (thus $(\ar, \ar') \ileadstost \prop ⇔ (\ar', \ar) \ileadstost \prop$).
-
-The relation $\ileadstost$ must satisfy the two following properties, or axioms. (A1) $\ileadstost \subseteq \ileadstoe$
-\footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $\ileadstopst \subseteq \ileadstope$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.}
-and (A2) $\forall \prop \in \alltopic: (\ar, \ar') \ileadstost (\prop, \text{sure}) ⇒ (\ar, \ar') \ileadstost (\prop, \text{possible})$
-\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}. 
-Observe that (A1) can equivalently be formulated as $\forall \prop \in \alltopic: [(\ar, \ar') \ileadstost (\prop, \text{sure}) ⇒ (\ar, \ar') \ileadstoe (\prop, \text{sure})]$, or equivalently, $\forall \prop \in \alltopic: [(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇒ (\ar, \ar') \ileadstoe (\prop, \text{possible})]$, and (A2) is equivalent to $\forall \prop \in \alltopic: [(\ar, \ar') \ileadstoe (\prop, \text{sure}) ⇒ (\ar, \ar') \ileadstoe (\prop, \text{possible})]$.
 
@@
 \footnote{$\propsuredec ⇔ \forall \ar': (\ar', \ar) \ileadstosst \prop ⇔ \forall \ar': ¬[(\ar', \ar) \ileadstope ¬\prop]$, $\proppossdec ⇔ \forall \ar': (\ar', \ar) \ileadstopst \prop$.
-Note that “both” $≠$ “we donno”: in case “both”, we know how to prove that both are reasonable options, in the sense that neither is certain.
+Note that “both” ≠ “we donno”: in case “both”, we know how to prove that both are reasonable options, in the sense that neither is certain.
 We have excluded some possibilities (and some other model could disagree with the “both” conclusion).}
@@
 Consider $\ar_2 \mbeats^\text{fail} \ar_1$ (to be continued…)
-
-\bibliography{simple}
-
 \end{document}

### 2020-04-19 simple.tex
Proof works but too complex and mult conds not necessary

@@
 Define ${\ibeatse} \subseteq \allargs × \gargs$ such that $\ar' \ibeatse \ar$ iff $\exists \phi \suchthat \ar \in \gargs[\phi] \text{ and } (\ar', \ar) \ileadstoe ¬\phi$. 
-Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[\phi]} \subseteq \allargs × \gargs[\phi]$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$. 
+Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \gargs[\phi]$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$.
+Define ${\ibeatse[\phi]} \subseteq \gargs[\phi] × \allargs$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe \phi$.
 Define ${\ibeatsst} \subseteq \gargs × \allargs$ such that $\ar' \ibeatsst \ar$ iff $\forall \phi \suchthat \ar' \in \gargs[\phi]: (\ar', \ar) \ileadstost \phi$.
@@
 	$\forall n \in \N$, if $n > b_l$, there is no sequence of arguments $(\ar_k)_{0 ≤ k < n}$ such that $[\exists \phi \suchthat \forall (0 ≤ k < 2n): \ar_{2k} \in \gargs[\phi]]$ and $(\ar_{k + 1}, \ar_k) \ileadstoe \phi$ and $(\ar_{k + 1}, \ar_k) \ileadstoe ¬\phi$.
+\commentOC{This requires that $\ar_4$ have no attacker, not only in the sense that $\ar_4$ argues successfully against $\ar_3$, but in the (too strong) sense that $\ar_4$ argues successfully for $\phi$.
+It makes $\ar_4$ decisive, thus, requires that $\ar_4$ also argues against $\ar_1$, $\ar'_1, …$, and it makes the other arguments non useful.
+(Though may be useful for other dms, as we do not know in advance which one will be decisive.) I suppose I could simplify the presentation by making $\gargs[2]$ contain every good arguments and using only this one.}
 \end{definition}
@@
 \begin{theorem}
-	If a theory is answerable, satisfies reinstatement, has bounded width and length, and is operationally valid, it is valid.
+	If a theory is answerable, satisfies reinstatement, has bounded width and length, and is operationally valid, it is valid. \commentOC{We don’t seem to need most of these conditions!}
 \end{theorem}
@@
 
-	Fix $\phi \in {\gleadsto}(\allargs)$. For all $k \in \N$, define $\gargs[k] = [\gbeatsinv]^{2k}({\gleadstoinv}(\phi))$.
-	Note that $\ar \in \gargs[\phi] ⇔ \exists k \in \N \suchthat \ar \in \gargs[k]$.
+	Fix $\phi \in {\gleadsto}(\allargs)$. We have to show that $\exists \ar \in \allargs \suchthat \ar \ileadstost \phi$.
 
-	Lemma: $\gargs[k+2]$ $\phi$-defends $\gargs[k]$.
+	For all $k \in \N$, define $\gargs[2k] = [({\gbeatsinv} \cap {\ibeatseinv[\phi]}) \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})]^{k}({\gleadstoinv}(\phi))$.
+	Note that $[\exists k \in 2\N \suchthat \ar \in \gargs[k]] ⇒ \ar \in \gargs[\phi]$.
+
+	Lemma: $\forall k \in 2\N: \gargs[k+2]$ $\phi$-defends $\gargs[k]$.
 To prove this, fix $\ar_1 \in \allargs, \ar_0 \in \gargs[k] \suchthat (\ar_1, \ar_0) \ileadstoe ¬\phi$.
 We need to exhibit $\ar_2 \in \gargs[k+2] \suchthat (\ar_2, \ar_1) \ileadstoe \phi$.
-Indeed, we know that $\ar_1 \ibeatse[\phi] \ar_0$, and we can use Operational validity as $\ar_0 \in \gargs[\phi]$, thus, $\ar_1 \gbeats \ar_0$ and $\exists \ar_2 \in {\gbeatsinv}(\ar_1) \suchthat (\ar_2, \ar_1) \ileadstoe \phi$.
+Indeed, we know that $\ar_1 \ibeatse[!\phi] \ar_0$, and we can use Operational validity as $\ar_0 \in \gargs[\phi]$, thus, $\ar_1 \gbeats \ar_0$ and $\exists \ar_2 \in {\gbeatsinv}(\ar_1) \suchthat (\ar_2, \ar_1) \ileadstoe \phi$.
 
@@
 
-	Pick any even $b > b_l$. Lemma: $\gargs[b] = \emptyset$, and $\gargs[b]$ defends $\gargs[b-2]$, thus, $\gargs[b-2]$ has no attacker.
+	Lemma: $\forall k \in 2\N$, if $\gargs[k+2] = \emptyset$, then $\forall s_0 \in \gargs[k]: s_0 \ileadstost \phi$.
+	From the previous lemma, $\gargs[k+2]$ $\phi$-defends $\gargs[k]$, and, considering the implication in the definition of $\phi$-defense and observing that its consequent is false, we can negate its antecedent, obtaining: $\forall \ar_1 \in \allargs, \ar_0 \in \gargs[k]: (\ar_1, \ar_0) \ileadstost \phi$.
+This proves the lemma.
+	\commentOC{Stuff at level $k$ should only take care of rebutting attackers at level $k-1$, and we would instead in this lemma obtain that they do take care of them successfully, enabling the use of reinstatement to get to the $k-2$ level.
+Still, it’s strange that Answerability is not needed.}
 
-	Th: $\gargs[4]$ decisively defends $\gargs[2]$ (easy if $j = 4$).
-	Then: if $\gargs[4]$ decisively defends $\gargs[2]$, then anything $\gargs[2]$ defends, it decisively defends.
+	Pick any even $b > b_l$. 
+	Thanks to Bounded length, $\gargs[b] = \emptyset$. 
+	Define $d = \max\set{k \in 2\N \suchthat k < b, \gargs[k] ≠ \emptyset}$ (which exists because $\gargs[0] ≠ \emptyset$). 
+	Thus, the last lemma can be applied with $k=d$ to obtain $\forall s_0 \in \gargs[d]: s_0 \ileadstost \phi$. Because $\gargs[d] ≠ \emptyset$, this concludes the proof.
 \end{proof}
+
+Change conditions.
+I should be able to prove the theorem using reinst + bounded width instead of bounded length.
+Reinst should serve to discard: $(\ar_2, \ar_1) \ileadstost \phi$, $(\ar'_2, \ar'_1) \ileadstost \phi$, $(\ar'_1, \ar_2) \ileadstoe ¬\phi$, $(\ar_1, \ar'_2) \ileadstoe ¬\phi$.
+
+Clarification.
+General theory says that $\ar_1$ is replaceable (suspects that it’s good for some people): $(\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ (\ar'_1, \ar_0) \ileadstoe ¬\phi$.
+(This will fail if some $i$ thinks $\ar'_1$ is bad arg because of $\ar_0$ but $\ar_1$ is bad because of $\ar_2$.) It may say that $\ar_1$ is bad.
+General theory prepares potentially good arg $\ar_0$ and claims that if $\ar_0 \ileadstoe \phi$, then $\ar_0 \ileadstost \phi$ (this is Answerability).
+So that the model only has to prove the weaker existential claim.
 

### 2020-04-28 simple.tex
Cosmetic small impr
Strengthening (?) of Reinstatement in hope of replacing Bounded length (and because it is necessary for it to make sense anyway).

@@
 To lighten notations, $\ileadstost[i]$ will generally be denoted by $\ileadstost$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$.
-When the symbol $i$ is used in a formula without being bound, the binding $\forall i \in I$ is implied.
+When the symbol $i$, $\ileadstost$ or $\gleadsto$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
 
@@
 \begin{definition}[Reinstatement]
-	A theory satisfies \emph{reinstatement} iff $\forall \ar_1, \ar_3 \in \gargs[\phi], \ar_2 \in \allargs: [\ar_1 \ileadstoe \phi, (\ar_2, \ar_1) \ileadstoe ¬\phi, (\ar_3, \ar_2) \ileadstost \phi] ⇒ (\ar_1 + \ar_3, \ar_2) \ileadstost \phi$.
+	A theory satisfies \emph{reinstatement} iff $\forall \ar_1, \ar_3 \in \gargs[\phi], \ar_2 \in \allargs: [\ar_1 \ileadstoe \phi, (\ar_2, \ar_1) \ileadstoe ¬\phi, (\ar_3, \ar_2) \ileadstoe \phi] ⇒ (\ar_1 + \ar_3, \ar_2) \ileadstoe \phi \land [\forall \ar_4 \ibeatse \ar_1 + \ar_3: \ar_4 \ibeatse \ar_1 \lor \ar_4 \ibeatse \ar_3]$.
 \end{definition}

### 2020-04-30 simple.tex
New conditions that hopefully wake sense

@@
 
-A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstost[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats)$,
-with $\gargs \subseteq \allargs$, ${\ileadstost[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
-where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$.
-
-To lighten notations, $\ileadstost[i]$ will generally be denoted by $\ileadstost$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$.
-When the symbol $i$, $\ileadstost$ or $\gleadsto$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
-
-As usual, $(\ar', \ar) \nileadstost \phi$ means $¬[(\ar', \ar) \ileadstost \phi]$.
+\subsection{Definition}
+A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstost[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
+with ${\ileadstost[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
+where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$, and $+$ a commutative associative internal binary operation on $\allargs$.
+The notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.
 
@@
 
+To lighten notations, $\ileadstost[i]$ will generally be denoted by $\ileadstost$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$.
+When the symbol $i$, $\ileadstost$ or $\gleadsto$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
+
+As usual with binary relations, $(\ar', \ar) \nileadstost \phi$ means $¬[(\ar', \ar) \ileadstost \phi]$.
 Abusing notation, given $\ar \in \allargs$ and $\phi \in \Phi$, I write $\ar \ileadstost \phi$ to mean $[\forall \ar' \in \allargs: (\ar', \ar) \ileadstost \phi]$.
@@
 When $(\prop, \text{possible}) \in \iphi$, $\prop$ is considered as a possibility in the deliberated judgment of $i$ (it is not rejected), and when $(\prop, \text{sure}) \in \iPhi$, $\prop$ is considered as a certainty in the deliberated judgment of $i$.
-TODO we should have $(\prop, \text{sure}) \in \iPhi ⇒ (¬\prop, \text{possible}) \notin \iPhi$.
 Part of the content of $\Phi$ is known as a result of a correct normative and empirical analysis.
+
+Given $\ar_0 \in \gargs$, let $c(\ar_0) = \bigcup \set{\args \subseteq \gargs \suchthat \ar_0 = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar_0$.
+
+Given $\phi \in {\gleadsto}(\allargs)$, an argument $\ar \in \allargs$ is \emph{in favor of $\phi$}, $\ar \in \gargs[\phi, 0]$, iff $\ar \in [\gbeatsinv]^{2k}({\gleadstoinv}(\phi))$ for some $k \in \N$, where $R^\alpha$ denotes $\alpha$ times the composition of the relation $R$ with itself.
+(Throughout the article, $\N$ includes zero.)
+Define $\gargs[\phi] = \set{\ar \suchthat c(\ar) \subseteq \gargs[\phi, 0]}$.
+Define $\gargs = \cup_{\phi \in {\gleadstoinv}(\allargs)} \gargs[\phi]$.
+
+Given $\ar_2 \in \gargs, \ar_1 \in \allargs$, $\ar_2 \mbeats \ar_1$ has the semantic that $\gamma$ claims that $\ar_2$ trumps $\ar_1$ if necessary.
+Given $\ar_1 \in \allargs, \ar_0 \in \gargs$, $\ar_1 \mbeats \ar_0$ has the semantic that $\gamma$ claims that it knows how to resist an attack from $\ar_1$ coming in response to using $\ar_0$, if it does come.
 
@@
 
-Given $\phi \in {\gleadsto}(\allargs)$, an argument $\ar \in \allargs$ is \emph{in favor of $\phi$}, $\ar \in \gargs[\phi]$, iff $\ar \in [\gbeatsinv]^{2k}({\gleadstoinv}(\phi))$ for some $k \in \N$, where $R^\alpha$ denotes $\alpha$ times the composition of the relation $R$ with itself.
-(Throughout the article, $\N$ includes zero.) Define $\gargs = \cup_{\phi \in {\gleadstoinv}(\allargs)} \gargs[\phi]$.
-
-Define ${\ibeatse} \subseteq \allargs × \gargs$ such that $\ar' \ibeatse \ar$ iff $\exists \phi \suchthat \ar \in \gargs[\phi] \text{ and } (\ar', \ar) \ileadstoe ¬\phi$. 
 Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \gargs[\phi]$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$.
 Define ${\ibeatse[\phi]} \subseteq \gargs[\phi] × \allargs$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe \phi$.
-Define ${\ibeatsst} \subseteq \gargs × \allargs$ such that $\ar' \ibeatsst \ar$ iff $\forall \phi \suchthat \ar' \in \gargs[\phi]: (\ar', \ar) \ileadstost \phi$.
-\footnote{When both $\ar_1, \ar_2 \in \gargs$, the relationship is as follows.
-$\ar_2 \ibeatse \ar_1 ⇒ \ar_2 \nibeatsst \ar_1$, the converse failing only if $\ar_2$ has some claims that $\ar_1$ does not have (thus $\exists \phi \suchthat \ar_2 \in \gargs[\phi] \land \ar_1 \notin \gargs[\phi]$): $\ar_2 \nibeatsst \ar_1$ exactly when $\ar_2$ fails to argue decisively for some of its claims, and $\ar_2 \nibeatse \ar_1$ exactly when $\ar_1$ argues decisively for all of its claims.}
 
+\subsection{Classify propositions}
 A normative theory starts with an axiom stating its normative adequacy.
@@
 
+\subsection{Validity and conditions}
 \begin{definition}[Validity]
@@
 
+$\ar_0 + \ar_2$ anticipates attacks from those attacking either, minus those attacked by any.
+(Actually any attacked may still attack the addition, but that’s because of some other not-yet-attacked, anticipated, attack.)
+
+Define $\mbeats[g] \subseteq \gargs × \allargs$ as $\ar_2 \mbeats[g] \ar_1$ iff $\exists \ar \in c(\ar_2) \suchthat \ar \mbeats \ar_1$.
+Define $\mbeats[a] \subseteq \allargs × \gargs$ as $\ar_1 \mbeats[a] \ar_0$ iff $\exists \ar \in c(\ar_0) \suchthat \ar_1 \mbeats \ar$ and $\nexists \ar \in c(\ar_0) \suchthat \ar \mbeats \ar_1]$.
+Define $\mbeats[*] \subseteq \allargs × \allargs$ as $\gbeatsstar = {\mbeats[g]} \cup {\mbeats[a]}$.
+
 The following condition mandates that if the arguments used by the theory are not decisive, it knows a reason.
 \begin{definition}[Answerability]
-	$\forall \phi \in \Phi, \ar_1 \in \allargs, \ar_2 \in \gargs[\phi] \cap {\gbeatsinv}(\ar_1): (\ar_2, \ar_1) \ileadstoe ¬\phi ⇒ [\exists \ar_3 \in {\gbeatsinv}(\ar_2) \suchthat (\ar_3, \ar_2) \ileadstoe \phi]$.
-\end{definition}
-
-\begin{definition}[Bounded width]
-	$\forall \ar \in \gargs: \card{\ibeatseinv(\ar)} ≤ b_w$.
+	$\forall \phi \in \Phi, \ar_1 \in \allargs, \ar_2 \in \gargs[\phi] \cap {\gbeatsstarinv}(\ar_1): (\ar_2, \ar_1) \ileadstoe ¬\phi ⇒ [\exists \ar_3 \in {\gbeatsstarinv}(\ar_2) \suchthat (\ar_3, \ar_2) \ileadstoe \phi]$.
 \end{definition}
@@
 \begin{definition}[Bounded length]
-	$\forall n \in \N$, if $n > b_l$, there is no sequence of arguments $(\ar_k)_{0 ≤ k < n}$ such that $[\exists \phi \suchthat \forall (0 ≤ k < 2n): \ar_{2k} \in \gargs[\phi]]$ and $(\ar_{k + 1}, \ar_k) \ileadstoe \phi$ and $(\ar_{k + 1}, \ar_k) \ileadstoe ¬\phi$.
-\commentOC{This requires that $\ar_4$ have no attacker, not only in the sense that $\ar_4$ argues successfully against $\ar_3$, but in the (too strong) sense that $\ar_4$ argues successfully for $\phi$.
-It makes $\ar_4$ decisive, thus, requires that $\ar_4$ also argues against $\ar_1$, $\ar'_1, …$, and it makes the other arguments non useful.
-(Though may be useful for other dms, as we do not know in advance which one will be decisive.) I suppose I could simplify the presentation by making $\gargs[2]$ contain every good arguments and using only this one.}
-\end{definition}
-
-\begin{definition}[Reinstatement]
-	A theory satisfies \emph{reinstatement} iff $\forall \ar_1, \ar_3 \in \gargs[\phi], \ar_2 \in \allargs: [\ar_1 \ileadstoe \phi, (\ar_2, \ar_1) \ileadstoe ¬\phi, (\ar_3, \ar_2) \ileadstoe \phi] ⇒ (\ar_1 + \ar_3, \ar_2) \ileadstoe \phi \land [\forall \ar_4 \ibeatse \ar_1 + \ar_3: \ar_4 \ibeatse \ar_1 \lor \ar_4 \ibeatse \ar_3]$.
+	$\gargs$ must be finite.
 \end{definition}
@@
 \begin{definition}[Operational validity]
-	A theory is \emph{operationally valid} iff $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ [\ar_1 \gbeats \ar_0] \land [\exists \ar_2 \in {\gbeatsinv}(\ar_1) \suchthat (\ar_2, \ar_1) \ileadstoe \phi]$.
+	A theory is \emph{operationally valid} iff $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ [\ar_1 \gbeats \ar_0] \land [\exists \ar_2 \in {\gbeatsinv}(\ar_1) \suchthat (\ar_0 + \ar_2, \ar_1) \ileadstoe \phi]$.
 \end{definition}
 
+\subsection{Example model}
+\begin{itemize}
+	\item $\ar_0 = \text{“Veg bec of ethics and health”}$
+	\item $\ar_1 = \text{“Ethics is not defined”}$
+	\item $\ar_2 = \text{“It is since Aristotle at least”}$
+	\item $\ar_1' = \text{“Health isn’t important”}$
+	\item $\ar_2' = \text{“Ask my grandmother”}$
+	\item $\ar_1 \mbeats \ar_0$, $\ar_1' \mbeats \ar_0$
+	\item $\ar_2 \mbeats \ar_1$, $\ar_2' \mbeats \ar_1'$
+	\item $\ar_0 + \ar_2 \mbeats \ar_1$
+	\item $\ar_1' \mbeats \ar_0 + \ar_2$
+	\item $\ar_0 + \ar_2' \mbeats \ar_1'$
+	\item $\ar_1 \mbeats \ar_0 + \ar_2'$
+	\item $\ar_0 + \ar_2 + \ar_2' \mbeats \ar_1$
+	\item $\ar_0 + \ar_2 + \ar_2' \mbeats \ar_1'$
+\end{itemize}
+
+\subsection{Theorem}
 \begin{theorem}
-	If a theory is answerable, satisfies reinstatement, has bounded width and length, and is operationally valid, it is valid. \commentOC{We don’t seem to need most of these conditions!}
+	If a theory is answerable, has bounded length, and is operationally valid, it is valid.
 \end{theorem}
 \begin{proof}
+	TODO adapt to new definitions!
+
 	Given $\phi \in {\gleadsto}(\allargs), \args_2, \args_0 \subseteq \gargs$, define $\args_2$ as \emph{$\phi$-defending} $\args_0$ iff $\forall \ar_1 \in \allargs: [\exists \ar_0 \in \args_0 \suchthat (\ar_1, \ar_0) \ileadstoe ¬\phi] ⇒ [\exists \ar_2 \in \args_2 \suchthat (\ar_2, \ar_1) \ileadstoe \phi]$.

### 2020-04-30 simple.tex
Simple proof, working.

@@
 Define $\mbeats[g] \subseteq \gargs × \allargs$ as $\ar_2 \mbeats[g] \ar_1$ iff $\exists \ar \in c(\ar_2) \suchthat \ar \mbeats \ar_1$.
-Define $\mbeats[a] \subseteq \allargs × \gargs$ as $\ar_1 \mbeats[a] \ar_0$ iff $\exists \ar \in c(\ar_0) \suchthat \ar_1 \mbeats \ar$ and $\nexists \ar \in c(\ar_0) \suchthat \ar \mbeats \ar_1]$.
-Define $\mbeats[*] \subseteq \allargs × \allargs$ as $\gbeatsstar = {\mbeats[g]} \cup {\mbeats[a]}$.
+Define $\mbeats[a] \subseteq \allargs × \gargs$ as $\ar_1 \mbeats[a] \ar_0$ iff $\exists \ar \in c(\ar_0) \suchthat \ar_1 \mbeats \ar$ and $\nexists \ar \in c(\ar_0) \suchthat \ar \mbeats \ar_1$.
+Define ${\gbeatsstar} \subseteq \allargs × \allargs$ as ${\gbeatsstar} = {\mbeats[g]} \cup {\mbeats[a]}$.
+
+\begin{remark}
+	I currently conceive these conditions in the following way.
+The model must anticipate in its initial arguments the counter-arguments that $i$ may have in mind.
+Thus, $\ar_1$ trumps $\ar_0$ is observed when $i$ has been given $\ar_1$.
+When the model answers with $\ar_2$, if $i$ is unconvinced (of $\ar_2 + \ar_0$ trumping $\ar_1$), the procedure stops (the model can’t argue that yes-but-maybe-$i$-has-$\ar_1'$-in-mind; in particular, it wouldn’t be feasible to interrogate $i$ if the arguments are given thanks to labeling in a supermarket).
+However, if $i$ is given $\ar_1'$, the model must be given a chance to play its counter-argument, and may not be falsified because $\ar_2 + \ar_0$ is not enough: once $i$ is given $\ar_1'$, it is no more claimed by the model that $\ar_2 + \ar_0$ suffices any longer.
+
+	Relatedly, Operational validity is (almost) void when $\ar_1$ trumps $\ar_0$ and $\ar_0 \gbeats \ar_1$ (and has already observed to be successful, thus $\ar_0$ trumps $\ar_1$): in that case, suffices to play $\ar_2 = \ar_0$ and define $\ar_0 + \ar_0 = \ar_0$, so $\ar_2 + \ar_0$ trumps $\ar_1$.
+
+	In summary: when $\ar_1$ trumps $\ar_0$, and the model has not already answered this argument using $\ar_0$ (thus $¬ \ar_0 \gbeats \ar_1$), Op.
+val.
+demands an answer.
+When $\ar_1$ trumps $\ar_0$, and the model has answered already using $\ar_0$, and we have checked that indeed $\ar_0$ trumps $\ar_1$, Answerability demands that the model can explain this instability by the fact that someone must have given another argument $\ar_1'$ to $i$ (and this is to be checked using means outside the formal model).
+\end{remark}
 
@@
 \begin{definition}[Answerability]
-	$\forall \phi \in \Phi, \ar_1 \in \allargs, \ar_2 \in \gargs[\phi] \cap {\gbeatsstarinv}(\ar_1): (\ar_2, \ar_1) \ileadstoe ¬\phi ⇒ [\exists \ar_3 \in {\gbeatsstarinv}(\ar_2) \suchthat (\ar_3, \ar_2) \ileadstoe \phi]$.
+	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ [\exists \ar_1' \in {\gbeatsstarinv}(\ar_0) \suchthat (\ar_1', \ar_0) \ileadstoe ¬\phi]$.
 \end{definition}
@@
 
+\begin{definition}[No self-attack]
+	$\gbeats$ must be irreflexive.
+\end{definition}
+
 \begin{definition}[Operational validity]
-	A theory is \emph{operationally valid} iff $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ [\ar_1 \gbeats \ar_0] \land [\exists \ar_2 \in {\gbeatsinv}(\ar_1) \suchthat (\ar_0 + \ar_2, \ar_1) \ileadstoe \phi]$.
+	A theory is \emph{operationally valid} iff $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1) \suchthat (\ar_0 + \ar_2, \ar_1) \ileadstoe \phi$.
 \end{definition}
+
+\subsection{Theorem}
+\begin{theorem}
+	If a theory is answerable, has bounded length, does not self-attack, and is operationally valid, it is valid.
+\end{theorem}
+\begin{proof}
+	Lemma: given $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$, if $\ar[k] \nileadstost \phi$, then: $\exists \ar[k + 1] \in \gargs[\phi] \suchthat \card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
+
+	Pick any $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$.
+We know that $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar[k]$.
+Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeatsstar \ar[k] \land \ar_1' \ibeatse[!\phi] \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$ and $\ar[k] + \ar_2 \ibeatse[\phi] \ar'_1$.
+	Define $\ar[k + 1] = \ar_2 + \ar[k]$.
+
+	\commentOC{Note that we do not have $\ar_1 \gbeats \ar[k]$.}
+	By No self-attack, $¬(\ar[k] \gbeatsstar \ar'_1)$.
+Thus, $\ar_2 \notin c(\ar[k])$ (because $\ar_2 \in c(\ar[k])$ and $\ar_2 \gbeats \ar'_1$ implies $\ar[k] \gbeatsstar \ar'_1$ by definition of $\gbeatsstar$).
+	Thus, $\card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
+
+	\commentOC{No use of of $\ar[k] + \ar_2 \ibeatse \ar_1$, and we use Op val only on planned attacks!
+The current protocol amounts to: each time the model is endangered, it has to produce one more arg.
+in support, and we check only at the end (after at worst finitely many steps, as $\gargs$ is bounded) if it has managed to convince.
+With the difference that the model is indicated which $\ar_1$ is endangering it, to guide selection of the ultimately decisive argument.
+Actually, if playing $\ar_2$ at some stage did not move $i$ and $\ar_1$ still attacks $\ar_0 + \ar_2$, we can say that the model missed answering that step, thus either we choose to give it a second chance (maybe it chose the wrong $\ar_2$ to counter the $\ar_1'$ it believed was relevant, or it needed both $\ar_2$ and $\ar_4$), or we give up in fear of losing our time.
+Actually, the protocol is that when applying Answerability, we are supposed to pick the $\ar_1'$ that $i$ just was given by another model, thus, if that’s still the same $\ar_1$ as the step before, the model has lost (it can’t map what it’s told to an argument it knows how to answer).}
+	This proves the lemma.
+
+	To prove the theorem, given $\phi \in {\gleadsto}(\allargs)$, we need to exhibit an argument $\ar$ such that $\ar \ileadstost \phi$.
+	Define a finite sequence $(\ar[0], \ar[1], \ar[2], …)$, starting from $\ar[0] = {\gleadstoinv}(\phi)$, using the lemma, until the condition $\ar[k] \nileadstost \phi$ no longer holds.
+This condition must turn false after some finite number of steps, because $\card{c(\ar[k])}$ grows at each step, $c(\ar[k]) \subseteq \gargs$ by definition of $c(.)$, and using Bounded length.
+The last element of the sequence is the argument we look for.
+\end{proof}
 
@@
 
-\subsection{Theorem}
-\begin{theorem}
-	If a theory is answerable, has bounded length, and is operationally valid, it is valid.
-\end{theorem}
-\begin{proof}
-	TODO adapt to new definitions!
-
-	Given $\phi \in {\gleadsto}(\allargs), \args_2, \args_0 \subseteq \gargs$, define $\args_2$ as \emph{$\phi$-defending} $\args_0$ iff $\forall \ar_1 \in \allargs: [\exists \ar_0 \in \args_0 \suchthat (\ar_1, \ar_0) \ileadstoe ¬\phi] ⇒ [\exists \ar_2 \in \args_2 \suchthat (\ar_2, \ar_1) \ileadstoe \phi]$.
-Define $\args_2$ as \emph{decisively $\phi$-defending} $\args_0$ iff $\forall \ar_1 \in \allargs: [\exists \ar_0 \in \args_0 \suchthat (\ar_1, \ar_0) \ileadstoe ¬\phi] ⇒ [\exists \ar_2 \in \args_2 \suchthat (\ar_2, \ar_1) \ileadstost \phi]$.
-
-	Fix $\phi \in {\gleadsto}(\allargs)$. We have to show that $\exists \ar \in \allargs \suchthat \ar \ileadstost \phi$.
-
-	For all $k \in \N$, define $\gargs[2k] = [({\gbeatsinv} \cap {\ibeatseinv[\phi]}) \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})]^{k}({\gleadstoinv}(\phi))$.
-	Note that $[\exists k \in 2\N \suchthat \ar \in \gargs[k]] ⇒ \ar \in \gargs[\phi]$.
-
-	Lemma: $\forall k \in 2\N: \gargs[k+2]$ $\phi$-defends $\gargs[k]$.
-To prove this, fix $\ar_1 \in \allargs, \ar_0 \in \gargs[k] \suchthat (\ar_1, \ar_0) \ileadstoe ¬\phi$.
-We need to exhibit $\ar_2 \in \gargs[k+2] \suchthat (\ar_2, \ar_1) \ileadstoe \phi$.
-Indeed, we know that $\ar_1 \ibeatse[!\phi] \ar_0$, and we can use Operational validity as $\ar_0 \in \gargs[\phi]$, thus, $\ar_1 \gbeats \ar_0$ and $\exists \ar_2 \in {\gbeatsinv}(\ar_1) \suchthat (\ar_2, \ar_1) \ileadstoe \phi$.
-
-	\commentOC{I suppose that, therefore, $\gargs$ $\phi$-defends itself!}
-
-	Lemma: $\forall k \in 2\N$, if $\gargs[k+2] = \emptyset$, then $\forall s_0 \in \gargs[k]: s_0 \ileadstost \phi$.
-	From the previous lemma, $\gargs[k+2]$ $\phi$-defends $\gargs[k]$, and, considering the implication in the definition of $\phi$-defense and observing that its consequent is false, we can negate its antecedent, obtaining: $\forall \ar_1 \in \allargs, \ar_0 \in \gargs[k]: (\ar_1, \ar_0) \ileadstost \phi$.
-This proves the lemma.
-	\commentOC{Stuff at level $k$ should only take care of rebutting attackers at level $k-1$, and we would instead in this lemma obtain that they do take care of them successfully, enabling the use of reinstatement to get to the $k-2$ level.
-Still, it’s strange that Answerability is not needed.}
-
-	Pick any even $b > b_l$. 
-	Thanks to Bounded length, $\gargs[b] = \emptyset$. 
-	Define $d = \max\set{k \in 2\N \suchthat k < b, \gargs[k] ≠ \emptyset}$ (which exists because $\gargs[0] ≠ \emptyset$). 
-	Thus, the last lemma can be applied with $k=d$ to obtain $\forall s_0 \in \gargs[d]: s_0 \ileadstost \phi$. Because $\gargs[d] ≠ \emptyset$, this concludes the proof.
-\end{proof}
-
+\subsection{The rest}
 Change conditions.

### 2020-05-01 simple.tex
Corr irrefl ⇒ asymm

@@
 \begin{definition}[No self-attack]
-	$\gbeats$ must be irreflexive.
+	$\gbeatsstar$ must be asymmetric.
+\end{definition}
+
+\begin{definition}[No repetition]
+	$\nexists \ar_0 \in \gargs[\phi], \ar_1 \in \allargs, \ar_2 \in c(\ar_0) \suchthat \ar_2 \gbeats \ar_1 \gbeatsstar \ar_0$.
 \end{definition}
@@
 \end{definition}
+
+\begin{remark}
+	When $\gbeatsstar$ is as defined above, asymmetry of $\gbeatsstar$ with the other conditions implies No repetition: by construction of $\gbeatsstar$, $\forall \ar_0 \in \gargs[\phi], \ar_1 \in \allargs, \ar_2 \in c(\ar_0) \suchthat \ar_2 \gbeats \ar_1: \ar_0 \gbeatsstar \ar_1$, thus, by asymmetry, $¬(\ar_1 \gbeatsstar \ar_0)$.
+\end{remark}
 

### 2020-05-02 simple.tex
Sketch of what comes next

@@
 where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$, and $+$ a commutative associative internal binary operation on $\allargs$.
-The notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.
+Given $\args \subseteq \allargs$, the notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.
 
@@
 
-\begin{definition}[No self-attack]
-	$\gbeatsstar$ must be asymmetric.
-\end{definition}
-
 \begin{definition}[No repetition]
@@
 
-\begin{remark}
-	When $\gbeatsstar$ is as defined above, asymmetry of $\gbeatsstar$ with the other conditions implies No repetition: by construction of $\gbeatsstar$, $\forall \ar_0 \in \gargs[\phi], \ar_1 \in \allargs, \ar_2 \in c(\ar_0) \suchthat \ar_2 \gbeats \ar_1: \ar_0 \gbeatsstar \ar_1$, thus, by asymmetry, $¬(\ar_1 \gbeatsstar \ar_0)$.
-\end{remark}
-
 \subsection{Theorem}
 \begin{theorem}
-	If a theory is answerable, has bounded length, does not self-attack, and is operationally valid, it is valid.
+	If a theory is answerable, has bounded length, does not repeat, and is operationally valid, it is valid.
 \end{theorem}
@@
 Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeatsstar \ar[k] \land \ar_1' \ibeatse[!\phi] \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$ and $\ar[k] + \ar_2 \ibeatse[\phi] \ar'_1$.
-	Define $\ar[k + 1] = \ar_2 + \ar[k]$.
+	Define $\ar[k + 1] = \ar[k] + \ar_2$.
 
 	\commentOC{Note that we do not have $\ar_1 \gbeats \ar[k]$.}
-	By No self-attack, $¬(\ar[k] \gbeatsstar \ar'_1)$.
-Thus, $\ar_2 \notin c(\ar[k])$ (because $\ar_2 \in c(\ar[k])$ and $\ar_2 \gbeats \ar'_1$ implies $\ar[k] \gbeatsstar \ar'_1$ by definition of $\gbeatsstar$).
+	By No repetition, $\ar_2 \notin c(\ar[k])$.
 	Thus, $\card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
@@
 \end{proof}
+
+\subsection{Current question}
+Should I leave open the uplifting of $+$ for more generality?
+Is this really sufficiently general to encompass both interpretations of Answerability, and more?
+Or should I stick to the current, “single-try”, approach and interpretation?
+
+\subsection{Interpreting Answerability}
+At a given stage in operationalizing the protocol, define $f(\ar_0)$ as the arguments that are considered as having a chance to attack $\ar_0$ (without backtracking).
+Thus, this will not include $\ar_1$ if indeed $\ar_2$ is considered by $i$ as a satisfying answer to $\ar_1$.
+We can interpret Answerability in two ways.
+Strong answ: $\exists \ar_1 \in f(\ar_0) \suchthat \ar_1 \gbeats \ar_0$.
+Weak answ: $f(\ar_0) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0$.
+
+A model can be allowed to try only once each answer. If $\ar_2 \gbeats \ar_1 \land \ar_1 \in f(\ar_0 + \ar_2)$, the model has lost.
+
+Thus, four variants, given $\ar_2 \gbeats \ar_1$.
+\begin{itemize}
+	\item Strong answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land \forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeatsstar \ar_0 + \ar_2$.
+	\item Strong answ with multiple tries: $\forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeatsstar \ar_0 + \ar_2$.
+(Example: $\ar_1 = \text{“for ethical reasons”}$, and $\eta$ knows two c-a to this, from different angles.) 	\item Weak answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land [f(\ar_0 + \ar_2) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0]$.
+	\item Weak answ with multiple tries: $f(\ar_0 + \ar_2) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0 + \ar_2$.
+\end{itemize}
+
+Goal: leave addition free so as to admit multiple tries, and prove that Strong answ with multiple tries is the right one for a general approach: suitable restriction to the model permits single try (with same conditions); and weak answ actually does not permit more models.
+
+When $f$ is available and is single-valued, question: should we use Strong or weak answ?
+Right answer: use Strong answ.
+It is stricly more general.
+A model that wants weak answ can define its internal attacks suitable (to be proven); and a model that wants to claim more can.
+
+When $f$ is not available, only remains: single try (just give a decisive argument) or multiple tries (try more and more arguments, blindly).
+
+Suppose that a model also defines $f_\eta$, meaning: $f_\eta(\ar_1) = \ar_2$ the argument the model plays against $\ar_1$.
+Thus $f_\eta$, like $\gbeats$, is a binary relation over $\allargs$, but $f_\eta$ in supplement returns a single argument or none.
+Also, $\ar_2 = f(\ar_1) ⇒ \ar_2 \gbeats \ar_1$.
+When a reason $\ar_1$ for rejecting $\ar_0$ is not known, $f_\eta(\ar_0)$ instead gives the argument to be played next.
+Note that $f_\eta$ is only useful when (in the known c-a variant) for some $\ar_1$ there are multiple candidates $\ar_2$ or when (in the unknown c-a variant) for some $\ar_0$ here are multiple candidates $\ar_2$.
+In fact, this is more complicated: $f_\eta(\ar_1)$ can give first $\ar_2$, then, if that is not enough, $\ar_4$ (thus it’s rather $f_\eta(\ar_1, \ar_0)$).
+
+Under Strong anws, we ask that $f(\ar_0) \cap {\gbeatsinv}(\ar_0) ≠ \emptyset$, and (inevitably) that $f_\eta(\ar_1) ≠ \emptyset$.
+Under weak answ, we do not expect anticipation and only demand that $f_\eta(\ar_1) ≠ \emptyset$.
+But this does not allow supplementary models.
+TODO prove this.
+
+\subsection{Single-try models}
+The above models can define several $\ar_2$ for one $\ar_1$.
+Even when interpreting Answerability in the strong sense (mandating that exactly the $\ar_1'$ we search for be defined, not just any $\ar_1'$), this gives a lot of flexibility to the model, and correspondingly, makes it very difficult to falsify: we only know that is unconclusive when all possible subset of answers to a $\ar_1$ has been tried
+
+TODO false: we try any sequence and then poof. Thus, is my approach insufficiently general (and thus should be restrained to the single-try models anyway)?
+
+\begin{definition}[No self-attack]
+	$\gbeatsstar$ must be asymmetric.
+\end{definition}
+
+\begin{remark}
+	When $\gbeatsstar$ is as defined above, asymmetry of $\gbeatsstar$ with the other conditions implies No repetition: by construction of $\gbeatsstar$, $\forall \ar_0 \in \gargs[\phi], \ar_1 \in \allargs, \ar_2 \in c(\ar_0) \suchthat \ar_2 \gbeats \ar_1: \ar_0 \gbeatsstar \ar_1$, thus, by asymmetry, $¬(\ar_1 \gbeatsstar \ar_0)$.
+\end{remark}
 

### 2020-05-02 simple.tex
Stripped down conditions and proof

@@
 \begin{definition}[Answerability]
-	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ [\exists \ar_1' \in {\gbeatsstarinv}(\ar_0) \suchthat (\ar_1', \ar_0) \ileadstoe ¬\phi]$.
+	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ [\exists \ar_1' \in {\gbeatsstarinv}(\ar_0)]$.
 \end{definition}
@@
 \begin{definition}[Operational validity]
-	A theory is \emph{operationally valid} iff $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1) \suchthat (\ar_0 + \ar_2, \ar_1) \ileadstoe \phi$.
+	A theory is \emph{operationally valid} iff $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
 \end{definition}
@@
 	Lemma: given $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$, if $\ar[k] \nileadstost \phi$, then: $\exists \ar[k + 1] \in \gargs[\phi] \suchthat \card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
-
-	Pick any $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$.
+	To prove the lemma, let us pick any $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$.
 We know that $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar[k]$.
-Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeatsstar \ar[k] \land \ar_1' \ibeatse[!\phi] \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$ and $\ar[k] + \ar_2 \ibeatse[\phi] \ar'_1$.
+Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeatsstar \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$.
 	Define $\ar[k + 1] = \ar[k] + \ar_2$. 
-
-	\commentOC{Note that we do not have $\ar_1 \gbeats \ar[k]$.}
 	By No repetition, $\ar_2 \notin c(\ar[k])$.
@@
 
+	To prove the theorem, given $\phi \in {\gleadsto}(\allargs)$, we need to exhibit an argument $\ar$ such that $\ar \ileadstost \phi$.
+	Define a finite sequence $(\ar[0], \ar[1], \ar[2], …)$, starting from $\ar[0] = {\gleadstoinv}(\phi)$, using the lemma, until the condition $\ar[k] \nileadstost \phi$ no longer holds.
+This condition must turn false after some finite number of steps, because $\card{c(\ar[k])}$ grows at each step, $c(\ar[k]) \subseteq \gargs$ by definition of $c(.)$, and using Bounded length.
+The last element of the sequence is the argument we look for.
+\end{proof}
 	\commentOC{No use of of $\ar[k] + \ar_2 \ibeatse \ar_1$, and we use Op val only on planned attacks!
@@
 Actually, the protocol is that when applying Answerability, we are supposed to pick the $\ar_1'$ that $i$ just was given by another model, thus, if that’s still the same $\ar_1$ as the step before, the model has lost (it can’t map what it’s told to an argument it knows how to answer).}
-	This proves the lemma.
-
-	To prove the theorem, given $\phi \in {\gleadsto}(\allargs)$, we need to exhibit an argument $\ar$ such that $\ar \ileadstost \phi$.
-	Define a finite sequence $(\ar[0], \ar[1], \ar[2], …)$, starting from $\ar[0] = {\gleadstoinv}(\phi)$, using the lemma, until the condition $\ar[k] \nileadstost \phi$ no longer holds.
-This condition must turn false after some finite number of steps, because $\card{c(\ar[k])}$ grows at each step, $c(\ar[k]) \subseteq \gargs$ by definition of $c(.)$, and using Bounded length.
-The last element of the sequence is the argument we look for.
-\end{proof}
 

### 2020-05-02 simple.tex
Weakening of Op val and comment about the No Answ case.

@@
 \begin{definition}[Validity]
-	A theory is \emph{valid} iff ${\gleadsto}(\allargs) \subseteq \iphi$.
+	A theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iphi \land ¬\phi \notin \iphi]$.
 \end{definition}
@@
 \begin{definition}[Operational validity]
-	A theory is \emph{operationally valid} iff $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
+	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeatsstar \ar_0 \land (\ar_1, \ar_0) \ileadstoe ¬\phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
 \end{definition}
@@
 Thus, this will not include $\ar_1$ if indeed $\ar_2$ is considered by $i$ as a satisfying answer to $\ar_1$.
-We can interpret Answerability in two ways.
+We can interpret Answerability in the following ways.
 Strong answ: $\exists \ar_1 \in f(\ar_0) \suchthat \ar_1 \gbeats \ar_0$.
 Weak answ: $f(\ar_0) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0$.
+Or suppress Answ and replace Op.
+val.
+by Strong op.
+val.: $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
 

### 2020-05-03 simple.tex
Started analysis of conditions for no contradictory conclusions

@@
 \subsection{Classify propositions}
-A normative theory starts with an axiom stating its normative adequacy.
-\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$]
-	A general normative theory is \emph{normatively adequate} iff $\forall \phi \in \Phi$: 
+The notations $\iphi$ and $\iphibar$ designate subsets of $\Phi$, representing the propositions that $i$ accepts and rejects, respectively.
+
+\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$ 1]
+	$\forall \phi \in \Phi$: 
 	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ 
-		\begin{cases}
-			\phi \in \iphi,\\
-			\lnot\phi \notin \iphi.
-		\end{cases}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iphi.
 	\end{equation}
 \end{axiom}
+\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$ 2]
+	$\forall \phi \in \Phi$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \lnot\phi \in \iphibar.
+	\end{equation}
+\end{axiom}
+\begin{axiom}[Coherent complement]
+	$\forall \phi \in \Phi: \phi \in \iphi ⇒ \phi \notin \iphibar$.
+\end{axiom}
 
-This notation is justified only if it is impossible that both $\phi \in \iphi$ and $\phi \notin \iphi$ be implied. \commentOC{TODO clarify.} The following conditions permit to obtain this result.
+\begin{definition}[Coherent protocol]
+	$\forall \phi \in \Phi: \ar \ileadstost \phi ⇒ \ar \nileadstost ¬\phi$.
+\end{definition}
+
+\begin{theorem}
+	Under axioms of Normative adequacy, Coherent complement ⇒ Coherent protocol.
+\end{theorem}
+\begin{proof}
+	Coherent complement is equivalent to $\forall \phi \in \phi: ¬(\phi \in \iphi \land \phi \in \iphibar)$.
+	Coherent protocol is equivalent to $\forall \phi \in \Phi: ¬(\ar \ileadstost \phi \land \ar \ileadstost ¬\phi)$, which implies (using Norm ad 1 and 2) $\forall \phi \in \Phi: ¬(\phi \in \iphi \land \phi \in \iphibar)$.
+\end{proof}
+
+\begin{theorem}
+	Under axioms of Normative adequacy, Coherent protocol ⇒ Coherent complement.
+\end{theorem}
+\begin{proof}
+	This is false under the current definitions: if $\ileadstost = \emptyset$, coherent protocol, but $\phi \in \iphi \land \phi \in \iphibar$ possible.
+\end{proof}
+
+\begin{axiom}[Coherent negation]
+	$\forall \phi \in \Phi: \phi \in \iphi ⇔ ¬\phi \in \iphibar$.
+\end{axiom}
+This notation (writing $\phi \in \iphibar$ as equivalent to $\phi \notin \iphi$) is justified only if it is impossible that both $\phi \in \iphi$ and $\phi \notin \iphi$ be implied (thus, if Coherent complement).
+\commentOC{TODO clarify.} The following conditions permit to obtain this result.
+\commentOC{Cond.
+1 is stronger than necessary: we could have ¬cond.
+1 and still Coh compl: $(\ar_2, \ar_1) \ileadstost \phi$ and $(\ar_2, \ar_1) \ileadstost ¬\phi$ without problems if $\ar_2$ and $\ar_1$ are not decisive.
+In fact, $(\ar_2, \ar_1) \ileadstoe ¬\phi$ should be defined as $(\ar_2, \ar_1) \nileadstost \phi) \lor (\ar_2, \ar_1) \ileadstost ¬\phi$, just in case a strange protocol allows both leading always to $\phi$ and $¬\phi$, and I think the rest goes through.}
 

### 2020-05-03 simple.tex
Tentative def for case gargs for certainty ≠ gargs for possibility
Seems unfructuous because anyway the gargs for certainty must resist rebuttal against possibility, thus mandating that they also be gargs for possibility is free (and much simpler)

@@
 \subsection{Definition}
-A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstost[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
-with ${\ileadstost[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
+A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
+with ${\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
 where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$, and $+$ a commutative associative internal binary operation on $\allargs$.
@@
 
-To lighten notations, $\ileadstost[i]$ will generally be denoted by $\ileadstost$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$.
+Given any $\ar', \ar, \prop$, let $(\ar', \ar) \ileadstost (\prop, \text{sure})$ be equivalent to $(\ar', \ar) \nileadstoe (¬\prop, \text{poss}) \land (\ar', \ar) \ileadstoe (\prop, \text{sure}) \land (\ar', \ar) \nileadstoe (¬\prop, \text{sure})$; and $(\ar', \ar) \ileadstost (\prop, \text{poss})$ be equivalent to $(\ar', \ar) \nileadstoe (¬\prop, \text{sure})$.
+\footnote{Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$.
+Define $(\ar', \ar) \ileadstoe (\prop, \text{sure})$ iff she sometimes chooses $\set{\prop}$ and $(\ar', \ar) \ileadstoe (\prop, \text{poss})$ iff she sometimes chooses $\set{\prop}$ or $\set{\prop, ¬\prop}$.
+Then, $(\ar', \ar) \ileadstost (\prop, \text{sure})$ iff she always chooses $\set{\prop}$ and $(\ar', \ar) \ileadstost (\prop, \text{poss})$ iff she always chooses either $\set{\prop}$ or $\set{\prop, ¬\prop}$.}
+
+To lighten notations, $\ileadstoe[i]$ will generally be denoted by $\ileadstoe$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$.
 When the symbol $i$, $\ileadstost$ or $\gleadsto$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
@@
 Given $\ar_1 \in \allargs, \ar_0 \in \gargs$, $\ar_1 \mbeats \ar_0$ has the semantic that $\gamma$ claims that it knows how to resist an attack from $\ar_1$ coming in response to using $\ar_0$, if it does come.
-
-To ease intuition, let $(\ar', \ar) \ileadstoe \phi$ be equivalent to $(\ar', \ar) \nileadstost ¬\phi$, $\forall \ar', \ar, \phi$.
-
-Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \gargs[\phi]$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$.
-Define ${\ibeatse[\phi]} \subseteq \gargs[\phi] × \allargs$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe \phi$.
 
@@
 
+Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \gargs[\phi]$ such that, when $\phi = (\prop, \text{sure})$, $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe (¬\prop, \text{poss}) \lor (\ar', \ar) \ileadstoe (¬\prop, \text{sure})$, and when $\phi = (\prop, \text{poss})$, $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$.
+Define ${\ibeatse[\phi]} \subseteq \gargs[\phi] × \allargs$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe \phi$.
+
 The following condition mandates that if the arguments used by the theory are not decisive, it knows a reason.
@@
 
+\begin{definition}[Claiming certainty requires claiming possibility]
+	$\forall (\prop, \text{sure}) \in {\gleadsto}(\allargs): (\prop, \text{poss}) \in {\gleadsto}(\allargs)$.
+\end{definition}
+
+\begin{definition}[Challenging possibility implies challenging certainty]
+	$\forall (\prop, \text{sure}) \in {\gleadsto}(\allargs), \ar_1 \in \allargs, \ar_0 \in \gargs[(\prop, \text{sure})]: (\ar_1, \ar_0) \ileadstoe (¬\prop, \text{sure}) ⇒ (\ar_1, \ar_0) \ileadstoe (¬\prop, \text{poss})$.
+\end{definition}
+
 \subsection{Theorem}
@@
 	To prove the lemma, let us pick any $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$. 
+	We know that $\exists \ar_1 \in \allargs \suchthat (\ar_1, \ar[k]) \nileadstost \phi$.
+
+	We want to prove, first, that $(\ar_1, \ar[k]) \ileadstoe ¬\phi$. If $\phi = (\prop, \text{poss})$, that is clear from the definition of $\ileadstost$. If $\phi = (\prop, \text{sure})$,
+
+	\commentOC{With new definition of $\ileadstost$, when $\phi = (\prop, \text{sure})$, from $\ar \nileadstost \phi$ we only obtain that $\ar \ileadstoe ¬\phi \lor …$, thus, we still need to show that $\ileadstoe (\prop, \text{sure})$ and that $\nileadstoe (¬\prop, \text{sure})$.}
 	We know that $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar[k]$.

### 2020-05-08 simple.tex
(Probably) wrong path for clarifiying possible status of a prop

@@
 
-The set $\iphi \subseteq \Phi$ is the set of interest. 
-When $(\prop, \text{possible}) \in \iphi$, $\prop$ is considered as a possibility in the deliberated judgment of $i$ (it is not rejected), and when $(\prop, \text{sure}) \in \iPhi$, $\prop$ is considered as a certainty in the deliberated judgment of $i$.
+The set $\iPhi \subseteq \Phi$ is the set of interest. 
+When $(\prop, \text{possible}) \in \iPhi$, $\prop$ is considered as a possibility in the deliberated judgment of $i$ (it is not rejected), and when $(\prop, \text{sure}) \in \iPhi$, $\prop$ is considered as a certainty in the deliberated judgment of $i$.
 Part of the content of $\Phi$ is known as a result of a correct normative and empirical analysis.
 
-Given $\ar_0 \in \gargs$, let $c(\ar_0) = \bigcup \set{\args \subseteq \gargs \suchthat \ar_0 = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar_0$.
+Given $\phi \in {\gleadsto}(\allargs)$, an argument $\ar \in \allargs$ is \emph{in favor of $\phi$}, $\ar \in \gargs[\phi, 1]$, iff $\ar \in [\gbeatsinv]^{2k}({\gleadstoinv}(\phi))$ for some $k \in \N$, where $R^\alpha$ denotes $\alpha$ times the composition of the relation $R$ with itself.
+(Throughout the article, $\N$ includes zero.)
 
-Given $\phi \in {\gleadsto}(\allargs)$, an argument $\ar \in \allargs$ is \emph{in favor of $\phi$}, $\ar \in \gargs[\phi, 0]$, iff $\ar \in [\gbeatsinv]^{2k}({\gleadstoinv}(\phi))$ for some $k \in \N$, where $R^\alpha$ denotes $\alpha$ times the composition of the relation $R$ with itself.
-(Throughout the article, $\N$ includes zero.)
-Define $\gargs[\phi] = \set{\ar \suchthat c(\ar) \subseteq \gargs[\phi, 0]}$.
-Define $\gargs = \cup_{\phi \in {\gleadstoinv}(\allargs)} \gargs[\phi]$.
+Given $\phi \in {\gleadsto}(\allargs)$ and $1 ≤ k \in \N$, define $\gargs[\phi, k + 1] = \gargs[\phi, k] + \gargs[\phi, 1] = \set{\ar_k + \ar_1 \suchthat \ar_k \in \gargs[\phi, k], \ar_1  \in \gargs[\phi, 1]}$.
+Define $\gargs[\phi] = \bigcup_{1 ≤ k \in \N} \gargs[\phi, k]$, and $\gargs = \cup_{\phi \in {\gleadstoinv}(\allargs)} \gargs[\phi]$.
+
+Given $\phi \in \Phi$ and $\ar_0 \in \gargs[\phi]$, let $c^\phi(\ar_0) = \bigcup \set{\args \subseteq \gargs[\phi, 0] \suchthat \ar_0 = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar_0$ in favor of $\phi$.
 
@@
 
+Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \gargs[\phi]$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$.
+Define ${\ibeatse[\phi]} \subseteq \gargs[\phi] × \allargs$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe \phi$.
+
 \subsection{Classify propositions}
-The notations $\iphi$ and $\iphibar$ designate subsets of $\Phi$, representing the propositions that $i$ accepts and rejects, respectively.
+The notations $\iPhi$ and $\iPhirej$ designate the subsets of $\Phi$ whose propositions $i$ deliberately accepts and rejects, respectively.
 
@@
 	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iphi.
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iPhi.
 	\end{equation}
@@
 	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \lnot\phi \in \iphibar.
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \lnot\phi \in \iPhirej.
 	\end{equation}
 \end{axiom}
-\begin{axiom}[Coherent complement]
-	$\forall \phi \in \Phi: \phi \in \iphi ⇒ \phi \notin \iphibar$.
-\end{axiom}
+\begin{property}[Coherent complement]
+	$\iPhi \cap \iPhirej = \emptyset$.
+\end{property}
+
+The following definition may be useful for analytic clarification, but this property is not required as an axiom for the results in this article.
+\begin{property}[Exhaustivity]
+	$\forall \phi \in \Phi: \phi \notin \iPhi ⇒ \phi \in \iPhirej$.
+\end{property}
+Exhaustivity can be considered a strong demand, as it requires every proposition to be deliberately accepted or rejected.
+\commentOC{I’m not so sure: could consider that $t$ is merely possible when not determined.}
+
+Define the propositions whose status is determined as $\iPhidet = \iPhi \cup \iPhirej$.
+
+\begin{property}[Suppl]
+	$\forall \prop \in \allprops: \propsure \notin \iPhi ⇒ \propsure \in \iPhirej$.
+\end{property}
+\begin{property}[Negation coherence]
+	\label{prop:cohb}
+	$\forall \phi \in \Phi: \phi \in \iPhi ⇔ ¬\phi \in \iPhirej$, and $\forall \prop \in \allprops: \propsure \in \iPhi ⇒ (¬\prop, \text{sure}) \in \iPhirej$.
+\end{property}
+This property entails the following one.
+\begin{property}[Per-proposition coherence]
+	$\forall \prop \in \allprops$, exactly one of the following four propositions is true: 
+	\begin{itemize}
+		\item $\propsure \in \iPhi \land \propposs \in \iPhi \land (¬\prop, \text{sure}) \in \iPhirej \land (¬\prop, \text{poss}) \in \iPhirej$;
+		\item $\propsure \in \iPhirej \land \propposs \in \iPhi \land (¬\prop, \text{sure}) \in \iPhirej \land (¬\prop, \text{poss}) \in \iPhi$;
+		\item $\propsure \in \iPhirej \land \propposs \in \iPhirej \land (¬\prop, \text{sure}) \in \iPhi \land (¬\prop, \text{poss}) \in \iPhi$;
+		\item $\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \Phi \setminus \iPhidet$;
+	\end{itemize}
+\end{property}
+\begin{proof}
+	If $\propsure \in \iPhi$, then $\notpropsure \in \iPhirej$, thus $\propposs \in \iPhi$ as $\notpropsure = ¬\propposs$ and $\phi \in \iPhi ⇔ ¬\phi \in \iPhirej$; and finally, $\notpropposs \in \iPhirej$ as $\notpropposs = ¬\propsure$ and $\phi \in \iPhi ⇔ ¬\phi \in \iPhirej$.
+
+	If $\propsure \notin \iPhi$ and $\propposs \in \iPhi$, then?
+\end{proof}
+
+This property in turn entails the following one.
+\begin{property}[Per-proposition determination]
+	$\forall \prop \in \allprops: [\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \iPhidet] \lor [\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \Phi \setminus \iPhidet]$.
+\end{property}
+
+Given a normative model, define $\mPhi \subseteq \Phi$ as the set of propositions whose status is determined by the Normative adequacy axioms: $\phi \in \mPhi ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost \phi]$.
+
+\Cref{prop:cohb} can’t be proven, but the following weaker versions can: $\forall \phi \in \Phi: \phi \in \mPhi ⇒ ¬\phi \in \iPhirej$ and $\forall \phi \in \Phi: \propsure \in \mPhi ⇒ ¬\propsure \in \iPhirej$.
+
+\begin{property}[Per-proposition weaker coherence bis]
+	$\forall \phi \in \Phi: \phi \in \mPhi ⇒ ¬\phi \notin \mPhi$.
+\end{property}
+
+A proposition $\phi$ has a determined status iff $\phi \in \mPhi \lor ¬\phi \in \mPhi$. (Not both?)
+
+\begin{property}[Coherent determination]
+	$\forall \prop \in \allprops: $ either all propositions among $\set{\propsure, \propposs, ¬\propsure, ¬\propposs}$ have a determined status, or none have.
+\end{property}
+
+… and it is coherent!
+
+the subset of $\Phi$ about which $\allargs$ and $\ileadstoe$ give access:
 
@@
 \begin{proof}
-	Coherent complement is equivalent to $\forall \phi \in \phi: ¬(\phi \in \iphi \land \phi \in \iphibar)$.
-	Coherent protocol is equivalent to $\forall \phi \in \Phi: ¬(\ar \ileadstost \phi \land \ar \ileadstost ¬\phi)$, which implies (using Norm ad 1 and 2) $\forall \phi \in \Phi: ¬(\phi \in \iphi \land \phi \in \iphibar)$.
+	Coherent complement is equivalent to $\forall \phi \in \phi: ¬(\phi \in \iPhi \land \phi \in \iPhirej)$.
+	Coherent protocol is equivalent to $\forall \phi \in \Phi: ¬(\ar \ileadstost \phi \land \ar \ileadstost ¬\phi)$, which implies (using Norm ad 1 and 2) $\forall \phi \in \Phi: ¬(\phi \in \iPhi \land \phi \in \iPhirej)$.
 \end{proof}
@@
 \begin{proof}
-	This is false under the current definitions: if $\ileadstost = \emptyset$, coherent protocol, but $\phi \in \iphi \land \phi \in \iphibar$ possible.
+	This is false under the current definitions: if $\ileadstost = \emptyset$, coherent protocol, but $\phi \in \iPhi \land \phi \in \iPhirej$ possible.
 \end{proof}
@@
 \begin{axiom}[Coherent negation]
-	$\forall \phi \in \Phi: \phi \in \iphi ⇔ ¬\phi \in \iphibar$.
+	$\forall \phi \in \Phi: \phi \in \iPhi ⇔ ¬\phi \in \iPhirej$.
 \end{axiom}
-This notation (writing $\phi \in \iphibar$ as equivalent to $\phi \notin \iphi$) is justified only if it is impossible that both $\phi \in \iphi$ and $\phi \notin \iphi$ be implied (thus, if Coherent complement).
+
+\begin{proposition}
+	$\forall \ar \in \allargs: \ar \ileadstost \propsure ⇒ \ar \ileadstost \propposs$.
+\end{proposition}
+\begin{proof}
+	By hypothesis, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadstost \propsure$, which implies, by definition of $\ileadstost$, that $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoe (¬\prop, \text{sure})$.
+Therefore, $\ar \ileadstost \propposs$.
+\end{proof}
+
+This notation (writing $\phi \in \iPhirej$ as equivalent to $\phi \notin \iPhi$) is justified only if it is impossible that both $\phi \in \iPhi$ and $\phi \notin \iPhi$ be implied (thus, if Coherent complement).
 \commentOC{TODO clarify.} The following conditions permit to obtain this result.
@@
 \begin{definition}[Validity]
-	A theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iphi \land ¬\phi \notin \iphi]$.
+	A theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
 \end{definition}
@@
 Define ${\gbeatsstar} \subseteq \allargs × \allargs$ as ${\gbeatsstar} = {\mbeats[g]} \cup {\mbeats[a]}$.
+\commentOC{TODO $c^\phi$, not $c$.
+Use $c = \cup_{\phi} c^\phi$?}
 
@@
 
-Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \gargs[\phi]$ such that, when $\phi = (\prop, \text{sure})$, $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe (¬\prop, \text{poss}) \lor (\ar', \ar) \ileadstoe (¬\prop, \text{sure})$, and when $\phi = (\prop, \text{poss})$, $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$.
-Define ${\ibeatse[\phi]} \subseteq \gargs[\phi] × \allargs$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe \phi$.
-
 The following condition mandates that if the arguments used by the theory are not decisive, it knows a reason.
 \begin{definition}[Answerability]
-	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ [\exists \ar_1' \in {\gbeatsstarinv}(\ar_0)]$.
+	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \nileadstost \phi ⇒ [\exists \ar_1' \in {\gbeatsstarinv}(\ar_0)]$.
 \end{definition}
@@
 \begin{definition}[Operational validity]
-	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeatsstar \ar_0 \land (\ar_1, \ar_0) \ileadstoe ¬\phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
+	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeatsstar \ar_0 \land (\ar_1, \ar_0) \nileadstost \phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
 \end{definition}
 
-\begin{definition}[Claiming certainty requires claiming possibility]
-	$\forall (\prop, \text{sure}) \in {\gleadsto}(\allargs): (\prop, \text{poss}) \in {\gleadsto}(\allargs)$.
+\begin{definition}[Claiming certainty also claims possibility]
+	$\forall \ar_0 \in \allargs: \ar_0 \gleadsto (\prop, \text{sure}) ⇒ \ar_0 \gleadsto (\prop, \text{poss})$.
 \end{definition}
 
-\begin{definition}[Challenging possibility implies challenging certainty]
-	$\forall (\prop, \text{sure}) \in {\gleadsto}(\allargs), \ar_1 \in \allargs, \ar_0 \in \gargs[(\prop, \text{sure})]: (\ar_1, \ar_0) \ileadstoe (¬\prop, \text{sure}) ⇒ (\ar_1, \ar_0) \ileadstoe (¬\prop, \text{poss})$.
+\begin{proposition}[Arguments for certainty also argue for possibility]
+	From Claiming certainty also claims possibility follows that $\forall (\prop, \text{sure}) \in {\gleadsto}(\allargs): \ar_0 \in \gargs[(\prop, \text{sure})] ⇒ \ar_0 \in \gargs[(\prop, \text{poss})]$.
+\end{proposition}
+\begin{proof}
+	TODO
+\end{proof}
+
+\begin{definition}
+	$\forall \ar_0 \gleadsto (\prop, \text{sure}), \ar_1 \in \allargs: (\ar_1, \ar_0) \nileadstoe \phi ⇒ (\ar_1, \ar_0) \ileadstoe ¬\phi$.
 \end{definition}

### 2020-05-10 simple.tex
Some suppl rmk about wrong path
Much drafts about classification of props and Normative axiom

@@
 \renewcommand{\phi}{\varphi}
+\DeclareMathAlphabet{\mathup}{OT1}{\familydefault}{m}{n}
 
@@
 
-\subsection{Classify propositions}
-The notations $\iPhi$ and $\iPhirej$ designate the subsets of $\Phi$ whose propositions $i$ deliberately accepts and rejects, respectively.
+\subsection{Classify propositions (mix attempt)}
+Define $p \ileadstostw \phi$ iff $p \nileadstoe ¬\phi$.
+
+\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstoe$ mix 1]
+	$\forall \phi \in \Phi$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \nileadstoe ¬\phi] ⇒ \phi \in \iPhi.
+	\end{equation}
+\end{axiom}
+\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstoe$ mix 2]
+	$\forall \phi \in \Phi$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \nileadstoe ¬\phi] ⇒ ¬\phi \notin \iPhi.
+	\end{equation}
+\end{axiom}
+These two axioms imply that not $(\ar \nileadstoe ¬\phi \land \ar' \nileadstoe \phi)$ (a form of coherent complement); equivalently, not $(\ar \ileadstostw \propsure \land \ar' \ileadstostw \notpropposs)$.
+
+\commentOC{This is unsatisfactory because of a mix between normative and empirical assumptions; and because an axiom should be true, not empirically falsifiable.
+Also, if the protocol is such; then we should simply weaken the conclusion, not have to conclude that the axioms are false.}
+
+To avoid risk of empirical falsification, we can weaken the axioms. Also, the first axiom seems too strong.
+
+Recall that $\ar \ileadstoe \phi$ means $\exists \ar_1 \suchthat (\ar_1, \ar) \ileadstoe \phi$.
+
+\begin{axiom}[Normative adequacy 1, weaker]
+	$\forall \prop \in \allprops$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \nileadstoe \notpropposs \land \ar \ileadstoe \propsure \land \ar \nileadstoe \notpropsure] ⇒ \propsure \in \iPhi;
+	\end{equation}
+	$\forall \prop \in \allprops$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \nileadstoe \propsure] ⇒ \notpropposs \in \iPhi.
+	\end{equation}
+\end{axiom}
+\begin{axiom}[Normative adequacy 2, weaker]
+	$\forall \prop \in \allprops$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \nileadstoe \notpropposs \land \ar \ileadstoe \propsure \land \ar \nileadstoe \notpropsure] ⇒ \notpropposs \notin \iPhi;
+	\end{equation}
+	$\forall \prop \in \allprops$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \nileadstoe \propsure] ⇒ \propsure \notin \iPhi.
+	\end{equation}
+\end{axiom}
+
+This version is still too strong: never observing $\propsure$ should not suffice to reject $\propsure$.
+Rejecting $\propsure$ is not only about observing that no decisive argument leads to it: it is about positively proving that $\notpropposs$ (that is, with a decisive argument).
+That is, if nothing is decisive in $\allargs$, the axioms should say nothing rather than claiming that $\propsure$ is rejected.
+This makes the required axioms weaker, thus, is good.
+And we don’t lose much as, under indecisiveness, there is no short proof of rejection of $\propsure$.
+It is also simpler, as it rejects $\propsure$ exactly when it accepts $\notpropposs$ exactly when some short proof of it exists.
+
+Another problem is that this still asks the question whether these axioms could be empirically falsified.
+On the contrary, the axioms should obviously mandate nothing empirical.
+They should be weaker, and the resulting equivalent statement, looking like those above, should be obtained as a result.
+
+\subsection{Classify propositions, mandating positive observations}
+Define $(\ar_1, \ar) \ileadstostp \phi$ iff $(\ar_1, \ar) \nileadstoe ¬\phi \land (\ar_1, \ar) \ileadstoe \phi$.
+Define $\ar \ileadstostp \phi$ iff $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadstostp \phi$.
+
+\begin{axiom}[Normative adequacy 1, positive]
+	$\forall \prop \in \allprops$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs] ⇒ \propsure \in \iPhi;
+	\end{equation}
+	$\forall \prop \in \allprops$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \notpropposs] ⇒ \notpropposs \in \iPhi.
+	\end{equation}
+\end{axiom}
+\begin{axiom}[Normative adequacy 2, positive]
+	$\forall \prop \in \allprops$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs] ⇒ \notpropposs \notin \iPhi;
+	\end{equation}
+	$\forall \prop \in \allprops$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \notpropposs] ⇒ \propsure \notin \iPhi.
+	\end{equation}
+\end{axiom}
+
+Problem: we should deal with accepting and rejecting possibilities only. Thus, proving $\propsure$ only serves to reject $\notpropposs$.
+
+\subsection{Classify propositions, only two implications}
+\begin{axiom}[Normative adequacy in two implications]
+	$\forall \prop \in \allprops$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propposs] ⇒ \propposs \in \iPhi;
+	\end{equation}
+	$\forall \prop \in \allprops$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs] ⇒ \propsure \in \iPhi.
+	\end{equation}
+\end{axiom}
+
+Given a model, define $\Box\Phi \subseteq \Phi$ as 
+$\propposs \in \Box\Phi$ iff $[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propposs]$
+and 
+$\propsure \in \Box\Phi$ iff $[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs]$.
+\begin{property}[Model completeness]
+	$\forall \phi \in \Phi: \phi \in \Box\Phi \lor ¬\phi \in \Box\Phi$.
+\end{property}
+\begin{property}[Deliberation completeness]
+	$\forall \phi \in \Phi: \phi \in \iPhi \lor ¬\phi \in \iPhi$.
+\end{property}
+\begin{proposition}
+	Under Normative adequacy, Model completeness implies Deliberation completeness.
+\end{proposition}
+Models as defined here do not mandate Model completeness, and in fact, even the weaker Deliberation completeness is not mandated.
+This is good for two reasons.
+First, Deliberation completeness can appear too strong.
+Second, it is dubious that, for non trivial decision problems, models can be found for which both Normative adequacy is normatively compelling and Model completeness holds.
+
+\subsection{Classify propositions, draft}
+The notations $\iacc$ and $\irej$ designate the subsets of $\Phi$ whose propositions $i$ deliberately accepts and rejects, respectively.
 
@@
 	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iPhi.
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iacc.
 	\end{equation}
@@
 	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \lnot\phi \in \iPhirej.
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \lnot\phi \in \irej.
 	\end{equation}
 \end{axiom}
+
+\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$ 1 weaker]
+	$\forall \phi \in \Phi$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \propsure] ⇒ \propsure \in \iacc.
+	\end{equation}
+\end{axiom}
+\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$ 2 weaker]
+	$\forall \phi \in \Phi$: 
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \propposs] ⇒ \notpropsure \in \irej.
+	\end{equation}
+\end{axiom}
+
+I suppose I can’t prove this.
 \begin{property}[Coherent complement]
-	$\iPhi \cap \iPhirej = \emptyset$.
+	$\iacc \cap \irej = \emptyset$.
+\end{property}
+
+Given a normative model, define $\mPhi \subseteq \Phi$ as the set of propositions whose status is determined by the Normative adequacy axioms: $\phi \in \mPhi ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost \phi]$.
+
+I certainly want this (equivalent to coh co restricted to the props determined).
+\begin{property}[Desired? 1]
+	$\phi \in \mPhi ⇒ ¬\phi \notin \mPhi$.
+\end{property}
+\begin{property}[Desired? 2]
+	$\propsure \in \mPhi ⇒ \propposs \in \iacc$.
 \end{property}
@@
 \begin{property}[Exhaustivity]
-	$\forall \phi \in \Phi: \phi \notin \iPhi ⇒ \phi \in \iPhirej$.
+	$\forall \phi \in \Phi: \phi \notin \iacc ⇒ \phi \in \irej$.
 \end{property}
@@
 
-Define the propositions whose status is determined as $\iPhidet = \iPhi \cup \iPhirej$.
+Define the propositions whose status is determined as $\idet = \iacc \cup \irej$.
 
 \begin{property}[Suppl]
-	$\forall \prop \in \allprops: \propsure \notin \iPhi ⇒ \propsure \in \iPhirej$.
+	$\forall \prop \in \allprops: \propsure \notin \iacc ⇒ \propsure \in \irej$.
 \end{property}
@@
 	\label{prop:cohb}
-	$\forall \phi \in \Phi: \phi \in \iPhi ⇔ ¬\phi \in \iPhirej$, and $\forall \prop \in \allprops: \propsure \in \iPhi ⇒ (¬\prop, \text{sure}) \in \iPhirej$.
+	$\forall \phi \in \Phi: \phi \in \iacc ⇔ ¬\phi \in \irej$, and $\forall \prop \in \allprops: \propsure \in \iacc ⇒ (¬\prop, \text{sure}) \in \irej$.
 \end{property}
@@
 	\begin{itemize}
-		\item $\propsure \in \iPhi \land \propposs \in \iPhi \land (¬\prop, \text{sure}) \in \iPhirej \land (¬\prop, \text{poss}) \in \iPhirej$;
-		\item $\propsure \in \iPhirej \land \propposs \in \iPhi \land (¬\prop, \text{sure}) \in \iPhirej \land (¬\prop, \text{poss}) \in \iPhi$;
-		\item $\propsure \in \iPhirej \land \propposs \in \iPhirej \land (¬\prop, \text{sure}) \in \iPhi \land (¬\prop, \text{poss}) \in \iPhi$;
-		\item $\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \Phi \setminus \iPhidet$;
+		\item $\propsure \in \iacc \land \propposs \in \iacc \land (¬\prop, \text{sure}) \in \irej \land (¬\prop, \text{poss}) \in \irej$;
+		\item $\propsure \in \irej \land \propposs \in \iacc \land (¬\prop, \text{sure}) \in \irej \land (¬\prop, \text{poss}) \in \iacc$;
+		\item $\propsure \in \irej \land \propposs \in \irej \land (¬\prop, \text{sure}) \in \iacc \land (¬\prop, \text{poss}) \in \iacc$;
+		\item $\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \Phi \setminus \idet$;
 	\end{itemize}
@@
 \begin{proof}
-	If $\propsure \in \iPhi$, then $\notpropsure \in \iPhirej$, thus $\propposs \in \iPhi$ as $\notpropsure = ¬\propposs$ and $\phi \in \iPhi ⇔ ¬\phi \in \iPhirej$; and finally, $\notpropposs \in \iPhirej$ as $\notpropposs = ¬\propsure$ and $\phi \in \iPhi ⇔ ¬\phi \in \iPhirej$.
-
-	If $\propsure \notin \iPhi$ and $\propposs \in \iPhi$, then?
+	If $\propsure \in \iacc$, then $\notpropsure \in \irej$, thus $\propposs \in \iacc$ as $\notpropsure = ¬\propposs$ and $\phi \in \iacc ⇔ ¬\phi \in \irej$; and finally, $\notpropposs \in \irej$ as $\notpropposs = ¬\propsure$ and $\phi \in \iacc ⇔ ¬\phi \in \irej$.
+
+	If $\propsure \notin \iacc$ and $\propposs \in \iacc$, then?
 \end{proof}
@@
 \begin{property}[Per-proposition determination]
-	$\forall \prop \in \allprops: [\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \iPhidet] \lor [\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \Phi \setminus \iPhidet]$.
+	$\forall \prop \in \allprops: [\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \idet] \lor [\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \Phi \setminus \idet]$.
 \end{property}
-
-Given a normative model, define $\mPhi \subseteq \Phi$ as the set of propositions whose status is determined by the Normative adequacy axioms: $\phi \in \mPhi ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost \phi]$.
-
-\Cref{prop:cohb} can’t be proven, but the following weaker versions can: $\forall \phi \in \Phi: \phi \in \mPhi ⇒ ¬\phi \in \iPhirej$ and $\forall \phi \in \Phi: \propsure \in \mPhi ⇒ ¬\propsure \in \iPhirej$.
+\commentOC{There appears to be no reason to want per-proposition determination, even at the mere model level.
+I could have a model say that $\propposs$ should be accepted, but have nothing to say about whether $\propsure$ should as well, or $\notpropposs$ is okay as well.}
+
+\Cref{prop:cohb} can’t be proven, but the following weaker versions can: $\forall \phi \in \Phi: \phi \in \mPhi ⇒ ¬\phi \in \irej$ and $\forall \phi \in \Phi: \propsure \in \mPhi ⇒ ¬\propsure \in \irej$.
 
@@
 \begin{proof}
-	Coherent complement is equivalent to $\forall \phi \in \phi: ¬(\phi \in \iPhi \land \phi \in \iPhirej)$.
-	Coherent protocol is equivalent to $\forall \phi \in \Phi: ¬(\ar \ileadstost \phi \land \ar \ileadstost ¬\phi)$, which implies (using Norm ad 1 and 2) $\forall \phi \in \Phi: ¬(\phi \in \iPhi \land \phi \in \iPhirej)$.
+	Coherent complement is equivalent to $\forall \phi \in \phi: ¬(\phi \in \iacc \land \phi \in \irej)$.
+	Coherent protocol is equivalent to $\forall \phi \in \Phi: ¬(\ar \ileadstost \phi \land \ar \ileadstost ¬\phi)$, which implies (using Norm ad 1 and 2) $\forall \phi \in \Phi: ¬(\phi \in \iacc \land \phi \in \irej)$.
 \end{proof}
@@
 \begin{proof}
-	This is false under the current definitions: if $\ileadstost = \emptyset$, coherent protocol, but $\phi \in \iPhi \land \phi \in \iPhirej$ possible.
+	This is false under the current definitions: if $\ileadstost = \emptyset$, coherent protocol, but $\phi \in \iacc \land \phi \in \irej$ possible.
 \end{proof}
@@
 \begin{axiom}[Coherent negation]
-	$\forall \phi \in \Phi: \phi \in \iPhi ⇔ ¬\phi \in \iPhirej$.
+	$\forall \phi \in \Phi: \phi \in \iacc ⇔ ¬\phi \in \irej$.
 \end{axiom}
@@
 
-This notation (writing $\phi \in \iPhirej$ as equivalent to $\phi \notin \iPhi$) is justified only if it is impossible that both $\phi \in \iPhi$ and $\phi \notin \iPhi$ be implied (thus, if Coherent complement).
+This notation (writing $\phi \in \irej$ as equivalent to $\phi \notin \iacc$) is justified only if it is impossible that both $\phi \in \iacc$ and $\phi \notin \iacc$ be implied (thus, if Coherent complement).
 \commentOC{TODO clarify.} The following conditions permit to obtain this result.

### 2020-05-10 simple.tex
Clean normative axiom and some analysis of it

@@
 $\propsure \in \Box\Phi$ iff $[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs]$.
-\begin{property}[Model completeness]
+\begin{definition}[Model completeness]
 	$\forall \phi \in \Phi: \phi \in \Box\Phi \lor ¬\phi \in \Box\Phi$.
-\end{property}
-\begin{property}[Deliberation completeness]
+\end{definition}
+\begin{definition}[Deliberation completeness]
 	$\forall \phi \in \Phi: \phi \in \iPhi \lor ¬\phi \in \iPhi$.
-\end{property}
+\end{definition}
 \begin{proposition}
@@
 
-\subsection{Classify propositions, draft}
-The notations $\iacc$ and $\irej$ designate the subsets of $\Phi$ whose propositions $i$ deliberately accepts and rejects, respectively.
-
-\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$ 1]
-	$\forall \phi \in \Phi$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iacc.
-	\end{equation}
-\end{axiom}
-\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$ 2]
-	$\forall \phi \in \Phi$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \lnot\phi \in \irej.
-	\end{equation}
-\end{axiom}
-
-\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$ 1 weaker]
-	$\forall \phi \in \Phi$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \propsure] ⇒ \propsure \in \iacc.
-	\end{equation}
-\end{axiom}
-\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$ 2 weaker]
-	$\forall \phi \in \Phi$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \propposs] ⇒ \notpropsure \in \irej.
-	\end{equation}
-\end{axiom}
-
-I suppose I can’t prove this.
-\begin{property}[Coherent complement]
-	$\iacc \cap \irej = \emptyset$.
+\subsection{Negation coherence and analysis of normative adequacy}
+The propositions such that $\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi$ are those on which the model permits to take a position.
+For that subset of propositions (which can be empty): $\phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$, where $\oplus$ denotes the exclusive disjunction; equivalently: $\phi \in \Box\Phi ⇔ ¬\phi \notin \Box\Phi$.
+\begin{property}[Protocol coherence]
+	\label{prop:protcoh}
+	$[\exists \ar \in \allargs \suchthat \ar \ileadstost[pos] \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost[pos] ¬\phi]$.
 \end{property}
-
-Given a normative model, define $\mPhi \subseteq \Phi$ as the set of propositions whose status is determined by the Normative adequacy axioms: $\phi \in \mPhi ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost \phi]$.
-
-I certainly want this (equivalent to coh co restricted to the props determined).
-\begin{property}[Desired? 1]
-	$\phi \in \mPhi ⇒ ¬\phi \notin \mPhi$.
+\begin{property}[Internal negation coherence]
+	\label{prop:intnegcoh}
+	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$.
 \end{property}
-\begin{property}[Desired? 2]
-	$\propsure \in \mPhi ⇒ \propposs \in \iacc$.
+\begin{property}[Restricted negation coherence]
+	\label{prop:restrnegcoh}
+	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \iPhi \lor ¬\phi \in \iPhi$.
 \end{property}
-
-The following definition may be useful for analytic clarification, but this property is not required as an axiom for the results in this article.
-\begin{property}[Exhaustivity]
-	$\forall \phi \in \Phi: \phi \notin \iacc ⇒ \phi \in \irej$.
-\end{property}
-Exhaustivity can be considered a strong demand, as it requires every proposition to be deliberately accepted or rejected.
-\commentOC{I’m not so sure: could consider that $t$ is merely possible when not determined.}
-
-Define the propositions whose status is determined as $\idet = \iacc \cup \irej$.
-
-\begin{property}[Suppl]
-	$\forall \prop \in \allprops: \propsure \notin \iacc ⇒ \propsure \in \irej$.
-\end{property}
-\begin{property}[Negation coherence]
-	\label{prop:cohb}
-	$\forall \phi \in \Phi: \phi \in \iacc ⇔ ¬\phi \in \irej$, and $\forall \prop \in \allprops: \propsure \in \iacc ⇒ (¬\prop, \text{sure}) \in \irej$.
-\end{property}
-This property entails the following one.
-\begin{property}[Per-proposition coherence]
-	$\forall \prop \in \allprops$, exactly one of the following four propositions is true: 
-	\begin{itemize}
-		\item $\propsure \in \iacc \land \propposs \in \iacc \land (¬\prop, \text{sure}) \in \irej \land (¬\prop, \text{poss}) \in \irej$;
-		\item $\propsure \in \irej \land \propposs \in \iacc \land (¬\prop, \text{sure}) \in \irej \land (¬\prop, \text{poss}) \in \iacc$;
-		\item $\propsure \in \irej \land \propposs \in \irej \land (¬\prop, \text{sure}) \in \iacc \land (¬\prop, \text{poss}) \in \iacc$;
-		\item $\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \Phi \setminus \idet$;
-	\end{itemize}
-\end{property}
+\begin{proposition}[Restricted negation coherence satisfaction]
+	A normatively adequate model satisfies Internal negation coherence and Restricted negation coherence.
+\end{proposition}
 \begin{proof}
-	If $\propsure \in \iacc$, then $\notpropsure \in \irej$, thus $\propposs \in \iacc$ as $\notpropsure = ¬\propposs$ and $\phi \in \iacc ⇔ ¬\phi \in \irej$; and finally, $\notpropposs \in \irej$ as $\notpropposs = ¬\propsure$ and $\phi \in \iacc ⇔ ¬\phi \in \irej$.
-
-	If $\propsure \notin \iacc$ and $\propposs \in \iacc$, then?
+	First, observe that Protocol coherence is satisfied by definition of $\ileadstost[pos]$.
+Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost[pos] \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoe ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost[pos] ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar_1, \ar') \ileadstoe ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadstoe ¬\phi$ (using the fact that the pair to the left of $\ileadstoe$ is unordered).
+
+	Consider $\phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]$.
+Proving \cref{prop:intnegcoh} only requires to show that $\phi \in \Box\Phi ⇒ ¬\phi \notin \Box\Phi$.
+By definition, $\phi \in \Box\Phi$ implies that $\exists \ar \suchthat \ar \ileadstost[pos] \phi$, and the implication is thus proven by using \cref{prop:protcoh}: $\phi \in \Box\Phi ⇒ [\exists \ar \suchthat \ar \ileadstost[pos] \phi] ⇒ ¬[\exists \ar \suchthat \ar \ileadstost[pos] ¬\phi] ⇒ \phi \notin \Box\Phi$.
+
+	Finally, \cref{prop:restrnegcoh} follows from \cref{prop:intnegcoh} thanks to normative adequacy.
 \end{proof}
 
-This property in turn entails the following one.
-\begin{property}[Per-proposition determination]
-	$\forall \prop \in \allprops: [\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \idet] \lor [\set{\prop, ¬\prop} × \set{\text{sure}, \text{poss}} \subseteq \Phi \setminus \idet]$.
-\end{property}
-\commentOC{There appears to be no reason to want per-proposition determination, even at the mere model level.
-I could have a model say that $\propposs$ should be accepted, but have nothing to say about whether $\propsure$ should as well, or $\notpropposs$ is okay as well.}
-
-\Cref{prop:cohb} can’t be proven, but the following weaker versions can: $\forall \phi \in \Phi: \phi \in \mPhi ⇒ ¬\phi \in \irej$ and $\forall \phi \in \Phi: \propsure \in \mPhi ⇒ ¬\propsure \in \irej$.
-
-\begin{property}[Per-proposition weaker coherence bis]
-	$\forall \phi \in \Phi: \phi \in \mPhi ⇒ ¬\phi \notin \mPhi$.
-\end{property}
-
-A proposition $\phi$ has a determined status iff $\phi \in \mPhi \lor ¬\phi \in \mPhi$. (Not both?)
-
-\begin{property}[Coherent determination]
-	$\forall \prop \in \allprops: $ either all propositions among $\set{\propsure, \propposs, ¬\propsure, ¬\propposs}$ have a determined status, or none have.
-\end{property}
-
-… and it is coherent!
-
-the subset of $\Phi$ about which $\allargs$ and $\ileadstoe$ give access:
-
+We want to adopt a normative axiom satisfying the following meta-axioms.
+\begin{definition}[Meta-axiom: negation coherence]
+	$\forall \phi \in \Phi: ¬(\phi \in \iPhi \land ¬\phi \in \iPhi)$.
+\end{definition}
+\begin{definition}[Meta-axiom: certainty implies possibility]
+	$\forall \phi \in \Phi: \propsure \in \iPhi ⇒ \propposs \in \iPhi$.
+\end{definition}
+Also, we want the normative axiom to be based on observation, and to allow for incompleteness. And the meta-axioms must hold for any possible observations (they are not empirical claims).
+
+From all this, hopefully, I can justify my normative axiom; by justifying its form $\ar \ileadstost[undef] \phi ⇒ \phi \in \iPhi$ in terms of a yet-undefined $\ileadstost[undef]$, then by proving that $\ileadstost[undef]$ must satisfy Protocol coherence and Certainty implies possibility.
+
+\begin{definition}[Certainty implies possibility]
+	$\forall \ar \in \allargs: \ar \ileadstost[undef] \propsure ⇒ \ar \ileadstost[undef] \propposs$.
+\end{definition}
+
+\subsection{draft}
 \begin{definition}[Coherent protocol]

### 2020-05-10 simple.tex
Rm alternative propositions and analysis of normative adequacy

@@
 
-\subsection{Classify propositions (mix attempt)}
-Define $p \ileadstostw \phi$ iff $p \nileadstoe ¬\phi$.
-
-\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstoe$ mix 1]
-	$\forall \phi \in \Phi$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \nileadstoe ¬\phi] ⇒ \phi \in \iPhi.
-	\end{equation}
-\end{axiom}
-\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstoe$ mix 2]
-	$\forall \phi \in \Phi$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \nileadstoe ¬\phi] ⇒ ¬\phi \notin \iPhi.
-	\end{equation}
-\end{axiom}
-These two axioms imply that not $(\ar \nileadstoe ¬\phi \land \ar' \nileadstoe \phi)$ (a form of coherent complement); equivalently, not $(\ar \ileadstostw \propsure \land \ar' \ileadstostw \notpropposs)$.
-
-\commentOC{This is unsatisfactory because of a mix between normative and empirical assumptions; and because an axiom should be true, not empirically falsifiable.
-Also, if the protocol is such; then we should simply weaken the conclusion, not have to conclude that the axioms are false.}
-
-To avoid risk of empirical falsification, we can weaken the axioms. Also, the first axiom seems too strong.
-
-Recall that $\ar \ileadstoe \phi$ means $\exists \ar_1 \suchthat (\ar_1, \ar) \ileadstoe \phi$.
-
-\begin{axiom}[Normative adequacy 1, weaker]
-	$\forall \prop \in \allprops$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \nileadstoe \notpropposs \land \ar \ileadstoe \propsure \land \ar \nileadstoe \notpropsure] ⇒ \propsure \in \iPhi;
-	\end{equation}
-	$\forall \prop \in \allprops$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \nileadstoe \propsure] ⇒ \notpropposs \in \iPhi.
-	\end{equation}
-\end{axiom}
-\begin{axiom}[Normative adequacy 2, weaker]
-	$\forall \prop \in \allprops$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \nileadstoe \notpropposs \land \ar \ileadstoe \propsure \land \ar \nileadstoe \notpropsure] ⇒ \notpropposs \notin \iPhi;
-	\end{equation}
-	$\forall \prop \in \allprops$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \nileadstoe \propsure] ⇒ \propsure \notin \iPhi.
-	\end{equation}
-\end{axiom}
-
-This version is still too strong: never observing $\propsure$ should not suffice to reject $\propsure$.
-Rejecting $\propsure$ is not only about observing that no decisive argument leads to it: it is about positively proving that $\notpropposs$ (that is, with a decisive argument).
-That is, if nothing is decisive in $\allargs$, the axioms should say nothing rather than claiming that $\propsure$ is rejected.
-This makes the required axioms weaker, thus, is good.
-And we don’t lose much as, under indecisiveness, there is no short proof of rejection of $\propsure$.
-It is also simpler, as it rejects $\propsure$ exactly when it accepts $\notpropposs$ exactly when some short proof of it exists.
-
-Another problem is that this still asks the question whether these axioms could be empirically falsified.
-On the contrary, the axioms should obviously mandate nothing empirical.
-They should be weaker, and the resulting equivalent statement, looking like those above, should be obtained as a result.
-
-\subsection{Classify propositions, mandating positive observations}
-Define $(\ar_1, \ar) \ileadstostp \phi$ iff $(\ar_1, \ar) \nileadstoe ¬\phi \land (\ar_1, \ar) \ileadstoe \phi$.
-Define $\ar \ileadstostp \phi$ iff $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadstostp \phi$.
-
-\begin{axiom}[Normative adequacy 1, positive]
-	$\forall \prop \in \allprops$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs] ⇒ \propsure \in \iPhi;
-	\end{equation}
-	$\forall \prop \in \allprops$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \notpropposs] ⇒ \notpropposs \in \iPhi.
-	\end{equation}
-\end{axiom}
-\begin{axiom}[Normative adequacy 2, positive]
-	$\forall \prop \in \allprops$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs] ⇒ \notpropposs \notin \iPhi;
-	\end{equation}
-	$\forall \prop \in \allprops$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \notpropposs] ⇒ \propsure \notin \iPhi.
-	\end{equation}
-\end{axiom}
-
-Problem: we should deal with accepting and rejecting possibilities only. Thus, proving $\propsure$ only serves to reject $\notpropposs$.
-
-\subsection{Classify propositions, only two implications}
-\begin{axiom}[Normative adequacy in two implications]
+\subsection{Classify propositions}
+\begin{axiom}[Normative adequacy]
 	$\forall \prop \in \allprops$: 
@@
 \end{proposition}
-Models as defined here do not mandate Model completeness, and in fact, even the weaker Deliberation completeness is not mandated.
+Models as defined here do not mandate Model completeness.
 This is good for two reasons.
-First, Deliberation completeness can appear too strong.
+First, even the weaker Deliberation completeness can appear too strong.
 Second, it is dubious that, for non trivial decision problems, models can be found for which both Normative adequacy is normatively compelling and Model completeness holds.
@@
 
-From all this, hopefully, I can justify my normative axiom; by justifying its form $\ar \ileadstost[undef] \phi ⇒ \phi \in \iPhi$ in terms of a yet-undefined $\ileadstost[undef]$, then by proving that $\ileadstost[undef]$ must satisfy Protocol coherence and Certainty implies possibility.
+From all this, hopefully, I can justify my normative axiom; by justifying its form $\ar \ileadstost[undef] \phi ⇒ \phi \in \iPhi$ in terms of a yet-undefined $\ileadstost[undef]$, then by proving that $\ileadstost[undef]$ must satisfy Protocol coherence (applied to undef instead of the current one) and Certainty implies possibility.
 
@@
 \end{definition}
-
-\subsection{draft}
-\begin{definition}[Coherent protocol]
-	$\forall \phi \in \Phi: \ar \ileadstost \phi ⇒ \ar \nileadstost ¬\phi$.
+Defining $\ar \ileadstoe[undef] \phi$ iff $\ar \nileadstost[undef] ¬\phi$, the following should adequately replace Coherent protocol.
+\begin{definition}[Always implies sometimes]
+	\label{cl:ais}
+	${\ileadstost[undef]} \subseteq {\ileadstoe[undef]}$.
 \end{definition}
-
-\begin{theorem}
-	Under axioms of Normative adequacy, Coherent complement ⇒ Coherent protocol.
-\end{theorem}
-\begin{proof}
-	Coherent complement is equivalent to $\forall \phi \in \phi: ¬(\phi \in \iacc \land \phi \in \irej)$.
-	Coherent protocol is equivalent to $\forall \phi \in \Phi: ¬(\ar \ileadstost \phi \land \ar \ileadstost ¬\phi)$, which implies (using Norm ad 1 and 2) $\forall \phi \in \Phi: ¬(\phi \in \iacc \land \phi \in \irej)$.
-\end{proof}
-
-\begin{theorem}
-	Under axioms of Normative adequacy, Coherent protocol ⇒ Coherent complement.
-\end{theorem}
-\begin{proof}
-	This is false under the current definitions: if $\ileadstost = \emptyset$, coherent protocol, but $\phi \in \iacc \land \phi \in \irej$ possible.
-\end{proof}
-
-\begin{axiom}[Coherent negation]
-	$\forall \phi \in \Phi: \phi \in \iacc ⇔ ¬\phi \in \irej$.
-\end{axiom}
-
-\begin{proposition}
-	$\forall \ar \in \allargs: \ar \ileadstost \propsure ⇒ \ar \ileadstost \propposs$.
-\end{proposition}
-\begin{proof}
-	By hypothesis, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadstost \propsure$, which implies, by definition of $\ileadstost$, that $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoe (¬\prop, \text{sure})$.
-Therefore, $\ar \ileadstost \propposs$.
-\end{proof}
-
-This notation (writing $\phi \in \irej$ as equivalent to $\phi \notin \iacc$) is justified only if it is impossible that both $\phi \in \iacc$ and $\phi \notin \iacc$ be implied (thus, if Coherent complement).
-\commentOC{TODO clarify.} The following conditions permit to obtain this result.
-\commentOC{Cond.
-1 is stronger than necessary: we could have ¬cond.
-1 and still Coh compl: $(\ar_2, \ar_1) \ileadstost \phi$ and $(\ar_2, \ar_1) \ileadstost ¬\phi$ without problems if $\ar_2$ and $\ar_1$ are not decisive.
-In fact, $(\ar_2, \ar_1) \ileadstoe ¬\phi$ should be defined as $(\ar_2, \ar_1) \nileadstost \phi) \lor (\ar_2, \ar_1) \ileadstost ¬\phi$, just in case a strange protocol allows both leading always to $\phi$ and $¬\phi$, and I think the rest goes through.}
-
-\begin{condition}[Always implies sometimes]
-	\label{cl:ais}
-	${\ileadstost} \subseteq {\ileadstoe}$.
-\end{condition}
-
-\begin{condition}[Sure implies possible]
-	\label{cl:sip}
-	$\forall \ar', \ar \in \allargs, t \in \allprops: (\ar', \ar) \ileadstost (\prop, \text{sure}) ⇒ (\ar', \ar) \ileadstost (\prop, \text{possible})$.
-\end{condition}
-
-\begin{proposition}
-	$\forall \phi \in \Phi$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi],
-	\end{equation}
-	and $\forall \prop \in \allprops$:
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost (\prop, \text{sure})] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost (¬\prop, \text{sure})].
-	\end{equation}
-\end{proposition}
-\begin{proof}
-	The first result obtains because $\ar \ileadstost \phi$ means that given any $\ar'$, $(\ar, \ar') \ileadstost \phi$, hence $(\ar, \ar') \ileadstoe \phi$ (using \cref{cl:ais}), or equivalently, $(\ar, \ar') \nileadstost ¬\phi$, thus no $\ar' \in \allargs$ satisfies $\ar' \ileadstost ¬\phi$.
-For the second one, a similar reasoning yields that $(\ar, \ar') \nileadstost (¬\prop, \text{possible})$, and using the contrapositive of \cref{cl:sip}, $(\ar, \ar') \nileadstost (¬\prop, \text{sure})$, thus no $\ar' \in \allargs$ satisfies $\ar' \ileadstost (¬\prop, \text{sure})$.
-\end{proof}
 

### 2020-05-18 simple.tex
Clarified normative axioms and discussion

@@
 \subsection{Classify propositions}
+Define $(\ar_1, \ar) \ileadstostp \phi$ iff $(\ar_1, \ar) \nileadstoe ¬\phi \land (\ar_1, \ar) \ileadstoe \phi$.
+Define $\ar \ileadstostp \phi$ iff $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadstostp \phi$.
+
+\begin{axiom}[No contradiction]
+	\label{ax:nocontr}
+	$\forall \phi \in \Phi: \phi \in \iPhi ⇒ ¬\phi \notin \iPhi$.
+\end{axiom}
 \begin{axiom}[Normative adequacy]
+	\label{ax:norm}
 	$\forall \prop \in \allprops$: 
@@
 	\end{equation}
-	$\forall \prop \in \allprops$: 
+	and
 	\begin{equation}
@@
 
+It is desirable to check that \cref{ax:nocontr,ax:norm} do not hide a requirement on the content of $\ileadstostp$, thus, that they are together satisfiable without constraining $\ileadstostp$.
+To define this more precisely, consider temporarily these axioms as properties of a set $\iPhi \subseteq \Phi$.
+I write $A^1(\iPhi)$ if “axiom” 1 (interpreted as a property of $\iPhi$) holds on $\iPhi$, and similarly for $A^2(\iPhi)$.
+The required check amounts to prove that $\exists \iPhi \subseteq \Phi \suchthat A^1(\iPhi) \land A^2(\iPhi)$.
+
 Given a model, define $\Box\Phi \subseteq \Phi$ as 
@@
 $\propsure \in \Box\Phi$ iff $[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs]$.
+
+The propositions such that $\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi$ are those on which the model permits to take a position.
+For that subset of propositions (which can be empty): $\phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$, where $\oplus$ denotes the exclusive disjunction; equivalently: $\phi \in \Box\Phi ⇔ ¬\phi \notin \Box\Phi$.
+This is proven below, and shows that \cref{ax:nocontr,ax:norm} are satisfiable together (suffices to define $\iPhi$ as the minimal set satisfying \cref{ax:norm}).
+Also proven below is that, for that same subset of propositions: $\phi \in \iPhi \oplus ¬\phi \in \iPhi$, which ensures an unambiguous interpretation of the content of $\iPhi$ for those propositions whose status is known thanks to the model.
+
+\begin{proposition}[Protocol coherence]
+	\label{prop:protcoh}
+	$[\exists \ar \in \allargs \suchthat \ar \ileadstost[pos] \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost[pos] ¬\phi]$.
+\end{proposition}
+\begin{proof}
+	Protocol coherence is satisfied by definition of $\ileadstost[pos]$.
+Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost[pos] \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoe ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost[pos] ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar_1, \ar') \ileadstoe ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadstoe ¬\phi$ (using the fact that the pair to the left of $\ileadstoe$ is unordered).
+\end{proof}
+
+\begin{proposition}[Internal negation coherence]
+	\label{th:intnegcoh}
+	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$.
+\end{proposition}
+\begin{proof}
+	Consider $\phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]$.
+Proving \cref{th:intnegcoh} only requires to show that $\phi \in \Box\Phi ⇒ ¬\phi \notin \Box\Phi$.
+By definition, $\phi \in \Box\Phi$ implies that $\exists \ar \suchthat \ar \ileadstost[pos] \phi$, and the implication is thus proven by using \cref{prop:protcoh}: $\phi \in \Box\Phi ⇒ [\exists \ar \suchthat \ar \ileadstost[pos] \phi] ⇒ ¬[\exists \ar \suchthat \ar \ileadstost[pos] ¬\phi] ⇒ \phi \notin \Box\Phi$.
+\end{proof}
+\begin{definition}[Restricted negation coherence]
+	\label{def:restrnegcoh}
+	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \iPhi \oplus ¬\phi \in \iPhi$.
+\end{definition}
+\begin{proposition}[Restricted negation coherence satisfaction]
+	Under \cref{ax:nocontr,ax:norm}, all models satisfy Restricted negation coherence.
+\end{proposition}
+\begin{proof}
+	This follows from \cref{th:intnegcoh}.
+\end{proof}
+
+\subsection{Non-completeness}
 \begin{definition}[Model completeness]
@@
 \subsection{Negation coherence and analysis of normative adequacy}
-The propositions such that $\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi$ are those on which the model permits to take a position.
-For that subset of propositions (which can be empty): $\phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$, where $\oplus$ denotes the exclusive disjunction; equivalently: $\phi \in \Box\Phi ⇔ ¬\phi \notin \Box\Phi$.
-\begin{property}[Protocol coherence]
-	\label{prop:protcoh}
-	$[\exists \ar \in \allargs \suchthat \ar \ileadstost[pos] \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost[pos] ¬\phi]$.
-\end{property}
-\begin{property}[Internal negation coherence]
-	\label{prop:intnegcoh}
-	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$.
-\end{property}
-\begin{property}[Restricted negation coherence]
-	\label{prop:restrnegcoh}
-	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \iPhi \lor ¬\phi \in \iPhi$.
-\end{property}
-\begin{proposition}[Restricted negation coherence satisfaction]
-	A normatively adequate model satisfies Internal negation coherence and Restricted negation coherence.
-\end{proposition}
-\begin{proof}
-	First, observe that Protocol coherence is satisfied by definition of $\ileadstost[pos]$.
-Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost[pos] \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoe ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost[pos] ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar_1, \ar') \ileadstoe ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadstoe ¬\phi$ (using the fact that the pair to the left of $\ileadstoe$ is unordered).
-
-	Consider $\phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]$.
-Proving \cref{prop:intnegcoh} only requires to show that $\phi \in \Box\Phi ⇒ ¬\phi \notin \Box\Phi$.
-By definition, $\phi \in \Box\Phi$ implies that $\exists \ar \suchthat \ar \ileadstost[pos] \phi$, and the implication is thus proven by using \cref{prop:protcoh}: $\phi \in \Box\Phi ⇒ [\exists \ar \suchthat \ar \ileadstost[pos] \phi] ⇒ ¬[\exists \ar \suchthat \ar \ileadstost[pos] ¬\phi] ⇒ \phi \notin \Box\Phi$.
-
-	Finally, \cref{prop:restrnegcoh} follows from \cref{prop:intnegcoh} thanks to normative adequacy.
-\end{proof}
-
 We want to adopt a normative axiom satisfying the following meta-axioms.

### 2020-05-20 simple.tex
Impr proof

@@
 A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
-with ${\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
+with $\zar \in \allargs, {\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
 where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$, and $+$ a commutative associative internal binary operation on $\allargs$.
@@
 	We know that $\exists \ar_1 \in \allargs \suchthat (\ar_1, \ar[k]) \nileadstost \phi$. 
-
-	We want to prove, first, that $(\ar_1, \ar[k]) \ileadstoe ¬\phi$. If $\phi = (\prop, \text{poss})$, that is clear from the definition of $\ileadstost$. If $\phi = (\prop, \text{sure})$,
-
-	\commentOC{With new definition of $\ileadstost$, when $\phi = (\prop, \text{sure})$, from $\ar \nileadstost \phi$ we only obtain that $\ar \ileadstoe ¬\phi \lor …$, thus, we still need to show that $\ileadstoe (\prop, \text{sure})$ and that $\nileadstoe (¬\prop, \text{sure})$.}
-	We know that $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar[k]$.
 	Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeatsstar \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$. 
@@
 \end{proof}
-\commentOC{No use of of $\ar[k] + \ar_2 \ibeatse \ar_1$, and we use Op val only on planned attacks!
-The current protocol amounts to: each time the model is endangered, it has to produce one more arg.
-in support, and we check only at the end (after at worst finitely many steps, as $\gargs$ is bounded) if it has managed to convince.
-With the difference that the model is indicated which $\ar_1$ is endangering it, to guide selection of the ultimately decisive argument.
-Actually, if playing $\ar_2$ at some stage did not move $i$ and $\ar_1$ still attacks $\ar_0 + \ar_2$, we can say that the model missed answering that step, thus either we choose to give it a second chance (maybe it chose the wrong $\ar_2$ to counter the $\ar_1'$ it believed was relevant, or it needed both $\ar_2$ and $\ar_4$), or we give up in fear of losing our time.
+\commentOC{If playing $\ar_2$ at some stage did not move $i$ and $\ar_1$ still attacks $\ar_0 + \ar_2$, we can say that the model missed answering that step, thus either we choose to give it a second chance (maybe it chose the wrong $\ar_2$ to counter the $\ar_1'$ it believed was relevant, or it needed both $\ar_2$ and $\ar_4$), or we give up in fear of losing our time.
 Actually, the protocol is that when applying Answerability, we are supposed to pick the $\ar_1'$ that $i$ just was given by another model, thus, if that’s still the same $\ar_1$ as the step before, the model has lost (it can’t map what it’s told to an argument it knows how to answer).}

### 2020-05-20 simple.tex
Rm spurious defs and conds not req for thm.
Were replaced by simply using stable instead of exists

@@
 	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeatsstar \ar_0 \land (\ar_1, \ar_0) \nileadstost \phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
-\end{definition}
-
-\begin{definition}[Claiming certainty also claims possibility]
-	$\forall \ar_0 \in \allargs: \ar_0 \gleadsto (\prop, \text{sure}) ⇒ \ar_0 \gleadsto (\prop, \text{poss})$.
-\end{definition}
-
-\begin{proposition}[Arguments for certainty also argue for possibility]
-	From Claiming certainty also claims possibility follows that $\forall (\prop, \text{sure}) \in {\gleadsto}(\allargs): \ar_0 \in \gargs[(\prop, \text{sure})] ⇒ \ar_0 \in \gargs[(\prop, \text{poss})]$.
-\end{proposition}
-\begin{proof}
-	TODO
-\end{proof}
-
-\begin{definition}
-	$\forall \ar_0 \gleadsto (\prop, \text{sure}), \ar_1 \in \allargs: (\ar_1, \ar_0) \nileadstoe \phi ⇒ (\ar_1, \ar_0) \ileadstoe ¬\phi$.
 \end{definition}

### 2020-05-20 simple.tex
Rm Meta-axiomatic analysis, to be done later.

@@
 Second, it is dubious that, for non trivial decision problems, models can be found for which both Normative adequacy is normatively compelling and Model completeness holds.
-
-\subsection{Negation coherence and analysis of normative adequacy}
-We want to adopt a normative axiom satisfying the following meta-axioms.
-\begin{definition}[Meta-axiom: negation coherence]
-	$\forall \phi \in \Phi: ¬(\phi \in \iPhi \land ¬\phi \in \iPhi)$.
-\end{definition}
-\begin{definition}[Meta-axiom: certainty implies possibility]
-	$\forall \phi \in \Phi: \propsure \in \iPhi ⇒ \propposs \in \iPhi$.
-\end{definition}
-Also, we want the normative axiom to be based on observation, and to allow for incompleteness. And the meta-axioms must hold for any possible observations (they are not empirical claims).
-
-From all this, hopefully, I can justify my normative axiom; by justifying its form $\ar \ileadstost[undef] \phi ⇒ \phi \in \iPhi$ in terms of a yet-undefined $\ileadstost[undef]$, then by proving that $\ileadstost[undef]$ must satisfy Protocol coherence (applied to undef instead of the current one) and Certainty implies possibility.
-
-\begin{definition}[Certainty implies possibility]
-	$\forall \ar \in \allargs: \ar \ileadstost[undef] \propsure ⇒ \ar \ileadstost[undef] \propposs$.
-\end{definition}
-Defining $\ar \ileadstoe[undef] \phi$ iff $\ar \nileadstost[undef] ¬\phi$, the following should adequately replace Coherent protocol.
-\begin{definition}[Always implies sometimes]
-	\label{cl:ais}
-	${\ileadstost[undef]} \subseteq {\ileadstoe[undef]}$.
-\end{definition}
 

### 2020-05-20 simple.tex
Renamed Negation coherence by Interpretability.
This is not only about negation coherence (phi in implies ¬\phi out), but also about restricted completeness (one of phi in or ¬\phi in).

@@
 
-\begin{proposition}[Internal negation coherence]
-	\label{th:intnegcoh}
+\begin{proposition}[Internal interpretability]
+	\label{th:intinterpr}
 	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$.
@@
 	Consider $\phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]$.
-Proving \cref{th:intnegcoh} only requires to show that $\phi \in \Box\Phi ⇒ ¬\phi \notin \Box\Phi$.
+Proving the claim only requires to show that $\phi \in \Box\Phi ⇒ ¬\phi \notin \Box\Phi$.
 By definition, $\phi \in \Box\Phi$ implies that $\exists \ar \suchthat \ar \ileadstost[pos] \phi$, and the implication is thus proven by using \cref{prop:protcoh}: $\phi \in \Box\Phi ⇒ [\exists \ar \suchthat \ar \ileadstost[pos] \phi] ⇒ ¬[\exists \ar \suchthat \ar \ileadstost[pos] ¬\phi] ⇒ \phi \notin \Box\Phi$.
 \end{proof}
-\begin{definition}[Restricted negation coherence]
-	\label{def:restrnegcoh}
+\begin{definition}[Restricted interpretability]
+	\label{def:restrinterpr}
 	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \iPhi \oplus ¬\phi \in \iPhi$.
 \end{definition}
-\begin{proposition}[Restricted negation coherence satisfaction]
-	Under \cref{ax:nocontr,ax:norm}, all models satisfy Restricted negation coherence.
+\begin{proposition}[Restricted interpretability satisfaction]
+	All models satisfying \cref{ax:nocontr,ax:norm} also satisfy Restricted interpretability.
 \end{proposition}
 \begin{proof}
-	This follows from \cref{th:intnegcoh}.
+	This follows from \cref{th:intinterpr}.
 \end{proof}

### 2020-05-20 simple.tex
Added Unrestricted interpretability for clarification

@@
 \end{definition}
+\begin{definition}[Unrestricted interpretability]
+	$\forall \phi \in \Phi: \phi \in \iPhi \oplus ¬\phi \in \iPhi$.
+\end{definition}
 \begin{definition}[Deliberation completeness]
@@
 \end{definition}
+The following proposition directly follows from the definitions.
 \begin{proposition}
-	Under Normative adequacy, Model completeness implies Deliberation completeness.
+	1) Under Normative adequacy, Model completeness implies Deliberation completeness.
+2) Unrestricted interpretability implies Deliberation completeness.
+3) Under No contradiction, Unrestricted interpretability is equivalent to Deliberation completeness.
 \end{proposition}

### 2020-05-20 simple.tex
\zar unnecessary, it seems

@@
 A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
-with $\zar \in \allargs, {\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
+with ${\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
 where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$, and $+$ a commutative associative internal binary operation on $\allargs$.

### 2020-05-20 simple.tex
Def \gargs to reduce to dynamic arguments that must be used

@@
 
-The set $\iPhi \subseteq \Phi$ is the set of interest. 
-When $(\prop, \text{possible}) \in \iPhi$, $\prop$ is considered as a possibility in the deliberated judgment of $i$ (it is not rejected), and when $(\prop, \text{sure}) \in \iPhi$, $\prop$ is considered as a certainty in the deliberated judgment of $i$.
-Part of the content of $\Phi$ is known as a result of a correct normative and empirical analysis.
+Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$.
 
-Given $\phi \in {\gleadsto}(\allargs)$, an argument $\ar \in \allargs$ is \emph{in favor of $\phi$}, $\ar \in \gargs[\phi, 1]$, iff $\ar \in [\gbeatsinv]^{2k}({\gleadstoinv}(\phi))$ for some $k \in \N$, where $R^\alpha$ denotes $\alpha$ times the composition of the relation $R$ with itself.
+Given $\phi \in {\gleadsto}(\allargs)$, define $\gargs[\phi, 0] \subseteq \allargs$ as $\gargs[\phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in \N$, define $\gargs[\phi, k + 1] = \gargs[\phi, k] + [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[\phi, k], \ar  \in [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k])}$.
 (Throughout the article, $\N$ includes zero.)
+Define $\gargs[\phi] = \bigcup_{k \in \N} \gargs[\phi, k]$, and $\gargs = \cup_{\phi \in {\gleadsto}(\allargs)} \gargs[\phi]$.
 
-Given $\phi \in {\gleadsto}(\allargs)$ and $1 ≤ k \in \N$, define $\gargs[\phi, k + 1] = \gargs[\phi, k] + \gargs[\phi, 1] = \set{\ar_k + \ar_1 \suchthat \ar_k \in \gargs[\phi, k], \ar_1  \in \gargs[\phi, 1]}$.
-Define $\gargs[\phi] = \bigcup_{1 ≤ k \in \N} \gargs[\phi, k]$, and $\gargs = \cup_{\phi \in {\gleadstoinv}(\allargs)} \gargs[\phi]$.
-
-Given $\phi \in \Phi$ and $\ar_0 \in \gargs[\phi]$, let $c^\phi(\ar_0) = \bigcup \set{\args \subseteq \gargs[\phi, 0] \suchthat \ar_0 = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar_0$ in favor of $\phi$.
+Given $\ar \in \gargs$, let $c(\ar) = \bigcup \set{\args \subseteq \gargs \suchthat \ar = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar$.
 
@@
 
-Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \gargs[\phi]$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$.
-Define ${\ibeatse[\phi]} \subseteq \gargs[\phi] × \allargs$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe \phi$.
+\commentOC{TODO next: check $\gbeatsstar$ can be replaced.
+Then, comment that Bounded length does not imply finiteness of arguments used as counter-arguments by the model: model is able to counter infinitely many arguments with infinitely many counter-args, but needs to declare that an (unknown) finite subset of those will suffice to convince $i$.}
 

### 2020-05-25 simple.tex
Normative theory separated from empirical one

@@
 \subsection{Definition}
-A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
-with ${\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
-where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$, and $+$ a commutative associative internal binary operation on $\allargs$.
-Given $\args \subseteq \allargs$, the notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.
+A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$, 
+with ${\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, 
+where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$.
 
@@
 
-To lighten notations, $\ileadstoe[i]$ will generally be denoted by $\ileadstoe$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$.
-When the symbol $i$, $\ileadstost$ or $\gleadsto$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
+To lighten notations, $\ileadstoe[i]$ will generally be denoted by $\ileadstoe$, this symbol being understood as the result of a function of $i$.
+When the symbol $i$, $\ileadstoe$ or $\ileadstost$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
 
@@
 Abusing notation, given $\ar \in \allargs$ and $\phi \in \Phi$, I write $\ar \ileadstost \phi$ to mean $[\forall \ar' \in \allargs: (\ar', \ar) \ileadstost \phi]$.
-
-Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$.
-
-Given $\phi \in {\gleadsto}(\allargs)$, define $\gargs[\phi, 0] \subseteq \allargs$ as $\gargs[\phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in \N$, define $\gargs[\phi, k + 1] = \gargs[\phi, k] + [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[\phi, k], \ar  \in [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k])}$.
-(Throughout the article, $\N$ includes zero.)
-Define $\gargs[\phi] = \bigcup_{k \in \N} \gargs[\phi, k]$, and $\gargs = \cup_{\phi \in {\gleadsto}(\allargs)} \gargs[\phi]$.
-
-Given $\ar \in \gargs$, let $c(\ar) = \bigcup \set{\args \subseteq \gargs \suchthat \ar = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar$.
-
-Given $\ar_2 \in \gargs, \ar_1 \in \allargs$, $\ar_2 \mbeats \ar_1$ has the semantic that $\gamma$ claims that $\ar_2$ trumps $\ar_1$ if necessary.
-Given $\ar_1 \in \allargs, \ar_0 \in \gargs$, $\ar_1 \mbeats \ar_0$ has the semantic that $\gamma$ claims that it knows how to resist an attack from $\ar_1$ coming in response to using $\ar_0$, if it does come.
-
-\commentOC{TODO next: check $\gbeatsstar$ can be replaced.
-Then, comment that Bounded length does not imply finiteness of arguments used as counter-arguments by the model: model is able to counter infinitely many arguments with infinitely many counter-args, but needs to declare that an (unknown) finite subset of those will suffice to convince $i$.}
 
@@
 
-It is desirable to check that \cref{ax:nocontr,ax:norm} do not hide a requirement on the content of $\ileadstostp$, thus, that they are together satisfiable without constraining $\ileadstostp$.
+For analytical clarity, it is desirable to check that \cref{ax:nocontr,ax:norm} do not hide a requirement on the content of $\ileadstostp$, thus, that they are together satisfiable without constraining $\ileadstostp$.
 To define this more precisely, consider temporarily these axioms as properties of a set $\iPhi \subseteq \Phi$.
@@
 
-Given a model, define $\Box\Phi \subseteq \Phi$ as 
+Given a normative theory, define $\Box\Phi \subseteq \Phi$ as 
 $\propposs \in \Box\Phi$ iff $[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propposs]$
@@
 $\propsure \in \Box\Phi$ iff $[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs]$.
+Define  $P^* \subseteq \Phi$ as the set of all \emph{decidable} propositions: $P^* = \set{\phi \in \Phi \suchthat \phi \in \Box\Phi \lor ¬\phi \in \Box\Phi}$; and define $P \subseteq \Phi$ as decidable iff $P \subseteq P^*$.
+The propositions in $P^*$ are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
 
-The propositions such that $\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi$ are those on which the model permits to take a position.
-For that subset of propositions (which can be empty): $\phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$, where $\oplus$ denotes the exclusive disjunction; equivalently: $\phi \in \Box\Phi ⇔ ¬\phi \notin \Box\Phi$.
-This is proven below, and shows that \cref{ax:nocontr,ax:norm} are satisfiable together (suffices to define $\iPhi$ as the minimal set satisfying \cref{ax:norm}).
+For any decidable proposition: $\phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$, where $\oplus$ denotes the exclusive disjunction; equivalently: $\phi \in \Box\Phi ⇔ ¬\phi \notin \Box\Phi$.
+This is proven below, and shows that \cref{ax:nocontr,ax:norm} are satisfiable together (suffices to define $\iPhi = \Box\Phi$).
 Also proven below is that, for that same subset of propositions: $\phi \in \iPhi \oplus ¬\phi \in \iPhi$, which ensures an unambiguous interpretation of the content of $\iPhi$ for those propositions whose status is known thanks to the model.
@@
 
+\section{Empirical theories}
+\subsection{Definition}
+An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
+with ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
+and $+$ a commutative associative internal binary operation on $\allargs$.
+Given a finite $\args \subseteq \allargs$, the notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.
+\commentOC{Check about finiteness.}
+
+An empirical theory is always defined for some normative theory.
+In the following, any reference to an empirical theory should always be understood as a reference to an implicit normative theory and an empirical theory for that normative theory.
+
+As above,  $\gleadsto$ will be used instead of $\gleadsto[q(i)]$ when it creates no ambiguity, with the understanding that this symbol result of applying a function of $q(i)$; and the binding $\forall i \in I$ will generally be omitted.
+
+Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \nileadstost \phi$.
+
+Given $\phi \in {\gleadsto}(\allargs)$, define $\gargs[\phi, 0] \subseteq \allargs$ as $\gargs[\phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in \N$, define $\gargs[\phi, k + 1] = \gargs[\phi, k] + [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[\phi, k], \ar  \in [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k])}$.
+(Throughout the article, $\N$ includes zero.)
+Define $\gargs[\phi] = \bigcup_{k \in \N} \gargs[\phi, k]$, and $\gargs = \cup_{\phi \in {\gleadsto}(\allargs)} \gargs[\phi]$.
+
+Given $\ar \in \gargs$, let $c(\ar) = \bigcup \set{\args \subseteq \gargs \suchthat \ar = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar$.
+
+Given $\ar_2 \in \gargs, \ar_1 \in \allargs$, $\ar_2 \mbeats \ar_1$ has the semantic that $\gamma$ claims that $\ar_2$ trumps $\ar_1$ if necessary.
+Given $\ar_1 \in \allargs, \ar_0 \in \gargs$, $\ar_1 \mbeats \ar_0$ has the semantic that $\gamma$ claims that it knows how to resist an attack from $\ar_1$ coming in response to using $\ar_0$, if it does come.
+
+\commentOC{TODO also: in general, the model defines $\gargs[\phi]$ as a function of $\ileadstoe$?
+Start with $\gargs[\phi, 0]$, then observe all $\ar_1$ attacking those, and the model may define $\gargs[\phi, 1]$ depending on this observation, and so on.
+The condition is that one such argument be decisive.}
+
 \subsection{Validity and conditions}
 \begin{definition}[Validity]
-	A theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
+	An empirical theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
 \end{definition}
@@
 
-Define $\mbeats[g] \subseteq \gargs × \allargs$ as $\ar_2 \mbeats[g] \ar_1$ iff $\exists \ar \in c(\ar_2) \suchthat \ar \mbeats \ar_1$.
-Define $\mbeats[a] \subseteq \allargs × \gargs$ as $\ar_1 \mbeats[a] \ar_0$ iff $\exists \ar \in c(\ar_0) \suchthat \ar_1 \mbeats \ar$ and $\nexists \ar \in c(\ar_0) \suchthat \ar \mbeats \ar_1$.
-Define ${\gbeatsstar} \subseteq \allargs × \allargs$ as ${\gbeatsstar} = {\mbeats[g]} \cup {\mbeats[a]}$.
-\commentOC{TODO $c^\phi$, not $c$.
-Use $c = \cup_{\phi} c^\phi$?}
+\begin{remark}
+	In fact, the model is tasked with finding a stable point after interrogating $i$.
+The process of trying counter-arguments $\ar_1, …$ is $q(i)$.
+When done, the model claims that $\ar_0 + \ar_2 + …$ is decisive.
+The model also claims that another process of interrogation does not lead to different answers.
+This is falsifiable.
+
+	It follows that trying different $\ar_2, \ar'_2, …$ is also admissible.
+
+	I need a (more) basic observable: a path $p$ is a sequence of arguments given to $i$, and I assume that whether $p \ileadsto[i] \phi$ is observable.
+But we can only assume that one path and its extensions is observable.
+
+	When claiming that $(\ar_1, \ar_0) \ileadstost[i] \phi$, the model really claims that $\nexists p, i' \in q^{-1}(q(i)) \suchthat p, \ar_1, \ar_0 \ileadsto[i'] ¬\phi \lor p, \ar_0, \ar_1 \ileadsto[i'] ¬\phi$, where $i' \in q^{-1}(q(i))$ iff $q(i) = q(i')$.
+
+	To say that $\phi \in \iPhi$, need to not depend on choice of $q$, in the following sense: if with $q$, $\phi$ seems stable, but with $q'$, $¬\phi$ seems stable, then $\phi$ is not proved as being in $\iPhi$.
+But if with $q$, $\phi$ seems stable, but with $q'$, nothing can be shown to be stable, then $\phi$ is proved (temporarily) as being in $\iPhi$.
+More precisely, after $q'$, the model must be able to stabilize $i$ with its $q$.
+\end{remark}
 
@@
 \begin{definition}[Answerability]
-	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \nileadstost \phi ⇒ [\exists \ar_1' \in {\gbeatsstarinv}(\ar_0)]$.
+	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \nileadstost \phi ⇒ [\exists \ar_1' \in {\gbeatsinv}(\ar_0)]$.
 \end{definition}
@@
 
+\begin{remark}
+	Bounded length does not imply finiteness of arguments used as counter-arguments by the model: model is able to counter infinitely many arguments with infinitely many counter-args, but needs to declare that an (unknown) finite subset of those will suffice to convince $i$.
+\end{remark}
+
 \begin{definition}[No repetition]
-	$\nexists \ar_0 \in \gargs[\phi], \ar_1 \in \allargs, \ar_2 \in c(\ar_0) \suchthat \ar_2 \gbeats \ar_1 \gbeatsstar \ar_0$.
+	$\nexists \ar_0 \in \gargs[\phi], \ar_1 \in \allargs, \ar_2 \in c(\ar_0) \suchthat \ar_2 \gbeats \ar_1 \gbeats \ar_0$.
 \end{definition}
@@
 \begin{definition}[Operational validity]
-	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeatsstar \ar_0 \land (\ar_1, \ar_0) \nileadstost \phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
+	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeats \ar_0 \land (\ar_1, \ar_0) \nileadstost \phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
 \end{definition}
+
+I want an empirical theory to: 1) declare some $P \subseteq \Phi$ and it being valid; 2) prove its claims (otherwise, uncheckable and unfalsifiable and thus not empirical) by producing decisive arguments; 3) permit reuse… Focusing on valid theories is thus justified by the fact that if no valid theory for some $P$, then any theory will not be able to prove its claims (as there is no decisive argument).
 
@@
 	We know that $\exists \ar_1 \in \allargs \suchthat (\ar_1, \ar[k]) \nileadstost \phi$. 
-	Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeatsstar \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$. 
-	Define $\ar[k + 1] = \ar[k] + \ar_2$. 
-	By No repetition, $\ar_2 \notin c(\ar[k])$.
-	Thus, $\card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
+	Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeats \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$. 
+	Define $\ar[k + 1] = \ar[k] + \ar_2$. This is the element we look for.
+	First, $\ar[k + 1] \in \gargs[\phi]$ because $\ar[k + 1] \gbeats \ar_1' \ibeatse[!\phi] \ar[k]$.
+	Second, by No repetition, $\ar_2 \notin c(\ar[k])$,
+	thus, $\card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$ (observing that, by definition of $c$, for any $\ar, \ar'$: $c(\ar) \subseteq c(\ar + \ar')$).
 
@@
 Actually, the protocol is that when applying Answerability, we are supposed to pick the $\ar_1'$ that $i$ just was given by another model, thus, if that’s still the same $\ar_1$ as the step before, the model has lost (it can’t map what it’s told to an argument it knows how to answer).}
+
+\subsection{Multiple tries}
+Should generalize the building of possible arguments attempted by the model.
+A model defines $m(\ar_0, \ar_1) \subseteq \allargs$ giving its possible arguments for answering $\ar_1$.
+Define $\gargs[\phi, 0] = \mleadsto(\allargs)$.
+If $\ar_k$ has lost (thus the model can’t answer some counter-argument to it), there must be another candidate argument.
+
+Mandate that $\exists \ar_0 \in \gargs[\phi, 0]$ such that $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar \land f(\ar_0, \ar_1) ≠ \emptyset$.
+
+\commentOC{TODO 1.
+Justify the fundamental restriction: mandates that $\exists \ar_0 \in \gargs[\phi] \suchthat \ar_0$ decisive.
+2.
+Rephrase condition as: must not be that at some point, for all $\ar_0$ in the current set of possibilities, $\nexists \ar_1 \ibeatse \ar_0 \suchthat \ar_2 \gbeats \ar_1$ (or rather $m(\ar_0, \ar_1) \subseteq C$ with $C$ the current set of possibilities).}
+
+First point is not restrictive: if there is a decisive argument for $\phi$, there is a valid model which says that $\phi$ (and if there is a valid model for $\phi$, then $\phi \in \iPhi$).
+
+First point bars models that want to fully explore $\ibeatse$ and then choose a decisive argument, for example.
+This would not be desirable because if model can’t be a priori expressed as a restricted model, then we have no means to check that really $\ar \ileadsto \phi$ as another path can’t be adopted (unless $i$ forgets).
+Also, what if $i$ gets tired after 10 arguments?
 
@@
 \begin{itemize}
-	\item Strong answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land \forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeatsstar \ar_0 + \ar_2$.
-	\item Strong answ with multiple tries: $\forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeatsstar \ar_0 + \ar_2$.
+	\item Strong answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land \forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeats \ar_0 + \ar_2$.
+	\item Strong answ with multiple tries: $\forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeats \ar_0 + \ar_2$.
 (Example: $\ar_1 = \text{“for ethical reasons”}$, and $\eta$ knows two c-a to this, from different angles.) 	\item Weak answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land [f(\ar_0 + \ar_2) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0]$.
@@
 
-TODO false: we try any sequence and then poof. Thus, is my approach insufficiently general (and thus should be restrained to the single-try models anyway)?
-
-\begin{definition}[No self-attack]
-	$\gbeatsstar$ must be asymmetric.
-\end{definition}
-
-\begin{remark}
-	When $\gbeatsstar$ is as defined above, asymmetry of $\gbeatsstar$ with the other conditions implies No repetition: by construction of $\gbeatsstar$, $\forall \ar_0 \in \gargs[\phi], \ar_1 \in \allargs, \ar_2 \in c(\ar_0) \suchthat \ar_2 \gbeats \ar_1: \ar_0 \gbeatsstar \ar_1$, thus, by asymmetry, $¬(\ar_1 \gbeatsstar \ar_0)$.
-\end{remark}
+\commentOC{This is incorrect.
+The current approach already mandates single-try.
+If $\ar_2 \gbeats \ar_1$, then $\ar_1 \ibeatse \ar_0 + \ar_2$, in the sense that $\ar_1$ would be the only such argument, is forbidden because this would require $\ar_1 \gbeats \ar_0 + \ar_2$ and thus yields a repetition.}
 

### 2020-05-25 simple.tex
Started using sequences (history) instead of pairs of args

@@
 A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$, 
-with ${\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, 
-where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$.
+with ${\ileadstoe[i]} \subseteq \allhist × \Phi$, 
+where $\allhist$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\text{possible}, \text{sure}}$.
 
-The symbol $¬$ is a negation operator on $\allprops$, such that $\forall \prop \in \allprops: ¬¬\prop = \prop$ (this article also uses this symbol to negate classical logic propositions and as a negation operator on $\Phi$, which should create no confusion).
-Define $¬$ on $\Phi$ as follows, $\forall \prop \in \allprops$: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
+The symbol $¬$ is a negation operator on $\allprops$, such that $\forall \prop \in \allprops: ¬¬\prop = \prop$.
+This article also uses this symbol as a negation operator on $\Phi$, defined as follows, $\forall \prop \in \allprops$: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
 Observe that $¬¬\phi = \phi$.
+(The symbol $¬$ is also used in this article to negate classical logic propositions; this should create no confusion.)
+As usual with binary relations, $\hist \nileadstoe[i] \phi$ means $(\hist, \phi) \notin {\ileadstoe[i]}$.
 
-Given any $\ar', \ar, \prop$, let $(\ar', \ar) \ileadstost (\prop, \text{sure})$ be equivalent to $(\ar', \ar) \nileadstoe (¬\prop, \text{poss}) \land (\ar', \ar) \ileadstoe (\prop, \text{sure}) \land (\ar', \ar) \nileadstoe (¬\prop, \text{sure})$; and $(\ar', \ar) \ileadstost (\prop, \text{poss})$ be equivalent to $(\ar', \ar) \nileadstoe (¬\prop, \text{sure})$.
-\footnote{Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$.
+Given any $\ar_0 \in \allargs, \phi \in \Phi$, define $\ar_0 \ileadstost[i] \phi$ iff $\forall \hist \in \allhist, \ar_1 \in \allargs: (\hist, \ar_0) \nileadstoe[i] ¬\phi \land (\hist, \ar_0) \ileadstoe[i] \phi \land (\hist, \ar_0, \ar_1) \nileadstoe[i] ¬\phi \land (\hist, \ar_0, \ar_1) \ileadstoe[i] \phi$.
+\footnote{TODO Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$.
 Define $(\ar', \ar) \ileadstoe (\prop, \text{sure})$ iff she sometimes chooses $\set{\prop}$ and $(\ar', \ar) \ileadstoe (\prop, \text{poss})$ iff she sometimes chooses $\set{\prop}$ or $\set{\prop, ¬\prop}$.
@@
 
-To lighten notations, $\ileadstoe[i]$ will generally be denoted by $\ileadstoe$, this symbol being understood as the result of a function of $i$.
-When the symbol $i$, $\ileadstoe$ or $\ileadstost$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
-
-As usual with binary relations, $(\ar', \ar) \nileadstost \phi$ means $¬[(\ar', \ar) \ileadstost \phi]$.
-Abusing notation, given $\ar \in \allargs$ and $\phi \in \Phi$, I write $\ar \ileadstost \phi$ to mean $[\forall \ar' \in \allargs: (\ar', \ar) \ileadstost \phi]$.
+To lighten notations, $\ileadstoe[i]$ and $\ileadstost[i]$ will generally be denoted by $\ileadstoe$ and $\ileadstost$, these symbols being understood as the result of a function of $i$. 
+When the symbol $\ileadstoe$ or $\ileadstost$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
 
 \subsection{Classify propositions}
-Define $(\ar_1, \ar) \ileadstostp \phi$ iff $(\ar_1, \ar) \nileadstoe ¬\phi \land (\ar_1, \ar) \ileadstoe \phi$.
-Define $\ar \ileadstostp \phi$ iff $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadstostp \phi$.
-
+\commentOC{Check if I current definition of $\ileadstost$ is correct, in which case I can get rid of $\ileadstostp$.}
 \begin{axiom}[No contradiction]
@@
 \section{Empirical theories}
+Given $\hist \in \allhist$ and $i \in I$, the claim $\hist \ileadstoe[i] \phi$ may not be verifiable, and is too specific to be falsifiable.
+However, given $\hist \in \allhist$, a broader claim is falsifiable: that for a given set of individuals $Q \subseteq I, \forall i \in Q, \hist \ileadstoe[i] \phi$ (provided $Q$ is big enough).
+Indeed, that claim it is equivalent to $\nexists i \in Q \suchthat \hist \nileadstoe[i] \phi$; exhibiting an $i \in Q$ such that $\hist \nileadstoe[i] \phi$ thus falsifies the broader claim.
+
 \subsection{Definition}
@@
 \end{remark}
+I think I need the following.
+Define $\ar_1 \ibeatse \ar_0$ iff $\exists \hist \suchthat (\hist, \ar_0, \ar_1) \ileadstoe ¬\phi$.
+The model claims that if $\ar_1 \ibeatse \ar_0$ and $\ar_3 \ibeatse \ar_0 + \ar_2$, then $(\hist, \ar_0 + \ar_2 + \ar_4) \ileadstoe \phi$ (for some suitable $\hist$ that does not contain yet this arg or their c-a, or perhaps just claim that $\exists \hist \suchthat \hist \ileadstoe \phi$ with $\hist$ containing this arg).
+
+Better: the model claims that if $\ar_1 \ileadstoe ¬\phi$ and if $\ar_0$ and $\ar_1$ are in $\hist$ and none of the anticipated attackers of $\ar_0 + \ar_2$ are, then $(\hist, \ar_0 + \ar_2) \ileadstoe \phi$ (or, at least, that the model has at least one available candidate).
 

### 2020-06-01 simple.tex
Phrased claim that looks plausibly adequate wrt validity and falsification; plus some discussion

@@
 
-\subsection{Validity and conditions}
+\subsection{Validity}
 \begin{definition}[Validity]
@@
 
+\subsection{Discussion}
 $\ar_0 + \ar_2$ anticipates attacks from those attacking either, minus those attacked by any.
@@
 \end{remark}
+
+There must exist a sequence $\ar_0, \ar_2, \ar_4, …$ such that $\ar_0$ is defended by $\ar_2$, and so on.
+
+\subsection{Conditions with history}
+$S_4$ defends $S_2$ under protection of $S_6$ iff: $[\exists \hist, \ar_3 \suchthat \hist, \ar_2, \ar_3 \ileadstoe ¬\phi] ⇒ [\forall \hist \suchthat \set{\ar_5 \suchthat f(\ar_5, \ar_4) \cap \args_6 ≠ \emptyset} \cap \hist = \emptyset: \hist, \ar_4 \ileadstoe \phi]$.
+No, my condition is about defending when required, so just need to defend in the sense: $\forall \hist \suchthat \set{\ar_5 \suchthat f(\ar_5, \ar_4) \cap \args_6 ≠ \emptyset} \cap \hist = \emptyset: \hist, \ar_4 \ileadstoe \phi$.
+This may be adequate as if $\ar_0$ seems suitable but some unplanned attacker $\ar_1$ attacks it, then use $\ar_1 \in \hist$ and observe that $¬(\hist, \ar_0) \ileadstoe \phi$ to falsify the theory.
+
+$\ar_4$ defends $\phi$ under protection of $S_6$ iff: $\forall \hist \in \allhist \suchthat \set{\ar_5 \in \allargs \suchthat f(\ar_5, \ar_4) \cap \args_6 ≠ \emptyset} \cap \hist = \emptyset: \hist, \ar_4 \ileadstoe \phi$.
+
+\begin{definition}[Claim]
+	$\exists k \in 2\N$ and a finite sequence $(\args_i)_{i \in 2\N, i ≤ k} \suchthat \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall i \in 2\N, i ≤ k, \forall \ar_i \in S_i: \ar_i$ defends $\phi$ under protection of $S_{i + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_i \subseteq \cup_{\ar_{i - 2} \in S_{i - 2}, \ar_{i - 1} \in \allargs} f(\ar_{i - 1}, \ar_{i - 2})$.
+\end{definition}
+Note that requiring that $\args_0$ be a singleton does not modify the condition, in the sense that any theory satisfying the condition also satisfies its restriction.
+
+No, rather: if $\ar_2$ can’t be defended, and $\ar'_2$ can’t either (all those attacking $\ar_1$, in fact), then $\ar_0$ is not necessary; thus some other $\ar'_0$ is enough.
+(Or is this equivalent?) Theimportant stuff is to anticipate attacks: if not $\ar_0$ decisive, then $\ar_1$ attacks $\ar_0$ and $\ar_2$ is decisive.
+
+I need a condition of the form: $\forall i \suchthat …, \ar$ decisive.
+And the above claim is of that form (?): given $i$, either $\ar_0$ is decisive, or $\ar_1$ attacks it but then $\ar_2$ is decisive, …
+
+\subsection{Conditions without history}
+To verify or falsify these conditions, whether $(\ar_1, \ar_0) \ileadstoe \phi$ must be observable, but one may suspect that once $i$ has seen some $\ar$, then no more $(\ar_1, \ar_0) \ileadstoe \phi$ but that this does not imply that this would hold without $\ar$ for $i$.
+The general falsifiable claim is not clear.
 

### 2020-06-01 simple.tex
Cleaned up various comments; clarified main claim

--- 2020-05-25 simple.tex
@@
 with ${\ileadstoe[i]} \subseteq \allhist × \Phi$, 
-where $\allhist$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\text{possible}, \text{sure}}$.
+where $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\text{possible}, \text{sure}}$.
 
@@
 
-\commentOC{TODO also: in general, the model defines $\gargs[\phi]$ as a function of $\ileadstoe$?
-Start with $\gargs[\phi, 0]$, then observe all $\ar_1$ attacking those, and the model may define $\gargs[\phi, 1]$ depending on this observation, and so on.
-The condition is that one such argument be decisive.}
-
-\subsection{Validity and conditions}
+\subsection{Validity}
 \begin{definition}[Validity]
@@
 
-$\ar_0 + \ar_2$ anticipates attacks from those attacking either, minus those attacked by any.
-(Actually any attacked may still attack the addition, but that’s because of some other not-yet-attacked, anticipated, attack.)
-
+\subsection{Conditions with history}
 \begin{remark}
@@
 This is falsifiable.
-
-	It follows that trying different $\ar_2, \ar'_2, …$ is also admissible.
-
-	I need a (more) basic observable: a path $p$ is a sequence of arguments given to $i$, and I assume that whether $p \ileadsto[i] \phi$ is observable.
-But we can only assume that one path and its extensions is observable.
-
 	When claiming that $(\ar_1, \ar_0) \ileadstost[i] \phi$, the model really claims that $\nexists p, i' \in q^{-1}(q(i)) \suchthat p, \ar_1, \ar_0 \ileadsto[i'] ¬\phi \lor p, \ar_0, \ar_1 \ileadsto[i'] ¬\phi$, where $i' \in q^{-1}(q(i))$ iff $q(i) = q(i')$.
@@
 \end{remark}
-I think I need the following.
-Define $\ar_1 \ibeatse \ar_0$ iff $\exists \hist \suchthat (\hist, \ar_0, \ar_1) \ileadstoe ¬\phi$.
-The model claims that if $\ar_1 \ibeatse \ar_0$ and $\ar_3 \ibeatse \ar_0 + \ar_2$, then $(\hist, \ar_0 + \ar_2 + \ar_4) \ileadstoe \phi$ (for some suitable $\hist$ that does not contain yet this arg or their c-a, or perhaps just claim that $\exists \hist \suchthat \hist \ileadstoe \phi$ with $\hist$ containing this arg).
 
-Better: the model claims that if $\ar_1 \ileadstoe ¬\phi$ and if $\ar_0$ and $\ar_1$ are in $\hist$ and none of the anticipated attackers of $\ar_0 + \ar_2$ are, then $(\hist, \ar_0 + \ar_2) \ileadstoe \phi$ (or, at least, that the model has at least one available candidate).
+Given $\ar_0 \in \allargs$ and $\args_2 \subseteq \allargs$, define the set $\args_1 \subseteq \allargs$ of arguments that $\args_2$ protects $\ar_0$ from as $S_1 = [f^{-1}(\args_2)]^{-1}(\ar_0) = \set{\ar_1 \in \allargs \suchthat f(\ar_1, \ar_0) \cap \args_2 ≠ \emptyset}$.
+Define $g(\ar_0) \subseteq \allargs × \allargs$ as $g(\ar_0) = \set{(\ar_2, \ar_1) \suchthat \ar_2 \in f(\ar_1, \ar_0)} = \bigcup_{\ar_1 \in \allargs} (f(\ar_1, \ar_0) × \set{\ar_1})$.
+The set $g(\ar_0)(\allargs)$ are the planned attacks on $\ar_0$ and the set $g(\ar_0)^{-1}(\ar_1)$ are the planned protections of $\ar_0$ against $\ar_1$.
+Then, $\args_1 = g(\ar_0)(\args_2)$.
+
+$\ar_0$ defends $\phi$ under protection of $S_2$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstoe \phi$, where $\args_1 = g(\ar_0)(\args_2)$.
+
+\begin{definition}[Claim]
+	$\forall i \in I, \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
+\end{definition}
+Note that requiring that $\args_0$ be a singleton does not modify the condition, in the sense that any theory satisfying the condition also satisfies its restriction.
 
 \begin{remark}
-	I currently conceive these conditions in the following way.
-The model must anticipate in its initial arguments the counter-arguments that $i$ may have in mind.
-Thus, $\ar_1$ trumps $\ar_0$ is observed when $i$ has been given $\ar_1$.
-When the model answers with $\ar_2$, if $i$ is unconvinced (of $\ar_2 + \ar_0$ trumping $\ar_1$), the procedure stops (the model can’t argue that yes-but-maybe-$i$-has-$\ar_1'$-in-mind; in particular, it wouldn’t be feasible to interrogate $i$ if the arguments are given thanks to labeling in a supermarket).
-However, if $i$ is given $\ar_1'$, the model must be given a chance to play its counter-argument, and may not be falsified because $\ar_2 + \ar_0$ is not enough: once $i$ is given $\ar_1'$, it is no more claimed by the model that $\ar_2 + \ar_0$ suffices any longer.
+	The claim must have the form: some structure is adequate for all individuals.
+Here, the structure is given by $f$.
+The claim should claim that looking at the attacks planned by $f$ is enough; and looking at the defenses planned by $f$ is enough.
 
-	Relatedly, Operational validity is (almost) void when $\ar_1$ trumps $\ar_0$ and $\ar_0 \gbeats \ar_1$ (and has already observed to be successful, thus $\ar_0$ trumps $\ar_1$): in that case, suffices to play $\ar_2 = \ar_0$ and define $\ar_0 + \ar_0 = \ar_0$, so $\ar_2 + \ar_0$ trumps $\ar_1$.
+	This may be adequate as if $\ar_0$ seems suitable but some unplanned attacker $\ar_1$ attacks it, then use $\ar_1 \in \hist$ and observe that $¬(\hist, \ar_0) \ileadstoe \phi$ to deny the claim.
 
-	In summary: when $\ar_1$ trumps $\ar_0$, and the model has not already answered this argument using $\ar_0$ (thus $¬ \ar_0 \gbeats \ar_1$), Op.
-val.
-demands an answer.
-When $\ar_1$ trumps $\ar_0$, and the model has answered already using $\ar_0$, and we have checked that indeed $\ar_0$ trumps $\ar_1$, Answerability demands that the model can explain this instability by the fact that someone must have given another argument $\ar_1'$ to $i$ (and this is to be checked using means outside the formal model).
+	Perhaps this could be phrased as follows.
+Say that $\ar_2$ is replaceable by $\args_2$ iff what $\ar_2$ protects is either protected by $\args_2$ or replaceable (by what?).
+Say that a set $\args$ is sufficient iff its complement is replaceable by $\args$.
+Then $g$ claims (among others) that $g(\ar_0)^{-1}(\ar_1)$ is sufficient.
+
+	The claim can (hopefully) be given the form: $\forall i \suchthat …, \ar$ decisive. Given $i$, either $\ar_0$ is decisive, or $\ar_1$ attacks it but then $\ar_2$ is decisive, …
 \end{remark}
+
+\subsection{Conditions without history}
+To verify or falsify these conditions, whether $(\ar_1, \ar_0) \ileadstoe \phi$ must be observable, but one may suspect that once $i$ has seen some $\ar$, then no more $(\ar_1, \ar_0) \ileadstoe \phi$ but that this does not imply that this would hold without $\ar$ for $i$.
+The general falsifiable claim is not clear.
 
@@
 \end{definition}
+
+$\ar_0 + \ar_2$ anticipates attacks from those attacking either, minus those attacked by any.
+(Actually any attacked may still attack the addition, but that’s because of some other not-yet-attacked, anticipated, attack.)
+
+\begin{remark}
+	I currently conceive these conditions in the following way.
+The model must anticipate in its initial arguments the counter-arguments that $i$ may have in mind.
+Thus, $\ar_1$ trumps $\ar_0$ is observed when $i$ has been given $\ar_1$.
+When the model answers with $\ar_2$, if $i$ is unconvinced (of $\ar_2 + \ar_0$ trumping $\ar_1$), the procedure stops (the model can’t argue that yes-but-maybe-$i$-has-$\ar_1'$-in-mind; in particular, it wouldn’t be feasible to interrogate $i$ if the arguments are given thanks to labeling in a supermarket).
+However, if $i$ is given $\ar_1'$, the model must be given a chance to play its counter-argument, and may not be falsified because $\ar_2 + \ar_0$ is not enough: once $i$ is given $\ar_1'$, it is no more claimed by the model that $\ar_2 + \ar_0$ suffices any longer.
+
+	Relatedly, Operational validity is (almost) void when $\ar_1$ trumps $\ar_0$ and $\ar_0 \gbeats \ar_1$ (and has already observed to be successful, thus $\ar_0$ trumps $\ar_1$): in that case, suffices to play $\ar_2 = \ar_0$ and define $\ar_0 + \ar_0 = \ar_0$, so $\ar_2 + \ar_0$ trumps $\ar_1$.
+
+	In summary: when $\ar_1$ trumps $\ar_0$, and the model has not already answered this argument using $\ar_0$ (thus $¬ \ar_0 \gbeats \ar_1$), Op.
+val.
+demands an answer.
+When $\ar_1$ trumps $\ar_0$, and the model has answered already using $\ar_0$, and we have checked that indeed $\ar_0$ trumps $\ar_1$, Answerability demands that the model can explain this instability by the fact that someone must have given another argument $\ar_1'$ to $i$ (and this is to be checked using means outside the formal model).
+\end{remark}
 

### 2020-06-09 simple.tex
Falsifiability demands (started)

@@
 where $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\text{possible}, \text{sure}}$.
+(Throughout the article, $\N$ includes zero, and note that $\intvl{1, 0} = \emptyset$.)
 
@@
 
+\commentOC{Discuss variant with an empirical claim: $\hist \ileadstoe \phi ⇒ \hist \nileadstoe ¬\phi$; and replace A2 with A2-weak: $[\forall \hist, \hist \ileadstoe \propposs] ⇒ \propposs \in \iPhi$, … This is essentially what will be done in the following, I suppose.}
+
 For analytical clarity, it is desirable to check that \cref{ax:nocontr,ax:norm} do not hide a requirement on the content of $\ileadstostp$, thus, that they are together satisfiable without constraining $\ileadstostp$.
@@
 I write $A^1(\iPhi)$ if “axiom” 1 (interpreted as a property of $\iPhi$) holds on $\iPhi$, and similarly for $A^2(\iPhi)$.
-The required check amounts to prove that $\exists \iPhi \subseteq \Phi \suchthat A^1(\iPhi) \land A^2(\iPhi)$.
+The required check amounts to prove that, given any $T, ¬, \allargs, I$, $\forall \ileadstoe: \exists \iPhi \subseteq \Phi \suchthat A^1(\iPhi) \land A^2(\iPhi)$.
 
@@
 	Protocol coherence is satisfied by definition of $\ileadstost[pos]$.
-Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost[pos] \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoe ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost[pos] ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar_1, \ar') \ileadstoe ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadstoe ¬\phi$ (using the fact that the pair to the left of $\ileadstoe$ is unordered).
+Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost[pos] \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoe ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost[pos] ¬\phi$ is false, because it requires that $\forall \hist \in \allhist, \ar_1 \in \allargs: (\hist, \ar', \ar_1) \ileadstoe ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadstoe ¬\phi$.
 \end{proof}
@@
 \begin{proposition}[Restricted interpretability satisfaction]
-	All models satisfying \cref{ax:nocontr,ax:norm} also satisfy Restricted interpretability.
+	All models satisfying \cref{ax:nocontr,ax:norm} satisfy Restricted interpretability.
 \end{proposition}
@@
 
-An empirical theory is always defined for some normative theory.
-In the following, any reference to an empirical theory should always be understood as a reference to an implicit normative theory and an empirical theory for that normative theory.
+An empirical theory is defined only given some normative theory.
+In the following, any reference to an empirical theory should always be understood as an empirical theory for some (possibly implicitly defined) normative theory.
 
@@
 Given $\phi \in {\gleadsto}(\allargs)$, define $\gargs[\phi, 0] \subseteq \allargs$ as $\gargs[\phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in \N$, define $\gargs[\phi, k + 1] = \gargs[\phi, k] + [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[\phi, k], \ar  \in [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k])}$.
-(Throughout the article, $\N$ includes zero.)
 Define $\gargs[\phi] = \bigcup_{k \in \N} \gargs[\phi, k]$, and $\gargs = \cup_{\phi \in {\gleadsto}(\allargs)} \gargs[\phi]$.
@@
 
-$\ar_0$ defends $\phi$ under protection of $S_2$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstoe \phi$, where $\args_1 = g(\ar_0)(\args_2)$.
+ Define $\hist \ileadstosts \phi$ iff $[\phi = \propposs ⇒ \hist \ileadstostp \phi] \land [\phi = \propsure ⇒ \hist \ileadstostp \phi \land \hist \ileadstostp \propposs]$.
 
-\begin{definition}[Claim]
-	$\forall i \in I, \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
+$\ar_0$ defends $\phi$ under protection of $S_2$ iff, defining $\args_1 = g(\ar_0)(\args_2)$, $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \phi$.
+
+\begin{definition}[Convincingness]
+	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
 \end{definition}
-Note that requiring that $\args_0$ be a singleton does not modify the condition, in the sense that any theory satisfying the condition also satisfies its restriction.
+Note that requiring that $\args_0$ be a singleton does not modify the condition, in the sense that any theory satisfying the condition also satisfies its strenghtening.
+Similarly, requiring that $S_k ≠ \emptyset$ does not modify the condition (because if some $k$ satisfy the condition with $S_k = \emptyset$, then picking $k' = k-2$ with the same sets $S_j$ also satisfy the condition, and because $S_0 ≠ \emptyset$, this recursion must end with a suitable $k$).
 
@@
 \end{remark}
+
+\begin{theorem}
+	If an empirical theory is convincing, and its normative theory satisfies \cref{ax:nocontr,ax:norm}, then it is valid.
+\end{theorem}
+\begin{proof}
+	Consider $i \in I$ and $\phi \in {\gleadsto}(\allargs)$. 
+	By hypothesis, $\exists k$ such that some $\ar_k \in \args_k$ defends $\phi$ under protection of $\emptyset$.
+Therefore, $\ar_k \ileadstosts \phi$.
+Using \cref{ax:norm}, this yields that $\phi \in \iPhi$, and validity follows from \cref{ax:nocontr}.
+\end{proof}
+
+\subsection{Checking in practice}
+NOW: need to establish how convincingness can be checked in practice. This should also justify the complexity of this condition (VS simply demanding a decisive argument).
+
+Given any $(\alltopic, ¬, \allhist, I)$, an \emph{observation protocol} (with memory) is a binary tree whose nodes are among $I × \allhist × \Phi$ and whose two edges out of any non leaf node are labeled by “yes” and “no”.
+The observation protocol is said to assume memory iff for each node $n = (i, \hist, \phi)$ about $i$, any node $n' = (i, {\hist}', \phi')$ about $i$ that is further down the tree continues the history, that is, the sequence ${\hist}'$ starts with $\hist$.
+Given an observation protocol and observables $(\ileadstoe[i])_{i \in I}$, the \emph{observed path} refers to the path in the tree defined recursively as consisting of the root node and, for each node $n = (i, \hist, \phi)$ in the path, the child node along the branch “yes” if $\hist \ileadstoe[i] \phi$ and the child node along the branch “no” otherwise.
+The \emph{observations} refer to the set of nodes along the observed path.
+
+Given any $(\alltopic, ¬, \allhist, I)$, a \emph{normative claim} is any proposition involving the atoms $\iPhi$ and $\ileadstoe$ which, together with \cref{ax:nocontr,ax:norm}, permits to deduce that $\phi \in \iPhi$ for some $i \in I$ and $\phi \in \Phi$.
+An observation protocol, together with observables $(\ileadstoe[i])_{i \in I}$, \emph{falsifies} a normative claim iff the falsity of the claim is deducible from \cref{ax:nocontr,ax:norm} and the observations.
+A normative claim is \emph{falsifiable} iff there exists an observation protocol such that for any observables $(\ileadstoe[i])_{i \in I} \in (\allhist × \Phi)^I$, if the claim is false, then it is possible to deduce it from $\cref{ax:nocontr,ax:norm}$ and the observations given the observables.
+
+\commentOC{I want: An empirical theory for a normative theory is something like a normative and falsifiable claim.
+It is also configurable: it must be possible to guarantee that the falsification be easy (if the claim is false) depending on the kind of claim.}
+
+\commentOC{Falsifiable may not be the right word.
+It suggests that if a claim is not falsifiable, then a weaker claim is not falsifiable either, which does not hold.
+My falsifiability criterion demands that if a claim is false, we can see it; whether Popper’s demands that the claim be possibly false.
+Perhaps I should demand that we can pick a set of consequences of the claim and show it wrong it at least one possible state of the universe.}
+
+Validity itself fails falsifiability.
+
+And the stronger claim that for a given $i$, $\phi \in \Box\Phi \land \phi \in \iPhi$ also does.
+If the theory says that for $i$, $\phi \in \iPhi$, and there are at least two arguments, then, a protocol that starts with $\ar_1$ will fail to detect if $\forall \hist \in \allhist: \ar_2, \hist \ileadsto ¬\phi$ (which proves that no argument is decisive, hence $\phi \notin \Box\Phi$).
 

### 2020-06-22 simple.tex
Fals single-try model (very messy)

@@
 \begin{document}
-%\title{Theories of deliberated preference}
-\title{Testable normative theories}
+\title{Empirical normative theories}
 \author{Olivier Cailloux}
@@
 
-Given any $\ar_0 \in \allargs, \phi \in \Phi$, define $\ar_0 \ileadstost[i] \phi$ iff $\forall \hist \in \allhist, \ar_1 \in \allargs: (\hist, \ar_0) \nileadstoe[i] ¬\phi \land (\hist, \ar_0) \ileadstoe[i] \phi \land (\hist, \ar_0, \ar_1) \nileadstoe[i] ¬\phi \land (\hist, \ar_0, \ar_1) \ileadstoe[i] \phi$.
+Given $\phi \in \Phi$, define ${\ibeatse[!\phi]} \subseteq (\allhist × \allargs) × \allargs$ such that $(\hist, \ar_1) \ibeatse[!\phi] \ar_0$ iff $[(\hist \ileadstoe ¬\phi) \lor (\hist \nileadstoe \phi)] \land [\hist \text{ ends with } \set{\ar_1, \ar_0}]$.
+I also write that $\ar_1 \ibeatse[!\phi] \ar_0$ iff $\exists \hist \in \allhist \suchthat (\hist, \ar_1) \ibeatse[!\phi] \ar_0$, and $\hist \ibeatse[!\phi] \ar_0$ iff $[(\hist \ileadstoe ¬\phi) \lor (\hist \nileadstoe \phi)] \land [(\exists \ar_1 \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0}) \lor (\hist = \set{\ar_0})]$.
+
+Given any $\hist \in \allhist, \ar_0 \in \allargs, \phi \in \Phi$, define $(\hist, \ar_0) \ileadstost[i] \phi$ iff $\forall \ar_1 \in \allargs: (\hist, \ar_0) \nileadstoe[i] ¬\phi \land (\hist, \ar_0) \ileadstoe[i] \phi \land (\hist, \ar_0, \ar_1) \nileadstoe[i] ¬\phi \land (\hist, \ar_0, \ar_1) \ileadstoe[i] \phi$.
+Define $(\hist, \ar_0) \ileadstosts \phi$ iff $[(\hist, \ar_0) \ileadstost \phi] \land [\phi = \propsure ⇒ (\hist, \ar_0) \ileadstost \propposs]$.
+Define $\ar_0 \ileadstost[i] \phi$ iff $\forall \hist \in \allhist, (\hist, \ar_0) \ileadstost[i] \phi$, and define similarly $\ar \ileadstosts \phi$ iff $\forall \hist \in \allhist, (\hist, \ar_0) \ileadstosts \phi$.
+Note in particular that: 
+\begin{equation}
+	\label{eq:st-in-terms-of-e}
+	\ar_0 \ileadstosts \phi ⇔ [\forall \ar_1: \ar_1 \nibeatse[!\phi] \ar_0] \land [\ar_0 \nileadstoe ¬\phi] \land [\ar_0 \ileadstoe \phi].
+\end{equation}
 \footnote{TODO Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$.
@@
 	\label{ax:norm}
-	$\forall \prop \in \allprops$: 
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propposs] ⇒ \propposs \in \iPhi;
-	\end{equation}
-	and
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs] ⇒ \propsure \in \iPhi.
-	\end{equation}
+	$\forall \phi \in \Phi: 
+		[\exists \ar \in \allargs \suchthat \ar \ileadstosts \phi] ⇒ \phi \in \iPhi.$
 \end{axiom}
@@
 
-For analytical clarity, it is desirable to check that \cref{ax:nocontr,ax:norm} do not hide a requirement on the content of $\ileadstostp$, thus, that they are together satisfiable without constraining $\ileadstostp$.
+For analytical clarity, it is desirable to check that \cref{ax:nocontr,ax:norm} do not hide a requirement on the content of $\ileadstost$, thus, that they are together satisfiable without constraining $\ileadstost$.
 To define this more precisely, consider temporarily these axioms as properties of a set $\iPhi \subseteq \Phi$.
 I write $A^1(\iPhi)$ if “axiom” 1 (interpreted as a property of $\iPhi$) holds on $\iPhi$, and similarly for $A^2(\iPhi)$.
-The required check amounts to prove that, given any $T, ¬, \allargs, I$, $\forall \ileadstoe: \exists \iPhi \subseteq \Phi \suchthat A^1(\iPhi) \land A^2(\iPhi)$.
+The required check amounts to prove that, given any $T, ¬, \allargs, I$, $\forall {\ileadstoe} \subseteq  \allhist × \Phi: \exists \iPhi \subseteq \Phi \suchthat A^1(\iPhi) \land A^2(\iPhi)$.
 
 Given a normative theory, define $\Box\Phi \subseteq \Phi$ as 
-$\propposs \in \Box\Phi$ iff $[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propposs]$
-and 
-$\propsure \in \Box\Phi$ iff $[\exists \ar \in \allargs \suchthat \ar \ileadstostp \propsure \land \ar \ileadstostp \propposs]$.
+$\Box\Phi = \set{\phi \in \Phi \suchthat \exists \ar \in \allargs \suchthat \ar \ileadstosts \phi}$.
 Define  $P^* \subseteq \Phi$ as the set of all \emph{decidable} propositions: $P^* = \set{\phi \in \Phi \suchthat \phi \in \Box\Phi \lor ¬\phi \in \Box\Phi}$; and define $P \subseteq \Phi$ as decidable iff $P \subseteq P^*$.
@@
 This is proven below, and shows that \cref{ax:nocontr,ax:norm} are satisfiable together (suffices to define $\iPhi = \Box\Phi$).
-Also proven below is that, for that same subset of propositions: $\phi \in \iPhi \oplus ¬\phi \in \iPhi$, which ensures an unambiguous interpretation of the content of $\iPhi$ for those propositions whose status is known thanks to the model.
+Also proven below is that, for any decidable proposition: $\phi \in \iPhi \oplus ¬\phi \in \iPhi$, which ensures an unambiguous interpretation of the content of $\iPhi$ for those propositions whose status is known thanks to the model.
 
@@
 	\label{prop:protcoh}
-	$[\exists \ar \in \allargs \suchthat \ar \ileadstost[pos] \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost[pos] ¬\phi]$.
+	$[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi]$.
 \end{proposition}
 \begin{proof}
-	Protocol coherence is satisfied by definition of $\ileadstost[pos]$.
-Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost[pos] \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoe ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost[pos] ¬\phi$ is false, because it requires that $\forall \hist \in \allhist, \ar_1 \in \allargs: (\hist, \ar', \ar_1) \ileadstoe ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadstoe ¬\phi$.
+	Protocol coherence is satisfied by definition of $\ileadstost$.
+Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoe ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost ¬\phi$ is false, because it requires that $\forall \hist \in \allhist, \ar_1 \in \allargs: (\hist, \ar', \ar_1) \ileadstoe ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadstoe ¬\phi$.
 \end{proof}
@@
 Proving the claim only requires to show that $\phi \in \Box\Phi ⇒ ¬\phi \notin \Box\Phi$.
-By definition, $\phi \in \Box\Phi$ implies that $\exists \ar \suchthat \ar \ileadstost[pos] \phi$, and the implication is thus proven by using \cref{prop:protcoh}: $\phi \in \Box\Phi ⇒ [\exists \ar \suchthat \ar \ileadstost[pos] \phi] ⇒ ¬[\exists \ar \suchthat \ar \ileadstost[pos] ¬\phi] ⇒ \phi \notin \Box\Phi$.
+By definition, $\phi \in \Box\Phi$ implies that $\exists \ar \suchthat \ar \ileadstost \phi$, and the implication is thus proven by using \cref{prop:protcoh}: $\phi \in \Box\Phi ⇒ [\exists \ar \suchthat \ar \ileadstost \phi] ⇒ ¬[\exists \ar \suchthat \ar \ileadstost ¬\phi] ⇒ \phi \notin \Box\Phi$.
 \end{proof}
@@
 \section{Empirical theories}
+\subsection{Falsifiability}
+\commentOC{I want: An empirical theory for a normative theory is something like a normative and falsifiable claim.
+It is also configurable: it must be possible to guarantee that the falsification be easy (if the claim is false) depending on the kind of claim.}
+
 Given $\hist \in \allhist$ and $i \in I$, the claim $\hist \ileadstoe[i] \phi$ may not be verifiable, and is too specific to be falsifiable.
@@
 
+Given any $(\alltopic, ¬, \allargs, I)$, an \emph{observation protocol} is a binary tree whose non-leaf nodes are among $I × \allhist × \Phi$ and whose two edges out of any non leaf node are labeled by “yes” and “no”; the leaf nodes being simply $\emptyset$.
+The observation protocol is said to assume memory iff for each non-leaf node $n = (i, \hist, \phi)$ about $i$, any node $n' = (i, {\hist}', \phi')$ about $i$ that is further down the tree continues the history, that is, the sequence ${\hist}'$ starts with $\hist$.
+Given an observation protocol and observables $(\ileadstoe[i])_{i \in I}$, the \emph{observed path} refers to the path in the tree defined recursively as consisting of the root node and, for each non-leaf node $n = (i, \hist, \phi)$ in the path, the child node along the branch “yes” if $\hist \ileadstoe[i] \phi$ and the child node along the branch “no” otherwise.
+The \emph{observations} refer to the set of nodes along the observed path.
+
+Given any $(\alltopic, ¬, \allargs, I)$, a \emph{normative claim} about $(\alltopic, ¬, \allargs, I)$ (or about $\allargs$, when the other defined objects are left implicit) is any first-order logic proposition involving the atoms $[(\hist, \phi) \in {\ileadstoe[i]}], \hist \in \allhist, \phi \in \Phi$ which, together with \cref{ax:nocontr,ax:norm}, permits to deduce that $\phi \in \iPhi$ for some $i \in I$ and $\phi \in \Phi$.
+The claim is said to be \emph{about} the given set $\allargs$.
+An observation protocol, together with observables $(\ileadstoe[i])_{i \in I}$, \emph{falsifies} a normative claim iff the falsity of the claim is deducible from \cref{ax:nocontr,ax:norm} and the observations.
+A normative claim is \emph{falsifiable} iff there exists a finite observation protocol such that for any observables $(\ileadstoe[i])_{i \in I} \in (\allhist × \Phi)^I$, if the claim is false given these observables, then it is possible to deduce it from \cref{ax:nocontr,ax:norm} and the observations given the observables.
+
+\commentOC{Falsifiable may not be the right word.
+Perhaps “provable“, meaning “tautological or Popper-falsifiable”.
+“Falsifiable” suggests that if a claim is not falsifiable, then a weaker claim is not falsifiable either, which does not hold.
+My falsifiability criterion demands that if a claim is false, we can see it; whether Popper’s demands that the claim be possibly false.
+Perhaps I should demand that we can pick a set of consequences of the claim and show it wrong it at least one possible state of the universe.}
+
+A normative claim is \emph{trivial} iff it is about a singleton $\allargs = \set{\ar}$, and has the form: $\ar \ileadstosts \phi$, for some $i \in I$.
+A normative claim is minimal iff it has the form: $\exists \ar \in \allargs \suchthat \ar \ileadstosts \phi$, for some $i \in I$ and $\phi \in \Phi$.
+Note that given a minimal claim, $\card{\allargs} = 1$ is equivalent to the claim being trivial.
+
+\begin{proposition}[Trivial claims are not falsifiable]
+	Given any $(\alltopic, ¬, \allargs ≠ \emptyset, I)$, no minimal normative claim is falsifiable.
+\end{proposition}
+\begin{proof}
+	Consider any claim about some $i$ and some $\phi$ and any finite observation protocol.
+We have to show that for some observables, the claim is false, but it is impossible to observe it (meaning, to deduce it from \cref{ax:nocontr,ax:norm} and observations).
+
+	Given $k \in \N$, define $\ileadstosts[k]$ as $\ar^k \ileadstosts \phi$ and $\ar^{k+1} \ileadstosts ¬\phi$ (where $\ar^k$ designates a finite sequence repeating $k$ times $\ar$, for $\ar \in \allargs$).
+I claim that for some $k$, the observables that include this relation makes the claim false, but not observably so.
+This is because the observation protocol is finite, thus, only permits to observe some finite number of instances of the relation $\ileadsto$.
+Suffices to define $k$ as that number.
+\end{proof}
+
+There is another reason for non falsifiability, which does not involve the problem of finiteness.
+\begin{proposition}[Minimal non-trivial claims are not falsifiable]
+	Given any $(\alltopic, ¬, \allargs, I), \card{\allargs} ≥ 2$, no minimal normative claim is falsifiable.
+\end{proposition}
+\begin{proof}
+	Define $\ar_1$ as the first element of the sequence $\hist$ of the root node of the observation protocol (if the observation protocol is empty, suffices to define any observables that make the claim false).
+Define the observables so that $\forall \hist \in \allhist: \ar_2, \hist \ileadsto ¬\phi$.
+This proves that no argument is decisive, hence $\phi \notin \Box\Phi$, and the claim is false.
+But the observables may also be defined so as to satisfy the protocol (defined as: when going through the protocol, the observations can’t fail the claim).
+\end{proof}
+
 \subsection{Definition}
-An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
-with ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
-and $+$ a commutative associative internal binary operation on $\allargs$.
-Given a finite $\args \subseteq \allargs$, the notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.
-\commentOC{Check about finiteness.}
-
-An empirical theory is defined only given some normative theory.
-In the following, any reference to an empirical theory should always be understood as an empirical theory for some (possibly implicitly defined) normative theory.
-
-As above,  $\gleadsto$ will be used instead of $\gleadsto[q(i)]$ when it creates no ambiguity, with the understanding that this symbol result of applying a function of $q(i)$; and the binding $\forall i \in I$ will generally be omitted.
-
-Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \nileadstost \phi$.
-
-Given $\phi \in {\gleadsto}(\allargs)$, define $\gargs[\phi, 0] \subseteq \allargs$ as $\gargs[\phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in \N$, define $\gargs[\phi, k + 1] = \gargs[\phi, k] + [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[\phi, k], \ar  \in [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k])}$.
-Define $\gargs[\phi] = \bigcup_{k \in \N} \gargs[\phi, k]$, and $\gargs = \cup_{\phi \in {\gleadsto}(\allargs)} \gargs[\phi]$.
-
-Given $\ar \in \gargs$, let $c(\ar) = \bigcup \set{\args \subseteq \gargs \suchthat \ar = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar$.
-
-Given $\ar_2 \in \gargs, \ar_1 \in \allargs$, $\ar_2 \mbeats \ar_1$ has the semantic that $\gamma$ claims that $\ar_2$ trumps $\ar_1$ if necessary.
-Given $\ar_1 \in \allargs, \ar_0 \in \gargs$, $\ar_1 \mbeats \ar_0$ has the semantic that $\gamma$ claims that it knows how to resist an attack from $\ar_1$ coming in response to using $\ar_0$, if it does come.
-
-\subsection{Validity}
-\begin{definition}[Validity]
-	An empirical theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
-\end{definition}
-
-\subsection{Conditions with history}
+A general empirical theory for a normative theory $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$ is a tuple $({\gleadsto}, f)$, where ${\gleadsto} \subseteq \allargs × \Phi$ and $f \subseteq (\allargs × \allargs) × \allargs$ with $f(\allargs × \allargs)$ being finite.
+
+Define $g(\ar_0) \subseteq \allargs × \allargs$ as $g(\ar_0) = \set{(\ar_2, \ar_1) \suchthat \ar_2 \in f(\ar_1, \ar_0)} = \bigcup_{\ar_1 \in \allargs} (f(\ar_1, \ar_0) × \set{\ar_1})$.
+The set $g(\ar_0)(\allargs)$ contains the planned attacks on $\ar_0$; the set $g(\ar_0)(\ar_2)$ contains the planned attacks on $\ar_0$ for which $\ar_2$ is a planned response; and the set $g(\ar_0)^{-1}(\ar_1) = f(\ar_1, \ar_0)$ contains the planned protections of $\ar_0$ against $\ar_1$.
+
+Given $\ar_0 \in \allargs$ and $\args_2 \subseteq \allargs$, define the set $\args_1 \subseteq \allargs$ of arguments that $\args_2$ protects $\ar_0$ from as $\args_1 = [f^{-1}(\args_2)]^{-1}(\ar_0) = \set{\ar_1 \in \allargs \suchthat f(\ar_1, \ar_0) \cap \args_2 ≠ \emptyset} = g(\ar_0)(\args_2) = dom(f^{-1}(\args_2) \cap \allargs × \set{\ar_0})$.
+
+\subsection{A general condition sufficient for validity and (hopefully) falsifiability}
+It should be possible to define this condition as a claim that does not involve $f$, so that it can be done before defining an empirical theory.
+Then, show that a normative and falsifiable claim must have the form of a convincingness claim.
+
 \begin{remark}
@@
 
-Given $\ar_0 \in \allargs$ and $\args_2 \subseteq \allargs$, define the set $\args_1 \subseteq \allargs$ of arguments that $\args_2$ protects $\ar_0$ from as $S_1 = [f^{-1}(\args_2)]^{-1}(\ar_0) = \set{\ar_1 \in \allargs \suchthat f(\ar_1, \ar_0) \cap \args_2 ≠ \emptyset}$.
-Define $g(\ar_0) \subseteq \allargs × \allargs$ as $g(\ar_0) = \set{(\ar_2, \ar_1) \suchthat \ar_2 \in f(\ar_1, \ar_0)} = \bigcup_{\ar_1 \in \allargs} (f(\ar_1, \ar_0) × \set{\ar_1})$.
-The set $g(\ar_0)(\allargs)$ are the planned attacks on $\ar_0$ and the set $g(\ar_0)^{-1}(\ar_1)$ are the planned protections of $\ar_0$ against $\ar_1$.
-Then, $\args_1 = g(\ar_0)(\args_2)$.
-
- Define $\hist \ileadstosts \phi$ iff $[\phi = \propposs ⇒ \hist \ileadstostp \phi] \land [\phi = \propsure ⇒ \hist \ileadstostp \phi \land \hist \ileadstostp \propposs]$.
-
-$\ar_0$ defends $\phi$ under protection of $S_2$ iff, defining $\args_1 = g(\ar_0)(\args_2)$, $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \phi$.
+$\ar_0$ $i$-defends $\phi$ when ignoring $S_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \phi$.
+$\ar_0$ $i$-defends $\phi$ under protection of $S_2$ iff $\ar_0$ $i$-defends $\phi$ when ignoring $g(\ar_0)(\args_2)$.
 
 \begin{definition}[Convincingness]
-	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
+	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
 \end{definition}
@@
 
-\subsection{Checking in practice}
-NOW: need to establish how convincingness can be checked in practice. This should also justify the complexity of this condition (VS simply demanding a decisive argument).
-
-Given any $(\alltopic, ¬, \allhist, I)$, an \emph{observation protocol} (with memory) is a binary tree whose nodes are among $I × \allhist × \Phi$ and whose two edges out of any non leaf node are labeled by “yes” and “no”.
-The observation protocol is said to assume memory iff for each node $n = (i, \hist, \phi)$ about $i$, any node $n' = (i, {\hist}', \phi')$ about $i$ that is further down the tree continues the history, that is, the sequence ${\hist}'$ starts with $\hist$.
-Given an observation protocol and observables $(\ileadstoe[i])_{i \in I}$, the \emph{observed path} refers to the path in the tree defined recursively as consisting of the root node and, for each node $n = (i, \hist, \phi)$ in the path, the child node along the branch “yes” if $\hist \ileadstoe[i] \phi$ and the child node along the branch “no” otherwise.
-The \emph{observations} refer to the set of nodes along the observed path.
-
-Given any $(\alltopic, ¬, \allhist, I)$, a \emph{normative claim} is any proposition involving the atoms $\iPhi$ and $\ileadstoe$ which, together with \cref{ax:nocontr,ax:norm}, permits to deduce that $\phi \in \iPhi$ for some $i \in I$ and $\phi \in \Phi$.
-An observation protocol, together with observables $(\ileadstoe[i])_{i \in I}$, \emph{falsifies} a normative claim iff the falsity of the claim is deducible from \cref{ax:nocontr,ax:norm} and the observations.
-A normative claim is \emph{falsifiable} iff there exists an observation protocol such that for any observables $(\ileadstoe[i])_{i \in I} \in (\allhist × \Phi)^I$, if the claim is false, then it is possible to deduce it from $\cref{ax:nocontr,ax:norm}$ and the observations given the observables.
-
-\commentOC{I want: An empirical theory for a normative theory is something like a normative and falsifiable claim.
-It is also configurable: it must be possible to guarantee that the falsification be easy (if the claim is false) depending on the kind of claim.}
-
-\commentOC{Falsifiable may not be the right word.
-It suggests that if a claim is not falsifiable, then a weaker claim is not falsifiable either, which does not hold.
-My falsifiability criterion demands that if a claim is false, we can see it; whether Popper’s demands that the claim be possibly false.
-Perhaps I should demand that we can pick a set of consequences of the claim and show it wrong it at least one possible state of the universe.}
-
-Validity itself fails falsifiability.
-
-And the stronger claim that for a given $i$, $\phi \in \Box\Phi \land \phi \in \iPhi$ also does.
-If the theory says that for $i$, $\phi \in \iPhi$, and there are at least two arguments, then, a protocol that starts with $\ar_1$ will fail to detect if $\forall \hist \in \allhist: \ar_2, \hist \ileadsto ¬\phi$ (which proves that no argument is decisive, hence $\phi \notin \Box\Phi$).
+\begin{theorem}
+	The convincingness claim of any empirical theory is falsifiable: given an ET, there exists a finite obs prot with memory such that for any observables, if the claim is false given these observables, then it is possible to deduce it from the axioms and observations.
+\end{theorem}
+\begin{proof}
+
+\end{proof}
+
+\section{Additive empirical theories}
+TODO: 3) define single-answer models.
+4) phrase conditions below for history and single-answer models.
+5) show that these conditions can be verified or falsified.
+6) show that if the claim of the model does not include these conditions, then the model is not falsifiable, as suggested here below for some form of claims.
+
+\subsection{Definition}
+An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
+with ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
+${\gbeatsinv}(\allargs)$ finite,
+and $+$ a commutative associative internal binary operation on $\allargs$.
+Given a finite $\args \subseteq \allargs$, the notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.
+\commentOC{Check about finiteness.}
+\commentOC{${\gbeatsinv}$ need not be finite, only those even ones: the transitive closure of ${\gleadstoinv}(\Phi)$ through ${\gbeatsinv}^2$, that is, $({\gbeatsinv})^2[{\gleadstoinv}(\Phi)] = \cup_{k \in 2\N}({\gbeatsinv}^{k}({\gleadstoinv}(\Phi)))$.}
+\commentOC{I should only define $\ar \in \allargs$ plus $\ard$.}
+
+This defines a function: $\forall \ar_1 \gbeats \ar_0: f(\ar_1, \ar_0) = \ar_0 + {\gbeatsinv}(\ar_1) = \set{\ar_0 + \ard_2 \suchthat \ard_2 \in {\gbeatsinv}(\ar_1)}$, and $f(\ar_1, \ar_0) = \emptyset$ otherwise.
+Thus, $f = \set{((\ar_1, \ar_0), \ar_2) \suchthat \exists \ard_2 \in \allargs \suchthat \ard_2 \gbeats \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2}$.
+Also, from the previous definition, $g(\ar_0)(\ar_0 + \argsd_2) = dom(f^{-1}(\ar_0 + \argsd_2) \cap (\allargs × \set{\ar_0})) = {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$ because $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \argsd_2) ⇔ \exists \ar_2 \in \ar_0 + \argsd_2 \suchthat \ar_2 \in f(\ar_1, \ar_0) ⇔ \ar_1 \gbeats \ar_0 \land \exists \ard \in \argsd_2 \suchthat \ard \gbeats \ar_1$.
+\commentOC{Could be false. Define }
+
+Note that $f^{-1}(\ar_0 + \ar_2) ≠ {\gbeats}(\ar_2) × \set{\ar_0}$: if ${\gbeats} = \set{(\ard_2, \ar_1), (\ar_1, \ar_0), (\ard_6, \ar_5), (\ar_5, \ar_4)}$, and $\ar_0 + \ard_2 = \ar_4 + \ard_6$, then $f^{-1}(\ar_0 + \ard_2) = f^{-1}(\ar_4 + \ard_6) = \set{(\ar_1, \ar_0), (\ar_5, \ar_4)}$ and ${\gbeats}(\ard_2) × \set{\ar_0} = \set{(\ar_1, \ar_0)}$.
+Also, note that $g(\ar_0)(\ar_0 + \argsd_2) ≠ {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$.
+Consider ${\gbeats} = \set{(\ard_2, \ar_1), (\ar_1, \ar_0)}, \ar_2 = \ar_0 + \ard = \ar_0 + \ard_2$.
+Then, $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \ard)$, hence, $\ar_1 \in g(\ar_0)(\ar_0 + \ard)$, but ${\gbeats}(\ard) = \emptyset$.
+
+$\ar_0$ $i$-defends $\phi$ when ignoring $\args_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \phi$.
+$\ar_0$ $i$-defends $\phi$ under protection of $\args_2$ iff $\ar_0$ $i$-defends $\phi$ when ignoring $g(\ar_0)(\args_2)$.
+$\ar_0$ $i$-defends $\phi$ under d-protection of $\argsd_2$ iff $\ar_0$ $i$-defends $\phi$ when ignoring ${\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$.
+
+Define the crossing of $\args_{j-2}, \argsd_j \subseteq \allargs$ as $\args_j = \set{\ar_{j-2} + \ard_j \suchthat \ar_{j-2} \in \args_{j-2}, \ard_j \in {\gbeatsmt}(\ar_{j-2}) \cap \argsd_j}$.
+\begin{definition}[Convincingness (outdated)]
+	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \exists k \in 2\N$ and finite sequences $(\args_j)_{j \in 2\N, j ≤ k}, (\argsd_j)_{j \in 2\N^*, j ≤ k}$ such that:
+	\begin{itemize}
+		\item $\emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$;
+		\item $\forall j \in 2\N^*, j ≤ k: \argsd_j \subseteq {\gbeatsmt}(\args_{j-2})$;
+		\item $\forall j \in 2\N^*, j ≤ k: \args_j$ is the crossing of $\args_{j-2}, \argsd_j$;
+		\item $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under d-protection of $\argsd_{j + 2}$ (defining $\argsd_{k + 2} = \emptyset$).
+	\end{itemize}
+\end{definition}
+
+Now prove that Convincingness is the same thing as requiring that the elements be selected exactly when $\ar_1$ attacks $\ar_0$ (with single-try models).
+
+Given $i \in I, \phi \in {\gleadsto}(\allargs)$, define the $\phi$-protectors of $\ard$ as $d^{i, \phi}(\ard) = [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\ard)$.
+Define the successors of $(\phi, \ar, \ard)$ as $\sigma^i(\phi, \ar, \ard) = \set{\phi} × \set{\ar + \ard} × d^{i, \phi}(\ard)$.
+Given $i \in I, \phi \in {\gleadsto}(\allargs)$, define $\gargs[i, \phi]$ as the transitive closure of $(\phi, \emptyset, \ar)$ under $\sigma^i$, with $\ar \gleadsto \phi$.
+\commentOC{Assuming only one $\ar$ leads to that $\phi$.}
+Define $\gargs[i, \phi] = \bigcup_{k \in 2\N} \gargs[i, \phi, k]$, and $\gargs = \cup_{i \in I, \phi \in {\gleadsto}(\allargs)} \gargs[i, \phi]$.
+
+\begin{definition}[Conv. single-try]
+	$\forall i \in I, \phi \in {\gleadsto}(\allargs), (\phi, \ar, \ard) \in \gargs[i, \phi], \ar_0 = \ar + \ard: \ar_0$ $i$-defends $\phi$ under d-protection of $d^{i, \phi}(\ard)$.
+\end{definition}
+
+\begin{proposition}
+	An empirical theory has only finite sets $\gargs[i, \phi]$, and an upper bound on their size exists that is independent of ${\ileadsto}$.
+\end{proposition}
+\begin{proof}
+	Given $i, \phi$.
+Observe that $\forall \ard: d^{i, \phi}(\ard) \subseteq {\gbeatsmt}(\ard)$.
+Thus, $d^{i, \phi}$ is finite.
+Also, the transitive closure through $\sigma^i$ changes a finite number of time, otherwise it is possible to build an infinite chain in ${\gbeatsmt}$.
+\end{proof}
+
+1. Checkpath: this is completely general.
+2. Only using model that counter-argues: requires a sort of path independence. (arguments can be condensed: s5, s4, s1 => s1big)
+
+A falsification instance of an empirical theory is a tuple $(i, \phi, \ar, \ard, \hist)$ such that $(\phi, \ar, \ard) \in \gargs[i, \phi]$ and, defining $\ar_0 = \ar + \ard$: $[{\gbeatsinv}(d^{i, \phi}(\ard)) \cap \hist = \emptyset] \land [\hist \ibeatse[!\phi] \ar_0]$ (the theory says that this history should defend $\phi$ under prot of something and that is not in the history).
+
+\begin{theorem}
+	An empirical theory is conv.\ single-try iff it has no falsification instances.
+\end{theorem}
+\begin{proof}
+	Given $i, \phi, (\phi, \ar, \ard) \in \gargs[i, \phi]$.
+Define $\args_1 = {\gbeats}(d^{i, \phi}(\ard)) \cap {\gbeatsinv}(\ar)$.
+Now $\ar$ $i$-defends $\phi$ ignoring $\args_1$ is equivalent to: $\forall \hist: \hist \cap \args_1 = \emptyset ⇒ (\hist, \ar) \ileadstosts \phi$.
+Negation: $\exists \hist \suchthat \hist \cap \args_1 = \emptyset \land (\hist, \ar) \nileadstosts \phi$.
+TODO prove that equivalent to no falsification.
+\end{proof}
+
+\subsection{Vrac from here}
+An empirical theory is defined only given some normative theory.
+In the following, any reference to an empirical theory should always be understood as an empirical theory for some (sometimes implicitly defined) normative theory.
+
+As above,  $\gleadsto$ will be used instead of $\gleadsto[q(i)]$ when it creates no ambiguity, with the understanding that this symbol result of applying a function of $q(i)$; and the binding $\forall i \in I$ will generally be omitted.
+
+Given $\phi \in {\gleadsto}(\allargs)$, define $\gargs[i, \phi, 0] \subseteq \allargs$ as $\gargs[i, \phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in 2\N$, define $\gargs[i, \phi, k + 2] = \gargs[i, \phi, k] + [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[i, \phi, k], \ar  \in [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k])}$.
+Define $\gargs[i, \phi] = \bigcup_{k \in 2\N} \gargs[i, \phi, k]$, and $\gargs = \cup_{i \in I, \phi \in {\gleadsto}(\allargs)} \gargs[i, \phi]$.
+
+Given $\ar \in \gargs$, let $c(\ar) = \bigcup \set{\args \subseteq \gargs \suchthat \ar = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar$.
+
+Given $\ar_2 \in \gargs, \ar_1 \in \allargs$, $\ar_2 \mbeats \ar_1$ has the semantic that $\gamma$ claims that $\ar_2$ trumps $\ar_1$ if necessary.
+Given $\ar_1 \in \allargs, \ar_0 \in \gargs$, $\ar_1 \mbeats \ar_0$ has the semantic that $\gamma$ claims that it knows how to resist an attack from $\ar_1$ coming in response to using $\ar_0$, if it does come.
+
+\subsection{Validity}
+\begin{definition}[Validity]
+	An empirical theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
+\end{definition}
+
+\subsection{Single-try empirical models}
+NB these two conditions should be phrased as properties of a claim. A claim has bl iff for some $k$, …
+
+What we search for here are conditions of the form: $\forall i$.
+
+For now, assume that $\ar_1$ attacks a single argument, so that there is no problem with replying with $\ar_2$ independently of which argument $\ar_1$ attacks.
+
+\begin{definition}[Conv.\ SA]
+	$\forall i \in I, \phi \in {\gleadsto}(\allargs), k \in 2\N, \ar \in \gargs[i, \phi, k]: \ar$ $i$-defends $\phi$ ignoring ${\gbeats}(\gargs[i, \phi, k + 2])$.
+\end{definition}
+
+\begin{definition}[Length bounded a priori]
+	$\exists m \in \N^* \suchthat ({\gbeats})^m(\allargs) = \emptyset$.
+\end{definition}
+
+\begin{theorem}
+	If an empirical theory is Conv.\ SA and has a priori bounded length, and its normative theory satisfies \cref{ax:nocontr,ax:norm}, then it is valid.
+\end{theorem}
+\begin{proof}
+	Consider $i \in I$ and $\phi \in {\gleadsto}(\allargs)$.
+
+	Lemma: $\forall \ar_0 \in \gargs[i, \phi], \ar_1 \in \allargs: \ar_1 \ibeatse \ar_0 ⇒ [\exists \ar_2, \ar_1' \in \allargs \suchthat \ar_2 \gbeats \ar_1' \gbeats \ar_0]$. 
+	Consider $\ar_0 \in \gargs[i, \phi], \ar_1 \in \allargs \suchthat \ar_1 \ibeatse \ar_0$.
+	Define $\args^1 = {\gbeats}(\gargs[i, \phi, k + 2])$.
+Thus, $\ar_0$ $i$-defends $\phi$ ignoring $\args^1$.
+Now, $\args^1 ≠ \emptyset$, because otherwise, by definition of $i$-defense, $\ar_0 \ileadstosts \phi$, which is incompatible with $\ar_1 \ibeatse \ar_0$, by \cref{eq:st-in-terms-of-e}.
+	Pick $\ar \in \args^1$ and observe that, by definition of $\args^1$, $\exists \ar_2 \in \gargs[i, \phi, k + 2] \suchthat \ar_2 \gbeats \ar$, and by definition of $\gargs[i, \phi, k + 2]$,  $\exists \ar_1' \suchthat \ar_2 \gbeats \ar_1' \gbeats \ar_0$.
+\commentOC{NO.
+I should be protected only from anticipated attacks.
+Currently, $\ar_1$ need not be anticipated (another $\ar_1'$ may be anticipated and then $\ar_2$ attacking both would suffice).
+Perhaps I need to define $\gargs[2]$ with only requiring that $\ar_1 \ibeatse \ar_0$, not $\ar_1 \ibeatse \ar_0$ and $\ar_1 \gbeats \ar_0$, because otherwise no requirements on attackers of attackers of $\ar_0$.
+I need to observe that if $\ar_1 \ibeatse \ar_0$, and $\ar_0$ defends $\phi$, then $\ar_1$ is ignored.
+Thus, it is anticipated (because I can ignore only those I anticipate).}
+
+	But $\ar_0$ i-def $\phi$, if not ignoring $\ar_1$, implies that $\forall \hist \in \allhist: (\hist, \ar_1, \ar_0) \ileadstosts \phi$. Thus, $\ar_1$ is ignored.
+
+	Thus, $\gargs[2] \subseteq ({\gbeatsinv})^2(\ar_0)$.
+	Thus, some $\gargs[k] = \emptyset$ (by bounded length).
+	Thus, some $\gargs[k] ≠ \emptyset$ that nobody attacks. This is our decisive argument.
+	Therefore, $\ar_k \ileadstosts \phi$. Using \cref{ax:norm}, this yields that $\phi \in \iPhi$, and validity follows from \cref{ax:nocontr}.
+\end{proof}
 
@@
 The general falsifiable claim is not clear.
+
+Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \nileadstost \phi$.
 

### 2020-06-22 simple.tex
Simpler defs of attack…

@@
 
-Given $\phi \in \Phi$, define ${\ibeatse[!\phi]} \subseteq (\allhist × \allargs) × \allargs$ such that $(\hist, \ar_1) \ibeatse[!\phi] \ar_0$ iff $[(\hist \ileadstoe ¬\phi) \lor (\hist \nileadstoe \phi)] \land [\hist \text{ ends with } \set{\ar_1, \ar_0}]$.
-I also write that $\ar_1 \ibeatse[!\phi] \ar_0$ iff $\exists \hist \in \allhist \suchthat (\hist, \ar_1) \ibeatse[!\phi] \ar_0$, and $\hist \ibeatse[!\phi] \ar_0$ iff $[(\hist \ileadstoe ¬\phi) \lor (\hist \nileadstoe \phi)] \land [(\exists \ar_1 \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0}) \lor (\hist = \set{\ar_0})]$.
-
-Given any $\hist \in \allhist, \ar_0 \in \allargs, \phi \in \Phi$, define $(\hist, \ar_0) \ileadstost[i] \phi$ iff $\forall \ar_1 \in \allargs: (\hist, \ar_0) \nileadstoe[i] ¬\phi \land (\hist, \ar_0) \ileadstoe[i] \phi \land (\hist, \ar_0, \ar_1) \nileadstoe[i] ¬\phi \land (\hist, \ar_0, \ar_1) \ileadstoe[i] \phi$.
-Define $(\hist, \ar_0) \ileadstosts \phi$ iff $[(\hist, \ar_0) \ileadstost \phi] \land [\phi = \propsure ⇒ (\hist, \ar_0) \ileadstost \propposs]$.
-Define $\ar_0 \ileadstost[i] \phi$ iff $\forall \hist \in \allhist, (\hist, \ar_0) \ileadstost[i] \phi$, and define similarly $\ar \ileadstosts \phi$ iff $\forall \hist \in \allhist, (\hist, \ar_0) \ileadstosts \phi$.
-Note in particular that: 
-\begin{equation}
-	\label{eq:st-in-terms-of-e}
-	\ar_0 \ileadstosts \phi ⇔ [\forall \ar_1: \ar_1 \nibeatse[!\phi] \ar_0] \land [\ar_0 \nileadstoe ¬\phi] \land [\ar_0 \ileadstoe \phi].
-\end{equation}
+Given $\phi \in \Phi$ and $\hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadstoe \phi \land \hist \nileadstoe ¬\phi$.
+Define $\hist \ileadstosts \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
+Define $\ar \ileadstosts \phi$ iff $\forall \hist \in \allhist \suchthat \hist \text{ has } \ar \text{ as last or before last position }: \hist \ileadstosts \phi$.
 \footnote{TODO Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$.
@@
 
+\begin{proposition}
+	An empirical theory has only finite sets $\gargs[i, \phi]$, and an upper bound on their size exists that is independent of ${\ileadsto}$.
+\end{proposition}
+\begin{proof}
+	Given $i, \phi$.
+Observe that $\forall \ard: d^{i, \phi}(\ard) \subseteq {\gbeatsmt}(\ard)$.
+Thus, $d^{i, \phi}$ is finite.
+Also, the transitive closure through $\sigma^i$ changes a finite number of time, otherwise it is possible to build an infinite chain in ${\gbeatsmt}$.
+\end{proof}
+
+Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatse[!\phi] \ar_0$ iff $\exists \hist \in \allhist \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0} \land \hist \nileadstosts \phi$.
+
+\begin{proposition}
+	$\forall i \in I, \phi \in \Phi, \ar_0 \in \allargs$:
+\begin{equation}
+	\label{eq:st-in-terms-of-e}
+	\ar_0 \nileadstosts \phi ⇔ [\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar_0].
+\end{equation}
+\end{proposition}
+\begin{proof}
+	By definition of ${\ileadstosts}$, $\ar_0 \ileadstosts \phi ⇔ \forall \hist \in \allhist \suchthat [\exists \ar_1 \in \allargs \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0}]: \hist \ileadstosts \phi.$ Equivalently, $\ar_0 \nileadstosts \phi ⇔ \exists \hist \in \allhist \suchthat [\exists \ar_1 \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0}] \land \hist \nileadstosts \phi$.
+This is also equivalent to $\ar_0 \nileadstosts \phi ⇔ \exists \hist \in \allhist, \ar_1 \in \allargs \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0} \land \hist \nileadstosts \phi$.
+By definition of ${\ibeatse}$, this is the proposition to be proven.
+\end{proof}
+
 $\ar_0$ $i$-defends $\phi$ when ignoring $\args_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \phi$.
@@
 
-\begin{proposition}
-	An empirical theory has only finite sets $\gargs[i, \phi]$, and an upper bound on their size exists that is independent of ${\ileadsto}$.
-\end{proposition}
-\begin{proof}
-	Given $i, \phi$.
-Observe that $\forall \ard: d^{i, \phi}(\ard) \subseteq {\gbeatsmt}(\ard)$.
-Thus, $d^{i, \phi}$ is finite.
-Also, the transitive closure through $\sigma^i$ changes a finite number of time, otherwise it is possible to build an infinite chain in ${\gbeatsmt}$.
-\end{proof}
-
 1. Checkpath: this is completely general.
 2. Only using model that counter-argues: requires a sort of path independence. (arguments can be condensed: s5, s4, s1 => s1big)
+
+I also write that $\hist \ibeatse[!\phi] \ar_0$ iff $\exists \ar_1 \in \allargs \suchthat (\hist \text{ ends with } \set{\ar_1, \ar_0}) \land (\ar_1 \ibeatse[!\phi] \ar_0)$.
 

### 2020-06-23 simple.tex
Started clarif. falsif.

@@
 
+\subsection{Falsifiability}
 \begin{proposition}
@@
 
-Define the crossing of $\args_{j-2}, \argsd_j \subseteq \allargs$ as $\args_j = \set{\ar_{j-2} + \ard_j \suchthat \ar_{j-2} \in \args_{j-2}, \ard_j \in {\gbeatsmt}(\ar_{j-2}) \cap \argsd_j}$.
-\begin{definition}[Convincingness (outdated)]
-	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \exists k \in 2\N$ and finite sequences $(\args_j)_{j \in 2\N, j ≤ k}, (\argsd_j)_{j \in 2\N^*, j ≤ k}$ such that:
-	\begin{itemize}
-		\item $\emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$;
-		\item $\forall j \in 2\N^*, j ≤ k: \argsd_j \subseteq {\gbeatsmt}(\args_{j-2})$;
-		\item $\forall j \in 2\N^*, j ≤ k: \args_j$ is the crossing of $\args_{j-2}, \argsd_j$;
-		\item $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under d-protection of $\argsd_{j + 2}$ (defining $\argsd_{k + 2} = \emptyset$).
-	\end{itemize}
-\end{definition}
-
-Now prove that Convincingness is the same thing as requiring that the elements be selected exactly when $\ar_1$ attacks $\ar_0$ (with single-try models).
-
 Given $i \in I, \phi \in {\gleadsto}(\allargs)$, define the $\phi$-protectors of $\ard$ as $d^{i, \phi}(\ard) = [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\ard)$.
@@
 
-A falsification instance of an empirical theory is a tuple $(i, \phi, \ar, \ard, \hist)$ such that $(\phi, \ar, \ard) \in \gargs[i, \phi]$ and, defining $\ar_0 = \ar + \ard$: $[{\gbeatsinv}(d^{i, \phi}(\ard)) \cap \hist = \emptyset] \land [\hist \ibeatse[!\phi] \ar_0]$ (the theory says that this history should defend $\phi$ under prot of something and that is not in the history).
+A falsification instance of an empirical theory is a tuple $(i, \phi, \ar, \ard, \hist, \ar_1)$ such that $(\phi, \ar, \ard) \in \gargs[i, \phi]$ and, defining $\ar_0 = \ar + \ard$: $[{\gbeatsinv}(\ard) \cap \hist = \emptyset] \land [\hist \text{ ends with } \set{\ar_1, \ar_0}] \land \ar_1 \ibeatse[!\phi] \ar_0]$ (the theory says that this history should defend $\phi$ under prot of something and that is not in the history).
 

### 2020-06-23 simple.tex
Started centralizing draft notes

@@
 \section{Normative theories}
-Sketch: define normative models, using questions, and making claims about DJ.
-A problem is that models specific to a narrow situation will not offer enough means for falsification.
-Then define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.
-BUT what about a model for only one situation?
-Then we need to accept that $q$ can’t be falsified, and accept that it defines the individual (or just assume without proof that it does not).
-
 \subsection{Definition}
@@
 
+\section{Next}
+Define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.
+
+What about a model for only one situation? Then we need to accept that $q$ can’t be falsified, and accept that it defines the individual (or just assume without proof that it does not).
+
 \section{Theories proposing decisive arguments}

### 2020-06-23 simple.tex
Simpler notations, started cleaning, and attempt simpler write.

@@
 \subsection{Definition}
-A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$, 
-with ${\ileadstoe[i]} \subseteq \allhist × \Phi$, 
+A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoi)_{i \in I})$, 
+with ${\ileadstoi} \subseteq \allhist × \Phi$, 
 where $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\text{possible}, \text{sure}}$.
@@
 Observe that $¬¬\phi = \phi$.
-(The symbol $¬$ is also used in this article to negate classical logic propositions; this should create no confusion.)
-As usual with binary relations, $\hist \nileadstoe[i] \phi$ means $(\hist, \phi) \notin {\ileadstoe[i]}$.
-
-Given $\phi \in \Phi$ and $\hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadstoe \phi \land \hist \nileadstoe ¬\phi$.
-Define $\hist \ileadstosts \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
-Define $\ar \ileadstosts \phi$ iff $\forall \hist \in \allhist \suchthat \hist \text{ has } \ar \text{ as last or before last position }: \hist \ileadstosts \phi$.
-\footnote{TODO Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$.
-Define $(\ar', \ar) \ileadstoe (\prop, \text{sure})$ iff she sometimes chooses $\set{\prop}$ and $(\ar', \ar) \ileadstoe (\prop, \text{poss})$ iff she sometimes chooses $\set{\prop}$ or $\set{\prop, ¬\prop}$.
-Then, $(\ar', \ar) \ileadstost (\prop, \text{sure})$ iff she always chooses $\set{\prop}$ and $(\ar', \ar) \ileadstost (\prop, \text{poss})$ iff she always chooses either $\set{\prop}$ or $\set{\prop, ¬\prop}$.}
-
-To lighten notations, $\ileadstoe[i]$ and $\ileadstost[i]$ will generally be denoted by $\ileadstoe$ and $\ileadstost$, these symbols being understood as the result of a function of $i$. 
-When the symbol $\ileadstoe$ or $\ileadstost$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
+(The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
+As usual with binary relations, $\hist \nileadsto[i] \phi$ means $(\hist, \phi) \notin {\ileadsto[i]}$.
+
+Given $i \in I, \phi \in \Phi, \hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadstoi \phi \land \hist \nileadstoi ¬\phi$.
+Define $\hist \ileadstosti \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
+Given $\hist \in \allhist$, let $\hist_\mathit{end}$ denote the set containing the last two elements of the sequence $\hist$ if the sequence has at least two elements; the singleton set containing the last element of the sequence if it has exactly one element; and the empty set if $\hist = \emptyset$.
+Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstosti \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \hist_\mathit{end}: \hist \ileadstosti \phi$.
+
+To lighten notations, $\ileadstoi$ and $\ileadstosti$ will generally be denoted by $\ileadsto$ and $\ileadstosts$, these symbols being understood as the result of a function of $i$. 
+When the symbol $\ileadsto$ or $\ileadstosts$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
 
 \subsection{Classify propositions}
-\commentOC{Check if I current definition of $\ileadstost$ is correct, in which case I can get rid of $\ileadstostp$.}
 \begin{axiom}[No contradiction]
 	\label{ax:nocontr}
-	$\forall \phi \in \Phi: \phi \in \iPhi ⇒ ¬\phi \notin \iPhi$.
+	$\forall i \in I, \phi \in \Phi: \phi \in \iPhi ⇒ ¬\phi \notin \iPhi$.
 \end{axiom}
@@
 	\label{ax:norm}
-	$\forall \phi \in \Phi: 
-		[\exists \ar \in \allargs \suchthat \ar \ileadstosts \phi] ⇒ \phi \in \iPhi.$
+	$\forall i \in I, \phi \in \Phi: 
+		[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] ⇒ \phi \in \iPhi.$
 \end{axiom}
 
-\commentOC{Discuss variant with an empirical claim: $\hist \ileadstoe \phi ⇒ \hist \nileadstoe ¬\phi$; and replace A2 with A2-weak: $[\forall \hist, \hist \ileadstoe \propposs] ⇒ \propposs \in \iPhi$, … This is essentially what will be done in the following, I suppose.}
-
-For analytical clarity, it is desirable to check that \cref{ax:nocontr,ax:norm} do not hide a requirement on the content of $\ileadstost$, thus, that they are together satisfiable without constraining $\ileadstost$.
+For analytical clarity, it is desirable to check that \cref{ax:nocontr,ax:norm} do not hide a requirement on the content of $\ileadstosti$, thus, that they are together satisfiable without constraining $\ileadstosti$.
 To define this more precisely, consider temporarily these axioms as properties of a set $\iPhi \subseteq \Phi$.
 I write $A^1(\iPhi)$ if “axiom” 1 (interpreted as a property of $\iPhi$) holds on $\iPhi$, and similarly for $A^2(\iPhi)$.
-The required check amounts to prove that, given any $T, ¬, \allargs, I$, $\forall {\ileadstoe} \subseteq  \allhist × \Phi: \exists \iPhi \subseteq \Phi \suchthat A^1(\iPhi) \land A^2(\iPhi)$.
-
-Given a normative theory, define $\Box\Phi \subseteq \Phi$ as 
-$\Box\Phi = \set{\phi \in \Phi \suchthat \exists \ar \in \allargs \suchthat \ar \ileadstosts \phi}$.
-Define  $P^* \subseteq \Phi$ as the set of all \emph{decidable} propositions: $P^* = \set{\phi \in \Phi \suchthat \phi \in \Box\Phi \lor ¬\phi \in \Box\Phi}$; and define $P \subseteq \Phi$ as decidable iff $P \subseteq P^*$.
-The propositions in $P^*$ are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
-
-For any decidable proposition: $\phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$, where $\oplus$ denotes the exclusive disjunction; equivalently: $\phi \in \Box\Phi ⇔ ¬\phi \notin \Box\Phi$.
-This is proven below, and shows that \cref{ax:nocontr,ax:norm} are satisfiable together (suffices to define $\iPhi = \Box\Phi$).
-Also proven below is that, for any decidable proposition: $\phi \in \iPhi \oplus ¬\phi \in \iPhi$, which ensures an unambiguous interpretation of the content of $\iPhi$ for those propositions whose status is known thanks to the model.
+The required check amounts to prove that, given any $T, ¬, \allargs, I$, $\forall {\ileadstoi} \subseteq \allhist × \Phi: \exists \iPhi \subseteq \Phi \suchthat A^1(\iPhi) \land A^2(\iPhi)$.
+
+To further analyze this and related matters, define, given a normative theory and $i \in I$, $\Box^i\Phi \subseteq \Phi$ as 
+$\Box^i\Phi = \set{\phi \in \Phi \suchthat \exists \ar \in \allargs \suchthat \ar \ileadstosti \phi}$.
+Define  $P^{*, i} \subseteq \Phi$ as the set of all \emph{$i$-decidable} propositions: $P^{*, i} = \set{\phi \in \Phi \suchthat \phi \in \Box^i\Phi \lor ¬\phi \in \Box^i\Phi}$; and define a set of propositions $P \subseteq \Phi$ as $i$-decidable iff $P \subseteq P^{*, i}$.
+The propositions in $P^{*, i}$ are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
+
+For any $i$-decidable proposition: $\phi \in \Box^i\Phi \oplus ¬\phi \in \Box^i\Phi$, where $\oplus$ denotes the exclusive disjunction; equivalently: $\phi \in \Box^i\Phi ⇔ ¬\phi \notin \Box^i\Phi$.
+This is proven below, and shows that \cref{ax:nocontr,ax:norm} are satisfiable together (suffices to define $\iPhi = \Box^i\Phi$).
+Also proven below is that, for any $i$-decidable proposition: $\phi \in \iPhi \oplus ¬\phi \in \iPhi$, which ensures an unambiguous interpretation of the content of $\iPhi$ for those propositions whose status is known thanks to the model.
+
+To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\phi \in \Phi$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi$.
+The $i$-decidable propositions are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
+
+For any $i$-decidable proposition $\phi$: $[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] \oplus [\exists \ar \in \allargs \suchthat \ar \ileadstosti ¬\phi]$, where $\oplus$ denotes the exclusive disjunction; equivalently: $[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] ⇔ ¬[\exists \ar \in \allargs \suchthat \ar \ileadstosti ¬\phi]$.
+This is proven below, and shows that \cref{ax:nocontr,ax:norm} are satisfiable together (suffices to define $\iPhi = \set{\phi \suchthat [\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi]}$).
+Also proven below is that, for any $i$-decidable proposition: $\phi \in \iPhi \oplus ¬\phi \in \iPhi$, which ensures an unambiguous interpretation of the content of $\iPhi$ for those propositions whose status is known thanks to the model.
+
+\commentOC{If we do not have $\propsure$ implies $\propposs$, then we can have $\propsure$ and $\notpropsure$ both accepted. But those propositions would still hold, it seems.}
 
@@
 	\label{prop:protcoh}
-	$[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi]$.
+	$\forall i \in I, \phi \in \Phi$:
+	\begin{equation}
+		[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstosti ¬\phi].
+	\end{equation}
 \end{proposition}
 \begin{proof}
-	Protocol coherence is satisfied by definition of $\ileadstost$.
-Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoe ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost ¬\phi$ is false, because it requires that $\forall \hist \in \allhist, \ar_1 \in \allargs: (\hist, \ar', \ar_1) \ileadstoe ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadstoe ¬\phi$.
-\end{proof}
-
-\begin{proposition}[Internal interpretability]
-	\label{th:intinterpr}
-	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$.
-\end{proposition}
-\begin{proof}
-	Consider $\phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]$.
-Proving the claim only requires to show that $\phi \in \Box\Phi ⇒ ¬\phi \notin \Box\Phi$.
-By definition, $\phi \in \Box\Phi$ implies that $\exists \ar \suchthat \ar \ileadstost \phi$, and the implication is thus proven by using \cref{prop:protcoh}: $\phi \in \Box\Phi ⇒ [\exists \ar \suchthat \ar \ileadstost \phi] ⇒ ¬[\exists \ar \suchthat \ar \ileadstost ¬\phi] ⇒ \phi \notin \Box\Phi$.
-\end{proof}
+	Protocol coherence is satisfied by definition of $\ileadstosti$.
+Indeed, if for some $\ar \in \allargs$, $\ar \ileadstosti \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoi ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstosti ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadstoi ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadstoi ¬\phi$.
+\end{proof}
+
 \begin{definition}[Restricted interpretability]
 	\label{def:restrinterpr}
-	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \iPhi \oplus ¬\phi \in \iPhi$.
+	$\forall \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi] ⇒ [\phi \in \iPhi \oplus ¬\phi \in \iPhi]$.
 \end{definition}
@@
 \begin{proof}
-	This follows from \cref{th:intinterpr}.
+	It is only required to prove that if $\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi$, then $¬\phi \notin \iPhi$. This follows from \cref{th:intinterpr}.
 \end{proof}
@@
 
+Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$.
+Define $(\ar', \ar) \ileadstoe (\prop, \text{sure})$ iff she sometimes chooses $\set{\prop}$ and $(\ar', \ar) \ileadstoe (\prop, \text{poss})$ iff she sometimes chooses $\set{\prop}$ or $\set{\prop, ¬\prop}$.
+Then, $(\ar', \ar) \ileadstost (\prop, \text{sure})$ iff she always chooses $\set{\prop}$ and $(\ar', \ar) \ileadstost (\prop, \text{poss})$ iff she always chooses either $\set{\prop}$ or $\set{\prop, ¬\prop}$.
+
+Discuss variant with an empirical claim: $\hist \ileadstoi \phi ⇒ \hist \nileadstoi ¬\phi$; and change \cref{ax:norm}: $[\forall \hist, \hist \ileadstoi \propposs] ⇒ \propposs \in \iPhi$, … This is essentially what will be done in the following, I suppose.
+
 \section{Theories proposing decisive arguments}

### 2020-06-23 simple.tex
Shortened and simplified axiomatic analysis.

@@
 \subsection{Classify propositions}
-\begin{axiom}[No contradiction]
-	\label{ax:nocontr}
-	$\forall i \in I, \phi \in \Phi: \phi \in \iPhi ⇒ ¬\phi \notin \iPhi$.
-\end{axiom}
 \begin{axiom}[Normative adequacy]
@@
 	$\forall i \in I, \phi \in \Phi: 
-		[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] ⇒ \phi \in \iPhi.$
+		[(\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstosti ¬\phi)] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
 \end{axiom}
-
-For analytical clarity, it is desirable to check that \cref{ax:nocontr,ax:norm} do not hide a requirement on the content of $\ileadstosti$, thus, that they are together satisfiable without constraining $\ileadstosti$.
-To define this more precisely, consider temporarily these axioms as properties of a set $\iPhi \subseteq \Phi$.
-I write $A^1(\iPhi)$ if “axiom” 1 (interpreted as a property of $\iPhi$) holds on $\iPhi$, and similarly for $A^2(\iPhi)$.
-The required check amounts to prove that, given any $T, ¬, \allargs, I$, $\forall {\ileadstoi} \subseteq \allhist × \Phi: \exists \iPhi \subseteq \Phi \suchthat A^1(\iPhi) \land A^2(\iPhi)$.
-
-To further analyze this and related matters, define, given a normative theory and $i \in I$, $\Box^i\Phi \subseteq \Phi$ as 
-$\Box^i\Phi = \set{\phi \in \Phi \suchthat \exists \ar \in \allargs \suchthat \ar \ileadstosti \phi}$.
-Define  $P^{*, i} \subseteq \Phi$ as the set of all \emph{$i$-decidable} propositions: $P^{*, i} = \set{\phi \in \Phi \suchthat \phi \in \Box^i\Phi \lor ¬\phi \in \Box^i\Phi}$; and define a set of propositions $P \subseteq \Phi$ as $i$-decidable iff $P \subseteq P^{*, i}$.
-The propositions in $P^{*, i}$ are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
-
-For any $i$-decidable proposition: $\phi \in \Box^i\Phi \oplus ¬\phi \in \Box^i\Phi$, where $\oplus$ denotes the exclusive disjunction; equivalently: $\phi \in \Box^i\Phi ⇔ ¬\phi \notin \Box^i\Phi$.
-This is proven below, and shows that \cref{ax:nocontr,ax:norm} are satisfiable together (suffices to define $\iPhi = \Box^i\Phi$).
-Also proven below is that, for any $i$-decidable proposition: $\phi \in \iPhi \oplus ¬\phi \in \iPhi$, which ensures an unambiguous interpretation of the content of $\iPhi$ for those propositions whose status is known thanks to the model.
-
-To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\phi \in \Phi$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi$.
-The $i$-decidable propositions are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
-
-For any $i$-decidable proposition $\phi$: $[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] \oplus [\exists \ar \in \allargs \suchthat \ar \ileadstosti ¬\phi]$, where $\oplus$ denotes the exclusive disjunction; equivalently: $[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] ⇔ ¬[\exists \ar \in \allargs \suchthat \ar \ileadstosti ¬\phi]$.
-This is proven below, and shows that \cref{ax:nocontr,ax:norm} are satisfiable together (suffices to define $\iPhi = \set{\phi \suchthat [\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi]}$).
-Also proven below is that, for any $i$-decidable proposition: $\phi \in \iPhi \oplus ¬\phi \in \iPhi$, which ensures an unambiguous interpretation of the content of $\iPhi$ for those propositions whose status is known thanks to the model.
-
-\commentOC{If we do not have $\propsure$ implies $\propposs$, then we can have $\propsure$ and $\notpropsure$ both accepted. But those propositions would still hold, it seems.}
-
+This axiom can be simplified, thanks to the following proposition.
 \begin{proposition}[Protocol coherence]
@@
 
-\begin{definition}[Restricted interpretability]
+Therefore, \cref{ax:norm} is actually equivalent to the following property.
+\begin{property}[Simple normative adequacy]
+	\label{ax:snorm}
+	$\forall i \in I, \phi \in \Phi: 
+		[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
+\end{property}
+
+To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\phi \in \Phi$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi$.
+The $i$-decidable propositions are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
+The next property ensures an unambiguous interpretation of the content of $\iPhi$ for all $i$-decidable propositions.
+In this definition, $\oplus$ denotes the exclusive disjunction; thus $\phi \in \iPhi \oplus ¬\phi \in \iPhi$ is equivalent to: $\phi \in \iPhi ⇔ ¬\phi \notin \iPhi$.
+It can be seen to hold by recalling that \cref{ax:snorm} is equivalent to \cref{ax:norm}.
+
+\begin{property}[Restricted interpretability]
 	\label{def:restrinterpr}
-	$\forall \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi] ⇒ [\phi \in \iPhi \oplus ¬\phi \in \iPhi]$.
-\end{definition}
-\begin{proposition}[Restricted interpretability satisfaction]
-	All models satisfying \cref{ax:nocontr,ax:norm} satisfy Restricted interpretability.
-\end{proposition}
-\begin{proof}
-	It is only required to prove that if $\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi$, then $¬\phi \notin \iPhi$. This follows from \cref{th:intinterpr}.
-\end{proof}
+	$\forall i \in I, \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi] ⇒ [\phi \in \iPhi \oplus ¬\phi \in \iPhi]$.
+\end{property}
 
 \subsection{Non-completeness}
-\begin{definition}[Model completeness]
-	$\forall \phi \in \Phi: \phi \in \Box\Phi \lor ¬\phi \in \Box\Phi$.
+\begin{definition}[Theory completeness]
+	$\forall \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstoi \phi] \lor [\exists \ar \in \allargs \suchthat \ar \ileadstoi ¬\phi]$.
 \end{definition}
@@
 \end{definition}
-The following proposition directly follows from the definitions.
+The following proposition directly follows from the definitions, together with \cref{prop:protcoh}.
 \begin{proposition}
-	1) Under Normative adequacy, Model completeness implies Deliberation completeness.
-2) Unrestricted interpretability implies Deliberation completeness.
-3) Under No contradiction, Unrestricted interpretability is equivalent to Deliberation completeness.
+	1) Under Normative adequacy, Theory completeness implies Deliberation completeness. 2) Unrestricted interpretability implies Deliberation completeness.
 \end{proposition}
-Models as defined here do not mandate Model completeness.
+Theories as defined here do not mandate Theory completeness.
 This is good for two reasons.
-First, even the weaker Deliberation completeness can appear too strong.
-Second, it is dubious that, for non trivial decision problems, models can be found for which both Normative adequacy is normatively compelling and Model completeness holds.
+First, even the weaker Deliberation completeness can be considered too strong.
+Second, it is dubious that, for non trivial decision problems, theories can be found for which both Normative adequacy is normatively compelling and Theory completeness holds.
 
@@
 
+If we do not have $\propsure$ implies $\propposs$, then we can have $\propsure$ and $\notpropsure$ both accepted.
+But all propositions of the normative analysis would still hold, it seems.
+We could have a property that says: $\propsure \in \iPhi ⇒ \propposs \in \iPhi \land \notpropsure \notin \iPhi \land \notpropposs \notin \iPhi$.
+
 \section{Theories proposing decisive arguments}

### 2020-06-24 simple.tex
Moved draft section

@@
 
-\section{Empirical theories}
-\subsection{Falsifiability}
-\commentOC{I want: An empirical theory for a normative theory is something like a normative and falsifiable claim.
-It is also configurable: it must be possible to guarantee that the falsification be easy (if the claim is false) depending on the kind of claim.}
-
-Given $\hist \in \allhist$ and $i \in I$, the claim $\hist \ileadstoe[i] \phi$ may not be verifiable, and is too specific to be falsifiable.
-However, given $\hist \in \allhist$, a broader claim is falsifiable: that for a given set of individuals $Q \subseteq I, \forall i \in Q, \hist \ileadstoe[i] \phi$ (provided $Q$ is big enough).
-Indeed, that claim it is equivalent to $\nexists i \in Q \suchthat \hist \nileadstoe[i] \phi$; exhibiting an $i \in Q$ such that $\hist \nileadstoe[i] \phi$ thus falsifies the broader claim.
-
-Given any $(\alltopic, ¬, \allargs, I)$, an \emph{observation protocol} is a binary tree whose non-leaf nodes are among $I × \allhist × \Phi$ and whose two edges out of any non leaf node are labeled by “yes” and “no”; the leaf nodes being simply $\emptyset$.
-The observation protocol is said to assume memory iff for each non-leaf node $n = (i, \hist, \phi)$ about $i$, any node $n' = (i, {\hist}', \phi')$ about $i$ that is further down the tree continues the history, that is, the sequence ${\hist}'$ starts with $\hist$.
-Given an observation protocol and observables $(\ileadstoe[i])_{i \in I}$, the \emph{observed path} refers to the path in the tree defined recursively as consisting of the root node and, for each non-leaf node $n = (i, \hist, \phi)$ in the path, the child node along the branch “yes” if $\hist \ileadstoe[i] \phi$ and the child node along the branch “no” otherwise.
-The \emph{observations} refer to the set of nodes along the observed path.
-
-Given any $(\alltopic, ¬, \allargs, I)$, a \emph{normative claim} about $(\alltopic, ¬, \allargs, I)$ (or about $\allargs$, when the other defined objects are left implicit) is any first-order logic proposition involving the atoms $[(\hist, \phi) \in {\ileadstoe[i]}], \hist \in \allhist, \phi \in \Phi$ which, together with \cref{ax:nocontr,ax:norm}, permits to deduce that $\phi \in \iPhi$ for some $i \in I$ and $\phi \in \Phi$.
-The claim is said to be \emph{about} the given set $\allargs$.
-An observation protocol, together with observables $(\ileadstoe[i])_{i \in I}$, \emph{falsifies} a normative claim iff the falsity of the claim is deducible from \cref{ax:nocontr,ax:norm} and the observations.
-A normative claim is \emph{falsifiable} iff there exists a finite observation protocol such that for any observables $(\ileadstoe[i])_{i \in I} \in (\allhist × \Phi)^I$, if the claim is false given these observables, then it is possible to deduce it from \cref{ax:nocontr,ax:norm} and the observations given the observables.
-
-\commentOC{Falsifiable may not be the right word.
-Perhaps “provable“, meaning “tautological or Popper-falsifiable”.
-“Falsifiable” suggests that if a claim is not falsifiable, then a weaker claim is not falsifiable either, which does not hold.
-My falsifiability criterion demands that if a claim is false, we can see it; whether Popper’s demands that the claim be possibly false.
-Perhaps I should demand that we can pick a set of consequences of the claim and show it wrong it at least one possible state of the universe.}
-
-A normative claim is \emph{trivial} iff it is about a singleton $\allargs = \set{\ar}$, and has the form: $\ar \ileadstosts \phi$, for some $i \in I$.
-A normative claim is minimal iff it has the form: $\exists \ar \in \allargs \suchthat \ar \ileadstosts \phi$, for some $i \in I$ and $\phi \in \Phi$.
-Note that given a minimal claim, $\card{\allargs} = 1$ is equivalent to the claim being trivial.
-
-\begin{proposition}[Trivial claims are not falsifiable]
-	Given any $(\alltopic, ¬, \allargs ≠ \emptyset, I)$, no minimal normative claim is falsifiable.
-\end{proposition}
-\begin{proof}
-	Consider any claim about some $i$ and some $\phi$ and any finite observation protocol.
-We have to show that for some observables, the claim is false, but it is impossible to observe it (meaning, to deduce it from \cref{ax:nocontr,ax:norm} and observations).
-
-	Given $k \in \N$, define $\ileadstosts[k]$ as $\ar^k \ileadstosts \phi$ and $\ar^{k+1} \ileadstosts ¬\phi$ (where $\ar^k$ designates a finite sequence repeating $k$ times $\ar$, for $\ar \in \allargs$).
-I claim that for some $k$, the observables that include this relation makes the claim false, but not observably so.
-This is because the observation protocol is finite, thus, only permits to observe some finite number of instances of the relation $\ileadsto$.
-Suffices to define $k$ as that number.
-\end{proof}
-
-There is another reason for non falsifiability, which does not involve the problem of finiteness.
-\begin{proposition}[Minimal non-trivial claims are not falsifiable]
-	Given any $(\alltopic, ¬, \allargs, I), \card{\allargs} ≥ 2$, no minimal normative claim is falsifiable.
-\end{proposition}
-\begin{proof}
-	Define $\ar_1$ as the first element of the sequence $\hist$ of the root node of the observation protocol (if the observation protocol is empty, suffices to define any observables that make the claim false).
-Define the observables so that $\forall \hist \in \allhist: \ar_2, \hist \ileadsto ¬\phi$.
-This proves that no argument is decisive, hence $\phi \notin \Box\Phi$, and the claim is false.
-But the observables may also be defined so as to satisfy the protocol (defined as: when going through the protocol, the observations can’t fail the claim).
-\end{proof}
-
-\subsection{Definition}
-A general empirical theory for a normative theory $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$ is a tuple $({\gleadsto}, f)$, where ${\gleadsto} \subseteq \allargs × \Phi$ and $f \subseteq (\allargs × \allargs) × \allargs$ with $f(\allargs × \allargs)$ being finite.
-
-Define $g(\ar_0) \subseteq \allargs × \allargs$ as $g(\ar_0) = \set{(\ar_2, \ar_1) \suchthat \ar_2 \in f(\ar_1, \ar_0)} = \bigcup_{\ar_1 \in \allargs} (f(\ar_1, \ar_0) × \set{\ar_1})$.
-The set $g(\ar_0)(\allargs)$ contains the planned attacks on $\ar_0$; the set $g(\ar_0)(\ar_2)$ contains the planned attacks on $\ar_0$ for which $\ar_2$ is a planned response; and the set $g(\ar_0)^{-1}(\ar_1) = f(\ar_1, \ar_0)$ contains the planned protections of $\ar_0$ against $\ar_1$.
-
-Given $\ar_0 \in \allargs$ and $\args_2 \subseteq \allargs$, define the set $\args_1 \subseteq \allargs$ of arguments that $\args_2$ protects $\ar_0$ from as $\args_1 = [f^{-1}(\args_2)]^{-1}(\ar_0) = \set{\ar_1 \in \allargs \suchthat f(\ar_1, \ar_0) \cap \args_2 ≠ \emptyset} = g(\ar_0)(\args_2) = dom(f^{-1}(\args_2) \cap \allargs × \set{\ar_0})$.
-
-\subsection{A general condition sufficient for validity and (hopefully) falsifiability}
-It should be possible to define this condition as a claim that does not involve $f$, so that it can be done before defining an empirical theory.
-Then, show that a normative and falsifiable claim must have the form of a convincingness claim.
-
-\begin{remark}
-	In fact, the model is tasked with finding a stable point after interrogating $i$.
-The process of trying counter-arguments $\ar_1, …$ is $q(i)$.
-When done, the model claims that $\ar_0 + \ar_2 + …$ is decisive.
-The model also claims that another process of interrogation does not lead to different answers.
-This is falsifiable.
-	When claiming that $(\ar_1, \ar_0) \ileadstost[i] \phi$, the model really claims that $\nexists p, i' \in q^{-1}(q(i)) \suchthat p, \ar_1, \ar_0 \ileadsto[i'] ¬\phi \lor p, \ar_0, \ar_1 \ileadsto[i'] ¬\phi$, where $i' \in q^{-1}(q(i))$ iff $q(i) = q(i')$.
-
-	To say that $\phi \in \iPhi$, need to not depend on choice of $q$, in the following sense: if with $q$, $\phi$ seems stable, but with $q'$, $¬\phi$ seems stable, then $\phi$ is not proved as being in $\iPhi$.
-But if with $q$, $\phi$ seems stable, but with $q'$, nothing can be shown to be stable, then $\phi$ is proved (temporarily) as being in $\iPhi$.
-More precisely, after $q'$, the model must be able to stabilize $i$ with its $q$.
-\end{remark}
-
-$\ar_0$ $i$-defends $\phi$ when ignoring $S_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \phi$.
-$\ar_0$ $i$-defends $\phi$ under protection of $S_2$ iff $\ar_0$ $i$-defends $\phi$ when ignoring $g(\ar_0)(\args_2)$.
-
-\begin{definition}[Convincingness]
-	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
-\end{definition}
-Note that requiring that $\args_0$ be a singleton does not modify the condition, in the sense that any theory satisfying the condition also satisfies its strenghtening.
-Similarly, requiring that $S_k ≠ \emptyset$ does not modify the condition (because if some $k$ satisfy the condition with $S_k = \emptyset$, then picking $k' = k-2$ with the same sets $S_j$ also satisfy the condition, and because $S_0 ≠ \emptyset$, this recursion must end with a suitable $k$).
-
-\begin{remark}
-	The claim must have the form: some structure is adequate for all individuals.
-Here, the structure is given by $f$.
-The claim should claim that looking at the attacks planned by $f$ is enough; and looking at the defenses planned by $f$ is enough.
-
-	This may be adequate as if $\ar_0$ seems suitable but some unplanned attacker $\ar_1$ attacks it, then use $\ar_1 \in \hist$ and observe that $¬(\hist, \ar_0) \ileadstoe \phi$ to deny the claim.
-
-	Perhaps this could be phrased as follows.
-Say that $\ar_2$ is replaceable by $\args_2$ iff what $\ar_2$ protects is either protected by $\args_2$ or replaceable (by what?).
-Say that a set $\args$ is sufficient iff its complement is replaceable by $\args$.
-Then $g$ claims (among others) that $g(\ar_0)^{-1}(\ar_1)$ is sufficient.
-
-	The claim can (hopefully) be given the form: $\forall i \suchthat …, \ar$ decisive. Given $i$, either $\ar_0$ is decisive, or $\ar_1$ attacks it but then $\ar_2$ is decisive, …
-\end{remark}
-
-\begin{theorem}
-	If an empirical theory is convincing, and its normative theory satisfies \cref{ax:nocontr,ax:norm}, then it is valid.
-\end{theorem}
-\begin{proof}
-	Consider $i \in I$ and $\phi \in {\gleadsto}(\allargs)$. 
-	By hypothesis, $\exists k$ such that some $\ar_k \in \args_k$ defends $\phi$ under protection of $\emptyset$.
-Therefore, $\ar_k \ileadstosts \phi$.
-Using \cref{ax:norm}, this yields that $\phi \in \iPhi$, and validity follows from \cref{ax:nocontr}.
-\end{proof}
-
-\begin{theorem}
-	The convincingness claim of any empirical theory is falsifiable: given an ET, there exists a finite obs prot with memory such that for any observables, if the claim is false given these observables, then it is possible to deduce it from the axioms and observations.
-\end{theorem}
-\begin{proof}
-
-\end{proof}
-
-\section{Additive empirical theories}
-TODO: 3) define single-answer models.
-4) phrase conditions below for history and single-answer models.
-5) show that these conditions can be verified or falsified.
-6) show that if the claim of the model does not include these conditions, then the model is not falsifiable, as suggested here below for some form of claims.
-
+\section{Additive single-answer empirical theories}
 \subsection{Definition}
@@
 
+Show that if the claim of the model is of a different form, then the model is not falsifiable, as suggested here below for some form of claims.
+
+Extend the definition of additive single-answer theories to non-additive single-answer theories.
+
+\section{Empirical theories}
+\subsection{Falsifiability}
+\commentOC{I want: An empirical theory for a normative theory is something like a normative and falsifiable claim.
+It is also configurable: it must be possible to guarantee that the falsification be easy (if the claim is false) depending on the kind of claim.}
+
+Given $\hist \in \allhist$ and $i \in I$, the claim $\hist \ileadstoe[i] \phi$ may not be verifiable, and is too specific to be falsifiable.
+However, given $\hist \in \allhist$, a broader claim is falsifiable: that for a given set of individuals $Q \subseteq I, \forall i \in Q, \hist \ileadstoe[i] \phi$ (provided $Q$ is big enough).
+Indeed, that claim it is equivalent to $\nexists i \in Q \suchthat \hist \nileadstoe[i] \phi$; exhibiting an $i \in Q$ such that $\hist \nileadstoe[i] \phi$ thus falsifies the broader claim.
+
+Given any $(\alltopic, ¬, \allargs, I)$, an \emph{observation protocol} is a binary tree whose non-leaf nodes are among $I × \allhist × \Phi$ and whose two edges out of any non leaf node are labeled by “yes” and “no”; the leaf nodes being simply $\emptyset$.
+The observation protocol is said to assume memory iff for each non-leaf node $n = (i, \hist, \phi)$ about $i$, any node $n' = (i, {\hist}', \phi')$ about $i$ that is further down the tree continues the history, that is, the sequence ${\hist}'$ starts with $\hist$.
+Given an observation protocol and observables $(\ileadstoe[i])_{i \in I}$, the \emph{observed path} refers to the path in the tree defined recursively as consisting of the root node and, for each non-leaf node $n = (i, \hist, \phi)$ in the path, the child node along the branch “yes” if $\hist \ileadstoe[i] \phi$ and the child node along the branch “no” otherwise.
+The \emph{observations} refer to the set of nodes along the observed path.
+
+Given any $(\alltopic, ¬, \allargs, I)$, a \emph{normative claim} about $(\alltopic, ¬, \allargs, I)$ (or about $\allargs$, when the other defined objects are left implicit) is any first-order logic proposition involving the atoms $[(\hist, \phi) \in {\ileadstoe[i]}], \hist \in \allhist, \phi \in \Phi$ which, together with the axioms, permits to deduce that $\phi \in \iPhi$ for some $i \in I$ and $\phi \in \Phi$.
+The claim is said to be \emph{about} the given set $\allargs$.
+An observation protocol, together with observables $(\ileadstoe[i])_{i \in I}$, \emph{falsifies} a normative claim iff the falsity of the claim is deducible from the axioms and the observations.
+A normative claim is \emph{falsifiable} iff there exists a finite observation protocol such that for any observables $(\ileadstoe[i])_{i \in I} \in (\allhist × \Phi)^I$, if the claim is false given these observables, then it is possible to deduce it from the axioms and the observations given the observables.
+
+\commentOC{Falsifiable may not be the right word.
+Perhaps “provable“, meaning “tautological or Popper-falsifiable”.
+“Falsifiable” suggests that if a claim is not falsifiable, then a weaker claim is not falsifiable either, which does not hold.
+My falsifiability criterion demands that if a claim is false, we can see it; whether Popper’s demands that the claim be possibly false.
+Perhaps I should demand that we can pick a set of consequences of the claim and show it wrong it at least one possible state of the universe.}
+
+A normative claim is \emph{trivial} iff it is about a singleton $\allargs = \set{\ar}$, and has the form: $\ar \ileadstosts \phi$, for some $i \in I$.
+A normative claim is minimal iff it has the form: $\exists \ar \in \allargs \suchthat \ar \ileadstosts \phi$, for some $i \in I$ and $\phi \in \Phi$.
+Note that given a minimal claim, $\card{\allargs} = 1$ is equivalent to the claim being trivial.
+
+\begin{proposition}[Trivial claims are not falsifiable]
+	Given any $(\alltopic, ¬, \allargs ≠ \emptyset, I)$, no minimal normative claim is falsifiable.
+\end{proposition}
+\begin{proof}
+	Consider any claim about some $i$ and some $\phi$ and any finite observation protocol.
+We have to show that for some observables, the claim is false, but it is impossible to observe it (meaning, to deduce it from the axioms and observations).
+
+	Given $k \in \N$, define $\ileadstosts[k]$ as $\ar^k \ileadstosts \phi$ and $\ar^{k+1} \ileadstosts ¬\phi$ (where $\ar^k$ designates a finite sequence repeating $k$ times $\ar$, for $\ar \in \allargs$).
+I claim that for some $k$, the observables that include this relation makes the claim false, but not observably so.
+This is because the observation protocol is finite, thus, only permits to observe some finite number of instances of the relation $\ileadsto$.
+Suffices to define $k$ as that number.
+\end{proof}
+
+There is another reason for non falsifiability, which does not involve the problem of finiteness.
+\begin{proposition}[Minimal non-trivial claims are not falsifiable]
+	Given any $(\alltopic, ¬, \allargs, I), \card{\allargs} ≥ 2$, no minimal normative claim is falsifiable.
+\end{proposition}
+\begin{proof}
+	Define $\ar_1$ as the first element of the sequence $\hist$ of the root node of the observation protocol (if the observation protocol is empty, suffices to define any observables that make the claim false).
+Define the observables so that $\forall \hist \in \allhist: \ar_2, \hist \ileadsto ¬\phi$.
+This proves that no argument is decisive, hence $\phi \notin \Box\Phi$, and the claim is false.
+But the observables may also be defined so as to satisfy the protocol (defined as: when going through the protocol, the observations can’t fail the claim).
+\end{proof}
+
+\subsection{Definition}
+A general empirical theory for a normative theory $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$ is a tuple $({\gleadsto}, f)$, where ${\gleadsto} \subseteq \allargs × \Phi$ and $f \subseteq (\allargs × \allargs) × \allargs$ with $f(\allargs × \allargs)$ being finite.
+
+Define $g(\ar_0) \subseteq \allargs × \allargs$ as $g(\ar_0) = \set{(\ar_2, \ar_1) \suchthat \ar_2 \in f(\ar_1, \ar_0)} = \bigcup_{\ar_1 \in \allargs} (f(\ar_1, \ar_0) × \set{\ar_1})$.
+The set $g(\ar_0)(\allargs)$ contains the planned attacks on $\ar_0$; the set $g(\ar_0)(\ar_2)$ contains the planned attacks on $\ar_0$ for which $\ar_2$ is a planned response; and the set $g(\ar_0)^{-1}(\ar_1) = f(\ar_1, \ar_0)$ contains the planned protections of $\ar_0$ against $\ar_1$.
+
+Given $\ar_0 \in \allargs$ and $\args_2 \subseteq \allargs$, define the set $\args_1 \subseteq \allargs$ of arguments that $\args_2$ protects $\ar_0$ from as $\args_1 = [f^{-1}(\args_2)]^{-1}(\ar_0) = \set{\ar_1 \in \allargs \suchthat f(\ar_1, \ar_0) \cap \args_2 ≠ \emptyset} = g(\ar_0)(\args_2) = dom(f^{-1}(\args_2) \cap \allargs × \set{\ar_0})$.
+
+\subsection{A general condition sufficient for validity and (hopefully) falsifiability}
+It should be possible to define this condition as a claim that does not involve $f$, so that it can be done before defining an empirical theory.
+Then, show that a normative and falsifiable claim must have the form of a convincingness claim.
+
+\begin{remark}
+	In fact, the model is tasked with finding a stable point after interrogating $i$.
+The process of trying counter-arguments $\ar_1, …$ is $q(i)$.
+When done, the model claims that $\ar_0 + \ar_2 + …$ is decisive.
+The model also claims that another process of interrogation does not lead to different answers.
+This is falsifiable.
+	When claiming that $(\ar_1, \ar_0) \ileadstost[i] \phi$, the model really claims that $\nexists p, i' \in q^{-1}(q(i)) \suchthat p, \ar_1, \ar_0 \ileadsto[i'] ¬\phi \lor p, \ar_0, \ar_1 \ileadsto[i'] ¬\phi$, where $i' \in q^{-1}(q(i))$ iff $q(i) = q(i')$.
+
+	To say that $\phi \in \iPhi$, need to not depend on choice of $q$, in the following sense: if with $q$, $\phi$ seems stable, but with $q'$, $¬\phi$ seems stable, then $\phi$ is not proved as being in $\iPhi$.
+But if with $q$, $\phi$ seems stable, but with $q'$, nothing can be shown to be stable, then $\phi$ is proved (temporarily) as being in $\iPhi$.
+More precisely, after $q'$, the model must be able to stabilize $i$ with its $q$.
+\end{remark}
+
+$\ar_0$ $i$-defends $\phi$ when ignoring $S_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \phi$.
+$\ar_0$ $i$-defends $\phi$ under protection of $S_2$ iff $\ar_0$ $i$-defends $\phi$ when ignoring $g(\ar_0)(\args_2)$.
+
+\begin{definition}[Convincingness]
+	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
+\end{definition}
+Note that requiring that $\args_0$ be a singleton does not modify the condition, in the sense that any theory satisfying the condition also satisfies its strenghtening.
+Similarly, requiring that $S_k ≠ \emptyset$ does not modify the condition (because if some $k$ satisfy the condition with $S_k = \emptyset$, then picking $k' = k-2$ with the same sets $S_j$ also satisfy the condition, and because $S_0 ≠ \emptyset$, this recursion must end with a suitable $k$).
+
+\begin{remark}
+	The claim must have the form: some structure is adequate for all individuals.
+Here, the structure is given by $f$.
+The claim should claim that looking at the attacks planned by $f$ is enough; and looking at the defenses planned by $f$ is enough.
+
+	This may be adequate as if $\ar_0$ seems suitable but some unplanned attacker $\ar_1$ attacks it, then use $\ar_1 \in \hist$ and observe that $¬(\hist, \ar_0) \ileadstoe \phi$ to deny the claim.
+
+	Perhaps this could be phrased as follows.
+Say that $\ar_2$ is replaceable by $\args_2$ iff what $\ar_2$ protects is either protected by $\args_2$ or replaceable (by what?).
+Say that a set $\args$ is sufficient iff its complement is replaceable by $\args$.
+Then $g$ claims (among others) that $g(\ar_0)^{-1}(\ar_1)$ is sufficient.
+
+	The claim can (hopefully) be given the form: $\forall i \suchthat …, \ar$ decisive. Given $i$, either $\ar_0$ is decisive, or $\ar_1$ attacks it but then $\ar_2$ is decisive, …
+\end{remark}
+
+\begin{theorem}
+	If an empirical theory is convincing, and its normative theory satisfies the axioms, then it is valid.
+\end{theorem}
+\begin{proof}
+	Consider $i \in I$ and $\phi \in {\gleadsto}(\allargs)$. 
+	By hypothesis, $\exists k$ such that some $\ar_k \in \args_k$ defends $\phi$ under protection of $\emptyset$. Therefore, $\ar_k \ileadstosts \phi$. Using \cref{ax:norm}, validity follows.
+\end{proof}
+
+\begin{theorem}
+	The convincingness claim of any empirical theory is falsifiable: given an ET, there exists a finite obs prot with memory such that for any observables, if the claim is false given these observables, then it is possible to deduce it from the axioms and observations.
+\end{theorem}
+
 \section{Theories proposing decisive arguments}

### 2020-06-24 simple.tex
Further clarification of notations and improvements

@@
 Define $\hist \ileadstosti \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
-Given $\hist \in \allhist$, let $\hist_\mathit{end}$ denote the set containing the last two elements of the sequence $\hist$ if the sequence has at least two elements; the singleton set containing the last element of the sequence if it has exactly one element; and the empty set if $\hist = \emptyset$.
-Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstosti \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \hist_\mathit{end}: \hist \ileadstosti \phi$.
+Given $\hist \in \allhist$, let $\histend$ denote the set containing the last two elements of the sequence $\hist$ if the sequence has at least two elements; the singleton set containing the last element of the sequence if it has exactly one element; and the empty set if $\hist = \emptyset$.
+Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstosti \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstosti \phi$.
 
@@
 \subsection{Definition}
-An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
-with ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
-${\gbeatsinv}(\allargs)$ finite,
-and $+$ a commutative associative internal binary operation on $\allargs$.
-Given a finite $\args \subseteq \allargs$, the notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.
-\commentOC{Check about finiteness.}
-\commentOC{${\gbeatsinv}$ need not be finite, only those even ones: the transitive closure of ${\gleadstoinv}(\Phi)$ through ${\gbeatsinv}^2$, that is, $({\gbeatsinv})^2[{\gleadstoinv}(\Phi)] = \cup_{k \in 2\N}({\gbeatsinv}^{k}({\gleadstoinv}(\Phi)))$.}
-\commentOC{I should only define $\ar \in \allargs$ plus $\ard$.}
-
-This defines a function: $\forall \ar_1 \gbeats \ar_0: f(\ar_1, \ar_0) = \ar_0 + {\gbeatsinv}(\ar_1) = \set{\ar_0 + \ard_2 \suchthat \ard_2 \in {\gbeatsinv}(\ar_1)}$, and $f(\ar_1, \ar_0) = \emptyset$ otherwise.
-Thus, $f = \set{((\ar_1, \ar_0), \ar_2) \suchthat \exists \ard_2 \in \allargs \suchthat \ard_2 \gbeats \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2}$.
-Also, from the previous definition, $g(\ar_0)(\ar_0 + \argsd_2) = dom(f^{-1}(\ar_0 + \argsd_2) \cap (\allargs × \set{\ar_0})) = {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$ because $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \argsd_2) ⇔ \exists \ar_2 \in \ar_0 + \argsd_2 \suchthat \ar_2 \in f(\ar_1, \ar_0) ⇔ \ar_1 \gbeats \ar_0 \land \exists \ard \in \argsd_2 \suchthat \ard \gbeats \ar_1$.
-\commentOC{Could be false. Define }
-
-Note that $f^{-1}(\ar_0 + \ar_2) ≠ {\gbeats}(\ar_2) × \set{\ar_0}$: if ${\gbeats} = \set{(\ard_2, \ar_1), (\ar_1, \ar_0), (\ard_6, \ar_5), (\ar_5, \ar_4)}$, and $\ar_0 + \ard_2 = \ar_4 + \ard_6$, then $f^{-1}(\ar_0 + \ard_2) = f^{-1}(\ar_4 + \ard_6) = \set{(\ar_1, \ar_0), (\ar_5, \ar_4)}$ and ${\gbeats}(\ard_2) × \set{\ar_0} = \set{(\ar_1, \ar_0)}$.
-Also, note that $g(\ar_0)(\ar_0 + \argsd_2) ≠ {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$.
-Consider ${\gbeats} = \set{(\ard_2, \ar_1), (\ar_1, \ar_0)}, \ar_2 = \ar_0 + \ard = \ar_0 + \ard_2$.
-Then, $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \ard)$, hence, $\ar_1 \in g(\ar_0)(\ar_0 + \ard)$, but ${\gbeats}(\ard) = \emptyset$.
+\commentOC{I leave the definition as is, but for the moment I only consider ${\gleadsto}$, a relation that does not depend on $i$; and I do not use $q(i)$.}
+An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$,
+with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
+${\gbeats} \subseteq \allargs × \allargs$,
+${\dbeats} \subseteq \alldargs × \allargs$ and is injective (thus $\forall \ar \in \allargs: {\dbeatsinv}(\ar)$ is a singleton or empty). 
+Define $\df \subseteq \allargs × \alldargs$ as $\df = {\dbeatsinv} \circ {\gbeatsinv}$. 
+The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
+As usual, $\ar + \ard$ means $+(\ar, \ard)$. 
+Define $\dfp \subseteq \allargs × \allargs$ as, $\forall \ar \in \allargs$: $\dfp(\ar) = \ar + \df(\ar) = \set{\ar + \ard \suchthat \ard \in \df(\ar)}$.
+An empirical theory must satisfy
+$\forall \ar \in {\gleadsto}(\allargs): \exists k \in \N^* \suchthat \dfp^k(\ar) = \emptyset$.
 
 \subsection{Falsifiability}
-\begin{proposition}
-	An empirical theory has only finite sets $\gargs[i, \phi]$, and an upper bound on their size exists that is independent of ${\ileadsto}$.
-\end{proposition}
-\begin{proof}
-	Given $i, \phi$.
-Observe that $\forall \ard: d^{i, \phi}(\ard) \subseteq {\gbeatsmt}(\ard)$.
-Thus, $d^{i, \phi}$ is finite.
-Also, the transitive closure through $\sigma^i$ changes a finite number of time, otherwise it is possible to build an infinite chain in ${\gbeatsmt}$.
-\end{proof}
-
-Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatse[!\phi] \ar_0$ iff $\exists \hist \in \allhist \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0} \land \hist \nileadstosts \phi$.
+Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$.
 
@@
 	\label{eq:st-in-terms-of-e}
-	\ar_0 \nileadstosts \phi ⇔ [\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar_0].
+	\ar_0 \nileadstosti \phi ⇔ [\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatsi \ar_0].
 \end{equation}
@@
 \begin{proof}
-	By definition of ${\ileadstosts}$, $\ar_0 \ileadstosts \phi ⇔ \forall \hist \in \allhist \suchthat [\exists \ar_1 \in \allargs \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0}]: \hist \ileadstosts \phi.$ Equivalently, $\ar_0 \nileadstosts \phi ⇔ \exists \hist \in \allhist \suchthat [\exists \ar_1 \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0}] \land \hist \nileadstosts \phi$.
-This is also equivalent to $\ar_0 \nileadstosts \phi ⇔ \exists \hist \in \allhist, \ar_1 \in \allargs \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0} \land \hist \nileadstosts \phi$.
-By definition of ${\ibeatse}$, this is the proposition to be proven.
+	By definition of ${\ileadstosti}$, $\ar_0 \ileadstosti \phi ⇔ \forall \hist \in \allhist \suchthat \ar_0 \in \histend: \hist \ileadstosti \phi$. 
+Equivalently, $\ar_0 \ileadstosti \phi ⇔ \forall \hist \in \allhist \suchthat [\exists \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend]: \hist \ileadstosti \phi$. 
+Still equivalently, $\ar_0 \nileadstosti \phi ⇔ \exists \hist \in \allhist \suchthat [\exists \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend] \land \hist \nileadstosti \phi$. 
+This can also be written: $\ar_0 \nileadstosti \phi ⇔ \exists \hist \in \allhist, \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$.
+By definition of ${\ibeatsi}$, this is the proposition to be proven.
 \end{proof}
+
+Given $i \in I, \phi \in {\gleadsto}(\allargs), \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $d^{i, \phi}(\ar) \subseteq \alldargs$, as $d^{i, \phi}(\ar) = [{\dbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatsiinv})](\ar)$.
+%Given $i \in I, \phi \in {\gleadsto}(\allargs), \ar \in \allargs, \ard \in \df(\ar)$, define the \emph{successors} of $(\ar, \ard)$ as $\sigma^{i, \phi}(\ar, \ard) = \set{\ar + \ard} × d^{i, \phi}(\ar + \ard)$.
+Given $i \in I, \phi \in {\gleadsto}(\allargs)$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dfp$: $\gargs[i, \phi] = \cup_{k \in \N} \dfp^k({\gleadstoinv}(\phi))$, where $\dfp^0$ is the identity function.
+
+%\begin{proposition}
+%	An empirical theory has only finite sets $\gargs[i, \phi]$, and an upper bound on their size exists that is independent of ${\ileadsto}$.
+%\end{proposition}
+%\begin{proof}
+%	Given $i, \phi$.
+Observe that $\forall \ard: d^{i, \phi}(\ard) \subseteq {\gbeatsmt}(\ard)$.
+Thus, $d^{i, \phi}$ is finite.
+Also, the transitive closure through $\sigma^i$ changes a finite number of time, otherwise it is possible to build an infinite chain in ${\gbeatsmt}$.
+%\end{proof}
 
@@
 $\ar_0$ $i$-defends $\phi$ under d-protection of $\argsd_2$ iff $\ar_0$ $i$-defends $\phi$ when ignoring ${\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$.
-
-Given $i \in I, \phi \in {\gleadsto}(\allargs)$, define the $\phi$-protectors of $\ard$ as $d^{i, \phi}(\ard) = [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\ard)$.
-Define the successors of $(\phi, \ar, \ard)$ as $\sigma^i(\phi, \ar, \ard) = \set{\phi} × \set{\ar + \ard} × d^{i, \phi}(\ard)$.
-Given $i \in I, \phi \in {\gleadsto}(\allargs)$, define $\gargs[i, \phi]$ as the transitive closure of $(\phi, \emptyset, \ar)$ under $\sigma^i$, with $\ar \gleadsto \phi$.
-\commentOC{Assuming only one $\ar$ leads to that $\phi$.}
-Define $\gargs[i, \phi] = \bigcup_{k \in 2\N} \gargs[i, \phi, k]$, and $\gargs = \cup_{i \in I, \phi \in {\gleadsto}(\allargs)} \gargs[i, \phi]$.
 
@@
 
+An additive theory need not have freedom for defining planned attacks on additive terms: this should be a consequence on the planned attacks on defenses and on initial arguments only.
+This makes the theory easier to define, as only attacks on partial arguments are to be defined.
+
 \section{Empirical theories}
+\subsection{Simple to complex}
+From an additive single-answer empirical theory, we can define a function: $\forall \ar_1 \gbeats \ar_0: f(\ar_1, \ar_0) = \ar_0 + {\gbeatsinv}(\ar_1) = \set{\ar_0 + \ard_2 \suchthat \ard_2 \in {\gbeatsinv}(\ar_1)}$, and $f(\ar_1, \ar_0) = \emptyset$ otherwise.
+Thus, $f = \set{((\ar_1, \ar_0), \ar_2) \suchthat \exists \ard_2 \in \allargs \suchthat \ard_2 \gbeats \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2}$.
+Also, from the previous definition, $g(\ar_0)(\ar_0 + \argsd_2) = dom(f^{-1}(\ar_0 + \argsd_2) \cap (\allargs × \set{\ar_0})) = {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$ because $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \argsd_2) ⇔ \exists \ar_2 \in \ar_0 + \argsd_2 \suchthat \ar_2 \in f(\ar_1, \ar_0) ⇔ \ar_1 \gbeats \ar_0 \land \exists \ard \in \argsd_2 \suchthat \ard \gbeats \ar_1$.
+\commentOC{Could be false. Define }
+
+Note that $f^{-1}(\ar_0 + \ar_2) ≠ {\gbeats}(\ar_2) × \set{\ar_0}$: if ${\gbeats} = \set{(\ard_2, \ar_1), (\ar_1, \ar_0), (\ard_6, \ar_5), (\ar_5, \ar_4)}$, and $\ar_0 + \ard_2 = \ar_4 + \ard_6$, then $f^{-1}(\ar_0 + \ard_2) = f^{-1}(\ar_4 + \ard_6) = \set{(\ar_1, \ar_0), (\ar_5, \ar_4)}$ and ${\gbeats}(\ard_2) × \set{\ar_0} = \set{(\ar_1, \ar_0)}$.
+Also, note that $g(\ar_0)(\ar_0 + \argsd_2) ≠ {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$.
+Consider ${\gbeats} = \set{(\ard_2, \ar_1), (\ar_1, \ar_0)}, \ar_2 = \ar_0 + \ard = \ar_0 + \ard_2$.
+Then, $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \ard)$, hence, $\ar_1 \in g(\ar_0)(\ar_0 + \ard)$, but ${\gbeats}(\ard) = \emptyset$.
+
 \subsection{Falsifiability}

### 2020-06-25 simple.tex
Rm old successors and prop about finite S
Clean falsifiability VS convincing

@@
 ${\gbeats} \subseteq \allargs × \allargs$,
-${\dbeats} \subseteq \alldargs × \allargs$ and is injective (thus $\forall \ar \in \allargs: {\dbeatsinv}(\ar)$ is a singleton or empty). 
+${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range equals ${\gbeatsinv}(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: ${\dbeatsinv}(\ar_1)$ is a singleton).
 Define $\df \subseteq \allargs × \alldargs$ as $\df = {\dbeatsinv} \circ {\gbeatsinv}$. 
@@
 Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$.
+
+Given $i \in I, \phi \in {\gleadsto}(\allargs), \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $d^{i, \phi}(\ar) \subseteq \alldargs$, as $d^{i, \phi}(\ar) = [{\dbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatsiinv})](\ar)$.
+Define $d^{i, \phi}_+$ as $d^{i, \phi}_+(\ar) = \ar + d^{i, \phi}(\ar)$.
+Given $i \in I, \phi \in {\gleadsto}(\allargs)$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $d^{i, \phi}_+$: $\gargs[i, \phi] = \cup_{k \in \N} (d^{i, \phi}_+)^k({\gleadstoinv}(\phi))$, where $(d^{i, \phi}_+)^0$ is the identity function.
+
+Given $\hist \in \allhist$, $\hist(\intvl{1, l(\hist)})$, where $l(\hist) \in \N$ is the length of the sequence $\hist$, denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
+Abusing notation, given $\args_1 \subseteq \allargs$, I write $\args_1 \cap \hist$ to designate $\args_1 \cap \hist(\intvl{1, l(\hist)})$, therefore using simply $\hist$ in that expression to denote the \emph{range} of $\hist$.
+
+$\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset\right]: \hist \ileadstosti \phi$.
+
+\begin{definition}[Convincingness]
+	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \ar \in \gargs[i, \phi]: \ar$ $i$-defends $\phi$.
+\end{definition}
+
+A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × {\gleadsto}(\allargs) × \allhist$ such that $\exists \ar \in \histend \cap \gargs[i, \phi] \suchthat {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.
+
+\begin{theorem}
+	An empirical theory is convincing iff it has no falsification instances.
+\end{theorem}
+\begin{proof}
+	For all $i \in I, \phi \in {\gleadsto}(\allargs)$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
+
+	For all $i \in I, \phi \in {\gleadsto}(\allargs)$, the following equivalences hold.
+$\forall \ar \in \gargs[i, \phi]$, $\ar$ $i$-defends $\phi$ iff $\forall \ar \in \gargs[i, \phi], \hist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset\right]$, $\hist \ileadstosti \phi$ iff $\forall \hist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset\right]$, $(i, \phi, \hist)$ is not a falsification instance.
+\end{proof}
 
@@
 Still equivalently, $\ar_0 \nileadstosti \phi ⇔ \exists \hist \in \allhist \suchthat [\exists \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend] \land \hist \nileadstosti \phi$. 
-This can also be written: $\ar_0 \nileadstosti \phi ⇔ \exists \hist \in \allhist, \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$.
+It can also be written $\ar_0 \nileadstosti \phi ⇔ \exists \hist \in \allhist, \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$.
 By definition of ${\ibeatsi}$, this is the proposition to be proven.
@@
 
-Given $i \in I, \phi \in {\gleadsto}(\allargs), \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $d^{i, \phi}(\ar) \subseteq \alldargs$, as $d^{i, \phi}(\ar) = [{\dbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatsiinv})](\ar)$.
-%Given $i \in I, \phi \in {\gleadsto}(\allargs), \ar \in \allargs, \ard \in \df(\ar)$, define the \emph{successors} of $(\ar, \ard)$ as $\sigma^{i, \phi}(\ar, \ard) = \set{\ar + \ard} × d^{i, \phi}(\ar + \ard)$.
-Given $i \in I, \phi \in {\gleadsto}(\allargs)$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dfp$: $\gargs[i, \phi] = \cup_{k \in \N} \dfp^k({\gleadstoinv}(\phi))$, where $\dfp^0$ is the identity function.
-
-%\begin{proposition}
-%	An empirical theory has only finite sets $\gargs[i, \phi]$, and an upper bound on their size exists that is independent of ${\ileadsto}$.
-%\end{proposition}
-%\begin{proof}
-%	Given $i, \phi$.
-Observe that $\forall \ard: d^{i, \phi}(\ard) \subseteq {\gbeatsmt}(\ard)$.
-Thus, $d^{i, \phi}$ is finite.
-Also, the transitive closure through $\sigma^i$ changes a finite number of time, otherwise it is possible to build an infinite chain in ${\gbeatsmt}$.
-%\end{proof}
-
-$\ar_0$ $i$-defends $\phi$ when ignoring $\args_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \phi$.
-$\ar_0$ $i$-defends $\phi$ under protection of $\args_2$ iff $\ar_0$ $i$-defends $\phi$ when ignoring $g(\ar_0)(\args_2)$.
-$\ar_0$ $i$-defends $\phi$ under d-protection of $\argsd_2$ iff $\ar_0$ $i$-defends $\phi$ when ignoring ${\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$.
-
-\begin{definition}[Conv. single-try]
-	$\forall i \in I, \phi \in {\gleadsto}(\allargs), (\phi, \ar, \ard) \in \gargs[i, \phi], \ar_0 = \ar + \ard: \ar_0$ $i$-defends $\phi$ under d-protection of $d^{i, \phi}(\ard)$.
-\end{definition}
-
+\subsection{Vrac from here}
 1. Checkpath: this is completely general.
@@
 
-A falsification instance of an empirical theory is a tuple $(i, \phi, \ar, \ard, \hist, \ar_1)$ such that $(\phi, \ar, \ard) \in \gargs[i, \phi]$ and, defining $\ar_0 = \ar + \ard$: $[{\gbeatsinv}(\ard) \cap \hist = \emptyset] \land [\hist \text{ ends with } \set{\ar_1, \ar_0}] \land \ar_1 \ibeatse[!\phi] \ar_0]$ (the theory says that this history should defend $\phi$ under prot of something and that is not in the history).
-
-\begin{theorem}
-	An empirical theory is conv.\ single-try iff it has no falsification instances.
-\end{theorem}
-\begin{proof}
-	Given $i, \phi, (\phi, \ar, \ard) \in \gargs[i, \phi]$.
-Define $\args_1 = {\gbeats}(d^{i, \phi}(\ard)) \cap {\gbeatsinv}(\ar)$.
-Now $\ar$ $i$-defends $\phi$ ignoring $\args_1$ is equivalent to: $\forall \hist: \hist \cap \args_1 = \emptyset ⇒ (\hist, \ar) \ileadstosts \phi$.
-Negation: $\exists \hist \suchthat \hist \cap \args_1 = \emptyset \land (\hist, \ar) \nileadstosts \phi$.
-TODO prove that equivalent to no falsification.
-\end{proof}
-
-\subsection{Vrac from here}
 An empirical theory is defined only given some normative theory.

### 2020-06-25 simple.tex
Rm unused proof and prop about attack-exists

@@
 	For all $i \in I, \phi \in {\gleadsto}(\allargs)$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
-
-	For all $i \in I, \phi \in {\gleadsto}(\allargs)$, the following equivalences hold.
-$\forall \ar \in \gargs[i, \phi]$, $\ar$ $i$-defends $\phi$ iff $\forall \ar \in \gargs[i, \phi], \hist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset\right]$, $\hist \ileadstosti \phi$ iff $\forall \hist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset\right]$, $(i, \phi, \hist)$ is not a falsification instance.
-\end{proof}
-
-\begin{proposition}
-	$\forall i \in I, \phi \in \Phi, \ar_0 \in \allargs$:
-\begin{equation}
-	\label{eq:st-in-terms-of-e}
-	\ar_0 \nileadstosti \phi ⇔ [\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatsi \ar_0].
-\end{equation}
-\end{proposition}
-\begin{proof}
-	By definition of ${\ileadstosti}$, $\ar_0 \ileadstosti \phi ⇔ \forall \hist \in \allhist \suchthat \ar_0 \in \histend: \hist \ileadstosti \phi$. 
-Equivalently, $\ar_0 \ileadstosti \phi ⇔ \forall \hist \in \allhist \suchthat [\exists \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend]: \hist \ileadstosti \phi$. 
-Still equivalently, $\ar_0 \nileadstosti \phi ⇔ \exists \hist \in \allhist \suchthat [\exists \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend] \land \hist \nileadstosti \phi$. 
-It can also be written $\ar_0 \nileadstosti \phi ⇔ \exists \hist \in \allhist, \ar_1 \in \allargs \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$.
-By definition of ${\ibeatsi}$, this is the proposition to be proven.
 \end{proof}

### 2020-07-02 simple.tex
Rewrite clean until Empirical th; disc about ET

@@
 An empirical theory must satisfy
-$\forall \ar \in {\gleadsto}(\allargs): \exists k \in \N^* \suchthat \dfp^k(\ar) = \emptyset$.
+$\forall \ar \in \gPhi: \exists k \in \N^* \suchthat \dfp^k(\ar) = \emptyset$.
 
 \subsection{Falsifiability}
-Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$.
-
-Given $i \in I, \phi \in {\gleadsto}(\allargs), \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $d^{i, \phi}(\ar) \subseteq \alldargs$, as $d^{i, \phi}(\ar) = [{\dbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatsiinv})](\ar)$.
-Define $d^{i, \phi}_+$ as $d^{i, \phi}_+(\ar) = \ar + d^{i, \phi}(\ar)$.
-Given $i \in I, \phi \in {\gleadsto}(\allargs)$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $d^{i, \phi}_+$: $\gargs[i, \phi] = \cup_{k \in \N} (d^{i, \phi}_+)^k({\gleadstoinv}(\phi))$, where $(d^{i, \phi}_+)^0$ is the identity function.
+Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$, and say that $\ar_1$ is an effective attack against $\ar_0$ (from $i$’s perspective).
+
+Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [{\dbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatsiinv})](\ar)$.
+Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
+Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$, where $(\dip)^0$ is the identity function over $\allargs$.
 
@@
 \begin{definition}[Convincingness]
-	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \ar \in \gargs[i, \phi]: \ar$ $i$-defends $\phi$.
-\end{definition}
-
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × {\gleadsto}(\allargs) × \allhist$ such that $\exists \ar \in \histend \cap \gargs[i, \phi] \suchthat {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.
+	$\forall i \in I, \phi \in \gPhi, \ar \in \gargs[i, \phi]: \ar$ $i$-defends $\phi$.
+\end{definition}
+
+A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.
 
@@
 \begin{proof}
-	For all $i \in I, \phi \in {\gleadsto}(\allargs)$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
+	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
+\end{proof}
+
+\begin{definition}[Validity]
+	An empirical theory is \emph{valid} iff $\forall i \in I, \phi \in \gPhi: [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
+\end{definition}
+
+\begin{remark}[TODO]
+	$\ar_1 \ibeatsi \ar_0$ only when $\ar_1$ att $\ar_0$ alone (among those planned attacks of $\ar_0$), but $\ar_1$ need not necessarily be at the end of $\hist$.
+Thus, ${\ibeatsi}$ is a theoretical claim (that other arguments do not matter and that $\ar_1$ is indeed responsible for the change of mind), and $\ar_1 \ibeatsi \ar_0 ⇒ \ar_1 \gbeats \ar_0$.
+
+	Also, a coalition can attack $\ar_0$.
+Required because could have coal together attacks $\ar_0$ but individual arguments do not.
+Thus, I am interested in minimal coalitions that attack.
+For those, the theory must be able to answer with the sum of its replies (in which order?).
+	Define $\set{\ar_1, \ar'_1} \ibeatsi \ar_0$.
+Requires that each argument of the coalition be among the planned attackers; and that sub-coalitions do not attack.
+This requires a specific answer from the theory, namely, $\ar_0 + \ar_2 + \ar'_2$.
+
+	Define that $\ar_0$ strongly defends $\phi$ iff defense works when using no planned attack, and that $\ar_0 + \ar_2$ works when using only $\ar_1$ and if $\ar_1 \ibeatsi \ar_0$, and that $\ar_0 + \ar_2 + \ar'_2$ works when using both $\ar_1$ and $\ar'_1$ and this is a minimal planned attacking coalition.
+
+	Now, a falsification instance is $\hist$ containing $\ar_1$ and $\ar'_1$, two planned attacks, such that $\ar_2$ alone sometimes fails, $\ar'_2$ alone sometimes fails, and the addition sometimes fails: this proves the theory wrong in all cases, one argument alone attacking or both together being required.
+
+	A coalition could have a synergic effect: theory can reply individually, but fail its collective reply.
+However, that should not deserve explicit consideration: if individual replies work, and individual argument attacks, then some decisive argument exists.
+\end{remark}
+
+I want that s1 attacks-i s0 only when it’s because of s1 (according to the theory).
+Otherwise, the theory is forced to answer s1, an irrelevant argument.
+Thus, s1 attacks-e s0 requires that no s1' (planned attack against s0) is used.
+
+Also, everything must be falsifications except when it’s because of s1 i-attacking s0 (in which case the theory commits to answer).
+Thus, if two planned attacks are used, this is a falsification instance?
+No, because the theory commits to answer each one separately.
+Thus, if two planned attacks are used AND individual ones do not i-attack, then it is a falsification instance.
+Also, if (s1, s0, s0) leads to not phi, and not (s0, s1, s0), then this is a falsification instance.
+
+Convincingness must happen exactly when there is no falsification instance.
+Thus, ar i-defends phi when all dangerous histories are answered to by ar and when two planned attacks i-attack, some individual one i-attacks and when (s1, s0, s0) leads to not phi, then (s0, s1, s0) leads to not phi.
+
+Hence, the dangerous histories are those such that no reordering lead to $\set{\ar_1, \ar_0} = \histend$ for some $\ar_1$ that is a planned, effective attack.
+(involve no planned-attack or multiple irreducible planned attacks or an attack that happens only with a strange ordering).
+Well, that’s not great: to know whether an instance falsifies, we’d need to ensure, for each reordering of planned attacks, that they are non effective attacks, which is basically impossible.
+NO suffices to exhibit some history hist' with ar1, ar0 at end and leading to phi.
+
+Thus, falsification: hist, ar1=> hist', ar1' => hist'', where hist uses ar1 and ar1' (which are all the planned attacks in hist) and hist' ends with ar1, ar0, hist => notphi, hist' => phi, and so on.
+
+%Rather keep falsification instances simple, and enlarge the situations that the theory commits to answer.
+If some history combine ar1 and ar1' and lead to not phi, the theory must answer either ar1 or ar1' (it can choose => if ar1, ar0 in histend lead to not phi, it must answer ar1; if ar1' etc.; and if none, then it has lost).
+Thus falsification happens when both ar1 and ar1' are used and some some hist, ar1 does not attack ar0 and for some hist, ar1' does not attack ar0.
+This can be checked.
+And about (s1, s0, s0) (with s1 not planned): this is a falsification instance.
+Define it as: no planned attack is used AND s1 in hist AND s0 in histend.
+
+\begin{theorem}
+	A normatively adequate and convincing empirical theory is valid.
+\end{theorem}
+\begin{proof}
+	\commentOC{This might be false.
+Consider ${\gbeats} = \set{(\ar_1, \ar_0)}, {\dbeats} = \set{(\ar_2, \ar_1)}, (\ar_1, \ar_0, \ar'_1) \ileadstoi ¬\phi$.
+There is no decisive argument in $\gargs[i, \phi]$ as $\ar'_1 \ibeatsi \ar_0$, but no falsification instance as $\hist = (\ar_1, \ar_0, \ar'_1)$ includes $\ar_1$.
+In such a situation, $\ar_1$ should be considered as attacking $\ar_0$, as (from the model pov) it is $\ar_1$ which makes $i$ fail to adopt $\phi$.}
+
+	For all $i \in I, \phi \in \gPhi$, suffices to show that for some $\ar \in \gargs[i, \phi]$, $\ar \ileadstosti \phi$.
+
+	Consider any $\ar_0 \gleadsto \phi$.
+	By definition of $\dip$, $\forall k \in \N^*: (\dip)^k(\ar_0) \subseteq \dfp^k(\ar_0)$.
+	By definition of an empirical theory, $\exists k \in \N^* \suchthat \dfp^k(\ar_0) = \emptyset$. 
+	Therefore, $\exists k \in \N^* \suchthat (\dip)^k(\ar_0) = \emptyset$. 
+	Define $l = \min \set{k \in \N^* \suchthat (\dip)^k(\ar_0) = \emptyset}$.
+
+	Consider any $\ar \in (\dip)^{l-1}(\ar_0)$, and let us show that $\ar \ileadstosti \phi$.
+
+	If $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatsi \ar$, then $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar} \subseteq \histend \land \hist \nileadstosti \phi$, and a falsification instance $(i, \phi, \hist)$ is found, which contradicts convincingness.
+\commentOC{Unless $\hist$ contains some planned attack!}
+	Therefore, no $\ar_1 \ibeatsi \ar$.
+
+	Because $\ar \in \gargs[i, \phi]$, $\ar$ $i$-defends $\phi$.
+Furthermore, ${\gbeatsinv}(\ar) = \emptyset$, because by definition of an empirical theory, if $\ar_1 \gbeats \ar$, then $\ar_2 \dbeats \ar_1$, which contradicts $\dip$ NO!
 \end{proof}
@@
 
-Given $\phi \in {\gleadsto}(\allargs)$, define $\gargs[i, \phi, 0] \subseteq \allargs$ as $\gargs[i, \phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in 2\N$, define $\gargs[i, \phi, k + 2] = \gargs[i, \phi, k] + [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[i, \phi, k], \ar  \in [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k])}$.
-Define $\gargs[i, \phi] = \bigcup_{k \in 2\N} \gargs[i, \phi, k]$, and $\gargs = \cup_{i \in I, \phi \in {\gleadsto}(\allargs)} \gargs[i, \phi]$.
+Given $\phi \in \gPhi$, define $\gargs[i, \phi, 0] \subseteq \allargs$ as $\gargs[i, \phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in 2\N$, define $\gargs[i, \phi, k + 2] = \gargs[i, \phi, k] + [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[i, \phi, k], \ar  \in [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k])}$.
+Define $\gargs[i, \phi] = \bigcup_{k \in 2\N} \gargs[i, \phi, k]$, and $\gargs = \cup_{i \in I, \phi \in \gPhi} \gargs[i, \phi]$.
 
@@
 \subsection{Validity}
-\begin{definition}[Validity]
-	An empirical theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
-\end{definition}
-
 \subsection{Single-try empirical models}
@@
 \begin{definition}[Conv.\ SA]
-	$\forall i \in I, \phi \in {\gleadsto}(\allargs), k \in 2\N, \ar \in \gargs[i, \phi, k]: \ar$ $i$-defends $\phi$ ignoring ${\gbeats}(\gargs[i, \phi, k + 2])$.
+	$\forall i \in I, \phi \in \gPhi, k \in 2\N, \ar \in \gargs[i, \phi, k]: \ar$ $i$-defends $\phi$ ignoring ${\gbeats}(\gargs[i, \phi, k + 2])$.
 \end{definition}
@@
 \begin{proof}
-	Consider $i \in I$ and $\phi \in {\gleadsto}(\allargs)$.
+	Consider $i \in I$ and $\phi \in \gPhi$.
 
@@
 
-Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \nileadstost \phi$.
+Given $\phi \in \gPhi$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \nileadstost \phi$.
 
@@
 \begin{definition}[Answerability]
-	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \nileadstost \phi ⇒ [\exists \ar_1' \in {\gbeatsinv}(\ar_0)]$.
+	$\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \nileadstost \phi ⇒ [\exists \ar_1' \in {\gbeatsinv}(\ar_0)]$.
 \end{definition}
@@
 \begin{definition}[Operational validity]
-	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeats \ar_0 \land (\ar_1, \ar_0) \nileadstost \phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
+	$\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeats \ar_0 \land (\ar_1, \ar_0) \nileadstost \phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
 \end{definition}
@@
 \begin{proof}
-	Lemma: given $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$, if $\ar[k] \nileadstost \phi$, then: $\exists \ar[k + 1] \in \gargs[\phi] \suchthat \card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
-	To prove the lemma, let us pick any $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$. 
+	Lemma: given $\phi \in \gPhi$ and $\ar[k] \in \gargs[\phi]$, if $\ar[k] \nileadstost \phi$, then: $\exists \ar[k + 1] \in \gargs[\phi] \suchthat \card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
+	To prove the lemma, let us pick any $\phi \in \gPhi$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$. 
 	We know that $\exists \ar_1 \in \allargs \suchthat (\ar_1, \ar[k]) \nileadstost \phi$. 
@@
 
-	To prove the theorem, given $\phi \in {\gleadsto}(\allargs)$, we need to exhibit an argument $\ar$ such that $\ar \ileadstost \phi$.
+	To prove the theorem, given $\phi \in \gPhi$, we need to exhibit an argument $\ar$ such that $\ar \ileadstost \phi$.
 	Define a finite sequence $(\ar[0], \ar[1], \ar[2], …)$, starting from $\ar[0] = {\gleadstoinv}(\phi)$, using the lemma, until the condition $\ar[k] \nileadstost \phi$ no longer holds.
@@
 by Strong op.
-val.: $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
+val.: $\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
 
@@
 \begin{definition}[Convincingness]
-	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
+	$\forall i \in I, \phi \in \gPhi, \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
 \end{definition}
@@
 \begin{proof}
-	Consider $i \in I$ and $\phi \in {\gleadsto}(\allargs)$. 
+	Consider $i \in I$ and $\phi \in \gPhi$. 
 	By hypothesis, $\exists k$ such that some $\ar_k \in \args_k$ defends $\phi$ under protection of $\emptyset$. Therefore, $\ar_k \ileadstosts \phi$. Using \cref{ax:norm}, validity follows.

### 2020-07-02 simple.tex
Trying def attack-exists using coalitions (but complex)

@@
 \subsection{Falsifiability}
-Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$, and say that $\ar_1$ is an effective attack against $\ar_0$ (from $i$’s perspective).
+Given $\hist \in \allhist$, $\hist(\intvl{1, l(\hist)})$, where $l(\hist) \in \N$ is the length of the sequence $\hist$, denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
+Abusing notation, given $\args \subseteq \allargs$, I write $\args \cap \hist$ to designate $\args \cap \hist(\intvl{1, l(\hist)})$, therefore using simply $\hist$ in that expression to denote the \emph{range} of $\hist$.
+
+Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs, \args \subseteq \allargs$, with $\args$ finite, define recursively, on the basis of the cardinality of $\args$: $\emptyset \nibeatsi \ar_0$, and $\args \ibeatsi \ar_0$ iff $[\args \subseteq {\gbeatsinv}(\ar_0)] \land [\exists \hist \in \allhist \suchthat (\hist \cap {\gbeatsinv}(\ar_0) \subseteq \args \land \ar_0 \in \histend)] \land [\forall \args' \subset \args: \args' \nibeatsi \ar_0]$.
+
+TODO claim that if $\hist \nileadstoi \phi$, with $\ar_1, \ar'_1 \in \hist$ and $\ar_0 \in \histend$, then $\ar_2$ is among the defensors, or $\ar'_2$ is.
 
@@
 Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$, where $(\dip)^0$ is the identity function over $\allargs$.
-
-Given $\hist \in \allhist$, $\hist(\intvl{1, l(\hist)})$, where $l(\hist) \in \N$ is the length of the sequence $\hist$, denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
-Abusing notation, given $\args_1 \subseteq \allargs$, I write $\args_1 \cap \hist$ to designate $\args_1 \cap \hist(\intvl{1, l(\hist)})$, therefore using simply $\hist$ in that expression to denote the \emph{range} of $\hist$.
 

### 2020-07-06 simple.tex
Some solutions to missing case of defender

@@
 
-Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs, \args \subseteq \allargs$, with $\args$ finite, define recursively, on the basis of the cardinality of $\args$: $\emptyset \nibeatsi \ar_0$, and $\args \ibeatsi \ar_0$ iff $[\args \subseteq {\gbeatsinv}(\ar_0)] \land [\exists \hist \in \allhist \suchthat (\hist \cap {\gbeatsinv}(\ar_0) \subseteq \args \land \ar_0 \in \histend)] \land [\forall \args' \subset \args: \args' \nibeatsi \ar_0]$.
-
-TODO claim that if $\hist \nileadstoi \phi$, with $\ar_1, \ar'_1 \in \hist$ and $\ar_0 \in \histend$, then $\ar_2$ is among the defensors, or $\ar'_2$ is.
-
-Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [{\dbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatsiinv})](\ar)$.
+Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat {\gbeatsinv}(\ar_0) \cap \hist = \set{\ar_1} \land \ar_0 \in \histend \land \hist \nileadstoi \phi$.
+
+Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [{\dbeatsinv} \circ {\ibeatsiinv}](\ar)$.
 Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
@@
 $\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset\right]: \hist \ileadstosti \phi$.
+$\ar_0$ recursively $i$-defends $\phi$ iff $\forall \ar \in \cup_{k \in \N}(\dip)^k(\ar_0)$: $\ar$ $i$-defends $\phi$.
 
@@
 
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.
+A \emph{convincingness falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.
 
 \begin{theorem}
-	An empirical theory is convincing iff it has no falsification instances.
+	An empirical theory is convincing iff it has no convincingness falsification instances.
 \end{theorem}
 \begin{proof}
-	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
+	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a convincingness falsification instance.
 \end{proof}
+
+\begin{definition}[Unnecessary coalitions]
+	$\forall i \in I, \phi \in \gPhi, \hist \in \allhist, \ar_0 \in \gargs[i, \phi], \set{\ar_1, \ar'_1} \subseteq {\gbeatsinv}(\ar_0) \cap \hist, \ar_0 \in \histend, \hist \nileadstoi \phi$: $\exists \ar_2 \in {\dbeatsinv}(\set{\ar_1, \ar'_1})$ such that $\ar_2$ recursively $i$-defends $\phi$.
+\end{definition}
 
@@
 
+Possible easy approach: If $\args \ibeatsi \ar_0$, then both $\ar_1 \ibeatsi \ar_0$ and $\ar'_1$.
+
+Sophistication: when $\args = \set{\ar_1, \ar'_1}$ attack $\ar_0$, it is too demanding to ask that both $\ar_2$ and $\ar'_2$ defend $\phi$.
+Perhaps $\ar_2$ does but $\ar'_2$ fails (and $\ar'_2 + \ar_2$ as well) because it confuses $i$, which finds $\ar'_1$ irrelevant or hard to understand.
+To relax the claim, could define that $\ar_1$ seems ineffective against $\ar_0$ iff $\exists \hist \suchthat \set{\ar_1, \ar_0} = \histend \land \hist \ileadstosti \phi$.
+If so, and if $\args \ibeatsi \ar_0$, then $\ar'_2$ must be in the defensors.
+This supplementary condition (about ineffectivity) is there to show that $\ar'_1$ plays at least some role in the attack, because the theory must not claim that $\ar'_2$ defends $\phi$ when $\ar'_1$ is not really an attacker, which it would seem to be if $\args \ibeatsi \ar_0$ because of $\ar_1$.
+More generally, $\args$ seems ineffective against $\ar_0$ iff $\exists \hist = (…, \args, \ar_0) \suchthat \hist \ileadstosti \phi$.
+If so, and if $\args \cup \set{\ar_1} \ibeatsi \ar_0$, then $\ar_2$ must be in the defensors.
+
+TODO implement the sophisticated approach with: $\args \cup \ar_1 att \ar_0 \land \args$ seems uneff implies $\ar_1 \ibeatsi \ar_0$.
+(Here att stands for $\ibeatsi$ for coalitions.) Check that it works for coalitions of more than two.
+
 \begin{remark}[TODO]
+	I could make that claim (unnecessary coalitions) stronger by mandating that if $\ar_0$ fails, that must be because some $\ar_1$ always attacks $\ar_0$, in the sense that when $\ar_1$ and $\ar_0$ are in $\histend$, then $¬\phi$.
+Such a claim largely eases falsification.
+But this is too demanding: $\ar_1$ may be a not-so-great argument that does sometimes contradict $\ar_0$ but not systematically, and that $\ar_2$ can reply to convincingly.
+
 	$\ar_1 \ibeatsi \ar_0$ only when $\ar_1$ att $\ar_0$ alone (among those planned attacks of $\ar_0$), but $\ar_1$ need not necessarily be at the end of $\hist$.
@@
 
-	For all $i \in I, \phi \in \gPhi$, suffices to show that for some $\ar \in \gargs[i, \phi]$, $\ar \ileadstosti \phi$.
-
-	Consider any $\ar_0 \gleadsto \phi$.
-	By definition of $\dip$, $\forall k \in \N^*: (\dip)^k(\ar_0) \subseteq \dfp^k(\ar_0)$.
-	By definition of an empirical theory, $\exists k \in \N^* \suchthat \dfp^k(\ar_0) = \emptyset$. 
-	Therefore, $\exists k \in \N^* \suchthat (\dip)^k(\ar_0) = \emptyset$. 
-	Define $l = \min \set{k \in \N^* \suchthat (\dip)^k(\ar_0) = \emptyset}$.
-
-	Consider any $\ar \in (\dip)^{l-1}(\ar_0)$, and let us show that $\ar \ileadstosti \phi$.
-
-	If $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatsi \ar$, then $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar} \subseteq \histend \land \hist \nileadstosti \phi$, and a falsification instance $(i, \phi, \hist)$ is found, which contradicts convincingness.
-\commentOC{Unless $\hist$ contains some planned attack!}
-	Therefore, no $\ar_1 \ibeatsi \ar$.
-
-	Because $\ar \in \gargs[i, \phi]$, $\ar$ $i$-defends $\phi$.
-Furthermore, ${\gbeatsinv}(\ar) = \emptyset$, because by definition of an empirical theory, if $\ar_1 \gbeats \ar$, then $\ar_2 \dbeats \ar_1$, which contradicts $\dip$ NO!
+	For all $i \in I, \phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstosti \phi$. (Actually, $\ar \in \dfp^k(\ar_0)$ for some $k$.)
+
+	Lemma: if $\ar_0$ recursively $i$-defends $\phi$, then either $\ar_0$ is decisive, or $\ard_2 \dbeats \ar_1 \gbeats \ar_0$ with $\ar_2 = \ar_0 + \ard_2$ recursively $i$-defending $\phi$ and $\ar_2 \in \dfp(\ar_0)$.
+	If $\ar_0$ is not decisive, and because $\ar_0$ defends, some $\hist$ ending with $\ar_0$ includes some $\ar_1 \gbeats \ar_0$.
+If this is the only one, then $\ar_1 \ibeatsi \ar_0$, and $\ar_2$ recursively defends.
+If it is not the only one, use the no coalition property.
 \end{proof}

### 2020-07-11 simple.tex
Empirical theory should be correct now

--- 2020-07-02 simple.tex
@@
 with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
-${\gbeats} \subseteq \allargs × \allargs$,
-${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range equals ${\gbeatsinv}(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: ${\dbeatsinv}(\ar_1)$ is a singleton).
-Define $\df \subseteq \allargs × \alldargs$ as $\df = {\dbeatsinv} \circ {\gbeatsinv}$. 
+${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
+${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range equals $\gbeatsinv(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton).
+Define $\df \subseteq \allargs × \alldargs$ as $\df = \dbeatsinv \circ \gbeatsinv$. 
 The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
@@
 An empirical theory must satisfy
-$\forall \ar \in \gPhi: \exists k \in \N^* \suchthat \dfp^k(\ar) = \emptyset$.
+$\exists k \in \N \suchthat \dfp^k(\gleadstoinv(\allprops)) = \emptyset$.
 
@@
 
-Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs, \args \subseteq \allargs$, with $\args$ finite, define recursively, on the basis of the cardinality of $\args$: $\emptyset \nibeatsi \ar_0$, and $\args \ibeatsi \ar_0$ iff $[\args \subseteq {\gbeatsinv}(\ar_0)] \land [\exists \hist \in \allhist \suchthat (\hist \cap {\gbeatsinv}(\ar_0) \subseteq \args \land \ar_0 \in \histend)] \land [\forall \args' \subset \args: \args' \nibeatsi \ar_0]$.
-
-TODO claim that if $\hist \nileadstoi \phi$, with $\ar_1, \ar'_1 \in \hist$ and $\ar_0 \in \histend$, then $\ar_2$ is among the defensors, or $\ar'_2$ is.
-
-Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [{\dbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatsiinv})](\ar)$.
+Given $\phi \in \Phi$, $\args \subseteq \allargs$ and $\ar_0 \in \allargs$, say that $\args$ seems $i$-ineffective against $\ar_0$ for $\phi$, $\args \bowtie^{i, \phi} \ar_0$, iff $\exists \hist \in \allhist \suchthat \hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0 \land \hist \ileadstosti \phi$, that is, when some $\hist$ ends with $\args$ followed by $\ar_0$ and leads to $\phi$.
+Note that for all $\ar_0 \in \allargs$ such that $\exists \hist \in \allhist \suchthat [\hist(l(\hist)) = \ar_0 \land \hist \ileadstosti \phi]$: $\emptyset \sinef \ar_0$.
+
+Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land \ar_0 \in \histend \land \hist \nileadstoi \phi \land (\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0$.
+
+Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [\dbeatsinv \circ {\ibeatsiinv}](\ar)$.
 Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
@@
 
-$\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset\right]: \hist \ileadstosti \phi$.
+$\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset\right]: \hist \ileadstosti \phi$. 
+%$\ar_0$ recursively $i$-defends $\phi$ iff $\forall \ar \in \cup_{k \in \N}(\dip)^k(\ar_0)$: $\ar$ $i$-defends $\phi$.
 
@@
 
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.
+A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.
 
@@
 \begin{proof}
-	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
+	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
 \end{proof}
@@
 \end{definition}
-
-\begin{remark}[TODO]
-	$\ar_1 \ibeatsi \ar_0$ only when $\ar_1$ att $\ar_0$ alone (among those planned attacks of $\ar_0$), but $\ar_1$ need not necessarily be at the end of $\hist$.
-Thus, ${\ibeatsi}$ is a theoretical claim (that other arguments do not matter and that $\ar_1$ is indeed responsible for the change of mind), and $\ar_1 \ibeatsi \ar_0 ⇒ \ar_1 \gbeats \ar_0$.
-
-	Also, a coalition can attack $\ar_0$.
-Required because could have coal together attacks $\ar_0$ but individual arguments do not.
-Thus, I am interested in minimal coalitions that attack.
-For those, the theory must be able to answer with the sum of its replies (in which order?).
-	Define $\set{\ar_1, \ar'_1} \ibeatsi \ar_0$.
-Requires that each argument of the coalition be among the planned attackers; and that sub-coalitions do not attack.
-This requires a specific answer from the theory, namely, $\ar_0 + \ar_2 + \ar'_2$.
-
-	Define that $\ar_0$ strongly defends $\phi$ iff defense works when using no planned attack, and that $\ar_0 + \ar_2$ works when using only $\ar_1$ and if $\ar_1 \ibeatsi \ar_0$, and that $\ar_0 + \ar_2 + \ar'_2$ works when using both $\ar_1$ and $\ar'_1$ and this is a minimal planned attacking coalition.
-
-	Now, a falsification instance is $\hist$ containing $\ar_1$ and $\ar'_1$, two planned attacks, such that $\ar_2$ alone sometimes fails, $\ar'_2$ alone sometimes fails, and the addition sometimes fails: this proves the theory wrong in all cases, one argument alone attacking or both together being required.
-
-	A coalition could have a synergic effect: theory can reply individually, but fail its collective reply.
-However, that should not deserve explicit consideration: if individual replies work, and individual argument attacks, then some decisive argument exists.
-\end{remark}
-
-I want that s1 attacks-i s0 only when it’s because of s1 (according to the theory).
-Otherwise, the theory is forced to answer s1, an irrelevant argument.
-Thus, s1 attacks-e s0 requires that no s1' (planned attack against s0) is used.
-
-Also, everything must be falsifications except when it’s because of s1 i-attacking s0 (in which case the theory commits to answer).
-Thus, if two planned attacks are used, this is a falsification instance?
-No, because the theory commits to answer each one separately.
-Thus, if two planned attacks are used AND individual ones do not i-attack, then it is a falsification instance.
-Also, if (s1, s0, s0) leads to not phi, and not (s0, s1, s0), then this is a falsification instance.
-
-Convincingness must happen exactly when there is no falsification instance.
-Thus, ar i-defends phi when all dangerous histories are answered to by ar and when two planned attacks i-attack, some individual one i-attacks and when (s1, s0, s0) leads to not phi, then (s0, s1, s0) leads to not phi.
-
-Hence, the dangerous histories are those such that no reordering lead to $\set{\ar_1, \ar_0} = \histend$ for some $\ar_1$ that is a planned, effective attack.
-(involve no planned-attack or multiple irreducible planned attacks or an attack that happens only with a strange ordering).
-Well, that’s not great: to know whether an instance falsifies, we’d need to ensure, for each reordering of planned attacks, that they are non effective attacks, which is basically impossible.
-NO suffices to exhibit some history hist' with ar1, ar0 at end and leading to phi.
-
-Thus, falsification: hist, ar1=> hist', ar1' => hist'', where hist uses ar1 and ar1' (which are all the planned attacks in hist) and hist' ends with ar1, ar0, hist => notphi, hist' => phi, and so on.
-
-%Rather keep falsification instances simple, and enlarge the situations that the theory commits to answer.
-If some history combine ar1 and ar1' and lead to not phi, the theory must answer either ar1 or ar1' (it can choose => if ar1, ar0 in histend lead to not phi, it must answer ar1; if ar1' etc.; and if none, then it has lost).
-Thus falsification happens when both ar1 and ar1' are used and some some hist, ar1 does not attack ar0 and for some hist, ar1' does not attack ar0.
-This can be checked.
-And about (s1, s0, s0) (with s1 not planned): this is a falsification instance.
-Define it as: no planned attack is used AND s1 in hist AND s0 in histend.
 
@@
 \begin{proof}
-	\commentOC{This might be false.
-Consider ${\gbeats} = \set{(\ar_1, \ar_0)}, {\dbeats} = \set{(\ar_2, \ar_1)}, (\ar_1, \ar_0, \ar'_1) \ileadstoi ¬\phi$.
-There is no decisive argument in $\gargs[i, \phi]$ as $\ar'_1 \ibeatsi \ar_0$, but no falsification instance as $\hist = (\ar_1, \ar_0, \ar'_1)$ includes $\ar_1$.
-In such a situation, $\ar_1$ should be considered as attacking $\ar_0$, as (from the model pov) it is $\ar_1$ which makes $i$ fail to adopt $\phi$.}
-
-	For all $i \in I, \phi \in \gPhi$, suffices to show that for some $\ar \in \gargs[i, \phi]$, $\ar \ileadstosti \phi$.
-
-	Consider any $\ar_0 \gleadsto \phi$.
-	By definition of $\dip$, $\forall k \in \N^*: (\dip)^k(\ar_0) \subseteq \dfp^k(\ar_0)$.
-	By definition of an empirical theory, $\exists k \in \N^* \suchthat \dfp^k(\ar_0) = \emptyset$. 
-	Therefore, $\exists k \in \N^* \suchthat (\dip)^k(\ar_0) = \emptyset$. 
-	Define $l = \min \set{k \in \N^* \suchthat (\dip)^k(\ar_0) = \emptyset}$.
-
-	Consider any $\ar \in (\dip)^{l-1}(\ar_0)$, and let us show that $\ar \ileadstosti \phi$.
-
-	If $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatsi \ar$, then $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar} \subseteq \histend \land \hist \nileadstosti \phi$, and a falsification instance $(i, \phi, \hist)$ is found, which contradicts convincingness.
-\commentOC{Unless $\hist$ contains some planned attack!}
-	Therefore, no $\ar_1 \ibeatsi \ar$.
-
-	Because $\ar \in \gargs[i, \phi]$, $\ar$ $i$-defends $\phi$.
-Furthermore, ${\gbeatsinv}(\ar) = \emptyset$, because by definition of an empirical theory, if $\ar_1 \gbeats \ar$, then $\ar_2 \dbeats \ar_1$, which contradicts $\dip$ NO!
+	\NewDocumentCommand{\allhistsznp}{}{\mathscr{S}^{*, \ar_0}_{\not⇝ \phi}}
+	\NewDocumentCommand{\allhistred}{}{\mathscr{S}^{*, \ar_0, \mathit{red}}_{\not⇝ \phi}}
+	\NewDocumentCommand{\allhistnonred}{}{\mathscr{S}^{*, \ar_0, \mathit{irred}}_{\not⇝ \phi}}
+
+	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstosti \phi$, and normative adequacy brings the conclusion.
+
+	Given any $\ar_0 \in \allargs$, define $\args^{\hist} = \gbeatsinv(\ar_0) \cap \hist$ and $\allhistsznp = \set{\hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstosti \phi}$.
+Given $\hist \in \allhistsznp$, say that $\hist$ is \emph{reducible} iff $\hist \in \allhistred$, defined as $\allhistred = \set{\hist \in \allhistsznp \suchthat \forall \ar_1 \in \args^{\hist}: \args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0}$; define accordingly $\allhistnonred = \allhistsznp \setminus \allhistred = \set{\hist \in \allhistsznp \suchthat \exists \ar_1 \in \args^{\hist} \suchthat \args^{\hist} \setminus \set{\ar_1} \sinef \ar_0}$.
+
+	Lemma: given any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$, if $\allhistsznp ≠ \emptyset$, $\hist \in \allhistred ⇒ \exists \histp \in \allhistsznp \suchthat \emptyset ≠ \args^{\histp} \subset \args^{\hist}$.
+To see this, pick as $\histp$ any sequence consisting of the arguments contained in $\args^{\hist} \setminus \set{\ar_1}$, followed by $\ar_0$.
+	First, $\histp \in \allhistsznp$, because as $\hist \in \allhistred$, $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$, thus, $\histp \nileadstosti \phi$. 
+	Second, $\args^{\histp} = \args^{\hist} \setminus \set{\ar_1}$, because $\args^{\hist} \setminus \set{\ar_1} \subseteq \args^{\histp} = \left(\gbeatsinv(\ar_0) \cap \histp\right) \subseteq \args^{\hist} \setminus \set{\ar_1}$.
+	Finally, $\args^{\histp} ≠ \emptyset$ follows from two facts: that $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$ (see “First” here above) and that $\emptyset \sinef \ar_0$, which is implied by $\ar_0$ $i$-defends $\phi$.
+
+	We conclude from this lemma that given any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$, if $\exists \hist \in \allhistsznp \suchthat \args^{\hist} ≠ \emptyset$, then $\exists \histp \in \allhistnonred$.
+To see this, given $\hist \in \allhistsznp \suchthat \args^{\hist} ≠ \emptyset$, define a finite sequence of sequences of arguments, starting with $\hist_0 = \hist$, then, for $k \in \N$, if $\hist_k \in \allhistred$, define $\hist_{k + 1} \in \allhistsznp$ by applying the lemma, thus with $\emptyset ≠ \args^{\hist_{k + 1}} \subset \args^{\hist_k}$.
+Because $\hist_0$ is finite (being an element of $\allhist$), $\args^{\hist_0}$ is finite, thus this process ends with some $\hist_k \in \allhistnonred$.
+
+	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstosti \phi ⇒ \exists \ar_1 \in \allargs, \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1 \ibeatsi \ar_0 \land \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2 \in \dip(\ar_0)$.
+	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstosti \phi$. 
+	By definition, $\ar_0 \nileadstosti \phi$ means that $\exists \hist \in \allhistsznp$.
+	Because $\ar_0$ $i$-defends $\phi$, $\args^{\hist} ≠ \emptyset$. 
+	From the preceding conclusion, we can pick some $\histp \in \allhistnonred$.
+	Thus, $\exists \ar_1 \in \args^{\histp} \suchthat \args^{\histp} \setminus \set{\ar_1} \sinef \ar_0$.
+	By definition, this means that $\ar_1 \ibeatsi \ar_0$ and, as $\ar_1 \in \args^{\histp} = \gbeatsinv(\ar_0) \cap \histp$, $\ar_1 \gbeats \ar_0$. 
+	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1$.
+Defining $\ar_2 = \ar_0 + \ard_2$, by definition of $\dip$, $\ar_2 \in \dip(\ar_0)$.
+
+	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs[i, \phi] \land \ar_0 \nileadstosti \phi] ⇒ \exists \ar_2 \in \gargs[i, \phi] \cap \dfp(\ar_0)$.
+That is because $\ar_0 \in \gargs[i, \phi] ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering $\ard_2$ and $\ar_2$ as defined in the lemma, $\ar_2 \in \gargs[i, \phi]$ by definition of $\gargs[i, \phi]$ and $\ard_2 \in \df(\ar_0)$ by definition of $\df$.
+
+	To prove the theorem, build a finite sequence of arguments in $\gargs[i, \phi]$, starting with any $\ar_0 \in \ileadstoinv(\phi)$.
+Observe that $\ar_0 \in \gargs[i, \phi]$.
+Given $k \in 2\N$, if $\ar_k \nileadstosti \phi$, define $\ar_{k + 2}$ using the deduction following the last lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$.
+	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstosti \phi$.
 \end{proof}
+
+\subsection{Effectively comparing models}
+\subsection{Preference theories}
+Given a set of alternatives $\allalts$. Define $\allprops = \prop_{ab}$.
 
@@
 \section{Decision situation}
+\newcommand{\alltopic}{T^*}
+
 The object of study in a given decision situation is the deliberated preferences of a given individual $i$. 

### 2020-07-16 simple.tex
Cleaned up old stuff; started (unsatisfactory) pref theory

@@
 with ${\ileadstoi} \subseteq \allhist × \Phi$, 
-where $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\text{possible}, \text{sure}}$.
+where $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\mathit{poss}, \mathit{sure}}$.
 (Throughout the article, $\N$ includes zero, and note that $\intvl{1, 0} = \emptyset$.)
@@
 The symbol $¬$ is a negation operator on $\allprops$, such that $\forall \prop \in \allprops: ¬¬\prop = \prop$.
-This article also uses this symbol as a negation operator on $\Phi$, defined as follows, $\forall \prop \in \allprops$: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
+This article also uses this symbol as a negation operator on $\Phi$, defined as follows, $\forall \prop \in \allprops$: $¬\propposs = (¬\prop, \mathit{sure})$ and $¬\propsure = (¬\prop, \mathit{poss})$.
 Observe that $¬¬\phi = \phi$.
@@
 \subsection{Effectively comparing models}
-\subsection{Preference theories}
-Given a set of alternatives $\allalts$. Define $\allprops = \prop_{ab}$.
-
-\subsection{Vrac from here}
-1. Checkpath: this is completely general.
-2. Only using model that counter-argues: requires a sort of path independence. (arguments can be condensed: s5, s4, s1 => s1big)
-
-I also write that $\hist \ibeatse[!\phi] \ar_0$ iff $\exists \ar_1 \in \allargs \suchthat (\hist \text{ ends with } \set{\ar_1, \ar_0}) \land (\ar_1 \ibeatse[!\phi] \ar_0)$.
-
-An empirical theory is defined only given some normative theory.
-In the following, any reference to an empirical theory should always be understood as an empirical theory for some (sometimes implicitly defined) normative theory.
-
-As above,  $\gleadsto$ will be used instead of $\gleadsto[q(i)]$ when it creates no ambiguity, with the understanding that this symbol result of applying a function of $q(i)$; and the binding $\forall i \in I$ will generally be omitted.
-
-Given $\phi \in \gPhi$, define $\gargs[i, \phi, 0] \subseteq \allargs$ as $\gargs[i, \phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in 2\N$, define $\gargs[i, \phi, k + 2] = \gargs[i, \phi, k] + [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[i, \phi, k], \ar  \in [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k])}$.
-Define $\gargs[i, \phi] = \bigcup_{k \in 2\N} \gargs[i, \phi, k]$, and $\gargs = \cup_{i \in I, \phi \in \gPhi} \gargs[i, \phi]$.
-
-Given $\ar \in \gargs$, let $c(\ar) = \bigcup \set{\args \subseteq \gargs \suchthat \ar = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar$.
-
-Given $\ar_2 \in \gargs, \ar_1 \in \allargs$, $\ar_2 \mbeats \ar_1$ has the semantic that $\gamma$ claims that $\ar_2$ trumps $\ar_1$ if necessary.
-Given $\ar_1 \in \allargs, \ar_0 \in \gargs$, $\ar_1 \mbeats \ar_0$ has the semantic that $\gamma$ claims that it knows how to resist an attack from $\ar_1$ coming in response to using $\ar_0$, if it does come.
-
-\subsection{Validity}
-\subsection{Single-try empirical models}
-NB these two conditions should be phrased as properties of a claim. A claim has bl iff for some $k$, …
-
-What we search for here are conditions of the form: $\forall i$.
-
-For now, assume that $\ar_1$ attacks a single argument, so that there is no problem with replying with $\ar_2$ independently of which argument $\ar_1$ attacks.
-
-\begin{definition}[Conv.\ SA]
-	$\forall i \in I, \phi \in \gPhi, k \in 2\N, \ar \in \gargs[i, \phi, k]: \ar$ $i$-defends $\phi$ ignoring ${\gbeats}(\gargs[i, \phi, k + 2])$.
-\end{definition}
-
-\begin{definition}[Length bounded a priori]
-	$\exists m \in \N^* \suchthat ({\gbeats})^m(\allargs) = \emptyset$.
-\end{definition}
-
-\begin{theorem}
-	If an empirical theory is Conv.\ SA and has a priori bounded length, and its normative theory satisfies \cref{ax:nocontr,ax:norm}, then it is valid.
-\end{theorem}
-\begin{proof}
-	Consider $i \in I$ and $\phi \in \gPhi$.
-
-	Lemma: $\forall \ar_0 \in \gargs[i, \phi], \ar_1 \in \allargs: \ar_1 \ibeatse \ar_0 ⇒ [\exists \ar_2, \ar_1' \in \allargs \suchthat \ar_2 \gbeats \ar_1' \gbeats \ar_0]$. 
-	Consider $\ar_0 \in \gargs[i, \phi], \ar_1 \in \allargs \suchthat \ar_1 \ibeatse \ar_0$.
-	Define $\args^1 = {\gbeats}(\gargs[i, \phi, k + 2])$.
-Thus, $\ar_0$ $i$-defends $\phi$ ignoring $\args^1$.
-Now, $\args^1 ≠ \emptyset$, because otherwise, by definition of $i$-defense, $\ar_0 \ileadstosts \phi$, which is incompatible with $\ar_1 \ibeatse \ar_0$, by \cref{eq:st-in-terms-of-e}.
-	Pick $\ar \in \args^1$ and observe that, by definition of $\args^1$, $\exists \ar_2 \in \gargs[i, \phi, k + 2] \suchthat \ar_2 \gbeats \ar$, and by definition of $\gargs[i, \phi, k + 2]$,  $\exists \ar_1' \suchthat \ar_2 \gbeats \ar_1' \gbeats \ar_0$.
-\commentOC{NO.
-I should be protected only from anticipated attacks.
-Currently, $\ar_1$ need not be anticipated (another $\ar_1'$ may be anticipated and then $\ar_2$ attacking both would suffice).
-Perhaps I need to define $\gargs[2]$ with only requiring that $\ar_1 \ibeatse \ar_0$, not $\ar_1 \ibeatse \ar_0$ and $\ar_1 \gbeats \ar_0$, because otherwise no requirements on attackers of attackers of $\ar_0$.
-I need to observe that if $\ar_1 \ibeatse \ar_0$, and $\ar_0$ defends $\phi$, then $\ar_1$ is ignored.
-Thus, it is anticipated (because I can ignore only those I anticipate).}
-
-	But $\ar_0$ i-def $\phi$, if not ignoring $\ar_1$, implies that $\forall \hist \in \allhist: (\hist, \ar_1, \ar_0) \ileadstosts \phi$. Thus, $\ar_1$ is ignored.
-
-	Thus, $\gargs[2] \subseteq ({\gbeatsinv})^2(\ar_0)$.
-	Thus, some $\gargs[k] = \emptyset$ (by bounded length).
-	Thus, some $\gargs[k] ≠ \emptyset$ that nobody attacks. This is our decisive argument.
-	Therefore, $\ar_k \ileadstosts \phi$. Using \cref{ax:norm}, this yields that $\phi \in \iPhi$, and validity follows from \cref{ax:nocontr}.
-\end{proof}
-
-\subsection{Conditions without history}
-To verify or falsify these conditions, whether $(\ar_1, \ar_0) \ileadstoe \phi$ must be observable, but one may suspect that once $i$ has seen some $\ar$, then no more $(\ar_1, \ar_0) \ileadstoe \phi$ but that this does not imply that this would hold without $\ar$ for $i$.
-The general falsifiable claim is not clear.
-
-Given $\phi \in \gPhi$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \nileadstost \phi$.
-
-The following condition mandates that if the arguments used by the theory are not decisive, it knows a reason.
-\begin{definition}[Answerability]
-	$\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \nileadstost \phi ⇒ [\exists \ar_1' \in {\gbeatsinv}(\ar_0)]$.
-\end{definition}
-
-\begin{definition}[Bounded length]
-	$\gargs$ must be finite.
-\end{definition}
-
-\begin{remark}
-	Bounded length does not imply finiteness of arguments used as counter-arguments by the model: model is able to counter infinitely many arguments with infinitely many counter-args, but needs to declare that an (unknown) finite subset of those will suffice to convince $i$.
-\end{remark}
-
-\begin{definition}[No repetition]
-	$\nexists \ar_0 \in \gargs[\phi], \ar_1 \in \allargs, \ar_2 \in c(\ar_0) \suchthat \ar_2 \gbeats \ar_1 \gbeats \ar_0$.
-\end{definition}
-
-\begin{definition}[Operational validity]
-	$\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeats \ar_0 \land (\ar_1, \ar_0) \nileadstost \phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
-\end{definition}
-
-$\ar_0 + \ar_2$ anticipates attacks from those attacking either, minus those attacked by any.
-(Actually any attacked may still attack the addition, but that’s because of some other not-yet-attacked, anticipated, attack.)
-
-\begin{remark}
-	I currently conceive these conditions in the following way.
-The model must anticipate in its initial arguments the counter-arguments that $i$ may have in mind.
-Thus, $\ar_1$ trumps $\ar_0$ is observed when $i$ has been given $\ar_1$.
-When the model answers with $\ar_2$, if $i$ is unconvinced (of $\ar_2 + \ar_0$ trumping $\ar_1$), the procedure stops (the model can’t argue that yes-but-maybe-$i$-has-$\ar_1'$-in-mind; in particular, it wouldn’t be feasible to interrogate $i$ if the arguments are given thanks to labeling in a supermarket).
-However, if $i$ is given $\ar_1'$, the model must be given a chance to play its counter-argument, and may not be falsified because $\ar_2 + \ar_0$ is not enough: once $i$ is given $\ar_1'$, it is no more claimed by the model that $\ar_2 + \ar_0$ suffices any longer.
-
-	Relatedly, Operational validity is (almost) void when $\ar_1$ trumps $\ar_0$ and $\ar_0 \gbeats \ar_1$ (and has already observed to be successful, thus $\ar_0$ trumps $\ar_1$): in that case, suffices to play $\ar_2 = \ar_0$ and define $\ar_0 + \ar_0 = \ar_0$, so $\ar_2 + \ar_0$ trumps $\ar_1$.
-
-	In summary: when $\ar_1$ trumps $\ar_0$, and the model has not already answered this argument using $\ar_0$ (thus $¬ \ar_0 \gbeats \ar_1$), Op.
-val.
-demands an answer.
-When $\ar_1$ trumps $\ar_0$, and the model has answered already using $\ar_0$, and we have checked that indeed $\ar_0$ trumps $\ar_1$, Answerability demands that the model can explain this instability by the fact that someone must have given another argument $\ar_1'$ to $i$ (and this is to be checked using means outside the formal model).
-\end{remark}
-
-I want an empirical theory to: 1) declare some $P \subseteq \Phi$ and it being valid; 2) prove its claims (otherwise, uncheckable and unfalsifiable and thus not empirical) by producing decisive arguments; 3) permit reuse… Focusing on valid theories is thus justified by the fact that if no valid theory for some $P$, then any theory will not be able to prove its claims (as there is no decisive argument).
-
-\subsection{Theorem}
-\begin{theorem}
-	If a theory is answerable, has bounded length, does not repeat, and is operationally valid, it is valid.
-\end{theorem}
-\begin{proof}
-	Lemma: given $\phi \in \gPhi$ and $\ar[k] \in \gargs[\phi]$, if $\ar[k] \nileadstost \phi$, then: $\exists \ar[k + 1] \in \gargs[\phi] \suchthat \card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
-	To prove the lemma, let us pick any $\phi \in \gPhi$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$. 
-	We know that $\exists \ar_1 \in \allargs \suchthat (\ar_1, \ar[k]) \nileadstost \phi$. 
-	Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeats \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$. 
-	Define $\ar[k + 1] = \ar[k] + \ar_2$. This is the element we look for.
-	First, $\ar[k + 1] \in \gargs[\phi]$ because $\ar[k + 1] \gbeats \ar_1' \ibeatse[!\phi] \ar[k]$.
-	Second, by No repetition, $\ar_2 \notin c(\ar[k])$,
-	thus, $\card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$ (observing that, by definition of $c$, for any $\ar, \ar'$: $c(\ar) \subseteq c(\ar + \ar')$).
-
-	To prove the theorem, given $\phi \in \gPhi$, we need to exhibit an argument $\ar$ such that $\ar \ileadstost \phi$.
-	Define a finite sequence $(\ar[0], \ar[1], \ar[2], …)$, starting from $\ar[0] = {\gleadstoinv}(\phi)$, using the lemma, until the condition $\ar[k] \nileadstost \phi$ no longer holds.
-This condition must turn false after some finite number of steps, because $\card{c(\ar[k])}$ grows at each step, $c(\ar[k]) \subseteq \gargs$ by definition of $c(.)$, and using Bounded length.
-The last element of the sequence is the argument we look for.
-\end{proof}
-\commentOC{If playing $\ar_2$ at some stage did not move $i$ and $\ar_1$ still attacks $\ar_0 + \ar_2$, we can say that the model missed answering that step, thus either we choose to give it a second chance (maybe it chose the wrong $\ar_2$ to counter the $\ar_1'$ it believed was relevant, or it needed both $\ar_2$ and $\ar_4$), or we give up in fear of losing our time.
-Actually, the protocol is that when applying Answerability, we are supposed to pick the $\ar_1'$ that $i$ just was given by another model, thus, if that’s still the same $\ar_1$ as the step before, the model has lost (it can’t map what it’s told to an argument it knows how to answer).}
-
-\subsection{Multiple tries}
-Should generalize the building of possible arguments attempted by the model.
-A model defines $m(\ar_0, \ar_1) \subseteq \allargs$ giving its possible arguments for answering $\ar_1$.
-Define $\gargs[\phi, 0] = \mleadsto(\allargs)$.
-If $\ar_k$ has lost (thus the model can’t answer some counter-argument to it), there must be another candidate argument.
-
-Mandate that $\exists \ar_0 \in \gargs[\phi, 0]$ such that $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar \land f(\ar_0, \ar_1) ≠ \emptyset$.
-
-\commentOC{TODO 1.
-Justify the fundamental restriction: mandates that $\exists \ar_0 \in \gargs[\phi] \suchthat \ar_0$ decisive.
-2.
-Rephrase condition as: must not be that at some point, for all $\ar_0$ in the current set of possibilities, $\nexists \ar_1 \ibeatse \ar_0 \suchthat \ar_2 \gbeats \ar_1$ (or rather $m(\ar_0, \ar_1) \subseteq C$ with $C$ the current set of possibilities).}
-
-First point is not restrictive: if there is a decisive argument for $\phi$, there is a valid model which says that $\phi$ (and if there is a valid model for $\phi$, then $\phi \in \iPhi$).
-
-First point bars models that want to fully explore $\ibeatse$ and then choose a decisive argument, for example.
-This would not be desirable because if model can’t be a priori expressed as a restricted model, then we have no means to check that really $\ar \ileadsto \phi$ as another path can’t be adopted (unless $i$ forgets).
-Also, what if $i$ gets tired after 10 arguments?
-
-\subsection{Current question}
-Should I leave open the uplifting of $+$ for more generality?
-Is this really sufficiently general to encompass both interpretations of Answerability, and more?
-Or should I stick to the current, “single-try”, approach and interpretation?
-
-\subsection{Interpreting Answerability}
-At a given stage in operationalizing the protocol, define $f(\ar_0)$ as the arguments that are considered as having a chance to attack $\ar_0$ (without backtracking).
-Thus, this will not include $\ar_1$ if indeed $\ar_2$ is considered by $i$ as a satisfying answer to $\ar_1$.
-We can interpret Answerability in the following ways.
-Strong answ: $\exists \ar_1 \in f(\ar_0) \suchthat \ar_1 \gbeats \ar_0$.
-Weak answ: $f(\ar_0) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0$.
-Or suppress Answ and replace Op.
-val.
-by Strong op.
-val.: $\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
-
-A model can be allowed to try only once each answer. If $\ar_2 \gbeats \ar_1 \land \ar_1 \in f(\ar_0 + \ar_2)$, the model has lost.
-
-Thus, four variants, given $\ar_2 \gbeats \ar_1$.
-\begin{itemize}
-	\item Strong answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land \forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeats \ar_0 + \ar_2$.
-	\item Strong answ with multiple tries: $\forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeats \ar_0 + \ar_2$.
-(Example: $\ar_1 = \text{“for ethical reasons”}$, and $\eta$ knows two c-a to this, from different angles.) 	\item Weak answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land [f(\ar_0 + \ar_2) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0]$.
-	\item Weak answ with multiple tries: $f(\ar_0 + \ar_2) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0 + \ar_2$.
-\end{itemize}
-
-Goal: leave addition free so as to admit multiple tries, and prove that Strong answ with multiple tries is the right one for a general approach: suitable restriction to the model permits single try (with same conditions); and weak answ actually does not permit more models.
-
-When $f$ is available and is single-valued, question: should we use Strong or weak answ?
-Right answer: use Strong answ.
-It is stricly more general.
-A model that wants weak answ can define its internal attacks suitable (to be proven); and a model that wants to claim more can.
-
-When $f$ is not available, only remains: single try (just give a decisive argument) or multiple tries (try more and more arguments, blindly).
-
-Suppose that a model also defines $f_\eta$, meaning: $f_\eta(\ar_1) = \ar_2$ the argument the model plays against $\ar_1$.
-Thus $f_\eta$, like $\gbeats$, is a binary relation over $\allargs$, but $f_\eta$ in supplement returns a single argument or none.
-Also, $\ar_2 = f(\ar_1) ⇒ \ar_2 \gbeats \ar_1$.
-When a reason $\ar_1$ for rejecting $\ar_0$ is not known, $f_\eta(\ar_0)$ instead gives the argument to be played next.
-Note that $f_\eta$ is only useful when (in the known c-a variant) for some $\ar_1$ there are multiple candidates $\ar_2$ or when (in the unknown c-a variant) for some $\ar_0$ here are multiple candidates $\ar_2$.
-In fact, this is more complicated: $f_\eta(\ar_1)$ can give first $\ar_2$, then, if that is not enough, $\ar_4$ (thus it’s rather $f_\eta(\ar_1, \ar_0)$).
-
-Under Strong anws, we ask that $f(\ar_0) \cap {\gbeatsinv}(\ar_0) ≠ \emptyset$, and (inevitably) that $f_\eta(\ar_1) ≠ \emptyset$.
-Under weak answ, we do not expect anticipation and only demand that $f_\eta(\ar_1) ≠ \emptyset$.
-But this does not allow supplementary models.
-TODO prove this.
-
-\subsection{Single-try models}
-The above models can define several $\ar_2$ for one $\ar_1$.
-Even when interpreting Answerability in the strong sense (mandating that exactly the $\ar_1'$ we search for be defined, not just any $\ar_1'$), this gives a lot of flexibility to the model, and correspondingly, makes it very difficult to falsify: we only know that is unconclusive when all possible subset of answers to a $\ar_1$ has been tried
-
-\commentOC{This is incorrect.
-The current approach already mandates single-try.
-If $\ar_2 \gbeats \ar_1$, then $\ar_1 \ibeatse \ar_0 + \ar_2$, in the sense that $\ar_1$ would be the only such argument, is forbidden because this would require $\ar_1 \gbeats \ar_0 + \ar_2$ and thus yields a repetition.}
-
-\subsection{Example model}
-\begin{itemize}
-	\item $\ar_0 = \text{“Veg bec of ethics and health”}$
-	\item $\ar_1 = \text{“Ethics is not defined”}$
-	\item $\ar_2 = \text{“It is since Aristotle at least”}$
-	\item $\ar_1' = \text{“Health isn’t important”}$
-	\item $\ar_2' = \text{“Ask my grandmother”}$
-	\item $\ar_1 \mbeats \ar_0$, $\ar_1' \mbeats \ar_0$
-	\item $\ar_2 \mbeats \ar_1$, $\ar_2' \mbeats \ar_1'$
-	\item $\ar_0 + \ar_2 \mbeats \ar_1$
-	\item $\ar_1' \mbeats \ar_0 + \ar_2$
-	\item $\ar_0 + \ar_2' \mbeats \ar_1'$
-	\item $\ar_1 \mbeats \ar_0 + \ar_2'$
-	\item $\ar_0 + \ar_2 + \ar_2' \mbeats \ar_1$
-	\item $\ar_0 + \ar_2 + \ar_2' \mbeats \ar_1'$
-\end{itemize}
-
-\subsection{The rest}
-Change conditions.
-I should be able to prove the theorem using reinst + bounded width instead of bounded length.
-Reinst should serve to discard: $(\ar_2, \ar_1) \ileadstost \phi$, $(\ar'_2, \ar'_1) \ileadstost \phi$, $(\ar'_1, \ar_2) \ileadstoe ¬\phi$, $(\ar_1, \ar'_2) \ileadstoe ¬\phi$.
-
-Clarification.
-General theory says that $\ar_1$ is replaceable (suspects that it’s good for some people): $(\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ (\ar'_1, \ar_0) \ileadstoe ¬\phi$.
-(This will fail if some $i$ thinks $\ar'_1$ is bad arg because of $\ar_0$ but $\ar_1$ is bad because of $\ar_2$.) It may say that $\ar_1$ is bad.
-General theory prepares potentially good arg $\ar_0$ and claims that if $\ar_0 \ileadstoe \phi$, then $\ar_0 \ileadstost \phi$ (this is Answerability).
-So that the model only has to prove the weaker existential claim.
-
 Model: for a given $i$.
@@
 
-TODO: theorist proposes theory $\gamma$.
-Contains set $\allargs$.
-The theory must exhibit a limited number of candidates $s_c$ when $s'$ sometimes trumps $s$ and $s'$ sometimes does not trump $s$ (valid for all $i$): that’s falsifiable, and then permits validation of $\eta$.
-Also, $\gamma$ must exhibit a replacer $s$ of $s_3, s_1$ against $s_2$, or a set of candidate replacers.
-The replacer (or candidates) may depend on $s_3$ and $s_1$, but not on $i$.
-This is falsifiable again.
-And $\gamma$ must fix bounds of width and breadth.
-And $\gamma$ must indicate how an $s \notin \args_\gamma$ is unnecessary, by exhibiting resistant [not trumped by any decisive argument in $\args_\gamma$] candidates from $\args_\gamma$ such that at least one trump $s$ or replace $s$.
-
-A counter-theory may propose $\args^\text{ext}$ with some arguments not in $\allargs$ (or, more generally, may propose to enlarge the conditions for considering that $s', s \ileadsto t$: if DM has eaten a pancake or has eaten no pancake, must be stable).
-Then they either can exhibit a plausible argument in $\args^\text{ext}$ not in $\allargs$ (and indeed $\allargs$ is rejected), or not, and then both theories are equivalent, better keep the simpler one.
-
-Thus, $\gamma$ takes positions only on those things true for all $i$.
-
-Then a theorist can propose a mapping $i$ to $\eta_i$. If $\gamma$ is valid, then it is easy to validate $\eta_i$.
-
-More generally, I need a set of possible situations, and an operation defined by the theory $\gamma$, that brings a situation to another situation, that is normatively better for taking a decision (or innocuous?).
-The operation is: adding an argument.
-This operation corresponds to forming the pair $(s', s)$: from a situation $s'$, we add the argument $s$ and bring $i$ in the situation $(s', s)$ where she has heard two arguments.
-
-Then the normative criterion is: $t$ in DJ of $i$ when $\exists s \suchthat \forall s': (s', s) \ileadstost t$ (the theory provides a part of this guarantee under falsification, claiming for all $i$, the model makes the rest under validation for this $i$).
-
-\commentOC{Say that a theory supposedly draws on general principles, which justifies that it talks about multiple $\phi$, even though at this level, there is no connection between them.}
+\subsection{Transitive, complete preference theories}
+Given a set of alternatives $\allalts$.
+Define $\allprops_\allalts = \set{\ppst, a ≠ b \in \allalts} \cup \set{\ppstba, a ≠ b \in \allalts}$.
+Define $¬_\allalts$ such that $\forall a, b \in \allalts: ¬_\allalts\ppst = \ppstba, ¬_\allalts\ppstba = \ppst$.
+Define $\Phi_\allalts = \props_\allalts × \set{\mathit{sure}, \mathit{poss}}$.
+
+Let $I$ represent a given set of individuals; $\allalts$ a set of products; 
+and $\allargs$ the set of all strings.
+Given $i \in I$, define $\ileadstosti$ as follows. 
+Given $\hist \in \allhist$ and $\phi \in \Phi_\allalts$, with $\phi \in \set{\ppst} × \set{\mathit{sure}, \mathit{poss}}$ for some $a ≠ b \in \allalts$, the individual is presented the arguments in $\hist$, and has then to choose a product from the set $\set{a, b}$.
+Define $\hist \ileadstosti \phi$ iff $i$ chooses $a$.
+\commentOC{This is inadequate: if $i$ picks $b$ from $\set{a, b, c}$, the current definition considers it compatible with $\ppstsure \in \iPhi$, thus, $\ppst$ does not have a meaningful content.
+Should rather define $\ppstsure$ so that $a$ is picked rather than $b$ whatever the choice set.
+This requires to generalize $\ileadstosti$.}
+
+Any normative theory of the form $(\allprops_\allalts, ¬_\allalts, \allargs, I, (\ileadstoi)_{i \in I})$, for some sets $\allargs$ and $I$, is called a normative theory about $\allalts$.
+
+Given a set $\domc \subseteq \powersetz{\allalts}$, where $\powersetz{\allalts}$ designates the set of subsets of $\allalts$ without the empty set, a function $c: \domc → \allalts$ is a choice function iff $\forall B \in \domc: c(B) \subseteq B$.
+
+Given a normative theory about $\allalts$, an individual $i \in I$, a set $\domc \subseteq \powersetz{\allalts}$ and a choice function $c$, say that $c$ represents a \emph{deliberated choice function} for $i$ iff $\forall B \in \domc: c(B) \subseteq \set{a \in B \suchthat \forall b \in B: \ppstsure[b][a] \notin \iPhi}$.
+
+A normative theory about $\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: [\exists \ar_{a \pst b} \in \allargs \suchthat \ar_{a \pst b} \ileadstosti \ppstsure] \land [\exists \ar_{b \pst c} \in \allargs \suchthat \ar_{b \pst c} \ileadstosti \ppstsure[b][c]] ⇒ [\exists \ar_{a \pst c} \in \allargs \suchthat \ar_{a \pst c} \ileadstosti \ppstsure[a][c]]$.
+
+A set of propositions $P \subseteq \Phi_\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: \ppstsure \in P \land \ppstsure[b][c] \in P ⇒ \ppstsure[a][c] \in P$.
+
+A transitive empirical preference theory about $\allalts$ is an empirical theory for a normative theory about $\allalts$ such that $\gPhi$ is transitive.
+
+Associate to such a theory a preference ordering $\succ$ on $\allalts$ as follows: $a \succ b$ iff $\ppstsure \in \gPhi$.
+
+The deliberated preference of $i$ under a normative theory 
+Then, observe $a$ incomp to $z$ using a good argument for $a > z$ and one for $z > a$.
+Observe also $b$ incomp to $z$.
+And observe $a > b$.
+This proves incompleteness as $z$ indifferent to the rest is impossible.
+BUT this requires to observe possibility.
+
+\subsubsection{Transitive arguments}
+Given a normative theory and a function $\tau: \allargs × \allargs → \allargs$, say that $\tau$ is a transitive argument builder iff $\forall a ≠ b ≠ c ≠ a \in \allalts, \ar_{a \pst b}, \ar_{b \pst c} \in \allargs \suchthat \ar_{a \pst b} \ileadstosti \ppstsure \land \ar_{b \pst c} \ileadstosti \ppstsure[b][c]: \tau(\ar_{a \pst b}, \ar_{b \pst c}) \ileadstosti \ppstsure[a][c]$.
+
+Observe that if a normative theory admits a transitive argument builder, then it is transitive.
+
+TODO It is possible to determine whether a given function $\tau$ is a transitive argument builder empiricially. But not to prove empirically that a normative theory is not transitive.
 
@@
 
+General theory says that $\ar_1$ is replaceable (suspects that it’s good for some people): $(\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ (\ar'_1, \ar_0) \ileadstoe ¬\phi$.
+(This will fail if some $i$ thinks $\ar'_1$ is bad arg because of $\ar_0$ but $\ar_1$ is bad because of $\ar_2$.) It may say that $\ar_1$ is bad.
+General theory prepares potentially good arg $\ar_0$ and claims that if $\ar_0 \ileadstoe \phi$, then $\ar_0 \ileadstost \phi$ (this is Answerability).
+So that the model only has to prove the weaker existential claim.
+
+\subsection{Example model}
+\begin{itemize}
+	\item $\ar_0 = \text{“Veg bec of ethics and health”}$
+	\item $\ar_1 = \text{“Ethics is not defined”}$
+	\item $\ar_2 = \text{“It is since Aristotle at least”}$
+	\item $\ar_1' = \text{“Health isn’t important”}$
+	\item $\ar_2' = \text{“Ask my grandmother”}$
+	\item $\ar_1 \mbeats \ar_0$, $\ar_1' \mbeats \ar_0$
+	\item $\ar_2 \mbeats \ar_1$, $\ar_2' \mbeats \ar_1'$
+	\item $\ar_0 + \ar_2 \mbeats \ar_1$
+	\item $\ar_1' \mbeats \ar_0 + \ar_2$
+	\item $\ar_0 + \ar_2' \mbeats \ar_1'$
+	\item $\ar_1 \mbeats \ar_0 + \ar_2'$
+	\item $\ar_0 + \ar_2 + \ar_2' \mbeats \ar_1$
+	\item $\ar_0 + \ar_2 + \ar_2' \mbeats \ar_1'$
+\end{itemize}
+
+\subsection{Interpreting Answerability}
+At a given stage in operationalizing the protocol, define $f(\ar_0)$ as the arguments that are considered as having a chance to attack $\ar_0$ (without backtracking).
+Thus, this will not include $\ar_1$ if indeed $\ar_2$ is considered by $i$ as a satisfying answer to $\ar_1$.
+We can interpret Answerability in the following ways.
+Strong answ: $\exists \ar_1 \in f(\ar_0) \suchthat \ar_1 \gbeats \ar_0$.
+Weak answ: $f(\ar_0) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0$.
+Or suppress Answ and replace Op.
+val.
+by Strong op.
+val.: $\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
+
+A model can be allowed to try only once each answer. If $\ar_2 \gbeats \ar_1 \land \ar_1 \in f(\ar_0 + \ar_2)$, the model has lost.
+
+Thus, four variants, given $\ar_2 \gbeats \ar_1$.
+\begin{itemize}
+	\item Strong answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land \forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeats \ar_0 + \ar_2$.
+	\item Strong answ with multiple tries: $\forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeats \ar_0 + \ar_2$.
+(Example: $\ar_1 = \text{“for ethical reasons”}$, and $\eta$ knows two c-a to this, from different angles.) 	\item Weak answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land [f(\ar_0 + \ar_2) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0]$.
+	\item Weak answ with multiple tries: $f(\ar_0 + \ar_2) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0 + \ar_2$.
+\end{itemize}
+
+Goal: leave addition free so as to admit multiple tries, and prove that Strong answ with multiple tries is the right one for a general approach: suitable restriction to the model permits single try (with same conditions); and weak answ actually does not permit more models.
+
+When $f$ is available and is single-valued, question: should we use Strong or weak answ?
+Right answer: use Strong answ.
+It is stricly more general.
+A model that wants weak answ can define its internal attacks suitable (to be proven); and a model that wants to claim more can.
+
+When $f$ is not available, only remains: single try (just give a decisive argument) or multiple tries (try more and more arguments, blindly).
+
+Suppose that a model also defines $f_\eta$, meaning: $f_\eta(\ar_1) = \ar_2$ the argument the model plays against $\ar_1$.
+Thus $f_\eta$, like $\gbeats$, is a binary relation over $\allargs$, but $f_\eta$ in supplement returns a single argument or none.
+Also, $\ar_2 = f(\ar_1) ⇒ \ar_2 \gbeats \ar_1$.
+When a reason $\ar_1$ for rejecting $\ar_0$ is not known, $f_\eta(\ar_0)$ instead gives the argument to be played next.
+Note that $f_\eta$ is only useful when (in the known c-a variant) for some $\ar_1$ there are multiple candidates $\ar_2$ or when (in the unknown c-a variant) for some $\ar_0$ here are multiple candidates $\ar_2$.
+In fact, this is more complicated: $f_\eta(\ar_1)$ can give first $\ar_2$, then, if that is not enough, $\ar_4$ (thus it’s rather $f_\eta(\ar_1, \ar_0)$).
+
+Under Strong anws, we ask that $f(\ar_0) \cap {\gbeatsinv}(\ar_0) ≠ \emptyset$, and (inevitably) that $f_\eta(\ar_1) ≠ \emptyset$.
+Under weak answ, we do not expect anticipation and only demand that $f_\eta(\ar_1) ≠ \emptyset$.
+But this does not allow supplementary models.
+TODO prove this.
+
 \section{Empirical theories}

### 2020-07-16 simple.tex
Moved unsatisfactory pref theory to later
Removed more old stuff

@@
 
-\subsection{Transitive, complete preference theories}
-Given a set of alternatives $\allalts$.
-Define $\allprops_\allalts = \set{\ppst, a ≠ b \in \allalts} \cup \set{\ppstba, a ≠ b \in \allalts}$.
-Define $¬_\allalts$ such that $\forall a, b \in \allalts: ¬_\allalts\ppst = \ppstba, ¬_\allalts\ppstba = \ppst$.
-Define $\Phi_\allalts = \props_\allalts × \set{\mathit{sure}, \mathit{poss}}$.
-
-Let $I$ represent a given set of individuals; $\allalts$ a set of products; 
-and $\allargs$ the set of all strings.
-Given $i \in I$, define $\ileadstosti$ as follows. 
-Given $\hist \in \allhist$ and $\phi \in \Phi_\allalts$, with $\phi \in \set{\ppst} × \set{\mathit{sure}, \mathit{poss}}$ for some $a ≠ b \in \allalts$, the individual is presented the arguments in $\hist$, and has then to choose a product from the set $\set{a, b}$.
-Define $\hist \ileadstosti \phi$ iff $i$ chooses $a$.
-\commentOC{This is inadequate: if $i$ picks $b$ from $\set{a, b, c}$, the current definition considers it compatible with $\ppstsure \in \iPhi$, thus, $\ppst$ does not have a meaningful content.
-Should rather define $\ppstsure$ so that $a$ is picked rather than $b$ whatever the choice set.
-This requires to generalize $\ileadstosti$.}
-
-Any normative theory of the form $(\allprops_\allalts, ¬_\allalts, \allargs, I, (\ileadstoi)_{i \in I})$, for some sets $\allargs$ and $I$, is called a normative theory about $\allalts$.
-
-Given a set $\domc \subseteq \powersetz{\allalts}$, where $\powersetz{\allalts}$ designates the set of subsets of $\allalts$ without the empty set, a function $c: \domc → \allalts$ is a choice function iff $\forall B \in \domc: c(B) \subseteq B$.
-
-Given a normative theory about $\allalts$, an individual $i \in I$, a set $\domc \subseteq \powersetz{\allalts}$ and a choice function $c$, say that $c$ represents a \emph{deliberated choice function} for $i$ iff $\forall B \in \domc: c(B) \subseteq \set{a \in B \suchthat \forall b \in B: \ppstsure[b][a] \notin \iPhi}$.
-
-A normative theory about $\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: [\exists \ar_{a \pst b} \in \allargs \suchthat \ar_{a \pst b} \ileadstosti \ppstsure] \land [\exists \ar_{b \pst c} \in \allargs \suchthat \ar_{b \pst c} \ileadstosti \ppstsure[b][c]] ⇒ [\exists \ar_{a \pst c} \in \allargs \suchthat \ar_{a \pst c} \ileadstosti \ppstsure[a][c]]$.
-
-A set of propositions $P \subseteq \Phi_\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: \ppstsure \in P \land \ppstsure[b][c] \in P ⇒ \ppstsure[a][c] \in P$.
-
-A transitive empirical preference theory about $\allalts$ is an empirical theory for a normative theory about $\allalts$ such that $\gPhi$ is transitive.
-
-Associate to such a theory a preference ordering $\succ$ on $\allalts$ as follows: $a \succ b$ iff $\ppstsure \in \gPhi$.
-
-The deliberated preference of $i$ under a normative theory 
-Then, observe $a$ incomp to $z$ using a good argument for $a > z$ and one for $z > a$.
-Observe also $b$ incomp to $z$.
-And observe $a > b$.
-This proves incompleteness as $z$ indifferent to the rest is impossible.
-BUT this requires to observe possibility.
-
-\subsubsection{Transitive arguments}
-Given a normative theory and a function $\tau: \allargs × \allargs → \allargs$, say that $\tau$ is a transitive argument builder iff $\forall a ≠ b ≠ c ≠ a \in \allalts, \ar_{a \pst b}, \ar_{b \pst c} \in \allargs \suchthat \ar_{a \pst b} \ileadstosti \ppstsure \land \ar_{b \pst c} \ileadstosti \ppstsure[b][c]: \tau(\ar_{a \pst b}, \ar_{b \pst c}) \ileadstosti \ppstsure[a][c]$.
-
-Observe that if a normative theory admits a transitive argument builder, then it is transitive.
-
-TODO It is possible to determine whether a given function $\tau$ is a transitive argument builder empiricially. But not to prove empirically that a normative theory is not transitive.
-
 \section{Decision situation}
@@
 
+\subsection{Example}
+\begin{example}[(cont.)]
+	Returning to the previous example, a theory $T$ could claim that, for all individuals that belong to some given socio-economic situation and that have some given degree (described by the theory in sufficient details that it is possible to determine precisely to which kind of individuals it applies), $(\prop_a, \text{sure})$ is in the deliberated preferences of the individuals, for a given alternative $\alt$ also described by $T$.
+The theory also suggests some argument $\ar$, a text that (according to $T$) will convince any individual (fitting the description) that $\prop_\alt$ holds, thus, that $\alt$ is a “good” food product for him.
+The theory can be put to the test by picking an individual fitting the description, presenting the argument together with any other argument (for example, proposed by another theory), and observing whether $i$ is convinced.
+$T$ resists to such a falsification test if $i$ is convinced.
+According to a previous theorem, $T$ tells the truth if it would resist to any possible falsification test.
+(This is impossible to definitely make sure of.)
+\end{example}
+This example illustrates a difference between this proposal and the classical revealed approach: it could be that $T$ tells the truth even though its claim does not correspond to the revealed preference of some individuals, thus that, given no argument, some individuals would consider $a$ as dominated by another alternative in the set considered.
+It also illustrates a difference between this proposal and persuasion: the goal of $T$ is not merely to convince $i$ (possibly by using its lack of knowledge of any counter-argument to what $T$ says), but to resist any falsification attempt.
+Thus, $T$ should be confronted to arguments coming from as varied perspectives as possible, in order to give confidence that it tells the truth.
+
 \section{Next}
@@
 TODO prove this.
+
+\subsection{Transitive, complete preference theories}
+Given a set of alternatives $\allalts$.
+Define $\allprops_\allalts = \set{\ppst, a ≠ b \in \allalts} \cup \set{\ppstba, a ≠ b \in \allalts}$.
+Define $¬_\allalts$ such that $\forall a, b \in \allalts: ¬_\allalts\ppst = \ppstba, ¬_\allalts\ppstba = \ppst$.
+Define $\Phi_\allalts = \props_\allalts × \set{\mathit{sure}, \mathit{poss}}$.
+
+Let $I$ represent a given set of individuals; $\allalts$ a set of products; 
+and $\allargs$ the set of all strings.
+Given $i \in I$, define $\ileadstosti$ as follows. 
+Given $\hist \in \allhist$ and $\phi \in \Phi_\allalts$, with $\phi \in \set{\ppst} × \set{\mathit{sure}, \mathit{poss}}$ for some $a ≠ b \in \allalts$, the individual is presented the arguments in $\hist$, and has then to choose a product from the set $\set{a, b}$.
+Define $\hist \ileadstosti \phi$ iff $i$ chooses $a$.
+\commentOC{This is inadequate: if $i$ picks $b$ from $\set{a, b, c}$, the current definition considers it compatible with $\ppstsure \in \iPhi$, thus, $\ppst$ does not have a meaningful content.
+Should rather define $\ppstsure$ so that $a$ is picked rather than $b$ whatever the choice set.
+This requires to generalize $\ileadstosti$.}
+
+Any normative theory of the form $(\allprops_\allalts, ¬_\allalts, \allargs, I, (\ileadstoi)_{i \in I})$, for some sets $\allargs$ and $I$, is called a normative theory about $\allalts$.
+
+Given a set $\domc \subseteq \powersetz{\allalts}$, where $\powersetz{\allalts}$ designates the set of subsets of $\allalts$ without the empty set, a function $c: \domc → \allalts$ is a choice function iff $\forall B \in \domc: c(B) \subseteq B$.
+
+Given a normative theory about $\allalts$, an individual $i \in I$, a set $\domc \subseteq \powersetz{\allalts}$ and a choice function $c$, say that $c$ represents a \emph{deliberated choice function} for $i$ iff $\forall B \in \domc: c(B) \subseteq \set{a \in B \suchthat \forall b \in B: \ppstsure[b][a] \notin \iPhi}$.
+
+A normative theory about $\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: [\exists \ar_{a \pst b} \in \allargs \suchthat \ar_{a \pst b} \ileadstosti \ppstsure] \land [\exists \ar_{b \pst c} \in \allargs \suchthat \ar_{b \pst c} \ileadstosti \ppstsure[b][c]] ⇒ [\exists \ar_{a \pst c} \in \allargs \suchthat \ar_{a \pst c} \ileadstosti \ppstsure[a][c]]$.
+
+A set of propositions $P \subseteq \Phi_\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: \ppstsure \in P \land \ppstsure[b][c] \in P ⇒ \ppstsure[a][c] \in P$.
+
+A transitive empirical preference theory about $\allalts$ is an empirical theory for a normative theory about $\allalts$ such that $\gPhi$ is transitive.
+
+Associate to such a theory a preference ordering $\succ$ on $\allalts$ as follows: $a \succ b$ iff $\ppstsure \in \gPhi$.
+
+The deliberated preference of $i$ under a normative theory 
+Then, observe $a$ incomp to $z$ using a good argument for $a > z$ and one for $z > a$.
+Observe also $b$ incomp to $z$.
+And observe $a > b$.
+This proves incompleteness as $z$ indifferent to the rest is impossible.
+BUT this requires to observe possibility.
+
+\subsubsection{Transitive arguments}
+Given a normative theory and a function $\tau: \allargs × \allargs → \allargs$, say that $\tau$ is a transitive argument builder iff $\forall a ≠ b ≠ c ≠ a \in \allalts, \ar_{a \pst b}, \ar_{b \pst c} \in \allargs \suchthat \ar_{a \pst b} \ileadstosti \ppstsure \land \ar_{b \pst c} \ileadstosti \ppstsure[b][c]: \tau(\ar_{a \pst b}, \ar_{b \pst c}) \ileadstosti \ppstsure[a][c]$.
+
+Observe that if a normative theory admits a transitive argument builder, then it is transitive.
+
+TODO It is possible to determine whether a given function $\tau$ is a transitive argument builder empiricially. But not to prove empirically that a normative theory is not transitive.
 
@@
 
-\section{Theories proposing decisive arguments}
-In most situations, there are too many arguments to attempt to exhaustively test whether any $\ar$ is a decisive argument for any $\phi$.
-And most importantly, it is impossible to confirm definitely that $(\ar, \ar') \ileadstost \phi$, whenever $(\ar, \ar') \ileadstost \phi$.
-This is why falsifiable theories are needed.
-
-A theory $T$ proposing decisive arguments describes a set $D_T$ of decision situations to which it applies, and proposes, for any situation $d = (\Phi, \allargs, \ileadstost) \in D_T$, a subset $\Phi_{d, T} \subseteq \Phi$ and a mapping $f_{d, T}: \Phi_{d, T} → \allargs$.
-The theory claims that it knows the deliberated preference of $i$ (the individual described by $\ileadstost$ in $d$) about the propositions in $\Phi_{d, T}$, and claims that $f_{d, T}(\phi)$ is a decisive argument for $\phi$.
-The theory $T$ is said to have a position about $\prop$ if $(\prop, \text{sure}) \in \Phi_{d, T} ∨ (¬\prop, \text{possible}) \in \Phi_{d, T}$.
-In order for the claims of the theory to be interpretable, it is requested that if $T$ has a position about $\prop$, then it must have a position about $¬\prop$.
-This forces $T$, for each pair $(\prop, ¬\prop)$, to either claim that one is sure, claim that both are possible, or have no claim about the pair.
-
-A falsification instance of $T$ is a triplet $(d, \ar', \phi) \in D_T × \allargs × \Phi_{d, T}$ such that $(f_{d, T}(\phi), \ar') \ileadstoe ¬\phi$.
-A theory $T$ is said to be falsified iff such a triplet is found.
-
-As is usual in science, falsification procedures should not be considered as ways of definitely validating a theory, but rather as ways of confronting theories.
-Two theories $T, T'$ are said to disagree on $\phi$ iff $\phi \in \Phi_{d, T}$ and $¬\phi \in \Phi_{d, T'}$ in some situation $d \in D_T ∪ D_{T'}$.
-$T$ and $T'$ are said to disagree iff they disagree on some $\phi \in \Phi$.
-To confront a theory $T$ to a disagreeing theory $T'$, suffice to test, for any situation $d \in D_T ∪ D_{T'}$ and $\phi$ such that $\phi \in \Phi_{d, T}, ¬\phi \in \Phi_{d, T'}$, whether $(f_{d, T}(\phi), f_{d, T'}(¬\phi)) \ileadstoe \phi$.
-Such a test necessarily falsifies one of the theories.
-
-The following proposition shows that this notion of falsification adequately tests the claims of the theory.
-\begin{proposition}
-	\label{thm:fals}
-	A theory $T$ proposing decisive arguments has no falsification instances iff $\forall d \in D_T, \forall \phi \in \Phi_{d, T}: f_{d, T}(\phi)$ is $\phidec$.
-Furthermore, if a theory $T$ proposing decisive arguments has no falsification instances, then $\Phi_{d, T} \subseteq \iPhi$, $\forall d \in D_T$.
-\end{proposition}
-
-\begin{example}[(cont.)]
-	Returning to the previous example, a theory $T$ could claim that, for all individuals that belong to some given socio-economic situation and that have some given degree (described by the theory in sufficient details that it is possible to determine precisely to which kind of individuals it applies), $(\prop_a, \text{sure})$ is in the deliberated preferences of the individuals, for a given alternative $\alt$ also described by $T$.
-The theory also suggests some argument $\ar$, a text that (according to $T$) will convince any individual (fitting the description) that $\prop_\alt$ holds, thus, that $\alt$ is a “good” food product for him.
-The theory can be put to the test by picking an individual fitting the description, presenting the argument together with any other argument (for example, proposed by another theory), and observing whether $i$ is convinced.
-$T$ resists to such a falsification test if $i$ is convinced.
-According to \cref{thm:fals}, $T$ tells the truth if it would resist to any possible falsification test.
-(This is impossible to definitely make sure of.)
-\end{example}
-This example illustrates a difference between this proposal and the classical revealed approach: it could be that $T$ tells the truth even though its claim does not correspond to the revealed preference of some individuals, thus that, given no argument, some individuals would consider $a$ as dominated by another alternative in the set considered.
-It also illustrates a difference between this proposal and persuasion: the goal of $T$ is not merely to convince $i$ (possibly by using its lack of knowledge of any counter-argument to what $T$ says), but to resist any falsification attempt.
-Thus, $T$ should be confronted to arguments coming from as varied perspectives as possible, in order to give confidence that it tells the truth.
-
 \bibliography{simple}
 \end{document}
-
-\section{Models}
-A model is a triple $(\mbeats, \mleadsto, +)$ defined as follows and satisfying the following constraints.
-
-$\mbeats$ a binary relation over $\allargs$.
-$\mleadsto \subseteq \allargs × \alltopic$.
-Define $\clargs \subseteq \allargs$ as the set of arguments used in $\mbeats ∪ \mleadsto$.
-Let $+$ be defined over arguments used in the model: $\ar_3 + \ar_1 = \ar'$ for some $\ar' \in \clargs$, for any $\ar_3, \ar_1 \in \clargs$.
-
-Requirements. The maximum length of a path in $\mbeats$ is finite (which implies that $\mbeats$ is acyclic).
-$\ar_3 \mbeats \ar_2 \mbeats \ar_1 ⇒ \ar_2 \mbeats \ar_3 + \ar_1$.\footnote{Necessary for definition of $\ar_3 \wibeatse[\phi] \ar_2$.
-TODO remove this condition, define $\wibeatse[\phi]$ more largely and never valid when not in $\mbeats$.}
-
-Notation. Let $\mleadstoinv(\alltopic) \subseteq \clargs$ denote the subset of arguments supporting propositions. 
-$\mbeats(\args)$: arguments that $\args$ attacks, $\ar_1 \in \mbeats(\args) ⇔ \exists \ar_2 \in \args \suchthat \ar_2 \mbeats \ar_1$; $\mbeatsinv(\ar)$: arguments attacking $\ar$, $\ar_2 \in \mbeatsinv(\ar) ⇔ \ar_2 \mbeats \ar$.
-We write $\ar \mleadsto (\prop, \text{possible})$ for $\ar \mleadsto \prop$ and $\ar \mleadsto (\prop, \text{sure})$ for $\ar \mleadsto \prop ∧ (¬\prop \notin \mleadsto(\allargs))$.
-
-Given a decision situation, we define the relations $\wibeatse[\phi], \nwibeatse[\phi] \subseteq \allargs × \allargs$ in order to obtain the following result, and with $\wibeatse[\phi], \nwibeatse[\phi] \subseteq \mbeats$.
-
-Given $\ar_3 \mbeats \ar_2, \phi \in \Phi$: $\ar_3 \wibeatse[\phi] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \nwibeatse[\phi] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe ¬\phi]$.
-
-Given $\ar_3 \mbeats \ar_2, \phi \in \Phi$: $\ar_3 \nwibeatse[\phi] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \wibeatse[\phi] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe \phi]$.
-
-This is done with the following construction.
-Given a model. 
-\begin{itemize}
-	\item Define a root as an argument that $\mbeats$-attacks nothing. 
-	\item Associate to each $\ar \in \clargs$ its depth $d(\ar)$, the distance to the farthest root: $d(\ar) = 0$ iff $\ar$ is a root and $d(\ar) = k+1$ iff $\ar$ $\mbeats$-attacks some $\ar'$ of depth $k$ and $\mbeats$-attacks no $\ar'$ of depth superior to $k$.
-\footnote{Thus $d(\ar) = 1$ iff $\ar$ attacks some and only root nodes; $d(\ar) = 2$ iff $\ar$ attacks some node of depth 1 and only nodes of depth 1 or 0; and so on.}
-	\item Observe that if $\ar_3 \mbeats \ar_2$ and $d(\ar_3) = k+1$, then $d(\ar_2) ≤ k$. 
-	\item Define $\wibeatse[\phi]_{(0)} = \nwibeatse[\phi]_{(0)} = \emptyset$. 
-	\item Define $\wibeatse[\phi]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\phi]_{(k+1)} \ar_2$ iff $\ar_3 \mbeats \ar_2$, $d(\ar_3) = k+1$, and: $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\phi]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe ¬\phi]$.
-Proceed similarly for $\nwibeatse[\phi]_{(k+1)}$.
-	\item Define $\wibeatse[\phi] = \bigcup_{k ≥ 0} \wibeatse[\phi]_{(k)}$, and similarly for $\nwibeatse[\phi]$.
-\end{itemize}
-
-Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\phi] \ar_1$, we have: $\ar_3 \wibeatse[\phi] \ar_2 ∨ \ar_3 \nwibeatse[\phi] \ar_2$.
-
-Define $\ar_2 \wibeatse \ar_1 ⇔ \exists \phi \in \alltopic \suchthat \ar_2 \wibeatse[\phi] \ar_1$.
-
-Hence, given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic)$: $¬ (\ar_3 \nwibeatse \ar_2)$ iff $\forall \ar_1 \in \mbeats(\ar_2) ∩ \wibeatse(\ar_2): ¬ (\ar_2 \wibeatse \ar_3 + \ar_1)$.
-
-\section{Conditions}
-All these conditions assume that a decision situation $(\allalts, \allargs, …)$ and a model $\eta = (\mbeats, \mleadsto, +)$ are given.
-
-Define $\argsdec^\phi = \clargs \setminus \text{im}(\wibeatse[\phi])$ the decisive arguments according to $\wibeatse[\phi]$, or $\wibeatse[\phi]$-decisive arguments for short: $\ar \in \argsdec^\phi ⇔ \wibeatseinv[\phi](\ar) = \emptyset$.
-
-We say that $\ar$ replaces $\ar_1$ iff $\mbeats(\ar_1) \subseteq \mbeats(\ar)$.
-
-\begin{definition}[Reinstatement]
-	Given $\ar_3 \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1, \ar_3 \in \argsdec^\phi$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
-	\footnote{TODO the condition must be $\wibeatseinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$ to allow $\ar_5 \mbeats \ar_4 \mbeats \ar_3 \mbeats \ar_2 \mbeats \ar_1$ and $\ar_5 \mbeats \ar_4 \mbeats \ar_3 + \ar_1$, considering that possibly $\ar_3$ is $\wibeatse$-decisive.
-This should not invalidate the conditions, but it does currently.
-But it’s not a problem: the model would actually not be built this way.
-In this scenario the argument $\ar_3 + \ar_1$ is useful only in case $\ar_3$ is decisive, thus $\ar_4 \mbeats \ar_3 + \ar_1$ must not be planned.
-Rather $\ar_5 + \ar_3$ decisive, then $(\ar_5 + \ar_3) + \ar_1$.
-Alternatively, also $\ar_4 \mbeats \ar_1$ and then no problem as well.}
-	\footnote{The stronger condition mandating $\mbeatsinv(\ar_3 + \ar_1) \subseteq \wibeatseinv(\ar_1) \setminus \mbeats(\ar_3)$ would be more difficult to check: when some $\ar_2 \wibeatse \ar_3 + \ar_1$, we’d need to check not only that $\ar_2 \mbeats \ar_1$ but also $\ar_2 \wibeatse \ar_1$.}
-	\footnote{We do not mandate that $\ar_3 + \ar_1 \ileadsto \phi$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice).}
-	\footnote{Is Reinf equivalent to Justifiable unstability?
-Define $\ar_3 \wibeatsst[\phi] \ar_2 ⇔ \ar_3 \wibeatse[\phi] \ar_2 ∧ ¬(\ar_3 \nwibeatse[\phi] \ar_2)$.
-Prove that $\ar_3 \wibeatsst[\phi] \ar_2 \wibeatse[\phi] \ar_2 ⇒ ¬(\ar_2 \wibeatse[\phi] \ar_3 + \ar_1)$.}
-\end{definition}
-
-\begin{definition}[Justifiable unstability]
-	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse[\phi] \ar_1, \ar_2 \nwibeatse[\phi] \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\phi] \ar_2$.
-\end{definition}
-
-$\ar$ is $\phi$-defended iff $\wibeatseinv[\phi](\ar) \subseteq \wibeatse[\phi](\argsdec^\phi)$ (its $\wibeatse[\phi]$-attackers are $\wibeatse[\phi]$-attacked by $\wibeatse[\phi]$-decisive arguments).
-
-\begin{definition}[Finite defense]
-	If $\wibeatseinv[\phi](\ar) \subseteq \wibeatse[\phi](\argsdec^\phi)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse[\phi](\args)$.
-\footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check).
-But it may be interesting to not limit it and declare that the model has specific replies to any counter-argument, but promises to use only a few rebuttals and that afterwards, the dm will stop using those kind of arguments (but we don’t know in advance which ones will be chosen).}
-\end{definition}
-Thus, if the attackers of $\ar$ are attacked by decisive arguments, then $j$ defenders are enough to defend $\ar$.
-
-Define $R^\phi$, the reinstates relation, as follows: $(\ar_3 + \ar_1) R^\phi \ar_1$ iff $\ar_3 \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1$ (for some $\ar_2, \phi$), $\ar_3 \in \argsdec^\phi$.
-Define $\gdargs^\phi$ as the transitive closure of $\mleadstoinv(\Phi)$ under $R^\phi$.
-Given $\phi, \ar \in \gdargs^\phi, \ar' \in \allargs$, define $\ar' \ibeatse[\phi] \ar ⇔ (\ar', \ar) \ileadstoe ¬\phi$.
-\begin{definition}[Covering]
-	$\forall \phi, \ar \in \gdargs^\phi, \ar' \in \allargs: \ar' \ibeatse[\phi] \ar ⇒ \ar' \wibeatse[\phi] \ar$. 
-\end{definition}
-
-\begin{definition}[Observable validity]
-	$\forall \ar_2 \mbeats \ar_1 \mleadsto \phi: ¬(\ar_2 \wibeatse[\phi] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\phi] \ar_2$.
-	\footnote{If the model claims $¬\prop \in \isure$, this requires clear-cut (for that prop), so we must mandate it (hopefully A3 or an equivalent such as Justifiable unstability fits).
-Thus we only need to prove $\prop \notin \iposs$, for which $(\ar_1, \ar) \ileadstose ¬\prop$, for each $\ar$, suffices.
-In fact, from $\ar_1$ in the model arguing for $\phi$ and $(\ar_1, \ar) \ileadstoe \phi \forall \ar \in \allargs$, we should probably be able, using the argument in the theorem about finite chains, to deduce that this is enough to conclude that $\ar_1$ is $\phidec$.}
-\end{definition}
-
-\section{Theorem}
-\begin{theorem}[Validity]
-	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iPhi$.
-\end{theorem}
-\begin{proof}
-First, we want to prove that $\ar_1$ $\phi$-defended implies $\ar_1$ replaceable by some $\wibeatse[\phi]$-decisive $\ar$, and if $\ar_1 \in \gdargs^\phi$, then its replacer $\ar$ is in $\gdargs^\phi$ as well.
-
-Because $\ar_1$ is $\phi$-defended, $\exists \args \subseteq \argsdec^\phi \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse[\phi](\args)$, $\args$ finite [Finite defense].
-
-Pick any $\ar_{3, 1} \in \args$ such that $\ar_{3, 1} \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1$ (if there’s none, $\ar_1 \in \argsdec^\phi$ and we’re done).
-$\ar_{3, 1} + \ar_1$ replaces $\ar_1$, and $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_{3, 1})$ [Reinstatement].
-Hence, $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \wibeatse[\phi](\args) \setminus \mbeats(\ar_{3, 1})$.
-Iterate by picking any $\ar_{3, 2} \in \args$ such that $\ar_{3, 2} \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_{3, 1} + \ar_1$ (if there’s none, $\ar_{3, 1} + \ar_1 \in \argsdec^\phi$ and we’re done) and obtaining $\ar_{3, 2} + (\ar_{3, 1} + \ar_1)$ replacing $\ar_{3, 1} + \ar_1$ (hence, replacing $\ar_1$) with $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \mbeatsinv(\ar_{3, 1} + \ar_1) \setminus \mbeats(\ar_{3, 2})$.
-Hence, $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \wibeatse[\phi](\args) \setminus \mbeats(\ar_{3, 1}) \setminus \mbeats(\ar_{3, 2})$.
-Iterating in such a way over the finite set $\args$ will finally yield an element that is $\wibeatse[\phi]$-decisive.
-The last point, $\ar_1 \in \gdargs^\phi ⇒ \ar \in \gdargs^\phi$, follows from the definition of $\gdargs^\phi$.
-
-Second, we want to prove that if $\ar_1$ is not $\phi$-defended and has no decisive $\wibeatse[\phi]$-attackers (meaning that $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$), then $\ar_1$ is $\wibeatse[\phi]$-attacked by some $\ar_2$ that is not $\phi$-defended and has no decisive $\wibeatse[\phi]$-attacker.
-
-Consider $\ar_1$ not $\phi$-defended and having no decisive $\wibeatse[\phi]$-attackers.
-Because $\ar_1$ is not $\phi$-defended, by definition, it is $\wibeatse[\phi]$-attacked by some $\ar_2$ that has no decisive $\wibeatse[\phi]$-attacker.
-Because $\ar_1$ has no decisive attacker, $\ar_2$ is not decisive.
-If $\ar_2$ was defended, by the first part of this proof, it would be replaceable by a decisive argument, and $\ar_1$ would have a decisive attacker.
-Thus, $\ar_2$ is not defended.
-
-We conclude from this second point that if $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$, then $\ar_1$ is $\phi$-defended.
-Otherwise, it would be attacked by some $\ar_2$, on which the condition would apply in turn, thus which would be attacked by some $\ar_3$, on which the condition would apply, and iterating in this way would build an infinite chain in $\wibeatse[\phi]$, a contradiction.
-
-Third, consider an argument $\ar_1 \in \mleadstoinv(\Phi)$.
-If some $\ar_2 \wibeatse[\phi] \ar_1$ then $\ar_3 \wibeatse[\phi] \ar_2$ [Obs val].
-Thus, $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$.
-Thus, $\ar_1$ is $\phi$-defended, by our second point.
-Hence, by our first point in this proof, $\ar_1$ is replaceable by some $\wibeatse[\phi]$-decisive $\ar \in \gdargs$.
-We obtain that $\forall \ar' \in \allargs: ¬(\ar' \wibeatse[\phi] \ar)$.
-As $\ar \in \gdargs$, $\ar' \ibeatse[\phi] \ar ⇒ \ar' \wibeatse[\phi] \ar$ [Covering], thus we obtain $¬(\ar' \ibeatse[\phi] \ar)$, hence $\ar$ is $\phidec$ and $\phi \in \iPhi$.
-\end{proof}
-
-\appendix
-\section{Todo}
-We define $(\ar, \ar') \ileadstopst \prop ⇔ \ar' \nibeatsst[\prop] \ar ⇔ \ileadsto(\ar, \ar') \subseteq \{\propsure, b\}$, and $(\ar, \ar') \ileadstosst ¬\prop ⇔ \ar \nibeatsst[¬\propsure] \ar' ⇔ \ileadsto(\ar, \ar') = \{¬\propsure\}$.
-Hence, $(\ar, \ar') \ileadstose ¬\prop ⇔ \ar' \ibeatse[\prop] \ar ⇔ ¬(\ar' \nibeatsst[\prop] \ar) ⇔ \ileadsto(\ar, \ar') \supseteq \{¬\propsure\}$, and $(\ar, \ar') \ileadstope \prop ⇔ \ar \ibeatse[¬\propsure] \ar' ⇔ ¬(\ar \nibeatsst[¬\propsure] \ar') ⇔ \ileadsto(\ar, \ar') ≠ \{¬\propsure\}$.
-
-\begin{itemize}
-	\item If $i$ does not consider $\ar$ as supporting $\prop$, it also works: if $\prop$ is not weakly acceptable by default, then any $\ar'$ is considered by $i$ as a better argument than $\ar$ in favor of certain $¬\prop$, and so on.
-In fact, whether $\emptyset \ibeatse[\prop] \emptyset$ determines whether $\prop$ is weakly supported by default.
-	\item I should define $\ar' (□\ibeatse[\prop]) \ar$ as an observable: “Assuming $\ar'$ would survive, do you consider $\ar'$ as leading to certainty of $¬\prop$, even when considering $\ar$?”.
-It distinguishes our knowledge and the truth: $\ar' (□\ibeatse[\prop]) \ar ⇒ \ar' \ibeatse[\prop] \ar$, thus, implies $¬ (\ar' \nibeatsst[\prop] \ar)$.
-But out of $¬ (\ar' (□\ibeatse[\prop]) \ar)$, nothing.
-	\item Partition (objectively) $\allargs$ (or $\allargs × \alltopic$) into arguments in favor of $\prop, \text{sure}$, $¬\prop, \text{sure}$, and similarly for possible.
-Use only one rel $\ibeatse$, defined on contradictory arguments only, instead of $\ibeatse[\prop, \text{sure}]$ and others.
-Define $\ar' \ibeatse[\prop] \ar$ equals no when $¬(\ar' \ileadsto ¬\prop, \text{sure})$, equals $\ibeatse$ for adequate arguments, and equals yes when $¬(\ar \ileadsto \prop, \text{possible})$ and $\ar' \ileadsto ¬\prop, \text{sure}$, with probably some complications needed for the argument $\emptyset$ (and related default attitude towards $\prop$).
-\end{itemize}
-
-Questions:
-Q1. Relationship with $\ar \ibeatse[\prop] \ar$?
-
-We want to exclude: $s$ supports $p$ perhaps, attacked by $s2$ (supporting $¬p$ sure), but then $s2$ is attacked by $s$.
-Exclude $\ar' \ibeatse[\prop] \ar$ and $\ar \ibeatse[¬\prop, \text{sure}] \ar'$.
-Require to assume that this situation implies another argument $\ar_3$ “attacking” $\ar'$, thus, such that $\ar_3 + \ar$ is no more attacked by $\ar_2$.
-
-\subsection{Attack rel}
-Given $\prop$, define a (symmetric) strong attack rel, $Q_\prop$, as $\ar Q_\prop \ar'$ iff $(\ar, \ar') \ileadstosst ¬\prop$.
-
-Define a (symmetric) weak attack rel, $R_\prop$, as $\ar R_\prop \ar'$ iff $(\ar, \ar') \ileadstopst ¬\prop$.
-
-Given $\prop$, we want to check the arguments that defend it. We want to build an asymmetric attack relation.
-$\ar_1 M \ar_0$, and not the converse, iff $\ar_1$ attacks $\ar_0$ and, would $\ar_1$ be attacked, $\ar_0$ reinstated would defend $\prop$.
-$\ar_1$ should be able to support a sub-claim $\prop'$, and then $\ar_2$ attack $\ar_1$ on that sub-claim precisely.
-$\ar_2$ decisive on this sub-claim and $\ar_0 + \ar_2$ decisive implies $\ar_1$ attacks $\ar_0$ and not conversely.
-
-Or simply. $\ar_1$ decisive for $¬\prop$ means $\ar_1$ attacks $\ar_0$ and not conversely.
-
-Then define $i$’s DJ in terms of argumentation semantics.
-
-\section{To think}
-Propositions weakly self-supported $T \subseteq \alltopic$: weakly accepted if no arg is given.
-Examples: $m$ = “eat miam”; $¬b$ = “beurk is to exclude”; or, in a problem where there’s no particularly good aliments, both $a$ = “eat this” and $¬a$.
-
-When given $(\ar, \prop)$, $i$ may say: $\ar$ does not survive; or: assuming $\ar$ survives, then $\ar$ supports $\prop$, or, assuming $\ar$ survives, then $\ar$ does not support $\prop$ anyway.
-
-When given $\ar'$ against $\ar$, $i$ may say: $\ar'$ does not survive, or: assuming $\ar'$ survives, then $\ar'$ supports $¬\prop$, …
-
-Given $(\ar_2, \prop), (\ar_1, ¬\prop) \in D$, define $¬(\ar_2 \wibeatse^\text{neg}_{¬\prop} \ar_1)$ iff for some $(\ar, \prop) \in D$, where $\ar_1 \ibeatse[\prop] \ar$: $\ar_1 \ibeatse[\prop] \ar + \ar_2$.
-Equivalently: $\ar_2 \wibeatse^\text{neg}_{¬\prop} \ar_1$ iff for all $\ar$, where $\ar_1 \ibeatse[\prop] \ar$: $¬(\ar_1 \ibeatse[\prop] \ar + \ar_2)$.
-(This does not seem right: if given $\ar_3$ attacking $\ar_2$, and not given $\ar_4$ which would convincingly rebut $\ar_3$, then temporarily it may hold again that $\ar_1 \ibeatse[\prop] \ar + \ar2$ (in the sense that $\ar_1 + \ar_3 \ibeatse[\prop] \ar + \ar_2$).)
-
-$\ar_2 \wibeatse_{¬\prop} \ar_1$ can perhaps be queried directly by asking (in the context of some $\ar_1 \ibeatse[\prop] \ar$): “assume $\ar_2$ survives, then does $\ar_2$ counter $\ar_1$?” (In the sense that $\ar_2$ is sufficiently convincing that $\prop$ holds perhaps, to cancel the argument $\ar_1$ according to which $¬\prop$ surely holds.)
-
-\section{Certainties}
-Looking for certainties. Those propositions that are in the reflexive preferences in a demanding sense: there is a strong enough reason to prefer it than its contrary.
-\begin{itemize}
-	\item $\ar' \wibeatse \ar$: weak attack; $\ar'$ renders $\ar$ invalid (can’t be used to say that $t$ holds for sure) (assuming $\ar'$ survives)
-	\item Propositions strongly self-supported: strongly accepted if no arg is given. Examples: $m$ = “eat miam”; $¬b$ = “beurk is to exclude”. We might have neither $c$ nor $¬c$ in that set.
-\end{itemize}
-
-\begin{definition}[Sure acceptance]
-	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$.
-A proposition $\prop \in \alltopic$ is accepted as sure iff $\exists \ar' \in \allargs \suchthat \forall \ar \in \allargs: \ar \nibeatsst[\prop, \text{sure}] \ar'$.
-\end{definition}
-
-Assume we use rather: if $p$ is not sure, then $¬p$ is weakly accepted (by def).
-Then we have never problems of inconsistency!
-But we could be in a situation where $p$ is not accepted as sure but nobody can tell why because it is fundamentally unstable (sometimes $p$ being accepted, sometimes not).
-
-\section{Example about model instanciation}
-The general conditions are Reinstatement, Justifiable unstability, Finite defense and Covering.
-A general model is a model that claims it satisfies the general conditions.
-
-TODO give up general models.
-In this example, $\ar_1$ would need to be planned as attacking sometimes $\ar_2$.
-Better consider an instanciation mechanism.
-An instantiated model is particular, and can be tested (especially against another one).
-\begin{example}
-	$\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto \prop$, $\ar_2 \mleadsto ¬\prop$; $\ar_3 + \ar_1 \mleadsto \prop$.
-\end{example}
-This model is compatible (meaning that it satisfies the general conditions) with the following decision situations. We describe $\ibeatse$ fully (no attack iff not mentioned).
-\begin{itemize}
-	\item Sure of $\prop$: $\ar_1 \mleadsto \prop$; $\ar_3 \ibeatse \ar_2$ (the rest is implied, for example $\forall \ar_4 \in \allargs: \ar_1 \ibeatse[¬\prop] \ar_4$ because of covering).
-	\item Sure of $\prop$ with reinstatement: $\ar_3 \ibeatse[\prop] \ar_2 \ibeatse[\prop] \ar_1 \mleadsto \prop$; $\ar_1 + \ar_3 \mleadsto \prop$; $\ar_3 \ibeatse[¬\prop] \ar_2$
-	\item Sure of $¬\prop$: $\ar_2 \mleadsto ¬\prop$; $\ar_2 \ibeatse \ar_1$
-	\item Both: $¬(\ar_2 \ibeatse \ar_1), \ar_1 \mleadsto \prop$, $¬(\ar_3 \ibeatse \ar_2), \ar_2 \mleadsto ¬\prop$
-\end{itemize}
-This situation falsifies the model. $\ar_4 \ibeatse \ar_1$, $\ar_4$ not attacked.
-
-\section{Model certainties}
-Assume we define $\ar_1 \wibeatse[¬\prop, \text{sure}] \ar_2 ⇔ \ar_2 \nwibeatse[\prop] \ar_1$.
-Then, indeed, given $\ar_1 \mleadsto \prop$, $\ar_2 \wibeatse[¬\prop, \text{sure}] \ar_1 ⇔ \ar_2 \ibeatse[¬\prop, \text{sure}] \ar_1$.
-But it gives the wrong conclusion.
-For $\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto t: \ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\ar_2 \nwibeatse[¬\prop] \ar_3$ iff $\exists \ar_1 \in \mbeats(\ar_3) \suchthat \ar_3 \wibeatse[¬\prop] \ar_1 ∧ \ar_3 \wibeatse[¬\prop] \ar_2 + \ar_1$.
-
-Given $\ar_1 \mleadsto \prop$, define $\ar_2 \wibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_2 \ibeatse[\prop, \text{sure}] \ar_1$.
-
-Given $\ar_1 \mleadsto \prop$, define $\ar_2 \nwibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_1 \ibeatse[¬\prop] \ar_2$.
-
-Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \nwibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.
-
-Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \nwibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \wibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.
-
-\section{Example about default arguments}
-s2 argues in favor of p against s1: s "le monde n’est pas fiable".
-s1 "le monde est fiable, bhl l’a dit".
-s2 "bhl est un clown, il s’est planté sur l’Irak".
-s3 "il avait raison sur l’Irak : l’Irak a des ADM".
-s4 "l’Irak n’a pas d’ADM, Bush l’a reconnu".
-Does s4 attack s3?
-"bhl est un clown, il s’est planté sur l’irak" + "l’irak n’a pas d’ADM, Bush l’a reconnu" VS "il avait raison sur l’Irak : l’Irak a des ADM" !
-
-Measure problem?
-
-\section{Alternative definitions of finite defense}
-Define Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec as: $\wibeatseinv(\ar) \subseteq \wibeatse(\clargs \setminus \text{im}(\mbeats)) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args)$.
-Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is insufficient to provide $T_\eta = \iposs$.
-Define $\ar' \mbeats^\text{fail} \ar$ iff $\ar' \mbeats \ar ∧ ¬(\ar' \wibeatse \ar)$.
-Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_4 \mbeats^\text{fail} \{\ar_3, \ar_3', …\}$.
-Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is artificially satisfied because the antecedent fails to trigger.
-
-Define Finite defense-$\wibeatse$-$\wibeatse$-subsets as: $\wibeatseinv(\ar) \subseteq \wibeatse(\args) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args')$.
-Finite defense-$\wibeatse$-$\wibeatse$-subsets is insufficient to provide $T_\eta = \iposs$.
-This is because Reinstatement allows for new attacks in $\wibeatse$ (it only forbids new attacks in $\mbeats$), thus we can forever transform previously failing attacks to new attacks, hence always satisfying Finite defense (always finite cover of $\wibeatse$, but infinite cover of $\mbeats$) but still not converging.
-Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3' \wibeatse \ar_2' \mbeats^\text{fail} \ar_1$, and so on; and $\ar_3' \wibeatse \ar_2' \wibeatse \ar_3 + \ar_1, \ar_3'' \wibeatse \ar_2'' \mbeats^\text{fail} \ar_3 + \ar_1$, and so on.
-
-Define Finite defense-$\mbeats$-$\wibeatse$-startdec as: $\mbeatsinv(\ar) \subseteq \wibeatse(\argsdec) ⇒ \mbeatsinv(\ar) \subseteq \wibeatse(\args)$.
-Finite defense-$\mbeats$-$\wibeatse$-startdec is insufficient to provide $T_\eta = \iposs$.
-Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_5 \mbeats^\text{fail} \ar_4 \mbeats^\text{fail} \ar_1$.
-Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\mbeats$-$\wibeatse$-startdec is satisfied as there is no cover of the $\mbeats$ attacks to $\ar_1$.
-
-Define Finite defense-$\mbeats$-$\mbeats$-startdec as: $\mbeatsinv(\ar) \subseteq \mbeats(\argsdec) ⇒ \mbeatsinv(\ar) \subseteq \mbeats(\args)$.
-Finite defense-$\mbeats$-$\mbeats$-startdec is insufficient to provide $T_\eta = \iposs$.
-Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar \mbeats^\text{fail} \{\ar_2, \ar_2', …\}$.
-Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\mbeats$-$\mbeats$-startdec is artificially satisfied because of $\ar$.
-Define Finite defense-$\mbeats$-$\mbeats$-subsets as: $\mbeatsinv(\ar) \subseteq \mbeats(\args) ⇒ \mbeatsinv(\ar) \subseteq \mbeats(\args')$ (for any $\args \subseteq \argsdec$).
-Finite defense-$\mbeats$-$\mbeats$-subsets is (rightly) non satisfied in this example.
-
-Define Finite defense-$\wibeatse$-$\wibeatse$-subsets as: $\wibeatseinv(\ar) \subseteq \wibeatse(\args) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args')$.
-Finite defense-$\mbeats$-$\wibeatse$-subsets $⇏$ Finite defense-$\wibeatse$-$\wibeatse$-subsets.
-Consider $\ar_2 \mbeats^\text{fail} \ar_1$ (to be continued…)
-\end{document}

### 2020-07-16 simple.tex
Removed a bit more stuff; changed some commands

@@
 The object of study in a given decision situation is the deliberated preferences of a given individual $i$. 
-A decision situation concerns a topic $\alltopic$, given a set of arguments $\allargs$, given a certain query protocol, and over a certain time frame.
+A decision situation concerns a topic $\allprops$, given a set of arguments $\allargs$, given a certain query protocol, and over a certain time frame.
 The relation $\ileadstost$, to be defined shortly, models the reaction of $i$ to arguments about the topic.
-The decision situation will be defined as a triple $(\alltopic, \allargs, \ileadstost)$ satisfying some conditions to be defined after having presented those three fundamental elements.
+The decision situation will be defined as a triple $(\allprops, \allargs, \ileadstost)$ satisfying some conditions to be defined after having presented those three fundamental elements.
 
-The decision situation relates to a topic denoted by $\alltopic$, which is a set of propositions $\prop \in \alltopic$ about which we are interested of knowing the deliberated preferences of $i$.
+The decision situation relates to a topic denoted by $\allprops$, which is a set of propositions $\prop \in \allprops$ about which we are interested of knowing the deliberated preferences of $i$.
 Propositions are not described further, but are supposedly understandable by $i$ (for example, they could be sentences in some natural language).
-Alternatively, in the case of an analyst helping $i$ to make a decision, $\alltopic$ is a set of propositions about which $i$ is interested to know his own deliberated preferences.
-I assume $\alltopic$ is closed under negation and introduce a symbol $¬$ for negating a proposition: if $\prop \in \alltopic$, then $¬\prop \in \alltopic$, and $¬(¬\prop) = \prop$.
+Alternatively, in the case of an analyst helping $i$ to make a decision, $\allprops$ is a set of propositions about which $i$ is interested to know his own deliberated preferences.
+I assume $\allprops$ is closed under negation and introduce a symbol $¬$ for negating a proposition: if $\prop \in \allprops$, then $¬\prop \in \allprops$, and $¬(¬\prop) = \prop$.
 
@@
 Under that view, $\allargs$ may contain anything that can possibly be considered as an argument by anyone, under the widest possible conception of an argument.
-The notion of deliberated judgment can however also be applied when considering a restricted set of arguments, for example, the arguments that have been put forward by some specific set of experts when talking about the topic $\alltopic$.
+The notion of deliberated judgment can however also be applied when considering a restricted set of arguments, for example, the arguments that have been put forward by some specific set of experts when talking about the topic $\allprops$.
 
@@
 	Consider a decision problem where a set of alternatives $\allalts$ is given, containing food products among which $i$ would like to form a deliberated preference (taking into account the effects of food on health, price, pleasure, morality issues related to the production process, and so on).
-The topic could be defined as $\alltopic$ = $\set{\prop_\alt, ¬\prop_\alt, \forall \alt \in \allalts}$, where $\prop_\alt$ is the proposition according to which $\alt$ is one of the best alternatives among $\allalts$ (there is no strictly better alternatives among $\allalts$, from $i$’s point of view), and $¬\prop_\alt$ is the proposition according to which $\alt$ is not one of the best alternatives among $\allalts$ (some $\alt' \in \allalts$ is a strictly better alternative, from $i$’s point of view).
+The topic could be defined as $\allprops$ = $\set{\prop_\alt, ¬\prop_\alt, \forall \alt \in \allalts}$, where $\prop_\alt$ is the proposition according to which $\alt$ is one of the best alternatives among $\allalts$ (there is no strictly better alternatives among $\allalts$, from $i$’s point of view), and $¬\prop_\alt$ is the proposition according to which $\alt$ is not one of the best alternatives among $\allalts$ (some $\alt' \in \allalts$ is a strictly better alternative, from $i$’s point of view).
 	The set $\allargs$ is defined as the set of all strings, because in this example it is considered acceptable to restrict arguments to those that can take a textual form.
@@
 
-Define $\Phi = \alltopic × \set{\text{possible}, \text{sure}}$. Elements in $\Phi$ will also be called propositions, which should create no ambiguity. 
+Define $\Phi = \allprops × \set{\text{possible}, \text{sure}}$. Elements in $\Phi$ will also be called propositions, which should create no ambiguity. 
 The relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$, pronounced “always leads to”, has the following semantics.
@@
 \begin{definition}[Decision situation]
-	A decision situation is a topic $\alltopic$ closed under negation, a set of arguments $\allargs$, an “always leads to” relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$ satisfying (A1) and (A2) and using unordered pairs of arguments, $\Phi$ being the set of propositions $\alltopic × \set{\text{sure}, \text{possible}}$.
+	A decision situation is a topic $\allprops$ closed under negation, a set of arguments $\allargs$, an “always leads to” relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$ satisfying (A1) and (A2) and using unordered pairs of arguments, $\Phi$ being the set of propositions $\allprops × \set{\text{sure}, \text{possible}}$.
 \end{definition}
@@
 The set designates all possible answers over time and over different order of asking the queries.
-Hence, given $\prop \in \alltopic$, define a relation $\ileadsto^\prop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadsto^\prop C$, with $C \subseteq \set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind.
-The querying protocol is supposedly made so that for any $\prop \in \alltopic$, $\ileadsto^\prop = \ileadsto^{¬\prop}$.
+Hence, given $\prop \in \allprops$, define a relation $\ileadsto^\prop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadsto^\prop C$, with $C \subseteq \set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind.
+The querying protocol is supposedly made so that for any $\prop \in \allprops$, $\ileadsto^\prop = \ileadsto^{¬\prop}$.
 
@@
 
-Define $\ileadstost$ from $\ileadsto^\prop$ as follows, for any $\prop \in \alltopic$: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadsto^\prop C$ with $C \subseteq \set{\prop, \text{both}}$; and $(\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadsto^\prop \set{\prop}$.
+Define $\ileadstost$ from $\ileadsto^\prop$ as follows, for any $\prop \in \allprops$: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadsto^\prop C$ with $C \subseteq \set{\prop, \text{both}}$; and $(\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadsto^\prop \set{\prop}$.
 
@@
 Thus, elements $\phi \in \Phi$ may be considered as simply equal to $\prop$ or $¬\prop$, as $(\prop, \text{sure})$ is treated exactly as $(\prop, \text{possible})$.
-
-\subsection{Deliberated preference}
-The following important definition is required in order to define the deliberated preference of $i$.
-An argument $\ar$ is decisive for $\phi$, in short, $\phi\text{-dec}$ iff $\forall \ar' \in \allargs: (\ar', \ar) \ileadstost \phi$.
-\footnote{Equivalently: $\ar \ \phidec ⇔ [\ileadstostinv(\phi)](\ar) = \allargs$, and $\exists \ar \ \phidec ⇔ [\ileadstostinv(\phi)]^{-1}(\allargs) ≠ \emptyset$.}
-I also say that $\ar$ is $\propsuredec$, $\proppossdec$, or $¬\proppossdec$, when $\phi=(\prop, \text{sure})$, $\phi=(\prop, \text{possible})$, or $\phi=(¬\prop, \text{possible})$, respectively.
-\footnote{$\propsuredec ⇔ \forall \ar': (\ar', \ar) \ileadstosst \prop ⇔ \forall \ar': ¬[(\ar', \ar) \ileadstope ¬\prop]$, $\proppossdec ⇔ \forall \ar': (\ar', \ar) \ileadstopst \prop$.
-Note that “both” ≠ “we donno”: in case “both”, we know how to prove that both are reasonable options, in the sense that neither is certain.
-We have excluded some possibilities (and some other model could disagree with the “both” conclusion).}
-
-\begin{proposition}
-	\label{thm:nocontrdec}
-	For any decision situation, a) $\exists \ar \ \phidec ⇒ \nexists \ar' \ ¬\phidec$ and b) $\exists \ar \ \propsuredec ⇒ \nexists \ar' \ ¬\propsuredec$.
-\end{proposition}
-\begin{proof}
-	About a), when $\ar$ is $\phidec$, given any $\ar'$, $(\ar, \ar') \ileadstost \phi$ hence $(\ar, \ar') \ileadstoe \phi$ (using (A1)), hence $(\ar, \ar') \nileadstost ¬\phi$.
-b) obtains similarly using (A2).
-\end{proof}
-
-The deliberated preference of $i$ maps each pair $(\prop, ¬\prop)$ to one among four possibilities, depending on the existence of decisive arguments supporting the propositions about $\prop$.
-The mapping is defined as follows.
-\begin{description}
-	\item[$\prop$ is sure] iff $\exists \ar \ \propsuredec$
-	\item[$¬\prop$ is sure] iff $\exists \ar \ ¬\propsuredec$
-	\item[both $\prop$ and $¬\prop$ are possible] iff $\exists \ar \ \proppossdec$ and $\exists \ar \ ¬\proppossdec$
-	\item[$(\prop, ¬\prop)$ is undecided] iff neither $\prop$ is sure, nor $¬\prop$ is sure, nor both are possible.
-\end{description}
-\Cref{thm:nocontrdec} shows that the cases are separate.
-\footnote{Example of $(\prop, ¬\prop)\text{-undecided}$: $\forall (\ar, \ar'), (\ar, \ar') \ileadstoe (¬\prop, \text{sure}), (\ar, \ar') \ileadstoe (\prop, \text{sure})$.}
-\footnote{Example of $\overline{¬\prop\text{-CC}} ∧ \prop \in \iposs$ (thus with $\prop\text{-CC}$ and no $(\prop, ¬\prop)$-unstability): $\forall (\ar, \ar'), (\ar, \ar') \ileadstose \prop, (\ar, \ar') \ileadstope ¬\prop, (\ar, \ar') \ileadstopst \prop$.
-In such a situation, it is unclear whether $\prop$ holds rather than $¬\prop$ or both $\prop$ and $¬\prop$.}
-\footnote{Something like Axiom JU should be sufficient for CC.
-We say $(\ar, \ar')$ is $\prop$-unstable iff $(\ar, \ar') \ileadstose \prop ∧ (\ar, \ar') \ileadstose ¬\prop$.
-JU: If $(\ar, \ar')$ is $\prop$-unstable, then $\exists \ar_2 \in \allargs$ such that for $(\ar_1, \ar_0) = (\ar, \ar')$ or for $(\ar_1, \ar_0) = (\ar', \ar)$, $\ar_2$ attacks decisively $\ar_1$, where we mean by this that $\ar_2$ combined with $\ar_0$ is decisive.
-Means that if not CC, then not JU.
-Hence, infinite discussion happens, or irreducible unstability.
-Or, the memory buffer of $i$ is too short to hold adequate reinstated arguments, in which case our approach based on decisive arguments is not adequate.}
-
-It should be clear that the validity of the conclusions obtained from any theory of deliberated preference rests on the acceptance of this just given normative definition, namely, it is to be considered meaningful that the deliberated preference of $i$ be defined in such a way, given the query protocol used for defining $\ileadstost$ in a particular application.
-
-\commentOC{TODO}
-We want to leave “undecided” as an option: the model takes no position, does not know about $(t, ¬t)$.
-But we want to exclude $t$ possible and $¬t$ unknown.
-Thus $t$ possible should imply $¬t$ possible or $t$ sure.
-If this holds, we can simplify the status of the propositions: only determine whether $t$ is possible for all $t \in \alltopic$, and from there, we know everything.
-This result can be obtained with: assume $s$ decisive for $t$ poss and no $s$ is decisive for $¬t$ poss, then, for some $(s_1, s)$ leading to $t$ sure and $(s_2, s)$ leading to $\set{t, ¬t}$, it is possible to form $(s_2, s_1, s)$, and if this leads to $t$ sure, it should imply that $s + s_1$ is decisive for $t$ sure; and if this leads to $¬t$ possible, then this should imply that $s+s_2$ is decisive for $¬t$ possible.
-
-This information is summarized by defining a subset $\iPhi \subseteq \Phi$ of propositions that represent $i$’s deliberated preference, defined as follows.
-\begin{description}
-	\item[$\prop$ is sure] ⇒ $(\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \in \iPhi ∧ (¬\prop, \text{possible}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$
-	\item[both $\prop$ and $¬\prop$ are possible] ⇒ $(\prop, \text{possible}) \in \iPhi ∧ (¬\prop, \text{possible}) \in \iPhi ∧ (\prop, \text{sure}) \notin \iPhi ∧ (¬\prop, \text{sure}) \notin \iPhi$
-	\item[$(\prop, ¬\prop)$ is undecided] ⇒ $\phi \notin \iPhi$ for all $\phi$ about $\prop$.
-\end{description}
-Because this defines unequivocally the membership of every proposition about $\prop$ for every $\prop \in \alltopic$, this suffices to define $\iPhi$; and it follows that the reverse implications hold as well.
-
-The following propositions can help get convinced that the proposed definition of deliberated preference makes sense.
-\begin{proposition}
-	a) $\phi \in \iPhi ⇒$ some $\ar$ is $\phidec$.
-b) $(\prop, \text{possible}) \in \iPhi$ iff $\exists \ar \ \proppossdec ∧ (\exists \ar \ \propsuredec ∨ \exists \ar \ ¬\proppossdec)$.
-c) $(\prop, \text{sure}) \in \iPhi ⇒ (\prop, \text{possible}) \in \iPhi$.
-d) $\phi \in \iPhi ⇒ ¬\phi \notin \iPhi$.
-e) $(\prop, ¬\prop)$ undecided $⇔ \phi \notin \iPhi ∧ ¬\phi \notin \iPhi$ for some $\phi$ about $\prop$.
-f) If $\phi \in \iPhi$ for some $\phi$ about $\prop$, then $\phi \in \iPhi ⇔ ¬\phi \notin \iPhi$ for all $\phi$ about $\prop$.
-g) If $\ileadstost$ does not distinguish sure from possible, no pair of proposition is mapped to “both are possible”.
-\end{proposition}
-\begin{proof}
-	a) is a consequence of A2.
-b) and c) follow from the definition of $\iPhi$.
-d) is obtained using a), \cref{thm:nocontrdec}, and the contrapositive of a).
-About e), we must show that $\phi \notin \iPhi ∧ ¬\phi \notin \iPhi$ for some $\phi$ about $\prop$ implies $\phi' \notin \iPhi$ for all $\phi'$ about $\prop$.
-Assume $\phi=(l, \text{possible})$ and $¬\phi = (¬l, \text{sure})$ are not in $\iPhi$, with $l = t$ or $l = ¬t$.
-We need to prove that $(l, \text{sure})$ and $(¬l, \text{possible})$ are not in $\iPhi$ either.
-We obtain $(l, \text{sure}) \notin \iPhi$ using the contrapositive of c).
-And $(¬l, \text{possible}) \notin \iPhi$ because $(¬l, \text{possible}) \in \iPhi$ would require another $\phi'$ about $\prop$ to be present in $\iPhi$, as can be checked from the definition of $\iPhi$.
-f) follows from d) together with the fact that $(\prop, ¬\prop)$ is (by definition) not undecided when $\phi \in \iPhi$ for some $\phi$ about $\prop$, hence, from e), $\phi \in \iPhi ∨ ¬\phi \in \iPhi$.
-Finally, g) is because in that case, $\exists \ar \ \proppossdec ⇔ \exists \ar \ \propsuredec$, thus using \cref{thm:nocontrdec}, $\exists \ar \ \proppossdec ⇒ \nexists \ar' \ ¬\proppossdec$.
-\end{proof}
-
-It is important to remark that when the query protocol does not admit observation of “both”, thus, when $\ileadstost$ does not distinguish sure from possible, it does \emph{not} follow that $i$ is sure of either $\prop$ or $¬\prop$ for every pair of proposition: the “undecided” case will hold whenever $i$ considers no argument as sufficiently strong to determine a decisive preference (assuming that in that case, $i$ at least sometimes alternates his choice).
-Admittedly, it might also happen that $i$ is really indifferent between $\prop$ and $¬\prop$ but still systematically chooses, say, $\prop$ over $¬\prop$, in which case it will be (somewhat) erroneously concluded that $\prop \in \iPhi$.
-This is the price to pay for using protocols that do not allow to observe indifference.
-Observe however that (depending on the application) this error might be considered not harmful, as the obtained model will be faithful to $i$’s behavior after deliberation.
 
@@
 So that the model only has to prove the weaker existential claim.
+
+It is important to remark that when the query protocol does not admit observation of “both”, thus, when $\ileadstost$ does not distinguish sure from possible, it does \emph{not} follow that $i$ is sure of either $\prop$ or $¬\prop$ for every pair of proposition: the “undecided” case will hold whenever $i$ considers no argument as sufficiently strong to determine a decisive preference (assuming that in that case, $i$ at least sometimes alternates his choice).
+Admittedly, it might also happen that $i$ is really indifferent between $\prop$ and $¬\prop$ but still systematically chooses, say, $\prop$ over $¬\prop$, in which case it will be (somewhat) erroneously concluded that $\prop \in \iPhi$.
+This is the price to pay for using protocols that do not allow to observe indifference.
+Observe however that (depending on the application) this error might be considered not harmful, as the obtained model will be faithful to $i$’s behavior after deliberation.
 
@@
 Also, from the previous definition, $g(\ar_0)(\ar_0 + \argsd_2) = dom(f^{-1}(\ar_0 + \argsd_2) \cap (\allargs × \set{\ar_0})) = {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$ because $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \argsd_2) ⇔ \exists \ar_2 \in \ar_0 + \argsd_2 \suchthat \ar_2 \in f(\ar_1, \ar_0) ⇔ \ar_1 \gbeats \ar_0 \land \exists \ard \in \argsd_2 \suchthat \ard \gbeats \ar_1$.
-\commentOC{Could be false. Define }
+\commentOC{Could be false.}
 
@@
 
-Given any $(\alltopic, ¬, \allargs, I)$, an \emph{observation protocol} is a binary tree whose non-leaf nodes are among $I × \allhist × \Phi$ and whose two edges out of any non leaf node are labeled by “yes” and “no”; the leaf nodes being simply $\emptyset$.
+Given any $(\allprops, ¬, \allargs, I)$, an \emph{observation protocol} is a binary tree whose non-leaf nodes are among $I × \allhist × \Phi$ and whose two edges out of any non leaf node are labeled by “yes” and “no”; the leaf nodes being simply $\emptyset$.
 The observation protocol is said to assume memory iff for each non-leaf node $n = (i, \hist, \phi)$ about $i$, any node $n' = (i, {\hist}', \phi')$ about $i$ that is further down the tree continues the history, that is, the sequence ${\hist}'$ starts with $\hist$.
@@
 
-Given any $(\alltopic, ¬, \allargs, I)$, a \emph{normative claim} about $(\alltopic, ¬, \allargs, I)$ (or about $\allargs$, when the other defined objects are left implicit) is any first-order logic proposition involving the atoms $[(\hist, \phi) \in {\ileadstoe[i]}], \hist \in \allhist, \phi \in \Phi$ which, together with the axioms, permits to deduce that $\phi \in \iPhi$ for some $i \in I$ and $\phi \in \Phi$.
+Given any $(\allprops, ¬, \allargs, I)$, a \emph{normative claim} about $(\allprops, ¬, \allargs, I)$ (or about $\allargs$, when the other defined objects are left implicit) is any first-order logic proposition involving the atoms $[(\hist, \phi) \in {\ileadstoe[i]}], \hist \in \allhist, \phi \in \Phi$ which, together with the axioms, permits to deduce that $\phi \in \iPhi$ for some $i \in I$ and $\phi \in \Phi$.
 The claim is said to be \emph{about} the given set $\allargs$.
@@
 \begin{proposition}[Trivial claims are not falsifiable]
-	Given any $(\alltopic, ¬, \allargs ≠ \emptyset, I)$, no minimal normative claim is falsifiable.
+	Given any $(\allprops, ¬, \allargs ≠ \emptyset, I)$, no minimal normative claim is falsifiable.
 \end{proposition}
@@
 \begin{proposition}[Minimal non-trivial claims are not falsifiable]
-	Given any $(\alltopic, ¬, \allargs, I), \card{\allargs} ≥ 2$, no minimal normative claim is falsifiable.
+	Given any $(\allprops, ¬, \allargs, I), \card{\allargs} ≥ 2$, no minimal normative claim is falsifiable.
 \end{proposition}

### 2020-07-16 simple.tex
Typo proof
Rm old commands
Simplified and sorted commands

@@
 (The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
-As usual with binary relations, $\hist \nileadsto[i] \phi$ means $(\hist, \phi) \notin {\ileadsto[i]}$.
+As usual with binary relations, $\hist \nileadstoi \phi$ means $(\hist, \phi) \notin {\ileadstoi}$.
 
@@
 Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstosti \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstosti \phi$.
-
-To lighten notations, $\ileadstoi$ and $\ileadstosti$ will generally be denoted by $\ileadsto$ and $\ileadstosts$, these symbols being understood as the result of a function of $i$. 
-When the symbol $\ileadsto$ or $\ileadstosts$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.
 
@@
 
-	To prove the theorem, build a finite sequence of arguments in $\gargs[i, \phi]$, starting with any $\ar_0 \in \ileadstoinv(\phi)$.
+	To prove the theorem, build a finite sequence of arguments in $\gargs[i, \phi]$, starting with any $\ar_0 \in \gleadstoinv(\phi)$.
 Observe that $\ar_0 \in \gargs[i, \phi]$.
@@
 Defends $\prop$.
-$\exists \ar_1 \in \args_\eta \suchthat \ar_1 \ileadstoe \prop$.
-Then, $\forall \ar_2 \in \gargs \suchthat (\ar_2, \ar_1) \ileadstoe ¬\prop: \exists \ar_3 \in \args_\eta \suchthat (\ar_3, \ar_2) \ileadstoe \prop.$
+$\exists \ar_1 \in \args_\eta \suchthat \ar_1 \ileadstoi \prop$.
+Then, $\forall \ar_2 \in \gargs \suchthat (\ar_2, \ar_1) \ileadstoi ¬\prop: \exists \ar_3 \in \args_\eta \suchthat (\ar_3, \ar_2) \ileadstoi \prop.$
 
 \section{Decision situation}
-\newcommand{\alltopic}{T^*}
+\NewDocumentCommand \ileadsto { o }{%
+	\IfValueTF{#1}{%
+		⇝^{#1}%
+	}{%
+		⇝%
+	}%
+}
+\NewDocumentCommand \nileadsto { o }{%
+	\IfValueTF{#1}{%
+		\not⇝^{#1}%
+	}{%
+		\not⇝%
+	}%
+}
+\NewDocumentCommand{\ileadstost}{O{}}{⇝^{#1}_\forall}
+\NewDocumentCommand{\ileadstosts}{}{⇝_*}
+\NewDocumentCommand{\ileadstos}{}{\overset{s}{⇝_i}}
+\NewDocumentCommand{\ileadstostw}{O{}}{⇝^\mathit{w}_\forall}
+\NewDocumentCommand{\ileadstostp}{O{}}{⇝^\mathit{pos}_\forall}
+\NewDocumentCommand{\nileadstosts}{}{\not⇝_*}
+\NewDocumentCommand{\Ti}{}{T_i}
+\NewDocumentCommand{\nileadstost}{O{}}{\not⇝^{#1}_\forall}
+\NewDocumentCommand{\ileadstoe}{O{}}{⇝^{#1}_\exists}
+\NewDocumentCommand{\nileadstoe}{O{}}{\not⇝^{#1}_\exists}
+\NewDocumentCommand{\ibeatse}{O{}}{⊳^{#1}_\exists}
+\NewDocumentCommand \ibeatseinv { o }{
+	\IfValueTF{#1}{%
+		{⊳_\exists^{#1}}^{-1}%
+	}{%
+		⊳_\exists^{-1}%
+	}%
+}
+\NewDocumentCommand{\zar}{}{\mathbf{0}}%zero, or empty, argument
+\NewDocumentCommand{\mPhi}{}{\Phi_\gamma}
+\NewDocumentCommand{\argsd}{}{S^\mathit{d}}
 
@@
 	\item $\ar_2' = \text{“Ask my grandmother”}$
-	\item $\ar_1 \mbeats \ar_0$, $\ar_1' \mbeats \ar_0$
-	\item $\ar_2 \mbeats \ar_1$, $\ar_2' \mbeats \ar_1'$
-	\item $\ar_0 + \ar_2 \mbeats \ar_1$
-	\item $\ar_1' \mbeats \ar_0 + \ar_2$
-	\item $\ar_0 + \ar_2' \mbeats \ar_1'$
-	\item $\ar_1 \mbeats \ar_0 + \ar_2'$
-	\item $\ar_0 + \ar_2 + \ar_2' \mbeats \ar_1$
-	\item $\ar_0 + \ar_2 + \ar_2' \mbeats \ar_1'$
+	\item $\ar_1 \gbeats \ar_0$, $\ar_1' \gbeats \ar_0$
+	\item $\ar_2 \gbeats \ar_1$, $\ar_2' \gbeats \ar_1'$
+	\item $\ar_0 + \ar_2 \gbeats \ar_1$
+	\item $\ar_1' \gbeats \ar_0 + \ar_2$
+	\item $\ar_0 + \ar_2' \gbeats \ar_1'$
+	\item $\ar_1 \gbeats \ar_0 + \ar_2'$
+	\item $\ar_0 + \ar_2 + \ar_2' \gbeats \ar_1$
+	\item $\ar_0 + \ar_2 + \ar_2' \gbeats \ar_1'$
 \end{itemize}

### 2020-07-16 simple.tex
More simplification of commands

@@
 \subsection{Definition}
-A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoi)_{i \in I})$, 
-with ${\ileadstoi} \subseteq \allhist × \Phi$, 
+A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadsto)_{i \in I})$, 
+with ${\ileadsto} \subseteq \allhist × \Phi$, 
 where $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\mathit{poss}, \mathit{sure}}$.
@@
 (The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
-As usual with binary relations, $\hist \nileadstoi \phi$ means $(\hist, \phi) \notin {\ileadstoi}$.
+As usual with binary relations, $\hist \nileadstoi \phi$ means $(\hist, \phi) \notin {\ileadsto}$.
 
-Given $i \in I, \phi \in \Phi, \hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadstoi \phi \land \hist \nileadstoi ¬\phi$.
+Given $i \in I, \phi \in \Phi, \hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadsto \phi \land \hist \nileadstoi ¬\phi$.
 Define $\hist \ileadstosti \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
@@
 	Protocol coherence is satisfied by definition of $\ileadstosti$.
-Indeed, if for some $\ar \in \allargs$, $\ar \ileadstosti \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoi ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstosti ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadstoi ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadstoi ¬\phi$.
+Indeed, if for some $\ar \in \allargs$, $\ar \ileadstosti \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoi ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstosti ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\phi$.
 \end{proof}
@@
 \begin{definition}[Theory completeness]
-	$\forall \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstoi \phi] \lor [\exists \ar \in \allargs \suchthat \ar \ileadstoi ¬\phi]$.
+	$\forall \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadsto \phi] \lor [\exists \ar \in \allargs \suchthat \ar \ileadsto ¬\phi]$.
 \end{definition}
@@
 Defends $\prop$.
-$\exists \ar_1 \in \args_\eta \suchthat \ar_1 \ileadstoi \prop$.
-Then, $\forall \ar_2 \in \gargs \suchthat (\ar_2, \ar_1) \ileadstoi ¬\prop: \exists \ar_3 \in \args_\eta \suchthat (\ar_3, \ar_2) \ileadstoi \prop.$
+$\exists \ar_1 \in \args_\eta \suchthat \ar_1 \ileadsto \prop$.
+Then, $\forall \ar_2 \in \gargs \suchthat (\ar_2, \ar_1) \ileadsto ¬\prop: \exists \ar_3 \in \args_\eta \suchthat (\ar_3, \ar_2) \ileadsto \prop.$
 
-\section{Decision situation}
-\NewDocumentCommand \ileadsto { o }{%
-	\IfValueTF{#1}{%
-		⇝^{#1}%
-	}{%
-		⇝%
-	}%
-}
-\NewDocumentCommand \nileadsto { o }{%
-	\IfValueTF{#1}{%
-		\not⇝^{#1}%
-	}{%
-		\not⇝%
-	}%
-}
-\NewDocumentCommand{\ileadstost}{O{}}{⇝^{#1}_\forall}
-\NewDocumentCommand{\ileadstosts}{}{⇝_*}
-\NewDocumentCommand{\ileadstos}{}{\overset{s}{⇝_i}}
-\NewDocumentCommand{\ileadstostw}{O{}}{⇝^\mathit{w}_\forall}
-\NewDocumentCommand{\ileadstostp}{O{}}{⇝^\mathit{pos}_\forall}
-\NewDocumentCommand{\nileadstosts}{}{\not⇝_*}
-\NewDocumentCommand{\Ti}{}{T_i}
-\NewDocumentCommand{\nileadstost}{O{}}{\not⇝^{#1}_\forall}
+\section{Next}
 \NewDocumentCommand{\ileadstoe}{O{}}{⇝^{#1}_\exists}
 \NewDocumentCommand{\nileadstoe}{O{}}{\not⇝^{#1}_\exists}
-\NewDocumentCommand{\ibeatse}{O{}}{⊳^{#1}_\exists}
-\NewDocumentCommand \ibeatseinv { o }{
-	\IfValueTF{#1}{%
-		{⊳_\exists^{#1}}^{-1}%
-	}{%
-		⊳_\exists^{-1}%
-	}%
-}
-\NewDocumentCommand{\zar}{}{\mathbf{0}}%zero, or empty, argument
-\NewDocumentCommand{\mPhi}{}{\Phi_\gamma}
-\NewDocumentCommand{\argsd}{}{S^\mathit{d}}
-
-The object of study in a given decision situation is the deliberated preferences of a given individual $i$. 
-A decision situation concerns a topic $\allprops$, given a set of arguments $\allargs$, given a certain query protocol, and over a certain time frame.
-The relation $\ileadstost$, to be defined shortly, models the reaction of $i$ to arguments about the topic.
-The decision situation will be defined as a triple $(\allprops, \allargs, \ileadstost)$ satisfying some conditions to be defined after having presented those three fundamental elements.
-
-The decision situation relates to a topic denoted by $\allprops$, which is a set of propositions $\prop \in \allprops$ about which we are interested of knowing the deliberated preferences of $i$.
-Propositions are not described further, but are supposedly understandable by $i$ (for example, they could be sentences in some natural language).
-Alternatively, in the case of an analyst helping $i$ to make a decision, $\allprops$ is a set of propositions about which $i$ is interested to know his own deliberated preferences.
-I assume $\allprops$ is closed under negation and introduce a symbol $¬$ for negating a proposition: if $\prop \in \allprops$, then $¬\prop \in \allprops$, and $¬(¬\prop) = \prop$.
-
-With the decision situation comes also a set of all arguments $\allargs$.
-This set contains all the arguments that may possibly be considered relevant by $i$ for his decision problem, and possibly more.
-Importantly, the notion of deliberated preferences does not require to constrain a priori $\allargs$ to some set of arguments that would fit some precise notion of relevancy, coherence, or even well-formedness.
-This permits to avoid introducing inadequate normative principles into the deliberated preferences: only the individual $i$ is then considered legitimate to dictate what is a relevant argument.
-Under that view, $\allargs$ may contain anything that can possibly be considered as an argument by anyone, under the widest possible conception of an argument.
-The notion of deliberated judgment can however also be applied when considering a restricted set of arguments, for example, the arguments that have been put forward by some specific set of experts when talking about the topic $\allprops$.
-
-The set $\allargs$ may be infinite or very large: as we will see, thanks to our falsificationist approach, there is no need to be able to explore it entirely.
-The set of arguments contains at least the empty argument, denoted by $\zar$.
-
-\begin{example}
-	Consider a decision problem where a set of alternatives $\allalts$ is given, containing food products among which $i$ would like to form a deliberated preference (taking into account the effects of food on health, price, pleasure, morality issues related to the production process, and so on).
-The topic could be defined as $\allprops$ = $\set{\prop_\alt, ¬\prop_\alt, \forall \alt \in \allalts}$, where $\prop_\alt$ is the proposition according to which $\alt$ is one of the best alternatives among $\allalts$ (there is no strictly better alternatives among $\allalts$, from $i$’s point of view), and $¬\prop_\alt$ is the proposition according to which $\alt$ is not one of the best alternatives among $\allalts$ (some $\alt' \in \allalts$ is a strictly better alternative, from $i$’s point of view).
-	The set $\allargs$ is defined as the set of all strings, because in this example it is considered acceptable to restrict arguments to those that can take a textual form.
-\end{example}
-
-Define $\Phi = \allprops × \set{\text{possible}, \text{sure}}$. Elements in $\Phi$ will also be called propositions, which should create no ambiguity. 
-The relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$, pronounced “always leads to”, has the following semantics.
-Whenever $(\ar, \ar') \ileadstost (\prop, \text{sure})$, $i$ always considers that $\prop$ is sure (meaning that $¬\prop$ is excluded), when presented with these two arguments, and whenever $(\ar, \ar') \ileadstost (\prop, \text{possible})$, $i$ always considers that $\prop$ is “at least” possible (meaning that $¬\prop$ may be possible as well), when presented with these two arguments.
-In both cases, the term “always” means that the consideration is stable over time, including after having presented other arguments to $i$.
-Two query protocols presented below will illustrate how these semantics might be satisfied. 
-However, I voluntarily leave the querying protocol not precisely specified in general, as multiple reasonable choices are possible.
-The results of this article depend only on assumptions about $\ileadstost$.
-
-Define the negation operator $¬$ over $\Phi$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
-It follows that $¬¬\phi = \phi$.
-Write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstost ¬\phi$.
-The relation $\ileadstoe$ is pronounced “sometimes leads to”.
-A proposition $\phi$ is about $\prop$ iff $\phi \in \{\prop, ¬\prop\} × \{\text{possible}, \text{sure}\}$.
-
-The pair $(\ar, \ar')$ is to be understood as unordered (thus $(\ar, \ar') \ileadstost \prop ⇔ (\ar', \ar) \ileadstost \prop$).
-
-\begin{definition}[Decision situation]
-	A decision situation is a topic $\allprops$ closed under negation, a set of arguments $\allargs$, an “always leads to” relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$ satisfying (A1) and (A2) and using unordered pairs of arguments, $\Phi$ being the set of propositions $\allprops × \set{\text{sure}, \text{possible}}$.
-\end{definition}
-
-\subsection{Query protocols}
-As vNM aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher.” The fundamental element here is the reaction of $i$ to arguments, which will serve as the informational basis to define $\ileadstost$.
-Given a proposition $\prop$ and two arguments $\ar, \ar' \in \allargs$, a query consists in presenting both arguments to $i$ and observing which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind: is it that $\prop$ holds, that $¬\prop$ holds, or that both are possible?
-The third possibility allows for the case where no argument appears more decisive than the other one.
-
-It is also necessary to capture the evolution of the position of $i$ towards arguments over time: a repeated query using a given pair of arguments may yield different answers, for example because the repeated question has been interleaved with another query containing other arguments (which $i$ may still have in mind when answering the second repetition), or for any other known or unknown reason.
-The important information for us is the \emph{set} of answers that $i$ could give to a query involving two given arguments and a given topic, among the set $\{\prop, ¬\prop, \text{both}\}$.
-The set designates all possible answers over time and over different order of asking the queries.
-Hence, given $\prop \in \allprops$, define a relation $\ileadsto^\prop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadsto^\prop C$, with $C \subseteq \set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind.
-The querying protocol is supposedly made so that for any $\prop \in \allprops$, $\ileadsto^\prop = \ileadsto^{¬\prop}$.
-
-This information is only indirectly observable: for example, if $(\ar, \ar') \ileadsto^\prop \{\prop\}$, a querier will never know more than $(\ar, \ar') \ileadsto^\prop C$ with $\prop \in C \subseteq \set{\prop, ¬\prop, \text{both}}$.
-Also, it may be only possible to test one ordering of the queries (assuming that $i$ forgets over time might permit to test different orderings, but this assumption might be unrealistic).
-In some cases, it may even be only possible to test a single query with a given individual.
-This limitation of our observation will not be a problem for the results of this article.
-Intuitively, this bears on the fact that, first, theories apply to multiple individuals, and second, if a theory claims that $(\ar, \ar') \ileadsto^\prop \{\prop\}$, then either this claim is correct, or it is falsifiable, in the sense that there is a possibility of observing a contradiction to its claim.
-
-To be more concrete, one possible choice of a query protocol, when arguments and propositions are strings, is to read both arguments to $i$, together with $\prop$, and ask $i$ to verbally report the choice he opts for among the three possibilities.
-Another is to present both arguments and ask $i$ to pick an item among some choice set and make the choice correspond to a validation of $\prop$ or $¬\prop$, possibly even letting the choice engage $i$, for example telling $i$ that she may keep the object of choice (this is illustrated in \cref{ex:pick}).
-This second possibility is especially interesting as it makes the protocol partially observable in the restricted sense usually appreciated in revealed preferences approaches.
-Note that depending on the protocol, the choice “both” is not necessarily observable (more about this below).
-%In that case, the semantics of $\prop$ and $¬\prop$ relatedly change: instead of meaning that $\prop$ is definitely the 
-%Indeed, \citet{tversky_intransitivity_1969} note that individuals “are not perfectly consistent in their choices.
-When faced with repeated choices between x and y, people often choose x in some instances and y in others.
-Furthermore, such inconsistencies are observed even in the absence of systematic changes in the decision maker’s taste which might be due to learning or sequential effects.
-It seems, therefore, that the observed inconsistencies reflect inherent variability or momentary fluctuation in the evaluative process.” This is an accepted fact of experimental psychology \citep{luce_utility_2000}.
-However, it is reasonable to suspect that fluctuations occur less often, if at all, for some choices.
-For example, facing a choice between tea or coffee, I would virtually never pick tea (all other things being equal).
-We are interested in capturing precisely those kind of preferences.
-
-One can also use $\zar$ as one or both of the arguments, in which case the protocol queries the preference of $i$ given only one or given no argument.
-
-\begin{example}[cont.]
-	\label{ex:pick}
-	Continuing the example, define the querying protocol as, given $\prop_\alt$, presenting two arguments to $i$ and let $i$ choose an item among $\allalts$. $i$ may keep the chosen item. 
-	If $i$ chooses $\alt$, it is considered that $i$ has validated $\prop_\alt$, otherwise, $¬\prop_\alt$. The option “both” is not observable.
-%	Queries are separated by one week at least, which (as supposed in this example) is enough to ensure that no effect of pleasure for variability enter into play. 
-\end{example}
-
-Define $\ileadstost$ from $\ileadsto^\prop$ as follows, for any $\prop \in \allprops$: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadsto^\prop C$ with $C \subseteq \set{\prop, \text{both}}$; and $(\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadsto^\prop \set{\prop}$.
-
-Note that (A1) and (A2) hold.
-
-When “both” is not observable, $\ileadstost$ is defined as: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadsto^\prop \set{\prop}$.
-(A1) and (A2) still hold.
-We say in this case that $\ileadstost$ does not distinguish sure from possible.
-Thus, elements $\phi \in \Phi$ may be considered as simply equal to $\prop$ or $¬\prop$, as $(\prop, \text{sure})$ is treated exactly as $(\prop, \text{possible})$.
-
-\subsection{Example}
-\begin{example}[(cont.)]
-	Returning to the previous example, a theory $T$ could claim that, for all individuals that belong to some given socio-economic situation and that have some given degree (described by the theory in sufficient details that it is possible to determine precisely to which kind of individuals it applies), $(\prop_a, \text{sure})$ is in the deliberated preferences of the individuals, for a given alternative $\alt$ also described by $T$.
-The theory also suggests some argument $\ar$, a text that (according to $T$) will convince any individual (fitting the description) that $\prop_\alt$ holds, thus, that $\alt$ is a “good” food product for him.
-The theory can be put to the test by picking an individual fitting the description, presenting the argument together with any other argument (for example, proposed by another theory), and observing whether $i$ is convinced.
-$T$ resists to such a falsification test if $i$ is convinced.
-According to a previous theorem, $T$ tells the truth if it would resist to any possible falsification test.
-(This is impossible to definitely make sure of.)
-\end{example}
-This example illustrates a difference between this proposal and the classical revealed approach: it could be that $T$ tells the truth even though its claim does not correspond to the revealed preference of some individuals, thus that, given no argument, some individuals would consider $a$ as dominated by another alternative in the set considered.
-It also illustrates a difference between this proposal and persuasion: the goal of $T$ is not merely to convince $i$ (possibly by using its lack of knowledge of any counter-argument to what $T$ says), but to resist any falsification attempt.
-Thus, $T$ should be confronted to arguments coming from as varied perspectives as possible, in order to give confidence that it tells the truth.
-
-\section{Next}
+\NewDocumentCommand{\ileadstost}{O{}}{⇝^{#1}_\forall}
+\NewDocumentCommand{\nileadstost}{O{}}{\not⇝^{#1}_\forall}
 Define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.
@@
 
-Discuss variant with an empirical claim: $\hist \ileadstoi \phi ⇒ \hist \nileadstoi ¬\phi$; and change \cref{ax:norm}: $[\forall \hist, \hist \ileadstoi \propposs] ⇒ \propposs \in \iPhi$, … This is essentially what will be done in the following, I suppose.
+Discuss variant with an empirical claim: $\hist \ileadsto \phi ⇒ \hist \nileadstoi ¬\phi$; and change \cref{ax:norm}: $[\forall \hist, \hist \ileadsto \propposs] ⇒ \propposs \in \iPhi$, … This is essentially what will be done in the following, I suppose.
 
@@
 
-Any normative theory of the form $(\allprops_\allalts, ¬_\allalts, \allargs, I, (\ileadstoi)_{i \in I})$, for some sets $\allargs$ and $I$, is called a normative theory about $\allalts$.
+Any normative theory of the form $(\allprops_\allalts, ¬_\allalts, \allargs, I, (\ileadsto)_{i \in I})$, for some sets $\allargs$ and $I$, is called a normative theory about $\allalts$.
 
@@
 TODO It is possible to determine whether a given function $\tau$ is a transitive argument builder empiricially. But not to prove empirically that a normative theory is not transitive.
+
+\section{Decision situation}
+\NewDocumentCommand{\ileadstoprop}{}{⇝^\prop}
+\NewDocumentCommand{\ileadstonprop}{}{⇝^{¬\prop}}
+\NewDocumentCommand \nileadsto { o }{%
+	\IfValueTF{#1}{%
+		\not⇝^{#1}%
+	}{%
+		\not⇝%
+	}%
+}
+\NewDocumentCommand{\ileadstosts}{}{⇝_*}
+\NewDocumentCommand{\ileadstos}{}{\overset{s}{⇝_i}}
+\NewDocumentCommand{\ileadstostw}{O{}}{⇝^\mathit{w}_\forall}
+\NewDocumentCommand{\ileadstostp}{O{}}{⇝^\mathit{pos}_\forall}
+\NewDocumentCommand{\nileadstosts}{}{\not⇝_*}
+\NewDocumentCommand{\Ti}{}{T_i}
+\NewDocumentCommand{\ibeatse}{O{}}{⊳^{#1}_\exists}
+\NewDocumentCommand \ibeatseinv { o }{
+	\IfValueTF{#1}{%
+		{⊳_\exists^{#1}}^{-1}%
+	}{%
+		⊳_\exists^{-1}%
+	}%
+}
+\NewDocumentCommand{\zar}{}{\mathbf{0}}%zero, or empty, argument
+\NewDocumentCommand{\mPhi}{}{\Phi_\gamma}
+\NewDocumentCommand{\argsd}{}{S^\mathit{d}}
+
+The object of study in a given decision situation is the deliberated preferences of a given individual $i$. 
+A decision situation concerns a topic $\allprops$, given a set of arguments $\allargs$, given a certain query protocol, and over a certain time frame.
+The relation $\ileadstost$, to be defined shortly, models the reaction of $i$ to arguments about the topic.
+The decision situation will be defined as a triple $(\allprops, \allargs, \ileadstost)$ satisfying some conditions to be defined after having presented those three fundamental elements.
+
+The decision situation relates to a topic denoted by $\allprops$, which is a set of propositions $\prop \in \allprops$ about which we are interested of knowing the deliberated preferences of $i$.
+Propositions are not described further, but are supposedly understandable by $i$ (for example, they could be sentences in some natural language).
+Alternatively, in the case of an analyst helping $i$ to make a decision, $\allprops$ is a set of propositions about which $i$ is interested to know his own deliberated preferences.
+I assume $\allprops$ is closed under negation and introduce a symbol $¬$ for negating a proposition: if $\prop \in \allprops$, then $¬\prop \in \allprops$, and $¬(¬\prop) = \prop$.
+
+With the decision situation comes also a set of all arguments $\allargs$.
+This set contains all the arguments that may possibly be considered relevant by $i$ for his decision problem, and possibly more.
+Importantly, the notion of deliberated preferences does not require to constrain a priori $\allargs$ to some set of arguments that would fit some precise notion of relevancy, coherence, or even well-formedness.
+This permits to avoid introducing inadequate normative principles into the deliberated preferences: only the individual $i$ is then considered legitimate to dictate what is a relevant argument.
+Under that view, $\allargs$ may contain anything that can possibly be considered as an argument by anyone, under the widest possible conception of an argument.
+The notion of deliberated judgment can however also be applied when considering a restricted set of arguments, for example, the arguments that have been put forward by some specific set of experts when talking about the topic $\allprops$.
+
+The set $\allargs$ may be infinite or very large: as we will see, thanks to our falsificationist approach, there is no need to be able to explore it entirely.
+The set of arguments contains at least the empty argument, denoted by $\zar$.
+
+\begin{example}
+	Consider a decision problem where a set of alternatives $\allalts$ is given, containing food products among which $i$ would like to form a deliberated preference (taking into account the effects of food on health, price, pleasure, morality issues related to the production process, and so on).
+The topic could be defined as $\allprops$ = $\set{\prop_\alt, ¬\prop_\alt, \forall \alt \in \allalts}$, where $\prop_\alt$ is the proposition according to which $\alt$ is one of the best alternatives among $\allalts$ (there is no strictly better alternatives among $\allalts$, from $i$’s point of view), and $¬\prop_\alt$ is the proposition according to which $\alt$ is not one of the best alternatives among $\allalts$ (some $\alt' \in \allalts$ is a strictly better alternative, from $i$’s point of view).
+	The set $\allargs$ is defined as the set of all strings, because in this example it is considered acceptable to restrict arguments to those that can take a textual form.
+\end{example}
+
+Define $\Phi = \allprops × \set{\text{possible}, \text{sure}}$. Elements in $\Phi$ will also be called propositions, which should create no ambiguity. 
+The relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$, pronounced “always leads to”, has the following semantics.
+Whenever $(\ar, \ar') \ileadstost (\prop, \text{sure})$, $i$ always considers that $\prop$ is sure (meaning that $¬\prop$ is excluded), when presented with these two arguments, and whenever $(\ar, \ar') \ileadstost (\prop, \text{possible})$, $i$ always considers that $\prop$ is “at least” possible (meaning that $¬\prop$ may be possible as well), when presented with these two arguments.
+In both cases, the term “always” means that the consideration is stable over time, including after having presented other arguments to $i$.
+Two query protocols presented below will illustrate how these semantics might be satisfied. 
+However, I voluntarily leave the querying protocol not precisely specified in general, as multiple reasonable choices are possible.
+The results of this article depend only on assumptions about $\ileadstost$.
+
+Define the negation operator $¬$ over $\Phi$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
+It follows that $¬¬\phi = \phi$.
+Write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstost ¬\phi$.
+The relation $\ileadstoe$ is pronounced “sometimes leads to”.
+A proposition $\phi$ is about $\prop$ iff $\phi \in \{\prop, ¬\prop\} × \{\text{possible}, \text{sure}\}$.
+
+The pair $(\ar, \ar')$ is to be understood as unordered (thus $(\ar, \ar') \ileadstost \prop ⇔ (\ar', \ar) \ileadstost \prop$).
+
+\begin{definition}[Decision situation]
+	A decision situation is a topic $\allprops$ closed under negation, a set of arguments $\allargs$, an “always leads to” relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$ satisfying (A1) and (A2) and using unordered pairs of arguments, $\Phi$ being the set of propositions $\allprops × \set{\text{sure}, \text{possible}}$.
+\end{definition}
+
+\subsection{Query protocols}
+As vNM aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher.” The fundamental element here is the reaction of $i$ to arguments, which will serve as the informational basis to define $\ileadstost$.
+Given a proposition $\prop$ and two arguments $\ar, \ar' \in \allargs$, a query consists in presenting both arguments to $i$ and observing which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind: is it that $\prop$ holds, that $¬\prop$ holds, or that both are possible?
+The third possibility allows for the case where no argument appears more decisive than the other one.
+
+It is also necessary to capture the evolution of the position of $i$ towards arguments over time: a repeated query using a given pair of arguments may yield different answers, for example because the repeated question has been interleaved with another query containing other arguments (which $i$ may still have in mind when answering the second repetition), or for any other known or unknown reason.
+The important information for us is the \emph{set} of answers that $i$ could give to a query involving two given arguments and a given topic, among the set $\{\prop, ¬\prop, \text{both}\}$.
+The set designates all possible answers over time and over different order of asking the queries.
+Hence, given $\prop \in \allprops$, define a relation $\ileadstoprop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadstoprop C$, with $C \subseteq \set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind.
+The querying protocol is supposedly made so that for any $\prop \in \allprops$, $\ileadstoprop = \ileadstonprop$.
+
+This information is only indirectly observable: for example, if $(\ar, \ar') \ileadstoprop \{\prop\}$, a querier will never know more than $(\ar, \ar') \ileadstoprop C$ with $\prop \in C \subseteq \set{\prop, ¬\prop, \text{both}}$.
+Also, it may be only possible to test one ordering of the queries (assuming that $i$ forgets over time might permit to test different orderings, but this assumption might be unrealistic).
+In some cases, it may even be only possible to test a single query with a given individual.
+This limitation of our observation will not be a problem for the results of this article.
+Intuitively, this bears on the fact that, first, theories apply to multiple individuals, and second, if a theory claims that $(\ar, \ar') \ileadstoprop \{\prop\}$, then either this claim is correct, or it is falsifiable, in the sense that there is a possibility of observing a contradiction to its claim.
+
+To be more concrete, one possible choice of a query protocol, when arguments and propositions are strings, is to read both arguments to $i$, together with $\prop$, and ask $i$ to verbally report the choice he opts for among the three possibilities.
+Another is to present both arguments and ask $i$ to pick an item among some choice set and make the choice correspond to a validation of $\prop$ or $¬\prop$, possibly even letting the choice engage $i$, for example telling $i$ that she may keep the object of choice (this is illustrated in \cref{ex:pick}).
+This second possibility is especially interesting as it makes the protocol partially observable in the restricted sense usually appreciated in revealed preferences approaches.
+Note that depending on the protocol, the choice “both” is not necessarily observable (more about this below).
+%In that case, the semantics of $\prop$ and $¬\prop$ relatedly change: instead of meaning that $\prop$ is definitely the 
+%Indeed, \citet{tversky_intransitivity_1969} note that individuals “are not perfectly consistent in their choices.
+When faced with repeated choices between x and y, people often choose x in some instances and y in others.
+Furthermore, such inconsistencies are observed even in the absence of systematic changes in the decision maker’s taste which might be due to learning or sequential effects.
+It seems, therefore, that the observed inconsistencies reflect inherent variability or momentary fluctuation in the evaluative process.” This is an accepted fact of experimental psychology \citep{luce_utility_2000}.
+However, it is reasonable to suspect that fluctuations occur less often, if at all, for some choices.
+For example, facing a choice between tea or coffee, I would virtually never pick tea (all other things being equal).
+We are interested in capturing precisely those kind of preferences.
+
+One can also use $\zar$ as one or both of the arguments, in which case the protocol queries the preference of $i$ given only one or given no argument.
+
+\begin{example}[cont.]
+	\label{ex:pick}
+	Continuing the example, define the querying protocol as, given $\prop_\alt$, presenting two arguments to $i$ and let $i$ choose an item among $\allalts$. $i$ may keep the chosen item. 
+	If $i$ chooses $\alt$, it is considered that $i$ has validated $\prop_\alt$, otherwise, $¬\prop_\alt$. The option “both” is not observable.
+%	Queries are separated by one week at least, which (as supposed in this example) is enough to ensure that no effect of pleasure for variability enter into play. 
+\end{example}
+
+Define $\ileadstost$ from $\ileadstoprop$ as follows, for any $\prop \in \allprops$: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadstoprop C$ with $C \subseteq \set{\prop, \text{both}}$; and $(\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadstoprop \set{\prop}$.
+
+Note that (A1) and (A2) hold.
+
+When “both” is not observable, $\ileadstost$ is defined as: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadstoprop \set{\prop}$.
+(A1) and (A2) still hold.
+We say in this case that $\ileadstost$ does not distinguish sure from possible.
+Thus, elements $\phi \in \Phi$ may be considered as simply equal to $\prop$ or $¬\prop$, as $(\prop, \text{sure})$ is treated exactly as $(\prop, \text{possible})$.
+
+\subsection{Example}
+\begin{example}[(cont.)]
+	Returning to the previous example, a theory $T$ could claim that, for all individuals that belong to some given socio-economic situation and that have some given degree (described by the theory in sufficient details that it is possible to determine precisely to which kind of individuals it applies), $(\prop_a, \text{sure})$ is in the deliberated preferences of the individuals, for a given alternative $\alt$ also described by $T$.
+The theory also suggests some argument $\ar$, a text that (according to $T$) will convince any individual (fitting the description) that $\prop_\alt$ holds, thus, that $\alt$ is a “good” food product for him.
+The theory can be put to the test by picking an individual fitting the description, presenting the argument together with any other argument (for example, proposed by another theory), and observing whether $i$ is convinced.
+$T$ resists to such a falsification test if $i$ is convinced.
+According to a previous theorem, $T$ tells the truth if it would resist to any possible falsification test.
+(This is impossible to definitely make sure of.)
+\end{example}
+This example illustrates a difference between this proposal and the classical revealed approach: it could be that $T$ tells the truth even though its claim does not correspond to the revealed preference of some individuals, thus that, given no argument, some individuals would consider $a$ as dominated by another alternative in the set considered.
+It also illustrates a difference between this proposal and persuasion: the goal of $T$ is not merely to convince $i$ (possibly by using its lack of knowledge of any counter-argument to what $T$ says), but to resist any falsification attempt.
+Thus, $T$ should be confronted to arguments coming from as varied perspectives as possible, in order to give confidence that it tells the truth.
 

### 2020-07-16 simple.tex
Commands without final redundant i

@@
 \addtokomafont{labelinglabel}{\sffamily\bfseries}
-\renewcommand{\phi}{\varphi}
+\renewcommand{\phi}{\varphi}%TODO
 \DeclareMathAlphabet{\mathup}{OT1}{\familydefault}{m}{n}
@@
 (The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
-As usual with binary relations, $\hist \nileadstoi \phi$ means $(\hist, \phi) \notin {\ileadsto}$.
+As usual with binary relations, $\hist \nileadsto \phi$ means $(\hist, \phi) \notin {\ileadsto}$.
 
-Given $i \in I, \phi \in \Phi, \hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadsto \phi \land \hist \nileadstoi ¬\phi$.
-Define $\hist \ileadstosti \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
+Given $i \in I, \phi \in \Phi, \hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadsto \phi \land \hist \nileadsto ¬\phi$.
+Define $\hist \ileadstost \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
 Given $\hist \in \allhist$, let $\histend$ denote the set containing the last two elements of the sequence $\hist$ if the sequence has at least two elements; the singleton set containing the last element of the sequence if it has exactly one element; and the empty set if $\hist = \emptyset$.
-Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstosti \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstosti \phi$.
+Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstost \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstost \phi$.
 
@@
 	$\forall i \in I, \phi \in \Phi: 
-		[(\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstosti ¬\phi)] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
+		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \phi) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi)] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
 \end{axiom}
@@
 	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstosti ¬\phi].
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi].
 	\end{equation}
@@
 \begin{proof}
-	Protocol coherence is satisfied by definition of $\ileadstosti$.
-Indeed, if for some $\ar \in \allargs$, $\ar \ileadstosti \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoi ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstosti ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\phi$.
+	Protocol coherence is satisfied by definition of $\ileadstost$.
+Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\phi$.
 \end{proof}
@@
 	$\forall i \in I, \phi \in \Phi: 
-		[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
 \end{property}
 
-To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\phi \in \Phi$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi$.
+To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\phi \in \Phi$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \phi \lor \ar \ileadstost ¬\phi$.
 The $i$-decidable propositions are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
@@
 	\label{def:restrinterpr}
-	$\forall i \in I, \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi] ⇒ [\phi \in \iPhi \oplus ¬\phi \in \iPhi]$.
+	$\forall i \in I, \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstost \phi \lor \ar \ileadstost ¬\phi] ⇒ [\phi \in \iPhi \oplus ¬\phi \in \iPhi]$.
 \end{property}
@@
 
-Given $\phi \in \Phi$, $\args \subseteq \allargs$ and $\ar_0 \in \allargs$, say that $\args$ seems $i$-ineffective against $\ar_0$ for $\phi$, $\args \bowtie^{i, \phi} \ar_0$, iff $\exists \hist \in \allhist \suchthat \hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0 \land \hist \ileadstosti \phi$, that is, when some $\hist$ ends with $\args$ followed by $\ar_0$ and leads to $\phi$.
-Note that for all $\ar_0 \in \allargs$ such that $\exists \hist \in \allhist \suchthat [\hist(l(\hist)) = \ar_0 \land \hist \ileadstosti \phi]$: $\emptyset \sinef \ar_0$.
+Given $\phi \in \Phi$, $\args \subseteq \allargs$ and $\ar_0 \in \allargs$, say that $\args$ seems $i$-ineffective against $\ar_0$ for $\phi$, $\args \bowtie^{i, \phi} \ar_0$, iff $\exists \hist \in \allhist \suchthat \hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0 \land \hist \ileadstost \phi$, that is, when some $\hist$ ends with $\args$ followed by $\ar_0$ and leads to $\phi$.
+Note that for all $\ar_0 \in \allargs$ such that $\exists \hist \in \allhist \suchthat [\hist(l(\hist)) = \ar_0 \land \hist \ileadstost \phi]$: $\emptyset \sinef \ar_0$.
 
-Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land \ar_0 \in \histend \land \hist \nileadstoi \phi \land (\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0$.
+Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat \ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land \ar_0 \in \histend \land \hist \nileadsto \phi \land (\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0$.
 
-Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [\dbeatsinv \circ {\ibeatsiinv}](\ar)$.
+Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [\dbeatsinv \circ {\ibeatsinv}](\ar)$.
 Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
@@
 
-$\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset\right]: \hist \ileadstosti \phi$. 
+$\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset\right]: \hist \ileadstost \phi$. 
 %$\ar_0$ recursively $i$-defends $\phi$ iff $\forall \ar \in \cup_{k \in \N}(\dip)^k(\ar_0)$: $\ar$ $i$-defends $\phi$.
@@
 
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.
+A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi$.
 
@@
 \begin{proof}
-	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
+	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
 \end{proof}
@@
 
-	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstosti \phi$, and normative adequacy brings the conclusion.
+	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$, and normative adequacy brings the conclusion.
 
-	Given any $\ar_0 \in \allargs$, define $\args^{\hist} = \gbeatsinv(\ar_0) \cap \hist$ and $\allhistsznp = \set{\hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstosti \phi}$.
+	Given any $\ar_0 \in \allargs$, define $\args^{\hist} = \gbeatsinv(\ar_0) \cap \hist$ and $\allhistsznp = \set{\hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi}$.
 Given $\hist \in \allhistsznp$, say that $\hist$ is \emph{reducible} iff $\hist \in \allhistred$, defined as $\allhistred = \set{\hist \in \allhistsznp \suchthat \forall \ar_1 \in \args^{\hist}: \args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0}$; define accordingly $\allhistnonred = \allhistsznp \setminus \allhistred = \set{\hist \in \allhistsznp \suchthat \exists \ar_1 \in \args^{\hist} \suchthat \args^{\hist} \setminus \set{\ar_1} \sinef \ar_0}$.
@@
 To see this, pick as $\histp$ any sequence consisting of the arguments contained in $\args^{\hist} \setminus \set{\ar_1}$, followed by $\ar_0$.
-	First, $\histp \in \allhistsznp$, because as $\hist \in \allhistred$, $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$, thus, $\histp \nileadstosti \phi$. 
+	First, $\histp \in \allhistsznp$, because as $\hist \in \allhistred$, $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$, thus, $\histp \nileadstost \phi$. 
 	Second, $\args^{\histp} = \args^{\hist} \setminus \set{\ar_1}$, because $\args^{\hist} \setminus \set{\ar_1} \subseteq \args^{\histp} = \left(\gbeatsinv(\ar_0) \cap \histp\right) \subseteq \args^{\hist} \setminus \set{\ar_1}$.
@@
 
-	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstosti \phi ⇒ \exists \ar_1 \in \allargs, \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1 \ibeatsi \ar_0 \land \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2 \in \dip(\ar_0)$.
-	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstosti \phi$. 
-	By definition, $\ar_0 \nileadstosti \phi$ means that $\exists \hist \in \allhistsznp$.
+	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \ar_1 \in \allargs, \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1 \ibeats \ar_0 \land \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2 \in \dip(\ar_0)$.
+	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
+	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhistsznp$.
 	Because $\ar_0$ $i$-defends $\phi$, $\args^{\hist} ≠ \emptyset$. 
@@
 	Thus, $\exists \ar_1 \in \args^{\histp} \suchthat \args^{\histp} \setminus \set{\ar_1} \sinef \ar_0$.
-	By definition, this means that $\ar_1 \ibeatsi \ar_0$ and, as $\ar_1 \in \args^{\histp} = \gbeatsinv(\ar_0) \cap \histp$, $\ar_1 \gbeats \ar_0$. 
+	By definition, this means that $\ar_1 \ibeats \ar_0$ and, as $\ar_1 \in \args^{\histp} = \gbeatsinv(\ar_0) \cap \histp$, $\ar_1 \gbeats \ar_0$. 
 	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1$.
@@
 
-	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs[i, \phi] \land \ar_0 \nileadstosti \phi] ⇒ \exists \ar_2 \in \gargs[i, \phi] \cap \dfp(\ar_0)$.
+	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs[i, \phi] \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs[i, \phi] \cap \dfp(\ar_0)$.
 That is because $\ar_0 \in \gargs[i, \phi] ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering $\ard_2$ and $\ar_2$ as defined in the lemma, $\ar_2 \in \gargs[i, \phi]$ by definition of $\gargs[i, \phi]$ and $\ard_2 \in \df(\ar_0)$ by definition of $\df$.
@@
 Observe that $\ar_0 \in \gargs[i, \phi]$.
-Given $k \in 2\N$, if $\ar_k \nileadstosti \phi$, define $\ar_{k + 2}$ using the deduction following the last lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$.
-	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstosti \phi$.
+Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the last lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$.
+	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
 \end{proof}
@@
 \NewDocumentCommand{\nileadstoe}{O{}}{\not⇝^{#1}_\exists}
-\NewDocumentCommand{\ileadstost}{O{}}{⇝^{#1}_\forall}
-\NewDocumentCommand{\nileadstost}{O{}}{\not⇝^{#1}_\forall}
 Define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.
@@
 
-Discuss variant with an empirical claim: $\hist \ileadsto \phi ⇒ \hist \nileadstoi ¬\phi$; and change \cref{ax:norm}: $[\forall \hist, \hist \ileadsto \propposs] ⇒ \propposs \in \iPhi$, … This is essentially what will be done in the following, I suppose.
+Discuss variant with an empirical claim: $\hist \ileadsto \phi ⇒ \hist \nileadsto ¬\phi$; and change \cref{ax:norm}: $[\forall \hist, \hist \ileadsto \propposs] ⇒ \propposs \in \iPhi$, … This is essentially what will be done in the following, I suppose.
 
@@
 and $\allargs$ the set of all strings.
-Given $i \in I$, define $\ileadstosti$ as follows. 
+Given $i \in I$, define $\ileadstost$ as follows. 
 Given $\hist \in \allhist$ and $\phi \in \Phi_\allalts$, with $\phi \in \set{\ppst} × \set{\mathit{sure}, \mathit{poss}}$ for some $a ≠ b \in \allalts$, the individual is presented the arguments in $\hist$, and has then to choose a product from the set $\set{a, b}$.
-Define $\hist \ileadstosti \phi$ iff $i$ chooses $a$.
+Define $\hist \ileadstost \phi$ iff $i$ chooses $a$.
 \commentOC{This is inadequate: if $i$ picks $b$ from $\set{a, b, c}$, the current definition considers it compatible with $\ppstsure \in \iPhi$, thus, $\ppst$ does not have a meaningful content.
 Should rather define $\ppstsure$ so that $a$ is picked rather than $b$ whatever the choice set.
-This requires to generalize $\ileadstosti$.}
+This requires to generalize $\ileadstost$.}
 
@@
 
-A normative theory about $\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: [\exists \ar_{a \pst b} \in \allargs \suchthat \ar_{a \pst b} \ileadstosti \ppstsure] \land [\exists \ar_{b \pst c} \in \allargs \suchthat \ar_{b \pst c} \ileadstosti \ppstsure[b][c]] ⇒ [\exists \ar_{a \pst c} \in \allargs \suchthat \ar_{a \pst c} \ileadstosti \ppstsure[a][c]]$.
+A normative theory about $\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: [\exists \ar_{a \pst b} \in \allargs \suchthat \ar_{a \pst b} \ileadstost \ppstsure] \land [\exists \ar_{b \pst c} \in \allargs \suchthat \ar_{b \pst c} \ileadstost \ppstsure[b][c]] ⇒ [\exists \ar_{a \pst c} \in \allargs \suchthat \ar_{a \pst c} \ileadstost \ppstsure[a][c]]$.
 
@@
 \subsubsection{Transitive arguments}
-Given a normative theory and a function $\tau: \allargs × \allargs → \allargs$, say that $\tau$ is a transitive argument builder iff $\forall a ≠ b ≠ c ≠ a \in \allalts, \ar_{a \pst b}, \ar_{b \pst c} \in \allargs \suchthat \ar_{a \pst b} \ileadstosti \ppstsure \land \ar_{b \pst c} \ileadstosti \ppstsure[b][c]: \tau(\ar_{a \pst b}, \ar_{b \pst c}) \ileadstosti \ppstsure[a][c]$.
+Given a normative theory and a function $\tau: \allargs × \allargs → \allargs$, say that $\tau$ is a transitive argument builder iff $\forall a ≠ b ≠ c ≠ a \in \allalts, \ar_{a \pst b}, \ar_{b \pst c} \in \allargs \suchthat \ar_{a \pst b} \ileadstost \ppstsure \land \ar_{b \pst c} \ileadstost \ppstsure[b][c]: \tau(\ar_{a \pst b}, \ar_{b \pst c}) \ileadstost \ppstsure[a][c]$.
 
@@
 \NewDocumentCommand{\ileadstonprop}{}{⇝^{¬\prop}}
-\NewDocumentCommand \nileadsto { o }{%
-	\IfValueTF{#1}{%
-		\not⇝^{#1}%
-	}{%
-		\not⇝%
-	}%
-}
 \NewDocumentCommand{\ileadstosts}{}{⇝_*}
@@
 \NewDocumentCommand{\argsd}{}{S^\mathit{d}}
+\RenewDocumentCommand{\ileadstost}{O{}}{⇝^{#1}_\forall}
+\RenewDocumentCommand{\nileadstost}{O{}}{\not⇝^{#1}_\forall}
 

### 2020-07-17 simple.tex
Clearer notations and a note about observable relations

@@
 \section{Next}
-\NewDocumentCommand{\ileadstoe}{O{}}{⇝^{#1}_\exists}
-\NewDocumentCommand{\nileadstoe}{O{}}{\not⇝^{#1}_\exists}
 Define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.
@@
 \subsection{Falsifiability}
+\commentOC{I should define $\Box(\hist \ileadsto \phi)$ iff it has been observed that $\hist \ileadsto \phi$.
+Then, axiom Correct observations (that is self-evident): $\Box(\hist \ileadsto \phi) ⇒ \hist \ileadsto \phi$ (what has been observed is).
+Supplementary axiom Falsification is enough (that is not self-evident): $\not\Box(\hist \ileadsto \phi) ⇒ \hist \nileadsto \phi$ (what has not been observed is not).}
+
 \commentOC{I want: An empirical theory for a normative theory is something like a normative and falsifiable claim.

### 2020-07-18 simple.tex
Slightly larger obligations for empirical theory

@@
 ${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
-${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range equals $\gbeatsinv(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton).
+${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton).
 Define $\df \subseteq \allargs × \alldargs$ as $\df = \dbeatsinv \circ \gbeatsinv$. 
@@
 An empirical theory must satisfy
-$\exists k \in \N \suchthat \dfp^k(\gleadstoinv(\allprops)) = \emptyset$.
+$\exists k \in \N \suchthat \dfp^k(\dfp(\zar) \cup \gleadstoinv(\Phi)) = \emptyset$, where $\dfp^0$ is the identity function over $\allargs$.
 
@@
 Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
-Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$, where $(\dip)^0$ is the identity function over $\allargs$.
+Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k(\dip(\zar) \cup {\gleadstoinv}(\phi))$.
 
@@
 \subsection{Effectively comparing models}
+Given a normative theory, consider two empirical theories $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$ and $(q', (\gleadsto[q(i)][\delta])_{q(i) \in q(I)}, \gbeats', \alldargs, \dbeats', +')$.
+
+Given a normative theory and $\phi \in \Phi$, say that two empirical theories (for that normative theory) disagree about $\phi$ iff $\phi \in \gPhi \land ¬\phi \in \gPhi[\delta]$.
+
+If $\gamma$ and $\delta$ agree about all $\phi$, there is nothing to test as the theories are compatible.
+Otherwise, here is a test procedure for that falsifies at least one of these theories, given any $\phi \in \Phi$ about which they disagree and any $i \in I$.
+
+Note first that $\ar_0 \gbeats \ar_0$ is impossible because … TODO why didn’t I need this before?
+
+Consider $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto \phi$.
+Test whether $(\ar_0) \ileadstost \phi$.
+If not, $(i, \phi, (\ar_0))$ is a falsification instance of $\gamma$.
+If $(\ar_0) \ileadsto \phi$, check whether some $\ar_1 \dbeats' \ar_0$.
+If not, $\delta$ is falsified?
+($\ar_0$ attacks $\delta$ but $\delta$ is not able to defend.)…
+
 Model: for a given $i$.
@@
 }
-\NewDocumentCommand{\zar}{}{\mathbf{0}}%zero, or empty, argument
 \NewDocumentCommand{\mPhi}{}{\Phi_\gamma}
 \NewDocumentCommand{\argsd}{}{S^\mathit{d}}
-\RenewDocumentCommand{\ileadstost}{O{}}{⇝^{#1}_\forall}
-\RenewDocumentCommand{\nileadstost}{O{}}{\not⇝^{#1}_\forall}
+\NewDocumentCommand{\ileadstoall}{O{}}{⇝^{#1}_\forall}
+\NewDocumentCommand{\nileadstoall}{O{}}{\not⇝^{#1}_\forall}
 
@@
 A decision situation concerns a topic $\allprops$, given a set of arguments $\allargs$, given a certain query protocol, and over a certain time frame.
-The relation $\ileadstost$, to be defined shortly, models the reaction of $i$ to arguments about the topic.
-The decision situation will be defined as a triple $(\allprops, \allargs, \ileadstost)$ satisfying some conditions to be defined after having presented those three fundamental elements.
+The relation $\ileadstoall$, to be defined shortly, models the reaction of $i$ to arguments about the topic.
+The decision situation will be defined as a triple $(\allprops, \allargs, \ileadstoall)$ satisfying some conditions to be defined after having presented those three fundamental elements.
 
@@
 Define $\Phi = \allprops × \set{\text{possible}, \text{sure}}$. Elements in $\Phi$ will also be called propositions, which should create no ambiguity. 
-The relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$, pronounced “always leads to”, has the following semantics.
-Whenever $(\ar, \ar') \ileadstost (\prop, \text{sure})$, $i$ always considers that $\prop$ is sure (meaning that $¬\prop$ is excluded), when presented with these two arguments, and whenever $(\ar, \ar') \ileadstost (\prop, \text{possible})$, $i$ always considers that $\prop$ is “at least” possible (meaning that $¬\prop$ may be possible as well), when presented with these two arguments.
+The relation $\ileadstoall \subseteq (\allargs × \allargs) × \Phi$, pronounced “always leads to”, has the following semantics.
+Whenever $(\ar, \ar') \ileadstoall (\prop, \text{sure})$, $i$ always considers that $\prop$ is sure (meaning that $¬\prop$ is excluded), when presented with these two arguments, and whenever $(\ar, \ar') \ileadstoall (\prop, \text{possible})$, $i$ always considers that $\prop$ is “at least” possible (meaning that $¬\prop$ may be possible as well), when presented with these two arguments.
 In both cases, the term “always” means that the consideration is stable over time, including after having presented other arguments to $i$.
@@
 However, I voluntarily leave the querying protocol not precisely specified in general, as multiple reasonable choices are possible.
-The results of this article depend only on assumptions about $\ileadstost$.
+The results of this article depend only on assumptions about $\ileadstoall$.
 
@@
 It follows that $¬¬\phi = \phi$.
-Write $(\ar, \ar') \nileadstost \phi$ for $¬[(\ar, \ar') \ileadstost \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstost ¬\phi$.
+Write $(\ar, \ar') \nileadstoall \phi$ for $¬[(\ar, \ar') \ileadstoall \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstoall ¬\phi$.
 The relation $\ileadstoe$ is pronounced “sometimes leads to”.
@@
 
-The pair $(\ar, \ar')$ is to be understood as unordered (thus $(\ar, \ar') \ileadstost \prop ⇔ (\ar', \ar) \ileadstost \prop$).
+The pair $(\ar, \ar')$ is to be understood as unordered (thus $(\ar, \ar') \ileadstoall \prop ⇔ (\ar', \ar) \ileadstoall \prop$).
 
 \begin{definition}[Decision situation]
-	A decision situation is a topic $\allprops$ closed under negation, a set of arguments $\allargs$, an “always leads to” relation $\ileadstost \subseteq (\allargs × \allargs) × \Phi$ satisfying (A1) and (A2) and using unordered pairs of arguments, $\Phi$ being the set of propositions $\allprops × \set{\text{sure}, \text{possible}}$.
+	A decision situation is a topic $\allprops$ closed under negation, a set of arguments $\allargs$, an “always leads to” relation $\ileadstoall \subseteq (\allargs × \allargs) × \Phi$ satisfying (A1) and (A2) and using unordered pairs of arguments, $\Phi$ being the set of propositions $\allprops × \set{\text{sure}, \text{possible}}$.
 \end{definition}
@@
 \subsection{Query protocols}
-As vNM aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher.” The fundamental element here is the reaction of $i$ to arguments, which will serve as the informational basis to define $\ileadstost$.
+As vNM aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher.” The fundamental element here is the reaction of $i$ to arguments, which will serve as the informational basis to define $\ileadstoall$.
 Given a proposition $\prop$ and two arguments $\ar, \ar' \in \allargs$, a query consists in presenting both arguments to $i$ and observing which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind: is it that $\prop$ holds, that $¬\prop$ holds, or that both are possible?
@@
 
-Define $\ileadstost$ from $\ileadstoprop$ as follows, for any $\prop \in \allprops$: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadstoprop C$ with $C \subseteq \set{\prop, \text{both}}$; and $(\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadstoprop \set{\prop}$.
+Define $\ileadstoall$ from $\ileadstoprop$ as follows, for any $\prop \in \allprops$: $(\ar, \ar') \ileadstoall (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadstoprop C$ with $C \subseteq \set{\prop, \text{both}}$; and $(\ar, \ar') \ileadstoall (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadstoprop \set{\prop}$.
 
@@
 
-When “both” is not observable, $\ileadstost$ is defined as: $(\ar, \ar') \ileadstost (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadstost (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadstoprop \set{\prop}$.
+When “both” is not observable, $\ileadstoall$ is defined as: $(\ar, \ar') \ileadstoall (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadstoall (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadstoprop \set{\prop}$.
 (A1) and (A2) still hold.
-We say in this case that $\ileadstost$ does not distinguish sure from possible.
+We say in this case that $\ileadstoall$ does not distinguish sure from possible.
 Thus, elements $\phi \in \Phi$ may be considered as simply equal to $\prop$ or $¬\prop$, as $(\prop, \text{sure})$ is treated exactly as $(\prop, \text{possible})$.
@@
 This is falsifiable.
-	When claiming that $(\ar_1, \ar_0) \ileadstost[i] \phi$, the model really claims that $\nexists p, i' \in q^{-1}(q(i)) \suchthat p, \ar_1, \ar_0 \ileadsto[i'] ¬\phi \lor p, \ar_0, \ar_1 \ileadsto[i'] ¬\phi$, where $i' \in q^{-1}(q(i))$ iff $q(i) = q(i')$.
+	When claiming that $(\ar_1, \ar_0) \ileadstoall[i] \phi$, the model really claims that $\nexists p, i' \in q^{-1}(q(i)) \suchthat p, \ar_1, \ar_0 \ileadsto[i'] ¬\phi \lor p, \ar_0, \ar_1 \ileadsto[i'] ¬\phi$, where $i' \in q^{-1}(q(i))$ iff $q(i) = q(i')$.
 

### 2020-07-21 simple.tex
Some heuristic note about bootstrap (zar); and cosmetic changes

@@
 
-Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat \ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land \ar_0 \in \histend \land \hist \nileadsto \phi \land (\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0$.
+Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat 
+	\ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land 
+	(\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0 \land 
+	\ar_0 \in \histend \land 
+	\hist \nileadsto \phi$.
 
@@
 	Given any $\ar_0 \in \allargs$, define $\args^{\hist} = \gbeatsinv(\ar_0) \cap \hist$ and $\allhistsznp = \set{\hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi}$.
-Given $\hist \in \allhistsznp$, say that $\hist$ is \emph{reducible} iff $\hist \in \allhistred$, defined as $\allhistred = \set{\hist \in \allhistsznp \suchthat \forall \ar_1 \in \args^{\hist}: \args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0}$; define accordingly $\allhistnonred = \allhistsznp \setminus \allhistred = \set{\hist \in \allhistsznp \suchthat \exists \ar_1 \in \args^{\hist} \suchthat \args^{\hist} \setminus \set{\ar_1} \sinef \ar_0}$.
+Given $\hist \in \allhistsznp$, say that $\hist$ is \emph{reducible} iff $\hist \in \allhistred = \set{\hist \in \allhistsznp \suchthat \forall \ar_1 \in \args^{\hist}: \args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0}$; define accordingly $\allhistnonred = \allhistsznp \setminus \allhistred = \set{\hist \in \allhistsznp \suchthat \exists \ar_1 \in \args^{\hist} \suchthat \args^{\hist} \setminus \set{\ar_1} \sinef \ar_0}$.
 
-	Lemma: given any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$, if $\allhistsznp ≠ \emptyset$, $\hist \in \allhistred ⇒ \exists \histp \in \allhistsznp \suchthat \emptyset ≠ \args^{\histp} \subset \args^{\hist}$.
+	Lemma: given any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$, if $\allhistsznp ≠ \emptyset$, then $\hist \in \allhistred ⇒ \exists \histp \in \allhistsznp \suchthat \emptyset ≠ \args^{\histp} \subset \args^{\hist}$.
 To see this, pick as $\histp$ any sequence consisting of the arguments contained in $\args^{\hist} \setminus \set{\ar_1}$, followed by $\ar_0$.
@@
 
+\begin{remark}
+	$\allargs \setminus \gleadstoinv(\phi)$ are the non-initial arguments.
+An empirical theory must satisfy: $\dbeats$ covers all attackers and $\allargs \setminus \gleadstoinv(\phi)$.
+Note that $\ar'_0 \gbeats \ar_0$ seems possible (thus, an attacker not in $\allargs \setminus \gleadstoinv(\phi)$), and $\zar$ not attacking anything but in $\allargs \setminus \gleadstoinv(\phi)$ is possible, where $\zar$ designates an argument that says nothing.
+
+	If $\hist$ does not include any initial argument, and includes $\ar_1$, and leads to $¬\phi$, then proceed as if $\ar_1$ attacks $\emptyset$, thus, include the defensor against $\ar_1$.
+This defensor must be in $\allargs \cap \alldargs$.
+(It’s probably better to remove the $\alldargs$ concept.)
+\end{remark}
+
 Consider $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto \phi$.
@@
 If not, $(i, \phi, (\ar_0))$ is a falsification instance of $\gamma$.
-If $(\ar_0) \ileadsto \phi$, check whether some $\ar_1 \dbeats' \ar_0$.
+If $(\ar_0) \ileadstost \phi$, check whether some $\ar_1 \dbeats' \ar_0$.
 If not, $\delta$ is falsified?

### 2020-07-21 simple.tex
Fixed def attack-exists
Impr wording of proof

@@
 	\ar_0 \in \histend \land 
-	\hist \nileadsto \phi$.
+	\hist \nileadstost \phi$.
 
@@
 	Thus, $\exists \ar_1 \in \args^{\histp} \suchthat \args^{\histp} \setminus \set{\ar_1} \sinef \ar_0$.
-	By definition, this means that $\ar_1 \ibeats \ar_0$ and, as $\ar_1 \in \args^{\histp} = \gbeatsinv(\ar_0) \cap \histp$, $\ar_1 \gbeats \ar_0$. 
-	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1$.
-Defining $\ar_2 = \ar_0 + \ard_2$, by definition of $\dip$, $\ar_2 \in \dip(\ar_0)$.
+	This shows that $\ar_1 \gbeats \ar_0$ and $\ar_1 \ibeats \ar_0$: 
+		by definition of $\args^{\histp}$, $\ar_1 \in \gbeatsinv(\ar_0) \cap \histp$; and 
+		$[\ar_0 \in \histp \land \histp \nileadstost \phi]$ follow from $\histp \in \allhistnonred$.
+	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \alldargs \suchthat \ard_2 \dbeats \ar_1$.
+Defining $\ar_2 = \ar_0 + \ard_2$, $\ar_2 \in \dip(\ar_0)$ by definition of $\dip$.
 

### 2020-07-21 simple.tex
Removed \zar, not useful

@@
 An empirical theory must satisfy
-$\exists k \in \N \suchthat \dfp^k(\dfp(\zar) \cup \gleadstoinv(\Phi)) = \emptyset$, where $\dfp^0$ is the identity function over $\allargs$.
+$\exists k \in \N \suchthat \dfp^k(\gleadstoinv(\Phi)) = \emptyset$, where $\dfp^0$ is the identity function over $\allargs$.
 
@@
 Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
-Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k(\dip(\zar) \cup {\gleadstoinv}(\phi))$.
+Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.
 

### 2020-07-21 simple.tex
Preparing simplification of minimal attacking coalitions

@@
 $\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset\right]: \hist \ileadstost \phi$.
-%$\ar_0$ recursively $i$-defends $\phi$ iff $\forall \ar \in \cup_{k \in \N}(\dip)^k(\ar_0)$: $\ar$ $i$-defends $\phi$.
+
+\begin{remark}
+	Perhaps the following simpler definition would work. 
+	Define $\args \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat 
+	\args \subseteq \gbeatsinv(\ar_0) \cap \hist \land 
+	\ar_0 \in \histend \land 
+	\hist \nileadstost \phi$.
+	Define $\ar_1 \ibeats \ar_0$ iff $\exists \set{\ar_1} \subseteq \args \subseteq \allargs \suchthat 
+	\args \ibeats \ar_0 \land
+	[\nexists \args' \subset \args \suchthat \args' \ibeats \ar_0]$.
+
+	I then need the following two facts.
+1) If $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \args \ibeats \ar_0$.
+2) Proving that $\ar_2 \in \gargs$ is easy enough, thus, if $\args = \set{\ar_1, \ar'_1}$ is minimal for $\args \ibeats \ar_0$, then, showing $\exists \hist = (…, \ar_1, \ar_0) \ileadstost \phi, \ar'_1 \notin \hist$ (and the same inverting $\ar_1$ and $\ar'_1$), is enough.
+But this seems false: it is possible that $\exists \hist… \land \ar_1 \ibeats \ar_0$.
+
+	Thus, maybe need to define $\args' \ibeats[\prime] \ar_0$ iff $\exists \hist… \ileadstost \phi$.
+\end{remark}
 
@@
 (It’s probably better to remove the $\alldargs$ concept.)
+
+	Better first simplify the related definitions in the “normal” case.
 \end{remark}

### 2020-07-24 simple.tex
New proof and defs started using coalition attacks

@@
 	Thus, maybe need to define $\args' \ibeats[\prime] \ar_0$ iff $\exists \hist… \ileadstost \phi$.
+
+	Given $i \in I, \phi \in \Phi$, define $\args \ibeatscoal \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.
+	Define $\args \ibeatscoalstr \ar_0$ iff $\forall \hist \in \allhist: [\hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0] ⇒ \hist \nileadstost \phi$, that is, iff no $\hist$ that end with $\args$ followed by $\ar_0$ lead to $\phi$.
+	Define $\ar_1 \ibeats \ar_0$ iff $\exists \set{\ar_1} \subseteq \args \subseteq \allargs \suchthat \args \ibeatscoal \ar_0 \land \args \setminus \set{\ar_1} \nibeatscoalstr \ar_0$.
+
+	Lemma.
+Given any $\ar_0$ that $i$-defends $\phi$, $\forall \args \subseteq \allargs: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$.
+Observe that the implication holds for $\args = \emptyset$, because $\emptyset \nibeatscoal \ar_0$ as $\ar_0$ $i$-defends $\phi$.
+Now, given $k \in \N$, assume that $\forall \args \subseteq \allargs \suchthat \card{\args} = k: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$, and let us show that $\forall \args \subseteq \allargs \suchthat \card{\args} = k + 1: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$.
+	Consider $\args \subseteq \allargs \suchthat \card{\args} = k + 1 \land \args \ibeatscoal \ar_0$.
+One of the following two cases hold.
+First case: $\forall \args' \subset \args \suchthat \card{\args'} = k: \args \nibeatscoalstr \ar_0$.
+Then, $\forall \ar_1 \in \args: \ar_1 \ibeats \ar_0$.
+Second case: $\exists \args' \subset \args \suchthat \card{\args'} = k \land \args' \ibeatscoalstr \ar_0$.
+Then, $\args' \ibeatscoal \ar_0$ (noting that ${\ibeatscoalstr} \subseteq {\ibeatscoal}$), thus $\exists \ar_1 \in \args' \suchthat \ar_1 \ibeats \ar_0$ (using the hypothesis of recurrence), hence, $\exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$.
+
+	This lemma permits to deduce that, given $\ar_0$ that $i$-defends $\phi$, $\hist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$, and $\args = \gbeatsinv(\ar_0) \cap \hist$: $\args ≠ \emptyset ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$.
+This holds because in that case, $\args \ibeatscoal \ar_0$.
+
+	Problem happens in the following case.
+$\ar'_1$ alone is uncertain, meaning $\exists \hist = (… \ar'_1 … \ar_0) \nileadstost \phi$ and $\exists \hist = (…, \ar'_1, \ar_0) \ileadstost \phi$.
+Then, a counter-theory $\delta$ may claim that $\ar'_1$ alone is ineffective: suffice to show the example $(…, \ar'_1, \ar_0) \ileadstost \phi$.
+Whereas in fact $\ar'_1$ alone is sometimes effective.
+Then, $\args = \set{\ar_1, \ar'_1}$ may be claimed to be effective by combination effect (and $\ar'_1$ can’t be blamed, although it should, as $\delta$ has “proven” it ineffective).
+Thus, $\ar_2$, defending against $\ar_1$, ends up in $\gargs$.
+Assume $\ar_1$ is innocuous for $i$ (otherwise, no problem, as $\ar_2$ is legitimate) ($\ar_1$ could be efficient for others than $i$, which justifies $\ar_1 \gbeats \ar_0$).
+Then $\ar_2$ shouldn’t be played, it is only included as a result of the weak demand about proving that $\ar'_1$ is ineffective.
+
+Note that if we agree that $\ar'_1$ is uncertain, then $\gamma$ should play $\ar'_2$ to answer the coalition $\args$ attack (as required even without the coalitions definition), not $\ar_2$.
+But this conflicts with the formal definitions.
+Note that if $\ar'_1$ is known as uncertain for everybody, there is no problem, as $\gamma$ should include $\ar'_2$ from the start.
+Problem happens if $\ar'_1$ is suspected uncertain for some and inefficient for others.
+
+	Here is a similar problem: assume $\ar_1$ and $\ar'_1$ are uncertain for some and innocuous for others (not necessarily the same).
+Assume we observed $(…, \ar_1, \ar_0) \ileadstost \phi$ (without $\ar'_1$) and $(…, \ar'_1, \ar_0) \ileadstost \phi$ (without $\ar_1$, and imagining this would be possible to know); but $\set{\ar_1, \ar'_1}$ attacks $\ar_0$.
+Then we ignore whether, for $i$, $\ar_1$ or $\ar'_1$ is innocuous; and thus ignore whether $\ar_2$ or $\ar'_2$ should be played.
+The right answer is probably: play $\ar_2 + \ar'_2$.
+In fact, suffices to assume that, whenever such situation can happen, $\gamma$ has planned that $\ar_2$ be attacked by $\ar'_1$, and conversely, and then we get immediately that $\ar_2 + \ar'_2$ is involved.
+(But also that $\ar_2$ should be defended, whereas this is perhaps too demanding?)
 \end{remark}

### 2020-07-24 simple.tex
Integrated defs and proof modifs

@@
 
-Given $\phi \in \Phi$, $\args \subseteq \allargs$ and $\ar_0 \in \allargs$, say that $\args$ seems $i$-ineffective against $\ar_0$ for $\phi$, $\args \bowtie^{i, \phi} \ar_0$, iff $\exists \hist \in \allhist \suchthat \hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0 \land \hist \ileadstost \phi$, that is, when some $\hist$ ends with $\args$ followed by $\ar_0$ and leads to $\phi$.
-Note that for all $\ar_0 \in \allargs$ such that $\exists \hist \in \allhist \suchthat [\hist(l(\hist)) = \ar_0 \land \hist \ileadstost \phi]$: $\emptyset \sinef \ar_0$.
+Given $i \in I, \phi \in \Phi, \ar_0 \in \allargs$ and $\args \subseteq \gbeatsinv(\ar_0)$, define $\args \ibeatscoal \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.
+Define $\args \ibeatscoalstr \ar_0$ iff $\forall \hist \in \allhist: [\hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0] ⇒ \hist \nileadstost \phi$, that is, iff no $\hist$ that end with $\args$ followed by $\ar_0$ lead to $\phi$.
+Note that $\forall \ar_0 \in \allargs, \args \subseteq \gbeatsinv(\ar_0): \args \ibeatscoalstr \ar_0 ⇒ \args \ibeatscoal \ar_0$.
+That is because $\ar_0 \ngbeats \ar_0$, because $\gbeats$ is irreflexive by definition of an empirical theory, and thus suffices to consider any sequence of arguments $\hist$ using only and all the arguments $\args \cup \set{\ar_0}$ and placing $\ar_0$ last: because $\args \ibeatscoalstr \ar_0$, $\hist \nileadstost \phi$, and the existence of $\hist$ proves that $\args \ibeatscoal \ar_0$.
 
-Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat 
-	\ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land 
-	(\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0 \land 
-	\ar_0 \in \histend \land 
-	\hist \nileadstost \phi$.
+Given $i \in I, \phi \in \Phi$ and $\ar_0, \ar_1 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \args \subseteq \gbeatsinv(\ar_0) \suchthat \ar_1 \in \args \land \args \ibeatscoal \ar_0 \land \args \setminus \set{\ar_1} \nibeatscoalstr \ar_0$.
 
@@
 
-$\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset\right]: \hist \ileadstost \phi$.
+$\ar$ $i$-defends $\phi$ iff $\emptyset \nibeatscoal \ar$.
 
 \begin{remark}
-	Perhaps the following simpler definition would work. 
-	Define $\args \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat 
-	\args \subseteq \gbeatsinv(\ar_0) \cap \hist \land 
-	\ar_0 \in \histend \land 
-	\hist \nileadstost \phi$.
-	Define $\ar_1 \ibeats \ar_0$ iff $\exists \set{\ar_1} \subseteq \args \subseteq \allargs \suchthat 
-	\args \ibeats \ar_0 \land
-	[\nexists \args' \subset \args \suchthat \args' \ibeats \ar_0]$.
-
-	I then need the following two facts.
+	I need the following two facts.
 1) If $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \args \ibeats \ar_0$.
 2) Proving that $\ar_2 \in \gargs$ is easy enough, thus, if $\args = \set{\ar_1, \ar'_1}$ is minimal for $\args \ibeats \ar_0$, then, showing $\exists \hist = (…, \ar_1, \ar_0) \ileadstost \phi, \ar'_1 \notin \hist$ (and the same inverting $\ar_1$ and $\ar'_1$), is enough.
-But this seems false: it is possible that $\exists \hist… \land \ar_1 \ibeats \ar_0$.
-
-	Thus, maybe need to define $\args' \ibeats[\prime] \ar_0$ iff $\exists \hist… \ileadstost \phi$.
-
-	Given $i \in I, \phi \in \Phi$, define $\args \ibeatscoal \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.
-	Define $\args \ibeatscoalstr \ar_0$ iff $\forall \hist \in \allhist: [\hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0] ⇒ \hist \nileadstost \phi$, that is, iff no $\hist$ that end with $\args$ followed by $\ar_0$ lead to $\phi$.
-	Define $\ar_1 \ibeats \ar_0$ iff $\exists \set{\ar_1} \subseteq \args \subseteq \allargs \suchthat \args \ibeatscoal \ar_0 \land \args \setminus \set{\ar_1} \nibeatscoalstr \ar_0$.
-
-	Lemma.
-Given any $\ar_0$ that $i$-defends $\phi$, $\forall \args \subseteq \allargs: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$.
-Observe that the implication holds for $\args = \emptyset$, because $\emptyset \nibeatscoal \ar_0$ as $\ar_0$ $i$-defends $\phi$.
-Now, given $k \in \N$, assume that $\forall \args \subseteq \allargs \suchthat \card{\args} = k: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$, and let us show that $\forall \args \subseteq \allargs \suchthat \card{\args} = k + 1: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$.
-	Consider $\args \subseteq \allargs \suchthat \card{\args} = k + 1 \land \args \ibeatscoal \ar_0$.
-One of the following two cases hold.
-First case: $\forall \args' \subset \args \suchthat \card{\args'} = k: \args \nibeatscoalstr \ar_0$.
-Then, $\forall \ar_1 \in \args: \ar_1 \ibeats \ar_0$.
-Second case: $\exists \args' \subset \args \suchthat \card{\args'} = k \land \args' \ibeatscoalstr \ar_0$.
-Then, $\args' \ibeatscoal \ar_0$ (noting that ${\ibeatscoalstr} \subseteq {\ibeatscoal}$), thus $\exists \ar_1 \in \args' \suchthat \ar_1 \ibeats \ar_0$ (using the hypothesis of recurrence), hence, $\exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$.
-
-	This lemma permits to deduce that, given $\ar_0$ that $i$-defends $\phi$, $\hist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$, and $\args = \gbeatsinv(\ar_0) \cap \hist$: $\args ≠ \emptyset ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$.
-This holds because in that case, $\args \ibeatscoal \ar_0$.
 
@@
 
-	Given any $\ar_0 \in \allargs$, define $\args^{\hist} = \gbeatsinv(\ar_0) \cap \hist$ and $\allhistsznp = \set{\hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi}$.
-Given $\hist \in \allhistsznp$, say that $\hist$ is \emph{reducible} iff $\hist \in \allhistred = \set{\hist \in \allhistsznp \suchthat \forall \ar_1 \in \args^{\hist}: \args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0}$; define accordingly $\allhistnonred = \allhistsznp \setminus \allhistred = \set{\hist \in \allhistsznp \suchthat \exists \ar_1 \in \args^{\hist} \suchthat \args^{\hist} \setminus \set{\ar_1} \sinef \ar_0}$.
+	Lemma.
+Given any $\ar_0$ that $i$-defends $\phi$, $\forall \args \subseteq \gbeatsinv(\ar_0): [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$.
+Observe that the implication holds for $\args = \emptyset$, because $\emptyset \nibeatscoal \ar_0$ as $\ar_0$ $i$-defends $\phi$.
+Now, given $k \in \N$, assume that $\forall \args \subseteq \allargs \suchthat \card{\args} = k: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$, and let us show that $\forall \args \subseteq \allargs \suchthat \card{\args} = k + 1: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$.
+	Consider $\args \subseteq \allargs \suchthat \card{\args} = k + 1 \land \args \ibeatscoal \ar_0$.
+One of the following two cases hold.
+First case: $\forall \args' \subset \args \suchthat \card{\args'} = k: \args \nibeatscoalstr \ar_0$.
+Then, $\forall \ar_1 \in \args: \ar_1 \ibeats \ar_0$.
+Second case: $\exists \args' \subset \args \suchthat \card{\args'} = k \land \args' \ibeatscoalstr \ar_0$.
+Then, $\args' \ibeatscoal \ar_0$ (recalling that ${\ibeatscoalstr} \subseteq {\ibeatscoal}$ and using the contrapositive), thus $\exists \ar_1 \in \args' \suchthat \ar_1 \ibeats \ar_0$ (using the induction hypothesis), hence, $\exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$.
 
-	Lemma: given any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$, if $\allhistsznp ≠ \emptyset$, then $\hist \in \allhistred ⇒ \exists \histp \in \allhistsznp \suchthat \emptyset ≠ \args^{\histp} \subset \args^{\hist}$.
-To see this, pick as $\histp$ any sequence consisting of the arguments contained in $\args^{\hist} \setminus \set{\ar_1}$, followed by $\ar_0$.
-	First, $\histp \in \allhistsznp$, because as $\hist \in \allhistred$, $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$, thus, $\histp \nileadstost \phi$. 
-	Second, $\args^{\histp} = \args^{\hist} \setminus \set{\ar_1}$, because $\args^{\hist} \setminus \set{\ar_1} \subseteq \args^{\histp} = \left(\gbeatsinv(\ar_0) \cap \histp\right) \subseteq \args^{\hist} \setminus \set{\ar_1}$.
-	Finally, $\args^{\histp} ≠ \emptyset$ follows from two facts: that $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$ (see “First” here above) and that $\emptyset \sinef \ar_0$, which is implied by $\ar_0$ $i$-defends $\phi$.
-
-	We conclude from this lemma that given any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$, if $\exists \hist \in \allhistsznp \suchthat \args^{\hist} ≠ \emptyset$, then $\exists \histp \in \allhistnonred$.
-To see this, given $\hist \in \allhistsznp \suchthat \args^{\hist} ≠ \emptyset$, define a finite sequence of sequences of arguments, starting with $\hist_0 = \hist$, then, for $k \in \N$, if $\hist_k \in \allhistred$, define $\hist_{k + 1} \in \allhistsznp$ by applying the lemma, thus with $\emptyset ≠ \args^{\hist_{k + 1}} \subset \args^{\hist_k}$.
-Because $\hist_0$ is finite (being an element of $\allhist$), $\args^{\hist_0}$ is finite, thus this process ends with some $\hist_k \in \allhistnonred$.
+	This lemma permits to deduce that, given $\ar_0$ that $i$-defends $\phi$, $\hist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$, and $\args = \gbeatsinv(\ar_0) \cap \hist$: $\args ≠ \emptyset ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$.
+This holds because in that case, $\args \ibeatscoal \ar_0$.
 
@@
 	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
-	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhistsznp$.
-	Because $\ar_0$ $i$-defends $\phi$, $\args^{\hist} ≠ \emptyset$. 
-	From the preceding conclusion, we can pick some $\histp \in \allhistnonred$.
-	Thus, $\exists \ar_1 \in \args^{\histp} \suchthat \args^{\histp} \setminus \set{\ar_1} \sinef \ar_0$.
-	This shows that $\ar_1 \gbeats \ar_0$ and $\ar_1 \ibeats \ar_0$: 
-		by definition of $\args^{\histp}$, $\ar_1 \in \gbeatsinv(\ar_0) \cap \histp$; and 
-		$[\ar_0 \in \histp \land \histp \nileadstost \phi]$ follow from $\histp \in \allhistnonred$.
+	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$.
+	Define $\args = \gbeatsinv(\ar_0) \cap \hist$.
+	Because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
+	From the preceding conclusion, $\exists \ar_1 \in \args \suchthat \ar_1 \gbeats \ar_0$ and $\ar_1 \ibeats \ar_0$.
 	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \alldargs \suchthat \ard_2 \dbeats \ar_1$.

### 2020-07-25 simple.tex
Rm commands about prev defs

@@
 \begin{proof}
-	\NewDocumentCommand{\allhistsznp}{}{\mathscr{S}^{*, \ar_0}_{\not⇝ \phi}}
-	\NewDocumentCommand{\allhistred}{}{\mathscr{S}^{*, \ar_0, \mathit{red}}_{\not⇝ \phi}}
-	\NewDocumentCommand{\allhistnonred}{}{\mathscr{S}^{*, \ar_0, \mathit{irred}}_{\not⇝ \phi}}
-
 	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$, and normative adequacy brings the conclusion.

### 2020-07-25 simple.tex
Drop minimal attacking coalitions, for simpler definitions and a much simpler proof.

@@
 ${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
-${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton).
-Define $\df \subseteq \allargs × \alldargs$ as $\df = \dbeatsinv \circ \gbeatsinv$. 
+${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton).
+Given $\ar \in \allargs$, define $\df(\ar) \subseteq \powersetz{\alldargs}$ as $\df(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)}$. 
 The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
-As usual, $\ar + \ard$ means $+(\ar, \ard)$. 
-Define $\dfp \subseteq \allargs × \allargs$ as, $\forall \ar \in \allargs$: $\dfp(\ar) = \ar + \df(\ar) = \set{\ar + \ard \suchthat \ard \in \df(\ar)}$.
+Given any $\ar \in \allargs$ and $\dargs \in \df(\ar)$, $\ar + \dargs$ means $+(\ar, \dargs)$. 
+Define $\dfp \subseteq \allargs × \allargs$ as $\forall \ar \in \allargs: \dfp(\ar) = \set{\ar + \dargs \suchthat \dargs \in \df(\ar)}$.
+
+\begin{remark}
+	Equivalently, $\df(\ar_0) = \powersetz{\dbeatsinv \circ \gbeatsinv}$.
+First, $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{\dbeatsinv \circ \gbeatsinv}$.
+Indeed, $\ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$, hence, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\dargs ≠ \emptyset$; and $\ard \in \dargs$ thus $\ard \dbeats \ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$.
+Second, $\dargs \in \powersetz{\dbeatsinv \circ \gbeatsinv} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$.
+Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, $\dbeatsinv(\args) = \dargs$: considering $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$, $\ar_1 \in \args$, $\ard \in \dbeatsinv(\ar_1)$, thus, $\ard \in \dbeatsinv(\args)$; and considering $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$.
+That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
+\end{remark}
+
 An empirical theory must satisfy
@@
 Given $i \in I, \phi \in \Phi, \ar_0 \in \allargs$ and $\args \subseteq \gbeatsinv(\ar_0)$, define $\args \ibeatscoal \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.
-Define $\args \ibeatscoalstr \ar_0$ iff $\forall \hist \in \allhist: [\hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0] ⇒ \hist \nileadstost \phi$, that is, iff no $\hist$ that end with $\args$ followed by $\ar_0$ lead to $\phi$.
-Note that $\forall \ar_0 \in \allargs, \args \subseteq \gbeatsinv(\ar_0): \args \ibeatscoalstr \ar_0 ⇒ \args \ibeatscoal \ar_0$.
-That is because $\ar_0 \ngbeats \ar_0$, because $\gbeats$ is irreflexive by definition of an empirical theory, and thus suffices to consider any sequence of arguments $\hist$ using only and all the arguments $\args \cup \set{\ar_0}$ and placing $\ar_0$ last: because $\args \ibeatscoalstr \ar_0$, $\hist \nileadstost \phi$, and the existence of $\hist$ proves that $\args \ibeatscoal \ar_0$.
 
-Given $i \in I, \phi \in \Phi$ and $\ar_0, \ar_1 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \args \subseteq \gbeatsinv(\ar_0) \suchthat \ar_1 \in \args \land \args \ibeatscoal \ar_0 \land \args \setminus \set{\ar_1} \nibeatscoalstr \ar_0$.
-
-Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [\dbeatsinv \circ {\ibeatsinv}](\ar)$.
-Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
+Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \args \ibeatscoal \ar_0}$.
+Observe that $\di(\ar) \subseteq \df(\ar)$.
+Define $\dip \subseteq \allargs × \allargs$ as $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$.
 Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.
@@
 $\ar$ $i$-defends $\phi$ iff $\emptyset \nibeatscoal \ar$.
-
-\begin{remark}
-	I need the following two facts.
-1) If $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \args \ibeats \ar_0$.
-2) Proving that $\ar_2 \in \gargs$ is easy enough, thus, if $\args = \set{\ar_1, \ar'_1}$ is minimal for $\args \ibeats \ar_0$, then, showing $\exists \hist = (…, \ar_1, \ar_0) \ileadstost \phi, \ar'_1 \notin \hist$ (and the same inverting $\ar_1$ and $\ar'_1$), is enough.
-
-	Problem happens in the following case.
-$\ar'_1$ alone is uncertain, meaning $\exists \hist = (… \ar'_1 … \ar_0) \nileadstost \phi$ and $\exists \hist = (…, \ar'_1, \ar_0) \ileadstost \phi$.
-Then, a counter-theory $\delta$ may claim that $\ar'_1$ alone is ineffective: suffice to show the example $(…, \ar'_1, \ar_0) \ileadstost \phi$.
-Whereas in fact $\ar'_1$ alone is sometimes effective.
-Then, $\args = \set{\ar_1, \ar'_1}$ may be claimed to be effective by combination effect (and $\ar'_1$ can’t be blamed, although it should, as $\delta$ has “proven” it ineffective).
-Thus, $\ar_2$, defending against $\ar_1$, ends up in $\gargs$.
-Assume $\ar_1$ is innocuous for $i$ (otherwise, no problem, as $\ar_2$ is legitimate) ($\ar_1$ could be efficient for others than $i$, which justifies $\ar_1 \gbeats \ar_0$).
-Then $\ar_2$ shouldn’t be played, it is only included as a result of the weak demand about proving that $\ar'_1$ is ineffective.
-
-Note that if we agree that $\ar'_1$ is uncertain, then $\gamma$ should play $\ar'_2$ to answer the coalition $\args$ attack (as required even without the coalitions definition), not $\ar_2$.
-But this conflicts with the formal definitions.
-Note that if $\ar'_1$ is known as uncertain for everybody, there is no problem, as $\gamma$ should include $\ar'_2$ from the start.
-Problem happens if $\ar'_1$ is suspected uncertain for some and inefficient for others.
-
-	Here is a similar problem: assume $\ar_1$ and $\ar'_1$ are uncertain for some and innocuous for others (not necessarily the same).
-Assume we observed $(…, \ar_1, \ar_0) \ileadstost \phi$ (without $\ar'_1$) and $(…, \ar'_1, \ar_0) \ileadstost \phi$ (without $\ar_1$, and imagining this would be possible to know); but $\set{\ar_1, \ar'_1}$ attacks $\ar_0$.
-Then we ignore whether, for $i$, $\ar_1$ or $\ar'_1$ is innocuous; and thus ignore whether $\ar_2$ or $\ar'_2$ should be played.
-The right answer is probably: play $\ar_2 + \ar'_2$.
-In fact, suffices to assume that, whenever such situation can happen, $\gamma$ has planned that $\ar_2$ be attacked by $\ar'_1$, and conversely, and then we get immediately that $\ar_2 + \ar'_2$ is involved.
-(But also that $\ar_2$ should be defended, whereas this is perhaps too demanding?)
-\end{remark}
 
@@
 
-	Lemma.
-Given any $\ar_0$ that $i$-defends $\phi$, $\forall \args \subseteq \gbeatsinv(\ar_0): [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$.
-Observe that the implication holds for $\args = \emptyset$, because $\emptyset \nibeatscoal \ar_0$ as $\ar_0$ $i$-defends $\phi$.
-Now, given $k \in \N$, assume that $\forall \args \subseteq \allargs \suchthat \card{\args} = k: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$, and let us show that $\forall \args \subseteq \allargs \suchthat \card{\args} = k + 1: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$.
-	Consider $\args \subseteq \allargs \suchthat \card{\args} = k + 1 \land \args \ibeatscoal \ar_0$.
-One of the following two cases hold.
-First case: $\forall \args' \subset \args \suchthat \card{\args'} = k: \args \nibeatscoalstr \ar_0$.
-Then, $\forall \ar_1 \in \args: \ar_1 \ibeats \ar_0$.
-Second case: $\exists \args' \subset \args \suchthat \card{\args'} = k \land \args' \ibeatscoalstr \ar_0$.
-Then, $\args' \ibeatscoal \ar_0$ (recalling that ${\ibeatscoalstr} \subseteq {\ibeatscoal}$ and using the contrapositive), thus $\exists \ar_1 \in \args' \suchthat \ar_1 \ibeats \ar_0$ (using the induction hypothesis), hence, $\exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$.
-
-	This lemma permits to deduce that, given $\ar_0$ that $i$-defends $\phi$, $\hist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$, and $\args = \gbeatsinv(\ar_0) \cap \hist$: $\args ≠ \emptyset ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$.
-This holds because in that case, $\args \ibeatscoal \ar_0$.
-
-	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \ar_1 \in \allargs, \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1 \ibeats \ar_0 \land \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2 \in \dip(\ar_0)$.
+	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \dargs \in \di(\ar_0)$.
 	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
 	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$.
-	Define $\args = \gbeatsinv(\ar_0) \cap \hist$.
-	Because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
-	From the preceding conclusion, $\exists \ar_1 \in \args \suchthat \ar_1 \gbeats \ar_0$ and $\ar_1 \ibeats \ar_0$.
-	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \alldargs \suchthat \ard_2 \dbeats \ar_1$.
-Defining $\ar_2 = \ar_0 + \ard_2$, $\ar_2 \in \dip(\ar_0)$ by definition of $\dip$.
+	Define $\args = \gbeatsinv(\ar_0) \cap \hist$. Thus, $\args \ibeatscoal \ar_0$.
+	Also, because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
+	Therefore, $\dbeatsinv(\args) \in \di(\ar_0)$.
 
 	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs[i, \phi] \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs[i, \phi] \cap \dfp(\ar_0)$.
-That is because $\ar_0 \in \gargs[i, \phi] ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering $\ard_2$ and $\ar_2$ as defined in the lemma, $\ar_2 \in \gargs[i, \phi]$ by definition of $\gargs[i, \phi]$ and $\ard_2 \in \df(\ar_0)$ by definition of $\df$.
+That is because $\ar_0 \in \gargs[i, \phi] ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering any $\dargs \in \di(\ar_0)$ and $\ar_2 = \ar_0 + \dargs$, $\ar_2 \in \gargs[i, \phi]$ by definition of $\gargs[i, \phi]$ and $\ar_2 \in \dfp(\ar_0)$ because $\dargs \in \di(\ar_0) ⇒ \dargs \in \df(\ar_0)$.
 
@@
 Observe that $\ar_0 \in \gargs[i, \phi]$.
-Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the last lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$.
+Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$.
 	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
@@
 	Better first simplify the related definitions in the “normal” case.
+
+	Consider extending $\histend$ with $\zar$ to have $\zar \in \histend$.
 \end{remark}
@@
 \subsection{Simple to complex}
-From an additive single-answer empirical theory, we can define a function: $\forall \ar_1 \gbeats \ar_0: f(\ar_1, \ar_0) = \ar_0 + {\gbeatsinv}(\ar_1) = \set{\ar_0 + \ard_2 \suchthat \ard_2 \in {\gbeatsinv}(\ar_1)}$, and $f(\ar_1, \ar_0) = \emptyset$ otherwise.
-Thus, $f = \set{((\ar_1, \ar_0), \ar_2) \suchthat \exists \ard_2 \in \allargs \suchthat \ard_2 \gbeats \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2}$.
+From an additive single-answer empirical theory, we can define a function: $\forall \ar_1 \gbeats \ar_0: f(\ar_1, \ar_0) = \ar_0 + {\gbeatsinv}(\ar_1) = \set{\ar_0 + \ard \suchthat \ard \in {\gbeatsinv}(\ar_1)}$, and $f(\ar_1, \ar_0) = \emptyset$ otherwise.
+Thus, $f = \set{((\ar_1, \ar_0), \ar_2) \suchthat \exists \ard \in \allargs \suchthat \ard \gbeats \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard}$.
 Also, from the previous definition, $g(\ar_0)(\ar_0 + \argsd_2) = dom(f^{-1}(\ar_0 + \argsd_2) \cap (\allargs × \set{\ar_0})) = {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$ because $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \argsd_2) ⇔ \exists \ar_2 \in \ar_0 + \argsd_2 \suchthat \ar_2 \in f(\ar_1, \ar_0) ⇔ \ar_1 \gbeats \ar_0 \land \exists \ard \in \argsd_2 \suchthat \ard \gbeats \ar_1$.
@@
 
-Note that $f^{-1}(\ar_0 + \ar_2) ≠ {\gbeats}(\ar_2) × \set{\ar_0}$: if ${\gbeats} = \set{(\ard_2, \ar_1), (\ar_1, \ar_0), (\ard_6, \ar_5), (\ar_5, \ar_4)}$, and $\ar_0 + \ard_2 = \ar_4 + \ard_6$, then $f^{-1}(\ar_0 + \ard_2) = f^{-1}(\ar_4 + \ard_6) = \set{(\ar_1, \ar_0), (\ar_5, \ar_4)}$ and ${\gbeats}(\ard_2) × \set{\ar_0} = \set{(\ar_1, \ar_0)}$.
+Note that $f^{-1}(\ar_0 + \ar_2) ≠ {\gbeats}(\ar_2) × \set{\ar_0}$: if ${\gbeats} = \set{(\ard, \ar_1), (\ar_1, \ar_0), (\ard[6], \ar_5), (\ar_5, \ar_4)}$, and $\ar_0 + \ard = \ar_4 + \ard[6]$, then $f^{-1}(\ar_0 + \ard) = f^{-1}(\ar_4 + \ard[6]) = \set{(\ar_1, \ar_0), (\ar_5, \ar_4)}$ and ${\gbeats}(\ard) × \set{\ar_0} = \set{(\ar_1, \ar_0)}$.
 Also, note that $g(\ar_0)(\ar_0 + \argsd_2) ≠ {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$.
-Consider ${\gbeats} = \set{(\ard_2, \ar_1), (\ar_1, \ar_0)}, \ar_2 = \ar_0 + \ard = \ar_0 + \ard_2$.
+Consider ${\gbeats} = \set{(\ard, \ar_1), (\ar_1, \ar_0)}, \ar_2 = \ar_0 + \ard = \ar_0 + \ard$.
 Then, $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \ard)$, hence, $\ar_1 \in g(\ar_0)(\ar_0 + \ard)$, but ${\gbeats}(\ard) = \emptyset$.

### 2020-07-26 simple.tex
Simpler commands and notation

@@
 
-Given $i \in I, \phi \in \Phi, \ar_0 \in \allargs$ and $\args \subseteq \gbeatsinv(\ar_0)$, define $\args \ibeatscoal \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.
+Given $i \in I, \phi \in \Phi, \ar_0 \in \allargs$ and $\args \subseteq \gbeatsinv(\ar_0)$, define $\args \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.
 
-Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \args \ibeatscoal \ar_0}$.
+Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \args \ibeats \ar_0}$.
 Observe that $\di(\ar) \subseteq \df(\ar)$.
@@
 
-$\ar$ $i$-defends $\phi$ iff $\emptyset \nibeatscoal \ar$.
+$\ar$ $i$-defends $\phi$ iff $\emptyset \nibeats \ar$.
 
@@
 	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$.
-	Define $\args = \gbeatsinv(\ar_0) \cap \hist$. Thus, $\args \ibeatscoal \ar_0$.
+	Define $\args = \gbeatsinv(\ar_0) \cap \hist$. Thus, $\args \ibeats \ar_0$.
 	Also, because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
@@
 Otherwise, here is a test procedure for that falsifies at least one of these theories, given any $\phi \in \Phi$ about which they disagree and any $i \in I$.
-
-Note first that $\ar_0 \gbeats \ar_0$ is impossible because … TODO why didn’t I need this before?
 

### 2020-07-26 simple.tex
Sketch of protocol comparing theories

@@
 Define $\dip \subseteq \allargs × \allargs$ as $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$.
-Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.
+Given $i \in I, \phi \in \gPhi$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.
 
@@
 \begin{definition}[Convincingness]
-	$\forall i \in I, \phi \in \gPhi, \ar \in \gargs[i, \phi]: \ar$ $i$-defends $\phi$.
+	$\forall i \in I, \phi \in \gPhi, \ar \in \gargs: \ar$ $i$-defends $\phi$.
 \end{definition}
 
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi$.
+A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs) \suchthat \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi$.
 
@@
 \begin{proof}
-	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
+	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs, \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
 \end{proof}
@@
 
-	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs[i, \phi] \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs[i, \phi] \cap \dfp(\ar_0)$.
-That is because $\ar_0 \in \gargs[i, \phi] ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering any $\dargs \in \di(\ar_0)$ and $\ar_2 = \ar_0 + \dargs$, $\ar_2 \in \gargs[i, \phi]$ by definition of $\gargs[i, \phi]$ and $\ar_2 \in \dfp(\ar_0)$ because $\dargs \in \di(\ar_0) ⇒ \dargs \in \df(\ar_0)$.
+	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$.
+That is because $\ar_0 \in \gargs ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering any $\dargs \in \di(\ar_0)$ and $\ar_2 = \ar_0 + \dargs$, $\ar_2 \in \gargs$ by definition of $\gargs$ and $\ar_2 \in \dfp(\ar_0)$ because $\dargs \in \di(\ar_0) ⇒ \dargs \in \df(\ar_0)$.
 
-	To prove the theorem, build a finite sequence of arguments in $\gargs[i, \phi]$, starting with any $\ar_0 \in \gleadstoinv(\phi)$.
-Observe that $\ar_0 \in \gargs[i, \phi]$.
-Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$.
+	To prove the theorem, build a finite sequence of arguments in $\gargs$, starting with any $\ar_0 \in \gleadstoinv(\phi)$.
+Observe that $\ar_0 \in \gargs$.
+Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the lemma, obtaining $\ar_{k + 2} \in \gargs \cap \dfp^\frac{k + 2}{2}(\ar_0)$.
 	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
@@
 If $\gamma$ and $\delta$ agree about all $\phi$, there is nothing to test as the theories are compatible.
-Otherwise, here is a test procedure for that falsifies at least one of these theories, given any $\phi \in \Phi$ about which they disagree and any $i \in I$.
+Otherwise, here is a test procedure that falsifies at least one of these theories, given any $\phi \in \Phi$ about which they disagree and any $i \in I$.
 
 \begin{remark}
-	$\allargs \setminus \gleadstoinv(\phi)$ are the non-initial arguments.
-An empirical theory must satisfy: $\dbeats$ covers all attackers and $\allargs \setminus \gleadstoinv(\phi)$.
-Note that $\ar'_0 \gbeats \ar_0$ seems possible (thus, an attacker not in $\allargs \setminus \gleadstoinv(\phi)$), and $\zar$ not attacking anything but in $\allargs \setminus \gleadstoinv(\phi)$ is possible, where $\zar$ designates an argument that says nothing.
+	Make $\gamma$ able to answer directly $\ar_1$ when $\delta$ starts the protocol.
 
-	If $\hist$ does not include any initial argument, and includes $\ar_1$, and leads to $¬\phi$, then proceed as if $\ar_1$ attacks $\emptyset$, thus, include the defensor against $\ar_1$.
-This defensor must be in $\allargs \cap \alldargs$.
-(It’s probably better to remove the $\alldargs$ concept.)
+	Using $\zar$, this can be done as follows.
+Assume $\zar \notin \allargs$.
+Define $\ar_1 \gbeats \zar$ iff $\ar_1 \in \allargs \setminus \gleadstoinv(\phi)$ (the non-initial arguments).
+Demand that $\dbeats$ cover all non-initial arguments.
+(Note that $\ar'_0 \gbeats \ar_0$ seems possible (thus, an attacker not in $\allargs \setminus \gleadstoinv(\phi)$), and $\zar$ not attacking anything but in $\allargs \setminus \gleadstoinv(\phi)$ is possible, where $\zar$ designates an argument that says nothing.) Remove the $\alldargs$ concept, so as to be able to use directly the defensors against the non-initial arguments (alternative: extend $+$ to allow $\zar + \ard$).
+Extend $\histend$ with $\zar$ to have $\zar \in \histend$.
+Define $\gargs = (\dip)^k(\gleadstoinv(\Phi) \cup \di(\zar))$.
 
-	Better first simplify the related definitions in the “normal” case.
-
-	Consider extending $\histend$ with $\zar$ to have $\zar \in \histend$.
+	It can also be done without using $\zar$, as follows.
+Demand that $\dbeats$ cover all non-initial arguments.
+Define $\di(\zar) = \set{\dbeatsinv(\args) \suchthat \exists \hist \in \allhist \suchthat \emptyset ≠ \args = \allargs \setminus \gbeatsinv(\Phi) \cap \hist \land \hist \nileadstost \phi}$.
+Define $\gargs = (\dip)^k(\gleadstoinv(\Phi) \cup \di(\zar))$.
 \end{remark}
 
+\begin{remark}
+	Informal idea.
 	Consider $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto \phi$.
@@
 ($\ar_0$ attacks $\delta$ but $\delta$ is not able to defend.)…
+\end{remark}
 
-Model: for a given $i$.
-Defends $\prop$.
-$\exists \ar_1 \in \args_\eta \suchthat \ar_1 \ileadsto \prop$.
-Then, $\forall \ar_2 \in \gargs \suchthat (\ar_2, \ar_1) \ileadsto ¬\prop: \exists \ar_3 \in \args_\eta \suchthat (\ar_3, \ar_2) \ileadsto \prop.$
+Lemma (variant of a previous one).
+$\ar_0$ $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, thus $\dargs = \dbeatsinv(\gbeatsinv(\ar_0) \cap \hist) \in \di(\ar_0)$, thus $\ar_2 = \ar_0 + \dargs \in \gargs \cap \dfp(\ar_0)$.
+
+Consider $(…, \ar_0) \ileadstost \phi$ and $\hist = (…, \ar_0, \ar_{-1}) \nileadstost ¬\phi$, with $\ar_0 \in \gargs, \ar_{-1} \in \gargs[¬\phi]$.
+By the lemma (applied on $\ar_{-1}$), $\ar_1 = \ar_{-1} + \dbeatsinv(\gbeatsinv(\ar_{-1}) \cap \hist) \in \gargs[¬\phi] \cap \dfp(\ar_{-1})$.
+Iterating if necessary, we obtain $(…, \ar_1) \ileadstost ¬\phi$.
+Now either already the previous step was $(…, \ar_0, \ar_1)$, or we test $(…, \ar_1, \ar_0)$.
+If $(…, \ar_1, \ar_0) \ileadstost \phi$, apply the lemma again on $\ar_1$, and go on.
+Finally: $\hist = (…, \ar_1, \ar_0) \nileadstost \phi$.
+Similarly, then, obtain $\ar_2 = \ar_0 + \dargs \in \gargs \cap \dfp(\ar_0)$.
+If $\ar_0 \in (\dfp)^k(…)$, then $\ar_2 \in (\dfp)^{k'}(…)$, with $k' > k$.
+And $(…, \ar_2, \ar_1) \nileadstost ¬\phi$, so we can apply the strating step again.
 

### 2020-08-02 simple.tex
Effective comparison (and a few other things)

@@
 \begin{proposition}[Protocol coherence]
-	\label{prop:protcoh}
+	\label{th:protcoh}
 	$\forall i \in I, \phi \in \Phi$:
@@
 \end{definition}
-The following proposition directly follows from the definitions, together with \cref{prop:protcoh}.
+The following proposition directly follows from the definitions, together with \cref{th:protcoh}.
 \begin{proposition}
@@
 	Second, $\dargs \in \powersetz{\dbeatsinv \circ \gbeatsinv} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
-Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, $\dbeatsinv(\args) = \dargs$: considering $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$, $\ar_1 \in \args$, $\ard \in \dbeatsinv(\ar_1)$, thus, $\ard \in \dbeatsinv(\args)$; and considering $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$.
+	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$, $\ar_1 \in \args$, $\ard \in \dbeatsinv(\ar_1)$, thus, $\ard \in \dbeatsinv(\args)$; and considering $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$.
 	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
@@
 An empirical theory must satisfy
-$\exists k \in \N \suchthat \dfp^k(\gleadstoinv(\Phi)) = \emptyset$, where $\dfp^0$ is the identity function over $\allargs$.
+$\exists k \in \N \suchthat (\dfp)^k(\gleadstoinv(\Phi)) = \emptyset$, where $(\dfp)^0$ is the identity function over $\allargs$.
 
@@
 
-Given $i \in I, \phi \in \Phi, \ar_0 \in \allargs$ and $\args \subseteq \gbeatsinv(\ar_0)$, define $\args \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.
+Given $i \in I, \phi \in \Phi, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \phi$.
 
-Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \args \ibeats \ar_0}$.
+Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
 Observe that $\di(\ar) \subseteq \df(\ar)$.
@@
 
-$\ar$ $i$-defends $\phi$ iff $\emptyset \nibeats \ar$.
+I write that $\ar$ \emph{$i$-defends} $\phi$ to mean that $\emptyset \nibeats \ar$.
 
@@
 
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs) \suchthat \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi$.
+A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist, \ar) \in I × \gPhi × \allhist × \gargs$ such that $\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \phi$.
+I also write that $(i, \phi, \hist, \ar)$ falsifies $\gamma$ to mean that it is a falsification instance of $\gamma$.
 
@@
 \begin{proof}
-	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs, \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
+	For all $i \in I, \phi \in \gPhi, \ar \in \gargs$: $\ar$ does not $i$-defend $\phi$ iff $\exists \hist \in \allhist \suchthat \left[\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist, \ar)$ falsifies $\gamma$.
+Therefore, $\gamma$ is not convincing iff $\exists (i, \phi, \ar) \suchthat \ar$ does not $i$-defend $\phi$ iff $\exists \hist \suchthat (i, \phi, \hist, \ar)$ falsifies $\gamma$ iff $\gamma$ has a falsification instance.
 \end{proof}
@@
 Observe that $\ar_0 \in \gargs$.
-Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the lemma, obtaining $\ar_{k + 2} \in \gargs \cap \dfp^\frac{k + 2}{2}(\ar_0)$.
-	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
+Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$.
+	By definition of an empirical theory, $\exists k \in \N \suchthat (\dfp)^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
 \end{proof}
@@
 \subsection{Effectively comparing models}
-Given a normative theory, consider two empirical theories $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$ and $(q', (\gleadsto[q(i)][\delta])_{q(i) \in q(I)}, \gbeats', \alldargs, \dbeats', +')$.
+\begin{lemma}
+	\label{th:produce}
+	Given $\phi \in \Phi$, $\ar_0 \in \allargs$ that $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$.
+Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
+\end{lemma}
+\begin{proof}
+	Because $\dargs \in \di(\ar_0)$.
+\end{proof}
 
-Given a normative theory and $\phi \in \Phi$, say that two empirical theories (for that normative theory) disagree about $\phi$ iff $\phi \in \gPhi \land ¬\phi \in \gPhi[\delta]$.
+Given $\phi \in \Phi$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\phi$ iff $\phi \in \gPhi[\gamma] \land ¬\phi \in \gPhi[\delta]$.
+Say that they are incompatible iff there is at least one $\phi \in \Phi$ that they disagree about.
 
-If $\gamma$ and $\delta$ agree about all $\phi$, there is nothing to test as the theories are compatible.
-Otherwise, here is a test procedure that falsifies at least one of these theories, given any $\phi \in \Phi$ about which they disagree and any $i \in I$.
+Given $\phi \in \Phi$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $(\gamma, \phi)$ iff $\hist \nileadstost \phi$ and $\ar_\gamma \in \histend$.
+Given $\phi \in \Phi, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \phi)$ or $(\hist, \ar_\delta)$ challenges $(\delta, ¬\phi)$.
+\commentOC{This should be called a $\phi$-or-$¬\phi$-challenge.}
+
+\begin{lemma}
+	\label{th:endchal}
+	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$: $(\hist, \ar_\gamma, \ar_\delta)$ is a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge.
+\end{lemma}
+\begin{proof}
+	Either $\hist \nileadstost \phi$, and $(\hist, \ar_\gamma, \ar_\delta)$ challenges $(\gamma, \phi)$, or $\hist \ileadstost \phi$, hence, by \cref{th:protcoh}, $\hist \nileadstost ¬\phi$, and $(\hist, \ar_\gamma, \ar_\delta)$ challenges $(\delta, ¬\phi)$.
+\end{proof}
+
+\begin{lemma}
+	\label{th:nextchal}
+	Given $(\hist, \ar_\gamma)$ challenging $(\gamma, \phi)$, with $\ar_\gamma \in \gargs \cap \dfpclosure$, and $\ar_\delta \in \gargsdelta$: either $(i, \phi, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\phi))$.
+\end{lemma}
+\begin{proof}
+	If $\ar_\gamma$ does not $i$-defend $\phi$, then $(i, \phi, \hist, \ar_\gamma)$ falsifies $\gamma$, which ends the proof. 
+	Thus, assume that $\ar_\gamma$ $i$-defends $\phi$.
+
+	\Cref{th:produce} applies and yields $\ar'_\gamma = \ar_\gamma + \dbeatsinv(\gbeatsinv(\ar_\gamma)) \in \gargs \cap \dfp(\ar_\gamma)$, thus $\ar'_\gamma \in (\dfp)^{(k + 1)}(\gleadstoinv(\phi))$. 
+	Now, define $\histpp = (\hist, \ar'_\gamma)$ and test whether $\histpp \nileadstost \phi$.
+
+	If $\histpp \nileadstost \phi$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\gamma, \ar_\delta)$ challenges $(\gamma, \phi)$, which concludes the proof. 
+	Thus, assume that $\histpp \ileadstost \phi$.
+
+	Let us now define $\histp$ such that $\set{\ar'_\gamma, \ar_\delta} \subseteq \histpend$, so that \cref{th:endchal} applies on $(\histp, \ar'_\gamma, \ar_\delta)$, which will conclude the proof.
+
+	If $\ar_\delta \in \histppend$, this is done by defining $\histp = \histpp$. Otherwise, define $\histp = (\histpp, \ar_\delta)$ and test whether $\histp \nileadstost \phi$. 
+\end{proof}
+
+Given a normative theory and two empirical theories for that normative theory and $i \in I$, 
+a \emph{test procedure with $i$} is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N^*$, of sequences of arguments, 
+such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$, and 
+such that $(i, \phi, {\hist}^N)$ falsifies one of the empirical theories for some $\phi \in \Phi$. 
+A sequence of arguments $\histp$ starts with a sequence of arguments $\hist$ of length $l$ iff $\histp$ has length at least $l$ and $\forall k \in \intvl{1, l}: \histp_k = \hist_k$.
+\commentOC{Need the test procedure to be a tree.
+Atom: $(k, \phi)$ meaning whether ${\hist}^k \ileadstost \phi$.
+Branch label: atoms linked using or and and operators.
+From a node $n = (\hist, \ar, \phi)$, let branches depart, such that their labels do not overlap.
+From a node, if no branch label is true, the node must falsify a theory.
+In the case of the procedure below, it is not a list because we may query several times the same theory or switch to the other one, depending on the last answer.
+But if simplifying the theory (single-try), we may then simplify the definition of a test procedure.}
+
+\begin{theorem}
+	Given two incompatible empirical theories for a given normative theory, $\alpha = (q, (\gleadsto[q(i)][\alpha])_{q(i) \in q(I)}, \gbeats[\alpha], \alldargs, \dbeats[\alpha], +_\alpha)$ and $\beta = (q', (\gleadsto[q(i)][\beta])_{q(i) \in q(I)}, \gbeats[\beta], \alldargs, \dbeats[\beta], +')$ and given any $i \in I$, there exists a test procedure with $i$ that falsifies one of these theories.
+\end{theorem}
+\begin{proof}
+	Pick any $\phi \in \Phi$ about which $\alpha$ and $\beta$ disagree.
+
+	Given $k_\alpha, k_\beta \in \N, \hist \in \allhist, \ar_\alpha \in \gargsalpha, \ar_\beta \in \gargsbeta$, 
+	say that 
+	$(\hist, \ar_\alpha, \ar_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta)$ iff 
+	$(\hist, \ar_\alpha, \ar_\beta)$ is a $(\alpha, \phi$ or $\beta, ¬\phi)$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\phi))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](¬\phi))$.
+
+	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[][\beta] ¬\phi$.
+Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](¬\phi))$.
+Test whether $(\ar_{-1}) \nileadstost \phi$.
+If so, $(i, \phi, (\ar_{-1}), \ar_{-1})$ falsifies $\beta$, which ends the procedure.
+	Thus, assume that $(\ar_{-1}) \ileadstost \phi$.
+
+	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[][\alpha] \phi$.
+Observe that $\ar_0 \in \gargsalpha \cap (\dfp[\alpha])^0(\gleadstoinv[\alpha](\phi))$.
+Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \phi$.
+By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $(\alpha, \phi$ or $\beta, ¬\phi)$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
+
+	Suffices now to apply \cref{th:nextchal} repetitively, until finding a falsification instance of $\alpha$ or $\beta$.
+This is because, given a challenge $(\hist, \ar_\alpha, \ar_\beta)$ of complexity $(k_\alpha, k_\beta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity.
+Indeed, if $(\hist, \ar_\alpha)$ challenges $(\alpha, \phi)$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
+And if $(\hist, \ar_\beta)$ challenges $(\beta, ¬\phi)$, apply \cref{th:nextchal} with $¬\phi$ for $\phi$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.
+
+	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\phi)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](¬\phi)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
+\end{proof}
 
@@
 
-\begin{remark}
-	Informal idea.
-	Consider $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto \phi$.
-Test whether $(\ar_0) \ileadstost \phi$.
-If not, $(i, \phi, (\ar_0))$ is a falsification instance of $\gamma$.
-If $(\ar_0) \ileadstost \phi$, check whether some $\ar_1 \dbeats' \ar_0$.
-If not, $\delta$ is falsified?
-($\ar_0$ attacks $\delta$ but $\delta$ is not able to defend.)…
-\end{remark}
+\subsection{TODO, about comparisons}
+Count the number of tests; assume simpler theory.
 
-Lemma (variant of a previous one).
-$\ar_0$ $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, thus $\dargs = \dbeatsinv(\gbeatsinv(\ar_0) \cap \hist) \in \di(\ar_0)$, thus $\ar_2 = \ar_0 + \dargs \in \gargs \cap \dfp(\ar_0)$.
+Indicate sufficient hypothesis for ensuring that if a model resisted every attack, it is valid. Thus, that searching for falsification instances in the tested ones is enough.
 
-Consider $(…, \ar_0) \ileadstost \phi$ and $\hist = (…, \ar_0, \ar_{-1}) \nileadstost ¬\phi$, with $\ar_0 \in \gargs, \ar_{-1} \in \gargs[¬\phi]$.
-By the lemma (applied on $\ar_{-1}$), $\ar_1 = \ar_{-1} + \dbeatsinv(\gbeatsinv(\ar_{-1}) \cap \hist) \in \gargs[¬\phi] \cap \dfp(\ar_{-1})$.
-Iterating if necessary, we obtain $(…, \ar_1) \ileadstost ¬\phi$.
-Now either already the previous step was $(…, \ar_0, \ar_1)$, or we test $(…, \ar_1, \ar_0)$.
-If $(…, \ar_1, \ar_0) \ileadstost \phi$, apply the lemma again on $\ar_1$, and go on.
-Finally: $\hist = (…, \ar_1, \ar_0) \nileadstost \phi$.
-Similarly, then, obtain $\ar_2 = \ar_0 + \dargs \in \gargs \cap \dfp(\ar_0)$.
-If $\ar_0 \in (\dfp)^k(…)$, then $\ar_2 \in (\dfp)^{k'}(…)$, with $k' > k$.
-And $(…, \ar_2, \ar_1) \nileadstost ¬\phi$, so we can apply the strating step again.
+\section{LS}
+%Idea: argue for P > $.
+%4 ways:
+%- choose
+%- rate attractivity: b1 → +; b2 → ++ thus b2 > b1
+%- bids to buy (B-bid): I’d pay max $4 to buy and play b1; I’d pay max $6 to play b2 thus b2 > b1
+%- bids to sell (S-bid): I’d sell b1 for at least $3; I’d sell b2 for at least $5 thus b2 > b1.
+%
+%First two: focus on probs. Last two: focus on amounts.
+%
+%Compare P = (.99, +$4; .01, −$0.1) VS $ = (.33, +$16; .67, −$2). Typically, choose P and bid more for $.
+%E[P] ≈ $4; E[$] ≈ 5+1/3 − 4/3 = $4.
+%
+%XP1.
+Choice VS S-bid.
+No gambling.
+6 P bets, 7 $ bets.
+12 pairs, of which 6 presented in the table: (P, $), choose one, and indicate the strength of your preference (slight to very strong).
+Then 19 bets using S-big, 6 practice (other bets) then 13 were analyzed.
+%
+%E[P] and E[$] (of the example above) are similar, but bids “greatly exceeding the expected value of $3.94 are common”.
+%
+%XP2. Choice VS B-bid.
+%
+%XP3. With effective gambling and iterated thinking to thing about their preference.
+Define $P = (.99, +\$4; .01, −\$0.1)$ and $D = (.33, +\$16; .67, −\$2)$.
+
+Theory claims that all $i$’s prefer deliberately $P$ to $D$, in the sense of betting at least as much for.
+
+Define $\phi$ as: $i$ deliberately prefers $P$ to $D$, in the sense of bidding at least as much for $P$ than for $D$ after deliberation.
+Define $¬\phi$ similarly, but bidding more for $D$ than for $P$.
+
+Define $\ileadsto$ as follows.
+Given $\hist = (…, \ar)$, $\hist \ileadstost \phi$ iff, in a situation of $i$ having been exposed to the prefix …, saying: “Considering the argument $\ar$, would you please indicate your maximum selling price for $P$, and for $D$” leads $i$ to act accordig to $\phi$.
+Note that $\hist \ileadsto \phi$ iff $\hist \nileadsto ¬\phi$.
+
+Thus, the normative axiom is satisfied iff, whenever there is a argument that, facing any counter-argument, leads $i$ to bid at least as much for $P$ than for $D$, we are ready to accept that $i$ deliberately prefers $P$ to $D$, in the bidding sense.
+
+Define $\ar_0$ as arguing that the bid for both P and D should equal their expected revenue, namely, $.99 × (\$4) − 0.01 × \$0.1$ or etc.
+“Imagine you play this bet 100 times.
+On average, you will win 99 times and lose 1 time, which means gaining 99 × \$4 = \$396 and losing 1 × \$0.10 = \$0.10, hence a total net gain of \$395.90.
+Thus, your average net gain for the $P$ bet would be \$3.9590.
+Etc.”
+
+Define $\ar_1$ as arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain.
+Define $\ar_2$ as arguing that the goal is to maximise average revenue, and thus, losses should count equally to gains.
+Define $\ar'_1$ as arguing by considering only what is to be gained and not the probabilities, and thus, arguing that $D$ is worth much more.
+Define $\ar'_2$ as arguing that also the probabilities should be taken into account.
+Define $+$ as the simple concatenation of its arguments.
+
+Then, define $\gbeats = \set{(\ar_1, \ar_0), (\ar'_1, \ar_0), (\ar'_1, \ar_2), (\ar_1, \ar'_2)}$, $\dbeats = \set{(\ar_2, \ar_1), (\ar'_2, \ar'_1)}$.
+
+TODO consider using only $\phi$ being sure, and dropping everything related to possibility.
 

### 2020-08-02 simple.tex
Cosmetic rework of normative analysis

@@
 \end{axiom}
-This axiom can be simplified, thanks to the following proposition.
-\begin{proposition}[Protocol coherence]
-	\label{th:protcoh}
+
+\Cref{ax:norm} is actually equivalent to the following property.
+\begin{property}[Simple normative adequacy]
+	\label{ax:snorm}
+	$\forall i \in I, \phi \in \Phi: 
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
+\end{property}
+
+To see why this hold, consider the following definition.
+\begin{definition}[Protocol coherence]
+	\label{def:protcoh}
 	$\forall i \in I, \phi \in \Phi$:
@@
 	\end{equation}
+\end{definition}
+\begin{proposition}
+	\label{th:protcoh}
+	Any normative theory satisfies Protocol coherence.
 \end{proposition}
@@
 
-Therefore, \cref{ax:norm} is actually equivalent to the following property.
-\begin{property}[Simple normative adequacy]
-	\label{ax:snorm}
-	$\forall i \in I, \phi \in \Phi: 
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
-\end{property}
+That \cref{ax:norm} is equivalent to \cref{ax:snorm} immediately follows from \cref{th:protcoh}.
+\begin{proposition}
+	\label{th:normeqsnorm}
+	Any normative theory satisfies Normative adequacy iff it satisfies simple normative adequacy.
+\end{proposition}
 
@@
 In this definition, $\oplus$ denotes the exclusive disjunction; thus $\phi \in \iPhi \oplus ¬\phi \in \iPhi$ is equivalent to: $\phi \in \iPhi ⇔ ¬\phi \notin \iPhi$.
-It can be seen to hold by recalling that \cref{ax:snorm} is equivalent to \cref{ax:norm}.
+It can be seen to hold by using \cref{th:normeqsnorm}.
 

### 2020-08-02 simple.tex
Slightly simpler def of empirical theories.

@@
 ${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton).
-Given $\ar \in \allargs$, define $\df(\ar) \subseteq \powersetz{\alldargs}$ as $\df(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)}$. 
-The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
-Given any $\ar \in \allargs$ and $\dargs \in \df(\ar)$, $\ar + \dargs$ means $+(\ar, \dargs)$. 
-Define $\dfp \subseteq \allargs × \allargs$ as $\forall \ar \in \allargs: \dfp(\ar) = \set{\ar + \dargs \suchthat \dargs \in \df(\ar)}$.
+Define $\df: \allargs → \powersetz{\allargs}$ as $\df = \dbeatsinv \circ \gbeatsinv$.
+Given $\ar \in \allargs$, $\df(\ar)$ denotes the \emph{fragments defending $\ar$}. 
+In other words, given $\ard \in \dargs$ and $\ar_0 \in \allargs$, $\ar_2 \in \df(\ar_0)$ iff $\exists \ar_1 \in \allargs \suchthat \ar_2 \dbeats \ar_1 \gbeats \ar_0$.
+A \emph{coalition defending $\ar$} is any element of $\powersetz{\df(\ar)}$.
+The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \powersetz{\df(\ar)}) → \allargs$.
+Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \df(\ar)$, $\ar + \dargs$ means $+(\ar, \dargs)$. 
+Given any $\ar \in \allargs$, define $\dfp(\ar)$, the \emph{defenders of $\ar$}, as $\dfp(\ar) = \set{\ar + \dargs \suchthat \emptyset ≠ \dargs \subseteq \df(\ar)}$.
+
+An empirical theory must satisfy
+$\exists k \in \N \suchthat (\dfp)^k(\gleadstoinv(\Phi)) = \emptyset$, where $(\dfp)^0$ is the identity function over $\allargs$.
 
 \begin{remark}
-	Equivalently, $\df(\ar_0) = \powersetz{\dbeatsinv \circ \gbeatsinv}$. 
+	$\df'(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$. 
 	First, $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{\dbeatsinv \circ \gbeatsinv}$. 
@@
 \end{remark}
-
-An empirical theory must satisfy
-$\exists k \in \N \suchthat (\dfp)^k(\gleadstoinv(\Phi)) = \emptyset$, where $(\dfp)^0$ is the identity function over $\allargs$.
 

### 2020-08-02 simple.tex
Better notations and removed q(i) parameterisation of a theory

@@
 \input{preamble/redac}
+\usepackage[normalem]{ulem}
 %\input{preamble/draw}
@@
 Define $\hist \ileadstost \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
+(The visual proximity of the symbols $\ileadsto$ and $\ileadstost$ creates a small risk of confusion, but I feel it is justified by the fact that $\ileadsto$ is not used in the rest of this article, except in the proof of \cref{th:protcoh}.)
 Given $\hist \in \allhist$, let $\histend$ denote the set containing the last two elements of the sequence $\hist$ if the sequence has at least two elements; the singleton set containing the last element of the sequence if it has exactly one element; and the empty set if $\hist = \emptyset$.
@@
 \begin{definition}[Theory completeness]
-	$\forall \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadsto \phi] \lor [\exists \ar \in \allargs \suchthat \ar \ileadsto ¬\phi]$.
+	$\forall \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] \lor [\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi]$.
 \end{definition}
@@
 \subsection{Definition}
-\commentOC{I leave the definition as is, but for the moment I only consider ${\gleadsto}$, a relation that does not depend on $i$; and I do not use $q(i)$.}
-An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$,
-with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
+An empirical theory for a normative theory is a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$,
+with ${\gleadsto} \subseteq \allargs × \Phi$, 
 ${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
@@
 Given $i \in I, \phi \in \Phi, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \phi$.
+(The striked through $\phi$ in superscript is there to suggest that, intuitively, $\args$ argue against $\phi$, from the point of view of $i$.)
 
@@
 Given $\phi \in \Phi, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \phi)$ or $(\hist, \ar_\delta)$ challenges $(\delta, ¬\phi)$.
-\commentOC{This should be called a $\phi$-or-$¬\phi$-challenge.}
+\commentOC{This should be called a $\phi$/$¬\phi$-challenge.}
 
@@
 	\label{th:nextchal}
-	Given $(\hist, \ar_\gamma)$ challenging $(\gamma, \phi)$, with $\ar_\gamma \in \gargs \cap \dfpclosure$, and $\ar_\delta \in \gargsdelta$: either $(i, \phi, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\phi))$.
+	Given $(\hist, \ar_\gamma)$ challenging $(\gamma, \phi)$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\phi))$, and $\ar_\delta \in \gargsdelta$: either $(i, \phi, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\phi))$.
 \end{lemma}
@@
 \begin{theorem}
-	Given two incompatible empirical theories for a given normative theory, $\alpha = (q, (\gleadsto[q(i)][\alpha])_{q(i) \in q(I)}, \gbeats[\alpha], \alldargs, \dbeats[\alpha], +_\alpha)$ and $\beta = (q', (\gleadsto[q(i)][\beta])_{q(i) \in q(I)}, \gbeats[\beta], \alldargs, \dbeats[\beta], +')$ and given any $i \in I$, there exists a test procedure with $i$ that falsifies one of these theories.
+	Given two incompatible empirical theories for a given normative theory, $\alpha = (\gleadsto[\alpha], \gbeats[\alpha], \alldargs, \dbeats[\alpha], +_\alpha)$ and $\beta = (\gleadsto[\beta], \gbeats[\beta], \alldargs, \dbeats[\beta], +')$ and given any $i \in I$, there exists a test procedure with $i$ that falsifies one of these theories.
 \end{theorem}
@@
 
-	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[][\beta] ¬\phi$.
+	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\beta] ¬\phi$.
 Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](¬\phi))$.
@@
 
-	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[][\alpha] \phi$.
+	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[\alpha] \phi$.
 Observe that $\ar_0 \in \gargsalpha \cap (\dfp[\alpha])^0(\gleadstoinv[\alpha](\phi))$.
@@
 
-Define $\ileadsto$ as follows.
+Define $\ileadstost$ as follows.
 Given $\hist = (…, \ar)$, $\hist \ileadstost \phi$ iff, in a situation of $i$ having been exposed to the prefix …, saying: “Considering the argument $\ar$, would you please indicate your maximum selling price for $P$, and for $D$” leads $i$ to act accordig to $\phi$.
-Note that $\hist \ileadsto \phi$ iff $\hist \nileadsto ¬\phi$.
+Note that $\hist \ileadstost \phi$ iff $\hist \nileadstost ¬\phi$.
 

### 2020-08-02 simple.tex
Impr notation; and started transform definition of defending coalitions (with incorrect proof)

@@
 
-\begin{remark}
-	$\df'(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$. 
-	First, $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{\dbeatsinv \circ \gbeatsinv}$. 
-	Indeed, $\ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$, hence, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\dargs ≠ \emptyset$; and $\ard \in \dargs$ thus $\ard \dbeats \ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$.
-	Second, $\dargs \in \powersetz{\dbeatsinv \circ \gbeatsinv} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
-	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$, $\ar_1 \in \args$, $\ard \in \dbeatsinv(\ar_1)$, thus, $\ard \in \dbeatsinv(\args)$; and considering $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$.
-	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
-\end{remark}
-
 \subsection{Falsifiability}
@@
 
-Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
+Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
+It represents the coalitions of fragments required to defend $\ar$ (when arguing for $\phi$) from the point of view of $i$.
+The following proposition shows that these coalitions can be added to $\ar$, and will be useful for other results.
+\begin{proposition}
+	$\dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
+\end{proposition}
+\begin{proof}
+	Let us prove that $\set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.
+
+	First (from left to right), $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{(\dbeatsinv \circ \gbeatsinv)(\ar)}$. 
+	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, and $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$.
+Also, picking any $\ard \in \dargs$, we see that for some $\ar_1 \in \args$, $\ard \dbeats \ar_1 \gbeats \ar_0$.
+
+	Second (from right to left), $\dargs \in \powersetz{(\dbeatsinv \circ \gbeatsinv)(\ar)} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
+	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$ \commentOC{This is incorrect.}.
+	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
+\end{proof}
+
 Observe that $\di(\ar) \subseteq \df(\ar)$.
@@
 \begin{proof}
-	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$, and normative adequacy brings the conclusion.
+	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$; the conclusion then follows thanks to normative adequacy.
 

### 2020-08-03 simple.tex
Attempts proofs correspondence c and def

@@
 Given $i \in I, \phi \in \Phi, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \phi$.
-(The striked through $\phi$ in superscript is there to suggest that, intuitively, $\args$ argue against $\phi$, from the point of view of $i$.)
+(The notation uses a striked through $\phi$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues against $\phi$, from the point of view of $i$.)
 
@@
 	Let us prove that $\set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.
+Note that by definition of $\df(\ar)$, $\dargs \in \powersetz{\df(\ar)}$ iff $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
 
-	First (from left to right), $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{(\dbeatsinv \circ \gbeatsinv)(\ar)}$. 
-	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, and $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$.
-Also, picking any $\ard \in \dargs$, we see that for some $\ar_1 \in \args$, $\ard \dbeats \ar_1 \gbeats \ar_0$.
+	First (from left to right), given any $\args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0)$, define $\dargs = \dbeatsinv(\args)$, and let us show that $\dargs ≠ \emptyset$ and that $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
+	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, from which follows that $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$.
+Also, because $\args \subseteq \gbeatsinv(\ar)$, $\dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
 
-	Second (from right to left), $\dargs \in \powersetz{(\dbeatsinv \circ \gbeatsinv)(\ar)} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
-	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$ \commentOC{This is incorrect.}.
+	Second (from right to left), $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)) ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
+	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$ \commentOC{This is incomplete, should mention injectivity.}.
 	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
+\end{proof}
+
+\begin{proof}[Alternative proof]
+	Given $\args, \dargs, \ar$ such that $\emptyset ≠ \args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar)$:
+	\begin{equation}
+		\dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
+	\end{equation}
+
+	LHS equiv $\ard \in \dargs ⇔ \exists \ar_1 \in \args \suchthat \ard \dbeats \ar_1$.
+	Using $\args \subseteq \gbeatsinv(\ar)$, it is also equivalent to: $\ard \in \dargs ⇔ \exists \ar_1 \in \args \suchthat \ard \dbeats \ar_1 \gbeats \ar$.
+
+	RHS equiv $\ard \in \dargs ⇒ \exists \ar_1 \in \allargs \suchthat \ard \dbeats \ar_1 \gbeats \ar$.
+
+	LHS implies RHS. Obvious.
+
+	RHS implies LHS.
+First, $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$ (by RHS), and $\ard \in \dbeatsinv(\gbeatsinv(\ar)) ⇔ \exists \ar_1 \in \gbeatsinv(\ar) \cap {\dbeats}(\ard) ⇔ \exists \ar_1 \in \gbeatsinv(\ar) \cap {\dbeats}(\dargs) \suchthat \ard \dbeats \ar_1 ⇔ \ard \in \dbeatsinv(\args)$.
+
+	Second, $\exists \ar_1 \in \args \suchthat \ard \dbeats \ar_1 ⇒ \ard \in \dargs$: it follows from $\args \subseteq \dbeats(\dargs)$ and injectivity: $\ar_1 \in \args$ thus $\ar_1 \in {\dbeats}(\dargs)$ thus $\exists \ar_2 \in \dargs \suchthat \ar_2 \dbeats \ar_1$, and $\ar_2 = \ard$ by injectivity, thus $\ard \in \dargs$.
+
+	Finally, prove that $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)) ⇔ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$.
+	\commentOC{This equivalence is true, but the proof above might be insufficient: it only proves that RHS ⇒ LHS when $\args$ is chosen as defined, but it could be that sometimes $\args$ can be chosen differently, so that $\dbeatsinv(\args) = \dargs$ but $\args ≠ {\dbeats}(\dargs)$.}
+\end{proof}
+
+\begin{proof}[More promising]
+	$\forall \dargs \subseteq \allargs$:
+	\begin{equation}
+		\exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \suchthat \dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
+	\end{equation}
+
+	LHS implies RHS.
+Prove that $\emptyset ≠ \dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
+$\args \subseteq \gbeatsinv(\ar)$, thus, $\dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
+Also, $\args ≠ \emptyset$, thus $\dbeatsinv(\args) ≠ \emptyset$, as mandated by $\dbeats$, by definition of empirical theories.
+
+	RHS implies LHS. Define $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar)$ and prove that $\args ≠ \emptyset$ and $\dbeatsinv(\args) = \dargs$.
+
+	First, $\dargs \subseteq \dbeatsinv(\args)$.
+That is because $\dbeatsinv(\gbeatsinv(\ar)) = \dbeatsinv(\args)$.
+This can be seen by: $\ard \in \dbeatsinv(\gbeatsinv(\ar)) ⇔ \exists \ar_1 \in \gbeatsinv(\ar) \cap {\dbeats}(\ard) ⇔ \exists \ar_1 \in \gbeatsinv(\ar) \cap {\dbeats}(\dargs) \suchthat \ard \dbeats \ar_1 ⇔ \ard \in \dbeatsinv(\args)$.
+
+	Second, $\dbeatsinv(\args) \subseteq \dargs$. That is because $\dbeatsinv(\args) \subseteq \dbeatsinv({\dbeats}(\dargs)) \subseteq \dargs$, by injectivity of $\dbeats$.
+
+	RHS implies LHS (alt).
+RHS implies $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$, which implies that $\dbeatsinv({\dbeats}(\dargs)) = \dargs$, by injectivity of $\dbeats$, and $\dbeatsinv({\dbeats}(\dargs)) = \dbeatsinv({\dbeats}(\dargs) \cap \gbeatsinv(\ar))$.
+	Therefore, $\dargs = \dbeatsinv({\dbeats}(\dargs)) = \dbeatsinv({\dbeats}(\dargs) \cap \gbeatsinv(\ar)) = \dbeatsinv(\args)$.
 \end{proof}

### 2020-08-03 simple.tex
Got rid of spurious proofs (and minor improvements)

--- 2020-08-02 simple.tex
@@
 Given $\ar \in \allargs$, $\df(\ar)$ denotes the \emph{fragments defending $\ar$}. 
-In other words, given $\ard \in \dargs$ and $\ar_0 \in \allargs$, $\ar_2 \in \df(\ar_0)$ iff $\exists \ar_1 \in \allargs \suchthat \ar_2 \dbeats \ar_1 \gbeats \ar_0$.
+In other words, given $\ard \in \dargs$ and $\ar_0 \in \allargs$, $\ard \in \df(\ar_0)$ iff $\exists \ar_1 \in \allargs \suchthat \ard \dbeats \ar_1 \gbeats \ar_0$.
 A \emph{coalition defending $\ar$} is any element of $\powersetz{\df(\ar)}$.
@@
 \begin{proposition}
-	$\dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
+	$\forall i \in I, \phi \in \gPhi, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
 \end{proposition}
 \begin{proof}
-	Let us prove that $\set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.
+	Let us prove that $\forall \ar \in \allargs: \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.
+Note that by definition of $\df(\ar)$, $\dargs \in \powersetz{\df(\ar)}$ iff $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
+	Thus, we have to prove that
+	$\forall \dargs \subseteq \allargs$:
+	\begin{equation}
+		\exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \suchthat \dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
+	\end{equation}
 
-	First (from left to right), $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{(\dbeatsinv \circ \gbeatsinv)(\ar)}$. 
-	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, and $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$.
-Also, picking any $\ard \in \dargs$, we see that for some $\ar_1 \in \args$, $\ard \dbeats \ar_1 \gbeats \ar_0$.
+	First (from left to right), given any $\args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \dargs = \dbeatsinv(\args)$, let us show that $\dargs ≠ \emptyset$ and that $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
+	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, from which follows that $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$.
+Also, because $\args \subseteq \gbeatsinv(\ar)$, $\dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
 
-	Second (from right to left), $\dargs \in \powersetz{(\dbeatsinv \circ \gbeatsinv)(\ar)} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
-	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$ \commentOC{This is incorrect.}.
+	Second (from right to left), let us show that $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)) ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
+	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ar' \in \dbeatsinv(\args)$, $\ar' \dbeats \ar_1$ for some $\ar_1 \in \args$, thus $\ar_1 \gbeats \ar_0$, thus, $\ar_1 \in {\dbeats}(\dargs)$, thus $\ard \dbeats \ar_1$ for some $\ard \in \dargs$, and by injectivity  of $\dargs$, $\ar' = \ard$, whence $\ar' \in \dargs$.
 	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
@@
 
-Observe that $\di(\ar) \subseteq \df(\ar)$.
-Define $\dip \subseteq \allargs × \allargs$ as $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$.
+Given $\ar \in \allargs$, define $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$, representing the subset of defenders of $\ar$ useful for proving $\phi$ from the point of view of $i$.
 Given $i \in I, \phi \in \gPhi$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.
@@
 \begin{definition}[Convincingness]
-	$\forall i \in I, \phi \in \gPhi, \ar \in \gargs: \ar$ $i$-defends $\phi$.
+	An empirical theory is \emph{convincing} iff $\forall i \in I, \phi \in \gPhi, \ar \in \gargs: \ar$ $i$-defends $\phi$.
 \end{definition}

### 2020-08-03 simple.tex
Slight rework proof with factorisation of a lemma

@@
 \begin{proposition}
+	\label{th:indf}
 	$\forall i \in I, \phi \in \gPhi, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
@@
 
+\begin{lemma}
+	\label{th:produce}
+	Given $\phi \in \gPhi$, $\ar_0 \in \gargs$ that $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$.
+Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
+\end{lemma}
+\begin{proof}
+	By definition of $\ibeats$, $\args \ibeats \ar_0$.
+	Also, because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
+	Therefore, $\dargs \in \di(\ar_0)$.
+	It follows that $\dargs \in \df(\ar_0)$, by \cref{th:indf}, and that $\ar_2 \in \dfp(\ar_0)$, by definition of $\dfp$. It also follows that $\ar_2 \in \dip(\ar_0)$, hence, that $\ar_2 \in \gargs$.
+\end{proof}
+
 \begin{theorem}
@@
 \begin{proof}
-	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$; the conclusion then follows thanks to normative adequacy.
+	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$; the conclusion then follows thanks to simple normative adequacy (equivalent to normative adequacy thanks to \cref{th:normeqsnorm}).
 
-	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \dargs \in \di(\ar_0)$.
-	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
-	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$.
-	Define $\args = \gbeatsinv(\ar_0) \cap \hist$. Thus, $\args \ibeats \ar_0$.
-	Also, because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
-	Therefore, $\dbeatsinv(\args) \in \di(\ar_0)$.
-
-	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$.
-That is because $\ar_0 \in \gargs ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering any $\dargs \in \di(\ar_0)$ and $\ar_2 = \ar_0 + \dargs$, $\ar_2 \in \gargs$ by definition of $\gargs$ and $\ar_2 \in \dfp(\ar_0)$ because $\dargs \in \di(\ar_0) ⇒ \dargs \in \df(\ar_0)$.
+	Lemma: $[\ar_0 \in \gargs \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$. That is because $\ar_0 \in \gargs ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and,
+	by definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$; \cref{th:produce} thus applies.
 
@@
 Observe that $\ar_0 \in \gargs$.
-Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$.
+Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the above lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$.
+Continue applying the lemma and producing further arguments as long as $\ar_k \nileadstost \phi$.
 	By definition of an empirical theory, $\exists k \in \N \suchthat (\dfp)^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
@@
 \subsection{Effectively comparing models}
-\begin{lemma}
-	\label{th:produce}
-	Given $\phi \in \Phi$, $\ar_0 \in \allargs$ that $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$.
-Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
-\end{lemma}
-\begin{proof}
-	Because $\dargs \in \di(\ar_0)$.
-\end{proof}
-
 Given $\phi \in \Phi$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\phi$ iff $\phi \in \gPhi[\gamma] \land ¬\phi \in \gPhi[\delta]$.

### 2020-08-03 simple.tex
Small presentation improvements

@@
 
-Given $\phi \in \Phi$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $(\gamma, \phi)$ iff $\hist \nileadstost \phi$ and $\ar_\gamma \in \histend$.
-Given $\phi \in \Phi, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \phi)$ or $(\hist, \ar_\delta)$ challenges $(\delta, ¬\phi)$.
-\commentOC{This should be called a $\phi$/$¬\phi$-challenge.}
+Given $\phi \in \Phi$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $\phi$ iff $\hist \nileadstost \phi$ and $\ar_\gamma \in \histend$.
+Given $\phi \in \Phi, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\phi/¬\phi$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \phi)$ or $(\hist, \ar_\delta)$ challenges $(\delta, ¬\phi)$.
 
@@
 	\label{th:endchal}
-	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$: $(\hist, \ar_\gamma, \ar_\delta)$ is a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge.
+	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$: $(\hist, \ar_\gamma, \ar_\delta)$ is a $\phi/¬\phi$-challenge.
 \end{lemma}
 \begin{proof}
-	Either $\hist \nileadstost \phi$, and $(\hist, \ar_\gamma, \ar_\delta)$ challenges $(\gamma, \phi)$, or $\hist \ileadstost \phi$, hence, by \cref{th:protcoh}, $\hist \nileadstost ¬\phi$, and $(\hist, \ar_\gamma, \ar_\delta)$ challenges $(\delta, ¬\phi)$.
+	Either $\hist \nileadstost \phi$, and $(\hist, \ar_\gamma)$ challenges $\phi$, or $\hist \ileadstost \phi$, hence, by \cref{th:protcoh}, $\hist \nileadstost ¬\phi$, and $(\hist, \ar_\delta)$ challenges $¬\phi$.
 \end{proof}
@@
 	\label{th:nextchal}
-	Given $(\hist, \ar_\gamma)$ challenging $(\gamma, \phi)$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\phi))$, and $\ar_\delta \in \gargsdelta$: either $(i, \phi, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\phi))$.
+	Given $(\hist, \ar_\gamma)$ challenging $\phi$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\phi))$, and $\ar_\delta \in \gargsdelta$: either $(i, \phi, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $\phi/¬\phi$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\phi))$.
 \end{lemma}
@@
 
-	If $\histpp \nileadstost \phi$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\gamma, \ar_\delta)$ challenges $(\gamma, \phi)$, which concludes the proof. 
+	If $\histpp \nileadstost \phi$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\gamma, \ar_\delta)$ challenges $\phi$, which concludes the proof. 
 	Thus, assume that $\histpp \ileadstost \phi$.
@@
 	$(\hist, \ar_\alpha, \ar_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta)$ iff 
-	$(\hist, \ar_\alpha, \ar_\beta)$ is a $(\alpha, \phi$ or $\beta, ¬\phi)$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\phi))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](¬\phi))$.
+	$(\hist, \ar_\alpha, \ar_\beta)$ is a $\phi/¬\phi$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\phi))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](¬\phi))$.
 
@@
 Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \phi$.
-By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $(\alpha, \phi$ or $\beta, ¬\phi)$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
+By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\phi/¬\phi$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
 
@@
 This is because, given a challenge $(\hist, \ar_\alpha, \ar_\beta)$ of complexity $(k_\alpha, k_\beta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity.
-Indeed, if $(\hist, \ar_\alpha)$ challenges $(\alpha, \phi)$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
-And if $(\hist, \ar_\beta)$ challenges $(\beta, ¬\phi)$, apply \cref{th:nextchal} with $¬\phi$ for $\phi$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.
+Indeed, if $(\hist, \ar_\alpha)$ challenges $\phi$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
+And if $(\hist, \ar_\beta)$ challenges $¬\phi$, apply \cref{th:nextchal} with $¬\phi$ for $\phi$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.
 

### 2020-08-03 simple.tex
Rm remark about using zero argument for better comparison

@@
 \end{proof}
-
-\begin{remark}
-	Make $\gamma$ able to answer directly $\ar_1$ when $\delta$ starts the protocol.
-
-	Using $\zar$, this can be done as follows.
-Assume $\zar \notin \allargs$.
-Define $\ar_1 \gbeats \zar$ iff $\ar_1 \in \allargs \setminus \gleadstoinv(\phi)$ (the non-initial arguments).
-Demand that $\dbeats$ cover all non-initial arguments.
-(Note that $\ar'_0 \gbeats \ar_0$ seems possible (thus, an attacker not in $\allargs \setminus \gleadstoinv(\phi)$), and $\zar$ not attacking anything but in $\allargs \setminus \gleadstoinv(\phi)$ is possible, where $\zar$ designates an argument that says nothing.) Remove the $\alldargs$ concept, so as to be able to use directly the defensors against the non-initial arguments (alternative: extend $+$ to allow $\zar + \ard$).
-Extend $\histend$ with $\zar$ to have $\zar \in \histend$.
-Define $\gargs = (\dip)^k(\gleadstoinv(\Phi) \cup \di(\zar))$.
-
-	It can also be done without using $\zar$, as follows.
-Demand that $\dbeats$ cover all non-initial arguments.
-Define $\di(\zar) = \set{\dbeatsinv(\args) \suchthat \exists \hist \in \allhist \suchthat \emptyset ≠ \args = \allargs \setminus \gbeatsinv(\Phi) \cap \hist \land \hist \nileadstost \phi}$.
-Define $\gargs = (\dip)^k(\gleadstoinv(\Phi) \cup \di(\zar))$.
-\end{remark}
 

### 2020-08-04 simple.tex
Somewhat simpler procedure presentation

@@
 
-Second, the concept of nudge \citep{thaler_nudge:_2009} has been tremendously popular in the recent past, but has also been vastly criticized: the risk of manipulation is particularly high whenever it is unsure that the individual would indeed have adopted the decision that the nudge suggests after careful thinking.
+Second, the concept of nudge \citep{thaler_nudge:_2009} has been tremendously popular in the recent past, but has also been vastly criticized: the risk of manipulation is particularly high whenever it is unsure that the individual would indeed, after careful thinking, have adopted the decision that the nudge promotes.
 
@@
 
-Given a normative theory and two empirical theories for that normative theory and $i \in I$, 
-a \emph{test procedure with $i$} is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N^*$, of sequences of arguments, 
-such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$, and 
-such that $(i, \phi, {\hist}^N)$ falsifies one of the empirical theories for some $\phi \in \Phi$. 
-A sequence of arguments $\histp$ starts with a sequence of arguments $\hist$ of length $l$ iff $\histp$ has length at least $l$ and $\forall k \in \intvl{1, l}: \histp_k = \hist_k$.
+%Given a normative theory and two empirical theories for that normative theory and $i \in I$, 
+%a \emph{test procedure with $i$} is a finite sequence 
 \commentOC{Need the test procedure to be a tree.
@@
 
-\begin{theorem}
-	Given two incompatible empirical theories for a given normative theory, $\alpha = (\gleadsto[\alpha], \gbeats[\alpha], \alldargs, \dbeats[\alpha], +_\alpha)$ and $\beta = (\gleadsto[\beta], \gbeats[\beta], \alldargs, \dbeats[\beta], +')$ and given any $i \in I$, there exists a test procedure with $i$ that falsifies one of these theories.
-\end{theorem}
-\begin{proof}
+An increasing sequence of arguments is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N^*$, of sequences of arguments, 
+such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$, and 
+such that $(i, \phi, {\hist}^N)$ falsifies one of the empirical theories for some $\phi \in \Phi$. 
+A sequence of arguments $\histp$ starts with a sequence of arguments $\hist$ of length $l$ iff $\histp$ has length at least $l$ and $\forall k \in \intvl{1, l}: \histp_k = \hist_k$.
+
+Given two incompatible empirical theories for a given normative theory, $\alpha = (\gleadsto[\alpha], \gbeats[\alpha], \alldargs_\alpha, \dbeats[\alpha], +_\alpha)$ and $\beta = (\gleadsto[\beta], \gbeats[\beta], \alldargs_\beta, \dbeats[\beta], +_\beta)$ and given any $i \in I$, the following procedure falsifies one of these theories, involve only $i$, and uses queries only about increasing sequences of arguments.
+\begin{procedure}
 	Pick any $\phi \in \Phi$ about which $\alpha$ and $\beta$ disagree.
@@
 	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\phi)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](¬\phi)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
-\end{proof}
+\end{procedure}
 

### 2020-08-04 simple.tex
Rm old abstract and intro

@@
 \begin{abstract}
-	In decision theory and economy in general, preferences are generally considered as “intuitive”, as originating from an “immediate sensation”, as famously written by \citeauthor{von_neumann_theory_2004}.
-This conception is insufficient to study the positions that individuals adopt towards difficult decision problems after careful thinking.
-This article introduces, and defines formally, the concept of deliberated preferences to fill this gap: the deliberated preferences of an individual about a given decision problem represent the position of that individual towards that problem that is stable facing counter-arguments.
-As defined, deliberated preferences are only indirectly observable.
-To make it possible to model deliberated preferences, the article also defines formally the notion of a theory of deliberated preferences, together with a protocol of falsification of such a theory.
-The proposed falsification protocol involves only observations similar to those used in classical theories of revealed preferences.
-It is shown that a theory of deliberated preference captures effectively a known subset of the deliberated preferences if and only if it is not falsifiable.
+	TODO
 \end{abstract}
@@
 \section{Motivation}
-In decision theory and economy in general, preferences are generally considered as “intuitive”, as originating from an “immediate sensation”, following the terms used by \citet{von_neumann_theory_2004} (vNM) \citep{fishburn_retrospective_1989, cailloux_reasons_2017}.
-Though appropriate when studying the everyday behavior of individuals, this conception is insufficient to study the positions that individuals adopt towards difficult decision problems after careful thinking.
-In this article I define the concept of deliberated preferences to fill this gap: the deliberated preferences of an individual about a given decision problem represent the position of that individual towards that problem that is stable facing counter-arguments.
-
-After having defined this concept formally, I define the notion of a theory pretending to capture the deliberated preferences of a set of individuals about some topic, I propose an empirical procedure to attempt to falsify such a theory, and I show that such a theory tells the truth whenever it is not falsifiable by that procedure.
-
-This article does not attempt to propose a concrete theory of deliberated preferences.
-It is more preliminarly.
-It proposes formal definitions for 1) the kind of object that are to be studied for capturing “more reflexive” preferences than considered usually, 2) what theories of such preferences should look like, 3) how to falsify such theories and using which information.
-Therefore, it proposes a research program rather than a direct solution to the problem of capturing reflexive preferences.
-
-Before delving into the formalism, let me present a bit of motivation for considering deliberated preferences as an interesting object to study.
-Being able to capture deliberated preferences can help provide a better understanding of human preferences in the large sense and may improve policy making (though this article does not explore issues of group decision).
-Besides this very broad goal, here are three example of contexts in which this notion is useful, which may give it a more concrete interest and serve to introduce this concept informally by indicating the kinds of things that it should be able to help understand.
-
-First, decision theory has produced several models of how an individual ought to decide, such as the seminal one of vNM.
-(The following remarks apply equally well to other normative models such as the one of \citet{savage_foundations_1972}, \citet{keeney_decisions_1993} or more recent ones.) Those models can be used to help individuals take “good” decisions, as opposed to predict their behavior (for which other models, taking into account cognitive limitations, are more appropriate \citep{wakker_prospect_2010}).
-But it is unclear how to validate recommendations obtained on the basis of such models.
-Some researchers have opposed the norms on which some of those models are based \citep{ellsberg_risk_1961, allais_so-called_1979}.
-As \citet{raiffa_back_1985} points out, while it is the case that some sophisticated decision makers may consciously refuse to abide by the vNM axioms (or others), it is also true that some decision makers simply fail to comply with them because of insufficient reflexion.
-However, no general proposal, as far as I know, has been described yet to test whether, for a given individual and context, those axioms would, after careful thinking, reveal acceptable.
-Psychologists have tried to test the convincing power of those axioms \citep{slovic_who_1974, maccrimmon_utility_1979}.
-Their conclusions inevitably depend on how axioms have been presented to the individuals and on whether counter-arguments have been presented, as \citet{slovic_who_1974} themselves point out.
-But lacking a systematic approach to determine stability facing counter-arguments, those conclusions only shed very partial light on the question of acceptance of specific norms by the general public.
-The notion of deliberated preferences can help confront different possible norms for normative decision theory by seeing them as constituents of theories of deliberated preferences and using the procedure described in this article to confront theories.
-
-Second, the concept of nudge \citep{thaler_nudge:_2009} has been tremendously popular in the recent past, but has also been vastly criticized: the risk of manipulation is particularly high whenever it is unsure that the individual would indeed, after careful thinking, have adopted the decision that the nudge promotes.
-
-Third, analytical philosophy has presented very elaborated and diverging views about the concept of justice.
-\citet{rawls_theory_1999}, in particular, suggests that the appropriate conception of justice is one that individuals would arrive at in a state of reflexive equilibrium (a concept borrowed from \citet{goodman_fact_1983}).
-\citeauthor{rawls_theory_1999} and \citeauthor{goodman_fact_1983} insist that individuals must not only accept principles, when thinking about difficult notions such as justice, but also think about consequences of those principles: sometimes, principles that appear intuitively acceptable yield consequences that do not appear intuitively acceptable, in which case something must give.
-The state of reflexive equilibrium is a state where accepted principles yield acceptable consequences only.
-The concept of deliberated preferences may be considered as defining that state of reflexive equilibrium, or to be a path towards such a goal (an important difference is that it does not explicitly model the difference between principles and consequences).
-One way to go beyond philosophers disagreement about the right conception of justice, then, is to ask non-philosophers about what they think is right and so use these laymen as arbiters of the competition between views of justice.
-Similar empirical studies have started to be conducted recently \citep{gaertner_empirical_2012}.
-But those studies are conducted by asking individuals only which distribution of goods they consider intuitively right in various circumstances.
-Thus, they do not try to capture their well-considered judgments for justice, where different reasonings in favor of different conceptions of justice would be presented to the individuals together with the distributions.
-Hence, this does not test appropriately whether laymen would accept, after thinking carefully, the sophisticated conceptions of justice presented by a given philosopher or economist.
-A more appropriate way of testing the convincing power of elaborated claims about justice may be considered to require, here again, to present his conception of justice to the individual and submit it to counter-arguments (possibly coming from other sophisticated thinkers).
-
-The first and third contexts of usage come together when it is desired to test whether an individual accepts some axiom as representing an acceptable way of reasoning for him.
-One simple way is to explain axioms individually and ask the individual whether they appear acceptable.
-But this fails to make sure the individual understands and accepts the consequences of the union of the axioms accepted by such a procedure \citep{meinard_justification_2018}.
-(Note that probably nobody is able to mentally deduce all consequences of a union of non trivial axioms.) As an example, in a context of trying to determine the voting rule that best represents someone’s notion of justice, the tested individual could accept the axioms of universal domain, independence of irrelevant alternatives, and pareto dominance, without realizing that he has just accepted dictatorship \citep{arrow_social_1963}.
 

### 2020-08-05 simple.tex
One more example of a theory: satisfying

@@
 \begin{abstract}
-	TODO
+	TODO: abstract
 \end{abstract}
@@
 \section{Motivation}
+Talk about \citet{von_neumann_theory_2004}.
 
@@
 
-\section{LS}
+\section{Preferences}
+\subsection{Preferences}
+Let $\allalts$ be a set of alternatives.
+Define $\Phi_\allalts$ as follows.
+Let $\phi_{a > b} \in \iPhi$ represent $i$ deliberately preferring strictly $a$ to $b$.
+Let $\phi_{a ≥ b} \in \iPhi$ represent $i$ deliberately preferring weakly $a$ to $b$.
+Define $¬\phi_{a > b} = \phi_{b ≥ a}$.
+
+A normative theory of preferences about $\allalts$ is a theory about $\Phi_\allalts$: a tuple $(\allprops, ¬, \allargs, I, (\ileadsto)_{i \in I})$, with $\allprops$ defined as $\allprops_\allalts$, $¬$ defined as above.
+
+Define $≥_i$, the deliberated preference of $i$, as $a ≥_i b$ iff $\phi_{a ≥ b} \in \iPhi$.
+
+Given an empirical theory for a normative theory of preferences, say that it claims a complete preference iff $\forall a, b \in \allalts: \phi_{a ≥ b} \in \gPhi \lor \phi_{b ≥ a} \in \gPhi$.
+Similarly, it claims a transitive preference iff $\forall a, b, c \in \allalts: \phi_{a ≥ b} \in \gPhi \land \phi_{b ≥ c} \in \gPhi ⇒ \phi_{a ≥ c} \in \gPhi$.
+Observe that establishing whether an empirical theory claims a complete or transitive preference can be determined a priori (without empirical observations).
+
+Given a bundle $B \subseteq \allalts$ and $i \in I$, $b \in B$ is a deliberated preferred choice for $i$ among $B$ iff $\forall b' \in B: b ≥_i b'$.
+
+The next result follows from these definitions and from classical results about choice functions and complete, transitive preferences. \TODO{Be more precise.}
+ \begin{theorem}
+ 	If an empirical theory for a normatively adequate normative theory of preference claims a complete and transitive preference and is valid, then, given any bundle $\emptyset ≠ B \subseteq \allalts$, some $b \in B$ is a deliberated preferred choice for $i$ among $B$.
+ \end{theorem}
+
+Given $i$ and $\phi_{a > b}$, $\hist \ileadsto \phi$ iff $i$, after having been presented $\ar$, is asked to choose among $a$, $b$, or declare she is indifferent if permitted; and $i$ chooses $a$.
+And $\hist \ileadsto \phi_{a ≥ b}$ iff $i$ does not choose $b$ (thus chooses $a$ or declare she is indifferent if permitted).
+Note that $\hist \ileadsto \phi ⇔ \hist \nileadsto ¬\phi$.
+
+\subsection{Satisfaction}
+Consider a normative theory of preferences about a given set of alternatives $\allalts$. Let $\gamma$ be the following empirical theory for that normative theory.
+
+Define $C$ a set of criteria, functions $c: \allalts → \R$ measuring the performances of the alternatives according to some point of view.
+Let $t: \R^C$ be a set of thresholds, thus, consisting of one real threshold $t_c \in \R$ per criterion.
+Say that $a \in \allalts$ is satisficing iff $\forall c \in C: c(a) ≥ t_c$.
+
+The theory $\gamma$ says that $i$ is a satisficer using some defined criteria $C$ and thresholds $t = (t_c)_{c \in C}$.
+The set $\gPhi$ is defined as $\set{\phi_{a > b} \suchthat a \text{ is satisficing and $b$ is not}}$.
+Given $a, b \in \allalts$, with $a$ satisficing and $b$ not, define $\ar_{a > b}$ as the text: “$a$ has performance $c_1(a)$ on criterion $c_1$, and it is reasonable to consider that having at least $t_{c_1}$ is satisfying enough from the point of view captured by $c_1$, (… same phrase for the other criteria…), therefore, it is a fully satisfactory alternative; whereas $b$ is not satisfactory on criteria (… enumeration of the criteria such that $c(b) < t_{c}$).”
+Define ${\gleadsto} = \set{\ar_{a > b}, \phi_{a > b}) \suchthat a \text{ is satisficing and $b$ is not}}$.
+Define $\alldargs = \gbeats = \dbeats = {+} = \emptyset$: the theory does not consider any counter-argument as potentially damaging. 
+This defines the theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$.
+
+Observe that $\gamma$ does not claim a complete preference, but, whenever there is exactly one satisficing alternative in $\allalts$, it still determines a deliberated preferred choice for $i$ among $\allalts$.
+
+\subsection{LS}
 %Idea: argue for P > $.
@@
 
-TODO consider using only $\phi$ being sure, and dropping everything related to possibility.
+\TODO{Consider using only $\phi$ being sure, and dropping everything related to possibility.}
 

### 2020-08-14 preamble/acronyms.tex
Much new stuff about presentation mainly

\DeclareAcronym{AMCD}{short=amcd, long={Aide Multicritère à la Décision}}
\DeclareAcronym{AHP}{short=AHP, long={Analytic Hierarchy Process}}
\DeclareAcronym{AR}{short=ar, long={Argumentative Recommender}}
\DeclareAcronym{DA}{short=da, long={Decision Analysis}}
\DeclareAcronym{DJ}{short=DJ, long={Deliberated Judgment}}
\DeclareAcronym{DM}{short=dm, long={Decision Maker}}
\DeclareAcronym{DP}{short=dp, long={Deliberated Preference}}
\DeclareAcronym{MAVT}{short=mavt, long={Multiple Attribute Value Theory}}
\DeclareAcronym{MCDA}{short=mcda, long={Multicriteria Decision Aid}}
\DeclareAcronym{MIP}{short=mip, long={Mixed Integer Program}}
\DeclareAcronym{SEU}{short=SEU, long={Subjective Expected Utility}}

### 2020-08-14 simple.tex
Much new stuff about presentation mainly

@@
 \begin{document}
-\title{Empirical normative theories}
+\title{Toward theories of deliberated preferences}
 \author{Olivier Cailloux}
@@
 \section{Motivation} 
-Talk about \citet{von_neumann_theory_2004}.
+\TODO{“Before asking whether agents want to revise their choices or not, both rival theories should be proposed.” Guala 2000.
+My approach can be qualified as a debiasing technique (Mitchell, Libertarian paternalism is an oxymoron.
+Nw UL Rev 99:1245–1817, 2005).
+Mitchell observes that “in many of those surveys that governments use in order to inform social policy there are not enough resources (time and money) in order to reach the stage where preferences are not labile” (exact quote?).}
+
+It has escaped nobody’s attention that 
+studying reflective preferences, in supplement to shallow preferences, is an important endeavor for economics: we want to recommend to individual decision makers; we want to adopt optimization criteria for society, and this ought not to merely faithfully reproduce unreflectful behavior.
+This is one important difference between the normative and the (inappropriately called, as will be seen) “descriptive” approach in economics.
+As \citet{hausman_preference_1994} illustrate with an example of a person drinking a fatal poison while erroneously thinking that it is water, shallow preferences are not sufficient to inform normative economics.
+Yet, classical methods to obtain preference models in economics are either formally defined on the basis of observable data that do not describe reflective preferences, or are obtained by other means than observable preferential data and systematic reproducible formal procedures.
+
+This article is interested in defining theories of decision making based on another kind of observable data, namely, the reactions of decision makers to arguments.
+This permits to overcome a current important limitation of normative approaches, that of being not empirical (in a sense that will be developed below).
+
+By reflective preferences (of an individual), I mean here preferences that represent informed, pondered decisions, that would be taken after due consideration by the individual.
+Reflective preferences can be contrasted to shallow preferences, those that \citet[p.\ 16]{von_neumann_theory_2004} describe as “intuitive”, as originating from an “immediate sensation” (cited in \citet{fishburn_retrospective_1989}).
+This distinction draws on our capacity, as human beings, to think about our shallow preferences and consider some of them as mistaken \citep{frankfurt_freedom_1971}.
+A famous example of such a situation is the one of \citet[pp.\ 101--103]{savage_foundations_1972} having realized, after due consideration, that his initial declared preference in a decision problem presented by \citet{allais_so-called_1979} was mistaken.
+
+It is well known that shallow preferences do not always match reflective ones.
+Indeed, forming reflective preferences is recognised as a difficult problem in many decision problems, contrary, by definition, to shallow preferences.
+For example, \citet[p.\ 6]{colell_microeconomic_1995} write, when presenting the preference relation that is the basis for most of their famous book about Microeconomic theory: “Introspection quickly reveals how hard it is to evaluate alternatives that are far from the realm of common experience.
+It takes work and serious reflection to find out one’s own preferences.”
+It can be expected that some behavior highlighted by psychologists \citet{lichtenstein_construction_2006}, such as framing effects, would be rejected by the individuals themselves when pondering their decisions.
+
+That reflective preferences are relevant to economic theory, in supplement to shallow preferences, is also illustrated by the general requirement of transitivity of preferences for economic theory, which is reasonably expected from reflective rather than from shallow preferences.
+As an illustration, \citet[p.\ 7]{colell_microeconomic_1995} go on writing: “the transitivity assumption can be hard to satisfy when evaluating alternatives far from common experience.
+As compared to the completeness property, however, it is also more fundamental in the sense that substantial portions of economic theory would not survive if economic agents could not be assumed to have transitive preferences.”
+
+Let me state how the approach proposed here differs from those proposed in the literature, and what problems it aims at solving.
+
+\subsection{Existing approaches for capturing reflective preferences}
+\subsubsection{Laundering preferences}
+An approach much discussed recently is the one of laundering preferences, also called preference purification \citep{bernheim_beyond_2009, rubinstein_eliciting_2011, infante_preference_2016}: having collected shallow preference data (from the field or from interviews), laundering preferences consists in transforming them, using a formal process, in such a way that they satisfy axioms generally considered as required by rationality, or keeping only preference data collected in some situations considered appropriate to determine welfare-relevant preferences.
+For example, \citet{bleichrodt_making_2001} transform observed preferences in order to obtain a classical Expected Utility model; \citet{bernheim_beyond_2009} propose to exclude situations where the individual seems (by objective criteria) unable to process information considered relevant.
+
+This creates a risk of mis-representing the reflective preferences of the individual: not only is it not known whether the individual would reflectively want to adhere to these axioms and, if so, how she would reflectively adapt her preferences when her shallow preferences exhibit related inconsistencies; but it is not even discussed how in principle this could be known.
+As a result, a theory postulating constraints on individual’s behavior on the basis of rational requirements is subject to the criticism addressed by \citet[p.\ 228]{dold_toward_2018} to libertarian paternalism, in that it “effectively denies the possibility that deviations from rational choice might be something to be acknowledged as reasonable”.
+That this is an important methodological problem is sometimes recognized by authors adopting this approach.
+\Citet{bleichrodt_making_2001}, for example, state that laundering require controversial assumptions (p.
+1500), and recommend it only as a last resort, recommending discussing with the decision-maker whenever possible to elicit her reflective preferences (p.
+1499).
+Note that nudging \citep{thaler_nudge_2009} creates a similar problem: we have to guess what the individual would like if he thought hard about the decision problem, was well-informed, and actively worked against the psychological features he himself does not consider adequate for good decision making.
+\TODO{Comment about akrasia: we may want to correct for features that the individual herself can’t correct.}
+
+Some axioms arguably seem innocuous.
+For example, Pareto-dominance requires that $a$ be weakly preferred to $b$ if $a$ is at least as good as $b$ on every point of view that matter.
+However, as has been amply remarked, what is required is not merely the correctness of the axiom in the abstract, but its correct application to the decision situation.
+Has a point of view that the decision maker considers relevant been forgotten, leading the analyst to mistakenly think that $a$ Pareto-dominates $b$, and the seemingly impeccable conclusion that $a$ ought to be preferred to $b$ turns incorrect.
+\citet{sen_maximisation_1997} illustrated this reasoning (with another axiom) with his well-known example of a person picking her second most-preferred fruit from a basket out of politeness reasons, which could be considered irrational by an analyst blindly applying WARP.
+As \citet[p.\ 40]{lecouteux_reconciling_2015} puts it (citing \citet[p.\ 13]{bacharach_beyond_2006} for the part in italics), and as analyzed by \citet{sen_information_1986, sen_internal_1993}, “whether a decision-theoretic principle of rationality has been violated \emph{depends on how we, the theorists, ‘cut up the world’}” \TODO{Find that book}.
+
+\subsubsection{Informal deliberation}
+Another path to obtain reflectful preferences has been followed: the one of deliberation, an umbrella term by which I designate processes, either, involving discussions between an analyst and a decision-maker while querying her preferences in view of building a formal model of it \citep{raiffa_back_1985, keeney_decisions_1993, roy_multicriteria_1996, belton_multiple_2002}, or involving group discussions, with presentations from experts to an audience and internal deliberation phases \citep{fishkin_when_2011}, aiming to obtain well-informed preferences.
+
+A major problem of these techniques is that they are not easily reproducible, and that the resulting preferences elicited from the subjects might reflect properties of the personalities of the intervening experts or group-dynamic effects rather than true reflective preferences of the individuals \commentOCf{Yves, as-tu une référence pour moi ?}.
+This problem is exacerbated by the fact that psychologists have shown that apparent coherence can appear, that is, preferences that do not violate axioms usually considered as representing rationality, although some framing effect may be at play that result in the apparently coherent preferences to arguably not represent reflective preferences \citep{ariely_predictably_2010}.
+It also remains to be clarified how to check on a principled, systematic basis, whether all relevant arguments have been presented faithfully.
+Comfronted with (possibly self-designated) experts with enough assertiveness, a decision-maker can be convinced to follow principles of decision-making that several experts in the field of decision-theory consider incorrect.
+As an illustration, after discussing the weaknesses of the \ac{AHP}, \citet[p.\ 53]{howard_foundations_2007} write: “Why, then, do inferior processes find favor with decision makers?
+The answer is that they do not force you to think very hard or to think in new ways.”
+Beyond the controversial \ac{AHP}, famous decision analysts have voiced disagreements with normative theories of decision making \citep{ellsberg_risk_1961, allais_so-called_1979} that are however generally applied in the field.
+\Citet[p.\ 669]{ellsberg_risk_1961} concluded his influential article as follows: “[In some situations, for some people,] the Bayesian or Savage approach gives [...] bad advice.
+[Some people] act in conflict with the axioms deliberately, without apology, because it seems to them the sensible way to behave.
+Are they clearly mistaken?”
+This rethorical question illustrates the need of systematic procedures able to determine whether decision-makers, when confronted with the relevant arguments, accept the soundness of the principles on whose basis the recommendation rests (this has been somewhat explored, but not systematically, for current lack of a systematic way of confronting decision makers to arguments \citep{slovic_who_1974, stanovich_discrepancies_1999}).
+
+Different analysts, using different methods and different axioms as their favorite conception of rational decision-making, will obtain possibly contradictory conclusions, “elicited” from the decision-makers who hire them.
+Some analysts admit this possibility and do not consider it to be a problem.
+For example, \citet[p.\ 214]{roy_comparison_1995} write: “In our view, these inevitable disagreements do not imply that decision-aid is useless but simply that a single problem may have several valid responses.
+Given that two different decision-aid models cannot be implemented in the same decision process, the decision-maker must be conscious of the qualitative choices implied by the different models – often conveying the analysts’ own ethical choices – before coming to personal conclusions on the choice to be made.
+In this domain, the many different approaches reflect in our view the complexity of the researcher's task much more than a scientific weakness.”
+%Some analysts claim that the value of such interactions between decision-makers and analysts is the fact that it made decision-makers think hard about the problem, and not the resulting preference model.
+Although being an important insight about the (likely vain) hope of determining a single correct recommendation in many complex decision situations (about which more below), this answer does not address the problem that some principles of decision making may be wrong guides in some situations, possibly including some principles that are commonly applied in the field, hence the need of principled ways of discriminating them.
+
+The prescriptive approach to decision making \citep{bell_decision_1988} has been proposed (in supplement to the normative one and the descriptive one), which insists on incorporating the findings of psychologists about decision maker’s weaknesses of reasoning in the procedures leading to recommendations.
+I do not discuss this approach specifically here, because its methods can be considered to fall into the two categories I have described here above when it aims at obtaining reflective preference models.
+When considering normative economics broadly, as I do here, as the methods aiming for valid prescription for an individual or a group, prescriptive approaches are a part of normative economics.
+
+\TODO{Argumentation theory inspired; but they consider arguments are given. Pursues another article of mine.}
+
+\subsection{This approach}
+The proposal of this article to capture reflective preferences while avoiding the just described problems is to define normative theories on the basis of a low demanding axiom complemented with principles of reasonings; that allow decision makers to “reconstruct” the reasoning proposed by the principles so as to be able to check that they apply to their situation; therefore permitting to falsify the theories using observable data representing the rejection by the decision makers of these principles.
+Such theories are therefore both normative and empirical: normative, in the sense of claiming to capture reflective preferences, which provide a better basis for recommendations or policy making than shallow preferences; and empirical, in the sense of the principles of reasoning being exposed to empirical falsification.
+
+The proposed approach is based on a concept of preference that I call deliberated preference, a formal refinement of the vague notion of reflective preferences.
+Those are the preferences of an individual that are stable facing counter-arguments.
+The arguments are presented to the decision maker, and her reaction is observed, for example, in the form of a choice between some alternatives.
+This is the basic observable of interest to the theories here defined.
+
+It is not an ambition of this article to actually propose concrete theories of deliberated preferences, for this is not achievable in a single article; and the theories as defined here admittedly still suffer important weaknesses.
+The ambition of this article is accordingly limited to present a novel approach of capturing reflective preferences in simple enough settings.
+%This requires to define precisely what such theories should aim to capture; and how they should be compared, which is the sole ambition of this article. 
+Some challenges that must be overcomed in order to build concrete theories applicable in realistic settings will be discussed in conclusion.
+
+One long-term goal of this research program is to give individuals the means to reject theories that they find unconvincing after due consideration of all arguments; and accordingly, give incentives to decision theorists to build defenses of these theories able to convince individuals whose preferences are modeled of the soundness of these theories.
+This might match \possessivecite{hausman_debate_2010} suggestion that we should use rational persuasion rather than nudge individuals, arguing that it would promote autonomy.
+
+\section{Informal presentation}
+Although the final aim is about the concept of deliberated preference, which permits to compare alternatives (options in a decision problem), this article will mostly discuss \acp{DJ}.
+That is because, once the concept of \ac{DJ} is clearly established, it is a simple matter to define deliberated preferences, and will be done in a later section, by viewing a preference instance as a judgment about a pair of alternatives.
+
+For a clear separation of concern, this article defines first normative theories, then empirical theories for these normative theories.
+A normative theory makes normative claims only, which have to be accepted or rejected on the basis of the apparent soundness of the axiom on which it rests.
+An empirical theory for a given normative theory, by contrast, makes empirical claims, hence, can be falsified by data.
+What I call here an empirical theory, for simplicity, is not however purely empirical, but can also be considered normative, for two reasons.
+First, its conclusions inevitably rest on the normative validity of the normative theory for which it is built.
+Second, it claims to capture preferences that provide an appropriate basis for recommendation.
+Empirical theories of \ac{DJ} could thus be called empirical normative theories of \ac{DJ}.
+
+\subsection{Normative theories}
+As \citet[p.\ 16]{von_neumann_theory_2004} aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher”.
+The fundamental element of a normative theory of deliberated preferences is the reaction of an individual, whose preferences are to be captured, to arguments.
+
+Normative theories define an agenda: a set of propositions that we are interested in knowing the deliberated judgment of individuals about; a set of individuals that the theory claims applies to; a set of arguments; and a protocol of observation of the judgments an individual adopts towards a proposition after exposure to various arguments.
+Normative theories also define a negation operation on the set of propositions, which this discussion neglects for the sake of simplicity.
+
+Examples of propositions in the agenda include: “I ought to pay at most \$100 for purchasing bundle $b$”, “I ought to acquire alternative $a$ rather than $b$ if it is available in the same conditions”; “I ought not to perform action $a$ because it is immoral”.
+
+The set of individuals in a normative theory represents the situations, socio-economic conditions, acquired diplomas, or other observable features of individuals that must be satisfied for the theory to apply to them.
+(More about this in conclusion.
+\TODO{})
+
+Arguments are defined here as anything that can be presented to an individual that may possibly influence her judgment.
+As an example, an argument can be a text presenting the features of an alternative, or arguing for the (im)morality of an action.
+The term argument evokes a debate, a metaphor appropriate for the comparison of theories that will be described later; but that should be taken with a grain of salt: an image, a tag price, a poem can be an argument in this article.
+
+The protocol of observation in a normative theory defines how the theory proposes to present a sequence of arguments to an individual, and how to observe her resulting judgment about a proposition of interest.
+This protocol permits to determine whether a sequence of arguments “leads” a given individual to a given proposition.
+If the arguments are texts and propositions are of the form “I ought to acquire alternative $a$ rather than $b$”, an example of such a protocol is: present each argument (each text) in the sequence to the individual, asking her to read it carefully; then give the individual a choice between $a$ and $b$; the sequence of arguments is considered to having led the individual to the proposition “I ought to acquire alternative $a$ rather than $b$” iff he chose $a$ rather than $b$.
+In order to allow for repeated observations with a given individual without modifying his endowment, this example protocol should either be content with purely hypothetical choices, or can make these choices binding by letting the individual know that one of his choices will be picked randomly at the end of the experiment and honored.
+
+The judgment of an individual towards propositions may evolve during her exposition to sequences of arguments.
+Of interest to theories of \ac{DJ} are the cases where a so-called decisive argument exists for a given proposition: an argument is decisive when its presence at the end of the sequence of arguments systematically leads the individual to the proposition, whatever the sequence of arguments.
+An argument is at the end of a sequence iff it is the last or before last argument of the sequence.
+Therefore, an argument is decisive when, intuitively, it is able to resist every counter-arguments.
+
+Theories of \ac{DJ} attempt to capture the \emph{\acl{DJ}} of the individuals it deals with, towards some of the propositions in the agenda. 
+The \ac{DJ} of an individual is conceived here as existing independently of any theories of decision.
+The \emph{normative adequacy} axiom, the sole axiom on which a normative theory rests, defines a proposition as being in the deliberated judgment of an individual whenever some argument is decisive for that proposition.
+Accepting this axiom require to accept that decisive arguments, in the sense defined here, reveal something about the \ac{DJ} of an individual.
+
+That the \ac{DJ} of an individual exists independently of any theory of decision making might be considered a strong assumption, by analogy to shallow preferences: psychologists have shown that shallow preferences often depend on a priori irrelevant features pertaining to the description of the decision problem or the context of interrogation.
+Preferences are often said to be constructed, thus, to not exist independently of the framing and context of study.
+
+With no intent of reducing the importance of these findings, it is important to qualify such statements.
+In supplement to them being not necessarily applicable to reflective preferences, the findings of psychologists do not, evidently, show that all preference statements are labile.
+As \citet[p.\ xvi]{lichtenstein_construction_2006} write, “To be sure, there are limits to the process of construction.
+Some televisions just won’t sell; most of the time, people are unlikely to want 80\% of their wages to go into savings.
+It would be an overstatement to say of preferences, as Gertrude Stein said of Oakland, that “there is no there there.”
+
+This remark points towards the importance of allowing for incomplete theories of reflective preferences.
+As \citet{mandler_difficult_2001} discusses in details, it would be unrealistic to postulate that individuals would, after due reflection, in non trivial decision problems, adopt a well specified judgment about any possible proposition of interest.
+From this does not follow that \acp{DJ} do not exist, but that someone’s \ac{DJ} should not be considered to be necessarily complete. 
+\TODO{Check Mandler.}
+The definitions of the theories presented here accordingly tolerate both theory incompleteness, which permits the theory to stay silent on some of the propositions in the agenda, and, more fundamentally, deliberation incompleteness, which permits to tolerate that for some propositions, neither it nor its negation figure in someone’s \ac{DJ}.
+%\cref{sec:incompl} defines formally the notions of theory incompleteness and deliberation incompleteness, and briefly analyzes their relationships.
+
+\subsection{Empirical theories}
+A normative theory defines how to determine that an argument is not decisive for a given proposition: suffices to find a sequence of arguments that does not lead to that proposition.
+This, in turn, under condition of accepting its normative validity, permits to know something about the \ac{DJ} of an individual.
+But this gives no concrete means to know someone’s \ac{DJ}.
+The set of potentially relevant arguments will generally be very large, and can’t be explored thoroughfully.
+More importantly, only some sequences of arguments can be tested for a given individual.
+That is because, first, the individual’s patience is limited, and second, once a sequence has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective.
+Postulating that the individual forgets after some time and separating the tests in time might mitigate this problem, but not necessarily cancel it.
+
+%As a result, it should be possible to determine someone’s \ac{DJ} using only a small increasing set of sequences of arguments.
+A set of sequences of arguments is increasing iff the sequences can be ordered completely such that each sequence following another one “continues” the other one: its first arguments are those constituting the sequence that it follows.
+
+These two problems are tackled by introducing empirical theories of \ac{DJ}.
+An empirical theory for a given normative theory defines a subset of propositions of the agenda, that it claims are contained in the \acp{DJ} of individuals concerned by the normative theory.
+They are called the proposition that the theory supports.
+The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments.
+This is accomplished by three binary relations, part of the definition of empiricial theories: one represents its initial arguments, one plans the possible attacks, and one defines its counter-arguments.
+(An empirical theory also defines a concatenation operation able to dynamically build arguments from fragments of arguments, an aspect which is not discussed in this informal presentation.)
+
+\TODO{Pursue here.}
+More precisely, the argumentation requirements are as follows.
+Given an individual, the empirical theory must be able to present an argument that is, at least initially, convincing to the individual (as judged thanks to the observation protocol of the normative theory).
+It is not mandated that this argument be decisive, as only a weaker requirement is enough to ensure the validity of its claims.
+Instead, the theory must declare which arguments it knows how to answer.
+Such arguments are called the planned attackers.
+Whether an argument effectively attacks another one (from the point of view of the individual) can, again, be defined in terms of the observation protocol of the normative theory.
+Requiring that the theory declares in advance its attackers mean that if an argument effectively attacks one of its argument, then this attack must have been planned.
+
+More precisely, the theory must, for each sequence of arguments leading the individual to a proposition contrary to what the theory supports, be able to exhibit an argument that, when appended to that sequence, leads the
+
+exhibit a decisive argument for that proposition, as judged from the individual’s point of view.
 
@@
 \subsection{Definition}
-A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadsto)_{i \in I})$, 
-with ${\ileadsto} \subseteq \allhist × \Phi$, 
-where $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\mathit{poss}, \mathit{sure}}$.
-(Throughout the article, $\N$ includes zero, and note that $\intvl{1, 0} = \emptyset$.)
+One of the primitive elements of a normative theory is a set of arguments $\allargs$.
+Given a set of arguments $\allargs$, define the set of finite sequences of elements in $\allargs$ (including the empty sequence) as $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$.
+Throughout the article, $\N$ includes zero and $\N^* = \N \setminus \set{0}$.
+Given $j, k \in \N$, the notation $\intvl{j, k}$ represents $\set{l \suchthat j ≤ l ≤ k}$.
+Note that $\intvl{1, 0} = \emptyset$, and given any set $S$, the notation $S^\emptyset$ represents the empty set.
+A generic element of $\allhist$ is denoted by $\hist$ and called a path.
 
-The symbol $¬$ is a negation operator on $\allprops$, such that $\forall \prop \in \allprops: ¬¬\prop = \prop$.
+Two supplementary primitive elements of a normative theory are its agenda $\allprops$, whose elements are called propositions; and a set of individuals $I$ that the theory applies to.
+Given a set of individuals, a set of arguments and an agenda, an observation protocol ${\allleadsto}: I → \Phi^{\allhist}$ maps individuals and paths to propositions. 
+Equivalently, given any individual $i \in I$, ${\ileadsto}: \allhist → \Phi$ maps paths to propositions for this individual. 
+Given an individual $i \in I$, a path $\hist$ and a proposition $\phi$, the path is said to lead to the proposition for this individual iff $\hist \ileadsto \phi$.
+
+A normative theory also defines an involution operator $¬$ on $\allprops$, thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$.
+
+A normative theory is a tuple $(\allprops, ¬, \allargs, I, {\allleadsto})$ 
+%with $\allprops$ an agenda, $¬$ a negation operator on $\allprops$, $\allargs$ a set of arguments, $I$ a set of individuals, and ${\allleadsto}$ an observation protocol, 
+satisfying the constraints described here above.
+%where $\Phi = \allprops × \set{\mathit{poss}, \mathit{sure}}$.
+
 This article also uses this symbol as a negation operator on $\Phi$, defined as follows, $\forall \prop \in \allprops$: $¬\propposs = (¬\prop, \mathit{sure})$ and $¬\propsure = (¬\prop, \mathit{poss})$.
@@
 Define $\hist \ileadstost \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
-(The visual proximity of the symbols $\ileadsto$ and $\ileadstost$ creates a small risk of confusion, but I feel it is justified by the fact that $\ileadsto$ is not used in the rest of this article, except in the proof of \cref{th:protcoh}.)
-Given $\hist \in \allhist$, let $\histend$ denote the set containing the last two elements of the sequence $\hist$ if the sequence has at least two elements; the singleton set containing the last element of the sequence if it has exactly one element; and the empty set if $\hist = \emptyset$.
+(The visual proximity of the symbols $\ileadsto$ and $\ileadstost$ creates a small risk of confusion, but its usage seems justified by the fact that $\ileadsto$ is not used in the rest of this article, except in the proof of \cref{th:protcoh}.)
+
+Given $\hist \in \allhist$, if $l$ denotes its length, $\hist(\intvl{1, l})$ denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
+Let $\histend = \hist(\intvl{\max(1, l-1), l})$ denote the set containing the last two arguments of the sequence $\hist$ if the sequence has at least two elements; and all arguments of the sequence if it has exactly one element or is empty.
+
 Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstost \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstost \phi$.
@@
 
-To see why this hold, consider the following definition.
+To see why this hold, consider the following definition and proposition.
 \begin{definition}[Protocol coherence]
@@
 \subsection{Non-completeness}
+\label{sec:incompl}
 \begin{definition}[Theory completeness]
@@
 
-\section{Additive single-answer empirical theories}
+\section{Empirical theories}
 \subsection{Definition}
-An empirical theory for a normative theory is a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$,
-with ${\gleadsto} \subseteq \allargs × \Phi$, 
-${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
-${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton).
+In this section, a normative theory is supposed given.
+
+An empirical theory is constituted of the following elements.
+
+An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ relates some arguments to some propositions.
+Its role in an empirical theory is to define the propositions that the empirical theory supports (corresponding to $\gPhi$, the range of ${\gleadsto}$) and, for each such proposition, to define the arguments that the theory wants to use as initial arguments to argue in favor of this proposition.
+The set of initial arguments is $\gleadstoinv(\Phi) = \set{\ar \in \allargs \suchthat \exists \phi \in \Phi \suchthat \ar \gleadsto \phi}$.
+
+A planned attacks relation ${\gbeats} \subseteq \allargs × \allargs$ is an irreflexive binary relation on the arguments.
+An argument $\ar_1$ is said to be a planned attack against an argument $\ar_0$ iff $\ar_1 \gbeats \ar_0$.
+Given  an argument $\ar_0$, $\gbeatsinv(\ar_0) = \set{\ar_1 \in \allargs \suchthat \ar_1 \gbeats \ar_0}$ denotes the set of planned attacks against $\ar_0$; and $\gbeatsinv(\allargs) = \set{\ar_1 \in \allargs \suchthat \exists \ar_0 \in \allargs \suchthat \ar_1 \gbeats \ar_0}$ denotes the set of arguments that are planned attacks against at least one argument.
+
+An empirical theory defines a set of argument fragments $\alldargs$.
+They are primitive elements that can be added to selected other fragments and arguments to form new arguments.
+They are used to dynamically build defensive arguments against the planned attacks.
+
+A defense relation ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is an injective and surjective binary relation over $\alldargs × \gbeatsinv(\allargs)$.
+Thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton.
+Note that $\dbeats$ need not be a bijection as it is generally not a function. 
+Given $\ar_1 \in \gbeatsinv(\allargs)$, $\dbeatsinv(\ar_1)$ represents the fragment that the theory $\gamma$ plans to use as a defense against the planned attack $\ar_1$.
+
+A fragment is said to defend an argument iff it is used as a defense against a planned attack against that argument.
+Formally, given any set $S$, define $\powersetz{S}$ as the set of subsets of $S$ without the empty set.
 Define $\df: \allargs → \powersetz{\allargs}$ as $\df = \dbeatsinv \circ \gbeatsinv$.
@@
 In other words, given $\ard \in \dargs$ and $\ar_0 \in \allargs$, $\ard \in \df(\ar_0)$ iff $\exists \ar_1 \in \allargs \suchthat \ard \dbeats \ar_1 \gbeats \ar_0$.
-A \emph{coalition defending $\ar$} is any element of $\powersetz{\df(\ar)}$.
-The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \powersetz{\df(\ar)}) → \allargs$.
-Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \df(\ar)$, $\ar + \dargs$ means $+(\ar, \dargs)$. 
-Given any $\ar \in \allargs$, define $\dfp(\ar)$, the \emph{defenders of $\ar$}, as $\dfp(\ar) = \set{\ar + \dargs \suchthat \emptyset ≠ \dargs \subseteq \df(\ar)}$.
 
+A \emph{coalition of fragments defending $\ar$} is any element of $\powersetz{\df(\ar)}$.
+Such a coalition can be combined with the argument it defends to form a new argument.
+An empirical theory defines, to that effect, a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \powersetz{\df(\ar)}) → \allargs$.
+Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \df(\ar)$, the notation $\ar + \dargs$ stands for $+(\ar, \dargs)$.
+
+This finally permits to define the defenders of an argument: they are all the arguments that can be formed by adding the argument to a coalition of fragments that defends it.
+Given any $\ar \in \allargs$, define $\dfp(\ar) \subseteq \allargs$, the \emph{defenders of $\ar$}, as $\dfp(\ar) = \set{\ar + \dargs \suchthat \emptyset ≠ \dargs \subseteq \df(\ar)}$.
+
+This mechanism permits to define defenders of defenders of an argument, $\dfp(\dfp(\ar))$, defenders of defenders of defenders of an argument, … An empirical theory must however be a priori restricted in the maximal “depth” of its argumentation strategy, in the following sense.
+Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
 An empirical theory must satisfy
-$\exists k \in \N \suchthat (\dfp)^k(\gleadstoinv(\Phi)) = \emptyset$, where $(\dfp)^0$ is the identity function over $\allargs$.
+$\exists k \in \N \suchthat (\dfp)^k(\gleadstoinv(\Phi)) = \emptyset$.
+This does not imply that the relations $\gbeats$ or $\dbeats$ should be finite, however.
+
+An empirical theory (for a normative theory) can now be defined as a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ satisfying the constraints described here above.
+
+An example permits to ensure that the constraint of finite depth does not mandate finiteness of the relations $\gbeats$ or $\dbeats$.
+\begin{proposition}[Possibility of infinite relations]
+	An empirical theory may involve infinite relations $\gbeats$ and $\dbeats$.
+\end{proposition}
+\begin{proof}
+	Consider an agenda containing two propositions, $\allprops = \set{\phi, ¬\phi}$, an infinite set of arguments $\allargs = \set{\ar_k \suchthat k \in \N}$ with $\forall j, k \in \N: \ar_j ≠ \ar_k$, and consider any set of individuals $I$ and observation protocol $\allleadsto$.
+	Define $2\N^* = \set{k \suchthat k / 2 \in \N^*}$ as the set of non-zero even integers.
+	Define ${\gleadsto} = \set{(\ar_0, \phi)}$.
+	Define ${\gbeats} = \set{(\ar_{k - 1}, \ar_0) \suchthat k \in 2\N^*}$ so that all odd numbered arguments are planned attacks against $\ar_0$. 
+	Consider an infinite set of fragments $\alldargs = \set{\ard[k] \suchthat k \in 2\N^*}$ with $\forall j, k \in 2\N^*: \ard[j] ≠ \ard[k]$ so that fragments correspond to non-zero even integers, and define ${\dbeats} = \set{(\ard[k], \ar_{k - 1}) \suchthat k \in 2\N^*}$ so that each (even numbered) defense fragment attacks exactly one (odd numbered) planned attacker of $\ar_0$.
+	Given any coalition of fragments $\dargs$ defending $\ar_0$, consider the set of indices corresponding to the fragments in the coalition, $K_{\dargs} = \set{k \in 2\N^* \suchthat \exists \ard[k] \in \dargs}$;
+	define $j_{\dargs} = \sum_{k \in K_{\dargs}}$ as the sum of these indices;
+	and define $\ar_0 + \dargs = \ar_{j_{\dargs}}$. 
+%	$\ard[k] \in \alldargs$, define $\ar_0 + \set{\ard[k]} = \ar_k$. 
+	Consider an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ for the normative theory $(\allprops, ¬, \allargs, I, {\allleadsto})$.
+That this is indeed a legal empirical theory can be confirmed by checking that all constraints are satisfied, in particular, $(\dfp)^2(\gleadstoinv(\Phi)) = \dfp(\dfp(\ar_0)) = \dfp(\set{\ar_k \suchthat k \in 2\N^*}) = \emptyset$ because there is no planned attack against any argument in $\set{\ar_k \suchthat k \in 2\N^*}$.
+This theory involves infinite relations $\gbeats$ and $\dbeats$.
+\end{proof}
 
 \subsection{Falsifiability}
-Given $\hist \in \allhist$, $\hist(\intvl{1, l(\hist)})$, where $l(\hist) \in \N$ is the length of the sequence $\hist$, denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
-Abusing notation, given $\args \subseteq \allargs$, I write $\args \cap \hist$ to designate $\args \cap \hist(\intvl{1, l(\hist)})$, therefore using simply $\hist$ in that expression to denote the \emph{range} of $\hist$.
+Given $\args \subseteq \allargs$, $\hist \in \allhist$, and letting $l$ denote the length of $\hist$,
+the set $\args \cap \hist(\intvl{1, l})$ denotes the arguments that are both in $\args$ and contained in the sequence $\hist$.
+Abusing notation, I write $\args \cap \hist$ to designate $\args \cap \hist(\intvl{1, l})$, therefore using simply $\hist$ in that expression to denote the \emph{range} of $\hist$.
 
 Given $i \in I, \phi \in \Phi, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \phi$.
-(The notation uses a striked through $\phi$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues against $\phi$, from the point of view of $i$.)
+Such a set $\args$, when not empty, represents an effective set of planned attackers of $\ar$ against $\phi$. 
+The notation uses a striked through $\phi$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues against $\phi$, from the point of view of $i$.
+I write that $\ar$ \emph{$i$-defends} $\phi$ to mean that $\emptyset \nibeats \ar$.
 
-Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
-It represents the coalitions of fragments required to defend $\ar$ (when arguing for $\phi$) from the point of view of $i$.
+Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
+It represents the coalitions of fragments defending $\ar$ (when arguing for $\phi$), from the point of view of $i$, against its effective planned attackers.
 The following proposition shows that these coalitions can be added to $\ar$, and will be useful for other results.
@@
 \begin{proof}
-	Let us prove that $\forall \ar \in \allargs: \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.
+	I will prove that $\forall \ar \in \allargs: \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.
 Note that by definition of $\df(\ar)$, $\dargs \in \powersetz{\df(\ar)}$ iff $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
@@
 	Second (from right to left), let us show that $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)) ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
-	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ar' \in \dbeatsinv(\args)$, $\ar' \dbeats \ar_1$ for some $\ar_1 \in \args$, thus $\ar_1 \gbeats \ar_0$, thus, $\ar_1 \in {\dbeats}(\dargs)$, thus $\ard \dbeats \ar_1$ for some $\ard \in \dargs$, and by injectivity  of $\dargs$, $\ar' = \ard$, whence $\ar' \in \dargs$.
+	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ar' \in \dbeatsinv(\args)$, $\ar' \dbeats \ar_1$ for some $\ar_1 \in \args$, thus $\ar_1 \gbeats \ar_0$, thus, $\ar_1 \in {\dbeats}(\dargs)$, thus $\ard \dbeats \ar_1$ for some $\ard \in \dargs$, and by injectivity  of $\dbeats$, $\ar' = \ard$, whence $\ar' \in \dargs$.
 	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
@@
 
-Given $\ar \in \allargs$, define $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$, representing the subset of defenders of $\ar$ useful for proving $\phi$ from the point of view of $i$.
+Given $\ar \in \allargs$, define $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\phi$.
 Given $i \in I, \phi \in \gPhi$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.
-
-I write that $\ar$ \emph{$i$-defends} $\phi$ to mean that $\emptyset \nibeats \ar$.
 
@@
 \begin{proof}
-	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$; the conclusion then follows thanks to simple normative adequacy (equivalent to normative adequacy thanks to \cref{th:normeqsnorm}).
+	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$; the conclusion then follows thanks to simple normative adequacy (that \cref{th:normeqsnorm} shows to be equivalent to normative adequacy).
 
-	Lemma: $[\ar_0 \in \gargs \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$. That is because $\ar_0 \in \gargs ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and,
+	Lemma: $[\ar_0 \in \gargs \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$.
+That is because $\ar_0 \in \gargs$ implies that $\ar_0$ $i$-defends $\phi$, by convincingness, and,
 	by definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$; \cref{th:produce} thus applies.
@@
 	\label{th:endchal}
-	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$: $(\hist, \ar_\gamma, \ar_\delta)$ is a $\phi/¬\phi$-challenge.
+	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$, $(\hist, \ar_\gamma, \ar_\delta)$ is a $\phi/¬\phi$-challenge.
 \end{lemma}
@@
 
-An increasing sequence of arguments is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N^*$, of sequences of arguments, 
-such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$, and 
-such that $(i, \phi, {\hist}^N)$ falsifies one of the empirical theories for some $\phi \in \Phi$. 
-A sequence of arguments $\histp$ starts with a sequence of arguments $\hist$ of length $l$ iff $\histp$ has length at least $l$ and $\forall k \in \intvl{1, l}: \histp_k = \hist_k$.
+A path $\histp$ starts with a path $\hist$ of length $l$ iff $\histp$ has length at least $l$ and $\forall k \in \intvl{1, l}: \histp_k = \hist_k$.
+An increasing sequence of paths is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N^*$, of paths, 
+such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$.
 
-Given two incompatible empirical theories for a given normative theory, $\alpha = (\gleadsto[\alpha], \gbeats[\alpha], \alldargs_\alpha, \dbeats[\alpha], +_\alpha)$ and $\beta = (\gleadsto[\beta], \gbeats[\beta], \alldargs_\beta, \dbeats[\beta], +_\beta)$ and given any $i \in I$, the following procedure falsifies one of these theories, involve only $i$, and uses queries only about increasing sequences of arguments.
+Given two incompatible empirical theories for a given normative theory, $\alpha = (\gleadsto[\alpha], \gbeats[\alpha], \alldargs_\alpha, \dbeats[\alpha], +_\alpha)$ and $\beta = (\gleadsto[\beta], \gbeats[\beta], \alldargs_\beta, \dbeats[\beta], +_\beta)$ and given any $i \in I$, the following procedure falsifies one of these theories, queries only $i$, and queries $i$ only about some increasing sequence of paths.
 \begin{procedure}
@@
 Let $\allalts$ be a set of alternatives.
-Define $\Phi_\allalts$ as follows.
-Let $\phi_{a > b} \in \iPhi$ represent $i$ deliberately preferring strictly $a$ to $b$.
-Let $\phi_{a ≥ b} \in \iPhi$ represent $i$ deliberately preferring weakly $a$ to $b$.
-Define $¬\phi_{a > b} = \phi_{b ≥ a}$.
+Define $\Phi_\allalts = \{\phi_{a \pst b} \suchthat a ≠ b \in \allalts\} \cup \{\phi_{a \peq b} \suchthat a ≠ b \in \allalts\}$, with $\phi_{a \pst b}$ intuitively representing a strict preference of $i$ for $a$ against $b$, and $\phi_{a \peq b}$ intuitively representing a weak preference of $i$ for $a$ against $b$.
+Define $¬\phi_{a \pst b} = \phi_{b \peq a}$ and $¬\phi_{a \peq b} = \phi_{b \pst a}$.
 
@@
 
-Define $≥_i$, the deliberated preference of $i$, as $a ≥_i b$ iff $\phi_{a ≥ b} \in \iPhi$.
+Define $\peqi$, the deliberated preference of $i$, as $a \peqi b$ iff $a = b \lor \phi_{a \peq b} \in \iPhi$.
 
-Given an empirical theory for a normative theory of preferences, say that it claims a complete preference iff $\forall a, b \in \allalts: \phi_{a ≥ b} \in \gPhi \lor \phi_{b ≥ a} \in \gPhi$.
-Similarly, it claims a transitive preference iff $\forall a, b, c \in \allalts: \phi_{a ≥ b} \in \gPhi \land \phi_{b ≥ c} \in \gPhi ⇒ \phi_{a ≥ c} \in \gPhi$.
+Given an empirical theory for a normative theory of preferences, say that it claims a complete preference iff $\forall a ≠ b \in \allalts: \phi_{a \peq b} \in \gPhi \lor \phi_{b \peq a} \in \gPhi$.
+Similarly, it claims a transitive preference iff $\forall a, b, c \in \allalts: \phi_{a \peq b} \in \gPhi \land \phi_{b \peq c} \in \gPhi ⇒ \phi_{a \peq c} \in \gPhi$.
 Observe that establishing whether an empirical theory claims a complete or transitive preference can be determined a priori (without empirical observations).
 
-Given a bundle $B \subseteq \allalts$ and $i \in I$, $b \in B$ is a deliberated preferred choice for $i$ among $B$ iff $\forall b' \in B: b ≥_i b'$.
+Given a bundle $B \subseteq \allalts$ and $i \in I$, $b \in B$ is a deliberated preferred choice for $i$ among $B$ iff $\forall b' \in B: b \peqi b'$.
 
@@
 \TODO{Consider using only $\phi$ being sure, and dropping everything related to possibility.}
+
+\section{Conclusion}
+Back To Bentham? Explorations Of Experienced Utility, Kahneman Wakker, Sarin, propose to measure hedonimeter total for normative.
+
+\citet[p.\ 100]{raiffa_back_1985} (about SEU): “Give therapy to deviators”.
+\citet[p.\ 108]{raiffa_back_1985}: “In experiments with my students, my ingenious protestations did not always prove to be ingenious enough.
+Yes, they were dazzled (and perhaps confused) but many remained unconvinced; if the chips were down, they would behave just as before.”
 
@@
 
+\hbadness 10000
 \bibliography{simple}

### 2020-08-14 simple.tex
Started new pref descr

@@
 \section{Preferences}
+\subsection{Preferences, better}
+Let $\allalts$ be a set of alternatives.
+
+A choice prediction $C_\gamma: \powersetz{\allalts} → \powersetz{\powersetz{\allalts}}$ is a mapping from each possible bundle $\emptyset ≠ B \subseteq \allalts$ to a non-empty set $\emptyset ≠ C_\gamma(B) = \mathcal{C} \subseteq \powersetz{B}$ of non-empty sets of alternatives included in the bundle.
+Thus, a generic element $\alts \in C_\gamma(B)$ satisfies $\emptyset ≠ \alts \subseteq B$. 
+The choice prediction given a bundle $B$ predicts that $i$ will, given $B$, choose some indifference set that includes one of the elements $\alts \in C_\gamma(B)$.
+
+Define $\Phi_\allalts = \set{\phi_{B, a \ind b} \suchthat \emptyset ≠ B \subseteq \allalts, a ≠ b \in B} \cup \set{\phi_{B, ¬a} \suchthat \emptyset ≠ B \subseteq \allalts, a \in B}$.
+
+Given $\emptyset ≠ B \subseteq \allalts$, define $\emptyset ≠ B_{\hist, i} \subseteq B$ as the subset that $i$ chooses as her indifference choice after exposure to $\hist$.
+Define $\hist \ileadsto \phi_{B, a \ind b}$ iff $[a \in B_{\hist, i} ⇔ b \in B_{\hist, i}]$.
+Define $\hist \ileadsto \phi_{B, ¬a}$ iff $a \notin B_{\hist, i}$.
+
+Given $a ≠ b$, define $a \peq b$ iff $\forall \set{a, b} \subseteq B: \phi_{B, a \ind b} \in \gPhi \lor \phi_{B, ¬b} \in \gPhi$.
+
+In order to be as resolute as possible, define an arbitrary connected ordering $>$ on $\allalts$ (a transitive, asymmetric and connected relation, connected meaning that $\forall a ≠ b \in \allalts:  [a > b \lor b > a]$), used to break indifference.
+Define $a \pst b$ iff $[a \peq b \land (b \npeq a \lor a > b)]$.
+
+Old approach follows.
+
+Define $\Phi_\allalts = \set{\phi_{B, \mathcal{C}} \suchthat \emptyset ≠ B \subseteq \allalts, \mathcal{C} \subseteq \powersetz{B}}$.
+
+$\gamma$ gives, for each 
+Define $\phi_{(B_k), B}$: $\hist \ileadsto \phi$ iff given $B$, $i$ chooses some $B_{\hist, i} \subseteq B$ such that $\exists B_k \subseteq B_{\hist, i}$.
+
+Define $a \peq b$ iff $\forall \set{a, b} \subseteq B: [\exists \set{a, b} \subseteq B_k \lor (\exists a \in B_k \land \nexists b \in B_k)]$.
+
+Define $a \pst b$ iff $a \peq b \land b \npst a$.
+
+To prove. 1) $\peq$ is transitive. 2) If $a \pst b$, then $b$ is never chosen by $i$ when $a$ is present: $\forall \phi_{B_k} \in \iPhi: $ no $B_k$ contain $b$.
+
 \subsection{Preferences}

### 2020-08-15 simple.tex
Rm old approach to new prefs (and minor impr)
Some new attempts about DPs

--- 2020-08-14 simple.tex
@@
 \section{Preferences}
+\subsection{Preferences, better}
+Let $\allalts$ be a set of alternatives.
+
+Define $\Phi_\allalts = \set{\phi_{B, a}, \phi_{B, ¬a} \suchthat \emptyset ≠ B \subseteq \allalts, a \in B}$.
+
+Given $\emptyset ≠ B \subseteq \allalts$, define $\emptyset ≠ B_{\hist, i} \subseteq B$ as the subset that $i$ chooses as her indifference choice after exposure to $\hist$.
+Define $\hist \ileadsto \phi_{B, a}$ iff $a \in B_{\hist, i}$.
+Define $\hist \ileadsto \phi_{B, ¬a}$ iff $a \notin B_{\hist, i}$.
+
+Given $a, b \in \allalts$, define $a \pst b$ iff $\forall \set{a, b} \subseteq B: \phi_{B, ¬b} \in \gPhi$.
+Define $a \ind b$ iff $ \forall c \in \allalts: [a \pst c ⇔ b \pst c] \land \forall \set{a, b} \subseteq B: [\phi_{B, a} \in \gPhi ⇔ \phi_{B, b} \in \gPhi]$.
+Define ${\peq} = {\pst} \cup {\ind}$.
+
+The $\peq$ relation is reflexive because $a = b ⇒ a \ind b$.
+\begin{proposition}[Transitivity]
+	The $\peq$ relation is transitive.
+\end{proposition}
+\begin{proof}
+	Well, this is false.
+\end{proof}
+
+\subsection{Older}
+A choice prediction $C_\gamma: \powersetz{\allalts} → \powersetz{\powersetz{\allalts}}$ is a mapping from each possible bundle $\emptyset ≠ B \subseteq \allalts$ to a non-empty set $\emptyset ≠ C_\gamma(B) = \mathcal{C} \subseteq \powersetz{B}$ of non-empty sets of alternatives included in the bundle.
+Thus, a generic element $\alts \in C_\gamma(B)$ satisfies $\emptyset ≠ \alts \subseteq B$. 
+The choice prediction given a bundle $B$ predicts that $i$ will, given $B$, choose some indifference set that includes one of the elements $\alts \in C_\gamma(B)$.
+
+Define $\Phi_\allalts = \set{\phi_{B, a \ind b} \suchthat \emptyset ≠ B \subseteq \allalts, a ≠ b \in B} \cup \set{\phi_{B, ¬a} \suchthat \emptyset ≠ B \subseteq \allalts, a \in B}$.
+
+Given $a, b \in \allalts$, define $a \peq b$ iff $[a = b] \lor [\forall \set{a, b} \subseteq B: \phi_{B, a \ind b} \in \gPhi \lor \phi_{B, ¬b} \in \gPhi]$.
+
+In order to be as resolute as possible, define an arbitrary connected ordering $>$ on $\allalts$ (a transitive, asymmetric and connected relation, connected meaning that $\forall a ≠ b \in \allalts:  [a > b \lor b > a]$), used to break indifference.
+Define $a \pst b$ iff $[a \peq b \land (b \npeq a \lor a > b)]$.
+
+Note that $\peq$ is not necessarily transitive.
+Given $\allalts = \set{a, b, c}$, given $i$, for all $\hist \in \allhist$, define $\set{a, b}_{\hist, i} = \set{a, b}$, $\set{a, c}_{\hist, i} = \set{a}$, $\set{b, c}_{\hist, i} = \set{b, c}$, and $\set{a, b, c}_{\hist, i} = \set{a, b, c}$.
+Then, $\gamma$ may be valid while supporting $a \ind b$ and $b \ind c$ and have no opinion about $a$ VS $c$: indeed, neither $¬c$ nor $a \ind c$ hold.
+That’s because WARP is broken: $\set{a, b, c}$ contain $\set{a, c}$ and $c$ is chosen, but in $\set{a, c}$, $c$ is not chosen.
+
+To prove.
+1) If $\peq$ is transitive and the model is valid, and $a \pst b$, then $b$ is never chosen by $i$ when $a$ is present.
+2) If a WARP argument is effective, then (something like) $\ipeq$ is transitive.
+
+Consider defining $\ipeq$ and showing that $\peq$ must be a subset of it, if valid?
+
+Perhaps, define $a \pst b$ iff $\forall \set{a, b} \subseteq B$, $a$ chosen or $b$ not chosen and sometimes both $a$ chosen and $b$ not chosen.
+Then define $a \ind b$ iff $\forall c \in \allalts: [a \pst c ⇔ b \pst c]$ and $\forall \set{a, b} \subseteq B$, $a$ chosen iff $b$ chosen.
+
 \subsection{Preferences}
@@
 
-Define $\peqi$, the deliberated preference of $i$, as $a \peqi b$ iff $a = b \lor \phi_{a \peq b} \in \iPhi$.
+Define $\ipeq$, the deliberated preference of $i$, as $a \ipeq b$ iff $a = b \lor \phi_{a \peq b} \in \iPhi$.
 
@@
 
-Given a bundle $B \subseteq \allalts$ and $i \in I$, $b \in B$ is a deliberated preferred choice for $i$ among $B$ iff $\forall b' \in B: b \peqi b'$.
+Given a bundle $B \subseteq \allalts$ and $i \in I$, $b \in B$ is a deliberated preferred choice for $i$ among $B$ iff $\forall b' \in B: b \ipeq b'$.
 

### 2020-08-16 simple.tex
Representing DP: done.

@@
 \section{Preferences}
-\subsection{Preferences, better}
+\subsection{Representing deliberated preferences}
 Let $\allalts$ be a set of alternatives.
@@
 
-Given $\emptyset ≠ B \subseteq \allalts$, define $\emptyset ≠ B_{\hist, i} \subseteq B$ as the subset that $i$ chooses as her indifference choice after exposure to $\hist$.
-Define $\hist \ileadsto \phi_{B, a}$ iff $a \in B_{\hist, i}$.
-Define $\hist \ileadsto \phi_{B, ¬a}$ iff $a \notin B_{\hist, i}$.
-
-Given $a, b \in \allalts$, define $a \pst b$ iff $\forall \set{a, b} \subseteq B: \phi_{B, ¬b} \in \gPhi$.
-Define $a \ind b$ iff $ \forall c \in \allalts: [a \pst c ⇔ b \pst c] \land \forall \set{a, b} \subseteq B: [\phi_{B, a} \in \gPhi ⇔ \phi_{B, b} \in \gPhi]$.
-Define ${\peq} = {\pst} \cup {\ind}$.
-
-The $\peq$ relation is reflexive because $a = b ⇒ a \ind b$.
-\begin{proposition}[Transitivity]
-	The $\peq$ relation is transitive.
+Given $\emptyset ≠ B \subseteq \allalts$, define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses as her indifference choice after exposure to $\hist$.
+Define $\hist \ileadsto \phi_{B, a}$ iff $a \in c^\hist_i(B)$.
+Define $\hist \ileadsto \phi_{B, ¬a}$ iff $a \notin c^\hist_i(B)$.
+
+Given $a, b \in \allalts$, define $a \gpst b$ iff $\forall \set{a, b} \subseteq B: \phi_{B, ¬b} \in \gPhi$.
+Define $a \gind b$ iff either $a = b$ or $\forall \set{a, b} \subseteq B: [\phi_{B, a} \in \gPhi \land \phi_{B, b} \in \gPhi] \lor [\exists c \in B \suchthat c \gpst a \land c \gpst b]$.
+Define ${\gpeq} = {\gpst} \cup {\gind}$.
+
+An empirical theory is said to be coherent iff $\forall \emptyset ≠ B \subseteq \allalts$: $¬(\forall a \in B: \phi_{B, ¬a} \in \gPhi) \land ¬(\exists a \in B \suchthat \phi_{B, a} \in \gPhi \land \phi_{B, ¬a} \in \gPhi)$.
+Coherence is required for validity, but, contrary to validity, is not an empirical property, in the sense that it can be verified without experiments, as it is independent of $\ileadsto$.
+
+If $\gpeq$ is transitive, and if $\gamma$ is valid, $\gpeq$ can be said to represent part of the deliberated preference of $i$, in the sense that choosing from the undominated elements of parts of $\gpeq$ restricts choice in a way that is systematically compatible with $i$’s \ac{DJ}.
+This is made precise below.
+
+Given $i \in I$ and a bundle $B$, say that a subset $B' \subseteq B$ is a deliberated restricted choice set for $i$ given $B$ iff $[\forall a \in B \setminus B': \phi_{B, ¬a} \in \iPhi] \lor [\exists a \in B' \suchthat \phi_{B, a} \in \iPhi]$.
+Restricting consideration to deliberated restricted choice sets respects $i$’s \ac{DJ} in the sense that such sets exclude from $B$ only alternatives that $i$ deliberately excludes from possible choice among the bundle $B$, or include an alternative that $i$ deliberately chooses when choosing from the bundle $B$.
+
+If $\gpeq$ is transitive and $\gamma$ is valid, the following theorem shows that a choice function can be defined by picking from undominated elements of $\gpeq$ in such a way that only deliberated restricted choice sets result.
+$\powersetz[\mathit{F}]{\allalts}$ designates the finite non-empty subsets of $\allalts$.
+
+\begin{theorem}[Deliberated preference]
+	\label{th:dp}
+	If $\gpeq$ is transitive and $\gamma$ is valid, let $r$ be a choice function such that, given any $B \in \powersetz[\mathit{F}]{\allalts}$, $r(B)$ contains exactly one arbitrary argument of each undominated equivalence classes of $B$, where $\gind$ determines the equivalence classes and $\gpst$ determines the undominated elements.
+Then, $\forall B \in \powersetz[\mathit{F}]{\allalts}$, $r(B)$ is a deliberated restricted choice set for $i$ given $B$.
+\end{theorem}
+\begin{proof}
+	Observe that under these hypothesis, $\gpeq$ is a transitive, reflexive binary relation on $\allalts$, $\gpst$ is its asymmetric part and $\gind$ is its symmetric part.
+That $\gpst$ is asymmetric follows from coherence, which requires, considering $B = \set{a, b}$, that $\phi_{B, ¬a} \notin \gPhi$ or $\phi_{B, ¬b} \notin \gPhi$ (hence $b \ngpst a$ or $a \ngpst b$).
+Coherence itself follows from validity.
+
+	The phrasing of the theorem only defines $r$ informally.
+These supplementary notations may be useful to avoid ambiguity.
+Given $B \subseteq \allalts$, let $B / {\gind} = \set{{\gind}(a) \suchthat a \in B}$ denote the equivalence classes defined by $\gind$ among the elements of $B$.
+The relation $\gpst$ can be used to discriminate some of these equivalence classes.
+Define $\gpst^*$, an asymmetric transitive relation on $B / {\gind}$, such that given any two equivalence classes $\alts, \alts' \in B / {\gind}$, $\alts \gpst^* \alts'$ iff $\forall \alt \in \alts, \alt' \in \alts': \alt \gpst \alt'$.
+Let $\max_{\gpst^*}(B / {\gind}) = \set{\alts \in B / {\gind} \suchthat \forall \alts' \in B / {\gind}: \alts' \ngpst^* \alts}$ denote the undominated equivalence classes of $B / {\gind}$ considering $\gpst^*$.
+
+	In some situations, multiple deliberated restricted choice sets exist.
+A linear ordering $>$ on $\allalts$ can be used to break ties and obtain a precisely defined choice function.
+(A linear ordering $>$ on $\allalts$ is a transitive, asymmetric and connected binary relation over $\allalts × \allalts$, connected meaning that $\forall a ≠ b \in \allalts:  [a > b \lor b > a]$.) Note that this tie breaking strategy is adopted for concreteness and conceptual simplicity, but the proof does not depend on this specific choice.
+It may in general depend on the bundle.
+
+	Define now the choice function $r: \powersetz[\mathit{F}]{\allalts} → \powersetz{\allalts}$ as picking the maximal element (as determined by $>$) of each undominated equivalence class in $B$, thus, $r(B) = \set{\max_>(\alts) \suchthat \alts \in \max_{\gpst^*}(B / {\gind})}$.
+
+	Given any bundle $B \in \powersetz[\mathit{F}]{\allalts}$, we now have to show that $B' = r(B)$ satisfies $[\forall a \in B \setminus B': \phi_{B, ¬a} \in \iPhi] \lor [\exists a \in B' \suchthat \phi_{B, a} \in \iPhi]$.
+Because $\gamma$ is valid, suffices to show that $[\forall a \in B \setminus B': \phi_{B, ¬a} \in \gPhi] \lor [\exists a \in B' \suchthat \phi_{B, a} \in \gPhi]$.
+	Consider any $a \in B \setminus B'$. Because $B'$ is finite, for some $b \in B'$, $b \gpst a$ or $b \gind a$.
+
+	If $b \gpst a$, and because $\set{a, b} \in B$, $\phi_{B, ¬a} \in \gPhi$.
+
+	If $b \gind a$, and because $\set{a, b} \in B$, $\phi_{B, b} \in \gPhi$ (because $\nexists c \in B \suchthat c \gpst b$, otherwise $b \notin B'$).
+\end{proof}
+The phrasing of this theorem considers only finite bundles for simplicity. It more generally applies to bundles that are closed according to $\gpst$. \TODO{Check.}
+
+\begin{proposition}[Completeness implies transitivity]
+	\label{th:comptrans}
+	If $\gpeq$ is complete ($\forall a, b \in \allalts: a \gpeq b \lor b \gpeq a$) and $\gamma$ is coherent, then it is transitive.
 \end{proposition}
 \begin{proof}
-	Well, this is false.
-\end{proof}
+	Consider any $a, b, c \in \allalts$ with $a \gpeq b \gpeq c$ and let us show that $a \gpeq c$.
+
+	Observe first that given any bundle $B \subseteq \allalts$ with $x, y \in B$, when $x \gpeq y$, $\phi_{B, ¬y} \notin \gPhi ⇒ \phi_{B, ¬x} \notin \gPhi$. 
+	Indeed, when $x ≠ y$,
+	because $x \gpeq y$, either $\phi_{B, ¬y} \in \gPhi$ or $\phi_{B, x} \in \gPhi$; thus, if $\phi_{B, ¬y} \notin \gPhi$, then $\phi_{B, x} \in \gPhi$, hence, by coherence, $\phi_{B, ¬x} \notin \gPhi$.
+
+	Consider now the bundle $B = \set{a, b, c}$.
+By coherence, $[\phi_{B, ¬a} \notin \gPhi \lor \phi_{B, ¬b} \notin \gPhi \lor \phi_{B, ¬c} \notin \gPhi]$.
+The above observation leads to $\phi_{B, ¬c} \notin \gPhi ⇒ \phi_{B, ¬b} \notin \gPhi$ and $\phi_{B, ¬b} \notin \gPhi ⇒ \phi_{B, ¬a} \notin \gPhi$.
+Therefore, $\phi_{B, ¬a} \notin \gPhi$.
+
+	Completeness implies that $a \gpeq c \lor c \gpeq a$, or equivalently, $a \gpeq c \lor c \gpst a \lor c \gind a$. Excluding $c \gpst a$ thanks to $\phi_{B, ¬a} \notin \gPhi$, we obtain $a \gpeq c$.
+\end{proof}
+
+The following proposition follows from \cref{th:comptrans,th:dp}.
+\begin{proposition}[Completeness implies single recommendations]
+	If $\gpeq$ is complete and $\gamma$ is valid, then the choice function $r$ defined in \cref{th:dp} associates to each finite bundle a singleton set.
+\end{proposition}
+
+When $\gpeq$ is not transitive, this relation still permits to define choice functions that could be said to respect, in some reasonable sense, the deliberated preference of the individuals.
+However, this claim is more arguable, as it is generally (though by all means not unanimously) considered in the literature that a reflective preference should be transitive.
+Further explorations of this path are left for future articles.
 

### 2020-08-16 simple.tex
Repl older pref with WARP section (failure)

@@
 
-\subsection{Older}
-A choice prediction $C_\gamma: \powersetz{\allalts} → \powersetz{\powersetz{\allalts}}$ is a mapping from each possible bundle $\emptyset ≠ B \subseteq \allalts$ to a non-empty set $\emptyset ≠ C_\gamma(B) = \mathcal{C} \subseteq \powersetz{B}$ of non-empty sets of alternatives included in the bundle.
-Thus, a generic element $\alts \in C_\gamma(B)$ satisfies $\emptyset ≠ \alts \subseteq B$. 
-The choice prediction given a bundle $B$ predicts that $i$ will, given $B$, choose some indifference set that includes one of the elements $\alts \in C_\gamma(B)$.
-
-Define $\Phi_\allalts = \set{\phi_{B, a \ind b} \suchthat \emptyset ≠ B \subseteq \allalts, a ≠ b \in B} \cup \set{\phi_{B, ¬a} \suchthat \emptyset ≠ B \subseteq \allalts, a \in B}$.
-
-Given $a, b \in \allalts$, define $a \peq b$ iff $[a = b] \lor [\forall \set{a, b} \subseteq B: \phi_{B, a \ind b} \in \gPhi \lor \phi_{B, ¬b} \in \gPhi]$.
-
-In order to be as resolute as possible, define an arbitrary connected ordering $>$ on $\allalts$ (a transitive, asymmetric and connected relation, connected meaning that $\forall a ≠ b \in \allalts:  [a > b \lor b > a]$), used to break indifference.
-Define $a \pst b$ iff $[a \peq b \land (b \npeq a \lor a > b)]$.
-
+\subsection{WARP}
 Note that $\peq$ is not necessarily transitive.
@@
 
-To prove.
-1) If $\peq$ is transitive and the model is valid, and $a \pst b$, then $b$ is never chosen by $i$ when $a$ is present.
-2) If a WARP argument is effective, then (something like) $\ipeq$ is transitive.
-
-Consider defining $\ipeq$ and showing that $\peq$ must be a subset of it, if valid?
-
-Perhaps, define $a \pst b$ iff $\forall \set{a, b} \subseteq B$, $a$ chosen or $b$ not chosen and sometimes both $a$ chosen and $b$ not chosen.
-Then define $a \ind b$ iff $\forall c \in \allalts: [a \pst c ⇔ b \pst c]$ and $\forall \set{a, b} \subseteq B$, $a$ chosen iff $b$ chosen.
+A normative theory satisfies WARP iff $[\exists \ar_{ab} \ileadstost \phi_{\set{a, b}, a} \land \exists \ar_{bc} \ileadstost \phi_{\set{b, c}, b}] ⇒ \exists \ar_{abc} \ileadstost \phi_{\set{a, b, c}, a}$.
+
+\begin{theorem}[WARP implies transitivity]
+	If an empirical theory $\gamma$ for a normative theory satisfying WARP is valid, then an empirical theory $\delta$ is valid with $\gpeq$ being transitive.
+\end{theorem}
+This is not enough.
+Need to build intermediate arguments: given $\ar_0$ for $\phi_{\set{a, b}, a}$ and $\ar_2$ for $\phi_{\set{b, c}, b}$, need $\ar = \ar_0 + \ar_2$ for $\phi_{\set{a, b, c}, a}$ that is subject to no more attacks.
 

### 2020-08-16 simple.tex
RM WARP section (requires too much stuff)

@@
 Further explorations of this path are left for future articles.
-
-\subsection{WARP}
-Note that $\peq$ is not necessarily transitive.
-Given $\allalts = \set{a, b, c}$, given $i$, for all $\hist \in \allhist$, define $\set{a, b}_{\hist, i} = \set{a, b}$, $\set{a, c}_{\hist, i} = \set{a}$, $\set{b, c}_{\hist, i} = \set{b, c}$, and $\set{a, b, c}_{\hist, i} = \set{a, b, c}$.
-Then, $\gamma$ may be valid while supporting $a \ind b$ and $b \ind c$ and have no opinion about $a$ VS $c$: indeed, neither $¬c$ nor $a \ind c$ hold.
-That’s because WARP is broken: $\set{a, b, c}$ contain $\set{a, c}$ and $c$ is chosen, but in $\set{a, c}$, $c$ is not chosen.
-
-A normative theory satisfies WARP iff $[\exists \ar_{ab} \ileadstost \phi_{\set{a, b}, a} \land \exists \ar_{bc} \ileadstost \phi_{\set{b, c}, b}] ⇒ \exists \ar_{abc} \ileadstost \phi_{\set{a, b, c}, a}$.
-
-\begin{theorem}[WARP implies transitivity]
-	If an empirical theory $\gamma$ for a normative theory satisfying WARP is valid, then an empirical theory $\delta$ is valid with $\gpeq$ being transitive.
-\end{theorem}
-This is not enough.
-Need to build intermediate arguments: given $\ar_0$ for $\phi_{\set{a, b}, a}$ and $\ar_2$ for $\phi_{\set{b, c}, b}$, need $\ar = \ar_0 + \ar_2$ for $\phi_{\set{a, b, c}, a}$ that is subject to no more attacks.
 

### 2020-08-16 simple.tex
Rm more old sections about prefs

@@
 
-Given $\emptyset ≠ B \subseteq \allalts$, define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses as her indifference choice after exposure to $\hist$.
+The observation protocol goes as follows.
+Given $i$ and $\emptyset ≠ B \subseteq \allalts$ and $\hist$, $i$, after having been presented $\hist$, is asked to choose among a subset of elements from $B$ among which she is indifferent.
+Define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses as her indifference choice after exposure to $\hist$.
 Define $\hist \ileadsto \phi_{B, a}$ iff $a \in c^\hist_i(B)$.
@@
 However, this claim is more arguable, as it is generally (though by all means not unanimously) considered in the literature that a reflective preference should be transitive.
-Further explorations of this path are left for future articles.
-
-\subsection{Preferences}
-Let $\allalts$ be a set of alternatives.
-Define $\Phi_\allalts = \{\phi_{a \pst b} \suchthat a ≠ b \in \allalts\} \cup \{\phi_{a \peq b} \suchthat a ≠ b \in \allalts\}$, with $\phi_{a \pst b}$ intuitively representing a strict preference of $i$ for $a$ against $b$, and $\phi_{a \peq b}$ intuitively representing a weak preference of $i$ for $a$ against $b$.
-Define $¬\phi_{a \pst b} = \phi_{b \peq a}$ and $¬\phi_{a \peq b} = \phi_{b \pst a}$.
-
-A normative theory of preferences about $\allalts$ is a theory about $\Phi_\allalts$: a tuple $(\allprops, ¬, \allargs, I, (\ileadsto)_{i \in I})$, with $\allprops$ defined as $\allprops_\allalts$, $¬$ defined as above.
-
-Define $\ipeq$, the deliberated preference of $i$, as $a \ipeq b$ iff $a = b \lor \phi_{a \peq b} \in \iPhi$.
-
-Given an empirical theory for a normative theory of preferences, say that it claims a complete preference iff $\forall a ≠ b \in \allalts: \phi_{a \peq b} \in \gPhi \lor \phi_{b \peq a} \in \gPhi$.
-Similarly, it claims a transitive preference iff $\forall a, b, c \in \allalts: \phi_{a \peq b} \in \gPhi \land \phi_{b \peq c} \in \gPhi ⇒ \phi_{a \peq c} \in \gPhi$.
-Observe that establishing whether an empirical theory claims a complete or transitive preference can be determined a priori (without empirical observations).
-
-Given a bundle $B \subseteq \allalts$ and $i \in I$, $b \in B$ is a deliberated preferred choice for $i$ among $B$ iff $\forall b' \in B: b \ipeq b'$.
-
-The next result follows from these definitions and from classical results about choice functions and complete, transitive preferences. \TODO{Be more precise.}
- \begin{theorem}
- 	If an empirical theory for a normatively adequate normative theory of preference claims a complete and transitive preference and is valid, then, given any bundle $\emptyset ≠ B \subseteq \allalts$, some $b \in B$ is a deliberated preferred choice for $i$ among $B$.
- \end{theorem}
-
-Given $i$ and $\phi_{a > b}$, $\hist \ileadsto \phi$ iff $i$, after having been presented $\ar$, is asked to choose among $a$, $b$, or declare she is indifferent if permitted; and $i$ chooses $a$.
-And $\hist \ileadsto \phi_{a ≥ b}$ iff $i$ does not choose $b$ (thus chooses $a$ or declare she is indifferent if permitted).
-Note that $\hist \ileadsto \phi ⇔ \hist \nileadsto ¬\phi$.
+Further explorations of this possibility are left for future articles.
 

### 2020-08-17 simple.tex
Minor changes, and a remark about the failure of this representation of DP

@@
 It takes work and serious reflection to find out one’s own preferences.”
-It can be expected that some behavior highlighted by psychologists \citet{lichtenstein_construction_2006}, such as framing effects, would be rejected by the individuals themselves when pondering their decisions.
+It can be expected that some behavior highlighted by psychologists \citep{kahneman_thinking_2012}, such as framing effects, would be rejected by the individuals themselves when pondering their decisions.
 
@@
 
-Let me state how the approach proposed here differs from those proposed in the literature, and what problems it aims at solving.
+Let me state how the approach proposed here to capture reflective preferences differs from those proposed in the literature, and what problems it aims at solving.
 
@@
 That this is an important methodological problem is sometimes recognized by authors adopting this approach.
-\Citet{bleichrodt_making_2001}, for example, state that laundering require controversial assumptions (p.
-1500), and recommend it only as a last resort, recommending discussing with the decision-maker whenever possible to elicit her reflective preferences (p.
-1499).
+\Citet{bleichrodt_making_2001}, for example, state that laundering require controversial assumptions (p.\ 1500), and recommend it only as a last resort, recommending discussing with the decision-maker whenever possible to elicit her reflective preferences (p.\ 1499).
 Note that nudging \citep{thaler_nudge_2009} creates a similar problem: we have to guess what the individual would like if he thought hard about the decision problem, was well-informed, and actively worked against the psychological features he himself does not consider adequate for good decision making.
@@
 
+Let $I$ and $\allargs$ be any sets of individuals and arguments.
+
 The observation protocol goes as follows.
-Given $i$ and $\emptyset ≠ B \subseteq \allalts$ and $\hist$, $i$, after having been presented $\hist$, is asked to choose among a subset of elements from $B$ among which she is indifferent.
-Define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses as her indifference choice after exposure to $\hist$.
+Given $i \in I$, $\emptyset ≠ B \subseteq \allalts$ and $\hist \in \allhist$, the individual $i$, after having been presented the arguments in the sequence $\hist$, is asked to choose among a subset of elements from $B$ among which she is indifferent.
+Define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses after exposure to $\hist$.
 Define $\hist \ileadsto \phi_{B, a}$ iff $a \in c^\hist_i(B)$.
@@
 
-Given $a, b \in \allalts$, define $a \gpst b$ iff $\forall \set{a, b} \subseteq B: \phi_{B, ¬b} \in \gPhi$.
+\begin{remark}
+	This does not work, because $\gamma$ supporting $\phi_{\set{a, b, c, d}, ¬b}$, $\phi_{\set{a, b, c, d}, ¬c}$ and $\phi_{\set{a, b, c, d}, ¬d}$ may be valid even if $i$ never chooses $a$: $i$ may satisfy $¬b$ (by picking $c$) when given an argument for $¬b$, satisfy both $¬b$ and $¬c$ (by picking $d$) when given arguments for $¬b$ and $¬c$, and so on.
+The individual $i$ is not obliged to satisfy the three arguments for $¬b$, $¬c$ and $¬d$ simultaneously, as these arguments are required to count only when they are at the end of the sequence.
+\end{remark}
+
+This defines normative theories about $\allalts$. Any empirical theory for a normative theory about $\allalts$ is said to be an empirical theory about $\allalts$.
+
+Given an empirical theory about $\allalts$ and $a, b \in \allalts$, define $a \gpst b$ iff $\forall \set{a, b} \subseteq B: \phi_{B, ¬b} \in \gPhi$.
 Define $a \gind b$ iff either $a = b$ or $\forall \set{a, b} \subseteq B: [\phi_{B, a} \in \gPhi \land \phi_{B, b} \in \gPhi] \lor [\exists c \in B \suchthat c \gpst a \land c \gpst b]$.
@@
 
-An empirical theory is said to be coherent iff $\forall \emptyset ≠ B \subseteq \allalts$: $¬(\forall a \in B: \phi_{B, ¬a} \in \gPhi) \land ¬(\exists a \in B \suchthat \phi_{B, a} \in \gPhi \land \phi_{B, ¬a} \in \gPhi)$.
-Coherence is required for validity, but, contrary to validity, is not an empirical property, in the sense that it can be verified without experiments, as it is independent of $\ileadsto$.
+An empirical theory about $\allalts$ is said to be coherent iff $\forall \emptyset ≠ B \subseteq \allalts$: $¬(\forall a \in B: \phi_{B, ¬a} \in \gPhi) \land ¬(\exists a \in B \suchthat \phi_{B, a} \in \gPhi \land \phi_{B, ¬a} \in \gPhi)$.
+Coherence is required for validity.
+Note that it is not an empirical property, in the sense that it can be verified without experiments, as it is independent of $\ileadsto$.
 
@@
 	\label{th:dp}
-	If $\gpeq$ is transitive and $\gamma$ is valid, let $r$ be a choice function such that, given any $B \in \powersetz[\mathit{F}]{\allalts}$, $r(B)$ contains exactly one arbitrary argument of each undominated equivalence classes of $B$, where $\gind$ determines the equivalence classes and $\gpst$ determines the undominated elements.
+	Let $\gamma$ be a valid empirical theory for a normatively adequate normative theory about $\allalts$, and such that $\gpeq$ is transitive.
+Let $r$ be a choice function such that, given any $B \in \powersetz[\mathit{F}]{\allalts}$, $r(B)$ contains exactly one arbitrary argument of each undominated equivalence classes of $B$, where $\gind$ determines the equivalence classes and $\gpst$ determines the undominated elements.
 Then, $\forall B \in \powersetz[\mathit{F}]{\allalts}$, $r(B)$ is a deliberated restricted choice set for $i$ given $B$.
@@
 \end{proof}
-The phrasing of this theorem considers only finite bundles for simplicity. It more generally applies to bundles that are closed according to $\gpst$. \TODO{Check.}
+The phrasing of this theorem considers only finite bundles for simplicity. It more generally applies to bundles that are closed according to $\gpst$. \TODO{Phrase this correctly.}
 
@@
 
-When $\gpeq$ is not transitive, this relation still permits to define choice functions that could be said to respect, in some reasonable sense, the deliberated preference of the individuals.
+When $\gpeq$ is not transitive, it still permits to define choice functions that could be said to respect, in some reasonable sense, the deliberated preference of the individuals.
 However, this claim is more arguable, as it is generally (though by all means not unanimously) considered in the literature that a reflective preference should be transitive.
@@
 
+The claims of an empirical theory about $\allalts$ can sometimes be defined on the basis of a preference ordering $\peq$. In such a case, the claims …
+
 \subsection{Satisfaction}
@@
 
-Define $C$ a set of criteria, functions $c: \allalts → \R$ measuring the performances of the alternatives according to some point of view.
-Let $t: \R^C$ be a set of thresholds, thus, consisting of one real threshold $t_c \in \R$ per criterion.
-Say that $a \in \allalts$ is satisficing iff $\forall c \in C: c(a) ≥ t_c$.
-
-The theory $\gamma$ says that $i$ is a satisficer using some defined criteria $C$ and thresholds $t = (t_c)_{c \in C}$.
+Define $C$ a set of criteria, functions $c: \allalts → \R$, each function measuring the performances of the alternatives according to some point of view.
+Let $t \in \R^C$ be a set of thresholds, thus, consisting of one real valued threshold $t_c \in \R$ per criterion.
+Say that $a \in \allalts$ is satisfying iff $\forall c \in C: c(a) ≥ t_c$.
+
+The theory $\gamma$ claims, intuitively, that individuals $i \in I$ are satisficers using some defined criteria $C$ and thresholds $t = (t_c)_{c \in C}$.
 The set $\gPhi$ is defined as $\set{\phi_{a > b} \suchthat a \text{ is satisficing and $b$ is not}}$.

### 2020-08-18 simple.tex
Mostly examples

@@
 It takes work and serious reflection to find out one’s own preferences.”
-It can be expected that some behavior highlighted by psychologists \citep{kahneman_thinking_2012}, such as framing effects, would be rejected by the individuals themselves when pondering their decisions.
+In the words of \citet[p.\ 9]{bell_descriptive_1988}, “Our decision makers are not economic automatons; they make mistakes, have remorse, suffer anxieties, and cannot make up their minds” (cited by \citet[p.\ 87]{deparis_etude_2012}).
+Indeed, it is to be expected that some behavior highlighted by psychologists \citep{kahneman_thinking_2012}, such as framing effects, would be rejected by the individuals themselves when pondering their decisions.
 
@@
 \subsection{Definition}
+\TODO{Consider using only $\phi$ being sure, and dropping everything related to possibility.}
+
 One of the primitive elements of a normative theory is a set of arguments $\allargs$.
@@
 Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstost \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstost \phi$.
+
+\begin{remark}
+	I’d rather drop the negation and observe that if the protocol is defined so that $\hist \ileadsto \phi_1 ⇒ \hist \nileadsto \phi_2$, then $\phi_1 \in \iPhi ⇒ \phi_2 \notin \iPhi$.
+Observe that this is always possible.
+The definitions about completeness should use a negation operator in supplement to the normative theory tuple.
+\end{remark}
 
@@
 An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ relates some arguments to some propositions.
-Its role in an empirical theory is to define the propositions that the empirical theory supports (corresponding to $\gPhi$, the range of ${\gleadsto}$) and, for each such proposition, to define the arguments that the theory wants to use as initial arguments to argue in favor of this proposition.
+Its role in an empirical theory is to define the propositions that the empirical theory supports (corresponding to $\gPhie$, the range of ${\gleadsto}$) and, for each such proposition, to define the arguments that the theory wants to use as initial arguments to argue in favor of this proposition.
 The set of initial arguments is $\gleadstoinv(\Phi) = \set{\ar \in \allargs \suchthat \exists \phi \in \Phi \suchthat \ar \gleadsto \phi}$.
@@
 
-Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
+Given $i \in I, \phi \in \gPhie, \ar \in \allargs$, define $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
 It represents the coalitions of fragments defending $\ar$ (when arguing for $\phi$), from the point of view of $i$, against its effective planned attackers.
@@
 	\label{th:indf}
-	$\forall i \in I, \phi \in \gPhi, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
+	$\forall i \in I, \phi \in \gPhie, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
 \end{proposition}
@@
 Given $\ar \in \allargs$, define $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\phi$.
-Given $i \in I, \phi \in \gPhi$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.
+Given $i \in I, \phi \in \gPhie$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.
 
 \begin{definition}[Convincingness]
-	An empirical theory is \emph{convincing} iff $\forall i \in I, \phi \in \gPhi, \ar \in \gargs: \ar$ $i$-defends $\phi$.
+	An empirical theory is \emph{convincing} iff $\forall i \in I, \phi \in \gPhie, \ar \in \gargs: \ar$ $i$-defends $\phi$.
 \end{definition}
 
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist, \ar) \in I × \gPhi × \allhist × \gargs$ such that $\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \phi$.
+A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist, \ar) \in I × \gPhie × \allhist × \gargs$ such that $\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \phi$.
 I also write that $(i, \phi, \hist, \ar)$ falsifies $\gamma$ to mean that it is a falsification instance of $\gamma$.
@@
 \begin{proof}
-	For all $i \in I, \phi \in \gPhi, \ar \in \gargs$: $\ar$ does not $i$-defend $\phi$ iff $\exists \hist \in \allhist \suchthat \left[\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist, \ar)$ falsifies $\gamma$.
+	For all $i \in I, \phi \in \gPhie, \ar \in \gargs$: $\ar$ does not $i$-defend $\phi$ iff $\exists \hist \in \allhist \suchthat \left[\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist, \ar)$ falsifies $\gamma$.
 Therefore, $\gamma$ is not convincing iff $\exists (i, \phi, \ar) \suchthat \ar$ does not $i$-defend $\phi$ iff $\exists \hist \suchthat (i, \phi, \hist, \ar)$ falsifies $\gamma$ iff $\gamma$ has a falsification instance.
@@
 \begin{definition}[Validity]
-	An empirical theory is \emph{valid} iff $\forall i \in I, \phi \in \gPhi: [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
+	An empirical theory is \emph{valid} iff $\forall i \in I, \phi \in \gPhie: [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
 \end{definition}
@@
 	\label{th:produce}
-	Given $\phi \in \gPhi$, $\ar_0 \in \gargs$ that $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$.
+	Given $\phi \in \gPhie$, $\ar_0 \in \gargs$ that $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$.
 Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
@@
 \begin{proof}
-	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$; the conclusion then follows thanks to simple normative adequacy (that \cref{th:normeqsnorm} shows to be equivalent to normative adequacy).
+	Given any $i \in I$ and $\phi \in \gPhie$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$; the conclusion then follows thanks to simple normative adequacy (that \cref{th:normeqsnorm} shows to be equivalent to normative adequacy).
 
@@
 \subsection{Effectively comparing models}
-Given $\phi \in \Phi$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\phi$ iff $\phi \in \gPhi[\gamma] \land ¬\phi \in \gPhi[\delta]$.
+Given $\phi \in \Phi$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\phi$ iff $\phi \in \gPhie[\gamma] \land ¬\phi \in \gPhie[\delta]$.
 Say that they are incompatible iff there is at least one $\phi \in \Phi$ that they disagree about.
@@
 
-Define $\Phi_\allalts = \set{\phi_{B, a}, \phi_{B, ¬a} \suchthat \emptyset ≠ B \subseteq \allalts, a \in B}$.
+Define $\Phi_\allalts = \set{\phi_{B, \choices} \suchthat \emptyset ≠ B \subseteq \allalts, \choices \subseteq \powersetz{B}}$.
 
@@
 Define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses after exposure to $\hist$.
-Define $\hist \ileadsto \phi_{B, a}$ iff $a \in c^\hist_i(B)$.
-Define $\hist \ileadsto \phi_{B, ¬a}$ iff $a \notin c^\hist_i(B)$.
-
-\begin{remark}
-	This does not work, because $\gamma$ supporting $\phi_{\set{a, b, c, d}, ¬b}$, $\phi_{\set{a, b, c, d}, ¬c}$ and $\phi_{\set{a, b, c, d}, ¬d}$ may be valid even if $i$ never chooses $a$: $i$ may satisfy $¬b$ (by picking $c$) when given an argument for $¬b$, satisfy both $¬b$ and $¬c$ (by picking $d$) when given arguments for $¬b$ and $¬c$, and so on.
-The individual $i$ is not obliged to satisfy the three arguments for $¬b$, $¬c$ and $¬d$ simultaneously, as these arguments are required to count only when they are at the end of the sequence.
-\end{remark}
-
-This defines normative theories about $\allalts$. Any empirical theory for a normative theory about $\allalts$ is said to be an empirical theory about $\allalts$.
-
-Given an empirical theory about $\allalts$ and $a, b \in \allalts$, define $a \gpst b$ iff $\forall \set{a, b} \subseteq B: \phi_{B, ¬b} \in \gPhi$.
-Define $a \gind b$ iff either $a = b$ or $\forall \set{a, b} \subseteq B: [\phi_{B, a} \in \gPhi \land \phi_{B, b} \in \gPhi] \lor [\exists c \in B \suchthat c \gpst a \land c \gpst b]$.
+Define $\hist \ileadsto \phi_{B, \choices}$ iff $c^\hist_i(B) \in \choices$.
+
+This defines normative theories about $\allalts$.
+Any empirical theory for a normative theory about $\allalts$ that satisfies $\forall \emptyset ≠ B \subseteq \allalts: \exists !
+\emptyset ≠ \choices \subseteq \powersetz{B} \suchthat \phi_{B, \choices} \in \gPhie$ is said to be an empirical theory about $\allalts$.
+The notation $\exists!$ means: there exists a unique element.
+The requirement that there is at least one is innocuous, as choosing $\choices = \powersetz{B}$ ensures that $\phi_{B, \choices} \in \iPhi$, by definition of $\ileadsto$.
+
+An empirical theory about $\allalts$ thus associates to each possible bundle $B$ a set of possible choices $\choices$, whose semantics is that the theory claims that the deliberated choice of $i$, given the bundle $B$, lies among $\choices$.
+Let $\gPhi(B) \subseteq \powersetz{B}$ denote this set of possible choices, thus $\gPhi(B) = \choices  ⇔ \phi_{B, \choices} \in \gPhie$.
+
+Given an empirical theory about $\allalts$ and $a, b \in \allalts$, define $a \gpst b$ iff $\forall \set{a, b} \subseteq B: b \notin \bigcup \gPhi(B)$.
+Thus, $a \gpst b$ iff $\gamma$ claims that $b$ is not deliberately chosen in presence of $a$.
+Define $a \gind b$ iff $\forall \set{a, b} \subseteq B: [\forall C \in \choices: a \in C ⇔ b \in C]$.
 Define ${\gpeq} = {\gpst} \cup {\gind}$.
-
-An empirical theory about $\allalts$ is said to be coherent iff $\forall \emptyset ≠ B \subseteq \allalts$: $¬(\forall a \in B: \phi_{B, ¬a} \in \gPhi) \land ¬(\exists a \in B \suchthat \phi_{B, a} \in \gPhi \land \phi_{B, ¬a} \in \gPhi)$.
-Coherence is required for validity.
-Note that it is not an empirical property, in the sense that it can be verified without experiments, as it is independent of $\ileadsto$.
 
@@
 
-Given $i \in I$ and a bundle $B$, say that a subset $B' \subseteq B$ is a deliberated restricted choice set for $i$ given $B$ iff $[\forall a \in B \setminus B': \phi_{B, ¬a} \in \iPhi] \lor [\exists a \in B' \suchthat \phi_{B, a} \in \iPhi]$.
-Restricting consideration to deliberated restricted choice sets respects $i$’s \ac{DJ} in the sense that such sets exclude from $B$ only alternatives that $i$ deliberately excludes from possible choice among the bundle $B$, or include an alternative that $i$ deliberately chooses when choosing from the bundle $B$.
+Given $i \in I$ and a bundle $B$, say that a subset $B' \subseteq B$ is a deliberated restricted choice set for $i$ given $B$ iff 
+$\exists \phi_{B, \choices} \in \iPhi \suchthat \forall C \in \choices: C \cap B' ≠ \emptyset$.
+Restricting consideration to deliberated restricted choice sets respects $i$’s \ac{DJ} in the sense that it necessarily includes at least one alternative that is a deliberated choice of $i$.
 
@@
 	Observe that under these hypothesis, $\gpeq$ is a transitive, reflexive binary relation on $\allalts$, $\gpst$ is its asymmetric part and $\gind$ is its symmetric part. 
-That $\gpst$ is asymmetric follows from coherence, which requires, considering $B = \set{a, b}$, that $\phi_{B, ¬a} \notin \gPhi$ or $\phi_{B, ¬b} \notin \gPhi$ (hence $b \ngpst a$ or $a \ngpst b$).
-Coherence itself follows from validity.
+	$\gpeq$ is reflexive because $\gind$ is.
+	That $\gpst$ is asymmetric is seen by considering, given any $a, b \in \allalts$, the bundle $B = \set{a, b}$: pick any $C \in \gPhi(B) \subseteq \powersetz{B}$, thus, $C \in \powersetz{B}$, hence, $a \in C$ or $b \in C$, and therefore, $b \ngpst a$ or $a \ngpst b$.
 
@@
 
-	Given any bundle $B \in \powersetz[\mathit{F}]{\allalts}$, we now have to show that $B' = r(B)$ satisfies $[\forall a \in B \setminus B': \phi_{B, ¬a} \in \iPhi] \lor [\exists a \in B' \suchthat \phi_{B, a} \in \iPhi]$.
-Because $\gamma$ is valid, suffices to show that $[\forall a \in B \setminus B': \phi_{B, ¬a} \in \gPhi] \lor [\exists a \in B' \suchthat \phi_{B, a} \in \gPhi]$.
-	Consider any $a \in B \setminus B'$. Because $B'$ is finite, for some $b \in B'$, $b \gpst a$ or $b \gind a$.
-
-	If $b \gpst a$, and because $\set{a, b} \in B$, $\phi_{B, ¬a} \in \gPhi$.
-
-	If $b \gind a$, and because $\set{a, b} \in B$, $\phi_{B, b} \in \gPhi$ (because $\nexists c \in B \suchthat c \gpst b$, otherwise $b \notin B'$).
+	Given any bundle $B \in \powersetz[\mathit{F}]{\allalts}$, we now have to show that $B' = r(B)$ satisfies 
+	$\exists \phi_{B, \choices} \in \iPhi \suchthat \forall C \in \choices: C \cap B' ≠ \emptyset$.
+%	$[\forall a \in B \setminus B': \phi_{B, ¬a} \in \iPhi] \lor [\exists a \in B' \suchthat \phi_{B, a} \in \iPhi]$. 
+	Because $\gamma$ is valid, suffices to show that, given $\choices = \gPhi(B) \subseteq \powersetz{B}$, 
+	$\forall C \in \choices: C \cap B' ≠ \emptyset$.
+%	$[\forall a \in B \setminus B': \phi_{B, ¬a} \in \gPhie] \lor [\exists a \in B' \suchthat \phi_{B, a} \in \gPhie]$.
+	Pick any $C \in \choices$ and any $a \in C$ (thus, $a \in B$). By definition of $\gpst$, $\nexists b \in B \suchthat b \gpst a$ as otherwise, $a \notin C$.
+	Note that, by construction of $B'$, as $a \in B$ is undominated, it belongs to some equivalence class of which a member has been brought in $B'$.
+In other words, $\exists b \in B' \suchthat b \gind a$.
+Therefore, by definition of $\gind$, $b \in C$.
+Thus, $b \in C \cap B'$.
 \end{proof}
@@
 	Consider any $a, b, c \in \allalts$ with $a \gpeq b \gpeq c$ and let us show that $a \gpeq c$.
-
-	Observe first that given any bundle $B \subseteq \allalts$ with $x, y \in B$, when $x \gpeq y$, $\phi_{B, ¬y} \notin \gPhi ⇒ \phi_{B, ¬x} \notin \gPhi$. 
-	Indeed, when $x ≠ y$,
-	because $x \gpeq y$, either $\phi_{B, ¬y} \in \gPhi$ or $\phi_{B, x} \in \gPhi$; thus, if $\phi_{B, ¬y} \notin \gPhi$, then $\phi_{B, x} \in \gPhi$, hence, by coherence, $\phi_{B, ¬x} \notin \gPhi$.
-
-	Consider now the bundle $B = \set{a, b, c}$.
-By coherence, $[\phi_{B, ¬a} \notin \gPhi \lor \phi_{B, ¬b} \notin \gPhi \lor \phi_{B, ¬c} \notin \gPhi]$.
-The above observation leads to $\phi_{B, ¬c} \notin \gPhi ⇒ \phi_{B, ¬b} \notin \gPhi$ and $\phi_{B, ¬b} \notin \gPhi ⇒ \phi_{B, ¬a} \notin \gPhi$.
-Therefore, $\phi_{B, ¬a} \notin \gPhi$.
-
-	Completeness implies that $a \gpeq c \lor c \gpeq a$, or equivalently, $a \gpeq c \lor c \gpst a \lor c \gind a$. Excluding $c \gpst a$ thanks to $\phi_{B, ¬a} \notin \gPhi$, we obtain $a \gpeq c$.
+	Consider the bundle $B = \set{a, b, c}$ and let $\choices = \gPhi(B)$.
+
+	Observe first that if $x, y \in B$ and $x \gpeq y$, $y \in \bigcup \choices ⇒ x \in \bigcup \choices$. 
+	Indeed, if $x \gpst y$, $y \notin \bigcup \choices$, and if $x \gind y$, $y \in \bigcup \choices ⇔ x \in \bigcup \choices$ as $x$ and $y$ can then be treated interchangeably considering their memberships to elements of $\choices$.
+
+	Because $\bigcup \choices ≠ \emptyset$, $[a \in \bigcup \choices \lor b \in \bigcup \choices \lor c \in \bigcup \choices]$.
+The above observation leads to $c \in \bigcup \choices ⇒ b \in \bigcup \choices$ and $b \in \bigcup \choices ⇒ a \in \bigcup \choices$.
+Therefore, $a \in \bigcup \choices$.
+
+	Completeness implies that $a \gpeq c \lor c \gpeq a$, or equivalently, $a \gpeq c \lor c \gpst a \lor c \gind a$. Excluding $c \gpst a$ thanks to $a \in \bigcup \choices$, we obtain $a \gpeq c$.
 \end{proof}
@@
 
-When $\gpeq$ is not transitive, it still permits to define choice functions that could be said to respect, in some reasonable sense, the deliberated preference of the individuals.
+Note that $\gpeq$ is independent of $\ileadsto$; thus, any property of $\gpeq$, such as transitiveness or completeness, is a priori (as opposed to empirical), meaning that its satisfaction can be verified without experiments.
+
+When $\gpeq$ is not transitive, choice functions could still be defined that could be said to respect, in some reasonable sense, the deliberated preference of the individuals.
 However, this claim is more arguable, as it is generally (though by all means not unanimously) considered in the literature that a reflective preference should be transitive.
@@
 
-The claims of an empirical theory about $\allalts$ can sometimes be defined on the basis of a preference ordering $\peq$. In such a case, the claims …
-
-\subsection{Satisfaction}
+In what follows, the claims of an empirical theory about $\allalts$ will be defined on the basis of a transitive preference ordering $\peq$ on $\allalts$, as follows.
+Given $\emptyset ≠ B \subseteq \allalts$, define $\gPhi(B) = \set{\cup \choices' \suchthat \emptyset ≠ \choices' \subseteq \choices}$, where $\choices$ are the undominated equivalence classes in $B$ according to $\peq$ (thus $\choices = \max_{\pst^*}(B / {\ind})$, using the notations defined in \cref{th:dp}).
+The check that ${\peq} = {\gpeq}$ is left to the reader.
+Thus, all the examples that follow have a transitive $\gpeq$ and therefore claim to represent a deliberated preference (when valid) in the sense defined in this section.
+
+\subsection{A theory based on Satisfaction}
 Consider a normative theory of preferences about a given set of alternatives $\allalts$. Let $\gamma$ be the following empirical theory for that normative theory.
@@
 Say that $a \in \allalts$ is satisfying iff $\forall c \in C: c(a) ≥ t_c$.
+ Let $A$ denote the satisfying alternatives.
 
 The theory $\gamma$ claims, intuitively, that individuals $i \in I$ are satisficers using some defined criteria $C$ and thresholds $t = (t_c)_{c \in C}$.
-The set $\gPhi$ is defined as $\set{\phi_{a > b} \suchthat a \text{ is satisficing and $b$ is not}}$.
-Given $a, b \in \allalts$, with $a$ satisficing and $b$ not, define $\ar_{a > b}$ as the text: “$a$ has performance $c_1(a)$ on criterion $c_1$, and it is reasonable to consider that having at least $t_{c_1}$ is satisfying enough from the point of view captured by $c_1$, (… same phrase for the other criteria…), therefore, it is a fully satisfactory alternative; whereas $b$ is not satisfactory on criteria (… enumeration of the criteria such that $c(b) < t_{c}$).”
-Define ${\gleadsto} = \set{\ar_{a > b}, \phi_{a > b}) \suchthat a \text{ is satisficing and $b$ is not}}$.
-Define $\alldargs = \gbeats = \dbeats = {+} = \emptyset$: the theory does not consider any counter-argument as potentially damaging. 
-This defines the theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$.
-
-Observe that $\gamma$ does not claim a complete preference, but, whenever there is exactly one satisficing alternative in $\allalts$, it still determines a deliberated preferred choice for $i$ among $\allalts$.
-
-\subsection{LS}
+Define $\peq$ as $a \peq b$ iff $a \in A \lor b \notin A$.
+Note that $\peq$ is complete and contains at most two equivalence classes: $A$, and $\allalts \setminus A$.
+This defines the set of claims that $\gamma$ supports, namely, for any $\emptyset ≠ B \subseteq \allalts$, $\gPhi(B) = B \cap A$.
+
+Given $a \in A$, define the fragment $\ar_a$ as the text: “$a$ has performance $c_1(a)$ on criterion $c_1$, and it is reasonable to consider that having at least $t_{c_1}$ is satisfying enough from the point of view captured by $c_1$, [… same phrase for the other criteria…], therefore, it is a fully satisfactory alternative.”
+Given $b \in \allalts \setminus A$, define $\ar_b$ as the text: “$b$ is not satisfactory on the criterion [some criterion such that $c(b) < t_{c}$]: the performance $t_c$ should be attained for considering $b$ as satisfying on that point of view, but it obtains only $c(b)$ on that criterion [… same phrase for the other criteria such that $c(b) < t_c$].”
+
+Given a bundle $B$, define $\ar_B$ as the text obtained by concatenating all fragments in $\set{\ar_a \suchthat a \in B}$.
+
+%Given $a \in A, b \in \allalts \setminus A$, define $\ar_{a > b}$ as the text: “$a$ has performance $c_1(a)$ on criterion $c_1$, and it is reasonable to consider that having at least $t_{c_1}$ is satisfying enough from the point of view captured by $c_1$, [… same phrase for the other criteria…], therefore, it is a fully satisfactory alternative; whereas $b$ is not satisfactory on criteria [… enumeration of the criteria such that $c(b) < t_{c}$].”
+Define ${\gleadsto} = \set{(\ar_B, \gPhi(B)) \suchthat \emptyset ≠ B \subseteq \allalts}$.
+Define $\alldargs = {\gbeats} = {\dbeats} = {+} = \emptyset$: the theory does not consider any counter-argument as potentially damaging. 
+This defines an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ about $\allargs$.
+
+A more realistic variant of this empirical theory would refrain from claiming that all satisfactory alternatives are equivalent, and that all non-satisfactory alternatives are equivalent.
+Indeed, this claims is likely to fail reflecting the deliberated preferences of the individuals: $i$ will probably pick $a$ rather than $\set{a, b}$ given a bundle of two satisfactory alternatives $\set{a, b}$ with $a$ Pareto-dominating $b$.
+
+To this effect, given $a, b \in \allalts$, define $a \peq b$ iff $a \in A \land b \notin A$ (this also changes the set of claims that $\gamma$ supports) and keep the other definitions intact.
+The resulting theory does not claim to capture complete deliberated preferences, as it ignores how any two alternatives that are both satisfactory, or both unsatisfactory, compare.
+However, whenever there is exactly one satisficing alternative in $B$, it still determines a single deliberated preferred choice for $i$ among $B$.
+
+\subsection{Comparing two lotteries}
 %Idea: argue for P > $.
@@
 %XP3. With effective gambling and iterated thinking to thing about their preference.
-Define $P = (.99, +\$4; .01, −\$0.1)$ and $D = (.33, +\$16; .67, −\$2)$.
-
-Theory claims that all $i$’s prefer deliberately $P$ to $D$, in the sense of betting at least as much for.
-
-Define $\phi$ as: $i$ deliberately prefers $P$ to $D$, in the sense of bidding at least as much for $P$ than for $D$ after deliberation.
-Define $¬\phi$ similarly, but bidding more for $D$ than for $P$.
+In an article about preference reversals, LS discuss an example involving two lotteries.
+The lottery $P$ makes you win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $P = (.99, +\$4; .01, −\$0.1)$.
+The lottery $D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
+The letter $P$ stands for probability: one salient aspect of $P$ is the very high chance of winning.
+The letter $D$ stands for dollar: one salient aspect of $D$ is the high gain it gives (compared to $P$) in dollar amount if the player is lucky.
+
+This example is interesting because when asked to bid for lotteries, the theory discussed by the authors predicts, and their experiments confirm, that subjects tend to bid more for $D$ than for $P$ (because the bidding question tend to make individuals focus on dollar amounts) whereas when asked to choose one lottery, the lotteries being presented in pairs, subjects tend to choose $P$ (giving a greater attention to probabilities).
+
+This section presents a theory that claims that $i$ deliberately prefers $P$ to $D$, in the sense of bidding at least as much for $P$ than for $D$.
+Because the goal of this example is mainly to illustrate the mechanisms of counter-argumentation, this example defines the theory only for these two lotteries.
+The reader should understand how the mechanisms described here above, together with the principle of argumentation presented here for these two specific lotteries, would permit to define a more general theory about lotteries that argues similarly to this one.
+\TODO{Think about the right discursive approach here.}
+
+Define $\allprops = \set{\phi, ¬\phi}$, $\phi$ representing intuitively the case that $i$ deliberately prefers $P$ to $D$, in the sense of bidding at least as much for $P$ than for $D$ after deliberation, and $¬\phi$, the opposite.
 
 Define $\ileadstost$ as follows.
-Given $\hist = (…, \ar)$, $\hist \ileadstost \phi$ iff, in a situation of $i$ having been exposed to the prefix …, saying: “Considering the argument $\ar$, would you please indicate your maximum selling price for $P$, and for $D$” leads $i$ to act accordig to $\phi$.
-Note that $\hist \ileadstost \phi$ iff $\hist \nileadstost ¬\phi$.
-
-Thus, the normative axiom is satisfied iff, whenever there is a argument that, facing any counter-argument, leads $i$ to bid at least as much for $P$ than for $D$, we are ready to accept that $i$ deliberately prefers $P$ to $D$, in the bidding sense.
-
-Define $\ar_0$ as arguing that the bid for both P and D should equal their expected revenue, namely, $.99 × (\$4) − 0.01 × \$0.1$ or etc.
+Given $\hist = (…, \ar)$, $\hist \ileadstost \phi$ iff, in a situation of $i$ having been exposed to these arguments, saying: “Considering these arguments, would you please indicate your maximum selling price for $P$, and for $D$” leads $i$ to bid at least as much for $P$ than for $D$.
+$\hist \ileadstost ¬\phi$ is defined similarly.
+%Note that $\hist \ileadstost \phi$ iff $\hist \nileadstost ¬\phi$.
+
+Thus, the normative adequacy axiom is satisfied iff, whenever there is a argument that, facing any counter-argument, leads $i$ to bid at least as much for $P$ than for $D$, we are ready to accept that $i$ deliberately prefers $P$ to $D$, in the bidding sense.
+
+Define $\ar_0$ as arguing that the bid for both $P$ and $D$ should equal their expected revenue, namely, $.99 × (\$4) − 0.01 × \$0.1$ for $P$.
+Here is a possible text for $\ar_0$.
 “Imagine you play this bet 100 times.
@@
 Thus, your average net gain for the $P$ bet would be \$3.9590.
-Etc.”
+Therefore, we suggest you bet \$3.9590 for $P$.
+[Similar text for $D$.]”
 
 Define $\ar_1$ as arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain.
-Define $\ar_2$ as arguing that the goal is to maximise average revenue, and thus, losses should count equally to gains.
-Define $\ar'_1$ as arguing by considering only what is to be gained and not the probabilities, and thus, arguing that $D$ is worth much more.
-Define $\ar'_2$ as arguing that also the probabilities should be taken into account.
-Define $+$ as the simple concatenation of its arguments.
-
-Then, define $\gbeats = \set{(\ar_1, \ar_0), (\ar'_1, \ar_0), (\ar'_1, \ar_2), (\ar_1, \ar'_2)}$, $\dbeats = \set{(\ar_2, \ar_1), (\ar'_2, \ar'_1)}$.
-
-\TODO{Consider using only $\phi$ being sure, and dropping everything related to possibility.}
+Define $\ard[2]$ as arguing that the goal is to maximise average revenue, and thus, losses should count equally to gains.
+Define $\ar_3$ as arguing by considering only what is to be gained and not the probabilities, and thus, arguing that $D$ is worth much more.
+Define $\ard[4]$ as arguing that also the probabilities should be taken into account.
+Define $+$ as the simple concatenation of its arguments, which define $\ar_2 = \ar_0 + \set{\ard[2]}$, $\ar_4 = \ar_0 + \set{\ard[4]}$, $\ar_6 = \ar_0 + \set{\ard[2], \ard[4]} = \ar_2 + \set{\ard[4]} = \ar_4 + \set{\ard[2]}$.
+
+Finally, define $\gbeats = \set{(\ar_1, \ar_0), (\ar_3, \ar_0), (\ar_3, \ar_2), (\ar_1, \ar_4)}$, $\dbeats = \set{(\ard[2], \ar_1), (\ard[4], \ar_3)}$.
+
+This defines a normative and an empirical theory about $\allalts = \set{P, D}$.
 
@@
 by Strong op.
-val.: $\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
+val.: $\forall \phi \in \gPhie, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
 
@@
 
-A transitive empirical preference theory about $\allalts$ is an empirical theory for a normative theory about $\allalts$ such that $\gPhi$ is transitive.
-
-Associate to such a theory a preference ordering $\succ$ on $\allalts$ as follows: $a \succ b$ iff $\ppstsure \in \gPhi$.
+A transitive empirical preference theory about $\allalts$ is an empirical theory for a normative theory about $\allalts$ such that $\gPhie$ is transitive.
+
+Associate to such a theory a preference ordering $\succ$ on $\allalts$ as follows: $a \succ b$ iff $\ppstsure \in \gPhie$.
 
@@
 \begin{definition}[Convincingness]
-	$\forall i \in I, \phi \in \gPhi, \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
+	$\forall i \in I, \phi \in \gPhie, \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
 \end{definition}
@@
 \begin{proof}
-	Consider $i \in I$ and $\phi \in \gPhi$. 
+	Consider $i \in I$ and $\phi \in \gPhie$. 
 	By hypothesis, $\exists k$ such that some $\ar_k \in \args_k$ defends $\phi$ under protection of $\emptyset$. Therefore, $\ar_k \ileadstosts \phi$. Using \cref{ax:norm}, validity follows.

### 2020-08-18 simple.tex
Dropped propsure and propposs

@@
 \addtokomafont{labelinglabel}{\sffamily\bfseries}
-\renewcommand{\phi}{\varphi}%TODO
 \DeclareMathAlphabet{\mathup}{OT1}{\familydefault}{m}{n}
@@
 \subsection{Definition}
-\TODO{Consider using only $\phi$ being sure, and dropping everything related to possibility.}
-
 One of the primitive elements of a normative theory is a set of arguments $\allargs$.
+(The calligraphic letter $S$ is used to denote the arguments in order to reserve the letter $A$ for sets of alternatives.)
 Given a set of arguments $\allargs$, define the set of finite sequences of elements in $\allargs$ (including the empty sequence) as $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$.
@@
 Two supplementary primitive elements of a normative theory are its agenda $\allprops$, whose elements are called propositions; and a set of individuals $I$ that the theory applies to.
-Given a set of individuals, a set of arguments and an agenda, an observation protocol ${\allleadsto}: I → \Phi^{\allhist}$ maps individuals and paths to propositions. 
-Equivalently, given any individual $i \in I$, ${\ileadsto}: \allhist → \Phi$ maps paths to propositions for this individual. 
-Given an individual $i \in I$, a path $\hist$ and a proposition $\phi$, the path is said to lead to the proposition for this individual iff $\hist \ileadsto \phi$.
+Given a set of individuals, a set of arguments and an agenda, an observation protocol ${\allleadsto}: I → \allprops^{\allhist}$ maps individuals and paths to propositions. 
+Equivalently, given any individual $i \in I$, ${\ileadsto}: \allhist → \allprops$ maps paths to propositions for this individual. 
+Given an individual $i \in I$, a path $\hist$ and a proposition $\prop$, the path is said to lead to the proposition for this individual iff $\hist \ileadsto \prop$.
 
 A normative theory also defines an involution operator $¬$ on $\allprops$, thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$.
+(The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
 
@@
 satisfying the constraints described here above.
-%where $\Phi = \allprops × \set{\mathit{poss}, \mathit{sure}}$.
-
-This article also uses this symbol as a negation operator on $\Phi$, defined as follows, $\forall \prop \in \allprops$: $¬\propposs = (¬\prop, \mathit{sure})$ and $¬\propsure = (¬\prop, \mathit{poss})$.
-Observe that $¬¬\phi = \phi$.
-(The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
-As usual with binary relations, $\hist \nileadsto \phi$ means $(\hist, \phi) \notin {\ileadsto}$.
-
-Given $i \in I, \phi \in \Phi, \hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadsto \phi \land \hist \nileadsto ¬\phi$.
-Define $\hist \ileadstost \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
+%where $\allprops = \allprops × \set{\mathit{poss}, \mathit{sure}}$.
+
+As usual with binary relations, $\hist \nileadsto \prop$ means $(\hist, \prop) \notin {\ileadsto}$.
+
+Given $i \in I, \prop \in \allprops, \hist \in \allhist$, say that $\hist$ leads strongly to $\prop$, $\hist \ileadstost \prop$, iff $\hist \ileadsto \prop \land \hist \nileadsto ¬\prop$.
 (The visual proximity of the symbols $\ileadsto$ and $\ileadstost$ creates a small risk of confusion, but its usage seems justified by the fact that $\ileadsto$ is not used in the rest of this article, except in the proof of \cref{th:protcoh}.)
@@
 
-Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstost \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstost \phi$.
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstost \prop$.
 
 \begin{remark}
-	I’d rather drop the negation and observe that if the protocol is defined so that $\hist \ileadsto \phi_1 ⇒ \hist \nileadsto \phi_2$, then $\phi_1 \in \iPhi ⇒ \phi_2 \notin \iPhi$.
+	I’d rather drop the negation and observe that if the protocol is defined so that $\hist \ileadsto \prop_1 ⇒ \hist \nileadsto \prop_2$, then $\prop_1 \in \iprops ⇒ \prop_2 \notin \iprops$.
 Observe that this is always possible.
@@
 	\label{ax:norm}
-	$\forall i \in I, \phi \in \Phi: 
-		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \phi) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi)] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
+	$\forall i \in I, \prop \in \allprops: 
+		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \prop) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\prop)] ⇒ \prop \in \iprops \land ¬\prop \notin \iprops.$
 \end{axiom}
@@
 	\label{ax:snorm}
-	$\forall i \in I, \phi \in \Phi: 
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
+	$\forall i \in I, \prop \in \allprops: 
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ \prop \in \iprops \land ¬\prop \notin \iprops.$
 \end{property}
@@
 	\label{def:protcoh}
-	$\forall i \in I, \phi \in \Phi$:
+	$\forall i \in I, \prop \in \allprops$:
 	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi].
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\prop].
 	\end{equation}
@@
 	Protocol coherence is satisfied by definition of $\ileadstost$.
-Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\phi$.
+Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost \prop$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto ¬\prop$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost ¬\prop$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\prop$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\prop$.
 \end{proof}
@@
 
-To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\phi \in \Phi$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \phi \lor \ar \ileadstost ¬\phi$.
+To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\prop \in \allprops$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop$.
 The $i$-decidable propositions are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
-The next property ensures an unambiguous interpretation of the content of $\iPhi$ for all $i$-decidable propositions.
-In this definition, $\oplus$ denotes the exclusive disjunction; thus $\phi \in \iPhi \oplus ¬\phi \in \iPhi$ is equivalent to: $\phi \in \iPhi ⇔ ¬\phi \notin \iPhi$.
+The next property ensures an unambiguous interpretation of the content of $\iprops$ for all $i$-decidable propositions.
+In this definition, $\oplus$ denotes the exclusive disjunction; thus $\prop \in \iprops \oplus ¬\prop \in \iprops$ is equivalent to: $\prop \in \iprops ⇔ ¬\prop \notin \iprops$.
 It can be seen to hold by using \cref{th:normeqsnorm}.
@@
 	\label{def:restrinterpr}
-	$\forall i \in I, \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstost \phi \lor \ar \ileadstost ¬\phi] ⇒ [\phi \in \iPhi \oplus ¬\phi \in \iPhi]$.
+	$\forall i \in I, \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop] ⇒ [\prop \in \iprops \oplus ¬\prop \in \iprops]$.
 \end{property}
@@
 \begin{definition}[Theory completeness]
-	$\forall \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] \lor [\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi]$.
+	$\forall \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] \lor [\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\prop]$.
 \end{definition}
 \begin{definition}[Unrestricted interpretability]
-	$\forall \phi \in \Phi: \phi \in \iPhi \oplus ¬\phi \in \iPhi$.
+	$\forall \prop \in \allprops: \prop \in \iprops \oplus ¬\prop \in \iprops$.
 \end{definition}
 \begin{definition}[Deliberation completeness]
-	$\forall \phi \in \Phi: \phi \in \iPhi \lor ¬\phi \in \iPhi$.
+	$\forall \prop \in \allprops: \prop \in \iprops \lor ¬\prop \in \iprops$.
 \end{definition}
@@
 An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ relates some arguments to some propositions.
-Its role in an empirical theory is to define the propositions that the empirical theory supports (corresponding to $\gPhie$, the range of ${\gleadsto}$) and, for each such proposition, to define the arguments that the theory wants to use as initial arguments to argue in favor of this proposition.
-The set of initial arguments is $\gleadstoinv(\Phi) = \set{\ar \in \allargs \suchthat \exists \phi \in \Phi \suchthat \ar \gleadsto \phi}$.
+Its role in an empirical theory is to define the propositions that the empirical theory supports (corresponding to $\gpropse$, the range of ${\gleadsto}$) and, for each such proposition, to define the arguments that the theory wants to use as initial arguments to argue in favor of this proposition.
+The set of initial arguments is $\gleadstoinv(\allprops) = \set{\ar \in \allargs \suchthat \exists \prop \in \allprops \suchthat \ar \gleadsto \prop}$.
 
@@
 An empirical theory must satisfy
-$\exists k \in \N \suchthat (\dfp)^k(\gleadstoinv(\Phi)) = \emptyset$.
+$\exists k \in \N \suchthat (\dfp)^k(\gleadstoinv(\allprops)) = \emptyset$.
 This does not imply that the relations $\gbeats$ or $\dbeats$ should be finite, however.
@@
 \begin{proof}
-	Consider an agenda containing two propositions, $\allprops = \set{\phi, ¬\phi}$, an infinite set of arguments $\allargs = \set{\ar_k \suchthat k \in \N}$ with $\forall j, k \in \N: \ar_j ≠ \ar_k$, and consider any set of individuals $I$ and observation protocol $\allleadsto$.
+	Consider an agenda containing two propositions, $\allprops = \set{\prop, ¬\prop}$, an infinite set of arguments $\allargs = \set{\ar_k \suchthat k \in \N}$ with $\forall j, k \in \N: \ar_j ≠ \ar_k$, and consider any set of individuals $I$ and observation protocol $\allleadsto$.
 	Define $2\N^* = \set{k \suchthat k / 2 \in \N^*}$ as the set of non-zero even integers.
-	Define ${\gleadsto} = \set{(\ar_0, \phi)}$.
+	Define ${\gleadsto} = \set{(\ar_0, \prop)}$.
 	Define ${\gbeats} = \set{(\ar_{k - 1}, \ar_0) \suchthat k \in 2\N^*}$ so that all odd numbered arguments are planned attacks against $\ar_0$. 
@@
 	Consider an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ for the normative theory $(\allprops, ¬, \allargs, I, {\allleadsto})$.
-That this is indeed a legal empirical theory can be confirmed by checking that all constraints are satisfied, in particular, $(\dfp)^2(\gleadstoinv(\Phi)) = \dfp(\dfp(\ar_0)) = \dfp(\set{\ar_k \suchthat k \in 2\N^*}) = \emptyset$ because there is no planned attack against any argument in $\set{\ar_k \suchthat k \in 2\N^*}$.
+That this is indeed a legal empirical theory can be confirmed by checking that all constraints are satisfied, in particular, $(\dfp)^2(\gleadstoinv(\allprops)) = \dfp(\dfp(\ar_0)) = \dfp(\set{\ar_k \suchthat k \in 2\N^*}) = \emptyset$ because there is no planned attack against any argument in $\set{\ar_k \suchthat k \in 2\N^*}$.
 This theory involves infinite relations $\gbeats$ and $\dbeats$.
@@
 
-Given $i \in I, \phi \in \Phi, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \phi$.
-Such a set $\args$, when not empty, represents an effective set of planned attackers of $\ar$ against $\phi$. 
-The notation uses a striked through $\phi$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues against $\phi$, from the point of view of $i$.
-I write that $\ar$ \emph{$i$-defends} $\phi$ to mean that $\emptyset \nibeats \ar$.
-
-Given $i \in I, \phi \in \gPhie, \ar \in \allargs$, define $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
-It represents the coalitions of fragments defending $\ar$ (when arguing for $\phi$), from the point of view of $i$, against its effective planned attackers.
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \prop$.
+Such a set $\args$, when not empty, represents an effective set of planned attackers of $\ar$ against $\prop$. 
+The notation uses a striked through $\prop$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues against $\prop$, from the point of view of $i$.
+I write that $\ar$ \emph{$i$-defends} $\prop$ to mean that $\emptyset \nibeats \ar$.
+
+Given $i \in I, \prop \in \gpropse, \ar \in \allargs$, define $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
+It represents the coalitions of fragments defending $\ar$ (when arguing for $\prop$), from the point of view of $i$, against its effective planned attackers.
 The following proposition shows that these coalitions can be added to $\ar$, and will be useful for other results.
@@
 	\label{th:indf}
-	$\forall i \in I, \phi \in \gPhie, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
+	$\forall i \in I, \prop \in \gpropse, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
 \end{proposition}
@@
 
-Given $\ar \in \allargs$, define $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\phi$.
-Given $i \in I, \phi \in \gPhie$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.
+Given $\ar \in \allargs$, define $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\prop$.
+Given $i \in I, \prop \in \gpropse$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\prop)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\prop))$.
 
 \begin{definition}[Convincingness]
-	An empirical theory is \emph{convincing} iff $\forall i \in I, \phi \in \gPhie, \ar \in \gargs: \ar$ $i$-defends $\phi$.
+	An empirical theory is \emph{convincing} iff $\forall i \in I, \prop \in \gpropse, \ar \in \gargs: \ar$ $i$-defends $\prop$.
 \end{definition}
 
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist, \ar) \in I × \gPhie × \allhist × \gargs$ such that $\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \phi$.
-I also write that $(i, \phi, \hist, \ar)$ falsifies $\gamma$ to mean that it is a falsification instance of $\gamma$.
+A \emph{falsification instance} of an empirical theory is a tuple $(i, \prop, \hist, \ar) \in I × \gpropse × \allhist × \gargs$ such that $\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \prop$.
+I also write that $(i, \prop, \hist, \ar)$ falsifies $\gamma$ to mean that it is a falsification instance of $\gamma$.
 
@@
 \begin{proof}
-	For all $i \in I, \phi \in \gPhie, \ar \in \gargs$: $\ar$ does not $i$-defend $\phi$ iff $\exists \hist \in \allhist \suchthat \left[\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist, \ar)$ falsifies $\gamma$.
-Therefore, $\gamma$ is not convincing iff $\exists (i, \phi, \ar) \suchthat \ar$ does not $i$-defend $\phi$ iff $\exists \hist \suchthat (i, \phi, \hist, \ar)$ falsifies $\gamma$ iff $\gamma$ has a falsification instance.
+	For all $i \in I, \prop \in \gpropse, \ar \in \gargs$: $\ar$ does not $i$-defend $\prop$ iff $\exists \hist \in \allhist \suchthat \left[\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \prop\right]$ iff $\exists \hist \in \allhist$ such that $(i, \prop, \hist, \ar)$ falsifies $\gamma$.
+Therefore, $\gamma$ is not convincing iff $\exists (i, \prop, \ar) \suchthat \ar$ does not $i$-defend $\prop$ iff $\exists \hist \suchthat (i, \prop, \hist, \ar)$ falsifies $\gamma$ iff $\gamma$ has a falsification instance.
 \end{proof}
@@
 \begin{definition}[Validity]
-	An empirical theory is \emph{valid} iff $\forall i \in I, \phi \in \gPhie: [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
+	An empirical theory is \emph{valid} iff $\forall i \in I, \prop \in \gpropse: [\prop \in \iprops \land ¬\prop \notin \iprops]$.
 \end{definition}
@@
 	\label{th:produce}
-	Given $\phi \in \gPhie$, $\ar_0 \in \gargs$ that $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$.
+	Given $\prop \in \gpropse$, $\ar_0 \in \gargs$ that $i$-defends $\prop$, and $\hist \nileadstost \prop$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$.
 Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
@@
 	By definition of $\ibeats$, $\args \ibeats \ar_0$.
-	Also, because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
+	Also, because $\ar_0$ $i$-defends $\prop$, $\args ≠ \emptyset$. 
 	Therefore, $\dargs \in \di(\ar_0)$.
@@
 \begin{proof}
-	Given any $i \in I$ and $\phi \in \gPhie$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$; the conclusion then follows thanks to simple normative adequacy (that \cref{th:normeqsnorm} shows to be equivalent to normative adequacy).
-
-	Lemma: $[\ar_0 \in \gargs \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$.
-That is because $\ar_0 \in \gargs$ implies that $\ar_0$ $i$-defends $\phi$, by convincingness, and,
-	by definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$; \cref{th:produce} thus applies.
-
-	To prove the theorem, build a finite sequence of arguments in $\gargs$, starting with any $\ar_0 \in \gleadstoinv(\phi)$.
+	Given any $i \in I$ and $\prop \in \gpropse$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \prop$; the conclusion then follows thanks to simple normative adequacy (that \cref{th:normeqsnorm} shows to be equivalent to normative adequacy).
+
+	Lemma: $[\ar_0 \in \gargs \land \ar_0 \nileadstost \prop] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$.
+That is because $\ar_0 \in \gargs$ implies that $\ar_0$ $i$-defends $\prop$, by convincingness, and,
+	by definition, $\ar_0 \nileadstost \prop$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \prop$; \cref{th:produce} thus applies.
+
+	To prove the theorem, build a finite sequence of arguments in $\gargs$, starting with any $\ar_0 \in \gleadstoinv(\prop)$.
 Observe that $\ar_0 \in \gargs$.
-Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the above lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$.
-Continue applying the lemma and producing further arguments as long as $\ar_k \nileadstost \phi$.
-	By definition of an empirical theory, $\exists k \in \N \suchthat (\dfp)^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
+Given $k \in 2\N$, if $\ar_k \nileadstost \prop$, define $\ar_{k + 2}$ using the above lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$.
+Continue applying the lemma and producing further arguments as long as $\ar_k \nileadstost \prop$.
+	By definition of an empirical theory, $\exists k \in \N \suchthat (\dfp)^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \prop$.
 \end{proof}
@@
 \subsection{Effectively comparing models}
-Given $\phi \in \Phi$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\phi$ iff $\phi \in \gPhie[\gamma] \land ¬\phi \in \gPhie[\delta]$.
-Say that they are incompatible iff there is at least one $\phi \in \Phi$ that they disagree about.
-
-Given $\phi \in \Phi$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $\phi$ iff $\hist \nileadstost \phi$ and $\ar_\gamma \in \histend$.
-Given $\phi \in \Phi, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\phi/¬\phi$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \phi)$ or $(\hist, \ar_\delta)$ challenges $(\delta, ¬\phi)$.
+Given $\prop \in \allprops$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\prop$ iff $\prop \in \gpropse[\gamma] \land ¬\prop \in \gpropse[\delta]$.
+Say that they are incompatible iff there is at least one $\prop \in \allprops$ that they disagree about.
+
+Given $\prop \in \allprops$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $\prop$ iff $\hist \nileadstost \prop$ and $\ar_\gamma \in \histend$.
+Given $\prop \in \allprops, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/¬\prop$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \prop)$ or $(\hist, \ar_\delta)$ challenges $(\delta, ¬\prop)$.
 
@@
 	\label{th:endchal}
-	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$, $(\hist, \ar_\gamma, \ar_\delta)$ is a $\phi/¬\phi$-challenge.
+	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$, $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/¬\prop$-challenge.
 \end{lemma}
 \begin{proof}
-	Either $\hist \nileadstost \phi$, and $(\hist, \ar_\gamma)$ challenges $\phi$, or $\hist \ileadstost \phi$, hence, by \cref{th:protcoh}, $\hist \nileadstost ¬\phi$, and $(\hist, \ar_\delta)$ challenges $¬\phi$.
+	Either $\hist \nileadstost \prop$, and $(\hist, \ar_\gamma)$ challenges $\prop$, or $\hist \ileadstost \prop$, hence, by \cref{th:protcoh}, $\hist \nileadstost ¬\prop$, and $(\hist, \ar_\delta)$ challenges $¬\prop$.
 \end{proof}
@@
 	\label{th:nextchal}
-	Given $(\hist, \ar_\gamma)$ challenging $\phi$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\phi))$, and $\ar_\delta \in \gargsdelta$: either $(i, \phi, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $\phi/¬\phi$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\phi))$.
+	Given $(\hist, \ar_\gamma)$ challenging $\prop$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\prop))$, and $\ar_\delta \in \gargsdelta$: either $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $\prop/¬\prop$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\prop))$.
 \end{lemma}
 \begin{proof}
-	If $\ar_\gamma$ does not $i$-defend $\phi$, then $(i, \phi, \hist, \ar_\gamma)$ falsifies $\gamma$, which ends the proof. 
-	Thus, assume that $\ar_\gamma$ $i$-defends $\phi$.
-
-	\Cref{th:produce} applies and yields $\ar'_\gamma = \ar_\gamma + \dbeatsinv(\gbeatsinv(\ar_\gamma)) \in \gargs \cap \dfp(\ar_\gamma)$, thus $\ar'_\gamma \in (\dfp)^{(k + 1)}(\gleadstoinv(\phi))$. 
-	Now, define $\histpp = (\hist, \ar'_\gamma)$ and test whether $\histpp \nileadstost \phi$.
-
-	If $\histpp \nileadstost \phi$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\gamma, \ar_\delta)$ challenges $\phi$, which concludes the proof. 
-	Thus, assume that $\histpp \ileadstost \phi$.
+	If $\ar_\gamma$ does not $i$-defend $\prop$, then $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, which ends the proof. 
+	Thus, assume that $\ar_\gamma$ $i$-defends $\prop$.
+
+	\Cref{th:produce} applies and yields $\ar'_\gamma = \ar_\gamma + \dbeatsinv(\gbeatsinv(\ar_\gamma)) \in \gargs \cap \dfp(\ar_\gamma)$, thus $\ar'_\gamma \in (\dfp)^{(k + 1)}(\gleadstoinv(\prop))$. 
+	Now, define $\histpp = (\hist, \ar'_\gamma)$ and test whether $\histpp \nileadstost \prop$.
+
+	If $\histpp \nileadstost \prop$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\gamma, \ar_\delta)$ challenges $\prop$, which concludes the proof. 
+	Thus, assume that $\histpp \ileadstost \prop$.
 
@@
 
-	If $\ar_\delta \in \histppend$, this is done by defining $\histp = \histpp$. Otherwise, define $\histp = (\histpp, \ar_\delta)$ and test whether $\histp \nileadstost \phi$. 
+	If $\ar_\delta \in \histppend$, this is done by defining $\histp = \histpp$. Otherwise, define $\histp = (\histpp, \ar_\delta)$ and test whether $\histp \nileadstost \prop$. 
 \end{proof}
@@
 \commentOC{Need the test procedure to be a tree.
-Atom: $(k, \phi)$ meaning whether ${\hist}^k \ileadstost \phi$.
+Atom: $(k, \prop)$ meaning whether ${\hist}^k \ileadstost \prop$.
 Branch label: atoms linked using or and and operators.
-From a node $n = (\hist, \ar, \phi)$, let branches depart, such that their labels do not overlap.
+From a node $n = (\hist, \ar, \prop)$, let branches depart, such that their labels do not overlap.
 From a node, if no branch label is true, the node must falsify a theory.
@@
 \begin{procedure}
-	Pick any $\phi \in \Phi$ about which $\alpha$ and $\beta$ disagree.
+	Pick any $\prop \in \allprops$ about which $\alpha$ and $\beta$ disagree.
 
@@
 	$(\hist, \ar_\alpha, \ar_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta)$ iff 
-	$(\hist, \ar_\alpha, \ar_\beta)$ is a $\phi/¬\phi$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\phi))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](¬\phi))$.
-
-	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\beta] ¬\phi$.
-Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](¬\phi))$.
-Test whether $(\ar_{-1}) \nileadstost \phi$.
-If so, $(i, \phi, (\ar_{-1}), \ar_{-1})$ falsifies $\beta$, which ends the procedure.
-	Thus, assume that $(\ar_{-1}) \ileadstost \phi$.
-
-	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[\alpha] \phi$.
-Observe that $\ar_0 \in \gargsalpha \cap (\dfp[\alpha])^0(\gleadstoinv[\alpha](\phi))$.
-Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \phi$.
-By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\phi/¬\phi$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
+	$(\hist, \ar_\alpha, \ar_\beta)$ is a $\prop/¬\prop$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\prop))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](¬\prop))$.
+
+	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\beta] ¬\prop$.
+Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](¬\prop))$.
+Test whether $(\ar_{-1}) \nileadstost \prop$.
+If so, $(i, \prop, (\ar_{-1}), \ar_{-1})$ falsifies $\beta$, which ends the procedure.
+	Thus, assume that $(\ar_{-1}) \ileadstost \prop$.
+
+	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[\alpha] \prop$.
+Observe that $\ar_0 \in \gargsalpha \cap (\dfp[\alpha])^0(\gleadstoinv[\alpha](\prop))$.
+Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \prop$.
+By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\prop/¬\prop$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
 
@@
 This is because, given a challenge $(\hist, \ar_\alpha, \ar_\beta)$ of complexity $(k_\alpha, k_\beta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity.
-Indeed, if $(\hist, \ar_\alpha)$ challenges $\phi$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
-And if $(\hist, \ar_\beta)$ challenges $¬\phi$, apply \cref{th:nextchal} with $¬\phi$ for $\phi$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.
-
-	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\phi)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](¬\phi)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
+Indeed, if $(\hist, \ar_\alpha)$ challenges $\prop$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
+And if $(\hist, \ar_\beta)$ challenges $¬\prop$, apply \cref{th:nextchal} with $¬\prop$ for $\prop$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.
+
+	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\prop)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](¬\prop)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
 \end{procedure}
@@
 
-Define $\Phi_\allalts = \set{\phi_{B, \choices} \suchthat \emptyset ≠ B \subseteq \allalts, \choices \subseteq \powersetz{B}}$.
+Define $\allprops_\allalts = \set{\prop_{B, \choices} \suchthat \emptyset ≠ B \subseteq \allalts, \choices \subseteq \powersetz{B}}$.
 
@@
 Define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses after exposure to $\hist$.
-Define $\hist \ileadsto \phi_{B, \choices}$ iff $c^\hist_i(B) \in \choices$.
+Define $\hist \ileadsto \prop_{B, \choices}$ iff $c^\hist_i(B) \in \choices$.
 
@@
 Any empirical theory for a normative theory about $\allalts$ that satisfies $\forall \emptyset ≠ B \subseteq \allalts: \exists !
-\emptyset ≠ \choices \subseteq \powersetz{B} \suchthat \phi_{B, \choices} \in \gPhie$ is said to be an empirical theory about $\allalts$.
+\emptyset ≠ \choices \subseteq \powersetz{B} \suchthat \prop_{B, \choices} \in \gpropse$ is said to be an empirical theory about $\allalts$.
 The notation $\exists!$ means: there exists a unique element.
-The requirement that there is at least one is innocuous, as choosing $\choices = \powersetz{B}$ ensures that $\phi_{B, \choices} \in \iPhi$, by definition of $\ileadsto$.
+The requirement that there is at least one is innocuous, as choosing $\choices = \powersetz{B}$ ensures that $\prop_{B, \choices} \in \iprops$, by definition of $\ileadsto$.
 
 An empirical theory about $\allalts$ thus associates to each possible bundle $B$ a set of possible choices $\choices$, whose semantics is that the theory claims that the deliberated choice of $i$, given the bundle $B$, lies among $\choices$.
-Let $\gPhi(B) \subseteq \powersetz{B}$ denote this set of possible choices, thus $\gPhi(B) = \choices  ⇔ \phi_{B, \choices} \in \gPhie$.
-
-Given an empirical theory about $\allalts$ and $a, b \in \allalts$, define $a \gpst b$ iff $\forall \set{a, b} \subseteq B: b \notin \bigcup \gPhi(B)$.
+Let $\gprops(B) \subseteq \powersetz{B}$ denote this set of possible choices, thus $\gprops(B) = \choices  ⇔ \prop_{B, \choices} \in \gpropse$.
+
+Given an empirical theory about $\allalts$ and $a, b \in \allalts$, define $a \gpst b$ iff $\forall \set{a, b} \subseteq B: b \notin \bigcup \gprops(B)$.
 Thus, $a \gpst b$ iff $\gamma$ claims that $b$ is not deliberately chosen in presence of $a$.
@@
 Given $i \in I$ and a bundle $B$, say that a subset $B' \subseteq B$ is a deliberated restricted choice set for $i$ given $B$ iff 
-$\exists \phi_{B, \choices} \in \iPhi \suchthat \forall C \in \choices: C \cap B' ≠ \emptyset$.
+$\exists \prop_{B, \choices} \in \iprops \suchthat \forall C \in \choices: C \cap B' ≠ \emptyset$.
 Restricting consideration to deliberated restricted choice sets respects $i$’s \ac{DJ} in the sense that it necessarily includes at least one alternative that is a deliberated choice of $i$.
@@
 	$\gpeq$ is reflexive because $\gind$ is.
-	That $\gpst$ is asymmetric is seen by considering, given any $a, b \in \allalts$, the bundle $B = \set{a, b}$: pick any $C \in \gPhi(B) \subseteq \powersetz{B}$, thus, $C \in \powersetz{B}$, hence, $a \in C$ or $b \in C$, and therefore, $b \ngpst a$ or $a \ngpst b$.
+	That $\gpst$ is asymmetric is seen by considering, given any $a, b \in \allalts$, the bundle $B = \set{a, b}$: pick any $C \in \gprops(B) \subseteq \powersetz{B}$, thus, $C \in \powersetz{B}$, hence, $a \in C$ or $b \in C$, and therefore, $b \ngpst a$ or $a \ngpst b$.
 
@@
 	Given any bundle $B \in \powersetz[\mathit{F}]{\allalts}$, we now have to show that $B' = r(B)$ satisfies 
-	$\exists \phi_{B, \choices} \in \iPhi \suchthat \forall C \in \choices: C \cap B' ≠ \emptyset$.
-%	$[\forall a \in B \setminus B': \phi_{B, ¬a} \in \iPhi] \lor [\exists a \in B' \suchthat \phi_{B, a} \in \iPhi]$. 
-	Because $\gamma$ is valid, suffices to show that, given $\choices = \gPhi(B) \subseteq \powersetz{B}$, 
+	$\exists \prop_{B, \choices} \in \iprops \suchthat \forall C \in \choices: C \cap B' ≠ \emptyset$.
+%	$[\forall a \in B \setminus B': \prop_{B, ¬a} \in \iprops] \lor [\exists a \in B' \suchthat \prop_{B, a} \in \iprops]$. 
+	Because $\gamma$ is valid, suffices to show that, given $\choices = \gprops(B) \subseteq \powersetz{B}$, 
 	$\forall C \in \choices: C \cap B' ≠ \emptyset$.
-%	$[\forall a \in B \setminus B': \phi_{B, ¬a} \in \gPhie] \lor [\exists a \in B' \suchthat \phi_{B, a} \in \gPhie]$.
+%	$[\forall a \in B \setminus B': \prop_{B, ¬a} \in \gpropse] \lor [\exists a \in B' \suchthat \prop_{B, a} \in \gpropse]$.
 	Pick any $C \in \choices$ and any $a \in C$ (thus, $a \in B$). By definition of $\gpst$, $\nexists b \in B \suchthat b \gpst a$ as otherwise, $a \notin C$.
@@
 	Consider any $a, b, c \in \allalts$ with $a \gpeq b \gpeq c$ and let us show that $a \gpeq c$.
-	Consider the bundle $B = \set{a, b, c}$ and let $\choices = \gPhi(B)$.
+	Consider the bundle $B = \set{a, b, c}$ and let $\choices = \gprops(B)$.
 
@@
 In what follows, the claims of an empirical theory about $\allalts$ will be defined on the basis of a transitive preference ordering $\peq$ on $\allalts$, as follows.
-Given $\emptyset ≠ B \subseteq \allalts$, define $\gPhi(B) = \set{\cup \choices' \suchthat \emptyset ≠ \choices' \subseteq \choices}$, where $\choices$ are the undominated equivalence classes in $B$ according to $\peq$ (thus $\choices = \max_{\pst^*}(B / {\ind})$, using the notations defined in \cref{th:dp}).
+Given $\emptyset ≠ B \subseteq \allalts$, define $\gprops(B) = \set{\cup \choices' \suchthat \emptyset ≠ \choices' \subseteq \choices}$, where $\choices$ are the undominated equivalence classes in $B$ according to $\peq$ (thus $\choices = \max_{\pst^*}(B / {\ind})$, using the notations defined in \cref{th:dp}).
 The check that ${\peq} = {\gpeq}$ is left to the reader.
@@
 Note that $\peq$ is complete and contains at most two equivalence classes: $A$, and $\allalts \setminus A$.
-This defines the set of claims that $\gamma$ supports, namely, for any $\emptyset ≠ B \subseteq \allalts$, $\gPhi(B) = B \cap A$.
+This defines the set of claims that $\gamma$ supports, namely, for any $\emptyset ≠ B \subseteq \allalts$, $\gprops(B) = B \cap A$.
 
@@
 %Given $a \in A, b \in \allalts \setminus A$, define $\ar_{a > b}$ as the text: “$a$ has performance $c_1(a)$ on criterion $c_1$, and it is reasonable to consider that having at least $t_{c_1}$ is satisfying enough from the point of view captured by $c_1$, [… same phrase for the other criteria…], therefore, it is a fully satisfactory alternative; whereas $b$ is not satisfactory on criteria [… enumeration of the criteria such that $c(b) < t_{c}$].”
-Define ${\gleadsto} = \set{(\ar_B, \gPhi(B)) \suchthat \emptyset ≠ B \subseteq \allalts}$.
+Define ${\gleadsto} = \set{(\ar_B, \gprops(B)) \suchthat \emptyset ≠ B \subseteq \allalts}$.
 Define $\alldargs = {\gbeats} = {\dbeats} = {+} = \emptyset$: the theory does not consider any counter-argument as potentially damaging. 
@@
 
-Define $\allprops = \set{\phi, ¬\phi}$, $\phi$ representing intuitively the case that $i$ deliberately prefers $P$ to $D$, in the sense of bidding at least as much for $P$ than for $D$ after deliberation, and $¬\phi$, the opposite.
+Define $\allprops = \set{\prop, ¬\prop}$, $\prop$ representing intuitively the case that $i$ deliberately prefers $P$ to $D$, in the sense of bidding at least as much for $P$ than for $D$ after deliberation, and $¬\prop$, the opposite.
 
 Define $\ileadstost$ as follows.
-Given $\hist = (…, \ar)$, $\hist \ileadstost \phi$ iff, in a situation of $i$ having been exposed to these arguments, saying: “Considering these arguments, would you please indicate your maximum selling price for $P$, and for $D$” leads $i$ to bid at least as much for $P$ than for $D$.
-$\hist \ileadstost ¬\phi$ is defined similarly.
-%Note that $\hist \ileadstost \phi$ iff $\hist \nileadstost ¬\phi$.
+Given $\hist = (…, \ar)$, $\hist \ileadstost \prop$ iff, in a situation of $i$ having been exposed to these arguments, saying: “Considering these arguments, would you please indicate your maximum selling price for $P$, and for $D$” leads $i$ to bid at least as much for $P$ than for $D$.
+$\hist \ileadstost ¬\prop$ is defined similarly.
+%Note that $\hist \ileadstost \prop$ iff $\hist \nileadstost ¬\prop$.
 
@@
 
-Discuss variant with an empirical claim: $\hist \ileadsto \phi ⇒ \hist \nileadsto ¬\phi$; and change \cref{ax:norm}: $[\forall \hist, \hist \ileadsto \propposs] ⇒ \propposs \in \iPhi$, … This is essentially what will be done in the following, I suppose.
-
-If we do not have $\propsure$ implies $\propposs$, then we can have $\propsure$ and $\notpropsure$ both accepted.
-But all propositions of the normative analysis would still hold, it seems.
-We could have a property that says: $\propsure \in \iPhi ⇒ \propposs \in \iPhi \land \notpropsure \notin \iPhi \land \notpropposs \notin \iPhi$.
-
 Show that if the claim of the model is of a different form, then the model is not falsifiable, as suggested here below for some form of claims.
@@
 
-General theory says that $\ar_1$ is replaceable (suspects that it’s good for some people): $(\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ (\ar'_1, \ar_0) \ileadstoe ¬\phi$.
+General theory says that $\ar_1$ is replaceable (suspects that it’s good for some people): $(\ar_1, \ar_0) \ileadstoe ¬\prop ⇒ (\ar'_1, \ar_0) \ileadstoe ¬\prop$.
 (This will fail if some $i$ thinks $\ar'_1$ is bad arg because of $\ar_0$ but $\ar_1$ is bad because of $\ar_2$.) It may say that $\ar_1$ is bad.
-General theory prepares potentially good arg $\ar_0$ and claims that if $\ar_0 \ileadstoe \phi$, then $\ar_0 \ileadstost \phi$ (this is Answerability).
+General theory prepares potentially good arg $\ar_0$ and claims that if $\ar_0 \ileadstoe \prop$, then $\ar_0 \ileadstost \prop$ (this is Answerability).
 So that the model only has to prove the weaker existential claim.
@@
 It is important to remark that when the query protocol does not admit observation of “both”, thus, when $\ileadstost$ does not distinguish sure from possible, it does \emph{not} follow that $i$ is sure of either $\prop$ or $¬\prop$ for every pair of proposition: the “undecided” case will hold whenever $i$ considers no argument as sufficiently strong to determine a decisive preference (assuming that in that case, $i$ at least sometimes alternates his choice).
-Admittedly, it might also happen that $i$ is really indifferent between $\prop$ and $¬\prop$ but still systematically chooses, say, $\prop$ over $¬\prop$, in which case it will be (somewhat) erroneously concluded that $\prop \in \iPhi$.
+Admittedly, it might also happen that $i$ is really indifferent between $\prop$ and $¬\prop$ but still systematically chooses, say, $\prop$ over $¬\prop$, in which case it will be (somewhat) erroneously concluded that $\prop \in \iprops$.
 This is the price to pay for using protocols that do not allow to observe indifference.
@@
 by Strong op.
-val.: $\forall \phi \in \gPhie, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
+val.: $\forall \prop \in \gpropse, \ar_0 \in \gargs[\prop], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\prop ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
 
@@
 \subsection{Transitive, complete preference theories}
+\NewDocumentCommand{\ppeqab}{}{t_{a \succeq b}}
+\NewDocumentCommand{\ppst}{O{a}O{b}}{t_{#1 \succ #2}}
+\NewDocumentCommand{\ppstsure}{O{a}O{b}}{(t_{#1 \succ #2}, \mathit{sure})}
+\NewDocumentCommand{\ppstbc}{}{t_{b \succ c}}
+\NewDocumentCommand{\ppstac}{}{t_{a \succ c}}
+\NewDocumentCommand{\ppstba}{}{t_{b \succ a}}
+\NewDocumentCommand{\ppeq}{O{a}O{b}}{t_{#1 \succeq #2}}
+\NewDocumentCommand{\ppeqsure}{O{a}O{b}}{(t_{#1 \succeq #2}, \mathit{sure})}
+\NewDocumentCommand{\domc}{}{\mathscr{B}}
+
 Given a set of alternatives $\allalts$.
@@
 Define $¬_\allalts$ such that $\forall a, b \in \allalts: ¬_\allalts\ppst = \ppstba, ¬_\allalts\ppstba = \ppst$.
-Define $\Phi_\allalts = \props_\allalts × \set{\mathit{sure}, \mathit{poss}}$.
+Define $\allprops_\allalts = T_\allalts × \set{\mathit{sure}, \mathit{poss}}$.
 
@@
 Given $i \in I$, define $\ileadstost$ as follows. 
-Given $\hist \in \allhist$ and $\phi \in \Phi_\allalts$, with $\phi \in \set{\ppst} × \set{\mathit{sure}, \mathit{poss}}$ for some $a ≠ b \in \allalts$, the individual is presented the arguments in $\hist$, and has then to choose a product from the set $\set{a, b}$.
-Define $\hist \ileadstost \phi$ iff $i$ chooses $a$.
-\commentOC{This is inadequate: if $i$ picks $b$ from $\set{a, b, c}$, the current definition considers it compatible with $\ppstsure \in \iPhi$, thus, $\ppst$ does not have a meaningful content.
+Given $\hist \in \allhist$ and $\prop \in \allprops_\allalts$, with $\prop \in \set{\ppst} × \set{\mathit{sure}, \mathit{poss}}$ for some $a ≠ b \in \allalts$, the individual is presented the arguments in $\hist$, and has then to choose a product from the set $\set{a, b}$.
+Define $\hist \ileadstost \prop$ iff $i$ chooses $a$.
+\commentOC{This is inadequate: if $i$ picks $b$ from $\set{a, b, c}$, the current definition considers it compatible with $\ppstsure \in \iprops$, thus, $\ppst$ does not have a meaningful content.
 Should rather define $\ppstsure$ so that $a$ is picked rather than $b$ whatever the choice set.
@@
 
-Given a normative theory about $\allalts$, an individual $i \in I$, a set $\domc \subseteq \powersetz{\allalts}$ and a choice function $c$, say that $c$ represents a \emph{deliberated choice function} for $i$ iff $\forall B \in \domc: c(B) \subseteq \set{a \in B \suchthat \forall b \in B: \ppstsure[b][a] \notin \iPhi}$.
+Given a normative theory about $\allalts$, an individual $i \in I$, a set $\domc \subseteq \powersetz{\allalts}$ and a choice function $c$, say that $c$ represents a \emph{deliberated choice function} for $i$ iff $\forall B \in \domc: c(B) \subseteq \set{a \in B \suchthat \forall b \in B: \ppstsure[b][a] \notin \iprops}$.
 
@@
 
-A set of propositions $P \subseteq \Phi_\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: \ppstsure \in P \land \ppstsure[b][c] \in P ⇒ \ppstsure[a][c] \in P$.
-
-A transitive empirical preference theory about $\allalts$ is an empirical theory for a normative theory about $\allalts$ such that $\gPhie$ is transitive.
-
-Associate to such a theory a preference ordering $\succ$ on $\allalts$ as follows: $a \succ b$ iff $\ppstsure \in \gPhie$.
+A set of propositions $P \subseteq \allprops_\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: \ppstsure \in P \land \ppstsure[b][c] \in P ⇒ \ppstsure[a][c] \in P$.
+
+A transitive empirical preference theory about $\allalts$ is an empirical theory for a normative theory about $\allalts$ such that $\gpropse$ is transitive.
+
+Associate to such a theory a preference ordering $\succ$ on $\allalts$ as follows: $a \succ b$ iff $\ppstsure \in \gpropse$.
 
@@
 }
-\NewDocumentCommand{\mPhi}{}{\Phi_\gamma}
+\NewDocumentCommand{\mPhi}{}{\allprops_\gamma}
 \NewDocumentCommand{\argsd}{}{S^\mathit{d}}
@@
 
-Define $\Phi = \allprops × \set{\text{possible}, \text{sure}}$. Elements in $\Phi$ will also be called propositions, which should create no ambiguity. 
-The relation $\ileadstoall \subseteq (\allargs × \allargs) × \Phi$, pronounced “always leads to”, has the following semantics.
+Define $\allprops = \allprops × \set{\text{possible}, \text{sure}}$. Elements in $\allprops$ will also be called propositions, which should create no ambiguity. 
+The relation $\ileadstoall \subseteq (\allargs × \allargs) × \allprops$, pronounced “always leads to”, has the following semantics.
 Whenever $(\ar, \ar') \ileadstoall (\prop, \text{sure})$, $i$ always considers that $\prop$ is sure (meaning that $¬\prop$ is excluded), when presented with these two arguments, and whenever $(\ar, \ar') \ileadstoall (\prop, \text{possible})$, $i$ always considers that $\prop$ is “at least” possible (meaning that $¬\prop$ may be possible as well), when presented with these two arguments.
@@
 
-Define the negation operator $¬$ over $\Phi$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
-It follows that $¬¬\phi = \phi$.
-Write $(\ar, \ar') \nileadstoall \phi$ for $¬[(\ar, \ar') \ileadstoall \phi]$ and define $(\ar, \ar') \ileadstoe \phi$ as equivalent to $(\ar, \ar') \nileadstoall ¬\phi$.
+Define the negation operator $¬$ over $\allprops$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
+It follows that $¬¬\prop = \prop$.
+Write $(\ar, \ar') \nileadstoall \prop$ for $¬[(\ar, \ar') \ileadstoall \prop]$ and define $(\ar, \ar') \ileadstoe \prop$ as equivalent to $(\ar, \ar') \nileadstoall ¬\prop$.
 The relation $\ileadstoe$ is pronounced “sometimes leads to”.
-A proposition $\phi$ is about $\prop$ iff $\phi \in \{\prop, ¬\prop\} × \{\text{possible}, \text{sure}\}$.
+A proposition $\prop$ is about $\prop$ iff $\prop \in \{\prop, ¬\prop\} × \{\text{possible}, \text{sure}\}$.
 
@@
 \begin{definition}[Decision situation]
-	A decision situation is a topic $\allprops$ closed under negation, a set of arguments $\allargs$, an “always leads to” relation $\ileadstoall \subseteq (\allargs × \allargs) × \Phi$ satisfying (A1) and (A2) and using unordered pairs of arguments, $\Phi$ being the set of propositions $\allprops × \set{\text{sure}, \text{possible}}$.
+	A decision situation is a topic $\allprops$ closed under negation, a set of arguments $\allargs$, an “always leads to” relation $\ileadstoall \subseteq (\allargs × \allargs) × \allprops$ satisfying (A1) and (A2) and using unordered pairs of arguments, $\allprops$ being the set of propositions $\allprops × \set{\text{sure}, \text{possible}}$.
 \end{definition}
@@
 We say in this case that $\ileadstoall$ does not distinguish sure from possible.
-Thus, elements $\phi \in \Phi$ may be considered as simply equal to $\prop$ or $¬\prop$, as $(\prop, \text{sure})$ is treated exactly as $(\prop, \text{possible})$.
+Thus, elements $\prop \in \allprops$ may be considered as simply equal to $\prop$ or $¬\prop$, as $(\prop, \text{sure})$ is treated exactly as $(\prop, \text{possible})$.
 
@@
 \subsection{Falsifiability}
-\commentOC{I should define $\Box(\hist \ileadsto \phi)$ iff it has been observed that $\hist \ileadsto \phi$.
-Then, axiom Correct observations (that is self-evident): $\Box(\hist \ileadsto \phi) ⇒ \hist \ileadsto \phi$ (what has been observed is).
-Supplementary axiom Falsification is enough (that is not self-evident): $\not\Box(\hist \ileadsto \phi) ⇒ \hist \nileadsto \phi$ (what has not been observed is not).}
+\commentOC{I should define $\Box(\hist \ileadsto \prop)$ iff it has been observed that $\hist \ileadsto \prop$.
+Then, axiom Correct observations (that is self-evident): $\Box(\hist \ileadsto \prop) ⇒ \hist \ileadsto \prop$ (what has been observed is).
+Supplementary axiom Falsification is enough (that is not self-evident): $\not\Box(\hist \ileadsto \prop) ⇒ \hist \nileadsto \prop$ (what has not been observed is not).}
 
@@
 
-Given $\hist \in \allhist$ and $i \in I$, the claim $\hist \ileadstoe[i] \phi$ may not be verifiable, and is too specific to be falsifiable.
-However, given $\hist \in \allhist$, a broader claim is falsifiable: that for a given set of individuals $Q \subseteq I, \forall i \in Q, \hist \ileadstoe[i] \phi$ (provided $Q$ is big enough).
-Indeed, that claim it is equivalent to $\nexists i \in Q \suchthat \hist \nileadstoe[i] \phi$; exhibiting an $i \in Q$ such that $\hist \nileadstoe[i] \phi$ thus falsifies the broader claim.
-
-Given any $(\allprops, ¬, \allargs, I)$, an \emph{observation protocol} is a binary tree whose non-leaf nodes are among $I × \allhist × \Phi$ and whose two edges out of any non leaf node are labeled by “yes” and “no”; the leaf nodes being simply $\emptyset$.
-The observation protocol is said to assume memory iff for each non-leaf node $n = (i, \hist, \phi)$ about $i$, any node $n' = (i, {\hist}', \phi')$ about $i$ that is further down the tree continues the history, that is, the sequence ${\hist}'$ starts with $\hist$.
-Given an observation protocol and observables $(\ileadstoe[i])_{i \in I}$, the \emph{observed path} refers to the path in the tree defined recursively as consisting of the root node and, for each non-leaf node $n = (i, \hist, \phi)$ in the path, the child node along the branch “yes” if $\hist \ileadstoe[i] \phi$ and the child node along the branch “no” otherwise.
+Given $\hist \in \allhist$ and $i \in I$, the claim $\hist \ileadstoe[i] \prop$ may not be verifiable, and is too specific to be falsifiable.
+However, given $\hist \in \allhist$, a broader claim is falsifiable: that for a given set of individuals $Q \subseteq I, \forall i \in Q, \hist \ileadstoe[i] \prop$ (provided $Q$ is big enough).
+Indeed, that claim it is equivalent to $\nexists i \in Q \suchthat \hist \nileadstoe[i] \prop$; exhibiting an $i \in Q$ such that $\hist \nileadstoe[i] \prop$ thus falsifies the broader claim.
+
+Given any $(\allprops, ¬, \allargs, I)$, an \emph{observation protocol} is a binary tree whose non-leaf nodes are among $I × \allhist × \allprops$ and whose two edges out of any non leaf node are labeled by “yes” and “no”; the leaf nodes being simply $\emptyset$.
+The observation protocol is said to assume memory iff for each non-leaf node $n = (i, \hist, \prop)$ about $i$, any node $n' = (i, {\hist}', \prop')$ about $i$ that is further down the tree continues the history, that is, the sequence ${\hist}'$ starts with $\hist$.
+Given an observation protocol and observables $(\ileadstoe[i])_{i \in I}$, the \emph{observed path} refers to the path in the tree defined recursively as consisting of the root node and, for each non-leaf node $n = (i, \hist, \prop)$ in the path, the child node along the branch “yes” if $\hist \ileadstoe[i] \prop$ and the child node along the branch “no” otherwise.
 The \emph{observations} refer to the set of nodes along the observed path.
 
-Given any $(\allprops, ¬, \allargs, I)$, a \emph{normative claim} about $(\allprops, ¬, \allargs, I)$ (or about $\allargs$, when the other defined objects are left implicit) is any first-order logic proposition involving the atoms $[(\hist, \phi) \in {\ileadstoe[i]}], \hist \in \allhist, \phi \in \Phi$ which, together with the axioms, permits to deduce that $\phi \in \iPhi$ for some $i \in I$ and $\phi \in \Phi$.
+Given any $(\allprops, ¬, \allargs, I)$, a \emph{normative claim} about $(\allprops, ¬, \allargs, I)$ (or about $\allargs$, when the other defined objects are left implicit) is any first-order logic proposition involving the atoms $[(\hist, \prop) \in {\ileadstoe[i]}], \hist \in \allhist, \prop \in \allprops$ which, together with the axioms, permits to deduce that $\prop \in \iprops$ for some $i \in I$ and $\prop \in \allprops$.
 The claim is said to be \emph{about} the given set $\allargs$.
 An observation protocol, together with observables $(\ileadstoe[i])_{i \in I}$, \emph{falsifies} a normative claim iff the falsity of the claim is deducible from the axioms and the observations.
-A normative claim is \emph{falsifiable} iff there exists a finite observation protocol such that for any observables $(\ileadstoe[i])_{i \in I} \in (\allhist × \Phi)^I$, if the claim is false given these observables, then it is possible to deduce it from the axioms and the observations given the observables.
+A normative claim is \emph{falsifiable} iff there exists a finite observation protocol such that for any observables $(\ileadstoe[i])_{i \in I} \in (\allhist × \allprops)^I$, if the claim is false given these observables, then it is possible to deduce it from the axioms and the observations given the observables.
 
@@
 
-A normative claim is \emph{trivial} iff it is about a singleton $\allargs = \set{\ar}$, and has the form: $\ar \ileadstosts \phi$, for some $i \in I$.
-A normative claim is minimal iff it has the form: $\exists \ar \in \allargs \suchthat \ar \ileadstosts \phi$, for some $i \in I$ and $\phi \in \Phi$.
+A normative claim is \emph{trivial} iff it is about a singleton $\allargs = \set{\ar}$, and has the form: $\ar \ileadstosts \prop$, for some $i \in I$.
+A normative claim is minimal iff it has the form: $\exists \ar \in \allargs \suchthat \ar \ileadstosts \prop$, for some $i \in I$ and $\prop \in \allprops$.
 Note that given a minimal claim, $\card{\allargs} = 1$ is equivalent to the claim being trivial.
@@
 \begin{proof}
-	Consider any claim about some $i$ and some $\phi$ and any finite observation protocol.
+	Consider any claim about some $i$ and some $\prop$ and any finite observation protocol.
 We have to show that for some observables, the claim is false, but it is impossible to observe it (meaning, to deduce it from the axioms and observations).
 
-	Given $k \in \N$, define $\ileadstosts[k]$ as $\ar^k \ileadstosts \phi$ and $\ar^{k+1} \ileadstosts ¬\phi$ (where $\ar^k$ designates a finite sequence repeating $k$ times $\ar$, for $\ar \in \allargs$).
+	Given $k \in \N$, define $\ileadstosts[k]$ as $\ar^k \ileadstosts \prop$ and $\ar^{k+1} \ileadstosts ¬\prop$ (where $\ar^k$ designates a finite sequence repeating $k$ times $\ar$, for $\ar \in \allargs$).
 I claim that for some $k$, the observables that include this relation makes the claim false, but not observably so.
@@
 	Define $\ar_1$ as the first element of the sequence $\hist$ of the root node of the observation protocol (if the observation protocol is empty, suffices to define any observables that make the claim false).
-Define the observables so that $\forall \hist \in \allhist: \ar_2, \hist \ileadsto ¬\phi$.
-This proves that no argument is decisive, hence $\phi \notin \Box\Phi$, and the claim is false.
+Define the observables so that $\forall \hist \in \allhist: \ar_2, \hist \ileadsto ¬\prop$.
+This proves that no argument is decisive, hence $\prop \notin \Box\Phi$, and the claim is false.
 But the observables may also be defined so as to satisfy the protocol (defined as: when going through the protocol, the observations can’t fail the claim).
@@
 \subsection{Definition}
-A general empirical theory for a normative theory $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$ is a tuple $({\gleadsto}, f)$, where ${\gleadsto} \subseteq \allargs × \Phi$ and $f \subseteq (\allargs × \allargs) × \allargs$ with $f(\allargs × \allargs)$ being finite.
+A general empirical theory for a normative theory $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$ is a tuple $({\gleadsto}, f)$, where ${\gleadsto} \subseteq \allargs × \allprops$ and $f \subseteq (\allargs × \allargs) × \allargs$ with $f(\allargs × \allargs)$ being finite.
 
@@
 This is falsifiable.
-	When claiming that $(\ar_1, \ar_0) \ileadstoall[i] \phi$, the model really claims that $\nexists p, i' \in q^{-1}(q(i)) \suchthat p, \ar_1, \ar_0 \ileadsto[i'] ¬\phi \lor p, \ar_0, \ar_1 \ileadsto[i'] ¬\phi$, where $i' \in q^{-1}(q(i))$ iff $q(i) = q(i')$.
-
-	To say that $\phi \in \iPhi$, need to not depend on choice of $q$, in the following sense: if with $q$, $\phi$ seems stable, but with $q'$, $¬\phi$ seems stable, then $\phi$ is not proved as being in $\iPhi$.
-But if with $q$, $\phi$ seems stable, but with $q'$, nothing can be shown to be stable, then $\phi$ is proved (temporarily) as being in $\iPhi$.
+	When claiming that $(\ar_1, \ar_0) \ileadstoall[i] \prop$, the model really claims that $\nexists p, i' \in q^{-1}(q(i)) \suchthat p, \ar_1, \ar_0 \ileadsto[i'] ¬\prop \lor p, \ar_0, \ar_1 \ileadsto[i'] ¬\prop$, where $i' \in q^{-1}(q(i))$ iff $q(i) = q(i')$.
+
+	To say that $\prop \in \iprops$, need to not depend on choice of $q$, in the following sense: if with $q$, $\prop$ seems stable, but with $q'$, $¬\prop$ seems stable, then $\prop$ is not proved as being in $\iprops$.
+But if with $q$, $\prop$ seems stable, but with $q'$, nothing can be shown to be stable, then $\prop$ is proved (temporarily) as being in $\iprops$.
 More precisely, after $q'$, the model must be able to stabilize $i$ with its $q$.
@@
 
-$\ar_0$ $i$-defends $\phi$ when ignoring $S_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \phi$.
-$\ar_0$ $i$-defends $\phi$ under protection of $S_2$ iff $\ar_0$ $i$-defends $\phi$ when ignoring $g(\ar_0)(\args_2)$.
+$\ar_0$ $i$-defends $\prop$ when ignoring $S_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \prop$.
+$\ar_0$ $i$-defends $\prop$ under protection of $S_2$ iff $\ar_0$ $i$-defends $\prop$ when ignoring $g(\ar_0)(\args_2)$.
 
 \begin{definition}[Convincingness]
-	$\forall i \in I, \phi \in \gPhie, \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
+	$\forall i \in I, \prop \in \gpropse, \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\prop)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\prop$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
 \end{definition}
@@
 
-	This may be adequate as if $\ar_0$ seems suitable but some unplanned attacker $\ar_1$ attacks it, then use $\ar_1 \in \hist$ and observe that $¬(\hist, \ar_0) \ileadstoe \phi$ to deny the claim.
+	This may be adequate as if $\ar_0$ seems suitable but some unplanned attacker $\ar_1$ attacks it, then use $\ar_1 \in \hist$ and observe that $¬(\hist, \ar_0) \ileadstoe \prop$ to deny the claim.
 
@@
 \begin{proof}
-	Consider $i \in I$ and $\phi \in \gPhie$. 
-	By hypothesis, $\exists k$ such that some $\ar_k \in \args_k$ defends $\phi$ under protection of $\emptyset$. Therefore, $\ar_k \ileadstosts \phi$. Using \cref{ax:norm}, validity follows.
+	Consider $i \in I$ and $\prop \in \gpropse$. 
+	By hypothesis, $\exists k$ such that some $\ar_k \in \args_k$ defends $\prop$ under protection of $\emptyset$. Therefore, $\ar_k \ileadstosts \prop$. Using \cref{ax:norm}, validity follows.
 \end{proof}

### 2020-08-18 simple.tex
Negation is now optional.

@@
 
-A normative theory also defines an involution operator $¬$ on $\allprops$, thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$.
-(The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
-
-A normative theory is a tuple $(\allprops, ¬, \allargs, I, {\allleadsto})$ 
-%with $\allprops$ an agenda, $¬$ a negation operator on $\allprops$, $\allargs$ a set of arguments, $I$ a set of individuals, and ${\allleadsto}$ an observation protocol, 
+A normative theory is a tuple $(\allprops, \allargs, I, {\allleadsto})$ 
 satisfying the constraints described here above.
-%where $\allprops = \allprops × \set{\mathit{poss}, \mathit{sure}}$.
 
 As usual with binary relations, $\hist \nileadsto \prop$ means $(\hist, \prop) \notin {\ileadsto}$.
-
-Given $i \in I, \prop \in \allprops, \hist \in \allhist$, say that $\hist$ leads strongly to $\prop$, $\hist \ileadstost \prop$, iff $\hist \ileadsto \prop \land \hist \nileadsto ¬\prop$.
-(The visual proximity of the symbols $\ileadsto$ and $\ileadstost$ creates a small risk of confusion, but its usage seems justified by the fact that $\ileadsto$ is not used in the rest of this article, except in the proof of \cref{th:protcoh}.)
 
@@
 
-\begin{remark}
-	I’d rather drop the negation and observe that if the protocol is defined so that $\hist \ileadsto \prop_1 ⇒ \hist \nileadsto \prop_2$, then $\prop_1 \in \iprops ⇒ \prop_2 \notin \iprops$.
-Observe that this is always possible.
-The definitions about completeness should use a negation operator in supplement to the normative theory tuple.
-\end{remark}
-
-\subsection{Classify propositions}
+\subsection{Coherence}
 \begin{axiom}[Normative adequacy]
@@
 	$\forall i \in I, \prop \in \allprops: 
-		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \prop) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\prop)] ⇒ \prop \in \iprops \land ¬\prop \notin \iprops.$
+		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \prop)] ⇒ \prop \in \iprops.$
 \end{axiom}
 
-\Cref{ax:norm} is actually equivalent to the following property.
-\begin{property}[Simple normative adequacy]
-	\label{ax:snorm}
-	$\forall i \in I, \prop \in \allprops: 
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ \prop \in \iprops \land ¬\prop \notin \iprops.$
-\end{property}
-
-To see why this hold, consider the following definition and proposition.
-\begin{definition}[Protocol coherence]
-	\label{def:protcoh}
-	$\forall i \in I, \prop \in \allprops$:
+A relation $n \subseteq \allprops × \allprops$ is said to be an incompatibility relation iff $\forall \hist \in \allhist, (\prop, \propbar) \in n: \hist \ileadsto \prop ⇒ \hist \nileadsto \propbar$.
+Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $(\prop, \prop') \in n$.
+Such a pair will generally denoted by $(\prop, \propbar)$.
+(This article does not use the overline to denote set complementarity, thus this notation should create no confusion.)
+
+It is desirable to ensure that this axiom cannot lead to incompatible propositions being considered deliberated. Consider the following proposition.
+\begin{proposition}[Protocol coherence]
+	\label{th:protcoh}
+	Given any normative theory and incompatibility relation $n$,
+	$\forall i \in I, (\prop, \propbar) \in n$:
 	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\prop].
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost \propbar].
 	\end{equation}
-\end{definition}
-\begin{proposition}
-	\label{th:protcoh}
-	Any normative theory satisfies Protocol coherence.
 \end{proposition}
 \begin{proof}
-	Protocol coherence is satisfied by definition of $\ileadstost$.
-Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost \prop$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto ¬\prop$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost ¬\prop$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\prop$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\prop$.
-\end{proof}
-
-That \cref{ax:norm} is equivalent to \cref{ax:snorm} immediately follows from \cref{th:protcoh}.
-\begin{proposition}
-	\label{th:normeqsnorm}
-	Any normative theory satisfies Normative adequacy iff it satisfies simple normative adequacy.
+	If for some $\ar \in \allargs$, $\ar \ileadstost \prop$, then by definition of $\ileadstost$, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadsto \prop$, thus by definition of $n$, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto \propbar$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost \propbar$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto \propbar$, and thus in particular, that $(\ar', \ar) \ileadsto \propbar$.
+\end{proof}
+
+To further analyze this and related matters, consider defined a negation operator $¬$ on $\allprops$.
+$¬$ is a negation operator iff it is an involution operator (thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$) and furthermore satisfying, $\forall \phi \in \allprops: \hist \ileadsto \prop ⇒ \hist \nileadsto ¬\prop$.
+Given any $i \in I$, say that a proposition $\prop \in \allprops$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost \propbar$.
+The $i$-decidable propositions are those on which the normative theory permits to take a position. 
+%It will generally be unknown in practical applications, and may be empty.
+The next proposition ensures an unambiguous interpretation of the content of $\iprops$ for all $i$-decidable propositions.
+The symbol $\oplus$ denotes the exclusive disjunction; thus $\prop \in \iprops \oplus ¬\prop \in \iprops$ is equivalent to: $\prop \in \iprops ⇔ ¬\prop \notin \iprops$.
+It can be seen to hold by using \cref{th:protcoh}.
+
+\begin{proposition}[Restricted interpretability]
+	\label{th:restrinterpr}
+	Any normative theory with a negation operator $¬$ satisfy,
+	$\forall i \in I, \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop] ⇒ [\prop \in \iprops \oplus ¬\prop \in \iprops]$.
 \end{proposition}
 
-To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\prop \in \allprops$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop$.
-The $i$-decidable propositions are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
-The next property ensures an unambiguous interpretation of the content of $\iprops$ for all $i$-decidable propositions.
-In this definition, $\oplus$ denotes the exclusive disjunction; thus $\prop \in \iprops \oplus ¬\prop \in \iprops$ is equivalent to: $\prop \in \iprops ⇔ ¬\prop \notin \iprops$.
-It can be seen to hold by using \cref{th:normeqsnorm}.
-
-\begin{property}[Restricted interpretability]
-	\label{def:restrinterpr}
-	$\forall i \in I, \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop] ⇒ [\prop \in \iprops \oplus ¬\prop \in \iprops]$.
-\end{property}
-
-\subsection{Non-completeness}
-\label{sec:incompl}
+This interpretability is however restricted to the $i$-decidable propositions.
+The following definitions and propositions (assuming a normative theory and a negation operator $¬$ defined) argue that going further is not desirable.
+
 \begin{definition}[Theory completeness]
@@
 \begin{proof}
-	Consider an agenda containing two propositions, $\allprops = \set{\prop, ¬\prop}$, an infinite set of arguments $\allargs = \set{\ar_k \suchthat k \in \N}$ with $\forall j, k \in \N: \ar_j ≠ \ar_k$, and consider any set of individuals $I$ and observation protocol $\allleadsto$.
-	Define $2\N^* = \set{k \suchthat k / 2 \in \N^*}$ as the set of non-zero even integers.
+	Consider an agenda $\allprops = \set{\prop}$ containing a single proposition, an infinite set of arguments $\allargs = \set{\ar_k \suchthat k \in \N}$ with $\forall j, k \in \N: \ar_j ≠ \ar_k$, and consider any set of individuals $I$ and observation protocol $\allleadsto$.
+	Define $2\N^* = \set{k \in \N^* \suchthat k / 2 \in \N^*}$ as the set of non-zero even integers.
 	Define ${\gleadsto} = \set{(\ar_0, \prop)}$.
@@
 %	$\ard[k] \in \alldargs$, define $\ar_0 + \set{\ard[k]} = \ar_k$. 
-	Consider an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ for the normative theory $(\allprops, ¬, \allargs, I, {\allleadsto})$.
+	Consider an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ for the normative theory $(\allprops, \allargs, I, {\allleadsto})$.
 That this is indeed a legal empirical theory can be confirmed by checking that all constraints are satisfied, in particular, $(\dfp)^2(\gleadstoinv(\allprops)) = \dfp(\dfp(\ar_0)) = \dfp(\set{\ar_k \suchthat k \in 2\N^*}) = \emptyset$ because there is no planned attack against any argument in $\set{\ar_k \suchthat k \in 2\N^*}$.
@@
 \begin{definition}[Validity]
-	An empirical theory is \emph{valid} iff $\forall i \in I, \prop \in \gpropse: [\prop \in \iprops \land ¬\prop \notin \iprops]$.
+	An empirical theory is \emph{valid} iff $\forall i \in I, \prop \in \gpropse: \prop \in \iprops$.
 \end{definition}
@@
 \begin{proof}
-	Given any $i \in I$ and $\prop \in \gpropse$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \prop$; the conclusion then follows thanks to simple normative adequacy (that \cref{th:normeqsnorm} shows to be equivalent to normative adequacy).
+	Given any $i \in I$ and $\prop \in \gpropse$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \prop$; the conclusion then follows thanks to normative adequacy.
 
@@
 \subsection{Effectively comparing models}
-Given $\prop \in \allprops$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\prop$ iff $\prop \in \gpropse[\gamma] \land ¬\prop \in \gpropse[\delta]$.
-Say that they are incompatible iff there is at least one $\prop \in \allprops$ that they disagree about.
+Given $\prop \in \allprops$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory with an incompatibility relation $n$, say that they disagree about $(\prop, \propbar) \in n$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$.
+Say that they are incompatible iff there is at least one pair $(\prop, \propbar) \in \allprops$ that they disagree about.
 
 Given $\prop \in \allprops$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $\prop$ iff $\hist \nileadstost \prop$ and $\ar_\gamma \in \histend$.
-Given $\prop \in \allprops, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/¬\prop$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \prop)$ or $(\hist, \ar_\delta)$ challenges $(\delta, ¬\prop)$.
+Given $\prop \in \allprops, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \prop)$ or $(\hist, \ar_\delta)$ challenges $(\delta, \propbar)$.
 
@@
 	\label{th:endchal}
-	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$, $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/¬\prop$-challenge.
+	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$, $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge.
 \end{lemma}
 \begin{proof}
-	Either $\hist \nileadstost \prop$, and $(\hist, \ar_\gamma)$ challenges $\prop$, or $\hist \ileadstost \prop$, hence, by \cref{th:protcoh}, $\hist \nileadstost ¬\prop$, and $(\hist, \ar_\delta)$ challenges $¬\prop$.
+	Either $\hist \nileadstost \prop$, and $(\hist, \ar_\gamma)$ challenges $\prop$, or $\hist \ileadstost \prop$, hence, by \cref{th:protcoh}, $\hist \nileadstost \propbar$, and $(\hist, \ar_\delta)$ challenges $\propbar$.
 \end{proof}
@@
 	\label{th:nextchal}
-	Given $(\hist, \ar_\gamma)$ challenging $\prop$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\prop))$, and $\ar_\delta \in \gargsdelta$: either $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $\prop/¬\prop$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\prop))$.
+	Given $(\hist, \ar_\gamma)$ challenging $\prop$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\prop))$, and $\ar_\delta \in \gargsdelta$: either $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $\prop/\propbar$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\prop))$.
 \end{lemma}
@@
 	$(\hist, \ar_\alpha, \ar_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta)$ iff 
-	$(\hist, \ar_\alpha, \ar_\beta)$ is a $\prop/¬\prop$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\prop))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](¬\prop))$.
-
-	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\beta] ¬\prop$.
-Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](¬\prop))$.
+	$(\hist, \ar_\alpha, \ar_\beta)$ is a $\prop/\propbar$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\prop))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](\propbar))$.
+
+	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\beta] \propbar$.
+Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](\propbar))$.
 Test whether $(\ar_{-1}) \nileadstost \prop$.
@@
 Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \prop$.
-By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\prop/¬\prop$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
+By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\prop/\propbar$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
 
@@
 Indeed, if $(\hist, \ar_\alpha)$ challenges $\prop$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
-And if $(\hist, \ar_\beta)$ challenges $¬\prop$, apply \cref{th:nextchal} with $¬\prop$ for $\prop$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.
-
-	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\prop)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](¬\prop)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
+And if $(\hist, \ar_\beta)$ challenges $\propbar$, apply \cref{th:nextchal} with $\propbar$ for $\prop$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.
+
+	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\prop)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](\propbar)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
 \end{procedure}

### 2020-08-18 simple.tex
End pres informal

@@
 Normative theories define an agenda: a set of propositions that we are interested in knowing the deliberated judgment of individuals about; a set of individuals that the theory claims applies to; a set of arguments; and a protocol of observation of the judgments an individual adopts towards a proposition after exposure to various arguments.
-Normative theories also define a negation operation on the set of propositions, which this discussion neglects for the sake of simplicity.
-
-Examples of propositions in the agenda include: “I ought to pay at most \$100 for purchasing bundle $b$”, “I ought to acquire alternative $a$ rather than $b$ if it is available in the same conditions”; “I ought not to perform action $a$ because it is immoral”.
+
+Examples of propositions to be included in agenda include: “I ought to pay at most \$100 for purchasing bundle $b$”, “I ought to acquire alternative $a$ rather than $b$ if it is available in the same conditions”; “I ought not to perform action $a$ because it is immoral”.
 
@@
 (An empirical theory also defines a concatenation operation able to dynamically build arguments from fragments of arguments, an aspect which is not discussed in this informal presentation.)
-
-\TODO{Pursue here.}
-More precisely, the argumentation requirements are as follows.
-Given an individual, the empirical theory must be able to present an argument that is, at least initially, convincing to the individual (as judged thanks to the observation protocol of the normative theory).
-It is not mandated that this argument be decisive, as only a weaker requirement is enough to ensure the validity of its claims.
-Instead, the theory must declare which arguments it knows how to answer.
-Such arguments are called the planned attackers.
-Whether an argument effectively attacks another one (from the point of view of the individual) can, again, be defined in terms of the observation protocol of the normative theory.
-Requiring that the theory declares in advance its attackers mean that if an argument effectively attacks one of its argument, then this attack must have been planned.
-
-More precisely, the theory must, for each sequence of arguments leading the individual to a proposition contrary to what the theory supports, be able to exhibit an argument that, when appended to that sequence, leads the
-
-exhibit a decisive argument for that proposition, as judged from the individual’s point of view.
+The theory claims that when one of its arguments in support of one of its claims is unconvincing to an individual, it is because of one of the planned attacks; and the theory claims to be able to provide counter-arguments to such attacks as they come, that will in turn be either convincing to the individual, or fail to be because of some planned attack.
+(The theory is also constrained to have “finite depth”, meaning that it must set an a priori limit to the number of such iterations of attacks and counter-arguments.)
+
+Thanks to these operators, an empirical theory may adjust its argumentation to each individual.
+Instead of having to give a single decisive argument in support of its claims, the theory may react to exactly the counter-arguments that a given individual thinks relevant.
+This task is easier, but still permits to obtain what is desired in this article.
+First, the claim of the theory, of being able to argue convincingly, can be checked by ensuring that no empirical counter-examples exist, thus, it is a fully empirical claim (in the sense that it requires no axiom).
+Second, if indeed a theory is convincing in that sense, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}.
+
+The following section defines normative and empirical theories precisely.
 
@@
 \end{procedure}
-
-\subsection{TODO, about comparisons}
-Count the number of tests; assume simpler theory.
-
-Indicate sufficient hypothesis for ensuring that if a model resisted every attack, it is valid. Thus, that searching for falsification instances in the tested ones is enough.
 
@@
 
+\subsection{About comparisons}
+Count the number of tests; assume simpler theory.
+
+Indicate sufficient hypothesis for ensuring that if a model resisted every attack, it is valid. Thus, that searching for falsification instances in the tested ones is enough.
+
 \subsection{Interpreting Answerability}

### 2020-08-19 simple.tex
Various suppl discussions; a sketch of a conclusion. Hidden appendices.

@@
 \section{Motivation} 
-\TODO{“Before asking whether agents want to revise their choices or not, both rival theories should be proposed.” Guala 2000.
-My approach can be qualified as a debiasing technique (Mitchell, Libertarian paternalism is an oxymoron.
-Nw UL Rev 99:1245–1817, 2005).
-Mitchell observes that “in many of those surveys that governments use in order to inform social policy there are not enough resources (time and money) in order to reach the stage where preferences are not labile” (exact quote?).}
-
 It has escaped nobody’s attention that 
@@
 An approach much discussed recently is the one of laundering preferences, also called preference purification \citep{bernheim_beyond_2009, rubinstein_eliciting_2011, infante_preference_2016}: having collected shallow preference data (from the field or from interviews), laundering preferences consists in transforming them, using a formal process, in such a way that they satisfy axioms generally considered as required by rationality, or keeping only preference data collected in some situations considered appropriate to determine welfare-relevant preferences.
-For example, \citet{bleichrodt_making_2001} transform observed preferences in order to obtain a classical Expected Utility model; \citet{bernheim_beyond_2009} propose to exclude situations where the individual seems (by objective criteria) unable to process information considered relevant.
+For example, \citet{bleichrodt_making_2001} transform observed preferences in order to obtain a classical Expected Utility model; \citet{bernheim_beyond_2009} propose to exclude situations where the individual seems (by objective criteria) unable to process information considered (by the theorist) as relevant information.
 
@@
 Note that nudging \citep{thaler_nudge_2009} creates a similar problem: we have to guess what the individual would like if he thought hard about the decision problem, was well-informed, and actively worked against the psychological features he himself does not consider adequate for good decision making.
-\TODO{Comment about akrasia: we may want to correct for features that the individual herself can’t correct.}
 
@@
 
+As a consequence of these techniques being not completely formalised and reproducible, each application requires manual intervention of (very skilled) experts.
+Eliciting reflective preferences therefore requires enormous resources.
+\Citet[p.\ 572]{pinto_normative_2012} observe that “in many of those surveys that governments use in order to inform social policy there are not enough resources (time and money) in order to reach the stage where preferences are not labile”.
+There is, to reduce this cost, a need for theories that can be iteratively improved upon and yield reusable knowledge about reflective preferences.
+
 Different analysts, using different methods and different axioms as their favorite conception of rational decision-making, will obtain possibly contradictory conclusions, “elicited” from the decision-makers who hire them.
@@
 In this domain, the many different approaches reflect in our view the complexity of the researcher's task much more than a scientific weakness.”
-%Some analysts claim that the value of such interactions between decision-makers and analysts is the fact that it made decision-makers think hard about the problem, and not the resulting preference model.
 Although being an important insight about the (likely vain) hope of determining a single correct recommendation in many complex decision situations (about which more below), this answer does not address the problem that some principles of decision making may be wrong guides in some situations, possibly including some principles that are commonly applied in the field, hence the need of principled ways of discriminating them.
 
+\subsection{Some other related approaches}
 The prescriptive approach to decision making \citep{bell_decision_1988} has been proposed (in supplement to the normative one and the descriptive one), which insists on incorporating the findings of psychologists about decision maker’s weaknesses of reasoning in the procedures leading to recommendations.
@@
 
-\TODO{Argumentation theory inspired; but they consider arguments are given. Pursues another article of mine.}
+Some authors have proposed to ground normative theories on observable aspects of nature and individuals, to solve some of the problems mentioned above; for example, \citet{kahneman_back_1997} propose to measure “experienced utility”, considered as a hedonic quality.
+To the best of my knowledge, these proposals never aim at observing reflective preferences as considered here and thus fall outside the scope of this article.
+
+The field of formal argumentation theory has developed technical approaches to deal with arguments.
+Such endeavor starts with an “attack” relation, which indicates which arguments argue against which.
+Various criteria can then be mathematically defined, in the form of a function selecting subsets of arguments given an attack relation, typically representing sets of arguments that “best resist” their counter-arguments.
+This field has greatly inspired this proposal, in particular, the notion of attack and of reinstatement.
+This field however does not view the attack relation as observable, but considers it as given, and its methodology is therefore not empirical in the sense seeked for here.
+(\Citet{cailloux_formal_2019} elaborates on this difference of objective.)
+
+An important literature exists about “debiasing techniques”: techniques that aim at encouraging individuals to think more about their decision problem in order to reduce occurrence of behavioral “mistakes”.
+Examples include suggesting the individuals to consider alternative points of view, or asking them to give reasons for their choices (an insightful article by \citet{mitchell_libertarian_2004} cite many such studies).
+This proposal is situated at another level, which could be considered as a way of justifying and comparing such debiasing techniques with no need of a prior agreement on what constitutes a behavioral mistake.
+
+The current proposal pursues a path started with \citet{cailloux_formal_2019}, an article that defines the notion of \ac{DJ} and models that enable interactions with individuals whose \acp{DJ} are to be captured.
+That article however requires as fundamental observable a “trump” relation, indicating whether an individual thinks that an argument is against another argument; and a “support” relation, indicating whether an individual thinks that an argument supports a proposition.
+The current proposal defines every required concepts, such as the notion of arguments attacking other arguments, on the basis of a single observable that is compatible with the revealed preference approach priviledged in economic theory, in the sense that it can be defined by reference to what individuals effectively choose under various circumstances.
+The current proposal also defines explicitly (in the form of an axiom) sufficient requirements to grant normative power to observations, an aspect which was previously left unclear.
+Finally, the current proposal links \ac{DJ} and deliberated preferences.
+
+\Citet{meinard_justification_2020} discuss some requirements on justification of recommendations, which gives further arguments in favor of studying \acp{DJ}.
 
@@
 The proposal of this article to capture reflective preferences while avoiding the just described problems is to define normative theories on the basis of a low demanding axiom complemented with principles of reasonings; that allow decision makers to “reconstruct” the reasoning proposed by the principles so as to be able to check that they apply to their situation; therefore permitting to falsify the theories using observable data representing the rejection by the decision makers of these principles.
-Such theories are therefore both normative and empirical: normative, in the sense of claiming to capture reflective preferences, which provide a better basis for recommendations or policy making than shallow preferences; and empirical, in the sense of the principles of reasoning being exposed to empirical falsification.
+Such theories are therefore both normative and empirical: normative, in the sense of claiming to capture reflective preferences, which provide a better basis for recommendations or policy making than shallow preferences; and empirical, in the sense of the principles of reasoning being exposed to empirical tests.
 
@@
 This might match \possessivecite{hausman_debate_2010} suggestion that we should use rational persuasion rather than nudge individuals, arguing that it would promote autonomy.
+It also follows \possessivecite[p.\ 72]{guala_logic_2000} suggestion (discussing the Allais paradox) about obtaining relevant data to compare normative behavioral theories: “Before asking whether agents want to revise their choices or not, \emph{both} rival theories should be proposed” (emphasis in the original text).
 
@@
 A normative theory makes normative claims only, which have to be accepted or rejected on the basis of the apparent soundness of the axiom on which it rests.
-An empirical theory for a given normative theory, by contrast, makes empirical claims, hence, can be falsified by data.
+An empirical theory for a given normative theory, by contrast, makes empirical claims, hence, can be confronted to observations.
 What I call here an empirical theory, for simplicity, is not however purely empirical, but can also be considered normative, for two reasons.
@@
 Instead of having to give a single decisive argument in support of its claims, the theory may react to exactly the counter-arguments that a given individual thinks relevant.
-This task is easier, but still permits to obtain what is desired in this article.
-First, the claim of the theory, of being able to argue convincingly, can be checked by ensuring that no empirical counter-examples exist, thus, it is a fully empirical claim (in the sense that it requires no axiom).
-Second, if indeed a theory is convincing in that sense, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}.
+This task is easier, but still permits to obtain what is desired in this article: there exists a purely empirical property of a theory, called convincingness, that, together with an axiom about the normative adequacy of the observation protocol, implies the correctness of the claims of the theory.
+In more details, first, the claim of the theory, of being able to argue convincingly, can be checked by ensuring that no falsification instances exist, thus, it is a fully empirical claim (in the sense that it requires no axiom).
+Second, granted normative adequacy, if indeed a theory is convincing, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}.
+These claims are proven in \cref{th:convnofals,th:valid}.
 
@@
 
-\subsection{Falsifiability}
+\subsection{Empirical tests}
 Given $\args \subseteq \allargs$, $\hist \in \allhist$, and letting $l$ denote the length of $\hist$,
@@
 \begin{theorem}
+	\label{th:convnofals}
 	An empirical theory is convincing iff it has no falsification instances.
@@
 \begin{theorem}
+	\label{th:valid}
 	A normatively adequate and convincing empirical theory is valid.
@@
 %a \emph{test procedure with $i$} is a finite sequence 
-\commentOC{Need the test procedure to be a tree.
+%\commentOC{Need the test procedure to be a tree.
 Atom: $(k, \prop)$ meaning whether ${\hist}^k \ileadstost \prop$.
@@
 \section{Conclusion}
-Back To Bentham? Explorations Of Experienced Utility, Kahneman Wakker, Sarin, propose to measure hedonimeter total for normative.
-
+(To be written.)
+
+- A theory will never be absolutely convincing in the sense defined here.
 \citet[p.\ 100]{raiffa_back_1985} (about SEU): “Give therapy to deviators”.
@@
 Yes, they were dazzled (and perhaps confused) but many remained unconvinced; if the chips were down, they would behave just as before.”
+Existence of a falsification instance does not mean that a theory should be rejected.
+Instead, comparing theories in the suggested way permits to gather information about their relative convincingness power, which in turn will inform on the appropriateness of using them normatively.
+Supplementary criteria might be required to decide on normative power.
+For example, policies that would contradict “very strongly” shallow preferences could be considered as excluded, for practical or for principled reasons, even possibly in situations where it could be shown convincingly that such policies would better satisfy reflective preferences.
+Relatedly, it is not claimed here that what society ought to do is exactly what \acp{DJ} indicate, only that reflective preferences provide an appropriate basis for such normative endeavors, in supplement to other criteria.
+Further discussions are required, which hopefully the formal definitions here can help clarify.
+
+- Theories must be able to adapt their claims to individuals. The mechanism described here that adapts arguments to individuals can be adapted to such goal. This is left for future work.
+
+- Back to the claim that a decision problem may admit several valid responses.
+The current approach partly permits to develop theories that agree with this claim, because these theories may be incomplete (in the sense of defining only a partial deliberated preference).
+Taking this view seriously, however, requires to account for meta-preferences (cf.
+Sen): a (possibly partial) ordering on the possible definitions of one’s preference.
+As an example, a theory should be able to express that $i$ will adopt either the view that $a > b > c$, or the view that $c > b > a$, but not $a > c > b$.
+%Relatedly, akrasia might be considered as well.
+An individual may be able to declare that she would prefer having a preference rather than another one; or be put in a situation that helps her follow a preference rather than another one.
+As an example, an individual might be willing to declare
+
+\bibliography{simple}
+\end{document}
 
@@
 \end{theorem}
-
-\hbadness 10000
-\bibliography{simple}
-\end{document}

### 2020-10-17 simple.tex
Commentaires de Yves reçus par e-mail.

@@
 \section{Motivation} 
+\commentYM{dans la mesure où tu dis concevoir ou avoir conçu ce draft comme étant presque soumettable, pourquoi as-tu cette section "motivation" plutôt qu'une classique introduction ?}}
 It has escaped nobody’s attention that 
-studying reflective preferences, in supplement to shallow preferences, is an important endeavor for economics: we want to recommend to individual decision makers; we want to adopt optimization criteria for society, and this ought not to merely faithfully reproduce unreflectful behavior.
-This is one important difference between the normative and the (inappropriately called, as will be seen) “descriptive” approach in economics.
+studying reflective preferences, in supplement to shallow preferences, is an important endeavor for economics: we want to recommend to individual decision makers; we want to adopt optimization criteria for society, and this ought not to merely faithfully reproduce unreflectful behavior.\commentYM{je trouve cette entame provocatrice assez maladroite, car elle s'appuie sur l'opposition reflective vs.
+shallow preference, qui ne parle (je pense) pas immédiatement au lecteur.
+Je pense indispensable de définir cette dichotomie avant d'en parler.
+Par ailleurs que veut dire "is an important endeavor for economics" ?
+Il me semble au contraire que c'est une tâche qui devrait tenir à coeur aux économistes, mais qui pourtant n'est pas pour eux une tâche à laquelle ils s'attèlent vigoureusements.
+Enfin, l'anglais de cette phrase me semble un peu maladroit} This is one important difference between the normative and the (inappropriately called, as will be seen) “descriptive” approach in economics\commentYM{où discutes-tu cette distinction, dans son application à l'économie en particulier ?}.
 As \citet{hausman_preference_1994} illustrate with an example of a person drinking a fatal poison while erroneously thinking that it is water, shallow preferences are not sufficient to inform normative economics.
 Yet, classical methods to obtain preference models in economics are either formally defined on the basis of observable data that do not describe reflective preferences, or are obtained by other means than observable preferential data and systematic reproducible formal procedures.
-
-This article is interested in defining theories of decision making based on another kind of observable data, namely, the reactions of decision makers to arguments.
-This permits to overcome a current important limitation of normative approaches, that of being not empirical (in a sense that will be developed below).
+\commentYM{je devine ce que tu veux dire, mais je ne comprends pas la dernière phrase.
+Il me semble important que tu t'expliques ici, car je pense que le lecteur ici ne peut pas comprendre la niche dans laquelle s'inscrit ton projet}
+
+This article is interested in defining theories of decision making based on another kind of observable data\commentYM{other than what?
+Juste avant tu dis que les autres s'appuient sur des données qui ne reflètent pas les préférences qui t'intéressent, et maintenant tu dis que tu vas regarder autre chose qu'eux.
+Cela donne l'impression que tu tournes autour du pot, car tu ne dis pas ce que les autres regardes et pourquoi ça ne t'intéresse pas}, namely, the reactions of decision makers to arguments.
+This permits to overcome a current important limitation of normative approaches, that of being not empirical (in a sense that will be developed below).\commentYM{phrase incompréhensible pour le lecteur, puisque tu dis toi même que tu en expliqueras les termes plus tard.
+C'est une rhétorique difficile à tenir dans une introduction}
 
@@
 This distinction draws on our capacity, as human beings, to think about our shallow preferences and consider some of them as mistaken \citep{frankfurt_freedom_1971}.
-A famous example of such a situation is the one of \citet[pp.\ 101--103]{savage_foundations_1972} having realized, after due consideration, that his initial declared preference in a decision problem presented by \citet{allais_so-called_1979} was mistaken.
-
-It is well known that shallow preferences do not always match reflective ones.
+\commentYM{ces définitions devraient être mises + haut, car le lecteur ne peut pas comprendre ce que tu racontes sans elles}A famous example of such a situation is the one of \citet[pp.\ 101--103]{savage_foundations_1972} having realized, after due consideration, that his initial declared preference in a decision problem presented by \citet{allais_so-called_1979} was mistaken.
+
+It is well known that shallow preferences do not always match reflective ones.\commentYM{à quoi sert la phrase précédente ?}
 Indeed, forming reflective preferences is recognised as a difficult problem in many decision problems, contrary, by definition, to shallow preferences.
@@
 It takes work and serious reflection to find out one’s own preferences.”
-In the words of \citet[p.\ 9]{bell_descriptive_1988}, “Our decision makers are not economic automatons; they make mistakes, have remorse, suffer anxieties, and cannot make up their minds” (cited by \citet[p.\ 87]{deparis_etude_2012}).
+In the words of \citet[p.\ 9]{bell_descriptive_1988}, “Our decision makers are not economic automatons; they make mistakes, have remorse, suffer anxieties, and cannot make up their minds”\commentYM{cette citation me semble mal venue ici, car elle ne pose pas que la question du contraste shallow/reflective, mais aussi la question de savoir s'il faudrait toujours faire un calcul économique.
+Par exemple avoir des remords ne me semble pas forcément une mauvaise chose} (cited by \citet[p.\ 87]{deparis_etude_2012}).
 Indeed, it is to be expected that some behavior highlighted by psychologists \citep{kahneman_thinking_2012}, such as framing effects, would be rejected by the individuals themselves when pondering their decisions.
+\commentYM{formulation ambigue : on dirait que tu dis que les gens nieraient que les framing effects existent}
 
@@
 As an illustration, \citet[p.\ 7]{colell_microeconomic_1995} go on writing: “the transitivity assumption can be hard to satisfy when evaluating alternatives far from common experience.
-As compared to the completeness property, however, it is also more fundamental in the sense that substantial portions of economic theory would not survive if economic agents could not be assumed to have transitive preferences.”
+As compared to the completeness property, however, it is also more fundamental in the sense that substantial portions of economic theory would not survive if economic agents could not be assumed to have transitive preferences.” \commentYM{la seconde phrase de la citation me parait superflue pour ce que tu as à dire ici.
+Plus généralement, la plus-value d'une citation ici me semble limitée.
+Plus fondamentalement, l'argument me semble incomplet.
+OK, les préférences shallow ont toutes les chances de n'être pas transitives.
+Mais pourquoi penser que les préférences réfléchies le seraient ?
+Il manque un argument}
 
@@
 For example, \citet{bleichrodt_making_2001} transform observed preferences in order to obtain a classical Expected Utility model; \citet{bernheim_beyond_2009} propose to exclude situations where the individual seems (by objective criteria) unable to process information considered (by the theorist) as relevant information.
-
-This creates a risk of mis-representing the reflective preferences of the individual: not only is it not known whether the individual would reflectively want to adhere to these axioms and, if so, how she would reflectively adapt her preferences when her shallow preferences exhibit related inconsistencies; but it is not even discussed how in principle this could be known.
-As a result, a theory postulating constraints on individual’s behavior on the basis of rational requirements is subject to the criticism addressed by \citet[p.\ 228]{dold_toward_2018} to libertarian paternalism, in that it “effectively denies the possibility that deviations from rational choice might be something to be acknowledged as reasonable”.
-That this is an important methodological problem is sometimes recognized by authors adopting this approach.
+\commentYM{les deux mécanismes évoqués sont très différents, et ont des enjeux différents.
+Je pense qu'il serait utile de les distinguer, et je pense qu'il faudrait en dire plus sur la nature de la transformation et du filtrage, sans quoi la discussion des ces approches est trop superficielle}
+
+This \commentYM{what?
+ici on voit qu'on gagnerait à savoir concrètement quelle est la manip déployée par les auteurs ci-dessus}creates a risk of mis-representing the reflective preferences of the individual: not only is it not known whether the individual would reflectively want to adhere to these axioms \commentYM{quels axiomes ?
+besoin d'expliquer + en détail ce que font ces auteurs ; et tu sembles pressupposer ici qu'adéhrer aux axiomes et s'approprier une transformation ou un filtre basé sur des axiomes, c'est la même chose, ce qui ne me semble pas évident}and, if so, how she would reflectively adapt her preferences when her shallow preferences exhibit related inconsistencies; but it is not even discussed how in principle this could be known \commentYM{phrase en + super longue : arrivée à la fin, je suis perdu}.
+As a result, a theory postulating constraints on individual’s behavior \commentYM{je ne comprends pas de quelles contraintes sur le comportement il est question ici.
+Les théories des laundered preferences que je connais n'imposent aucune contrainte au COMPORTEMENT.
+Cela souligne encore une fois qu'il faudrait être plus prolixe sur la description des approches dont tu parles}on the basis of rational requirements is subject to the criticism addressed by \citet[p.\ 228]{dold_toward_2018} to libertarian paternalism, in that it “effectively denies the possibility that deviations from rational choice might be something to be acknowledged as reasonable”.
+\commentYM{phrase bien alambiquée, qui fait référence à un concept ("libertarian paternalism") que je pense abscond pour bien des gens (dont moi).
+Je pense que tu devrais reformuler, donner l'argument plus directement, et si tu y tiens mettre entre parenthèse que cet arguement est utilisé dans un autre débat par x et y quand ils parlent de LP}
+That this is an important methodological problem is sometimes recognized by authors adopting \commentYM{endorsing}this approach \commentYM{je pense qu'en anglais il est + idiomatique d'éviter ce genre de tournure : plutôt dire "Authors...
+sometimes recognize that..."}.
 \Citet{bleichrodt_making_2001}, for example, state that laundering require controversial assumptions (p.\ 1500), and recommend it only as a last resort, recommending discussing with the decision-maker whenever possible to elicit her reflective preferences (p.\ 1499).
@@
 \citet{sen_maximisation_1997} illustrated this reasoning (with another axiom) with his well-known example of a person picking her second most-preferred fruit from a basket out of politeness reasons, which could be considered irrational by an analyst blindly applying WARP.
-As \citet[p.\ 40]{lecouteux_reconciling_2015} puts it (citing \citet[p.\ 13]{bacharach_beyond_2006} for the part in italics), and as analyzed by \citet{sen_information_1986, sen_internal_1993}, “whether a decision-theoretic principle of rationality has been violated \emph{depends on how we, the theorists, ‘cut up the world’}” \TODO{Find that book}.
+As \citet[p.\ 40]{lecouteux_reconciling_2015} puts it (citing \citet[p.\ 13]{bacharach_beyond_2006} for the part in italics), and as analyzed by \citet{sen_information_1986, sen_internal_1993}, “whether a decision-theoretic principle of rationality has been violated \emph{depends on how we, the theorists, ‘cut up the world’}” \TODO{Find that book}.\commentYM{Je § tout entier me semble mal placé ici.
+Les considérations évoquées sont relatives au choix d'un "bon" axiome, problématique classique dans les discussions des théories du choix rational, mais dont le lien avec le laundering des préférences ne crève pas les yeux.
+Il y a des moyens de faire le lien, mais là tu n'expliques aucun lien.
+Donc ton § tombe comme un cheveux sur la soupe et le lecteur est embrouillé, ne se rappelle même plus quel était l'object de la sous-sous section qu'il vient de lire}
 
 \subsubsection{Informal deliberation}
-Another path to obtain reflectful preferences has been followed: the one of deliberation, an umbrella term by which I designate processes, either, involving discussions between an analyst and a decision-maker while querying her preferences in view of building a formal model of it \citep{raiffa_back_1985, keeney_decisions_1993, roy_multicriteria_1996, belton_multiple_2002}, or involving group discussions, with presentations from experts to an audience and internal deliberation phases \citep{fishkin_when_2011}, aiming to obtain well-informed preferences.
-
-A major problem of these techniques is that they are not easily reproducible, and that the resulting preferences elicited from the subjects might reflect properties of the personalities of the intervening experts or group-dynamic effects rather than true reflective preferences of the individuals \commentOCf{Yves, as-tu une référence pour moi ?}.
-This problem is exacerbated by the fact that psychologists have shown that apparent coherence can appear, that is, preferences that do not violate axioms usually considered as representing rationality, although some framing effect may be at play that result in the apparently coherent preferences to arguably not represent reflective preferences \citep{ariely_predictably_2010}.
+Another path to obtain reflectful \commentYM{reflective ?} preferences has been followed: the one of deliberation, an umbrella term by which I designate processes, either, involving discussions between an analyst and a decision-maker while querying her preferences in view of building a formal model of it \commentYM{them ?} \citep{raiffa_back_1985, keeney_decisions_1993, roy_multicriteria_1996, belton_multiple_2002}, or involving group discussions, with presentations from experts to an audience and internal deliberation phases \citep{fishkin_when_2011}, aiming to obtain well-informed preferences.
+\commentYM{il me semble nécessaire ici de mentionner aussi tous les dispositifs participatifs et de concertation employés en routine dans les prises de décisions relatives aux politiques publiques et leur mise en oeuvre}
+
+A major problem of these techniques is that they are not easily reproducible \commentYM{il faudrait expliquer en quel sens}, and that the resulting preferences elicited from the subjects might reflect properties of the personalities of the intervening experts or group-dynamic effects rather than true reflective preferences of the individuals \commentOCf{Yves, as-tu une référence pour moi ?}\commentYM{on a mis des références pertinentes pour les différents aspects dan le papier soumis à Ecol Econ.
+Ces références ne te conviennent pas ?}.
+This problem is exacerbated \commentYM{compounded} by the fact that psychologists have shown that apparent coherence can appear, that is, preferences that do not violate axioms usually considered as representing rationality, although some framing effect may be at play that result in the apparently coherent preferences to arguably not represent reflective preferences \citep{ariely_predictably_2010} \commentYM{phrase beaucoup trop longue pour être compréhensible, qui fait par ailleurs référence au concept de rationalité sans le définir, ce qui est acceptable en début d'intro, mais me semble problématique à ce stade dans un papier qui cherche à éclairer les débats flous par des clarifications formelles et conceptuelles}.
 It also remains to be clarified how to check on a principled, systematic basis, whether all relevant arguments have been presented faithfully.
-Comfronted with (possibly self-designated) experts with enough assertiveness, a decision-maker can be convinced to follow principles of decision-making that several experts in the field of decision-theory consider incorrect.
-As an illustration, after discussing the weaknesses of the \ac{AHP}, \citet[p.\ 53]{howard_foundations_2007} write: “Why, then, do inferior processes find favor with decision makers?
-The answer is that they do not force you to think very hard or to think in new ways.”
+Comfronted with (possibly self-designated \commentYM{ceci est un tout autre problème, dont la mention ici brouille le propos}) experts with enough assertiveness, a decision-maker can be convinced to follow principles of decision-making that several experts in the field of decision-theory \commentYM{would} consider incorrect.
+As an illustration, after discussing the weaknesses of the \ac{AHP}, \citet[p.\ 53]{howard_foundations_2007} write \commentYM{s}: “Why, then, do inferior processes find favor with decision makers?
+The answer is that they do not force you to think very hard or to think in new ways.” \commentYM{je ne vois pas en quoi ceci est censé illustrer le propos précédent (ou alors je n'ai rien compris à la citation).
+J'ai l'impression que la citation dit que, parfois, il y a des forces psychologiques qui s'opposent à l'adoption d'un processus de décision, quand bien même celui-ci aurait des qualités indéniables}
 Beyond the controversial \ac{AHP}, famous decision analysts have voiced disagreements with normative theories of decision making \citep{ellsberg_risk_1961, allais_so-called_1979} that are however generally applied in the field.
+\commentYM{il me semble ici intenable de faire l'économie de définir ce que tu appelles "normative theories"}
 \Citet[p.\ 669]{ellsberg_risk_1961} concluded his influential article as follows: “[In some situations, for some people,] the Bayesian or Savage approach gives [...] bad advice.
 [Some people] act in conflict with the axioms deliberately, without apology, because it seems to them the sensible way to behave.
-Are they clearly mistaken?”
-This rethorical question illustrates the need of systematic procedures able to determine whether decision-makers, when confronted with the relevant arguments, accept the soundness of the principles on whose basis the recommendation rests (this has been somewhat explored, but not systematically, for current lack of a systematic way of confronting decision makers to arguments \citep{slovic_who_1974, stanovich_discrepancies_1999}).
-
-As a consequence of these techniques being not completely formalised and reproducible, each application requires manual intervention of (very skilled) experts.
+Are they clearly mistaken?” \commentYM{d'une manière générale, dans toute la section 1, l'avalanche de citation me semble nuire au propos.
+Cela induit des ruptures dans le style, et force le lecteur à se pencher sur des questions d'interprétation des citations qui l'empêchent de se focaliser sur ton propos à toi}
+This rethorical question illustrates the need of systematic procedures able to determine whether decision-makers, when confronted with the relevant arguments, accept the soundness of the principles on whose basis the recommendation rests \commentYM{the principles that the recommendation rests on}(this has been somewhat explored, but not systematically, for current lack \commentYM{for lack} }of a systematic way of confronting decision makers to arguments \citep{slovic_who_1974, stanovich_discrepancies_1999}).
+
+As a consequence of these techniques being not \commentYM{not being}completely formalised and reproducible, each application requires manual intervention \commentYM{quelles sont ces "interventions manuelles" ?
+à expliquer}of (very skilled) experts.
 Eliciting reflective preferences therefore requires enormous resources.
@@
 There is, to reduce this cost, a need for theories that can be iteratively improved upon and yield reusable knowledge about reflective preferences.
+\commentYM{Cette idée de limiter le coût est intéressante, et je me dis qu'elle peut faire mouche avec certains lecteurs.
+Mais en l'état ça ne fonctionne pas car tu ne expliques pas quels sont les coûts impliqués dans les approaches "manuelles"}
 
@@
 Some analysts admit this possibility and do not consider it to be a problem.
+\commentYM{il me semble que tu soulèves là encore un nouveau problème : comme la notion de rationalité n'est pas claire, il y a débat sur les axiomes qu'on peut vouloir lui associer, et du coup différentes approches, choisissant différents axiomes, vont éliciter des préférences différentes.
+Je te rejoins sur le fait que c'est un problème important, mais il est différent de ce qui a été discuté juste avant, et tu ne l'explicites pas.
+Il me semble qu'il faudrait bien distinguer les problèmes, et bien les formuler, et il faudrait que le plan soit plus clair et lisible.
+Là, en lisant, je ne sais pas si tu considères ce que tu abordes dans ce § comme un nouveau problème, ou comme un aspect ou une implication, du problème exploré précédemment}
 For example, \citet[p.\ 214]{roy_comparison_1995} write: “In our view, these inevitable disagreements do not imply that decision-aid is useless but simply that a single problem may have several valid responses.
 Given that two different decision-aid models cannot be implemented in the same decision process, the decision-maker must be conscious of the qualitative choices implied by the different models – often conveying the analysts’ own ethical choices – before coming to personal conclusions on the choice to be made.
-In this domain, the many different approaches reflect in our view the complexity of the researcher's task much more than a scientific weakness.”
-Although being an important insight about the (likely vain) hope of determining a single correct recommendation in many complex decision situations (about which more below), this answer does not address the problem that some principles of decision making may be wrong guides in some situations, possibly including some principles that are commonly applied in the field, hence the need of principled ways of discriminating them.
+In this domain, the many different approaches reflect in our view the complexity of the researcher's task much more than a scientific weakness.”\commentYM{ici encore, je fais une overdose de citations.
+Et je ne trouve pas celle-ci particulièrement éclairante pour ton propos.
+Certes il y a un lien entre ce que tu dis et ce que dit cette citation, mais elle n'est pas vraiment une illustration de ce que tu dis.
+Du coup elle brouille le message}
+Although being an important insight about the (likely vain) hope of determining a single correct recommendation in many complex decision situations (about which more below), this answer \commentYM{quelle answer ?
+à quelle question ?
+je suis perdu}does not address the problem that some principles of decision making may be wrong guides in some situations, possibly including some principles that are commonly applied in the field, hence the need of principled ways of discriminating them.
+\commentYM{est-ce vraiment ton projet ?
+as-tu l'intention de trouver la meilleure des axiomatiques de décision ?
+si c'est ton projet, il faut le dire clairement.
+Ce que je comprennais jusqu'ici était que tu cherchais un moyen de connaître les "preferences that represent informed, pondered decisions, that would be taken after due consideration by the individual", ce qui me semble être un tout autre projet}
 
 \subsection{Some other related approaches}
+\commentYM{related to what? to your approach or to the one explored above?}
 The prescriptive approach to decision making \citep{bell_decision_1988} has been proposed (in supplement to the normative one and the descriptive one), which insists on incorporating the findings of psychologists about decision maker’s weaknesses of reasoning in the procedures leading to recommendations.
-I do not discuss this approach specifically here, because its methods can be considered to fall into the two categories I have described here above when it aims at obtaining reflective preference models.
-When considering normative economics broadly, as I do here, as the methods aiming for valid prescription for an individual or a group, prescriptive approaches are a part of normative economics.
-
-Some authors have proposed to ground normative theories on observable aspects of nature and individuals, to solve some of the problems mentioned above; for example, \citet{kahneman_back_1997} propose to measure “experienced utility”, considered as a hedonic quality.
-To the best of my knowledge, these proposals never aim at observing reflective preferences as considered here and thus fall outside the scope of this article.
+I do not discuss this approach specifically here, because its methods can be considered to fall into the two categories I have described here above when it aims at obtaining reflective preference models \commentYM{j'ai rien compris.
+L'approche prescriptive tombe DANS LES DEUX CATEGORIES EN MEME TEMPS ?
+Il faut expliquer ce que tu racontes là}.
+When considering normative economics broadly, as I do here, as the methods aiming for valid prescription for an individual or a group, prescriptive approaches are a part of normative economics \commentYM{dans le papier sur la rationalité avec Alexis, on discute les faiblesse de la catégorisation de Bell et al., et je pense que ce qu'on dit va dans ton sens.
+Tu pourrais nous citer : ça me permettrait d'avoir 1 citation : personne ne cite mes papiers...
+snif...
+Plus sérieusement, je me demande ce que la normative ECONOMICS vient faire ici.
+Selon moi, le prescriptif sensu Bell et al.
+est une sous-catégorie du normatif sensu Bell et al.}.
+
+Some authors have proposed to ground \commentYM{base} normative theories on observable aspects of nature and individuals, to solve some of the problems mentioned above; for example, \citet{kahneman_back_1997} propose to measure “experienced utility”, considered as a hedonic quality.
+\commentYM{il me semble qu'il faudrait être + précis ici : tous les problèmes mentionnées + haut ne peuvent pas être résolus par cette approche.
+Certains peuvent l'être, et encore, ça se discute, d'autres ne peuvent pas l'être.
+Si tu ne dissèques pas cela, ton affirmation semble creuse}To the best of my knowledge, these proposals never aim at observing reflective preferences as considered here and thus fall outside the scope of this article.
+\commentYM{tout à fait d'accord, mais du coup la manière dont tu les mentionnes les met trop en avant, surtout vu que tu dis qu'ils prétendent traiter certains des problèmes que tu explores précédemment.
+Il faudrait trouver une meilleure manière de faire référence à ces approches (on te reprocherait de ne pas les discuter), en passant, et en montrant plus clairement qu'elles sont hors champs ; probablement + en amont dans le texte}
 
@@
 This field however does not view the attack relation as observable, but considers it as given, and its methodology is therefore not empirical in the sense seeked for here.
-(\Citet{cailloux_formal_2019} elaborates on this difference of objective.)
+(\Citet{cailloux_formal_2019} elaborates on this difference of objective.) \commentYM{ici aussi, je trouve la mention de ces approches maladroite, car elles sont mises en exergue comme si elles étaient des manières de traiter le problème qui t'intéresse, ce qu'elles ne sont pas}
 
@@
 Examples include suggesting the individuals to consider alternative points of view, or asking them to give reasons for their choices (an insightful article by \citet{mitchell_libertarian_2004} cite many such studies).
-This proposal is situated at another level, which could be considered as a way of justifying and comparing such debiasing techniques with no need of a prior agreement on what constitutes a behavioral mistake.
+This proposal \commentYM{de quoi tu parles ?
+de TON proposal ?
+pas clair} is situated at another level \commentYM{qu'est-ce que ça veut dire ?}, which could be considered as a way of justifying and comparing such debiasing techniques with no need of a prior agreement on what constitutes a behavioral mistake.\commentYM{très cryptique.
+Je n'ai rien compris à ce §, et je me demande pourquoi tu ne traites pas des debiasing techniques dans la même sous-section que les laundering techniques, qui me semblent poser les mêmes problèmes}
 
 The current proposal pursues a path started with \citet{cailloux_formal_2019}, an article that defines the notion of \ac{DJ} and models that enable interactions with individuals whose \acp{DJ} are to be captured.
-That article however requires as fundamental observable a “trump” relation, indicating whether an individual thinks that an argument is against another argument; and a “support” relation, indicating whether an individual thinks that an argument supports a proposition.
-The current proposal defines every required concepts, such as the notion of arguments attacking other arguments, on the basis of a single observable that is compatible with the revealed preference approach priviledged in economic theory, in the sense that it can be defined by reference to what individuals effectively choose under various circumstances.
-The current proposal also defines explicitly (in the form of an axiom) sufficient requirements to grant normative power to observations, an aspect which was previously left unclear.
+That article however requires as fundamental observable a “trump” relation, indicating whether an individual thinks that an argument is against another argument; and a “support” relation, indicating whether an individual thinks that an argument supports a proposition.\commentYM{je ne pense pas qu'on puisse tenir pour acquis que le lectorat connait par coeur l'article delibenv.
+Il faut du coup donner plus d'explication.
+Par ailleurs, il est impératif que tu expliques pourquoi tu considères qu'il n'est pas raisonnable de considérer que trump et support sont observables} The current proposal defines every required concepts, such as the notion of arguments attacking other arguments, on the basis of a single observable that is compatible with the revealed preference approach priviledged in economic theory \commentYM{je ne pense pas qu'on puisse dire que l'approche RP est privilégiée en économie.
+Elle est aussi très critiquée.
+Si tu la considère particulièrement solide, il faut expliquer pourquoi}, in the sense that it can be defined by reference to what individuals effectively choose under various circumstances.
+The current proposal also defines explicitly (in the form of an axiom \commentYM{il n'y QU'UN axiome au final ?}) sufficient requirements to grant normative power to observations, an aspect which was previously left unclear.
 Finally, the current proposal links \ac{DJ} and deliberated preferences.
+\commentYM{indispensable de dire explicitement quelle est la différence entre les deux dès maintenant}
 
@@
 
-\subsection{This approach}
-The proposal of this article to capture reflective preferences while avoiding the just described problems is to define normative theories on the basis of a low demanding axiom complemented with principles of reasonings; that allow decision makers to “reconstruct” the reasoning proposed by the principles so as to be able to check that they apply to their situation; therefore permitting to falsify the theories using observable data representing the rejection by the decision makers of these principles.
+\subsection{This approach}\commentYM{The proposed approach}
+The proposal of this article \commentYM{the proposal developed/elaborated/presented in this article}to capture reflective preferences while avoiding the just described problems is to define normative theories on the basis of a low demanding axiom complemented with principles of reasonings; \commentYM{je devine que cette phrase est importante mais elle ne se comprend pas.
+Sans le ";" ici elle se comprendrait.
+Mais est-ce que c'est comme ça qu'il faut la comprendre ?
+".
+This" à la place de "; that" donne un autre sense : lequel est le bon ?}that allow decision makers to “reconstruct” \commentYM{pourquoi ce terme est-il mis entre guillemets ?
+généralement on fait cela quand on veut souligner que le terme doit être compris en un sens différent d'un sens habituel proéminent.
+Mais il me semble pas que "reconstruct" ait un sens habituel proéminent dans ce contexte.
+Donc je bloque et je me dis "j'ai loupé un épisode"}the reasoning proposed by the principles so as to be able to check that they apply to their situation; therefore permitting to falsify the theories using observable data representing the rejection by the decision makers of these principles \commentYM{phrase à ralonge, vraiment pas idiomatique en anglais, et à peu près impossible à suivre (du moins pour les lecteurs de ma catégorie)}.
 Such theories are therefore both normative and empirical: normative, in the sense of claiming to capture reflective preferences, which provide a better basis for recommendations or policy making than shallow preferences; and empirical, in the sense of the principles of reasoning being exposed to empirical tests.
@@
 It is not an ambition of this article to actually propose concrete theories of deliberated preferences, for this is not achievable in a single article; and the theories as defined here admittedly still suffer important weaknesses.
-The ambition of this article is accordingly limited to present a novel approach of capturing reflective preferences in simple enough settings.
+\commentYM{ce qui précède n'est pas compréhensible si t n'explicites pas ce que veut dire "theory" dans cet article.
+Par ailleurs, qu'est-ce qu'une theorie CONCRETE ?
+A quoi cela s'oppose-t-il ?
+Le lecteur se demande aussi en quoi cela consiste de "définir" une théorie (ce que tu sous-entends que tu vas faire) sans la "proposer" (ce que tu dis dépasser tes ambitions).
+Enfin, de quelles "weaknesses" parles-tu ?}The ambition of this article is accordingly limited to present a novel approach of capturing reflective preferences in simple enough settings.\commentYM{quel sens faut-il donner à "setting" ici ?
+dans certains cas, on peut employer ce genre de terme de manière vague sans que ça choque.
+Ici je pense que ce n'est pas possible, car le lecteur ne comprend pas où tu vas, ni ce que tu vas faire, ni pourquoi c'est compliqué, ni quelle est la complexité dont tu parles, ni ce qui peut faire qu'un setting est "simple enough" ou complexe}
 %This requires to define precisely what such theories should aim to capture; and how they should be compared, which is the sole ambition of this article. 
-Some challenges that must be overcomed in order to build concrete theories applicable in realistic settings will be discussed in conclusion.
+Some challenges that must be overcomed \commentYM{overcome}in order to build concrete theories applicable in realistic settings will be discussed in conclusion.\commentYM{tu pourrais mettre ce genre de phrase à la fin d'une annonce de plan, mais là comme ça, elle ne sert à rien}
 
 One long-term goal of this research program is to give individuals the means to reject theories that they find unconvincing after due consideration of all arguments; and accordingly, give incentives to decision theorists to build defenses of these theories able to convince individuals whose preferences are modeled of the soundness of these theories.
-This might match \possessivecite{hausman_debate_2010} suggestion that we should use rational persuasion rather than nudge individuals, arguing that it would promote autonomy.
+\commentYM{phrase trop longue}This might match \possessivecite{hausman_debate_2010} suggestion that we should use rational persuasion rather than nudge individuals, arguing that it would promote autonomy.
 It also follows \possessivecite[p.\ 72]{guala_logic_2000} suggestion (discussing the Allais paradox) about obtaining relevant data to compare normative behavioral theories: “Before asking whether agents want to revise their choices or not, \emph{both} rival theories should be proposed” (emphasis in the original text).
 
+\commentYM{arrivé à la fin de la section 1, je suis perplexe.
+Si ce n'est pas une introduction (ce que ça ne semble pas être, car ça ne s'appelle pas "introduction", qu'est-ce que c'est, et pourquoi n'y a-t-il pas d'introduction ?
+Si c'est une introduction, il faut l'appeler comme ça, c'est très long, il est inhabituel d'avoir des découpages en sous-sections en intro, il n'y a pas d'annonce de plan (ce qui manque cruellement), il me semble que la problématique n'apparaît pas clairement, le lien avec l'article delibenv devrait être plus clair.
+Par ailleurs, il me semble qu'il y a quelques trous importants dans la revue de la littérature.
+Je pense en particulier à R.E.
+Goodin, « Laundering preferences », in J.
+Elster & A.
+Hylland (eds.), Foundations of
+Social Choice Theory, Cambridge University Press, 1986, p. 75-102 ; J.C. Harsanyi, Rational Behavior and Bargaining Equilibrium in Games and Social
+Situations, Cambridge University Press, 1977 ; S.-C.
+Kolm, Macrojustice, Cambridge University Press, 2005, chap.
+19.; ainsi qu'à l'économie expérimentale à base de jeux comme N.
+Frohlich & J.
+Oppenheimer, Choosing Justice.
+An Experimental
+Approach to Ethical Theory, University of California Press, 1992 ; V. Clément & D. Serra,
+« Égalitarisme et responsabilité, une investigation expérimentale », Revue d’économie politique
+111, 2001, p. 173-193.}
+
 \section{Informal presentation}
+\commentYM{Le lecteur n'a aucune idée de ce qu'il doit s'attendre à trouver dans cette section, et de la mesure dans laquelle ça va permettre d'avancer dans la résolution de la problématique : lecteur perdu = pas bien}
 Although the final aim is about the concept of deliberated preference, which permits to compare alternatives (options in a decision problem), this article will mostly discuss \acp{DJ}.
@@
 
-For a clear separation of concern, this article defines first normative theories, then empirical theories for these normative theories.
-A normative theory makes normative claims only, which have to be accepted or rejected on the basis of the apparent soundness of the axiom on which it rests.
-An empirical theory for a given normative theory, by contrast, makes empirical claims, hence, can be confronted to observations.
+For a clear separation of concern, this article defines first normative theories, then empirical theories for these normative theories \commentYM{je ne comprends pas ce "for" ; je ne comprends pas pourquoi tu utilises une autre opposition que la classique normative vs.
+empirical.
+Par ailleurs, je ne comprends pas DE QUELLES théories tu parles.
+Es-tu en train de parler des théories exitantes, ou des théories dont le développement serait une partie de la réalisation du projet du présent papier ?
+Comme déjà dit plus haut, en fait je ne sais pas ce que tu appelles une "theory"}.
+A normative theory makes normative claims only, which have to be accepted or rejected on the basis of the apparent soundness of the axiom on which it rests \commentYM{par qui ?
+dans le cadre de l'analyse ou en amont ?
+et pourquoi sur la seule base de la soundness de l'axiome ?
+pourquoi pas sur la base de ses implications dans des cas concrets ?}.
+An empirical theory for a given normative theory, by contrast, makes empirical claims, hence, can be confronted to observations \commentYM{quelle différence avec les implications empiriques d'une théorie normative ?}.
 What I call here an empirical theory, for simplicity, is not however purely empirical, but can also be considered normative, for two reasons.
@@
 Second, it claims to capture preferences that provide an appropriate basis for recommendation.
-Empirical theories of \ac{DJ} could thus be called empirical normative theories of \ac{DJ}.
+Empirical theories of \ac{DJ} could thus be called empirical normative theories of \ac{DJ}.\commentYM{est-ce la même chose que ce qui est déjà appelé à peu près comme ça dans la littérature ?
+Je parle par exemple de toutes les théories empiriques de la justice}
 
@@
 As \citet[p.\ 16]{von_neumann_theory_2004} aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher”.
-The fundamental element of a normative theory of deliberated preferences is the reaction of an individual, whose preferences are to be captured, to arguments.
-
-Normative theories define an agenda: a set of propositions that we are interested in knowing the deliberated judgment of individuals about; a set of individuals that the theory claims applies to; a set of arguments; and a protocol of observation of the judgments an individual adopts towards a proposition after exposure to various arguments.
-
-Examples of propositions to be included in agenda include: “I ought to pay at most \$100 for purchasing bundle $b$”, “I ought to acquire alternative $a$ rather than $b$ if it is available in the same conditions”; “I ought not to perform action $a$ because it is immoral”.
-
-The set of individuals in a normative theory represents the situations, socio-economic conditions, acquired diplomas, or other observable features of individuals that must be satisfied for the theory to apply to them.
+The fundamental element of a normative theory of deliberated preferences is the reaction of an individual, whose preferences are to be captured, to arguments.\commentYM{la vision vNM est très réductrice, et ne peut pas être considérée, me semble-t-il, comme valable pour toutes les théories normatives, car l'idée qu'il doit y avoir des sensations, atomiques et immédiates relève de l'empirisme logique qui sous-tend leur approche, et cette épistémologie, ou ontologie à ce stade, est loin d'être partagée par toutes les approches à même de développer des théories normatives.
+Ta phrase qui suit risque de n'être pas beaucoup plus convaincantes pour les lecteurs, je le crains.
+Imaginons par exemple une théorie marxiste, elle s'appuiera sur des intérêts matériels, et se contre fout des réactions des individus aux arguments.
+On peut envisager par ailleurs des théories supra-individualistes, qui se foutent des réactions des individus.
+Mais bien entendu la pertinence de ce que je dis là dépend de ta réponse à ma première question dans l'intro du 2.
+Si ce dont tu parles ici, ce n'est pas des théories normatives existantes ou possibles, mais uniquement des théories normatives QUE TU ACCEPTES COMME ELEMENTS DE TA CONSTRUCTION, alors le problème est différent : il faut justifier TON adhérence à l'empirisme logique, ce qui n'est pas une mince affaire étant donné le discrédit qui lui est aujourd'hui attaché}
+
+Normative theories define an agenda: a set of propositions that we are interested in knowing the deliberated judgment of individuals about ; a set of individuals that the theory claims applies to; a set of arguments;\commentYM{pourquoi est-ce que cela fait partie de la théorie ?
+c'est plutôt un des éléments du contexte d'une de SES APPLICATIONS à mon sens.
+L'expression  "normative model" serait selon moi bien plus appropriée si on veut que les détails du cas d'application fassent partie de l'objet.
+"Theory" a de très fortes connotations de généralité} and a protocol of observation of the judgments an individual adopts towards a proposition after exposure to various arguments \commentYM{pourquoi le protocole d'obs est-il déjà évoqué ici ?
+j'aurais cru que ce protocole relève de la théorie empirique qui se greffe sur la théorie normative en question.
+Par ailleurs, je croyais que c'était l'axiome de la théorie normative qui devait être mis à l'épreuve, pas une instantiation sur une propositon.
+De l'axiome, il n'est plus question.
+Où est-il ?}.\commentYM{il manque dans la "theorie normative" ce que j'aurais considéré comme le plus important : un modèle de la force de conviction des arguments et de leurs liens avec les propositions.
+J'aurais dit que l'axiome de la "théorie" se cacherait là-dedans}
+
+Examples of propositions to be included in \commentYM{the}agenda \commentYM{might}include: “I ought to pay at most \$100 for purchasing bundle $b$”, “I ought to acquire alternative $a$ rather than $b$ if it is available in the same conditions”; “I ought not to perform action $a$ because it is immoral”.
+
+The set of individuals in a normative theory represents the situations, socio-economic conditions, acquired diplomas, or other observable features of individuals that must be satisfied for the theory to apply to them \commentYM{cela ressemble plus à un domaine d'application, qu'à un ensemble d'individus auxquels ça s'applique.
+Dans ce cas pourquoi ne pas le dire clairement ?}.
 (More about this in conclusion.
@@
 Arguments are defined here as anything that can be presented to an individual that may possibly influence her judgment.
-As an example, an argument can be a text presenting the features of an alternative, or arguing for the (im)morality of an action.
+As an example, an argument can be a text presenting the features of an alternative \commentYM{donc un texte qui ne prend pas de position sur l'alternative, qui est purement descriptif, est un argument ?
+cela me semble raisonnable, mais ça mérite discussion}, or arguing for the (im)morality of an action.
 The term argument evokes a debate, a metaphor appropriate for the comparison of theories that will be described later; but that should be taken with a grain of salt: an image, a tag price, a poem can be an argument in this article.
 
-The protocol of observation in a normative theory defines how the theory proposes to present a sequence of arguments to an individual, and how to observe her resulting judgment about a proposition of interest.
+The protocol of observation in a normative theory defines how the theory proposes to present a sequence \commentYM{qu'est-ce qu'une séquence ?
+y a-t-il une notion de temporalité ?
+de lien logique entre les arguments ?
+une nécessité que chaque élément de la "séquence" attaque le précédent ?
+les embranchements sont-ils exclus ?
+les cycles ?
+bref, de quoi parles-tu ?}of arguments to an individual, and how to observe her resulting judgment about a proposition of interest.
 This protocol permits to determine whether a sequence of arguments “leads” a given individual to a given proposition.
 If the arguments are texts and propositions are of the form “I ought to acquire alternative $a$ rather than $b$”, an example of such a protocol is: present each argument (each text) in the sequence to the individual, asking her to read it carefully; then give the individual a choice between $a$ and $b$; the sequence of arguments is considered to having led the individual to the proposition “I ought to acquire alternative $a$ rather than $b$” iff he chose $a$ rather than $b$.
-In order to allow for repeated observations with a given individual without modifying his endowment, this example protocol should either be content with purely hypothetical choices, or can make these choices binding by letting the individual know that one of his choices will be picked randomly at the end of the experiment and honored.
+In order to allow for repeated observations with a given individual without modifying his endowment \commentYM{en quel sens utilises-tu ce terme ici ?}, this example protocol should either be content with purely hypothetical choices, or can make these choices binding by letting the individual know that one of his choices will be picked randomly at the end of the experiment and honored.\commentYM{pas compris le second membre de l'alternative}
 
 The judgment of an individual towards propositions may evolve during her exposition to sequences of arguments.
-Of interest to theories of \ac{DJ} are the cases where a so-called decisive argument exists for a given proposition: an argument is decisive when its presence at the end of the sequence of arguments systematically leads the individual to the proposition, whatever the sequence of arguments.
+Of interest to theories of \ac{DJ} are the cases where a so-called decisive argument exists for a given proposition: an argument is decisive when its presence at the end of the sequence of arguments systematically leads the individual to \commentYM{accepting}the proposition, whatever the sequence of arguments.
 An argument is at the end of a sequence iff it is the last or before last argument of the sequence.
@@
 Some televisions just won’t sell; most of the time, people are unlikely to want 80\% of their wages to go into savings.
-It would be an overstatement to say of preferences, as Gertrude Stein said of Oakland, that “there is no there there.”
+It would be an overstatement to say of preferences, as Gertrude Stein said of Oakland, that “there is no there there.” \commentYM{ce § et le précédent me semble mériter plus que le reste une réécriture.
+Par ailleurs, je ne vois pas à quoi ils servent dans cette sous-section}
 
 This remark points towards the importance of allowing for incomplete theories of reflective preferences.
-As \citet{mandler_difficult_2001} discusses in details, it would be unrealistic to postulate that individuals would, after due reflection, in non trivial decision problems, adopt a well specified judgment about any possible proposition of interest.
+\commentYM{définir ce qu'il faut entendre ici par "incomplete"} As \citet{mandler_difficult_2001} discusses in details, it would be unrealistic to postulate that individuals would, after due reflection, in non trivial decision problems, adopt a well specified judgment about any possible proposition of interest.
 From this does not follow that \acp{DJ} do not exist, but that someone’s \ac{DJ} should not be considered to be necessarily complete. 
@@
 \subsection{Empirical theories}
-A normative theory defines how to determine that an argument is not decisive for a given proposition: suffices to find a sequence of arguments that does not lead to that proposition.
-This, in turn, under condition of accepting its normative validity, permits to know something about the \ac{DJ} of an individual.
+A normative theory defines how to determine that an argument is not decisive for a given proposition: suffices to find a sequence of arguments that does not lead to that proposition \commentYM{pas compris : tu veux dire "une séquence qui se termine par cet argument et qui n'amène pas à cette proposition ?}.
+This, in turn, under condition of accepting its normative validity \commentYM{mais c'est quoi cette "normative validiy" ?
+de quelles conditions parles-tu ?}, permits to know something about the \ac{DJ} of an individual.
 But this gives no concrete means to know someone’s \ac{DJ}.
-The set of potentially relevant arguments will generally be very large, and can’t be explored thoroughfully.
+The set of potentially relevant arguments will generally be very large, and can’t be explored thoroughfully \commentYM{certain que ce terme existe ?}.
 More importantly, only some sequences of arguments can be tested for a given individual.
@@
 Postulating that the individual forgets after some time and separating the tests in time might mitigate this problem, but not necessarily cancel it.
+\commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question.
+Je doute cependant qu'un lecteur innocent comprenne un traitre mot}
 
@@
 They are called the proposition that the theory supports.
-The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments.
+\commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi} The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments.
 This is accomplished by three binary relations, part of the definition of empiricial theories: one represents its initial arguments, one plans the possible attacks, and one defines its counter-arguments.
@@
 
-Thanks to these operators, an empirical theory may adjust its argumentation to each individual.
+Thanks to these operators, an empirical theory may adjust its argumentation to each individual \commentYM{je ne comprends pas cette phrase, et en particulier le sens qu'il faut donner au terme "adjust"}.
 Instead of having to give a single decisive argument in support of its claims, the theory may react to exactly the counter-arguments that a given individual thinks relevant.
-This task is easier, but still permits to obtain what is desired in this article: there exists a purely empirical property of a theory, called convincingness, that, together with an axiom about the normative adequacy of the observation protocol, implies the correctness of the claims of the theory.
+This task is easier, but still permits to obtain what is desired in this article: there exists a purely empirical property \commentYM{kezako ?}of a theory, called convincingness, that, together with an axiom about the normative adequacy of the observation protocol, implies the correctness of the claims of the theory.
 In more details, first, the claim of the theory, of being able to argue convincingly, can be checked by ensuring that no falsification instances exist, thus, it is a fully empirical claim (in the sense that it requires no axiom).
@@
 
+\commentYM{arrivé à la fin du 2, je n'ai qu'une très vague idée de ce que sont ce que tu appelles des "theories normatives" et des "théories empiriques".
+Pour un lecteur comme moi du moins, cette section ne joue donc pas son rôle, qui je présume, est de donner une idée du contenu avant d'entrer dans le formalisme.}
+
 \section{Normative theories}
+
 \subsection{Definition}
@@
 (The calligraphic letter $S$ is used to denote the arguments in order to reserve the letter $A$ for sets of alternatives.)
-Given a set of arguments $\allargs$, define the set of finite sequences of elements in $\allargs$ (including the empty sequence) as $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$.
+Given a set of arguments $\allargs$, define the set of finite sequences of elements in $\allargs$ \commentYM{qu'est-ce qui lie les uns aux autres les éléments d'une séquence ?
+pourquoi est-ce que ça s'appelle une "séquence" ?
+une connotation temporelle ?
+une idée de succession ?}(including the empty sequence) as $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$.\commentYM{la notation $\allhist$ rend les choses inutilement difficiles à lire.
+Pourquoi noter ça comme on noterait $\allargs$ sans le zéro, si ça voulait dire quelque chose ?
+J'aurais inventé un symbole du genre $ \allargs^{\intvl{}}$ ; par ailleurs je trouve l'explication relative à l'empty sequence particulièrement alambiquée}
 Throughout the article, $\N$ includes zero and $\N^* = \N \setminus \set{0}$.
@@
 Equivalently, given any individual $i \in I$, ${\ileadsto}: \allhist → \allprops$ maps paths to propositions for this individual. 
-Given an individual $i \in I$, a path $\hist$ and a proposition $\prop$, the path is said to lead to the proposition for this individual iff $\hist \ileadsto \prop$.
+Given an individual $i \in I$, a path $\hist$ and a proposition $\prop$, the path is said to lead to the proposition for this individual iff $\hist \ileadsto \prop$.\commentYM{la correspondance entre cette définition et la définition du protocole donné dans la partie informelle est pour le moins difficile à voir.
+Où cette défintion formelle spécifie-t-elle comment on observe quoi ?
+Il me semble que ça ressemble + à une définition formelle de ce que je disais plus haut manquer dans ta définition}
 
 A normative theory is a tuple $(\allprops, \allargs, I, {\allleadsto})$ 
-satisfying the constraints described here above.
+satisfying the constraints described here above \commentYM{lesquelles ?
+je pense qu'un article doit guider le lecteur pour in fine le convaincre, pas tester ses capacités à retrouver son chemin dans un dédale.
+Quelles sont les contraintes en question ?
+Ou sont elles decrites "here above" ?}.
 
@@
 
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstost \prop$.
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstost \prop$.\commentYM{comprends pas.
+Tu définis $\ileadstost$ par $\ileadstost$.
+A part dans une définition par récurrence, qui réclame une conditions initiale, je ne vois pas comment une telle définition peut définir quoi que ce soit}
+\commentYM{et que va-t-on lire dans la suite ? faut un tout petit peu tenir la main du lecteur}
 
 \subsection{Coherence}
+\commentYM{qu'est-ce que le lecteur doit s'attendre à trouver dans cette section ? Le plan n'est pas compréhensible si tu n'en dis rien}
 \begin{axiom}[Normative adequacy]
@@
 \end{axiom}
+\commentYM{où est défini $\iprops$ ?
+Par ailleurs, je pense qu'il faut expliquer le sens des axiomes, sinon l'article ne peut pas être convaincant ; enfin, pourquoi cet axiome s'appelle-t-il ainsi ?
+cela ressemble plus à un critère de validité empirique quà un critère normatif.
+Mais peut-être mon incompréhension vient-elle du fait que je ne comprend pas ce que dénote $\iprops$}
 
@@
 \end{proposition}
+\commentYM{de même que je trouve très ténu et elliptique le lien entre le protocole dans sa description informelle et dans sa définition formelle, de même je trouve très dérangeant de mettre de terme "protocole" dans le nom de ce genre de proposition.
+Que l'usage de ce terme ait été choisi par provocation ou non, il me semble indispensable de le discuter}
 \begin{proof}
@@
 
-To further analyze this and related matters, consider defined a negation operator $¬$ on $\allprops$.
+To further analyze this \commentYM{analyser quoi ?
+qu'y a-t-il à analyser et pourquoi voudrait-on l'analyser ?}and related matters, consider defined a negation operator $¬$ on $\allprops$.
 $¬$ is a negation operator iff it is an involution operator (thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$) and furthermore satisfying, $\forall \phi \in \allprops: \hist \ileadsto \prop ⇒ \hist \nileadsto ¬\prop$.
@@
 The next proposition ensures an unambiguous interpretation of the content of $\iprops$ for all $i$-decidable propositions.
-The symbol $\oplus$ denotes the exclusive disjunction; thus $\prop \in \iprops \oplus ¬\prop \in \iprops$ is equivalent to: $\prop \in \iprops ⇔ ¬\prop \notin \iprops$.
+The symbol $\oplus$ denotes the exclusive disjunction; thus $\prop \in \iprops \oplus ¬\prop \in \iprops$ is equivalent to: $\prop \in \iprops ⇔ ¬\prop \notin \iprops$ \commentYM{au moins dans les propositions et définitons de cette section, l'introduction  de cet opérateur n'apporte rien, et rend la lecture inutilement difficile}.
 It can be seen to hold by using \cref{th:protcoh}.
@@
 This interpretability is however restricted to the $i$-decidable propositions.
-The following definitions and propositions (assuming a normative theory and a negation operator $¬$ defined) argue that going further is not desirable.
+The following definitions and propositions (assuming a normative theory and a negation operator $¬$ defined) argue \commentYM{"suggest" ou "show", mais je ne pense pas qu'on puisse dire que des "definitions" ou "propositons" "argue" quoi que ce soit}that going further is not desirable.
 
@@
 \end{proposition}
-Theories as defined here do not mandate Theory completeness.
-This is good for two reasons.
+Theories as defined here do not mandate Theory completeness.This is good for two reasons.
 First, even the weaker Deliberation completeness can be considered too strong.
 Second, it is dubious that, for non trivial decision problems, theories can be found for which both Normative adequacy is normatively compelling and Theory completeness holds.
+
+\commentYM{dans toute cette section, il me semble qu'il faudrait soit des exemples, soit des explications verbales}
 
@@
 An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ relates some arguments to some propositions.
-Its role in an empirical theory is to define the propositions that the empirical theory supports (corresponding to $\gpropse$, the range of ${\gleadsto}$) and, for each such proposition, to define the arguments that the theory wants to use as initial arguments to argue in favor of this proposition.
+Its role in an empirical theory is to define the propositions that the empirical theory supports (corresponding to $\gpropse$, the range of ${\gleadsto}$) and, for each such proposition, to define the arguments that the theory wants to use \commentYM{"that the theory uses" ?}as initial arguments to argue in favor of this proposition.
 The set of initial arguments is $\gleadstoinv(\allprops) = \set{\ar \in \allargs \suchthat \exists \prop \in \allprops \suchthat \ar \gleadsto \prop}$.
@@
 They are primitive elements that can be added to selected other fragments and arguments to form new arguments.
-They are used to dynamically build defensive arguments against the planned attacks.
+They are used to dynamically build defensive arguments against the planned attacks.\commentYM{je n'ai rien compris à ce §.
+Que veut dire "primitive" dans la seconde phrase ?
+Qu'apporte "selected" dans cette même phrase ?
+Ne peut-on pas l'enlever ?
+Que signifie "dynamically build" dans la dernière ?}
 
 A defense relation ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is an injective and surjective binary relation over $\alldargs × \gbeatsinv(\allargs)$.
-Thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton.
+\commentYM{le fait qu'elle soit surjective et injective est une exigence que tu poses dans la définiton ?
+pourquoi ?
+à quoi est-ce que cela sert ?} Thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton.
 Note that $\dbeats$ need not be a bijection as it is generally not a function. 
-Given $\ar_1 \in \gbeatsinv(\allargs)$, $\dbeatsinv(\ar_1)$ represents the fragment that the theory $\gamma$ plans to use as a defense against the planned attack $\ar_1$.
-
-A fragment is said to defend an argument iff it is used as a defense against a planned attack against that argument.
+Given $\ar_1 \in \gbeatsinv(\allargs)$, $\dbeatsinv(\ar_1)$ represents the fragment that the theory $\gamma$ plans to use as a defense against the planned attack $\ar_1$.\commentYM{dans toute cette sous-section la lecture est rendue très difficile par ce genre de formulation qui assigne une intentionnalité à la théorie.
+Je ne comprends pas le sens métaphorique de ces phrase, donc je ne les comprends pas}
+
+A fragment is said to defend an argument iff it is used as a defense against a planned attack against that argument \commentYM{"it is used" par qui, comment ?
+De quoi tu parles là ?
+Des stratégies argumentatives que contient la "théorie empirique" ?}.
 Formally, given any set $S$, define $\powersetz{S}$ as the set of subsets of $S$ without the empty set.
@@
 This mechanism permits to define defenders of defenders of an argument, $\dfp(\dfp(\ar))$, defenders of defenders of defenders of an argument, … An empirical theory must however be a priori restricted in the maximal “depth” of its argumentation strategy, in the following sense.
+\commentYM{ok soit, ça semble raisonnable, mais tu n'as pas de raison plus forte, j'adopterais une formulation plus modeste et ouverte, du genre "ça semble souhaitable"}
 Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
@@
 
-An empirical theory (for a normative theory) can now be defined as a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ satisfying the constraints described here above.
+An empirical theory (for a normative theory) can now be defined as a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ \commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}satisfying the constraints described here above \commentYM{ici encore : lesquelles ?
+définies où ?
+pas possible de suivre si tu donnes pas un peu la main au lecteur}.
 
@@
 \subsection{Empirical tests}
+\commentYM{Dans toute cette sous-section, il y a vraiment ENORMEMENT de notations.
+En conséquence, au moins pour moi, c'est extrêmement difficile à suivre.
+D'où le fait qu'il y a moins de commentaires de ma part à partir de là : je peine à suivre et du coup j'ai plus de mal à prendre du recul}
 Given $\args \subseteq \allargs$, $\hist \in \allhist$, and letting $l$ denote the length of $\hist$,
@@
 Given $\prop \in \allprops, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \prop)$ or $(\hist, \ar_\delta)$ challenges $(\delta, \propbar)$.
+
+\commentYM{il faudrait tenir la main du lecture : dire pourquoi tu définis ça.
+Ca se comprends, je sais, mais ça demande au lecteur un gros effort qui n'est pas récompensé par une impression de comprendre où ça va}
 

### 2020-10-17 simple.tex
Restoré compilation

@@
 \section{Motivation} 
-\commentYM{dans la mesure où tu dis concevoir ou avoir conçu ce draft comme étant presque soumettable, pourquoi as-tu cette section "motivation" plutôt qu'une classique introduction ?}}
+\commentYM{dans la mesure où tu dis concevoir ou avoir conçu ce draft comme étant presque soumettable, pourquoi as-tu cette section "motivation" plutôt qu'une classique introduction ?}
 It has escaped nobody’s attention that 
@@
 Cela induit des ruptures dans le style, et force le lecteur à se pencher sur des questions d'interprétation des citations qui l'empêchent de se focaliser sur ton propos à toi}
-This rethorical question illustrates the need of systematic procedures able to determine whether decision-makers, when confronted with the relevant arguments, accept the soundness of the principles on whose basis the recommendation rests \commentYM{the principles that the recommendation rests on}(this has been somewhat explored, but not systematically, for current lack \commentYM{for lack} }of a systematic way of confronting decision makers to arguments \citep{slovic_who_1974, stanovich_discrepancies_1999}).
+This rethorical question illustrates the need of systematic procedures able to determine whether decision-makers, when confronted with the relevant arguments, accept the soundness of the principles on whose basis the recommendation rests \commentYM{the principles that the recommendation rests on}(this has been somewhat explored, but not systematically, for current lack \commentYM{for lack} of a systematic way of confronting decision makers to arguments \citep{slovic_who_1974, stanovich_discrepancies_1999}).
 
@@
 Goodin, « Laundering preferences », in J.
-Elster & A.
+Elster \& A.
 Hylland (eds.), Foundations of
@@
 19.; ainsi qu'à l'économie expérimentale à base de jeux comme N.
-Frohlich & J.
+Frohlich \& J.
 Oppenheimer, Choosing Justice.
 An Experimental
-Approach to Ethical Theory, University of California Press, 1992 ; V. Clément & D. Serra,
+Approach to Ethical Theory, University of California Press, 1992 ; V. Clément \& D. Serra,
 « Égalitarisme et responsabilité, une investigation expérimentale », Revue d’économie politique

### 2020-10-20 simple.tex
Meilleure intro

@@
 
-\section{Motivation} 
-\commentYM{dans la mesure où tu dis concevoir ou avoir conçu ce draft comme étant presque soumettable, pourquoi as-tu cette section "motivation" plutôt qu'une classique introduction ?}
-It has escaped nobody’s attention that 
-studying reflective preferences, in supplement to shallow preferences, is an important endeavor for economics: we want to recommend to individual decision makers; we want to adopt optimization criteria for society, and this ought not to merely faithfully reproduce unreflectful behavior.\commentYM{je trouve cette entame provocatrice assez maladroite, car elle s'appuie sur l'opposition reflective vs.
-shallow preference, qui ne parle (je pense) pas immédiatement au lecteur.
-Je pense indispensable de définir cette dichotomie avant d'en parler.
-Par ailleurs que veut dire "is an important endeavor for economics" ?
-Il me semble au contraire que c'est une tâche qui devrait tenir à coeur aux économistes, mais qui pourtant n'est pas pour eux une tâche à laquelle ils s'attèlent vigoureusements.
-Enfin, l'anglais de cette phrase me semble un peu maladroit} This is one important difference between the normative and the (inappropriately called, as will be seen) “descriptive” approach in economics\commentYM{où discutes-tu cette distinction, dans son application à l'économie en particulier ?}.
-As \citet{hausman_preference_1994} illustrate with an example of a person drinking a fatal poison while erroneously thinking that it is water, shallow preferences are not sufficient to inform normative economics.
-Yet, classical methods to obtain preference models in economics are either formally defined on the basis of observable data that do not describe reflective preferences, or are obtained by other means than observable preferential data and systematic reproducible formal procedures.
-\commentYM{je devine ce que tu veux dire, mais je ne comprends pas la dernière phrase.
-Il me semble important que tu t'expliques ici, car je pense que le lecteur ici ne peut pas comprendre la niche dans laquelle s'inscrit ton projet}
-
-This article is interested in defining theories of decision making based on another kind of observable data\commentYM{other than what?
-Juste avant tu dis que les autres s'appuient sur des données qui ne reflètent pas les préférences qui t'intéressent, et maintenant tu dis que tu vas regarder autre chose qu'eux.
-Cela donne l'impression que tu tournes autour du pot, car tu ne dis pas ce que les autres regardes et pourquoi ça ne t'intéresse pas}, namely, the reactions of decision makers to arguments.
-This permits to overcome a current important limitation of normative approaches, that of being not empirical (in a sense that will be developed below).\commentYM{phrase incompréhensible pour le lecteur, puisque tu dis toi même que tu en expliqueras les termes plus tard.
-C'est une rhétorique difficile à tenir dans une introduction}
-
-By reflective preferences (of an individual), I mean here preferences that represent informed, pondered decisions, that would be taken after due consideration by the individual.
-Reflective preferences can be contrasted to shallow preferences, those that \citet[p.\ 16]{von_neumann_theory_2004} describe as “intuitive”, as originating from an “immediate sensation” (cited in \citet{fishburn_retrospective_1989}).
+\section{Introduction} 
+Decision theoretic approaches in economy divide into (at least) two sub-fields.
+Normative approaches aim at prescribing decision behavior; descriptive approaches aim at describing decision behavior.
+This partition is not always (depending on the authors) considered a complete cover of decision theoretic approaches in economy, but it is definitely considered disjoint.
+
+As a result, normative approaches are difficult to validate: being considered as non-descriptive in their goal, normative claims cannot be submitted to empirical tests that would permit to verify or falsify them.
+Instead, the validity of a normative approach is to be determined by examining the convincingness power of the normative axioms on which it rests.
+This validity criterion is unsatisfactory, as it is unable to settle disputes between experts when they arise.
+In supplement, agreement between experts in decision theory is arguably not enough to ground the practical applicability of some normative axioms: it is desirable to check that decision makers to which the prescription is addressed agree with the particular instanciation of these axioms in the specific decision problem under study.
+But no systematic, formally defined procedure has been proposed to proceed with this check, to the best of my knowledge.
+In practical applications, an expert may informally discuss the axioms with the decision maker in order to check endorsement, either in general, or by discussing violations on a case by case basis when they are observed during an interactive elicitation session.
+The resulting state of conviction arguably depends in part on the rethorical ability of the expert, not solely on the normative strength of the axioms.
+It may lead to a decision maker accepting a decision procedure considered unsound by many experts in the field, such as AHP.
+This problem is compounded by the enormous constraining power gained when axioms interact, as the celebrated theorem of Arrow shows dramatically: axioms that appear innocuous when taken alone may precipitate undesirable results when combined.
+
+By contrast, this difficulty of validation is much alleviated with descriptive approaches.
+Such approaches can be validated by comfronting their predictions to empirical data.
+When two descriptive theories disagree on their predictions, it is often possible to show that at least one of them is wrong with a suitable experiment.
+Alàs, descriptive approaches as currently existing in decision theory are not suitable to obtain valid prescriptions.
+
+This article defines decision theories, called theories of \ac{DJ}, that are both normative and descriptive: they claim to be able to yield valid prescriptions, and to allow confrontation to empirical data.
+
+It is by no means my intent to claim that descriptive approaches never face validation difficulties.
+Experimental tests to arbitrate between theories may not be feasible in practice, descriptions are not always solely about the future, falsificationist approaches in turn raise epistemological difficulties, and so on.
+Correspondingly, the possible confrontation to empirical data of the normative and descriptive theories defined here will likely not suffice to close every discussion about validation.
+My less naïve claim, that should suffice to motivate the present endeavor, is that it is often a good thing for a theory to make empirically testable claims, from the point of view of the possibilities of solving disputes and validating theories.
+
+As the plural indicates, this article defines a kind of theories, called theories of \ac{DJ}, not specific theories of \ac{DJ}.
+Specific theories of \ac{DJ} are tailored to a set of situations and yield claims relevant to those situations.
+For example, a specific theory of \ac{DJ} may be tailored to situations of choice between lotteries involving money.
+This article adopts a methodological point of view.
+It proposes a definition of what theories of \ac{DJ} should look like, and proves claims that hold for any specific theory of \ac{DJ}, showing that such theories are indeed normative and descriptive.
+
+\Cref{sec:approaches} defines more precisely what is meant here with normative and descriptive theories.
+These definitions permit to readily see why the apparent impossibility of a claim being both normative and descriptive is an illusion, thereby enabling a solution to what could be called the “normative against descriptive” gap.
+
+\section{Species of theories}
+\label{sec:approaches}
+For this article, a \emph{normative decision theory} is a theory that, when applied in the situations it self-describes as applicable to, claims to yield valid prescriptions.
+I consider a prescription in the wide sense: recommending against some behavior, or recommending conditionally, also counts as prescribing.
+
+A \emph{descriptive decision theory} is a theory that, when correctly applied in the situations it self-describes as applicable to, claims to predict the decision behavior of a given set of individuals.
+For this article, a claim counts as a prediction only when it is in principle possible to show that it is false using empirical data, thus predictions only apply to empirically observable data.
+
+I will simply write normative theory and descriptive theory from now on to mean normative and descriptive decision theories.
+
+For example, the \ac{SEU} theory of Savage is a normative theory.
+It may be used to recommend conditionally some behavior: “if you choose this lottery rather than that lottery, then you ought to \emph{not} choose this other lottery rather than that other lottery”.
+Examples of descriptive theories include the many variants of Prospect theory.
+
+These definitions avoid to define the concept of theory itself, for defining precisely such a fundamental concept raises serious difficulties.
+Is Prospect theory in general a theory, or only some of its variants, sufficiently precisely defined?
+Can a theory be extremely specific, or is some level of generality required to deserve being called a theory?
+Must a theory consist in a non-trivial assembly of laws, some being deducible from others?
+It is not necessary for the purpose of the present discussion to take position on these issues, rather, the focus is on the distinction between normative and descriptive approaches.
+An intuitive understanding of the concept of theory will suffice.
+Similarly, I sidestep insuperable difficulties pertaining to capturing in a short definition the concept of a descriptive theory in general: some descriptive theories may propose to describe without predicting, for example (historical decisions or trends come to mind); such endeavor simply does not enter the scope of this discussion, and I make no claim about its legitimacy to be called a descriptive theory in general.
+
+I say that a normative theory is also a descriptive theory when the prescriptions of the normative theory, in supplement of claiming to be valid prescriptions (in the situations that the theory claim to be applicable to), also claim to predict the decision behavior of a given set of individuals.
+
+Another contrast can now be introduced: the contrast between shallow and reflexive behavior. \emph{Shallow behavior} is defined as the everyday, usual behavior of an individual. 
+This is the behavior whose observation defines what \citet[p.\ 16]{von_neumann_theory_2004} describe as the “intuitive” preferences of an individual, those originating from an “immediate sensation” (cited in \citet{fishburn_retrospective_1989}).
+\emph{Reflexive behavior}, by contrast, is defined as the behavior that enacts informed, pondered decisions, those that would be taken after due consideration.
+% an individual has consciously adopted after having pondered everything that is possibly relevant to the decision. 
+%This pair of definitions is, again, vague and unsatisfactory for a deep philosophical discussion, but hopefully sufficient for the present one. 
+%What is meant by “pondering about everything that is possibly relevant to the decision” will be defined more precisely later; an intuitive understanding of this phrase will do at this stage.
 This distinction draws on our capacity, as human beings, to think about our shallow preferences and consider some of them as mistaken \citep{frankfurt_freedom_1971}. 
-\commentYM{ces définitions devraient être mises + haut, car le lecteur ne peut pas comprendre ce que tu racontes sans elles}A famous example of such a situation is the one of \citet[pp.\ 101--103]{savage_foundations_1972} having realized, after due consideration, that his initial declared preference in a decision problem presented by \citet{allais_so-called_1979} was mistaken.
-
+A famous example of such a situation is the one of \citet[pp.\ 101--103]{savage_foundations_1972} having realized, after due consideration, that his initial declared preference in a decision problem presented by \citet{allais_so-called_1979} was mistaken.
+
+This contrast raises a new distinction, which appears by simple combination of the just given definitions: a \emph{shallow descriptive theory} is a descriptive theory that claims to predict the shallow behavior of individuals; a \emph{reflexive descriptive theory} is one that claims to predict the reflexive behavior of individuals.
+
+The descriptive theories proposed in decision theory, in the sense defined here, are exclusively shallow descriptive theories, to the best of my knowledge.
+(\Cref{sec:laundering} discusses the theories that launder preferences.)
+%This need not be so. Indeed, this article introduces descriptive theories about reflexive behavior.
+This observation permits to understand what could be called the “normative versus descriptive gap”, implicit in the decision theoretic literature: because normative theories aim to prescribe, it is asked of them that they do not yield recommendations that precisely, systematically match shallow behavior.
+Given the numerous results in experimental psychology showing that shallow behavior is undefensible in many situations, a normative theory whose prescriptions would systematically match shallow behavior would be suspicious, to say the least.
+It is an immediate consequence of this minimal requirement that a normative theory cannot also be a shallow descriptive theory.
+As \citet{hausman_preference_1994} illustrate with an example of a person drinking a fatal poison while erroneously thinking that it is water, shallow behavior is not sufficient to inform normative economics.
+The “normative versus descriptive gap” comes from an implicit identification of descriptive theories with shallow descriptive theories.
+
+This gap can thus be overcome by considering reflexive descriptive theories, which is the path this article adopts.
+It defines theories that are both normative and descriptive: they attempt to deliver valid prescriptions, and these prescriptions are claimed to predict reflexive behavior.
+
+%This is done by defining on the one hand a non-observable set, containing those propositions that are valid prescriptions; and on the other hand an observable set, containing those propositions decisively defended by arguments, as judged by a given individual.
+This latter set is called the individual’s \ac{DJ}.
+%A normative axiom, that any theory of \ac{DJ} rests on, links these two sets by stating that what is in someone’s \ac{DJ} is a valid prescription.
+%This justifies the normative aspect of the theories. 
+%The theory yields descriptive claims thanks to the
+
+\section{Previous Motivation}
 It is well known that shallow preferences do not always match reflective ones.\commentYM{à quoi sert la phrase précédente ?}
@@
 \subsection{Existing approaches for capturing reflective preferences}
+%Yet, classical methods to obtain preference models in economics are either formally defined on the basis of observable data that do not describe reflective preferences, or are obtained by other means than observable preferential data and systematic reproducible formal procedures.
+\commentYM{je devine ce que tu veux dire, mais je ne comprends pas la dernière phrase.
+Il me semble important que tu t'expliques ici, car je pense que le lecteur ici ne peut pas comprendre la niche dans laquelle s'inscrit ton projet}
+
 \subsubsection{Laundering preferences}
+\label{sec:laundering}
 An approach much discussed recently is the one of laundering preferences, also called preference purification \citep{bernheim_beyond_2009, rubinstein_eliciting_2011, infante_preference_2016}: having collected shallow preference data (from the field or from interviews), laundering preferences consists in transforming them, using a formal process, in such a way that they satisfy axioms generally considered as required by rationality, or keeping only preference data collected in some situations considered appropriate to determine welfare-relevant preferences.

### 2020-10-24 simple.tex
Mostly review, improved (unfinished)

@@
 \label{sec:approaches}
+\subsection{Overview}
 For this article, a \emph{normative decision theory} is a theory that, when applied in the situations it self-describes as applicable to, claims to yield valid prescriptions.
@@
 A \emph{descriptive decision theory} is a theory that, when correctly applied in the situations it self-describes as applicable to, claims to predict the decision behavior of a given set of individuals.
-For this article, a claim counts as a prediction only when it is in principle possible to show that it is false using empirical data, thus predictions only apply to empirically observable data.
+For this article, a claim is a prediction only when it is in principle possible to show that it is false using empirical data.
 
@@
 Can a theory be extremely specific, or is some level of generality required to deserve being called a theory?
-Must a theory consist in a non-trivial assembly of laws, some being deducible from others?
+Must a theory consist in a non-trivial assembly of laws, some deducible from others?
 It is not necessary for the purpose of the present discussion to take position on these issues, rather, the focus is on the distinction between normative and descriptive approaches.
 An intuitive understanding of the concept of theory will suffice.
-Similarly, I sidestep insuperable difficulties pertaining to capturing in a short definition the concept of a descriptive theory in general: some descriptive theories may propose to describe without predicting, for example (historical decisions or trends come to mind); such endeavor simply does not enter the scope of this discussion, and I make no claim about its legitimacy to be called a descriptive theory in general.
-
-I say that a normative theory is also a descriptive theory when the prescriptions of the normative theory, in supplement of claiming to be valid prescriptions (in the situations that the theory claim to be applicable to), also claim to predict the decision behavior of a given set of individuals.
-
-Another contrast can now be introduced: the contrast between shallow and reflexive behavior. \emph{Shallow behavior} is defined as the everyday, usual behavior of an individual. 
+Similarly, I sidestep insuperable difficulties pertaining to capturing in a short definition the concept of a descriptive theory in general: some descriptive theories in a more general sense may propose to describe without predicting, for example (historical decisions or trends come to mind); such endeavor simply does not enter the scope of this discussion.
+For similar reasons, I do not claim that the term normative is unanimously used in the literature as defined here.
+This definition encompasses theories used in approaches that do not necessarily self-describe as normative \citep{bell_decision_1988, meinard_rationality_2019}; conversely, some theories considered as normative in the literature, such as some social choice theories, may not fall into the definition proposed here, depending on how they are interpreted.
+
+I say that a normative theory is also a descriptive theory when the prescriptions of the normative theory are also claimed to predict the decision behavior of a given set of individuals.
+
+Another contrast can now be introduced: the contrast between shallow and reflective behavior. \emph{Shallow behavior} is defined as the everyday, usual behavior of an individual. 
 This is the behavior whose observation defines what \citet[p.\ 16]{von_neumann_theory_2004} describe as the “intuitive” preferences of an individual, those originating from an “immediate sensation” (cited in \citet{fishburn_retrospective_1989}).
-\emph{Reflexive behavior}, by contrast, is defined as the behavior that enacts informed, pondered decisions, those that would be taken after due consideration.
+\emph{Reflective behavior}, by contrast, is defined as the behavior that enacts informed, pondered decisions, those that would be taken after due consideration.
 % an individual has consciously adopted after having pondered everything that is possibly relevant to the decision. 
@@
 
-This contrast raises a new distinction, which appears by simple combination of the just given definitions: a \emph{shallow descriptive theory} is a descriptive theory that claims to predict the shallow behavior of individuals; a \emph{reflexive descriptive theory} is one that claims to predict the reflexive behavior of individuals.
+This contrast raises a new distinction, which appears by simple combination of the just given definitions: a \emph{shallow descriptive theory} is a descriptive theory that claims to predict the shallow behavior of individuals; a \emph{reflective descriptive theory} is one that claims to predict the reflective behavior of individuals.
 
 The descriptive theories proposed in decision theory, in the sense defined here, are exclusively shallow descriptive theories, to the best of my knowledge.
-(\Cref{sec:laundering} discusses the theories that launder preferences.)
-%This need not be so. Indeed, this article introduces descriptive theories about reflexive behavior.
-This observation permits to understand what could be called the “normative versus descriptive gap”, implicit in the decision theoretic literature: because normative theories aim to prescribe, it is asked of them that they do not yield recommendations that precisely, systematically match shallow behavior.
+%This need not be so. Indeed, this article introduces descriptive theories about reflective behavior.
+This observation permits to understand what could be called the “normative versus descriptive gap”, implicit in the decision theoretic literature: because normative theories aim to prescribe, they are required to not yield recommendations that precisely, systematically match shallow behavior.
 Given the numerous results in experimental psychology showing that shallow behavior is undefensible in many situations, a normative theory whose prescriptions would systematically match shallow behavior would be suspicious, to say the least.
+It would also be of low practical interest.
 It is an immediate consequence of this minimal requirement that a normative theory cannot also be a shallow descriptive theory. 
-As \citet{hausman_preference_1994} illustrate with an example of a person drinking a fatal poison while erroneously thinking that it is water, shallow behavior is not sufficient to inform normative economics.
+In other words, as \citet{hausman_preference_1994} illustrate with an example of a person drinking a fatal poison while erroneously thinking that it is water, shallow behavior is not sufficient to inform normative economics.
 The “normative versus descriptive gap” comes from an implicit identification of descriptive theories with shallow descriptive theories.
 
-This gap can thus be overcome by considering reflexive descriptive theories, which is the path this article adopts.
-It defines theories that are both normative and descriptive: they attempt to deliver valid prescriptions, and these prescriptions are claimed to predict reflexive behavior.
+This gap can thus be overcome by considering reflective descriptive theories, instead of shallow descriptive theories. This is the path this article adopts.
+It defines theories that are both normative and descriptive: they attempt to deliver valid prescriptions, and these prescriptions are claimed to predict reflective behavior.
 
@@
 
-\section{Previous Motivation}
-It is well known that shallow preferences do not always match reflective ones.\commentYM{à quoi sert la phrase précédente ?}
-Indeed, forming reflective preferences is recognised as a difficult problem in many decision problems, contrary, by definition, to shallow preferences.
-For example, \citet[p.\ 6]{colell_microeconomic_1995} write, when presenting the preference relation that is the basis for most of their famous book about Microeconomic theory: “Introspection quickly reveals how hard it is to evaluate alternatives that are far from the realm of common experience.
-It takes work and serious reflection to find out one’s own preferences.”
-In the words of \citet[p.\ 9]{bell_descriptive_1988}, “Our decision makers are not economic automatons; they make mistakes, have remorse, suffer anxieties, and cannot make up their minds”\commentYM{cette citation me semble mal venue ici, car elle ne pose pas que la question du contraste shallow/reflective, mais aussi la question de savoir s'il faudrait toujours faire un calcul économique.
-Par exemple avoir des remords ne me semble pas forcément une mauvaise chose} (cited by \citet[p.\ 87]{deparis_etude_2012}).
-Indeed, it is to be expected that some behavior highlighted by psychologists \citep{kahneman_thinking_2012}, such as framing effects, would be rejected by the individuals themselves when pondering their decisions.
-\commentYM{formulation ambigue : on dirait que tu dis que les gens nieraient que les framing effects existent}
-
-That reflective preferences are relevant to economic theory, in supplement to shallow preferences, is also illustrated by the general requirement of transitivity of preferences for economic theory, which is reasonably expected from reflective rather than from shallow preferences.
-As an illustration, \citet[p.\ 7]{colell_microeconomic_1995} go on writing: “the transitivity assumption can be hard to satisfy when evaluating alternatives far from common experience.
-As compared to the completeness property, however, it is also more fundamental in the sense that substantial portions of economic theory would not survive if economic agents could not be assumed to have transitive preferences.” \commentYM{la seconde phrase de la citation me parait superflue pour ce que tu as à dire ici.
-Plus généralement, la plus-value d'une citation ici me semble limitée.
-Plus fondamentalement, l'argument me semble incomplet.
-OK, les préférences shallow ont toutes les chances de n'être pas transitives.
-Mais pourquoi penser que les préférences réfléchies le seraient ?
-Il manque un argument}
-
-Let me state how the approach proposed here to capture reflective preferences differs from those proposed in the literature, and what problems it aims at solving.
-
-\subsection{Existing approaches for capturing reflective preferences}
-%Yet, classical methods to obtain preference models in economics are either formally defined on the basis of observable data that do not describe reflective preferences, or are obtained by other means than observable preferential data and systematic reproducible formal procedures.
-\commentYM{je devine ce que tu veux dire, mais je ne comprends pas la dernière phrase.
-Il me semble important que tu t'expliques ici, car je pense que le lecteur ici ne peut pas comprendre la niche dans laquelle s'inscrit ton projet}
-
-\subsubsection{Laundering preferences}
-\label{sec:laundering}
-An approach much discussed recently is the one of laundering preferences, also called preference purification \citep{bernheim_beyond_2009, rubinstein_eliciting_2011, infante_preference_2016}: having collected shallow preference data (from the field or from interviews), laundering preferences consists in transforming them, using a formal process, in such a way that they satisfy axioms generally considered as required by rationality, or keeping only preference data collected in some situations considered appropriate to determine welfare-relevant preferences.
-For example, \citet{bleichrodt_making_2001} transform observed preferences in order to obtain a classical Expected Utility model; \citet{bernheim_beyond_2009} propose to exclude situations where the individual seems (by objective criteria) unable to process information considered (by the theorist) as relevant information.
+Let me state how the approach proposed here to capture reflective preferences differs from those proposed in the literature.
+
+\subsection{Existing approaches for modeling reflective preferences}
+The review of existing approaches aiming at obtaining a model of the reflective preferences of an individual distinguishes two kinds of approaches.
+\Cref{sec:purification} mentions formal techniques, that can be applied by following an explicit procedure, but that do not consider the reaction of individuals to arguments; while \cref{sec:informal} reviews studies that involve informal discussions with individuals, which do consider arguments, but require involving experts.
+By contrast, this article presents theories that can be confronted to empirical data in a formal, systematic way, and that consider the reactions of individuals to arguments.
+
+Before delving into these two categories of approaches, let me mention a few others that, though related to the topic discussed here, fall outside the scope of this article.
+
+Some authors have proposed to base normative theories on observable aspects of nature and individuals; for example, \citet{kahneman_back_1997} propose to measure “experienced utility”, considered as a hedonic quality.
+To the best of my knowledge, these proposals never aim at observing reflective preferences as considered here and thus fall outside the scope of this article.
+
+The field of formal argumentation theory has developed technical approaches to deal with arguments.
+Such endeavor starts with an “attack” relation, which indicates which arguments argue against which.
+Various criteria can then be mathematically defined, in the form of a function selecting subsets of arguments given an attack relation, typically representing sets of arguments that “best resist” their counter-arguments.
+This field has greatly inspired this proposal, in particular, the notion of attack and of reinstatement.
+This field however does not view the attack relation as observable, but considers it as given, and its methodology is therefore not empirical in the sense seeked for here.
+(\Citet{cailloux_formal_2019} elaborates on this difference of objective.)
+\commentYM{ici aussi, je trouve la mention de ces approches maladroite, car elles sont mises en exergue comme si elles étaient des manières de traiter le problème qui t'intéresse, ce qu'elles ne sont pas}
+
+\subsubsection{Preference purification}
+\label{sec:purification}
+An approach much discussed recently is the one of preference purification \citep{bernheim_beyond_2009, rubinstein_eliciting_2011, infante_preference_2016}.
+Having collected shallow preference data (from the field or from interviews), purifying preferences consists in transforming them, using a formal process, in such a way that they satisfy axioms generally considered as required by rationality, or keeping only preference data collected in some situations considered appropriate to determine welfare-relevant preferences.
+For example, \citet{bleichrodt_making_2001} transform observed preferences in order to obtain a classical Expected Utility model; \citet[Section VII]{bernheim_beyond_2009} propose to exclude situations where the individual seems (by objective criteria) unable to process information considered (by the theorist) as relevant information.%; \citet{rubinstein_eliciting_2011} study the possible “rational” preference relations that are coherent with the observed data when assuming some distortion process relating (shallow, observed) and (reflective, unobserved) behavior.
 \commentYM{les deux mécanismes évoqués sont très différents, et ont des enjeux différents.
 Je pense qu'il serait utile de les distinguer, et je pense qu'il faudrait en dire plus sur la nature de la transformation et du filtrage, sans quoi la discussion des ces approches est trop superficielle}
-
-This \commentYM{what?
-ici on voit qu'on gagnerait à savoir concrètement quelle est la manip déployée par les auteurs ci-dessus}creates a risk of mis-representing the reflective preferences of the individual: not only is it not known whether the individual would reflectively want to adhere to these axioms \commentYM{quels axiomes ?
-besoin d'expliquer + en détail ce que font ces auteurs ; et tu sembles pressupposer ici qu'adéhrer aux axiomes et s'approprier une transformation ou un filtre basé sur des axiomes, c'est la même chose, ce qui ne me semble pas évident}and, if so, how she would reflectively adapt her preferences when her shallow preferences exhibit related inconsistencies; but it is not even discussed how in principle this could be known \commentYM{phrase en + super longue : arrivée à la fin, je suis perdu}.
+\commentOC{Je ne vois pas comment faire ça sans en faire une digression énorme.
+Il faudrait introduire des notations, des définitions, … Je vois à peu près comment les présenter sous un cadre unifié et les comparer axiomatiquement aux théories du DJ, mais cela devrait faire l’objet d’un autre article, il me semble.}
+
+These proposals leave unspecified how to confirm or disconfirm them empirically, thus, in particular, how to empirically investigate disagreements between theories: if two theories, on the basis of the same observed data, postulate that they correspond to different purified preferences, the disagreement may at best be arbitrated using ad-hoc, case by case criteria to assess for their relative plausibility.
+By contrast, the present proposal indicates a clear, systematic empirical way to abitrate disagreements.
+%These proposals deserve a detailed comparison to the current one, but this requires a treatment that cannot be given in this article.
+Let me simply highlight one major difference.
+which can be done with a high level description of these approaches using a variant of the framework that \citet{rubinstein_eliciting_2011} describe.
+%Consider a set of possible observations $S$, describing shallow behavior, and a set of possible “rational” preference relations $R$.
+The set $S$ may contain observations of choice instances, for example, given the bundle $B$, the individual chose $b \in B$; or may contain all possible linear orders over some set of alternatives.
+The set $R$ contains all relations that satisfy some set of axioms of rationality, representing what the modeler considers as an acceptably purified relation.
+\Citet{bleichrodt_making_2001}, for example, use for $R$ the preference relations satisfying \ac{SEU}.
+
+%The purification process amounts to define a function $f: \powerset{S} \rightarrow \powerset{R}$, where $\powerset{A}$ represents the set of subsets of a given set $A$.
+The function $f$ relates a set of observations to their possible purified preference relations.
+The argument of the function represents observations obtained using different frames.
+se could be preference orders
+%This \commentYM{what?
+ici on voit qu'on gagnerait à savoir concrètement quelle est la manip déployée par les auteurs ci-dessus}creates a risk of mis-representing the reflective preferences of the individual: not only is it not known whether the individual would reflectively want to adhere to these axioms
+%\commentYM{quels axiomes ?
+besoin d'expliquer + en détail ce que font ces auteurs ; et tu sembles pressupposer ici qu'adéhrer aux axiomes et s'approprier une transformation ou un filtre basé sur des axiomes, c'est la même chose, ce qui ne me semble pas évident}
+%and, if so, how she would reflectively adapt her preferences when her shallow preferences exhibit related inconsistencies; but it is not even discussed how in principle this could be known \commentYM{phrase en + super longue : arrivée à la fin, je suis perdu}.
 As a result, a theory postulating constraints on individual’s behavior \commentYM{je ne comprends pas de quelles contraintes sur le comportement il est question ici.
@@
 Je pense que tu devrais reformuler, donner l'argument plus directement, et si tu y tiens mettre entre parenthèse que cet arguement est utilisé dans un autre débat par x et y quand ils parlent de LP}
-That this is an important methodological problem is sometimes recognized by authors adopting \commentYM{endorsing}this approach \commentYM{je pense qu'en anglais il est + idiomatique d'éviter ce genre de tournure : plutôt dire "Authors...
-sometimes recognize that..."}.
-\Citet{bleichrodt_making_2001}, for example, state that laundering require controversial assumptions (p.\ 1500), and recommend it only as a last resort, recommending discussing with the decision-maker whenever possible to elicit her reflective preferences (p.\ 1499).
+In other words, it is left unclear how, from a given observation of shallow behavior, one may obtain empirically information about reflective (or purified, in the terminology of this literature) preferences, or about the axioms they should satisfy.
+Authors endorsing this approach sometimes recognize that this is an important methodological problem.
+\Citet{bleichrodt_making_2001}, for example, state that their proposal require controversial assumptions (p.\ 1500), and recommend it only as a last resort, recommending discussing with the decision-maker whenever possible to elicit her reflective preferences (p.\ 1499).
 Note that nudging \citep{thaler_nudge_2009} creates a similar problem: we have to guess what the individual would like if he thought hard about the decision problem, was well-informed, and actively worked against the psychological features he himself does not consider adequate for good decision making.
@@
 \subsubsection{Informal deliberation}
-Another path to obtain reflectful \commentYM{reflective ?} preferences has been followed: the one of deliberation, an umbrella term by which I designate processes, either, involving discussions between an analyst and a decision-maker while querying her preferences in view of building a formal model of it \commentYM{them ?} \citep{raiffa_back_1985, keeney_decisions_1993, roy_multicriteria_1996, belton_multiple_2002}, or involving group discussions, with presentations from experts to an audience and internal deliberation phases \citep{fishkin_when_2011}, aiming to obtain well-informed preferences.
+\label{sec:informal}
+Another path to obtain reflective preferences has been followed: the one of deliberation, an umbrella term by which I designate processes, either, involving discussions between an analyst and a decision-maker while querying her preferences in view of building a formal model of them \citep{raiffa_back_1985, keeney_decisions_1993, roy_multicriteria_1996, belton_multiple_2002}, or involving group discussions, with presentations from experts to an audience and internal deliberation phases \citep{fishkin_when_2011, chappell_deliberative_2012}, aiming to obtain well-informed preferences.
+The term as used here also includes the informal use of debiasing techniques: techniques that aim at encouraging individuals to think more about their decision problem in order to reduce occurrence of behavioral “mistakes”.
+Examples include suggesting the individuals to consider alternative points of view, or asking them to give reasons for their choices (an insightful article by \citet{mitchell_libertarian_2004} cite many such studies).
 \commentYM{il me semble nécessaire ici de mentionner aussi tous les dispositifs participatifs et de concertation employés en routine dans les prises de décisions relatives aux politiques publiques et leur mise en oeuvre}
-
-A major problem of these techniques is that they are not easily reproducible \commentYM{il faudrait expliquer en quel sens}, and that the resulting preferences elicited from the subjects might reflect properties of the personalities of the intervening experts or group-dynamic effects rather than true reflective preferences of the individuals \commentOCf{Yves, as-tu une référence pour moi ?}\commentYM{on a mis des références pertinentes pour les différents aspects dan le papier soumis à Ecol Econ.
-Ces références ne te conviennent pas ?}.
-This problem is exacerbated \commentYM{compounded} by the fact that psychologists have shown that apparent coherence can appear, that is, preferences that do not violate axioms usually considered as representing rationality, although some framing effect may be at play that result in the apparently coherent preferences to arguably not represent reflective preferences \citep{ariely_predictably_2010} \commentYM{phrase beaucoup trop longue pour être compréhensible, qui fait par ailleurs référence au concept de rationalité sans le définir, ce qui est acceptable en début d'intro, mais me semble problématique à ce stade dans un papier qui cherche à éclairer les débats flous par des clarifications formelles et conceptuelles}.
-It also remains to be clarified how to check on a principled, systematic basis, whether all relevant arguments have been presented faithfully.
-Comfronted with (possibly self-designated \commentYM{ceci est un tout autre problème, dont la mention ici brouille le propos}) experts with enough assertiveness, a decision-maker can be convinced to follow principles of decision-making that several experts in the field of decision-theory \commentYM{would} consider incorrect.
-As an illustration, after discussing the weaknesses of the \ac{AHP}, \citet[p.\ 53]{howard_foundations_2007} write \commentYM{s}: “Why, then, do inferior processes find favor with decision makers?
+\commentOC{Je m’interroge. Ça me semble de pus en plus éloigné du scope, car je m’intéresse aux préférences d’un individu donné, hors questions d’agrégation.}
+
+A major problem of these techniques is that they are not easily reproducible \commentYM{il faudrait expliquer en quel sens}: the resulting preferences elicited from the subjects might reflect properties of the personalities of the intervening experts or group-dynamic effects rather than true reflective preferences of the individuals.
+
+This problem is compounded by the phenomenon of arbitrary coherence, exhibited by psychologists \citep{ariely_predictably_2010}.
+This term denotes situations where individuals form an apparently coherent system of preference that depends on the path taken to elicit it.
+\commentYM{phrase beaucoup trop longue pour être compréhensible, qui fait par ailleurs référence au concept de rationalité sans le définir, ce qui est acceptable en début d'intro, mais me semble problématique à ce stade dans un papier qui cherche à éclairer les débats flous par des clarifications formelles et conceptuelles}.
+
+It also remains to be clarified how to check on a principled, systematic basis, whether all relevant arguments have been presented faithfully. Comfronted with 
+%(possibly self-designated \commentYM{ceci est un tout autre problème, dont la mention ici brouille le propos}) 
+experts with enough assertiveness, a decision-maker can be convinced to follow principles of decision-making that several experts in the field of decision-theory would consider incorrect. 
+%As an illustration, after discussing the weaknesses of the \ac{AHP}, \citet[p.\ 53]{howard_foundations_2007} write \commentYM{s}: “Why, then, do inferior processes find favor with decision makers?
 The answer is that they do not force you to think very hard or to think in new ways.” \commentYM{je ne vois pas en quoi ceci est censé illustrer le propos précédent (ou alors je n'ai rien compris à la citation).
 J'ai l'impression que la citation dit que, parfois, il y a des forces psychologiques qui s'opposent à l'adoption d'un processus de décision, quand bien même celui-ci aurait des qualités indéniables}
-Beyond the controversial \ac{AHP}, famous decision analysts have voiced disagreements with normative theories of decision making \citep{ellsberg_risk_1961, allais_so-called_1979} that are however generally applied in the field.
+Beyond the controversial \ac{AHP} mentioned in the introduction, famous decision analysts have voiced disagreements with normative theories of decision making \citep{ellsberg_risk_1961, allais_so-called_1979} that are however generally applied in the field.
 \commentYM{il me semble ici intenable de faire l'économie de définir ce que tu appelles "normative theories"}
@@
 Cela induit des ruptures dans le style, et force le lecteur à se pencher sur des questions d'interprétation des citations qui l'empêchent de se focaliser sur ton propos à toi}
-This rethorical question illustrates the need of systematic procedures able to determine whether decision-makers, when confronted with the relevant arguments, accept the soundness of the principles on whose basis the recommendation rests \commentYM{the principles that the recommendation rests on}(this has been somewhat explored, but not systematically, for current lack \commentYM{for lack} of a systematic way of confronting decision makers to arguments \citep{slovic_who_1974, stanovich_discrepancies_1999}).
-
-As a consequence of these techniques being not \commentYM{not being}completely formalised and reproducible, each application requires manual intervention \commentYM{quelles sont ces "interventions manuelles" ?
-à expliquer}of (very skilled) experts.
-Eliciting reflective preferences therefore requires enormous resources.
-\Citet[p.\ 572]{pinto_normative_2012} observe that “in many of those surveys that governments use in order to inform social policy there are not enough resources (time and money) in order to reach the stage where preferences are not labile”.
-There is, to reduce this cost, a need for theories that can be iteratively improved upon and yield reusable knowledge about reflective preferences.
-\commentYM{Cette idée de limiter le coût est intéressante, et je me dis qu'elle peut faire mouche avec certains lecteurs.
-Mais en l'état ça ne fonctionne pas car tu ne expliques pas quels sont les coûts impliqués dans les approaches "manuelles"}
-
-Different analysts, using different methods and different axioms as their favorite conception of rational decision-making, will obtain possibly contradictory conclusions, “elicited” from the decision-makers who hire them.
+This rethorical question illustrates the need of systematic procedures able to determine whether decision-makers, when confronted with the relevant arguments, accept the soundness of the principles that the recommendation rests on (this has been somewhat explored, but not systematically, for lack of a systematic way of confronting decision makers to arguments \citep{slovic_who_1974, stanovich_discrepancies_1999}).
+
+Another way to view this problem is that different analysts, using different methods and different axioms as their favorite conception of rational decision-making, will obtain possibly contradictory conclusions, “elicited” from the decision-makers who hire them.
 Some analysts admit this possibility and do not consider it to be a problem.
@@
 Là, en lisant, je ne sais pas si tu considères ce que tu abordes dans ce § comme un nouveau problème, ou comme un aspect ou une implication, du problème exploré précédemment}
+\commentOCf{C’est discutable si c’est un autre problème ou un peu le même problème ou carrément le même problème vu autrement.
+Du point de vue logique, toutes les propositions fausses sont équivalentes.
+En l’absence d’une analyse comparative approfondie de toutes ces approches et de leurs propriétés, je ne vois pas à ce stade comment faire beaucoup plus clair.
+Mais je serais heureux d’en discuter si tu vois une manière de patcher le problème raisonnablement facilement.}
 For example, \citet[p.\ 214]{roy_comparison_1995} write: “In our view, these inevitable disagreements do not imply that decision-aid is useless but simply that a single problem may have several valid responses.
@@
 Du coup elle brouille le message}
-Although being an important insight about the (likely vain) hope of determining a single correct recommendation in many complex decision situations (about which more below), this answer \commentYM{quelle answer ?
-à quelle question ?
-je suis perdu}does not address the problem that some principles of decision making may be wrong guides in some situations, possibly including some principles that are commonly applied in the field, hence the need of principled ways of discriminating them.
+\commentOCf{J’ai un peu réduit les citations, j’espère que ça va mieux.
+Concernant celle-ci en particulier, elle me semble très utile.
+Je trouve stupéfiant qu’on puisse trouver ces propos dans la littérature, écrits noir sur blanc.
+Si je ne les cite pas, un lecteur pourrait (ou devrait) ne pas me croire quand j’affirme que des gens trouvent que ce n’est pas grave que deux études soi-disant scientifiques arrivent à des conclusions contradictoires.
+La citation étendue permet de comprendre, je crois, leur point de vue, et de se faire une idée de ce qu’ils veulent dire par là.}
+Although being an important insight about the (likely vain) hope of determining a single correct recommendation in many complex decision situations (about which more below), this insight does not address the problem that some principles of decision making may be wrong guides in some situations, possibly including some principles that are commonly applied in the field, hence the need of principled ways of discriminating them.
 \commentYM{est-ce vraiment ton projet ?
@@
 Ce que je comprennais jusqu'ici était que tu cherchais un moyen de connaître les "preferences that represent informed, pondered decisions, that would be taken after due consideration by the individual", ce qui me semble être un tout autre projet}
+\commentOCf{Je propose de trancher entre approches normatives en utilisant des données empiriques, plutôt que simplement la force de conviction des axiomes (qui parlent différemment à différentes personnes et peuvent conserver les désaccords intacts).
+Je ne sais pas si c’est plus clair maintenant.}
+
+As a consequence of these techniques not being completely formalised and reproducible, each application requires manual intervention \commentYM{quelles sont ces "interventions manuelles" ?
+à expliquer}of (very skilled) experts in order to elicit reflective preferences interactively.
+Eliciting reflective preferences therefore requires enormous resources.
+\Citet[p.\ 572]{pinto_normative_2012} observe that “in many of those surveys that governments use in order to inform social policy there are not enough resources (time and money) in order to reach the stage where preferences are not labile”.
+There is, to reduce this cost, a need for theories that can be iteratively improved upon and yield reusable knowledge about reflective preferences.
+\commentYM{Cette idée de limiter le coût est intéressante, et je me dis qu'elle peut faire mouche avec certains lecteurs.
+Mais en l'état ça ne fonctionne pas car tu ne expliques pas quels sont les coûts impliqués dans les approaches "manuelles"}
+\commentOC{J’ai reformulé légèrement, j’espère que ça suffit.
+Puis-je m’en tenir à l’idée qui me semble évidente que faire intervenir toute sorte d’experts pour discuter avec des gens chaque fois qu’on veut leur préférence coute cher ?}
 
@@
 \commentYM{related to what? to your approach or to the one explored above?}
-The prescriptive approach to decision making \citep{bell_decision_1988} has been proposed (in supplement to the normative one and the descriptive one), which insists on incorporating the findings of psychologists about decision maker’s weaknesses of reasoning in the procedures leading to recommendations.
-I do not discuss this approach specifically here, because its methods can be considered to fall into the two categories I have described here above when it aims at obtaining reflective preference models \commentYM{j'ai rien compris.
-L'approche prescriptive tombe DANS LES DEUX CATEGORIES EN MEME TEMPS ?
-Il faut expliquer ce que tu racontes là}.
-When considering normative economics broadly, as I do here, as the methods aiming for valid prescription for an individual or a group, prescriptive approaches are a part of normative economics \commentYM{dans le papier sur la rationalité avec Alexis, on discute les faiblesse de la catégorisation de Bell et al., et je pense que ce qu'on dit va dans ton sens.
-Tu pourrais nous citer : ça me permettrait d'avoir 1 citation : personne ne cite mes papiers...
-snif...
-Plus sérieusement, je me demande ce que la normative ECONOMICS vient faire ici.
-Selon moi, le prescriptif sensu Bell et al.
-est une sous-catégorie du normatif sensu Bell et al.}.
-
-Some authors have proposed to ground \commentYM{base} normative theories on observable aspects of nature and individuals, to solve some of the problems mentioned above; for example, \citet{kahneman_back_1997} propose to measure “experienced utility”, considered as a hedonic quality.
-\commentYM{il me semble qu'il faudrait être + précis ici : tous les problèmes mentionnées + haut ne peuvent pas être résolus par cette approche.
-Certains peuvent l'être, et encore, ça se discute, d'autres ne peuvent pas l'être.
-Si tu ne dissèques pas cela, ton affirmation semble creuse}To the best of my knowledge, these proposals never aim at observing reflective preferences as considered here and thus fall outside the scope of this article.
-\commentYM{tout à fait d'accord, mais du coup la manière dont tu les mentionnes les met trop en avant, surtout vu que tu dis qu'ils prétendent traiter certains des problèmes que tu explores précédemment.
-Il faudrait trouver une meilleure manière de faire référence à ces approches (on te reprocherait de ne pas les discuter), en passant, et en montrant plus clairement qu'elles sont hors champs ; probablement + en amont dans le texte}
-
-The field of formal argumentation theory has developed technical approaches to deal with arguments.
-Such endeavor starts with an “attack” relation, which indicates which arguments argue against which.
-Various criteria can then be mathematically defined, in the form of a function selecting subsets of arguments given an attack relation, typically representing sets of arguments that “best resist” their counter-arguments.
-This field has greatly inspired this proposal, in particular, the notion of attack and of reinstatement.
-This field however does not view the attack relation as observable, but considers it as given, and its methodology is therefore not empirical in the sense seeked for here.
-(\Citet{cailloux_formal_2019} elaborates on this difference of objective.) \commentYM{ici aussi, je trouve la mention de ces approches maladroite, car elles sont mises en exergue comme si elles étaient des manières de traiter le problème qui t'intéresse, ce qu'elles ne sont pas}
-
-An important literature exists about “debiasing techniques”: techniques that aim at encouraging individuals to think more about their decision problem in order to reduce occurrence of behavioral “mistakes”.
-Examples include suggesting the individuals to consider alternative points of view, or asking them to give reasons for their choices (an insightful article by \citet{mitchell_libertarian_2004} cite many such studies).
-This proposal \commentYM{de quoi tu parles ?
-de TON proposal ?
-pas clair} is situated at another level \commentYM{qu'est-ce que ça veut dire ?}, which could be considered as a way of justifying and comparing such debiasing techniques with no need of a prior agreement on what constitutes a behavioral mistake.\commentYM{très cryptique.
-Je n'ai rien compris à ce §, et je me demande pourquoi tu ne traites pas des debiasing techniques dans la même sous-section que les laundering techniques, qui me semblent poser les mêmes problèmes}
-
 The current proposal pursues a path started with \citet{cailloux_formal_2019}, an article that defines the notion of \ac{DJ} and models that enable interactions with individuals whose \acp{DJ} are to be captured.

### 2020-10-26 simple.tex
Review improved

@@
 Experimental tests to arbitrate between theories may not be feasible in practice, descriptions are not always solely about the future, falsificationist approaches in turn raise epistemological difficulties, and so on.
-Correspondingly, the possible confrontation to empirical data of the normative and descriptive theories defined here will likely not suffice to close every discussion about validation.
+Correspondingly, the possible confrontation to empirical data of the theories defined here will likely not suffice to close every discussion about validation.
 My less naïve claim, that should suffice to motivate the present endeavor, is that it is often a good thing for a theory to make empirically testable claims, from the point of view of the possibilities of solving disputes and validating theories.
 
-As the plural indicates, this article defines a kind of theories, called theories of \ac{DJ}, not specific theories of \ac{DJ}.
+As the plural indicates, this article defines a kind of theories, called theories of \ac{DJ}, not a specific theory of \ac{DJ}.
 Specific theories of \ac{DJ} are tailored to a set of situations and yield claims relevant to those situations.
 For example, a specific theory of \ac{DJ} may be tailored to situations of choice between lotteries involving money.
-This article adopts a methodological point of view.
+This article adopts a more general point of view.
 It proposes a definition of what theories of \ac{DJ} should look like, and proves claims that hold for any specific theory of \ac{DJ}, showing that such theories are indeed normative and descriptive.
@@
 These definitions permit to readily see why the apparent impossibility of a claim being both normative and descriptive is an illusion, thereby enabling a solution to what could be called the “normative against descriptive” gap.
-
-\section{Species of theories}
+It also reviews related works in the literature, and briefly sketches the current proposal.
+\Cref{sec:normative,sec:descriptive} define the theories of \ac{DJ} and prove that these theories are normative and descriptive in the sense defined in \cref{sec:approaches}.
+\Cref{sec:preferences} define theories of \ac{DP} on the basis of theories of \ac{DJ}, and \cref{sec:conclusion} concludes.
+
+\section{Eliciting reflective preferences}
 \label{sec:approaches}
-\subsection{Overview}
+\subsection{Species of theories}
 For this article, a \emph{normative decision theory} is a theory that, when applied in the situations it self-describes as applicable to, claims to yield valid prescriptions.
@@
 %This need not be so. Indeed, this article introduces descriptive theories about reflective behavior.
-This observation permits to understand what could be called the “normative versus descriptive gap”, implicit in the decision theoretic literature: because normative theories aim to prescribe, they are required to not yield recommendations that precisely, systematically match shallow behavior.
+This observation permits to understand what could be called the “normative versus descriptive gap”, referring to the belief, implicit in the decision theoretic literature, that a theory cannot be both normative and descriptive.
+Because normative theories aim to prescribe, they are required to not yield recommendations that precisely, systematically match shallow behavior.
 Given the numerous results in experimental psychology showing that shallow behavior is undefensible in many situations, a normative theory whose prescriptions would systematically match shallow behavior would be suspicious, to say the least.
@@
 
-\subsection{Existing approaches for modeling reflective preferences}
 The review of existing approaches aiming at obtaining a model of the reflective preferences of an individual distinguishes two kinds of approaches.
@@
 
-\subsubsection{Preference purification}
+\subsection{Preference purification}
 \label{sec:purification}
@@
 
-\subsubsection{Informal deliberation}
+\subsection{Informal deliberation}
 \label{sec:informal}
@@
 
-A major problem of these techniques is that they are not easily reproducible \commentYM{il faudrait expliquer en quel sens}: the resulting preferences elicited from the subjects might reflect properties of the personalities of the intervening experts or group-dynamic effects rather than true reflective preferences of the individuals.
-
-This problem is compounded by the phenomenon of arbitrary coherence, exhibited by psychologists \citep{ariely_predictably_2010}.
+A major problem of these techniques is that they are not easily reproducible \commentYM{il faudrait expliquer en quel sens}, because they require informal interactions with experts.
+Furthermore, the resulting preferences elicited from the subjects might reflect properties of the personalities of the intervening experts or group-dynamic effects rather than true reflective preferences of the individuals.
+
+This problem is compounded by the phenomenon of path dependency, or arbitrary coherence, exhibited by psychologists \citep{ariely_predictably_2010}.
 This term denotes situations where individuals form an apparently coherent system of preference that depends on the path taken to elicit it.
@@
 En l’absence d’une analyse comparative approfondie de toutes ces approches et de leurs propriétés, je ne vois pas à ce stade comment faire beaucoup plus clair.
-Mais je serais heureux d’en discuter si tu vois une manière de patcher le problème raisonnablement facilement.}
+Mais je serais heureux d’en discuter si tu vois une manière de corriger le problème raisonnablement facilement.}
 For example, \citet[p.\ 214]{roy_comparison_1995} write: “In our view, these inevitable disagreements do not imply that decision-aid is useless but simply that a single problem may have several valid responses.
@@
 
-\subsection{Some other related approaches}
-\commentYM{related to what? to your approach or to the one explored above?}
-The current proposal pursues a path started with \citet{cailloux_formal_2019}, an article that defines the notion of \ac{DJ} and models that enable interactions with individuals whose \acp{DJ} are to be captured.
-That article however requires as fundamental observable a “trump” relation, indicating whether an individual thinks that an argument is against another argument; and a “support” relation, indicating whether an individual thinks that an argument supports a proposition.\commentYM{je ne pense pas qu'on puisse tenir pour acquis que le lectorat connait par coeur l'article delibenv.
+\subsection{Previous proposal to study \aclp{DJ}}
+The current proposal pursues a path started with \citet{cailloux_formal_2019}, an article that defines the notion of \ac{DJ} and describe how \acp{DJ} can be observed.
+
+That previous proposal postulates that an individual $i$, whose reflective preferences are being modeled, can adopt multiple perspectives.
+The proposal postulates that the modeler can observe two relations by interacting with $i$, called support and trump.
+They constitute the argumentative disposition of an individual $i$ and are defined as follows.
+
+An argument $\ar$ supports a proposition $\prop$ iff $i$ considers that $\ar$ is in favor of $\prop$.
+This notion is conditional, in the sense that it does not say anything about the validity of $\ar$; only that if $\ar$ holds, then $i$ should endorse $\prop$.
+
+An argument $\ar_1$ trumps another argument $\ar_2$ iff there is at least one perspective within which $i$ considers that $\ar_2$ turns $\ar_1$ into an ineffective argument.
+(This notion is formally decomposed into two relations, “trump in some perspective” and “does not trump in some perspective”, but these details do not need to be discussed here.)
+
+That proposal then defines a number of notions, including the central notion of the \ac{DJ} of $i$, on the basis of her argumentative disposition.
+An individual’s \ac{DJ} is the set of propositions that resist counter-arguments, in some technical sense defined on the basis of these relations.
+
+The current article improves on several aspects over this previous proposal.
+
+First, the previous proposal requires the individual to declaratively take position on notions that may be unclear to him, as they include some possibly counterfactual situations, and as the concept of turning an argument into an uneffective argument may not be understood in the same way by everybody.
+In order for the conclusions about $i$’s \ac{DJ} to hold, we must be sure that $i$ understands the semantics of the relations on which it is based as we do.
+It is therefore desirable that these notions have unambiguous semantics.
+It is undoubtedly an important strength of \citet{samuelson_foundations_1983}, \citet{von_neumann_theory_2004} or \citet{savage_foundations_1972}’s theories that they use as primitive notions observable entities whose semantics is unambiguous.
+This is not to say that these proposals cannot be criticized.
+For example, the claim that the notion of preference can be disposed of entirely has been much criticized \citep{hausman_preference_2011, wong_foundations_2006}, with good reasons; and observations of shallow behavior, though having a clear semantics, are insufficient to deduce normative claims, as has been amply remarked and as argued in this very article.
+This is also not to say that declarations should never be used and that only choice acts should matter to any theory in economics.
+Nonetheless, as \citet[p.\ 16]{von_neumann_theory_2004} aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher”.
+A weakness of the previous proposal for studying \acp{DJ} is that the observable relations it uses may be considered inadequate primitive notions.
+This article improves on this aspect by postulating a non-ambiguous observable relation, that does not require $i$ to take position declaratively on relative qualities of arguments; but rather to choose (by declaration of preference or by act) among bundles, or to declare whether $i$ adheres to a given proposition in her current perspective.
+(In the latter case, the clarity of the semantics of the observable relation will depend on the clarity of the propositions.)
+
+Another central aspect of the study of \acp{DJ} is that individuals may change perspective, thus, change opinion about whether an argument trumps another one.
+An important case of change of perspective is when the current perspective depends on which arguments $i$ has seen so far.
+The previous proposal studies these changes of perspectives through the trump relation, without modeling explicitly the arguments seen so far.
+This has the advantage of simplicity, but the price to pay is a lack of ability to reason explicitly about path dependency mechanisms: individuals may form stable opinions that differ according to, for example, the first argument they have seen.
+In such a case, although their opinion may stabilize (in the sense of resisting counter-arguments), it is still arbitrary.
+This article models paths (sequences of arguments) explicitly and prohibits such situations of arbitrariness to count as forming \acp{DJ}.
+
+This article also clarifies the normative and descriptive status of the theories of \acp{DJ}.
+It introduces an explicit axiom which gives them their normative strength.
+This axiom is supplemented by claims, which are shown to be falsifiable by empirical data.
+The previous proposal defines conditions and discusses several possible interpretations of them, including empirical ones, but leaves open the question of how to test these conditions systematically using the observable relations.
+
+\commentYM{la vision vNM est très réductrice, et ne peut pas être considérée, me semble-t-il, comme valable pour toutes les théories normatives, car l'idée qu'il doit y avoir des sensations, atomiques et immédiates relève de l'empirisme logique qui sous-tend leur approche, et cette épistémologie, ou ontologie à ce stade, est loin d'être partagée par toutes les approches à même de développer des théories normatives.
+Ta phrase qui suit risque de n'être pas beaucoup plus convaincantes pour les lecteurs, je le crains.
+Imaginons par exemple une théorie marxiste, elle s'appuiera sur des intérêts matériels, et se contre fout des réactions des individus aux arguments.
+On peut envisager par ailleurs des théories supra-individualistes, qui se foutent des réactions des individus.
+Mais bien entendu la pertinence de ce que je dis là dépend de ta réponse à ma première question dans l'intro du 2.
+Si ce dont tu parles ici, ce n'est pas des théories normatives existantes ou possibles, mais uniquement des théories normatives QUE TU ACCEPTES COMME ELEMENTS DE TA CONSTRUCTION, alors le problème est différent : il faut justifier TON adhérence à l'empirisme logique, ce qui n'est pas une mince affaire étant donné le discrédit qui lui est aujourd'hui attaché}
+\commentOCf{Je soupçonne que le problème était dû à une formulation maladroite de ma part (\og{}The fundamental element of a normative theory of deliberated preferences is the reaction of an individual, whose preferences are to be captured, to arguments\fg).
+Si ma reformulation ne résoud pas le problème, je suis intéressé qu’on en discute.}
+
+\commentYM{je ne pense pas qu'on puisse tenir pour acquis que le lectorat connait par coeur l'article delibenv.
 Il faut du coup donner plus d'explication.
-Par ailleurs, il est impératif que tu expliques pourquoi tu considères qu'il n'est pas raisonnable de considérer que trump et support sont observables} The current proposal defines every required concepts, such as the notion of arguments attacking other arguments, on the basis of a single observable that is compatible with the revealed preference approach priviledged in economic theory \commentYM{je ne pense pas qu'on puisse dire que l'approche RP est privilégiée en économie.
-Elle est aussi très critiquée.
-Si tu la considère particulièrement solide, il faut expliquer pourquoi}, in the sense that it can be defined by reference to what individuals effectively choose under various circumstances.
-The current proposal also defines explicitly (in the form of an axiom \commentYM{il n'y QU'UN axiome au final ?}) sufficient requirements to grant normative power to observations, an aspect which was previously left unclear.
-Finally, the current proposal links \ac{DJ} and deliberated preferences.
-\commentYM{indispensable de dire explicitement quelle est la différence entre les deux dès maintenant}
+Par ailleurs, il est impératif que tu expliques pourquoi tu considères qu'il n'est pas raisonnable de considérer que trump et support sont observables}
+\commentYM{je ne pense pas qu'on puisse dire que l'approche RP est privilégiée en économie. Elle est aussi très critiquée. Si tu la considère particulièrement solide, il faut expliquer pourquoi}
+\commentYM{il n'y QU'UN axiome au final ?}
+
+Finally, the current proposal links \ac{DJ} and deliberated preferences. \commentYM{indispensable de dire explicitement quelle est la différence entre les deux dès maintenant}
 
@@
 
-\subsection{This approach}\commentYM{The proposed approach}
-The proposal of this article \commentYM{the proposal developed/elaborated/presented in this article}to capture reflective preferences while avoiding the just described problems is to define normative theories on the basis of a low demanding axiom complemented with principles of reasonings; \commentYM{je devine que cette phrase est importante mais elle ne se comprend pas.
-Sans le ";" ici elle se comprendrait.
-Mais est-ce que c'est comme ça qu'il faut la comprendre ?
-".
-This" à la place de "; that" donne un autre sense : lequel est le bon ?}that allow decision makers to “reconstruct” \commentYM{pourquoi ce terme est-il mis entre guillemets ?
-généralement on fait cela quand on veut souligner que le terme doit être compris en un sens différent d'un sens habituel proéminent.
-Mais il me semble pas que "reconstruct" ait un sens habituel proéminent dans ce contexte.
-Donc je bloque et je me dis "j'ai loupé un épisode"}the reasoning proposed by the principles so as to be able to check that they apply to their situation; therefore permitting to falsify the theories using observable data representing the rejection by the decision makers of these principles \commentYM{phrase à ralonge, vraiment pas idiomatique en anglais, et à peu près impossible à suivre (du moins pour les lecteurs de ma catégorie)}.
-Such theories are therefore both normative and empirical: normative, in the sense of claiming to capture reflective preferences, which provide a better basis for recommendations or policy making than shallow preferences; and empirical, in the sense of the principles of reasoning being exposed to empirical tests.
-
-The proposed approach is based on a concept of preference that I call deliberated preference, a formal refinement of the vague notion of reflective preferences.
-Those are the preferences of an individual that are stable facing counter-arguments.
-The arguments are presented to the decision maker, and her reaction is observed, for example, in the form of a choice between some alternatives.
-This is the basic observable of interest to the theories here defined.
-
-It is not an ambition of this article to actually propose concrete theories of deliberated preferences, for this is not achievable in a single article; and the theories as defined here admittedly still suffer important weaknesses.
-\commentYM{ce qui précède n'est pas compréhensible si t n'explicites pas ce que veut dire "theory" dans cet article.
-Par ailleurs, qu'est-ce qu'une theorie CONCRETE ?
-A quoi cela s'oppose-t-il ?
-Le lecteur se demande aussi en quoi cela consiste de "définir" une théorie (ce que tu sous-entends que tu vas faire) sans la "proposer" (ce que tu dis dépasser tes ambitions).
-Enfin, de quelles "weaknesses" parles-tu ?}The ambition of this article is accordingly limited to present a novel approach of capturing reflective preferences in simple enough settings.\commentYM{quel sens faut-il donner à "setting" ici ?
-dans certains cas, on peut employer ce genre de terme de manière vague sans que ça choque.
-Ici je pense que ce n'est pas possible, car le lecteur ne comprend pas où tu vas, ni ce que tu vas faire, ni pourquoi c'est compliqué, ni quelle est la complexité dont tu parles, ni ce qui peut faire qu'un setting est "simple enough" ou complexe}
-%This requires to define precisely what such theories should aim to capture; and how they should be compared, which is the sole ambition of this article. 
-Some challenges that must be overcomed \commentYM{overcome}in order to build concrete theories applicable in realistic settings will be discussed in conclusion.\commentYM{tu pourrais mettre ce genre de phrase à la fin d'une annonce de plan, mais là comme ça, elle ne sert à rien}
-
-One long-term goal of this research program is to give individuals the means to reject theories that they find unconvincing after due consideration of all arguments; and accordingly, give incentives to decision theorists to build defenses of these theories able to convince individuals whose preferences are modeled of the soundness of these theories.
+\subsection{The proposed approach}
+The proposal elaborated in this article defines theories that are both normative, and descriptive of reflective behavior.
+The kind of behavior of interest here is choice behavior, although the proposal is more general.
+
+In fact, the main object of study of this article is judgments about propositions. The main goal is accordingly to study reflective adherence to propositions.
+This will then be applied to determining reflective choice behavior.
+Choice behavior is obtained when considering adherence to propositions of the form: “I ought to choose alternative $\alt$ rather than $\alt'$ if both are available”.
+The alternatives can be concrete objects such as consumable goods.
+
+One of our main preoccupation will be to clarify, using formal and precise definitions, the intuitive notion of reflective adherence to propositions.
+This is done using the concept of \emph{deliberated} judgments (a normative concept) and of \emph{acceptable} propositions (a descriptive concept).
+
+A theory of \ac{DJ} applies to a set of individuals and a set of propositions.
+The \ac{DJ} of an individual $i$ is the set of propositions $\prop$ such that it is legitimate to recommend to $i$ adherence to $\prop$.
+Someone’s \ac{DJ} is not directly observable.
+However, we can observe the reactions of $i$ to arguments in favor and against the propositions.
+A theory of \ac{DJ} assumes that it knows a set of arguments such that exploring the reactions to these arguments “sufficiently” permits to obtain knowledge about someone’s \ac{DJ}.
+Thus, one important task dealt with in \cref{sec:normative} will be to define the notion of acceptability, that serves to capture formally this notion of “sufficient” exploration.
+Intuitively, a proposition is acceptable when some argument makes $i$ seem (according to the observations) to adhere to the proposition whatever the counter-arguments given to $i$, and whatever the sequence of arguments given to $i$ previously.
+
+A theory of \ac{DJ} must use an axiom that relates the descriptive notion of acceptability to the normative notion of being deliberated.
+This axiom simply mandates that whatever is acceptable, is deliberated.
+\Cref{sec:normative} presents it formally.
+
+This defines theories of \ac{DJ} that can be considered normative, as accepting the axiom is sufficient to determine unambiguously a set of legitimate prescriptions to be given to individuals. 
+This is done by linking \acp{DJ} to acceptable propositions, a notion whose major interest is that it can be confronted to empirical observations.
+But at this stage, it is still unclear how to obtain knowledge of someone’s \ac{DJ}, and accordingly, such theories cannot still be considered as descriptive.
+In particular, they are not falsifiable, as they take no position on the reactions of individuals to arguments.
+\Cref{sec:descriptive} accordingly defines descriptive theories of acceptable propositions, assuming given a normative theory of \ac{DJ}.
+
+Such descriptive theories can take multiple forms, and some of them would permit to see clearly that the theory is descriptive in the required sense, that is, that its claims can be falsified given observational data.
+But the task we face, for such theories to be useful, is more complex than this minimal requirement: we have to find forms of theories that are not hugely demanding on the part of the theorist.
+In particular, we do not want to oblige the theorist to predict the whole of the argumentative attitude of individuals if this is not required to obtain information about her \ac{DJ}.
+Thus, \cref{sec:descriptive} defines descriptive theories of \ac{DJ} that only claim to be able to answer counter-arguments, in a sense that will be made precise.
+The desire that its claim be falsifiable is also defined formally.
+More formally, the result that is obtained in that section, and that is the central result of this article, is that if a theory is convincing and normatively adequate, then it is valid.
+That a theory is convincing is (as also shown in the same section) the same as demanding that it resists all empirical falsification attempts.
+It is normatively adequate if it satisfies the normative axiom described here above informally (and formally in \cref{sec:normative}).
+And it is valid if the propositions that it claims are in someone’s \ac{DJ} are indeed in that person’s \ac{DJ}.
+This central result thus amounts to prove the main claim of this article, namely, that accepting a weak normative axiom, supplemented with empirical claims, is enough to capture someone’s reflective preferences.
+
+A possible objection to the usefulness of this approach should perhaps be lifted before delving into the formal descriptions of this rough sketch.
+It may be argued that because this proposition needs a normative axiom, which cannot be validated empirically, it does not fare better than the alternative propositions examined in the previous sections.
+\ac{SEU}, for example, also claim to obtain reflective preferences on the basis of normative axioms.
+I grant that it is impossible to get completely rid of normative axioms, because prescriptions must be linked to descriptions, and this cannot be done in a complete empirical way.
+However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims.
+The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science (again, accepting this claim does not require to ignore that observations themselves rest upon theories).
+Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance or of being compatible with more preference relations.
+(This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.) This does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences.
+It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
+It is also worth noting that this axiom has a specific form that may permit decision makers to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation.
+Detailed exploration of this aspect is deferred to future work.
+
+One long-term goal of this research program is to give individuals the means to reject theories that they find unconvincing after due consideration of all arguments; and accordingly, give incentives to decision theorists to build defenses of these theories able to convince individuals of the soundness of these theories.
 \commentYM{phrase trop longue}This might match \possessivecite{hausman_debate_2010} suggestion that we should use rational persuasion rather than nudge individuals, arguing that it would promote autonomy.
@@
 \section{Informal presentation}
+\commentOCf{Je pense changer d’approche : enlever cette section et intégrer les explications informelles directement dans la présentation formelle. À faire…}
 \commentYM{Le lecteur n'a aucune idée de ce qu'il doit s'attendre à trouver dans cette section, et de la mesure dans laquelle ça va permettre d'avancer dans la résolution de la problématique : lecteur perdu = pas bien}
-Although the final aim is about the concept of deliberated preference, which permits to compare alternatives (options in a decision problem), this article will mostly discuss \acp{DJ}.
-That is because, once the concept of \ac{DJ} is clearly established, it is a simple matter to define deliberated preferences, and will be done in a later section, by viewing a preference instance as a judgment about a pair of alternatives.
-
-For a clear separation of concern, this article defines first normative theories, then empirical theories for these normative theories \commentYM{je ne comprends pas ce "for" ; je ne comprends pas pourquoi tu utilises une autre opposition que la classique normative vs.
-empirical.
-Par ailleurs, je ne comprends pas DE QUELLES théories tu parles.
-Es-tu en train de parler des théories exitantes, ou des théories dont le développement serait une partie de la réalisation du projet du présent papier ?
-Comme déjà dit plus haut, en fait je ne sais pas ce que tu appelles une "theory"}.
-A normative theory makes normative claims only, which have to be accepted or rejected on the basis of the apparent soundness of the axiom on which it rests \commentYM{par qui ?
-dans le cadre de l'analyse ou en amont ?
-et pourquoi sur la seule base de la soundness de l'axiome ?
-pourquoi pas sur la base de ses implications dans des cas concrets ?}.
+\commentYM{par qui ? dans le cadre de l'analyse ou en amont ? et pourquoi sur la seule base de la soundness de l'axiome ? pourquoi pas sur la base de ses implications dans des cas concrets ?}
 An empirical theory for a given normative theory, by contrast, makes empirical claims, hence, can be confronted to observations \commentYM{quelle différence avec les implications empiriques d'une théorie normative ?}.
@@
 \subsection{Normative theories}
-As \citet[p.\ 16]{von_neumann_theory_2004} aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher”.
-The fundamental element of a normative theory of deliberated preferences is the reaction of an individual, whose preferences are to be captured, to arguments.\commentYM{la vision vNM est très réductrice, et ne peut pas être considérée, me semble-t-il, comme valable pour toutes les théories normatives, car l'idée qu'il doit y avoir des sensations, atomiques et immédiates relève de l'empirisme logique qui sous-tend leur approche, et cette épistémologie, ou ontologie à ce stade, est loin d'être partagée par toutes les approches à même de développer des théories normatives.
-Ta phrase qui suit risque de n'être pas beaucoup plus convaincantes pour les lecteurs, je le crains.
-Imaginons par exemple une théorie marxiste, elle s'appuiera sur des intérêts matériels, et se contre fout des réactions des individus aux arguments.
-On peut envisager par ailleurs des théories supra-individualistes, qui se foutent des réactions des individus.
-Mais bien entendu la pertinence de ce que je dis là dépend de ta réponse à ma première question dans l'intro du 2.
-Si ce dont tu parles ici, ce n'est pas des théories normatives existantes ou possibles, mais uniquement des théories normatives QUE TU ACCEPTES COMME ELEMENTS DE TA CONSTRUCTION, alors le problème est différent : il faut justifier TON adhérence à l'empirisme logique, ce qui n'est pas une mince affaire étant donné le discrédit qui lui est aujourd'hui attaché}
-
 Normative theories define an agenda: a set of propositions that we are interested in knowing the deliberated judgment of individuals about ; a set of individuals that the theory claims applies to; a set of arguments;\commentYM{pourquoi est-ce que cela fait partie de la théorie ?
@@
 \section{Normative theories}
-
+\label{sec:normative}
 \subsection{Definition}
@@
 
-\section{Empirical theories}
+\section{Descriptive theories}
+\label{sec:descriptive}
 \subsection{Definition}
@@
 \section{Preferences}
+\label{sec:preferences}
 \subsection{Representing deliberated preferences}
@@
 \section{Conclusion}
+\label{sec:conclusion}
 (To be written.)

### 2020-10-26 simple.tex
Weaken claim

@@
 
-The descriptive theories proposed in decision theory, in the sense defined here, are exclusively shallow descriptive theories, to the best of my knowledge.
+The descriptive theories proposed in decision theory, in the sense defined here, are mostly shallow descriptive theories, to the best of my knowledge (\cref{sec:purification} discusses the particular case of “preference purification” approaches).
 %This need not be so. Indeed, this article introduces descriptive theories about reflective behavior.

### 2020-10-30 simple.tex
Improved pres. normative; started better pres. descriptive

@@
 Instead, the validity of a normative approach is to be determined by examining the convincingness power of the normative axioms on which it rests.
+\commentYM{par qui ? dans le cadre de l'analyse ou en amont ? et pourquoi sur la seule base de la soundness de l'axiome ? pourquoi pas sur la base de ses implications dans des cas concrets ?}
 This validity criterion is unsatisfactory, as it is unable to settle disputes between experts when they arise.
@@
 The resulting state of conviction arguably depends in part on the rethorical ability of the expert, not solely on the normative strength of the axioms.
-It may lead to a decision maker accepting a decision procedure considered unsound by many experts in the field, such as AHP.
+It may lead to a decision maker accepting a decision procedure considered unsound by many experts in the field, such as the \ac{AHP} \citep{smith_anniversary_2004}.
 This problem is compounded by the enormous constraining power gained when axioms interact, as the celebrated theorem of Arrow shows dramatically: axioms that appear innocuous when taken alone may precipitate undesirable results when combined.
@@
 When two descriptive theories disagree on their predictions, it is often possible to show that at least one of them is wrong with a suitable experiment.
+\commentYM{quelle différence avec les implications empiriques d'une théorie normative ?}
 Alàs, descriptive approaches as currently existing in decision theory are not suitable to obtain valid prescriptions.
@@
 Experimental tests to arbitrate between theories may not be feasible in practice, descriptions are not always solely about the future, falsificationist approaches in turn raise epistemological difficulties, and so on.
-Correspondingly, the possible confrontation to empirical data of the theories defined here will likely not suffice to close every discussion about validation.
+Correspondingly, the possible confrontation to empirical data of the theories defined here is no magical means to definitively solve every difficulty about validation.
 My less naïve claim, that should suffice to motivate the present endeavor, is that it is often a good thing for a theory to make empirically testable claims, from the point of view of the possibilities of solving disputes and validating theories.
 
-As the plural indicates, this article defines a kind of theories, called theories of \ac{DJ}, not a specific theory of \ac{DJ}.
+As the plural indicates, this article defines a kind of theory, namely, theories of \ac{DJ}, not a specific theory of \ac{DJ}.
 Specific theories of \ac{DJ} are tailored to a set of situations and yield claims relevant to those situations.
@@
 For similar reasons, I do not claim that the term normative is unanimously used in the literature as defined here.
-This definition encompasses theories used in approaches that do not necessarily self-describe as normative \citep{bell_decision_1988, meinard_rationality_2019}; conversely, some theories considered as normative in the literature, such as some social choice theories, may not fall into the definition proposed here, depending on how they are interpreted.
+The present definition encompasses theories used in approaches that do not necessarily self-describe as normative \citep{bell_decision_1988, meinard_rationality_2019}; conversely, some theories considered as normative in the literature, such as some social choice theories, may not fall into the definition proposed here, depending on how they are interpreted.
 
@@
 Another contrast can now be introduced: the contrast between shallow and reflective behavior. \emph{Shallow behavior} is defined as the everyday, usual behavior of an individual. 
-This is the behavior whose observation defines what \citet[p.\ 16]{von_neumann_theory_2004} describe as the “intuitive” preferences of an individual, those originating from an “immediate sensation” (cited in \citet{fishburn_retrospective_1989}).
+This is the behavior whose observation defines what \citet[p.\ 16]{von_neumann_theory_2004} describe as the “intuitive” preferences of an individual, those originating from an “immediate sensation” (the quotes from their article used here are cited by \citet{fishburn_retrospective_1989}).
 \emph{Reflective behavior}, by contrast, is defined as the behavior that enacts informed, pondered decisions, those that would be taken after due consideration.
@@
 
-Let me state how the approach proposed here to capture reflective preferences differs from those proposed in the literature.
-
-The review of existing approaches aiming at obtaining a model of the reflective preferences of an individual distinguishes two kinds of approaches.
+\subsection{The proposed approach}
+The proposal elaborated in this article defines theories that are both normative, and descriptive of reflective behavior.
+The kind of behavior of interest here is choice behavior, although the proposal is more general.
+
+In fact, the main object of study of this article is judgments about propositions. The main goal is accordingly to study reflective adherence to propositions.
+This will then be applied to determining reflective choice behavior.
+Choice behavior is obtained when considering adherence to propositions of the form: “I ought to choose alternative $\alt$ rather than $\alt'$ if both are available”.
+The alternatives can be concrete objects such as consumable goods.
+
+One of our main preoccupation will be to clarify, using formal and precise definitions, the intuitive notion of reflective adherence to propositions.
+This is done using the concept of \emph{deliberated} judgments (a normative concept) and of \emph{acceptable} propositions (a descriptive concept).
+
+A theory of \ac{DJ} applies to a set of individuals and a set of propositions.
+The \ac{DJ} of an individual $i$ is the set of propositions $\prop$ such that it is legitimate to recommend to $i$ adherence to $\prop$.
+Someone’s \ac{DJ} is not directly observable.
+However, we can observe the reactions of $i$ to arguments in favor and against the propositions.
+A theory of \ac{DJ} assumes that it knows a set of arguments such that exploring the reactions to these arguments “sufficiently” permits to obtain knowledge about someone’s \ac{DJ}.
+Thus, one important task dealt with in \cref{sec:normative} will be to define the notion of acceptability, that serves to capture formally this notion of “sufficient” exploration.
+Intuitively, a proposition is acceptable when some argument makes $i$ seem (according to the observations) to adhere to the proposition whatever the counter-arguments given to $i$, and whatever the sequence of arguments given to $i$ previously.
+
+A theory of \ac{DJ} must use an axiom that relates the descriptive notion of acceptability to the normative notion of being deliberated.
+This axiom simply mandates that whatever is acceptable, is deliberated.
+\Cref{sec:normative} presents it formally.
+
+This defines theories of \ac{DJ} that can be considered normative, as accepting the axiom is sufficient to determine unambiguously a set of legitimate prescriptions to be given to individuals. 
+This is done by linking \acp{DJ} to acceptable propositions, a notion whose major interest is that it can be confronted to empirical observations.
+But at this stage, it is still unclear how to obtain knowledge of someone’s \ac{DJ}, and accordingly, such theories cannot still be considered as descriptive.
+In particular, they are not falsifiable, as they take no position on the reactions of individuals to arguments.
+\Cref{sec:descriptive} accordingly defines descriptive theories of acceptable propositions, assuming given a normative theory of \ac{DJ}.
+
+Such descriptive theories can take multiple forms, and some of them would permit to see clearly that the theory is descriptive in the required sense, that is, that its claims can be falsified given observational data.
+But the task we face, for such theories to be useful, is more complex than this minimal requirement: we have to find forms of theories that are not hugely demanding on the part of the theorist.
+In particular, we do not want to oblige the theorist to predict the whole of the argumentative attitude of individuals if this is not required to obtain information about her \ac{DJ}.
+Thus, \cref{sec:descriptive} defines descriptive theories of \ac{DJ} that only claim to be able to answer counter-arguments, in a sense that will be made precise.
+The desire that its claim be falsifiable is also defined formally.
+More formally, the result that is obtained in that section, and that is the central result of this article, is that if a theory resists all empirical falsification attempts, then it is valid, assuming acceptance of the normative axiom described here above informally (and formally in \cref{sec:normative}).
+A theory is valid if the propositions that it claims are in someone’s \ac{DJ} are indeed in that person’s \ac{DJ}.
+This central result thus amounts to prove the main claim of this article, namely, that accepting a weak normative axiom, supplemented with empirical claims, is enough to capture someone’s reflective preferences.
+
+A possible objection to the usefulness of this approach should perhaps be lifted before delving into the formal descriptions of this rough sketch.
+It may be argued that because this proposition needs a normative axiom, which cannot be validated empirically, it does not fare better than the alternative propositions existing in the literature.
+\ac{SEU}, for example, also can be considered to claim to obtain reflective preferences on the basis of normative axioms.
+I grant that it is impossible to get completely rid of normative axioms, because prescriptions must be linked to descriptions, and this cannot be done in a complete empirical way.
+However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims.
+The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science (again, accepting this claim does not require to ignore that observations themselves rest upon theories).
+Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance.
+(This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.) This does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences.
+It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
+It is also worth noting that the proposed axiom has a specific form that may permit decision makers to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation.
+Detailed exploration of this aspect is deferred to future work.
+
+One long-term goal of this research program is to give individuals the means to reject theories that they find unconvincing after due consideration of all arguments; and accordingly, give incentives to decision theorists to build defenses of these theories able to convince individuals of the soundness of these theories.
+\commentYM{phrase trop longue}This might match \possessivecite{hausman_debate_2010} suggestion that we should use rational persuasion rather than nudge individuals, arguing that it would promote autonomy.
+It also follows \possessivecite[p.\ 72]{guala_logic_2000} suggestion (discussing the Allais paradox) about obtaining relevant data to compare normative behavioral theories: “Before asking whether agents want to revise their choices or not, \emph{both} rival theories should be proposed” (emphasis in the original text).
+
+Let us now examine how the approach proposed here to capture reflective preferences differs from those proposed in the literature.
+
+The next two sections review existing approaches aiming at obtaining a model of the reflective preferences of an individual.
+They distinguish two kinds of approaches.
 \Cref{sec:purification} mentions formal techniques, that can be applied by following an explicit procedure, but that do not consider the reaction of individuals to arguments; while \cref{sec:informal} reviews studies that involve informal discussions with individuals, which do consider arguments, but require involving experts.
@@
 \commentYM{ici aussi, je trouve la mention de ces approches maladroite, car elles sont mises en exergue comme si elles étaient des manières de traiter le problème qui t'intéresse, ce qu'elles ne sont pas}
+
+The field of Empirical social choice \citep{gaertner_empirical_2012} investigates individuals’s judgments about fairness: in a typical laboratory experiment, subjects are described some setting requiring to distribute resources among a set of individuals, and are asked to choose a distribution that they consider fair.
+These interesting approaches permit to study empirically the sense of fairness of real individuals, and compare them to social choice theories.
+They are distinct from the currently proposed approach as they do not involve arguments; and do not specifically aim to prescribe to an individual.
 
@@
 These proposals leave unspecified how to confirm or disconfirm them empirically, thus, in particular, how to empirically investigate disagreements between theories: if two theories, on the basis of the same observed data, postulate that they correspond to different purified preferences, the disagreement may at best be arbitrated using ad-hoc, case by case criteria to assess for their relative plausibility.
-By contrast, the present proposal indicates a clear, systematic empirical way to abitrate disagreements.
+By contrast, the present proposal indicates a clear, systematic empirical way to arbitrate disagreements.
 %These proposals deserve a detailed comparison to the current one, but this requires a treatment that cannot be given in this article.
@@
 J'ai l'impression que la citation dit que, parfois, il y a des forces psychologiques qui s'opposent à l'adoption d'un processus de décision, quand bien même celui-ci aurait des qualités indéniables}
-Beyond the controversial \ac{AHP} mentioned in the introduction, famous decision analysts have voiced disagreements with normative theories of decision making \citep{ellsberg_risk_1961, allais_so-called_1979} that are however generally applied in the field.
+Beyond the controversial \ac{AHP} mentioned in the introduction, strongly criticized, for example, by \citet[p.\ 53]{howard_foundations_2007}, famous decision analysts have voiced disagreements with normative theories of decision making \citep{ellsberg_risk_1961, allais_so-called_1979} that are however generally applied in the field.
 \commentYM{il me semble ici intenable de faire l'économie de définir ce que tu appelles "normative theories"}
@@
 Je trouve stupéfiant qu’on puisse trouver ces propos dans la littérature, écrits noir sur blanc.
-Si je ne les cite pas, un lecteur pourrait (ou devrait) ne pas me croire quand j’affirme que des gens trouvent que ce n’est pas grave que deux études soi-disant scientifiques arrivent à des conclusions contradictoires.
+Si je ne les cite pas, un lecteur pourrait (ou devrait) ne pas me croire quand j’affirme que des gens trouvent que deux études soi-disant scientifiques puissent arriver à des conclusions apparemment contradictoires et être toutes les deux valides.
 La citation étendue permet de comprendre, je crois, leur point de vue, et de se faire une idée de ce qu’ils veulent dire par là.}
@@
 Ce que je comprennais jusqu'ici était que tu cherchais un moyen de connaître les "preferences that represent informed, pondered decisions, that would be taken after due consideration by the individual", ce qui me semble être un tout autre projet}
-\commentOCf{Je propose de trancher entre approches normatives en utilisant des données empiriques, plutôt que simplement la force de conviction des axiomes (qui parlent différemment à différentes personnes et peuvent conserver les désaccords intacts).
+\commentOCf{En gros, je propose de trancher entre approches normatives en utilisant des données empiriques, plutôt que simplement la force de conviction des axiomes (qui parlent différemment à différentes personnes et peuvent conserver les désaccords intacts).
 Je ne sais pas si c’est plus clair maintenant.}
@@
 First, the previous proposal requires the individual to declaratively take position on notions that may be unclear to him, as they include some possibly counterfactual situations, and as the concept of turning an argument into an uneffective argument may not be understood in the same way by everybody.
-In order for the conclusions about $i$’s \ac{DJ} to hold, we must be sure that $i$ understands the semantics of the relations on which it is based as we do.
+In order for the conclusions about $i$’s \ac{DJ} to hold, we must be sure that $i$ understands the semantics of the relations on which it is based as analysts do.
 It is therefore desirable that these notions have unambiguous semantics.
@@
 
-Finally, the current proposal links \ac{DJ} and deliberated preferences. \commentYM{indispensable de dire explicitement quelle est la différence entre les deux dès maintenant}
+Finally, the current proposal links \acp{DJ} and \acp{DP}. \commentYM{indispensable de dire explicitement quelle est la différence entre les deux dès maintenant}
 
 \Citet{meinard_justification_2020} discuss some requirements on justification of recommendations, which gives further arguments in favor of studying \acp{DJ}.
-
-\subsection{The proposed approach}
-The proposal elaborated in this article defines theories that are both normative, and descriptive of reflective behavior.
-The kind of behavior of interest here is choice behavior, although the proposal is more general.
-
-In fact, the main object of study of this article is judgments about propositions. The main goal is accordingly to study reflective adherence to propositions.
-This will then be applied to determining reflective choice behavior.
-Choice behavior is obtained when considering adherence to propositions of the form: “I ought to choose alternative $\alt$ rather than $\alt'$ if both are available”.
-The alternatives can be concrete objects such as consumable goods.
-
-One of our main preoccupation will be to clarify, using formal and precise definitions, the intuitive notion of reflective adherence to propositions.
-This is done using the concept of \emph{deliberated} judgments (a normative concept) and of \emph{acceptable} propositions (a descriptive concept).
-
-A theory of \ac{DJ} applies to a set of individuals and a set of propositions.
-The \ac{DJ} of an individual $i$ is the set of propositions $\prop$ such that it is legitimate to recommend to $i$ adherence to $\prop$.
-Someone’s \ac{DJ} is not directly observable.
-However, we can observe the reactions of $i$ to arguments in favor and against the propositions.
-A theory of \ac{DJ} assumes that it knows a set of arguments such that exploring the reactions to these arguments “sufficiently” permits to obtain knowledge about someone’s \ac{DJ}.
-Thus, one important task dealt with in \cref{sec:normative} will be to define the notion of acceptability, that serves to capture formally this notion of “sufficient” exploration.
-Intuitively, a proposition is acceptable when some argument makes $i$ seem (according to the observations) to adhere to the proposition whatever the counter-arguments given to $i$, and whatever the sequence of arguments given to $i$ previously.
-
-A theory of \ac{DJ} must use an axiom that relates the descriptive notion of acceptability to the normative notion of being deliberated.
-This axiom simply mandates that whatever is acceptable, is deliberated.
-\Cref{sec:normative} presents it formally.
-
-This defines theories of \ac{DJ} that can be considered normative, as accepting the axiom is sufficient to determine unambiguously a set of legitimate prescriptions to be given to individuals. 
-This is done by linking \acp{DJ} to acceptable propositions, a notion whose major interest is that it can be confronted to empirical observations.
-But at this stage, it is still unclear how to obtain knowledge of someone’s \ac{DJ}, and accordingly, such theories cannot still be considered as descriptive.
-In particular, they are not falsifiable, as they take no position on the reactions of individuals to arguments.
-\Cref{sec:descriptive} accordingly defines descriptive theories of acceptable propositions, assuming given a normative theory of \ac{DJ}.
-
-Such descriptive theories can take multiple forms, and some of them would permit to see clearly that the theory is descriptive in the required sense, that is, that its claims can be falsified given observational data.
-But the task we face, for such theories to be useful, is more complex than this minimal requirement: we have to find forms of theories that are not hugely demanding on the part of the theorist.
-In particular, we do not want to oblige the theorist to predict the whole of the argumentative attitude of individuals if this is not required to obtain information about her \ac{DJ}.
-Thus, \cref{sec:descriptive} defines descriptive theories of \ac{DJ} that only claim to be able to answer counter-arguments, in a sense that will be made precise.
-The desire that its claim be falsifiable is also defined formally.
-More formally, the result that is obtained in that section, and that is the central result of this article, is that if a theory is convincing and normatively adequate, then it is valid.
-That a theory is convincing is (as also shown in the same section) the same as demanding that it resists all empirical falsification attempts.
-It is normatively adequate if it satisfies the normative axiom described here above informally (and formally in \cref{sec:normative}).
-And it is valid if the propositions that it claims are in someone’s \ac{DJ} are indeed in that person’s \ac{DJ}.
-This central result thus amounts to prove the main claim of this article, namely, that accepting a weak normative axiom, supplemented with empirical claims, is enough to capture someone’s reflective preferences.
-
-A possible objection to the usefulness of this approach should perhaps be lifted before delving into the formal descriptions of this rough sketch.
-It may be argued that because this proposition needs a normative axiom, which cannot be validated empirically, it does not fare better than the alternative propositions examined in the previous sections.
-\ac{SEU}, for example, also claim to obtain reflective preferences on the basis of normative axioms.
-I grant that it is impossible to get completely rid of normative axioms, because prescriptions must be linked to descriptions, and this cannot be done in a complete empirical way.
-However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims.
-The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science (again, accepting this claim does not require to ignore that observations themselves rest upon theories).
-Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance or of being compatible with more preference relations.
-(This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.) This does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences.
-It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
-It is also worth noting that this axiom has a specific form that may permit decision makers to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation.
-Detailed exploration of this aspect is deferred to future work.
-
-One long-term goal of this research program is to give individuals the means to reject theories that they find unconvincing after due consideration of all arguments; and accordingly, give incentives to decision theorists to build defenses of these theories able to convince individuals of the soundness of these theories.
-\commentYM{phrase trop longue}This might match \possessivecite{hausman_debate_2010} suggestion that we should use rational persuasion rather than nudge individuals, arguing that it would promote autonomy.
-It also follows \possessivecite[p.\ 72]{guala_logic_2000} suggestion (discussing the Allais paradox) about obtaining relevant data to compare normative behavioral theories: “Before asking whether agents want to revise their choices or not, \emph{both} rival theories should be proposed” (emphasis in the original text).
 
@@
 
-\section{Informal presentation}
-\commentOCf{Je pense changer d’approche : enlever cette section et intégrer les explications informelles directement dans la présentation formelle. À faire…}
-\commentYM{Le lecteur n'a aucune idée de ce qu'il doit s'attendre à trouver dans cette section, et de la mesure dans laquelle ça va permettre d'avancer dans la résolution de la problématique : lecteur perdu = pas bien}
-\commentYM{par qui ? dans le cadre de l'analyse ou en amont ? et pourquoi sur la seule base de la soundness de l'axiome ? pourquoi pas sur la base de ses implications dans des cas concrets ?}
-An empirical theory for a given normative theory, by contrast, makes empirical claims, hence, can be confronted to observations \commentYM{quelle différence avec les implications empiriques d'une théorie normative ?}.
-What I call here an empirical theory, for simplicity, is not however purely empirical, but can also be considered normative, for two reasons.
-First, its conclusions inevitably rest on the normative validity of the normative theory for which it is built.
-Second, it claims to capture preferences that provide an appropriate basis for recommendation.
-Empirical theories of \ac{DJ} could thus be called empirical normative theories of \ac{DJ}.\commentYM{est-ce la même chose que ce qui est déjà appelé à peu près comme ça dans la littérature ?
-Je parle par exemple de toutes les théories empiriques de la justice}
-
-\subsection{Normative theories}
-Normative theories define an agenda: a set of propositions that we are interested in knowing the deliberated judgment of individuals about ; a set of individuals that the theory claims applies to; a set of arguments;\commentYM{pourquoi est-ce que cela fait partie de la théorie ?
-c'est plutôt un des éléments du contexte d'une de SES APPLICATIONS à mon sens.
-L'expression  "normative model" serait selon moi bien plus appropriée si on veut que les détails du cas d'application fassent partie de l'objet.
-"Theory" a de très fortes connotations de généralité} and a protocol of observation of the judgments an individual adopts towards a proposition after exposure to various arguments \commentYM{pourquoi le protocole d'obs est-il déjà évoqué ici ?
+\section{Normative theories}
+\label{sec:normative}
+\subsection{Definition}
+A normative theory of \ac{DJ} is a tuple $(\allprops, \allargs, I, {\allleadsto})$, where $\allprops$ is a set of propositions, $\allargs$ is a set of arguments, $I$ represents a set of individuals, and ${\allleadsto}$ is an observation protocol.
+Intuitively speaking, the theory claims that the proposed observation protocol, observing the reactions of individuals from $I$ to arguments from $\allargs$, is normatively appropriate to yield recommendations to individuals about the propositions from $\allprops$.
+These concepts are detailed in this section.
+\commentYM{pourquoi le protocole d'obs est-il déjà évoqué ici ?
 j'aurais cru que ce protocole relève de la théorie empirique qui se greffe sur la théorie normative en question.
@@
 De l'axiome, il n'est plus question.
-Où est-il ?}.\commentYM{il manque dans la "theorie normative" ce que j'aurais considéré comme le plus important : un modèle de la force de conviction des arguments et de leurs liens avec les propositions.
+Où est-il ?}.
+\commentYM{il manque dans la "theorie normative" ce que j'aurais considéré comme le plus important : un modèle de la force de conviction des arguments et de leurs liens avec les propositions.
 J'aurais dit que l'axiome de la "théorie" se cacherait là-dedans}
 
-Examples of propositions to be included in \commentYM{the}agenda \commentYM{might}include: “I ought to pay at most \$100 for purchasing bundle $b$”, “I ought to acquire alternative $a$ rather than $b$ if it is available in the same conditions”; “I ought not to perform action $a$ because it is immoral”.
+The set $\allprops$ is called the agenda of the theory.
+Propositions composing the agenda are not further detailed, they are simply atomic elements.
+A proposition must be an element such that one can observe whether an individual adheres to it, or whether an individual’s behavior is consistent with it.
+\commentYM{pourquoi est-ce que cela fait partie de la théorie ?
+c'est plutôt un des éléments du contexte d'une de SES APPLICATIONS à mon sens.
+L'expression  "normative model" serait selon moi bien plus appropriée si on veut que les détails du cas d'application fassent partie de l'objet.
+"Theory" a de très fortes connotations de généralité}
+Examples of propositions include: “I ought to pay at most \$100 for purchasing bundle $b$”, “I ought to acquire alternative $a$ rather than $b$ if it is available in the same conditions”; “I ought not to perform action $a$ because it is immoral”.
+
+Another primitive elements of a normative theory is the set of arguments $\allargs$.
+Arguments are defined here as anything that can be presented to an individual that may possibly influence her judgment.
+As an example, an argument can be a text presenting the features of an alternative
+\commentYM{donc un texte qui ne prend pas de position sur l'alternative, qui est purement descriptif, est un argument ?
+cela me semble raisonnable, mais ça mérite discussion}, or arguing for the (im)morality of an action.
+An argument may be purely descriptive or may forcefully argue in favor of the truth or falsity of one or several propositions.
+The term argument generally evokes a debate, a metaphor appropriate for the comparison of theories that will be described later; but that should be taken with a grain of salt: an image, a tag price, a poem can be an argument in this article.
 
@@
 Dans ce cas pourquoi ne pas le dire clairement ?}.
-(More about this in conclusion.
-\TODO{})
-
-Arguments are defined here as anything that can be presented to an individual that may possibly influence her judgment.
-As an example, an argument can be a text presenting the features of an alternative \commentYM{donc un texte qui ne prend pas de position sur l'alternative, qui est purement descriptif, est un argument ?
-cela me semble raisonnable, mais ça mérite discussion}, or arguing for the (im)morality of an action.
-The term argument evokes a debate, a metaphor appropriate for the comparison of theories that will be described later; but that should be taken with a grain of salt: an image, a tag price, a poem can be an argument in this article.
 
@@
 les cycles ?
-bref, de quoi parles-tu ?}of arguments to an individual, and how to observe her resulting judgment about a proposition of interest.
+bref, de quoi parles-tu ?}
+\commentOCf{C’est le \href{https://en.wikipedia.org/wiki/Sequence}{terme habituel} en mathématiques, à ma connaissance.}
+of arguments to an individual, and how to observe her resulting judgment about a proposition of interest.
 This protocol permits to determine whether a sequence of arguments “leads” a given individual to a given proposition.
 If the arguments are texts and propositions are of the form “I ought to acquire alternative $a$ rather than $b$”, an example of such a protocol is: present each argument (each text) in the sequence to the individual, asking her to read it carefully; then give the individual a choice between $a$ and $b$; the sequence of arguments is considered to having led the individual to the proposition “I ought to acquire alternative $a$ rather than $b$” iff he chose $a$ rather than $b$.
-In order to allow for repeated observations with a given individual without modifying his endowment \commentYM{en quel sens utilises-tu ce terme ici ?}, this example protocol should either be content with purely hypothetical choices, or can make these choices binding by letting the individual know that one of his choices will be picked randomly at the end of the experiment and honored.\commentYM{pas compris le second membre de l'alternative}
-
-The judgment of an individual towards propositions may evolve during her exposition to sequences of arguments.
-Of interest to theories of \ac{DJ} are the cases where a so-called decisive argument exists for a given proposition: an argument is decisive when its presence at the end of the sequence of arguments systematically leads the individual to \commentYM{accepting}the proposition, whatever the sequence of arguments.
-An argument is at the end of a sequence iff it is the last or before last argument of the sequence.
-Therefore, an argument is decisive when, intuitively, it is able to resist every counter-arguments.
-
-Theories of \ac{DJ} attempt to capture the \emph{\acl{DJ}} of the individuals it deals with, towards some of the propositions in the agenda. 
-The \ac{DJ} of an individual is conceived here as existing independently of any theories of decision.
-The \emph{normative adequacy} axiom, the sole axiom on which a normative theory rests, defines a proposition as being in the deliberated judgment of an individual whenever some argument is decisive for that proposition.
-Accepting this axiom require to accept that decisive arguments, in the sense defined here, reveal something about the \ac{DJ} of an individual.
-
-That the \ac{DJ} of an individual exists independently of any theory of decision making might be considered a strong assumption, by analogy to shallow preferences: psychologists have shown that shallow preferences often depend on a priori irrelevant features pertaining to the description of the decision problem or the context of interrogation.
-Preferences are often said to be constructed, thus, to not exist independently of the framing and context of study.
-
-With no intent of reducing the importance of these findings, it is important to qualify such statements.
-In supplement to them being not necessarily applicable to reflective preferences, the findings of psychologists do not, evidently, show that all preference statements are labile.
-As \citet[p.\ xvi]{lichtenstein_construction_2006} write, “To be sure, there are limits to the process of construction.
-Some televisions just won’t sell; most of the time, people are unlikely to want 80\% of their wages to go into savings.
-It would be an overstatement to say of preferences, as Gertrude Stein said of Oakland, that “there is no there there.” \commentYM{ce § et le précédent me semble mériter plus que le reste une réécriture.
-Par ailleurs, je ne vois pas à quoi ils servent dans cette sous-section}
-
-This remark points towards the importance of allowing for incomplete theories of reflective preferences.
-\commentYM{définir ce qu'il faut entendre ici par "incomplete"} As \citet{mandler_difficult_2001} discusses in details, it would be unrealistic to postulate that individuals would, after due reflection, in non trivial decision problems, adopt a well specified judgment about any possible proposition of interest.
-From this does not follow that \acp{DJ} do not exist, but that someone’s \ac{DJ} should not be considered to be necessarily complete. 
-\TODO{Check Mandler.}
-The definitions of the theories presented here accordingly tolerate both theory incompleteness, which permits the theory to stay silent on some of the propositions in the agenda, and, more fundamentally, deliberation incompleteness, which permits to tolerate that for some propositions, neither it nor its negation figure in someone’s \ac{DJ}.
-%\cref{sec:incompl} defines formally the notions of theory incompleteness and deliberation incompleteness, and briefly analyzes their relationships.
-
-\subsection{Empirical theories}
-A normative theory defines how to determine that an argument is not decisive for a given proposition: suffices to find a sequence of arguments that does not lead to that proposition \commentYM{pas compris : tu veux dire "une séquence qui se termine par cet argument et qui n'amène pas à cette proposition ?}.
-This, in turn, under condition of accepting its normative validity \commentYM{mais c'est quoi cette "normative validiy" ?
-de quelles conditions parles-tu ?}, permits to know something about the \ac{DJ} of an individual.
-But this gives no concrete means to know someone’s \ac{DJ}.
-The set of potentially relevant arguments will generally be very large, and can’t be explored thoroughfully \commentYM{certain que ce terme existe ?}.
-More importantly, only some sequences of arguments can be tested for a given individual.
-That is because, first, the individual’s patience is limited, and second, once a sequence has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective.
-Postulating that the individual forgets after some time and separating the tests in time might mitigate this problem, but not necessarily cancel it.
-\commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question.
-Je doute cependant qu'un lecteur innocent comprenne un traitre mot}
-
-%As a result, it should be possible to determine someone’s \ac{DJ} using only a small increasing set of sequences of arguments.
-A set of sequences of arguments is increasing iff the sequences can be ordered completely such that each sequence following another one “continues” the other one: its first arguments are those constituting the sequence that it follows.
-
-These two problems are tackled by introducing empirical theories of \ac{DJ}.
-An empirical theory for a given normative theory defines a subset of propositions of the agenda, that it claims are contained in the \acp{DJ} of individuals concerned by the normative theory.
-They are called the proposition that the theory supports.
-\commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi} The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments.
-This is accomplished by three binary relations, part of the definition of empiricial theories: one represents its initial arguments, one plans the possible attacks, and one defines its counter-arguments.
-(An empirical theory also defines a concatenation operation able to dynamically build arguments from fragments of arguments, an aspect which is not discussed in this informal presentation.)
-The theory claims that when one of its arguments in support of one of its claims is unconvincing to an individual, it is because of one of the planned attacks; and the theory claims to be able to provide counter-arguments to such attacks as they come, that will in turn be either convincing to the individual, or fail to be because of some planned attack.
-(The theory is also constrained to have “finite depth”, meaning that it must set an a priori limit to the number of such iterations of attacks and counter-arguments.)
-
-Thanks to these operators, an empirical theory may adjust its argumentation to each individual \commentYM{je ne comprends pas cette phrase, et en particulier le sens qu'il faut donner au terme "adjust"}.
-Instead of having to give a single decisive argument in support of its claims, the theory may react to exactly the counter-arguments that a given individual thinks relevant.
-This task is easier, but still permits to obtain what is desired in this article: there exists a purely empirical property \commentYM{kezako ?}of a theory, called convincingness, that, together with an axiom about the normative adequacy of the observation protocol, implies the correctness of the claims of the theory.
-In more details, first, the claim of the theory, of being able to argue convincingly, can be checked by ensuring that no falsification instances exist, thus, it is a fully empirical claim (in the sense that it requires no axiom).
-Second, granted normative adequacy, if indeed a theory is convincing, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}.
-These claims are proven in \cref{th:convnofals,th:valid}.
-
-The following section defines normative and empirical theories precisely.
-
-\commentYM{arrivé à la fin du 2, je n'ai qu'une très vague idée de ce que sont ce que tu appelles des "theories normatives" et des "théories empiriques".
-Pour un lecteur comme moi du moins, cette section ne joue donc pas son rôle, qui je présume, est de donner une idée du contenu avant d'entrer dans le formalisme.}
-
-\section{Normative theories}
-\label{sec:normative}
-\subsection{Definition}
-One of the primitive elements of a normative theory is a set of arguments $\allargs$.
-(The calligraphic letter $S$ is used to denote the arguments in order to reserve the letter $A$ for sets of alternatives.)
-Given a set of arguments $\allargs$, define the set of finite sequences of elements in $\allargs$ \commentYM{qu'est-ce qui lie les uns aux autres les éléments d'une séquence ?
+
+To define formally the notion of an observation protocol, the concept of a sequence of arguments is required.
+Define the set of finite sequences of elements in $\allargs$ \commentYM{qu'est-ce qui lie les uns aux autres les éléments d'une séquence ?
 pourquoi est-ce que ça s'appelle une "séquence" ?
 une connotation temporelle ?
-une idée de succession ?}(including the empty sequence) as $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$.\commentYM{la notation $\allhist$ rend les choses inutilement difficiles à lire.
+une idée de succession ?}
+(including the empty sequence) as $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$.\commentYM{la notation $\allhist$ rend les choses inutilement difficiles à lire.
 Pourquoi noter ça comme on noterait $\allargs$ sans le zéro, si ça voulait dire quelque chose ?
 J'aurais inventé un symbole du genre $ \allargs^{\intvl{}}$ ; par ailleurs je trouve l'explication relative à l'empty sequence particulièrement alambiquée}
-Throughout the article, $\N$ includes zero and $\N^* = \N \setminus \set{0}$.
+\commentOCf{Il me semble assez naturel de, étant donné un ensemble de caractères $S$, définir l’ensemble des chaines de caractères par $S^*$ (représentant le fait de prendre toutes les puissances possibles de $S$), mais c’est peut-être un tropisme d’informaticien qui ne sera donc pas compris par des lecteurs économistes.
+J’ai vu la notation $Seq(\allargs)$ être utilisée, mais elle me semble un peu longue, vu l’usage intensif de ce symbole.
+Oui, peut-être en viendrai-je à l’invention que tu proposes, mais inventer ses propres symboles n’est légitime que si aucun n’existe déjà.
+Je vais essayer d’interroger d’autres gens, dis-moi en attendant si tu penses qu’on peut s’y habituer ou si c’est vraiment très dérangeant.}
+Throughout the article, $\N$ includes zero. %and $\N^* = \N \setminus \set{0}$. 
 Given $j, k \in \N$, the notation $\intvl{j, k}$ represents $\set{l \suchthat j ≤ l ≤ k}$. 
-Note that $\intvl{1, 0} = \emptyset$, and given any set $S$, the notation $S^\emptyset$ represents the empty set.
-A generic element of $\allhist$ is denoted by $\hist$ and called a path.
-
-Two supplementary primitive elements of a normative theory are its agenda $\allprops$, whose elements are called propositions; and a set of individuals $I$ that the theory applies to.
-Given a set of individuals, a set of arguments and an agenda, an observation protocol ${\allleadsto}: I → \allprops^{\allhist}$ maps individuals and paths to propositions. 
+%Note that $\intvl{1, 0} = \emptyset$, and given any set $S$, the notation $S^\emptyset$ represents the empty set. 
+A generic element of $\allhist$ is denoted by $\hist$ and called an argumentative path, or simply a path when this raises no ambiguity.
+
+An observation protocol ${\allleadsto}: I → \allprops^{\allhist}$ maps individuals and paths to propositions. 
 Equivalently, given any individual $i \in I$, ${\ileadsto}: \allhist → \allprops$ maps paths to propositions for this individual. 
@@
 Il me semble que ça ressemble + à une définition formelle de ce que je disais plus haut manquer dans ta définition}
-
-A normative theory is a tuple $(\allprops, \allargs, I, {\allleadsto})$ 
-satisfying the constraints described here above \commentYM{lesquelles ?
-je pense qu'un article doit guider le lecteur pour in fine le convaincre, pas tester ses capacités à retrouver son chemin dans un dédale.
-Quelles sont les contraintes en question ?
-Ou sont elles decrites "here above" ?}.
+\commentOCf{Je ne comprends pas le problème, il faut qu’on en discute.}
+
+This defines a normative theory of \ac{DJ}. 
+To make it useful, an axiom is required that links the observable reactions of the individuals to their \ac{DJ}.
+This will be done through the notion of a decisive argument, that is, intuitively, an argument that is able to convince an individual of the acceptability of a proposition whatever the argumentative path the individual has been submitted to.
+For formal definitions, some supplementary notations must be defined.
+
+\subsection{Normative adequacy}
+The \ac{DJ} of an individual $i$ is denoted by $\iprops \subseteq \allprops$.
+It represents the (a priori unknown) set of propositions that can legitimately be recommended to $i$.
+It is independent of any normative theory.
+A normative theory of \ac{DJ} claims that it knows part of the \ac{DJ} of the individuals $i \in I$.
 
@@
 
-Given $\hist \in \allhist$, if $l$ denotes its length, $\hist(\intvl{1, l})$ denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
-Let $\histend = \hist(\intvl{\max(1, l-1), l})$ denote the set containing the last two arguments of the sequence $\hist$ if the sequence has at least two elements; and all arguments of the sequence if it has exactly one element or is empty.
-
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstost \prop$.\commentYM{comprends pas.
-Tu définis $\ileadstost$ par $\ileadstost$.
-A part dans une définition par récurrence, qui réclame une conditions initiale, je ne vois pas comment une telle définition peut définir quoi que ce soit}
-\commentYM{et que va-t-on lire dans la suite ? faut un tout petit peu tenir la main du lecteur}
-
-\subsection{Coherence}
-\commentYM{qu'est-ce que le lecteur doit s'attendre à trouver dans cette section ? Le plan n'est pas compréhensible si tu n'en dis rien}
+The judgment of an individual towards propositions may evolve during her exposition to sequences of arguments.
+Of interest to theories of \ac{DJ} are the cases where a so-called decisive argument exists for a given proposition: an argument is decisive, informally, when its presence towards the end of the sequence of arguments systematically leads the individual to accepting the proposition, whatever the sequence of arguments.
+Therefore, an argument is decisive when, intuitively, it is able to resist every counter-arguments.
+
+Given $\hist \in \allhist$, if $l$ denotes its length, $\range(\hist) = \hist(\intvl{1, l})$ denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
+Let $\histend = \hist(\intvl{\max(1, l-1), l})$ denote the set containing the last two arguments of the sequence $\hist$ if the sequence has at least two elements; the unique argument of the sequence if it has exactly one element; and the empty set if it is empty.
+
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto \prop$. 
+When $\ar \ileadstost \prop$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view. 
+This definition mandates that $\ar$ be effective (in the sense of leading $i$ to adhere to $\prop$, as determined by the observation protocol) whatever the sequence of arguments presented to $i$, so long as $\ar$ is presented “towards the end” of the sequence, that is, as a last or before last argument.
+Given any $i \in I$, when some argument is decisive for some proposition $\prop$, thus, when $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop$, the proposition is said to be acceptable, from $i$’s point of view.
+
+The following axiom permits the theory to have bite on what should be recommended to $i$. It says that it is sufficient that a proposition be acceptable to be in $i$’s \ac{DJ}.
 \begin{axiom}[Normative adequacy]
@@
 
-A relation $n \subseteq \allprops × \allprops$ is said to be an incompatibility relation iff $\forall \hist \in \allhist, (\prop, \propbar) \in n: \hist \ileadsto \prop ⇒ \hist \nileadsto \propbar$.
+To end the presentation of the normative theories of \ac{DJ}, it may be useful to analyze the status of contradictory propositions.
+\Cref{th:protcoh} shows that two propositions which are readily judged to be incompatible by $i$ cannot both be acceptable.
+In supplement, it may be interesting to observe that theories of \ac{DJ} do not require to postulate that $i$’s \ac{DJ} is complete, in the sense that when the agenda is closed under negation, it must not necessarily be the case that either the proposition or its negation is in $i$’s \ac{DJ}.
+This justifies that the normative axiom asks only for an implication between acceptability and \ac{DJ}, instead of an equivalence.
+
+\subsection{Coherence and completeness}
+A relation $n \subseteq \allprops × \allprops$ is said to be an incompatibility relation iff $\forall \hist \in \allhist, (\prop, \prop') \in n: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$.
 Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $(\prop, \prop') \in n$.
-Such a pair will generally denoted by $(\prop, \propbar)$.
-(This article does not use the overline to denote set complementarity, thus this notation should create no confusion.)
-
-It is desirable to ensure that this axiom cannot lead to incompatible propositions being considered deliberated. Consider the following proposition.
-\begin{proposition}[Protocol coherence]
+
+The following proposition shows that \cref{ax:norm} cannot lead to incompatible propositions being considered deliberated. 
+\begin{proposition}[Coherence of acceptability]
 	\label{th:protcoh}
@@
 
-To further analyze this \commentYM{analyser quoi ?
-qu'y a-t-il à analyser et pourquoi voudrait-on l'analyser ?}and related matters, consider defined a negation operator $¬$ on $\allprops$.
+To further analyze coherence matters, 
+\commentYM{analyser quoi ? qu'y a-t-il à analyser et pourquoi voudrait-on l'analyser ?}
+consider defined a negation operator $¬$ on $\allprops$.
 $¬$ is a negation operator iff it is an involution operator (thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$) and furthermore satisfying, $\forall \phi \in \allprops: \hist \ileadsto \prop ⇒ \hist \nileadsto ¬\prop$.
 Given any $i \in I$, say that a proposition $\prop \in \allprops$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost \propbar$.
-The $i$-decidable propositions are those on which the normative theory permits to take a position. 
+The $i$-decidable propositions are those on which the normative theory permits, in principle, to take a position. 
 %It will generally be unknown in practical applications, and may be empty.
-The next proposition ensures an unambiguous interpretation of the content of $\iprops$ for all $i$-decidable propositions.
-The symbol $\oplus$ denotes the exclusive disjunction; thus $\prop \in \iprops \oplus ¬\prop \in \iprops$ is equivalent to: $\prop \in \iprops ⇔ ¬\prop \notin \iprops$ \commentYM{au moins dans les propositions et définitons de cette section, l'introduction  de cet opérateur n'apporte rien, et rend la lecture inutilement difficile}.
+When a proposition $\prop$ is such that $\prop \in \iprops ⇔ ¬\prop \notin \iprops$, I say that this proposition admits an unambiguous interpretation in terms of $i$’s \ac{DJ}.
+The next proposition ensures an unambiguous interpretation of all $i$-decidable propositions.
+%The symbol $\oplus$ denotes the exclusive disjunction; thus $\prop \in \iprops \oplus ¬\prop \in \iprops$ is equivalent to: $\prop \in \iprops ⇔ ¬\prop \notin \iprops$ \commentYM{au moins dans les propositions et définitons de cette section, l'introduction  de cet opérateur n'apporte rien, et rend la lecture inutilement difficile}.
 It can be seen to hold by using \cref{th:protcoh}.
@@
 	Any normative theory with a negation operator $¬$ satisfy,
-	$\forall i \in I, \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop] ⇒ [\prop \in \iprops \oplus ¬\prop \in \iprops]$.
+	$\forall i \in I, \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop] ⇒ [\prop \in \iprops ⇔ ¬\prop \notin \iprops]$.
 \end{proposition}
 
-This interpretability is however restricted to the $i$-decidable propositions.
-The following definitions and propositions (assuming a normative theory and a negation operator $¬$ defined) argue \commentYM{"suggest" ou "show", mais je ne pense pas qu'on puisse dire que des "definitions" ou "propositons" "argue" quoi que ce soit}that going further is not desirable.
+This interpretability is however restricted to the $i$-decidable propositions. The following proposition and discussion (assuming a normative theory and a negation operator $¬$ defined) argue 
+\commentYM{"suggest" ou "show", mais je ne pense pas qu'on puisse dire que des "definitions" ou "propositons" "argue" quoi que ce soit}
+that going further is not desirable.
 
@@
 \end{proposition}
-Theories as defined here do not mandate Theory completeness.This is good for two reasons.
+Theories as defined here do not mandate Theory completeness.
+This is good for two reasons.
 First, even the weaker Deliberation completeness can be considered too strong.
@@
 
+That the \ac{DJ} of an individual exists independently of any theory of decision making might be considered a strong assumption, by analogy to shallow preferences: psychologists have shown that shallow preferences often depend on a priori irrelevant features pertaining to the description of the decision problem or the context of interrogation.
+Preferences are often said to be constructed, thus, to not exist independently of the framing and context of study.
+
+With no intent of reducing the importance of these findings, it is important to qualify such statements.
+In supplement to them being not necessarily applicable to reflective preferences, the findings of psychologists do not, evidently, show that all preference statements are labile.
+As \citet[p.\ xvi]{lichtenstein_construction_2006} write, “To be sure, there are limits to the process of construction.
+Some televisions just won’t sell; most of the time, people are unlikely to want 80\% of their wages to go into savings.
+It would be an overstatement to say of preferences, as Gertrude Stein said of Oakland, that “there is no there there.”
+\commentYM{ce § et le précédent me semble mériter plus que le reste une réécriture. Par ailleurs, je ne vois pas à quoi ils servent dans cette sous-section}
+
+This remark points towards the importance of allowing for incomplete theories of reflective preferences. \commentYM{définir ce qu'il faut entendre ici par "incomplete"} 
+As \citet{mandler_difficult_2001} discusses in details, it would be unrealistic to postulate that individuals would, after due reflection, in non trivial decision problems, adopt a well specified judgment about any possible proposition of interest.
+From this does not follow that \acp{DJ} do not exist, but that someone’s \ac{DJ} should not be considered to be necessarily complete. 
+\TODO{Check Mandler.}
+The definitions of the theories presented here accordingly tolerate both theory incompleteness, which permits the theory to stay silent on some of the propositions in the agenda, and, more fundamentally, deliberation incompleteness, which permits to tolerate that for some propositions, neither it nor its negation figure in someone’s \ac{DJ}.
+
 \commentYM{dans toute cette section, il me semble qu'il faudrait soit des exemples, soit des explications verbales}
@@
 \label{sec:descriptive}
+\subsection{Empirical theories, informally}
+\commentOCf{TODO : intégrer les explications dans la partie formelle et les reformuler.}
+A normative theory defines how to determine that an argument is not decisive for a given proposition: suffices to find a sequence of arguments that does not lead to that proposition \commentYM{pas compris : tu veux dire "une séquence qui se termine par cet argument et qui n'amène pas à cette proposition ?}.
+This, in turn, under condition of accepting its normative validity \commentYM{mais c'est quoi cette "normative validiy" ?
+de quelles conditions parles-tu ?}, permits to know something about the \ac{DJ} of an individual.
+But this gives no concrete means to know someone’s \ac{DJ}.
+The set of potentially relevant arguments will generally be very large, and can’t be explored thoroughfully \commentYM{certain que ce terme existe ?}.
+More importantly, only some sequences of arguments can be tested for a given individual.
+That is because, first, the individual’s patience is limited, and second, once a sequence has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective.
+Postulating that the individual forgets after some time and separating the tests in time might mitigate this problem, but not necessarily cancel it.
+\commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question.
+Je doute cependant qu'un lecteur innocent comprenne un traitre mot}
+
+%As a result, it should be possible to determine someone’s \ac{DJ} using only a small increasing set of sequences of arguments.
+A set of sequences of arguments is increasing iff the sequences can be ordered completely such that each sequence following another one “continues” the other one: its first arguments are those constituting the sequence that it follows.
+
+These two problems are tackled by introducing empirical theories of \ac{DJ}.
+An empirical theory for a given normative theory defines a subset of propositions of the agenda, that it claims are contained in the \acp{DJ} of individuals concerned by the normative theory.
+They are called the proposition that the theory supports.
+\commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi} The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments.
+This is accomplished by three binary relations, part of the definition of empiricial theories: one represents its initial arguments, one plans the possible attacks, and one defines its counter-arguments.
+(An empirical theory also defines a concatenation operation able to dynamically build arguments from fragments of arguments, an aspect which is not discussed in this informal presentation.)
+The theory claims that when one of its arguments in support of one of its claims is unconvincing to an individual, it is because of one of the anticipated attacks; and the theory claims to be able to provide counter-arguments to such attacks as they come, that will in turn be either convincing to the individual, or fail to be because of some anticipated attack.
+(The theory is also constrained to have “finite depth”, meaning that it must set an a priori limit to the number of such iterations of attacks and counter-arguments.)
+
+Thanks to these operators, an empirical theory may adjust its argumentation to each individual \commentYM{je ne comprends pas cette phrase, et en particulier le sens qu'il faut donner au terme "adjust"}.
+Instead of having to give a single decisive argument in support of its claims, the theory may react to exactly the counter-arguments that a given individual thinks relevant.
+This task is easier, but still permits to obtain what is desired in this article: there exists a purely empirical property \commentYM{kezako ?}of a theory, called convincingness, that, together with an axiom about the normative adequacy of the observation protocol, implies the correctness of the claims of the theory.
+In more details, first, the claim of the theory, of being able to argue convincingly, can be checked by ensuring that no falsification instances exist, thus, it is a fully empirical claim (in the sense that it requires no axiom).
+Second, granted normative adequacy, if indeed a theory is convincing, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}.
+These claims are proven in \cref{th:convnofals,th:valid}.
+
 \subsection{Definition}
-In this section, a normative theory is supposed given.
-
-An empirical theory is constituted of the following elements.
-
-An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ relates some arguments to some propositions.
-Its role in an empirical theory is to define the propositions that the empirical theory supports (corresponding to $\gpropse$, the range of ${\gleadsto}$) and, for each such proposition, to define the arguments that the theory wants to use \commentYM{"that the theory uses" ?}as initial arguments to argue in favor of this proposition.
-The set of initial arguments is $\gleadstoinv(\allprops) = \set{\ar \in \allargs \suchthat \exists \prop \in \allprops \suchthat \ar \gleadsto \prop}$.
-
-A planned attacks relation ${\gbeats} \subseteq \allargs × \allargs$ is an irreflexive binary relation on the arguments.
-An argument $\ar_1$ is said to be a planned attack against an argument $\ar_0$ iff $\ar_1 \gbeats \ar_0$.
-Given  an argument $\ar_0$, $\gbeatsinv(\ar_0) = \set{\ar_1 \in \allargs \suchthat \ar_1 \gbeats \ar_0}$ denotes the set of planned attacks against $\ar_0$; and $\gbeatsinv(\allargs) = \set{\ar_1 \in \allargs \suchthat \exists \ar_0 \in \allargs \suchthat \ar_1 \gbeats \ar_0}$ denotes the set of arguments that are planned attacks against at least one argument.
-
-An empirical theory defines a set of argument fragments $\alldargs$.
-They are primitive elements that can be added to selected other fragments and arguments to form new arguments.
-They are used to dynamically build defensive arguments against the planned attacks.\commentYM{je n'ai rien compris à ce §.
-Que veut dire "primitive" dans la seconde phrase ?
-Qu'apporte "selected" dans cette même phrase ?
-Ne peut-on pas l'enlever ?
-Que signifie "dynamically build" dans la dernière ?}
+In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
+An empirical theory for a normative theory of \ac{DJ} is defined as a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$, where ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation; ${\gbeats} \subseteq \allargs × \allargs$ is an anticipated attacks relation; $\alldargs$ is a primitive set of argument fragments; ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is a defense relation; and $+$ combines arguments to coalitions of fragments to form new arguments; with the supplementary constraint that the tuple must have a bounded depth.
+These concepts are now defined formally.
+\commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}
+
+An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ defines the set of supported  propositions and, for each supported propositions, the set of initial arguments for these propositions.
+More precisely, let $\gpropse$, the range of ${\gleadsto}$, be called the propositions supported by the descriptive theory.
+Given such a supported proposition $\prop \in \gpropse$, let $\gleadstoinv(\prop) = \set{\ar \in \allargs \suchthat \ar \gleadsto \prop}$ be called the initial arguments in favor of $\prop$.
+
+An anticipated attacks relation ${\gbeats} \subseteq \allargs × \allargs$ is an irreflexive binary relation on the arguments.
+An argument $\ar_1$ is said to be an anticipated attack against an argument $\ar_0$ iff $\ar_1 \gbeats \ar_0$.
+Given  an argument $\ar_0$, $\gbeatsinv(\ar_0) = \set{\ar_1 \in \allargs \suchthat \ar_1 \gbeats \ar_0}$ denotes the set of anticipated attacks against $\ar_0$; and $\gbeatsinv(\allargs) = \set{\ar_1 \in \allargs \suchthat \exists \ar_0 \in \allargs \suchthat \ar_1 \gbeats \ar_0}$ denotes the set of arguments that are anticipated attacks against at least one argument.
 
@@
 pourquoi ?
-à quoi est-ce que cela sert ?} Thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton.
+à quoi est-ce que cela sert ?}
+These constraints guarantee that every anticipated attack has exactly one fragment defending against it, thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton.
 Note that $\dbeats$ need not be a bijection as it is generally not a function. 
-Given $\ar_1 \in \gbeatsinv(\allargs)$, $\dbeatsinv(\ar_1)$ represents the fragment that the theory $\gamma$ plans to use as a defense against the planned attack $\ar_1$.\commentYM{dans toute cette sous-section la lecture est rendue très difficile par ce genre de formulation qui assigne une intentionnalité à la théorie.
+Given $\ar_1 \in \gbeatsinv(\allargs)$, define $\dbeatsinv(\ar_1)$ as the fragment defending against the anticipated attack $\ar_1$.
+\commentYM{dans toute cette sous-section la lecture est rendue très difficile par ce genre de formulation qui assigne une intentionnalité à la théorie.
 Je ne comprends pas le sens métaphorique de ces phrase, donc je ne les comprends pas}
 
-A fragment is said to defend an argument iff it is used as a defense against a planned attack against that argument \commentYM{"it is used" par qui, comment ?
+A fragment is said to defend an argument iff it defends against an anticipated attack against that argument.
+\commentYM{"it is used" par qui, comment ?
 De quoi tu parles là ?
-Des stratégies argumentatives que contient la "théorie empirique" ?}.
-Formally, given any set $S$, define $\powersetz{S}$ as the set of subsets of $S$ without the empty set.
-Define $\df: \allargs → \powersetz{\allargs}$ as $\df = \dbeatsinv \circ \gbeatsinv$.
-Given $\ar \in \allargs$, $\df(\ar)$ denotes the \emph{fragments defending $\ar$}. 
-In other words, given $\ard \in \dargs$ and $\ar_0 \in \allargs$, $\ard \in \df(\ar_0)$ iff $\exists \ar_1 \in \allargs \suchthat \ard \dbeats \ar_1 \gbeats \ar_0$.
-
-A \emph{coalition of fragments defending $\ar$} is any element of $\powersetz{\df(\ar)}$.
+Des stratégies argumentatives que contient la "théorie empirique" ?}
+Formally, 
+given any set $S$, define $\powerset{S}$ as the set of subsets of $S$ and $\powersetz{S}$ as the set of subsets of $S$ without the empty set.
+Define $\df: \allargs → \powerset{\alldargs}$ as follows:
+given $\ar_0 \in \allargs$ and $\ard \in \dargs$, $\ard \in \df(\ar_0)$ iff $\exists \ar_1 \in \allargs \suchthat \ard \dbeats \ar_1 \gbeats \ar_0$.
+In other words, $\df = \dbeatsinv \circ \gbeatsinv$.
+Given $\ar \in \allargs$, $\df(\ar)$ denotes \emph{all fragments defending $\ar$}.
+
+A \emph{coalition of fragments defending $\ar$} is any non-empty subset of $\df(\ar)$.
 Such a coalition can be combined with the argument it defends to form a new argument.
-An empirical theory defines, to that effect, a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \powersetz{\df(\ar)}) → \allargs$.
-Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \df(\ar)$, the notation $\ar + \dargs$ stands for $+(\ar, \dargs)$.
+An empirical theory defines, to that effect, a function $+: \allargs × \powersetz{\alldargs} → \allargs$.
+Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \alldargs$, the notation $\ar + \dargs$ stands for $+(\ar, \dargs)$.
+(The function $+$ need not be defined on so large a domain, because an argument is only ever added to its own defenders, but this definition is adopted for simplicity; \cref{sec:append} refines this requirement.)
 
@@
 
-This mechanism permits to define defenders of defenders of an argument, $\dfp(\dfp(\ar))$, defenders of defenders of defenders of an argument, … An empirical theory must however be a priori restricted in the maximal “depth” of its argumentation strategy, in the following sense.
+This mechanism permits to define defenders of defenders of an argument, $\dfp(\dfp(\ar))$, defenders of defenders of defenders of an argument, … 
+For the results to be presented here to hold, an empirical theory must be a priori restricted in the maximal “depth” of its argumentation strategy, in the following sense. 
 \commentYM{ok soit, ça semble raisonnable, mais tu n'as pas de raison plus forte, j'adopterais une formulation plus modeste et ouverte, du genre "ça semble souhaitable"}
 Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
-An empirical theory must satisfy
+A tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ has a bounded depth iff
 $\exists k \in \N \suchthat (\dfp)^k(\gleadstoinv(\allprops)) = \emptyset$.
-This does not imply that the relations $\gbeats$ or $\dbeats$ should be finite, however.
-
-An empirical theory (for a normative theory) can now be defined as a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ \commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}satisfying the constraints described here above \commentYM{ici encore : lesquelles ?
-définies où ?
-pas possible de suivre si tu donnes pas un peu la main au lecteur}.
-
-An example permits to ensure that the constraint of finite depth does not mandate finiteness of the relations $\gbeats$ or $\dbeats$.
-\begin{proposition}[Possibility of infinite relations]
-	An empirical theory may involve infinite relations $\gbeats$ and $\dbeats$.
-\end{proposition}
-\begin{proof}
-	Consider an agenda $\allprops = \set{\prop}$ containing a single proposition, an infinite set of arguments $\allargs = \set{\ar_k \suchthat k \in \N}$ with $\forall j, k \in \N: \ar_j ≠ \ar_k$, and consider any set of individuals $I$ and observation protocol $\allleadsto$.
-	Define $2\N^* = \set{k \in \N^* \suchthat k / 2 \in \N^*}$ as the set of non-zero even integers.
-	Define ${\gleadsto} = \set{(\ar_0, \prop)}$.
-	Define ${\gbeats} = \set{(\ar_{k - 1}, \ar_0) \suchthat k \in 2\N^*}$ so that all odd numbered arguments are planned attacks against $\ar_0$. 
-	Consider an infinite set of fragments $\alldargs = \set{\ard[k] \suchthat k \in 2\N^*}$ with $\forall j, k \in 2\N^*: \ard[j] ≠ \ard[k]$ so that fragments correspond to non-zero even integers, and define ${\dbeats} = \set{(\ard[k], \ar_{k - 1}) \suchthat k \in 2\N^*}$ so that each (even numbered) defense fragment attacks exactly one (odd numbered) planned attacker of $\ar_0$.
-	Given any coalition of fragments $\dargs$ defending $\ar_0$, consider the set of indices corresponding to the fragments in the coalition, $K_{\dargs} = \set{k \in 2\N^* \suchthat \exists \ard[k] \in \dargs}$;
-	define $j_{\dargs} = \sum_{k \in K_{\dargs}}$ as the sum of these indices;
-	and define $\ar_0 + \dargs = \ar_{j_{\dargs}}$. 
-%	$\ard[k] \in \alldargs$, define $\ar_0 + \set{\ard[k]} = \ar_k$. 
-	Consider an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ for the normative theory $(\allprops, \allargs, I, {\allleadsto})$.
-That this is indeed a legal empirical theory can be confirmed by checking that all constraints are satisfied, in particular, $(\dfp)^2(\gleadstoinv(\allprops)) = \dfp(\dfp(\ar_0)) = \dfp(\set{\ar_k \suchthat k \in 2\N^*}) = \emptyset$ because there is no planned attack against any argument in $\set{\ar_k \suchthat k \in 2\N^*}$.
-This theory involves infinite relations $\gbeats$ and $\dbeats$.
-\end{proof}
-
-\subsection{Empirical tests}
-\commentYM{Dans toute cette sous-section, il y a vraiment ENORMEMENT de notations.
-En conséquence, au moins pour moi, c'est extrêmement difficile à suivre.
-D'où le fait qu'il y a moins de commentaires de ma part à partir de là : je peine à suivre et du coup j'ai plus de mal à prendre du recul}
-Given $\args \subseteq \allargs$, $\hist \in \allhist$, and letting $l$ denote the length of $\hist$,
-the set $\args \cap \hist(\intvl{1, l})$ denotes the arguments that are both in $\args$ and contained in the sequence $\hist$.
-Abusing notation, I write $\args \cap \hist$ to designate $\args \cap \hist(\intvl{1, l})$, therefore using simply $\hist$ in that expression to denote the \emph{range} of $\hist$.
-
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \prop$.
-Such a set $\args$, when not empty, represents an effective set of planned attackers of $\ar$ against $\prop$. 
-The notation uses a striked through $\prop$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues against $\prop$, from the point of view of $i$.
-I write that $\ar$ \emph{$i$-defends} $\prop$ to mean that $\emptyset \nibeats \ar$.
-
-Given $i \in I, \prop \in \gpropse, \ar \in \allargs$, define $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
-It represents the coalitions of fragments defending $\ar$ (when arguing for $\prop$), from the point of view of $i$, against its effective planned attackers.
-The following proposition shows that these coalitions can be added to $\ar$, and will be useful for other results.
-\begin{proposition}
-	\label{th:indf}
-	$\forall i \in I, \prop \in \gpropse, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
-\end{proposition}
-\begin{proof}
-	I will prove that $\forall \ar \in \allargs: \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.
-Note that by definition of $\df(\ar)$, $\dargs \in \powersetz{\df(\ar)}$ iff $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
-	Thus, we have to prove that
-	$\forall \dargs \subseteq \allargs$:
-	\begin{equation}
-		\exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \suchthat \dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
-	\end{equation}
-
-	First (from left to right), given any $\args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \dargs = \dbeatsinv(\args)$, let us show that $\dargs ≠ \emptyset$ and that $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
-	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, from which follows that $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$.
-Also, because $\args \subseteq \gbeatsinv(\ar)$, $\dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
-
-	Second (from right to left), let us show that $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)) ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
-	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ar' \in \dbeatsinv(\args)$, $\ar' \dbeats \ar_1$ for some $\ar_1 \in \args$, thus $\ar_1 \gbeats \ar_0$, thus, $\ar_1 \in {\dbeats}(\dargs)$, thus $\ard \dbeats \ar_1$ for some $\ard \in \dargs$, and by injectivity  of $\dbeats$, $\ar' = \ard$, whence $\ar' \in \dargs$.
-	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
-\end{proof}
-
-Given $\ar \in \allargs$, define $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\prop$.
-Given $i \in I, \prop \in \gpropse$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\prop)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\prop))$.
-
-\begin{definition}[Convincingness]
-	An empirical theory is \emph{convincing} iff $\forall i \in I, \prop \in \gpropse, \ar \in \gargs: \ar$ $i$-defends $\prop$.
-\end{definition}
-
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \prop, \hist, \ar) \in I × \gpropse × \allhist × \gargs$ such that $\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \prop$.
-I also write that $(i, \prop, \hist, \ar)$ falsifies $\gamma$ to mean that it is a falsification instance of $\gamma$.
-
-\begin{theorem}
-	\label{th:convnofals}
-	An empirical theory is convincing iff it has no falsification instances.
-\end{theorem}
-\begin{proof}
-	For all $i \in I, \prop \in \gpropse, \ar \in \gargs$: $\ar$ does not $i$-defend $\prop$ iff $\exists \hist \in \allhist \suchthat \left[\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \prop\right]$ iff $\exists \hist \in \allhist$ such that $(i, \prop, \hist, \ar)$ falsifies $\gamma$.
-Therefore, $\gamma$ is not convincing iff $\exists (i, \prop, \ar) \suchthat \ar$ does not $i$-defend $\prop$ iff $\exists \hist \suchthat (i, \prop, \hist, \ar)$ falsifies $\gamma$ iff $\gamma$ has a falsification instance.
-\end{proof}
+
+The bounded depth constraint does not imply finiteness of the relations $\gbeats$ or $\dbeats$, as \cref{th:infinite} shows.
+
+\subsection{Falsification}
+\label{sec:fals}
+Given $\args \subseteq \allargs$ and $\hist \in \allhist$,
+the set $\args \cap \range(\hist)$ denotes the arguments that are both in $\args$ and contained in the sequence $\hist$.
+
+Define a falsification sequence for $i, \ar_0, \phi$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $\hist^1, \hist^3, …, \hist^{k + 1}$, $k \in 2\N$, such that it presents successive challenges, which means the following.
+Given $l \in 2\N \suchthat l ≤ k$, $\ar_l \in \allargs$ and $\hist^{l + 1} \in \allhist$, 
+define $\args_{l + 1} = \gbeatsinv(\ar_l) \cap \range(\hist^{l + 1})$; 
+define $\dargs[l + 2] = \dbeatsinv(\args_{l + 1})$ as those fragments defending against the anticipated attackers $\args_{l + 1}$; 
+and, if $\args_{l + 1} ≠ \emptyset$ (equivalently, if $\dargs[l + 2] ≠ \emptyset$), define $\ar_{l + 2} = \ar_l + \dargs[l + 2]$. 
+The sequence presents successive challenges iff, $\forall l \in 2\N \suchthat l ≤ k$, we have that $\ar_l \in \histend[l + 1]$, $\hist^{l + 1} \nileadstost \phi$, and $[\args_{l + 1} = \emptyset ⇔ l = k]$.
 
@@
 
-\begin{lemma}
-	\label{th:produce}
-	Given $\prop \in \gpropse$, $\ar_0 \in \gargs$ that $i$-defends $\prop$, and $\hist \nileadstost \prop$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$.
-Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
-\end{lemma}
-\begin{proof}
-	By definition of $\ibeats$, $\args \ibeats \ar_0$.
-	Also, because $\ar_0$ $i$-defends $\prop$, $\args ≠ \emptyset$. 
-	Therefore, $\dargs \in \di(\ar_0)$.
-	It follows that $\dargs \in \df(\ar_0)$, by \cref{th:indf}, and that $\ar_2 \in \dfp(\ar_0)$, by definition of $\dfp$. It also follows that $\ar_2 \in \dip(\ar_0)$, hence, that $\ar_2 \in \gargs$.
-\end{proof}
-
 \begin{theorem}
-	\label{th:valid}
-	A normatively adequate and convincing empirical theory is valid.
+	\label{th:svalid}
+	A normatively adequate empirical theory that has no falsification sequence is valid.
 \end{theorem}
-\begin{proof}
-	Given any $i \in I$ and $\prop \in \gpropse$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \prop$; the conclusion then follows thanks to normative adequacy.
-
-	Lemma: $[\ar_0 \in \gargs \land \ar_0 \nileadstost \prop] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$.
-That is because $\ar_0 \in \gargs$ implies that $\ar_0$ $i$-defends $\prop$, by convincingness, and,
-	by definition, $\ar_0 \nileadstost \prop$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \prop$; \cref{th:produce} thus applies.
-
-	To prove the theorem, build a finite sequence of arguments in $\gargs$, starting with any $\ar_0 \in \gleadstoinv(\prop)$.
-Observe that $\ar_0 \in \gargs$.
-Given $k \in 2\N$, if $\ar_k \nileadstost \prop$, define $\ar_{k + 2}$ using the above lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$.
-Continue applying the lemma and producing further arguments as long as $\ar_k \nileadstost \prop$.
-	By definition of an empirical theory, $\exists k \in \N \suchthat (\dfp)^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \prop$.
-\end{proof}
 
@@
 
+In order to allow for repeated observations with a given individual without modifying his endowment \commentYM{en quel sens utilises-tu ce terme ici ?}, this example protocol should either be content with purely hypothetical choices, or can make these choices binding by letting the individual know that one of his choices will be picked randomly at the end of the experiment and honored.\commentYM{pas compris le second membre de l'alternative}
+
 \bibliography{simple}
+
+\appendix
+\section{Finiteness}
+This example permits to ensure that the constraint of bounded depth does not mandate finiteness of the relations $\gbeats$ or $\dbeats$.
+\begin{proposition}[Possibility of infinite relations]
+	\label{th:infinite}
+	An empirical theory may involve infinite relations $\gbeats$ and $\dbeats$.
+\end{proposition}
+\begin{proof}
+	Consider an agenda $\allprops = \set{\prop}$ containing a single proposition, an infinite set of arguments $\allargs = \set{\ar_k \suchthat k \in \N}$ with $\forall j, k \in \N: \ar_j ≠ \ar_k$, and consider any set of individuals $I$ and observation protocol $\allleadsto$.
+	Define $2\N^* = \set{k \in \N^* \suchthat k / 2 \in \N^*}$ as the set of non-zero even integers.
+	Define ${\gleadsto} = \set{(\ar_0, \prop)}$.
+	Define ${\gbeats} = \set{(\ar_{k - 1}, \ar_0) \suchthat k \in 2\N^*}$ so that all odd numbered arguments are anticipated attacks against $\ar_0$. 
+	Consider an infinite set of fragments $\alldargs = \set{\ard[k] \suchthat k \in 2\N^*}$ with $\forall j, k \in 2\N^*: \ard[j] ≠ \ard[k]$ so that fragments correspond to non-zero even integers, and define ${\dbeats} = \set{(\ard[k], \ar_{k - 1}) \suchthat k \in 2\N^*}$ so that each (even numbered) defense fragment attacks exactly one (odd numbered) anticipated attacker of $\ar_0$.
+	Given any coalition of fragments $\dargs$ defending $\ar_0$, consider the set of indices corresponding to the fragments in the coalition, $K_{\dargs} = \set{k \in 2\N^* \suchthat \exists \ard[k] \in \dargs}$;
+	define $j_{\dargs} = \sum_{k \in K_{\dargs}}$ as the sum of these indices;
+	and define $\ar_0 + \dargs = \ar_{j_{\dargs}}$. 
+%	$\ard[k] \in \alldargs$, define $\ar_0 + \set{\ard[k]} = \ar_k$. 
+	Consider an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ for the normative theory $(\allprops, \allargs, I, {\allleadsto})$.
+That this is indeed a legal empirical theory can be confirmed by checking that all constraints are satisfied, in particular, $(\dfp)^2(\gleadstoinv(\allprops)) = \dfp(\dfp(\ar_0)) = \dfp(\set{\ar_k \suchthat k \in 2\N^*}) = \emptyset$ because there is no anticipated attack against any argument in $\set{\ar_k \suchthat k \in 2\N^*}$.
+This theory involves infinite relations $\gbeats$ and $\dbeats$.
+\end{proof}
+
+\section{Empirical validity}
+\label{sec:append}
+A \emph{coalition of fragments defending $\ar$} is any non-empty subset of $\df(\ar)$ (equivalently, any element of $\powersetz{\df(\ar)}$).
+Such a coalition can be combined with the argument it defends to form a new argument.
+An empirical theory defines, to that effect, a function $+: \bigcup_{\ar \in \allargs}(\set{\ar} × \powersetz{\df(\ar)}) → \allargs$.
+This function permits to add any $\ar \in \allargs$ to any subset $\emptyset ≠ \dargs \subseteq \df(\ar)$
+
+\commentYM{Dans toute cette sous-section, il y a vraiment ENORMEMENT de notations.
+En conséquence, au moins pour moi, c'est extrêmement difficile à suivre.
+D'où le fait qu'il y a moins de commentaires de ma part à partir de là : je peine à suivre et du coup j'ai plus de mal à prendre du recul}
+
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \range(\hist) \land \ar \in \histend \land \hist \nileadstost \prop$.
+Such a set $\args$, when not empty, represents an effective set of anticipated attackers of $\ar$ against $\prop$. 
+The notation uses a striked through $\prop$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues against $\prop$, from the point of view of $i$.
+I write that $\ar$ \emph{$i$-defends} $\prop$ to mean that $\emptyset \nibeats \ar$.
+
+Given $i \in I, \prop \in \gpropse, \ar \in \allargs$, define $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
+It represents the coalitions of fragments defending $\ar$ (when arguing for $\prop$), from the point of view of $i$, against its effective anticipated attackers.
+\Cref{th:indf} shows that these coalitions can be added to $\ar$, and is useful for the later results.
+\begin{proposition}
+	\label{th:indf}
+	$\forall i \in I, \prop \in \gpropse, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
+\end{proposition}
+\begin{proof}
+	I will prove that $\forall \ar \in \allargs: \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.
+Note that by definition of $\df(\ar)$, $\dargs \in \powersetz{\df(\ar)}$ iff $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
+	Thus, we have to prove that
+	$\forall \dargs \subseteq \allargs$:
+	\begin{equation}
+		\exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \suchthat \dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
+	\end{equation}
+
+	First (from left to right), given any $\args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \dargs = \dbeatsinv(\args)$, let us show that $\dargs ≠ \emptyset$ and that $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
+	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, from which follows that $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$.
+Also, because $\args \subseteq \gbeatsinv(\ar)$, $\dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
+
+	Second (from right to left), let us show that $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)) ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
+	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ar' \in \dbeatsinv(\args)$, $\ar' \dbeats \ar_1$ for some $\ar_1 \in \args$, thus $\ar_1 \gbeats \ar_0$, thus, $\ar_1 \in {\dbeats}(\dargs)$, thus $\ard \dbeats \ar_1$ for some $\ard \in \dargs$, and by injectivity  of $\dbeats$, $\ar' = \ard$, whence $\ar' \in \dargs$.
+	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
+\end{proof}
+
+Given $\ar \in \allargs$, define $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\prop$.
+Given $i \in I, \prop \in \gpropse$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\prop)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\prop))$.
+
+\begin{definition}[Convincingness]
+	An empirical theory is \emph{convincing} iff $\forall i \in I, \prop \in \gpropse, \ar \in \gargs: \ar$ $i$-defends $\prop$.
+\end{definition}
+
+A \emph{falsification instance} of an empirical theory is a tuple $(i, \prop, \hist, \ar) \in I × \gpropse × \allhist × \gargs$ such that $\gbeatsinv(\ar) \cap \range(\hist) = \emptyset \land \ar \in \histend \land \hist \nileadstost \prop$.
+I also write that $(i, \prop, \hist, \ar)$ falsifies $\gamma$ to mean that it is a falsification instance of $\gamma$.
+
+\begin{lemma}
+	\label{th:convnofals}
+	An empirical theory is convincing iff it has no falsification instances.
+\end{lemma}
+\begin{proof}
+	For all $i \in I, \prop \in \gpropse, \ar \in \gargs$: $\ar$ does not $i$-defend $\prop$ iff $\exists \hist \in \allhist \suchthat \left[\gbeatsinv(\ar) \cap \range(\hist) = \emptyset \land \ar \in \histend \land \hist \nileadstost \prop\right]$ iff $\exists \hist \in \allhist$ such that $(i, \prop, \hist, \ar)$ falsifies $\gamma$.
+Therefore, $\gamma$ is not convincing iff $\exists (i, \prop, \ar) \suchthat \ar$ does not $i$-defend $\prop$ iff $\exists \hist \suchthat (i, \prop, \hist, \ar)$ falsifies $\gamma$ iff $\gamma$ has a falsification instance.
+\end{proof}
+
+\begin{lemma}
+	\label{th:dpiconstr}
+	$\forall \ar_0, \ar_2 \in \allargs: \ar_2 \in \dip(\ar_0) ⇔ \exists \hist \in \allhist, \args = \gbeatsinv(\ar_0) \cap \range(\hist), \dargs = \dbeatsinv(\args) \suchthat [\hist \nileadstost \phi
+	\land \ar_0 \in \histend
+	\land \emptyset ≠ \args \ibeats \ar_0
+	\land \ar_2 = \ar_0 + \dargs]$.
+\end{lemma}
+\begin{proof}
+	$\ar_2 \in \dip(\ar_0) ⇔ \exists \dargs \in \di(\ar_0) \suchthat \ar_2 = \ar_0 + \dargs$.
+	Also, $\exists \dargs \in \di(\ar_0) ⇔ \exists \args \subseteq \gbeatsinv(\ar_0) \suchthat \dargs = \dbeatsinv(\args) \land \emptyset ≠ \args \ibeats \ar_0$.
+Equivalently, $\exists \args \subseteq \gbeatsinv(\ar_0) \suchthat \dargs = \dbeatsinv(\args) \land \emptyset ≠ \args  \land \exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \range(\hist) \land \ar_0 \in \histend \land \hist \nileadstost \prop$.
+\end{proof}
+
+\begin{lemma}
+	\label{th:instseq}
+	An empirical theory has a falsification instance iff it has a falsification sequence.
+\end{lemma}
+\begin{proof}
+	First, from right to left, consider a falsification sequence $(\hist^{l + 1})_{l \in 2\N, l ≤ k}$ for some $k \in 2\N$, define, as in \cref{sec:fals}, $\args_{l + 1} = \gbeatsinv(\ar_l) \cap \range(\hist^{l + 1})$, $\dargs[l + 2] = \dbeatsinv(\args_{l + 1})$ and (for $l ≤ k - 2$) $\ar_{l + 2} = \ar_l + \dargs[l + 2]$, and let us show that $(i, \phi, \hist^{k + 1}, \ar_{k})$ is a falsification instance.
+This amounts to show that $\ar_k \in \gargs$, which can be done by observing that $\ar_0 \in \gargs$, and showing that, $\forall l \in 2\N, l ≤ k - 2$, $\ar_l \in \gargs ⇒ \ar_{l + 2} \in \gargs$.
+	Indeed, \cref{th:dpiconstr} applies with $\ar_l$ for $\ar_0$ and $\ar_{l + 2}$ for $\ar_2$.
+As the second member of the equivalence is true by definition of a falsification sequence, $\ar_{l + 2} \in (\dip)(\ar_l)$, and because $\ar_l \in \gargs$, $\ar_{l + 2} \in \gargs$.
+
+	Second, from left to right, consider a falsification instance $(i, \phi, \hist^{k + 1}, \ar_{k})$.
+As $\ar_k \in \gargs$, $\ar_k \in (\dip)^k({\gleadstoinv}(\prop))$ (equalizing the indices $k$ wlog).
+Given $\ar_{l + 2} \in (\dip)^j({\gleadstoinv}(\prop))$, with $j > 0$, thus $\ar_{l + 2} \in \dip(\ar_l)$ for some $\ar_l \in (\dip)^{j - 1}({\gleadstoinv}(\prop))$, apply \cref{th:dpiconstr}, obtain $\hist_{l + 1}$.
+Iterate while $j > 0$.
+When $j = 0$, the $\hist$ found corresponds to an initial argument.
+
+	TODO improve this proof.
+\end{proof}
+
+\begin{lemma}
+	\label{th:produce}
+	Given $\prop \in \gpropse$, $\ar_0 \in \gargs$ that $i$-defends $\prop$, and $\hist \nileadstost \prop$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \range(\hist)$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$.
+Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
+\end{lemma}
+\begin{proof}
+	By definition of $\ibeats$, $\args \ibeats \ar_0$.
+	Also, because $\ar_0$ $i$-defends $\prop$, $\args ≠ \emptyset$. 
+	Therefore, $\dargs \in \di(\ar_0)$.
+	It follows that $\dargs \in \df(\ar_0)$, by \cref{th:indf}, and that $\ar_2 \in \dfp(\ar_0)$, by definition of $\dfp$. It also follows that $\ar_2 \in \dip(\ar_0)$, hence, that $\ar_2 \in \gargs$.
+\end{proof}
+
+\Cref{th:svalid} claims that a normatively adequate empirical theory that has no falsification sequence is valid. TODO prove it.
+
+\begin{theorem}
+	\label{th:valid}
+	An empirical theory that is normatively adequate and convincing is valid.
+\end{theorem}
+\begin{proof}[of \cref{th:valid}]
+	Given any $i \in I$ and $\prop \in \gpropse$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \prop$; the conclusion then follows thanks to normative adequacy.
+
+	Lemma: $[\ar_0 \in \gargs \land \ar_0 \nileadstost \prop] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$.
+That is because $\ar_0 \in \gargs$ implies that $\ar_0$ $i$-defends $\prop$, by convincingness, and,
+	by definition, $\ar_0 \nileadstost \prop$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \prop$; \cref{th:produce} thus applies.
+
+	To prove the theorem, build a finite sequence of arguments in $\gargs$, starting with any $\ar_0 \in \gleadstoinv(\prop)$.
+Observe that $\ar_0 \in \gargs$.
+Given $k \in 2\N$, if $\ar_k \nileadstost \prop$, define $\ar_{k + 2}$ using the above lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$.
+Continue applying the lemma and producing further arguments as long as $\ar_k \nileadstost \prop$.
+	By definition of an empirical theory, $\exists k \in \N \suchthat (\dfp)^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \prop$.
+\end{proof}
+
 \end{document}
@@
 
-An additive theory need not have freedom for defining planned attacks on additive terms: this should be a consequence on the planned attacks on defenses and on initial arguments only.
+An additive theory need not have freedom for defining anticipated attacks on additive terms: this should be a consequence on the anticipated attacks on defenses and on initial arguments only.
 This makes the theory easier to define, as only attacks on partial arguments are to be defined.
@@
 Define $g(\ar_0) \subseteq \allargs × \allargs$ as $g(\ar_0) = \set{(\ar_2, \ar_1) \suchthat \ar_2 \in f(\ar_1, \ar_0)} = \bigcup_{\ar_1 \in \allargs} (f(\ar_1, \ar_0) × \set{\ar_1})$.
-The set $g(\ar_0)(\allargs)$ contains the planned attacks on $\ar_0$; the set $g(\ar_0)(\ar_2)$ contains the planned attacks on $\ar_0$ for which $\ar_2$ is a planned response; and the set $g(\ar_0)^{-1}(\ar_1) = f(\ar_1, \ar_0)$ contains the planned protections of $\ar_0$ against $\ar_1$.
+The set $g(\ar_0)(\allargs)$ contains the anticipated attacks on $\ar_0$; the set $g(\ar_0)(\ar_2)$ contains the anticipated attacks on $\ar_0$ for which $\ar_2$ is a planned response; and the set $g(\ar_0)^{-1}(\ar_1) = f(\ar_1, \ar_0)$ contains the planned protections of $\ar_0$ against $\ar_1$.
 
@@
 
-$\ar_0$ $i$-defends $\prop$ when ignoring $S_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \hist = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \prop$.
+$\ar_0$ $i$-defends $\prop$ when ignoring $S_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \range(\hist) = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \prop$.
 $\ar_0$ $i$-defends $\prop$ under protection of $S_2$ iff $\ar_0$ $i$-defends $\prop$ when ignoring $g(\ar_0)(\args_2)$.

### 2020-11-01 simple.tex
Better Descr. th.

@@
 
-This article defines decision theories, called theories of \ac{DJ}, that are both normative and descriptive: they claim to be able to yield valid prescriptions, and to allow confrontation to empirical data.
+This article defines decision theories, called theories of \ac{DJ}, that are both normative and descriptive: they claim to be able to yield valid prescriptions, and these prescriptions are claimed to predict reflective behavior.
+Reflective behavior as defined in this article is observable, by means of observing the reaction of individuals to arguments.
+This allows to confront theories of \ac{DJ} to empirical data.
 
@@
 
+Here is an example opposing two simplistic theories of \ac{DJ}, meant to give a flavor of the sort of theories this article aims at defining.
+
+\begin{example}[Two theories about two alternatives]
+	Consider a set $\alts = \set{\alt_1, \alt_2}$ of two alternatives whose evaluations on two criteria (say, price and speed, for concreteness), are $(g_1(\alt_1), g_2(\alt_1))$ and $(g_1(\alt_2), g_2(\alt_2))$, respectively, where $g_i: \alts → \R$ are functions giving the performance of alternatives on the criterion $i$.
+
+	Two theories of \ac{DJ} are opposed on their prediction of the reflexive choice of a given set of individuals $I$ having to choose one alternative among $\alts$.
+	The \emph{satisfycing} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever alternative is satisfying (and be indifferent if they are both satisfying or if none of them is).
+An alternative $\alt$ is satisfying iff $g_1(\alt) < t_1 \land g_2(\alt) > t_2$, where $t_1$ and $t_2$ are two real numbers chosen by the theorist.
+	The \emph{additive} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever alternative $\alt$ maximises $v(\alt) = v_1(g_1(\alt)) + v_2(g_2(\alt))$, where $v_i: \R → \R$ are functions  chosen by the theorist.
+	How the parameters of these theories, $t_i$ and $v_i$, are determined is irrelevant to the questions tackled in this article, because it aims at defining and studying theories of \ac{DJ} in general, not at proposing a way of building a specific theory of \ac{DJ}.
+%For this example, one can assume that these parameters are determined on the basis of observation of the behavior of some population in some similar circumstances.
+
+	Assume that the theories disagree, thus, that $\alt_1$ is satisfying and $\alt_2$ is not (say, it fails on the speed criterion), but $v(\alt_2) > v(\alt_1)$.
+To determine which theory is right, it is insufficient to simply observe what an individual $i \in I$ effectively chooses.
+This would merely reflect her unreflective behavior.
+The approach adopted in this article to capture \acp{DJ} is to declare that the winning theory (if any) is the one that exhibit arguments able to systematically convince individuals that their proposed choice is to be adopted.
+	The satisfycing theory could argue as follows: “$\alt_1$ is better than $\alt_2$, because it has a satisfactory price (lower than $t_1$, an acceptable price) and a satisfactory speed (higher than $t_2$, thus an acceptable performance); whereas $\alt_2$ is not satisfactory on the speed criterion”.
+	The additive theory could use the following argument: “$\alt_2$ is better than $\alt_1$, because $\alt_2$ is cheaper than $\alt_1$, and this more than compensates for its weaker performance in terms of speed”.
+
+	Determining which theory is right requires to present both arguments to $i$, then let her choose one alternative in $\alts$.
+\end{example}
+%The proposed approach starts with this intuition that the reaction of individuals to arguments should matter, and presents a general solution to the problem of capturing reflective judgments or choices.
+Contrary to the simplistic situation of \cref{ex:two}, this solution must allow to confront more than just two arguments or two theories.
+It should define precisely what is required for a judgment to be called deliberated, and determine formally which hypothesis are required for the prescriptions of a theory of \ac{DJ} to be valid.
+
+This article is structured as follows.
 \Cref{sec:approaches} defines more precisely what is meant here with normative and descriptive theories.
@@
 This gap can thus be overcome by considering reflective descriptive theories, instead of shallow descriptive theories. This is the path this article adopts.
-It defines theories that are both normative and descriptive: they attempt to deliver valid prescriptions, and these prescriptions are claimed to predict reflective behavior.
 
@@
 \label{sec:descriptive}
-\subsection{Empirical theories, informally}
-\commentOCf{TODO : intégrer les explications dans la partie formelle et les reformuler.}
-A normative theory defines how to determine that an argument is not decisive for a given proposition: suffices to find a sequence of arguments that does not lead to that proposition \commentYM{pas compris : tu veux dire "une séquence qui se termine par cet argument et qui n'amène pas à cette proposition ?}.
+\subsection{Informal presentation}
+\commentOCf{Je ne me suis pas encore décidé : descriptive theory or empirical theory ? Pour le moment, j’utilise les deux expressions de façon interchangeable.}
+A normative theory defines when a given argument is decisive for a given proposition and a given individual: whenever every sequence of arguments having that argument towards the end of the sequence lead the individual to adhere to the proposition.
 This, in turn, under condition of accepting its normative validity \commentYM{mais c'est quoi cette "normative validiy" ?
-de quelles conditions parles-tu ?}, permits to know something about the \ac{DJ} of an individual.
+de quelles conditions parles-tu ?}, permits in principle to know something about the \ac{DJ} of an individual.
 But this gives no concrete means to know someone’s \ac{DJ}.
-The set of potentially relevant arguments will generally be very large, and can’t be explored thoroughfully \commentYM{certain que ce terme existe ?}.
-More importantly, only some sequences of arguments can be tested for a given individual.
-That is because, first, the individual’s patience is limited, and second, once a sequence has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective.
-Postulating that the individual forgets after some time and separating the tests in time might mitigate this problem, but not necessarily cancel it.
-\commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question.
-Je doute cependant qu'un lecteur innocent comprenne un traitre mot}
-
-%As a result, it should be possible to determine someone’s \ac{DJ} using only a small increasing set of sequences of arguments.
-A set of sequences of arguments is increasing iff the sequences can be ordered completely such that each sequence following another one “continues” the other one: its first arguments are those constituting the sequence that it follows.
-
-These two problems are tackled by introducing empirical theories of \ac{DJ}.
+The set of finite sequence of arguments is infinite.
+The definition of decisiveness could admittedly be modified to account for an a priori bound on the maximal length of sequences, but this would not solve the practical problem that this set would be too large to be explored thoroughly
+\commentYM{certain que ce terme existe ?}
+\commentOCf{Non, thoroughfully n’existe pas, en effet}. 
+Furthermore, only some sequences of arguments can be tested for a given individual: the individual’s patience is limited.
+A supplementary problem might happen in some situations.
+Once a sequence has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective.
+Let me call this possibility the hypothesis of memory.
+The converse hypothesis amounts to postulating that the individual forgets after some time and use an observation protocol that separates the tests in time sufficiently.
+\commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question. Je doute cependant qu'un lecteur innocent comprenne un traitre mot}
+
+Achieving knowledge of someone’s \ac{DJ} in practice is tackled by introducing empirical theories of \ac{DJ}.
 An empirical theory for a given normative theory defines a subset of propositions of the agenda, that it claims are contained in the \acp{DJ} of individuals concerned by the normative theory.
 They are called the proposition that the theory supports.
-\commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi} The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments.
+\commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi}
+The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments.
 This is accomplished by three binary relations, part of the definition of empiricial theories: one represents its initial arguments, one plans the possible attacks, and one defines its counter-arguments.
-(An empirical theory also defines a concatenation operation able to dynamically build arguments from fragments of arguments, an aspect which is not discussed in this informal presentation.)
+An empirical theory also defines a concatenation operation able to dynamically build arguments from fragments of arguments.
 The theory claims that when one of its arguments in support of one of its claims is unconvincing to an individual, it is because of one of the anticipated attacks; and the theory claims to be able to provide counter-arguments to such attacks as they come, that will in turn be either convincing to the individual, or fail to be because of some anticipated attack.
-(The theory is also constrained to have “finite depth”, meaning that it must set an a priori limit to the number of such iterations of attacks and counter-arguments.)
-
-Thanks to these operators, an empirical theory may adjust its argumentation to each individual \commentYM{je ne comprends pas cette phrase, et en particulier le sens qu'il faut donner au terme "adjust"}.
+The theory is also constrained to have “finite depth”, meaning that it must set an a priori limit to the number of such iterations of attacks and counter-arguments.
+
+Thanks to these operators, an empirical theory may argue in a way that depends on the counter-arguments each individual finds appealing
+\commentYM{je ne comprends pas cette phrase, et en particulier le sens qu'il faut donner au terme "adjust"}.
 Instead of having to give a single decisive argument in support of its claims, the theory may react to exactly the counter-arguments that a given individual thinks relevant.
-This task is easier, but still permits to obtain what is desired in this article: there exists a purely empirical property \commentYM{kezako ?}of a theory, called convincingness, that, together with an axiom about the normative adequacy of the observation protocol, implies the correctness of the claims of the theory.
-In more details, first, the claim of the theory, of being able to argue convincingly, can be checked by ensuring that no falsification instances exist, thus, it is a fully empirical claim (in the sense that it requires no axiom).
+
+Such theories satisfy the two properties that are mandatory to achieve what has been announced, namely, to obtain theories of \ac{DJ} whose power rest on a weak normative axiom and on empirically falsifiable claims.
+First, the main claim of the theory, of being able to argue convincingly, holds if and only if no falsification sequence exist.
 Second, granted normative adequacy, if indeed a theory is convincing, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}.
-These claims are proven in \cref{th:convnofals,th:valid}.
+These two claims are laid out formally in \cref{th:svalid}.
+
+A second goal of this section is to prove that when two theories disagree about incompatible propositions, one of the theories at least must fail some given series of empirical tests, which the proof describes.
+Importantly, these tests can be performed on a single individual and are robust against the hypothesis of memory.
 
@@
 
-\subsection{Falsification}
-\label{sec:fals}
+\subsection{Validity}
+\label{sec:validity}
 Given $\args \subseteq \allargs$ and $\hist \in \allhist$,
@@
 
-Define a falsification sequence for $i, \ar_0, \phi$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $\hist^1, \hist^3, …, \hist^{k + 1}$, $k \in 2\N$, such that it presents successive challenges, which means the following.
-Given $l \in 2\N \suchthat l ≤ k$, $\ar_l \in \allargs$ and $\hist^{l + 1} \in \allhist$, 
-define $\args_{l + 1} = \gbeatsinv(\ar_l) \cap \range(\hist^{l + 1})$; 
-define $\dargs[l + 2] = \dbeatsinv(\args_{l + 1})$ as those fragments defending against the anticipated attackers $\args_{l + 1}$; 
-and, if $\args_{l + 1} ≠ \emptyset$ (equivalently, if $\dargs[l + 2] ≠ \emptyset$), define $\ar_{l + 2} = \ar_l + \dargs[l + 2]$. 
-The sequence presents successive challenges iff, $\forall l \in 2\N \suchthat l ≤ k$, we have that $\ar_l \in \histend[l + 1]$, $\hist^{l + 1} \nileadstost \phi$, and $[\args_{l + 1} = \emptyset ⇔ l = k]$.
+Define a falsification sequence for $i, \ar_0, \phi$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $\hist^1, \hist^3, …, \hist^{N + 1}$, for some $N \in 2\N$, such that it presents successive challenges, which means the following.
+Given $k \in 2\N \suchthat k ≤ N$, $\ar_k \in \allargs$ and $\hist^{k + 1} \in \allhist$, 
+define $\args_{k + 1} = \gbeatsinv(\ar_k) \cap \range(\hist^{k + 1})$; 
+define $\dargs[k + 2] = \dbeatsinv(\args_{k + 1})$ as those fragments defending against the anticipated attackers $\args_{k + 1}$; 
+and, if $\args_{k + 1} ≠ \emptyset$ (equivalently, if $\dargs[k + 2] ≠ \emptyset$), define $\ar_{k + 2} = \ar_k + \dargs[k + 2]$. 
+The sequence presents successive challenges iff, $\forall k \in 2\N \suchthat k ≤ N$, we have that $\ar_k \in \histend[k + 1]$, $\hist^{k + 1} \nileadstost \phi$, and $[\args_{k + 1} = \emptyset ⇔ k = N]$.
 
@@
 
-Given $\prop \in \allprops$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $\prop$ iff $\hist \nileadstost \prop$ and $\ar_\gamma \in \histend$.
-Given $\prop \in \allprops, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \prop)$ or $(\hist, \ar_\delta)$ challenges $(\delta, \propbar)$.
-
-\commentYM{il faudrait tenir la main du lecture : dire pourquoi tu définis ça.
-Ca se comprends, je sais, mais ça demande au lecteur un gros effort qui n'est pas récompensé par une impression de comprendre où ça va}
-
-\begin{lemma}
-	\label{th:endchal}
-	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$, $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge.
-\end{lemma}
-\begin{proof}
-	Either $\hist \nileadstost \prop$, and $(\hist, \ar_\gamma)$ challenges $\prop$, or $\hist \ileadstost \prop$, hence, by \cref{th:protcoh}, $\hist \nileadstost \propbar$, and $(\hist, \ar_\delta)$ challenges $\propbar$.
-\end{proof}
-
-\begin{lemma}
-	\label{th:nextchal}
-	Given $(\hist, \ar_\gamma)$ challenging $\prop$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\prop))$, and $\ar_\delta \in \gargsdelta$: either $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $\prop/\propbar$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\prop))$.
-\end{lemma}
-\begin{proof}
-	If $\ar_\gamma$ does not $i$-defend $\prop$, then $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, which ends the proof. 
-	Thus, assume that $\ar_\gamma$ $i$-defends $\prop$.
-
-	\Cref{th:produce} applies and yields $\ar'_\gamma = \ar_\gamma + \dbeatsinv(\gbeatsinv(\ar_\gamma)) \in \gargs \cap \dfp(\ar_\gamma)$, thus $\ar'_\gamma \in (\dfp)^{(k + 1)}(\gleadstoinv(\prop))$. 
-	Now, define $\histpp = (\hist, \ar'_\gamma)$ and test whether $\histpp \nileadstost \prop$.
-
-	If $\histpp \nileadstost \prop$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\gamma, \ar_\delta)$ challenges $\prop$, which concludes the proof. 
-	Thus, assume that $\histpp \ileadstost \prop$.
-
-	Let us now define $\histp$ such that $\set{\ar'_\gamma, \ar_\delta} \subseteq \histpend$, so that \cref{th:endchal} applies on $(\histp, \ar'_\gamma, \ar_\delta)$, which will conclude the proof.
-
-	If $\ar_\delta \in \histppend$, this is done by defining $\histp = \histpp$. Otherwise, define $\histp = (\histpp, \ar_\delta)$ and test whether $\histp \nileadstost \prop$. 
-\end{proof}
-
-%Given a normative theory and two empirical theories for that normative theory and $i \in I$, 
-%a \emph{test procedure with $i$} is a finite sequence 
-%\commentOC{Need the test procedure to be a tree.
-Atom: $(k, \prop)$ meaning whether ${\hist}^k \ileadstost \prop$.
-Branch label: atoms linked using or and and operators.
-From a node $n = (\hist, \ar, \prop)$, let branches depart, such that their labels do not overlap.
-From a node, if no branch label is true, the node must falsify a theory.
-In the case of the procedure below, it is not a list because we may query several times the same theory or switch to the other one, depending on the last answer.
-But if simplifying the theory (single-try), we may then simplify the definition of a test procedure.}
-
 A path $\histp$ starts with a path $\hist$ of length $l$ iff $\histp$ has length at least $l$ and $\forall k \in \intvl{1, l}: \histp_k = \hist_k$.
-An increasing sequence of paths is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N^*$, of paths, 
+An increasing sequence of paths is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N$, of paths, 
 such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$.
 
-Given two incompatible empirical theories for a given normative theory, $\alpha = (\gleadsto[\alpha], \gbeats[\alpha], \alldargs_\alpha, \dbeats[\alpha], +_\alpha)$ and $\beta = (\gleadsto[\beta], \gbeats[\beta], \alldargs_\beta, \dbeats[\beta], +_\beta)$ and given any $i \in I$, the following procedure falsifies one of these theories, queries only $i$, and queries $i$ only about some increasing sequence of paths.
-\begin{procedure}
-	Pick any $\prop \in \allprops$ about which $\alpha$ and $\beta$ disagree.
-
-	Given $k_\alpha, k_\beta \in \N, \hist \in \allhist, \ar_\alpha \in \gargsalpha, \ar_\beta \in \gargsbeta$, 
-	say that 
-	$(\hist, \ar_\alpha, \ar_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta)$ iff 
-	$(\hist, \ar_\alpha, \ar_\beta)$ is a $\prop/\propbar$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\prop))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](\propbar))$.
-
-	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\beta] \propbar$.
-Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](\propbar))$.
-Test whether $(\ar_{-1}) \nileadstost \prop$.
-If so, $(i, \prop, (\ar_{-1}), \ar_{-1})$ falsifies $\beta$, which ends the procedure.
-	Thus, assume that $(\ar_{-1}) \ileadstost \prop$.
-
-	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[\alpha] \prop$.
-Observe that $\ar_0 \in \gargsalpha \cap (\dfp[\alpha])^0(\gleadstoinv[\alpha](\prop))$.
-Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \prop$.
-By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\prop/\propbar$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
-
-	Suffices now to apply \cref{th:nextchal} repetitively, until finding a falsification instance of $\alpha$ or $\beta$.
-This is because, given a challenge $(\hist, \ar_\alpha, \ar_\beta)$ of complexity $(k_\alpha, k_\beta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity.
-Indeed, if $(\hist, \ar_\alpha)$ challenges $\prop$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
-And if $(\hist, \ar_\beta)$ challenges $\propbar$, apply \cref{th:nextchal} with $\propbar$ for $\prop$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.
-
-	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\prop)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](\propbar)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
-\end{procedure}
+\begin{theorem}
+	\label{th:proc}
+	Given two incompatible empirical theories for a given normative theory, $\alpha = (\gleadsto[\alpha], \gbeats[\alpha], \alldargs_\alpha, \dbeats[\alpha], +_\alpha)$ and $\beta = (\gleadsto[\beta], \gbeats[\beta], \alldargs_\beta, \dbeats[\beta], +_\beta)$ and given any $i \in I$, there exists a procedure that falsifies one of these theories, queries only $i$, and queries $i$ only about some increasing sequence of paths.
+\end{theorem}
+That procedure is described in \cref{sec:proc}.
 
@@
 Let $t \in \R^C$ be a set of thresholds, thus, consisting of one real valued threshold $t_c \in \R$ per criterion.
-Say that $a \in \allalts$ is satisfying iff $\forall c \in C: c(a) ≥ t_c$.
- Let $A$ denote the satisfying alternatives.
+Say that $\alt \in \allalts$ is satisfying iff $\forall c \in C: c(\alt) ≥ t_c$.
+ Let $\alts$ denote the satisfying alternatives.
 
 The theory $\gamma$ claims, intuitively, that individuals $i \in I$ are satisficers using some defined criteria $C$ and thresholds $t = (t_c)_{c \in C}$.
-Define $\peq$ as $a \peq b$ iff $a \in A \lor b \notin A$.
-Note that $\peq$ is complete and contains at most two equivalence classes: $A$, and $\allalts \setminus A$.
-This defines the set of claims that $\gamma$ supports, namely, for any $\emptyset ≠ B \subseteq \allalts$, $\gprops(B) = B \cap A$.
-
-Given $a \in A$, define the fragment $\ar_a$ as the text: “$a$ has performance $c_1(a)$ on criterion $c_1$, and it is reasonable to consider that having at least $t_{c_1}$ is satisfying enough from the point of view captured by $c_1$, [… same phrase for the other criteria…], therefore, it is a fully satisfactory alternative.”
-Given $b \in \allalts \setminus A$, define $\ar_b$ as the text: “$b$ is not satisfactory on the criterion [some criterion such that $c(b) < t_{c}$]: the performance $t_c$ should be attained for considering $b$ as satisfying on that point of view, but it obtains only $c(b)$ on that criterion [… same phrase for the other criteria such that $c(b) < t_c$].”
-
-Given a bundle $B$, define $\ar_B$ as the text obtained by concatenating all fragments in $\set{\ar_a \suchthat a \in B}$.
+Define $\peq$ as $\alt \peq \altp$ iff $\alt \in \alts \lor \altp \notin \alts$.
+Note that $\peq$ is complete and contains at most two equivalence classes: $\alts$, and $\allalts \setminus \alts$.
+This defines the set of claims that $\gamma$ supports, namely, for any $\emptyset ≠ B \subseteq \allalts$, $\gprops(B) = B \cap \alts$.
+
+Given $\alt \in \alts$, define the fragment $\ar_\alt$ as the text: “$\alt$ has performance $c_1(\alt)$ on criterion $c_1$, and it is reasonable to consider that having at least $t_{c_1}$ is satisfying enough from the point of view captured by $c_1$, [… same phrase for the other criteria…], therefore, it is a fully satisfactory alternative.”
+Given $\altp \in \allalts \setminus \alts$, define $\ar_\altp$ as the text: “$\altp$ is not satisfactory on the criterion [some criterion such that $c(\altp) < t_{c}$]: the performance $t_c$ should be attained for considering $\altp$ as satisfying on that point of view, but it obtains only $c(\altp)$ on that criterion [… same phrase for the other criteria such that $c(\altp) < t_c$].”
+
+Given a bundle $B$, define $\ar_B$ as the text obtained by concatenating all fragments in $\set{\ar_\alt \suchthat \alt \in B}$.
 
@@
 A more realistic variant of this empirical theory would refrain from claiming that all satisfactory alternatives are equivalent, and that all non-satisfactory alternatives are equivalent.
-Indeed, this claims is likely to fail reflecting the deliberated preferences of the individuals: $i$ will probably pick $a$ rather than $\set{a, b}$ given a bundle of two satisfactory alternatives $\set{a, b}$ with $a$ Pareto-dominating $b$.
-
-To this effect, given $a, b \in \allalts$, define $a \peq b$ iff $a \in A \land b \notin A$ (this also changes the set of claims that $\gamma$ supports) and keep the other definitions intact.
+Indeed, this claims is likely to fail reflecting the deliberated preferences of the individuals: $i$ will probably pick $\alt$ rather than $\set{\alt, \altp}$ given a bundle of two satisfactory alternatives $\set{\alt, \altp}$ with $\alt$ Pareto-dominating $\altp$.
+
+To this effect, given $\alt, \altp \in \allalts$, define $\alt \peq \altp$ iff $\alt \in \alts \land \altp \notin \alts$ (this also changes the set of claims that $\gamma$ supports) and keep the other definitions intact.
 The resulting theory does not claim to capture complete deliberated preferences, as it ignores how any two alternatives that are both satisfactory, or both unsatisfactory, compare.
@@
 Such a set $\args$, when not empty, represents an effective set of anticipated attackers of $\ar$ against $\prop$. 
-The notation uses a striked through $\prop$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues against $\prop$, from the point of view of $i$.
+The notation uses a striked through $\prop$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues successfully against $\prop$ despite the presence of $\ar$, from the point of view of $i$.
 I write that $\ar$ \emph{$i$-defends} $\prop$ to mean that $\emptyset \nibeats \ar$.
@@
 \begin{proof}
-	First, from right to left, consider a falsification sequence $(\hist^{l + 1})_{l \in 2\N, l ≤ k}$ for some $k \in 2\N$, define, as in \cref{sec:fals}, $\args_{l + 1} = \gbeatsinv(\ar_l) \cap \range(\hist^{l + 1})$, $\dargs[l + 2] = \dbeatsinv(\args_{l + 1})$ and (for $l ≤ k - 2$) $\ar_{l + 2} = \ar_l + \dargs[l + 2]$, and let us show that $(i, \phi, \hist^{k + 1}, \ar_{k})$ is a falsification instance.
-This amounts to show that $\ar_k \in \gargs$, which can be done by observing that $\ar_0 \in \gargs$, and showing that, $\forall l \in 2\N, l ≤ k - 2$, $\ar_l \in \gargs ⇒ \ar_{l + 2} \in \gargs$.
-	Indeed, \cref{th:dpiconstr} applies with $\ar_l$ for $\ar_0$ and $\ar_{l + 2}$ for $\ar_2$.
-As the second member of the equivalence is true by definition of a falsification sequence, $\ar_{l + 2} \in (\dip)(\ar_l)$, and because $\ar_l \in \gargs$, $\ar_{l + 2} \in \gargs$.
-
-	Second, from left to right, consider a falsification instance $(i, \phi, \hist^{k + 1}, \ar_{k})$.
-As $\ar_k \in \gargs$, $\ar_k \in (\dip)^k({\gleadstoinv}(\prop))$ (equalizing the indices $k$ wlog).
-Given $\ar_{l + 2} \in (\dip)^j({\gleadstoinv}(\prop))$, with $j > 0$, thus $\ar_{l + 2} \in \dip(\ar_l)$ for some $\ar_l \in (\dip)^{j - 1}({\gleadstoinv}(\prop))$, apply \cref{th:dpiconstr}, obtain $\hist_{l + 1}$.
+	First, from right to left, consider a falsification sequence $(\hist^{k + 1})_{k \in 2\N, k ≤ N}$ for some $N \in 2\N$, define, as in \cref{sec:validity}, $\args_{k + 1} = \gbeatsinv(\ar_k) \cap \range(\hist^{k + 1})$, $\dargs[k + 2] = \dbeatsinv(\args_{k + 1})$ and (for $k ≤ N - 2$) $\ar_{k + 2} = \ar_k + \dargs[k + 2]$, and let us show that $(i, \phi, \hist^{N + 1}, \ar_N)$ is a falsification instance.
+This amounts to show that $\ar_N \in \gargs$, which can be done by observing that $\ar_0 \in \gargs$, and showing that, $\forall k \in 2\N, k ≤ N - 2$, $\ar_k \in \gargs ⇒ \ar_{k + 2} \in \gargs$.
+	Indeed, \cref{th:dpiconstr} applies with $\ar_k$ for $\ar_0$ and $\ar_{k + 2}$ for $\ar_2$.
+As the second member of the equivalence is true by definition of a falsification sequence, $\ar_{k + 2} \in (\dip)(\ar_k)$, and because $\ar_k \in \gargs$, $\ar_{k + 2} \in \gargs$.
+
+	Second, from left to right, consider a falsification instance $(i, \phi, \hist^{N + 1}, \ar_N)$.
+As $\ar_N \in \gargs$, $\ar_N \in (\dip)^N({\gleadstoinv}(\prop))$ (equalizing the indices $N$ wlog).
+Given $\ar_{k + 2} \in (\dip)^j({\gleadstoinv}(\prop))$, with $j > 0$, thus $\ar_{k + 2} \in \dip(\ar_k)$ for some $\ar_k \in (\dip)^{j - 1}({\gleadstoinv}(\prop))$, apply \cref{th:dpiconstr}, obtain $\hist_{k + 1}$.
 Iterate while $j > 0$.
@@
 \end{theorem}
-\begin{proof}[of \cref{th:valid}]
+\begin{proof}
 	Given any $i \in I$ and $\prop \in \gpropse$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \prop$; the conclusion then follows thanks to normative adequacy.
@@
 \end{proof}
+
+\section{Comparing theories}
+\label{sec:proc}
+This section proves \cref{th:proc} constructively, by describing the sequence of tests that must be performed and showing that they must lead to falsifying one of the theories.
+To do this, the notion of challenge must be defined and a few simple lemmas are required.
+
+Given $\prop \in \allprops$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $\prop$ iff $\hist \nileadstost \prop$ and $\ar_\gamma \in \histend$.
+Given $\prop \in \allprops, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \prop)$ or $(\hist, \ar_\delta)$ challenges $(\delta, \propbar)$.
+
+\commentYM{il faudrait tenir la main du lecture : dire pourquoi tu définis ça.
+Ca se comprends, je sais, mais ça demande au lecteur un gros effort qui n'est pas récompensé par une impression de comprendre où ça va}
+
+\begin{lemma}
+	\label{th:endchal}
+	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$, $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge.
+\end{lemma}
+\begin{proof}
+	Either $\hist \nileadstost \prop$, and $(\hist, \ar_\gamma)$ challenges $\prop$, or $\hist \ileadstost \prop$, hence, by \cref{th:protcoh}, $\hist \nileadstost \propbar$, and $(\hist, \ar_\delta)$ challenges $\propbar$.
+\end{proof}
+
+\begin{lemma}
+	\label{th:nextchal}
+	Given $(\hist, \ar_\gamma)$ challenging $\prop$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\prop))$, and $\ar_\delta \in \gargsdelta$: either $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $\prop/\propbar$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\prop))$.
+\end{lemma}
+\begin{proof}
+	If $\ar_\gamma$ does not $i$-defend $\prop$, then $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, which ends the proof. 
+	Thus, assume that $\ar_\gamma$ $i$-defends $\prop$.
+
+	\Cref{th:produce} applies and yields $\ar'_\gamma = \ar_\gamma + \dbeatsinv(\gbeatsinv(\ar_\gamma)) \in \gargs \cap \dfp(\ar_\gamma)$, thus $\ar'_\gamma \in (\dfp)^{(k + 1)}(\gleadstoinv(\prop))$. 
+	Now, define $\histpp = (\hist, \ar'_\gamma)$ and test whether $\histpp \nileadstost \prop$.
+
+	If $\histpp \nileadstost \prop$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\gamma, \ar_\delta)$ challenges $\prop$, which concludes the proof. 
+	Thus, assume that $\histpp \ileadstost \prop$.
+
+	Let us now define $\histp$ such that $\set{\ar'_\gamma, \ar_\delta} \subseteq \histpend$, so that \cref{th:endchal} applies on $(\histp, \ar'_\gamma, \ar_\delta)$, which will conclude the proof.
+
+	If $\ar_\delta \in \histppend$, this is done by defining $\histp = \histpp$. Otherwise, define $\histp = (\histpp, \ar_\delta)$ and test whether $\histp \nileadstost \prop$. 
+\end{proof}
+
+%Given a normative theory and two empirical theories for that normative theory and $i \in I$, 
+%a \emph{test procedure with $i$} is a finite sequence 
+%\commentOC{Need the test procedure to be a tree.
+Atom: $(k, \prop)$ meaning whether ${\hist}^k \ileadstost \prop$.
+Branch label: atoms linked using or and and operators.
+From a node $n = (\hist, \ar, \prop)$, let branches depart, such that their labels do not overlap.
+From a node, if no branch label is true, the node must falsify a theory.
+In the case of the procedure below, it is not a list because we may query several times the same theory or switch to the other one, depending on the last answer.
+But if simplifying the theory (single-try), we may then simplify the definition of a test procedure.}
+
+\begin{procedure}
+	\label{proc}
+	Pick any $\prop \in \allprops$ about which $\alpha$ and $\beta$ disagree.
+
+	Given $k_\alpha, k_\beta \in \N, \hist \in \allhist, \ar_\alpha \in \gargsalpha, \ar_\beta \in \gargsbeta$, 
+	say that 
+	$(\hist, \ar_\alpha, \ar_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta)$ iff 
+	$(\hist, \ar_\alpha, \ar_\beta)$ is a $\prop/\propbar$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\prop))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](\propbar))$.
+
+	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\beta] \propbar$.
+Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](\propbar))$.
+Test whether $(\ar_{-1}) \nileadstost \prop$.
+If so, $(i, \prop, (\ar_{-1}), \ar_{-1})$ falsifies $\beta$, which ends the procedure.
+	Thus, assume that $(\ar_{-1}) \ileadstost \prop$.
+
+	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[\alpha] \prop$.
+Observe that $\ar_0 \in \gargsalpha \cap (\dfp[\alpha])^0(\gleadstoinv[\alpha](\prop))$.
+Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \prop$.
+By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\prop/\propbar$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
+
+	Suffices now to apply \cref{th:nextchal} repetitively, until finding a falsification instance of $\alpha$ or $\beta$.
+This is because, given a challenge $(\hist, \ar_\alpha, \ar_\beta)$ of complexity $(k_\alpha, k_\beta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity.
+Indeed, if $(\hist, \ar_\alpha)$ challenges $\prop$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
+And if $(\hist, \ar_\beta)$ challenges $\propbar$, apply \cref{th:nextchal} with $\propbar$ for $\prop$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.
+
+	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\prop)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](\propbar)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
+\end{procedure}
 

### 2020-11-03 simple.tex
Totalitarism vocabulary

@@
 
-A defense relation ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is an injective and surjective binary relation over $\alldargs × \gbeatsinv(\allargs)$.
+A defense relation ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is an injective (left-unique) and surjective (right-total) binary relation over $\alldargs × \gbeatsinv(\allargs)$.
 \commentYM{le fait qu'elle soit surjective et injective est une exigence que tu poses dans la définiton ?
@@
 These constraints guarantee that every anticipated attack has exactly one fragment defending against it, thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton.
-Note that $\dbeats$ need not be a bijection as it is generally not a function. 
+Note that $\dbeats$ need not be a bijection as it is generally not a function (it is not restrictive to suppose it left-total, but it is generally not right-unique). 
 Given $\ar_1 \in \gbeatsinv(\allargs)$, define $\dbeatsinv(\ar_1)$ as the fragment defending against the anticipated attack $\ar_1$.

### 2020-11-10 simple.tex
Clearer intro

@@
 By contrast, this difficulty of validation is much alleviated with descriptive approaches.
-Such approaches can be validated by comfronting their predictions to empirical data.
+Such approaches can be validated by confronting their predictions to empirical data.
 When two descriptive theories disagree on their predictions, it is often possible to show that at least one of them is wrong with a suitable experiment.
@@
 	The \emph{additive} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever alternative $\alt$ maximises $v(\alt) = v_1(g_1(\alt)) + v_2(g_2(\alt))$, where $v_i: \R → \R$ are functions  chosen by the theorist.
-	How the parameters of these theories, $t_i$ and $v_i$, are determined is irrelevant to the questions tackled in this article, because it aims at defining and studying theories of \ac{DJ} in general, not at proposing a way of building a specific theory of \ac{DJ}.
-%For this example, one can assume that these parameters are determined on the basis of observation of the behavior of some population in some similar circumstances.
 
@@
 To determine which theory is right, it is insufficient to simply observe what an individual $i \in I$ effectively chooses.
-This would merely reflect her unreflective behavior.
+This would merely represent her unreflective behavior.
 The approach adopted in this article to capture \acp{DJ} is to declare that the winning theory (if any) is the one that exhibit arguments able to systematically convince individuals that their proposed choice is to be adopted.
@@
 
-This article is structured as follows.
+The important question about how the parameters $t_i$ and $v_i$ of these illustrative theories would be determined is left aside in this article.
+This article aims at defining and studying theories of \ac{DJ} in general, not at proposing a way of building a specific theory of \ac{DJ}.
+%For this example, one can assume that these parameters are determined on the basis of observation of the behavior of some population in some similar circumstances.
+
+The approach it adopts is the following.
+First, it introduces a normative axiom that mandates that whatever propositions the \ac{DM} accepts when reasoning carefully can be prescribed.
+This notion of careful acceptability is defined formally on the basis of an observable relation that captures the reactions of the \ac{DM} to arguments.
+This requirement is described here as a normative axiom because it has to be accepted on the basis of its apparent adequacy to capture what is intuitively an acceptable requirement for a procedure aiming at prescribing to a \ac{DM}.
+In other words, it is not a hypothesis on the observable world: that the requirement holds cannot be proven by observation.
+It has, in that sense, a similar epistemological status as axioms of classical decision theories when they are applied for prescription, for example, Savage’s sure thing principle.
+Arguably, we can observe whether individuals unreflectively behave according to Savage’s sure thing principle, or any other decision-theoretic axiom, but even when they fail to, it can be said that this is because of a mistake: the normative status of an axiom is not hit by violations due to unreflective behavior.
+In that sense, such axioms are not falsifiable.
+
+Second, this article defines descriptive theories of acceptable propositions.
+Acceptable here is in the sense of the careful acceptability just defined informally.
+Descriptive here means that these theories can predict at least some of the propositions that will be considered acceptable by the \ac{DM}.
+This is arguably the more important and difficult part of the current research program: it has to convince that it is practically possible to define theories that predict such an a priori volatile thing as the way individuals reason.
+It is plain that mandating that theories be able to predict the reaction of individuals to every possible sequence of arguments they are exposed to would be plainly irrealistic.
+Some weaker criterion is required.
+How weak can it become?
+As announced, the proposed theories must be purely descriptive, apart from the required acceptance of the normative adequacy axiom described in the above paragraph.
+In other words, their conclusions must hold on the sole basis of the unique normative axiom, aided by claims that can be proven false experimentally.
+Equivalently, if the theory is invalid, in the sense of failing its predictions about the acceptability of propositions, then it must be falsifiable: there must exist a set of observable reactions of the \ac{DM} to arguments that contradict the claims of the theory.
+Accordingly, this article claims and proves that empirical theories of \ac{DJ} as defined here are such that under normative adequacy, if the theory is not falsified, then it is valid.
+I admit readily that this might not suffice to convince that building such concrete theories is feasible.
+It is only one of the difficulties to tackle.
+
+A possible objection to the usefulness of this approach should perhaps be lifted before delving into the formal descriptions of this rough sketch.
+It may be argued that because this proposition needs a normative axiom, which cannot be validated empirically, it does not fare better than the alternative propositions existing in the literature. 
+%\ac{SEU}, for example, also can be considered to claim to obtain reflective preferences on the basis of normative axioms.
+I grant that it is impossible to get completely rid of normative axioms, because prescriptions must be linked to descriptions, and this cannot be done in a complete empirical way.
+However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims.
+The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science (again, accepting this claim does not require to ignore that observations themselves rest upon theories).
+This article postulates that the normative axiom it proposes will be consensual, at least for some non trivial concrete instanciations of the proposed approach, among economists, practitioners, external observers and \acp{DM}.
+Furthermore, its simplicity and a priori obviousness is a strong point in its favor.
+It has, in some intuitive sense that cannot be described formally, less “content”, in the sense of that word used when economists argue that their theories should not have content about the preferences of the individuals (for fear of being paternalistic or dictatorial).
+Of course, any decision theory has content in a wider sense of imposing some structure to preferences, otherwise, the theory is void.
+The question is: are the restrictions imposed of a kind that can be judged acceptable with respect to the considered applications of the theory?
+Mandating, as is done here, that the judgments be of the sort that resists against counter-arguments seems to me to capture exactly what is desired in a prescription context.
+%Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance.
+(This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.)
+The lack of concrete substance in its axiom does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences.
+It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
+It is also worth noting that the proposed axiom has a specific form that may permit decision makers to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation.
+Detailed exploration of this aspect is deferred to future work.
+
+The rest of this article is structured as follows.
 \Cref{sec:approaches} defines more precisely what is meant here with normative and descriptive theories.
@@
 This central result thus amounts to prove the main claim of this article, namely, that accepting a weak normative axiom, supplemented with empirical claims, is enough to capture someone’s reflective preferences.
-
-A possible objection to the usefulness of this approach should perhaps be lifted before delving into the formal descriptions of this rough sketch.
-It may be argued that because this proposition needs a normative axiom, which cannot be validated empirically, it does not fare better than the alternative propositions existing in the literature.
-\ac{SEU}, for example, also can be considered to claim to obtain reflective preferences on the basis of normative axioms.
-I grant that it is impossible to get completely rid of normative axioms, because prescriptions must be linked to descriptions, and this cannot be done in a complete empirical way.
-However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims.
-The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science (again, accepting this claim does not require to ignore that observations themselves rest upon theories).
-Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance.
-(This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.) This does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences.
-It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
-It is also worth noting that the proposed axiom has a specific form that may permit decision makers to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation.
-Detailed exploration of this aspect is deferred to future work.
 
@@
 \commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question. Je doute cependant qu'un lecteur innocent comprenne un traitre mot}
+The hypothesis of memory further reduces the possible sequences that can be tested with a given individual.
 
@@
 \commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi}
-The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments.
+%The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments.
 This is accomplished by three binary relations, part of the definition of empiricial theories: one represents its initial arguments, one plans the possible attacks, and one defines its counter-arguments.
 An empirical theory also defines a concatenation operation able to dynamically build arguments from fragments of arguments.
-The theory claims that when one of its arguments in support of one of its claims is unconvincing to an individual, it is because of one of the anticipated attacks; and the theory claims to be able to provide counter-arguments to such attacks as they come, that will in turn be either convincing to the individual, or fail to be because of some anticipated attack.
+%The theory claims that when one of its arguments in support of one of its claims is unconvincing to an individual, it is because of one of the anticipated attacks; and the theory claims to be able to provide counter-arguments to such attacks as they come, that will in turn be either convincing to the individual, or fail to be because of some anticipated attack.
 The theory is also constrained to have “finite depth”, meaning that it must set an a priori limit to the number of such iterations of attacks and counter-arguments.
 
-Thanks to these operators, an empirical theory may argue in a way that depends on the counter-arguments each individual finds appealing
-\commentYM{je ne comprends pas cette phrase, et en particulier le sens qu'il faut donner au terme "adjust"}.
+%Thanks to these operators, an empirical theory may argue in a way that depends on the counter-arguments each individual finds appealing
+%\commentYM{je ne comprends pas cette phrase, et en particulier le sens qu'il faut donner au terme "adjust"}.
 Instead of having to give a single decisive argument in support of its claims, the theory may react to exactly the counter-arguments that a given individual thinks relevant.
@@
 Such theories satisfy the two properties that are mandatory to achieve what has been announced, namely, to obtain theories of \ac{DJ} whose power rest on a weak normative axiom and on empirically falsifiable claims.
-First, the main claim of the theory, of being able to argue convincingly, holds if and only if no falsification sequence exist.
-Second, granted normative adequacy, if indeed a theory is convincing, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}.
+First, the claim of the theory that it argues convincingly holds if and only if no falsification sequence exist (falsification sequences are defined formally here below).
+Second, granted normative adequacy, if indeed a theory argues convincingly, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}.
 These two claims are laid out formally in \cref{th:svalid}.
 
-A second goal of this section is to prove that when two theories disagree about incompatible propositions, one of the theories at least must fail some given series of empirical tests, which the proof describes.
+A second goal of this section is to prove that when two theories disagree about incompatible propositions, one of the theories at least must fail some given sequence of empirical tests, which the proof describes.
 Importantly, these tests can be performed on a single individual and are robust against the hypothesis of memory.
@@
 In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
-An empirical theory for a normative theory of \ac{DJ} is defined as a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$, where ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation; ${\gbeats} \subseteq \allargs × \allargs$ is an anticipated attacks relation; $\alldargs$ is a primitive set of argument fragments; ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is a defense relation; and $+$ combines arguments to coalitions of fragments to form new arguments; with the supplementary constraint that the tuple must have a bounded depth.
+A descriptive tuple for a normative theory of \ac{DJ} is defined as a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$, where ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation; ${\gbeats} \subseteq \allargs × \allargs$ is an anticipated attacks relation; $\alldargs$ is a primitive set of argument fragments; ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is a defense relation; and $+$ combines arguments to coalitions of fragments in order to form new arguments.
+A descriptive theory for a normative theory of \ac{DJ} is a descriptive tuple that has a bounded depth.
 These concepts are now defined formally.
@@
 An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ defines the set of supported  propositions and, for each supported propositions, the set of initial arguments for these propositions.
-More precisely, let $\gpropse$, the range of ${\gleadsto}$, be called the propositions supported by the descriptive theory.
+More precisely, let $\gpropse$, the range of ${\gleadsto}$, be called the propositions \emph{supported} by the descriptive theory.
 Given such a supported proposition $\prop \in \gpropse$, let $\gleadstoinv(\prop) = \set{\ar \in \allargs \suchthat \ar \gleadsto \prop}$ be called the initial arguments in favor of $\prop$.
@@
 These constraints guarantee that every anticipated attack has exactly one fragment defending against it, thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton.
-Note that $\dbeats$ need not be a bijection as it is generally not a function (it is not restrictive to suppose it left-total, but it is generally not right-unique). 
+Note that $\dbeats$ need not be a bijection as it is generally not a function (it is not restrictive to suppose it left-total, but it generally is not right-unique). 
 Given $\ar_1 \in \gbeatsinv(\allargs)$, define $\dbeatsinv(\ar_1)$ as the fragment defending against the anticipated attack $\ar_1$.
@@
 Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \alldargs$, the notation $\ar + \dargs$ stands for $+(\ar, \dargs)$.
-(The function $+$ need not be defined on so large a domain, because an argument is only ever added to its own defenders, but this definition is adopted for simplicity; \cref{sec:append} refines this requirement.)
+(The function $+$ need not be defined on so large a domain, because an argument is only ever added to its own defenders, but this definition is adopted here for simplicity; \cref{sec:append} refines this requirement.)
 

### 2020-11-10 simple.tex
Got rid of unclear ()

@@
 However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims.
-The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science (again, accepting this claim does not require to ignore that observations themselves rest upon theories).
+The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science.
 This article postulates that the normative axiom it proposes will be consensual, at least for some non trivial concrete instanciations of the proposed approach, among economists, practitioners, external observers and \acp{DM}.
@@
 It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
-It is also worth noting that the proposed axiom has a specific form that may permit decision makers to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation.
+It is also worth noting that the proposed axiom has a specific form that may permit \acp{DM} to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation.
 Detailed exploration of this aspect is deferred to future work.

### 2020-11-10 simple.tex
Wording

@@
 The question is: are the restrictions imposed of a kind that can be judged acceptable with respect to the considered applications of the theory?
-Mandating, as is done here, that the judgments be of the sort that resists against counter-arguments seems to me to capture exactly what is desired in a prescription context.
+Favoring judgments that resist against counter-arguments, as is done here, seems to me to capture exactly what is desired in a prescription context.
 %Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance.

### 2020-11-10 simple.tex
Slight wording change

@@
 The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science.
-This article postulates that the normative axiom it proposes will be consensual, at least for some non trivial concrete instanciations of the proposed approach, among economists, practitioners, external observers and \acp{DM}.
-Furthermore, its simplicity and a priori obviousness is a strong point in its favor.
+I postulate that the normative axiom proposed here will be consensual, at least for some non trivial concrete instanciations of the proposed approach, among economists, practitioners, external observers and \acp{DM}.
+Furthermore, its simplicity and a priori obviousness are strong points in its favor.
 It has, in some intuitive sense that cannot be described formally, less “content”, in the sense of that word used when economists argue that their theories should not have content about the preferences of the individuals (for fear of being paternalistic or dictatorial).
@@
 (This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.)
-The lack of concrete substance in its axiom does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences.
+The lack of concrete substance in this normative axiom does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences.
 It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.

### 2020-11-11 simple.tex
Examples Normative theory

@@
 J'aurais inventé un symbole du genre $ \allargs^{\intvl{}}$ ; par ailleurs je trouve l'explication relative à l'empty sequence particulièrement alambiquée}
-\commentOCf{Il me semble assez naturel de, étant donné un ensemble de caractères $S$, définir l’ensemble des chaines de caractères par $S^*$ (représentant le fait de prendre toutes les puissances possibles de $S$), mais c’est peut-être un tropisme d’informaticien qui ne sera donc pas compris par des lecteurs économistes.
-J’ai vu la notation $Seq(\allargs)$ être utilisée, mais elle me semble un peu longue, vu l’usage intensif de ce symbole.
+\commentOCf{Il me semble assez naturel de, étant donné un ensemble de caractères $S$, définir l’ensemble des chaines de caractères par $S^*$ (représentant le fait de prendre toutes les puissances possibles de $S$), mais c’est peut-être un tropisme d’informaticien qui ne sera donc pas compris par des lecteurs économistes, et effectivement l’étoile est aussi utilisée pour exclure zéro, ce qui n’a rien à voir.
+J’ai vu la notation $Seq(\allargs)$ être utilisée, mais elle me semble un peu longue, vu l’usage intensif de ce symbole ici.
 Oui, peut-être en viendrai-je à l’invention que tu proposes, mais inventer ses propres symboles n’est légitime que si aucun n’existe déjà.
@@
 Throughout the article, $\N$ includes zero. %and $\N^* = \N \setminus \set{0}$. 
-Given $j, k \in \N$, the notation $\intvl{j, k}$ represents $\set{l \suchthat j ≤ l ≤ k}$. 
+Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$.
+Thus, given an argumentative path $\alpha$ of length $l \in \N$, $\forall k \in \intvl{1, l}$, $\alpha_k \in A$, and $\alpha = \emptyset ⇔ l = 0$.
 %Note that $\intvl{1, 0} = \emptyset$, and given any set $S$, the notation $S^\emptyset$ represents the empty set. 
@@
 This defines a normative theory of \ac{DJ}.
-To make it useful, an axiom is required that links the observable reactions of the individuals to their \ac{DJ}.
+
+\begin{example}[A normative theory about two lotteries]
+	\label{ex:twolott}
+	In a famous article about preference reversals, \citet{lichtenstein_reversals_2006} discuss an example involving two lotteries.
+The lottery $P$ makes you win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $P = (.99, +\$4; .01, −\$0.1)$.
+The lottery $D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
+The letter $P$ stands for probability: one salient aspect of $P$ is the very high chance of winning.
+The letter $D$ stands for dollar: one salient aspect of $D$ is the high gain it gives (compared to $P$) in dollar amount if the player is lucky.
+
+This example is interesting because when asked to bid for lotteries, the theory discussed by the authors predicts, and their experiments confirm, that subjects tend to bid more for $D$ than for $P$ (because the bidding question tend to make individuals focus on dollar amounts) whereas when asked to choose one lottery, the lotteries being presented in pairs, subjects tend to choose $P$ (giving a greater attention to probabilities) among the pair $\set{P, D}$.
+
+Define $\allprops = \set{P ≥ D, P > D, D ≥ P, D > P}$, where $P ≥ D$ represents the proposition that $i$ should choose $P$ or declare to be indifferent when choosing among $\set{P, D}$; $P > D$, the proposition that $i$ should choose $P$ and not $D$ when choosing among $\set{P, D}$; and similarly for $D ≥ P$ and $D > P$.
+
+Define $\ar_0$ as a text arguing that the choice for both $P$ and $D$ should be according to their expected revenue, namely, $\$3.9590$ for $P$ and $\$4$ for $D$.
+Here is a possible text for $\ar_0$.
+“Imagine you play this bet 100 times.
+On average, you would win 99 times and lose once, which means gaining 99 × \$4 = \$396 and losing 1 × \$0.10 = \$0.10, hence a total net gain of \$395.90.
+Thus, your average net gain for the $P$ bet would be \$3.9590.
+[Similar text for $D$.] Therefore, we suggest you choose $D$ for a higher expected revenue.”
+Define $\ar_1$ as a text arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain. 
+Omitting many other relevant arguments for now (such as observing that utility should be linear for small amounts of money, for example), define $\allargs = \set{\ar_0, \ar_1}$.
+
+Define $I$ as a set of individuals facing a choice between $P$ and $D$ in a laboratory experiment.
+
+Define $\ileadsto$ as follows.
+Given $\hist$, $\hist \ileadsto (P ≥ D)$ iff, in a situation of $i$ having been exposed, in order, to the arguments in $\hist$, saying: “Considering these arguments, would you please choose either to play $P$, or play $D$, or declare to be indifferent (in which case one will be picked randomly for you)” leads $i$ to choose $P$ than $D$, or declare indifference.
+$\hist \ileadsto \prop$ is defined similarly for other elements $\prop \in \allprops$.
+
+The tuple $(\allprops, \allargs, I, {\allleadsto})$ is an example of a normative theory of \ac{DJ}.
+\end{example}
+
+We now need an axiom that links the observable reactions of the individuals to their \ac{DJ}.
 This will be done through the notion of a decisive argument, that is, intuitively, an argument that is able to convince an individual of the acceptability of a proposition whatever the argumentative path the individual has been submitted to.
@@
 
+\begin{example}[Two lotteries (cont.)]
+	Continuing \cref{ex:twolott}, the normative adequacy axiom is satisfied for that normative theory iff, for all $i \in I$, if there is a argument $\ar \in \allargs$ that leads $i$ to never choose $D$, facing any counter-argument and in the context of any preceding argumentative path, under condition that $\ar$ be included towards the end of the path, then we are ready to accept that $i$ deliberately judges that he should choose $P$ rather than $D$, and similarly for the other propositions $\prop \in \allprops$.
+
+	As described in \cref{ex:twolott}, the set $\allargs$ is not wide enough to make this axiom reasonably acceptable: normative adequacy can only be considered a reasonable requirement when the set of arguments includes all arguments that can possibly change the opinion of at least one individual $i \in I$ about the considered topic $\allprops$.
+\end{example}
+
 To end the presentation of the normative theories of \ac{DJ}, it may be useful to analyze the status of contradictory propositions.
-\Cref{th:protcoh} shows that two propositions which are readily judged to be incompatible by $i$ cannot both be acceptable.
+\Cref{th:protcoh} shows that two incompatible propositions cannot both be acceptable.
 In supplement, it may be interesting to observe that theories of \ac{DJ} do not require to postulate that $i$’s \ac{DJ} is complete, in the sense that when the agenda is closed under negation, it must not necessarily be the case that either the proposition or its negation is in $i$’s \ac{DJ}.
@@
 consider defined a negation operator $¬$ on $\allprops$.
-$¬$ is a negation operator iff it is an involution operator (thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$) and furthermore satisfying, $\forall \phi \in \allprops: \hist \ileadsto \prop ⇒ \hist \nileadsto ¬\prop$.
-Given any $i \in I$, say that a proposition $\prop \in \allprops$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost \propbar$.
+$¬$ is a negation operator iff it is an involution operator (thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$) and furthermore satisfying, $\forall \hist \in \allhist, \phi \in \allprops: \hist \ileadsto \prop ⇒ \hist \nileadsto ¬\prop$.
+Given any $i \in I$, say that a proposition $\prop \in \allprops$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop$.
 The $i$-decidable propositions are those on which the normative theory permits, in principle, to take a position. 
@@
 \begin{definition}[Unrestricted interpretability]
-	$\forall \prop \in \allprops: \prop \in \iprops \oplus ¬\prop \in \iprops$.
+	$\forall \prop \in \allprops: \prop \in \iprops ⇔ ¬\prop \notin \iprops$.
 \end{definition}
@@
 \end{definition}
+
 The following proposition directly follows from the definitions, together with \cref{th:protcoh}.
@@
 \end{proposition}
+
+\begin{example}[Two lotteries: completeness]
+	Applying these definitions and results to \cref{ex:twolott}, we can define a negation operator such that $¬(P ≥ D) = D > P$ and $¬(D ≥ P) = P > D$.
+We see that $P ≥ D$ is $i$-decidable iff $D > P$ is $i$-decidable iff there exists a decisive argument $\ar \in \allargs$ for $P ≥ D$ or for $D > P$.
+It follows from \cref{th:restrinterpr} that at most one of $P ≥ D$ and $D > P$ are in $\iprops$.
+	Theory completeness holds iff there exists a decisive argument for $P ≥ D$ or for $D > P$ and a decisive argument for $D ≥ P$ or for $P > D$.
+In such a case, and assuming normative adequacy holds, Deliberation completeness holds as well, thus for every proposition, either it or its contrary is in $i$’s \ac{DJ}.
+\end{example}
+
 Theories as defined here do not mandate Theory completeness.
@@
 
-That the \ac{DJ} of an individual exists independently of any theory of decision making might be considered a strong assumption, by analogy to shallow preferences: psychologists have shown that shallow preferences often depend on a priori irrelevant features pertaining to the description of the decision problem or the context of interrogation.
+It might be useful to exemplify those remarks in the case of our running example before discussing them further.
+\begin{example}[Discussion about completeness]
+	It should be remarked that there is no logical contradiction in assuming that $i$ could, for example, deliberately judge that $P ≥ D$, but have no deliberated judgment about whether $D ≥ P$ or rather $P > D$ holds, thus, whether these two lotteries have equal worth in terms of bidding or whether $P$ is worth strictly more.
+In such a case, Deliberation completeness does not hold.
+	More pragmatically, there may be no argument in $\allargs$ strong enough to convince $i$ to pick $P$ rather than $D$, but no argument strong enough to convince $i$ that $P$ and $D$ are equally preferable.
+For a formal example where this would happen, assume $\ileadsto$ is such that it $i$ is lead to choose only $P$ when $\ar_0$ comes last in the argumentative path, but $i$ is lead to be indifferent when $\ar_0$ is before last in the argumentative path.
+\end{example}
+
+Not mandating Theory completeness is a first important element to allow hope that effective theories of \ac{DJ} can be built.
+
+That the \ac{DJ} of an individual exists independently of any theory of decision making might be considered a strong assumption, by analogy to the case of shallow preferences: psychologists have shown that shallow preferences often depend on a priori irrelevant features pertaining to the description of the decision problem or the context of interrogation.
 Preferences are often said to be constructed, thus, to not exist independently of the framing and context of study.
@@
 Some televisions just won’t sell; most of the time, people are unlikely to want 80\% of their wages to go into savings.
-It would be an overstatement to say of preferences, as Gertrude Stein said of Oakland, that “there is no there there.”
+It would be an overstatement to say of preferences, as Gertrude Stein said of Oakland, that ‘there is no there there’.”
 \commentYM{ce § et le précédent me semble mériter plus que le reste une réécriture. Par ailleurs, je ne vois pas à quoi ils servent dans cette sous-section}
@@
 %XP3. With effective gambling and iterated thinking to thing about their preference.
-In an article about preference reversals, LS discuss an example involving two lotteries.
-The lottery $P$ makes you win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $P = (.99, +\$4; .01, −\$0.1)$.
-The lottery $D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
-The letter $P$ stands for probability: one salient aspect of $P$ is the very high chance of winning.
-The letter $D$ stands for dollar: one salient aspect of $D$ is the high gain it gives (compared to $P$) in dollar amount if the player is lucky.
-
-This example is interesting because when asked to bid for lotteries, the theory discussed by the authors predicts, and their experiments confirm, that subjects tend to bid more for $D$ than for $P$ (because the bidding question tend to make individuals focus on dollar amounts) whereas when asked to choose one lottery, the lotteries being presented in pairs, subjects tend to choose $P$ (giving a greater attention to probabilities).
-
 This section presents a theory that claims that $i$ deliberately prefers $P$ to $D$, in the sense of bidding at least as much for $P$ than for $D$.
@@
 
-Define $\allprops = \set{\prop, ¬\prop}$, $\prop$ representing intuitively the case that $i$ deliberately prefers $P$ to $D$, in the sense of bidding at least as much for $P$ than for $D$ after deliberation, and $¬\prop$, the opposite.
-
-Define $\ileadstost$ as follows.
-Given $\hist = (…, \ar)$, $\hist \ileadstost \prop$ iff, in a situation of $i$ having been exposed to these arguments, saying: “Considering these arguments, would you please indicate your maximum selling price for $P$, and for $D$” leads $i$ to bid at least as much for $P$ than for $D$.
-$\hist \ileadstost ¬\prop$ is defined similarly.
-%Note that $\hist \ileadstost \prop$ iff $\hist \nileadstost ¬\prop$.
-
-Thus, the normative adequacy axiom is satisfied iff, whenever there is a argument that, facing any counter-argument, leads $i$ to bid at least as much for $P$ than for $D$, we are ready to accept that $i$ deliberately prefers $P$ to $D$, in the bidding sense.
-
-Define $\ar_0$ as arguing that the bid for both $P$ and $D$ should equal their expected revenue, namely, $.99 × (\$4) − 0.01 × \$0.1$ for $P$.
-Here is a possible text for $\ar_0$.
-“Imagine you play this bet 100 times.
-On average, you will win 99 times and lose 1 time, which means gaining 99 × \$4 = \$396 and losing 1 × \$0.10 = \$0.10, hence a total net gain of \$395.90.
-Thus, your average net gain for the $P$ bet would be \$3.9590.
-Therefore, we suggest you bet \$3.9590 for $P$.
-[Similar text for $D$.]”
-
-Define $\ar_1$ as arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain.
 Define $\ard[2]$ as arguing that the goal is to maximise average revenue, and thus, losses should count equally to gains.

### 2020-11-12 simple.tex
Mainly descriptive improv; started getting rid of parametric incompatibility relation

@@
 The question is: are the restrictions imposed of a kind that can be judged acceptable with respect to the considered applications of the theory?
-Favoring judgments that resist against counter-arguments, as is done here, seems to me to capture exactly what is desired in a prescription context.
+Favoring judgments that resist counter-arguments, as done here, seems to me to capture exactly what is desired in a prescription context.
 %Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance.
@@
 This field has greatly inspired this proposal, in particular, the notion of attack and of reinstatement.
-This field however does not view the attack relation as observable, but considers it as given, and its methodology is therefore not empirical in the sense seeked for here.
-(\Citet{cailloux_formal_2019} elaborates on this difference of objective.)
+This field however does not view the attack relation as observable, but considers it as given, and its methodology is therefore not empirical in the sense seeked here.
+(\Citet{cailloux_formal_2019} elaborates somewhat on this difference of objective.)
 \commentYM{ici aussi, je trouve la mention de ces approches maladroite, car elles sont mises en exergue comme si elles étaient des manières de traiter le problème qui t'intéresse, ce qu'elles ne sont pas}
@@
 These interesting approaches permit to study empirically the sense of fairness of real individuals, and compare them to social choice theories.
-They are distinct from the currently proposed approach as they do not involve arguments; and do not specifically aim to prescribe to an individual.
+They are distinct from the currently proposed approach as they seek to obtain their a priori sense of fairness, rather than aim at observing how subjects would appreciate (possibly counter-intuitive) claims about justice when they are backed by (possibly elaborate) arguments; and do not specifically aim to prescribe to an individual.
 
@@
 
-Define $\ar_0$ as a text arguing that the choice for both $P$ and $D$ should be according to their expected revenue, namely, $\$3.9590$ for $P$ and $\$4$ for $D$.
+Define $\ar_0$ as a text arguing that the choice between $P$ and $D$ should be according to their expected revenue, namely, $\$3.959$ for $P$ and $\$4$ for $D$.
 Here is a possible text for $\ar_0$.
@@
 Define $\ar_1$ as a text arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain. 
-Omitting many other relevant arguments for now (such as observing that utility should be linear for small amounts of money, for example), define $\allargs = \set{\ar_0, \ar_1}$.
+Omitting many other relevant arguments for now (such as arguing that utility should be linear for small amounts of money, for example), define $\allargs = \set{\ar_0, \ar_1}$.
 
@@
 Define $\ileadsto$ as follows.
-Given $\hist$, $\hist \ileadsto (P ≥ D)$ iff, in a situation of $i$ having been exposed, in order, to the arguments in $\hist$, saying: “Considering these arguments, would you please choose either to play $P$, or play $D$, or declare to be indifferent (in which case one will be picked randomly for you)” leads $i$ to choose $P$ than $D$, or declare indifference.
-$\hist \ileadsto \prop$ is defined similarly for other elements $\prop \in \allprops$.
+Given an argumentative path $\hist$, $\hist \ileadsto (P ≥ D)$ iff, in a situation of $i$ having been exposed, in order, to the arguments in $\hist$, letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$, or declare indifference.
+Here is a possible text presented to $i$ to ask for a choice: “Considering these arguments, would you please choose either to play $P$, or play $D$, or declare to be indifferent (in which case one will be picked randomly for you)”.
+Similarly, define $\hist \ileadsto (P > D)$ iff showing the arguments in $\hist$ to $i$ and letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$ and not $D$. 
+Define similarly $\hist \ileadsto \prop$ for $\prop \in \set{D ≥ P, D > P}$.
 
@@
 We now need an axiom that links the observable reactions of the individuals to their \ac{DJ}.
-This will be done through the notion of a decisive argument, that is, intuitively, an argument that is able to convince an individual of the acceptability of a proposition whatever the argumentative path the individual has been submitted to.
+This will be done through the notion of a decisive argument, that is, intuitively, an argument that is able to convince an individual of the acceptability of a proposition whatever the argumentative path submitted to the individual.
 For formal definitions, some supplementary notations must be defined.
@@
 \subsection{Coherence and completeness}
-A relation $n \subseteq \allprops × \allprops$ is said to be an incompatibility relation iff $\forall \hist \in \allhist, (\prop, \prop') \in n: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$.
-Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $(\prop, \prop') \in n$.
+%A relation $n \subseteq \allprops × \allprops$ is said to be an incompatibility relation iff $\forall \hist \in \allhist, (\prop, \prop') \in n: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$. 
+%Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $(\prop, \prop') \in n$.
+Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $\forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$.
+Let $\incompat \subseteq \Phi × \Phi$ denote the set of incompatible pairs of propositions.
 
@@
 	\label{th:protcoh}
-	Given any normative theory and incompatibility relation $n$,
-	$\forall i \in I, (\prop, \propbar) \in n$:
+	Given any normative theory,
+	$\forall i \in I, (\prop, \propbar) \in \incompat$:
 	\begin{equation}
@@
 \begin{proof}
-	If for some $\ar \in \allargs$, $\ar \ileadstost \prop$, then by definition of $\ileadstost$, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadsto \prop$, thus by definition of $n$, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto \propbar$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost \propbar$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto \propbar$, and thus in particular, that $(\ar', \ar) \ileadsto \propbar$.
+	If for some $\ar \in \allargs$, $\ar \ileadstost \prop$, then by definition of $\ileadstost$, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadsto \prop$, thus by definition of incompatibility, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto \propbar$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost \propbar$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto \propbar$, and thus in particular, that $(\ar', \ar) \ileadsto \propbar$.
 \end{proof}
@@
 de quelles conditions parles-tu ?}, permits in principle to know something about the \ac{DJ} of an individual.
-But this gives no concrete means to know someone’s \ac{DJ}.
-The set of finite sequence of arguments is infinite.
+But this gives no concrete means to know anyone’s \ac{DJ}.
+The set of finite sequence of arguments, thus of argumentative paths, is infinite.
 The definition of decisiveness could admittedly be modified to account for an a priori bound on the maximal length of sequences, but this would not solve the practical problem that this set would be too large to be explored thoroughly
@@
 \commentOCf{Non, thoroughfully n’existe pas, en effet}. 
-Furthermore, only some sequences of arguments can be tested for a given individual: the individual’s patience is limited.
+Furthermore, only some argumentative paths can be tested for a given individual: the individual’s patience is limited.
 A supplementary problem might happen in some situations.
-Once a sequence has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective.
+Once an argumentative path has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective.
 Let me call this possibility the hypothesis of memory.
@@
 \commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question. Je doute cependant qu'un lecteur innocent comprenne un traitre mot}
-The hypothesis of memory further reduces the possible sequences that can be tested with a given individual.
-
-Achieving knowledge of someone’s \ac{DJ} in practice is tackled by introducing empirical theories of \ac{DJ}.
+The hypothesis of memory further reduces the possible paths that can be tested with a given individual.
+
+Importantly, theories of \ac{DJ} must also be able to argue differently for different individuals.
+Even considering individuals with the same \ac{DJ}, different individuals might consider as decisive different arguments.
+Accepting non trivial propositions often requires to accept several sub-propositions, that together permit to be convinced of the acceptability of the proposition.
+Depending on which of these sub-propositions the individual already considers to be acceptable, parts of the argumentation can be omitted, and, perhaps, must be omitted: an overly long argument, stating many things that the listener already knows, has fewer chance to convince the listener than a short argument that goes straight to the point about which the listener doubts.
+%Mathematicians do not write their proofs starting from the axioms of set theory: they use results that they assume the reader already is aware of, and are ready (in principle) to supply the proofs of these intermediate results if a reader has doubt about some of them.
+In other words, what is needed for a theory of \ac{DJ} is not just a capacity to produce a unique decisive argument, with the claim that this argument will convince individuals in $I$, but rather a capacity to produce dynamically arguments that depend on which counter-arguments the individual finds appealing, with a claim that this dynamic argumentation strategy will succeed in convincing individuals in $I$.
+
+Achieving practical knowledge of \acp{DJ} is tackled by introducing descriptive theories of \ac{DJ}.
+They are defined in \cref{sec:descrdef}.
 An empirical theory for a given normative theory defines a subset of propositions of the agenda, that it claims are contained in the \acp{DJ} of individuals concerned by the normative theory.
@@
 Second, granted normative adequacy, if indeed a theory argues convincingly, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}.
-These two claims are laid out formally in \cref{th:svalid}.
-
-A second goal of this section is to prove that when two theories disagree about incompatible propositions, one of the theories at least must fail some given sequence of empirical tests, which the proof describes.
-Importantly, these tests can be performed on a single individual and are robust against the hypothesis of memory.
+These two claims are laid out formally in \cref{sec:validity}.
+
+This permits to ensure that, under Normative adequacy, Validity is an empirical property.
+But it does not give a concrete way of arbitrating between conflicting theories.
+A supplementary important result, described in \cref{sec:compare}, is that when two theories disagree about incompatible propositions, one of the theories at least must fail some given sequence of empirical tests, which the proof describes.
+These tests can be performed on a single individual and are robust against the hypothesis of memory.
 
 \subsection{Definition}
+\label{sec:descrdef}
 In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
@@
 à quoi est-ce que cela sert ?}
-These constraints guarantee that every anticipated attack has exactly one fragment defending against it, thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton.
+These constraints guarantee that every anticipated attack has exactly one fragment defending against it, thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$, $\dbeatsinv(\ar_1)$ is a singleton.
 Note that $\dbeats$ need not be a bijection as it is generally not a function (it is not restrictive to suppose it left-total, but it generally is not right-unique). 
@@
 
-\subsection{Validity}
+\subsection{Validity and falsification sequences}
 \label{sec:validity}
+\begin{definition}[Validity]
+	An empirical theory is \emph{valid} iff $\forall i \in I, \prop \in \gpropse: \prop \in \iprops$.
+\end{definition}
+
 Given $\args \subseteq \allargs$ and $\hist \in \allhist$,
-the set $\args \cap \range(\hist)$ denotes the arguments that are both in $\args$ and contained in the sequence $\hist$.
-
-Define a falsification sequence for $i, \ar_0, \phi$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $\hist^1, \hist^3, …, \hist^{N + 1}$, for some $N \in 2\N$, such that it presents successive challenges, which means the following.
+recall that the set $\args \cap \range(\hist)$ denotes the arguments that are both in $\args$ and contained in the sequence $\hist$.
+
+Define a falsification sequence for $(i, \ar_0, \phi)$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $\hist^1, \hist^3, …, \hist^{N + 1}$, for some $N \in 2\N$, such that it presents successive challenges, which means the following.
 Given $k \in 2\N \suchthat k ≤ N$, $\ar_k \in \allargs$ and $\hist^{k + 1} \in \allhist$, 
@@
 
-\begin{definition}[Validity]
-	An empirical theory is \emph{valid} iff $\forall i \in I, \prop \in \gpropse: \prop \in \iprops$.
-\end{definition}
+A descriptive theory has no falsification sequence iff $\forall (i, \ar_0, \phi)$, no finite sequence of paths present successive challenges.
 
@@
 \subsection{Effectively comparing models}
+\label{sec:compare}
 Given $\prop \in \allprops$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory with an incompatibility relation $n$, say that they disagree about $(\prop, \propbar) \in n$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$.

### 2020-11-12 simple.tex
No more parametric incompatibility relation

@@
 \subsection{Coherence and completeness}
-%A relation $n \subseteq \allprops × \allprops$ is said to be an incompatibility relation iff $\forall \hist \in \allhist, (\prop, \prop') \in n: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$. 
-%Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $(\prop, \prop') \in n$.
+\label{sec:coh}
 Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $\forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$.
@@
 \label{sec:compare}
-Given $\prop \in \allprops$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory with an incompatibility relation $n$, say that they disagree about $(\prop, \propbar) \in n$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$.
-Say that they are incompatible iff there is at least one pair $(\prop, \propbar) \in \allprops$ that they disagree about.
+Recall from \cref{sec:coh} that $\incompat = \set{(\prop, \prop') \suchthat \forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'}$ denotes the set of pairs of incompatible propositions.
+Given two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $(\prop, \propbar) \in \incompat$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$.
+Say that the theories are incompatible iff there is at least one pair $(\prop, \propbar) \in \incompat$ that they disagree about.
 
@@
 	\label{proc}
-	Pick any $\prop \in \allprops$ about which $\alpha$ and $\beta$ disagree.
+	Pick any $\prop, \propbar \in \incompat$ about which $\alpha$ and $\beta$ disagree.
 

### 2020-11-12 simple.tex
Impr expl completeness

@@
 \begin{example}[Two lotteries: completeness]
-	Applying these definitions and results to \cref{ex:twolott}, we can define a negation operator such that $¬(P ≥ D) = D > P$ and $¬(D ≥ P) = P > D$.
+	Applying these definitions and results to \cref{ex:twolott}, we see that $\set{(P ≥ D, D > P), (D ≥ P, P > D)} \subseteq \incompat$, and we can define a negation operator such that $¬(P ≥ D) = D > P$ and $¬(D ≥ P) = P > D$.
 We see that $P ≥ D$ is $i$-decidable iff $D > P$ is $i$-decidable iff there exists a decisive argument $\ar \in \allargs$ for $P ≥ D$ or for $D > P$.
@@
 	Theory completeness holds iff there exists a decisive argument for $P ≥ D$ or for $D > P$ and a decisive argument for $D ≥ P$ or for $P > D$.
-In such a case, and assuming normative adequacy holds, Deliberation completeness holds as well, thus for every proposition, either it or its contrary is in $i$’s \ac{DJ}.
+In such a case, and assuming Normative Adequacy holds, Deliberation completeness holds as well, thus for every $i$ and every proposition, either it or its contrary is in $i$’s \ac{DJ}.
 \end{example}
@@
 \begin{example}[Discussion about completeness]
-	It should be remarked that there is no logical contradiction in assuming that $i$ could, for example, deliberately judge that $P ≥ D$, but have no deliberated judgment about whether $D ≥ P$ or rather $P > D$ holds, thus, whether these two lotteries have equal worth in terms of bidding or whether $P$ is worth strictly more.
+	It should be remarked that there is no logical contradiction in assuming that $i$ could, for example, deliberately judge that $P ≥ D$, but have no deliberated judgment about whether $D ≥ P$ or rather $P > D$ holds, thus, whether these two lotteries have equal worth or whether $P$ is strictly more valuable.
 In such a case, Deliberation completeness does not hold.
-	More pragmatically, there may be no argument in $\allargs$ strong enough to convince $i$ to pick $P$ rather than $D$, but no argument strong enough to convince $i$ that $P$ and $D$ are equally preferable.
-For a formal example where this would happen, assume $\ileadsto$ is such that it $i$ is lead to choose only $P$ when $\ar_0$ comes last in the argumentative path, but $i$ is lead to be indifferent when $\ar_0$ is before last in the argumentative path.
+	More pragmatically, there may be a decisive argument in $\allargs$ for $P ≥ D$, but no argument in $\allargs$ strong enough to convince $i$ to pick $P$ rather than $D$ against all counter-arguments, and no argument strong enough to convince $i$ that $P$ and $D$ are equally preferable.
+For a formal example where this would happen, assume $\ileadsto$ is such that $i$ is lead to choose only $P$ for some of the paths including $\ar_0$ towards their end, but to be indifferent for the other ones.
+Thus: $\forall \hist \in \allhist \suchthat \ar_0 \in \histend: \hist \ileadsto P ≥ D$, $\exists \hist \suchthat \ar_0 \in \histend \land \hist \ileadsto P > D$ and $\exists \hist \suchthat \ar_0 \in \histend \land \hist \ileadsto D ≥ P$.
 \end{example}

### 2020-11-12 simple.tex
Better explan incompl

@@
 Not mandating Theory completeness is a first important element to allow hope that effective theories of \ac{DJ} can be built. 
-
-That the \ac{DJ} of an individual exists independently of any theory of decision making might be considered a strong assumption, by analogy to the case of shallow preferences: psychologists have shown that shallow preferences often depend on a priori irrelevant features pertaining to the description of the decision problem or the context of interrogation.
+To understand why, an analogy with the case of shallow preferences may be useful.
+Psychologists have shown that shallow preferences often depend on a priori irrelevant features pertaining to the description of the decision problem or the context of interrogation.
 Preferences are often said to be constructed, thus, to not exist independently of the framing and context of study.
-
-With no intent of reducing the importance of these findings, it is important to qualify such statements.
-In supplement to them being not necessarily applicable to reflective preferences, the findings of psychologists do not, evidently, show that all preference statements are labile.
+But, with no intent of reducing the importance of these findings, it is important to qualify such statements. 
+The findings of psychologists do not, evidently, show that all preference statements are labile.
 As \citet[p.\ xvi]{lichtenstein_construction_2006} write, “To be sure, there are limits to the process of construction.
@@
 \commentYM{ce § et le précédent me semble mériter plus que le reste une réécriture. Par ailleurs, je ne vois pas à quoi ils servent dans cette sous-section}
+This observation justifies propositions that obtain only partial shallow preference models: a shallow statement preference would be considered to exist only when it stays intact under all framings considered relevant.
+The proposal of \citet{bernheim_beyond_2009} may be understood under that light.
 
@@
 \TODO{Check Mandler.}
+This observation also offers a way of reconciling the remark of \citet{roy_comparison_1995} cited in \cref{sec:informal} and the objectivity of the conclusions of a decision theoretic approach: if, for some propositions, both the proposition and its contrary proposition can be held, with no argument being strong enough to impose one of them, let neither these propositions nor their contrary be part of $i$’s \ac{DJ}; and let the theorist focus on the subset of propositions for which argumentative stability can be found.
+
 The definitions of the theories presented here accordingly tolerate both theory incompleteness, which permits the theory to stay silent on some of the propositions in the agenda, and, more fundamentally, deliberation incompleteness, which permits to tolerate that for some propositions, neither it nor its negation figure in someone’s \ac{DJ}.

### 2020-11-12 simple.tex
Mostly: hypo of memory exemplified and discussed

@@
 The approach adopted in this article to capture \acp{DJ} is to declare that the winning theory (if any) is the one that exhibit arguments able to systematically convince individuals that their proposed choice is to be adopted.
-	The satisfycing theory could argue as follows: “$\alt_1$ is better than $\alt_2$, because it has a satisfactory price (lower than $t_1$, an acceptable price) and a satisfactory speed (higher than $t_2$, thus an acceptable performance); whereas $\alt_2$ is not satisfactory on the speed criterion”.
+	The satisfycing theory could argue as follows: “$\alt_1$ is better than $\alt_2$, because it has a satisfactory price (lower than $t_1$, an acceptable price) and a satisfactory speed (higher than $t_2$, an acceptable performance); whereas $\alt_2$ is not satisfactory on the speed criterion”.
 	The additive theory could use the following argument: “$\alt_2$ is better than $\alt_1$, because $\alt_2$ is cheaper than $\alt_1$, and this more than compensates for its weaker performance in terms of speed”.
 
-	Determining which theory is right requires to present both arguments to $i$, then let her choose one alternative in $\alts$.
+	The basic intuition on which this article is based is that determining which theory is right requires to present both arguments to $i$, then let her choose one alternative in $\alts$, to see which argument she finds more convincing.
 \end{example}
@@
 \begin{example}[Discussion about completeness]
+\label{ex:incompl}
 	It should be remarked that there is no logical contradiction in assuming that $i$ could, for example, deliberately judge that $P ≥ D$, but have no deliberated judgment about whether $D ≥ P$ or rather $P > D$ holds, thus, whether these two lotteries have equal worth or whether $P$ is strictly more valuable.
@@
 Furthermore, only some argumentative paths can be tested for a given individual: the individual’s patience is limited.
+
 A supplementary problem might happen in some situations.
 Once an argumentative path has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective.
-Let me call this possibility the hypothesis of memory.
+Let me call this possibility the hypothesis of persistence, and the converse hypothesis, the hypothesis of immediacy.
+Under the hypothesis of persistence, it is impossible to test twice the same path.
+Tests of the stability of the opinion of $i$ towards a given set of arguments can still be performed, as the next example indicates.
 The converse hypothesis amounts to postulating that the individual forgets after some time and use an observation protocol that separates the tests in time sufficiently.
@@
 The hypothesis of memory further reduces the possible paths that can be tested with a given individual.
+An illustration of some consequences of these possibilities on our running example may be useful. 
+\begin{example}[Hypothesis of memory]
+	 The definition of $\ileadsto$ as given so far implicitly assumes that a given path can be tested at most once with a given individual, as it does not indicate what to conclude when a path $\hist$ leads $i$ to adopt a proposition $\prop$ only some of the time.
+This is justified under the hypothesis of memory.
+	 Recall that in \cref{ex:incompl}, $\hist \ileadsto P ≥ D$ and $\hist' \ileadsto D > P$ for some $\hist, \hist' \in \allhist$.
+If we further assume that $\range(\hist) = \range(\hist')$, in other words, that these two paths use the same arguments, this illustrates the remark that instability of $i$ towards some set of argument can be observed even under the hypothesis of memory.
+Consider $\hist = \left<\ar_0, \ar_1\right>$ and $\alpha' = \left<\ar_0, \ar_1, \ar_0\right>$ as an example.
+As $\hist'$ is a sequence that starts with $\hist$, it is possible to test these two paths on $i$, even under the hypothesis of memory.
+
+	If, on the contrary, it is considered that the individual forgets over time, we must define $\ileadsto$ differently.
+Define $T$ a series of time steps, and given $t \in T$, define $\hist \ileadsto^t \prop$ as the observation of the adoption of $\prop$ by $i$ when having been presented the arguments in $\hist$ at time $t$.
+Define then $\hist \ileadsto \prop$ iff $\forall t \in T: \hist \ileadsto^t \prop$.
+Under the hypothesis of immediacy, it could be that $\exists \hist \suchthat \hist \nileadsto P ≥ D \land \hist \nileadsto D > P$.
+\end{example}
 
@@
 
-Such theories satisfy the two properties that are mandatory to achieve what has been announced, namely, to obtain theories of \ac{DJ} whose power rest on a weak normative axiom and on empirically falsifiable claims.
-First, the claim of the theory that it argues convincingly holds if and only if no falsification sequence exist (falsification sequences are defined formally here below).
-Second, granted normative adequacy, if indeed a theory argues convincingly, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}.
-These two claims are laid out formally in \cref{sec:validity}.
-
-This permits to ensure that, under Normative adequacy, Validity is an empirical property.
+Such theories achieve what has been announced, namely, their conclusions rest solely on a weak normative axiom and on empirically falsifiable claims. 
+Granted normative adequacy, if no falsification sequence exist for a given theory of \ac{DJ}, then it is valid, meaning that the propositions that it claims are \acp{DJ} are indeed \acp{DJ}.
+\Cref{sec:validity} defines formally the notion of falsification sequence and proves this central claim.
+The practical meaningfulness of this result is not affected by the hypothesis of memory, under condition that the set $I$ be large enough: we can always then perform falsification tests on different individuals for each path that has to be tested, so that memory of individuals does not matter.
+Exploring settings where $I$ is too small to apply this strategy is left aside in this article.
+
+This result permits to ensure that, under Normative adequacy, Validity is an empirical property.
 But it does not give a concrete way of arbitrating between conflicting theories.
 A supplementary important result, described in \cref{sec:compare}, is that when two theories disagree about incompatible propositions, one of the theories at least must fail some given sequence of empirical tests, which the proof describes.
-These tests can be performed on a single individual and are robust against the hypothesis of memory.
+These tests can all be performed on a single individual and are robust against the hypothesis of memory, which suggest that arbitration between theories could be performed reasonably easily.
 

### 2020-11-12 simple.tex
Got rid of l for length

@@
 Throughout the article, $\N$ includes zero. %and $\N^* = \N \setminus \set{0}$. 
+A generic element of $\allhist$ is denoted by $\hist$ and called an argumentative path, or simply a path when this raises no ambiguity. Its length is denoted by $\card{\hist} \in \N$.
 Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$.
-Thus, given an argumentative path $\alpha$ of length $l \in \N$, $\forall k \in \intvl{1, l}$, $\alpha_k \in A$, and $\alpha = \emptyset ⇔ l = 0$.
+Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}$, $\hist_k \in A$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
 %Note that $\intvl{1, 0} = \emptyset$, and given any set $S$, the notation $S^\emptyset$ represents the empty set.
-A generic element of $\allhist$ is denoted by $\hist$ and called an argumentative path, or simply a path when this raises no ambiguity.
 
@@
 
-Given $\hist \in \allhist$, if $l$ denotes its length, $\range(\hist) = \hist(\intvl{1, l})$ denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
-Let $\histend = \hist(\intvl{\max(1, l-1), l})$ denote the set containing the last two arguments of the sequence $\hist$ if the sequence has at least two elements; the unique argument of the sequence if it has exactly one element; and the empty set if it is empty.
+Given $\hist \in \allhist$, $\range(\hist) = \hist(\intvl{1, \card{\hist}})$ denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
+Let $\histend = \hist(\intvl{\max(1, \card{\hist} - 1), \card{\hist}})$ denote the set containing the last two arguments of the sequence $\hist$ if the sequence has at least two elements; the unique argument of the sequence if it has exactly one element; and the empty set if it is empty.
 
@@
 
-A path $\histp$ starts with a path $\hist$ of length $l$ iff $\histp$ has length at least $l$ and $\forall k \in \intvl{1, l}: \histp_k = \hist_k$.
+A path $\histp$ starts with a path $\hist$ iff $\card{\histp} ≥ \card{\hist}$ and $\forall k \in \intvl{1, \card{\hist}}: \histp_k = \hist_k$.
 An increasing sequence of paths is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N$, of paths, 

### 2020-11-12 simple.tex
No model should be named \alpha!

@@
 	\label{th:proc}
-	Given two incompatible empirical theories for a given normative theory, $\alpha = (\gleadsto[\alpha], \gbeats[\alpha], \alldargs_\alpha, \dbeats[\alpha], +_\alpha)$ and $\beta = (\gleadsto[\beta], \gbeats[\beta], \alldargs_\beta, \dbeats[\beta], +_\beta)$ and given any $i \in I$, there exists a procedure that falsifies one of these theories, queries only $i$, and queries $i$ only about some increasing sequence of paths.
+	Given two incompatible empirical theories for a given normative theory, $\gamma = (\gleadsto[\gamma], \gbeats[\gamma], \alldargs_\gamma, \dbeats[\gamma], +_\gamma)$ and $\delta = (\gleadsto[\delta], \gbeats[\delta], \alldargs_\delta, \dbeats[\delta], +_\delta)$ and given any $i \in I$, there exists a procedure that falsifies one of these theories, queries only $i$, and queries $i$ only about some increasing sequence of paths.
 \end{theorem}
@@
 To do this, the notion of challenge must be defined and a few simple lemmas are required.
-
-Given $\prop \in \allprops$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $\prop$ iff $\hist \nileadstost \prop$ and $\ar_\gamma \in \histend$.
-Given $\prop \in \allprops, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \prop)$ or $(\hist, \ar_\delta)$ challenges $(\delta, \propbar)$.
+In order to leave the letters $\gamma$ and $\delta$ unbounded for clearer application of the intermediate results to the theorem to be proven, let $\mu$ and $\nu$ designate any two descriptive theories for a given normative theory of \ac{DJ}.
+Given $\prop \in \allprops$, $\hist \in \allhist$ and $\ar_\mu \in \gargsmu$, say that $(\hist, \ar_\mu)$ challenges $\prop$ iff $\hist \nileadsto \prop$ and $\ar_\mu \in \histend$.
+Given $\prop \in \allprops, \ar_\mu \in \gargsmu, \ar_\nu \in \gargsnu$, say that $(\hist, \ar_\mu, \ar_\nu)$ is a $\prop/\propbar$-challenge iff $(\hist, \ar_\mu)$ challenges $(\mu, \prop)$ or $(\hist, \ar_\nu)$ challenges $(\nu, \propbar)$.
 
@@
 	\label{th:endchal}
-	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$, $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge.
+	Given $\ar_\mu \in \gargs$, $\ar_\nu \in \gargsnu$ and $\hist \in \allhist$ such that $\set{\ar_\mu, \ar_\nu} \subseteq \histend$, $(\hist, \ar_\mu, \ar_\nu)$ is a $\prop/\propbar$-challenge.
 \end{lemma}
 \begin{proof}
-	Either $\hist \nileadstost \prop$, and $(\hist, \ar_\gamma)$ challenges $\prop$, or $\hist \ileadstost \prop$, hence, by \cref{th:protcoh}, $\hist \nileadstost \propbar$, and $(\hist, \ar_\delta)$ challenges $\propbar$.
+	Either $\hist \nileadsto \prop$, and $(\hist, \ar_\mu)$ challenges $\prop$, or $\hist \ileadsto \prop$, hence, by incompatibility of $\prop$ and $\propbar$, $\hist \nileadsto \propbar$, and $(\hist, \ar_\nu)$ challenges $\propbar$.
 \end{proof}
@@
 	\label{th:nextchal}
-	Given $(\hist, \ar_\gamma)$ challenging $\prop$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\prop))$, and $\ar_\delta \in \gargsdelta$: either $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $\prop/\propbar$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\prop))$.
+	Given $(\hist, \ar_\mu)$ challenging $\prop$, with $\ar_\mu \in \gargsmu \cap (\dfp)^k(\gleadstoinv(\prop))$, and $\ar_\nu \in \gargsnu$: either $(i, \prop, \hist, \ar_\mu)$ falsifies $\mu$, or there exists a $\prop/\propbar$-challenge $(\histp, \ar'_\mu, \ar_\nu)$, with $\ar'_\mu \in \gargsmu \cap (\dfp)^{k + 1}(\gleadstoinv(\prop))$.
 \end{lemma}
 \begin{proof}
-	If $\ar_\gamma$ does not $i$-defend $\prop$, then $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, which ends the proof. 
-	Thus, assume that $\ar_\gamma$ $i$-defends $\prop$.
-
-	\Cref{th:produce} applies and yields $\ar'_\gamma = \ar_\gamma + \dbeatsinv(\gbeatsinv(\ar_\gamma)) \in \gargs \cap \dfp(\ar_\gamma)$, thus $\ar'_\gamma \in (\dfp)^{(k + 1)}(\gleadstoinv(\prop))$. 
-	Now, define $\histpp = (\hist, \ar'_\gamma)$ and test whether $\histpp \nileadstost \prop$.
-
-	If $\histpp \nileadstost \prop$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\gamma, \ar_\delta)$ challenges $\prop$, which concludes the proof. 
-	Thus, assume that $\histpp \ileadstost \prop$.
-
-	Let us now define $\histp$ such that $\set{\ar'_\gamma, \ar_\delta} \subseteq \histpend$, so that \cref{th:endchal} applies on $(\histp, \ar'_\gamma, \ar_\delta)$, which will conclude the proof.
-
-	If $\ar_\delta \in \histppend$, this is done by defining $\histp = \histpp$. Otherwise, define $\histp = (\histpp, \ar_\delta)$ and test whether $\histp \nileadstost \prop$. 
+	If $\ar_\mu$ does not $i$-defend $\prop$, then $(i, \prop, \hist, \ar_\mu)$ falsifies $\mu$, which ends the proof. 
+	Thus, assume that $\ar_\mu$ $i$-defends $\prop$.
+
+	\Cref{th:produce} applies and yields $\ar'_\mu = \ar_\mu + \dbeatsinv(\gbeatsinv(\ar_\mu)) \in \gargsmu \cap \dfp(\ar_\mu)$, thus $\ar'_\mu \in (\dfp)^{(k + 1)}(\gleadstoinv(\prop))$. 
+	Now, define $\histpp = (\hist, \ar'_\mu)$ and test whether $\histpp \nileadstost \prop$.
+
+	If $\histpp \nileadsto \prop$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\mu, \ar_\nu)$ challenges $\prop$, which concludes the proof. 
+	Thus, assume that $\histpp \ileadsto \prop$.
+
+	Let us now define $\histp$ such that $\set{\ar'_\mu, \ar_\nu} \subseteq \histpend$, so that \cref{th:endchal} applies on $(\histp, \ar'_\mu, \ar_\nu)$, which will conclude the proof.
+
+	If $\ar_\nu \in \histppend$, this is done by defining $\histp = \histpp$. Otherwise, define $\histp = (\histpp, \ar_\nu)$ and test whether $\histp \nileadsto \prop$. 
 \end{proof}
@@
 	\label{proc}
-	Pick any $\prop, \propbar \in \incompat$ about which $\alpha$ and $\beta$ disagree.
-
-	Given $k_\alpha, k_\beta \in \N, \hist \in \allhist, \ar_\alpha \in \gargsalpha, \ar_\beta \in \gargsbeta$, 
+	Pick any $\prop, \propbar \in \incompat$ about which $\gamma$ and $\delta$ disagree.
+
+	Given $k_\gamma, k_\delta \in \N, \hist \in \allhist, \ar_\gamma \in \gargsgamma, \ar_\delta \in \gargsdelta$, 
 	say that 
-	$(\hist, \ar_\alpha, \ar_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta)$ iff 
-	$(\hist, \ar_\alpha, \ar_\beta)$ is a $\prop/\propbar$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\prop))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](\propbar))$.
-
-	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\beta] \propbar$.
-Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](\propbar))$.
-Test whether $(\ar_{-1}) \nileadstost \prop$.
-If so, $(i, \prop, (\ar_{-1}), \ar_{-1})$ falsifies $\beta$, which ends the procedure.
-	Thus, assume that $(\ar_{-1}) \ileadstost \prop$.
-
-	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[\alpha] \prop$.
-Observe that $\ar_0 \in \gargsalpha \cap (\dfp[\alpha])^0(\gleadstoinv[\alpha](\prop))$.
-Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \prop$.
+	$(\hist, \ar_\gamma, \ar_\delta)$ is a challenge of complexity $(k_\gamma, k_\delta)$ iff 
+	$(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge, $\ar_\gamma \in (\dfp[\gamma])^{k_\gamma}(\gleadstoinv[\gamma](\prop))$, and $\ar_\delta \in (\dfp[\delta])^{k_\delta}(\gleadstoinv[\delta](\propbar))$.
+
+	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\delta] \propbar$.
+Observe that $\ar_{-1} \in \gargsdelta \cap (\dfp[\delta])^0(\gleadstoinv[\delta](\propbar))$.
+Test whether $(\ar_{-1}) \nileadsto \prop$.
+If so, $(i, \prop, (\ar_{-1}), \ar_{-1})$ falsifies $\delta$, which ends the procedure.
+	Thus, assume that $(\ar_{-1}) \ileadsto \prop$.
+
+	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[\gamma] \prop$.
+Observe that $\ar_0 \in \gargsgamma \cap (\dfp[\gamma])^0(\gleadstoinv[\gamma](\prop))$.
+Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadsto \prop$.
 By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\prop/\propbar$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
 
-	Suffices now to apply \cref{th:nextchal} repetitively, until finding a falsification instance of $\alpha$ or $\beta$.
-This is because, given a challenge $(\hist, \ar_\alpha, \ar_\beta)$ of complexity $(k_\alpha, k_\beta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity.
-Indeed, if $(\hist, \ar_\alpha)$ challenges $\prop$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
-And if $(\hist, \ar_\beta)$ challenges $\propbar$, apply \cref{th:nextchal} with $\propbar$ for $\prop$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.
-
-	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\prop)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](\propbar)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
+	Suffices now to apply \cref{th:nextchal} repetitively, until finding a falsification instance of $\gamma$ or $\delta$.
+This is because, given a challenge $(\hist, \ar_\gamma, \ar_\delta)$ of complexity $(k_\gamma, k_\delta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity.
+Indeed, if $(\hist, \ar_\gamma)$ challenges $\prop$, apply \cref{th:nextchal} with $\gamma$ for $\mu$, $\delta$ for $\nu$, and obtain either that $\hist$ falsifies $\gamma$, or a new tuple $(\histp, \ar'_\gamma, \ar_\delta)$ that is a challenge of complexity $(k_\gamma + 1, k_\delta)$.
+And if $(\hist, \ar_\delta)$ challenges $\propbar$, apply \cref{th:nextchal} with $\propbar$ for $\prop$, $\delta$ for $\mu$, $\gamma$ for $\nu$, and obtain either that $\hist$ falsifies $\delta$, or a new tuple $(\histp, \ar'_\delta, \ar_\gamma)$ such that $(\histp, \ar_\gamma, \ar'_\delta)$ is a challenge of complexity $(k_\gamma, k_\delta + 1)$.
+
+	Given that $\exists K_\gamma \suchthat (\dfp[\gamma])^{K_\gamma}(\gleadstoinv[\gamma](\prop)) = \emptyset$ and $\exists K_\delta \suchthat (\dfp[\delta])^{K_\delta}(\gleadstoinv[\delta](\propbar)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\gamma$ or $\delta$.
 \end{procedure}

### 2020-11-14 simple.tex
Strong simplification started with only one symbol for the defense strategy

@@
 In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
-A descriptive tuple for a normative theory of \ac{DJ} is defined as a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$, where ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation; ${\gbeats} \subseteq \allargs × \allargs$ is an anticipated attacks relation; $\alldargs$ is a primitive set of argument fragments; ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is a defense relation; and $+$ combines arguments to coalitions of fragments in order to form new arguments.
-A descriptive theory for a normative theory of \ac{DJ} is a descriptive tuple that has a bounded depth.
+A descriptive theory for a normative theory of \ac{DJ} is defined as a tuple $(\gleadsto, \dg)$, where ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation and $\dg$ is a defense relation; satisfying bounded depth.
 These concepts are now defined formally.
@@
 
-An anticipated attacks relation ${\gbeats} \subseteq \allargs × \allargs$ is an irreflexive binary relation on the arguments.
-An argument $\ar_1$ is said to be an anticipated attack against an argument $\ar_0$ iff $\ar_1 \gbeats \ar_0$.
-Given  an argument $\ar_0$, $\gbeatsinv(\ar_0) = \set{\ar_1 \in \allargs \suchthat \ar_1 \gbeats \ar_0}$ denotes the set of anticipated attacks against $\ar_0$; and $\gbeatsinv(\allargs) = \set{\ar_1 \in \allargs \suchthat \exists \ar_0 \in \allargs \suchthat \ar_1 \gbeats \ar_0}$ denotes the set of arguments that are anticipated attacks against at least one argument.
-
-A defense relation ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is an injective (left-unique) and surjective (right-total) binary relation over $\alldargs × \gbeatsinv(\allargs)$.
-\commentYM{le fait qu'elle soit surjective et injective est une exigence que tu poses dans la définiton ?
-pourquoi ?
-à quoi est-ce que cela sert ?}
-These constraints guarantee that every anticipated attack has exactly one fragment defending against it, thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$, $\dbeatsinv(\ar_1)$ is a singleton.
-Note that $\dbeats$ need not be a bijection as it is generally not a function (it is not restrictive to suppose it left-total, but it generally is not right-unique). 
-Given $\ar_1 \in \gbeatsinv(\allargs)$, define $\dbeatsinv(\ar_1)$ as the fragment defending against the anticipated attack $\ar_1$.
-\commentYM{dans toute cette sous-section la lecture est rendue très difficile par ce genre de formulation qui assigne une intentionnalité à la théorie.
-Je ne comprends pas le sens métaphorique de ces phrase, donc je ne les comprends pas}
-
-A fragment is said to defend an argument iff it defends against an anticipated attack against that argument.
-\commentYM{"it is used" par qui, comment ?
-De quoi tu parles là ?
-Des stratégies argumentatives que contient la "théorie empirique" ?}
-Formally, 
-given any set $S$, define $\powerset{S}$ as the set of subsets of $S$ and $\powersetz{S}$ as the set of subsets of $S$ without the empty set.
-Define $\df: \allargs → \powerset{\alldargs}$ as follows:
-given $\ar_0 \in \allargs$ and $\ard \in \dargs$, $\ard \in \df(\ar_0)$ iff $\exists \ar_1 \in \allargs \suchthat \ard \dbeats \ar_1 \gbeats \ar_0$.
-In other words, $\df = \dbeatsinv \circ \gbeatsinv$.
-Given $\ar \in \allargs$, $\df(\ar)$ denotes \emph{all fragments defending $\ar$}.
-
-A \emph{coalition of fragments defending $\ar$} is any non-empty subset of $\df(\ar)$.
-Such a coalition can be combined with the argument it defends to form a new argument.
-An empirical theory defines, to that effect, a function $+: \allargs × \powersetz{\alldargs} → \allargs$.
-Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \alldargs$, the notation $\ar + \dargs$ stands for $+(\ar, \dargs)$.
-(The function $+$ need not be defined on so large a domain, because an argument is only ever added to its own defenders, but this definition is adopted here for simplicity; \cref{sec:append} refines this requirement.)
-
-This finally permits to define the defenders of an argument: they are all the arguments that can be formed by adding the argument to a coalition of fragments that defends it.
-Given any $\ar \in \allargs$, define $\dfp(\ar) \subseteq \allargs$, the \emph{defenders of $\ar$}, as $\dfp(\ar) = \set{\ar + \dargs \suchthat \emptyset ≠ \dargs \subseteq \df(\ar)}$.
-
-This mechanism permits to define defenders of defenders of an argument, $\dfp(\dfp(\ar))$, defenders of defenders of defenders of an argument, … 
+A defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ is a right-unique relation, thus given any $\ar \in \allargs, \hist \in \allhist$, $\dg(\ar, \hist)$ is empty or is a singleton.
+%, and must satisfy $\ar \notin \histend ⇒ \dg(\ar, \hist) = \emptyset$.
+As is usual for right-unique relations, I write $\dg(\ar_0, \hist) = \ar_1$ instead of $\dg(\ar_0, \hist) = \set{\ar_1}$.
+Say that $\ar_1$ defends $\ar_0$ iff $\exists \hist \suchthat \dg(\ar_0, \hist) = \ar_1$.
+Define $\dg(\ar) = \dfp(\ar) = \dg(\ar, \allhist) = \set{\dg(\ar, \hist) \suchthat \hist \in \allhist} \subseteq \allargs$ as all the defenders of $\ar$.
+The relation $\dg$ defines the argumentation strategy of the theory.
+Informally speaking, its role is to adapt the arguments the theory produces to the reactions of the individual it is trying to convince.
+Assuming the theory has played an argument $\ar_0$ and a path $\hist$ challenges some of the conclusions this argument supports (as judged by the individual), $\dg(\ar_0, \hist)$ is the argument that the theory plays as a counter-argument to the path $\hist$.
+%The condition that when $\dg(\ar_0, \hist)$, $\ar_0 \in \histend$ is imposed for simplicity: as will appear, an argument $\ar_0$ needs defense only when it is challenged by some path $\hist \suchthat \ar_0 \in \histend$, thus, letting $\dg$ define counter-arguments to paths not satisfying this condition would be of no use.
+
+This mechanism permits to define defenders of defenders of an argument, $\dg(\dg(\ar))$, defenders of defenders of defenders of an argument, … 
 For the results to be presented here to hold, an empirical theory must be a priori restricted in the maximal “depth” of its argumentation strategy, in the following sense. 
@@
 Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
-A tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ has a bounded depth iff
-$\exists k \in \N \suchthat (\dfp)^k(\gleadstoinv(\allprops)) = \emptyset$.
-
-The bounded depth constraint does not imply finiteness of the relations $\gbeats$ or $\dbeats$, as \cref{th:infinite} shows.
+The bounded depth condition on a descriptive theory imposes that
+$\exists k \in \N \suchthat (\dg)^k(\gleadstoinv(\allprops)) = \emptyset$.
+The smallest such $k$ is called the depth of the theory.
+
+Here is an example of a theory that does not use an argumentation strategy, but simply plays an argument that it claims is decisive for everybody.
+\begin{example}[Constant argumentation]
+	Given the normative theory of \cref{ex:twolott}, define ${\gleadsto} = \set{(\ar_0, D > P)}$ and $\dg = \emptyset$. This defines a descriptive theory of depth $1$ for that normative theory.
+\end{example}
+
+\begin{example}[A theory for $P$]
+	\label{ex:twolottstrings}
+	Define a normative theory as in \cref{ex:twolott}, with an extended set of arguments: define $\allargs$ as the set of all strings.
+(This correspondingly changes $\allhist$ and thus $\ileadsto$, which must be extended to its new domain.) Define $\ar_0$ as in \cref{ex:twolott}.
+	Define $\ar_\text{for$P$}$ as the text “We recommend to adopt $P$: it has a much higher probability of winning.” 
+	Define ${\gleadsto} = \set{(\ar_\text{for$P$}, P > D)}$.
+	In order to define a counter-argument to $\ar_0$, given a real number $r \in \R$, define $\ar^r_\text{non-linear}$ as the text “It is absurd to reason in terms of expected gain.
+For example, consider a choice between winning $r$ dollars with probability $0.8$ and winning $2r$ dollars with probability $0.4$.
+They have the same expected gain, but the first one is clearly preferrable”.
+(The value of $r$ and $2r$ is to be used in the relevant places in  the text.)
+	Define $\dg = \set{(\ar_\text{for$P$}, \hist, \ar^{10^6}_\text{non-linear}) \suchthat \hist \in \allhist \land \ar_0 \in \hist}$.
+This strategy anticipates a possible attack using $\ar_0$ against $\ar_\text{for$P$}$, and prepares $\ar^{10^6}_\text{non-linear}$ as a counter-argument.
+	This defines a descriptive theory of depth $2$.
+\end{example}
+
+The following less trivial example of a descriptive theory illustrates a theory that claims to be able to answer an infinite number of arguments.
+This also shows that the bounded depth constraint does not imply finiteness of the relation $\dg$.
+\begin{example}[Infinite $\dg$]
+	\label{ex:infinite}
+	Define a normative theory and the arguments $\ar_0$ and $\ar^r_\text{non-linear}$ for any $r \in \R$ as in \cref{ex:twolottstrings}.
+	Define ${\gleadsto} = \set{(\ar_0, D > P)}$.
+	Define $\ar_\text{linear}$ as the text “We agree that when the money amounts involved are large and the game is not repeated, there is no good reason to consider only expected gains when choosing a lottery.
+But in our case, the money amounts are small and the game is repeated.
+Therefore, expected gain is the right indicator to consider for a systematic and sound decision strategy.”
+	Define $\dg = \set{(\ar_0, \ar^r_\text{non-linear}, \ar_\text{linear}) \suchthat r \in \R}$.
+This strategy sets up the argument $\ar_\text{linear}$ as an answer to any argument of the form described in \cref{ex:twolottstrings}, arguing for non-linearity of utility of money.
+	This defines a descriptive theory of depth $2$.
+\end{example}
 
@@
 \label{sec:validity}
+An empirical theory claims to be valid, in the following sense.
 \begin{definition}[Validity]
@@
 \end{definition}
-
-Given $\args \subseteq \allargs$ and $\hist \in \allhist$,
-recall that the set $\args \cap \range(\hist)$ denotes the arguments that are both in $\args$ and contained in the sequence $\hist$.
-
-Define a falsification sequence for $(i, \ar_0, \phi)$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $\hist^1, \hist^3, …, \hist^{N + 1}$, for some $N \in 2\N$, such that it presents successive challenges, which means the following.
-Given $k \in 2\N \suchthat k ≤ N$, $\ar_k \in \allargs$ and $\hist^{k + 1} \in \allhist$, 
-define $\args_{k + 1} = \gbeatsinv(\ar_k) \cap \range(\hist^{k + 1})$; 
-define $\dargs[k + 2] = \dbeatsinv(\args_{k + 1})$ as those fragments defending against the anticipated attackers $\args_{k + 1}$; 
-and, if $\args_{k + 1} ≠ \emptyset$ (equivalently, if $\dargs[k + 2] ≠ \emptyset$), define $\ar_{k + 2} = \ar_k + \dargs[k + 2]$. 
-The sequence presents successive challenges iff, $\forall k \in 2\N \suchthat k ≤ N$, we have that $\ar_k \in \histend[k + 1]$, $\hist^{k + 1} \nileadstost \phi$, and $[\args_{k + 1} = \emptyset ⇔ k = N]$.
+To achieve this goal, it claims that it is able to produce decisive arguments for its supported propositions.
+These arguments can vary according to the individual $i \in I$.
+Given an individual, the theory claims that a decisive argument will be systematically found by starting from an initial argument given by $\gleadsto$, and following a chain of defense defined by $\dg$ as required, depending on the paths that challenge the arguments produced along the way, as judged by the individual $i$.
+The property that a theory manages to systematically produce decisive arguments in such a way is named Convincingness.
+Defining it requires to define first the notion of required arguments.
+
+Given $i \in I, \prop \in \gpropse$, define $\dgip(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \notin \histend \land \hist \nileadsto \phi} \subseteq \dg(\ar)$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\prop$.
+Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
+Define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\prop)$ under $\dgip$: $\gargs = \cup_{k \in \N} (\dgip)^k({\gleadstoinv}(\prop))$.
+The set $\gargs$ is the set of arguments required to convince $i$ of $\phi$.
+\begin{example}[Required arguments]
+	\label{ex:required}
+	Continuing \cref{ex:infinite}, define the subset of individuals that find some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ as the set of $i \in I$ such that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \ar^r_\text{non-linear} \in \range(\hist) \land \hist \nileadsto D > P$.
+	We see that for any $i$ in that set of individuals, $\gargs[D > P] = \set{\ar_0, \ar_\text{linear}}$, and for any $i$ in the complementary set of individuals, $\gargs[D > P] = \set{\ar_0}$.
+\end{example}
+
+Given $\ar \in \gargs$, say that $\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend \land \hist \nileadsto \phi: d(\ar, \hist) ≠ \emptyset$.
+\begin{definition}[Convincingness]
+	An empirical theory is \emph{convincing} iff $\forall i \in I, \prop \in \gpropse, \ar \in \gargs: \ar$ $i$-defends $\prop$.
+\end{definition}
+\begin{example}[Convincingness]
+	Pursuing with \cref{ex:required}, that theory will be convincing iff either $i$ finds some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and both $\ar_0$ and $\ar_\text{linear}$ $i$-defend $D > P$, or $i$ does not find any argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and $\ar_0$ $i$-defends $D > P$.
+
+	$\ar_0$ $i$-defends $D > P$ iff any argumentative path $\hist$ that contains $\ar_0$ towards its end and that does not lead $i$ to accept $D > P$ is such that $\dg(\ar_0, \hist) ≠ \emptyset$, or equivalently, is such that the theory has some argument to answer to $\hist$, or still equivalently, is such that it contains some $\ar^r_\text{non-linear}$.
+	This property mandates that no argumentative path has been “forgotten” in $\dg$: if some path is found that attacks $\ar_0$ successfully (thus $\ar_0 \in \histend \land \hist \nileadsto D > P$), and if the theory has nothing to answer to it (thus $\dg(\ar_0, \hist) = \emptyset$), then the theory is not Convincing.
+\end{example}
+
+To verify that the property of Convincingness is purely empirical, it is necessary to show that whenever a theory fails it, it is possible to see it using a set of observations of $\ileadsto$.
+Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count as falsifying a theory.
+The following example may help forging an intuition about what the possible falsifying sets of observations are.
+\begin{example}[Falsification sequences]
+	Let us examine the possible observations that would suffice to show that the theory presented in our running example is not Convincing.
+
+	First, one could exhibit a path $\hist$ that attacks $\ar_0$ and does not trigger the strategic defense of the theory.
+Those are the paths that satisfy $\ar_0 \in \histend \land \hist \nileadsto D > P \land \forall r \in \R: \ar^r_\text{non-linear} \in \range(\hist)$.
+
+	The second possibility is slightly more demanding, and is the only one that is available if indeed $\ar_0$ $i$-defends $D > P$.
+It requires first to show that $\ar_\text{linear}$ is a required argument to convince $i$, then to show that this argument fails to convince $i$.
+For this, two paths are required: $\hist^0 \in \allhist \suchthat \ar_0 \in \histend[0] \land \hist^0 \nileadsto D > P \land [\exists r \in \R \suchthat \ar^r_\text{non-linear} \in \range(\hist^0)]$, and $\hist^1 \in \allhist \suchthat \ar_\text{linear} \in \histend[1] \land \hist^1 \nileadsto D > P$.
+\end{example}
+
+NB suffices to prove that any $\ar_k \in (\dgip)^k$ iff $\exists (\ar_0, \hist^0, \ar_1 = \dg(\ar_0, \hist^0), …, \ar_k)$ with $\ar_0 \in \histend \land \hist \nileadsto \phi$.
+
+Define a falsification sequence for $(i, \ar_0, \phi)$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $(\hist^k)_{k \in \intvl{0, N}}$, for some $N \in \N$, such that it presents successive challenges, which means the following.
+Given $k \in \intvl{0, N}$, assuming $\ar_k$ is defined, define $\ar_{k + 1} = d(\ar_k, \hist^k)$ if $d(\ar_k, \hist^k) ≠ \emptyset$ and say that $\ar_{k + 1}$ is undefined otherwise.
+%Define the \emph{defending} sequence of arguments as a finite sequence of arguments $\ar_{k + 1} = d(\ar_k, \hist^k)$, for $k \in \intvl{1, N}$, as long as $d(\ar_k, \hist^k)$ is not empty, thus letting the length of the sequence be the first value of $k$ for which $d(\ar_k, \hist^k) = \emptyset$.
+A falsification sequence presents successive challenges iff [$\ar_{k + 1}$ is undefined exactly when $k = N$] and [$\forall k \in \intvl{0, N}: \ar_k \in \histend[k] \land \hist^k \nileadsto \phi$].
+
+%Given $\args \subseteq \allargs$ and $\hist \in \allhist$, recall that the set $\args \cap \range(\hist)$ denotes the arguments that are both in $\args$ and contained in the sequence $\hist$.
+
+%Define a falsification sequence for $(i, \ar_0, \phi)$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $\hist^1, \hist^3, …, \hist^{N + 1}$, for some $N \in 2\N$, such that it presents successive challenges, which means the following.
+%Given $k \in 2\N \suchthat k ≤ N$, $\ar_k \in \allargs$ and $\hist^{k + 1} \in \allhist$, 
+%define $\args_{k + 1} = \gbeatsinv(\ar_k) \cap \range(\hist^{k + 1})$; 
+%define $\dargs[k + 2] = \dbeatsinv(\args_{k + 1})$ as those fragments defending against the anticipated attackers $\args_{k + 1}$; 
+%and, if $\args_{k + 1} ≠ \emptyset$ (equivalently, if $\dargs[k + 2] ≠ \emptyset$), define $\ar_{k + 2} = \ar_k + \dargs[k + 2]$. 
+%The sequence presents successive challenges iff, $\forall k \in 2\N \suchthat k ≤ N$, we have that $\ar_k \in \histend[k + 1]$, $\hist^{k + 1} \nileadsto \phi$, and $[\args_{k + 1} = \emptyset ⇔ k = N]$.
 
@@
 
-\begin{definition}[Convincingness]
-	An empirical theory is \emph{convincing} iff $\forall i \in I, \prop \in \gpropse, \ar \in \gargs: \ar$ $i$-defends $\prop$.
-\end{definition}
-
 A \emph{falsification instance} of an empirical theory is a tuple $(i, \prop, \hist, \ar) \in I × \gpropse × \allhist × \gargs$ such that $\gbeatsinv(\ar) \cap \range(\hist) = \emptyset \land \ar \in \histend \land \hist \nileadstost \prop$.
+
+A \emph{falsification instance} of an empirical theory is a tuple $(i, \prop, \hist, \ar) \in I × \gpropse × \allhist × \gargs$ such that $\ar \in \histend \land \hist \nileadsto \prop \land \dg(\ar, \hist) = \emptyset$.
 I also write that $(i, \prop, \hist, \ar)$ falsifies $\gamma$ to mean that it is a falsification instance of $\gamma$.
+We readily see that \cref{th:convnofals} is true.
+With a falsification sequence $(\ar_0, \hist^0, \ar_1, \hist^1)$, we see that $\ar_1 \in (\dgip)^1(\ar_0)$, and similarly for longer falsification sequences, $\ar_k \in (\dgip)^k(\ar_0)$.
 

### 2020-11-14 simple.tex
Better argumentation about memory

@@
 A supplementary problem might happen in some situations.
-Once an argumentative path has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective.
-Let me call this possibility the hypothesis of persistence, and the converse hypothesis, the hypothesis of immediacy.
-Under the hypothesis of persistence, it is impossible to test twice the same path.
-Tests of the stability of the opinion of $i$ towards a given set of arguments can still be performed, as the next example indicates.
-The converse hypothesis amounts to postulating that the individual forgets after some time and use an observation protocol that separates the tests in time sufficiently.
+Once an argumentative path has been presented to the individual, this cannot necessarily be undone easily: she might remember some of the arguments, and they may have a lasting influence on her perspective.
+This may render difficult to test several unrelated paths on a given individual: such tests require to wait long enough that it can be reasonably thought that the individual is no more under influence of the arguments he has seen.
+It is therefore desirable to point out which testing protocols permit to avoid these difficulties.
 \commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question. Je doute cependant qu'un lecteur innocent comprenne un traitre mot}
-The hypothesis of memory further reduces the possible paths that can be tested with a given individual.
 An illustration of some consequences of these possibilities on our running example may be useful. 
 \begin{example}[Hypothesis of memory]
-	 The definition of $\ileadsto$ as given so far implicitly assumes that a given path can be tested at most once with a given individual, as it does not indicate what to conclude when a path $\hist$ leads $i$ to adopt a proposition $\prop$ only some of the time.
-This is justified under the hypothesis of memory.
-	 Recall that in \cref{ex:incompl}, $\hist \ileadsto P ≥ D$ and $\hist' \ileadsto D > P$ for some $\hist, \hist' \in \allhist$.
-If we further assume that $\range(\hist) = \range(\hist')$, in other words, that these two paths use the same arguments, this illustrates the remark that instability of $i$ towards some set of argument can be observed even under the hypothesis of memory.
-Consider $\hist = \left<\ar_0, \ar_1\right>$ and $\alpha' = \left<\ar_0, \ar_1, \ar_0\right>$ as an example.
-As $\hist'$ is a sequence that starts with $\hist$, it is possible to test these two paths on $i$, even under the hypothesis of memory.
-
-	If, on the contrary, it is considered that the individual forgets over time, we must define $\ileadsto$ differently.
-Define $T$ a series of time steps, and given $t \in T$, define $\hist \ileadsto^t \prop$ as the observation of the adoption of $\prop$ by $i$ when having been presented the arguments in $\hist$ at time $t$.
-Define then $\hist \ileadsto \prop$ iff $\forall t \in T: \hist \ileadsto^t \prop$.
-Under the hypothesis of immediacy, it could be that $\exists \hist \suchthat \hist \nileadsto P ≥ D \land \hist \nileadsto D > P$.
+	 The definition of $\ileadsto$ as given so far implicitly assumes that a given path can be tested at most once with a given individual, as it does not indicate what to conclude when a path $\hist$ leads $i$ to accept a proposition $\prop$ only some of the time.
+This is justified under the hypothesis that individuals remember arguments forever.
+	It is interesting to note that even in that case, instability of $i$ towards some set of argument can be observed.
+As an illustration of such an instability, recall \cref{ex:incompl}, which assumes that for some $\hist, \hist' \in \allhist$, $\hist \ileadsto P ≥ D$ and $\hist' \ileadsto D > P$.
+	Consider $\hist = \left<\ar_0, \ar_1\right>$ and $\hist' = \left<\ar_0, \ar_1, \ar_0\right>$ and assume we tested first $\hist$ then $\hist'$ on the same individual.
+Even assuming that the individual remembers, when exposed to $\hist'$, having seen these two arguments during the previous test, she might be fundamentally undecided as to whether $P ≥ D$ or $D > P$, and pick items randomly when exposed to these two arguments in any order.
+As $\hist'$ is a sequence that starts with $\hist$, it is possible to test these two paths on $i$, even under the hypothesis of unbounded memory, and observe an instability of $i$ towards the arguments $\ar_0$ and $\ar_1$.
+
+	Under the more realistic hypothesis that the individual forgets over time, not only can we test unrelated paths on a given individual, but we can test several times the same path.
+We must then define $\ileadsto$ differently.
+Define $\hist \ileadsto \prop$ iff the individual would be lead to accept $\prop$ on every presentation of $\hist$.
+It is then possible that $\exists \hist \in \allhist \suchthat \hist \nileadsto P ≥ D \land \hist \nileadsto D > P$.
+	Note that this makes it impossible to observe that $\hist \ileadsto \prop$.
+This is not a problem for the methodology presented here: it is still possible to observe that $\hist \nileadsto \prop$, as it suffices to observe that the individual did not accept $\prop$ under at least one presentation of $\hist$.
+The falsification sequences defined here below rest only on that kind of observations.
 \end{example}
@@
 \Cref{sec:validity} defines formally the notion of falsification sequence and proves this central claim.
-The practical meaningfulness of this result is not affected by the hypothesis of memory, under condition that the set $I$ be large enough: we can always then perform falsification tests on different individuals for each path that has to be tested, so that memory of individuals does not matter.
-Exploring settings where $I$ is too small to apply this strategy is left aside in this article.
 
@@
 A supplementary important result, described in \cref{sec:compare}, is that when two theories disagree about incompatible propositions, one of the theories at least must fail some given sequence of empirical tests, which the proof describes.
-These tests can all be performed on a single individual and are robust against the hypothesis of memory, which suggest that arbitration between theories could be performed reasonably easily.
+
+These arbitration tests can all be performed on a single individual and are robust against the hypothesis of memory, which suggest that arbitration between theories could be performed reasonably easily.
+By contrast, the falsification sequences used in the preceding result of \cref{sec:validity} may require to test unrelated paths on the same individual, which may be practically difficult, as acknowledged here above.
+I expect however that the second result, permitting to arbitrate between theories, will be more often used in practice, thus, that falsification tests of the previous kind will be comparatively rare.
+This article is content with the existence of a principled, systematic way of falsifying theories of \ac{DJ} and leaves to later studies the comparison of approaches from the practical point of view of easiness of falsifying them.
 
@@
 	Define ${\gleadsto} = \set{(\ar_\text{for$P$}, P > D)}$.
-	In order to define a counter-argument to $\ar_0$, given a real number $r \in \R$, define $\ar^r_\text{non-linear}$ as the text “It is absurd to reason in terms of expected gain.
+	In order to define a counter-argument to $\ar_0$, given a real number $r \in \R$, define $\ar^r_\text{non-linear}$ as the text “$D$ is better than $P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
 For example, consider a choice between winning $r$ dollars with probability $0.8$ and winning $2r$ dollars with probability $0.4$.
-They have the same expected gain, but the first one is clearly preferrable”.
+They have the same expected gain, but the first one is clearly preferrable.
+Therefore, we recommend to rather pick $P$ as it presents a much better chance of earning money”.
 (The value of $r$ and $2r$ is to be used in the relevant places in  the text.)
@@
 Therefore, expected gain is the right indicator to consider for a systematic and sound decision strategy.”
-	Define $\dg = \set{(\ar_0, \ar^r_\text{non-linear}, \ar_\text{linear}) \suchthat r \in \R}$.
-This strategy sets up the argument $\ar_\text{linear}$ as an answer to any argument of the form described in \cref{ex:twolottstrings}, arguing for non-linearity of utility of money.
+	Define $+$ as the concatenation operator over strings.
+	Define $\dg = \set{(\ar_0, \ar^r_\text{non-linear}, \ar_0 + \ar_\text{linear}) \suchthat r \in \R}$.
+This strategy sets up the argument $\ar_0 + \ar_\text{linear}$ as an answer to any argument of the form described in \cref{ex:twolottstrings}, arguing for non-linearity of utility of money.
 	This defines a descriptive theory of depth $2$.
@@
 	Continuing \cref{ex:infinite}, define the subset of individuals that find some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ as the set of $i \in I$ such that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \ar^r_\text{non-linear} \in \range(\hist) \land \hist \nileadsto D > P$.
-	We see that for any $i$ in that set of individuals, $\gargs[D > P] = \set{\ar_0, \ar_\text{linear}}$, and for any $i$ in the complementary set of individuals, $\gargs[D > P] = \set{\ar_0}$.
+	We see that for any $i$ in that set of individuals, $\gargs[D > P] = \set{\ar_0, \ar_0 + \ar_\text{linear}}$, and for any $i$ in the complementary set of individuals, $\gargs[D > P] = \set{\ar_0}$.
 \end{example}
@@
 \begin{example}[Convincingness]
-	Pursuing with \cref{ex:required}, that theory will be convincing iff either $i$ finds some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and both $\ar_0$ and $\ar_\text{linear}$ $i$-defend $D > P$, or $i$ does not find any argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and $\ar_0$ $i$-defends $D > P$.
+	Pursuing with \cref{ex:required}, that theory will be convincing iff either $i$ finds some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and both $\ar_0$ and $\ar_0 + \ar_\text{linear}$ $i$-defend $D > P$, or $i$ does not find any argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and $\ar_0$ $i$-defends $D > P$.
 
@@
 
-To verify that the property of Convincingness is purely empirical, it is necessary to show that whenever a theory fails it, it is possible to see it using a set of observations of $\ileadsto$.
-Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count as falsifying a theory.
+To verify that the property of Convincingness is purely empirical, it is necessary to show that whenever a theory fails it, it is possible to see it using a set of observations of $\leadsto$.
+Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count for falsifying a theory.
 The following example may help forging an intuition about what the possible falsifying sets of observations are.
@@
 	The second possibility is slightly more demanding, and is the only one that is available if indeed $\ar_0$ $i$-defends $D > P$.
-It requires first to show that $\ar_\text{linear}$ is a required argument to convince $i$, then to show that this argument fails to convince $i$.
-For this, two paths are required: $\hist^0 \in \allhist \suchthat \ar_0 \in \histend[0] \land \hist^0 \nileadsto D > P \land [\exists r \in \R \suchthat \ar^r_\text{non-linear} \in \range(\hist^0)]$, and $\hist^1 \in \allhist \suchthat \ar_\text{linear} \in \histend[1] \land \hist^1 \nileadsto D > P$.
+It requires first to show that $\ar_0 + \ar_\text{linear}$ is a required argument to convince $i$, then to show that this argument fails to convince $i$.
+For this, two paths are required: $\hist^0 \in \allhist \suchthat \ar_0 \in \histend[0] \land \hist^0 \nileadsto D > P \land \dg(\ar_0, \hist^0) = \ar_0 + \ar_\text{linear}$, and $\hist^1 \in \allhist \suchthat (\ar_0 + \ar_\text{linear}) \in \histend[1] \land \hist^1 \nileadsto D > P$.
 \end{example}
-
-NB suffices to prove that any $\ar_k \in (\dgip)^k$ iff $\exists (\ar_0, \hist^0, \ar_1 = \dg(\ar_0, \hist^0), …, \ar_k)$ with $\ar_0 \in \histend \land \hist \nileadsto \phi$.
 
@@
 %Define the \emph{defending} sequence of arguments as a finite sequence of arguments $\ar_{k + 1} = d(\ar_k, \hist^k)$, for $k \in \intvl{1, N}$, as long as $d(\ar_k, \hist^k)$ is not empty, thus letting the length of the sequence be the first value of $k$ for which $d(\ar_k, \hist^k) = \emptyset$.
-A falsification sequence presents successive challenges iff [$\ar_{k + 1}$ is undefined exactly when $k = N$] and [$\forall k \in \intvl{0, N}: \ar_k \in \histend[k] \land \hist^k \nileadsto \phi$].
+A sequence $(\hist^k)_{k \in \intvl{0, N}}$ presents successive challenges iff [$\ar_{k + 1}$ is undefined exactly when $k = N$] and [$\forall k \in \intvl{0, N}: \ar_k \in \histend[k] \land \hist^k \nileadsto \phi$].
 
@@
 A descriptive theory has no falsification sequence iff $\forall (i, \ar_0, \phi)$, no finite sequence of paths present successive challenges.
+
+\commentOC{Suffices to prove that any $\ar_k \in (\dgip)^k$ iff $\exists (\ar_0, \hist^0, \ar_1 = \dg(\ar_0, \hist^0), …, \ar_k)$ with $\ar_0 \in \histend \land \hist \nileadsto \phi$.}
 

### 2020-11-16 simple.tex
Typo symbol

@@
 
-To verify that the property of Convincingness is purely empirical, it is necessary to show that whenever a theory fails it, it is possible to see it using a set of observations of $\leadsto$.
+To verify that the property of Convincingness is purely empirical, it is necessary to show that whenever a theory fails it, it is possible to see it using a set of observations of $\allleadsto$.
 Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count for falsifying a theory.

### 2020-12-07 simple.tex
Some refs; attempt shorter path to falsification

@@
 
+The phrase “\acl{DP}” has been used by \citet{orchard-webb_deliberative_2016, kenter_deliberative_2017} in the context of group deliberation.
+As used in this article, the concept of deliberation does not necessarily refer to a group deliberation: this approach is agnostic as to the provenance of the arguments.
+
+The idea of using axiomatized decision theories to systematically generate explanations targeted to non experts has received much interest recently \citep{labreuche_general_2011, belahcene_explaining_2017, belahcene_accountable_2018, belahcene_comparing_2019, cailloux_arguing_2016, boixel_automated_2020, peters_explainable_2020, procaccia_axioms_2019}.
+These works are most interesting from the point of view of producing concrete theories of \ac{DJ}, but do not discuss how to systematically exploit decision makers’s judgments about the strengths of texts promoting different alternatives.
+They should therefore be viewed as complementary to this proposition.
+
 \subsection{Preference purification}
@@
 \commentYM{il me semble nécessaire ici de mentionner aussi tous les dispositifs participatifs et de concertation employés en routine dans les prises de décisions relatives aux politiques publiques et leur mise en oeuvre}
-\commentOC{Je m’interroge. Ça me semble de pus en plus éloigné du scope, car je m’intéresse aux préférences d’un individu donné, hors questions d’agrégation.}
+\commentOC{Je m’interroge. Ça me semble de plus en plus éloigné du scope, car je m’intéresse aux préférences d’un individu donné, hors questions d’agrégation.}
 
@@
 bref, de quoi parles-tu ?}
-\commentOCf{C’est le \href{https://en.wikipedia.org/wiki/Sequence}{terme habituel} en mathématiques, à ma connaissance.}
+\commentOCf{C’est le \hrefblue{https://en.wikipedia.org/wiki/Sequence}{\underline{terme habituel}} en mathématiques, à ma connaissance.}
 of arguments to an individual, and how to observe her resulting judgment about a proposition of interest.
@@
 Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count for falsifying a theory.
-The following example may help forging an intuition about what the possible falsifying sets of observations are.
+The following example may help to form an intuition about what the possible falsifying sets of observations are.
 \begin{example}[Falsification sequences]
@@
 
+\subsection{Attempt}
+As $\ileadsto \subseteq I × \allhist × \Phi$, the set of a priori possible $\ileadsto$ is $\powerset{I × \allhist × \Phi}$.
+
+A claim $C$ is a subset of $\powerset{I × \allhist × \Phi}$.
+
 \commentOC{Suffices to prove that any $\ar_k \in (\dgip)^k$ iff $\exists (\ar_0, \hist^0, \ar_1 = \dg(\ar_0, \hist^0), …, \ar_k)$ with $\ar_0 \in \histend \land \hist \nileadsto \phi$.}
+\commentOC{We want a descriptive theory to have a property $P$ that implies validity, and that is falsifiable, that is, $P$ implying that no finite sequence of alphas exist in some given set.}
+A theory $\gamma$ must define a set $P$ of possible $\ileadsto$ and the theory claims that any effective $\ileadsto$ is in $P$.
+It must be visible that no, if no, with a finite set of observations of $\ileadsto$.
+
+A claim about $\ileadsto$ is a set $P \subseteq I × \allhist × \Phi$.
+A claim $P$ is falsifiable iff $\exists O \subseteq I × \allhist × \Phi$, $O$ finite, such that $P \cap \set{{\leadsto} \suchthat {\leadsto} \supseteq O} = \emptyset$.
+
+The theory is falsifiable iff $\exists$ finite $O$ st no completion of it makes the theory convincing.
+
+In other words, such a set $O$ is sufficient to show that the theory is not convincing.
+
+Theorem: the theory is falsifiable iff it says more than nothing.
 

### 2020-12-07 simple.tex
Falsifiability of a claim in general (too general, interruptus)

@@
 \end{example}
+
+It is now necessary to verify that, first, the claim of convincingness is falsifiable, and second, that it suffices to prove validity.
+
+Let us first clarify what falsifiability formally means in our context.
+Define a claim $C \subseteq \powerset{I × \allhist × \Phi}$ as a subset of the possible relations $\leadsto$.
+When a theory claims that $C$, it claims that $\leadsto$ is indeed a member of $C$.
+Say that a set of observations $O \subseteq I × \allhist × \Phi$ falsifies the claim $C$ iff $C \cap \set{R \subseteq O} = \emptyset$.
+In such a case, $C$ contains no possible relation $R$ compatible with the observations in $O$, or in other words, the observations $O$ prove that ${\leadsto} \notin C$.
+Say that $C$ is falsifiable iff some finite set of observation falsifies it.
+\begin{example}[Two claims]
+	Given a normative theory and $\phi \in \Phi$, the claim $C_1 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \exists \ar \in \allargs \suchthat \ar \ileadstost \phi}$ corresponds to claiming that for all individuals $i \in I$, some argument is $i$-decisive for $\phi$.
+If the set of arguments is infinite, $C_1$ is not falsifiable.
+	Given $\ar \in \allargs$ and $\phi \in \Phi$, the set $C_2 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \ar \ileadstost \phi}$ denotes the claim that all individuals will consider the argument $\ar$ as decisive for $\phi$.
+This claim is falsified by any observation such that $\hist \nileadsto \phi$ for some $\hist \in \allhist$ with $\ar \in \histend$, thus, $C_2$ is falsifiable.
+\end{example}
+
+Let the claim of a descriptive theory by defined as $C = …$.
+\begin{theorem}
+	…
 

### 2020-12-07 simple.tex
Attempt fals using claim of Convincingness, interrupted as well because difficult to describe convincingness.

--- 2020-12-07 simple.tex
@@
 
-\subsection{Validity and falsification sequences}
+\subsection{Validity and falsification}
 \label{sec:validity}
@@
 The property that a theory manages to systematically produce decisive arguments in such a way is named Convincingness.
-Defining it requires to define first the notion of required arguments.
+Defining it precisely requires to define first the notion of required arguments.
 
@@
 
-To verify that the property of Convincingness is purely empirical, it is necessary to show that whenever a theory fails it, it is possible to see it using a set of observations of $\allleadsto$.
-Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count for falsifying a theory.
-The following example may help to form an intuition about what the possible falsifying sets of observations are.
-\begin{example}[Falsification sequences]
-	Let us examine the possible observations that would suffice to show that the theory presented in our running example is not Convincing.
-
-	First, one could exhibit a path $\hist$ that attacks $\ar_0$ and does not trigger the strategic defense of the theory.
-Those are the paths that satisfy $\ar_0 \in \histend \land \hist \nileadsto D > P \land \forall r \in \R: \ar^r_\text{non-linear} \in \range(\hist)$.
-
-	The second possibility is slightly more demanding, and is the only one that is available if indeed $\ar_0$ $i$-defends $D > P$.
-It requires first to show that $\ar_0 + \ar_\text{linear}$ is a required argument to convince $i$, then to show that this argument fails to convince $i$.
-For this, two paths are required: $\hist^0 \in \allhist \suchthat \ar_0 \in \histend[0] \land \hist^0 \nileadsto D > P \land \dg(\ar_0, \hist^0) = \ar_0 + \ar_\text{linear}$, and $\hist^1 \in \allhist \suchthat (\ar_0 + \ar_\text{linear}) \in \histend[1] \land \hist^1 \nileadsto D > P$.
-\end{example}
-
-Define a falsification sequence for $(i, \ar_0, \phi)$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $(\hist^k)_{k \in \intvl{0, N}}$, for some $N \in \N$, such that it presents successive challenges, which means the following.
-Given $k \in \intvl{0, N}$, assuming $\ar_k$ is defined, define $\ar_{k + 1} = d(\ar_k, \hist^k)$ if $d(\ar_k, \hist^k) ≠ \emptyset$ and say that $\ar_{k + 1}$ is undefined otherwise.
-%Define the \emph{defending} sequence of arguments as a finite sequence of arguments $\ar_{k + 1} = d(\ar_k, \hist^k)$, for $k \in \intvl{1, N}$, as long as $d(\ar_k, \hist^k)$ is not empty, thus letting the length of the sequence be the first value of $k$ for which $d(\ar_k, \hist^k) = \emptyset$.
-A sequence $(\hist^k)_{k \in \intvl{0, N}}$ presents successive challenges iff [$\ar_{k + 1}$ is undefined exactly when $k = N$] and [$\forall k \in \intvl{0, N}: \ar_k \in \histend[k] \land \hist^k \nileadsto \phi$].
-
-%Given $\args \subseteq \allargs$ and $\hist \in \allhist$, recall that the set $\args \cap \range(\hist)$ denotes the arguments that are both in $\args$ and contained in the sequence $\hist$.
-
-%Define a falsification sequence for $(i, \ar_0, \phi)$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $\hist^1, \hist^3, …, \hist^{N + 1}$, for some $N \in 2\N$, such that it presents successive challenges, which means the following.
-%Given $k \in 2\N \suchthat k ≤ N$, $\ar_k \in \allargs$ and $\hist^{k + 1} \in \allhist$, 
-%define $\args_{k + 1} = \gbeatsinv(\ar_k) \cap \range(\hist^{k + 1})$; 
-%define $\dargs[k + 2] = \dbeatsinv(\args_{k + 1})$ as those fragments defending against the anticipated attackers $\args_{k + 1}$; 
-%and, if $\args_{k + 1} ≠ \emptyset$ (equivalently, if $\dargs[k + 2] ≠ \emptyset$), define $\ar_{k + 2} = \ar_k + \dargs[k + 2]$. 
-%The sequence presents successive challenges iff, $\forall k \in 2\N \suchthat k ≤ N$, we have that $\ar_k \in \histend[k + 1]$, $\hist^{k + 1} \nileadsto \phi$, and $[\args_{k + 1} = \emptyset ⇔ k = N]$.
-
-A descriptive theory has no falsification sequence iff $\forall (i, \ar_0, \phi)$, no finite sequence of paths present successive challenges.
-
-\subsection{Attempt}
-As $\ileadsto \subseteq I × \allhist × \Phi$, the set of a priori possible $\ileadsto$ is $\powerset{I × \allhist × \Phi}$.
-
-A claim $C$ is a subset of $\powerset{I × \allhist × \Phi}$.
-
-\commentOC{Suffices to prove that any $\ar_k \in (\dgip)^k$ iff $\exists (\ar_0, \hist^0, \ar_1 = \dg(\ar_0, \hist^0), …, \ar_k)$ with $\ar_0 \in \histend \land \hist \nileadsto \phi$.}
-\commentOC{We want a descriptive theory to have a property $P$ that implies validity, and that is falsifiable, that is, $P$ implying that no finite sequence of alphas exist in some given set.}
-A theory $\gamma$ must define a set $P$ of possible $\ileadsto$ and the theory claims that any effective $\ileadsto$ is in $P$.
-It must be visible that no, if no, with a finite set of observations of $\ileadsto$.
-
-A claim about $\ileadsto$ is a set $P \subseteq I × \allhist × \Phi$.
-A claim $P$ is falsifiable iff $\exists O \subseteq I × \allhist × \Phi$, $O$ finite, such that $P \cap \set{{\leadsto} \suchthat {\leadsto} \supseteq O} = \emptyset$.
-
-The theory is falsifiable iff $\exists$ finite $O$ st no completion of it makes the theory convincing.
-
-In other words, such a set $O$ is sufficient to show that the theory is not convincing.
-
-Theorem: the theory is falsifiable iff it says more than nothing.
-
+It is now necessary to verify that the claim of convincingness is, first, falsifiable, and second, sufficient to yield validity.
+
+Let us first clarify what falsifiability formally means in our context.
+So far, convincingness is defined only for the “real” relation $\leadsto$; we now need it defined more generally.
+Given any relation $R \subseteq I × \allhist × \Phi$, say that a descriptive theory is convincing under $R$ whenever it is convincing, as defined above, but replacing $\leadsto$ by $R$.
+We can now speak counterfactually of the theory being convincing, or not, assuming the observable relation is $R$ instead of $\leadsto$. 
+Observations of the relation $\leadsto$ can in general include positive statements, of the form $\hist \ileadsto \phi$, and negative ones, of the form $\hist \nileadsto \phi$.
+(One way to obtain such negative observations is to use an incompatible proposition $\phi'$ and deduce from $\hist \ileadsto \phi'$ that $\hist \nileadsto \phi$.) A relation $R \subseteq I × \allhist × \Phi$ is compatible with the positive observations $O \subseteq I × \allhist × \Phi$ and the negative observations $O' \subseteq I × \allhist × \Phi$ iff $O \subseteq R \land R \cap O' = \emptyset$.
+The claim of convincingness is said to be falsifiable iff there exists finite set of observations $O, O' \subseteq I × \allhist × \Phi$ such that $\forall R \subseteq I × \allhist × \Phi \suchthat O \supseteq R \land R \cap O' = \emptyset$, the theory is not convincing under $R$.
+In such a case, no possible relation $R$ compatible with the observations $O, O'$ make the theory convincing; in other words, the observations $O, O'$ prove that the theory is not convincing.
+%\begin{example}[Two claims]
+%	Given a normative theory and $\phi \in \Phi$, the claim $C_1 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \exists \ar \in \allargs \suchthat \ar \ileadstost \phi}$ corresponds to claiming that for all individuals $i \in I$, some argument is $i$-decisive for $\phi$.
+If the set of arguments is infinite, $C_1$ is not falsifiable.
+%	Given $\ar \in \allargs$ and $\phi \in \Phi$, the set $C_2 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \ar \ileadstost \phi}$ denotes the claim that all individuals will consider the argument $\ar$ as decisive for $\phi$.
+This claim is falsified by any observation such that $\hist \nileadsto \phi$ for some $\hist \in \allhist$ with $\ar \in \histend$, thus, $C_2$ is falsifiable.
+%\end{example}
+
+The following theorem states that the descriptive theories defined here are falsifiable, unless they state nothing about anybody’s \ac{DJ}.
+\Cref{sec:prooffals} proves it and describes the set of falsifiers of such theories.
+This theorem implicitly assumes full observability, that is, it supposes that any positive or negative observations are in principle observable and thus available for falsification attempts.
+Further works should investigate to which extent this hypothesis can be relaxed.
 \begin{theorem}
-	\label{th:svalid}
-	A normatively adequate empirical theory that has no falsification sequence is valid.
+	\label{th:convfals}
+	The claim of convincingness is falsifiable iff ${\gleadsto} ≠ \emptyset$.
+\end{theorem}
+It can also be seen that if a theory is not constrained in its depth, its claim of convincingness may be unfalsifiable, thus the hypothesis of finite depth is required to obtain this theorem.
+The formal proof of this fact is omitted because it is not especially enlightening; that this fact holds can be seen by examining the use of this hypothesis in the proof of \cref{th:convfals}.
+
+Only remains now to prove that convincingness, together with normative adequacy, is sufficient to obtain validity. The proof is also provided in \cref{sec:prooffals}.
+\begin{theorem}
+	\label{th:convvalid}
+	A normatively adequate empirical theory that is convincing is valid.
 \end{theorem}
@@
 Recall from \cref{sec:coh} that $\incompat = \set{(\prop, \prop') \suchthat \forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'}$ denotes the set of pairs of incompatible propositions.
+\commentOC{Does this mandate completeness?}
 Given two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $(\prop, \propbar) \in \incompat$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$.
@@
 
+\section{Empirical validity, first}
+\label{sec:prooffals}
+To verify that the property of Convincingness is purely empirical, it is necessary to show that whenever a theory fails it, it is possible to see it using a set of observations of $\allleadsto$.
+Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count for falsifying a theory.
+In other words, it is desirable to capture exactly which sets of observations falsify the claim of convincingness. This will also provide a proof of \cref{th:convfals}.
+
+The following example may help to form an intuition about what the possible falsifying sets of observations are.
+\begin{example}[Falsification sequences]
+	Let us examine the possible observations that would suffice to show that the theory presented in our running example is not Convincing.
+
+	First, one could exhibit a path $\hist$ that attacks $\ar_0$ and does not trigger the strategic defense of the theory.
+Those are the paths that satisfy $\ar_0 \in \histend \land \hist \nileadsto D > P \land \forall r \in \R: \ar^r_\text{non-linear} \in \range(\hist)$.
+
+	The second possibility is slightly more demanding, and is the only one that is available if indeed $\ar_0$ $i$-defends $D > P$.
+It requires first to show that $\ar_0 + \ar_\text{linear}$ is a required argument to convince $i$, then to show that this argument fails to convince $i$.
+For this, two paths are required: $\hist^0 \in \allhist \suchthat \ar_0 \in \histend[0] \land \hist^0 \nileadsto D > P \land \dg(\ar_0, \hist^0) = \ar_0 + \ar_\text{linear}$, and $\hist^1 \in \allhist \suchthat (\ar_0 + \ar_\text{linear}) \in \histend[1] \land \hist^1 \nileadsto D > P$.
+\end{example}
+
+Define a falsification sequence for $(i, \ar_0, \phi)$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $(\hist^k)_{k \in \intvl{0, N}}$, for some $N \in \N$, such that it presents successive challenges, which means the following.
+Given $k \in \intvl{0, N}$, assuming $\ar_k$ is defined, define $\ar_{k + 1} = d(\ar_k, \hist^k)$ if $d(\ar_k, \hist^k) ≠ \emptyset$ and say that $\ar_{k + 1}$ is undefined otherwise.
+%Define the \emph{defending} sequence of arguments as a finite sequence of arguments $\ar_{k + 1} = d(\ar_k, \hist^k)$, for $k \in \intvl{1, N}$, as long as $d(\ar_k, \hist^k)$ is not empty, thus letting the length of the sequence be the first value of $k$ for which $d(\ar_k, \hist^k) = \emptyset$.
+A sequence $(\hist^k)_{k \in \intvl{0, N}}$ presents successive challenges iff [$\ar_{k + 1}$ is undefined exactly when $k = N$] and [$\forall k \in \intvl{0, N}: \ar_k \in \histend[k] \land \hist^k \nileadsto \phi$].
+
+%Given $\args \subseteq \allargs$ and $\hist \in \allhist$, recall that the set $\args \cap \range(\hist)$ denotes the arguments that are both in $\args$ and contained in the sequence $\hist$.
+
+%Define a falsification sequence for $(i, \ar_0, \phi)$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $\hist^1, \hist^3, …, \hist^{N + 1}$, for some $N \in 2\N$, such that it presents successive challenges, which means the following.
+%Given $k \in 2\N \suchthat k ≤ N$, $\ar_k \in \allargs$ and $\hist^{k + 1} \in \allhist$, 
+%define $\args_{k + 1} = \gbeatsinv(\ar_k) \cap \range(\hist^{k + 1})$; 
+%define $\dargs[k + 2] = \dbeatsinv(\args_{k + 1})$ as those fragments defending against the anticipated attackers $\args_{k + 1}$; 
+%and, if $\args_{k + 1} ≠ \emptyset$ (equivalently, if $\dargs[k + 2] ≠ \emptyset$), define $\ar_{k + 2} = \ar_k + \dargs[k + 2]$. 
+%The sequence presents successive challenges iff, $\forall k \in 2\N \suchthat k ≤ N$, we have that $\ar_k \in \histend[k + 1]$, $\hist^{k + 1} \nileadsto \phi$, and $[\args_{k + 1} = \emptyset ⇔ k = N]$.
+
+A descriptive theory has no falsification sequence iff $\forall (i, \ar_0, \phi)$, no finite sequence of paths present successive challenges.
+
+ \commentOC{Suffices to prove that any $\ar_k \in (\dgip)^k$ iff $\exists (\ar_0, \hist^0, \ar_1 = \dg(\ar_0, \hist^0), …, \ar_k)$ with $\ar_0 \in \histend \land \hist \nileadsto \phi$.}
+\commentOC{We want a descriptive theory to have a property $P$ that implies validity, and that is falsifiable, that is, $P$ implying that no finite sequence of alphas exist in some given set.}
+A theory $\gamma$ must define a set $P$ of possible $\ileadsto$ and the theory claims that any effective $\ileadsto$ is in $P$.
+It must be visible that no, if no, with a finite set of observations of $\ileadsto$.
+
+A claim about $\ileadsto$ is a set $P \subseteq I × \allhist × \Phi$.
+A claim $P$ is falsifiable iff $\exists O \subseteq I × \allhist × \Phi$, $O$ finite, such that $P \cap \set{{\leadsto} \suchthat {\leadsto} \supseteq O} = \emptyset$.
+
+The theory is falsifiable iff $\exists$ finite $O$ st no completion of it makes the theory convincing.
+
+In other words, such a set $O$ is sufficient to show that the theory is not convincing.
+
+Theorem: the theory is falsifiable iff it says more than nothing.
+
 \section{Empirical validity}

### 2020-12-07 simple.tex
Started abstract attempt

@@
 
-A supplementary problem might happen in some situations.
-Once an argumentative path has been presented to the individual, this cannot necessarily be undone easily: she might remember some of the arguments, and they may have a lasting influence on her perspective.
-This may render difficult to test several unrelated paths on a given individual: such tests require to wait long enough that it can be reasonably thought that the individual is no more under influence of the arguments he has seen.
-It is therefore desirable to point out which testing protocols permit to avoid these difficulties.
-\commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question. Je doute cependant qu'un lecteur innocent comprenne un traitre mot}
-An illustration of some consequences of these possibilities on our running example may be useful. 
-\begin{example}[Hypothesis of memory]
-	 The definition of $\ileadsto$ as given so far implicitly assumes that a given path can be tested at most once with a given individual, as it does not indicate what to conclude when a path $\hist$ leads $i$ to accept a proposition $\prop$ only some of the time.
-This is justified under the hypothesis that individuals remember arguments forever.
-	It is interesting to note that even in that case, instability of $i$ towards some set of argument can be observed.
-As an illustration of such an instability, recall \cref{ex:incompl}, which assumes that for some $\hist, \hist' \in \allhist$, $\hist \ileadsto P ≥ D$ and $\hist' \ileadsto D > P$.
-	Consider $\hist = \left<\ar_0, \ar_1\right>$ and $\hist' = \left<\ar_0, \ar_1, \ar_0\right>$ and assume we tested first $\hist$ then $\hist'$ on the same individual.
-Even assuming that the individual remembers, when exposed to $\hist'$, having seen these two arguments during the previous test, she might be fundamentally undecided as to whether $P ≥ D$ or $D > P$, and pick items randomly when exposed to these two arguments in any order.
-As $\hist'$ is a sequence that starts with $\hist$, it is possible to test these two paths on $i$, even under the hypothesis of unbounded memory, and observe an instability of $i$ towards the arguments $\ar_0$ and $\ar_1$.
-
-	Under the more realistic hypothesis that the individual forgets over time, not only can we test unrelated paths on a given individual, but we can test several times the same path.
-We must then define $\ileadsto$ differently.
-Define $\hist \ileadsto \prop$ iff the individual would be lead to accept $\prop$ on every presentation of $\hist$.
-It is then possible that $\exists \hist \in \allhist \suchthat \hist \nileadsto P ≥ D \land \hist \nileadsto D > P$.
-	Note that this makes it impossible to observe that $\hist \ileadsto \prop$.
-This is not a problem for the methodology presented here: it is still possible to observe that $\hist \nileadsto \prop$, as it suffices to observe that the individual did not accept $\prop$ under at least one presentation of $\hist$.
-The falsification sequences defined here below rest only on that kind of observations.
-\end{example}
-
-Importantly, theories of \ac{DJ} must also be able to argue differently for different individuals.
-Even considering individuals with the same \ac{DJ}, different individuals might consider as decisive different arguments.
-Accepting non trivial propositions often requires to accept several sub-propositions, that together permit to be convinced of the acceptability of the proposition.
-Depending on which of these sub-propositions the individual already considers to be acceptable, parts of the argumentation can be omitted, and, perhaps, must be omitted: an overly long argument, stating many things that the listener already knows, has fewer chance to convince the listener than a short argument that goes straight to the point about which the listener doubts.
-%Mathematicians do not write their proofs starting from the axioms of set theory: they use results that they assume the reader already is aware of, and are ready (in principle) to supply the proofs of these intermediate results if a reader has doubt about some of them.
-In other words, what is needed for a theory of \ac{DJ} is not just a capacity to produce a unique decisive argument, with the claim that this argument will convince individuals in $I$, but rather a capacity to produce dynamically arguments that depend on which counter-arguments the individual finds appealing, with a claim that this dynamic argumentation strategy will succeed in convincing individuals in $I$.
-
-Achieving practical knowledge of \acp{DJ} is tackled by introducing descriptive theories of \ac{DJ}.
-They are defined in \cref{sec:descrdef}.
-An empirical theory for a given normative theory defines a subset of propositions of the agenda, that it claims are contained in the \acp{DJ} of individuals concerned by the normative theory.
-They are called the proposition that the theory supports.
-\commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi}
-%The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments.
-This is accomplished by three binary relations, part of the definition of empiricial theories: one represents its initial arguments, one plans the possible attacks, and one defines its counter-arguments.
-An empirical theory also defines a concatenation operation able to dynamically build arguments from fragments of arguments.
-%The theory claims that when one of its arguments in support of one of its claims is unconvincing to an individual, it is because of one of the anticipated attacks; and the theory claims to be able to provide counter-arguments to such attacks as they come, that will in turn be either convincing to the individual, or fail to be because of some anticipated attack.
-The theory is also constrained to have “finite depth”, meaning that it must set an a priori limit to the number of such iterations of attacks and counter-arguments.
-
-%Thanks to these operators, an empirical theory may argue in a way that depends on the counter-arguments each individual finds appealing
-%\commentYM{je ne comprends pas cette phrase, et en particulier le sens qu'il faut donner au terme "adjust"}.
-Instead of having to give a single decisive argument in support of its claims, the theory may react to exactly the counter-arguments that a given individual thinks relevant.
-
-Such theories achieve what has been announced, namely, their conclusions rest solely on a weak normative axiom and on empirically falsifiable claims. 
-Granted normative adequacy, if no falsification sequence exist for a given theory of \ac{DJ}, then it is valid, meaning that the propositions that it claims are \acp{DJ} are indeed \acp{DJ}.
-\Cref{sec:validity} defines formally the notion of falsification sequence and proves this central claim.
-
-This result permits to ensure that, under Normative adequacy, Validity is an empirical property.
-But it does not give a concrete way of arbitrating between conflicting theories.
-A supplementary important result, described in \cref{sec:compare}, is that when two theories disagree about incompatible propositions, one of the theories at least must fail some given sequence of empirical tests, which the proof describes.
-
-These arbitration tests can all be performed on a single individual and are robust against the hypothesis of memory, which suggest that arbitration between theories could be performed reasonably easily.
-By contrast, the falsification sequences used in the preceding result of \cref{sec:validity} may require to test unrelated paths on the same individual, which may be practically difficult, as acknowledged here above.
-I expect however that the second result, permitting to arbitrate between theories, will be more often used in practice, thus, that falsification tests of the previous kind will be comparatively rare.
-This article is content with the existence of a principled, systematic way of falsifying theories of \ac{DJ} and leaves to later studies the comparison of approaches from the practical point of view of easiness of falsifying them.
+Achieving practical knowledge of \acp{DJ} is tackled by introducing descriptive theories of \ac{DJ}, the subject of the next section.
 
@@
 In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
-A descriptive theory for a normative theory of \ac{DJ} is defined as a tuple $(\gleadsto, \dg)$, where ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation and $\dg$ is a defense relation; satisfying bounded depth.
+A descriptive theory for a normative theory of \ac{DJ} is defined as a tuple $(\gC, \gPhi)$, where $\gC \subseteq \powerset{I × \allhist × \Phi}$ is a falsifiable claim and $\gPhi \subseteq \Phi$ are the proposition that the theory claims are in the \acp{DJ} of the individuals.
+\commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi}
+
 These concepts are now defined formally.
 \commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}
+
+A claim $\gC \subseteq \powerset{I × \allhist × \Phi}$ represents the theory’s claim about the relation $\leadsto$: the theory claims that $\leadsto \in \gC$. 
+A claim $\gC \subseteq \powerset{I × \allhist × \Phi}$ is falsifiable iff
 

### 2020-12-08 simple.tex
Expl abstract claims, including overly complicated one

@@
 In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
-A descriptive theory for a normative theory of \ac{DJ} is defined as a tuple $(\gC, \gPhi)$, where $\gC \subseteq \powerset{I × \allhist × \Phi}$ is a falsifiable claim and $\gPhi \subseteq \Phi$ are the proposition that the theory claims are in the \acp{DJ} of the individuals.
+A descriptive theory $\gamma$ for a normative theory of \ac{DJ} is defined as a tuple $(\gC, \gPhi)$, where $\gC \subseteq \powerset{I × \allhist × \Phi}$ is a falsifiable claim, $\gPhi \subseteq \Phi$ are the propositions that the theory claims are in the \acp{DJ} of the individuals, and such that its falsifiable claim implies its validity.
 \commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi} 
-
 These concepts are now defined formally.
@@
 
-A claim $\gC \subseteq \powerset{I × \allhist × \Phi}$ represents the theory’s claim about the relation $\leadsto$: the theory claims that $\leadsto \in \gC$. 
-A claim $\gC \subseteq \powerset{I × \allhist × \Phi}$ is falsifiable iff
-
-An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ defines the set of supported  propositions and, for each supported propositions, the set of initial arguments for these propositions.
-More precisely, let $\gpropse$, the range of ${\gleadsto}$, be called the propositions \emph{supported} by the descriptive theory.
-Given such a supported proposition $\prop \in \gpropse$, let $\gleadstoinv(\prop) = \set{\ar \in \allargs \suchthat \ar \gleadsto \prop}$ be called the initial arguments in favor of $\prop$.
-
-A defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ is a right-unique relation, thus given any $\ar \in \allargs, \hist \in \allhist$, $\dg(\ar, \hist)$ is empty or is a singleton.
-%, and must satisfy $\ar \notin \histend ⇒ \dg(\ar, \hist) = \emptyset$.
-As is usual for right-unique relations, I write $\dg(\ar_0, \hist) = \ar_1$ instead of $\dg(\ar_0, \hist) = \set{\ar_1}$.
-Say that $\ar_1$ defends $\ar_0$ iff $\exists \hist \suchthat \dg(\ar_0, \hist) = \ar_1$.
-Define $\dg(\ar) = \dfp(\ar) = \dg(\ar, \allhist) = \set{\dg(\ar, \hist) \suchthat \hist \in \allhist} \subseteq \allargs$ as all the defenders of $\ar$.
-The relation $\dg$ defines the argumentation strategy of the theory.
-Informally speaking, its role is to adapt the arguments the theory produces to the reactions of the individual it is trying to convince.
-Assuming the theory has played an argument $\ar_0$ and a path $\hist$ challenges some of the conclusions this argument supports (as judged by the individual), $\dg(\ar_0, \hist)$ is the argument that the theory plays as a counter-argument to the path $\hist$.
-%The condition that when $\dg(\ar_0, \hist)$, $\ar_0 \in \histend$ is imposed for simplicity: as will appear, an argument $\ar_0$ needs defense only when it is challenged by some path $\hist \suchthat \ar_0 \in \histend$, thus, letting $\dg$ define counter-arguments to paths not satisfying this condition would be of no use.
-
-This mechanism permits to define defenders of defenders of an argument, $\dg(\dg(\ar))$, defenders of defenders of defenders of an argument, … 
-For the results to be presented here to hold, an empirical theory must be a priori restricted in the maximal “depth” of its argumentation strategy, in the following sense. 
-\commentYM{ok soit, ça semble raisonnable, mais tu n'as pas de raison plus forte, j'adopterais une formulation plus modeste et ouverte, du genre "ça semble souhaitable"}
-Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
-The bounded depth condition on a descriptive theory imposes that
-$\exists k \in \N \suchthat (\dg)^k(\gleadstoinv(\allprops)) = \emptyset$.
-The smallest such $k$ is called the depth of the theory.
-
-Here is an example of a theory that does not use an argumentation strategy, but simply plays an argument that it claims is decisive for everybody.
+A claim $\gC \subseteq \powerset{I × \allhist × \Phi}$ represents the theory’s claim about the relation $\leadsto$: the theory claims that ${\leadsto} \in \gC$.
+Such a claim is required to be falsifiable, which is defined as follows.
+Observations of the relation $\leadsto$ can in general include positive statements, of the form $\hist \ileadsto \phi$, and negative ones, of the form $\hist \nileadsto \phi$.
+(One way to obtain such negative observations is to use an incompatible proposition $\phi'$ and deduce from $\hist \ileadsto \phi'$ that $\hist \nileadsto \phi$.) A relation $R \subseteq I × \allhist × \Phi$ is compatible with the positive observations $O \subseteq I × \allhist × \Phi$ and the negative observations $O' \subseteq I × \allhist × \Phi$ iff $O \subseteq R \land R \cap O' = \emptyset$.
+The claim $\gC$ is said to be falsifiable iff there exists finite set of observations $O, O' \subseteq I × \allhist × \Phi$ such that $\forall R \subseteq I × \allhist × \Phi \suchthat O \subseteq R \land R \cap O' = \emptyset$: $R \notin \gC$.
+In such a case, no possible relation $R$ compatible with the observations $O, O'$ are in $\gC$; in other words, the observations $O, O'$ prove that the claim that ${\leadsto} \in \gC$ is false.
+
+The notion of validity permits to relate the falsifiable claim of a theory, $\gC$, and the set of propositions it supports, $\gPhi$.
+\begin{definition}[Validity]
+	An empirical theory is \emph{valid} iff $\forall i \in I, \gPhi \subseteq \iprops$.
+\end{definition}
+The required relationship is as follows: it is required that, assuming normative acceptability, if ${\leadsto} \in \gC$, then the theory is valid.
+
+\begin{example}[Two claims]
+	Given a normative theory and $\phi \in \Phi$, the claim $C_1 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \exists \ar \in \allargs \suchthat \ar \ileadstost \phi}$ corresponds to claiming that for all individuals $i \in I$, some argument is $i$-decisive for $\phi$.
+If the set of arguments is infinite, $C_1$ is not falsifiable.
+	Given $\ar \in \allargs$ and $\phi \in \Phi$, the set $C_2 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \ar \ileadstost \phi}$ denotes the claim that all individuals will consider the argument $\ar$ as decisive for $\phi$.
+This claim is falsified by any observation such that $\hist \nileadsto \phi$ for some $\hist \in \allhist$ with $\ar \in \histend$, thus, $C_2$ is falsifiable.
+
+	Consider the pairs $(C_1, \set{\phi})$ and $(C_2, \set{\phi})$: only the second one constitutes a descriptive theory.
+Both pairs satisfy the requirement that, assuming normative adequacy, if $\leadsto \in \gC$, then $\forall i \in I: \phi \in \iprops$ (with $\gC = C_1$ or $\gC = C_2$), but $C_1$ fails to be falsifiable.
+\end{example}
+
+Returning to our running scenario permits to give more concrete examples. Here is an example of a theory that simply claims that a given argument is decisive for everybody.
 \begin{example}[Constant argumentation]
-	Given the normative theory of \cref{ex:twolott}, define ${\gleadsto} = \set{(\ar_0, D > P)}$ and $\dg = \emptyset$. This defines a descriptive theory of depth $1$ for that normative theory.
+	Given the normative theory of \cref{ex:twolott}, and the argument $\ar_0$ as defined there, define $\gC = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I: \ar_0 \ileadstost D > P}$ and $\gPhi = \set{D > P}$.
+The pair $(\gC, \gPhi)$ is a descriptive theory for that normative theory.
 \end{example}
+
+The following example illustrates that a descriptive theory need not claim that a given argument will convince everybody.
 
@@
 	Define a normative theory as in \cref{ex:twolott}, with an extended set of arguments: define $\allargs$ as the set of all strings.
-(This correspondingly changes $\allhist$ and thus $\ileadsto$, which must be extended to its new domain.) Define $\ar_0$ as in \cref{ex:twolott}.
+(This correspondingly changes $\allhist$ and thus $\ileadsto$, which must be extended to its new domain.)
+	Define $\ar_0$ as in \cref{ex:twolott}.
 	Define $\ar_\text{for$P$}$ as the text “We recommend to adopt $P$: it has a much higher probability of winning.”
-	Define ${\gleadsto} = \set{(\ar_\text{for$P$}, P > D)}$.
-	In order to define a counter-argument to $\ar_0$, given a real number $r \in \R$, define $\ar^r_\text{non-linear}$ as the text “$D$ is better than $P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
-For example, consider a choice between winning $r$ dollars with probability $0.8$ and winning $2r$ dollars with probability $0.4$.
-They have the same expected gain, but the first one is clearly preferrable.
+
+	The goal of this example is to define a theory that argues in favor of $P$ using two arguments.
+Following the intuition described just above, the theory will first attempt to use $\ar_\text{for$P$}$, a short argument that may be sufficient to convince a subset of individuals.
+But some may be left unconvinced because of the counter-argument $\ar_0$ in favor of $D$.
+In that case, the theory is ready to use another argument, more subtle, designed to counter $\ar_0$.
+The theory claims that at least one of these two arguments is decisive.
+	In order to define a counter-argument to $\ar_0$, define $\ar_\text{non-linear}$ as the text “$D$ is better than $P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
+For example, consider a choice between winning $10^6$ dollars with probability $0.8$ and winning $2 × 10^6$ dollars with probability $0.4$.
+These two lotteries have the same expected gain, but the first one is clearly preferrable.
 Therefore, we recommend to rather pick $P$ as it presents a much better chance of earning money”.
-(The value of $r$ and $2r$ is to be used in the relevant places in  the text.)
-	Define $\dg = \set{(\ar_\text{for$P$}, \hist, \ar^{10^6}_\text{non-linear}) \suchthat \hist \in \allhist \land \ar_0 \in \hist}$.
-This strategy anticipates a possible attack using $\ar_0$ against $\ar_\text{for$P$}$, and prepares $\ar^{10^6}_\text{non-linear}$ as a counter-argument.
-	This defines a descriptive theory of depth $2$.
+
+	Define $\gC = \set{{\leadsto} \suchthat \forall i \in I: \ar_\text{for$P$} \ileadstost P > D \lor \ar_\text{non-linear} \ileadstost P > D}$.
+	Define $\gPhi = \set{P > D}$.
+	Define the theory as $(\gC, \gPhi)$.
+We see that the claim $\gC$ is indeed falsifiable, as any set of observation including $\alpha^0 \ileadsto D > P$ and $\alpha^1 \ileadsto D > P$ such that $\ar_\text{for$P$} \in \histend^0 \land \ar_\text{non-linear} \in \histend^1$ will falsify the claim.
+
+	This example thus defines a theory that anticipates a possible attack using $\ar_0$ against $\ar_\text{for$P$}$, and prepares $\ar_\text{non-linear}$ as an alternative argument in case $\ar_\text{for$P$}$ does not convince an individual.
 \end{example}
-
-The following less trivial example of a descriptive theory illustrates a theory that claims to be able to answer an infinite number of arguments.
-This also shows that the bounded depth constraint does not imply finiteness of the relation $\dg$.
-\begin{example}[Infinite $\dg$]
+Refining such descriptive theories to let them articulate better the arguments and counter-arguments, and describing more realistic argumentative strategies, is left for future work.
+
+Here is a less trivial example of a descriptive theory that claims to be able to answer an infinite number of arguments.
+This shows that the requirement of being falsifiable using a finite set of observations does not imply a requirement of dealing only with finitely many arguments.
+\begin{example}[Arguing for $D$ against infinitely many counter-arguments]
 	\label{ex:infinite}
-	Define a normative theory and the arguments $\ar_0$ and $\ar^r_\text{non-linear}$ for any $r \in \R$ as in \cref{ex:twolottstrings}.
+	Suppose that a theorist is interested in defining a more general theory of \ac{DJ}, able to argue about lotteries spanning a wider range of outcomes than just $P$ and $D$.
+To keep this example reasonably small, as only the intuition is important here, I will describe this theory without introducing all the formal notations required to be fully precise.
+Assume that a normative theory is defined, similar to the one of \cref{ex:twolottstrings}, but with an enlarged set $\Phi$ covering a lottery space spanning small (a few dollars) to big (millions of dollars) monetary amounts.
+Assume the theorist postulates that the \acp{DJ} of the individuals in $I$ can be described using a utility function of money the form $u(x) = 1 - \frac{1}{e^{10^{-5}x}}$, where $x$ is the dollar amount.
+
+	For small monetary amounts, it is reasonable to consider such utility as linear, and thus the argument $\ar_\text{for$P$}$ defined previously can be used for arguing in favor of $P > D$.
+But this is insufficent, as individuals in $I$ may be convinced by a counter-argument similar to $\ar_\text{non-linear}$ defined above.
+Our example theorist wants to plan arguments for such individuals that go slightly deeper into the intricacies of utility theory, in order to keep them convinced that the theory applies generally and makes sense.
+But she also wants to keep the reasoning concrete by instantiating the reasoning on specific monetary amounts, such as $10^6$ dollars as used above.
+This argumentation should be adaptative, because similar arguments than $\ar_\text{non-linear}$ could be used, using other monetary amounts than $10^6$ dollars.
+
+	Given a real number $r \in \R$, define $\ar^r_\text{non-linear}$ as the same text than $\ar_\text{non-linear}$ but where the value of $r$ and $2r$ is used instead of $10^6$ and $2 × 10^6$.
 	Define ${\gleadsto} = \set{(\ar_0, D > P)}$.
-	Define $\ar_\text{linear}$ as the text “We agree that when the money amounts involved are large and the game is not repeated, there is no good reason to consider only expected gains when choosing a lottery.
-But in our case, the money amounts are small and the game is repeated.
-Therefore, expected gain is the right indicator to consider for a systematic and sound decision strategy.”
-	Define $+$ as the concatenation operator over strings.
-	Define $\dg = \set{(\ar_0, \ar^r_\text{non-linear}, \ar_0 + \ar_\text{linear}) \suchthat r \in \R}$.
-This strategy sets up the argument $\ar_0 + \ar_\text{linear}$ as an answer to any argument of the form described in \cref{ex:twolottstrings}, arguing for non-linearity of utility of money.
-	This defines a descriptive theory of depth $2$.
+	Define $\ar^r_\text{linear}$ as the text “Large monetary amounts should be “discounted” by transforming them before computing expectations using the lottery probabilities.
+For example, we attribute a “worth” of $1 - \frac{1}{e^{10^{-5} r}} = u(r)$ to the amount $\$ r$ and $1 - \frac{1}{e^{10^{-5} 2 r}} = u(2r)$ to the amount $\$ 2r$, hence, winning $\$ r$ with probability $0.8$ is worth $0.8 × u(r)$, which is equivalent to winning $\$ 2r$ with probability $\frac{0.8 × u(r)}{u(2r)}$.
+However, in the case of choosing between $P$ and $D$, the monetary amounts are small enough that such discounting does not change significantly the worth of the related lotteries.
+Therefore, expected gain (with discounted worth for large monetary amounts) is the right indicator to consider for a systematic and sound decision strategy, which leads us to recommend to choose D rather than P.” (The computed values of $u(r)$, $u(2r)$ and $\frac{0.8 × u(r)}{u(2r)}$ have to be used in the text in the relevant places.)
+
 \end{example}
@@
 \label{sec:validity}
-An empirical theory claims to be valid, in the following sense.
-\begin{definition}[Validity]
-	An empirical theory is \emph{valid} iff $\forall i \in I, \prop \in \gpropse: \prop \in \iprops$.
-\end{definition}
 To achieve this goal, it claims that it is able to produce decisive arguments for its supported propositions.
@@
 In such a case, no possible relation $R$ compatible with the observations $O, O'$ make the theory convincing; in other words, the observations $O, O'$ prove that the theory is not convincing.
-%\begin{example}[Two claims]
-%	Given a normative theory and $\phi \in \Phi$, the claim $C_1 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \exists \ar \in \allargs \suchthat \ar \ileadstost \phi}$ corresponds to claiming that for all individuals $i \in I$, some argument is $i$-decisive for $\phi$.
-If the set of arguments is infinite, $C_1$ is not falsifiable.
-%	Given $\ar \in \allargs$ and $\phi \in \Phi$, the set $C_2 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \ar \ileadstost \phi}$ denotes the claim that all individuals will consider the argument $\ar$ as decisive for $\phi$.
-This claim is falsified by any observation such that $\hist \nileadsto \phi$ for some $\hist \in \allhist$ with $\ar \in \histend$, thus, $C_2$ is falsifiable.
-%\end{example}
 

### 2020-12-08 simple.tex
Reused § about need for adaptive argumentation strategies

@@
 \end{example}
-Refining such descriptive theories to let them articulate better the arguments and counter-arguments, and describing more realistic argumentative strategies, is left for future work.
+
+Importantly, theories of \ac{DJ} must also be able to argue differently for different individuals.
+Even considering individuals with the same \ac{DJ}, different individuals might consider as decisive different arguments.
+Accepting non trivial propositions often requires to accept several sub-propositions, that together permit to be convinced of the acceptability of the proposition.
+Depending on which of these sub-propositions the individual already considers to be acceptable, parts of the argumentation can be omitted, and, perhaps, must be omitted: an overly long argument, stating many things that the listener already knows, has fewer chance to convince the listener than a short argument that goes straight to the point about which the listener doubts.
+%Mathematicians do not write their proofs starting from the axioms of set theory: they use results that they assume the reader already is aware of, and are ready (in principle) to supply the proofs of these intermediate results if a reader has doubt about some of them.
+In other words, what is needed for a theory of \ac{DJ} is not just a capacity to produce a unique decisive argument, with the claim that this argument will convince individuals in $I$, but rather a capacity to produce dynamically arguments that depend on which counter-arguments the individual finds appealing, with a claim that this dynamic argumentation strategy will succeed in convincing individuals in $I$.
 
@@
 \end{example}
+Refining such descriptive theories to let them articulate better the arguments and counter-arguments, and describing more realistic argumentative strategies, is left for future work.
 

### 2020-12-08 simple.tex
Removed complicated example and discussion about adaptive argumentation

--- 2020-12-08 simple.tex
@@
 Refining such descriptive theories to let them articulate better the arguments and counter-arguments, and describing more realistic argumentative strategies, is left for future work.
-
-Here is a less trivial example of a descriptive theory that claims to be able to answer an infinite number of arguments.
-This shows that the requirement of being falsifiable using a finite set of observations does not imply a requirement of dealing only with finitely many arguments.
-\begin{example}[Arguing for $D$ against infinitely many counter-arguments]
-	\label{ex:infinite}
-	Suppose that a theorist is interested in defining a more general theory of \ac{DJ}, able to argue about lotteries spanning a wider range of outcomes than just $P$ and $D$.
-To keep this example reasonably small, as only the intuition is important here, I will describe this theory without introducing all the formal notations required to be fully precise.
-Assume that a normative theory is defined, similar to the one of \cref{ex:twolottstrings}, but with an enlarged set $\Phi$ covering a lottery space spanning small (a few dollars) to big (millions of dollars) monetary amounts.
-Assume the theorist postulates that the \acp{DJ} of the individuals in $I$ can be described using a utility function of money the form $u(x) = 1 - \frac{1}{e^{10^{-5}x}}$, where $x$ is the dollar amount.
-
-	For small monetary amounts, it is reasonable to consider such utility as linear, and thus the argument $\ar_\text{for$P$}$ defined previously can be used for arguing in favor of $P > D$.
-But this is insufficent, as individuals in $I$ may be convinced by a counter-argument similar to $\ar_\text{non-linear}$ defined above.
-Our example theorist wants to plan arguments for such individuals that go slightly deeper into the intricacies of utility theory, in order to keep them convinced that the theory applies generally and makes sense.
-But she also wants to keep the reasoning concrete by instantiating the reasoning on specific monetary amounts, such as $10^6$ dollars as used above.
-This argumentation should be adaptative, because similar arguments than $\ar_\text{non-linear}$ could be used, using other monetary amounts than $10^6$ dollars.
-
-	Given a real number $r \in \R$, define $\ar^r_\text{non-linear}$ as the same text than $\ar_\text{non-linear}$ but where the value of $r$ and $2r$ is used instead of $10^6$ and $2 × 10^6$.
-	Define ${\gleadsto} = \set{(\ar_0, D > P)}$.
-	Define $\ar^r_\text{linear}$ as the text “Large monetary amounts should be “discounted” by transforming them before computing expectations using the lottery probabilities.
-For example, we attribute a “worth” of $1 - \frac{1}{e^{10^{-5} r}} = u(r)$ to the amount $\$ r$ and $1 - \frac{1}{e^{10^{-5} 2 r}} = u(2r)$ to the amount $\$ 2r$, hence, winning $\$ r$ with probability $0.8$ is worth $0.8 × u(r)$, which is equivalent to winning $\$ 2r$ with probability $\frac{0.8 × u(r)}{u(2r)}$.
-However, in the case of choosing between $P$ and $D$, the monetary amounts are small enough that such discounting does not change significantly the worth of the related lotteries.
-Therefore, expected gain (with discounted worth for large monetary amounts) is the right indicator to consider for a systematic and sound decision strategy, which leads us to recommend to choose D rather than P.” (The computed values of $u(r)$, $u(2r)$ and $\frac{0.8 × u(r)}{u(2r)}$ have to be used in the text in the relevant places.)
-
-\end{example}
-
-\subsection{Validity and falsification}
-\label{sec:validity}
-To achieve this goal, it claims that it is able to produce decisive arguments for its supported propositions.
-These arguments can vary according to the individual $i \in I$.
-Given an individual, the theory claims that a decisive argument will be systematically found by starting from an initial argument given by $\gleadsto$, and following a chain of defense defined by $\dg$ as required, depending on the paths that challenge the arguments produced along the way, as judged by the individual $i$.
-The property that a theory manages to systematically produce decisive arguments in such a way is named Convincingness.
-Defining it precisely requires to define first the notion of required arguments.
-
-Given $i \in I, \prop \in \gpropse$, define $\dgip(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \notin \histend \land \hist \nileadsto \phi} \subseteq \dg(\ar)$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\prop$.
-Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
-Define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\prop)$ under $\dgip$: $\gargs = \cup_{k \in \N} (\dgip)^k({\gleadstoinv}(\prop))$.
-The set $\gargs$ is the set of arguments required to convince $i$ of $\phi$.
-\begin{example}[Required arguments]
-	\label{ex:required}
-	Continuing \cref{ex:infinite}, define the subset of individuals that find some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ as the set of $i \in I$ such that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \ar^r_\text{non-linear} \in \range(\hist) \land \hist \nileadsto D > P$.
-	We see that for any $i$ in that set of individuals, $\gargs[D > P] = \set{\ar_0, \ar_0 + \ar_\text{linear}}$, and for any $i$ in the complementary set of individuals, $\gargs[D > P] = \set{\ar_0}$.
-\end{example}
-
-Given $\ar \in \gargs$, say that $\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend \land \hist \nileadsto \phi: d(\ar, \hist) ≠ \emptyset$.
-\begin{definition}[Convincingness]
-	An empirical theory is \emph{convincing} iff $\forall i \in I, \prop \in \gpropse, \ar \in \gargs: \ar$ $i$-defends $\prop$.
-\end{definition}
-\begin{example}[Convincingness]
-	Pursuing with \cref{ex:required}, that theory will be convincing iff either $i$ finds some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and both $\ar_0$ and $\ar_0 + \ar_\text{linear}$ $i$-defend $D > P$, or $i$ does not find any argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and $\ar_0$ $i$-defends $D > P$.
-
-	$\ar_0$ $i$-defends $D > P$ iff any argumentative path $\hist$ that contains $\ar_0$ towards its end and that does not lead $i$ to accept $D > P$ is such that $\dg(\ar_0, \hist) ≠ \emptyset$, or equivalently, is such that the theory has some argument to answer to $\hist$, or still equivalently, is such that it contains some $\ar^r_\text{non-linear}$.
-	This property mandates that no argumentative path has been “forgotten” in $\dg$: if some path is found that attacks $\ar_0$ successfully (thus $\ar_0 \in \histend \land \hist \nileadsto D > P$), and if the theory has nothing to answer to it (thus $\dg(\ar_0, \hist) = \emptyset$), then the theory is not Convincing.
-\end{example}
-
-It is now necessary to verify that the claim of convincingness is, first, falsifiable, and second, sufficient to yield validity.
-
-Let us first clarify what falsifiability formally means in our context.
-So far, convincingness is defined only for the “real” relation $\leadsto$; we now need it defined more generally.
-Given any relation $R \subseteq I × \allhist × \Phi$, say that a descriptive theory is convincing under $R$ whenever it is convincing, as defined above, but replacing $\leadsto$ by $R$.
-We can now speak counterfactually of the theory being convincing, or not, assuming the observable relation is $R$ instead of $\leadsto$. 
-Observations of the relation $\leadsto$ can in general include positive statements, of the form $\hist \ileadsto \phi$, and negative ones, of the form $\hist \nileadsto \phi$.
-(One way to obtain such negative observations is to use an incompatible proposition $\phi'$ and deduce from $\hist \ileadsto \phi'$ that $\hist \nileadsto \phi$.) A relation $R \subseteq I × \allhist × \Phi$ is compatible with the positive observations $O \subseteq I × \allhist × \Phi$ and the negative observations $O' \subseteq I × \allhist × \Phi$ iff $O \subseteq R \land R \cap O' = \emptyset$.
-The claim of convincingness is said to be falsifiable iff there exists finite set of observations $O, O' \subseteq I × \allhist × \Phi$ such that $\forall R \subseteq I × \allhist × \Phi \suchthat O \supseteq R \land R \cap O' = \emptyset$, the theory is not convincing under $R$.
-In such a case, no possible relation $R$ compatible with the observations $O, O'$ make the theory convincing; in other words, the observations $O, O'$ prove that the theory is not convincing.
-
-The following theorem states that the descriptive theories defined here are falsifiable, unless they state nothing about anybody’s \ac{DJ}.
-\Cref{sec:prooffals} proves it and describes the set of falsifiers of such theories.
-This theorem implicitly assumes full observability, that is, it supposes that any positive or negative observations are in principle observable and thus available for falsification attempts.
-Further works should investigate to which extent this hypothesis can be relaxed.
-\begin{theorem}
-	\label{th:convfals}
-	The claim of convincingness is falsifiable iff ${\gleadsto} ≠ \emptyset$.
-\end{theorem}
-It can also be seen that if a theory is not constrained in its depth, its claim of convincingness may be unfalsifiable, thus the hypothesis of finite depth is required to obtain this theorem.
-The formal proof of this fact is omitted because it is not especially enlightening; that this fact holds can be seen by examining the use of this hypothesis in the proof of \cref{th:convfals}.
-
-Only remains now to prove that convincingness, together with normative adequacy, is sufficient to obtain validity. The proof is also provided in \cref{sec:prooffals}.
-\begin{theorem}
-	\label{th:convvalid}
-	A normatively adequate empirical theory that is convincing is valid.
-\end{theorem}
-
-\subsection{Effectively comparing models}
-\label{sec:compare}
-Recall from \cref{sec:coh} that $\incompat = \set{(\prop, \prop') \suchthat \forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'}$ denotes the set of pairs of incompatible propositions.
-\commentOC{Does this mandate completeness?}
-Given two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $(\prop, \propbar) \in \incompat$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$.
-Say that the theories are incompatible iff there is at least one pair $(\prop, \propbar) \in \incompat$ that they disagree about.
-
-A path $\histp$ starts with a path $\hist$ iff $\card{\histp} ≥ \card{\hist}$ and $\forall k \in \intvl{1, \card{\hist}}: \histp_k = \hist_k$.
-An increasing sequence of paths is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N$, of paths, 
-such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$.
-
-\begin{theorem}
-	\label{th:proc}
-	Given two incompatible empirical theories for a given normative theory, $\gamma = (\gleadsto[\gamma], \gbeats[\gamma], \alldargs_\gamma, \dbeats[\gamma], +_\gamma)$ and $\delta = (\gleadsto[\delta], \gbeats[\delta], \alldargs_\delta, \dbeats[\delta], +_\delta)$ and given any $i \in I$, there exists a procedure that falsifies one of these theories, queries only $i$, and queries $i$ only about some increasing sequence of paths.
-\end{theorem}
-That procedure is described in \cref{sec:proc}.
 

### 2020-12-09 simple.tex
Some notes about a requirement about the falsification concept, currently not met.

@@
 
+TODO distinguigh: exists real relation $\leadsto$ suchthat exists observations that show the claim is false VS forall relations $\leadsto$ not in C, exists observations that show the claim is false.
+If I claim "a is dec for phi", if this is false, it is possible to show it (second case); but if I claim "a is dec for phi AND some argument is decisive for phi'" (or "$\alpha \ileadsto \phi$ and some argument is decisive for phi"), then the first case is satisfied, but not the second one: if indeed $\alpha \ileadsto \phi$ but NO arg dec, it is impossible to observe the falsity of the claim.
+Note that the first requirement is satisfied by BR but not the second one.
+
 The notion of validity permits to relate the falsifiable claim of a theory, $\gC$, and the set of propositions it supports, $\gPhi$.
@@
 \subsection{Representing deliberated preferences}
+A normative theory of deliberated choice is a normative theory of DJ using propositions of a certain form and a specific protocol of observation.
+
 Let $\allalts$ be a set of alternatives.
@@
 The observation protocol goes as follows.
-Given $i \in I$, $\emptyset ≠ B \subseteq \allalts$ and $\hist \in \allhist$, the individual $i$, after having been presented the arguments in the sequence $\hist$, is asked to choose among a subset of elements from $B$ among which she is indifferent.
+Given $i \in I$, $\emptyset ≠ B \subseteq \allalts$ and $\hist \in \allhist$, the individual $i$, after having been presented the arguments in the sequence $\hist$, is asked to choose a subset of elements from $B$ among which she is indifferent.
 Define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses after exposure to $\hist$.

### 2020-12-09 simple.tex
Attempt about falsification

@@
 A claim $\gC \subseteq \powerset{I × \allhist × \Phi}$ represents the theory’s claim about the relation $\leadsto$: the theory claims that ${\leadsto} \in \gC$.
-Such a claim is required to be falsifiable, which is defined as follows.
+Such a claim is required to be falsifiable.
+Defining falsification formally require to consider the relationship between the real relation $\leadsto$ and what one can know about it through observations.
+
+Recall that $\leadsto$ will in general not be known in its entirety, but can be queried through observations.
 Observations of the relation $\leadsto$ can in general include positive statements, of the form $\hist \ileadsto \phi$, and negative ones, of the form $\hist \nileadsto \phi$.
-(One way to obtain such negative observations is to use an incompatible proposition $\phi'$ and deduce from $\hist \ileadsto \phi'$ that $\hist \nileadsto \phi$.) A relation $R \subseteq I × \allhist × \Phi$ is compatible with the positive observations $O \subseteq I × \allhist × \Phi$ and the negative observations $O' \subseteq I × \allhist × \Phi$ iff $O \subseteq R \land R \cap O' = \emptyset$.
-The claim $\gC$ is said to be falsifiable iff there exists finite set of observations $O, O' \subseteq I × \allhist × \Phi$ such that $\forall R \subseteq I × \allhist × \Phi \suchthat O \subseteq R \land R \cap O' = \emptyset$: $R \notin \gC$.
-In such a case, no possible relation $R$ compatible with the observations $O, O'$ are in $\gC$; in other words, the observations $O, O'$ prove that the claim that ${\leadsto} \in \gC$ is false.
+(One way to obtain such negative observations is to use an incompatible proposition $\phi'$ and deduce from $\hist \ileadsto \phi'$ that $\hist \nileadsto \phi$.)
+Assuming (possibly counterfactually) that $R \subseteq I × \allhist × \Phi$ is the “real” relation $\leadsto$, the possible observations are $(O, O') \suchthat O, O' \subseteq I × \allhist × \Phi \land [O \subseteq R] \land [R \cap O' = \emptyset]$; and conversely, once we have gathered some observations $(O, O')$, we know that ${\leadsto} \in \set{R \subseteq I × \allhist × \Phi \suchthat O \subseteq R \land R \cap O' = \emptyset}$.
+
+A claim about ${\leadsto}$ being included in some given set is said to be falsifiable iff either it is true, or it is possible to prove it false using a finite set of observations.
+Formally, the claim $\gC \subseteq \powerset{I × \allhist × \Phi}$ is falsifiable iff $\forall R \notin \gC: \exists \text{ finite sets } O, O' \subseteq I × \allhist × \Phi \suchthat \forall R' \subseteq I × \allhist × \Phi \suchthat O \subseteq R' \land R' \cap O' = \emptyset: R' \notin \gC$.
+In such a case, no possible relation $R'$ compatible with the observations $O, O'$ are in $\gC$; in other words, the observations $O, O'$ prove that the claim that ${\leadsto} \in \gC$ is false.
 

### 2021-04-18 simple.tex
Some defs and somewhat rewritten intro

@@
 \begin{document}
-\title{Toward theories of deliberated preferences}
+\title{A definition of descriptive theories with normative power}
 \author{Olivier Cailloux}
@@
 \section{Introduction} 
-Decision theoretic approaches in economy divide into (at least) two sub-fields.
+Decision theoretic approaches in economy are classically divided into normative and descriptive approaches.
 Normative approaches aim at prescribing decision behavior; descriptive approaches aim at describing decision behavior.
-This partition is not always (depending on the authors) considered a complete cover of decision theoretic approaches in economy, but it is definitely considered disjoint.
+These two goals are generally considered incompatible: what is normative is not to be judged on descriptive grounds, and conversely.
+(Some authors consider prescription as the art of using descriptive insights to inform recommendation \citep{bell_decision_1988}, a view that also considers the normative aim as distinct to the descriptive aim.)
 
 As a result, normative approaches are difficult to validate: being considered as non-descriptive in their goal, normative claims cannot be submitted to empirical tests that would permit to verify or falsify them.
-Instead, the validity of a normative approach is to be determined by examining the convincingness power of the normative axioms on which it rests.
+Observing a behavior that deviates from a prescribed norm can be taken as a sign that the norm is useful: a decision maker does not hire analysts just to be prescribed the choice that she would have naturally opted for.
+Instead, the validity of a normative approach is generally considered to be determined by examining the convincingness power of the normative axioms on which it rests.
 \commentYM{par qui ? dans le cadre de l'analyse ou en amont ? et pourquoi sur la seule base de la soundness de l'axiome ? pourquoi pas sur la base de ses implications dans des cas concrets ?}
 This validity criterion is unsatisfactory, as it is unable to settle disputes between experts when they arise.
-In supplement, agreement between experts in decision theory is arguably not enough to ground the practical applicability of some normative axioms: it is desirable to check that decision makers to which the prescription is addressed agree with the particular instanciation of these axioms in the specific decision problem under study.
+In supplement, agreement between experts in decision theory is arguably not enough to ground the practical applicability of some normative axioms: one must ensure that decision makers to which the prescription is addressed agree with the particular instanciation of these axioms in the specific decision problem under study.
 But no systematic, formally defined procedure has been proposed to proceed with this check, to the best of my knowledge.
@@
 Such approaches can be validated by confronting their predictions to empirical data.
-When two descriptive theories disagree on their predictions, it is often possible to show that at least one of them is wrong with a suitable experiment.
+When two descriptive theories disagree on their predictions, it is in principle possible to show that at least one of them is wrong with a suitable experiment.
 \commentYM{quelle différence avec les implications empiriques d'une théorie normative ?}
-Alàs, descriptive approaches as currently existing in decision theory are not suitable to obtain valid prescriptions.
+\commentOC{Est-ce plus clair maintenant ?}
+Alàs, descriptive approaches as currently existing in decision theory are not suitable to obtain valid prescriptions, as we do not merely want to prescribe natural, unreflectful behavior.
 
@@
 
-It is by no means my intent to claim that descriptive approaches never face validation difficulties.
-Experimental tests to arbitrate between theories may not be feasible in practice, descriptions are not always solely about the future, falsificationist approaches in turn raise epistemological difficulties, and so on.
-Correspondingly, the possible confrontation to empirical data of the theories defined here is no magical means to definitively solve every difficulty about validation.
-My less naïve claim, that should suffice to motivate the present endeavor, is that it is often a good thing for a theory to make empirically testable claims, from the point of view of the possibilities of solving disputes and validating theories.
-
-As the plural indicates, this article defines a kind of theory, namely, theories of \ac{DJ}, not a specific theory of \ac{DJ}.
+This article defines theories of \ac{DJ} in general, not a specific theory of \ac{DJ}.
 Specific theories of \ac{DJ} are tailored to a set of situations and yield claims relevant to those situations.
@@
 This article adopts a more general point of view.
-It proposes a definition of what theories of \ac{DJ} should look like, and proves claims that hold for any specific theory of \ac{DJ}, showing that such theories are indeed normative and descriptive.
+It defines a general form for theories of \ac{DJ}, and proves claims that hold for any specific theory of \ac{DJ}, showing that such theories are indeed normative and descriptive in some technical sense to be defined.
 
@@
 
-\begin{example}[Two theories about two alternatives]
-	Consider a set $\alts = \set{\alt_1, \alt_2}$ of two alternatives whose evaluations on two criteria (say, price and speed, for concreteness), are $(g_1(\alt_1), g_2(\alt_1))$ and $(g_1(\alt_2), g_2(\alt_2))$, respectively, where $g_i: \alts → \R$ are functions giving the performance of alternatives on the criterion $i$.
-
-	Two theories of \ac{DJ} are opposed on their prediction of the reflexive choice of a given set of individuals $I$ having to choose one alternative among $\alts$.
-	The \emph{satisfycing} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever alternative is satisfying (and be indifferent if they are both satisfying or if none of them is).
-An alternative $\alt$ is satisfying iff $g_1(\alt) < t_1 \land g_2(\alt) > t_2$, where $t_1$ and $t_2$ are two real numbers chosen by the theorist.
-	The \emph{additive} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever alternative $\alt$ maximises $v(\alt) = v_1(g_1(\alt)) + v_2(g_2(\alt))$, where $v_i: \R → \R$ are functions  chosen by the theorist.
-
-	Assume that the theories disagree, thus, that $\alt_1$ is satisfying and $\alt_2$ is not (say, it fails on the speed criterion), but $v(\alt_2) > v(\alt_1)$.
+\begin{example}[Two disagreeing theories]
+	\label{ex:two}
+	Consider a set $\allalts$ of items evaluated on two criteria, say, price and speed, using functions $g_1$ and $g_2$, where $g_i: \allalts → \R$ measures the performance of items on the criterion $i$, and a set of individuals $I$ whose reflective choice among $\allalts$ we are interested in.
+	Consider the following the theories of \ac{DJ}.
+
+	The \emph{satisfycing} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever item is satisfying (and be indifferent if they are both satisfying or if none of them is).
+An item $\alt$ is satisfying iff $g_1(\alt) < t_1 \land g_2(\alt) > t_2$, where $t_1$ and $t_2$ are two real numbers determined by the theorist.
+
+	The \emph{additive} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever item $\alt$ maximises $v(\alt) = v_1(g_1(\alt)) + v_2(g_2(\alt))$, where $v_i: \R → \R$ are functions  chosen by the theorist.
+
+	Consider a set $\alts = \set{\alt_1, \alt_2} \subset \allalts$ of two items, and assume the two theories of \ac{DJ} are opposed on their prediction of the reflexive choice of individuals having to choose one item among $\alts$.
+Say, $\alt_1$ is satisfying and $\alt_2$ is not, failing on the speed criterion; while $v(\alt_2) > v(\alt_1)$.
+
 	To determine which theory is right, it is insufficient to simply observe what an individual $i \in I$ effectively chooses.
@@
 
-	The basic intuition on which this article is based is that determining which theory is right requires to present both arguments to $i$, then let her choose one alternative in $\alts$, to see which argument she finds more convincing.
+	The basic intuition on which this article is based is that determining which theory is right requires to present both arguments to $i$, then let her choose one item in $\alts$, to see which argument she finds more convincing.
 \end{example}
-%The proposed approach starts with this intuition that the reaction of individuals to arguments should matter, and presents a general solution to the problem of capturing reflective judgments or choices.
+
+The proposed approach starts with this intuition that the reaction of individuals to arguments should matter, and presents a general solution to the problem of capturing reflective judgments or choices.
 Contrary to the simplistic situation of \cref{ex:two}, this solution must allow to confront more than just two arguments or two theories.
@@
 
-The important question about how the parameters $t_i$ and $v_i$ of these illustrative theories would be determined is left aside in this article.
-This article aims at defining and studying theories of \ac{DJ} in general, not at proposing a way of building a specific theory of \ac{DJ}.
-%For this example, one can assume that these parameters are determined on the basis of observation of the behavior of some population in some similar circumstances.
-
-The approach it adopts is the following.
-First, it introduces a normative axiom that mandates that whatever propositions the \ac{DM} accepts when reasoning carefully can be prescribed.
+The pursued path is as follows.
+This article introduces first a normative axiom that mandates that whatever propositions the \ac{DM} accepts when reasoning carefully can be prescribed.
 This notion of careful acceptability is defined formally on the basis of an observable relation that captures the reactions of the \ac{DM} to arguments.
@@
 In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
-A descriptive theory $\gamma$ for a normative theory of \ac{DJ} is defined as a tuple $(\gC, \gPhi)$, where $\gC \subseteq \powerset{I × \allhist × \Phi}$ is a falsifiable claim, $\gPhi \subseteq \Phi$ are the propositions that the theory claims are in the \acp{DJ} of the individuals, and such that its falsifiable claim implies its validity.
+A descriptive theory $\gamma$ for a normative theory of \ac{DJ} is defined as a tuple $(\gC, \gPhi)$, where $\gC \subseteq \powerset{I × \allhist × \Phi}$ is a falsifiable claim, $\gPhi \subseteq \Phi$ are the propositions that the theory claims are in the \acp{DJ} of the individuals, and such that its falsifiable claim implies its convincingness.
 \commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi} 
@@
 
-A claim about ${\leadsto}$ being included in some given set is said to be falsifiable iff either it is true, or it is possible to prove it false using a finite set of observations.
+A claim that ${\leadsto}$ is included in some given set is said to be falsifiable iff, assuming the claim is false, and whatever the real relation is that makes it false, it is possible to prove that the claim is false using a finite set of observations.
 Formally, the claim $\gC \subseteq \powerset{I × \allhist × \Phi}$ is falsifiable iff $\forall R \notin \gC: \exists \text{ finite sets } O, O' \subseteq I × \allhist × \Phi \suchthat \forall R' \subseteq I × \allhist × \Phi \suchthat O \subseteq R' \land R' \cap O' = \emptyset: R' \notin \gC$.
@@
 
-TODO distinguigh: exists real relation $\leadsto$ suchthat exists observations that show the claim is false VS forall relations $\leadsto$ not in C, exists observations that show the claim is false.
-If I claim "a is dec for phi", if this is false, it is possible to show it (second case); but if I claim "a is dec for phi AND some argument is decisive for phi'" (or "$\alpha \ileadsto \phi$ and some argument is decisive for phi"), then the first case is satisfied, but not the second one: if indeed $\alpha \ileadsto \phi$ but NO arg dec, it is impossible to observe the falsity of the claim.
-Note that the first requirement is satisfied by BR but not the second one.
+%Distinguish this condition from: $\exists R, finite O such that C is proven false$: the claim "a is dec for phi AND some argument is decisive for phi'" (or "$\alpha \ileadsto \phi$ and some argument is decisive for phi") satisfies this weaker condition, but it should not be considered falsifiable as it is not necessarily possible to distinguish it empirically from a disagreeing theory: if indeed $\alpha \ileadsto \phi$ but NO arg dec, it is impossible to observe the falsity of the claim.
+Note that the weaker requirement is satisfied by BR but not the stronger one.
+
+Finally, a descriptive theory must ensure that its falsifiable claim implies it being convincing, it the sense of being able to show the existence of decisive arguments in favor of its supported propositions, whatever the true relation is.
+So far, $\ar$ being a decisive argument for $\phi$ from the point of view of $i$ is denoted $\ar \ileadstost \phi$, this being defined on the basis of the real relation ${\leadsto}$.
+We need to extend this definition and notation: assuming the observable relation would be any $R \subseteq I × \allhist × \Phi$ (and not specifically $\leadsto$), let $\ar \ileadstost^R \phi$ denote the fact that $\ar$ is a decisive argument for $\phi$ from the point of view of $i$ when the observable relation is $R$.
+\begin{definition}[Conditional convincingness]
+	A pair $(\gC, \gPhi)$ is conditionally convincing iff $\forall R \in \gC, i \in I, \phi \in \gPhi: \exists \ar \in \allargs \suchthat \ar \ileadstost^R \phi$.
+\end{definition}
+TODO use notation: $a \suchthat \set{\hist \in \allhist \suchthat \ar \in \histend} R_i \phi$.
 
@@
 \end{definition}
-The required relationship is as follows: it is required that, assuming normative acceptability, if ${\leadsto} \in \gC$, then the theory is valid.
+The condition that the falsifiable claim entails convincingness is equivalent to the requirement that, assuming normative acceptability, if ${\leadsto} \in \gC$, then the theory is valid.
 
@@
 	Consider the pairs $(C_1, \set{\phi})$ and $(C_2, \set{\phi})$: only the second one constitutes a descriptive theory.
-Both pairs satisfy the requirement that, assuming normative adequacy, if $\leadsto \in \gC$, then $\forall i \in I: \phi \in \iprops$ (with $\gC = C_1$ or $\gC = C_2$), but $C_1$ fails to be falsifiable.
+Both pairs satisfy the requirement that if $\leadsto \in \gC$, then $\forall i \in I: \phi \in \iprops$ (with $\gC = C_1$ or $\gC = C_2$), but $C_1$ fails to be falsifiable.
 \end{example}
@@
 Refining such descriptive theories to let them articulate better the arguments and counter-arguments, and describing more realistic argumentative strategies, is left for future work.
+
+Given any two disagreeing descriptive theories $(\gC, \gPhi)$ and $(\gC[δ], \gPhi[δ])$ for a given normative theory and any two propositions $\prop, \propbar \in \incompat$, say that these two theories disagree about $(\prop, \propbar)$ iff $[\prop \in \gPhi ⇔ \propbar \notin \gPhi[δ]]$.
+Say that two theories disagree iff there exists some propositions about which they disagree.
+
+If two theories disagree, then it is possible to prove one of them wrong using a finite set of observations.
+\begin{proposition}
+	Consider two disagreeing descriptive theories $(\gC, \gPhi)$ and $(\gC[δ], \gPhi[δ])$ for a given normative theory.
+There exists a finite set of observations that prove $\gC$ false, or that prove $\gC$ false.
+\end{proposition}
+\begin{proof}
+	If they disagree, then $\gC \cap \gC[δ] = \emptyset$, otherwise, pick any $R \in \gC \cap \gC[δ]$, and obtain, using convincingness, the existence of decisive arguments for both $\prop$ and $\propbar$, which is impossible as seen in \cref{th:protcoh}.
+
+	As $\gC \cap \gC[δ] = \emptyset$, then at least one of these propositions is true: ${\leadsto} \notin \gC$ or ${\leadsto} \notin \gC[δ]$.
+In both cases, thanks to falsifiability, the existence is proven.
+\end{proof}
 
@@
 \appendix
+\section{Optional supplements}
+It is by no means my intent to claim that descriptive approaches never face validation difficulties.
+Experimental tests to arbitrate between theories may not be feasible in practice, descriptions are not always solely about the future, falsificationist approaches in turn raise epistemological difficulties, and so on.
+Correspondingly, the possible confrontation to empirical data of the theories defined here is no magical means to definitively solve every difficulty about validation.
+My less naïve claim, that should suffice to motivate the present endeavor, is that it is often a good thing for a theory to make empirically testable claims, from the point of view of the possibilities of solving disputes and validating theories.
+
+The important question about how the parameters $t_i$ and $v_i$ of these illustrative theories would be determined is left aside in this article.
+This article aims at defining and studying theories of \ac{DJ} in general, not at proposing a way of building a specific theory of \ac{DJ}.
+%For this example, one can assume that these parameters are determined on the basis of observation of the behavior of some population in some similar circumstances.
+
 \section{Finiteness}

### 2021-04-30 simple.tex
dos2unix EOL
Started short version

@@
 \begin{document}
-\title{A definition of descriptive theories with normative power}
+\title{A definition of descriptive theories of choice with normative power}
 \author{Olivier Cailloux}
@@
 \section{Introduction} 
+This article defines theories that are prescriptive and empirical.
+They are prescriptive in that the claim $a \succ b$ has the semantics of recommending choosing $a$ rather than $b$ when both are available.
+They are empirical in that the validity of their recommendations rests on the basis of a mild axiom (compared to usual normative theories such as Savage’s Expected Utility theory) together with empirical claims, thus, claims that observations can falsify.
+
+For conceptual clarity, I will focus on the case of a single binary decision to take, akin to a choice situation facing a bundle of two objects among which exactly one must be adopted.
+
+\section{The model}
+Let $\Phi = \set{\phi, ¬\phi}$ represent the decision at stake. Let $I$ be a set of individuals.
+
+A prescriptive theory is a tuple $(\allargs, {\allleadsto})$.
+$\allargs$ is a set of arguments. 
+Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments. A sequence of arguments is called an argumentative path, or simply a path.
+The function ${\allleadsto} \in \powersetz{\Phi}^{I × \allhist}$ associates to each individual and path a non-empty subset of $\Phi$.
+
+ which associates to each $i \in I$ an element of $\Phi$ or nothing, with the semantics that this decision is the right one for that individual or that the theory abstains from recommending.
+
+\appendix
+\section{Old introduction} 
 Decision theoretic approaches in economy are classically divided into normative and descriptive approaches.
@@
 
+\section{Normative theories (focused)}
+Define a normative axiom as a formal constraint on behavior that constrains behavior so as to yield valid prescription. 
+Define a descriptive axiom as a formal constraint on behavior interpreted as an empirical prediction, that is, as a claim that behavior (in some a priori described circumstances) satisfies the constraint.
+
+A normative axiom has to be accepted on the basis of its apparent adequacy to capture what is intuitively an acceptable requirement for a prescription to a \ac{DM}.
+In other words, it is not a hypothesis on the observable world: that the requirement holds cannot be proven by observation.
+Examples are given by the axioms of classical decision theories, when they are applied for prescription.
+Consider for example Savage’s sure thing principle.
+One can observe whether individuals unreflectively behave according to Savage’s sure thing principle, but even when they fail to, it can be said that this is because of a mistake: the normative status of an axiom is not hit by violations due to unreflective behavior.
+Such axioms are not falsifiable by behavioral observation.
+Conversely, observing that some axiom perfectly matches observed behavior, that empirical observation alone does not yield any validity to prescription based on that constraint: accepting the validity of a prescription rests on accepting the soundness of its reasoning, not on its ability to reflect natural behavior.
+
+Let us assume that some natural behavior is not to be prescribed.
+
+At least one such axiom is required to ground any prescription.
+Hence, no theory can be fully descriptive, and theories of \ac{DJ} make no exception.
+The proposed path out of this conundrum is to restrict normative axioms to a self-evident claim, and leave most of the constraining power to descriptive claims.
+
 The pursued path is as follows.
@@
 This notion of careful acceptability is defined formally on the basis of an observable relation that captures the reactions of the \ac{DM} to arguments.
-This requirement is described here as a normative axiom because it has to be accepted on the basis of its apparent adequacy to capture what is intuitively an acceptable requirement for a procedure aiming at prescribing to a \ac{DM}.
-In other words, it is not a hypothesis on the observable world: that the requirement holds cannot be proven by observation.
-It has, in that sense, a similar epistemological status as axioms of classical decision theories when they are applied for prescription, for example, Savage’s sure thing principle.
-Arguably, we can observe whether individuals unreflectively behave according to Savage’s sure thing principle, or any other decision-theoretic axiom, but even when they fail to, it can be said that this is because of a mistake: the normative status of an axiom is not hit by violations due to unreflective behavior.
-In that sense, such axioms are not falsifiable.
 
@@
 
-\appendix
 \section{Optional supplements}
@@
 Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count for falsifying a theory.
-In other words, it is desirable to capture exactly which sets of observations falsify the claim of convincingness. This will also provide a proof of \cref{th:convfals}.
+In other words, it is desirable to capture exactly which sets of observations falsify the claim of convincingness. This will also provide a proof of cref{th:convfals}.
 
@@
 \begin{proof}
-	First, from right to left, consider a falsification sequence $(\hist^{k + 1})_{k \in 2\N, k ≤ N}$ for some $N \in 2\N$, define, as in \cref{sec:validity}, $\args_{k + 1} = \gbeatsinv(\ar_k) \cap \range(\hist^{k + 1})$, $\dargs[k + 2] = \dbeatsinv(\args_{k + 1})$ and (for $k ≤ N - 2$) $\ar_{k + 2} = \ar_k + \dargs[k + 2]$, and let us show that $(i, \phi, \hist^{N + 1}, \ar_N)$ is a falsification instance.
+	First, from right to left, consider a falsification sequence $(\hist^{k + 1})_{k \in 2\N, k ≤ N}$ for some $N \in 2\N$, define, as in cref{sec:validity}, $\args_{k + 1} = \gbeatsinv(\ar_k) \cap \range(\hist^{k + 1})$, $\dargs[k + 2] = \dbeatsinv(\args_{k + 1})$ and (for $k ≤ N - 2$) $\ar_{k + 2} = \ar_k + \dargs[k + 2]$, and let us show that $(i, \phi, \hist^{N + 1}, \ar_N)$ is a falsification instance.
 This amounts to show that $\ar_N \in \gargs$, which can be done by observing that $\ar_0 \in \gargs$, and showing that, $\forall k \in 2\N, k ≤ N - 2$, $\ar_k \in \gargs ⇒ \ar_{k + 2} \in \gargs$.
-	Indeed, \cref{th:dpiconstr} applies with $\ar_k$ for $\ar_0$ and $\ar_{k + 2}$ for $\ar_2$.
+	Indeed, cref{th:dpiconstr} applies with $\ar_k$ for $\ar_0$ and $\ar_{k + 2}$ for $\ar_2$.
 As the second member of the equivalence is true by definition of a falsification sequence, $\ar_{k + 2} \in (\dip)(\ar_k)$, and because $\ar_k \in \gargs$, $\ar_{k + 2} \in \gargs$.
@@
 As $\ar_N \in \gargs$, $\ar_N \in (\dip)^N({\gleadstoinv}(\prop))$ (equalizing the indices $N$ wlog).
-Given $\ar_{k + 2} \in (\dip)^j({\gleadstoinv}(\prop))$, with $j > 0$, thus $\ar_{k + 2} \in \dip(\ar_k)$ for some $\ar_k \in (\dip)^{j - 1}({\gleadstoinv}(\prop))$, apply \cref{th:dpiconstr}, obtain $\hist_{k + 1}$.
+Given $\ar_{k + 2} \in (\dip)^j({\gleadstoinv}(\prop))$, with $j > 0$, thus $\ar_{k + 2} \in \dip(\ar_k)$ for some $\ar_k \in (\dip)^{j - 1}({\gleadstoinv}(\prop))$, apply cref{th:dpiconstr}, obtain $\hist_{k + 1}$.
 Iterate while $j > 0$.
@@
 
-\Cref{th:svalid} claims that a normatively adequate empirical theory that has no falsification sequence is valid. TODO prove it.
+Cref{th:svalid} claims that a normatively adequate empirical theory that has no falsification sequence is valid. TODO prove it.
 
@@
 \label{sec:proc}
-This section proves \cref{th:proc} constructively, by describing the sequence of tests that must be performed and showing that they must lead to falsifying one of the theories.
+This section proves cref{th:proc} constructively, by describing the sequence of tests that must be performed and showing that they must lead to falsifying one of the theories.
 To do this, the notion of challenge must be defined and a few simple lemmas are required.

### 2022-07-17 simple.tex
Dont remember

@@
 A prescriptive theory is a tuple $(\allargs, {\allleadsto})$.
+
 $\allargs$ is a set of arguments. 
+Throughout the article, $\N$ includes zero. %and $\N^* = \N \setminus \set{0}$. 
 Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments. A sequence of arguments is called an argumentative path, or simply a path.
-The function ${\allleadsto} \in \powersetz{\Phi}^{I × \allhist}$ associates to each individual and path a non-empty subset of $\Phi$.
-
- which associates to each $i \in I$ an element of $\Phi$ or nothing, with the semantics that this decision is the right one for that individual or that the theory abstains from recommending.
+A generic element of $\allhist$ is denoted by $\hist$ and called an argumentative path, or simply a path when this raises no ambiguity. Its length is denoted by $\card{\hist} \in \N$.
+Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$.
+Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}$, $\hist_k \in A$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
+
+The function ${\allleadsto}: I × \allhist → \powersetz{\Phi}$ associates to each individual and path a non-empty subset of $\Phi$.
+The case $\Phi$ is used to represent indifferent choice, in case this is observable.
+The observation that $\phi$ is considered among the best by $i$ considering $\alpha$ is represented by $\alpha \ileadsto \phi$, considering ${\ileadsto} \subseteq \allhist × \Phi$ as a binary relation.
+As usual with binary relations, $\hist \nileadsto \prop$ means $(\hist, \prop) \notin {\ileadsto}$.
+
+% which associates to each $i \in I$ an element of $\Phi$ or nothing, with the semantics that this decision is the right one for that individual or that the theory abstains from recommending.
+
+Given $\hist \in \allhist$, $\range(\hist) = \hist(\intvl{1, \card{\hist}})$ denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
+Let $\histend = \hist(\intvl{\max(1, \card{\hist} - 1), \card{\hist}})$ denote the set containing the last two arguments of the sequence $\hist$ if the sequence has at least two elements; the unique argument of the sequence if it has exactly one element; and the empty set if it is empty.
+
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto \prop$. 
+When $\ar \ileadstost \prop$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view. 
+Given any $i \in I$, when some argument is decisive for some proposition $\prop$, thus, when $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop$, the proposition is said to be acceptable, from $i$’s point of view.
+
+The following axiom permits the theory to have bite on what should be recommended to $i$. It says that it is sufficient that a proposition be acceptable to be in $i$’s \ac{DJ}.
+\begin{axiom}[Normative adequacy]
+%	\label{ax:norm}
+	$\forall i \in I, \prop \in \allprops: 
+		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \prop)] ⇒ \prop \in \iprops.$
+\end{axiom}
 

### 2022-07-17 simple.tex
A new hope

@@
 \begin{document}
-\title{A definition of descriptive theories of choice with normative power}
+\title{Theories of deliberated judgment}
 \author{Olivier Cailloux}
@@
 \section{Introduction} 
+Classical descriptive theories of choice in economics are limited to shallow observations.
+
 This article defines theories that are prescriptive and empirical.

### 2022-07-22 simple.tex
Clearer intro

@@
 \section{Introduction} 
-Classical descriptive theories of choice in economics are limited to shallow observations.
-
-This article defines theories that are prescriptive and empirical.
-They are prescriptive in that the claim $a \succ b$ has the semantics of recommending choosing $a$ rather than $b$ when both are available.
-They are empirical in that the validity of their recommendations rests on the basis of a mild axiom (compared to usual normative theories such as Savage’s Expected Utility theory) together with empirical claims, thus, claims that observations can falsify.
+Observing subjects performing acts of choice is the basis of much work in econometrics.
+Such acts have been used, among others, to give an observable basis to the concept of preference, thanks in part to the seminal work of Samuelson.
+Acts of choice are considered here in the broad sense of choice between courses of actions, encompassing the simple setting of choosing between various elementary consumption bundles as well as settings involving more abstract acts such as choosing between defection or cooperation in a game-theoretical setting.
+
+Most of these approaches consider only acts of choice that are performed spontaneously in the normal course of action of an individual, or that are given a specific frame depending on the psychological aspect that is to be studied.
+As an example of the former kind, typical willingness to pay studies asks the subject whether she prefers an object at some price or another object at another price, describing the objects in a way that is considered immediately understandable by the subject (or simply showing the objects).
+Examples of the latter kind include the celebrated work of Kahneman and Tversky.
+
+On the other hand, since at least the seminal work of Fishkin, another sort of judgment involving subjective desirability is emerging as also worth studying.
+These are judgments given by subjects after arguments in favor and against different possible stance have been considered.
+Such judgments may differ from immediate judgments of desirability given in natural conditions.
+Indeed, individuals may change opinion on the desirability of some course of action, and therefore revise their choice, while learning about the properties of objects, the consequences of some acts (or empirical knowledge useful to estimate the likelihood of some consequences), or the logical or empirical impossibilities between consequences (for example, in some situations, you can’t both pay less taxes and have better government provided services).
+This is particularly likely to happen when choosing among non everyday objects or acts whose consequences are not well known by the subject.
+
+While numerous articles have discussed the concept of deliberation in the last decades, it remains unsettled, to the best of my knowledge, how to observe a deliberated judgment, or, correspondingly, how to define this concept in a way that makes it amenable to empirical study, sufficiently precisely that any disagreement about someone’s deliberated judgment in a given context could be solved, at least in principle, by an empirical experiment.
+%This article is interested in defining the concept of deliberated judgementof a subject, as opposed to the classical one, that will henceforth be called her natural judgment, that is, the way that she chooses between acts when she does not face any arguments, i.e.,
+
+While the concept of deliberation in the deliberative democracy literature usually refers to multiple individuals debating, this article considers deliberation as related to a single individual at a time: an individual deliberates (in the sense of: carefully weights) the stance she considers most appropriate while being confronted to arguments.
+The deliberated judgment of an individual is thus defined with no requirement that the arguments be uttered by peers in a debate; they can be given by an automata, for example.
+In this sense, deliberated judgments come close to what Rawls calls reflective equilibrium (referring to an idea of Goodman), a concept that has much inspired the present proposal.
+
+To define deliberated judgments, one needs to start with the set of arguments under consideration, and the way the subject gets to know them, called hereafter the “exposure protocol”.
+As a result, we need always talk about the deliberated judgment \emph{given some exposure protocol}.
+The notion of argument invoked here is an extremely large one, including texts, images, sounds, experiences (a hiking trip), and so on: anything that can be transmitted to a subject qualifies as a possible argument.
+Such an “argument” need not even have the logical structure of what is considered a proper argument in argumentation theory, which permits to avoid having to take position on what is a correct argument, and permits to study wide enough conceptions of deliberated judgment, including those involving no paternalism: anything that influences the judgment of a subject may a priori be considered worth including in at least some conceptions of deliberated judgment.
+
+The dependence of the deliberated judgment concept on the exposure protocol yields a first qualification about the concept of deliberated judgments defined here when one desires to use it normatively: it is only as reasonable to call the resulting judgments “deliberate” in a normative sense as the exposure protocol is normatively relevant to deliberation.
+A sufficiently restricted, or even purposefully chosen, set of arguments may yield judgments that are only deliberate in the technical sense used here, but that pertain more to brain-washing than to reflective judgments.
+While it is indeed a long-term goal of this research stream to yield a normatively relevant conception of preference (appropriate, for example, for recommendation), it is not a claim of this article that anything that corresponds to deliberated judgments as defined here qualify as being appropriate for recommendation (or for any other normative use): much depends on the chosen exposure protocol.
+The goal of this article is, more modestly, one of a conceptual and practical clarification.
+It proposes a sharp distinction between the empirical content and the normative content of the concept of deliberated judgments: the definition proposed here transfers the full normative weight on the choice of the exposure protocol; and leaves the rest of the disagreements to empirical settling.
+This is methodologically akin, mutatis mutandis, to the axiomatic study of justice such as done in social choice, only replacing mathematical deduction with empirical claims.
+In social choice, the choice of axioms bears the full normative weight; once axioms are chosen, it is a matter of deduction which social choice rules (if any) correspond to that choice.
+In our case, once an exposure protocol is chosen, it is a pure empirical matter which deliberated judgments result.
+In supplement to a possibly helpful conceptual clarification, such a sharp separation may reveal practically useful for separation of concern as it permits to study deliberated judgments empirically under various exposure protocols independently of possible persistent disagreements about which norms are more appropriate for deliberation in which circumstances.
+
+The deliberated judgment of a subject is said to depend on the exposure protocol, that is, on the set of arguments and the way they are submitted to the subject, and not only on the set of arguments, because the very way that they are transmitted to the individual may affect her judgment differently.
+For example, reading an image description and showing an image to a subject may impress them differently.
+
+The exposure protocol defines a set of argument and, importantly, how arguments are sent to the subject and her subsequent choice observed.
+There is, as need be, no requirement on the internal process that occurs in the subject’s mind while she (possibly) processes the arguments, as it is not desirable to assume that the internal process could be observed.
+We consider subjects as black boxes and only require a capacity of observation of their choices after exposure to arguments.
+Depending on the exposure protocol and the subject, it is of course possible for the arguments to never affect any judgment of the subject, a conclusion that may be interesting in its own right.
+
+The deliberated judgment of a subject is defined as a function of the exposure protocol, as accepting every claims that resists every counter-arguments.
+The notion of resistance is itself defined according to the exposure protocol.
+
+Studying judgments resulting from exposure to arguments includes a difficulty that is not present with natural choice experiments: exposing an individual to arguments may change the individual’s stance, an effect that cannot be erased to submit the individual (considered “clean” again) to another sequence of arguments.
+The observer thus cannot in general assume that multiple unrelated sequences of arguments can be tested on a given individual.
+This difficulty will be worked around by considering general theories of deliberated judgments, that apply to sets of individuals.
+This is methodologically similar to defining theories of how objects break.
+One can test only one way of breaking a given object (assuming it cannot be repaired), so such theories must apply to sets of objects if one wants to be able to test multiple ways of falsifying the theories.
 
@@
 \section{The model}
-Let $\Phi = \set{\phi, ¬\phi}$ represent the decision at stake. Let $I$ be a set of individuals.
-
-A prescriptive theory is a tuple $(\allargs, {\allleadsto})$.
+Let $\Phi = \set{\phi, ¬\phi}$ represent the decision at stake.
+
+An exposure protocol is a tuple $(I, \allargs, {\allleadsto})$, where $I$ is a set of individuals, $\allargs$ is a set of arguments, and ${\allleadsto}$ is the behavior of the individuals as a function of the arguments they have been exposed to.
 
@@
 Throughout the article, $\N$ includes zero. %and $\N^* = \N \setminus \set{0}$. 
+Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \N: \intvl{j, 0} = \emptyset$).
 Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments. A sequence of arguments is called an argumentative path, or simply a path.
 A generic element of $\allhist$ is denoted by $\hist$ and called an argumentative path, or simply a path when this raises no ambiguity. Its length is denoted by $\card{\hist} \in \N$.
-Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$.
-Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}$, $\hist_k \in A$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
+Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}$, $\hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
 
@@
 
-	Consider a set $\alts = \set{\alt_1, \alt_2} \subset \allalts$ of two items, and assume the two theories of \ac{DJ} are opposed on their prediction of the reflexive choice of individuals having to choose one item among $\alts$.
+	Consider a set $\alts = \set{\alt_1, \alt_2} \subset \allalts$ of two items, and assume the two theories of \ac{DJ} are opposed on their prediction of the reflective choice of individuals having to choose one item among $\alts$.
 Say, $\alt_1$ is satisfying and $\alt_2$ is not, failing on the speed criterion; while $v(\alt_2) > v(\alt_1)$.

### 2022-07-22 simple.tex
hbadness for biblio
Deliberated choice

@@
 Such judgments may differ from immediate judgments of desirability given in natural conditions.
-Indeed, individuals may change opinion on the desirability of some course of action, and therefore revise their choice, while learning about the properties of objects, the consequences of some acts (or empirical knowledge useful to estimate the likelihood of some consequences), or the logical or empirical impossibilities between consequences (for example, in some situations, you can’t both pay less taxes and have better government provided services).
+Indeed, individuals may change opinion on the desirability of some course of action, and therefore revise their choice, while learning about the properties of objects, the consequences of some acts (or empirical knowledge useful to estimate the likelihood of some consequences), or the logical or empirical impossibilities between consequences.
 This is particularly likely to happen when choosing among non everyday objects or acts whose consequences are not well known by the subject.
@@
 The notion of argument invoked here is an extremely large one, including texts, images, sounds, experiences (a hiking trip), and so on: anything that can be transmitted to a subject qualifies as a possible argument.
-Such an “argument” need not even have the logical structure of what is considered a proper argument in argumentation theory, which permits to avoid having to take position on what is a correct argument, and permits to study wide enough conceptions of deliberated judgment, including those involving no paternalism: anything that influences the judgment of a subject may a priori be considered worth including in at least some conceptions of deliberated judgment.
+Such an “argument” need not even have the logical structure of what is considered a proper argument in argumentation theory, which permits to avoid having to take position on what is a correct argument, and permits to study wide enough conceptions of deliberated judgment, including those involving no paternalism: anything that influences the judgment of a subject may a priori be considered worth including in at least some conceptions of deliberated judgment, thus including whatever some could consider “bad reasoning” or “bad reasons”.
 
@@
 A sufficiently restricted, or even purposefully chosen, set of arguments may yield judgments that are only deliberate in the technical sense used here, but that pertain more to brain-washing than to reflective judgments.
-While it is indeed a long-term goal of this research stream to yield a normatively relevant conception of preference (appropriate, for example, for recommendation), it is not a claim of this article that anything that corresponds to deliberated judgments as defined here qualify as being appropriate for recommendation (or for any other normative use): much depends on the chosen exposure protocol.
+While it is indeed a long-term goal of this research program to yield a normatively relevant conception of preference (appropriate, for example, for recommendation), it is not a claim of this article that anything that corresponds to deliberated judgments as defined here qualify as being appropriate for recommendation (or for any other normative use): much depends on the chosen exposure protocol.
 The goal of this article is, more modestly, one of a conceptual and practical clarification.
@@
 
+\subsection{Exposure protocol}
 An exposure protocol is a tuple $(I, \allargs, {\allleadsto})$, where $I$ is a set of individuals, $\allargs$ is a set of arguments, and ${\allleadsto}$ is the behavior of the individuals as a function of the arguments they have been exposed to.
 
-$\allargs$ is a set of arguments. 
+While $I$ and $\allargs$ are fundamental sets whose elements are considered elementary, a few notations and concepts are required to define ${\allleadsto}$.
 Throughout the article, $\N$ includes zero. %and $\N^* = \N \setminus \set{0}$. 
 Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \N: \intvl{j, 0} = \emptyset$).
-Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments. A sequence of arguments is called an argumentative path, or simply a path.
-A generic element of $\allhist$ is denoted by $\hist$ and called an argumentative path, or simply a path when this raises no ambiguity. Its length is denoted by $\card{\hist} \in \N$.
+Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence. 
+A generic element of $\allhist$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path when this raises no ambiguity.
+Its length is denoted by $\card{\hist} \in \N$.
 Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}$, $\hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
 
-The function ${\allleadsto}: I × \allhist → \powersetz{\Phi}$ associates to each individual and path a non-empty subset of $\Phi$.
-The case $\Phi$ is used to represent indifferent choice, in case this is observable.
-The observation that $\phi$ is considered among the best by $i$ considering $\alpha$ is represented by $\alpha \ileadsto \phi$, considering ${\ileadsto} \subseteq \allhist × \Phi$ as a binary relation.
-As usual with binary relations, $\hist \nileadsto \prop$ means $(\hist, \prop) \notin {\ileadsto}$.
-
-% which associates to each $i \in I$ an element of $\Phi$ or nothing, with the semantics that this decision is the right one for that individual or that the theory abstains from recommending.
+The function ${\allleadsto}: I × \allhist → \powersetz{\Phi}$ associates to each individual and path a non-empty subset of $\Phi$, ${\allleadsto}(i, \alpha)$ representing the choice of $i$ following exposure to the arguemnts of $\alpha$, in order.
+The case ${\allleadsto}(i, \alpha) = \Phi$ is used to represent indifferent choice, in case this is considered observable.
+If $\phi \in {\allleadsto}(i, \alpha)$, we say that $\phi$ is considered as one of the best options by $i$ considering $\alpha$. 
+It is also denoted by $\alpha \ileadsto \phi$, considering ${\ileadsto} \subseteq \allhist × \Phi$ as a binary relation.
+As usual with binary relations, $\hist \nileadsto \prop$ means $(\hist, \prop) \notin {\ileadsto}$ or equivalently $\phi \notin {\allleadsto}(i, \alpha)$.
+
+\subsection{Deliberated choice}
+We can now define the deliberated choice of $i$ given the exposure protocol $(I, \allargs, {\allleadsto})$.
+It is denoted $\Phi_i$ and is a subset of $\Phi$, with the semantics that $\phi \in \Phi_i$ means that $\phi$ is considered by $i$, after deliberation, one of the best options, given the exposure protocol.
+In other words, if $\Phi_i = \Phi$, the individual considers both $\phi$ and $¬\phi$ equally worth after deliberation and if $\Phi_i = \set{\phi}$, the individual considers $\phi$ the strictly best option among the proposed set, after deliberation (and similarly for $\Phi_i = \set{¬\phi}$).
 
@@
 
+\hbadness=10000
 \bibliography{simple}

### 2022-08-02 simple.tex
Mv indiff and skipped it; went on with concrete tutor example

@@
 This is methodologically similar to defining theories of how objects break.
-One can test only one way of breaking a given object (assuming it cannot be repaired), so such theories must apply to sets of objects if one wants to be able to test multiple ways of falsifying the theories.
-
-For conceptual clarity, I will focus on the case of a single binary decision to take, akin to a choice situation facing a bundle of two objects among which exactly one must be adopted.
-
-\section{The model}
+One can test only one way of breaking a given (unrepairable) object, so such theories must apply to sets of objects if one wants to be able to test multiple ways of falsifying the theories.
+
+For conceptual clarity, I will focus on the case of a single binary decision to take, akin to a choice situation facing a bundle of two courses of action, exactly one of which must be adopted.
+
+\section{Exposure protocol and deliberated choice}
 Let $\Phi = \set{\phi, ¬\phi}$ represent the decision at stake.
+The set $\Phi$ represents two antagonistic acts, such as “buy this object for the price of \$15” and “do not buy this object for the price of \$15”, or “take this job offer” and “decline this job offer”.
 
@@
 \subsection{Deliberated choice}
-We can now define the deliberated choice of $i$ given the exposure protocol $(I, \allargs, {\allleadsto})$.
-It is denoted $\Phi_i$ and is a subset of $\Phi$, with the semantics that $\phi \in \Phi_i$ means that $\phi$ is considered by $i$, after deliberation, one of the best options, given the exposure protocol.
-In other words, if $\Phi_i = \Phi$, the individual considers both $\phi$ and $¬\phi$ equally worth after deliberation and if $\Phi_i = \set{\phi}$, the individual considers $\phi$ the strictly best option among the proposed set, after deliberation (and similarly for $\Phi_i = \set{¬\phi}$).
+The deliberated choice of $i$ given the exposure protocol $(I, \allargs, {\allleadsto})$ is denoted $\iprops$ and is a strict subset of $\allprops$, with the semantics that $\iprops = \set{\prop}$ iff $\prop$ is considered by $i$ as the best option among the proposed set $\allprops$, after deliberation, given the exposure protocol.
+In other words, if $\iprops = \set{\phi}$, the individual considers $\phi$ strictly better than $\nprop$, after deliberation (and conversely for $\iprops = \set{¬\phi}$); and if $\iprops = \emptyset$, the deliberated judgment of $i$ considers neither $\phi$ nor $¬\phi$ as strictly better than the alternative.
+This latter possibility covers both the situation of indifference between both options (in the sense of being evaluated by $i$ as being exactly equally worth), which will be further developed in \cref{sec:multiple}, or the situation that $\phi$ is neither deliberately strictly better than, exactly equivalent to or strictly worst than $\nprop$.
+
+This latter possibility may look unpleasant, but it is a fact that facing some difficult problems, individuals sometimes are undecided, and it is an a priori empirical possibility that the individual remains undecided (or even, becomes \emph{more} undecided) when considering multiple arguments.
+That classical protocols of natural choice do not allow to observe such incompleteness has often been considered a weakness of those protocols, that our richer observational basis permits to overcome.
+
+The formal definition of $\iprops$ given $(I, \allargs, {\allleadsto})$ requires to define the notion of decisive argument.
 
@@
 
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto \prop$. 
-When $\ar \ileadstost \prop$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view. 
-Given any $i \in I$, when some argument is decisive for some proposition $\prop$, thus, when $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop$, the proposition is said to be acceptable, from $i$’s point of view.
-
-The following axiom permits the theory to have bite on what should be recommended to $i$. It says that it is sufficient that a proposition be acceptable to be in $i$’s \ac{DJ}.
-\begin{axiom}[Normative adequacy]
-%	\label{ax:norm}
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \nileadsto \nprop$; equivalently, iff $\forall \hist \in \allhist \suchthat \ar \in \histend: {\leadsto}(i, \hist) = \set{\prop}$.
+When $\ar \ileadstost \prop$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view (or just a decisive argument, for short). 
+The deliberated judgment of $i$ is then considered to contain the set of propositions supported by decisive arguments.
+\begin{axiom}[Decisive arguments define deliberated judgments]
+	\label{ax:decisive}
 	$\forall i \in I, \prop \in \allprops: 
-		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \prop)] ⇒ \prop \in \iprops.$
+		\prop \in \iprops ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop].$
 \end{axiom}
+
+\subsection{An example and a discussion about observability}
+The following toy example is inspired by citet[p.~59]{Railton}, who uses this example to support his claim that beliefs may influence decisions. Here is his story.
+\begin{quote}
+An experiment in cognitive psychology reveals that when subjects observe two individuals taking a test, one of whom answers a high percentage of the early questions correctly but then falters, while the other does
+poorly initially but then answers a high percentage of the later questions
+correctly, the first is usually viewed as more able, even though in the end
+each answers the same number of questions correctly in all. If the subjects had been asked which test-taker they would prefer as a math tutor,
+they likely would have answered “The first,” and perhaps they would also
+have been willing to pay a premium to secure his services. But if they
+were to become convinced of the influence of sheer order on their evaluations of relative ability, they presumably would no longer want their
+initial preference for the first test-taker to influence their choices – or
+willingness to pay – in this way.
+\end{quote}
+\begin{example}[Math tutor]
+	\label{ex:tutor}
+	Let $I$ be a set of individuals desiring to evaluate two candidates $\set{m_1, m_2}$ for math tutoring.
+	Let ${\leadsto}(i, a_1)$ represent $i$ being shown a test of candidate $m_1$ wherein $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly.
+	Let ${\leadsto}(i, a_2)$ represent $i$ being shown a test of candidate $m_2$ wherein $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly.
+%	Let ${\leadsto}(i, a_e)$ represent $i$ being given an explanation about the psychological phenomenon described in the quote above.
+	Let ${\leadsto}(i, a_e)$ represent $i$ being given the following argument.
+“When tested, $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly; whereas $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly.
+It follows than $m_1$ answers on average less well than $m_2$.
+Observing the candidates take the tests may yield a contrary impression; this is a well-known psychological phenomenon depending on the order of the questions that the candidates answer correctly.”
+	Let $\Phi = \set{\prop_1, \prop_2}$ where $\prop_1$ represent $m_1$ and $\prop_2$ represent $m_2$.
+
+	If the prediction described in the quote is correct, and applies equally to this modified experiment, then, given $i \in I$, $i$’s deliberated choice is $\prop_2$ because $a_e$ is a decisive argument for $\prop_2$, even though $i$ might have rather chosen $\prop_1$ if given only the arguments $a_1$ and $a_2$ without $a_e$.
+\end{example}
+
+That the deliberated choice of any individual $i$ is well-defined may be doubtful, as it involves counterfactuals.
+To see this, let $\alpha_{123} = (a_1, a_2, a_e)$ designate the history where the arguments are shown in the order they are described in the example, and let $\alpha_{321} = (a_3, a_2, a_1)$ designate the reverse order.
+The deliberated choice of $i$ is defined so as to not depend on the (arbitrary) order of the arguments shown to $i$: for $\prop \in \iprops$, it must be that directing to $i$ the path $\alpha_{123}$ or the path $\alpha_{321}$ both lead $i$ to choose $\prop$.
+However, once we have shown to $i$, say, $\alpha_{123}$, we cannot show to her $\alpha_{321}$ (unless assuming $i$ forgets arguments after a while and waiting for sufficiently long, which would create practical and theoretical difficulties).
+
+This difficulty is resolved using falsifiable general theories, applicable to $I$ and not solely to a given $i$, so that, intuitively speaking, $\alpha_{321}$ can be tested on some $i' ≠ i$.
+Indeed, what is needed is a way to make a claim such as the one concluding \cref{ex:tutor} empirically testable.
+This is achieved in the next section thanks to theories of deliberated choice.
+Such theories are defined so as to satisfy two properties.
+First, such a theory must be falsifiable in principle, meaning that there exists a world in which it is possible to observe it to be false.
+As a counter-example, using \cref{ex:tutor}, a theory that claims that $\forall i \in I: \alpha_{123} \ileadsto \prop_1 \lor \alpha_{321} \ileadsto \prop_1$ is not falsifiable in principle, as, whatever the real $\ileadsto$ relation, with a given $i$, one can never show that $\alpha_{123} \nileadsto \prop_1 \land \alpha_{123} \nileadsto \prop_1$.
+Second, such a theory must be so that if it is not possible to empirically falsify it, meaning that in the actual world it is not possible to observe it to be false, then it implies that some given alternative is in the deliberated judgment of the individuals in $I$.
+
+\section{Theories of deliberated choice}
+This section assumes that an exposure protocol $(I, \allargs, {\leadsto})$ is defined, and defines theories of deliberated choice associated with that exposure protocol.
+
+\subsection{Theories using a static decisive argument}
+\Cref{ex:tutor} suggests a simple form for theories of deliberated choice: suffice to determine an argument $\ar \in \allargs$ and an alternative $\prop \in \Phi$ such that the theory claims that $\forall i \in I: \ar \ileadstost \prop$.
+
+\begin{definition}[Static theory]
+	A static theory is a pair $(\ar, \prop)$ for some $\ar \in \allargs$ and some $\prop \in \Phi$.
+\end{definition}
+
+\section{Multiple}
+\label{sec:multiple}
 
@@
 Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $\forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$.
-Let $\incompat \subseteq \Phi × \Phi$ denote the set of incompatible pairs of propositions.
+Let $\incompat \subseteq \allprops × \allprops$ denote the set of incompatible pairs of propositions.
 
@@
 
+\section{Binary choice with indifference}
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost^\text{strong} \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \nileadsto \nprop$, equivalently, ${\ileadsto}(i, \hist) = \set{\prop}$.
+
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost^\text{vweak} \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto \prop$.
+
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost^\text{indif} \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto \prop \land \hist \ileadsto \nprop$, equivalently, ${\ileadsto}(i, \hist) = \Phi$.
+
+Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost^\text{right} \prop$ iff $\forall \hist \in \allhist_{… a} \suchthat \ar \in \histend: \hist \ileadsto \prop \land \forall \hist, \hist' \in \allhist \suchthat \ar \in \histend, \ar \in \histend': {\ileadsto}(i, \hist) = {\ileadsto}(i, \hist')$, equivalently, $[\forall \hist \in \allhist \suchthat \ar \in \histend: {\ileadsto}(i, \hist) = \Phi] \lor [\forall \hist \in \allhist \suchthat \ar \in \histend: {\ileadsto}(i, \hist) = \set{\phi}]$.
+
+The converse of this is: $\ar \nileadstost^\text{right} \prop$ iff $\exists \hist \suchthat \hist \ileadsto \nprop \land [\exists \hist \suchthat \hist \nileadsto \prop \lor \exists \hist \suchthat \hist \nileadsto \nprop]$.
+
+Equivalently: $\ar \nileadstost^\text{right} \prop$ iff $[\exists \hist \suchthat \hist \ileadsto \nprop \land \exists \hist \suchthat \hist \nileadsto \prop] \lor [\exists \hist \suchthat \hist \ileadsto \nprop \land \exists \hist \suchthat \hist \nileadsto \nprop]$.
+
+The converse of this is: $\ar \ileadstost^\text{right} \prop$ iff $[\forall \hist: \hist \nileadsto \nprop \lor \forall \hist: \hist \ileadsto \prop] \land [\forall \hist: \hist \nileadsto \nprop \lor \forall \hist: \hist \ileadsto \nprop]$.
+
+Equivalently: $\ar \ileadstost^\text{right} \prop$ iff $[\forall \hist: \hist \nileadsto \nprop] \lor [\forall \hist: \hist \ileadsto \prop \land \forall \hist: \hist \ileadsto \nprop]$.
+
+The real thing that we need is this.
+\begin{axiom}[Really]
+	$\forall i \in I, \hist \in \allhist \suchthat \hist \ileadsto \prop: 
+		[\exists \ar \in \allargs \suchthat [\ar \ileadstost^\text{strong} \prop] \lor [\ar \ileadstost^\text{indif} \prop]] ⇔ \prop \in \iprops.$
+\end{axiom}
+
+\subsection{Draft}
+The following axiom imposes that given any $i \in I$, when some argument is decisive for some proposition $\prop$, thus, when $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop$, the proposition is in $i$’s \ac{DJ}.
+\begin{axiom}[Decisive argument sufficiency]
+%	\label{ax:norm}
+	$\forall i \in I, \prop \in \allprops: 
+		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ \prop \in \iprops.$
+\end{axiom}
+\begin{property}[Decisive argument necessity]
+%	\label{ax:norm}
+	$\forall i \in I, \prop \in \allprops: 
+		[\nexists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ \prop \notin \iprops.$
+\end{property} 
+A path $\hist$ is in favor of $\prop$ for $i$ iff $\hist \ileadsto \prop$. The path is countered back to $\nprop$ iff $(\hist, a) \nileadsto \prop$.
+\begin{axiom}[Counter sufficiency]
+%	\label{ax:norm}
+	$\forall i \in I, \hist \in \allhist \suchthat \hist \ileadsto \prop: 
+		[\exists \ar \in \allargs \suchthat (\hist, \ar) \nileadsto \prop] ⇒ \prop \notin \iprops.$
+\end{axiom}
+
+With these axioms alone, if $\iprops = \emptyset$, it is impossible to know it. That is because if we can derive $\prop \notin \iprops$, then it follows that $\nprop \in \iprops$.
+
+Mandate stability. Either dec arg for $\set{\prop}$ or dec arg for $\Phi$ (then indifference).
+
+Try to obtain stability as a consequence of: if strong arg, then $\prop$ and not $¬\prop$; if unstability, then do not conclude ($\prop \notin \iprops$).
+
+\subsection{Draft concl}
+$[\exists \hist \suchthat \hist \nileadsto \prop] ⇒ \ar \nileadstost^\text{right} \prop$.
+
+$[\exists \hist \suchthat \hist \ileadsto \nprop \land \exists \hist \suchthat \hist \nileadsto \nprop] ⇒ \ar \nileadstost^\text{right} \prop$.
+
+$[\forall \hist: \hist \nileadsto \nprop] ⇒ \ar \ileadstost^\text{right} \prop$.
+
+$[\forall \hist: \hist \ileadsto \prop \land \forall \hist: \hist \ileadsto \nprop] ⇒ \ar \ileadstost^\text{right} \prop$.
+
+\subsection{Perhaps better}
+$\ar \ileadstost^\text{right} \prop ⇒ [\forall \hist: \hist \ileadsto \prop]$.
+
+$\ar \ileadstost^\text{right} \prop ⇒ [\forall \hist: \hist \nileadsto \nprop \lor \forall \hist: \hist \ileadsto \nprop]$.
+
+$[\forall \hist: \hist \nileadsto \nprop] ⇒ \ar \ileadstost^\text{right} \prop$.
+
+$[\forall \hist: \hist \ileadsto \prop \land \forall \hist: \hist \ileadsto \nprop] ⇒ \ar \ileadstost^\text{right} \prop$.
+
+We want that if we introduce phi-indiff that says “phi and ¬phi are indiff”, phi-indiff is adopted iff phi and ¬phi are indiff.
+
 \end{document}

### 2022-08-03 simple.tex
Static th and justifying more

@@
 This is achieved in the next section thanks to theories of deliberated choice.
-Such theories are defined so as to satisfy two properties.
-First, such a theory must be falsifiable in principle, meaning that there exists a world in which it is possible to observe it to be false.
+% Such theories contain an observable claim and a conclusion claim, so as to satisfy two properties.
+First, such a theory must be falsifiable in principle, meaning that it must be possible, using our observational basis (propositions of the sort $\alpha \ileadsto \phi$), to invalidate the observable claim of the theory.
 As a counter-example, using \cref{ex:tutor}, a theory that claims that $\forall i \in I: \alpha_{123} \ileadsto \prop_1 \lor \alpha_{321} \ileadsto \prop_1$ is not falsifiable in principle, as, whatever the real $\ileadsto$ relation, with a given $i$, one can never show that $\alpha_{123} \nileadsto \prop_1 \land \alpha_{123} \nileadsto \prop_1$.
-Second, such a theory must be so that if it is not possible to empirically falsify it, meaning that in the actual world it is not possible to observe it to be false, then it implies that some given alternative is in the deliberated judgment of the individuals in $I$.
+Second, such a theory must be so that if its observable claim holds, then some given alternative is in the deliberated judgment of the individuals in $I$.
 
@@
 This section assumes that an exposure protocol $(I, \allargs, {\leadsto})$ is defined, and defines theories of deliberated choice associated with that exposure protocol.
+We will start with very simple theories in order to build an intuition about the conditions required on theories of deliberated choice (\cref{sec:static}), then give an example to illustrate why more complex theories are needed (\cref{sec:lichtenstein}) and finally define more general theories of deliberated choice (\cref{sec:dynamic}).
 
 \subsection{Theories using a static decisive argument}
-\Cref{ex:tutor} suggests a simple form for theories of deliberated choice: suffice to determine an argument $\ar \in \allargs$ and an alternative $\prop \in \Phi$ such that the theory claims that $\forall i \in I: \ar \ileadstost \prop$.
+\label{sec:static}
+\Cref{ex:tutor} suggests a simple form for theories of deliberated choice: suffice to determine an argument $\ar \in \allargs$ and an alternative $\prop \in \Phi$ such that the theory claims that $\forall i \in I: \ar \ileadstost \prop$ and that $\prop \in \iprops$.
 
 \begin{definition}[Static theory]
+	\label{def:static}
 	A static theory is a pair $(\ar, \prop)$ for some $\ar \in \allargs$ and some $\prop \in \Phi$.
 \end{definition}
+Such a theory is said to be truthful iff $\forall i \in I: \ar \ileadstost \prop$, and to be correct iff $\prop \in \iprops$.
+We can then say that such theories are valid, meaning that their truthfulness implies their correctness.
+Let us make this (very simple) result stand out as a theorem, because a parallel will be usefully made with more complicated theories.
+%Note that this result immediately follows from \cref{ax:decisive}.
+\begin{theorem}[Static theories are valid]
+	Any truthful static theory is correct.
+\end{theorem}
+\begin{proof}
+	The result immediately follows from \cref{ax:decisive}.
+\end{proof}
+Importantly, truthfulness can indeed be checked using our observational basis, that is, if $\exists i \in I \suchthat \ar \nileadstost \prop$, then it is possible to exhibit this fact experimentally.
+
+Such theories have the merit of simplicity, but there is a need to design more adaptive theories: in many interesting cases, no single argument will be considered decisive by all individuals in $I$.
+What we need is a way to argue with individuals by reacting to what they consider good arguments.
+The following example illustrates this need.
+
+\subsection{Some decision problems with no single decisive argument}
+\label{sec:lichtenstein}
+One ambition of the theories to be proposed here is to permit exhibiting the existence of a deliberated consensus among a large set of persons about issues that involve numerous arguments and counter-arguments.
+
+In many decision problems, individuals will not be attracted by the same set of arguments and counter-arguments, even though they may finally opt for the same alternative.
+Imagine that some individual $i_1$ considers an argument $a_1$ for $\nprop$ relevant and some individual $i_2$ considers an argument $a_2$ for $\nprop$ relevant, but $i_1$ does not consider $a_2$ relevant and $i_2$ does not consider $a_1$ relevant (for example, because they already have some counter-arguments in mind to those arguments).
+Imagine further that there is some counter-argument $a'_1$ that can be given to $i_1$ to rebut $a_1$, and a different counter-argument $a'_2$ that can be given to $i_2$ to rebut $a_2$, so that they both have $\prop$ in their deliberated judgment when considering all these arguments.
+In such situation, static theories as defined in \cref{sec:static} are ill suited: these theories need to present the same argument to all individuals and would thus need to define a bigger argument $a$ containing both $a'_1$ and $a'_2$.
+Such an argument could be too long to be convincing to $i_1$ or $i_2$, as it needlessly spends efforts countering an argument that the individual already considers irrelevant.
+This  will become an important problem if there are not only two but many a priori possible arguments $a_k$ for $\nprop$, each with their own counter-argument $a'_k$ for $\prop$.
+
+%For a partial illustration about an ambitious setting, consider a decision to be taken about the relevance of some concrete action to help cope with climate change, and let $I$ be a set of citizens interested in the climate issue.
+The complete set of all arguments that will be considered relevant by at least one individual may well be very large.
+It may also be that, for each individual who considers relevant some arguments $A$ against the proposed concrete action, it is possible to give counter-arguments $A'$ that will convince the individual to opt for the proposal.
+One of the settings discussed by citet{sunstein} permits to illustrate this point more concretely.
+The authors claim that workers tend to not save enough because of psychological biases. 
+It is therefore tempting to conjecture that the deliberated choice of those workers is to save more, in the sense defined here, than what their natural choice (in absence of arguments) leads to.
+Let $I$ be a set of workers interested in establishing a savings plan. 
+A difficulty related to this decision problem is that the complete set of all arguments that will be considered relevant by at least one individual for such a complex issue may well be very large.
+It may also be that, for each individual who considers relevant some arguments $A$ for saving not much (i.e., spending more in the short term), it is possible to give counter-arguments $A'$ that will convince the individual to opt for saving more.
+But no single argument could be decisive for each $i \in I$: it could be that only tailored counter-arguments could convince individuals, given the complexity of the issue.
+This illustrates that the deliberated choice of each individuals in $I$ may be to save more even though no static theory (\cref{def:static}) may achieve showing it, as it could be that no such theory is truthful.
+
+The above setting illustrates the ambition of this research program, but at the price of rendering impossible in the confines of this article to define fully the set of arguments and giving a complete account of a concrete theory of deliberated choice in such a complex setting, an endeavor of its own.
+
+The following example illustrates this same point in a simpler setting which permits a complete definition of $\allargs$ and $\leadsto$.%, which permits defining the setting completely at the price of a reduced realism.
+\begin{example}[A decision problem about two lotteries]
+	\label{ex:lichtenstein}
+	In a famous article about preference reversals, \citet{lichtenstein_reversals_2006} discuss an example involving two lotteries.
+The lottery $P$ makes you win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $P = (.99, +\$4; .01, −\$0.1)$.
+The lottery $D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
+The letter $P$ stands for probability: one salient aspect of $P$ is the very high chance of winning.
+The letter $D$ stands for dollar: one salient aspect of $D$ is the high gain it gives (compared to $P$) in dollar amount if the player is lucky.
+
+This example is interesting because when asked to bid for lotteries, the theory discussed by the authors predicts, and their experiments confirm, that subjects tend to bid more for $D$ than for $P$, because the bidding question tend to make individuals focus on dollar amounts; whereas when asked to choose one lottery, the lotteries being presented in pairs, subjects tend to choose $P$ among the pair $\set{P, D}$, giving greater attention to probabilities.
+
+Define $\allprops = \set{\phi_P, \phi_D}$.
+
+Define $\ar_e$ as a text arguing that the choice between $P$ and $D$ should be determined by their expected revenue, namely, $\$3.959$ for $P$ and $\$4$ for $D$.
+\footnote{Here is a possible text for $\ar_e$.
+“Imagine you play $P$ 100 times.
+On average, you would win 99 times and lose once, which means gaining 99 × \$4 = \$396 and losing 1 × \$0.10 = \$0.10, hence a total net gain of \$395.90.
+Thus, your average net gain for the $P$ bet would be \$3.9590.
+[Similar text for $D$.] Therefore, we suggest you choose $D$ for a higher expected revenue.”}
+Define $\ar_u$ as a text arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain. 
+\footnote{Here is a possible text for $\ar_u$.
+“$D$ is better than $P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
+For example, consider a choice between winning $10^6$ dollars with probability $0.8$ and winning $2 × 10^6$ dollars with probability $0.4$.
+These two lotteries have the same expected gain, but the first one is clearly preferrable.
+Therefore, we recommend to rather pick $P$ as it presents a much better chance of earning money”.}
+Define a counter-argument to $\ar_u$, $\ar_l$, indicating that for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.
+\footnote{Here is a possible text for $\ar_l$.
+“The lottery $D$ has a higher expected revenue, and thus, a higher utility than $P$, because for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.”}
+Define $\ar$ so as to include the contents of $\ar_e$, $\ar_u$ and $\ar_l$.
+\footnote{Here is a possible text for $\ar$.
+[Text of $\ar_e$] “Note that one could say that the utility of money should matter, but for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.”}
+%Omitting many other relevant arguments for now (such as arguing that utility should be linear for small amounts of money, for example), 
+Define $\allargs = \set{\ar_e, \ar_u, \ar_l, \ar}$.
+
+Define $I$ as a set of individuals facing a choice between $P$ and $D$ in a laboratory experiment.
+Define $\ileadsto$ as simply exposing $i$ to $\alpha$ and observing the resulting choice by asking $i$ to indicate which lottery she prefers playing. 
+%Given an argumentative path $\hist$, $\hist \ileadsto (P ≥ D)$ iff, in a situation of $i$ having been exposed, in order, to the arguments in $\hist$, letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$, or declare indifference.
+Here is a possible text presented to $i$ to ask for a choice: “Considering these arguments, would you please choose either to play $P$, or play $D$, or declare to be indifferent (in which case one will be picked randomly for you)”.
+%Similarly, define $\hist \ileadsto (P > D)$ iff showing the arguments in $\hist$ to $i$ and letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$ and not $D$. 
+%Define similarly $\hist \ileadsto \prop$ for $\prop \in \set{D ≥ P, D > P}$.
+
+Assume that some individuals $i \in I$ do not see the point of argument $\ar_u$ and some do but are convinced by the counter-argument $\ar_l$.
+Accordingly, define $\ileadsto[e]$, representing the first kind of individuals, as follows.
+$\forall \hist \in \allhist: \hist \ileadsto[e] D ⇔ [\ar_e \in R(\hist)]$.
+Note that in particular, if $\hist$ contains $\ar$ but not $\ar_e$, $\ar \nileadsto[e] D$, as we assume such individuals are confused by the longer argument $\ar$ referring to abstract notions and could therefore opt for $P$ (falling back to the common psychological bias).
+TODO change notation
+
+The exposure protocol $(I, \allargs, {\allleadsto})$ is an example of a normative theory of \ac{DJ}.
+\end{example}
+
+\subsection{Dynamic theories}
+\label{sec:dynamic}
 

### 2022-08-03 simple.tex
Notation for single \phi; some minor fixes

@@
 
-The function ${\allleadsto}: I × \allhist → \powersetz{\Phi}$ associates to each individual and path a non-empty subset of $\Phi$, ${\allleadsto}(i, \alpha)$ representing the choice of $i$ following exposure to the arguemnts of $\alpha$, in order.
-The case ${\allleadsto}(i, \alpha) = \Phi$ is used to represent indifferent choice, in case this is considered observable.
-If $\phi \in {\allleadsto}(i, \alpha)$, we say that $\phi$ is considered as one of the best options by $i$ considering $\alpha$. 
-It is also denoted by $\alpha \ileadsto \phi$, considering ${\ileadsto} \subseteq \allhist × \Phi$ as a binary relation.
-As usual with binary relations, $\hist \nileadsto \prop$ means $(\hist, \prop) \notin {\ileadsto}$ or equivalently $\phi \notin {\allleadsto}(i, \alpha)$.
+The function ${\allleadsto}: I × \allhist → \set{\phi, ¬\phi, 0}$ associates to each individual and path an element of $\Phi$ or the special symbol $0$ representing the absence of a strict preference.
+That is, ${\allleadsto}(i, \alpha)$ represents the choice of $i$ following exposure to the arguemnts of $\alpha$, in order.
+The case ${\allleadsto}(i, \alpha) = 0$ is used to represent indifference.
+The notation $\alpha \ileadsto \phi$ will be used to mean ${\allleadsto}(i, \alpha) = \phi$, considering ${\ileadsto} \subseteq \allhist × \Phi$ as a binary relation.
+As usual with binary relations, $\hist \nileadsto \prop$ means ${\allleadsto}(i, \alpha) ≠ \prop$ or equivalently ${\allleadsto}(i, \alpha) \in \set{\nprop, 0}$.
 
@@
 What we need is a way to argue with individuals by reacting to what they consider good arguments.
-The following example illustrates this need.
+The following section illustrates this need.
 
@@
 In such situation, static theories as defined in \cref{sec:static} are ill suited: these theories need to present the same argument to all individuals and would thus need to define a bigger argument $a$ containing both $a'_1$ and $a'_2$.
-Such an argument could be too long to be convincing to $i_1$ or $i_2$, as it needlessly spends efforts countering an argument that the individual already considers irrelevant.
-This  will become an important problem if there are not only two but many a priori possible arguments $a_k$ for $\nprop$, each with their own counter-argument $a'_k$ for $\prop$.
+Such an argument could be too long to be convincing to $i_1$ or $i_2$, as it needlessly spends efforts countering an argument that the individual considers irrelevant to start with.
+This  will become an important problem if there are not only two but many a priori possible arguments $a_k$ for $\nprop$, a small subset of which is considered relevant by a given individual, each with their own counter-argument $a'_k$ for $\prop$.
 
@@
 One of the settings discussed by citet{sunstein} permits to illustrate this point more concretely.
+Let $I$ be a set of workers interested in establishing a savings plan. 
 The authors claim that workers tend to not save enough because of psychological biases. 
-It is therefore tempting to conjecture that the deliberated choice of those workers is to save more, in the sense defined here, than what their natural choice (in absence of arguments) leads to.
-Let $I$ be a set of workers interested in establishing a savings plan. 
+It is therefore tempting to conjecture that the deliberated choice of those workers is to save more, in the sense defined here, than what their natural choice (the one revealed in absence of arguments) leads to.
 A difficulty related to this decision problem is that the complete set of all arguments that will be considered relevant by at least one individual for such a complex issue may well be very large.
@@
 
-The above setting illustrates the ambition of this research program, but at the price of rendering impossible in the confines of this article to define fully the set of arguments and giving a complete account of a concrete theory of deliberated choice in such a complex setting, an endeavor of its own.
+%The above setting illustrates the ambition of this research program, but at the price of rendering impossible in the confines of this article to define fully the set of arguments and giving a complete account of a concrete theory of deliberated choice in such a complex setting, an endeavor of its own.
 

### 2022-08-05 simple.tex
Some rephrasing

@@
 Such acts have been used, among others, to give an observable basis to the concept of preference, thanks in part to the seminal work of Samuelson.
-Acts of choice are considered here in the broad sense of choice between courses of actions, encompassing the simple setting of choosing between various elementary consumption bundles as well as settings involving more abstract acts such as choosing between defection or cooperation in a game-theoretical setting.
+%Acts of choice are considered here in the broad sense of choice between courses of actions, encompassing the simple setting of choosing between various elementary consumption bundles as well as settings involving more abstract acts such as choosing a strategy in a game-theoretical setting.
 
@@
 	In a famous article about preference reversals, \citet{lichtenstein_reversals_2006} discuss an example involving two lotteries.
-The lottery $P$ makes you win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $P = (.99, +\$4; .01, −\$0.1)$.
+The lottery $P$ lets the subject win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $P = (.99, +\$4; .01, −\$0.1)$.
 The lottery $D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
 The letter $P$ stands for probability: one salient aspect of $P$ is the very high chance of winning.
-The letter $D$ stands for dollar: one salient aspect of $D$ is the high gain it gives (compared to $P$) in dollar amount if the player is lucky.
+The letter $D$ stands for dollar: one salient aspect of $D$ is the high gain it gives (compared to $P$) in dollar amount if the subject is lucky.
 
@@
 [Text of $\ar_e$] “Note that one could say that the utility of money should matter, but for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.”}
-%Omitting many other relevant arguments for now (such as arguing that utility should be linear for small amounts of money, for example), 
 Define $\allargs = \set{\ar_e, \ar_u, \ar_l, \ar}$.
@@
 Accordingly, define $\ileadsto[e]$, representing the first kind of individuals, as follows.
-$\forall \hist \in \allhist: \hist \ileadsto[e] D ⇔ [\ar_e \in R(\hist)]$.
-Note that in particular, if $\hist$ contains $\ar$ but not $\ar_e$, $\ar \nileadsto[e] D$, as we assume such individuals are confused by the longer argument $\ar$ referring to abstract notions and could therefore opt for $P$ (falling back to the common psychological bias).
-TODO change notation
-
-The exposure protocol $(I, \allargs, {\allleadsto})$ is an example of a normative theory of \ac{DJ}.
+$\forall \hist \in \allhist: \hist \ileadsto[e] D ⇔ [\ar_e \in R(\hist)]$, and $\hist \ileadsto[e] P$ otherwise.
+Note that in particular, if $\hist$ contains $\ar$ but not $\ar_e$, $\ar \nileadsto[e] D$, as we assume such individuals are confused by the longer argument $\ar$ referring to abstract notions and therefore opt for $P$, falling back to the common psychological bias.
+The second kind of individuals is represented by $\ileadsto[u]$ defined as $\forall \hist \in \allhist: \hist \ileadsto[u] D ⇔ [\ar_u \notin R(\hist) \lor \ar \in R(\hist) \lor \set{\ar_u, \ar_l} \subseteq R(\hist)]$, and $\hist \ileadsto[u] P$ otherwise.
+We assume here that such individuals think about $\ar_u$ as a correct argument in favor of $P$ until shown the rebuttal $\ar_l$ (or $\ar$, which contains the same rebuttal).
+Assuming finally $\allleadsto$ as equal to $\ileadsto[e]$ for individuals of the first kind and $\ileadsto[u]$ otherwise concludes the definition of the exposure protocol $(I, \allargs, {\allleadsto})$.
+
+It follows from this definition that $\forall i \in I: \prop_D \in \iprops$, and that no static theory of that exposure protocol is truthful: only $\ar_e$ is a decisive argument for $\prop_D$ for the first kind of individuals whereas for the second kind, only $\ar$ is.
 \end{example}
-
-\subsection{Dynamic theories}
+This example illustrates the need for theories that are able to react to arguments depending on what a given individual considers relevant. This is the object of the next section.
+
+\subsection{General theories of deliberated choice}
 \label{sec:dynamic}
+A theory of deliberated choice presents a claim $C$ under the form of a constraint on ${\ileadsto}$.
+That claim
 

### 2022-08-06 simple.tex
Brought old defs

@@
 
-\subsection{General theories of deliberated choice}
+\subsection{Argumentative theories of deliberated choice}
 \label{sec:dynamic}
-A theory of deliberated choice presents a claim $C$ under the form of a constraint on ${\ileadsto}$.
-That claim
+An argumentative theory of \ac{DC} is defined as a tuple $(\gleadsto, \dg)$, where ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation and $\dg$ is a defense relation; satisfying bounded depth.
+
+\subsection{Old definition}
+\label{sec:descrdef}
+In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
+These concepts are now defined formally.
+\commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}
+
+An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ defines the set of supported  propositions and, for each supported propositions, the set of initial arguments for these propositions.
+More precisely, let $\gpropse$, the range of ${\gleadsto}$, be called the propositions \emph{supported} by the descriptive theory.
+Given such a supported proposition $\prop \in \gpropse$, let $\gleadstoinv(\prop) = \set{\ar \in \allargs \suchthat \ar \gleadsto \prop}$ be called the initial arguments in favor of $\prop$.
+
+A defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ is a right-unique relation, thus given any $\ar \in \allargs, \hist \in \allhist$, $\dg(\ar, \hist)$ is empty or is a singleton.
+%, and must satisfy $\ar \notin \histend ⇒ \dg(\ar, \hist) = \emptyset$.
+As is usual for right-unique relations, I write $\dg(\ar_0, \hist) = \ar_1$ instead of $\dg(\ar_0, \hist) = \set{\ar_1}$.
+Say that $\ar_1$ defends $\ar_0$ iff $\exists \hist \suchthat \dg(\ar_0, \hist) = \ar_1$.
+Define $\dg(\ar) = \dfp(\ar) = \dg(\ar, \allhist) = \set{\dg(\ar, \hist) \suchthat \hist \in \allhist} \subseteq \allargs$ as all the defenders of $\ar$.
+The relation $\dg$ defines the argumentation strategy of the theory.
+Informally speaking, its role is to adapt the arguments the theory produces to the reactions of the individual it is trying to convince.
+Assuming the theory has played an argument $\ar_0$ and a path $\hist$ challenges some of the conclusions this argument supports (as judged by the individual), $\dg(\ar_0, \hist)$ is the argument that the theory plays as a counter-argument to the path $\hist$.
+%The condition that when $\dg(\ar_0, \hist)$, $\ar_0 \in \histend$ is imposed for simplicity: as will appear, an argument $\ar_0$ needs defense only when it is challenged by some path $\hist \suchthat \ar_0 \in \histend$, thus, letting $\dg$ define counter-arguments to paths not satisfying this condition would be of no use.
+
+This mechanism permits to define defenders of defenders of an argument, $\dg(\dg(\ar))$, defenders of defenders of defenders of an argument, … 
+For the results to be presented here to hold, an empirical theory must be a priori restricted in the maximal “depth” of its argumentation strategy, in the following sense. 
+\commentYM{ok soit, ça semble raisonnable, mais tu n'as pas de raison plus forte, j'adopterais une formulation plus modeste et ouverte, du genre "ça semble souhaitable"}
+Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
+The bounded depth condition on a descriptive theory imposes that
+$\exists k \in \N \suchthat (\dg)^k(\gleadstoinv(\allprops)) = \emptyset$.
+The smallest such $k$ is called the depth of the theory.
+
+Here is an example of a theory that does not use an argumentation strategy, but simply plays an argument that it claims is decisive for everybody.
+\begin{example}[Constant argumentation]
+	Given the normative theory of \cref{ex:twolott}, define ${\gleadsto} = \set{(\ar_0, D > P)}$ and $\dg = \emptyset$. This defines a descriptive theory of depth $1$ for that normative theory.
+\end{example}
+
+\begin{example}[A theory for $P$]
+	\label{ex:twolottstrings}
+	Define a normative theory as in \cref{ex:twolott}, with an extended set of arguments: define $\allargs$ as the set of all strings.
+(This correspondingly changes $\allhist$ and thus $\ileadsto$, which must be extended to its new domain.) Define $\ar_0$ as in \cref{ex:twolott}.
+	Define $\ar_\text{for$P$}$ as the text “We recommend to adopt $P$: it has a much higher probability of winning.” 
+	Define ${\gleadsto} = \set{(\ar_\text{for$P$}, P > D)}$.
+	In order to define a counter-argument to $\ar_0$, given a real number $r \in \R$, define $\ar^r_\text{non-linear}$ as the text “$D$ is better than $P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
+For example, consider a choice between winning $r$ dollars with probability $0.8$ and winning $2r$ dollars with probability $0.4$.
+They have the same expected gain, but the first one is clearly preferrable.
+Therefore, we recommend to rather pick $P$ as it presents a much better chance of earning money”.
+(The value of $r$ and $2r$ is to be used in the relevant places in  the text.)
+	Define $\dg = \set{(\ar_\text{for$P$}, \hist, \ar^{10^6}_\text{non-linear}) \suchthat \hist \in \allhist \land \ar_0 \in \hist}$.
+This strategy anticipates a possible attack using $\ar_0$ against $\ar_\text{for$P$}$, and prepares $\ar^{10^6}_\text{non-linear}$ as a counter-argument.
+	This defines a descriptive theory of depth $2$.
+\end{example}
+
+The following less trivial example of a descriptive theory illustrates a theory that claims to be able to answer an infinite number of arguments.
+This also shows that the bounded depth constraint does not imply finiteness of the relation $\dg$.
+\begin{example}[Infinite $\dg$]
+	\label{ex:infinite}
+	Define a normative theory and the arguments $\ar_0$ and $\ar^r_\text{non-linear}$ for any $r \in \R$ as in \cref{ex:twolottstrings}.
+	Define ${\gleadsto} = \set{(\ar_0, D > P)}$.
+	Define $\ar_\text{linear}$ as the text “We agree that when the money amounts involved are large and the game is not repeated, there is no good reason to consider only expected gains when choosing a lottery.
+But in our case, the money amounts are small and the game is repeated.
+Therefore, expected gain is the right indicator to consider for a systematic and sound decision strategy.”
+	Define $+$ as the concatenation operator over strings.
+	Define $\dg = \set{(\ar_0, \ar^r_\text{non-linear}, \ar_0 + \ar_\text{linear}) \suchthat r \in \R}$.
+This strategy sets up the argument $\ar_0 + \ar_\text{linear}$ as an answer to any argument of the form described in \cref{ex:twolottstrings}, arguing for non-linearity of utility of money.
+	This defines a descriptive theory of depth $2$.
+\end{example}
+
+\subsection{Validity and falsification}
+\label{sec:validity}
+An empirical theory claims to be valid, in the following sense.
+\begin{definition}[Validity]
+	An empirical theory is \emph{valid} iff $\forall i \in I, \prop \in \gpropse: \prop \in \iprops$.
+\end{definition}
+To achieve this goal, it claims that it is able to produce decisive arguments for its supported propositions.
+These arguments can vary according to the individual $i \in I$.
+Given an individual, the theory claims that a decisive argument will be systematically found by starting from an initial argument given by $\gleadsto$, and following a chain of defense defined by $\dg$ as required, depending on the paths that challenge the arguments produced along the way, as judged by the individual $i$.
+The property that a theory manages to systematically produce decisive arguments in such a way is named Convincingness.
+Defining it precisely requires to define first the notion of required arguments.
+
+Given $i \in I, \prop \in \gpropse$, define $\dgip(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \notin \histend \land \hist \nileadsto \phi} \subseteq \dg(\ar)$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\prop$.
+Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
+Define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\prop)$ under $\dgip$: $\gargs = \cup_{k \in \N} (\dgip)^k({\gleadstoinv}(\prop))$.
+The set $\gargs$ is the set of arguments required to convince $i$ of $\phi$.
+\begin{example}[Required arguments]
+	\label{ex:required}
+	Continuing \cref{ex:infinite}, define the subset of individuals that find some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ as the set of $i \in I$ such that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \ar^r_\text{non-linear} \in \range(\hist) \land \hist \nileadsto D > P$.
+	We see that for any $i$ in that set of individuals, $\gargs[D > P] = \set{\ar_0, \ar_0 + \ar_\text{linear}}$, and for any $i$ in the complementary set of individuals, $\gargs[D > P] = \set{\ar_0}$.
+\end{example}
+
+Given $\ar \in \gargs$, say that $\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend \land \hist \nileadsto \phi: d(\ar, \hist) ≠ \emptyset$.
+\begin{definition}[Convincingness]
+	An empirical theory is \emph{convincing} iff $\forall i \in I, \prop \in \gpropse, \ar \in \gargs: \ar$ $i$-defends $\prop$.
+\end{definition}
+\begin{example}[Convincingness]
+	Pursuing with \cref{ex:required}, that theory will be convincing iff either $i$ finds some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and both $\ar_0$ and $\ar_0 + \ar_\text{linear}$ $i$-defend $D > P$, or $i$ does not find any argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and $\ar_0$ $i$-defends $D > P$.
+
+	$\ar_0$ $i$-defends $D > P$ iff any argumentative path $\hist$ that contains $\ar_0$ towards its end and that does not lead $i$ to accept $D > P$ is such that $\dg(\ar_0, \hist) ≠ \emptyset$, or equivalently, is such that the theory has some argument to answer to $\hist$, or still equivalently, is such that it contains some $\ar^r_\text{non-linear}$.
+	This property mandates that no argumentative path has been “forgotten” in $\dg$: if some path is found that attacks $\ar_0$ successfully (thus $\ar_0 \in \histend \land \hist \nileadsto D > P$), and if the theory has nothing to answer to it (thus $\dg(\ar_0, \hist) = \emptyset$), then the theory is not Convincing.
+\end{example}
+
+It is now necessary to verify that the claim of convincingness is, first, falsifiable, and second, sufficient to yield validity.
+
+Let us first clarify what falsifiability formally means in our context.
+So far, convincingness is defined only for the “real” relation $\leadsto$; we now need it defined more generally.
+Given any relation $R \subseteq I × \allhist × \Phi$, say that a descriptive theory is convincing under $R$ whenever it is convincing, as defined above, but replacing $\leadsto$ by $R$.
+We can now speak counterfactually of the theory being convincing, or not, assuming the observable relation is $R$ instead of $\leadsto$. 
+Observations of the relation $\leadsto$ can in general include positive statements, of the form $\hist \ileadsto \phi$, and negative ones, of the form $\hist \nileadsto \phi$.
+(One way to obtain such negative observations is to use an incompatible proposition $\phi'$ and deduce from $\hist \ileadsto \phi'$ that $\hist \nileadsto \phi$.) A relation $R \subseteq I × \allhist × \Phi$ is compatible with the positive observations $O \subseteq I × \allhist × \Phi$ and the negative observations $O' \subseteq I × \allhist × \Phi$ iff $O \subseteq R \land R \cap O' = \emptyset$.
+The claim of convincingness is said to be falsifiable iff there exists finite set of observations $O, O' \subseteq I × \allhist × \Phi$ such that $\forall R \subseteq I × \allhist × \Phi \suchthat O \supseteq R \land R \cap O' = \emptyset$, the theory is not convincing under $R$.
+In such a case, no possible relation $R$ compatible with the observations $O, O'$ make the theory convincing; in other words, the observations $O, O'$ prove that the theory is not convincing.
+%\begin{example}[Two claims]
+%	Given a normative theory and $\phi \in \Phi$, the claim $C_1 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \exists \ar \in \allargs \suchthat \ar \ileadstost \phi}$ corresponds to claiming that for all individuals $i \in I$, some argument is $i$-decisive for $\phi$.
+If the set of arguments is infinite, $C_1$ is not falsifiable.
+%	Given $\ar \in \allargs$ and $\phi \in \Phi$, the set $C_2 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \ar \ileadstost \phi}$ denotes the claim that all individuals will consider the argument $\ar$ as decisive for $\phi$.
+This claim is falsified by any observation such that $\hist \nileadsto \phi$ for some $\hist \in \allhist$ with $\ar \in \histend$, thus, $C_2$ is falsifiable.
+%\end{example}
+
+The following theorem states that the descriptive theories defined here are falsifiable, unless they state nothing about anybody’s \ac{DJ}.
+\Cref{sec:prooffals} proves it and describes the set of falsifiers of such theories.
+This theorem implicitly assumes full observability, that is, it supposes that any positive or negative observations are in principle observable and thus available for falsification attempts.
+Further works should investigate to which extent this hypothesis can be relaxed.
+\begin{theorem}
+	\label{th:convfals}
+	The claim of convincingness is falsifiable iff ${\gleadsto} ≠ \emptyset$.
+\end{theorem}
+It can also be seen that if a theory is not constrained in its depth, its claim of convincingness may be unfalsifiable, thus the hypothesis of finite depth is required to obtain this theorem.
+The formal proof of this fact is omitted because it is not especially enlightening; that this fact holds can be seen by examining the use of this hypothesis in the proof of \cref{th:convfals}.
+
+Only remains now to prove that convincingness, together with normative adequacy, is sufficient to obtain validity. The proof is also provided in \cref{sec:prooffals}.
+\begin{theorem}
+	\label{th:convvalid}
+	A normatively adequate empirical theory that is convincing is valid.
+\end{theorem}
+
+\subsection{Effectively comparing models}
+\label{sec:compare}
+Recall from \cref{sec:coh} that $\incompat = \set{(\prop, \prop') \suchthat \forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'}$ denotes the set of pairs of incompatible propositions.
+\commentOC{Does this mandate completeness?}
+Given two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $(\prop, \propbar) \in \incompat$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$.
+Say that the theories are incompatible iff there is at least one pair $(\prop, \propbar) \in \incompat$ that they disagree about.
+
+A path $\histp$ starts with a path $\hist$ iff $\card{\histp} ≥ \card{\hist}$ and $\forall k \in \intvl{1, \card{\hist}}: \histp_k = \hist_k$.
+An increasing sequence of paths is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N$, of paths, 
+such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$.
+
+\begin{theorem}
+	\label{th:proc}
+	Given two incompatible empirical theories for a given normative theory, $\gamma = (\gleadsto[\gamma], \gbeats[\gamma], \alldargs_\gamma, \dbeats[\gamma], +_\gamma)$ and $\delta = (\gleadsto[\delta], \gbeats[\delta], \alldargs_\delta, \dbeats[\delta], +_\delta)$ and given any $i \in I$, there exists a procedure that falsifies one of these theories, queries only $i$, and queries $i$ only about some increasing sequence of paths.
+\end{theorem}
+That procedure is described in \cref{sec:proc}.
 
@@
 
-\subsection{Definition}
-\label{sec:descrdef}
+\subsection{Old definition appendix}
+\label{sec:descrdefapdx}
 In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
@@
 \begin{example}[A theory for $P$]
-	\label{ex:twolottstrings}
 	Define a normative theory as in \cref{ex:twolott}, with an extended set of arguments: define $\allargs$ as the set of all strings.

### 2022-08-06 preamble/acronyms.tex
Improved pres. normative; started better pres. descriptive
DC acro

@@
-\DeclareAcronym{AMCD}{short=amcd, long={Aide Multicritère à la Décision}}
+\DeclareAcronym{AMCD}{short=AMCD, long={Aide Multicritère à la Décision}}
 \DeclareAcronym{AHP}{short=AHP, long={Analytic Hierarchy Process}}
-\DeclareAcronym{AR}{short=ar, long={Argumentative Recommender}}
-\DeclareAcronym{DA}{short=da, long={Decision Analysis}}
+\DeclareAcronym{AR}{short=AR, long={Argumentative Recommender}}
+\DeclareAcronym{DA}{short=DA, long={Decision Analysis}}
+\DeclareAcronym{DC}{short=DC, long={Deliberated Choice}}
 \DeclareAcronym{DJ}{short=DJ, long={Deliberated Judgment}}
-\DeclareAcronym{DM}{short=dm, long={Decision Maker}}
-\DeclareAcronym{DP}{short=dp, long={Deliberated Preference}}
-\DeclareAcronym{MAVT}{short=mavt, long={Multiple Attribute Value Theory}}
-\DeclareAcronym{MCDA}{short=mcda, long={Multicriteria Decision Aid}}
-\DeclareAcronym{MIP}{short=mip, long={Mixed Integer Program}}
+\DeclareAcronym{DM}{short=DM, long={Decision Maker}}
+\DeclareAcronym{DP}{short=DP, long={Deliberated Preference}}
+\DeclareAcronym{MAVT}{short=MAVT, long={Multiple Attribute Value Theory}}
+\DeclareAcronym{MCDA}{short=MCDA, long={Multicriteria Decision Aid}}
+\DeclareAcronym{MIP}{short=MIP, long={Mixed Integer Program}}
+\DeclareAcronym{SCR}{short=SCR, long={Social Choice Rule}}
 \DeclareAcronym{SEU}{short=SEU, long={Subjective Expected Utility}}

### 2022-08-06 simple.tex
Started using P instead of Phi

@@
 \section{Exposure protocol and deliberated choice}
-Let $\Phi = \set{\phi, ¬\phi}$ represent the decision at stake.
-The set $\Phi$ represents two antagonistic acts, such as “buy this object for the price of \$15” and “do not buy this object for the price of \$15”, or “take this job offer” and “decline this job offer”.
+I assume given two antagonistic acts, constituting the decision at stake, such as “buy this object for the price of \$15” and “do not buy this object for the price of \$15”, or “take this job offer” and “decline this job offer”.
+%The letter $\phi$ will be used to denote a generic act (one of these two), and given an act $\phi$, $¬\phi$ denotes the other act.
+Let the set $P = \set{\phi, ¬\phi, 0}$ denote the set of possible preferences, where $\phi$ denote a strict preference for the first act against the other one, $¬\phi$ conversely, and $0$ denotes indifference (both acts are considered equally worth).
 
@@
 
-The function ${\allleadsto}: I × \allhist → \set{\phi, ¬\phi, 0}$ associates to each individual and path an element of $\Phi$ or the special symbol $0$ representing the absence of a strict preference.
-That is, ${\allleadsto}(i, \alpha)$ represents the choice of $i$ following exposure to the arguemnts of $\alpha$, in order.
-The case ${\allleadsto}(i, \alpha) = 0$ is used to represent indifference.
-The notation $\alpha \ileadsto \phi$ will be used to mean ${\allleadsto}(i, \alpha) = \phi$, considering ${\ileadsto} \subseteq \allhist × \Phi$ as a binary relation.
-As usual with binary relations, $\hist \nileadsto \prop$ means ${\allleadsto}(i, \alpha) ≠ \prop$ or equivalently ${\allleadsto}(i, \alpha) \in \set{\nprop, 0}$.
+The function ${\allleadsto}: I × \allhist → P$ associates to each individual and path an element of $P$, ${\allleadsto}(i, \alpha)$ representing the choice of $i$ following exposure to the arguments of $\alpha$, in order.
+That is, ${\allleadsto}(i, \alpha) = \phi$ denotes that $i$ chooses the first act after exposure to $\alpha$, ${\allleadsto}(i, \alpha) = ¬\phi$ denotes $i$ choosing the second act and ${\allleadsto}(i, \alpha) = 0$ is used to represent indifference of $i$.
+The notation $\alpha \ileadsto p$ will be used to mean ${\allleadsto}(i, \alpha) = p$, considering ${\ileadsto} \subseteq \allhist × P$ as a binary relation.
+As usual with binary relations, $\hist \nileadsto p$ means ${\allleadsto}(i, \alpha) ≠ p$ or equivalently ${\allleadsto}(i, \alpha) \in P \setminus \set{p}$.
 

### 2022-08-06 simple.tex
Started def DC with P as pref

@@
 \subsection{Deliberated choice}
-The deliberated choice of $i$ given the exposure protocol $(I, \allargs, {\allleadsto})$ is denoted $\iprops$ and is a strict subset of $\allprops$, with the semantics that $\iprops = \set{\prop}$ iff $\prop$ is considered by $i$ as the best option among the proposed set $\allprops$, after deliberation, given the exposure protocol.
-In other words, if $\iprops = \set{\phi}$, the individual considers $\phi$ strictly better than $\nprop$, after deliberation (and conversely for $\iprops = \set{¬\phi}$); and if $\iprops = \emptyset$, the deliberated judgment of $i$ considers neither $\phi$ nor $¬\phi$ as strictly better than the alternative.
-This latter possibility covers both the situation of indifference between both options (in the sense of being evaluated by $i$ as being exactly equally worth), which will be further developed in \cref{sec:multiple}, or the situation that $\phi$ is neither deliberately strictly better than, exactly equivalent to or strictly worst than $\nprop$.
+The deliberated choice of $i$ given the exposure protocol $(I, \allargs, {\allleadsto})$ is denoted $p_i \in P$, with the semantics that $p_i$ represents the preference of $i$ over the proposed set of two acts, after deliberation, given the exposure protocol.
+In other words, if $p_i = \phi$, the individual considers the first act strictly better than the second one, after deliberation (and conversely for $p_i = ¬\phi$); and if $p_i = 0$, the deliberated choice of $i$ considers neither no act as strictly better than the alternative.
+This latter possibility covers both the situation of indifference between both options (in the sense of being evaluated by $i$ as being exactly equally worth), which will be further developed in \cref{sec:multiple}, or the situation that no act is deliberately strictly better than the other one and that they are also not deliberately exactly equivalent to each other.
+\footnote{It should be clear that $P$ as used as the codomain of ${\leadsto}$ and as the set of possible values of $p_i$ denote different entities.
+The letter is reused simply to reduce notations.
+The value ${\leadsto}(i, \alpha) \in P$ designates the directly observed choice of $i$ whereas the value $p_i \in P$ designates the non directly observable deliberated choice of $i$%; furthermore, $0$ in particular may acquire a very different meaning as the value ${\leadsto}(i, \alpha)$ than as the value $p_i = 0$
+.}
 
@@
 
-The formal definition of $\iprops$ given $(I, \allargs, {\allleadsto})$ requires to define the notion of decisive argument.
+The formal definition of $p_i$ given $(I, \allargs, {\allleadsto})$ requires to define the notion of decisive argument.
 
@@
 
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \nileadsto \nprop$; equivalently, iff $\forall \hist \in \allhist \suchthat \ar \in \histend: {\leadsto}(i, \hist) = \set{\prop}$.
-When $\ar \ileadstost \prop$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view (or just a decisive argument, for short). 
-The deliberated judgment of $i$ is then considered to contain the set of propositions supported by decisive arguments.
+Given $i \in I, p \in P, \ar \in \allargs$, define $\ar \ileadstost p$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto p$.
+When $\ar \ileadstost p$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view given the exposure protocol. 
+The deliberated judgment of $i$ is then considered as the set of propositions supported by decisive arguments.
 \begin{axiom}[Decisive arguments define deliberated judgments]
 	\label{ax:decisive}
-	$\forall i \in I, \prop \in \allprops: 
-		\prop \in \iprops ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop].$
+	$\forall i \in I, p \in P: 
+		p \in P_i ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop].$
 \end{axiom}

### 2022-08-07 simple.tex
Defining DC instead of capturing it; gave up observing incompleteness

@@
 Its length is denoted by $\card{\hist} \in \N$.
-Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}$, $\hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
+Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}: \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
 
@@
 \subsection{Deliberated choice}
-The deliberated choice of $i$ given the exposure protocol $(I, \allargs, {\allleadsto})$ is denoted $p_i \in P$, with the semantics that $p_i$ represents the preference of $i$ over the proposed set of two acts, after deliberation, given the exposure protocol.
-In other words, if $p_i = \phi$, the individual considers the first act strictly better than the second one, after deliberation (and conversely for $p_i = ¬\phi$); and if $p_i = 0$, the deliberated choice of $i$ considers neither no act as strictly better than the alternative.
-This latter possibility covers both the situation of indifference between both options (in the sense of being evaluated by $i$ as being exactly equally worth), which will be further developed in \cref{sec:multiple}, or the situation that no act is deliberately strictly better than the other one and that they are also not deliberately exactly equivalent to each other.
-\footnote{It should be clear that $P$ as used as the codomain of ${\leadsto}$ and as the set of possible values of $p_i$ denote different entities.
-The letter is reused simply to reduce notations.
-The value ${\leadsto}(i, \alpha) \in P$ designates the directly observed choice of $i$ whereas the value $p_i \in P$ designates the non directly observable deliberated choice of $i$%; furthermore, $0$ in particular may acquire a very different meaning as the value ${\leadsto}(i, \alpha)$ than as the value $p_i = 0$
-.}
-
-This latter possibility may look unpleasant, but it is a fact that facing some difficult problems, individuals sometimes are undecided, and it is an a priori empirical possibility that the individual remains undecided (or even, becomes \emph{more} undecided) when considering multiple arguments.
-That classical protocols of natural choice do not allow to observe such incompleteness has often been considered a weakness of those protocols, that our richer observational basis permits to overcome.
-
-The formal definition of $p_i$ given $(I, \allargs, {\allleadsto})$ requires to define the notion of decisive argument.
+The deliberated choice of $i$ given the exposure protocol $(I, \allargs, {\allleadsto})$ is denoted $P_i \subset P$.
+Its formal defnition requires the notion of decisive argument.
 
@@
 When $\ar \ileadstost p$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view given the exposure protocol.
-The deliberated judgment of $i$ is then considered as the set of propositions supported by decisive arguments.
-\begin{axiom}[Decisive arguments define deliberated judgments]
-	\label{ax:decisive}
+
+The deliberated choice of $i$ is then considered as the set of propositions supported by decisive arguments.
+\begin{definition}[Deliberated choice]
+	\label{def:decisive}
 	$\forall i \in I, p \in P: 
-		p \in P_i ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop].$
-\end{axiom}
+		p \in P_i ⇔ [\exists \ar \in \allargs \suchthat \ar \ileadstost p].$
+\end{definition}
+
+It follows from the consideration of “end” as the last \emph{two} arguments that decisive arguments can argue for at most one proposition, thus, that the deliberated choice cannot hold more than one proposition.
+\begin{theorem}[Deliberated choice singularity]
+	$\forall i \in I: \card{P_i} ≤ 1$.
+\end{theorem}
+\begin{proof}
+	Assume that $\exists \ar, \ar' \in \allargs, p, p' \in P \suchthat \ar \ileadstost p \land \ar' \ileadstost p'$.
+	Since $\ar \ileadstost p$, $(\ar, \ar') \ileadsto p$, and since $\ar' \ileadstost p'$, $(\ar, \ar') \ileadsto p'$, hence $p' = p$.
+\end{proof}
+
+The intended semantics is that $P_i$ represents the preference of $i$ over the proposed set of two acts, after deliberation, given the exposure protocol.
+In other words, if $P_i = \set{\phi}$, the individual considers the first act strictly better than the second one, after deliberation (and conversely for $P_i = \set{¬\phi}$); if $P_i = \set{0}$, the deliberated judgment of $i$ is that both acts are equally worth; and if $P_i = \emptyset$, no act is deliberately strictly better than the other one and they are also not deliberately exactly equivalent to each other.
+
+This latter possibility may look unpleasant, but it is a fact that facing some difficult problems, individuals sometimes are undecided, and it is an a priori empirical possibility that the individual remains undecided (or even, becomes \emph{more} undecided) when considering multiple arguments.
 
@@
 \label{sec:static}
-\Cref{ex:tutor} suggests a simple form for theories of deliberated choice: suffice to determine an argument $\ar \in \allargs$ and an alternative $\prop \in \Phi$ such that the theory claims that $\forall i \in I: \ar \ileadstost \prop$ and that $\prop \in \iprops$.
+\Cref{ex:tutor} suggests a simple form for theories of deliberated choice: suffice to determine an argument $\ar \in \allargs$ and an alternative $\prop \in \Phi$ such that the theory claims that $\forall i \in I: \ar \ileadstost \prop$ and that $\forall i \in I: \prop \in \iprops$.
 
@@
 \end{definition}
-Such a theory is said to be truthful iff $\forall i \in I: \ar \ileadstost \prop$, and to be correct iff $\prop \in \iprops$.
+Such a theory is said to be truthful iff $\forall i \in I: \ar \ileadstost \prop$, and to be correct iff $\forall i \in I: \prop \in \iprops$.
 We can then say that such theories are valid, meaning that their truthfulness implies their correctness.
@@
 \begin{proof}
-	The result immediately follows from \cref{ax:decisive}.
+	This follows immediately from \cref{def:decisive}.
 \end{proof}
@@
 
-The following example illustrates this same point in a simpler setting which permits a complete definition of $\allargs$ and $\leadsto$.%, which permits defining the setting completely at the price of a reduced realism.
+The following example illustrates this same point in a constrained setting which permits a complete definition of $\allargs$ and $\leadsto$.%, which permits defining the setting completely at the price of a reduced realism.
 \begin{example}[A decision problem about two lotteries]
@@
 \label{sec:dynamic}
-An argumentative theory of \ac{DC} is defined as a tuple $(\gleadsto, \dg)$, where ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation and $\dg$ is a defense relation; satisfying bounded depth.
+An argumentative theory of \ac{DC} is defined as a tuple $(p, \gleadsto, \dg)$, where $p \in P$ is the proposition supported by the theory, ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation and $\dg$ is a defense relation; satisfying bounded depth.
 

### 2022-08-07 simple.tex
Def Argumentative theory

@@
 \label{sec:dynamic}
-An argumentative theory of \ac{DC} is defined as a tuple $(p, \gleadsto, \dg)$, where $p \in P$ is the proposition supported by the theory, ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation and $\dg$ is a defense relation; satisfying bounded depth.
-
-\subsection{Old definition}
-\label{sec:descrdef}
-In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
-These concepts are now defined formally.
+An argumentative theory of \ac{DC} $\gamma$ is defined as a tuple $(\pga, \arga, \dg)$, where $\pga \in P$ is the proposition supported by the theory, $\arga \in \allargs$ is the initial argument and $\dg$ is a defense relation.
 \commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}
 
-An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ defines the set of supported  propositions and, for each supported propositions, the set of initial arguments for these propositions.
-More precisely, let $\gpropse$, the range of ${\gleadsto}$, be called the propositions \emph{supported} by the descriptive theory.
-Given such a supported proposition $\prop \in \gpropse$, let $\gleadstoinv(\prop) = \set{\ar \in \allargs \suchthat \ar \gleadsto \prop}$ be called the initial arguments in favor of $\prop$.
-
-A defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ is a right-unique relation, thus given any $\ar \in \allargs, \hist \in \allhist$, $\dg(\ar, \hist)$ is empty or is a singleton.
+The defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ defines the argumentation strategy of the theory.
+Informally speaking, its role is to produce the arguments that the theory claims will convince the individuals in $I$ to choose $\pga$.
+Assuming that the theory has played an argument $\ar_0$ and a path $\hist$ challenges its intended conclusion in favor of $\pga$ (as judged by the individual), $\dg(\ar_0, \hist)$ is the argument that the theory plays as a counter-argument to the path $\hist$.
+
+Formally speaking, a defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ is a right-unique relation satisfying bounded depth.
+Right-unique means that given any $\ar \in \allargs, \hist \in \allhist$, $\dg(\ar, \hist)$ is empty or is a singleton.
 %, and must satisfy $\ar \notin \histend ⇒ \dg(\ar, \hist) = \emptyset$.
@@
 Say that $\ar_1$ defends $\ar_0$ iff $\exists \hist \suchthat \dg(\ar_0, \hist) = \ar_1$.
-Define $\dg(\ar) = \dfp(\ar) = \dg(\ar, \allhist) = \set{\dg(\ar, \hist) \suchthat \hist \in \allhist} \subseteq \allargs$ as all the defenders of $\ar$.
-The relation $\dg$ defines the argumentation strategy of the theory.
-Informally speaking, its role is to adapt the arguments the theory produces to the reactions of the individual it is trying to convince.
-Assuming the theory has played an argument $\ar_0$ and a path $\hist$ challenges some of the conclusions this argument supports (as judged by the individual), $\dg(\ar_0, \hist)$ is the argument that the theory plays as a counter-argument to the path $\hist$.
-%The condition that when $\dg(\ar_0, \hist)$, $\ar_0 \in \histend$ is imposed for simplicity: as will appear, an argument $\ar_0$ needs defense only when it is challenged by some path $\hist \suchthat \ar_0 \in \histend$, thus, letting $\dg$ define counter-arguments to paths not satisfying this condition would be of no use.
-
-This mechanism permits to define defenders of defenders of an argument, $\dg(\dg(\ar))$, defenders of defenders of defenders of an argument, … 
-For the results to be presented here to hold, an empirical theory must be a priori restricted in the maximal “depth” of its argumentation strategy, in the following sense. 
-\commentYM{ok soit, ça semble raisonnable, mais tu n'as pas de raison plus forte, j'adopterais une formulation plus modeste et ouverte, du genre "ça semble souhaitable"}
+Define $\dg(\ar) = \dg(\ar, \allhist) = \set{\dg(\ar, \hist) \suchthat \hist \in \allhist} \subseteq \allargs$ as all the defenders of $\ar$.
+
+This mechanism permits to define defenders of defenders of an argument, $\dg(\dg(\ar))$, defenders of defenders of defenders of an argument, … This yields the following notion of depth.
 Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
-The bounded depth condition on a descriptive theory imposes that
+The bounded depth condition on the defense relation imposes that
 $\exists k \in \N \suchthat (\dg)^k(\gleadstoinv(\allprops)) = \emptyset$.
 The smallest such $k$ is called the depth of the theory.
+\commentYM{ok soit, ça semble raisonnable, mais tu n'as pas de raison plus forte, j'adopterais une formulation plus modeste et ouverte, du genre "ça semble souhaitable"}
+
+%The condition that when $\dg(\ar_0, \hist)$, $\ar_0 \in \histend$ is imposed for simplicity: as will appear, an argument $\ar_0$ needs defense only when it is challenged by some path $\hist \suchthat \ar_0 \in \histend$, thus, letting $\dg$ define counter-arguments to paths not satisfying this condition would be of no use.
+
+\subsubsection{Validity (draft)}
+I believe that I will need the following axiom.
+
+If truthful, given $a_2$ defending $a_1$, $\forall \hist \suchthat a_2 \in \histend: (a_1, \hist) \ileadsto p ⇒ \hist \ileadsto p$.
+
+This seems reasonable because $a_2$, as a defender of $a_1$, “contains” $a_1$.
+
+\subsection{Old definition}
+\label{sec:descrdef}
 

### 2022-08-10 simple.tex
Claims of argumentative theories

@@
 We consider subjects as black boxes and only require a capacity of observation of their choices after exposure to arguments.
-Depending on the exposure protocol and the subject, it is of course possible for the arguments to never affect any judgment of the subject, a conclusion that may be interesting in its own right.
+Depending on the exposure protocol and the subject, it is of course possible for the arguments to never affect any choice of the subject, a conclusion that may be interesting in its own right.
 
@@
 	\label{def:static}
-	A static theory is a pair $(\ar, \prop)$ for some $\ar \in \allargs$ and some $\prop \in \Phi$.
+	A static theory is a pair $(p, \ar)$ for some $p \in P$ and some $\ar \in \allargs$.
 \end{definition}
-Such a theory is said to be truthful iff $\forall i \in I: \ar \ileadstost \prop$, and to be correct iff $\forall i \in I: \prop \in \iprops$.
+A static theory $(p, \ar)$ is said to be truthful iff $\forall i \in I: \ar \ileadstost \prop$, and to be correct iff $\forall i \in I: \prop \in \iprops$.
 We can then say that such theories are valid, meaning that their truthfulness implies their correctness.
@@
 \label{sec:dynamic}
-An argumentative theory of \ac{DC} $\gamma$ is defined as a tuple $(\pga, \arga, \dg)$, where $\pga \in P$ is the proposition supported by the theory, $\arga \in \allargs$ is the initial argument and $\dg$ is a defense relation.
+An argumentative theory of \ac{DC} $\gamma$ is defined as a tuple $(\pga, \arga, \dg)$, where $\pga \in P$ is the proposition supported by the theory, $\arga \in \allargs$ is the initial argument in favor of $\pga$ and $\dg$ is a defense relation.
 \commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}
@@
 The defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ defines the argumentation strategy of the theory.
-Informally speaking, its role is to produce the arguments that the theory claims will convince the individuals in $I$ to choose $\pga$.
+Informally speaking, its role is, together with $\arga$, to produce the arguments that the theory claims will convince the individuals in $I$ to choose $\pga$.
 Assuming that the theory has played an argument $\ar_0$ and a path $\hist$ challenges its intended conclusion in favor of $\pga$ (as judged by the individual), $\dg(\ar_0, \hist)$ is the argument that the theory plays as a counter-argument to the path $\hist$.
 
-Formally speaking, a defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ is a right-unique relation satisfying bounded depth.
+Formally speaking, a defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ is a right-unique relation satisfying bounded depth (to be defined shortly).
 Right-unique means that given any $\ar \in \allargs, \hist \in \allhist$, $\dg(\ar, \hist)$ is empty or is a singleton.
@@
 
-\subsubsection{Validity (draft)}
-I believe that I will need the following axiom.
-
-If truthful, given $a_2$ defending $a_1$, $\forall \hist \suchthat a_2 \in \histend: (a_1, \hist) \ileadsto p ⇒ \hist \ileadsto p$.
-
+An argumentative theory claims that its argumentation strategy, embodied by $\arga$ and $\dg$, will convince the individuals in $I$.
+More precisely, given $i \in I$, it claims that $\arga$ either is a decisive argument for $\pga$, or, if $\arga$ is not, that the theory will defend the argument by replying to every counter-argument to $\arga$ with an argument that either is a decisive argument for $\pga$ or, in turn, will be defended by the theory, and so on as long as the theory has counter-arguments to produce; the theory claiming that some argument along that chain is decisive.
+
+To define this formally, note that either $\arga$ is a decisive argument for $\pga$, or some paths challenge this claim, namely those in $\set{\hist \in \allhist \suchthat \arga \in \histend \land \hist \nileadsto \pga}$.
+Generalizing this observation, given $i \in I$, define $\dgi(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \in \histend \land \hist \nileadsto \pga} \subseteq \dg(\ar)$ as the subset of defenders of $\ar$ required for convincing $i$ of choosing $\pga$.
+Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
+Define $\gargsi \subseteq \allargs$ as the transitive closure of $\arga$ under $\dgi$: $\gargsi = \cup_{k \in \N} (\dgi)^k(\arga)$.
+The set $\gargsi$ is the set of arguments required to convince $i$ of choosing $\pga$.
+
+Given $\ar \in \gargsi$, say that $\ar$ $i$-defends $\pga$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend \land \hist \nileadsto \pga: d(\ar, \hist) ≠ \emptyset$.
+Note that if an argument fails to $i$-defend $\pga$, then the argumentative strategy of the theory has failed: some path challenge an argument of the theory, and the theory is not ready to counter-argue against that path.
+
+Accordingly, an argumentative theory claims that all the arguments required to convince $i$ of choosing $\pga$ do $i$-defend $\pga$.
+It is said to be truthful iff this claim is correct.
+\begin{definition}[Truthfulness]
+	\label{def:truth}
+	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, \ar \in \gargsi: \ar$ $i$-defends $\pga$.
+\end{definition}
+
+NB we can check $a_1, a_x, a_y, a_2, …$ but not other paths after $a_2$.
+Thus, among the paths that contain $a_2$, they all contain $a_1$ before $a_2$.
+
+Note that a static theory $(p, \ar)$ can be considered as an argumentative theory $(p, \ar, \emptyset)$, and is truthful in the sense of \cref{sec:static} iff $(p, \ar, \emptyset)$ is truthful in the sense of \cref{def:truth}.
+
+Associated with an argumentative theory also comes the following axiom, that mandates that if some argument $\ar_2$ defends some argument $\ar_1$, and if $\ar_2$ leads $i$ to opt for $\pga$ in some path containing $\ar_1$, then $\ar_1$ can be omitted and the path will still lead $i$ to opt for $\pga$.
+
+\begin{axiom}[Omitting the defended argument]
+	\label{ax:omitting}
+	If the theory is truthful, then $\forall \ar_1, \ar_2 \in \gargsi, \hist \suchthat \ar_2 \in \dgi(\ar_1) \land \ar_2 \in \histend: (\ar_1, \hist) \ileadsto \pga ⇒ \hist \ileadsto \pga$.
+\end{axiom}
+This is called an axiom because it cannot be falsified using observables.
+It has to be accepted on the basis of the rest of the observations.
+What it states are counterfactuals: if $i$ had been presented with $\hist$ not containing $\ar_1$, and assuming $i$ would have accepted an argument $\ar_2$ for $\pga$, …
 This seems reasonable because $a_2$, as a defender of $a_1$, “contains” $a_1$. 
+(To be finished.)
+
+An argumentative theory is said to be correct iff $\forall i \in I: \pga \in \iprops$.
+As previously, it is said to be valid iff its truthfulness leads to its correctness, except that the above axiom needs now be included as a price for the added flexibility of the theory.
+\begin{theorem}[Validity]
+	If an argumentative theory is truthful, then \cref{ax:omitting} implies that the theory is correct.
+\end{theorem}
+\begin{proof}
+	Assume, to start with, that $\arga$ is not decisive because $\hist \nileadsto \pga, \arga \in \histend$.
+	Assume that $\dgi(\arga) = \ar_2$ with no further hist against it.
+	…
+\end{proof}
 

### 2022-08-10 simple.tex
Proof sketch seems okay with def Axiom strengthened

@@
 
-Given $\ar \in \gargsi$, say that $\ar$ $i$-defends $\pga$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend \land \hist \nileadsto \pga: d(\ar, \hist) ≠ \emptyset$.
-Note that if an argument fails to $i$-defend $\pga$, then the argumentative strategy of the theory has failed: some path challenge an argument of the theory, and the theory is not ready to counter-argue against that path.
-
-Accordingly, an argumentative theory claims that all the arguments required to convince $i$ of choosing $\pga$ do $i$-defend $\pga$.
+An argumentative theory claims that whenever some of its arguments fail to convince $i$ of choosing $\pga$, it can argue something else.
 It is said to be truthful iff this claim is correct.
@@
 	\label{def:truth}
-	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, \ar \in \gargsi: \ar$ $i$-defends $\pga$.
+	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, \ar_2 \in \dgi(\arga), \ar_3 \in \dgi(\ar_2), …, \forall \hist \in \allhist \suchthat \hist = (\arga, …, \ar_2, …, \ar_3, …) \land \ar_3 \in \histend: [\hist \nileadsto \pga ⇒ d(\ar_3, \hist) ≠ \emptyset]$.
 \end{definition}
 
-NB we can check $a_1, a_x, a_y, a_2, …$ but not other paths after $a_2$.
-Thus, among the paths that contain $a_2$, they all contain $a_1$ before $a_2$.
-
 Note that a static theory $(p, \ar)$ can be considered as an argumentative theory $(p, \ar, \emptyset)$, and is truthful in the sense of \cref{sec:static} iff $(p, \ar, \emptyset)$ is truthful in the sense of \cref{def:truth}.
@@
 
-\begin{axiom}[Omitting the defended argument]
+\begin{axiom}[Omitting defended arguments]
 	\label{ax:omitting}
-	If the theory is truthful, then $\forall \ar_1, \ar_2 \in \gargsi, \hist \suchthat \ar_2 \in \dgi(\ar_1) \land \ar_2 \in \histend: (\ar_1, \hist) \ileadsto \pga ⇒ \hist \ileadsto \pga$.
+	If the theory is truthful, then $\forall \ar_2 \in \dgi(\arga), \ar_3 \in \dgi(\ar_2), …, \hist \suchthat \ar_7 \in \histend: (…, \ar_4, \ar_5, …, \hist) \ileadsto \pga ⇒ (…, \ar_5, …, \hist) \ileadsto \pga$.
 \end{axiom}
@@
 \begin{proof}
-	Assume, to start with, that $\arga$ is not decisive because $\hist \nileadsto \pga, \arga \in \histend$.
-	Assume that $\dgi(\arga) = \ar_2$ with no further hist against it.
-	…
+	Assume, to start with, that the theory is of depth 2, more precisely, $\arga$ is not decisive because $\hist \nileadsto \pga, \arga \in \histend$ and $\dgi(\arga) = \ar_2$ with no further hist against it.
+
+	Consider any $i \in I$.
+	Assume $\arga$ is not decisive.
+
+	Truthfulness brings this.
+	$\forall \hist = (\arga, …, \ar_2, …) \suchthat \ar_2 \in \histend: \hist \ileadsto \pga$.
+
+	The axiom brings this.
+	$\forall \hist \suchthat \ar_2 \in \histend: (\arga, \hist) \ileadsto \pga ⇒ \hist \ileadsto \pga$.
+
+	Consider any $\hist \suchthat \ar_2 \in \histend$. We want to show that $\hist \ileadsto \pga$.
+	If it starts with $\arga$: done thanks to truthfulness.
+	Otherwise: done thanks to truthfulness and the axiom.
+
+Consider now a theory of depth 3. 
+	Consider any $i \in I$.
+	Assume $\arga$ not decisive, $\ar_2$ not decisive.
+
+	Truthfulness brings this.
+	$\forall \hist = (\arga, …, \ar_2, …, \ar_3, …) \suchthat \ar_3 \in \histend: \hist \ileadsto \pga$.
+
+	The axiom brings this.
+	$\forall \hist \suchthat \ar_3 \in \histend: (\ar_2, \hist) \ileadsto \pga ⇒ (\hist) \ileadsto \pga$.
+	And this.
+	$\forall \hist \suchthat \ar_3 \in \histend: (\ar_1, \ar_2, \hist) \ileadsto \pga ⇒ (\ar_2, \hist) \ileadsto \pga$.
+	And $(\ar_1, \ar_2, \hist) \ileadsto \pga$ holds thanks to truthfulness, so $(\ar_2, \hist) \ileadsto \pga$, so $\hist \ileadsto \pga$.
+
+	Consider any $\hist \suchthat \ar_3 \in \histend$. We want to show that $\hist \ileadsto \pga$.
+	If it includes a1 then a2, ok thanks to truthfulness.
+
 \end{proof}

### 2022-08-11 simple.tex
Def Truthfulness using arguments in order

@@
 It is said to be truthful iff this claim is correct.
+More precisely, its claims are about paths of the sort $\hist = (\arga, …, \ar_2, …, \ar_3, …)$ where $\ar_2 \in \dgi(\arga)$, $\ar_3 \in \dgi(\ar_2)$, … The following definition makes this precise.
 \begin{definition}[Truthfulness]
 	\label{def:truth}
-	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, \ar_2 \in \dgi(\arga), \ar_3 \in \dgi(\ar_2), …, \forall \hist \in \allhist \suchthat \hist = (\arga, …, \ar_2, …, \ar_3, …) \land \ar_3 \in \histend: [\hist \nileadsto \pga ⇒ d(\ar_3, \hist) ≠ \emptyset]$.
+	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, k \in \N^*, (\ar_j) \in \allargs^k, \hist \in \allhist \suchthat [\ar_1 = \arga \land \ar_k \in \histend \land d(\ar_k, \hist) = \emptyset \land \forall j \in \intvl{2, k}: \hist^{-1}(\ar_{j - 1}) < \hist^{-1}(\ar_j) \land \ar_j \in \dgi(\ar_{j - 1})]: [\hist \ileadsto \pga]$.
 \end{definition}

### 2022-08-11 simple.tex
Truthfulness without order

@@
 	\label{def:truth}
-	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, k \in \N^*, (\ar_j) \in \allargs^k, \hist \in \allhist \suchthat [\ar_1 = \arga \land \ar_k \in \histend \land d(\ar_k, \hist) = \emptyset \land \forall j \in \intvl{2, k}: \hist^{-1}(\ar_{j - 1}) < \hist^{-1}(\ar_j) \land \ar_j \in \dgi(\ar_{j - 1})]: [\hist \ileadsto \pga]$.
+	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, k \in \N^*, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist \in \allhist \suchthat [\ar_1 = \arga \land \ar_k \in \histend \land d(\ar_k, \hist) = \emptyset \land \forall j \in \intvl{1, k}: \ar_j \in R(\hist) \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1})]: [\hist \ileadsto \pga]$.
 \end{definition}

### 2022-08-11 simple.tex
Axiom, formally

@@
 	\label{ax:omitting}
-	If the theory is truthful, then $\forall \ar_2 \in \dgi(\arga), \ar_3 \in \dgi(\ar_2), …, \hist \suchthat \ar_7 \in \histend: (…, \ar_4, \ar_5, …, \hist) \ileadsto \pga ⇒ (…, \ar_5, …, \hist) \ileadsto \pga$.
+	If the theory is truthful, then $\forall i \in I, k \in \N^*, l \in \intvl{2, k}, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist, \beta \in \allhist \suchthat [\ar_k \in \histend \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1})]:
+	(\beta, \ar_{l - 1}, \ar_l, \hist) \ileadsto \pga ⇒ (\beta, \ar_l, \hist) \ileadsto \pga$.
 \end{axiom}

### 2022-08-11 simple.tex
A correct sketch, and some refs

@@
 Observing subjects performing acts of choice is the basis of much work in econometrics.
-Such acts have been used, among others, to give an observable basis to the concept of preference, thanks in part to the seminal work of Samuelson.
+Such acts have been used, among others, to give an observable basis to the concept of preference \citep{samuelson_foundations_1983}.
 %Acts of choice are considered here in the broad sense of choice between courses of actions, encompassing the simple setting of choosing between various elementary consumption bundles as well as settings involving more abstract acts such as choosing a strategy in a game-theoretical setting.
@@
 As an example of the former kind, typical willingness to pay studies asks the subject whether she prefers an object at some price or another object at another price, describing the objects in a way that is considered immediately understandable by the subject (or simply showing the objects).
-Examples of the latter kind include the celebrated work of Kahneman and Tversky.
-
-On the other hand, since at least the seminal work of Fishkin, another sort of judgment involving subjective desirability is emerging as also worth studying.
+Examples of the latter kind include the celebrated work of Kahneman and Tversky \citep{bell_descriptive_1988, kahneman_thinking_2012}.
+
+On the other hand, since at least the seminal work of \citet{fishkin_when_2011}, another sort of judgment involving subjective desirability is emerging as also worth studying.
 These are judgments given by subjects after arguments in favor and against different possible stance have been considered.
@@
 \subsection{An example and a discussion about observability}
-The following toy example is inspired by citet[p.~59]{Railton}, who uses this example to support his claim that beliefs may influence decisions. Here is his story.
+The following toy example is inspired by citet[p.~59]{Railton}\commentOC{TODO}, who uses this example to support his claim that beliefs may influence decisions. Here is his story.
 \begin{quote}
@@
 It may also be that, for each individual who considers relevant some arguments $A$ against the proposed concrete action, it is possible to give counter-arguments $A'$ that will convince the individual to opt for the proposal.
-One of the settings discussed by citet{sunstein} permits to illustrate this point more concretely.
+One of the settings discussed by \citet{thaler_nudge_2009} permits to illustrate this point more concretely.
 Let $I$ be a set of workers interested in establishing a savings plan. 
@@
 \end{theorem}
-\begin{proof}
+\begin{proof}[Sketch of proof]
 	Assume, to start with, that the theory is of depth 2, more precisely, $\arga$ is not decisive because $\hist \nileadsto \pga, \arga \in \histend$ and $\dgi(\arga) = \ar_2$ with no further hist against it.
@@
 	Assume $\arga$ is not decisive.
-
-	Truthfulness brings this.
-	$\forall \hist = (\arga, …, \ar_2, …) \suchthat \ar_2 \in \histend: \hist \ileadsto \pga$.
-
-	The axiom brings this.
-	$\forall \hist \suchthat \ar_2 \in \histend: (\arga, \hist) \ileadsto \pga ⇒ \hist \ileadsto \pga$.
-
 	Consider any $\hist \suchthat \ar_2 \in \histend$. We want to show that $\hist \ileadsto \pga$.
-	If it starts with $\arga$: done thanks to truthfulness.
-	Otherwise: done thanks to truthfulness and the axiom.
+
+IF $\hist$ contains $\arga$ before $\ar_2$, done by TF.
+Otherwise, define $hist'$ which has a1 just before a2.
+Apply TF on hist' then apply axiom.
 
@@
 	Assume $\arga$ not decisive, $\ar_2$ not decisive.
-
-	Truthfulness brings this.
-	$\forall \hist = (\arga, …, \ar_2, …, \ar_3, …) \suchthat \ar_3 \in \histend: \hist \ileadsto \pga$.
-
-	The axiom brings this.
-	$\forall \hist \suchthat \ar_3 \in \histend: (\ar_2, \hist) \ileadsto \pga ⇒ (\hist) \ileadsto \pga$.
-	And this.
-	$\forall \hist \suchthat \ar_3 \in \histend: (\ar_1, \ar_2, \hist) \ileadsto \pga ⇒ (\ar_2, \hist) \ileadsto \pga$.
-	And $(\ar_1, \ar_2, \hist) \ileadsto \pga$ holds thanks to truthfulness, so $(\ar_2, \hist) \ileadsto \pga$, so $\hist \ileadsto \pga$.
-
 	Consider any $\hist \suchthat \ar_3 \in \histend$. We want to show that $\hist \ileadsto \pga$.
+
 	If it includes a1 then a2, ok thanks to truthfulness.
-
+	Otherwise, build hist3 that has a1 then a2 just before a3.
+	That’s ok thanks to TF.
+	By axiom, hist2 with only a2 just before a3 is thus ok.
+	By axiom, hist is thus ok.
 \end{proof}

### 2022-08-11 simple.tex
Rm a lot of stuff

@@
 
-\subsection{Old definition}
-\label{sec:descrdef}
-
-Here is an example of a theory that does not use an argumentation strategy, but simply plays an argument that it claims is decisive for everybody.
-\begin{example}[Constant argumentation]
-	Given the normative theory of \cref{ex:twolott}, define ${\gleadsto} = \set{(\ar_0, D > P)}$ and $\dg = \emptyset$. This defines a descriptive theory of depth $1$ for that normative theory.
-\end{example}
-
-\begin{example}[A theory for $P$]
-	\label{ex:twolottstrings}
-	Define a normative theory as in \cref{ex:twolott}, with an extended set of arguments: define $\allargs$ as the set of all strings.
-(This correspondingly changes $\allhist$ and thus $\ileadsto$, which must be extended to its new domain.) Define $\ar_0$ as in \cref{ex:twolott}.
-	Define $\ar_\text{for$P$}$ as the text “We recommend to adopt $P$: it has a much higher probability of winning.” 
-	Define ${\gleadsto} = \set{(\ar_\text{for$P$}, P > D)}$.
-	In order to define a counter-argument to $\ar_0$, given a real number $r \in \R$, define $\ar^r_\text{non-linear}$ as the text “$D$ is better than $P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
-For example, consider a choice between winning $r$ dollars with probability $0.8$ and winning $2r$ dollars with probability $0.4$.
-They have the same expected gain, but the first one is clearly preferrable.
-Therefore, we recommend to rather pick $P$ as it presents a much better chance of earning money”.
-(The value of $r$ and $2r$ is to be used in the relevant places in  the text.)
-	Define $\dg = \set{(\ar_\text{for$P$}, \hist, \ar^{10^6}_\text{non-linear}) \suchthat \hist \in \allhist \land \ar_0 \in \hist}$.
-This strategy anticipates a possible attack using $\ar_0$ against $\ar_\text{for$P$}$, and prepares $\ar^{10^6}_\text{non-linear}$ as a counter-argument.
-	This defines a descriptive theory of depth $2$.
-\end{example}
-
-The following less trivial example of a descriptive theory illustrates a theory that claims to be able to answer an infinite number of arguments.
-This also shows that the bounded depth constraint does not imply finiteness of the relation $\dg$.
-\begin{example}[Infinite $\dg$]
-	\label{ex:infinite}
-	Define a normative theory and the arguments $\ar_0$ and $\ar^r_\text{non-linear}$ for any $r \in \R$ as in \cref{ex:twolottstrings}.
-	Define ${\gleadsto} = \set{(\ar_0, D > P)}$.
-	Define $\ar_\text{linear}$ as the text “We agree that when the money amounts involved are large and the game is not repeated, there is no good reason to consider only expected gains when choosing a lottery.
-But in our case, the money amounts are small and the game is repeated.
-Therefore, expected gain is the right indicator to consider for a systematic and sound decision strategy.”
-	Define $+$ as the concatenation operator over strings.
-	Define $\dg = \set{(\ar_0, \ar^r_\text{non-linear}, \ar_0 + \ar_\text{linear}) \suchthat r \in \R}$.
-This strategy sets up the argument $\ar_0 + \ar_\text{linear}$ as an answer to any argument of the form described in \cref{ex:twolottstrings}, arguing for non-linearity of utility of money.
-	This defines a descriptive theory of depth $2$.
-\end{example}
-
-\subsection{Validity and falsification}
-\label{sec:validity}
-An empirical theory claims to be valid, in the following sense.
-\begin{definition}[Validity]
-	An empirical theory is \emph{valid} iff $\forall i \in I, \prop \in \gpropse: \prop \in \iprops$.
-\end{definition}
-To achieve this goal, it claims that it is able to produce decisive arguments for its supported propositions.
-These arguments can vary according to the individual $i \in I$.
-Given an individual, the theory claims that a decisive argument will be systematically found by starting from an initial argument given by $\gleadsto$, and following a chain of defense defined by $\dg$ as required, depending on the paths that challenge the arguments produced along the way, as judged by the individual $i$.
-The property that a theory manages to systematically produce decisive arguments in such a way is named Convincingness.
-Defining it precisely requires to define first the notion of required arguments.
-
-Given $i \in I, \prop \in \gpropse$, define $\dgip(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \notin \histend \land \hist \nileadsto \phi} \subseteq \dg(\ar)$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\prop$.
-Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
-Define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\prop)$ under $\dgip$: $\gargs = \cup_{k \in \N} (\dgip)^k({\gleadstoinv}(\prop))$.
-The set $\gargs$ is the set of arguments required to convince $i$ of $\phi$.
-\begin{example}[Required arguments]
-	\label{ex:required}
-	Continuing \cref{ex:infinite}, define the subset of individuals that find some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ as the set of $i \in I$ such that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \ar^r_\text{non-linear} \in \range(\hist) \land \hist \nileadsto D > P$.
-	We see that for any $i$ in that set of individuals, $\gargs[D > P] = \set{\ar_0, \ar_0 + \ar_\text{linear}}$, and for any $i$ in the complementary set of individuals, $\gargs[D > P] = \set{\ar_0}$.
-\end{example}
-
-Given $\ar \in \gargs$, say that $\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend \land \hist \nileadsto \phi: d(\ar, \hist) ≠ \emptyset$.
-\begin{definition}[Convincingness]
-	An empirical theory is \emph{convincing} iff $\forall i \in I, \prop \in \gpropse, \ar \in \gargs: \ar$ $i$-defends $\prop$.
-\end{definition}
-\begin{example}[Convincingness]
-	Pursuing with \cref{ex:required}, that theory will be convincing iff either $i$ finds some argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and both $\ar_0$ and $\ar_0 + \ar_\text{linear}$ $i$-defend $D > P$, or $i$ does not find any argument $\ar^r_\text{non-linear}$ convincing in presence of $\ar_0$ and $\ar_0$ $i$-defends $D > P$.
-
-	$\ar_0$ $i$-defends $D > P$ iff any argumentative path $\hist$ that contains $\ar_0$ towards its end and that does not lead $i$ to accept $D > P$ is such that $\dg(\ar_0, \hist) ≠ \emptyset$, or equivalently, is such that the theory has some argument to answer to $\hist$, or still equivalently, is such that it contains some $\ar^r_\text{non-linear}$.
-	This property mandates that no argumentative path has been “forgotten” in $\dg$: if some path is found that attacks $\ar_0$ successfully (thus $\ar_0 \in \histend \land \hist \nileadsto D > P$), and if the theory has nothing to answer to it (thus $\dg(\ar_0, \hist) = \emptyset$), then the theory is not Convincing.
-\end{example}
-
-It is now necessary to verify that the claim of convincingness is, first, falsifiable, and second, sufficient to yield validity.
-
-Let us first clarify what falsifiability formally means in our context.
-So far, convincingness is defined only for the “real” relation $\leadsto$; we now need it defined more generally.
-Given any relation $R \subseteq I × \allhist × \Phi$, say that a descriptive theory is convincing under $R$ whenever it is convincing, as defined above, but replacing $\leadsto$ by $R$.
-We can now speak counterfactually of the theory being convincing, or not, assuming the observable relation is $R$ instead of $\leadsto$. 
-Observations of the relation $\leadsto$ can in general include positive statements, of the form $\hist \ileadsto \phi$, and negative ones, of the form $\hist \nileadsto \phi$.
-(One way to obtain such negative observations is to use an incompatible proposition $\phi'$ and deduce from $\hist \ileadsto \phi'$ that $\hist \nileadsto \phi$.) A relation $R \subseteq I × \allhist × \Phi$ is compatible with the positive observations $O \subseteq I × \allhist × \Phi$ and the negative observations $O' \subseteq I × \allhist × \Phi$ iff $O \subseteq R \land R \cap O' = \emptyset$.
-The claim of convincingness is said to be falsifiable iff there exists finite set of observations $O, O' \subseteq I × \allhist × \Phi$ such that $\forall R \subseteq I × \allhist × \Phi \suchthat O \supseteq R \land R \cap O' = \emptyset$, the theory is not convincing under $R$.
-In such a case, no possible relation $R$ compatible with the observations $O, O'$ make the theory convincing; in other words, the observations $O, O'$ prove that the theory is not convincing.
-%\begin{example}[Two claims]
-%	Given a normative theory and $\phi \in \Phi$, the claim $C_1 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \exists \ar \in \allargs \suchthat \ar \ileadstost \phi}$ corresponds to claiming that for all individuals $i \in I$, some argument is $i$-decisive for $\phi$.
-If the set of arguments is infinite, $C_1$ is not falsifiable.
-%	Given $\ar \in \allargs$ and $\phi \in \Phi$, the set $C_2 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \ar \ileadstost \phi}$ denotes the claim that all individuals will consider the argument $\ar$ as decisive for $\phi$.
-This claim is falsified by any observation such that $\hist \nileadsto \phi$ for some $\hist \in \allhist$ with $\ar \in \histend$, thus, $C_2$ is falsifiable.
-%\end{example}
-
-The following theorem states that the descriptive theories defined here are falsifiable, unless they state nothing about anybody’s \ac{DJ}.
-\Cref{sec:prooffals} proves it and describes the set of falsifiers of such theories.
-This theorem implicitly assumes full observability, that is, it supposes that any positive or negative observations are in principle observable and thus available for falsification attempts.
-Further works should investigate to which extent this hypothesis can be relaxed.
-\begin{theorem}
-	\label{th:convfals}
-	The claim of convincingness is falsifiable iff ${\gleadsto} ≠ \emptyset$.
-\end{theorem}
-It can also be seen that if a theory is not constrained in its depth, its claim of convincingness may be unfalsifiable, thus the hypothesis of finite depth is required to obtain this theorem.
-The formal proof of this fact is omitted because it is not especially enlightening; that this fact holds can be seen by examining the use of this hypothesis in the proof of \cref{th:convfals}.
-
-Only remains now to prove that convincingness, together with normative adequacy, is sufficient to obtain validity. The proof is also provided in \cref{sec:prooffals}.
-\begin{theorem}
-	\label{th:convvalid}
-	A normatively adequate empirical theory that is convincing is valid.
-\end{theorem}
-
-\subsection{Effectively comparing models}
-\label{sec:compare}
-Recall from \cref{sec:coh} that $\incompat = \set{(\prop, \prop') \suchthat \forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'}$ denotes the set of pairs of incompatible propositions.
-\commentOC{Does this mandate completeness?}
-Given two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $(\prop, \propbar) \in \incompat$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$.
-Say that the theories are incompatible iff there is at least one pair $(\prop, \propbar) \in \incompat$ that they disagree about.
-
-A path $\histp$ starts with a path $\hist$ iff $\card{\histp} ≥ \card{\hist}$ and $\forall k \in \intvl{1, \card{\hist}}: \histp_k = \hist_k$.
-An increasing sequence of paths is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N$, of paths, 
-such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$.
-
-\begin{theorem}
-	\label{th:proc}
-	Given two incompatible empirical theories for a given normative theory, $\gamma = (\gleadsto[\gamma], \gbeats[\gamma], \alldargs_\gamma, \dbeats[\gamma], +_\gamma)$ and $\delta = (\gleadsto[\delta], \gbeats[\delta], \alldargs_\delta, \dbeats[\delta], +_\delta)$ and given any $i \in I$, there exists a procedure that falsifies one of these theories, queries only $i$, and queries $i$ only about some increasing sequence of paths.
-\end{theorem}
-That procedure is described in \cref{sec:proc}.
-
-\section{Multiple}
-\label{sec:multiple}
-
-\appendix
-\section{Old introduction} 
-Decision theoretic approaches in economy are classically divided into normative and descriptive approaches.
-Normative approaches aim at prescribing decision behavior; descriptive approaches aim at describing decision behavior.
-These two goals are generally considered incompatible: what is normative is not to be judged on descriptive grounds, and conversely.
-(Some authors consider prescription as the art of using descriptive insights to inform recommendation \citep{bell_decision_1988}, a view that also considers the normative aim as distinct to the descriptive aim.)
-
-As a result, normative approaches are difficult to validate: being considered as non-descriptive in their goal, normative claims cannot be submitted to empirical tests that would permit to verify or falsify them.
-Observing a behavior that deviates from a prescribed norm can be taken as a sign that the norm is useful: a decision maker does not hire analysts just to be prescribed the choice that she would have naturally opted for.
-Instead, the validity of a normative approach is generally considered to be determined by examining the convincingness power of the normative axioms on which it rests.
-\commentYM{par qui ? dans le cadre de l'analyse ou en amont ? et pourquoi sur la seule base de la soundness de l'axiome ? pourquoi pas sur la base de ses implications dans des cas concrets ?}
-This validity criterion is unsatisfactory, as it is unable to settle disputes between experts when they arise.
-In supplement, agreement between experts in decision theory is arguably not enough to ground the practical applicability of some normative axioms: one must ensure that decision makers to which the prescription is addressed agree with the particular instanciation of these axioms in the specific decision problem under study.
-But no systematic, formally defined procedure has been proposed to proceed with this check, to the best of my knowledge.
-In practical applications, an expert may informally discuss the axioms with the decision maker in order to check endorsement, either in general, or by discussing violations on a case by case basis when they are observed during an interactive elicitation session.
-The resulting state of conviction arguably depends in part on the rethorical ability of the expert, not solely on the normative strength of the axioms.
-It may lead to a decision maker accepting a decision procedure considered unsound by many experts in the field, such as the \ac{AHP} \citep{smith_anniversary_2004}.
-This problem is compounded by the enormous constraining power gained when axioms interact, as the celebrated theorem of Arrow shows dramatically: axioms that appear innocuous when taken alone may precipitate undesirable results when combined.
-
-By contrast, this difficulty of validation is much alleviated with descriptive approaches.
-Such approaches can be validated by confronting their predictions to empirical data.
-When two descriptive theories disagree on their predictions, it is in principle possible to show that at least one of them is wrong with a suitable experiment.
-\commentYM{quelle différence avec les implications empiriques d'une théorie normative ?}
-\commentOC{Est-ce plus clair maintenant ?}
-Alàs, descriptive approaches as currently existing in decision theory are not suitable to obtain valid prescriptions, as we do not merely want to prescribe natural, unreflectful behavior.
-
-This article defines decision theories, called theories of \ac{DJ}, that are both normative and descriptive: they claim to be able to yield valid prescriptions, and these prescriptions are claimed to predict reflective behavior.
-Reflective behavior as defined in this article is observable, by means of observing the reaction of individuals to arguments.
-This allows to confront theories of \ac{DJ} to empirical data.
-
-This article defines theories of \ac{DJ} in general, not a specific theory of \ac{DJ}.
-Specific theories of \ac{DJ} are tailored to a set of situations and yield claims relevant to those situations.
-For example, a specific theory of \ac{DJ} may be tailored to situations of choice between lotteries involving money.
-This article adopts a more general point of view.
-It defines a general form for theories of \ac{DJ}, and proves claims that hold for any specific theory of \ac{DJ}, showing that such theories are indeed normative and descriptive in some technical sense to be defined.
-
-Here is an example opposing two simplistic theories of \ac{DJ}, meant to give a flavor of the sort of theories this article aims at defining.
-
-\begin{example}[Two disagreeing theories]
-	\label{ex:two}
-	Consider a set $\allalts$ of items evaluated on two criteria, say, price and speed, using functions $g_1$ and $g_2$, where $g_i: \allalts → \R$ measures the performance of items on the criterion $i$, and a set of individuals $I$ whose reflective choice among $\allalts$ we are interested in.
-	Consider the following the theories of \ac{DJ}.
-
-	The \emph{satisfycing} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever item is satisfying (and be indifferent if they are both satisfying or if none of them is).
-An item $\alt$ is satisfying iff $g_1(\alt) < t_1 \land g_2(\alt) > t_2$, where $t_1$ and $t_2$ are two real numbers determined by the theorist.
-
-	The \emph{additive} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever item $\alt$ maximises $v(\alt) = v_1(g_1(\alt)) + v_2(g_2(\alt))$, where $v_i: \R → \R$ are functions  chosen by the theorist.
-
-	Consider a set $\alts = \set{\alt_1, \alt_2} \subset \allalts$ of two items, and assume the two theories of \ac{DJ} are opposed on their prediction of the reflective choice of individuals having to choose one item among $\alts$.
-Say, $\alt_1$ is satisfying and $\alt_2$ is not, failing on the speed criterion; while $v(\alt_2) > v(\alt_1)$.
-
-	To determine which theory is right, it is insufficient to simply observe what an individual $i \in I$ effectively chooses.
-This would merely represent her unreflective behavior.
-The approach adopted in this article to capture \acp{DJ} is to declare that the winning theory (if any) is the one that exhibit arguments able to systematically convince individuals that their proposed choice is to be adopted.
-	The satisfycing theory could argue as follows: “$\alt_1$ is better than $\alt_2$, because it has a satisfactory price (lower than $t_1$, an acceptable price) and a satisfactory speed (higher than $t_2$, an acceptable performance); whereas $\alt_2$ is not satisfactory on the speed criterion”.
-	The additive theory could use the following argument: “$\alt_2$ is better than $\alt_1$, because $\alt_2$ is cheaper than $\alt_1$, and this more than compensates for its weaker performance in terms of speed”.
-
-	The basic intuition on which this article is based is that determining which theory is right requires to present both arguments to $i$, then let her choose one item in $\alts$, to see which argument she finds more convincing.
-\end{example}
-
-The proposed approach starts with this intuition that the reaction of individuals to arguments should matter, and presents a general solution to the problem of capturing reflective judgments or choices.
-Contrary to the simplistic situation of \cref{ex:two}, this solution must allow to confront more than just two arguments or two theories.
-It should define precisely what is required for a judgment to be called deliberated, and determine formally which hypothesis are required for the prescriptions of a theory of \ac{DJ} to be valid.
-
-\section{Normative theories (focused)}
-Define a normative axiom as a formal constraint on behavior that constrains behavior so as to yield valid prescription. 
-Define a descriptive axiom as a formal constraint on behavior interpreted as an empirical prediction, that is, as a claim that behavior (in some a priori described circumstances) satisfies the constraint.
-
-A normative axiom has to be accepted on the basis of its apparent adequacy to capture what is intuitively an acceptable requirement for a prescription to a \ac{DM}.
-In other words, it is not a hypothesis on the observable world: that the requirement holds cannot be proven by observation.
-Examples are given by the axioms of classical decision theories, when they are applied for prescription.
-Consider for example Savage’s sure thing principle.
-One can observe whether individuals unreflectively behave according to Savage’s sure thing principle, but even when they fail to, it can be said that this is because of a mistake: the normative status of an axiom is not hit by violations due to unreflective behavior.
-Such axioms are not falsifiable by behavioral observation.
-Conversely, observing that some axiom perfectly matches observed behavior, that empirical observation alone does not yield any validity to prescription based on that constraint: accepting the validity of a prescription rests on accepting the soundness of its reasoning, not on its ability to reflect natural behavior.
-
-Let us assume that some natural behavior is not to be prescribed.
-
-At least one such axiom is required to ground any prescription.
-Hence, no theory can be fully descriptive, and theories of \ac{DJ} make no exception.
-The proposed path out of this conundrum is to restrict normative axioms to a self-evident claim, and leave most of the constraining power to descriptive claims.
-
-The pursued path is as follows.
-This article introduces first a normative axiom that mandates that whatever propositions the \ac{DM} accepts when reasoning carefully can be prescribed.
-This notion of careful acceptability is defined formally on the basis of an observable relation that captures the reactions of the \ac{DM} to arguments.
-
-Second, this article defines descriptive theories of acceptable propositions.
-Acceptable here is in the sense of the careful acceptability just defined informally.
-Descriptive here means that these theories can predict at least some of the propositions that will be considered acceptable by the \ac{DM}.
-This is arguably the more important and difficult part of the current research program: it has to convince that it is practically possible to define theories that predict such an a priori volatile thing as the way individuals reason.
-It is plain that mandating that theories be able to predict the reaction of individuals to every possible sequence of arguments they are exposed to would be plainly irrealistic.
-Some weaker criterion is required.
-How weak can it become?
-As announced, the proposed theories must be purely descriptive, apart from the required acceptance of the normative adequacy axiom described in the above paragraph.
-In other words, their conclusions must hold on the sole basis of the unique normative axiom, aided by claims that can be proven false experimentally.
-Equivalently, if the theory is invalid, in the sense of failing its predictions about the acceptability of propositions, then it must be falsifiable: there must exist a set of observable reactions of the \ac{DM} to arguments that contradict the claims of the theory.
-Accordingly, this article claims and proves that empirical theories of \ac{DJ} as defined here are such that under normative adequacy, if the theory is not falsified, then it is valid.
-I admit readily that this might not suffice to convince that building such concrete theories is feasible.
-It is only one of the difficulties to tackle.
-
-A possible objection to the usefulness of this approach should perhaps be lifted before delving into the formal descriptions of this rough sketch.
-It may be argued that because this proposition needs a normative axiom, which cannot be validated empirically, it does not fare better than the alternative propositions existing in the literature. 
-%\ac{SEU}, for example, also can be considered to claim to obtain reflective preferences on the basis of normative axioms.
-I grant that it is impossible to get completely rid of normative axioms, because prescriptions must be linked to descriptions, and this cannot be done in a complete empirical way.
-However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims.
-The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science.
-I postulate that the normative axiom proposed here will be consensual, at least for some non trivial concrete instanciations of the proposed approach, among economists, practitioners, external observers and \acp{DM}.
-Furthermore, its simplicity and a priori obviousness are strong points in its favor.
-It has, in some intuitive sense that cannot be described formally, less “content”, in the sense of that word used when economists argue that their theories should not have content about the preferences of the individuals (for fear of being paternalistic or dictatorial).
-Of course, any decision theory has content in a wider sense of imposing some structure to preferences, otherwise, the theory is void.
-The question is: are the restrictions imposed of a kind that can be judged acceptable with respect to the considered applications of the theory?
-Favoring judgments that resist counter-arguments, as done here, seems to me to capture exactly what is desired in a prescription context.
-%Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance.
-(This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.)
-The lack of concrete substance in this normative axiom does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences.
-It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
-It is also worth noting that the proposed axiom has a specific form that may permit \acp{DM} to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation.
-Detailed exploration of this aspect is deferred to future work.
-
-The rest of this article is structured as follows.
-\Cref{sec:approaches} defines more precisely what is meant here with normative and descriptive theories.
-These definitions permit to readily see why the apparent impossibility of a claim being both normative and descriptive is an illusion, thereby enabling a solution to what could be called the “normative against descriptive” gap.
-It also reviews related works in the literature, and briefly sketches the current proposal.
-\Cref{sec:normative,sec:descriptive} define the theories of \ac{DJ} and prove that these theories are normative and descriptive in the sense defined in \cref{sec:approaches}.
-\Cref{sec:preferences} define theories of \ac{DP} on the basis of theories of \ac{DJ}, and \cref{sec:conclusion} concludes.
-
-\section{Eliciting reflective preferences}
-\label{sec:approaches}
-\subsection{Species of theories}
-For this article, a \emph{normative decision theory} is a theory that, when applied in the situations it self-describes as applicable to, claims to yield valid prescriptions.
-I consider a prescription in the wide sense: recommending against some behavior, or recommending conditionally, also counts as prescribing.
-
-A \emph{descriptive decision theory} is a theory that, when correctly applied in the situations it self-describes as applicable to, claims to predict the decision behavior of a given set of individuals.
-For this article, a claim is a prediction only when it is in principle possible to show that it is false using empirical data.
-
-I will simply write normative theory and descriptive theory from now on to mean normative and descriptive decision theories.
-
-For example, the \ac{SEU} theory of Savage is a normative theory.
-It may be used to recommend conditionally some behavior: “if you choose this lottery rather than that lottery, then you ought to \emph{not} choose this other lottery rather than that other lottery”.
-Examples of descriptive theories include the many variants of Prospect theory.
-
-These definitions avoid to define the concept of theory itself, for defining precisely such a fundamental concept raises serious difficulties.
-Is Prospect theory in general a theory, or only some of its variants, sufficiently precisely defined?
-Can a theory be extremely specific, or is some level of generality required to deserve being called a theory?
-Must a theory consist in a non-trivial assembly of laws, some deducible from others?
-It is not necessary for the purpose of the present discussion to take position on these issues, rather, the focus is on the distinction between normative and descriptive approaches.
-An intuitive understanding of the concept of theory will suffice.
-Similarly, I sidestep insuperable difficulties pertaining to capturing in a short definition the concept of a descriptive theory in general: some descriptive theories in a more general sense may propose to describe without predicting, for example (historical decisions or trends come to mind); such endeavor simply does not enter the scope of this discussion.
-For similar reasons, I do not claim that the term normative is unanimously used in the literature as defined here.
-The present definition encompasses theories used in approaches that do not necessarily self-describe as normative \citep{bell_decision_1988, meinard_rationality_2019}; conversely, some theories considered as normative in the literature, such as some social choice theories, may not fall into the definition proposed here, depending on how they are interpreted.
-
-I say that a normative theory is also a descriptive theory when the prescriptions of the normative theory are also claimed to predict the decision behavior of a given set of individuals.
-
-Another contrast can now be introduced: the contrast between shallow and reflective behavior. \emph{Shallow behavior} is defined as the everyday, usual behavior of an individual. 
-This is the behavior whose observation defines what \citet[p.\ 16]{von_neumann_theory_2004} describe as the “intuitive” preferences of an individual, those originating from an “immediate sensation” (the quotes from their article used here are cited by \citet{fishburn_retrospective_1989}).
-\emph{Reflective behavior}, by contrast, is defined as the behavior that enacts informed, pondered decisions, those that would be taken after due consideration.
-% an individual has consciously adopted after having pondered everything that is possibly relevant to the decision. 
-%This pair of definitions is, again, vague and unsatisfactory for a deep philosophical discussion, but hopefully sufficient for the present one. 
-%What is meant by “pondering about everything that is possibly relevant to the decision” will be defined more precisely later; an intuitive understanding of this phrase will do at this stage.
-This distinction draws on our capacity, as human beings, to think about our shallow preferences and consider some of them as mistaken \citep{frankfurt_freedom_1971}. 
-A famous example of such a situation is the one of \citet[pp.\ 101--103]{savage_foundations_1972} having realized, after due consideration, that his initial declared preference in a decision problem presented by \citet{allais_so-called_1979} was mistaken.
-
-This contrast raises a new distinction, which appears by simple combination of the just given definitions: a \emph{shallow descriptive theory} is a descriptive theory that claims to predict the shallow behavior of individuals; a \emph{reflective descriptive theory} is one that claims to predict the reflective behavior of individuals.
-
-The descriptive theories proposed in decision theory, in the sense defined here, are mostly shallow descriptive theories, to the best of my knowledge (\cref{sec:purification} discusses the particular case of “preference purification” approaches).
-%This need not be so. Indeed, this article introduces descriptive theories about reflective behavior.
-This observation permits to understand what could be called the “normative versus descriptive gap”, referring to the belief, implicit in the decision theoretic literature, that a theory cannot be both normative and descriptive.
-Because normative theories aim to prescribe, they are required to not yield recommendations that precisely, systematically match shallow behavior.
-Given the numerous results in experimental psychology showing that shallow behavior is undefensible in many situations, a normative theory whose prescriptions would systematically match shallow behavior would be suspicious, to say the least.
-It would also be of low practical interest.
-It is an immediate consequence of this minimal requirement that a normative theory cannot also be a shallow descriptive theory. 
-In other words, as \citet{hausman_preference_1994} illustrate with an example of a person drinking a fatal poison while erroneously thinking that it is water, shallow behavior is not sufficient to inform normative economics.
-The “normative versus descriptive gap” comes from an implicit identification of descriptive theories with shallow descriptive theories.
-
-This gap can thus be overcome by considering reflective descriptive theories, instead of shallow descriptive theories. This is the path this article adopts.
-
-%This is done by defining on the one hand a non-observable set, containing those propositions that are valid prescriptions; and on the other hand an observable set, containing those propositions decisively defended by arguments, as judged by a given individual.
-This latter set is called the individual’s \ac{DJ}.
-%A normative axiom, that any theory of \ac{DJ} rests on, links these two sets by stating that what is in someone’s \ac{DJ} is a valid prescription.
-%This justifies the normative aspect of the theories. 
-%The theory yields descriptive claims thanks to the
-
-\subsection{The proposed approach}
-The proposal elaborated in this article defines theories that are both normative, and descriptive of reflective behavior.
-The kind of behavior of interest here is choice behavior, although the proposal is more general.
-
-In fact, the main object of study of this article is judgments about propositions. The main goal is accordingly to study reflective adherence to propositions.
-This will then be applied to determining reflective choice behavior.
-Choice behavior is obtained when considering adherence to propositions of the form: “I ought to choose alternative $\alt$ rather than $\alt'$ if both are available”.
-The alternatives can be concrete objects such as consumable goods.
-
-One of our main preoccupation will be to clarify, using formal and precise definitions, the intuitive notion of reflective adherence to propositions.
-This is done using the concept of \emph{deliberated} judgments (a normative concept) and of \emph{acceptable} propositions (a descriptive concept).
-
-A theory of \ac{DJ} applies to a set of individuals and a set of propositions.
-The \ac{DJ} of an individual $i$ is the set of propositions $\prop$ such that it is legitimate to recommend to $i$ adherence to $\prop$.
-Someone’s \ac{DJ} is not directly observable.
-However, we can observe the reactions of $i$ to arguments in favor and against the propositions.
-A theory of \ac{DJ} assumes that it knows a set of arguments such that exploring the reactions to these arguments “sufficiently” permits to obtain knowledge about someone’s \ac{DJ}.
-Thus, one important task dealt with in \cref{sec:normative} will be to define the notion of acceptability, that serves to capture formally this notion of “sufficient” exploration.
-Intuitively, a proposition is acceptable when some argument makes $i$ seem (according to the observations) to adhere to the proposition whatever the counter-arguments given to $i$, and whatever the sequence of arguments given to $i$ previously.
-
-A theory of \ac{DJ} must use an axiom that relates the descriptive notion of acceptability to the normative notion of being deliberated.
-This axiom simply mandates that whatever is acceptable, is deliberated.
-\Cref{sec:normative} presents it formally.
-
-This defines theories of \ac{DJ} that can be considered normative, as accepting the axiom is sufficient to determine unambiguously a set of legitimate prescriptions to be given to individuals. 
-This is done by linking \acp{DJ} to acceptable propositions, a notion whose major interest is that it can be confronted to empirical observations.
-But at this stage, it is still unclear how to obtain knowledge of someone’s \ac{DJ}, and accordingly, such theories cannot still be considered as descriptive.
-In particular, they are not falsifiable, as they take no position on the reactions of individuals to arguments.
-\Cref{sec:descriptive} accordingly defines descriptive theories of acceptable propositions, assuming given a normative theory of \ac{DJ}.
-
-Such descriptive theories can take multiple forms, and some of them would permit to see clearly that the theory is descriptive in the required sense, that is, that its claims can be falsified given observational data.
-But the task we face, for such theories to be useful, is more complex than this minimal requirement: we have to find forms of theories that are not hugely demanding on the part of the theorist.
-In particular, we do not want to oblige the theorist to predict the whole of the argumentative attitude of individuals if this is not required to obtain information about her \ac{DJ}.
-Thus, \cref{sec:descriptive} defines descriptive theories of \ac{DJ} that only claim to be able to answer counter-arguments, in a sense that will be made precise.
-The desire that its claim be falsifiable is also defined formally.
-More formally, the result that is obtained in that section, and that is the central result of this article, is that if a theory resists all empirical falsification attempts, then it is valid, assuming acceptance of the normative axiom described here above informally (and formally in \cref{sec:normative}).
-A theory is valid if the propositions that it claims are in someone’s \ac{DJ} are indeed in that person’s \ac{DJ}.
-This central result thus amounts to prove the main claim of this article, namely, that accepting a weak normative axiom, supplemented with empirical claims, is enough to capture someone’s reflective preferences.
-
-One long-term goal of this research program is to give individuals the means to reject theories that they find unconvincing after due consideration of all arguments; and accordingly, give incentives to decision theorists to build defenses of these theories able to convince individuals of the soundness of these theories.
-\commentYM{phrase trop longue}This might match \possessivecite{hausman_debate_2010} suggestion that we should use rational persuasion rather than nudge individuals, arguing that it would promote autonomy.
-It also follows \possessivecite[p.\ 72]{guala_logic_2000} suggestion (discussing the Allais paradox) about obtaining relevant data to compare normative behavioral theories: “Before asking whether agents want to revise their choices or not, \emph{both} rival theories should be proposed” (emphasis in the original text).
-
-Let us now examine how the approach proposed here to capture reflective preferences differs from those proposed in the literature.
-
-The next two sections review existing approaches aiming at obtaining a model of the reflective preferences of an individual.
-They distinguish two kinds of approaches.
-\Cref{sec:purification} mentions formal techniques, that can be applied by following an explicit procedure, but that do not consider the reaction of individuals to arguments; while \cref{sec:informal} reviews studies that involve informal discussions with individuals, which do consider arguments, but require involving experts.
-By contrast, this article presents theories that can be confronted to empirical data in a formal, systematic way, and that consider the reactions of individuals to arguments.
-
-Before delving into these two categories of approaches, let me mention a few others that, though related to the topic discussed here, fall outside the scope of this article.
-
-Some authors have proposed to base normative theories on observable aspects of nature and individuals; for example, \citet{kahneman_back_1997} propose to measure “experienced utility”, considered as a hedonic quality.
-To the best of my knowledge, these proposals never aim at observing reflective preferences as considered here and thus fall outside the scope of this article.
-
-The field of formal argumentation theory has developed technical approaches to deal with arguments.
-Such endeavor starts with an “attack” relation, which indicates which arguments argue against which.
-Various criteria can then be mathematically defined, in the form of a function selecting subsets of arguments given an attack relation, typically representing sets of arguments that “best resist” their counter-arguments.
-This field has greatly inspired this proposal, in particular, the notion of attack and of reinstatement.
-This field however does not view the attack relation as observable, but considers it as given, and its methodology is therefore not empirical in the sense seeked here.
-(\Citet{cailloux_formal_2019} elaborates somewhat on this difference of objective.)
-\commentYM{ici aussi, je trouve la mention de ces approches maladroite, car elles sont mises en exergue comme si elles étaient des manières de traiter le problème qui t'intéresse, ce qu'elles ne sont pas}
-
-The field of Empirical social choice \citep{gaertner_empirical_2012} investigates individuals’s judgments about fairness: in a typical laboratory experiment, subjects are described some setting requiring to distribute resources among a set of individuals, and are asked to choose a distribution that they consider fair.
-These interesting approaches permit to study empirically the sense of fairness of real individuals, and compare them to social choice theories.
-They are distinct from the currently proposed approach as they seek to obtain their a priori sense of fairness, rather than aim at observing how subjects would appreciate (possibly counter-intuitive) claims about justice when they are backed by (possibly elaborate) arguments; and do not specifically aim to prescribe to an individual.
-
-The phrase “\acl{DP}” has been used by \citet{orchard-webb_deliberative_2016, kenter_deliberative_2017} in the context of group deliberation.
-As used in this article, the concept of deliberation does not necessarily refer to a group deliberation: this approach is agnostic as to the provenance of the arguments.
-
-The idea of using axiomatized decision theories to systematically generate explanations targeted to non experts has received much interest recently \citep{labreuche_general_2011, belahcene_explaining_2017, belahcene_accountable_2018, belahcene_comparing_2019, cailloux_arguing_2016, boixel_automated_2020, peters_explainable_2020, procaccia_axioms_2019}.
-These works are most interesting from the point of view of producing concrete theories of \ac{DJ}, but do not discuss how to systematically exploit decision makers’s judgments about the strengths of texts promoting different alternatives.
-They should therefore be viewed as complementary to this proposition.
-
-\subsection{Preference purification}
-\label{sec:purification}
-An approach much discussed recently is the one of preference purification \citep{bernheim_beyond_2009, rubinstein_eliciting_2011, infante_preference_2016}.
-Having collected shallow preference data (from the field or from interviews), purifying preferences consists in transforming them, using a formal process, in such a way that they satisfy axioms generally considered as required by rationality, or keeping only preference data collected in some situations considered appropriate to determine welfare-relevant preferences.
-For example, \citet{bleichrodt_making_2001} transform observed preferences in order to obtain a classical Expected Utility model; \citet[Section VII]{bernheim_beyond_2009} propose to exclude situations where the individual seems (by objective criteria) unable to process information considered (by the theorist) as relevant information.%; \citet{rubinstein_eliciting_2011} study the possible “rational” preference relations that are coherent with the observed data when assuming some distortion process relating (shallow, observed) and (reflective, unobserved) behavior.
-\commentYM{les deux mécanismes évoqués sont très différents, et ont des enjeux différents.
-Je pense qu'il serait utile de les distinguer, et je pense qu'il faudrait en dire plus sur la nature de la transformation et du filtrage, sans quoi la discussion des ces approches est trop superficielle}
-\commentOC{Je ne vois pas comment faire ça sans en faire une digression énorme.
-Il faudrait introduire des notations, des définitions, … Je vois à peu près comment les présenter sous un cadre unifié et les comparer axiomatiquement aux théories du DJ, mais cela devrait faire l’objet d’un autre article, il me semble.}
-
-These proposals leave unspecified how to confirm or disconfirm them empirically, thus, in particular, how to empirically investigate disagreements between theories: if two theories, on the basis of the same observed data, postulate that they correspond to different purified preferences, the disagreement may at best be arbitrated using ad-hoc, case by case criteria to assess for their relative plausibility.
-By contrast, the present proposal indicates a clear, systematic empirical way to arbitrate disagreements.
-%These proposals deserve a detailed comparison to the current one, but this requires a treatment that cannot be given in this article.
-Let me simply highlight one major difference.
-which can be done with a high level description of these approaches using a variant of the framework that \citet{rubinstein_eliciting_2011} describe.
-%Consider a set of possible observations $S$, describing shallow behavior, and a set of possible “rational” preference relations $R$.
-The set $S$ may contain observations of choice instances, for example, given the bundle $B$, the individual chose $b \in B$; or may contain all possible linear orders over some set of alternatives.
-The set $R$ contains all relations that satisfy some set of axioms of rationality, representing what the modeler considers as an acceptably purified relation.
-\Citet{bleichrodt_making_2001}, for example, use for $R$ the preference relations satisfying \ac{SEU}.
-
-%The purification process amounts to define a function $f: \powerset{S} \rightarrow \powerset{R}$, where $\powerset{A}$ represents the set of subsets of a given set $A$.
-The function $f$ relates a set of observations to their possible purified preference relations.
-The argument of the function represents observations obtained using different frames.
-se could be preference orders
-%This \commentYM{what?
-ici on voit qu'on gagnerait à savoir concrètement quelle est la manip déployée par les auteurs ci-dessus}creates a risk of mis-representing the reflective preferences of the individual: not only is it not known whether the individual would reflectively want to adhere to these axioms
-%\commentYM{quels axiomes ?
-besoin d'expliquer + en détail ce que font ces auteurs ; et tu sembles pressupposer ici qu'adéhrer aux axiomes et s'approprier une transformation ou un filtre basé sur des axiomes, c'est la même chose, ce qui ne me semble pas évident}
-%and, if so, how she would reflectively adapt her preferences when her shallow preferences exhibit related inconsistencies; but it is not even discussed how in principle this could be known \commentYM{phrase en + super longue : arrivée à la fin, je suis perdu}.
-As a result, a theory postulating constraints on individual’s behavior \commentYM{je ne comprends pas de quelles contraintes sur le comportement il est question ici.
-Les théories des laundered preferences que je connais n'imposent aucune contrainte au COMPORTEMENT.
-Cela souligne encore une fois qu'il faudrait être plus prolixe sur la description des approches dont tu parles}on the basis of rational requirements is subject to the criticism addressed by \citet[p.\ 228]{dold_toward_2018} to libertarian paternalism, in that it “effectively denies the possibility that deviations from rational choice might be something to be acknowledged as reasonable”.
-\commentYM{phrase bien alambiquée, qui fait référence à un concept ("libertarian paternalism") que je pense abscond pour bien des gens (dont moi).
-Je pense que tu devrais reformuler, donner l'argument plus directement, et si tu y tiens mettre entre parenthèse que cet arguement est utilisé dans un autre débat par x et y quand ils parlent de LP}
-In other words, it is left unclear how, from a given observation of shallow behavior, one may obtain empirically information about reflective (or purified, in the terminology of this literature) preferences, or about the axioms they should satisfy.
-Authors endorsing this approach sometimes recognize that this is an important methodological problem.
-\Citet{bleichrodt_making_2001}, for example, state that their proposal require controversial assumptions (p.\ 1500), and recommend it only as a last resort, recommending discussing with the decision-maker whenever possible to elicit her reflective preferences (p.\ 1499).
-Note that nudging \citep{thaler_nudge_2009} creates a similar problem: we have to guess what the individual would like if he thought hard about the decision problem, was well-informed, and actively worked against the psychological features he himself does not consider adequate for good decision making.
-
-Some axioms arguably seem innocuous.
-For example, Pareto-dominance requires that $a$ be weakly preferred to $b$ if $a$ is at least as good as $b$ on every point of view that matter.
-However, as has been amply remarked, what is required is not merely the correctness of the axiom in the abstract, but its correct application to the decision situation.
-Has a point of view that the decision maker considers relevant been forgotten, leading the analyst to mistakenly think that $a$ Pareto-dominates $b$, and the seemingly impeccable conclusion that $a$ ought to be preferred to $b$ turns incorrect.
-\citet{sen_maximisation_1997} illustrated this reasoning (with another axiom) with his well-known example of a person picking her second most-preferred fruit from a basket out of politeness reasons, which could be considered irrational by an analyst blindly applying WARP.
-As \citet[p.\ 40]{lecouteux_reconciling_2015} puts it (citing \citet[p.\ 13]{bacharach_beyond_2006} for the part in italics), and as analyzed by \citet{sen_information_1986, sen_internal_1993}, “whether a decision-theoretic principle of rationality has been violated \emph{depends on how we, the theorists, ‘cut up the world’}” \TODO{Find that book}.\commentYM{Je § tout entier me semble mal placé ici.
-Les considérations évoquées sont relatives au choix d'un "bon" axiome, problématique classique dans les discussions des théories du choix rational, mais dont le lien avec le laundering des préférences ne crève pas les yeux.
-Il y a des moyens de faire le lien, mais là tu n'expliques aucun lien.
-Donc ton § tombe comme un cheveux sur la soupe et le lecteur est embrouillé, ne se rappelle même plus quel était l'object de la sous-sous section qu'il vient de lire}
-
-\subsection{Informal deliberation}
-\label{sec:informal}
-Another path to obtain reflective preferences has been followed: the one of deliberation, an umbrella term by which I designate processes, either, involving discussions between an analyst and a decision-maker while querying her preferences in view of building a formal model of them \citep{raiffa_back_1985, keeney_decisions_1993, roy_multicriteria_1996, belton_multiple_2002}, or involving group discussions, with presentations from experts to an audience and internal deliberation phases \citep{fishkin_when_2011, chappell_deliberative_2012}, aiming to obtain well-informed preferences.
-The term as used here also includes the informal use of debiasing techniques: techniques that aim at encouraging individuals to think more about their decision problem in order to reduce occurrence of behavioral “mistakes”.
-Examples include suggesting the individuals to consider alternative points of view, or asking them to give reasons for their choices (an insightful article by \citet{mitchell_libertarian_2004} cite many such studies).
-\commentYM{il me semble nécessaire ici de mentionner aussi tous les dispositifs participatifs et de concertation employés en routine dans les prises de décisions relatives aux politiques publiques et leur mise en oeuvre}
-\commentOC{Je m’interroge. Ça me semble de plus en plus éloigné du scope, car je m’intéresse aux préférences d’un individu donné, hors questions d’agrégation.}
-
-A major problem of these techniques is that they are not easily reproducible \commentYM{il faudrait expliquer en quel sens}, because they require informal interactions with experts.
-Furthermore, the resulting preferences elicited from the subjects might reflect properties of the personalities of the intervening experts or group-dynamic effects rather than true reflective preferences of the individuals.
-
-This problem is compounded by the phenomenon of path dependency, or arbitrary coherence, exhibited by psychologists \citep{ariely_predictably_2010}.
-This term denotes situations where individuals form an apparently coherent system of preference that depends on the path taken to elicit it.
-\commentYM{phrase beaucoup trop longue pour être compréhensible, qui fait par ailleurs référence au concept de rationalité sans le définir, ce qui est acceptable en début d'intro, mais me semble problématique à ce stade dans un papier qui cherche à éclairer les débats flous par des clarifications formelles et conceptuelles}.
-
-It also remains to be clarified how to check on a principled, systematic basis, whether all relevant arguments have been presented faithfully. Comfronted with 
-%(possibly self-designated \commentYM{ceci est un tout autre problème, dont la mention ici brouille le propos}) 
-experts with enough assertiveness, a decision-maker can be convinced to follow principles of decision-making that several experts in the field of decision-theory would consider incorrect. 
-%As an illustration, after discussing the weaknesses of the \ac{AHP}, \citet[p.\ 53]{howard_foundations_2007} write \commentYM{s}: “Why, then, do inferior processes find favor with decision makers?
-The answer is that they do not force you to think very hard or to think in new ways.” \commentYM{je ne vois pas en quoi ceci est censé illustrer le propos précédent (ou alors je n'ai rien compris à la citation).
-J'ai l'impression que la citation dit que, parfois, il y a des forces psychologiques qui s'opposent à l'adoption d'un processus de décision, quand bien même celui-ci aurait des qualités indéniables}
-Beyond the controversial \ac{AHP} mentioned in the introduction, strongly criticized, for example, by \citet[p.\ 53]{howard_foundations_2007}, famous decision analysts have voiced disagreements with normative theories of decision making \citep{ellsberg_risk_1961, allais_so-called_1979} that are however generally applied in the field.
-\commentYM{il me semble ici intenable de faire l'économie de définir ce que tu appelles "normative theories"}
-\Citet[p.\ 669]{ellsberg_risk_1961} concluded his influential article as follows: “[In some situations, for some people,] the Bayesian or Savage approach gives [...] bad advice.
-[Some people] act in conflict with the axioms deliberately, without apology, because it seems to them the sensible way to behave.
-Are they clearly mistaken?” \commentYM{d'une manière générale, dans toute la section 1, l'avalanche de citation me semble nuire au propos.
-Cela induit des ruptures dans le style, et force le lecteur à se pencher sur des questions d'interprétation des citations qui l'empêchent de se focaliser sur ton propos à toi}
-This rethorical question illustrates the need of systematic procedures able to determine whether decision-makers, when confronted with the relevant arguments, accept the soundness of the principles that the recommendation rests on (this has been somewhat explored, but not systematically, for lack of a systematic way of confronting decision makers to arguments \citep{slovic_who_1974, stanovich_discrepancies_1999}).
-
-Another way to view this problem is that different analysts, using different methods and different axioms as their favorite conception of rational decision-making, will obtain possibly contradictory conclusions, “elicited” from the decision-makers who hire them.
-Some analysts admit this possibility and do not consider it to be a problem.
-\commentYM{il me semble que tu soulèves là encore un nouveau problème : comme la notion de rationalité n'est pas claire, il y a débat sur les axiomes qu'on peut vouloir lui associer, et du coup différentes approches, choisissant différents axiomes, vont éliciter des préférences différentes.
-Je te rejoins sur le fait que c'est un problème important, mais il est différent de ce qui a été discuté juste avant, et tu ne l'explicites pas.
-Il me semble qu'il faudrait bien distinguer les problèmes, et bien les formuler, et il faudrait que le plan soit plus clair et lisible.
-Là, en lisant, je ne sais pas si tu considères ce que tu abordes dans ce § comme un nouveau problème, ou comme un aspect ou une implication, du problème exploré précédemment}
-\commentOCf{C’est discutable si c’est un autre problème ou un peu le même problème ou carrément le même problème vu autrement.
-Du point de vue logique, toutes les propositions fausses sont équivalentes.
-En l’absence d’une analyse comparative approfondie de toutes ces approches et de leurs propriétés, je ne vois pas à ce stade comment faire beaucoup plus clair.
-Mais je serais heureux d’en discuter si tu vois une manière de corriger le problème raisonnablement facilement.}
-For example, \citet[p.\ 214]{roy_comparison_1995} write: “In our view, these inevitable disagreements do not imply that decision-aid is useless but simply that a single problem may have several valid responses.
-Given that two different decision-aid models cannot be implemented in the same decision process, the decision-maker must be conscious of the qualitative choices implied by the different models – often conveying the analysts’ own ethical choices – before coming to personal conclusions on the choice to be made.
-In this domain, the many different approaches reflect in our view the complexity of the researcher's task much more than a scientific weakness.”\commentYM{ici encore, je fais une overdose de citations.
-Et je ne trouve pas celle-ci particulièrement éclairante pour ton propos.
-Certes il y a un lien entre ce que tu dis et ce que dit cette citation, mais elle n'est pas vraiment une illustration de ce que tu dis.
-Du coup elle brouille le message}
-\commentOCf{J’ai un peu réduit les citations, j’espère que ça va mieux.
-Concernant celle-ci en particulier, elle me semble très utile.
-Je trouve stupéfiant qu’on puisse trouver ces propos dans la littérature, écrits noir sur blanc.
-Si je ne les cite pas, un lecteur pourrait (ou devrait) ne pas me croire quand j’affirme que des gens trouvent que deux études soi-disant scientifiques puissent arriver à des conclusions apparemment contradictoires et être toutes les deux valides.
-La citation étendue permet de comprendre, je crois, leur point de vue, et de se faire une idée de ce qu’ils veulent dire par là.}
-Although being an important insight about the (likely vain) hope of determining a single correct recommendation in many complex decision situations (about which more below), this insight does not address the problem that some principles of decision making may be wrong guides in some situations, possibly including some principles that are commonly applied in the field, hence the need of principled ways of discriminating them.
-\commentYM{est-ce vraiment ton projet ?
-as-tu l'intention de trouver la meilleure des axiomatiques de décision ?
-si c'est ton projet, il faut le dire clairement.
-Ce que je comprennais jusqu'ici était que tu cherchais un moyen de connaître les "preferences that represent informed, pondered decisions, that would be taken after due consideration by the individual", ce qui me semble être un tout autre projet}
-\commentOCf{En gros, je propose de trancher entre approches normatives en utilisant des données empiriques, plutôt que simplement la force de conviction des axiomes (qui parlent différemment à différentes personnes et peuvent conserver les désaccords intacts).
-Je ne sais pas si c’est plus clair maintenant.}
-
-As a consequence of these techniques not being completely formalised and reproducible, each application requires manual intervention \commentYM{quelles sont ces "interventions manuelles" ?
-à expliquer}of (very skilled) experts in order to elicit reflective preferences interactively.
-Eliciting reflective preferences therefore requires enormous resources.
-\Citet[p.\ 572]{pinto_normative_2012} observe that “in many of those surveys that governments use in order to inform social policy there are not enough resources (time and money) in order to reach the stage where preferences are not labile”.
-There is, to reduce this cost, a need for theories that can be iteratively improved upon and yield reusable knowledge about reflective preferences.
-\commentYM{Cette idée de limiter le coût est intéressante, et je me dis qu'elle peut faire mouche avec certains lecteurs.
-Mais en l'état ça ne fonctionne pas car tu ne expliques pas quels sont les coûts impliqués dans les approaches "manuelles"}
-\commentOC{J’ai reformulé légèrement, j’espère que ça suffit.
-Puis-je m’en tenir à l’idée qui me semble évidente que faire intervenir toute sorte d’experts pour discuter avec des gens chaque fois qu’on veut leur préférence coute cher ?}
-
-\subsection{Previous proposal to study \aclp{DJ}}
-The current proposal pursues a path started with \citet{cailloux_formal_2019}, an article that defines the notion of \ac{DJ} and describe how \acp{DJ} can be observed.
-
-That previous proposal postulates that an individual $i$, whose reflective preferences are being modeled, can adopt multiple perspectives.
-The proposal postulates that the modeler can observe two relations by interacting with $i$, called support and trump.
-They constitute the argumentative disposition of an individual $i$ and are defined as follows.
-
-An argument $\ar$ supports a proposition $\prop$ iff $i$ considers that $\ar$ is in favor of $\prop$.
-This notion is conditional, in the sense that it does not say anything about the validity of $\ar$; only that if $\ar$ holds, then $i$ should endorse $\prop$.
-
-An argument $\ar_1$ trumps another argument $\ar_2$ iff there is at least one perspective within which $i$ considers that $\ar_2$ turns $\ar_1$ into an ineffective argument.
-(This notion is formally decomposed into two relations, “trump in some perspective” and “does not trump in some perspective”, but these details do not need to be discussed here.)
-
-That proposal then defines a number of notions, including the central notion of the \ac{DJ} of $i$, on the basis of her argumentative disposition.
-An individual’s \ac{DJ} is the set of propositions that resist counter-arguments, in some technical sense defined on the basis of these relations.
-
-The current article improves on several aspects over this previous proposal.
-
-First, the previous proposal requires the individual to declaratively take position on notions that may be unclear to him, as they include some possibly counterfactual situations, and as the concept of turning an argument into an uneffective argument may not be understood in the same way by everybody.
-In order for the conclusions about $i$’s \ac{DJ} to hold, we must be sure that $i$ understands the semantics of the relations on which it is based as analysts do.
-It is therefore desirable that these notions have unambiguous semantics.
-It is undoubtedly an important strength of \citet{samuelson_foundations_1983}, \citet{von_neumann_theory_2004} or \citet{savage_foundations_1972}’s theories that they use as primitive notions observable entities whose semantics is unambiguous.
-This is not to say that these proposals cannot be criticized.
-For example, the claim that the notion of preference can be disposed of entirely has been much criticized \citep{hausman_preference_2011, wong_foundations_2006}, with good reasons; and observations of shallow behavior, though having a clear semantics, are insufficient to deduce normative claims, as has been amply remarked and as argued in this very article.
-This is also not to say that declarations should never be used and that only choice acts should matter to any theory in economics.
-Nonetheless, as \citet[p.\ 16]{von_neumann_theory_2004} aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher”.
-A weakness of the previous proposal for studying \acp{DJ} is that the observable relations it uses may be considered inadequate primitive notions.
-This article improves on this aspect by postulating a non-ambiguous observable relation, that does not require $i$ to take position declaratively on relative qualities of arguments; but rather to choose (by declaration of preference or by act) among bundles, or to declare whether $i$ adheres to a given proposition in her current perspective.
-(In the latter case, the clarity of the semantics of the observable relation will depend on the clarity of the propositions.)
-
-Another central aspect of the study of \acp{DJ} is that individuals may change perspective, thus, change opinion about whether an argument trumps another one.
-An important case of change of perspective is when the current perspective depends on which arguments $i$ has seen so far.
-The previous proposal studies these changes of perspectives through the trump relation, without modeling explicitly the arguments seen so far.
-This has the advantage of simplicity, but the price to pay is a lack of ability to reason explicitly about path dependency mechanisms: individuals may form stable opinions that differ according to, for example, the first argument they have seen.
-In such a case, although their opinion may stabilize (in the sense of resisting counter-arguments), it is still arbitrary.
-This article models paths (sequences of arguments) explicitly and prohibits such situations of arbitrariness to count as forming \acp{DJ}.
-
-This article also clarifies the normative and descriptive status of the theories of \acp{DJ}.
-It introduces an explicit axiom which gives them their normative strength.
-This axiom is supplemented by claims, which are shown to be falsifiable by empirical data.
-The previous proposal defines conditions and discusses several possible interpretations of them, including empirical ones, but leaves open the question of how to test these conditions systematically using the observable relations.
-
-\commentYM{la vision vNM est très réductrice, et ne peut pas être considérée, me semble-t-il, comme valable pour toutes les théories normatives, car l'idée qu'il doit y avoir des sensations, atomiques et immédiates relève de l'empirisme logique qui sous-tend leur approche, et cette épistémologie, ou ontologie à ce stade, est loin d'être partagée par toutes les approches à même de développer des théories normatives.
-Ta phrase qui suit risque de n'être pas beaucoup plus convaincantes pour les lecteurs, je le crains.
-Imaginons par exemple une théorie marxiste, elle s'appuiera sur des intérêts matériels, et se contre fout des réactions des individus aux arguments.
-On peut envisager par ailleurs des théories supra-individualistes, qui se foutent des réactions des individus.
-Mais bien entendu la pertinence de ce que je dis là dépend de ta réponse à ma première question dans l'intro du 2.
-Si ce dont tu parles ici, ce n'est pas des théories normatives existantes ou possibles, mais uniquement des théories normatives QUE TU ACCEPTES COMME ELEMENTS DE TA CONSTRUCTION, alors le problème est différent : il faut justifier TON adhérence à l'empirisme logique, ce qui n'est pas une mince affaire étant donné le discrédit qui lui est aujourd'hui attaché}
-\commentOCf{Je soupçonne que le problème était dû à une formulation maladroite de ma part (\og{}The fundamental element of a normative theory of deliberated preferences is the reaction of an individual, whose preferences are to be captured, to arguments\fg).
-Si ma reformulation ne résoud pas le problème, je suis intéressé qu’on en discute.}
-
-\commentYM{je ne pense pas qu'on puisse tenir pour acquis que le lectorat connait par coeur l'article delibenv.
-Il faut du coup donner plus d'explication.
-Par ailleurs, il est impératif que tu expliques pourquoi tu considères qu'il n'est pas raisonnable de considérer que trump et support sont observables}
-\commentYM{je ne pense pas qu'on puisse dire que l'approche RP est privilégiée en économie. Elle est aussi très critiquée. Si tu la considère particulièrement solide, il faut expliquer pourquoi}
-\commentYM{il n'y QU'UN axiome au final ?}
-
-Finally, the current proposal links \acp{DJ} and \acp{DP}. \commentYM{indispensable de dire explicitement quelle est la différence entre les deux dès maintenant}
-
-\Citet{meinard_justification_2020} discuss some requirements on justification of recommendations, which gives further arguments in favor of studying \acp{DJ}.
-
-\commentYM{arrivé à la fin de la section 1, je suis perplexe.
-Si ce n'est pas une introduction (ce que ça ne semble pas être, car ça ne s'appelle pas "introduction", qu'est-ce que c'est, et pourquoi n'y a-t-il pas d'introduction ?
-Si c'est une introduction, il faut l'appeler comme ça, c'est très long, il est inhabituel d'avoir des découpages en sous-sections en intro, il n'y a pas d'annonce de plan (ce qui manque cruellement), il me semble que la problématique n'apparaît pas clairement, le lien avec l'article delibenv devrait être plus clair.
-Par ailleurs, il me semble qu'il y a quelques trous importants dans la revue de la littérature.
-Je pense en particulier à R.E.
-Goodin, « Laundering preferences », in J.
-Elster \& A.
-Hylland (eds.), Foundations of
-Social Choice Theory, Cambridge University Press, 1986, p. 75-102 ; J.C. Harsanyi, Rational Behavior and Bargaining Equilibrium in Games and Social
-Situations, Cambridge University Press, 1977 ; S.-C.
-Kolm, Macrojustice, Cambridge University Press, 2005, chap.
-19.; ainsi qu'à l'économie expérimentale à base de jeux comme N.
-Frohlich \& J.
-Oppenheimer, Choosing Justice.
-An Experimental
-Approach to Ethical Theory, University of California Press, 1992 ; V. Clément \& D. Serra,
-« Égalitarisme et responsabilité, une investigation expérimentale », Revue d’économie politique
-111, 2001, p. 173-193.}
-
-\section{Normative theories}
-\label{sec:normative}
-\subsection{Definition}
-A normative theory of \ac{DJ} is a tuple $(\allprops, \allargs, I, {\allleadsto})$, where $\allprops$ is a set of propositions, $\allargs$ is a set of arguments, $I$ represents a set of individuals, and ${\allleadsto}$ is an observation protocol.
-Intuitively speaking, the theory claims that the proposed observation protocol, observing the reactions of individuals from $I$ to arguments from $\allargs$, is normatively appropriate to yield recommendations to individuals about the propositions from $\allprops$.
-These concepts are detailed in this section.
-\commentYM{pourquoi le protocole d'obs est-il déjà évoqué ici ?
-j'aurais cru que ce protocole relève de la théorie empirique qui se greffe sur la théorie normative en question.
-Par ailleurs, je croyais que c'était l'axiome de la théorie normative qui devait être mis à l'épreuve, pas une instantiation sur une propositon.
-De l'axiome, il n'est plus question.
-Où est-il ?}.
-\commentYM{il manque dans la "theorie normative" ce que j'aurais considéré comme le plus important : un modèle de la force de conviction des arguments et de leurs liens avec les propositions.
-J'aurais dit que l'axiome de la "théorie" se cacherait là-dedans}
-
-The set $\allprops$ is called the agenda of the theory.
-Propositions composing the agenda are not further detailed, they are simply atomic elements.
-A proposition must be an element such that one can observe whether an individual adheres to it, or whether an individual’s behavior is consistent with it.
-\commentYM{pourquoi est-ce que cela fait partie de la théorie ?
-c'est plutôt un des éléments du contexte d'une de SES APPLICATIONS à mon sens.
-L'expression  "normative model" serait selon moi bien plus appropriée si on veut que les détails du cas d'application fassent partie de l'objet.
-"Theory" a de très fortes connotations de généralité}
-Examples of propositions include: “I ought to pay at most \$100 for purchasing bundle $b$”, “I ought to acquire alternative $a$ rather than $b$ if it is available in the same conditions”; “I ought not to perform action $a$ because it is immoral”.
-
-Another primitive elements of a normative theory is the set of arguments $\allargs$.
-Arguments are defined here as anything that can be presented to an individual that may possibly influence her judgment.
-As an example, an argument can be a text presenting the features of an alternative
-\commentYM{donc un texte qui ne prend pas de position sur l'alternative, qui est purement descriptif, est un argument ?
-cela me semble raisonnable, mais ça mérite discussion}, or arguing for the (im)morality of an action.
-An argument may be purely descriptive or may forcefully argue in favor of the truth or falsity of one or several propositions.
-The term argument generally evokes a debate, a metaphor appropriate for the comparison of theories that will be described later; but that should be taken with a grain of salt: an image, a tag price, a poem can be an argument in this article.
-
-The set of individuals in a normative theory represents the situations, socio-economic conditions, acquired diplomas, or other observable features of individuals that must be satisfied for the theory to apply to them \commentYM{cela ressemble plus à un domaine d'application, qu'à un ensemble d'individus auxquels ça s'applique.
-Dans ce cas pourquoi ne pas le dire clairement ?}.
-
-The protocol of observation in a normative theory defines how the theory proposes to present a sequence \commentYM{qu'est-ce qu'une séquence ?
-y a-t-il une notion de temporalité ?
-de lien logique entre les arguments ?
-une nécessité que chaque élément de la "séquence" attaque le précédent ?
-les embranchements sont-ils exclus ?
-les cycles ?
-bref, de quoi parles-tu ?}
-\commentOCf{C’est le \hrefblue{https://en.wikipedia.org/wiki/Sequence}{\underline{terme habituel}} en mathématiques, à ma connaissance.}
-of arguments to an individual, and how to observe her resulting judgment about a proposition of interest.
-This protocol permits to determine whether a sequence of arguments “leads” a given individual to a given proposition.
-If the arguments are texts and propositions are of the form “I ought to acquire alternative $a$ rather than $b$”, an example of such a protocol is: present each argument (each text) in the sequence to the individual, asking her to read it carefully; then give the individual a choice between $a$ and $b$; the sequence of arguments is considered to having led the individual to the proposition “I ought to acquire alternative $a$ rather than $b$” iff he chose $a$ rather than $b$.
-
-To define formally the notion of an observation protocol, the concept of a sequence of arguments is required.
-Define the set of finite sequences of elements in $\allargs$ \commentYM{qu'est-ce qui lie les uns aux autres les éléments d'une séquence ?
-pourquoi est-ce que ça s'appelle une "séquence" ?
-une connotation temporelle ?
-une idée de succession ?}
-(including the empty sequence) as $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$.\commentYM{la notation $\allhist$ rend les choses inutilement difficiles à lire.
-Pourquoi noter ça comme on noterait $\allargs$ sans le zéro, si ça voulait dire quelque chose ?
-J'aurais inventé un symbole du genre $ \allargs^{\intvl{}}$ ; par ailleurs je trouve l'explication relative à l'empty sequence particulièrement alambiquée}
-\commentOCf{Il me semble assez naturel de, étant donné un ensemble de caractères $S$, définir l’ensemble des chaines de caractères par $S^*$ (représentant le fait de prendre toutes les puissances possibles de $S$), mais c’est peut-être un tropisme d’informaticien qui ne sera donc pas compris par des lecteurs économistes, et effectivement l’étoile est aussi utilisée pour exclure zéro, ce qui n’a rien à voir.
-J’ai vu la notation $Seq(\allargs)$ être utilisée, mais elle me semble un peu longue, vu l’usage intensif de ce symbole ici.
-Oui, peut-être en viendrai-je à l’invention que tu proposes, mais inventer ses propres symboles n’est légitime que si aucun n’existe déjà.
-Je vais essayer d’interroger d’autres gens, dis-moi en attendant si tu penses qu’on peut s’y habituer ou si c’est vraiment très dérangeant.}
-Throughout the article, $\N$ includes zero. %and $\N^* = \N \setminus \set{0}$. 
-A generic element of $\allhist$ is denoted by $\hist$ and called an argumentative path, or simply a path when this raises no ambiguity. Its length is denoted by $\card{\hist} \in \N$.
-Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$.
-Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}$, $\hist_k \in A$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
-%Note that $\intvl{1, 0} = \emptyset$, and given any set $S$, the notation $S^\emptyset$ represents the empty set.
-
-An observation protocol ${\allleadsto}: I → \allprops^{\allhist}$ maps individuals and paths to propositions. 
-Equivalently, given any individual $i \in I$, ${\ileadsto}: \allhist → \allprops$ maps paths to propositions for this individual. 
-Given an individual $i \in I$, a path $\hist$ and a proposition $\prop$, the path is said to lead to the proposition for this individual iff $\hist \ileadsto \prop$.\commentYM{la correspondance entre cette définition et la définition du protocole donné dans la partie informelle est pour le moins difficile à voir.
-Où cette défintion formelle spécifie-t-elle comment on observe quoi ?
-Il me semble que ça ressemble + à une définition formelle de ce que je disais plus haut manquer dans ta définition}
-\commentOCf{Je ne comprends pas le problème, il faut qu’on en discute.}
-
-This defines a normative theory of \ac{DJ}.
-
-\begin{example}[A normative theory about two lotteries]
-	\label{ex:twolott}
-	In a famous article about preference reversals, \citet{lichtenstein_reversals_2006} discuss an example involving two lotteries.
-The lottery $P$ makes you win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $P = (.99, +\$4; .01, −\$0.1)$.
-The lottery $D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
-The letter $P$ stands for probability: one salient aspect of $P$ is the very high chance of winning.
-The letter $D$ stands for dollar: one salient aspect of $D$ is the high gain it gives (compared to $P$) in dollar amount if the player is lucky.
-
-This example is interesting because when asked to bid for lotteries, the theory discussed by the authors predicts, and their experiments confirm, that subjects tend to bid more for $D$ than for $P$ (because the bidding question tend to make individuals focus on dollar amounts) whereas when asked to choose one lottery, the lotteries being presented in pairs, subjects tend to choose $P$ (giving a greater attention to probabilities) among the pair $\set{P, D}$.
-
-Define $\allprops = \set{P ≥ D, P > D, D ≥ P, D > P}$, where $P ≥ D$ represents the proposition that $i$ should choose $P$ or declare to be indifferent when choosing among $\set{P, D}$; $P > D$, the proposition that $i$ should choose $P$ and not $D$ when choosing among $\set{P, D}$; and similarly for $D ≥ P$ and $D > P$.
-
-Define $\ar_0$ as a text arguing that the choice between $P$ and $D$ should be according to their expected revenue, namely, $\$3.959$ for $P$ and $\$4$ for $D$.
-Here is a possible text for $\ar_0$.
-“Imagine you play this bet 100 times.
-On average, you would win 99 times and lose once, which means gaining 99 × \$4 = \$396 and losing 1 × \$0.10 = \$0.10, hence a total net gain of \$395.90.
-Thus, your average net gain for the $P$ bet would be \$3.9590.
-[Similar text for $D$.] Therefore, we suggest you choose $D$ for a higher expected revenue.”
-Define $\ar_1$ as a text arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain. 
-Omitting many other relevant arguments for now (such as arguing that utility should be linear for small amounts of money, for example), define $\allargs = \set{\ar_0, \ar_1}$.
-
-Define $I$ as a set of individuals facing a choice between $P$ and $D$ in a laboratory experiment.
-
-Define $\ileadsto$ as follows.
-Given an argumentative path $\hist$, $\hist \ileadsto (P ≥ D)$ iff, in a situation of $i$ having been exposed, in order, to the arguments in $\hist$, letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$, or declare indifference.
-Here is a possible text presented to $i$ to ask for a choice: “Considering these arguments, would you please choose either to play $P$, or play $D$, or declare to be indifferent (in which case one will be picked randomly for you)”.
-Similarly, define $\hist \ileadsto (P > D)$ iff showing the arguments in $\hist$ to $i$ and letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$ and not $D$. 
-Define similarly $\hist \ileadsto \prop$ for $\prop \in \set{D ≥ P, D > P}$.
-
-The tuple $(\allprops, \allargs, I, {\allleadsto})$ is an example of a normative theory of \ac{DJ}.
-\end{example}
-
-We now need an axiom that links the observable reactions of the individuals to their \ac{DJ}.
-This will be done through the notion of a decisive argument, that is, intuitively, an argument that is able to convince an individual of the acceptability of a proposition whatever the argumentative path submitted to the individual.
-For formal definitions, some supplementary notations must be defined.
-
-\subsection{Normative adequacy}
-The \ac{DJ} of an individual $i$ is denoted by $\iprops \subseteq \allprops$.
-It represents the (a priori unknown) set of propositions that can legitimately be recommended to $i$.
-It is independent of any normative theory.
-A normative theory of \ac{DJ} claims that it knows part of the \ac{DJ} of the individuals $i \in I$.
-
-As usual with binary relations, $\hist \nileadsto \prop$ means $(\hist, \prop) \notin {\ileadsto}$.
-
-The judgment of an individual towards propositions may evolve during her exposition to sequences of arguments.
-Of interest to theories of \ac{DJ} are the cases where a so-called decisive argument exists for a given proposition: an argument is decisive, informally, when its presence towards the end of the sequence of arguments systematically leads the individual to accepting the proposition, whatever the sequence of arguments.
-Therefore, an argument is decisive when, intuitively, it is able to resist every counter-arguments.
-
-Given $\hist \in \allhist$, $\range(\hist) = \hist(\intvl{1, \card{\hist}})$ denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
-Let $\histend = \hist(\intvl{\max(1, \card{\hist} - 1), \card{\hist}})$ denote the set containing the last two arguments of the sequence $\hist$ if the sequence has at least two elements; the unique argument of the sequence if it has exactly one element; and the empty set if it is empty.
-
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto \prop$. 
-When $\ar \ileadstost \prop$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view. 
-This definition mandates that $\ar$ be effective (in the sense of leading $i$ to adhere to $\prop$, as determined by the observation protocol) whatever the sequence of arguments presented to $i$, so long as $\ar$ is presented “towards the end” of the sequence, that is, as a last or before last argument.
-Given any $i \in I$, when some argument is decisive for some proposition $\prop$, thus, when $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop$, the proposition is said to be acceptable, from $i$’s point of view.
-
-The following axiom permits the theory to have bite on what should be recommended to $i$. It says that it is sufficient that a proposition be acceptable to be in $i$’s \ac{DJ}.
-\begin{axiom}[Normative adequacy]
-	\label{ax:norm}
-	$\forall i \in I, \prop \in \allprops: 
-		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \prop)] ⇒ \prop \in \iprops.$
-\end{axiom}
-\commentYM{où est défini $\iprops$ ?
-Par ailleurs, je pense qu'il faut expliquer le sens des axiomes, sinon l'article ne peut pas être convaincant ; enfin, pourquoi cet axiome s'appelle-t-il ainsi ?
-cela ressemble plus à un critère de validité empirique quà un critère normatif.
-Mais peut-être mon incompréhension vient-elle du fait que je ne comprend pas ce que dénote $\iprops$}
-
-\begin{example}[Two lotteries (cont.)]
-	Continuing \cref{ex:twolott}, the normative adequacy axiom is satisfied for that normative theory iff, for all $i \in I$, if there is a argument $\ar \in \allargs$ that leads $i$ to never choose $D$, facing any counter-argument and in the context of any preceding argumentative path, under condition that $\ar$ be included towards the end of the path, then we are ready to accept that $i$ deliberately judges that he should choose $P$ rather than $D$, and similarly for the other propositions $\prop \in \allprops$.
-
-	As described in \cref{ex:twolott}, the set $\allargs$ is not wide enough to make this axiom reasonably acceptable: normative adequacy can only be considered a reasonable requirement when the set of arguments includes all arguments that can possibly change the opinion of at least one individual $i \in I$ about the considered topic $\allprops$.
-\end{example}
-
-To end the presentation of the normative theories of \ac{DJ}, it may be useful to analyze the status of contradictory propositions.
-\Cref{th:protcoh} shows that two incompatible propositions cannot both be acceptable.
-In supplement, it may be interesting to observe that theories of \ac{DJ} do not require to postulate that $i$’s \ac{DJ} is complete, in the sense that when the agenda is closed under negation, it must not necessarily be the case that either the proposition or its negation is in $i$’s \ac{DJ}.
-This justifies that the normative axiom asks only for an implication between acceptability and \ac{DJ}, instead of an equivalence.
-
-\subsection{Coherence and completeness}
-\label{sec:coh}
-Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $\forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$.
-Let $\incompat \subseteq \allprops × \allprops$ denote the set of incompatible pairs of propositions.
-
-The following proposition shows that \cref{ax:norm} cannot lead to incompatible propositions being considered deliberated. 
-\begin{proposition}[Coherence of acceptability]
-	\label{th:protcoh}
-	Given any normative theory,
-	$\forall i \in I, (\prop, \propbar) \in \incompat$:
-	\begin{equation}
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost \propbar].
-	\end{equation}
-\end{proposition}
-\commentYM{de même que je trouve très ténu et elliptique le lien entre le protocole dans sa description informelle et dans sa définition formelle, de même je trouve très dérangeant de mettre de terme "protocole" dans le nom de ce genre de proposition.
-Que l'usage de ce terme ait été choisi par provocation ou non, il me semble indispensable de le discuter}
-\begin{proof}
-	If for some $\ar \in \allargs$, $\ar \ileadstost \prop$, then by definition of $\ileadstost$, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadsto \prop$, thus by definition of incompatibility, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto \propbar$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost \propbar$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto \propbar$, and thus in particular, that $(\ar', \ar) \ileadsto \propbar$.
-\end{proof}
-
-To further analyze coherence matters, 
-\commentYM{analyser quoi ? qu'y a-t-il à analyser et pourquoi voudrait-on l'analyser ?}
-consider defined a negation operator $¬$ on $\allprops$.
-$¬$ is a negation operator iff it is an involution operator (thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$) and furthermore satisfying, $\forall \hist \in \allhist, \phi \in \allprops: \hist \ileadsto \prop ⇒ \hist \nileadsto ¬\prop$.
-Given any $i \in I$, say that a proposition $\prop \in \allprops$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop$.
-The $i$-decidable propositions are those on which the normative theory permits, in principle, to take a position. 
-%It will generally be unknown in practical applications, and may be empty.
-When a proposition $\prop$ is such that $\prop \in \iprops ⇔ ¬\prop \notin \iprops$, I say that this proposition admits an unambiguous interpretation in terms of $i$’s \ac{DJ}.
-The next proposition ensures an unambiguous interpretation of all $i$-decidable propositions.
-%The symbol $\oplus$ denotes the exclusive disjunction; thus $\prop \in \iprops \oplus ¬\prop \in \iprops$ is equivalent to: $\prop \in \iprops ⇔ ¬\prop \notin \iprops$ \commentYM{au moins dans les propositions et définitons de cette section, l'introduction  de cet opérateur n'apporte rien, et rend la lecture inutilement difficile}.
-It can be seen to hold by using \cref{th:protcoh}.
-
-\begin{proposition}[Restricted interpretability]
-	\label{th:restrinterpr}
-	Any normative theory with a negation operator $¬$ satisfy,
-	$\forall i \in I, \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop] ⇒ [\prop \in \iprops ⇔ ¬\prop \notin \iprops]$.
-\end{proposition}
-
-This interpretability is however restricted to the $i$-decidable propositions. The following proposition and discussion (assuming a normative theory and a negation operator $¬$ defined) argue 
-\commentYM{"suggest" ou "show", mais je ne pense pas qu'on puisse dire que des "definitions" ou "propositons" "argue" quoi que ce soit}
-that going further is not desirable.
-
-\begin{definition}[Theory completeness]
-	$\forall \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] \lor [\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\prop]$.
-\end{definition}
-\begin{definition}[Unrestricted interpretability]
-	$\forall \prop \in \allprops: \prop \in \iprops ⇔ ¬\prop \notin \iprops$.
-\end{definition}
-\begin{definition}[Deliberation completeness]
-	$\forall \prop \in \allprops: \prop \in \iprops \lor ¬\prop \in \iprops$.
-\end{definition}
-
-The following proposition directly follows from the definitions, together with \cref{th:protcoh}.
-\begin{proposition}
-	1) Under Normative adequacy, Theory completeness implies Deliberation completeness. 2) Unrestricted interpretability implies Deliberation completeness.
-\end{proposition}
-
-\begin{example}[Two lotteries: completeness]
-	Applying these definitions and results to \cref{ex:twolott}, we see that $\set{(P ≥ D, D > P), (D ≥ P, P > D)} \subseteq \incompat$, and we can define a negation operator such that $¬(P ≥ D) = D > P$ and $¬(D ≥ P) = P > D$.
-We see that $P ≥ D$ is $i$-decidable iff $D > P$ is $i$-decidable iff there exists a decisive argument $\ar \in \allargs$ for $P ≥ D$ or for $D > P$.
-It follows from \cref{th:restrinterpr} that at most one of $P ≥ D$ and $D > P$ are in $\iprops$.
-	Theory completeness holds iff there exists a decisive argument for $P ≥ D$ or for $D > P$ and a decisive argument for $D ≥ P$ or for $P > D$.
-In such a case, and assuming Normative Adequacy holds, Deliberation completeness holds as well, thus for every $i$ and every proposition, either it or its contrary is in $i$’s \ac{DJ}.
-\end{example}
-
-Theories as defined here do not mandate Theory completeness.
-This is good for two reasons.
-First, even the weaker Deliberation completeness can be considered too strong.
-Second, it is dubious that, for non trivial decision problems, theories can be found for which both Normative adequacy is normatively compelling and Theory completeness holds.
-
-It might be useful to exemplify those remarks in the case of our running example before discussing them further.
-\begin{example}[Discussion about completeness]
-\label{ex:incompl}
-	It should be remarked that there is no logical contradiction in assuming that $i$ could, for example, deliberately judge that $P ≥ D$, but have no deliberated judgment about whether $D ≥ P$ or rather $P > D$ holds, thus, whether these two lotteries have equal worth or whether $P$ is strictly more valuable.
-In such a case, Deliberation completeness does not hold.
-	More pragmatically, there may be a decisive argument in $\allargs$ for $P ≥ D$, but no argument in $\allargs$ strong enough to convince $i$ to pick $P$ rather than $D$ against all counter-arguments, and no argument strong enough to convince $i$ that $P$ and $D$ are equally preferable.
-For a formal example where this would happen, assume $\ileadsto$ is such that $i$ is lead to choose only $P$ for some of the paths including $\ar_0$ towards their end, but to be indifferent for the other ones.
-Thus: $\forall \hist \in \allhist \suchthat \ar_0 \in \histend: \hist \ileadsto P ≥ D$, $\exists \hist \suchthat \ar_0 \in \histend \land \hist \ileadsto P > D$ and $\exists \hist \suchthat \ar_0 \in \histend \land \hist \ileadsto D ≥ P$.
-\end{example}
-
-Not mandating Theory completeness is a first important element to allow hope that effective theories of \ac{DJ} can be built. 
-To understand why, an analogy with the case of shallow preferences may be useful.
-Psychologists have shown that shallow preferences often depend on a priori irrelevant features pertaining to the description of the decision problem or the context of interrogation.
-Preferences are often said to be constructed, thus, to not exist independently of the framing and context of study.
-But, with no intent of reducing the importance of these findings, it is important to qualify such statements. 
-The findings of psychologists do not, evidently, show that all preference statements are labile.
-As \citet[p.\ xvi]{lichtenstein_construction_2006} write, “To be sure, there are limits to the process of construction.
-Some televisions just won’t sell; most of the time, people are unlikely to want 80\% of their wages to go into savings.
-It would be an overstatement to say of preferences, as Gertrude Stein said of Oakland, that ‘there is no there there’.”
-\commentYM{ce § et le précédent me semble mériter plus que le reste une réécriture. Par ailleurs, je ne vois pas à quoi ils servent dans cette sous-section}
-This observation justifies propositions that obtain only partial shallow preference models: a shallow statement preference would be considered to exist only when it stays intact under all framings considered relevant.
-The proposal of \citet{bernheim_beyond_2009} may be understood under that light.
-
-This remark points towards the importance of allowing for incomplete theories of reflective preferences. \commentYM{définir ce qu'il faut entendre ici par "incomplete"} 
-As \citet{mandler_difficult_2001} discusses in details, it would be unrealistic to postulate that individuals would, after due reflection, in non trivial decision problems, adopt a well specified judgment about any possible proposition of interest.
-From this does not follow that \acp{DJ} do not exist, but that someone’s \ac{DJ} should not be considered to be necessarily complete. 
-\TODO{Check Mandler.}
-This observation also offers a way of reconciling the remark of \citet{roy_comparison_1995} cited in \cref{sec:informal} and the objectivity of the conclusions of a decision theoretic approach: if, for some propositions, both the proposition and its contrary proposition can be held, with no argument being strong enough to impose one of them, let neither these propositions nor their contrary be part of $i$’s \ac{DJ}; and let the theorist focus on the subset of propositions for which argumentative stability can be found.
-
-The definitions of the theories presented here accordingly tolerate both theory incompleteness, which permits the theory to stay silent on some of the propositions in the agenda, and, more fundamentally, deliberation incompleteness, which permits to tolerate that for some propositions, neither it nor its negation figure in someone’s \ac{DJ}.
-
-\commentYM{dans toute cette section, il me semble qu'il faudrait soit des exemples, soit des explications verbales}
-
-\section{Descriptive theories}
-\label{sec:descriptive}
-\subsection{Informal presentation}
-\commentOCf{Je ne me suis pas encore décidé : descriptive theory or empirical theory ? Pour le moment, j’utilise les deux expressions de façon interchangeable.}
-A normative theory defines when a given argument is decisive for a given proposition and a given individual: whenever every sequence of arguments having that argument towards the end of the sequence lead the individual to adhere to the proposition.
-This, in turn, under condition of accepting its normative validity \commentYM{mais c'est quoi cette "normative validiy" ?
-de quelles conditions parles-tu ?}, permits in principle to know something about the \ac{DJ} of an individual.
-But this gives no concrete means to know anyone’s \ac{DJ}.
-The set of finite sequence of arguments, thus of argumentative paths, is infinite.
-The definition of decisiveness could admittedly be modified to account for an a priori bound on the maximal length of sequences, but this would not solve the practical problem that this set would be too large to be explored thoroughly
-\commentYM{certain que ce terme existe ?}
-\commentOCf{Non, thoroughfully n’existe pas, en effet}. 
-Furthermore, only some argumentative paths can be tested for a given individual: the individual’s patience is limited.
-
-Achieving practical knowledge of \acp{DJ} is tackled by introducing descriptive theories of \ac{DJ}, the subject of the next section.
-
-\subsection{Old definition appendix}
-\label{sec:descrdefapdx}
-In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
-A descriptive theory $\gamma$ for a normative theory of \ac{DJ} is defined as a tuple $(\gC, \gPhi)$, where $\gC \subseteq \powerset{I × \allhist × \Phi}$ is a falsifiable claim, $\gPhi \subseteq \Phi$ are the propositions that the theory claims are in the \acp{DJ} of the individuals, and such that its falsifiable claim implies its convincingness.
-\commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi} 
-These concepts are now defined formally.
-\commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}
-
-A claim $\gC \subseteq \powerset{I × \allhist × \Phi}$ represents the theory’s claim about the relation $\leadsto$: the theory claims that ${\leadsto} \in \gC$.
-Such a claim is required to be falsifiable.
-Defining falsification formally require to consider the relationship between the real relation $\leadsto$ and what one can know about it through observations.
-
-Recall that $\leadsto$ will in general not be known in its entirety, but can be queried through observations.
-Observations of the relation $\leadsto$ can in general include positive statements, of the form $\hist \ileadsto \phi$, and negative ones, of the form $\hist \nileadsto \phi$.
-(One way to obtain such negative observations is to use an incompatible proposition $\phi'$ and deduce from $\hist \ileadsto \phi'$ that $\hist \nileadsto \phi$.)
-Assuming (possibly counterfactually) that $R \subseteq I × \allhist × \Phi$ is the “real” relation $\leadsto$, the possible observations are $(O, O') \suchthat O, O' \subseteq I × \allhist × \Phi \land [O \subseteq R] \land [R \cap O' = \emptyset]$; and conversely, once we have gathered some observations $(O, O')$, we know that ${\leadsto} \in \set{R \subseteq I × \allhist × \Phi \suchthat O \subseteq R \land R \cap O' = \emptyset}$.
-
-A claim that ${\leadsto}$ is included in some given set is said to be falsifiable iff, assuming the claim is false, and whatever the real relation is that makes it false, it is possible to prove that the claim is false using a finite set of observations.
-Formally, the claim $\gC \subseteq \powerset{I × \allhist × \Phi}$ is falsifiable iff $\forall R \notin \gC: \exists \text{ finite sets } O, O' \subseteq I × \allhist × \Phi \suchthat \forall R' \subseteq I × \allhist × \Phi \suchthat O \subseteq R' \land R' \cap O' = \emptyset: R' \notin \gC$.
-In such a case, no possible relation $R'$ compatible with the observations $O, O'$ are in $\gC$; in other words, the observations $O, O'$ prove that the claim that ${\leadsto} \in \gC$ is false.
-
-%Distinguish this condition from: $\exists R, finite O such that C is proven false$: the claim "a is dec for phi AND some argument is decisive for phi'" (or "$\alpha \ileadsto \phi$ and some argument is decisive for phi") satisfies this weaker condition, but it should not be considered falsifiable as it is not necessarily possible to distinguish it empirically from a disagreeing theory: if indeed $\alpha \ileadsto \phi$ but NO arg dec, it is impossible to observe the falsity of the claim.
-Note that the weaker requirement is satisfied by BR but not the stronger one.
-
-Finally, a descriptive theory must ensure that its falsifiable claim implies it being convincing, it the sense of being able to show the existence of decisive arguments in favor of its supported propositions, whatever the true relation is.
-So far, $\ar$ being a decisive argument for $\phi$ from the point of view of $i$ is denoted $\ar \ileadstost \phi$, this being defined on the basis of the real relation ${\leadsto}$.
-We need to extend this definition and notation: assuming the observable relation would be any $R \subseteq I × \allhist × \Phi$ (and not specifically $\leadsto$), let $\ar \ileadstost^R \phi$ denote the fact that $\ar$ is a decisive argument for $\phi$ from the point of view of $i$ when the observable relation is $R$.
-\begin{definition}[Conditional convincingness]
-	A pair $(\gC, \gPhi)$ is conditionally convincing iff $\forall R \in \gC, i \in I, \phi \in \gPhi: \exists \ar \in \allargs \suchthat \ar \ileadstost^R \phi$.
-\end{definition}
-TODO use notation: $a \suchthat \set{\hist \in \allhist \suchthat \ar \in \histend} R_i \phi$.
-
-The notion of validity permits to relate the falsifiable claim of a theory, $\gC$, and the set of propositions it supports, $\gPhi$.
-\begin{definition}[Validity]
-	An empirical theory is \emph{valid} iff $\forall i \in I, \gPhi \subseteq \iprops$.
-\end{definition}
-The condition that the falsifiable claim entails convincingness is equivalent to the requirement that, assuming normative acceptability, if ${\leadsto} \in \gC$, then the theory is valid.
-
-\begin{example}[Two claims]
-	Given a normative theory and $\phi \in \Phi$, the claim $C_1 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \exists \ar \in \allargs \suchthat \ar \ileadstost \phi}$ corresponds to claiming that for all individuals $i \in I$, some argument is $i$-decisive for $\phi$.
-If the set of arguments is infinite, $C_1$ is not falsifiable.
-	Given $\ar \in \allargs$ and $\phi \in \Phi$, the set $C_2 = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I, \ar \ileadstost \phi}$ denotes the claim that all individuals will consider the argument $\ar$ as decisive for $\phi$.
-This claim is falsified by any observation such that $\hist \nileadsto \phi$ for some $\hist \in \allhist$ with $\ar \in \histend$, thus, $C_2$ is falsifiable.
-
-	Consider the pairs $(C_1, \set{\phi})$ and $(C_2, \set{\phi})$: only the second one constitutes a descriptive theory.
-Both pairs satisfy the requirement that if $\leadsto \in \gC$, then $\forall i \in I: \phi \in \iprops$ (with $\gC = C_1$ or $\gC = C_2$), but $C_1$ fails to be falsifiable.
-\end{example}
-
-Returning to our running scenario permits to give more concrete examples. Here is an example of a theory that simply claims that a given argument is decisive for everybody.
-\begin{example}[Constant argumentation]
-	Given the normative theory of \cref{ex:twolott}, and the argument $\ar_0$ as defined there, define $\gC = \set{{\leadsto} \subseteq I × \allhist × \Phi \suchthat \forall i \in I: \ar_0 \ileadstost D > P}$ and $\gPhi = \set{D > P}$.
-The pair $(\gC, \gPhi)$ is a descriptive theory for that normative theory.
-\end{example}
-
-The following example illustrates that a descriptive theory need not claim that a given argument will convince everybody.
-
-\begin{example}[A theory for $P$]
-	Define a normative theory as in \cref{ex:twolott}, with an extended set of arguments: define $\allargs$ as the set of all strings.
-(This correspondingly changes $\allhist$ and thus $\ileadsto$, which must be extended to its new domain.)
-	Define $\ar_0$ as in \cref{ex:twolott}.
-	Define $\ar_\text{for$P$}$ as the text “We recommend to adopt $P$: it has a much higher probability of winning.”
-
-	The goal of this example is to define a theory that argues in favor of $P$ using two arguments.
-Following the intuition described just above, the theory will first attempt to use $\ar_\text{for$P$}$, a short argument that may be sufficient to convince a subset of individuals.
-But some may be left unconvinced because of the counter-argument $\ar_0$ in favor of $D$.
-In that case, the theory is ready to use another argument, more subtle, designed to counter $\ar_0$.
-The theory claims that at least one of these two arguments is decisive.
-	In order to define a counter-argument to $\ar_0$, define $\ar_\text{non-linear}$ as the text “$D$ is better than $P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
-For example, consider a choice between winning $10^6$ dollars with probability $0.8$ and winning $2 × 10^6$ dollars with probability $0.4$.
-These two lotteries have the same expected gain, but the first one is clearly preferrable.
-Therefore, we recommend to rather pick $P$ as it presents a much better chance of earning money”.
-
-	Define $\gC = \set{{\leadsto} \suchthat \forall i \in I: \ar_\text{for$P$} \ileadstost P > D \lor \ar_\text{non-linear} \ileadstost P > D}$.
-	Define $\gPhi = \set{P > D}$.
-	Define the theory as $(\gC, \gPhi)$.
-We see that the claim $\gC$ is indeed falsifiable, as any set of observation including $\alpha^0 \ileadsto D > P$ and $\alpha^1 \ileadsto D > P$ such that $\ar_\text{for$P$} \in \histend^0 \land \ar_\text{non-linear} \in \histend^1$ will falsify the claim.
-
-	This example thus defines a theory that anticipates a possible attack using $\ar_0$ against $\ar_\text{for$P$}$, and prepares $\ar_\text{non-linear}$ as an alternative argument in case $\ar_\text{for$P$}$ does not convince an individual.
-\end{example}
-Refining such descriptive theories to let them articulate better the arguments and counter-arguments, and describing more realistic argumentative strategies, is left for future work.
-
-Given any two disagreeing descriptive theories $(\gC, \gPhi)$ and $(\gC[δ], \gPhi[δ])$ for a given normative theory and any two propositions $\prop, \propbar \in \incompat$, say that these two theories disagree about $(\prop, \propbar)$ iff $[\prop \in \gPhi ⇔ \propbar \notin \gPhi[δ]]$.
-Say that two theories disagree iff there exists some propositions about which they disagree.
-
-If two theories disagree, then it is possible to prove one of them wrong using a finite set of observations.
-\begin{proposition}
-	Consider two disagreeing descriptive theories $(\gC, \gPhi)$ and $(\gC[δ], \gPhi[δ])$ for a given normative theory.
-There exists a finite set of observations that prove $\gC$ false, or that prove $\gC$ false.
-\end{proposition}
-\begin{proof}
-	If they disagree, then $\gC \cap \gC[δ] = \emptyset$, otherwise, pick any $R \in \gC \cap \gC[δ]$, and obtain, using convincingness, the existence of decisive arguments for both $\prop$ and $\propbar$, which is impossible as seen in \cref{th:protcoh}.
-
-	As $\gC \cap \gC[δ] = \emptyset$, then at least one of these propositions is true: ${\leadsto} \notin \gC$ or ${\leadsto} \notin \gC[δ]$.
-In both cases, thanks to falsifiability, the existence is proven.
-\end{proof}
-
-\section{Preferences}
-\label{sec:preferences}
-\subsection{Representing deliberated preferences}
-A normative theory of deliberated choice is a normative theory of DJ using propositions of a certain form and a specific protocol of observation.
-
-Let $\allalts$ be a set of alternatives.
-
-Define $\allprops_\allalts = \set{\prop_{B, \choices} \suchthat \emptyset ≠ B \subseteq \allalts, \choices \subseteq \powersetz{B}}$.
-
-Let $I$ and $\allargs$ be any sets of individuals and arguments.
-
-The observation protocol goes as follows.
-Given $i \in I$, $\emptyset ≠ B \subseteq \allalts$ and $\hist \in \allhist$, the individual $i$, after having been presented the arguments in the sequence $\hist$, is asked to choose a subset of elements from $B$ among which she is indifferent.
-Define $\emptyset ≠ c^\hist_i(B) \subseteq B$ as the subset that $i$ chooses after exposure to $\hist$.
-Define $\hist \ileadsto \prop_{B, \choices}$ iff $c^\hist_i(B) \in \choices$.
-
-This defines normative theories about $\allalts$.
-Any empirical theory for a normative theory about $\allalts$ that satisfies $\forall \emptyset ≠ B \subseteq \allalts: \exists !
-\emptyset ≠ \choices \subseteq \powersetz{B} \suchthat \prop_{B, \choices} \in \gpropse$ is said to be an empirical theory about $\allalts$.
-The notation $\exists!$ means: there exists a unique element.
-The requirement that there is at least one is innocuous, as choosing $\choices = \powersetz{B}$ ensures that $\prop_{B, \choices} \in \iprops$, by definition of $\ileadsto$.
-
-An empirical theory about $\allalts$ thus associates to each possible bundle $B$ a set of possible choices $\choices$, whose semantics is that the theory claims that the deliberated choice of $i$, given the bundle $B$, lies among $\choices$.
-Let $\gprops(B) \subseteq \powersetz{B}$ denote this set of possible choices, thus $\gprops(B) = \choices  ⇔ \prop_{B, \choices} \in \gpropse$.
-
-Given an empirical theory about $\allalts$ and $a, b \in \allalts$, define $a \gpst b$ iff $\forall \set{a, b} \subseteq B: b \notin \bigcup \gprops(B)$.
-Thus, $a \gpst b$ iff $\gamma$ claims that $b$ is not deliberately chosen in presence of $a$.
-Define $a \gind b$ iff $\forall \set{a, b} \subseteq B: [\forall C \in \choices: a \in C ⇔ b \in C]$.
-Define ${\gpeq} = {\gpst} \cup {\gind}$.
-
-If $\gpeq$ is transitive, and if $\gamma$ is valid, $\gpeq$ can be said to represent part of the deliberated preference of $i$, in the sense that choosing from the undominated elements of parts of $\gpeq$ restricts choice in a way that is systematically compatible with $i$’s \ac{DJ}.
-This is made precise below.
-
-Given $i \in I$ and a bundle $B$, say that a subset $B' \subseteq B$ is a deliberated restricted choice set for $i$ given $B$ iff 
-$\exists \prop_{B, \choices} \in \iprops \suchthat \forall C \in \choices: C \cap B' ≠ \emptyset$.
-Restricting consideration to deliberated restricted choice sets respects $i$’s \ac{DJ} in the sense that it necessarily includes at least one alternative that is a deliberated choice of $i$.
-
-If $\gpeq$ is transitive and $\gamma$ is valid, the following theorem shows that a choice function can be defined by picking from undominated elements of $\gpeq$ in such a way that only deliberated restricted choice sets result.
-$\powersetz[\mathit{F}]{\allalts}$ designates the finite non-empty subsets of $\allalts$.
-
-\begin{theorem}[Deliberated preference]
-	\label{th:dp}
-	Let $\gamma$ be a valid empirical theory for a normatively adequate normative theory about $\allalts$, and such that $\gpeq$ is transitive.
-Let $r$ be a choice function such that, given any $B \in \powersetz[\mathit{F}]{\allalts}$, $r(B)$ contains exactly one arbitrary argument of each undominated equivalence classes of $B$, where $\gind$ determines the equivalence classes and $\gpst$ determines the undominated elements.
-Then, $\forall B \in \powersetz[\mathit{F}]{\allalts}$, $r(B)$ is a deliberated restricted choice set for $i$ given $B$.
-\end{theorem}
-\begin{proof}
-	Observe that under these hypothesis, $\gpeq$ is a transitive, reflexive binary relation on $\allalts$, $\gpst$ is its asymmetric part and $\gind$ is its symmetric part. 
-	$\gpeq$ is reflexive because $\gind$ is.
-	That $\gpst$ is asymmetric is seen by considering, given any $a, b \in \allalts$, the bundle $B = \set{a, b}$: pick any $C \in \gprops(B) \subseteq \powersetz{B}$, thus, $C \in \powersetz{B}$, hence, $a \in C$ or $b \in C$, and therefore, $b \ngpst a$ or $a \ngpst b$.
-
-	The phrasing of the theorem only defines $r$ informally.
-These supplementary notations may be useful to avoid ambiguity.
-Given $B \subseteq \allalts$, let $B / {\gind} = \set{{\gind}(a) \suchthat a \in B}$ denote the equivalence classes defined by $\gind$ among the elements of $B$.
-The relation $\gpst$ can be used to discriminate some of these equivalence classes.
-Define $\gpst^*$, an asymmetric transitive relation on $B / {\gind}$, such that given any two equivalence classes $\alts, \alts' \in B / {\gind}$, $\alts \gpst^* \alts'$ iff $\forall \alt \in \alts, \alt' \in \alts': \alt \gpst \alt'$.
-Let $\max_{\gpst^*}(B / {\gind}) = \set{\alts \in B / {\gind} \suchthat \forall \alts' \in B / {\gind}: \alts' \ngpst^* \alts}$ denote the undominated equivalence classes of $B / {\gind}$ considering $\gpst^*$.
-
-	In some situations, multiple deliberated restricted choice sets exist.
-A linear ordering $>$ on $\allalts$ can be used to break ties and obtain a precisely defined choice function.
-(A linear ordering $>$ on $\allalts$ is a transitive, asymmetric and connected binary relation over $\allalts × \allalts$, connected meaning that $\forall a ≠ b \in \allalts:  [a > b \lor b > a]$.) Note that this tie breaking strategy is adopted for concreteness and conceptual simplicity, but the proof does not depend on this specific choice.
-It may in general depend on the bundle.
-
-	Define now the choice function $r: \powersetz[\mathit{F}]{\allalts} → \powersetz{\allalts}$ as picking the maximal element (as determined by $>$) of each undominated equivalence class in $B$, thus, $r(B) = \set{\max_>(\alts) \suchthat \alts \in \max_{\gpst^*}(B / {\gind})}$.
-
-	Given any bundle $B \in \powersetz[\mathit{F}]{\allalts}$, we now have to show that $B' = r(B)$ satisfies 
-	$\exists \prop_{B, \choices} \in \iprops \suchthat \forall C \in \choices: C \cap B' ≠ \emptyset$.
-%	$[\forall a \in B \setminus B': \prop_{B, ¬a} \in \iprops] \lor [\exists a \in B' \suchthat \prop_{B, a} \in \iprops]$. 
-	Because $\gamma$ is valid, suffices to show that, given $\choices = \gprops(B) \subseteq \powersetz{B}$, 
-	$\forall C \in \choices: C \cap B' ≠ \emptyset$.
-%	$[\forall a \in B \setminus B': \prop_{B, ¬a} \in \gpropse] \lor [\exists a \in B' \suchthat \prop_{B, a} \in \gpropse]$.
-	Pick any $C \in \choices$ and any $a \in C$ (thus, $a \in B$). By definition of $\gpst$, $\nexists b \in B \suchthat b \gpst a$ as otherwise, $a \notin C$.
-	Note that, by construction of $B'$, as $a \in B$ is undominated, it belongs to some equivalence class of which a member has been brought in $B'$.
-In other words, $\exists b \in B' \suchthat b \gind a$.
-Therefore, by definition of $\gind$, $b \in C$.
-Thus, $b \in C \cap B'$.
-\end{proof}
-The phrasing of this theorem considers only finite bundles for simplicity. It more generally applies to bundles that are closed according to $\gpst$. \TODO{Phrase this correctly.}
-
-\begin{proposition}[Completeness implies transitivity]
-	\label{th:comptrans}
-	If $\gpeq$ is complete ($\forall a, b \in \allalts: a \gpeq b \lor b \gpeq a$) and $\gamma$ is coherent, then it is transitive.
-\end{proposition}
-\begin{proof}
-	Consider any $a, b, c \in \allalts$ with $a \gpeq b \gpeq c$ and let us show that $a \gpeq c$.
-	Consider the bundle $B = \set{a, b, c}$ and let $\choices = \gprops(B)$.
-
-	Observe first that if $x, y \in B$ and $x \gpeq y$, $y \in \bigcup \choices ⇒ x \in \bigcup \choices$. 
-	Indeed, if $x \gpst y$, $y \notin \bigcup \choices$, and if $x \gind y$, $y \in \bigcup \choices ⇔ x \in \bigcup \choices$ as $x$ and $y$ can then be treated interchangeably considering their memberships to elements of $\choices$.
-
-	Because $\bigcup \choices ≠ \emptyset$, $[a \in \bigcup \choices \lor b \in \bigcup \choices \lor c \in \bigcup \choices]$.
-The above observation leads to $c \in \bigcup \choices ⇒ b \in \bigcup \choices$ and $b \in \bigcup \choices ⇒ a \in \bigcup \choices$.
-Therefore, $a \in \bigcup \choices$.
-
-	Completeness implies that $a \gpeq c \lor c \gpeq a$, or equivalently, $a \gpeq c \lor c \gpst a \lor c \gind a$. Excluding $c \gpst a$ thanks to $a \in \bigcup \choices$, we obtain $a \gpeq c$.
-\end{proof}
-
-The following proposition follows from \cref{th:comptrans,th:dp}.
-\begin{proposition}[Completeness implies single recommendations]
-	If $\gpeq$ is complete and $\gamma$ is valid, then the choice function $r$ defined in \cref{th:dp} associates to each finite bundle a singleton set.
-\end{proposition}
-
-Note that $\gpeq$ is independent of $\ileadsto$; thus, any property of $\gpeq$, such as transitiveness or completeness, is a priori (as opposed to empirical), meaning that its satisfaction can be verified without experiments.
-
-When $\gpeq$ is not transitive, choice functions could still be defined that could be said to respect, in some reasonable sense, the deliberated preference of the individuals.
-However, this claim is more arguable, as it is generally (though by all means not unanimously) considered in the literature that a reflective preference should be transitive.
-Further explorations of this possibility are left for future articles.
-
-In what follows, the claims of an empirical theory about $\allalts$ will be defined on the basis of a transitive preference ordering $\peq$ on $\allalts$, as follows.
-Given $\emptyset ≠ B \subseteq \allalts$, define $\gprops(B) = \set{\cup \choices' \suchthat \emptyset ≠ \choices' \subseteq \choices}$, where $\choices$ are the undominated equivalence classes in $B$ according to $\peq$ (thus $\choices = \max_{\pst^*}(B / {\ind})$, using the notations defined in \cref{th:dp}).
-The check that ${\peq} = {\gpeq}$ is left to the reader.
-Thus, all the examples that follow have a transitive $\gpeq$ and therefore claim to represent a deliberated preference (when valid) in the sense defined in this section.
-
-\subsection{A theory based on Satisfaction}
-Consider a normative theory of preferences about a given set of alternatives $\allalts$. Let $\gamma$ be the following empirical theory for that normative theory.
-
-Define $C$ a set of criteria, functions $c: \allalts → \R$, each function measuring the performances of the alternatives according to some point of view.
-Let $t \in \R^C$ be a set of thresholds, thus, consisting of one real valued threshold $t_c \in \R$ per criterion.
-Say that $\alt \in \allalts$ is satisfying iff $\forall c \in C: c(\alt) ≥ t_c$.
- Let $\alts$ denote the satisfying alternatives.
-
-The theory $\gamma$ claims, intuitively, that individuals $i \in I$ are satisficers using some defined criteria $C$ and thresholds $t = (t_c)_{c \in C}$.
-Define $\peq$ as $\alt \peq \altp$ iff $\alt \in \alts \lor \altp \notin \alts$.
-Note that $\peq$ is complete and contains at most two equivalence classes: $\alts$, and $\allalts \setminus \alts$.
-This defines the set of claims that $\gamma$ supports, namely, for any $\emptyset ≠ B \subseteq \allalts$, $\gprops(B) = B \cap \alts$.
-
-Given $\alt \in \alts$, define the fragment $\ar_\alt$ as the text: “$\alt$ has performance $c_1(\alt)$ on criterion $c_1$, and it is reasonable to consider that having at least $t_{c_1}$ is satisfying enough from the point of view captured by $c_1$, [… same phrase for the other criteria…], therefore, it is a fully satisfactory alternative.”
-Given $\altp \in \allalts \setminus \alts$, define $\ar_\altp$ as the text: “$\altp$ is not satisfactory on the criterion [some criterion such that $c(\altp) < t_{c}$]: the performance $t_c$ should be attained for considering $\altp$ as satisfying on that point of view, but it obtains only $c(\altp)$ on that criterion [… same phrase for the other criteria such that $c(\altp) < t_c$].”
-
-Given a bundle $B$, define $\ar_B$ as the text obtained by concatenating all fragments in $\set{\ar_\alt \suchthat \alt \in B}$.
-
-%Given $a \in A, b \in \allalts \setminus A$, define $\ar_{a > b}$ as the text: “$a$ has performance $c_1(a)$ on criterion $c_1$, and it is reasonable to consider that having at least $t_{c_1}$ is satisfying enough from the point of view captured by $c_1$, [… same phrase for the other criteria…], therefore, it is a fully satisfactory alternative; whereas $b$ is not satisfactory on criteria [… enumeration of the criteria such that $c(b) < t_{c}$].”
-Define ${\gleadsto} = \set{(\ar_B, \gprops(B)) \suchthat \emptyset ≠ B \subseteq \allalts}$.
-Define $\alldargs = {\gbeats} = {\dbeats} = {+} = \emptyset$: the theory does not consider any counter-argument as potentially damaging. 
-This defines an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ about $\allargs$.
-
-A more realistic variant of this empirical theory would refrain from claiming that all satisfactory alternatives are equivalent, and that all non-satisfactory alternatives are equivalent.
-Indeed, this claims is likely to fail reflecting the deliberated preferences of the individuals: $i$ will probably pick $\alt$ rather than $\set{\alt, \altp}$ given a bundle of two satisfactory alternatives $\set{\alt, \altp}$ with $\alt$ Pareto-dominating $\altp$.
-
-To this effect, given $\alt, \altp \in \allalts$, define $\alt \peq \altp$ iff $\alt \in \alts \land \altp \notin \alts$ (this also changes the set of claims that $\gamma$ supports) and keep the other definitions intact.
-The resulting theory does not claim to capture complete deliberated preferences, as it ignores how any two alternatives that are both satisfactory, or both unsatisfactory, compare.
-However, whenever there is exactly one satisficing alternative in $B$, it still determines a single deliberated preferred choice for $i$ among $B$.
-
-\subsection{Comparing two lotteries}
-%Idea: argue for P > $.
-%4 ways:
-%- choose
-%- rate attractivity: b1 → +; b2 → ++ thus b2 > b1
-%- bids to buy (B-bid): I’d pay max $4 to buy and play b1; I’d pay max $6 to play b2 thus b2 > b1
-%- bids to sell (S-bid): I’d sell b1 for at least $3; I’d sell b2 for at least $5 thus b2 > b1.
-%
-%First two: focus on probs. Last two: focus on amounts.
-%
-%Compare P = (.99, +$4; .01, −$0.1) VS $ = (.33, +$16; .67, −$2). Typically, choose P and bid more for $.
-%E[P] ≈ $4; E[$] ≈ 5+1/3 − 4/3 = $4.
-%
-%XP1.
-Choice VS S-bid.
-No gambling.
-6 P bets, 7 $ bets.
-12 pairs, of which 6 presented in the table: (P, $), choose one, and indicate the strength of your preference (slight to very strong).
-Then 19 bets using S-big, 6 practice (other bets) then 13 were analyzed.
-%
-%E[P] and E[$] (of the example above) are similar, but bids “greatly exceeding the expected value of $3.94 are common”.
-%
-%XP2. Choice VS B-bid.
-%
-%XP3. With effective gambling and iterated thinking to thing about their preference.
-This section presents a theory that claims that $i$ deliberately prefers $P$ to $D$, in the sense of bidding at least as much for $P$ than for $D$.
-Because the goal of this example is mainly to illustrate the mechanisms of counter-argumentation, this example defines the theory only for these two lotteries.
-The reader should understand how the mechanisms described here above, together with the principle of argumentation presented here for these two specific lotteries, would permit to define a more general theory about lotteries that argues similarly to this one.
-\TODO{Think about the right discursive approach here.}
-
-Define $\ard[2]$ as arguing that the goal is to maximise average revenue, and thus, losses should count equally to gains.
-Define $\ar_3$ as arguing by considering only what is to be gained and not the probabilities, and thus, arguing that $D$ is worth much more.
-Define $\ard[4]$ as arguing that also the probabilities should be taken into account.
-Define $+$ as the simple concatenation of its arguments, which define $\ar_2 = \ar_0 + \set{\ard[2]}$, $\ar_4 = \ar_0 + \set{\ard[4]}$, $\ar_6 = \ar_0 + \set{\ard[2], \ard[4]} = \ar_2 + \set{\ard[4]} = \ar_4 + \set{\ard[2]}$.
-
-Finally, define $\gbeats = \set{(\ar_1, \ar_0), (\ar_3, \ar_0), (\ar_3, \ar_2), (\ar_1, \ar_4)}$, $\dbeats = \set{(\ard[2], \ar_1), (\ard[4], \ar_3)}$.
-
-This defines a normative and an empirical theory about $\allalts = \set{P, D}$.
-
-\section{Conclusion}
-\label{sec:conclusion}
-(To be written.)
-
-- A theory will never be absolutely convincing in the sense defined here.
-\citet[p.\ 100]{raiffa_back_1985} (about SEU): “Give therapy to deviators”.
-\citet[p.\ 108]{raiffa_back_1985}: “In experiments with my students, my ingenious protestations did not always prove to be ingenious enough.
-Yes, they were dazzled (and perhaps confused) but many remained unconvinced; if the chips were down, they would behave just as before.”
-Existence of a falsification instance does not mean that a theory should be rejected.
-Instead, comparing theories in the suggested way permits to gather information about their relative convincingness power, which in turn will inform on the appropriateness of using them normatively.
-Supplementary criteria might be required to decide on normative power.
-For example, policies that would contradict “very strongly” shallow preferences could be considered as excluded, for practical or for principled reasons, even possibly in situations where it could be shown convincingly that such policies would better satisfy reflective preferences.
-Relatedly, it is not claimed here that what society ought to do is exactly what \acp{DJ} indicate, only that reflective preferences provide an appropriate basis for such normative endeavors, in supplement to other criteria.
-Further discussions are required, which hopefully the formal definitions here can help clarify.
-
-- Theories must be able to adapt their claims to individuals. The mechanism described here that adapts arguments to individuals can be adapted to such goal. This is left for future work.
-
-- Back to the claim that a decision problem may admit several valid responses.
-The current approach partly permits to develop theories that agree with this claim, because these theories may be incomplete (in the sense of defining only a partial deliberated preference).
-Taking this view seriously, however, requires to account for meta-preferences (cf.
-Sen): a (possibly partial) ordering on the possible definitions of one’s preference.
-As an example, a theory should be able to express that $i$ will adopt either the view that $a > b > c$, or the view that $c > b > a$, but not $a > c > b$.
-%Relatedly, akrasia might be considered as well.
-An individual may be able to declare that she would prefer having a preference rather than another one; or be put in a situation that helps her follow a preference rather than another one.
-As an example, an individual might be willing to declare
-
-In order to allow for repeated observations with a given individual without modifying his endowment \commentYM{en quel sens utilises-tu ce terme ici ?}, this example protocol should either be content with purely hypothetical choices, or can make these choices binding by letting the individual know that one of his choices will be picked randomly at the end of the experiment and honored.\commentYM{pas compris le second membre de l'alternative}
-
 \hbadness=10000
 \bibliography{simple}
-
-\section{Optional supplements}
-It is by no means my intent to claim that descriptive approaches never face validation difficulties.
-Experimental tests to arbitrate between theories may not be feasible in practice, descriptions are not always solely about the future, falsificationist approaches in turn raise epistemological difficulties, and so on.
-Correspondingly, the possible confrontation to empirical data of the theories defined here is no magical means to definitively solve every difficulty about validation.
-My less naïve claim, that should suffice to motivate the present endeavor, is that it is often a good thing for a theory to make empirically testable claims, from the point of view of the possibilities of solving disputes and validating theories.
-
-The important question about how the parameters $t_i$ and $v_i$ of these illustrative theories would be determined is left aside in this article.
-This article aims at defining and studying theories of \ac{DJ} in general, not at proposing a way of building a specific theory of \ac{DJ}.
-%For this example, one can assume that these parameters are determined on the basis of observation of the behavior of some population in some similar circumstances.
-
-\section{Finiteness}
-This example permits to ensure that the constraint of bounded depth does not mandate finiteness of the relations $\gbeats$ or $\dbeats$.
-\begin{proposition}[Possibility of infinite relations]
-	\label{th:infinite}
-	An empirical theory may involve infinite relations $\gbeats$ and $\dbeats$.
-\end{proposition}
-\begin{proof}
-	Consider an agenda $\allprops = \set{\prop}$ containing a single proposition, an infinite set of arguments $\allargs = \set{\ar_k \suchthat k \in \N}$ with $\forall j, k \in \N: \ar_j ≠ \ar_k$, and consider any set of individuals $I$ and observation protocol $\allleadsto$.
-	Define $2\N^* = \set{k \in \N^* \suchthat k / 2 \in \N^*}$ as the set of non-zero even integers.
-	Define ${\gleadsto} = \set{(\ar_0, \prop)}$.
-	Define ${\gbeats} = \set{(\ar_{k - 1}, \ar_0) \suchthat k \in 2\N^*}$ so that all odd numbered arguments are anticipated attacks against $\ar_0$. 
-	Consider an infinite set of fragments $\alldargs = \set{\ard[k] \suchthat k \in 2\N^*}$ with $\forall j, k \in 2\N^*: \ard[j] ≠ \ard[k]$ so that fragments correspond to non-zero even integers, and define ${\dbeats} = \set{(\ard[k], \ar_{k - 1}) \suchthat k \in 2\N^*}$ so that each (even numbered) defense fragment attacks exactly one (odd numbered) anticipated attacker of $\ar_0$.
-	Given any coalition of fragments $\dargs$ defending $\ar_0$, consider the set of indices corresponding to the fragments in the coalition, $K_{\dargs} = \set{k \in 2\N^* \suchthat \exists \ard[k] \in \dargs}$;
-	define $j_{\dargs} = \sum_{k \in K_{\dargs}}$ as the sum of these indices;
-	and define $\ar_0 + \dargs = \ar_{j_{\dargs}}$. 
-%	$\ard[k] \in \alldargs$, define $\ar_0 + \set{\ard[k]} = \ar_k$. 
-	Consider an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ for the normative theory $(\allprops, \allargs, I, {\allleadsto})$.
-That this is indeed a legal empirical theory can be confirmed by checking that all constraints are satisfied, in particular, $(\dfp)^2(\gleadstoinv(\allprops)) = \dfp(\dfp(\ar_0)) = \dfp(\set{\ar_k \suchthat k \in 2\N^*}) = \emptyset$ because there is no anticipated attack against any argument in $\set{\ar_k \suchthat k \in 2\N^*}$.
-This theory involves infinite relations $\gbeats$ and $\dbeats$.
-\end{proof}
-
-\section{Empirical validity, first}
-\label{sec:prooffals}
-To verify that the property of Convincingness is purely empirical, it is necessary to show that whenever a theory fails it, it is possible to see it using a set of observations of $\allleadsto$.
-Conversely, it is also desirable to ensure that only the observations that ensure that Convincingness is false count for falsifying a theory.
-In other words, it is desirable to capture exactly which sets of observations falsify the claim of convincingness. This will also provide a proof of cref{th:convfals}.
-
-The following example may help to form an intuition about what the possible falsifying sets of observations are.
-\begin{example}[Falsification sequences]
-	Let us examine the possible observations that would suffice to show that the theory presented in our running example is not Convincing.
-
-	First, one could exhibit a path $\hist$ that attacks $\ar_0$ and does not trigger the strategic defense of the theory.
-Those are the paths that satisfy $\ar_0 \in \histend \land \hist \nileadsto D > P \land \forall r \in \R: \ar^r_\text{non-linear} \in \range(\hist)$.
-
-	The second possibility is slightly more demanding, and is the only one that is available if indeed $\ar_0$ $i$-defends $D > P$.
-It requires first to show that $\ar_0 + \ar_\text{linear}$ is a required argument to convince $i$, then to show that this argument fails to convince $i$.
-For this, two paths are required: $\hist^0 \in \allhist \suchthat \ar_0 \in \histend[0] \land \hist^0 \nileadsto D > P \land \dg(\ar_0, \hist^0) = \ar_0 + \ar_\text{linear}$, and $\hist^1 \in \allhist \suchthat (\ar_0 + \ar_\text{linear}) \in \histend[1] \land \hist^1 \nileadsto D > P$.
-\end{example}
-
-Define a falsification sequence for $(i, \ar_0, \phi)$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $(\hist^k)_{k \in \intvl{0, N}}$, for some $N \in \N$, such that it presents successive challenges, which means the following.
-Given $k \in \intvl{0, N}$, assuming $\ar_k$ is defined, define $\ar_{k + 1} = d(\ar_k, \hist^k)$ if $d(\ar_k, \hist^k) ≠ \emptyset$ and say that $\ar_{k + 1}$ is undefined otherwise.
-%Define the \emph{defending} sequence of arguments as a finite sequence of arguments $\ar_{k + 1} = d(\ar_k, \hist^k)$, for $k \in \intvl{1, N}$, as long as $d(\ar_k, \hist^k)$ is not empty, thus letting the length of the sequence be the first value of $k$ for which $d(\ar_k, \hist^k) = \emptyset$.
-A sequence $(\hist^k)_{k \in \intvl{0, N}}$ presents successive challenges iff [$\ar_{k + 1}$ is undefined exactly when $k = N$] and [$\forall k \in \intvl{0, N}: \ar_k \in \histend[k] \land \hist^k \nileadsto \phi$].
-
-%Given $\args \subseteq \allargs$ and $\hist \in \allhist$, recall that the set $\args \cap \range(\hist)$ denotes the arguments that are both in $\args$ and contained in the sequence $\hist$.
-
-%Define a falsification sequence for $(i, \ar_0, \phi)$, with $\ar_0 \gleadsto \phi$, thus $\ar_0$ an initial argument for $\phi$, as a finite sequence $\hist^1, \hist^3, …, \hist^{N + 1}$, for some $N \in 2\N$, such that it presents successive challenges, which means the following.
-%Given $k \in 2\N \suchthat k ≤ N$, $\ar_k \in \allargs$ and $\hist^{k + 1} \in \allhist$, 
-%define $\args_{k + 1} = \gbeatsinv(\ar_k) \cap \range(\hist^{k + 1})$; 
-%define $\dargs[k + 2] = \dbeatsinv(\args_{k + 1})$ as those fragments defending against the anticipated attackers $\args_{k + 1}$; 
-%and, if $\args_{k + 1} ≠ \emptyset$ (equivalently, if $\dargs[k + 2] ≠ \emptyset$), define $\ar_{k + 2} = \ar_k + \dargs[k + 2]$. 
-%The sequence presents successive challenges iff, $\forall k \in 2\N \suchthat k ≤ N$, we have that $\ar_k \in \histend[k + 1]$, $\hist^{k + 1} \nileadsto \phi$, and $[\args_{k + 1} = \emptyset ⇔ k = N]$.
-
-A descriptive theory has no falsification sequence iff $\forall (i, \ar_0, \phi)$, no finite sequence of paths present successive challenges.
-
- \commentOC{Suffices to prove that any $\ar_k \in (\dgip)^k$ iff $\exists (\ar_0, \hist^0, \ar_1 = \dg(\ar_0, \hist^0), …, \ar_k)$ with $\ar_0 \in \histend \land \hist \nileadsto \phi$.}
-\commentOC{We want a descriptive theory to have a property $P$ that implies validity, and that is falsifiable, that is, $P$ implying that no finite sequence of alphas exist in some given set.}
-A theory $\gamma$ must define a set $P$ of possible $\ileadsto$ and the theory claims that any effective $\ileadsto$ is in $P$.
-It must be visible that no, if no, with a finite set of observations of $\ileadsto$.
-
-A claim about $\ileadsto$ is a set $P \subseteq I × \allhist × \Phi$.
-A claim $P$ is falsifiable iff $\exists O \subseteq I × \allhist × \Phi$, $O$ finite, such that $P \cap \set{{\leadsto} \suchthat {\leadsto} \supseteq O} = \emptyset$.
-
-The theory is falsifiable iff $\exists$ finite $O$ st no completion of it makes the theory convincing.
-
-In other words, such a set $O$ is sufficient to show that the theory is not convincing.
-
-Theorem: the theory is falsifiable iff it says more than nothing.
-
-\section{Empirical validity}
-\label{sec:append}
-A \emph{coalition of fragments defending $\ar$} is any non-empty subset of $\df(\ar)$ (equivalently, any element of $\powersetz{\df(\ar)}$).
-Such a coalition can be combined with the argument it defends to form a new argument.
-An empirical theory defines, to that effect, a function $+: \bigcup_{\ar \in \allargs}(\set{\ar} × \powersetz{\df(\ar)}) → \allargs$.
-This function permits to add any $\ar \in \allargs$ to any subset $\emptyset ≠ \dargs \subseteq \df(\ar)$
-
-\commentYM{Dans toute cette sous-section, il y a vraiment ENORMEMENT de notations.
-En conséquence, au moins pour moi, c'est extrêmement difficile à suivre.
-D'où le fait qu'il y a moins de commentaires de ma part à partir de là : je peine à suivre et du coup j'ai plus de mal à prendre du recul}
-
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \range(\hist) \land \ar \in \histend \land \hist \nileadstost \prop$.
-Such a set $\args$, when not empty, represents an effective set of anticipated attackers of $\ar$ against $\prop$. 
-The notation uses a striked through $\prop$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues successfully against $\prop$ despite the presence of $\ar$, from the point of view of $i$.
-I write that $\ar$ \emph{$i$-defends} $\prop$ to mean that $\emptyset \nibeats \ar$.
-
-Given $i \in I, \prop \in \gpropse, \ar \in \allargs$, define $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$.
-It represents the coalitions of fragments defending $\ar$ (when arguing for $\prop$), from the point of view of $i$, against its effective anticipated attackers.
-\Cref{th:indf} shows that these coalitions can be added to $\ar$, and is useful for the later results.
-\begin{proposition}
-	\label{th:indf}
-	$\forall i \in I, \prop \in \gpropse, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
-\end{proposition}
-\begin{proof}
-	I will prove that $\forall \ar \in \allargs: \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.
-Note that by definition of $\df(\ar)$, $\dargs \in \powersetz{\df(\ar)}$ iff $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
-	Thus, we have to prove that
-	$\forall \dargs \subseteq \allargs$:
-	\begin{equation}
-		\exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \suchthat \dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
-	\end{equation}
-
-	First (from left to right), given any $\args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \dargs = \dbeatsinv(\args)$, let us show that $\dargs ≠ \emptyset$ and that $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
-	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, from which follows that $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$.
-Also, because $\args \subseteq \gbeatsinv(\ar)$, $\dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$.
-
-	Second (from right to left), let us show that $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)) ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
-	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ar' \in \dbeatsinv(\args)$, $\ar' \dbeats \ar_1$ for some $\ar_1 \in \args$, thus $\ar_1 \gbeats \ar_0$, thus, $\ar_1 \in {\dbeats}(\dargs)$, thus $\ard \dbeats \ar_1$ for some $\ard \in \dargs$, and by injectivity  of $\dbeats$, $\ar' = \ard$, whence $\ar' \in \dargs$.
-	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
-\end{proof}
-
-Given $\ar \in \allargs$, define $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$, representing the subset of defenders of $\ar$ required for convincing $i$ of $\prop$.
-Given $i \in I, \prop \in \gpropse$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\prop)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\prop))$.
-
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \prop, \hist, \ar) \in I × \gpropse × \allhist × \gargs$ such that $\gbeatsinv(\ar) \cap \range(\hist) = \emptyset \land \ar \in \histend \land \hist \nileadstost \prop$.
-
-A \emph{falsification instance} of an empirical theory is a tuple $(i, \prop, \hist, \ar) \in I × \gpropse × \allhist × \gargs$ such that $\ar \in \histend \land \hist \nileadsto \prop \land \dg(\ar, \hist) = \emptyset$.
-I also write that $(i, \prop, \hist, \ar)$ falsifies $\gamma$ to mean that it is a falsification instance of $\gamma$.
-We readily see that \cref{th:convnofals} is true.
-With a falsification sequence $(\ar_0, \hist^0, \ar_1, \hist^1)$, we see that $\ar_1 \in (\dgip)^1(\ar_0)$, and similarly for longer falsification sequences, $\ar_k \in (\dgip)^k(\ar_0)$.
-
-\begin{lemma}
-	\label{th:convnofals}
-	An empirical theory is convincing iff it has no falsification instances.
-\end{lemma}
-\begin{proof}
-	For all $i \in I, \prop \in \gpropse, \ar \in \gargs$: $\ar$ does not $i$-defend $\prop$ iff $\exists \hist \in \allhist \suchthat \left[\gbeatsinv(\ar) \cap \range(\hist) = \emptyset \land \ar \in \histend \land \hist \nileadstost \prop\right]$ iff $\exists \hist \in \allhist$ such that $(i, \prop, \hist, \ar)$ falsifies $\gamma$.
-Therefore, $\gamma$ is not convincing iff $\exists (i, \prop, \ar) \suchthat \ar$ does not $i$-defend $\prop$ iff $\exists \hist \suchthat (i, \prop, \hist, \ar)$ falsifies $\gamma$ iff $\gamma$ has a falsification instance.
-\end{proof}
-
-\begin{lemma}
-	\label{th:dpiconstr}
-	$\forall \ar_0, \ar_2 \in \allargs: \ar_2 \in \dip(\ar_0) ⇔ \exists \hist \in \allhist, \args = \gbeatsinv(\ar_0) \cap \range(\hist), \dargs = \dbeatsinv(\args) \suchthat [\hist \nileadstost \phi
-	\land \ar_0 \in \histend
-	\land \emptyset ≠ \args \ibeats \ar_0
-	\land \ar_2 = \ar_0 + \dargs]$.
-\end{lemma}
-\begin{proof}
-	$\ar_2 \in \dip(\ar_0) ⇔ \exists \dargs \in \di(\ar_0) \suchthat \ar_2 = \ar_0 + \dargs$.
-	Also, $\exists \dargs \in \di(\ar_0) ⇔ \exists \args \subseteq \gbeatsinv(\ar_0) \suchthat \dargs = \dbeatsinv(\args) \land \emptyset ≠ \args \ibeats \ar_0$.
-Equivalently, $\exists \args \subseteq \gbeatsinv(\ar_0) \suchthat \dargs = \dbeatsinv(\args) \land \emptyset ≠ \args  \land \exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \range(\hist) \land \ar_0 \in \histend \land \hist \nileadstost \prop$.
-\end{proof}
-
-\begin{lemma}
-	\label{th:instseq}
-	An empirical theory has a falsification instance iff it has a falsification sequence.
-\end{lemma}
-\begin{proof}
-	First, from right to left, consider a falsification sequence $(\hist^{k + 1})_{k \in 2\N, k ≤ N}$ for some $N \in 2\N$, define, as in cref{sec:validity}, $\args_{k + 1} = \gbeatsinv(\ar_k) \cap \range(\hist^{k + 1})$, $\dargs[k + 2] = \dbeatsinv(\args_{k + 1})$ and (for $k ≤ N - 2$) $\ar_{k + 2} = \ar_k + \dargs[k + 2]$, and let us show that $(i, \phi, \hist^{N + 1}, \ar_N)$ is a falsification instance.
-This amounts to show that $\ar_N \in \gargs$, which can be done by observing that $\ar_0 \in \gargs$, and showing that, $\forall k \in 2\N, k ≤ N - 2$, $\ar_k \in \gargs ⇒ \ar_{k + 2} \in \gargs$.
-	Indeed, cref{th:dpiconstr} applies with $\ar_k$ for $\ar_0$ and $\ar_{k + 2}$ for $\ar_2$.
-As the second member of the equivalence is true by definition of a falsification sequence, $\ar_{k + 2} \in (\dip)(\ar_k)$, and because $\ar_k \in \gargs$, $\ar_{k + 2} \in \gargs$.
-
-	Second, from left to right, consider a falsification instance $(i, \phi, \hist^{N + 1}, \ar_N)$.
-As $\ar_N \in \gargs$, $\ar_N \in (\dip)^N({\gleadstoinv}(\prop))$ (equalizing the indices $N$ wlog).
-Given $\ar_{k + 2} \in (\dip)^j({\gleadstoinv}(\prop))$, with $j > 0$, thus $\ar_{k + 2} \in \dip(\ar_k)$ for some $\ar_k \in (\dip)^{j - 1}({\gleadstoinv}(\prop))$, apply cref{th:dpiconstr}, obtain $\hist_{k + 1}$.
-Iterate while $j > 0$.
-When $j = 0$, the $\hist$ found corresponds to an initial argument.
-
-	TODO improve this proof.
-\end{proof}
-
-\begin{lemma}
-	\label{th:produce}
-	Given $\prop \in \gpropse$, $\ar_0 \in \gargs$ that $i$-defends $\prop$, and $\hist \nileadstost \prop$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \range(\hist)$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$.
-Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
-\end{lemma}
-\begin{proof}
-	By definition of $\ibeats$, $\args \ibeats \ar_0$.
-	Also, because $\ar_0$ $i$-defends $\prop$, $\args ≠ \emptyset$. 
-	Therefore, $\dargs \in \di(\ar_0)$.
-	It follows that $\dargs \in \df(\ar_0)$, by \cref{th:indf}, and that $\ar_2 \in \dfp(\ar_0)$, by definition of $\dfp$. It also follows that $\ar_2 \in \dip(\ar_0)$, hence, that $\ar_2 \in \gargs$.
-\end{proof}
-
-Cref{th:svalid} claims that a normatively adequate empirical theory that has no falsification sequence is valid. TODO prove it.
-
-\begin{theorem}
-	\label{th:valid}
-	An empirical theory that is normatively adequate and convincing is valid.
-\end{theorem}
-\begin{proof}
-	Given any $i \in I$ and $\prop \in \gpropse$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \prop$; the conclusion then follows thanks to normative adequacy.
-
-	Lemma: $[\ar_0 \in \gargs \land \ar_0 \nileadstost \prop] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$.
-That is because $\ar_0 \in \gargs$ implies that $\ar_0$ $i$-defends $\prop$, by convincingness, and,
-	by definition, $\ar_0 \nileadstost \prop$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \prop$; \cref{th:produce} thus applies.
-
-	To prove the theorem, build a finite sequence of arguments in $\gargs$, starting with any $\ar_0 \in \gleadstoinv(\prop)$.
-Observe that $\ar_0 \in \gargs$.
-Given $k \in 2\N$, if $\ar_k \nileadstost \prop$, define $\ar_{k + 2}$ using the above lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$.
-Continue applying the lemma and producing further arguments as long as $\ar_k \nileadstost \prop$.
-	By definition of an empirical theory, $\exists k \in \N \suchthat (\dfp)^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \prop$.
-\end{proof}
-
-\section{Comparing theories}
-\label{sec:proc}
-This section proves cref{th:proc} constructively, by describing the sequence of tests that must be performed and showing that they must lead to falsifying one of the theories.
-To do this, the notion of challenge must be defined and a few simple lemmas are required.
-In order to leave the letters $\gamma$ and $\delta$ unbounded for clearer application of the intermediate results to the theorem to be proven, let $\mu$ and $\nu$ designate any two descriptive theories for a given normative theory of \ac{DJ}.
-Given $\prop \in \allprops$, $\hist \in \allhist$ and $\ar_\mu \in \gargsmu$, say that $(\hist, \ar_\mu)$ challenges $\prop$ iff $\hist \nileadsto \prop$ and $\ar_\mu \in \histend$.
-Given $\prop \in \allprops, \ar_\mu \in \gargsmu, \ar_\nu \in \gargsnu$, say that $(\hist, \ar_\mu, \ar_\nu)$ is a $\prop/\propbar$-challenge iff $(\hist, \ar_\mu)$ challenges $(\mu, \prop)$ or $(\hist, \ar_\nu)$ challenges $(\nu, \propbar)$.
-
-\commentYM{il faudrait tenir la main du lecture : dire pourquoi tu définis ça.
-Ca se comprends, je sais, mais ça demande au lecteur un gros effort qui n'est pas récompensé par une impression de comprendre où ça va}
-
-\begin{lemma}
-	\label{th:endchal}
-	Given $\ar_\mu \in \gargs$, $\ar_\nu \in \gargsnu$ and $\hist \in \allhist$ such that $\set{\ar_\mu, \ar_\nu} \subseteq \histend$, $(\hist, \ar_\mu, \ar_\nu)$ is a $\prop/\propbar$-challenge.
-\end{lemma}
-\begin{proof}
-	Either $\hist \nileadsto \prop$, and $(\hist, \ar_\mu)$ challenges $\prop$, or $\hist \ileadsto \prop$, hence, by incompatibility of $\prop$ and $\propbar$, $\hist \nileadsto \propbar$, and $(\hist, \ar_\nu)$ challenges $\propbar$.
-\end{proof}
-
-\begin{lemma}
-	\label{th:nextchal}
-	Given $(\hist, \ar_\mu)$ challenging $\prop$, with $\ar_\mu \in \gargsmu \cap (\dfp)^k(\gleadstoinv(\prop))$, and $\ar_\nu \in \gargsnu$: either $(i, \prop, \hist, \ar_\mu)$ falsifies $\mu$, or there exists a $\prop/\propbar$-challenge $(\histp, \ar'_\mu, \ar_\nu)$, with $\ar'_\mu \in \gargsmu \cap (\dfp)^{k + 1}(\gleadstoinv(\prop))$.
-\end{lemma}
-\begin{proof}
-	If $\ar_\mu$ does not $i$-defend $\prop$, then $(i, \prop, \hist, \ar_\mu)$ falsifies $\mu$, which ends the proof. 
-	Thus, assume that $\ar_\mu$ $i$-defends $\prop$.
-
-	\Cref{th:produce} applies and yields $\ar'_\mu = \ar_\mu + \dbeatsinv(\gbeatsinv(\ar_\mu)) \in \gargsmu \cap \dfp(\ar_\mu)$, thus $\ar'_\mu \in (\dfp)^{(k + 1)}(\gleadstoinv(\prop))$. 
-	Now, define $\histpp = (\hist, \ar'_\mu)$ and test whether $\histpp \nileadstost \prop$.
-
-	If $\histpp \nileadsto \prop$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\mu, \ar_\nu)$ challenges $\prop$, which concludes the proof. 
-	Thus, assume that $\histpp \ileadsto \prop$.
-
-	Let us now define $\histp$ such that $\set{\ar'_\mu, \ar_\nu} \subseteq \histpend$, so that \cref{th:endchal} applies on $(\histp, \ar'_\mu, \ar_\nu)$, which will conclude the proof.
-
-	If $\ar_\nu \in \histppend$, this is done by defining $\histp = \histpp$. Otherwise, define $\histp = (\histpp, \ar_\nu)$ and test whether $\histp \nileadsto \prop$. 
-\end{proof}
-
-%Given a normative theory and two empirical theories for that normative theory and $i \in I$, 
-%a \emph{test procedure with $i$} is a finite sequence 
-%\commentOC{Need the test procedure to be a tree.
-Atom: $(k, \prop)$ meaning whether ${\hist}^k \ileadstost \prop$.
-Branch label: atoms linked using or and and operators.
-From a node $n = (\hist, \ar, \prop)$, let branches depart, such that their labels do not overlap.
-From a node, if no branch label is true, the node must falsify a theory.
-In the case of the procedure below, it is not a list because we may query several times the same theory or switch to the other one, depending on the last answer.
-But if simplifying the theory (single-try), we may then simplify the definition of a test procedure.}
-
-\begin{procedure}
-	\label{proc}
-	Pick any $\prop, \propbar \in \incompat$ about which $\gamma$ and $\delta$ disagree.
-
-	Given $k_\gamma, k_\delta \in \N, \hist \in \allhist, \ar_\gamma \in \gargsgamma, \ar_\delta \in \gargsdelta$, 
-	say that 
-	$(\hist, \ar_\gamma, \ar_\delta)$ is a challenge of complexity $(k_\gamma, k_\delta)$ iff 
-	$(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge, $\ar_\gamma \in (\dfp[\gamma])^{k_\gamma}(\gleadstoinv[\gamma](\prop))$, and $\ar_\delta \in (\dfp[\delta])^{k_\delta}(\gleadstoinv[\delta](\propbar))$.
-
-	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\delta] \propbar$.
-Observe that $\ar_{-1} \in \gargsdelta \cap (\dfp[\delta])^0(\gleadstoinv[\delta](\propbar))$.
-Test whether $(\ar_{-1}) \nileadsto \prop$.
-If so, $(i, \prop, (\ar_{-1}), \ar_{-1})$ falsifies $\delta$, which ends the procedure.
-	Thus, assume that $(\ar_{-1}) \ileadsto \prop$.
-
-	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[\gamma] \prop$.
-Observe that $\ar_0 \in \gargsgamma \cap (\dfp[\gamma])^0(\gleadstoinv[\gamma](\prop))$.
-Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadsto \prop$.
-By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\prop/\propbar$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.
-
-	Suffices now to apply \cref{th:nextchal} repetitively, until finding a falsification instance of $\gamma$ or $\delta$.
-This is because, given a challenge $(\hist, \ar_\gamma, \ar_\delta)$ of complexity $(k_\gamma, k_\delta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity.
-Indeed, if $(\hist, \ar_\gamma)$ challenges $\prop$, apply \cref{th:nextchal} with $\gamma$ for $\mu$, $\delta$ for $\nu$, and obtain either that $\hist$ falsifies $\gamma$, or a new tuple $(\histp, \ar'_\gamma, \ar_\delta)$ that is a challenge of complexity $(k_\gamma + 1, k_\delta)$.
-And if $(\hist, \ar_\delta)$ challenges $\propbar$, apply \cref{th:nextchal} with $\propbar$ for $\prop$, $\delta$ for $\mu$, $\gamma$ for $\nu$, and obtain either that $\hist$ falsifies $\delta$, or a new tuple $(\histp, \ar'_\delta, \ar_\gamma)$ such that $(\histp, \ar_\gamma, \ar'_\delta)$ is a challenge of complexity $(k_\gamma, k_\delta + 1)$.
-
-	Given that $\exists K_\gamma \suchthat (\dfp[\gamma])^{K_\gamma}(\gleadstoinv[\gamma](\prop)) = \emptyset$ and $\exists K_\delta \suchthat (\dfp[\delta])^{K_\delta}(\gleadstoinv[\delta](\propbar)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\gamma$ or $\delta$.
-\end{procedure}
-
-\section{Binary choice with indifference}
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost^\text{strong} \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \nileadsto \nprop$, equivalently, ${\ileadsto}(i, \hist) = \set{\prop}$.
-
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost^\text{vweak} \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto \prop$.
-
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost^\text{indif} \prop$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto \prop \land \hist \ileadsto \nprop$, equivalently, ${\ileadsto}(i, \hist) = \Phi$.
-
-Given $i \in I, \prop \in \allprops, \ar \in \allargs$, define $\ar \ileadstost^\text{right} \prop$ iff $\forall \hist \in \allhist_{… a} \suchthat \ar \in \histend: \hist \ileadsto \prop \land \forall \hist, \hist' \in \allhist \suchthat \ar \in \histend, \ar \in \histend': {\ileadsto}(i, \hist) = {\ileadsto}(i, \hist')$, equivalently, $[\forall \hist \in \allhist \suchthat \ar \in \histend: {\ileadsto}(i, \hist) = \Phi] \lor [\forall \hist \in \allhist \suchthat \ar \in \histend: {\ileadsto}(i, \hist) = \set{\phi}]$.
-
-The converse of this is: $\ar \nileadstost^\text{right} \prop$ iff $\exists \hist \suchthat \hist \ileadsto \nprop \land [\exists \hist \suchthat \hist \nileadsto \prop \lor \exists \hist \suchthat \hist \nileadsto \nprop]$.
-
-Equivalently: $\ar \nileadstost^\text{right} \prop$ iff $[\exists \hist \suchthat \hist \ileadsto \nprop \land \exists \hist \suchthat \hist \nileadsto \prop] \lor [\exists \hist \suchthat \hist \ileadsto \nprop \land \exists \hist \suchthat \hist \nileadsto \nprop]$.
-
-The converse of this is: $\ar \ileadstost^\text{right} \prop$ iff $[\forall \hist: \hist \nileadsto \nprop \lor \forall \hist: \hist \ileadsto \prop] \land [\forall \hist: \hist \nileadsto \nprop \lor \forall \hist: \hist \ileadsto \nprop]$.
-
-Equivalently: $\ar \ileadstost^\text{right} \prop$ iff $[\forall \hist: \hist \nileadsto \nprop] \lor [\forall \hist: \hist \ileadsto \prop \land \forall \hist: \hist \ileadsto \nprop]$.
-
-The real thing that we need is this.
-\begin{axiom}[Really]
-	$\forall i \in I, \hist \in \allhist \suchthat \hist \ileadsto \prop: 
-		[\exists \ar \in \allargs \suchthat [\ar \ileadstost^\text{strong} \prop] \lor [\ar \ileadstost^\text{indif} \prop]] ⇔ \prop \in \iprops.$
-\end{axiom}
-
-\subsection{Draft}
-The following axiom imposes that given any $i \in I$, when some argument is decisive for some proposition $\prop$, thus, when $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop$, the proposition is in $i$’s \ac{DJ}.
-\begin{axiom}[Decisive argument sufficiency]
-%	\label{ax:norm}
-	$\forall i \in I, \prop \in \allprops: 
-		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ \prop \in \iprops.$
-\end{axiom}
-\begin{property}[Decisive argument necessity]
-%	\label{ax:norm}
-	$\forall i \in I, \prop \in \allprops: 
-		[\nexists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ \prop \notin \iprops.$
-\end{property} 
-A path $\hist$ is in favor of $\prop$ for $i$ iff $\hist \ileadsto \prop$. The path is countered back to $\nprop$ iff $(\hist, a) \nileadsto \prop$.
-\begin{axiom}[Counter sufficiency]
-%	\label{ax:norm}
-	$\forall i \in I, \hist \in \allhist \suchthat \hist \ileadsto \prop: 
-		[\exists \ar \in \allargs \suchthat (\hist, \ar) \nileadsto \prop] ⇒ \prop \notin \iprops.$
-\end{axiom}
-
-With these axioms alone, if $\iprops = \emptyset$, it is impossible to know it. That is because if we can derive $\prop \notin \iprops$, then it follows that $\nprop \in \iprops$.
-
-Mandate stability. Either dec arg for $\set{\prop}$ or dec arg for $\Phi$ (then indifference).
-
-Try to obtain stability as a consequence of: if strong arg, then $\prop$ and not $¬\prop$; if unstability, then do not conclude ($\prop \notin \iprops$).
-
-\subsection{Draft concl}
-$[\exists \hist \suchthat \hist \nileadsto \prop] ⇒ \ar \nileadstost^\text{right} \prop$.
-
-$[\exists \hist \suchthat \hist \ileadsto \nprop \land \exists \hist \suchthat \hist \nileadsto \nprop] ⇒ \ar \nileadstost^\text{right} \prop$.
-
-$[\forall \hist: \hist \nileadsto \nprop] ⇒ \ar \ileadstost^\text{right} \prop$.
-
-$[\forall \hist: \hist \ileadsto \prop \land \forall \hist: \hist \ileadsto \nprop] ⇒ \ar \ileadstost^\text{right} \prop$.
-
-\subsection{Perhaps better}
-$\ar \ileadstost^\text{right} \prop ⇒ [\forall \hist: \hist \ileadsto \prop]$.
-
-$\ar \ileadstost^\text{right} \prop ⇒ [\forall \hist: \hist \nileadsto \nprop \lor \forall \hist: \hist \ileadsto \nprop]$.
-
-$[\forall \hist: \hist \nileadsto \nprop] ⇒ \ar \ileadstost^\text{right} \prop$.
-
-$[\forall \hist: \hist \ileadsto \prop \land \forall \hist: \hist \ileadsto \nprop] ⇒ \ar \ileadstost^\text{right} \prop$.
-
-We want that if we introduce phi-indiff that says “phi and ¬phi are indiff”, phi-indiff is adopted iff phi and ¬phi are indiff.
-
 \end{document}
-
-\section{Next}
-Define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.
-
-What about a model for only one situation? Then we need to accept that $q$ can’t be falsified, and accept that it defines the individual (or just assume without proof that it does not).
-
-Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$.
-Define $(\ar', \ar) \ileadstoe (\prop, \text{sure})$ iff she sometimes chooses $\set{\prop}$ and $(\ar', \ar) \ileadstoe (\prop, \text{poss})$ iff she sometimes chooses $\set{\prop}$ or $\set{\prop, ¬\prop}$.
-Then, $(\ar', \ar) \ileadstost (\prop, \text{sure})$ iff she always chooses $\set{\prop}$ and $(\ar', \ar) \ileadstost (\prop, \text{poss})$ iff she always chooses either $\set{\prop}$ or $\set{\prop, ¬\prop}$.
-
-Show that if the claim of the model is of a different form, then the model is not falsifiable, as suggested here below for some form of claims.
-
-Extend the definition of additive single-answer theories to non-additive single-answer theories.
-
-An additive theory need not have freedom for defining anticipated attacks on additive terms: this should be a consequence on the anticipated attacks on defenses and on initial arguments only.
-This makes the theory easier to define, as only attacks on partial arguments are to be defined.
-
-General theory says that $\ar_1$ is replaceable (suspects that it’s good for some people): $(\ar_1, \ar_0) \ileadstoe ¬\prop ⇒ (\ar'_1, \ar_0) \ileadstoe ¬\prop$.
-(This will fail if some $i$ thinks $\ar'_1$ is bad arg because of $\ar_0$ but $\ar_1$ is bad because of $\ar_2$.) It may say that $\ar_1$ is bad.
-General theory prepares potentially good arg $\ar_0$ and claims that if $\ar_0 \ileadstoe \prop$, then $\ar_0 \ileadstost \prop$ (this is Answerability).
-So that the model only has to prove the weaker existential claim.
-
-It is important to remark that when the query protocol does not admit observation of “both”, thus, when $\ileadstost$ does not distinguish sure from possible, it does \emph{not} follow that $i$ is sure of either $\prop$ or $¬\prop$ for every pair of proposition: the “undecided” case will hold whenever $i$ considers no argument as sufficiently strong to determine a decisive preference (assuming that in that case, $i$ at least sometimes alternates his choice).
-Admittedly, it might also happen that $i$ is really indifferent between $\prop$ and $¬\prop$ but still systematically chooses, say, $\prop$ over $¬\prop$, in which case it will be (somewhat) erroneously concluded that $\prop \in \iprops$.
-This is the price to pay for using protocols that do not allow to observe indifference.
-Observe however that (depending on the application) this error might be considered not harmful, as the obtained model will be faithful to $i$’s behavior after deliberation.
-
-\subsection{Example model}
-\begin{itemize}
-	\item $\ar_0 = \text{“Veg bec of ethics and health”}$
-	\item $\ar_1 = \text{“Ethics is not defined”}$
-	\item $\ar_2 = \text{“It is since Aristotle at least”}$
-	\item $\ar_1' = \text{“Health isn’t important”}$
-	\item $\ar_2' = \text{“Ask my grandmother”}$
-	\item $\ar_1 \gbeats \ar_0$, $\ar_1' \gbeats \ar_0$
-	\item $\ar_2 \gbeats \ar_1$, $\ar_2' \gbeats \ar_1'$
-	\item $\ar_0 + \ar_2 \gbeats \ar_1$
-	\item $\ar_1' \gbeats \ar_0 + \ar_2$
-	\item $\ar_0 + \ar_2' \gbeats \ar_1'$
-	\item $\ar_1 \gbeats \ar_0 + \ar_2'$
-	\item $\ar_0 + \ar_2 + \ar_2' \gbeats \ar_1$
-	\item $\ar_0 + \ar_2 + \ar_2' \gbeats \ar_1'$
-\end{itemize}
-
-\subsection{About comparisons}
-Count the number of tests; assume simpler theory.
-
-Indicate sufficient hypothesis for ensuring that if a model resisted every attack, it is valid. Thus, that searching for falsification instances in the tested ones is enough.
-
-\subsection{Interpreting Answerability}
-At a given stage in operationalizing the protocol, define $f(\ar_0)$ as the arguments that are considered as having a chance to attack $\ar_0$ (without backtracking).
-Thus, this will not include $\ar_1$ if indeed $\ar_2$ is considered by $i$ as a satisfying answer to $\ar_1$.
-We can interpret Answerability in the following ways.
-Strong answ: $\exists \ar_1 \in f(\ar_0) \suchthat \ar_1 \gbeats \ar_0$.
-Weak answ: $f(\ar_0) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0$.
-Or suppress Answ and replace Op.
-val.
-by Strong op.
-val.: $\forall \prop \in \gpropse, \ar_0 \in \gargs[\prop], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\prop ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
-
-A model can be allowed to try only once each answer. If $\ar_2 \gbeats \ar_1 \land \ar_1 \in f(\ar_0 + \ar_2)$, the model has lost.
-
-Thus, four variants, given $\ar_2 \gbeats \ar_1$.
-\begin{itemize}
-	\item Strong answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land \forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeats \ar_0 + \ar_2$.
-	\item Strong answ with multiple tries: $\forall \ar_1' \in f(\ar_0 + \ar_2): \ar_1' \gbeats \ar_0 + \ar_2$.
-(Example: $\ar_1 = \text{“for ethical reasons”}$, and $\eta$ knows two c-a to this, from different angles.) 	\item Weak answ with single try: $\ar_1 \notin f(\ar_0 + \ar_2) \land [f(\ar_0 + \ar_2) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0]$.
-	\item Weak answ with multiple tries: $f(\ar_0 + \ar_2) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0 + \ar_2$.
-\end{itemize}
-
-Goal: leave addition free so as to admit multiple tries, and prove that Strong answ with multiple tries is the right one for a general approach: suitable restriction to the model permits single try (with same conditions); and weak answ actually does not permit more models.
-
-When $f$ is available and is single-valued, question: should we use Strong or weak answ?
-Right answer: use Strong answ.
-It is stricly more general.
-A model that wants weak answ can define its internal attacks suitable (to be proven); and a model that wants to claim more can.
-
-When $f$ is not available, only remains: single try (just give a decisive argument) or multiple tries (try more and more arguments, blindly).
-
-Suppose that a model also defines $f_\eta$, meaning: $f_\eta(\ar_1) = \ar_2$ the argument the model plays against $\ar_1$.
-Thus $f_\eta$, like $\gbeats$, is a binary relation over $\allargs$, but $f_\eta$ in supplement returns a single argument or none.
-Also, $\ar_2 = f(\ar_1) ⇒ \ar_2 \gbeats \ar_1$.
-When a reason $\ar_1$ for rejecting $\ar_0$ is not known, $f_\eta(\ar_0)$ instead gives the argument to be played next.
-Note that $f_\eta$ is only useful when (in the known c-a variant) for some $\ar_1$ there are multiple candidates $\ar_2$ or when (in the unknown c-a variant) for some $\ar_0$ here are multiple candidates $\ar_2$.
-In fact, this is more complicated: $f_\eta(\ar_1)$ can give first $\ar_2$, then, if that is not enough, $\ar_4$ (thus it’s rather $f_\eta(\ar_1, \ar_0)$).
-
-Under Strong anws, we ask that $f(\ar_0) \cap {\gbeatsinv}(\ar_0) ≠ \emptyset$, and (inevitably) that $f_\eta(\ar_1) ≠ \emptyset$.
-Under weak answ, we do not expect anticipation and only demand that $f_\eta(\ar_1) ≠ \emptyset$.
-But this does not allow supplementary models.
-TODO prove this.
-
-\subsection{Transitive, complete preference theories}
-\NewDocumentCommand{\ppeqab}{}{t_{a \succeq b}}
-\NewDocumentCommand{\ppst}{O{a}O{b}}{t_{#1 \succ #2}}
-\NewDocumentCommand{\ppstsure}{O{a}O{b}}{(t_{#1 \succ #2}, \mathit{sure})}
-\NewDocumentCommand{\ppstbc}{}{t_{b \succ c}}
-\NewDocumentCommand{\ppstac}{}{t_{a \succ c}}
-\NewDocumentCommand{\ppstba}{}{t_{b \succ a}}
-\NewDocumentCommand{\ppeq}{O{a}O{b}}{t_{#1 \succeq #2}}
-\NewDocumentCommand{\ppeqsure}{O{a}O{b}}{(t_{#1 \succeq #2}, \mathit{sure})}
-\NewDocumentCommand{\domc}{}{\mathscr{B}}
-
-Given a set of alternatives $\allalts$.
-Define $\allprops_\allalts = \set{\ppst, a ≠ b \in \allalts} \cup \set{\ppstba, a ≠ b \in \allalts}$.
-Define $¬_\allalts$ such that $\forall a, b \in \allalts: ¬_\allalts\ppst = \ppstba, ¬_\allalts\ppstba = \ppst$.
-Define $\allprops_\allalts = T_\allalts × \set{\mathit{sure}, \mathit{poss}}$.
-
-Let $I$ represent a given set of individuals; $\allalts$ a set of products; 
-and $\allargs$ the set of all strings.
-Given $i \in I$, define $\ileadstost$ as follows. 
-Given $\hist \in \allhist$ and $\prop \in \allprops_\allalts$, with $\prop \in \set{\ppst} × \set{\mathit{sure}, \mathit{poss}}$ for some $a ≠ b \in \allalts$, the individual is presented the arguments in $\hist$, and has then to choose a product from the set $\set{a, b}$.
-Define $\hist \ileadstost \prop$ iff $i$ chooses $a$.
-\commentOC{This is inadequate: if $i$ picks $b$ from $\set{a, b, c}$, the current definition considers it compatible with $\ppstsure \in \iprops$, thus, $\ppst$ does not have a meaningful content.
-Should rather define $\ppstsure$ so that $a$ is picked rather than $b$ whatever the choice set.
-This requires to generalize $\ileadstost$.}
-
-Any normative theory of the form $(\allprops_\allalts, ¬_\allalts, \allargs, I, (\ileadsto)_{i \in I})$, for some sets $\allargs$ and $I$, is called a normative theory about $\allalts$.
-
-Given a set $\domc \subseteq \powersetz{\allalts}$, where $\powersetz{\allalts}$ designates the set of subsets of $\allalts$ without the empty set, a function $c: \domc → \allalts$ is a choice function iff $\forall B \in \domc: c(B) \subseteq B$.
-
-Given a normative theory about $\allalts$, an individual $i \in I$, a set $\domc \subseteq \powersetz{\allalts}$ and a choice function $c$, say that $c$ represents a \emph{deliberated choice function} for $i$ iff $\forall B \in \domc: c(B) \subseteq \set{a \in B \suchthat \forall b \in B: \ppstsure[b][a] \notin \iprops}$.
-
-A normative theory about $\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: [\exists \ar_{a \pst b} \in \allargs \suchthat \ar_{a \pst b} \ileadstost \ppstsure] \land [\exists \ar_{b \pst c} \in \allargs \suchthat \ar_{b \pst c} \ileadstost \ppstsure[b][c]] ⇒ [\exists \ar_{a \pst c} \in \allargs \suchthat \ar_{a \pst c} \ileadstost \ppstsure[a][c]]$.
-
-A set of propositions $P \subseteq \allprops_\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: \ppstsure \in P \land \ppstsure[b][c] \in P ⇒ \ppstsure[a][c] \in P$.
-
-A transitive empirical preference theory about $\allalts$ is an empirical theory for a normative theory about $\allalts$ such that $\gpropse$ is transitive.
-
-Associate to such a theory a preference ordering $\succ$ on $\allalts$ as follows: $a \succ b$ iff $\ppstsure \in \gpropse$.
-
-The deliberated preference of $i$ under a normative theory 
-Then, observe $a$ incomp to $z$ using a good argument for $a > z$ and one for $z > a$.
-Observe also $b$ incomp to $z$.
-And observe $a > b$.
-This proves incompleteness as $z$ indifferent to the rest is impossible.
-BUT this requires to observe possibility.
-
-\subsubsection{Transitive arguments}
-Given a normative theory and a function $\tau: \allargs × \allargs → \allargs$, say that $\tau$ is a transitive argument builder iff $\forall a ≠ b ≠ c ≠ a \in \allalts, \ar_{a \pst b}, \ar_{b \pst c} \in \allargs \suchthat \ar_{a \pst b} \ileadstost \ppstsure \land \ar_{b \pst c} \ileadstost \ppstsure[b][c]: \tau(\ar_{a \pst b}, \ar_{b \pst c}) \ileadstost \ppstsure[a][c]$.
-
-Observe that if a normative theory admits a transitive argument builder, then it is transitive.
-
-TODO It is possible to determine whether a given function $\tau$ is a transitive argument builder empiricially. But not to prove empirically that a normative theory is not transitive.
-
-\section{Decision situation}
-\NewDocumentCommand{\ileadstoprop}{}{⇝^\prop}
-\NewDocumentCommand{\ileadstonprop}{}{⇝^{¬\prop}}
-\NewDocumentCommand{\ileadstosts}{}{⇝_*}
-\NewDocumentCommand{\ileadstos}{}{\overset{s}{⇝_i}}
-\NewDocumentCommand{\ileadstostw}{O{}}{⇝^\mathit{w}_\forall}
-\NewDocumentCommand{\ileadstostp}{O{}}{⇝^\mathit{pos}_\forall}
-\NewDocumentCommand{\nileadstosts}{}{\not⇝_*}
-\NewDocumentCommand{\Ti}{}{T_i}
-\NewDocumentCommand{\ibeatse}{O{}}{⊳^{#1}_\exists}
-\NewDocumentCommand \ibeatseinv { o }{
-	\IfValueTF{#1}{%
-		{⊳_\exists^{#1}}^{-1}%
-	}{%
-		⊳_\exists^{-1}%
-	}%
-}
-\NewDocumentCommand{\mPhi}{}{\allprops_\gamma}
-\NewDocumentCommand{\argsd}{}{S^\mathit{d}}
-\NewDocumentCommand{\ileadstoall}{O{}}{⇝^{#1}_\forall}
-\NewDocumentCommand{\nileadstoall}{O{}}{\not⇝^{#1}_\forall}
-
-The object of study in a given decision situation is the deliberated preferences of a given individual $i$. 
-A decision situation concerns a topic $\allprops$, given a set of arguments $\allargs$, given a certain query protocol, and over a certain time frame.
-The relation $\ileadstoall$, to be defined shortly, models the reaction of $i$ to arguments about the topic.
-The decision situation will be defined as a triple $(\allprops, \allargs, \ileadstoall)$ satisfying some conditions to be defined after having presented those three fundamental elements.
-
-The decision situation relates to a topic denoted by $\allprops$, which is a set of propositions $\prop \in \allprops$ about which we are interested of knowing the deliberated preferences of $i$.
-Propositions are not described further, but are supposedly understandable by $i$ (for example, they could be sentences in some natural language).
-Alternatively, in the case of an analyst helping $i$ to make a decision, $\allprops$ is a set of propositions about which $i$ is interested to know his own deliberated preferences.
-I assume $\allprops$ is closed under negation and introduce a symbol $¬$ for negating a proposition: if $\prop \in \allprops$, then $¬\prop \in \allprops$, and $¬(¬\prop) = \prop$.
-
-With the decision situation comes also a set of all arguments $\allargs$.
-This set contains all the arguments that may possibly be considered relevant by $i$ for his decision problem, and possibly more.
-Importantly, the notion of deliberated preferences does not require to constrain a priori $\allargs$ to some set of arguments that would fit some precise notion of relevancy, coherence, or even well-formedness.
-This permits to avoid introducing inadequate normative principles into the deliberated preferences: only the individual $i$ is then considered legitimate to dictate what is a relevant argument.
-Under that view, $\allargs$ may contain anything that can possibly be considered as an argument by anyone, under the widest possible conception of an argument.
-The notion of deliberated judgment can however also be applied when considering a restricted set of arguments, for example, the arguments that have been put forward by some specific set of experts when talking about the topic $\allprops$.
-
-The set $\allargs$ may be infinite or very large: as we will see, thanks to our falsificationist approach, there is no need to be able to explore it entirely.
-The set of arguments contains at least the empty argument, denoted by $\zar$.
-
-\begin{example}
-	Consider a decision problem where a set of alternatives $\allalts$ is given, containing food products among which $i$ would like to form a deliberated preference (taking into account the effects of food on health, price, pleasure, morality issues related to the production process, and so on).
-The topic could be defined as $\allprops$ = $\set{\prop_\alt, ¬\prop_\alt, \forall \alt \in \allalts}$, where $\prop_\alt$ is the proposition according to which $\alt$ is one of the best alternatives among $\allalts$ (there is no strictly better alternatives among $\allalts$, from $i$’s point of view), and $¬\prop_\alt$ is the proposition according to which $\alt$ is not one of the best alternatives among $\allalts$ (some $\alt' \in \allalts$ is a strictly better alternative, from $i$’s point of view).
-	The set $\allargs$ is defined as the set of all strings, because in this example it is considered acceptable to restrict arguments to those that can take a textual form.
-\end{example}
-
-Define $\allprops = \allprops × \set{\text{possible}, \text{sure}}$. Elements in $\allprops$ will also be called propositions, which should create no ambiguity. 
-The relation $\ileadstoall \subseteq (\allargs × \allargs) × \allprops$, pronounced “always leads to”, has the following semantics.
-Whenever $(\ar, \ar') \ileadstoall (\prop, \text{sure})$, $i$ always considers that $\prop$ is sure (meaning that $¬\prop$ is excluded), when presented with these two arguments, and whenever $(\ar, \ar') \ileadstoall (\prop, \text{possible})$, $i$ always considers that $\prop$ is “at least” possible (meaning that $¬\prop$ may be possible as well), when presented with these two arguments.
-In both cases, the term “always” means that the consideration is stable over time, including after having presented other arguments to $i$.
-Two query protocols presented below will illustrate how these semantics might be satisfied. 
-However, I voluntarily leave the querying protocol not precisely specified in general, as multiple reasonable choices are possible.
-The results of this article depend only on assumptions about $\ileadstoall$.
-
-Define the negation operator $¬$ over $\allprops$ as: $¬(\prop, \text{possible}) = (¬\prop, \text{sure})$ and $¬(\prop, \text{sure}) = (¬\prop, \text{possible})$.
-It follows that $¬¬\prop = \prop$.
-Write $(\ar, \ar') \nileadstoall \prop$ for $¬[(\ar, \ar') \ileadstoall \prop]$ and define $(\ar, \ar') \ileadstoe \prop$ as equivalent to $(\ar, \ar') \nileadstoall ¬\prop$.
-The relation $\ileadstoe$ is pronounced “sometimes leads to”.
-A proposition $\prop$ is about $\prop$ iff $\prop \in \{\prop, ¬\prop\} × \{\text{possible}, \text{sure}\}$.
-
-The pair $(\ar, \ar')$ is to be understood as unordered (thus $(\ar, \ar') \ileadstoall \prop ⇔ (\ar', \ar) \ileadstoall \prop$).
-
-\begin{definition}[Decision situation]
-	A decision situation is a topic $\allprops$ closed under negation, a set of arguments $\allargs$, an “always leads to” relation $\ileadstoall \subseteq (\allargs × \allargs) × \allprops$ satisfying (A1) and (A2) and using unordered pairs of arguments, $\allprops$ being the set of propositions $\allprops × \set{\text{sure}, \text{possible}}$.
-\end{definition}
-
-\subsection{Query protocols}
-As vNM aptly summarize, “It is clear that every measurement – or rather every claim of measurability – must ultimately be based on some immediate sensation, which possibly cannot and certainly need not be analyzed any futher.” The fundamental element here is the reaction of $i$ to arguments, which will serve as the informational basis to define $\ileadstoall$.
-Given a proposition $\prop$ and two arguments $\ar, \ar' \in \allargs$, a query consists in presenting both arguments to $i$ and observing which proposition $i$ considers valid in her current state of mind, thus using both arguments and possibly other arguments she has in mind: is it that $\prop$ holds, that $¬\prop$ holds, or that both are possible?
-The third possibility allows for the case where no argument appears more decisive than the other one.
-
-It is also necessary to capture the evolution of the position of $i$ towards arguments over time: a repeated query using a given pair of arguments may yield different answers, for example because the repeated question has been interleaved with another query containing other arguments (which $i$ may still have in mind when answering the second repetition), or for any other known or unknown reason.
-The important information for us is the \emph{set} of answers that $i$ could give to a query involving two given arguments and a given topic, among the set $\{\prop, ¬\prop, \text{both}\}$.
-The set designates all possible answers over time and over different order of asking the queries.
-Hence, given $\prop \in \allprops$, define a relation $\ileadstoprop \subseteq (\allargs × \allargs) × \powersetz{\{\prop, ¬\prop, \text{both}\}}$, where $\powersetz{B}$ designates the subsets of $B$ excluding the emptyset, with the semantics that $(\ar, \ar') \ileadstoprop C$, with $C \subseteq \set{\prop, ¬\prop, \text{both}}$, iff $\forall c \in C$, it is observable at least once that $i$, when presented with $(\ar, \ar')$, considers $c$ valid in her current state of mind.
-The querying protocol is supposedly made so that for any $\prop \in \allprops$, $\ileadstoprop = \ileadstonprop$.
-
-This information is only indirectly observable: for example, if $(\ar, \ar') \ileadstoprop \{\prop\}$, a querier will never know more than $(\ar, \ar') \ileadstoprop C$ with $\prop \in C \subseteq \set{\prop, ¬\prop, \text{both}}$.
-Also, it may be only possible to test one ordering of the queries (assuming that $i$ forgets over time might permit to test different orderings, but this assumption might be unrealistic).
-In some cases, it may even be only possible to test a single query with a given individual.
-This limitation of our observation will not be a problem for the results of this article.
-Intuitively, this bears on the fact that, first, theories apply to multiple individuals, and second, if a theory claims that $(\ar, \ar') \ileadstoprop \{\prop\}$, then either this claim is correct, or it is falsifiable, in the sense that there is a possibility of observing a contradiction to its claim.
-
-To be more concrete, one possible choice of a query protocol, when arguments and propositions are strings, is to read both arguments to $i$, together with $\prop$, and ask $i$ to verbally report the choice he opts for among the three possibilities.
-Another is to present both arguments and ask $i$ to pick an item among some choice set and make the choice correspond to a validation of $\prop$ or $¬\prop$, possibly even letting the choice engage $i$, for example telling $i$ that she may keep the object of choice (this is illustrated in \cref{ex:pick}).
-This second possibility is especially interesting as it makes the protocol partially observable in the restricted sense usually appreciated in revealed preferences approaches.
-Note that depending on the protocol, the choice “both” is not necessarily observable (more about this below).
-%In that case, the semantics of $\prop$ and $¬\prop$ relatedly change: instead of meaning that $\prop$ is definitely the 
-%Indeed, \citet{tversky_intransitivity_1969} note that individuals “are not perfectly consistent in their choices.
-When faced with repeated choices between x and y, people often choose x in some instances and y in others.
-Furthermore, such inconsistencies are observed even in the absence of systematic changes in the decision maker’s taste which might be due to learning or sequential effects.
-It seems, therefore, that the observed inconsistencies reflect inherent variability or momentary fluctuation in the evaluative process.” This is an accepted fact of experimental psychology \citep{luce_utility_2000}.
-However, it is reasonable to suspect that fluctuations occur less often, if at all, for some choices.
-For example, facing a choice between tea or coffee, I would virtually never pick tea (all other things being equal).
-We are interested in capturing precisely those kind of preferences.
-
-One can also use $\zar$ as one or both of the arguments, in which case the protocol queries the preference of $i$ given only one or given no argument.
-
-\begin{example}[cont.]
-	\label{ex:pick}
-	Continuing the example, define the querying protocol as, given $\prop_\alt$, presenting two arguments to $i$ and let $i$ choose an item among $\allalts$. $i$ may keep the chosen item. 
-	If $i$ chooses $\alt$, it is considered that $i$ has validated $\prop_\alt$, otherwise, $¬\prop_\alt$. The option “both” is not observable.
-%	Queries are separated by one week at least, which (as supposed in this example) is enough to ensure that no effect of pleasure for variability enter into play. 
-\end{example}
-
-Define $\ileadstoall$ from $\ileadstoprop$ as follows, for any $\prop \in \allprops$: $(\ar, \ar') \ileadstoall (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadstoprop C$ with $C \subseteq \set{\prop, \text{both}}$; and $(\ar, \ar') \ileadstoall (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadstoprop \set{\prop}$.
-
-Note that (A1) and (A2) hold.
-
-When “both” is not observable, $\ileadstoall$ is defined as: $(\ar, \ar') \ileadstoall (\prop, \text{possible}) ⇔ (\ar, \ar') \ileadstoall (\prop, \text{sure}) ⇔ (\ar, \ar') \ileadstoprop \set{\prop}$.
-(A1) and (A2) still hold.
-We say in this case that $\ileadstoall$ does not distinguish sure from possible.
-Thus, elements $\prop \in \allprops$ may be considered as simply equal to $\prop$ or $¬\prop$, as $(\prop, \text{sure})$ is treated exactly as $(\prop, \text{possible})$.
-
-\subsection{Example}
-\begin{example}[(cont.)]
-	Returning to the previous example, a theory $T$ could claim that, for all individuals that belong to some given socio-economic situation and that have some given degree (described by the theory in sufficient details that it is possible to determine precisely to which kind of individuals it applies), $(\prop_a, \text{sure})$ is in the deliberated preferences of the individuals, for a given alternative $\alt$ also described by $T$.
-The theory also suggests some argument $\ar$, a text that (according to $T$) will convince any individual (fitting the description) that $\prop_\alt$ holds, thus, that $\alt$ is a “good” food product for him.
-The theory can be put to the test by picking an individual fitting the description, presenting the argument together with any other argument (for example, proposed by another theory), and observing whether $i$ is convinced.
-$T$ resists to such a falsification test if $i$ is convinced.
-According to a previous theorem, $T$ tells the truth if it would resist to any possible falsification test.
-(This is impossible to definitely make sure of.)
-\end{example}
-This example illustrates a difference between this proposal and the classical revealed approach: it could be that $T$ tells the truth even though its claim does not correspond to the revealed preference of some individuals, thus that, given no argument, some individuals would consider $a$ as dominated by another alternative in the set considered.
-It also illustrates a difference between this proposal and persuasion: the goal of $T$ is not merely to convince $i$ (possibly by using its lack of knowledge of any counter-argument to what $T$ says), but to resist any falsification attempt.
-Thus, $T$ should be confronted to arguments coming from as varied perspectives as possible, in order to give confidence that it tells the truth.
-
-\section{Empirical theories}
-\subsection{Simple to complex}
-From an additive single-answer empirical theory, we can define a function: $\forall \ar_1 \gbeats \ar_0: f(\ar_1, \ar_0) = \ar_0 + {\gbeatsinv}(\ar_1) = \set{\ar_0 + \ard \suchthat \ard \in {\gbeatsinv}(\ar_1)}$, and $f(\ar_1, \ar_0) = \emptyset$ otherwise.
-Thus, $f = \set{((\ar_1, \ar_0), \ar_2) \suchthat \exists \ard \in \allargs \suchthat \ard \gbeats \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard}$.
-Also, from the previous definition, $g(\ar_0)(\ar_0 + \argsd_2) = dom(f^{-1}(\ar_0 + \argsd_2) \cap (\allargs × \set{\ar_0})) = {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$ because $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \argsd_2) ⇔ \exists \ar_2 \in \ar_0 + \argsd_2 \suchthat \ar_2 \in f(\ar_1, \ar_0) ⇔ \ar_1 \gbeats \ar_0 \land \exists \ard \in \argsd_2 \suchthat \ard \gbeats \ar_1$.
-\commentOC{Could be false.}
-
-Note that $f^{-1}(\ar_0 + \ar_2) ≠ {\gbeats}(\ar_2) × \set{\ar_0}$: if ${\gbeats} = \set{(\ard, \ar_1), (\ar_1, \ar_0), (\ard[6], \ar_5), (\ar_5, \ar_4)}$, and $\ar_0 + \ard = \ar_4 + \ard[6]$, then $f^{-1}(\ar_0 + \ard) = f^{-1}(\ar_4 + \ard[6]) = \set{(\ar_1, \ar_0), (\ar_5, \ar_4)}$ and ${\gbeats}(\ard) × \set{\ar_0} = \set{(\ar_1, \ar_0)}$.
-Also, note that $g(\ar_0)(\ar_0 + \argsd_2) ≠ {\gbeats}(\argsd_2) \cap {\gbeatsinv}(\ar_0)$.
-Consider ${\gbeats} = \set{(\ard, \ar_1), (\ar_1, \ar_0)}, \ar_2 = \ar_0 + \ard = \ar_0 + \ard$.
-Then, $(\ar_1, \ar_0) \in f^{-1}(\ar_0 + \ard)$, hence, $\ar_1 \in g(\ar_0)(\ar_0 + \ard)$, but ${\gbeats}(\ard) = \emptyset$.
-
-\subsection{Falsifiability}
-\commentOC{I should define $\Box(\hist \ileadsto \prop)$ iff it has been observed that $\hist \ileadsto \prop$.
-Then, axiom Correct observations (that is self-evident): $\Box(\hist \ileadsto \prop) ⇒ \hist \ileadsto \prop$ (what has been observed is).
-Supplementary axiom Falsification is enough (that is not self-evident): $\not\Box(\hist \ileadsto \prop) ⇒ \hist \nileadsto \prop$ (what has not been observed is not).}
-
-\commentOC{I want: An empirical theory for a normative theory is something like a normative and falsifiable claim.
-It is also configurable: it must be possible to guarantee that the falsification be easy (if the claim is false) depending on the kind of claim.}
-
-Given $\hist \in \allhist$ and $i \in I$, the claim $\hist \ileadstoe[i] \prop$ may not be verifiable, and is too specific to be falsifiable.
-However, given $\hist \in \allhist$, a broader claim is falsifiable: that for a given set of individuals $Q \subseteq I, \forall i \in Q, \hist \ileadstoe[i] \prop$ (provided $Q$ is big enough).
-Indeed, that claim it is equivalent to $\nexists i \in Q \suchthat \hist \nileadstoe[i] \prop$; exhibiting an $i \in Q$ such that $\hist \nileadstoe[i] \prop$ thus falsifies the broader claim.
-
-Given any $(\allprops, ¬, \allargs, I)$, an \emph{observation protocol} is a binary tree whose non-leaf nodes are among $I × \allhist × \allprops$ and whose two edges out of any non leaf node are labeled by “yes” and “no”; the leaf nodes being simply $\emptyset$.
-The observation protocol is said to assume memory iff for each non-leaf node $n = (i, \hist, \prop)$ about $i$, any node $n' = (i, {\hist}', \prop')$ about $i$ that is further down the tree continues the history, that is, the sequence ${\hist}'$ starts with $\hist$.
-Given an observation protocol and observables $(\ileadstoe[i])_{i \in I}$, the \emph{observed path} refers to the path in the tree defined recursively as consisting of the root node and, for each non-leaf node $n = (i, \hist, \prop)$ in the path, the child node along the branch “yes” if $\hist \ileadstoe[i] \prop$ and the child node along the branch “no” otherwise.
-The \emph{observations} refer to the set of nodes along the observed path.
-
-Given any $(\allprops, ¬, \allargs, I)$, a \emph{normative claim} about $(\allprops, ¬, \allargs, I)$ (or about $\allargs$, when the other defined objects are left implicit) is any first-order logic proposition involving the atoms $[(\hist, \prop) \in {\ileadstoe[i]}], \hist \in \allhist, \prop \in \allprops$ which, together with the axioms, permits to deduce that $\prop \in \iprops$ for some $i \in I$ and $\prop \in \allprops$.
-The claim is said to be \emph{about} the given set $\allargs$.
-An observation protocol, together with observables $(\ileadstoe[i])_{i \in I}$, \emph{falsifies} a normative claim iff the falsity of the claim is deducible from the axioms and the observations.
-A normative claim is \emph{falsifiable} iff there exists a finite observation protocol such that for any observables $(\ileadstoe[i])_{i \in I} \in (\allhist × \allprops)^I$, if the claim is false given these observables, then it is possible to deduce it from the axioms and the observations given the observables.
-
-\commentOC{Falsifiable may not be the right word.
-Perhaps “provable“, meaning “tautological or Popper-falsifiable”.
-“Falsifiable” suggests that if a claim is not falsifiable, then a weaker claim is not falsifiable either, which does not hold.
-My falsifiability criterion demands that if a claim is false, we can see it; whether Popper’s demands that the claim be possibly false.
-Perhaps I should demand that we can pick a set of consequences of the claim and show it wrong it at least one possible state of the universe.}
-
-A normative claim is \emph{trivial} iff it is about a singleton $\allargs = \set{\ar}$, and has the form: $\ar \ileadstosts \prop$, for some $i \in I$.
-A normative claim is minimal iff it has the form: $\exists \ar \in \allargs \suchthat \ar \ileadstosts \prop$, for some $i \in I$ and $\prop \in \allprops$.
-Note that given a minimal claim, $\card{\allargs} = 1$ is equivalent to the claim being trivial.
-
-\begin{proposition}[Trivial claims are not falsifiable]
-	Given any $(\allprops, ¬, \allargs ≠ \emptyset, I)$, no minimal normative claim is falsifiable.
-\end{proposition}
-\begin{proof}
-	Consider any claim about some $i$ and some $\prop$ and any finite observation protocol.
-We have to show that for some observables, the claim is false, but it is impossible to observe it (meaning, to deduce it from the axioms and observations).
-
-	Given $k \in \N$, define $\ileadstosts[k]$ as $\ar^k \ileadstosts \prop$ and $\ar^{k+1} \ileadstosts ¬\prop$ (where $\ar^k$ designates a finite sequence repeating $k$ times $\ar$, for $\ar \in \allargs$).
-I claim that for some $k$, the observables that include this relation makes the claim false, but not observably so.
-This is because the observation protocol is finite, thus, only permits to observe some finite number of instances of the relation $\ileadsto$.
-Suffices to define $k$ as that number.
-\end{proof}
-
-There is another reason for non falsifiability, which does not involve the problem of finiteness.
-\begin{proposition}[Minimal non-trivial claims are not falsifiable]
-	Given any $(\allprops, ¬, \allargs, I), \card{\allargs} ≥ 2$, no minimal normative claim is falsifiable.
-\end{proposition}
-\begin{proof}
-	Define $\ar_1$ as the first element of the sequence $\hist$ of the root node of the observation protocol (if the observation protocol is empty, suffices to define any observables that make the claim false).
-Define the observables so that $\forall \hist \in \allhist: \ar_2, \hist \ileadsto ¬\prop$.
-This proves that no argument is decisive, hence $\prop \notin \Box\Phi$, and the claim is false.
-But the observables may also be defined so as to satisfy the protocol (defined as: when going through the protocol, the observations can’t fail the claim).
-\end{proof}
-
-\subsection{Definition}
-A general empirical theory for a normative theory $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$ is a tuple $({\gleadsto}, f)$, where ${\gleadsto} \subseteq \allargs × \allprops$ and $f \subseteq (\allargs × \allargs) × \allargs$ with $f(\allargs × \allargs)$ being finite.
-
-Define $g(\ar_0) \subseteq \allargs × \allargs$ as $g(\ar_0) = \set{(\ar_2, \ar_1) \suchthat \ar_2 \in f(\ar_1, \ar_0)} = \bigcup_{\ar_1 \in \allargs} (f(\ar_1, \ar_0) × \set{\ar_1})$.
-The set $g(\ar_0)(\allargs)$ contains the anticipated attacks on $\ar_0$; the set $g(\ar_0)(\ar_2)$ contains the anticipated attacks on $\ar_0$ for which $\ar_2$ is a planned response; and the set $g(\ar_0)^{-1}(\ar_1) = f(\ar_1, \ar_0)$ contains the planned protections of $\ar_0$ against $\ar_1$.
-
-Given $\ar_0 \in \allargs$ and $\args_2 \subseteq \allargs$, define the set $\args_1 \subseteq \allargs$ of arguments that $\args_2$ protects $\ar_0$ from as $\args_1 = [f^{-1}(\args_2)]^{-1}(\ar_0) = \set{\ar_1 \in \allargs \suchthat f(\ar_1, \ar_0) \cap \args_2 ≠ \emptyset} = g(\ar_0)(\args_2) = dom(f^{-1}(\args_2) \cap \allargs × \set{\ar_0})$.
-
-\subsection{A general condition sufficient for validity and (hopefully) falsifiability}
-It should be possible to define this condition as a claim that does not involve $f$, so that it can be done before defining an empirical theory.
-Then, show that a normative and falsifiable claim must have the form of a convincingness claim.
-
-\begin{remark}
-	In fact, the model is tasked with finding a stable point after interrogating $i$.
-The process of trying counter-arguments $\ar_1, …$ is $q(i)$.
-When done, the model claims that $\ar_0 + \ar_2 + …$ is decisive.
-The model also claims that another process of interrogation does not lead to different answers.
-This is falsifiable.
-	When claiming that $(\ar_1, \ar_0) \ileadstoall[i] \prop$, the model really claims that $\nexists p, i' \in q^{-1}(q(i)) \suchthat p, \ar_1, \ar_0 \ileadsto[i'] ¬\prop \lor p, \ar_0, \ar_1 \ileadsto[i'] ¬\prop$, where $i' \in q^{-1}(q(i))$ iff $q(i) = q(i')$.
-
-	To say that $\prop \in \iprops$, need to not depend on choice of $q$, in the following sense: if with $q$, $\prop$ seems stable, but with $q'$, $¬\prop$ seems stable, then $\prop$ is not proved as being in $\iprops$.
-But if with $q$, $\prop$ seems stable, but with $q'$, nothing can be shown to be stable, then $\prop$ is proved (temporarily) as being in $\iprops$.
-More precisely, after $q'$, the model must be able to stabilize $i$ with its $q$.
-\end{remark}
-
-$\ar_0$ $i$-defends $\prop$ when ignoring $S_1$ iff $\forall \hist \in \allhist: [\args_1 \cap \range(\hist) = \emptyset] ⇒ (\hist, \ar_0) \ileadstosts \prop$.
-$\ar_0$ $i$-defends $\prop$ under protection of $S_2$ iff $\ar_0$ $i$-defends $\prop$ when ignoring $g(\ar_0)(\args_2)$.
-
-\begin{definition}[Convincingness]
-	$\forall i \in I, \prop \in \gpropse, \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\prop)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\prop$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
-\end{definition}
-Note that requiring that $\args_0$ be a singleton does not modify the condition, in the sense that any theory satisfying the condition also satisfies its strenghtening.
-Similarly, requiring that $S_k ≠ \emptyset$ does not modify the condition (because if some $k$ satisfy the condition with $S_k = \emptyset$, then picking $k' = k-2$ with the same sets $S_j$ also satisfy the condition, and because $S_0 ≠ \emptyset$, this recursion must end with a suitable $k$).
-
-\begin{remark}
-	The claim must have the form: some structure is adequate for all individuals.
-Here, the structure is given by $f$.
-The claim should claim that looking at the attacks planned by $f$ is enough; and looking at the defenses planned by $f$ is enough.
-
-	This may be adequate as if $\ar_0$ seems suitable but some unplanned attacker $\ar_1$ attacks it, then use $\ar_1 \in \hist$ and observe that $¬(\hist, \ar_0) \ileadstoe \prop$ to deny the claim.
-
-	Perhaps this could be phrased as follows.
-Say that $\ar_2$ is replaceable by $\args_2$ iff what $\ar_2$ protects is either protected by $\args_2$ or replaceable (by what?).
-Say that a set $\args$ is sufficient iff its complement is replaceable by $\args$.
-Then $g$ claims (among others) that $g(\ar_0)^{-1}(\ar_1)$ is sufficient.
-
-	The claim can (hopefully) be given the form: $\forall i \suchthat …, \ar$ decisive. Given $i$, either $\ar_0$ is decisive, or $\ar_1$ attacks it but then $\ar_2$ is decisive, …
-\end{remark}
-
-\begin{theorem}
-	If an empirical theory is convincing, and its normative theory satisfies the axioms, then it is valid.
-\end{theorem}
-\begin{proof}
-	Consider $i \in I$ and $\prop \in \gpropse$. 
-	By hypothesis, $\exists k$ such that some $\ar_k \in \args_k$ defends $\prop$ under protection of $\emptyset$. Therefore, $\ar_k \ileadstosts \prop$. Using \cref{ax:norm}, validity follows.
-\end{proof}
-
-\begin{theorem}
-	The convincingness claim of any empirical theory is falsifiable: given an ET, there exists a finite obs prot with memory such that for any observables, if the claim is false given these observables, then it is possible to deduce it from the axioms and observations.
-\end{theorem}

### 2022-08-15 simple.tex
Phrasing and bib

@@
 \begin{document}
-\title{Theories of deliberated judgment}
+\title{Theories of deliberated choice}
 \author{Olivier Cailloux}
@@
 \section{Introduction} 
-Observing subjects performing acts of choice is the basis of much work in econometrics.
+Observing subjects perform acts of choice is the basis of much work in econometrics.
 Such acts have been used, among others, to give an observable basis to the concept of preference \citep{samuelson_foundations_1983}.
@@
 
-While numerous articles have discussed the concept of deliberation in the last decades, it remains unsettled, to the best of my knowledge, how to observe a deliberated judgment, or, correspondingly, how to define this concept in a way that makes it amenable to empirical study, sufficiently precisely that any disagreement about someone’s deliberated judgment in a given context could be solved, at least in principle, by an empirical experiment.
-%This article is interested in defining the concept of deliberated judgementof a subject, as opposed to the classical one, that will henceforth be called her natural judgment, that is, the way that she chooses between acts when she does not face any arguments, i.e.,
+While numerous articles have discussed the concept of deliberation in the last decades, it remains unsettled, to the best of my knowledge, how to observe a deliberated judgment in a systematic and reproducible fashion.
+There is a need to define this concept sufficiently precisely that, first, it is clear what counts as a deliberated judgment (i.e., when “sufficient” \citep{meinard_justification_2020} or “correct” deliberation has happened); and second, it is clear which part of the claim is empirical and which part stems from an unfalsifiable conception of what “deliberated” means.
+This permits to study deliberated judgments empirically, meaning here that disagreements about someone’s deliberated judgment in a given context can be solved, at least in principle, by an empirical experiment, provided the very conception of what constitutes a deliberated judgment is shared.
+This article is interested in defining the concept of deliberated judgement of a subject and show how one can study it in an emprical manner.
+The “classical” counterpart of deliberated judgments,, that does not involve confrontation with arguments, will henceforth be called the natural judgment.
+As we deal with choice acts, we will also name the concept “deliberated choice”, as opposed to “natural choice”.
 
@@
 The deliberated judgment of an individual is thus defined with no requirement that the arguments be uttered by peers in a debate; they can be given by an automata, for example.
-In this sense, deliberated judgments come close to what Rawls calls reflective equilibrium (referring to an idea of Goodman), a concept that has much inspired the present proposal.
+In this sense, deliberated judgments come close to what \citet{rawls_theory_1999} calls reflective equilibrium (referring to an idea of \citet{goodman_fact_1983}), a concept that has much inspired the present proposal.
 
@@
 The notion of argument invoked here is an extremely large one, including texts, images, sounds, experiences (a hiking trip), and so on: anything that can be transmitted to a subject qualifies as a possible argument.
-Such an “argument” need not even have the logical structure of what is considered a proper argument in argumentation theory, which permits to avoid having to take position on what is a correct argument, and permits to study wide enough conceptions of deliberated judgment, including those involving no paternalism: anything that influences the judgment of a subject may a priori be considered worth including in at least some conceptions of deliberated judgment, thus including whatever some could consider “bad reasoning” or “bad reasons”.
+In particular, such an “argument” need not have the logical structure of what is considered a proper argument in argumentation theory.
+This important feature of this proposal permits to avoid taking a position on what is a correct argument, and permits to study wide enough conceptions of deliberated judgment, including those involving no paternalism \citep{cailloux_formal_2020}: anything that influences the judgment of a subject, as judged by the subject herself and not by any external standard, may a priori be considered worth including in at least some conceptions of deliberated judgment, thus including whatever some could consider as “incorrect reasoning” or “bad reasons”.
 
-The dependence of the deliberated judgment concept on the exposure protocol yields a first qualification about the concept of deliberated judgments defined here when one desires to use it normatively: it is only as reasonable to call the resulting judgments “deliberate” in a normative sense as the exposure protocol is normatively relevant to deliberation.
+The dependence of the deliberated judgment concept on the exposure protocol yields a first qualification about the concept of deliberated judgments when one desires to use it normatively: it is only as reasonable to call the resulting judgments “deliberate” in a normative sense as the exposure protocol is normatively relevant to deliberation.
 A sufficiently restricted, or even purposefully chosen, set of arguments may yield judgments that are only deliberate in the technical sense used here, but that pertain more to brain-washing than to reflective judgments.
-While it is indeed a long-term goal of this research program to yield a normatively relevant conception of preference (appropriate, for example, for recommendation), it is not a claim of this article that anything that corresponds to deliberated judgments as defined here qualify as being appropriate for recommendation (or for any other normative use): much depends on the chosen exposure protocol.
-The goal of this article is, more modestly, one of a conceptual and practical clarification.
+While it is indeed a long-term goal of this research program to yield a normatively relevant conception of preference (appropriate, for example, for recommendation), it is not a claim of this article that anything that corresponds to deliberated judgments as defined here qualify as being appropriate for any normative use: much depends on the chosen exposure protocol.
+The goal of this article is one of a conceptual and practical clarification.
 It proposes a sharp distinction between the empirical content and the normative content of the concept of deliberated judgments: the definition proposed here transfers the full normative weight on the choice of the exposure protocol; and leaves the rest of the disagreements to empirical settling.
-This is methodologically akin, mutatis mutandis, to the axiomatic study of justice such as done in social choice, only replacing mathematical deduction with empirical claims.
-In social choice, the choice of axioms bears the full normative weight; once axioms are chosen, it is a matter of deduction which social choice rules (if any) correspond to that choice.
-In our case, once an exposure protocol is chosen, it is a pure empirical matter which deliberated judgments result.
-In supplement to a possibly helpful conceptual clarification, such a sharp separation may reveal practically useful for separation of concern as it permits to study deliberated judgments empirically under various exposure protocols independently of possible persistent disagreements about which norms are more appropriate for deliberation in which circumstances.
+This is methodologically akin, mutatis mutandis, to the axiomatic study of justice such as done in social choice, only complementing mathematical deduction with empirical claims.
+In social choice, the choice of axioms bears the full normative weight; once axioms are chosen, it is a matter of logic which social choice rules (if any) correspond to that choice.
+In our case, once an exposure protocol is chosen, it is an empirical matter which deliberated judgments result.
+In supplement to a possibly helpful conceptual clarification, such a sharp separation may reveal practically useful for separation of concern as it permits to study deliberated judgments empirically under various exposure protocols independently of possible disagreements about which norms are more appropriate for deliberation in which circumstances.
 
 The deliberated judgment of a subject is said to depend on the exposure protocol, that is, on the set of arguments and the way they are submitted to the subject, and not only on the set of arguments, because the very way that they are transmitted to the individual may affect her judgment differently.
-For example, reading an image description and showing an image to a subject may impress them differently.
+For example, reading an image description and showing an image to a subject may impress them differently \citep{railton_facts_2003}.
 
 The exposure protocol defines a set of argument and, importantly, how arguments are sent to the subject and her subsequent choice observed.
-There is, as need be, no requirement on the internal process that occurs in the subject’s mind while she (possibly) processes the arguments, as it is not desirable to assume that the internal process could be observed.
+There is no explicit dependency on the internal process that occurs in the subject’s mind while she (possibly) processes the arguments, as it is not desirable to assume that the internal process could be observed.
 We consider subjects as black boxes and only require a capacity of observation of their choices after exposure to arguments.
@@
 
-Studying judgments resulting from exposure to arguments includes a difficulty that is not present with natural choice experiments: exposing an individual to arguments may change the individual’s stance, an effect that cannot be erased to submit the individual (considered “clean” again) to another sequence of arguments.
+Studying judgments resulting from exposure to arguments includes a difficulty that is not present with natural choice experiments: exposing an individual to arguments may change the individual’s stance, an effect that cannot be erased in order to submit the individual to an unrelated sequence of arguments.
 The observer thus cannot in general assume that multiple unrelated sequences of arguments can be tested on a given individual.
@@
 Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence. 
-A generic element of $\allhist$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path when this raises no ambiguity.
-Its length is denoted by $\card{\hist} \in \N$.
+A generic element of $\allhist$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path. Its length is denoted by $\card{\hist} \in \N$.
 Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}: \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
@@
 The deliberated choice of $i$ given the exposure protocol $(I, \allargs, {\allleadsto})$ is denoted $P_i \subset P$.
-Its formal defnition requires the notion of decisive argument.
+Its formal definition requires the notion of decisive argument.
 
@@
 \subsection{An example and a discussion about observability}
-The following toy example is inspired by citet[p.~59]{Railton}\commentOC{TODO}, who uses this example to support his claim that beliefs may influence decisions. Here is his story.
+The following toy example is inspired by an argument from \citet[p.~59]{railton_facts_2003}. Here is his argument.
 \begin{quote}
@@
 Observing the candidates take the tests may yield a contrary impression; this is a well-known psychological phenomenon depending on the order of the questions that the candidates answer correctly.”
-	Let $\Phi = \set{\prop_1, \prop_2}$ where $\prop_1$ represent $m_1$ and $\prop_2$ represent $m_2$.
+	Let $\prop_1$ represent the choice of $m_1$ and $\prop_2$ that of $m_2$.
 
-	If the prediction described in the quote is correct, and applies equally to this modified experiment, then, given $i \in I$, $i$’s deliberated choice is $\prop_2$ because $a_e$ is a decisive argument for $\prop_2$, even though $i$ might have rather chosen $\prop_1$ if given only the arguments $a_1$ and $a_2$ without $a_e$.
+	If the prediction described in the quote is correct when applied to this modified experiment, then, given $i \in I$, $i$’s deliberated choice is $\prop_2$ because $a_e$ is a decisive argument for $\prop_2$, even though $i$ might have rather chosen $\prop_1$ if given only the arguments $a_1$ and $a_2$ without $a_e$.
 \end{example}
@@
 That the deliberated choice of any individual $i$ is well-defined may be doubtful, as it involves counterfactuals.
-To see this, let $\alpha_{123} = (a_1, a_2, a_e)$ designate the history where the arguments are shown in the order they are described in the example, and let $\alpha_{321} = (a_3, a_2, a_1)$ designate the reverse order.
-The deliberated choice of $i$ is defined so as to not depend on the (arbitrary) order of the arguments shown to $i$: for $\prop \in \iprops$, it must be that directing to $i$ the path $\alpha_{123}$ or the path $\alpha_{321}$ both lead $i$ to choose $\prop$.
-However, once we have shown to $i$, say, $\alpha_{123}$, we cannot show to her $\alpha_{321}$ (unless assuming $i$ forgets arguments after a while and waiting for sufficiently long, which would create practical and theoretical difficulties).
+To see this, let $\alpha = (a_1, a_2, a_e)$ designate the argumentative path where the arguments are shown in the order they are described in the example, and let $\alpha' = (a_e, a_2, a_1)$ designate the reverse order.
+The deliberated choice concept is defined so as to not depend on the (arbitrary) order of the arguments shown to $i$: for $\prop \in P_i$, it must be that directing to $i$ the path $\alpha$ or the path $\alpha'$ both lead $i$ to choose $\prop$.
+However, once we have shown $\alpha$ to $i$, we cannot show to her $\alpha'$ (unless assuming $i$ forgets arguments after a while and waiting for sufficiently long, which would create practical and theoretical difficulties).
 
-This difficulty is resolved using falsifiable general theories, applicable to $I$ and not solely to a given $i$, so that, intuitively speaking, $\alpha_{321}$ can be tested on some $i' ≠ i$.
-Indeed, what is needed is a way to make a claim such as the one concluding \cref{ex:tutor} empirically testable.
+This difficulty is resolved using falsifiable general theories, applicable to $I$ and not solely to a given $i$, so that $\alpha$ can be tested on $i$ and $\alpha'$ on some $i' ≠ i$.
+Indeed, what is needed is a way to make a claim such as the one concluding \cref{ex:tutor}, according to which $a_e$ is a decisive argument, empirically testable.
 This is achieved in the next section thanks to theories of deliberated choice.
@@
 This section assumes that an exposure protocol $(I, \allargs, {\leadsto})$ is defined, and defines theories of deliberated choice associated with that exposure protocol.
-We will start with very simple theories in order to build an intuition about the conditions required on theories of deliberated choice (\cref{sec:static}), then give an example to illustrate why more complex theories are needed (\cref{sec:lichtenstein}) and finally define more general theories of deliberated choice (\cref{sec:dynamic}).
+We will start with very simple theories (\cref{sec:static}) in order to build an intuition about the conditions required on theories of deliberated choice, then justify the need for more complex theories (\cref{sec:lichtenstein}) and finally define more general theories of deliberated choice (\cref{sec:dynamic}).
 
@@
 Such an argument could be too long to be convincing to $i_1$ or $i_2$, as it needlessly spends efforts countering an argument that the individual considers irrelevant to start with.
-This  will become an important problem if there are not only two but many a priori possible arguments $a_k$ for $\nprop$, a small subset of which is considered relevant by a given individual, each with their own counter-argument $a'_k$ for $\prop$.
+This  will become an important problem if there are not only two but many a priori possible arguments $a_k$ for $\nprop$, a small subset of which is considered relevant by any given individual, each with their own counter-argument $a'_k$ for $\prop$.
 
@@
 It may also be that, for each individual who considers relevant some arguments $A$ for saving not much (i.e., spending more in the short term), it is possible to give counter-arguments $A'$ that will convince the individual to opt for saving more.
-But no single argument could be decisive for each $i \in I$: it could be that only tailored counter-arguments could convince individuals, given the complexity of the issue.
+But no single argument could be decisive for each $i \in I$: it could be that only counter-arguments built specifically according to what a given individual considers relevant could convince him, given the complexity of the issue.
 This illustrates that the deliberated choice of each individuals in $I$ may be to save more even though no static theory (\cref{def:static}) may achieve showing it, as it could be that no such theory is truthful.
@@
 
-Define $\allprops = \set{\phi_P, \phi_D}$.
+Define $P = \set{\phi_P, \phi_D, 0}$.
 
@@
 Therefore, we recommend to rather pick $P$ as it presents a much better chance of earning money”.}
-Define a counter-argument to $\ar_u$, $\ar_l$, indicating that for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.
+Define a counter-argument $\ar_l$ to $\ar_u$, indicating that for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.
 \footnote{Here is a possible text for $\ar_l$.
@@
 $\forall \hist \in \allhist: \hist \ileadsto[e] D ⇔ [\ar_e \in R(\hist)]$, and $\hist \ileadsto[e] P$ otherwise.
-Note that in particular, if $\hist$ contains $\ar$ but not $\ar_e$, $\ar \nileadsto[e] D$, as we assume such individuals are confused by the longer argument $\ar$ referring to abstract notions and therefore opt for $P$, falling back to the common psychological bias.
+Note that in particular, if $\hist$ contains $\ar$ but not $\ar_e$, $\ar \ileadsto[e] P$, as we assume such individuals are confused by the longer argument $\ar$ referring to abstract notions and therefore opt for $P$, falling back to the common psychological bias.
 The second kind of individuals is represented by $\ileadsto[u]$ defined as $\forall \hist \in \allhist: \hist \ileadsto[u] D ⇔ [\ar_u \notin R(\hist) \lor \ar \in R(\hist) \lor \set{\ar_u, \ar_l} \subseteq R(\hist)]$, and $\hist \ileadsto[u] P$ otherwise.
-We assume here that such individuals think about $\ar_u$ as a correct argument in favor of $P$ until shown the rebuttal $\ar_l$ (or $\ar$, which contains the same rebuttal).
+We assume here that such individuals think about $\ar_u$ as a correct argument in favor of $P$ until shown the rebuttal $\ar_l$ (or $\ar$, which contains a similar rebuttal).
 Assuming finally $\allleadsto$ as equal to $\ileadsto[e]$ for individuals of the first kind and $\ileadsto[u]$ otherwise concludes the definition of the exposure protocol $(I, \allargs, {\allleadsto})$.
@@
 \label{sec:dynamic}
-An argumentative theory of \ac{DC} $\gamma$ is defined as a tuple $(\pga, \arga, \dg)$, where $\pga \in P$ is the proposition supported by the theory, $\arga \in \allargs$ is the initial argument in favor of $\pga$ and $\dg$ is a defense relation.
+An argumentative theory of deliberated choice $\gamma$ is defined as a tuple $(\pga, \arga, \dg)$, where $\pga \in P$ is the proposition supported by the theory, $\arga \in \allargs$ is the initial argument in favor of $\pga$ and $\dg$ is a defense relation.
 \commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}
@@
 %, and must satisfy $\ar \notin \histend ⇒ \dg(\ar, \hist) = \emptyset$.
-As is usual for right-unique relations, I write $\dg(\ar_0, \hist) = \ar_1$ instead of $\dg(\ar_0, \hist) = \set{\ar_1}$.
+As is usual for right-unique relations, we write $\dg(\ar_0, \hist) = \ar_1$ instead of $\dg(\ar_0, \hist) = \set{\ar_1}$.
 Say that $\ar_1$ defends $\ar_0$ iff $\exists \hist \suchthat \dg(\ar_0, \hist) = \ar_1$.
@@
 The bounded depth condition on the defense relation imposes that
-$\exists k \in \N \suchthat (\dg)^k(\gleadstoinv(\allprops)) = \emptyset$.
+$\exists k \in \N^* \suchthat (\dg)^k(\arga) = \emptyset$.
 The smallest such $k$ is called the depth of the theory.
@@
 Generalizing this observation, given $i \in I$, define $\dgi(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \in \histend \land \hist \nileadsto \pga} \subseteq \dg(\ar)$ as the subset of defenders of $\ar$ required for convincing $i$ of choosing $\pga$.
-Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
 Define $\gargsi \subseteq \allargs$ as the transitive closure of $\arga$ under $\dgi$: $\gargsi = \cup_{k \in \N} (\dgi)^k(\arga)$.
@@
 
+This definition of truthfulness is adopted because of our goal of distinguishing empirical claims.
+Truthfulness, so defined, can be falsified empirically: if any of the set of claims embedded in this definition does not hold, it is possible to determine this empirically.
+
 Note that a static theory $(p, \ar)$ can be considered as an argumentative theory $(p, \ar, \emptyset)$, and is truthful in the sense of \cref{sec:static} iff $(p, \ar, \emptyset)$ is truthful in the sense of \cref{def:truth}.
 
-Associated with an argumentative theory also comes the following axiom, that mandates that if some argument $\ar_2$ defends some argument $\ar_1$, and if $\ar_2$ leads $i$ to opt for $\pga$ in some path containing $\ar_1$, then $\ar_1$ can be omitted and the path will still lead $i$ to opt for $\pga$.
+Associated with an argumentative theory also comes the following axiom, that mandates a more general version of the following requirement: if some argument $\ar_2$ defends some argument $\ar_1$, and if $\ar_2$ leads $i$ to opt for $\pga$ whenever it immediately follows $\ar_1$, then omitting $\ar_1$ would still have lead $i$ to opt for $\pga$.
 
@@
 This is called an axiom because it cannot be falsified using observables.
-It has to be accepted on the basis of the rest of the observations.
-What it states are counterfactuals: if $i$ had been presented with $\hist$ not containing $\ar_1$, and assuming $i$ would have accepted an argument $\ar_2$ for $\pga$, …
-This seems reasonable because $a_2$, as a defender of $a_1$, “contains” $a_1$. 
-(To be finished.)
+It has to be accepted on the basis of the rest of the observations and on the contents of the defending arguments.
+As \cref{ex:lichtenstein} suggests, theories can be built so as to make this axiom plausible by embedding within defending arguments the content of the defended argument.
 

### 2022-08-15 simple.tex
Update on Overleaf.

@@
 An argumentative theory of deliberated choice $\gamma$ is defined as a tuple $(\pga, \arga, \dg)$, where $\pga \in P$ is the proposition supported by the theory, $\arga \in \allargs$ is the initial argument in favor of $\pga$ and $\dg$ is a defense relation.
-\commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}
 
@@
 The smallest such $k$ is called the depth of the theory.
-\commentYM{ok soit, ça semble raisonnable, mais tu n'as pas de raison plus forte, j'adopterais une formulation plus modeste et ouverte, du genre "ça semble souhaitable"}
 

### 2022-09-21 simple.tex
Update on Overleaf.
p, not φ

@@
 \label{sec:static}
-\Cref{ex:tutor} suggests a simple form for theories of deliberated choice: suffice to determine an argument $\ar \in \allargs$ and an alternative $\prop \in \Phi$ such that the theory claims that $\forall i \in I: \ar \ileadstost \prop$ and that $\forall i \in I: \prop \in \iprops$.
+\Cref{ex:tutor} suggests a simple form for theories of deliberated choice: suffice to determine an argument $\ar \in \allargs$ and a preference $p \in P$ such that the theory claims that $\forall i \in I: \ar \ileadstost p$ and that $\forall i \in I: p \in P_i$.
 
@@
 \end{definition}
-A static theory $(p, \ar)$ is said to be truthful iff $\forall i \in I: \ar \ileadstost \prop$, and to be correct iff $\forall i \in I: \prop \in \iprops$.
+A static theory $(p, \ar)$ is said to be truthful iff $\forall i \in I: \ar \ileadstost p$, and to be correct iff $\forall i \in I: p \in P_i$.
 We can then say that such theories are valid, meaning that their truthfulness implies their correctness.
@@
 \end{proof}
-Importantly, truthfulness can indeed be checked using our observational basis, that is, if $\exists i \in I \suchthat \ar \nileadstost \prop$, then it is possible to exhibit this fact experimentally.
+Importantly, truthfulness can indeed be checked using our observational basis, that is, if $\exists i \in I \suchthat \ar \nileadstost p$, then it is possible to exhibit this fact experimentally.
 
@@
 	In a famous article about preference reversals, \citet{lichtenstein_reversals_2006} discuss an example involving two lotteries.
-The lottery $P$ lets the subject win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $P = (.99, +\$4; .01, −\$0.1)$.
-The lottery $D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
-The letter $P$ stands for probability: one salient aspect of $P$ is the very high chance of winning.
-The letter $D$ stands for dollar: one salient aspect of $D$ is the high gain it gives (compared to $P$) in dollar amount if the subject is lucky.
+The lottery $P$ lets the subject win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $L_P = (.99, +\$4; .01, −\$0.1)$.
+The lottery $L_D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
+The letter $P$ stands for probability: one salient aspect of $L_P$ is the very high chance of winning.
+The letter $D$ stands for dollar: one salient aspect of $L_D$ is the high gain it gives (compared to $P$) in dollar amount if the subject is lucky.
 
-This example is interesting because when asked to bid for lotteries, the theory discussed by the authors predicts, and their experiments confirm, that subjects tend to bid more for $D$ than for $P$, because the bidding question tend to make individuals focus on dollar amounts; whereas when asked to choose one lottery, the lotteries being presented in pairs, subjects tend to choose $P$ among the pair $\set{P, D}$, giving greater attention to probabilities.
+This example is interesting because when asked to bid for lotteries, the theory discussed by the authors predicts, and their experiments confirm, that subjects tend to bid more for $L_D$ than for $L_P$, because the bidding question tend to make individuals focus on dollar amounts; whereas when asked to choose one lottery, the lotteries being presented in pairs, subjects tend to choose $L_P$ among the pair $\set{L_P, L_D}$, giving greater attention to probabilities.
 
-Define $P = \set{\phi_P, \phi_D, 0}$.
+Define $P = \set{L_P, L_D, 0}$.
 
-Define $\ar_e$ as a text arguing that the choice between $P$ and $D$ should be determined by their expected revenue, namely, $\$3.959$ for $P$ and $\$4$ for $D$.
+Define $\ar_e$ as a text arguing that the choice between $L_P$ and $L_D$ should be determined by their expected revenue, namely, $\$3.959$ for $L_P$ and $\$4$ for $L_D$.
 \footnote{Here is a possible text for $\ar_e$.
-“Imagine you play $P$ 100 times.
+“Imagine you play $L_P$ 100 times.
 On average, you would win 99 times and lose once, which means gaining 99 × \$4 = \$396 and losing 1 × \$0.10 = \$0.10, hence a total net gain of \$395.90.
-Thus, your average net gain for the $P$ bet would be \$3.9590.
-[Similar text for $D$.] Therefore, we suggest you choose $D$ for a higher expected revenue.”}
+Thus, your average net gain for the $L_P$ bet would be \$3.9590.
+[Similar text for $L_D$.] Therefore, we suggest you choose $L_D$ for a higher expected revenue.”}
 Define $\ar_u$ as a text arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain. 
 \footnote{Here is a possible text for $\ar_u$.
-“$D$ is better than $P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
+“$L_D$ is better than $L_P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
 For example, consider a choice between winning $10^6$ dollars with probability $0.8$ and winning $2 × 10^6$ dollars with probability $0.4$.
 These two lotteries have the same expected gain, but the first one is clearly preferrable.
-Therefore, we recommend to rather pick $P$ as it presents a much better chance of earning money”.}
+Therefore, we recommend to rather pick $L_P$ as it presents a much better chance of earning money”.}
 Define a counter-argument $\ar_l$ to $\ar_u$, indicating that for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.
 \footnote{Here is a possible text for $\ar_l$.
-“The lottery $D$ has a higher expected revenue, and thus, a higher utility than $P$, because for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.”}
+“The lottery $L_D$ has a higher expected revenue, and thus, a higher utility than $L_P$, because for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.”}
 Define $\ar$ so as to include the contents of $\ar_e$, $\ar_u$ and $\ar_l$.
@@
 
-Define $I$ as a set of individuals facing a choice between $P$ and $D$ in a laboratory experiment.
+Define $I$ as a set of individuals facing a choice between $L_P$ and $L_D$ in a laboratory experiment.
 Define $\ileadsto$ as simply exposing $i$ to $\alpha$ and observing the resulting choice by asking $i$ to indicate which lottery she prefers playing. 
@@
 Accordingly, define $\ileadsto[e]$, representing the first kind of individuals, as follows.
-$\forall \hist \in \allhist: \hist \ileadsto[e] D ⇔ [\ar_e \in R(\hist)]$, and $\hist \ileadsto[e] P$ otherwise.
-Note that in particular, if $\hist$ contains $\ar$ but not $\ar_e$, $\ar \ileadsto[e] P$, as we assume such individuals are confused by the longer argument $\ar$ referring to abstract notions and therefore opt for $P$, falling back to the common psychological bias.
-The second kind of individuals is represented by $\ileadsto[u]$ defined as $\forall \hist \in \allhist: \hist \ileadsto[u] D ⇔ [\ar_u \notin R(\hist) \lor \ar \in R(\hist) \lor \set{\ar_u, \ar_l} \subseteq R(\hist)]$, and $\hist \ileadsto[u] P$ otherwise.
-We assume here that such individuals think about $\ar_u$ as a correct argument in favor of $P$ until shown the rebuttal $\ar_l$ (or $\ar$, which contains a similar rebuttal).
+$\forall \hist \in \allhist: \hist \ileadsto[e] L_D ⇔ [\ar_e \in R(\hist)]$, and $\hist \ileadsto[e] L_P$ otherwise.
+Note that in particular, if $\hist$ contains $\ar$ but not $\ar_e$, $\ar \ileadsto[e] L_P$, as we assume such individuals are confused by the longer argument $\ar$ referring to abstract notions and therefore opt for $L_P$, falling back to the common psychological bias.
+The second kind of individuals is represented by $\ileadsto[u]$ defined as $\forall \hist \in \allhist: \hist \ileadsto[u] L_D ⇔ [\ar_u \notin R(\hist) \lor \ar \in R(\hist) \lor \set{\ar_u, \ar_l} \subseteq R(\hist)]$, and $\hist \ileadsto[u] L_P$ otherwise.
+We assume here that such individuals think about $\ar_u$ as a correct argument in favor of $L_P$ until shown the rebuttal $\ar_l$ (or $\ar$, which contains a similar rebuttal).
 Assuming finally $\allleadsto$ as equal to $\ileadsto[e]$ for individuals of the first kind and $\ileadsto[u]$ otherwise concludes the definition of the exposure protocol $(I, \allargs, {\allleadsto})$.
 
-It follows from this definition that $\forall i \in I: \prop_D \in \iprops$, and that no static theory of that exposure protocol is truthful: only $\ar_e$ is a decisive argument for $\prop_D$ for the first kind of individuals whereas for the second kind, only $\ar$ is.
+It follows from this definition that $\forall i \in I: L_D \in P_i$, and that no static theory of that exposure protocol is truthful: only $\ar_e$ is a decisive argument for $L_D$ for the first kind of individuals whereas for the second kind, only $\ar$ is.
 \end{example}

### 2022-10-24 simple.tex
Typesetting and reworded def equivalently

@@
 
-Define $\ar_e$ as a text arguing that the choice between $L_P$ and $L_D$ should be determined by their expected revenue, namely, $\$3.959$ for $L_P$ and $\$4$ for $L_D$.
+Define $\ar_e$ as a text arguing that the choice between $L_P$ and $L_D$ should be determined by their expected revenue, namely, $\$3.959$ for $L_P$ and $\$4$ for $L_D$.%
 \footnote{Here is a possible text for $\ar_e$.
@@
 [Similar text for $L_D$.] Therefore, we suggest you choose $L_D$ for a higher expected revenue.”}
-Define $\ar_u$ as a text arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain. 
+Define $\ar_u$ as a text arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain.% 
 \footnote{Here is a possible text for $\ar_u$.
@@
 Therefore, we recommend to rather pick $L_P$ as it presents a much better chance of earning money”.}
-Define a counter-argument $\ar_l$ to $\ar_u$, indicating that for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.
+Define a counter-argument $\ar_l$ to $\ar_u$, indicating that for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.%
 \footnote{Here is a possible text for $\ar_l$.
 “The lottery $L_D$ has a higher expected revenue, and thus, a higher utility than $L_P$, because for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.”}
-Define $\ar$ so as to include the contents of $\ar_e$, $\ar_u$ and $\ar_l$.
+Define $\ar$ so as to include the contents of $\ar_e$, $\ar_u$ and $\ar_l$.%
 \footnote{Here is a possible text for $\ar$.
@@
 
-To define this formally, note that either $\arga$ is a decisive argument for $\pga$, or some paths challenge this claim, namely those in $\set{\hist \in \allhist \suchthat \arga \in \histend \land \hist \nileadsto \pga}$.
+To define this formally, note that either $\arga$ is a decisive argument for $\pga$, or some paths challenge this claim, namely those $\hist \in \allhist$ such that $[\arga \in \histend \land \hist \nileadsto \pga]$.
 Generalizing this observation, given $i \in I$, define $\dgi(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \in \histend \land \hist \nileadsto \pga} \subseteq \dg(\ar)$ as the subset of defenders of $\ar$ required for convincing $i$ of choosing $\pga$.
@@
 It is said to be truthful iff this claim is correct.
-More precisely, its claims are about paths of the sort $\hist = (\arga, …, \ar_2, …, \ar_3, …)$ where $\ar_2 \in \dgi(\arga)$, $\ar_3 \in \dgi(\ar_2)$, … The following definition makes this precise.
+More precisely, its claims are about paths $\hist$ containing ${\arga, \ar_2, \ar_3, …, \ar_k}$ where $\ar_2 \in \dgi(\arga)$, $\ar_3 \in \dgi(\ar_2)$, …, $\ar_k \in \histend$.
+The following definition makes this precise.
 \begin{definition}[Truthfulness]
 	\label{def:truth}
-	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, k \in \N^*, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist \in \allhist \suchthat [\ar_1 = \arga \land \ar_k \in \histend \land d(\ar_k, \hist) = \emptyset \land \forall j \in \intvl{1, k}: \ar_j \in R(\hist) \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1})]: [\hist \ileadsto \pga]$.
+	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, k \in \N^*, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist \in \allhist \suchthat [\ar_1 = \arga \land \ar_k \in \histend \land \forall j \in \intvl{1, k}: \ar_j \in R(\hist) \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1}) \land \hist \nileadsto \pga]: [d(\ar_k, \hist) ≠ \emptyset]$.
 \end{definition}
@@
 This definition of truthfulness is adopted because of our goal of distinguishing empirical claims.
-Truthfulness, so defined, can be falsified empirically: if any of the set of claims embedded in this definition does not hold, it is possible to determine this empirically.
+Truthfulness, so defined, can be falsified empirically: if it does not hold, it is possible to prove this empirically by exhibiting a counter-example in the form of a tuple $i, k, (a_j)_{j \in \intvl{1, k}}, \alpha$ such that TODO.
 
-Note that a static theory $(p, \ar)$ can be considered as an argumentative theory $(p, \ar, \emptyset)$, and is truthful in the sense of \cref{sec:static} iff $(p, \ar, \emptyset)$ is truthful in the sense of \cref{def:truth}.
+Note that a static theory $(p, \ar)$ can be considered as an argumentative theory $(p, \ar, \emptyset)$, and $(p, \ar)$ is truthful in the sense of \cref{sec:static} iff $(p, \ar, \emptyset)$ is truthful in the sense of \cref{def:truth}.
 

### 2022-10-26 simple.tex
Complicated remarks about shortcoming of this simple approach

@@
 	\label{def:truth}
-	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, k \in \N^*, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist \in \allhist \suchthat [\ar_1 = \arga \land \ar_k \in \histend \land \forall j \in \intvl{1, k}: \ar_j \in R(\hist) \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1}) \land \hist \nileadsto \pga]: [d(\ar_k, \hist) ≠ \emptyset]$.
+	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, k \in \N^*, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist \in \allhist \suchthat [\forall j \in \intvl{1, k}: \ar_j \in R(\hist) \land \ar_k \in \histend \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1}) \land \hist \nileadsto \pga]: [d(\ar_k, \hist) ≠ \emptyset]$.
 \end{definition}
+
+\begin{remark}
+	There is a problem. First, truthfulness must be reduced as we can empirically only test $(a_1, a_5, a_2)$ when $a_2$ defends $a_1$ \emph{because of $a_5$} (not because of something else).
+	Second, consider the following may hold for some $i$.
+$a_1, a_5, a_2$ not convincing, $a_1, a_4$ not convincing, whil $a_1, a_5$ and $a_1, a_4, a_2$ and other variants convincing.
+Then for all $i$ one of $a_1$ or $a_2$ will appear to be decisive although for those people neither is.
+
+	Problem might be solved by observing that $(a_1, a_5, a_2, a_1)$ convincing means that $a_1$ is decisive after all; and not convincing means that we have observed not truthfulness.
+\end{remark}
+\begin{remark}
+	We want that if the theory is invalid (thus some $i$ is not convinced), then either axiom fails or the theory is experimentally falsifiable.
+	In the following example, the theory seems invalid but the axiom holds and the theory can’t seem to be defeated experimentally.
+
+	Imagine $i$ thinks as follows.
+$a_1$ counter $a_5$; $a_2$ counters $a_4$; but $a_4$ and $a_5$ together make $a_1$ and $a_2$ invalid, so that $(a_4, a_5)$ counter both $a_1$ and $a_2$ (and also $a_1$ and $a_2$ together).
+Also assume that $i$ has short memory so that $a_1, a_4, a_5$ does not convince ($a_4$ and $a_5$ win) while $a_4, a_5, a_1$ do ($a_1$ wins as $a_4$ is too far away).
+BUT $a_5, a_4, a_1$ should then not convince.
+
+	Path is convincing depending only the last two arguments (unordered): $\set{(a_1, a_5), (a_2, a_4), (a_1, a_2)}$ are convincing; $\set{(a_1, a_4), (a_2, a_5), (a_4, a_5)}$ are not.
+	\begin{description}
+		\item[$(a_1, a_2, a_4, a_5)$] $\nileadsto p$
+		\item[$(a_1, a_2, a_5, a_4)$] $\nileadsto p$
+		\item[$(a_1, a_4, a_2, a_5)$] $\nileadsto p$
+		\item[$(a_1, a_4, a_5, a_2)$] $\nileadsto p$
+		\item[$(a_1, a_5, a_2, a_4)$] $\ileadsto p$
+		\item[$(a_1, a_5, a_4, a_2)$] $\ileadsto p$
+		\item[$(a_2, a_1, a_4, a_5)$] $\nileadsto p$
+		\item[$(a_2, a_1, a_5, a_4)$] $\nileadsto p$
+		\item[$(a_2, a_4, a_1, a_5)$] $\ileadsto p$
+		\item[$(a_2, a_4, a_5, a_1)$] $\ileadsto p$
+		\item[$(a_2, a_5, a_1, a_4)$] $\nileadsto p$
+		\item[$(a_2, a_5, a_4, a_1)$] $\nileadsto p$
+		\item[$(a_4, a_1, a_2, a_5)$] $\nileadsto p$
+		\item[$(a_4, a_1, a_5, a_2)$] $\nileadsto p$
+		\item[$(a_4, a_2, a_1, a_5)$] $\ileadsto p$
+		\item[$(a_4, a_2, a_5, a_1)$] $\ileadsto p$
+		\item[$(a_4, a_5, a_1, a_2)$] $\ileadsto p$
+		\item[$(a_4, a_5, a_2, a_1)$] $\ileadsto p$
+		\item[$(a_5, a_1, a_2, a_4)$] $\ileadsto p$
+		\item[$(a_5, a_1, a_4, a_2)$] $\ileadsto p$
+		\item[$(a_5, a_2, a_1, a_4)$] $\nileadsto p$
+		\item[$(a_5, a_2, a_4, a_1)$] $\nileadsto p$
+		\item[$(a_5, a_4, a_1, a_2)$] $\ileadsto p$
+		\item[$(a_5, a_4, a_2, a_1)$] $\ileadsto p$
+	\end{description}
+	It follows that no argument is decisive.
+	The axiom' fails as $(a_4, a_1, a_5, a_2) \nileadsto p$ but $(a_4, a_1, a_5, a_4, a_2) \ileadsto p$!
+
+	Let’s treat $a_1$ as including $a_5$ and $a_2$ as including $a_4$.
+
+	Ends with $a_1$ and $a_2$: convincing. Ends with only $a_1$: convincing. Ends with $a_1$ and $a_4$: no. Ends with $a_2$ and $a_5$: no.
+	\begin{description}
+		\item[$(a_1, a_2, a_4, a_5)$] $\ileadsto p$
+		\item[$(a_1, a_2, a_5, a_4)$] $\ileadsto p$
+		\item[$(a_1, a_4, a_2, a_5)$] $\nileadsto p$
+		\item[$(a_1, a_4, a_5, a_2)$] $\nileadsto p$
+		\item[$(a_1, a_5, a_2, a_4)$] $\nileadsto p$
+		\item[$(a_1, a_5, a_4, a_2)$] $\nileadsto p$
+		\item[$(a_2, a_1, a_4, a_5)$] $\nileadsto p$
+		\item[$(a_2, a_1, a_5, a_4)$] $\nileadsto p$
+		\item[$(a_2, a_4, a_1, a_5)$] $\ileadsto p$
+		\item[$(a_2, a_4, a_5, a_1)$] $\ileadsto p$
+		\item[$(a_2, a_5, a_1, a_4)$] $\nileadsto p$
+		\item[$(a_2, a_5, a_4, a_1)$] $\nileadsto p$
+		\item[$(a_4, a_1, a_2, a_5)$] $\nileadsto p$
+		\item[$(a_4, a_1, a_5, a_2)$] $\nileadsto p$
+		\item[$(a_4, a_2, a_1, a_5)$] $\ileadsto p$
+		\item[$(a_4, a_2, a_5, a_1)$] $\ileadsto p$
+		\item[$(a_4, a_5, a_1, a_2)$] $\ileadsto p$
+		\item[$(a_4, a_5, a_2, a_1)$] $\ileadsto p$
+		\item[$(a_5, a_1, a_2, a_4)$] $\ileadsto p$
+		\item[$(a_5, a_1, a_4, a_2)$] $\ileadsto p$
+		\item[$(a_5, a_2, a_1, a_4)$] $\nileadsto p$
+		\item[$(a_5, a_2, a_4, a_1)$] $\nileadsto p$
+		\item[$(a_5, a_4, a_1, a_2)$] $\ileadsto p$
+		\item[$(a_5, a_4, a_2, a_1)$] $\ileadsto p$
+	\end{description}
+	It follows that no argument is decisive.
+\end{remark}
 

### 2022-10-31 simple.tex
Towards better axioms

--- 2022-10-24 simple.tex
@@
 It is said to be truthful iff this claim is correct.
-More precisely, its claims are about paths $\hist$ containing ${\arga, \ar_2, \ar_3, …, \ar_k}$ where $\ar_2 \in \dgi(\arga)$, $\ar_3 \in \dgi(\ar_2)$, …, $\ar_k \in \histend$.
-The following definition makes this precise.
+The following definition makes this precise.%
+\footnote{To be fixed.
+If $a_1$, used by the theory, is not decisive, then the theory has an answer, namely, $a_2$, which works at least temporarily.}
 \begin{definition}[Truthfulness]
 	\label{def:truth}
-	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, k \in \N^*, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist \in \allhist \suchthat [\ar_1 = \arga \land \ar_k \in \histend \land \forall j \in \intvl{1, k}: \ar_j \in R(\hist) \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1}) \land \hist \nileadsto \pga]: [d(\ar_k, \hist) ≠ \emptyset]$.
+	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, \hist \in \allhist, \ar \in \histend, \ar_1 \in \histend: [\hist \nileadsto \pga] ⇒ [\dg(\ar_1, \hist) ≠ \emptyset \land (\hist, \dg(\ar_1, \hist)) \ileadsto \pga]$.
 \end{definition}
+\begin{axiom}[Answerability]
+	\label{ax:ans}
+	$\forall \ar, \ar': [\exists \hist \suchthat (\hist, \ar, \ar') \nileadsto \pga \land \exists \hist \suchthat (\hist, \ar, \ar') \ileadsto \pga] ⇒ \exists \hist, \ar_c \suchthat (\hist, \ar, \ar', \ar_c) \nileadsto \pga$.
+\end{axiom}
+\footnote{$a_1, a_2, a_3$ NOT and $a_1, a_2, a_3, a_4$ YES and $a_1', a_2, a_3, a_4$ NO imply that $a_1, a_2, a_3, a_4, a'_1$ NO.
+Generalizing: $\alpha$ NO and $\alpha, a_4$ YES and $\alpha', a_4$ NO imply that $\exists a' \in \alpha' \suchthat \alpha, a_4, a'$ NO.
+Let’s try with this too powerful axiom, but then we should weaken it, as it could be that $a_1$ AND $a_4$ TOGETHER are decisive, whence the axiom fails.
+We should have then some argument $a_1 + a_4$ to replace them, and…?}
+\begin{axiom}[Reinstatement]
+	\label{ax:r}
+	$\forall \hist, \ar_1 \in \gargsi: [(\hist, a_1, a) \nileadsto p \land (\hist, a_1, a, a_2, …) \ileadsto p] ⇒ [(\hist, a_2) \ileadsto p \land \forall \hist': (\hist', a_2, a') \ileadsto p ⇒ (\hist', a_1, a') \nileadsto p]$.
+\end{axiom}
+\begin{example}[No reinstatement]
+	Reinstatement is required. Consider $a_1$ not decisive because of $a$ and then $(a_1, a, a_2) \ileadsto p$. But still $a_2$ not decisive: $a2 \nileadsto p$.
+\end{example}
+\begin{theorem}[Validity]
+	If an argumentative theory $(\pga, \arga, \dg)$ is truthful and $\allargs$ is finite, then \cref{ax:ans,ax:r} imply that the theory is correct.
+\end{theorem}
+\begin{proof}[Sketch of proof]
+	Consider any $i$. We have to show that $\pga \in \Phi_i$.%
+	\footnote{Assume $(a_4, \arga, a) \nileadsto \pga$ (thus, $a$ attacks $\arga$). 
+	By tf, $(a_4, \arga, a, \ar_2, …) \ileadsto \pga$.
+	We get $(a_3, \arga, a, \ar_2) \ileadsto \pga$ by answ.
+	By reinst: $(\ar_2)$ YES.}
+
+	Assume that $\arga$ is not decisive (otherwise, done). Thus, for some $\hist: (\hist, \arga, \ar) \nileadsto \pga$ or $(\hist, \ar, \arga)$.
+	Consider that $\hist: (\hist, \arga, \ar) \nileadsto \pga$.
+	Consider $\hist'$ and wonder whether $(\hist', \arga, \ar) \ileadsto \pga$. If so, 	
+	By Answ, this means that $\forall \hist, (\hist, \arga, \ar) \nileadsto \pga$.
+	By truthfulness, $\ar_2 = \dg(\ar_1, (\hist, \arga, \ar)) ≠ \emptyset \land (\hist, \arga, \ar, \ar_2) \ileadsto \pga$.
+	Assume now that $(\hist, \arga, \ar, \ar_2, …) \ileadsto \pga$.
+	Then by Reinstatement, $(\hist, \ar_2) \ileadsto \pga$.
+
+%	Assume, to start with, that the theory is of depth 2, more precisely, $\arga$ is not decisive because $\hist \nileadsto \pga, \arga \in \histend$ and $\dgi(\arga) = \ar_2$ with no further hist against it.
+\end{proof}
 

### 2022-11-01 simple.tex
Attempt more precise Tf

@@
 A generic element of $\allhist$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path. Its length is denoted by $\card{\hist} \in \N$.
-Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}: \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
+Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}: \hist(k) = \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
 
@@
 \footnote{To be fixed.
-If $a_1$, used by the theory, is not decisive, then the theory has an answer, namely, $a_2$, which works at least temporarily.}
+If $a_1$, used by the theory, is not decisive, then the theory has an answer, namely, $a_2$, which works at least temporarily.
+If $a_1$ used by th is not dec, and $a_2$ used by th is not dec *in the same sequence*, then $a_3$ needs to defend *in the same sequence*.
+$(…, a_1)$ NO and $(…, a_1, …, a_2)$ NO then $a_3$ defends it.
+$\alpha$ of the form $(\alpha^1, \alpha^2)$ where $a_1$ in end of $α^1$ NO and $a_2$ in end of $α^2$ NO.}
+In the following definition, $(\hist^1, …, \hist^j, …, \hist^n)$ represent the sequence $\hist^1$ to which is suffixed the sequence $\hist^2$ and so on.
 \begin{definition}[Truthfulness]
 	\label{def:truth}
-	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff $\forall i \in I, \hist \in \allhist, \ar \in \histend, \ar_1 \in \histend: [\hist \nileadsto \pga] ⇒ [\dg(\ar_1, \hist) ≠ \emptyset \land (\hist, \dg(\ar_1, \hist)) \ileadsto \pga]$.
+	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff 
+	$\forall i \in I, \hist \in \allhist \suchthat 
+	k_j \in \intvl{1, \card \hist} \land
+	\hist^j = (\hist_1, …, \hist_{k_j}) \land
+	\forall j: [k_{j - 1} < k_j \land \hist^j \nileadsto \pga \land \ar_1 = \arga \land \ar_j \in \histend[j] \land \ar_{j + 1} = \dg(\ar_j, \hist^j)]: (\hist, \ar_{n + 1}) \ileadsto \pga]$.
 \end{definition}

### 2022-11-01 simple.tex
Better TF

@@
 It is said to be truthful iff this claim is correct.
-The following definition makes this precise.%
-\footnote{To be fixed.
+More precisely, its claims are about paths of the sort $\hist = (\arga, …, \ar_2, …, \ar_3, …)$ where $\ar_2 \in \dgi(\arga)$, $\ar_3 \in \dgi(\ar_2)$, …
+The following definition makes this precise by mandating that whenever increasing subsequences of $\hist$, involving arguments $\ar_j$ proposed by the theory, are not convincing, then the theory is able to produce yet another argument in defense of its claim.%
+\footnote{Intuition.
 If $a_1$, used by the theory, is not decisive, then the theory has an answer, namely, $a_2$, which works at least temporarily.
@@
 $\alpha$ of the form $(\alpha^1, \alpha^2)$ where $a_1$ in end of $α^1$ NO and $a_2$ in end of $α^2$ NO.}
-In the following definition, $(\hist^1, …, \hist^j, …, \hist^n)$ represent the sequence $\hist^1$ to which is suffixed the sequence $\hist^2$ and so on.
 \begin{definition}[Truthfulness]
@@
 	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff 
-	$\forall i \in I, \hist \in \allhist \suchthat 
-	k_j \in \intvl{1, \card \hist} \land
-	\hist^j = (\hist_1, …, \hist_{k_j}) \land
-	\forall j: [k_{j - 1} < k_j \land \hist^j \nileadsto \pga \land \ar_1 = \arga \land \ar_j \in \histend[j] \land \ar_{j + 1} = \dg(\ar_j, \hist^j)]: (\hist, \ar_{n + 1}) \ileadsto \pga]$.
+	$\forall i \in I, \hist \in \allhist, n \in \N, k \in \intvl{1, \card \hist}^n, \ar \in \allargs^n$:
+	\begin{equation}
+		\left.\begin{aligned}
+			&\ar_1 = \arga \\
+			&\forall 1 ≤ j < n: \ar_{j + 1} = \dg(\ar_j, α_{\intvl{1, k_j}}) \in \histbend{k_{j + 1}} \\
+			&\forall 1 ≤ j ≤ n: \hist_{\intvl{1, k_j}} \nileadsto \pga
+		\end{aligned}\right\}
+		⇒ \dg(\ar_n, \hist) ≠ \emptyset.
+	\end{equation}
 \end{definition}

### 2022-11-17 simple.tex
Var

@@
 	\label{ax:ans}
-	$\forall \ar, \ar': [\exists \hist \suchthat (\hist, \ar, \ar') \nileadsto \pga \land \exists \hist \suchthat (\hist, \ar, \ar') \ileadsto \pga] ⇒ \exists \hist, \ar_c \suchthat (\hist, \ar, \ar', \ar_c) \nileadsto \pga$.
+	$\forall i \in I, \hist \in \allhist, \ar \in \gargsi$:
+	\begin{equation}
+		\left.\begin{aligned}
+			&\hist \nileadsto \pga \\
+			&(\hist, \ar) \ileadsto \pga \\
+			&\forall \ar' \in \allargs: (\hist, \ar, \ar') \ileadsto \pga
+		\end{aligned}\right\}
+		⇒ \ar \ileadstost \pga.
+	\end{equation}
 \end{axiom}
@@
 Let’s try with this too powerful axiom, but then we should weaken it, as it could be that $a_1$ AND $a_4$ TOGETHER are decisive, whence the axiom fails.
-We should have then some argument $a_1 + a_4$ to replace them, and…?}
+We should have then some argument $a_1 + a_4$ to replace them, and…?
+In summary, we want to avoid that $a$ is not decisive but we can’t observe it when starting with some $α$ even though $α$ has also no decisive arguments: if $α$ has no decisive argument, then it must be possible to counter it.
+
+In fact, we might need (a weakening of) the following.
+If $a_1$ is “decisive” when starting with some $α$ (meaning $(α, a_1, a')$ YES for all arguments $a'$), then $a_1$ is decisive.
+Hopefully: if $(α, a')$ YES for all arguments $a'$, then some $a \in α$ is decisive.}
+\footnote{
+	There is a problem.
+Consider the following may hold for some $i$.
+$a_1, a_5, a_2$ not convincing, $a_1, a_4$ not convincing, whil $a_1, a_5$ and $a_1, a_4, a_2$ and other variants convincing.
+Then for all $i$ one of $a_1$ or $a_2$ will appear to be decisive although for those people neither is.
+
+	Problem might be solved by observing that $(a_1, a_5, a_2, a_1)$ convincing means that $a_1$ is decisive after all; and not convincing means that we have observed not truthfulness.
+
+	We want that if the theory is invalid (thus some $i$ is not convinced), then either axiom fails or the theory is experimentally falsifiable.
+	In the following example, the theory seems invalid but the axiom holds and the theory can’t seem to be defeated experimentally.
+
+	Imagine $i$ thinks as follows.
+$a_1$ counter $a_5$; $a_2$ counters $a_4$; but $a_4$ and $a_5$ together make $a_1$ and $a_2$ invalid, so that $(a_4, a_5)$ counter both $a_1$ and $a_2$ (and also $a_1$ and $a_2$ together).
+Also assume that $i$ has short memory so that $a_1, a_4, a_5$ does not convince ($a_4$ and $a_5$ win) while $a_4, a_5, a_1$ do ($a_1$ wins as $a_4$ is too far away).
+BUT $a_5, a_4, a_1$ should then not convince.
+}
+
 \begin{axiom}[Reinstatement]
 	\label{ax:r}
-	$\forall \hist, \ar_1 \in \gargsi: [(\hist, a_1, a) \nileadsto p \land (\hist, a_1, a, a_2, …) \ileadsto p] ⇒ [(\hist, a_2) \ileadsto p \land \forall \hist': (\hist', a_2, a') \ileadsto p ⇒ (\hist', a_1, a') \nileadsto p]$.
+	$\forall i \in I, \hist \in \allhist, \ar_1, \ar_2 \in \gargsi, \ar \in \allargs$:
+	\begin{equation}
+		\left.\begin{aligned}
+			&(\hist, \ar_1, \ar) \nileadsto \pga \\
+			&(\hist, \ar_1, \ar, \ar_2) \ileadsto \pga \\
+			&(\hist, \ar_1, \ar, \ar_2, \ar) \ileadsto \pga
+		\end{aligned}\right\}
+		⇒ 
+		\left\{\begin{aligned}
+			&(\hist, \ar_2) \ileadsto \pga \\
+			&(\hist, \ar_2, \ar) \ileadsto \pga \\
+			&\forall \ar': (\hist, a_2, a') \nileadsto \pga ⇒ (\hist, a_1, a') \nileadsto \pga.
+		\end{aligned}\right.
+	\end{equation}
 \end{axiom}
-\begin{example}[No reinstatement]
-	Reinstatement is required. Consider $a_1$ not decisive because of $a$ and then $(a_1, a, a_2) \ileadsto p$. But still $a_2$ not decisive: $a2 \nileadsto p$.
+\begin{example}[Reinstatement is required]
+	Consider $a_1$ not decisive because of $a$ and then $(a_1, a, a_2) \ileadsto p$. But still $a_2$ not decisive: $a2 \nileadsto p$.
 \end{example}
+
+\begin{axiom}[Self-sufficiency of positive arguments, version for $\ar$]
+	$\forall \ar_1, \ar_2 \in \gargsi, \ar \in \allargs, \hist \in \allhist$:
+	\begin{equation}
+		\left.\begin{aligned}
+			&(\hist, \ar_1, \ar) \nileadsto \pga \\
+			&(\hist, \ar_2, \ar) \nileadsto \pga
+		\end{aligned}\right\}
+		⇒ (\hist, \ar_1, \ar_2, \ar) \nileadsto \pga,
+	\end{equation}
+	and, $\forall \ar_1, \ar_2 \in \gargsi, \hist \in \allhist$:
+	\begin{equation}
+		\left.\begin{aligned}
+			&(\hist, \ar_1) \nileadsto \pga \\
+			&(\hist, \ar_2) \nileadsto \pga
+		\end{aligned}\right\}
+		⇒ (\hist, \ar_1, \ar_2) \nileadsto \pga.
+	\end{equation}
+\end{axiom}
+
 \begin{theorem}[Validity]
-	If an argumentative theory $(\pga, \arga, \dg)$ is truthful and $\allargs$ is finite, then \cref{ax:ans,ax:r} imply that the theory is correct.
+	If an argumentative theory $(\pga, \arga, \dg)$ is truthful and satisfy \cref{ax:ans,ax:r} and $\allargs$ is finite, then the theory is correct.
 \end{theorem}
+\begin{proof}
+	Consider any $i \in I$.
+	We have to show that $\pga \in \Phi_i$.
+	Assume depth $3$.
+	Assume that $\arga$ and $\ar_2$ are not decisive. Let’s show that $\ar_3$ is decisive.
+	Assume that $(a_4, \arga, \ar_2, a) \nileadsto \pga$.
+	By TF, $(a_4, \arga, \ar_2, a, \ar_3, ?) \ileadsto \pga$ (where $?$ stands for any argument or nothing).
+	By Reinst, $(a_4, \arga, \ar_3, ?) \ileadsto \pga$.
+	By Self-s, $(a_4, \ar_3, ?) \ileadsto \pga$.
+
+	Now consider $(\ar_5, \ar_2) \ileadsto \pga$. (Or any such path not ending with $\ar_3$.)
+	By Answ, $\exists a \suchthat (\ar_5, \ar_2, a) \nileadsto \pga$.
+	We obtain $(\ar_5, \ar_3) \ileadsto \pga$.
+\end{proof}
 \begin{proof}[Sketch of proof]

### 2022-11-17 simple.tex
Self-suff using decisive paths (and such def)

@@
 Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence. 
-A generic element of $\allhist$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path. Its length is denoted by $\card{\hist} \in \N$.
+A generic element of $\allhist$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path.
+Its length is denoted by $\card{\hist} \in \N$ and its elements, $\hist(k)$ or $\hist_k$.
 Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}: \hist(k) = \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
@@
 \end{definition}
+Given the paths $\alpha, \alpha'$, the sequence $(\alpha, \alpha')$ denotes a path constituted of the arguments in $\alpha$ followed by the arguments of $\alpha'$.
 \begin{axiom}[Answerability]
@@
 
-\begin{axiom}[Self-sufficiency of positive arguments, version for $\ar$]
+A path can be shortened to its first $k \in \intvl{0, \card{\hist}}$ elements, which is denoted by $\restr{\hist}{\intvl{1, k}}$, and “shortening” a path beyond its length yields the same path again, thus given $k \in \N$, $\restr{\hist}{\intvl{1, k}} = \restr{\hist}{\intvl{1, \min\set{\card{\hist}, k}}}$.
+Define a path as being decisive for $p$, $\hist \ileadstost p$, iff $\hist \ileadsto p \land \forall \ar \in \allargs: (\hist, \ar) \ileadsto p$, or equivalently, iff $\forall \hist' \suchthat \card{\hist} ≤ \card{\hist'} ≤ \card{\hist} + 1 \land \restr{\hist'}{\intvl{1, \card{\hist}}} = \hist: \hist' \ileadsto p$.
+Thus, $\hist \nileadstost p ⇔ \exists \ar \in \allargs \suchthat (\hist, \ar) \nileadsto p$.
+
+\begin{axiom}[Self-sufficiency of positive arguments]
 	$\forall \ar_1, \ar_2 \in \gargsi, \ar \in \allargs, \hist \in \allhist$:
@@
 		\left.\begin{aligned}
-			&(\hist, \ar_1, \ar) \nileadsto \pga \\
-			&(\hist, \ar_2, \ar) \nileadsto \pga
+			&(\hist, \ar_1) \nileadstost \pga \\
+			&(\hist, \ar_2) \nileadstost \pga
 		\end{aligned}\right\}
-		⇒ (\hist, \ar_1, \ar_2, \ar) \nileadsto \pga,
-	\end{equation}
-	and, $\forall \ar_1, \ar_2 \in \gargsi, \hist \in \allhist$:
-	\begin{equation}
-		\left.\begin{aligned}
-			&(\hist, \ar_1) \nileadsto \pga \\
-			&(\hist, \ar_2) \nileadsto \pga
-		\end{aligned}\right\}
-		⇒ (\hist, \ar_1, \ar_2) \nileadsto \pga.
+		⇒ (\hist, \ar_1, \ar_2) \nileadstost \pga.
 	\end{equation}

### 2022-11-24 simple.tex
More attempts of Answ

@@
 			&\forall 1 ≤ j < n: \ar_{j + 1} = \dg(\ar_j, α_{\intvl{1, k_j}}) \in \histbend{k_{j + 1}} \\
-			&\forall 1 ≤ j ≤ n: \hist_{\intvl{1, k_j}} \nileadsto \pga
+			&\forall 1 ≤ j ≤ n: \restr{\hist}{\intvl{1, k_j}} \nileadsto \pga
 		\end{aligned}\right\}
@@
 Given the paths $\alpha, \alpha'$, the sequence $(\alpha, \alpha')$ denotes a path constituted of the arguments in $\alpha$ followed by the arguments of $\alpha'$.
+\begin{axiom}[Answerability-1]
+	$\forall …$:
+	\begin{equation}
+		\left.\begin{aligned}
+			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
+			&(\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
+			&(\ar_5, \ar_2, \ar) \nileadsto \pga
+		\end{aligned}\right\}
+		⇒ (\ar_5, \ar_2, \ar, \ar_3) \ileadstost \pga.
+	\end{equation}
+\end{axiom}
+Requires excluding:
+	\begin{equation}
+		\left.\begin{aligned}
+			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
+			&(\ar_4, \ar_2, \ar, \ar_3, \ar') \ileadsto \pga \\
+			&(\ar_5, \ar_2, \ar) \nileadsto \pga\\
+			&(\ar_5, \ar_2, \ar, \ar_3, \ar') \nileadsto \pga.
+		\end{aligned}\right\}
+	\end{equation}
+
+To exclude:
+	\begin{equation}
+		\left.\begin{aligned}
+			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
+			&(\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
+			&(\ar_5, \ar_2, \ar) \ileadsto \pga\\
+			&(\ar_5, \ar_2, \ar_3, \ar') \nileadsto \pga
+		\end{aligned}\right\}
+	\end{equation}
+Using:
+	\begin{equation}
+		\left.\begin{aligned}
+			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
+			&(\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
+			&(\ar_5, \ar_2, \ar) \ileadsto \pga
+		\end{aligned}\right\}
+		⇒ (\ar_5, \ar_2, \ar_3) \ileadstost \pga.
+	\end{equation}
+
 \begin{axiom}[Answerability]
@@
 
+\begin{axiom}[Answerability - using newly built arguments (newest so far)]
+	\label{ax:ansn}
+	$\forall i \in I, \hist^j \in (\allhist)^n$:
+	\begin{equation}
+		[\forall j: \hist^j \ileadstost \pga] ⇒ [\exists \ar \in \allargs \suchthat \forall j: (\hist^j, \ar) \ileadstost \pga].
+	\end{equation}
+\end{axiom}
+
 \begin{axiom}[Reinstatement]
@@
 Define a path as being decisive for $p$, $\hist \ileadstost p$, iff $\hist \ileadsto p \land \forall \ar \in \allargs: (\hist, \ar) \ileadsto p$, or equivalently, iff $\forall \hist' \suchthat \card{\hist} ≤ \card{\hist'} ≤ \card{\hist} + 1 \land \restr{\hist'}{\intvl{1, \card{\hist}}} = \hist: \hist' \ileadsto p$.
-Thus, $\hist \nileadstost p ⇔ \exists \ar \in \allargs \suchthat (\hist, \ar) \nileadsto p$.
+Thus, $\hist \nileadstost p ⇔ \exists \ar \in \allargs \suchthat (\hist, \ar) \nileadsto p$ (or…?).
 
@@
 	Assume that $(a_4, \arga, \ar_2, a) \nileadsto \pga$.
-	By TF, $(a_4, \arga, \ar_2, a, \ar_3, ?) \ileadsto \pga$ (where $?$ stands for any argument or nothing).
-	By Reinst, $(a_4, \arga, \ar_3, ?) \ileadsto \pga$.
-	By Self-s, $(a_4, \ar_3, ?) \ileadsto \pga$.
+	By TF, $(a_4, \arga, \ar_2, a, \ar_3) \ileadstost \pga$.
+	By Reinst, $(a_4, \arga, \ar_2, \ar_3) \ileadstost \pga$.
+	By Self-s, $(a_4, \arga, \ar_3) \ileadstost \pga$.
+	By Self-s, $(a_4, \ar_3) \ileadstost \pga$.
 
 	Now consider $(\ar_5, \ar_2) \ileadsto \pga$. (Or any such path not ending with $\ar_3$.)
+	We want $(\ar_5, \ar_2, \ar_3) \ileadstost \pga$.
 	By Answ, $\exists a \suchthat (\ar_5, \ar_2, a) \nileadsto \pga$.
-	We obtain $(\ar_5, \ar_3) \ileadsto \pga$.
 \end{proof}

### 2023-06-02 simple.tex
Introduced then revised depth using iterated defense

@@
 This permits to study deliberated judgments empirically, meaning here that disagreements about someone’s deliberated judgment in a given context can be solved, at least in principle, by an empirical experiment, provided the very conception of what constitutes a deliberated judgment is shared.
-This article is interested in defining the concept of deliberated judgement of a subject and show how one can study it in an emprical manner.
+This article is interested in defining the concept of deliberated judgement of a subject and show how one can study it in an empirical manner.
 The “classical” counterpart of deliberated judgments,, that does not involve confrontation with arguments, will henceforth be called the natural judgment.
@@
 
-While the concept of deliberation in the deliberative democracy literature usually refers to multiple individuals debating, this article considers deliberation as related to a single individual at a time: an individual deliberates (in the sense of: carefully weights) the stance she considers most appropriate while being confronted to arguments.
-The deliberated judgment of an individual is thus defined with no requirement that the arguments be uttered by peers in a debate; they can be given by an automata, for example.
+While the concept of deliberation in the deliberative democracy literature usually refers to multiple individuals debating, this article considers deliberation as related to a single individual: an individual deliberates (in the sense of: carefully weights) the stance she considers most appropriate while being confronted to arguments.
+The deliberated judgment of an individual is thus defined with no requirement that the arguments be uttered by peers in a debate; they can be given by an automaton, for example.
 In this sense, deliberated judgments come close to what \citet{rawls_theory_1999} calls reflective equilibrium (referring to an idea of \citet{goodman_fact_1983}), a concept that has much inspired the present proposal.
@@
 This is methodologically similar to defining theories of how objects break.
-One can test only one way of breaking a given (unrepairable) object, so such theories must apply to sets of objects if one wants to be able to test multiple ways of falsifying the theories.
+One can break a given (unrepairable) object only once, so such theories must apply to sets of objects if one wants to be able to test multiple ways of falsifying the theories.
 
@@
 \subsection{Exposure protocol}
-An exposure protocol is a tuple $(I, \allargs, {\allleadsto})$, where $I$ is a set of individuals, $\allargs$ is a set of arguments, and ${\allleadsto}$ is the behavior of the individuals as a function of the arguments they have been exposed to.
+An exposure protocol is a tuple $(I, \allargs, {\allleadsto})$, where $I$ is a set of individuals, $\allargs$ is a set of arguments, and ${\allleadsto}$, “leads to”, is the behavior of the individuals as a function of the arguments they have been exposed to.
 
@@
 Throughout the article, $\N$ includes zero. %and $\N^* = \N \setminus \set{0}$. 
-Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \N: \intvl{j, 0} = \emptyset$).
+Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \N^*: \intvl{j, 0} = \emptyset$).
 Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence. 
@@
 That is, ${\allleadsto}(i, \alpha) = \phi$ denotes that $i$ chooses the first act after exposure to $\alpha$, ${\allleadsto}(i, \alpha) = ¬\phi$ denotes $i$ choosing the second act and ${\allleadsto}(i, \alpha) = 0$ is used to represent indifference of $i$.
-The notation $\alpha \ileadsto p$ will be used to mean ${\allleadsto}(i, \alpha) = p$, considering ${\ileadsto} \subseteq \allhist × P$ as a binary relation.
+The notation $\alpha \ileadsto p$, pronounced “$\alpha$ leads $i$ to $p$”, will be used to mean ${\allleadsto}(i, \alpha) = p$, considering ${\ileadsto} \subseteq \allhist × P$ as a binary relation.
 As usual with binary relations, $\hist \nileadsto p$ means ${\allleadsto}(i, \alpha) ≠ p$ or equivalently ${\allleadsto}(i, \alpha) \in P \setminus \set{p}$.
@@
 
-Given $i \in I, p \in P, \ar \in \allargs$, define $\ar \ileadstost p$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto p$.
+Given $i \in I, p \in P, \ar \in \allargs$, define $\ar \ileadstost p$, pronounced “$a$ leads definitely $i$ to $p$”, iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto p$.
 When $\ar \ileadstost p$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view given the exposure protocol.
@@
 
-This latter possibility may look unpleasant, but it is a fact that facing some difficult problems, individuals sometimes are undecided, and it is an a priori empirical possibility that the individual remains undecided (or even, becomes \emph{more} undecided) when considering multiple arguments.
+This latter possibility may look unpleasant, but it is a fact that facing some difficult problems, individuals sometimes are undecided, and it is an a priori empirical possibility that the individual remains undecided (or even, \emph{becomes} undecided) when considering multiple arguments.
+Being undecided is not the same state as being decidedly indifferent about two issues, and those states can be distinguished empirically, as we will see.
 
@@
 	Let $I$ be a set of individuals desiring to evaluate two candidates $\set{m_1, m_2}$ for math tutoring.
+	Consider one individual $i \in I$.
 	Let ${\leadsto}(i, a_1)$ represent $i$ being shown a test of candidate $m_1$ wherein $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly.
@@
 
-	If the prediction described in the quote is correct when applied to this modified experiment, then, given $i \in I$, $i$’s deliberated choice is $\prop_2$ because $a_e$ is a decisive argument for $\prop_2$, even though $i$ might have rather chosen $\prop_1$ if given only the arguments $a_1$ and $a_2$ without $a_e$.
+	If the prediction described in the quote applies to $i$, the relation $\ileadsto$ is as follows, $\forall k \in \N^*$ (recall that for $\args \subseteq \allargs$, $\args^k$ represents the set of sequences of length $k$ using arguments from $\args$): $\forall \hist \in \set{a_e}^k, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_1, a_2}^k, \hist \ileadsto \prop_1$; $\forall \hist \in \set{a_1, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_2, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \allargs^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$.
+The values of ${\leadsto}(i, \hist)$ for $\hist = \emptyset$ and for $\hist \in \allargs^k \suchthat a_e \notin \histend$ are undetermined by the prediction, but whatever they are, $a_e$ is a decisive argument for $\prop_2$, hence, $i$’s deliberated choice is $\prop_2$.
 \end{example}
@@
 That the deliberated choice of any individual $i$ is well-defined may be doubtful, as it involves counterfactuals.
-To see this, let $\alpha = (a_1, a_2, a_e)$ designate the argumentative path where the arguments are shown in the order they are described in the example, and let $\alpha' = (a_e, a_2, a_1)$ designate the reverse order.
-The deliberated choice concept is defined so as to not depend on the (arbitrary) order of the arguments shown to $i$: for $\prop \in P_i$, it must be that directing to $i$ the path $\alpha$ or the path $\alpha'$ both lead $i$ to choose $\prop$.
-However, once we have shown $\alpha$ to $i$, we cannot show to her $\alpha'$ (unless assuming $i$ forgets arguments after a while and waiting for sufficiently long, which would create practical and theoretical difficulties).
+To see this, let $\hist = (a_1, a_2, a_e)$ designate the argumentative path where the arguments are shown in the order they are described in \cref{ex:tutor}, and let $\hist' = (a_e, a_2, a_1)$ designate the reverse order.
+The deliberated choice concept is defined so as to not depend on the order of the arguments shown to $i$: for having $\prop \in P_i$, it must be that directing to $i$ the path $\hist$ or the path $\hist'$ both lead $i$ to choose $\prop$.
+However, once we have shown $\hist$ to $i$, we cannot show to her $\hist'$ (unless assuming $i$ forgets arguments after a while and waiting for sufficiently long, which would create practical and theoretical difficulties).
 
-This difficulty is resolved using falsifiable general theories, applicable to $I$ and not solely to a given $i$, so that $\alpha$ can be tested on $i$ and $\alpha'$ on some $i' ≠ i$.
-Indeed, what is needed is a way to make a claim such as the one concluding \cref{ex:tutor}, according to which $a_e$ is a decisive argument, empirically testable.
+This difficulty is resolved using falsifiable general theories, applicable to $I$ and not solely to a given $i$, so that $\hist$ can be tested on $i$ and $\hist'$ on some $i' ≠ i$.
+Indeed, we need a way to empirically test claims such as the one concluding \cref{ex:tutor}, according to which $a_e$ is a decisive argument.
 This is achieved in the next section thanks to theories of deliberated choice.
@@
 A static theory $(p, \ar)$ is said to be truthful iff $\forall i \in I: \ar \ileadstost p$, and to be correct iff $\forall i \in I: p \in P_i$.
-We can then say that such theories are valid, meaning that their truthfulness implies their correctness.
+We can then deduce that such theories are valid, meaning that their truthfulness implies their correctness.
 Let us make this (very simple) result stand out as a theorem, because a parallel will be usefully made with more complicated theories.
@@
 Such theories have the merit of simplicity, but there is a need to design more adaptive theories: in many interesting cases, no single argument will be considered decisive by all individuals in $I$.
-What we need is a way to argue with individuals by reacting to what they consider good arguments.
+We then need theories that argue with individuals by reacting to what they consider good arguments.
 The following section illustrates this need.
@@
 
-In many decision problems, individuals will not be attracted by the same set of arguments and counter-arguments, even though they may finally opt for the same alternative.
+In many decision problems, individuals will not be attracted by the same set of arguments and counter-arguments, even though they may finally settle to the same preference.
 Imagine that some individual $i_1$ considers an argument $a_1$ for $\nprop$ relevant and some individual $i_2$ considers an argument $a_2$ for $\nprop$ relevant, but $i_1$ does not consider $a_2$ relevant and $i_2$ does not consider $a_1$ relevant (for example, because they already have some counter-arguments in mind to those arguments).
@@
 This  will become an important problem if there are not only two but many a priori possible arguments $a_k$ for $\nprop$, a small subset of which is considered relevant by any given individual, each with their own counter-argument $a'_k$ for $\prop$.
+This section is devoted to describing two examples to illustrate that point.
+Bear in mind that these examples may look somehow naïve on the aspect of the hypothesis they make about what convinces individuals.
+Real-world complex decision situations will require complex theories that do not fit the purpose of simple illustrative examples.
+Their goal is to argue that non-static theories are required, but not to fully describe such theories.
 
@@
 It may also be that, for each individual who considers relevant some arguments $A$ against the proposed concrete action, it is possible to give counter-arguments $A'$ that will convince the individual to opt for the proposal.
-One of the settings discussed by \citet{thaler_nudge_2009} permits to illustrate this point more concretely.
+One of the settings discussed by \citet{thaler_nudge_2009} permits such an illustration. %to illustrate this point more concretely.
 Let $I$ be a set of workers interested in establishing a savings plan. 
@@
 It may also be that, for each individual who considers relevant some arguments $A$ for saving not much (i.e., spending more in the short term), it is possible to give counter-arguments $A'$ that will convince the individual to opt for saving more.
-But no single argument could be decisive for each $i \in I$: it could be that only counter-arguments built specifically according to what a given individual considers relevant could convince him, given the complexity of the issue.
+But no single argument could be decisive for each $i \in I$: it could be that only counter-arguments built specifically according to what a given individual considers relevant could convince her, given the complexity of the issue.
 This illustrates that the deliberated choice of each individuals in $I$ may be to save more even though no static theory (\cref{def:static}) may achieve showing it, as it could be that no such theory is truthful.
@@
 	In a famous article about preference reversals, \citet{lichtenstein_reversals_2006} discuss an example involving two lotteries.
-The lottery $P$ lets the subject win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $L_P = (.99, +\$4; .01, −\$0.1)$.
+The lottery $L_P$ lets the subject win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $L_P = (.99, +\$4; .01, −\$0.1)$.
 The lottery $L_D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
@@
 Define $I$ as a set of individuals facing a choice between $L_P$ and $L_D$ in a laboratory experiment.
-Define $\ileadsto$ as simply exposing $i$ to $\alpha$ and observing the resulting choice by asking $i$ to indicate which lottery she prefers playing. 
+Define $\ileadsto$ as exposing $i$ to $\alpha$ and observing the resulting choice by asking $i$ to indicate which lottery she prefers playing, or declare being indifferent. 
 %Given an argumentative path $\hist$, $\hist \ileadsto (P ≥ D)$ iff, in a situation of $i$ having been exposed, in order, to the arguments in $\hist$, letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$, or declare indifference.
@@
 \label{sec:dynamic}
-An argumentative theory of deliberated choice $\gamma$ is defined as a tuple $(\pga, \arga, \dg)$, where $\pga \in P$ is the proposition supported by the theory, $\arga \in \allargs$ is the initial argument in favor of $\pga$ and $\dg$ is a defense relation.
+An argumentative theory of deliberated choice $\gamma$ is defined as a tuple $(\pga, \dg)$, where $\pga \in P$ is the proposition supported by the theory and $\dg$ is a defense relation.
 
-The defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ defines the argumentation strategy of the theory.
-Informally speaking, its role is, together with $\arga$, to produce the arguments that the theory claims will convince the individuals in $I$ to choose $\pga$.
-Assuming that the theory has played an argument $\ar_0$ and a path $\hist$ challenges its intended conclusion in favor of $\pga$ (as judged by the individual), $\dg(\ar_0, \hist)$ is the argument that the theory plays as a counter-argument to the path $\hist$.
+The defense relation $\dg \subseteq \allhist × \allargs$ defines the argumentation strategy of the theory.
+Informally speaking, it defines the arguments that the theory claims will convince the individuals in $I$ to choose $\pga$.
+Assuming that some path $\hist$ challenges the theory’s intended conclusion in favor of $\pga$ (as judged by the individual), $\dg(\hist)$ is the argument that the theory plays as a counter-argument to the path $\hist$.
 
-Formally speaking, a defense relation $\dg \subseteq (\allargs × \allhist) × \allargs$ is a right-unique relation satisfying bounded depth (to be defined shortly).
-Right-unique means that given any $\ar \in \allargs, \hist \in \allhist$, $\dg(\ar, \hist)$ is empty or is a singleton.
-%, and must satisfy $\ar \notin \histend ⇒ \dg(\ar, \hist) = \emptyset$.
-As is usual for right-unique relations, we write $\dg(\ar_0, \hist) = \ar_1$ instead of $\dg(\ar_0, \hist) = \set{\ar_1}$.
-Say that $\ar_1$ defends $\ar_0$ iff $\exists \hist \suchthat \dg(\ar_0, \hist) = \ar_1$.
-Define $\dg(\ar) = \dg(\ar, \allhist) = \set{\dg(\ar, \hist) \suchthat \hist \in \allhist} \subseteq \allargs$ as all the defenders of $\ar$.
+Formally speaking, a defense relation $\dg \subseteq \allhist × \allargs$ is a right-unique relation satisfying bounded depth (to be defined shortly).
+Right-unique means that given any $\hist \in \allhist$, $\dg(\hist) = \set{\ar \in \allargs \suchthat (\hist, \ar) \in \dg}$ is empty or is a singleton.
+As is usual for right-unique relations, we write $\dg(\hist) = \ar$ instead of $\dg(\hist) = \set{\ar}$ when $\dg(\hist)$ is a singleton (and $\dg(\hist) = \emptyset$ otherwise).
+Given $H \subseteq \allhist$, define $\dg(H) = \set{\dg(\hist) \suchthat \alpha \in H} \subseteq \allargs$. 
+Given $\ar_0, \ar_1 \in \allargs$, say that $\ar_1$ defends $\ar_0$ 
+iff $\exists \hist \in \allhist \suchthat \ar_0 \in R(\hist) \land \dg(\hist) = \ar_1$, equivalently, 
+iff $\ar_0 \in R(\dg^{-1}(\ar_1))$, equivalently, 
+iff $\ar_1 \in \dg(\set{\hist \suchthat \ar_0 \in R(\hist)})$.
 
-This mechanism permits to define defenders of defenders of an argument, $\dg(\dg(\ar))$, defenders of defenders of defenders of an argument, … This yields the following notion of depth.
+Say that $\gamma$ has depth at least $k \in \N^*$ iff $\exists (\alpha_i, 1 ≤ i ≤ k) \suchthat \forall 1 ≤ i ≤ k, d(\alpha_i) ≠ \emptyset \land \forall 1 ≤ i ≤ k - 1, \alpha_i \cup \set{d(\alpha_i)} \subseteq \alpha_{i + 1}$.
+The bounded depth condition on the defense relation imposes that for some $k \in \N^*$, $\gamma$ does not have depth at least $k$.
+The depth of a theory is defined as the smallest value $k \in \N$ such that it does not have depth at least $k + 1$.
+For example, $\gamma$ has depth $0$ iff $\dg = \emptyset$; and $\gamma$ has depth $1$ iff $\exists \alpha_1 \suchthat d(\alpha_1) ≠ \emptyset \land \forall \alpha_1 \cup \set{d(\alpha_1)} \subseteq \alpha_2: d(\alpha_2) = \emptyset$.
+
+Given $\ar \in \allargs$, define $\dlg(\ar) = \dg(\set{\hist \in \allhist \suchthat \ar \in R(\hist)}) = \set{\dg(\hist) \suchthat \hist \in \allhist \land \ar \in R(\hist)} \subseteq \allargs$ as all the defenders of $\ar$.
+Given $\args \subseteq \allargs$, define $\dlg(\args)$ as $\set{\dlg(\ar) \suchthat \ar \in \args}$.
+This is imperfect as $\dlg(\emptyset)$ should include the stuff that $\dg$ answers to when its own arguments are not involved.
+This permits to define defenders of defenders of an argument, $\dlg(\dlg(\ar))$, defenders of defenders of defenders of an argument, …
+
+This yields the following notion of depth.
 Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
 The bounded depth condition on the defense relation imposes that
-$\exists k \in \N^* \suchthat (\dg)^k(\arga) = \emptyset$.
+$\exists k \in \N \suchthat (\dlg)^k(\dg(\emptyset)) = \emptyset$.
 The smallest such $k$ is called the depth of the theory.
-
+For example, $γ$ has depth $0$ iff $\dg(\emptyset) = \emptyset$.
+TODO that seems wrong: could be hist to which the theory wishes to reply.
 %The condition that when $\dg(\ar_0, \hist)$, $\ar_0 \in \histend$ is imposed for simplicity: as will appear, an argument $\ar_0$ needs defense only when it is challenged by some path $\hist \suchthat \ar_0 \in \histend$, thus, letting $\dg$ define counter-arguments to paths not satisfying this condition would be of no use.

### 2023-06-02 simple.tex
Rm old defense iterated function and gave intuition

@@
 For example, $\gamma$ has depth $0$ iff $\dg = \emptyset$; and $\gamma$ has depth $1$ iff $\exists \alpha_1 \suchthat d(\alpha_1) ≠ \emptyset \land \forall \alpha_1 \cup \set{d(\alpha_1)} \subseteq \alpha_2: d(\alpha_2) = \emptyset$.
-
-Given $\ar \in \allargs$, define $\dlg(\ar) = \dg(\set{\hist \in \allhist \suchthat \ar \in R(\hist)}) = \set{\dg(\hist) \suchthat \hist \in \allhist \land \ar \in R(\hist)} \subseteq \allargs$ as all the defenders of $\ar$.
-Given $\args \subseteq \allargs$, define $\dlg(\args)$ as $\set{\dlg(\ar) \suchthat \ar \in \args}$.
-This is imperfect as $\dlg(\emptyset)$ should include the stuff that $\dg$ answers to when its own arguments are not involved.
-This permits to define defenders of defenders of an argument, $\dlg(\dlg(\ar))$, defenders of defenders of defenders of an argument, …
-
-This yields the following notion of depth.
-Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
-The bounded depth condition on the defense relation imposes that
-$\exists k \in \N \suchthat (\dlg)^k(\dg(\emptyset)) = \emptyset$.
-The smallest such $k$ is called the depth of the theory.
-For example, $γ$ has depth $0$ iff $\dg(\emptyset) = \emptyset$.
-TODO that seems wrong: could be hist to which the theory wishes to reply.
-%The condition that when $\dg(\ar_0, \hist)$, $\ar_0 \in \histend$ is imposed for simplicity: as will appear, an argument $\ar_0$ needs defense only when it is challenged by some path $\hist \suchthat \ar_0 \in \histend$, thus, letting $\dg$ define counter-arguments to paths not satisfying this condition would be of no use.
+\commentOC{Intuition.
+When last defense is burried under multiple other arguments so that it is not at end any more, just repeat the last defense.
+Otherwise the theory also needs to be able to compress the arguments against it.
+We prefer to keep this separated.
+As a result, an argument $\ar_0$ needs defense only when it is challenged by some path $\hist \suchthat \ar_0 \in \histend$, thus, letting $\dg$ define counter-arguments to paths not satisfying this condition would be of no use.}
 

### 2023-06-02 simple.tex
Replaced intuition by more complex def of defense which may reuse args.

@@
 
-Say that $\gamma$ has depth at least $k \in \N^*$ iff $\exists (\alpha_i, 1 ≤ i ≤ k) \suchthat \forall 1 ≤ i ≤ k, d(\alpha_i) ≠ \emptyset \land \forall 1 ≤ i ≤ k - 1, \alpha_i \cup \set{d(\alpha_i)} \subseteq \alpha_{i + 1}$.
+Say that $\gamma$ has depth at least $k \in \N^*$ iff $\exists (\alpha_i, 1 ≤ i ≤ k) \suchthat \forall 1 ≤ i ≤ k, \dg(\set{\alpha_j \suchthat 1 ≤ j ≤ i - 1}) \subsetneq \dg(\set{\alpha_j \suchthat 1 ≤ j ≤ i}) \land \forall 1 ≤ i ≤ k - 1, \alpha_i \cup \set{\dg(\alpha_i)} \subseteq \alpha_{i + 1}$.
 The bounded depth condition on the defense relation imposes that for some $k \in \N^*$, $\gamma$ does not have depth at least $k$.
 The depth of a theory is defined as the smallest value $k \in \N$ such that it does not have depth at least $k + 1$.
-For example, $\gamma$ has depth $0$ iff $\dg = \emptyset$; and $\gamma$ has depth $1$ iff $\exists \alpha_1 \suchthat d(\alpha_1) ≠ \emptyset \land \forall \alpha_1 \cup \set{d(\alpha_1)} \subseteq \alpha_2: d(\alpha_2) = \emptyset$.
-\commentOC{Intuition.
-When last defense is burried under multiple other arguments so that it is not at end any more, just repeat the last defense.
-Otherwise the theory also needs to be able to compress the arguments against it.
-We prefer to keep this separated.
-As a result, an argument $\ar_0$ needs defense only when it is challenged by some path $\hist \suchthat \ar_0 \in \histend$, thus, letting $\dg$ define counter-arguments to paths not satisfying this condition would be of no use.}
+For example, $\gamma$ has depth $0$ iff $\dg = \emptyset$; and $\gamma$ has depth $1$ iff $[\exists \alpha_1 \suchthat \dg(\alpha_1) ≠ \emptyset] \land [\forall \alpha_1, \alpha_2 \suchthat \dg(\alpha_1) ≠ \emptyset \land \alpha_1 \cup \set{\dg(\alpha_1)} \subseteq \alpha_2: \dg(\alpha_2) \subseteq \dg(\alpha_1)]$.
 
 An argumentative theory claims that its argumentation strategy, embodied by $\arga$ and $\dg$, will convince the individuals in $I$.
-More precisely, given $i \in I$, it claims that $\arga$ either is a decisive argument for $\pga$, or, if $\arga$ is not, that the theory will defend the argument by replying to every counter-argument to $\arga$ with an argument that either is a decisive argument for $\pga$ or, in turn, will be defended by the theory, and so on as long as the theory has counter-arguments to produce; the theory claiming that some argument along that chain is decisive.
+More precisely, given $i \in I$, it claims that $\arga$ either is a decisive argument for $\pga$, or, if $\arga$ is not, that the theory will defend the argument by replying to every counter-argument to $\arga$ with an argument that either is a decisive argument for $\pga$ or, in turn, will be defended by the theory, and so on as long as the theory has new counter-arguments to produce; the theory claiming that some argument along that chain is decisive.
 

### 2023-06-16 simple.tex
Falsifiability again

@@
 Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}: \hist(k) = \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
+A path $\hist$ is a sub-path of another path $\histp$ whenever $\hist \subseteq \histp$, thus, $\forall k \in \intvl{1, \card{\hist}}: \hist_k = \histp_k$.
 
@@
 
+\subsection{Form of theories (draft)}
+Given an exposure protocol $(I, \allargs, {\leadsto})$, we want to phrase some claims under the form of a logical sentence $C$ such that:
+if $C$ holds, then it implies something about the dj of some $i$;
+if $C$ fails, it is possible to falsify it.
+
+We can observe set $O$ that forms a function $f(i) = \set{\alpha \ileadsto \phi, \alpha' \ileadsto ¬\phi, …}$, with $\alpha \subset \alpha \subset …$ and with finite $O$.
+Our second condition is that $¬C \implies \exists O \suchthat O \implies ¬C$.
+For example, if $C$ is $\alpha \ileadsto \phi \lor \beta \leadsto[j] \phi$, $O$ is $\alpha \ileadsto ¬\phi \land \beta \leadsto ¬\phi$, then $O$ implies $¬C$.
+As another example, $C$ being $\exists \alpha \suchthat \alpha \ileadsto \phi$ is unfalsifiable, as its negation is $\forall \alpha: \alpha \nileadsto \phi$, which requires infinite $O$.
+
+Consider $\leadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadsto \phi$.
+Then some suitable $C$ exists.
+It is $\forall i: \ar \ileadstost \phi$.
+If false, it is falsifiable.
+Even though it is not provable by any $O$.
+
+Now consider $\leadsto$ such that $\exists J, K \subset I \suchthat \ar \ileadstost[j] \phi, \ar' \ileadstost[k] \phi$.
+Then no suitable $C$ exists?
+
+If $C$ has the form, whenever $a$ fails, $a'$ is then decisive, it is falsifiable, but does not lead to a decisive argument.
+Want to show: $j \ileadstost \phi$. Need to show: $ar$ or $ar'$ is decisive.
+Assume we know who is a $j$. Then we can!
+Claim: $\ar \ileadsto \phi$.
+Now assume that our claim has to be anonymous.
+Also, assume the formulas involve one $i$ at a time (not needed, probably, but not much restrictive so okay for now).
+So it is of the form $(i, \alpha, \phi) \lor (i, \alpha, \phi') \land (i, \alpha', \phi)…$ implies something decisive.
+So it must be of the form: all $\alpha$ ending with $\ar$ do $\ileadsto \phi$. Or must imply this.
+Let’s make it very strong, as much as possible, thus equal to $\ileadsto \cap \ileadsto[j]$.
+That’s not strong enough!
+
+Escaping?
+Assume that we know that 50\% are J and 50\% are K.
+
+\subsection{Form of theories}
+Given an exposure protocol $(I, \allargs, {\leadsto})$, recall that ${\leadsto} \in P^{I × \allhist}$.
+
+Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\leadsto$, thus, $C \subseteq P^{I × \allhist}$.
+The claim holds iff ${\leadsto} \in C$.
+When writing $C$ as a formula, it is intended to mean the set $\set{{\leadsto} \in P^{I × \allhist} \suchthat C({\leadsto})}$.
+
+Given a pair $(I, \allargs)$, a general observation $O$ is a finite subset of $I × \allhist × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in O: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
+General observations are the a priori possible observations, that is, those that can be considered possible when nothing is known about $\leadsto$.
+Let $S_O = \set{f \in P^{I × \allhist} \suchthat O \subseteq f}$ denote the possibilities for $\leadsto$ compatible with the observations.
+
+A claim $C$ is falsifiable iff $\exists O \suchthat O \implies ¬C$, by which I mean $S_O \cap C = \emptyset$.
+\begin{example}
+	$(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …$ is not falsifiable.
+%	Its negation is $\forall k: (\ar^k) \nileadsto \phi$.
+%	The claim represents the set $\set{{\leadsto} \in P^{I × \allhist} \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
+	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$.
+Pick any $\leadsto$ such that $O \subset {\leadsto} \land (\ar)^l \ileadsto \phi$.
+We have ${\leadsto} \in S_O \cap C ≠ \emptyset$.
+\end{example}
+\begin{example}
+	$(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi$ is not falsifiable.
+	Given any $O$, it may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $\leadsto$ such that $O \subset {\leadsto} \land t \in {\leadsto}$.
+We have ${\leadsto} \in S_O \cap C ≠ \emptyset$.
+\end{example}
+\begin{example}[Fals. but shouldn’t]
+	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …]$ is falsifiable.
+	Consider $O = \set{(j, \hist, ¬\phi)}$.
+\end{example}
+\begin{example}[Fals. but shouldn’t, better]
+	\label{ex:fbs}
+	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi]$ is falsifiable.
+	Consider $O = \set{(j, \hist, ¬\phi)}$.
+\end{example}
+\begin{example}
+	$\forall i: \ar \ileadstost \phi$ is falsifiable.
+	Consider any $i \in I$ and $O = \set{(i, (\ar), ¬\phi)}$.
+\end{example}
+
+\Cref{ex:fbs} shows that this definition of falsifiability is wrong.
+We now say that $C$ is falsifiable iff $\forall {\leadsto} \in P^{I × \allhist}: ¬C({\leadsto}) \implies \exists O \subseteq {\leadsto} \suchthat O \implies ¬C$, meaning that
+$\forall {\leadsto} \notin C: \exists O \subseteq {\leadsto} \suchthat S_O \cap C = \emptyset$.
+\begin{example}
+	$(\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …$ is falsifiable.
+	Consider any ${\leadsto} \notin C$, thus satisfying $\exists k \suchthat (\ar)^k \nileadsto \phi$.
+Consider $O = \set{(i, (\ar)^k, {\leadsto}(i, (\ar)^k) ≠ \phi)}$, thus with $O \subset {\leadsto}$.
+We have $S_O \cap C = \emptyset$: consider any $O \subset f$, it is not in $C$.
+\end{example}
+\begin{example}
+	$(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi$ is not falsifiable.
+	Consider any ${\leadsto} \notin C$, thus satisfying $(\ar) \nileadsto \phi \land (\ar') \nileadsto \phi$.
+	Consider any $O \subseteq {\leadsto}$ and let us prove that $S_O \cap C ≠ \emptyset$.
+	By definition of a general observation, $O$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $f$ such that $O \subset {f} \land t \in {f}$.
+We have ${f} \in S_O \cap C ≠ \emptyset$.
+\end{example}
+\begin{example}[TODO]
+	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …]$ is not falsifiable?
+	Consider any ${\leadsto} \notin C$, thus satisfying $\hist \nileadsto[j] \phi \lor [(\ar) \nileadsto \phi \land (\ar, \ar) \nileadsto \phi \land …]$.
+	Consider $O = \set{(j, \hist, ¬\phi)}$.
+\end{example}
+
 \subsection{Argumentative theories of deliberated choice}
@@
 
-Say that $\gamma$ has depth at least $k \in \N^*$ iff $\exists (\alpha_i, 1 ≤ i ≤ k) \suchthat \forall 1 ≤ i ≤ k, \dg(\set{\alpha_j \suchthat 1 ≤ j ≤ i - 1}) \subsetneq \dg(\set{\alpha_j \suchthat 1 ≤ j ≤ i}) \land \forall 1 ≤ i ≤ k - 1, \alpha_i \cup \set{\dg(\alpha_i)} \subseteq \alpha_{i + 1}$.
+Say that $\gamma$ has depth at least $k \in \N^*$ iff $\exists (\alpha_i, 1 ≤ i ≤ k) \suchthat \forall 1 ≤ i ≤ k, \dg(\set{\alpha_j \suchthat 1 ≤ j ≤ i - 1}) \subsetneq \dg(\set{\alpha_j \suchthat 1 ≤ j ≤ i}) \land \forall 1 ≤ i ≤ k - 1, \alpha_i \cup \dg(\alpha_i) \subseteq \alpha_{i + 1}$.
 The bounded depth condition on the defense relation imposes that for some $k \in \N^*$, $\gamma$ does not have depth at least $k$.
 The depth of a theory is defined as the smallest value $k \in \N$ such that it does not have depth at least $k + 1$.
-For example, $\gamma$ has depth $0$ iff $\dg = \emptyset$; and $\gamma$ has depth $1$ iff $[\exists \alpha_1 \suchthat \dg(\alpha_1) ≠ \emptyset] \land [\forall \alpha_1, \alpha_2 \suchthat \dg(\alpha_1) ≠ \emptyset \land \alpha_1 \cup \set{\dg(\alpha_1)} \subseteq \alpha_2: \dg(\alpha_2) \subseteq \dg(\alpha_1)]$.
+For example, $\gamma$ has depth $0$ iff $\dg = \emptyset$; and $\gamma$ has depth $1$ iff $[\exists \alpha_1 \suchthat \dg(\alpha_1) ≠ \emptyset] \land [\forall \alpha_1, \alpha_2 \suchthat \dg(\alpha_1) ≠ \emptyset \land \alpha_1 \cup \dg(\alpha_1) \subseteq \alpha_2: \dg(\alpha_2) \subseteq \dg(\alpha_1)]$.
+
+\commentOC{Intuition.
+Invoke $\dg$ at $\alpha$ only when $\alpha$ fails.
+Permit to invoke a previous defense again as maybe the counter was too long to perform when summarized.
+If $a_2$ fails, we must invoke $\dg(…, a_2, x)$; failures of $\dg(…, a_2, …, x)$ should not count.
+We should invoke $\dg$ only when $\alpha$ fails with some defense produced by $\dg()$ belongs to $\histend$.}
+
+%Falsification seems done when $\exists \alpha, \beta \suchthat d(\beta) \in \histend \land \alpha \ileadsto p$. But then seems to be required to tell $d$ what has been tried already!}
 
@@
 More precisely, given $i \in I$, it claims that $\arga$ either is a decisive argument for $\pga$, or, if $\arga$ is not, that the theory will defend the argument by replying to every counter-argument to $\arga$ with an argument that either is a decisive argument for $\pga$ or, in turn, will be defended by the theory, and so on as long as the theory has new counter-arguments to produce; the theory claiming that some argument along that chain is decisive.
+
+\commentOC{Condition: $\hist \nileadsto \pga \land \exists \hist' \subseteq \hist \suchthat \dg(\histp) \in \histend \land \dg(\hist)$ is not decisive ($\exists \beta \subseteq \hist \suchthat \dg(\hist) \in \beta_\text{end} \land \beta \ileadsto \pga$).}
 
@@
 BUT $a_5, a_4, a_1$ should then not convince.
+
+The solution is: after $a1, a5, a2$, $a1$ appears decisive, thus also $a1,a5, a2, a1, a4$ ok.
+Then some subset $a$ of $a1 \cup a_5 \cup a2$ should satisfy $a, a4$ OK and replace $a1$.
+And $a$ is decisive.
 }

### 2023-06-17 simple.tex
Rm unclear Fals. but shouldn’t exmpl
Further falsifiability nonsense

@@
 Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\leadsto$, thus, $C \subseteq P^{I × \allhist}$.
-The claim holds iff ${\leadsto} \in C$.
 When writing $C$ as a formula, it is intended to mean the set $\set{{\leadsto} \in P^{I × \allhist} \suchthat C({\leadsto})}$.
@@
 \begin{example}[Fals. but shouldn’t]
-	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …]$ is falsifiable.
-	Consider $O = \set{(j, \hist, ¬\phi)}$.
-\end{example}
-\begin{example}[Fals. but shouldn’t, better]
 	\label{ex:fbs}
@@
 \end{example}
+\Cref{ex:fbs} shows that this definition of falsifiability is wrong.
 
-\Cref{ex:fbs} shows that this definition of falsifiability is wrong.
 We now say that $C$ is falsifiable iff $\forall {\leadsto} \in P^{I × \allhist}: ¬C({\leadsto}) \implies \exists O \subseteq {\leadsto} \suchthat O \implies ¬C$, meaning that
@@
 \begin{example}
+	\label{ex:unfals}
 	$(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi$ is not falsifiable.
@@
 \end{example}
-\begin{example}[TODO]
-	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …]$ is not falsifiable?
-	Consider any ${\leadsto} \notin C$, thus satisfying $\hist \nileadsto[j] \phi \lor [(\ar) \nileadsto \phi \land (\ar, \ar) \nileadsto \phi \land …]$.
-	Consider $O = \set{(j, \hist, ¬\phi)}$.
+\begin{example}
+	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi]$ is not falsifiable.
+	Consider any $\leadsto$ satisfying $(\ar) \nileadsto \phi \land (\ar') \nileadsto \phi$, thus with ${\leadsto} \notin C$.
+	\Cref{ex:unfals} concludes.
+\end{example}
+
+Deliberated choices are an element $\pi({\leadsto}) \subseteq I × P$ which is right unique (meaning that $\forall i \in I: \card{\pi({\leadsto})(i)} ≤ 1$).
+Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\leadsto}) \in (P \cup \set{\emptyset})^I$.
+We say that $C$ is informative iff $\exists f \in (P \cup \set{\emptyset})^I \suchthat C \implies ¬f$, meaning that $\pi(C) = \set{\pi(\leadsto) \suchthat {\leadsto} \in C} ≠ (P \cup \set{\emptyset})^I$.
+
+Given an exposure protocol, we say that a claim $C$ holds iff ${\leadsto} \in C$.
+$C$ is $\leadsto$-suitable iff it is informative and falsifiable and ${\leadsto} \in C$.
+
+The following theorem verifies that when $C$ holds, it will not be falsified ex post (though it may be (a priori) falsifiable).
+\begin{theorem}
+	\label{th:ex-post}
+	If ${\leadsto} \in C$, $\nexists O \subseteq {\leadsto} \suchthat S_O \cap C = \emptyset$.
+\end{theorem}
+\begin{proof}
+	Equivalently, considering any $O \subseteq {\leadsto} \in C$: $\exists O \subseteq f \suchthat f \in C$.
+	This holds as ${\leadsto}$ satisfies this.
+\end{proof}
+\Cref{th:ex-post} together with the definition of falsifiability leads to \cref{th:holdsiff}.
+\begin{corollary}
+	\label{th:holdsiff}
+	$C$ is falsifiable iff [${\leadsto} \in C$ iff $\nexists O \subseteq {\leadsto} \suchthat S_O \cap C = \emptyset$].
+\end{corollary}
+%\begin{proof}
+%	Assume that $C$ does not hold, thus, ${\leadsto} \notin C$.
+%	Because $C$ is falsifiable, $\exists O \subseteq {\leadsto} \suchthat S_O \cap C = \emptyset$.
+
+\begin{example}[To be corrected]
+Consider any $\leadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
+Then some suitable $C$ exists, for example, $\forall i: \ar \ileadstost \phi$.
+Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
+\end{example}
+
+\begin{example}[To be corrected]
+Now consider $\leadsto$ such that $\exists J, K \subset I \suchthat \forall j \in J: \ar \ileadstost[j] \phi \land \forall k \in K: \ar' \ileadstost[k] \phi$.
+Then some suitable $C$ exists, for example, $\ar \ileadstost[j] \phi$.
 \end{example}

### 2023-06-18 simple.tex
Rm unuseful proof
A post fals, corrected

--- 2023-06-16 simple.tex
@@
 	Consider one individual $i \in I$.
-	Let ${\leadsto}(i, a_1)$ represent $i$ being shown a test of candidate $m_1$ wherein $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly.
-	Let ${\leadsto}(i, a_2)$ represent $i$ being shown a test of candidate $m_2$ wherein $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly.
-%	Let ${\leadsto}(i, a_e)$ represent $i$ being given an explanation about the psychological phenomenon described in the quote above.
-	Let ${\leadsto}(i, a_e)$ represent $i$ being given the following argument.
+	Let ${\allleadsto}(i, a_1)$ represent $i$ being shown a test of candidate $m_1$ wherein $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly.
+	Let ${\allleadsto}(i, a_2)$ represent $i$ being shown a test of candidate $m_2$ wherein $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly.
+%	Let ${\allleadsto}(i, a_e)$ represent $i$ being given an explanation about the psychological phenomenon described in the quote above.
+	Let ${\allleadsto}(i, a_e)$ represent $i$ being given the following argument.
 “When tested, $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly; whereas $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly.
@@
 	If the prediction described in the quote applies to $i$, the relation $\ileadsto$ is as follows, $\forall k \in \N^*$ (recall that for $\args \subseteq \allargs$, $\args^k$ represents the set of sequences of length $k$ using arguments from $\args$): $\forall \hist \in \set{a_e}^k, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_1, a_2}^k, \hist \ileadsto \prop_1$; $\forall \hist \in \set{a_1, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_2, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \allargs^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$.
-The values of ${\leadsto}(i, \hist)$ for $\hist = \emptyset$ and for $\hist \in \allargs^k \suchthat a_e \notin \histend$ are undetermined by the prediction, but whatever they are, $a_e$ is a decisive argument for $\prop_2$, hence, $i$’s deliberated choice is $\prop_2$.
+The values of ${\allleadsto}(i, \hist)$ for $\hist = \emptyset$ and for $\hist \in \allargs^k \suchthat a_e \notin \histend$ are undetermined by the prediction, but whatever they are, $a_e$ is a decisive argument for $\prop_2$, hence, $i$’s deliberated choice is $\prop_2$.
 \end{example}
@@
 \section{Theories of deliberated choice}
-This section assumes that an exposure protocol $(I, \allargs, {\leadsto})$ is defined, and defines theories of deliberated choice associated with that exposure protocol.
+This section assumes that an exposure protocol $(I, \allargs, {\allleadsto})$ is defined, and defines theories of deliberated choice associated with that exposure protocol.
 We will start with very simple theories (\cref{sec:static}) in order to build an intuition about the conditions required on theories of deliberated choice, then justify the need for more complex theories (\cref{sec:lichtenstein}) and finally define more general theories of deliberated choice (\cref{sec:dynamic}).
@@
 
-The following example illustrates this same point in a constrained setting which permits a complete definition of $\allargs$ and $\leadsto$.%, which permits defining the setting completely at the price of a reduced realism.
+The following example illustrates this same point in a constrained setting which permits a complete definition of $\allargs$ and $\allleadsto$.%, which permits defining the setting completely at the price of a reduced realism.
 \begin{example}[A decision problem about two lotteries]
@@
 \subsection{Form of theories (draft)}
-Given an exposure protocol $(I, \allargs, {\leadsto})$, we want to phrase some claims under the form of a logical sentence $C$ such that:
+Given an exposure protocol $(I, \allargs, {\allleadsto})$, we want to phrase some claims under the form of a logical sentence $C$ such that:
 if $C$ holds, then it implies something about the dj of some $i$;
@@
 Our second condition is that $¬C \implies \exists O \suchthat O \implies ¬C$.
-For example, if $C$ is $\alpha \ileadsto \phi \lor \beta \leadsto[j] \phi$, $O$ is $\alpha \ileadsto ¬\phi \land \beta \leadsto ¬\phi$, then $O$ implies $¬C$.
+For example, if $C$ is $\alpha \ileadsto \phi \lor \beta \allleadsto[j] \phi$, $O$ is $\alpha \ileadsto ¬\phi \land \beta \allleadsto ¬\phi$, then $O$ implies $¬C$.
 As another example, $C$ being $\exists \alpha \suchthat \alpha \ileadsto \phi$ is unfalsifiable, as its negation is $\forall \alpha: \alpha \nileadsto \phi$, which requires infinite $O$.
 
-Consider $\leadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadsto \phi$.
+Consider $\allleadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadsto \phi$.
 Then some suitable $C$ exists.
@@
 
-Now consider $\leadsto$ such that $\exists J, K \subset I \suchthat \ar \ileadstost[j] \phi, \ar' \ileadstost[k] \phi$.
+Now consider $\allleadsto$ such that $\exists J, K \subset I \suchthat \ar \ileadstost[j] \phi, \ar' \ileadstost[k] \phi$.
 Then no suitable $C$ exists?
@@
 \subsection{Form of theories}
-Given an exposure protocol $(I, \allargs, {\leadsto})$, recall that ${\leadsto} \in P^{I × \allhist}$.
+Given an exposure protocol $(I, \allargs, {\allleadsto})$, recall that ${\allleadsto} \in P^{I × \allhist}$.
 
-Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\leadsto$, thus, $C \subseteq P^{I × \allhist}$.
-The claim holds iff ${\leadsto} \in C$.
-When writing $C$ as a formula, it is intended to mean the set $\set{{\leadsto} \in P^{I × \allhist} \suchthat C({\leadsto})}$.
+Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq P^{I × \allhist}$.
+When writing $C$ as a formula, it is intended to mean the set $\set{{\allleadstog} \in P^{I × \allhist} \suchthat C({\allleadstog})}$.
 
-Given a pair $(I, \allargs)$, a general observation $O$ is a finite subset of $I × \allhist × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in O: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
-General observations are the a priori possible observations, that is, those that can be considered possible when nothing is known about $\leadsto$.
-Let $S_O = \set{f \in P^{I × \allhist} \suchthat O \subseteq f}$ denote the possibilities for $\leadsto$ compatible with the observations.
+Given a pair $(I, \allargs)$, a general observation $O$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in O: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
+General observations are the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
+Let $S_O = \set{{\allleadstog} \in P^{I × \allhist} \suchthat O \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
 
@@
 \begin{example}
-	$(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …$ is not falsifiable.
+	$(\ar) \ileadstog \phi \lor (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
 %	Its negation is $\forall k: (\ar^k) \nileadsto \phi$.
-%	The claim represents the set $\set{{\leadsto} \in P^{I × \allhist} \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
+%	The claim represents the set $\set{{\allleadsto} \in P^{I × \allhist} \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
 	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$.
-Pick any $\leadsto$ such that $O \subset {\leadsto} \land (\ar)^l \ileadsto \phi$.
-We have ${\leadsto} \in S_O \cap C ≠ \emptyset$.
+Pick any $\allleadstog$ such that $O \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
+We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
 \end{example}
 \begin{example}
-	$(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi$ is not falsifiable.
-	Given any $O$, it may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $\leadsto$ such that $O \subset {\leadsto} \land t \in {\leadsto}$.
-We have ${\leadsto} \in S_O \cap C ≠ \emptyset$.
+	$(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
+	Given any $O$, it may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $\allleadstog$ such that $O \subset {\allleadstog} \land t \in {\allleadstog}$.
+We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
 \end{example}
 \begin{example}[Fals. but shouldn’t]
-	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …]$ is falsifiable.
-	Consider $O = \set{(j, \hist, ¬\phi)}$.
-\end{example}
-\begin{example}[Fals. but shouldn’t, better]
 	\label{ex:fbs}
-	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi]$ is falsifiable.
+	$\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is falsifiable.
 	Consider $O = \set{(j, \hist, ¬\phi)}$.
@@
 \begin{example}
-	$\forall i: \ar \ileadstost \phi$ is falsifiable.
+	$\forall i: \ar \ileadstostg \phi$ is falsifiable.
 	Consider any $i \in I$ and $O = \set{(i, (\ar), ¬\phi)}$.
 \end{example}
+\Cref{ex:fbs} shows that this definition of falsifiability is wrong.
 
-\Cref{ex:fbs} shows that this definition of falsifiability is wrong.
-We now say that $C$ is falsifiable iff $\forall {\leadsto} \in P^{I × \allhist}: ¬C({\leadsto}) \implies \exists O \subseteq {\leadsto} \suchthat O \implies ¬C$, meaning that
-$\forall {\leadsto} \notin C: \exists O \subseteq {\leadsto} \suchthat S_O \cap C = \emptyset$.
+We now say that $C$ is falsifiable iff $\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists O \subseteq {\allleadstog} \suchthat O \implies ¬C$, meaning that
+$\forall {\allleadstog} \notin C: \exists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset$.
 \begin{example}
-	$(\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …$ is falsifiable.
-	Consider any ${\leadsto} \notin C$, thus satisfying $\exists k \suchthat (\ar)^k \nileadsto \phi$.
-Consider $O = \set{(i, (\ar)^k, {\leadsto}(i, (\ar)^k) ≠ \phi)}$, thus with $O \subset {\leadsto}$.
+	$(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is falsifiable.
+	Consider any ${\allleadstog} \notin C$, thus satisfying $\exists k \suchthat (\ar)^k \nileadstog \phi$.
+Consider $O = \set{(i, (\ar)^k, {\allleadstog}(i, (\ar)^k) ≠ \phi)}$, thus with $O \subset {\allleadstog}$.
 We have $S_O \cap C = \emptyset$: consider any $O \subset f$, it is not in $C$.
@@
 \begin{example}
-	$(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi$ is not falsifiable.
-	Consider any ${\leadsto} \notin C$, thus satisfying $(\ar) \nileadsto \phi \land (\ar') \nileadsto \phi$.
-	Consider any $O \subseteq {\leadsto}$ and let us prove that $S_O \cap C ≠ \emptyset$.
+	\label{ex:unfals}
+	$(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
+	Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
+	Consider any $O \subseteq {\allleadstog}$ and let us prove that $S_O \cap C ≠ \emptyset$.
 	By definition of a general observation, $O$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $f$ such that $O \subset {f} \land t \in {f}$.
@@
 \end{example}
-\begin{example}[TODO]
-	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …]$ is not falsifiable?
-	Consider any ${\leadsto} \notin C$, thus satisfying $\hist \nileadsto[j] \phi \lor [(\ar) \nileadsto \phi \land (\ar, \ar) \nileadsto \phi \land …]$.
-	Consider $O = \set{(j, \hist, ¬\phi)}$.
+\begin{example}
+	$\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
+	Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
+	\Cref{ex:unfals} concludes.
+\end{example}
+
+Given an exposure protocol $\allleadsto$, deliberated choices are represented by an element $\pi({\allleadsto}) \subseteq I × P$ which is right unique (meaning that $\forall i \in I: \card{\pi({\allleadsto})(i)} ≤ 1$).
+Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\allleadsto}) \in (P \cup \set{\emptyset})^I$.
+We say that $C$ is informative iff $\exists {\allleadstog} \in (P \cup \set{\emptyset})^I \suchthat C \implies ¬{\allleadstog}$, meaning that $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.
+
+Given an exposure protocol $\allleadsto$, we say that a claim $C$ holds iff $C \ni {\allleadsto}$.
+$C$ is $\allleadsto$-suitable iff it is informative and falsifiable and ${\allleadsto} \in C$.
+
+The following theorem verifies that when $C$ holds, it will not be falsified ex post (though it may be (a priori) falsifiable).
+\begin{theorem}
+	\label{th:ex-post}
+	$\forall C \ni {\allleadsto}: \nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset$.
+\end{theorem}
+\begin{proof}
+	We have, $\forall C \suchthat C \ni {\allleadsto}, \forall O \subseteq {\allleadsto}$: $O \subseteq {\allleadsto} \in C$, equivalently, ${\allleadsto} \in S_O \cap C$, thus $S_O \cap C ≠ \emptyset$.
+\end{proof}
+Therefore, falsifiability guarantees that a claim holds if, and only if, it is not a posteriori falsifiable.
+\begin{theorem}
+	\label{th:holdsiff}
+	For all falsifiable $C$: ${\allleadsto} \in C$ iff $\nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset$.
+\end{theorem}
+\begin{proof}
+	Consider any falsifiable $C$.
+	By definition of falsifiability, $\forall {\allleadstog}: \nexists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset \implies {\allleadstog} \in C$.
+	In particular,
+	$\nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset \implies {\allleadsto} \in C$.
+	The reverse implication is proven by \cref{th:ex-post}.
+\end{proof}
+Note that the reverse implication of $\cref{th:holdsiff} does not hold: a claim may hold and be not a posteriori falsifiable but be not a priori falsifiable.
+
+\begin{example}[To be corrected]
+Consider any $\allleadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
+Then some suitable $C$ exists, for example, $\forall i: \ar \ileadstost \phi$.
+Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
+\end{example}
+
+\begin{example}[To be corrected]
+Now consider $\allleadsto$ such that $\exists J, K \subset I \suchthat \forall j \in J: \ar \ileadstost[j] \phi \land \forall k \in K: \ar' \ileadstost[k] \phi$.
+Then some suitable $C$ exists, for example, $\ar \ileadstost[j] \phi$.
 \end{example}
@@
 	\label{def:truth}
-	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff 
+	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\allleadsto})$ is \emph{truthful} iff 
 	$\forall i \in I, \hist \in \allhist, n \in \N, k \in \intvl{1, \card \hist}^n, \ar \in \allargs^n$:

### 2023-06-18 simple.tex
Rm note about reverse impl
Notation f

@@
 
-We now say that $C$ is falsifiable iff $\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists O \subseteq {\allleadstog} \suchthat O \implies ¬C$, meaning that
+We now say that $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists O \subseteq {\allleadstog} \suchthat O \implies ¬C$, meaning that
 $\forall {\allleadstog} \notin C: \exists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset$.
@@
 	Consider any $O \subseteq {\allleadstog}$ and let us prove that $S_O \cap C ≠ \emptyset$.
-	By definition of a general observation, $O$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $f$ such that $O \subset {f} \land t \in {f}$.
-We have ${f} \in S_O \cap C ≠ \emptyset$.
+	By definition of a general observation, $O$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any ${\allleadstog'}$ such that $O \subset {\allleadstog'} \land t \in {\allleadstog'}$.
+We have ${\allleadstog'} \in S_O \cap C ≠ \emptyset$.
 \end{example}
@@
 \end{example}
+\begin{example}
+	Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
+	Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $O = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
+\end{example}
 
-Given an exposure protocol $\allleadsto$, deliberated choices are represented by an element $\pi({\allleadsto}) \subseteq I × P$ which is right unique (meaning that $\forall i \in I: \card{\pi({\allleadsto})(i)} ≤ 1$).
-Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\allleadsto}) \in (P \cup \set{\emptyset})^I$.
-We say that $C$ is informative iff $\exists {\allleadstog} \in (P \cup \set{\emptyset})^I \suchthat C \implies ¬{\allleadstog}$, meaning that $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.
-
-Given an exposure protocol $\allleadsto$, we say that a claim $C$ holds iff $C \ni {\allleadsto}$.
-$C$ is $\allleadsto$-suitable iff it is informative and falsifiable and ${\allleadsto} \in C$.
+Given an exposure protocol $\allleadsto$, we say that a claim $C$ \emph{holds} iff $C \ni {\allleadsto}$.
 
@@
 \end{proof}
-Therefore, falsifiability guarantees that a claim holds if, and only if, it is not a posteriori falsifiable.
+Therefore, falsifiability guarantees that a claim holds if, and only if, it is not a posteriori falsifiable. (TODO syntactically fals VS empirically fals.)
 \begin{theorem}
@@
 \end{proof}
-Note that the reverse implication of $\cref{th:holdsiff} does not hold: a claim may hold and be not a posteriori falsifiable but be not a priori falsifiable.
 
+Given an exposure protocol $\allleadsto$, deliberated choices are represented by an element $\pi({\allleadsto}) \subseteq I × P$ which is right unique (meaning that $\forall i \in I: \card{\pi({\allleadsto})(i)} ≤ 1$).
+Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\allleadsto}) \in (P \cup \set{\emptyset})^I$.
+We say that $C$ is \emph{informative} iff $\exists {\allleadstog} \in (P \cup \set{\emptyset})^I \suchthat C \implies ¬{\allleadstog}$, meaning that $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.
+
+$C$ is \emph{suitable} iff it holds and is informative and falsifiable.
 \begin{example}[To be corrected]
-Consider any $\allleadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
-Then some suitable $C$ exists, for example, $\forall i: \ar \ileadstost \phi$.
+	Assume that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
+	Then $\forall i: \ar \ileadstostg \phi$ is suitable.
+
 	Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).

### 2023-06-18 simple.tex
Corr: infinite claim is NOT fals
Anonymity

@@
 \begin{example}
-	$(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is falsifiable.
-	Consider any ${\allleadstog} \notin C$, thus satisfying $\exists k \suchthat (\ar)^k \nileadstog \phi$.
-Consider $O = \set{(i, (\ar)^k, {\allleadstog}(i, (\ar)^k) ≠ \phi)}$, thus with $O \subset {\allleadstog}$.
-We have $S_O \cap C = \emptyset$: consider any $O \subset f$, it is not in $C$.
+	$(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
+	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$.
+Pick any $\allleadstog$ such that $O \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
+We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
 \end{example}
@@
 
-$C$ is \emph{suitable} iff it holds and is informative and falsifiable.
-\begin{example}[To be corrected]
+Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in P^{I × \allhist}$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
+A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
+(TODO Alt: very strong, $\forall \allleadsto \in C, i, j \in I: \ileadsto = \jleadsto$; misses for example $\card{\set{i \suchthat \hist \ileadsto \phi}} = \frac{I}{2}$; strong: $\set{\ileadsto \suchthat \allleadsto \in C} = \set{\jleadsto \suchthat \allleadsto \in C}$; misses perhaps “if $i$ says… then $j$ says…”.)
+\begin{example}
+	Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$.
+Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
+\end{example}
+
+$C$ is \emph{suitable} iff it holds and is anonymous, informative and falsifiable.
+\begin{example}
 	Assume that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
 	Then $\forall i: \ar \ileadstostg \phi$ is suitable.
-
 	Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).

### 2023-06-18 simple.tex
Rm alt anonymity

@@
 A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
-(TODO Alt: very strong, $\forall \allleadsto \in C, i, j \in I: \ileadsto = \jleadsto$; misses for example $\card{\set{i \suchthat \hist \ileadsto \phi}} = \frac{I}{2}$; strong: $\set{\ileadsto \suchthat \allleadsto \in C} = \set{\jleadsto \suchthat \allleadsto \in C}$; misses perhaps “if $i$ says… then $j$ says…”.)
 \begin{example}

### 2023-06-21 simple.tex
Towards proving equivalence with edge case

@@
 \end{example}
+\begin{example}
+	Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
+	Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $O \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_O \cap C ≠ \emptyset$.
+\end{example}
 
@@
 
+\NewDocumentCommand{\histk}{}{α^{(k)}}
+\NewDocumentCommand{\histkend}{}{α^{(k)}_\mathit{end}}
+\NewDocumentCommand{\histl}{}{α^{(l)}}
+\NewDocumentCommand{\histlend}{}{α^{(l)}_\mathit{end}}
+\begin{theorem}[To be checked and proven!]
+	Given any $\phi \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: 
+	\begin{equation}
+		\left\{\begin{aligned}
+			&\forall i \in I, \hist \in \allhist \suchthat \ar_k \in \histend \land \hist \nileadstog \phi: \set{\histp \suchthat \hist \subseteq \histp \land \ar_l \in \histpend} \ileadstog \phi;\\
+			&\forall i \in I, \hist \in \allhist \suchthat \ar_l \in \histend \land \hist \nileadstog \phi: \set{\histp \suchthat \hist \subseteq \histp \land \ar_k \in \histpend} \ileadstog \phi.
+		\end{aligned}\right.
+	\end{equation}
+	Assume that ${\allleadsto} \in C$. Then 
+	$[\ar_k \nileadstost \phi \land \ar_l \nileadstost \phi]$ 
+	is equivalent to: 
+	\begin{equation}
+		\left\{\begin{aligned}
+			&\exists \histk \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi \land \set{\histp \suchthat \histk \subseteq \hist' \land \ar_l \in \histpend} \ileadsto \phi;\\
+			&\exists \histl \suchthat \ar_l \in \histlend \land \histl \nileadsto \phi \land \set{\histp \suchthat \histl \subseteq \hist' \land \ar_k \in \histpend} \ileadsto \phi.
+		\end{aligned}\right.
+	\end{equation}
+\end{theorem}
+\begin{remark}
+	Idea: then use contrapositive. Not cons implies some dec arg.
+	Prove equivalence to establish that we need to assume not cons to make such claims informative (in such a way).
+
+	As an example, with the shortest possible paths, we get $\histk = (\ar_k)$ and $\histl = (\ar_l)$, thus:
+	\begin{equation}
+		\left\{\begin{aligned}
+			&(\ar_k ) \nileadsto \phi \land \set{\histp \suchthat (\ar_k) \subseteq \histp \land \ar_l \in \histpend} \ileadsto \phi;\\
+			&(\ar_l) \nileadsto \phi \land \set{\histp \suchthat (\ar_l) \subseteq \histp \land \ar_k \in \histpend} \ileadsto \phi.
+		\end{aligned}\right.
+	\end{equation}
+
+	Idea: first consider that $a_l$ equals $a_j \cup a_k$ so that we can reasonably use an axiom.
+	Then in the more general case, assume $\phi$ is not in DJ at all, which also implies that $a = a_k \cup a_l$ fails; and we fall back to the same.
+\end{remark}
+\begin{remark}
+	The theorem is realistic in the following sense.
+	Some need $a_k$ only; others need $a_j \cup a_k$ (ignorant of $a_j$ at start).
+	Consider $C$ saying that if $a_k$ not convincing, then $a_j \cup a_k$ is convincing afterwards and if $a_j \cup a_k$ not convincing, then $a_k$ convincing afterwards. 
+	Define $a_l = a_j \cup a_k$.
+
+	In other words.
+	Assume that knowing both $a_j$ and $a_k$ is required to get to $\phi$.
+	Assume that $J$ knows $a_j$ and when told it, gets bored, thus not convincing. For $j$, only $a_k$ is decisive.
+	But $K$ ignores $a_j$. For $k$, only $a_j \cup a_k$ is decisive.
+%	
+%	Could have:
+%	a_k then a_l OK
+%	ak KO
+%	al KO
+%	al then ak OK
+\end{remark}
+
 Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in P^{I × \allhist}$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
@@
 
-\begin{example}[To be corrected]
-Now consider $\allleadsto$ such that $\exists J, K \subset I \suchthat \forall j \in J: \ar \ileadstost[j] \phi \land \forall k \in K: \ar' \ileadstost[k] \phi$.
-Then some suitable $C$ exists, for example, $\ar \ileadstost[j] \phi$.
+\begin{example}[To be completed]
+	Assume that $\exists \ar_j ≠ \ar_k, J, K \subset I \suchthat J \cup K = I \land \card{J} \notin \N \land \card{K} \notin \N \land \forall j \in J: \ar_j \ileadstost[j] \phi \land \forall k \in K: \ar_k \ileadstost[k] \phi \land \forall \ar \in \allargs \setminus \set{\ar_j, \ar_k}, i \in I: \ar \nileadstost \phi$.
+	Then no suitable $C$ exists?
+
+	Let’s find some suitable $C$ that shows that $\phi \in P_i$.
 \end{example}
+
+Intuition: if $a_j$ and afterwards $a_k$ is convincing, then either $a_j$ is unuseful in which case $a_k$ is decisive; or $a_j$ is useful in which case $a_j \cup a_k$ is decisive.
+However, could also be that $a_j$ is essential as first argument; thus $a_j$ is useful but $a_j \cup a_k$ is not decisive as $a'$ then $a_j \cup a_k$ is not convincing.
+Note that the latter part can be excluded by a falsifiable claim: $\nexists a' \suchthat a', a_j \cup a_k \nileadsto \phi$.
+
+The following antecedent excludes two of these three hypothesis, leaving only the one that $a_j$ is useful.
+$((a_j), …, a_k)$ convincing ; $a_k$ not decisive (or $(a_k)$ not convincing?); $\nexists \ar \suchthat [(\ar, …, a_k)$ not convincing $\land(\ar, …,  a_j \cup a_k)$ not convincing].
+The conclusion is: $a_j \cup a_k$ decisive.
+
+Is this an axiom or is this provable?
+And: is the part with $\nexists \ar$ a falsifiable claim?
 

### 2023-06-21 simple.tex
Extended thm
Rm extended thm with short expl
siffx paths

@@
 
-\NewDocumentCommand{\histk}{}{α^{(k)}}
-\NewDocumentCommand{\histkend}{}{α^{(k)}_\mathit{end}}
-\NewDocumentCommand{\histl}{}{α^{(l)}}
-\NewDocumentCommand{\histlend}{}{α^{(l)}_\mathit{end}}
-\begin{theorem}[To be checked and proven!]
+Given $\hist \in \allhist$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, \text{\ding{55}}, …, \ar_l, ?)$ denote the set $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.
+
+\begin{theorem}
 	Given any $\phi \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: 
@@
 	\end{equation}
+	In short,
+	$\forall \hist: [\ar_k \in \histend \land \hist \nileadstog \phi] \implies (\hist, …, \ar_l, ?) \ileadstog \phi$.
+	In shorter,
+	$(\hist, \ar_k, ?, \text{\ding{55}}, …, \ar_l, ?) \ileadstog \phi$, which is $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \ar_l \in \histlend \land \histk \nileadsto \phi}$.
+
 	Assume that ${\allleadsto} \in C$. Then 
@@
 \end{theorem}
+\begin{proof}
+	$\ar_k \nileadstost \phi$ iff $\exists \histk \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi$.
+\end{proof}
+\begin{remark}
+	Idea.
+	That consequence is unfalsifiable so we cannot include anything like this in $C$ (only something stronger, but of course a stronger statement could be false).
+Therefore, with no addition, we are doomed that exists some situations where no claim is suitable.
+\end{remark}
+\begin{theorem}
+	Assume that the NOT consequence holds and the claim holds.
+	Prove that there is no suitable claim.
+	If the claim is just the NOT cons and claim, then it is not fals.
+	If the claim is weaker, it does not permit to prove that $\ar_k$ or $\ar_l$ is decisive. (BUT does it possibly prove that some arg is decisive? But it may be false.)
+	If the claim is stronger, it may be false.
+\end{theorem}
 \begin{remark}
@@
 	Prove equivalence to establish that we need to assume not cons to make such claims informative (in such a way).
+	We could also attempt to prove that $\exists \ar \suchthat \ar \ileadstost \phi$ but assuming the claim $C$ is everything we know, there is no hope in proving something about some argument that we ignore.
 

### 2023-06-21 simple.tex
cross mark

@@
 
-Given $\hist \in \allhist$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, \text{\ding{55}}, …, \ar_l, ?)$ denote the set $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.
+Given $\hist \in \allhist$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, ✗, …, \ar_l, ?)$ denote the set $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.
 

### 2023-06-21 simple.tex
Further notations

@@
 
-Given $\hist \in \allhist$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, ✗, …, \ar_l, ?)$ denote the set $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.
+Given $\hist \in \allhist$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, ✗, …, \ar_l, ?)$ denote the set 
+$\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.
+Given $\ar_k, \ar_l \in \allargs$, let $(…, \ar_k, ?, ✗, …, \ar_l, ?)$ denote the set 
+$\cup_{\hist \in \allhist} (\hist, \ar_k, ?, ✗, …, \ar_l, ?) = 
+\set{\histl \suchthat \exists \hist, \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend} = 
+\set{\histl \suchthat \exists \histk \suchthat \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.
 
 \begin{theorem}
-	Given any $\phi \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: 
+	Given any $\phi \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: $\forall i \in I$,
 	\begin{equation}
 		\left\{\begin{aligned}
-			&\forall i \in I, \hist \in \allhist \suchthat \ar_k \in \histend \land \hist \nileadstog \phi: \set{\histp \suchthat \hist \subseteq \histp \land \ar_l \in \histpend} \ileadstog \phi;\\
-			&\forall i \in I, \hist \in \allhist \suchthat \ar_l \in \histend \land \hist \nileadstog \phi: \set{\histp \suchthat \hist \subseteq \histp \land \ar_k \in \histpend} \ileadstog \phi.
+			&\forall \histk \in \allhist \suchthat \ar_k \in \histkend \land \histk \nileadstog \phi: \set{\histl \suchthat \histk \subseteq \histl \land \ar_l \in \histlend} \ileadstog \phi;\\
+			&\forall \hist \in \allhist \suchthat \ar_l \in \histend \land \hist \nileadstog \phi: \set{\histp \suchthat \hist \subseteq \histp \land \ar_k \in \histpend} \ileadstog \phi.
 		\end{aligned}\right.

### 2023-06-21 simple.tex
Reasonably condensed

--- 2023-06-21 simple.tex
@@
 
-Given $\hist \in \allhist$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, ✗, …, \ar_l, ?)$ denote the set $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.
+Given $\histk \in \allhist$ and $\ar_l \in \allargs$, let $(\histk, …, \ar_l, ?)$ denote the set 
+$\set{\histl \suchthat \histk \subset \histl \land \ar_l \in \histlend}$.
+Given $\hist \in \allhist$, ${\ileadstog}$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set 
+$\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
+Given $\ar_k, \ar_l \in \allargs$, let 
+$(…, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set 
+$\cup_{\hist \in \allhist} (\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?) = 
+\set{\histl \suchthat \exists \hist, \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend} = 
+\set{\histl \suchthat \exists \histk \suchthat \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
+Given ${\ileadstog}$, $p \in P$ and $S \subseteq \allargs$, let $S \ileadstog p$ stand for $\forall s \in S: s \ileadstog p$ and $s \in S \ileadstog p$ stand for $s \in \set{s \in S \suchthat s \ileadstog p}$.
 
 \begin{theorem}
-	Given any $\phi \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: 
+	Given any $\phi \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: $\forall i \in I$,
 	\begin{equation}
 		\left\{\begin{aligned}
-			&\forall i \in I, \hist \in \allhist \suchthat \ar_k \in \histend \land \hist \nileadstog \phi: \set{\histp \suchthat \hist \subseteq \histp \land \ar_l \in \histpend} \ileadstog \phi;\\
-			&\forall i \in I, \hist \in \allhist \suchthat \ar_l \in \histend \land \hist \nileadstog \phi: \set{\histp \suchthat \hist \subseteq \histp \land \ar_k \in \histpend} \ileadstog \phi.
+			&(…, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?) \ileadstog \phi;\\
+			&\forall \histk \in (…, \ar_k, ?) \suchthat \histk \nileadstog \phi: (\histk, …, \ar_l, ?) \ileadstog \phi;\\
+			&(…, \ar_l, ?, \nileadstog \phi, …, \ar_k, ?) \ileadstog \phi.
 		\end{aligned}\right.
 	\end{equation}
-	In short,
-	$\forall \hist: [\ar_k \in \histend \land \hist \nileadstog \phi] \implies (\hist, …, \ar_l, ?) \ileadstog \phi$.
-	In shorter,
-	$(\hist, \ar_k, ?, \text{\ding{55}}, …, \ar_l, ?) \ileadstog \phi$, which is $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \ar_l \in \histlend \land \histk \nileadsto \phi}$.
+	(The first two statements are equivalent.)
 
@@
 		\left\{\begin{aligned}
-			&\exists \histk \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi \land \set{\histp \suchthat \histk \subseteq \hist' \land \ar_l \in \histpend} \ileadsto \phi;\\
-			&\exists \histl \suchthat \ar_l \in \histlend \land \histl \nileadsto \phi \land \set{\histp \suchthat \histl \subseteq \hist' \land \ar_k \in \histpend} \ileadsto \phi.
+			&\exists \histk \in (…, \ar_k, ?) \suchthat \histk \nileadsto \phi \land (\histk, …, \ar_l, ?) \ileadsto \phi;\\
+			&\exists \histl \in (…, \ar_l, ?) \suchthat \histl \nileadsto \phi \land (\histl, …, \ar_k, ?) \ileadsto \phi.
 		\end{aligned}\right.

### 2023-06-21 simple.tex
Denser
Much denser

@@
 \begin{theorem}
-	Given any $\phi \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: $\forall i \in I$,
-	\begin{equation}
-		\left\{\begin{aligned}
-			&(…, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?) \ileadstog \phi;\\
-			&\forall \histk \in (…, \ar_k, ?) \suchthat \histk \nileadstog \phi: (\histk, …, \ar_l, ?) \ileadstog \phi;\\
-			&(…, \ar_l, ?, \nileadstog \phi, …, \ar_k, ?) \ileadstog \phi.
-		\end{aligned}\right.
-	\end{equation}
-	(The first two statements are equivalent.)
+	Given any $p \in P, \ar_k, \ar_l \in \allargs$, consider the claim $C = \forall i \in I, \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l},
+\forall \hist \in (…, \ar_1, ?) \nileadstog p: (\hist, …, \ar_2, ?) \ileadstog p$.
 
 	Assume that ${\allleadsto} \in C$. Then 
-	$[\ar_k \nileadstost \phi \land \ar_l \nileadstost \phi]$ 
+	$[\ar_k \nileadstost p \land \ar_l \nileadstost p]$ 
 	is equivalent to: 
 	\begin{equation}
-		\left\{\begin{aligned}
-			&\exists \histk \in (…, \ar_k, ?) \suchthat \histk \nileadsto \phi \land (\histk, …, \ar_l, ?) \ileadsto \phi;\\
-			&\exists \histl \in (…, \ar_l, ?) \suchthat \histl \nileadsto \phi \land (\histl, …, \ar_k, ?) \ileadsto \phi.
-		\end{aligned}\right.
+		\forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l}:
+		\exists \hist \in (…, \ar_1, ?) \nileadsto p \suchthat (\hist, …, \ar_2, ?) \ileadsto p.
 	\end{equation}
@@
 \begin{proof}
-	$\ar_k \nileadstost \phi$ iff $\exists \histk \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi$.
+	$\ar_k \nileadstost p$ iff $\exists \hist \suchthat \ar_k \in \histend \land \hist \nileadsto p$.
 \end{proof}

### 2023-07-28 simple.tex
Suitable

@@
 
+$C$ is \emph{suitable} iff it holds and is anonymous, informative and falsifiable.
+\begin{example}
+	Assume that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
+	Then $\forall i: \ar \ileadstostg \phi$ is suitable.
+	Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
+\end{example}
+
 \begin{theorem}
-	Given any $p \in P, \ar_k, \ar_l \in \allargs$, consider the claim $C = \forall i \in I, \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l},
-\forall \hist \in (…, \ar_1, ?) \nileadstog p: (\hist, …, \ar_2, ?) \ileadstog p$.
-
+	Given any $p \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: 
+	\begin{equation}
+		\label{eq:cl}
+		\forall i \in I, \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l},
+		\forall \hist \in (…, \ar_1, ?) \nileadstog p: (\hist, …, \ar_2, ?) \ileadstog p.
+	\end{equation}
 	Assume that ${\allleadsto} \in C$. Then 
-	$[\ar_k \nileadstost p \land \ar_l \nileadstost p]$ 
+	$\exists i \in I \suchthat [\ar_k \nileadstost p \land \ar_l \nileadstost p]$ 
 	is equivalent to: 
 	\begin{equation}
-		\forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l}:
+		\exists i \in I \suchthat \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l}:
 		\exists \hist \in (…, \ar_1, ?) \nileadsto p \suchthat (\hist, …, \ar_2, ?) \ileadsto p.
@@
 \end{remark}
-\begin{theorem}
+\begin{theorem}[Informal]
 	Assume that the NOT consequence holds and the claim holds.
@@
 \end{theorem}
+\begin{theorem}[Formal]
+	Pick any $\ar_k ≠ \ar_l$ and $p \in P$ and assume that $\allleadsto$ fails the above consequence, that is, satisfies:
+	\begin{equation}
+		\label{eq:answerable}
+		\forall i \in I, \exists \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l} \land
+		\forall \hist \in (…, \ar_1, ?) \nileadsto p: (\hist, …, \ar_2, ?) \nileadsto p.
+	\end{equation}
+	Assume further that $\allleadsto$ satisfies \eqref{eq:cl}, thus:
+	$\forall i \in I, \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l},
+\forall \hist \in (…, \ar_1, ?) \nileadsto p: (\hist, …, \ar_2, ?) \ileadsto p$.
+	Then, there is no suitable claim.
+\end{theorem}
+\begin{proof}
+	Note that $\allleadsto$ satisfies, $\forall i \in I, \exists \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l} \land \forall \hist \in (…, \ar_1, ?): \hist \ileadsto p$; equivalently, $\ar_k \ileadstost p \lor \ar_l \ileadstost p$.
+
+	Assume the claim is just \eqref{eq:cl} $\land$ \eqref{eq:answerable}. Then if is not fals. 
+%	Intuitively, because it might require (with $\hist = (\ar_1)$) to observe that for a given $i$, $(a_1) \nileadsto p \land (\ar_1, \ar_2) \ileadsto p$ and also $(\ar_2) \nileadsto p \land (\ar_2, \ar_1) \ileadsto p$.
+	We need to exhibit some ${\allleadstog} \notin C$ such that $\forall O \subseteq {\allleadstog}: S_O \cap C ≠ \emptyset$.
+	Define $\allleadstog$ as, $\forall i \in I$, $(\ar_k) \nileadstog p, (\ar_l) \nileadstog p, \forall \hist \in \allhist \setminus \set{(\ar_k), (\ar_l)}: \hist \ileadstog p$.
+	It follows that $\ar_k \nileadstog p \land \ar_l \nileadstog p$. Thus, ${\allleadstog} \notin C$.
+	Now pick any $O \subseteq {\allleadstog}$. The set $O$ can’t have both $(\ar_k) \nileadstog p$ and $(\ar_l) \nileadstog p$.
+	Assume, wlog, that $(\ar_k, i, {\allleadstog}(\ar_k, i)) \notin O$.
+%	Then, intuitively, $\ar_k$ decisive is in $S_O \cap C$.
+	Pick any $p' ≠ p$ and define $\allleadstog'$ as, $\forall i \in I: \forall \hist \in \allhist \setminus \set{(\ar_l)}, \hist \ileadstog' p \land (\ar_l) \ileadstog' p' ≠ p$.
+	We have ${\allleadstog'} \in S_O \cap C$, which concludes [NB need to do it for each $i$, instead].
+
+	If the claim is sufficiently stronger (to be falsifiable) than this (thus with $C' \subset C$, thus with ${\allleadstog} \notin C'$ as defined above), then it may be false.
+	Indeed, to be falsifiable, we need ${\allleadstog'} \notin C'$.
+	Now we need $C'$ to hold so it must contain ${\allleadsto}$ but not contain ${\allleadstog'}$.
+It does not contain ${\allleadstog'}$ iff it implies $¬(\land_{\hist \in \allhist \setminus \set{(\ar_l)}} \hist \ileadstog' p \land (\ar_l) \ileadstog' p')$.
+	%So it must claim that $\ar_l$ is not decisive. Or something like, for some $\hist_1$: if $\ar_l \ileadstog' p'$, then $\hist_1 \ileadstog' ¬p$.
+
+	Intuitively, need that when we do not observe $(\ar_k)$ for a given $i$, but only $(\ar_l)$ for that $i$, the claim says something contrary about that $(\ar_l, i)$. 
+\end{proof}
 \begin{remark}
@@
 Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
-\end{example}
-
-$C$ is \emph{suitable} iff it holds and is anonymous, informative and falsifiable.
-\begin{example}
-	Assume that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
-	Then $\forall i: \ar \ileadstostg \phi$ is suitable.
-	Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
 \end{example}

### 2023-08-23 simple.tex
Shorter notation

@@
 	$(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
-	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$.
+	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in O$, and $l = 1$ otherwise.
 Pick any $\allleadstog$ such that $O \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
@@
 \set{\histl \suchthat \exists \histk \suchthat \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
-Given ${\ileadstog}$, $p \in P$ and $S \subseteq \allargs$, let $S \ileadstog p$ stand for $\forall s \in S: s \ileadstog p$ and $s \in S \ileadstog p$ stand for $s \in \set{s \in S \suchthat s \ileadstog p}$.
+Given ${\ileadstog}$, $p \in P$, $s \in \allargs$ and $S \subseteq \allargs$, note that $s \in \ileadstoinvg(p)$ stand for $s \ileadstog p$ and $S \subseteq \ileadstoinvg(p)$ stand for $\forall s \in S: s \ileadstog p$.
 
@@
 	Given any $p \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: 
-	\begin{equation}
+	\begin{multline}
 		\label{eq:cl}
 		\forall i \in I, \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l},
-		\forall \hist \in (…, \ar_1, ?) \nileadstog p: (\hist, …, \ar_2, ?) \ileadstog p.
-	\end{equation}
+		\forall \hist \in (…, \ar_1, ?) \cap \nileadstoinvg(p): \\
+		(\hist, …, \ar_2, ?) \subseteq \ileadstoinvg(p).
+	\end{multline}
 	Assume that ${\allleadsto} \in C$. Then 
@@
 	is equivalent to: 
-	\begin{equation}
-		\exists i \in I \suchthat \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l}:
-		\exists \hist \in (…, \ar_1, ?) \nileadsto p \suchthat (\hist, …, \ar_2, ?) \ileadsto p.
-	\end{equation}
+	\begin{multline}
+		\label{eq:cln}
+		\exists i \in I \suchthat \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l}:\\
+		\exists \hist \in (…, \ar_1, ?) \cap \nileadstoinv(p) \suchthat
+		(\hist, …, \ar_2, ?) \subseteq \ileadstoinv(p).
+	\end{multline}
 \end{theorem}
@@
 \end{remark}
+\begin{theorem}
+	The claim \eqref{eq:cl} and not \eqref{eq:cln}, thus, \eqref{eq:cl} and $\forall i, \ar_k \ileadstostg p \lor \ar_l \ileadstostg p$ is not falsifiable.
+\end{theorem}
+\begin{proof}
+
+\end{proof}
 \begin{theorem}[Informal]
@@
 \begin{theorem}[Formal]
-	Pick any $\ar_k ≠ \ar_l$ and $p \in P$ and assume that $\allleadsto$ fails the above consequence, that is, satisfies:
-	\begin{equation}
+	Pick any $p \in P$ and $\ar_k ≠ \ar_l \in \allargs$ and assume that $\allleadsto$ fails \cref{eq:cln}, that is, satisfies:
+	\begin{multline}
 		\label{eq:answerable}
-		\forall i \in I, \exists \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l} \land
-		\forall \hist \in (…, \ar_1, ?) \nileadsto p: (\hist, …, \ar_2, ?) \nileadsto p.
-	\end{equation}
+		\forall i \in I, \exists \set{\ar_1, \ar_2} \suchthat
+		\set{\ar_1, \ar_2} = \set{\ar_k, \ar_l} \\ \land
+		\forall \hist \in (…, \ar_1, ?) \cap \nileadstoinv(p): 
+		(\hist, …, \ar_2, ?) \nsubseteq \nileadstoinv(p).
+	\end{multline}
 	Assume further that $\allleadsto$ satisfies \eqref{eq:cl}, thus:
 	$\forall i \in I, \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l},
-\forall \hist \in (…, \ar_1, ?) \nileadsto p: (\hist, …, \ar_2, ?) \ileadsto p$.
+\forall \hist \in (…, \ar_1, ?) \cap \nileadstoinv(p): (\hist, …, \ar_2, ?) \subseteq \ileadstoinv(p)$.
 	Then, there is no suitable claim.

### 2023-10-09 simple.tex
Branched while forgetting crashed version

@@
 This article is interested in defining the concept of deliberated judgement of a subject and show how one can study it in an empirical manner.
-The “classical” counterpart of deliberated judgments,, that does not involve confrontation with arguments, will henceforth be called the natural judgment.
+The “classical” counterpart of deliberated judgments, that does not involve confrontation with arguments, will henceforth be called the natural judgment.
 As we deal with choice acts, we will also name the concept “deliberated choice”, as opposed to “natural choice”.
@@
 We can observe set $O$ that forms a function $f(i) = \set{\alpha \ileadsto \phi, \alpha' \ileadsto ¬\phi, …}$, with $\alpha \subset \alpha \subset …$ and with finite $O$.
-Our second condition is that $¬C \implies \exists O \suchthat O \implies ¬C$.
+Our second condition is that $¬C \implies \exists θ \suchthat θ \implies ¬C$.
 For example, if $C$ is $\alpha \ileadsto \phi \lor \beta \allleadsto[j] \phi$, $O$ is $\alpha \ileadsto ¬\phi \land \beta \allleadsto ¬\phi$, then $O$ implies $¬C$.
@@
 Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq P^{I × \allhist}$.
-When writing $C$ as a formula, it is intended to mean the set $\set{{\allleadstog} \in P^{I × \allhist} \suchthat C({\allleadstog})}$.
+Given a formula $\psi$, let the corresponding claim be $C_\psi = \set{{\allleadstog} \in P^{I × \allhist} \suchthat {\allleadstog} \text{ satisfies } \psi}$.
+A claim is finite iff its cardinal is finite (meaning that it is compatible with a finite number of possibilities).
 
-Given a pair $(I, \allargs)$, a general observation $O$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in O: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
+Given a pair $(I, \allargs)$, a general observation $θ$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
 General observations are the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
-Let $S_O = \set{{\allleadstog} \in P^{I × \allhist} \suchthat O \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
+Let $S_θ = \set{{\allleadstog} \in P^{I × \allhist} \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
 
-A claim $C$ is falsifiable iff $\exists O \suchthat O \implies ¬C$, by which I mean $S_O \cap C = \emptyset$.
+\begin{definition}
+  We say that $C$ is \emph{syntactically falsifiable}, or just falsifiable, iff
+  %$\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
+  $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset$.
+\end{definition}
 \begin{example}
   $(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
-%	Its negation is $\forall k: (\ar^k) \nileadsto \phi$.
-%	The claim represents the set $\set{{\allleadsto} \in P^{I × \allhist} \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
-	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$.
-Pick any $\allleadstog$ such that $O \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
-We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
-\end{example}
-\begin{example}
-	$(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
-	Given any $O$, it may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $\allleadstog$ such that $O \subset {\allleadstog} \land t \in {\allleadstog}$.
-We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
-\end{example}
-\begin{example}[Fals. but shouldn’t]
-	\label{ex:fbs}
-	$\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is falsifiable.
-	Consider $O = \set{(j, \hist, ¬\phi)}$.
-\end{example}
-\begin{example}
-	$\forall i: \ar \ileadstostg \phi$ is falsifiable.
-	Consider any $i \in I$ and $O = \set{(i, (\ar), ¬\phi)}$.
-\end{example}
-\Cref{ex:fbs} shows that this definition of falsifiability is wrong.
-
-We now say that $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists O \subseteq {\allleadstog} \suchthat O \implies ¬C$, meaning that
-$\forall {\allleadstog} \notin C: \exists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset$.
-\begin{example}
-	$(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
-	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in O$, and $l = 1$ otherwise.
-Pick any $\allleadstog$ such that $O \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
-We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
+  Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise.
+Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
+We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
 \end{example}
@@
   Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
-	Consider any $O \subseteq {\allleadstog}$ and let us prove that $S_O \cap C ≠ \emptyset$.
-	By definition of a general observation, $O$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any ${\allleadstog'}$ such that $O \subset {\allleadstog'} \land t \in {\allleadstog'}$.
-We have ${\allleadstog'} \in S_O \cap C ≠ \emptyset$.
+  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $S_θ \cap C ≠ \emptyset$.
+  By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$.
+We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
 \end{example}
@@
   Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
-	Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $O = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
+  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
 \end{example}
@@
   Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
-	Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $O \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_O \cap C ≠ \emptyset$.
+  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_θ \cap C ≠ \emptyset$.
+\end{example}
+\begin{example}
+  Consider any $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_1) \ileadstog^2 p'$.
+  The claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$ is unfalsifiable.
+
+  Consider … (seems redundant).
+\end{example}
+\begin{remark}
+  The claim “For each glass, it will not break on a monday or not break on a tuesday, whatever happens to it.” is not falsifiable.
+But one can make it stronger and falsify it, by giving a general theory of how glasses break, proving that it holds, and that it is not compatible with the claim.
+I should think about this.
+\end{remark}
+\begin{remark}
+  To be falsifiable, I need each time I exclude some relation $R$ to also exclude a subset $Cbar$ such that some $O \subseteq R$ satisfies $S_O$ is entirely in $Cbar$.
+\end{remark}
+\begin{theorem}
+  A claim $C$ is falsifiable iff its complement $\Cbar$ satisfies:
+  $\forall {\allleadstog} \in \Cbar, \exists O \subseteq {\allleadstog} \suchthat S_O \subseteq \Cbar$, or equivalently:
+  $\forall {\allleadstog} \in \Cbar, \exists O \subseteq {\allleadstog} \suchthat S_O \subseteq \Cbar$.
+\end{theorem}
+
+Let $E \subseteq I × \allhist$ denote an observable compatible set. It is downwards closed.
+Let $M$ denote a maximal $E$.
+Any $M$ maps each individual $i \in I$ to an increasing sequence.
+Given ${\allleadsto}$, let $E_{\allleadsto} \subseteq {\allleadsto}$ denote the observable compatible sets (triples, not pairs, thus including values).
+These are the $E$ to which the value associated is the one given by $\allleadsto$.
+Define similarly $M_{\allleadsto}$.
+Let $X_C \subseteq I × \allhist × P$ denote a subset that is completable to some ${\allleadsto}$ in $C$. It is downwards closed.
+Let $N_C$ denote a maximal such subset.
+A claim is not falsifiable iff $\exists {\allleadsto} \notin C \suchthat$ each $E_{\allleadsto}$ equals some $X_C$.
+A claim is not falsifiable iff $\exists {\allleadsto} \notin C \suchthat$ each $M_{\allleadsto}$ equals some $X_C$.
+A claim is not falsifiable iff it is possible to pick some $M_{\allleadsto_1}$ from $C$ (that is, a mapping of each individual to an increasing sequence, together with the associated value from $\allleadsto_1$), some other $M_{\allleadsto_2}$ from $C$, and on their common entries (if any) these two relations agree (so their union is a right-unique relation), and so on for each possible mappings $M$, so as to form a complete $\allleadsto$ that is not in $C$.
+A claim is falsifiable iff it is closed under the above picking operation.
+Equivalently, a claim is not falsifiable iff this can be done for a given number of $M$ whose union is not an $X_C$.
+We could need more than two such $M$'s, I suppose: for the theorem below, the number of such $M$'s is equal to the cardinal of the set on which they differ.
+TODO what about finiteness of observables? Might fail falsifiability because only infinite obs would falsify.
+
+Any claim containing two relations that differ only on incompatible observations is not falsifiable.
+\begin{theorem}
+  Any $C$ such that $\exists {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$) and the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, does not contain two elements that are simultaneously observable (meaning that no $θ$ contains more than one of these elements), is not falsifiable.
+\end{theorem}
+\begin{proof}
+  Consider any $θ \subset {\allleadstog}$.
+  If $θ$ is fully compatible with ${\allleadstog^1}$, then ${\allleadstog^1} \in S_θ \cap C ≠ \emptyset$.
+  Otherwise, $θ$ contains some element $(i, \hist, {\allleadstog^2}(i, \hist))$ with ${\allleadstog^2}(i, \hist) ≠ {\allleadstog^1}(i, \hist)$.
+Then, ${\allleadstog^2} \in S_θ \cap C ≠ \emptyset$, for otherwise, for at least one other element $(i', \histp)$, $θ$ contains $(i', \histp, {\allleadstog^1}(i', \histp))$ with ${\allleadstog^1}(i', \histp) ≠ {\allleadstog^2}(i', \histp)$, which violates the hypothesis.
+\end{proof}
+The following example illustrates the need for the condition about the combination in the theorem.
+\begin{example}
+  Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhist$ with $\hist$ and $\histp$ non prefix related.
+  The claim $\psi = (\hist \ileadstog p \lor \hist \ileadstog p') \land (\histp \ileadstog p \lor \histp \ileadstog p') \land (\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p)$ is falsifiable.
+
+  Given $q, q' \in P$, let ${\allleadstog^{q, q'}}$ be defined as $\hist \ileadstog^{q, q'} q$, $\histp \ileadstog q'$ and $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p$.
+  Note that $C_\psi = \set{{\allleadstog^{p, p}}, {\allleadstog^{p, p'}}, {\allleadstog^{p', p}}, {\allleadstog^{p', p'}}}$.
 \end{example}
 
+\begin{conjecture}
+  If a claim $C$ is not falsifiable, then $\exists {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$) and the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, does not contain two elements that are simultaneously observable (meaning that no $θ$ contains more than one of these elements).
+\end{conjecture}
+\begin{conjecture}
+  If $\forall {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$), the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, contains at least two elements that are simultaneously observable (meaning that some $θ$ contains more than one of these elements), then $C$ is falsifiable.
+\end{conjecture}
+\begin{proof}
+  We need a stronger hypothesis.
+  Consider $one$ and $two$ differ on $(i, (a))$, $(i, (b))$ and $(i, (a, a))$.
+And some $three$ not in $C$ has $(i, (a)), (i, (a, a))$ as in $one$ and $(i, (b))$ as in $two$.
+Then $C$ is not falsifiable.
+\end{proof}
+\begin{conjecture}
+  If $\forall {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$), the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, we can find some $(i, \hist) \in {\allleadstog^1}, (j, \hist') \in {\allleadstog^2}$ obs-compatible, then $C$ is falsifiable.
+\end{conjecture}
+\begin{proof}
+  This fails.
+Could have $one$, $two$, $three$, each sending everything to $p$, $¬p$ and $0$, respectively, and any combination of two of these in $C$, but no comb of three in $C$.
+Then $four$ a combination of the three ($i, a, p, i, b, ¬p, i, c, 0$), but $C$ not falsifiable.
+Actually, even if we can observe two among the three (using $i, a, p, i, aa, ¬p, i, b, 0$), we can’t falsifiy $four$.
+\end{proof}
+
 Given an exposure protocol $\allleadsto$, we say that a claim $C$ \emph{holds} iff $C \ni {\allleadsto}$.
+We say that $C$ is \emph{empirically falsifiable} iff $\exists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset$.
 
-The following theorem verifies that when $C$ holds, it will not be falsified ex post (though it may be (a priori) falsifiable).
+The following theorem verifies that when $C$ holds, it is not empirically falsifiable (though it may be syntactically falsifiable).
 \begin{theorem}
   \label{th:ex-post}
-	$\forall C \ni {\allleadsto}: \nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset$.
+  $\forall C \ni {\allleadsto}: \nexists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset$.
 \end{theorem}
 \begin{proof}
-	We have, $\forall C \suchthat C \ni {\allleadsto}, \forall O \subseteq {\allleadsto}$: $O \subseteq {\allleadsto} \in C$, equivalently, ${\allleadsto} \in S_O \cap C$, thus $S_O \cap C ≠ \emptyset$.
+  We have, $\forall C \suchthat C \ni {\allleadsto}, \forall θ \subseteq {\allleadsto}$: $θ \subseteq {\allleadsto} \in C$, equivalently, ${\allleadsto} \in S_θ \cap C$, thus $S_θ \cap C ≠ \emptyset$.
 \end{proof}
-Therefore, falsifiability guarantees that a claim holds if, and only if, it is not a posteriori falsifiable. (TODO syntactically fals VS empirically fals.)
+Therefore, synctactic falsifiability guarantees that a claim holds if, and only if, it is not empirically falsifiable.
 \begin{theorem}
   \label{th:holdsiff}
-	For all falsifiable $C$: ${\allleadsto} \in C$ iff $\nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset$.
+  For all syntactically falsifiable $C$: ${\allleadsto} \in C$ iff $\nexists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset$.
 \end{theorem}
 \begin{proof}
-	Consider any falsifiable $C$.
-	By definition of falsifiability, $\forall {\allleadstog}: \nexists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset \implies {\allleadstog} \in C$.
+  Consider any syntactically falsifiable $C$.
+  By definition of falsifiability, $\forall {\allleadstog}: \nexists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset \implies {\allleadstog} \in C$.
   In particular,
-	$\nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset \implies {\allleadsto} \in C$.
+  $\nexists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset \implies {\allleadsto} \in C$.
   The reverse implication is proven by \cref{th:ex-post}.
@@
 
+\begin{definition}[Anonymity]
+  Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in P^{I × \allhist}$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
+  A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
+\end{definition}
+\begin{example}
+  Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$.
+Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
+\end{example}
+
+$C$ is \emph{suitable} iff it holds and is anonymous, informative and falsifiable.
+\begin{example}
+  Assume that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
+  Then $\forall i: \ar \ileadstostg \phi$ is suitable.
+  Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
+\end{example}
+
+Our goal now is to find an exposure protocol $\allleadsto$ with no suitable claim.
+
+\subsection{Ideas for no suitable}
 Given $\histk \in \allhist$ and $\ar_l \in \allargs$, let $(\histk, …, \ar_l, ?)$ denote the set
@@
 Given ${\ileadstog}$, $p \in P$, $s \in \allargs$ and $S \subseteq \allargs$, note that $s \in \ileadstoinvg(p)$ stand for $s \ileadstog p$ and $S \subseteq \ileadstoinvg(p)$ stand for $\forall s \in S: s \ileadstog p$.
-
-$C$ is \emph{suitable} iff it holds and is anonymous, informative and falsifiable.
-\begin{example}
-	Assume that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
-	Then $\forall i: \ar \ileadstostg \phi$ is suitable.
-	Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
-\end{example}
 
@@
 \begin{theorem}
-	The claim \eqref{eq:cl} and not \eqref{eq:cln}, thus, \eqref{eq:cl} and $\forall i, \ar_k \ileadstostg p \lor \ar_l \ileadstostg p$ is not falsifiable.
+  Pick any $p \in P$ and $\ar_k ≠ \ar_l \in \allargs$ and consider the claim \eqref{eq:cl} and not \eqref{eq:cln}, thus, \eqref{eq:cl} and $\forall i, \ar_k \ileadstostg p \lor \ar_l \ileadstostg p$.
+It is not falsifiable.
 \end{theorem}
 \begin{proof}
-
+  %	Intuitively, because it might require (with $\hist = (\ar_1)$) to observe that for a given $i$, $(a_1) \nileadsto p \land (\ar_1, \ar_2) \ileadsto p$ and also $(\ar_2) \nileadsto p \land (\ar_2, \ar_1) \ileadsto p$.
+  We need to exhibit some ${\allleadstog} \notin C$ such that $\forall θ \subseteq {\allleadstog}: S_θ \cap C ≠ \emptyset$.
+  Define $\allleadstog$ as, $\forall i \in I$, $(\ar_k) \nileadstog p, (\ar_l) \nileadstog p, \forall \hist \in \allhist \setminus \set{(\ar_k), (\ar_l)}: \hist \ileadstog p$.
+  It follows that $\ar_k \nileadstostg p \land \ar_l \nileadstostg p$. Thus, ${\allleadstog} \notin C$.
+  Now pick any $θ \subseteq {\allleadstog}$.
+  % The set $O$ can’t have both $(\ar_k) \nileadstog p$ and $(\ar_l) \nileadstog p$.
+  % Assume, wlog, that $(\ar_k, i, {\allleadstog}(\ar_k, i)) \notin O$.
+  %	Then, intuitively, $\ar_k$ decisive is in $S_θ \cap C$.
+  Define $\allleadstog'$ as, $\forall i \in I: \forall \hist \in \allhist \setminus \set{(\ar_k), (\ar_l)}, \hist \ileadstog' p$
+  and $\forall \ar \in \set{\ar_k, \ar_l}$, $(\ar) \ileadstog' ({\allleadstog}(\ar, i))$ if $(\ar, i, {\allleadstog}(\ar, i)) \in O$, $(\ar) \ileadstog' p$ otherwise.
+  %Pick any $p' ≠ p$ and define $\allleadstog'$ as, $\forall i \in I: \forall \hist \in \allhist \setminus \set{(\ar_l)}, \hist \ileadstog' p \land (\ar_l) \ileadstog' p' ≠ p$.
+  The set $O$ can’t have both $(\ar_k) \nileadstog p$ and $(\ar_l) \nileadstog p$, thus, ${\allleadstog'} \in C$.
+  We conclude that ${\allleadstog'} \in S_θ \cap C$.
 \end{proof}
@@
     \label{eq:answerable}
-		\forall i \in I, \exists \set{\ar_1, \ar_2} \suchthat
-		\set{\ar_1, \ar_2} = \set{\ar_k, \ar_l} \\ \land
-		\forall \hist \in (…, \ar_1, ?) \cap \nileadstoinv(p): 
-		(\hist, …, \ar_2, ?) \nsubseteq \nileadstoinv(p).
+    \forall i \in I, \exists \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l} \suchthat
+    \forall \hist \in (…, \ar_1, ?) \cap \nileadstoinv(p): \\
+    (\hist, …, \ar_2, ?) \cap \ileadstoinv(p) ≠ \emptyset.
   \end{multline}
@@
   Assume the claim is just \eqref{eq:cl} $\land$ \eqref{eq:answerable}. Then if is not fals.
-%	Intuitively, because it might require (with $\hist = (\ar_1)$) to observe that for a given $i$, $(a_1) \nileadsto p \land (\ar_1, \ar_2) \ileadsto p$ and also $(\ar_2) \nileadsto p \land (\ar_2, \ar_1) \ileadsto p$.
-	We need to exhibit some ${\allleadstog} \notin C$ such that $\forall O \subseteq {\allleadstog}: S_O \cap C ≠ \emptyset$.
-	Define $\allleadstog$ as, $\forall i \in I$, $(\ar_k) \nileadstog p, (\ar_l) \nileadstog p, \forall \hist \in \allhist \setminus \set{(\ar_k), (\ar_l)}: \hist \ileadstog p$.
-	It follows that $\ar_k \nileadstog p \land \ar_l \nileadstog p$. Thus, ${\allleadstog} \notin C$.
-	Now pick any $O \subseteq {\allleadstog}$. The set $O$ can’t have both $(\ar_k) \nileadstog p$ and $(\ar_l) \nileadstog p$.
-	Assume, wlog, that $(\ar_k, i, {\allleadstog}(\ar_k, i)) \notin O$.
-%	Then, intuitively, $\ar_k$ decisive is in $S_O \cap C$.
-	Pick any $p' ≠ p$ and define $\allleadstog'$ as, $\forall i \in I: \forall \hist \in \allhist \setminus \set{(\ar_l)}, \hist \ileadstog' p \land (\ar_l) \ileadstog' p' ≠ p$.
-	We have ${\allleadstog'} \in S_O \cap C$, which concludes [NB need to do it for each $i$, instead].
 
@@
     \left\{\begin{aligned}
-			&(\ar_k ) \nileadsto \phi \land \set{\histp \suchthat (\ar_k) \subseteq \histp \land \ar_l \in \histpend} \ileadsto \phi;\\
-			&(\ar_l) \nileadsto \phi \land \set{\histp \suchthat (\ar_l) \subseteq \histp \land \ar_k \in \histpend} \ileadsto \phi.
+       & (\ar_k ) \nileadsto \phi \land \set{\histp \suchthat (\ar_k) \subseteq \histp \land \ar_l \in \histpend} \ileadsto \phi; \\
+       & (\ar_l) \nileadsto \phi \land \set{\histp \suchthat (\ar_l) \subseteq \histp \land \ar_k \in \histpend} \ileadsto \phi.
     \end{aligned}\right.
@@
 
-Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in P^{I × \allhist}$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
-A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
-\begin{example}
-	Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$.
-Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
-\end{example}
-
 \begin{example}[To be completed]
@@
   And: is the part with $\nexists \ar$ a falsifiable claim?
+
+  \subsection{Alternative definition of syntactic falsifiability}
+  A claim $C$ is attempt-falsifiable iff $\exists θ \suchthat θ \implies ¬C$, by which I mean $S_θ \cap C = \emptyset$.
+  \begin{example}
+    $(\ar) \ileadstog \phi \lor (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
+    %	Its negation is $\forall k: (\ar^k) \nileadsto \phi$.
+    %	The claim represents the set $\set{{\allleadsto} \in P^{I × \allhist} \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
+    Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$.
+Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
+We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
+  \end{example}
+  \begin{example}
+    $(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
+    Given any $O$, it may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land t \in {\allleadstog}$.
+We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
+  \end{example}
+  \begin{example}[Fals. but shouldn’t]
+    \label{ex:fbs}
+    $\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is falsifiable.
+    Consider $θ = \set{(j, \hist, ¬\phi)}$.
+  \end{example}
+  \begin{example}
+    $\forall i: \ar \ileadstostg \phi$ is falsifiable.
+    Consider any $i \in I$ and $θ = \set{(i, (\ar), ¬\phi)}$.
+  \end{example}
+  \Cref{ex:fbs} shows that this definition of falsifiability is wrong.
 
@@
       \left.\begin{aligned}
-			&\ar_1 = \arga \\
-			&\forall 1 ≤ j < n: \ar_{j + 1} = \dg(\ar_j, α_{\intvl{1, k_j}}) \in \histbend{k_{j + 1}} \\
-			&\forall 1 ≤ j ≤ n: \restr{\hist}{\intvl{1, k_j}} \nileadsto \pga
+         & \ar_1 = \arga                                                                            \\
+         & \forall 1 ≤ j < n: \ar_{j + 1} = \dg(\ar_j, α_{\intvl{1, k_j}}) \in \histbend{k_{j + 1}} \\
+         & \forall 1 ≤ j ≤ n: \restr{\hist}{\intvl{1, k_j}} \nileadsto \pga
       \end{aligned}\right\}
@@
       \left.\begin{aligned}
-			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
-			&(\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
-			&(\ar_5, \ar_2, \ar) \nileadsto \pga
+         & (\ar_4, \ar_2, \ar) \nileadsto \pga         \\
+         & (\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
+         & (\ar_5, \ar_2, \ar) \nileadsto \pga
       \end{aligned}\right\}
@@
     \left.\begin{aligned}
-			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
-			&(\ar_4, \ar_2, \ar, \ar_3, \ar') \ileadsto \pga \\
-			&(\ar_5, \ar_2, \ar) \nileadsto \pga\\
-			&(\ar_5, \ar_2, \ar, \ar_3, \ar') \nileadsto \pga.
+       & (\ar_4, \ar_2, \ar) \nileadsto \pga               \\
+       & (\ar_4, \ar_2, \ar, \ar_3, \ar') \ileadsto \pga   \\
+       & (\ar_5, \ar_2, \ar) \nileadsto \pga               \\
+       & (\ar_5, \ar_2, \ar, \ar_3, \ar') \nileadsto \pga.
     \end{aligned}\right\}
@@
     \left.\begin{aligned}
-			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
-			&(\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
-			&(\ar_5, \ar_2, \ar) \ileadsto \pga\\
-			&(\ar_5, \ar_2, \ar_3, \ar') \nileadsto \pga
+       & (\ar_4, \ar_2, \ar) \nileadsto \pga         \\
+       & (\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
+       & (\ar_5, \ar_2, \ar) \ileadsto \pga          \\
+       & (\ar_5, \ar_2, \ar_3, \ar') \nileadsto \pga
     \end{aligned}\right\}
@@
     \left.\begin{aligned}
-			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
-			&(\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
-			&(\ar_5, \ar_2, \ar) \ileadsto \pga
+       & (\ar_4, \ar_2, \ar) \nileadsto \pga         \\
+       & (\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
+       & (\ar_5, \ar_2, \ar) \ileadsto \pga
     \end{aligned}\right\}
@@
       \left.\begin{aligned}
-			&\hist \nileadsto \pga \\
-			&(\hist, \ar) \ileadsto \pga \\
-			&\forall \ar' \in \allargs: (\hist, \ar, \ar') \ileadsto \pga
+         & \hist \nileadsto \pga                                        \\
+         & (\hist, \ar) \ileadsto \pga                                  \\
+         & \forall \ar' \in \allargs: (\hist, \ar, \ar') \ileadsto \pga
       \end{aligned}\right\}
@@
       \left.\begin{aligned}
-			&(\hist, \ar_1, \ar) \nileadsto \pga \\
-			&(\hist, \ar_1, \ar, \ar_2) \ileadsto \pga \\
-			&(\hist, \ar_1, \ar, \ar_2, \ar) \ileadsto \pga
+         & (\hist, \ar_1, \ar) \nileadsto \pga            \\
+         & (\hist, \ar_1, \ar, \ar_2) \ileadsto \pga      \\
+         & (\hist, \ar_1, \ar, \ar_2, \ar) \ileadsto \pga
       \end{aligned}\right\}
@@
       \left\{\begin{aligned}
-			&(\hist, \ar_2) \ileadsto \pga \\
-			&(\hist, \ar_2, \ar) \ileadsto \pga \\
-			&\forall \ar': (\hist, a_2, a') \nileadsto \pga ⇒ (\hist, a_1, a') \nileadsto \pga.
+         & (\hist, \ar_2) \ileadsto \pga                                                      \\
+         & (\hist, \ar_2, \ar) \ileadsto \pga                                                 \\
+         & \forall \ar': (\hist, a_2, a') \nileadsto \pga ⇒ (\hist, a_1, a') \nileadsto \pga.
       \end{aligned}\right.
@@
       \left.\begin{aligned}
-			&(\hist, \ar_1) \nileadstost \pga \\
-			&(\hist, \ar_2) \nileadstost \pga
+         & (\hist, \ar_1) \nileadstost \pga \\
+         & (\hist, \ar_2) \nileadstost \pga
       \end{aligned}\right\}

### 2023-10-10 simple.tex
More about falsification.

@@
 While $I$ and $\allargs$ are fundamental sets whose elements are considered elementary, a few notations and concepts are required to define ${\allleadsto}$.
-Throughout the article, $\N$ includes zero. %and $\N^* = \N \setminus \set{0}$. 
+Throughout the article, $\N$ includes zero and $\N^* = \N \setminus \set{0}$. 
 Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \N^*: \intvl{j, 0} = \emptyset$).
@@
 A claim is finite iff its cardinal is finite (meaning that it is compatible with a finite number of possibilities).
+Let $C^\subseteq = \set{c \subseteq (I × \allhist) × P \suchthat \exists {\allleadstog} \in C \suchthat c \subseteq {\allleadstog}}$ denote the set of non necessarily complete possibilities compatible with $C$ (thus, each element $c \in C^\subseteq$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhist)$).
+Note that $C^\subseteq$ is downwards closed, meaning that $\forall c \in C^\subseteq: c' \subseteq c \implies c' \in C^\subseteq$.
 
-Given a pair $(I, \allargs)$, a general observation $θ$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
-General observations are the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
+Given a pair $(I, \allargs)$, an observation $θ \in \Theta$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
+The set $\Theta$ contains the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
 Let $S_θ = \set{{\allleadstog} \in P^{I × \allhist} \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
+We say that an observation $\theta$ is compatible with a claim $C$ iff $S_\theta \cap C ≠ \emptyset$, equivalently, iff $\theta \in C^\subseteq$.
+
+Given an observation $\theta$, let $\theta^{-1}(P) \subseteq I × \allhist$ denote the pairs $(i, \hist)$ in $\theta$.
+Let $\incr(\allhist) = \cup_{N \subseteq \N} \set{A \in (\allhist)^N \suchthat \card{A_i} = i \land i < j \implies A_i \subsetneq A_j} \subseteq \powerset{\allhist}$ denote the possibly empty embedded sequences of paths.
+An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhist)$, thus, a possibly empty embedded sequence of elements in $\allhist$.
+Therefore, we let $\incr(\allhist)^I = \set{\theta^{-1}(P) \suchthat \theta \in \Theta}$ denote the set of possible observations restricted to $I × \allhist$, the elements of which being called \emph{a priori observation}.
+Note that $\incr(\allhist)^I$ is downwards closed, meaning that $\forall O \in \incr(\allhist)^I: O' \subseteq O \implies O' \in \incr(\allhist)^I$.
+Let also $\max\incr(\allhist) = \set{A \in \incr(\allhist) \suchthat \nexists A' \in \incr(\allhist) \suchthat A \subset A'} = \set{A \in \incr(\allhist) \cap (\allhist)^\N}$ denote the maximal elements of $\incr(\allhist)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\N$.
+Let a \emph{simple a priori observation} be defined as an element $O \in (\allhist)^I$.
+Given a simple a priori observation $O: I \mapsto \allhist$, we can define the a priori observation $O_O = \set{(i, \hist) \in I × \allhist \suchthat \forall i \in I: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.
+Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.
+
+Similarly, we can view an observation $\theta$ as a function $\theta: I \mapsto \cup_{A \in \incr(\allhist)} P^A$ and thus $\Theta = \finite((\cup_{A \in \incr(\allhist)} P^A)^I)$, where $\finite$ designates the finite relations (considered as a set of triples).
+Note that $(\cup_{A \in \max \incr(\allhist)}P^A)^I$ is the set of functions that associate to each $I$ a maximal increasing sequence of paths, together with values from $P$.
+
+Given a claim $C$, we can also define the set $\Theta \cap C^\subseteq$ of possibilities for increasing sequences corresponding to the claim.
+This set is downwards-closed, as both $\Theta$ and $C^\subseteq$ are.
 
@@
   \end{definition}
+  Equivalently, iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$.
+  Equivalently, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
   \begin{example}
@@
     A claim $C$ is falsifiable iff its complement $\Cbar$ satisfies:
-  $\forall {\allleadstog} \in \Cbar, \exists O \subseteq {\allleadstog} \suchthat S_O \subseteq \Cbar$, or equivalently:
-  $\forall {\allleadstog} \in \Cbar, \exists O \subseteq {\allleadstog} \suchthat S_O \subseteq \Cbar$.
+    $\forall {\allleadstog} \in \Cbar, \exists \theta \subseteq {\allleadstog} \suchthat S_\theta \subseteq \Cbar$, or equivalently:
+    $\forall {\allleadstog} \in \Cbar, \exists O \in (\allhist)^I \suchthat S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
   \end{theorem}
+\begin{proof}
+  The first phrasing follows from the definition of falsifiability.
+  Also, the second phrasing implies the first one: pick $\theta = \restr{\allleadstog}{O_O}$.
 
+  Let us prove that the first phrasing implies the second one.
+  Given $\theta$, define $O = \set{(i, \argmax_{\hist \in (\theta(i) \cup \emptyset)} \card{\hist})}$ as associating to each $i$ the longest corresponding $\hist$ from $\theta$, or the empty sequence if $\theta(i)$ is empty.
+  It follows that $\theta \subseteq \restr{\allleadstog}{O_O}$.
+  Thus, $S_{\restr{\allleadstog}{O_O}} \subseteq S_\theta$.
+  As $S_\theta \subseteq \Cbar$, we obtain $S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
+\end{proof}
+\begin{conjecture}
+  Test each $O$ of a given length.
+If find ${\allleadstog} \in \Cbar \suchthat S_{\restr{\allleadstog}{O_O}} \cap C \neq \emptyset$, and also the more lengthy $O'$ completing $O$ satisfy this, then $C$ is not falsifiable; otherwise, it is.
+  Equivalently, pick $k \in \N$, test each $O$ of that length; and proceed for each $k$. Nah.
+\end{conjecture}
+
+  \begin{remark}
     Let $E \subseteq I × \allhist$ denote an observable compatible set. It is downwards closed.
@@
     TODO what about finiteness of observables? Might fail falsifiability because only infinite obs would falsify.
+  \end{remark}
+  \begin{remark}
+    If $C$ is such that $\exists {\allleadsto} \notin C \suchthat$ each $M_{\allleadsto}$ equals some $X_C$, then $C$ is not falsifiable.
+    This looks correct:
+    our counter-example has the relation with some $M$ not equal to any $X_C$.
+
+    To obtain non fals, need to form a relation whose all decompositions into incr associations are in $C$, but itself not in $C$.
+  \end{remark}
+  \begin{conjecture}
+    Given a claim $C$, consider the subsets of $(\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ whose union, considered as a relation on $(I × \allhist) × P$, is total and right-unique (that is, the subsets that form a new relation $\allleadstog$).
+    $C$ is falsifiable iff these new elements are necessarily in $C$.
+  \end{conjecture}
+  \begin{proof}
+    This seems false.
+(Consider $I = \set{i_1, i_2}$ and $\args = \set{a, b}$ and $\psi$ is ${\ileadsto[i_1]} = {\ileadsto[i_2]}$ and $S = \set{R_1, R_2, …}$ with $R_1$ are all sequences starting with $a$ sent to $p$ and $R_2$ are all sequences starting with $b$ sent to $p' ≠ p$.)
+    % Consider $S \subseteq (\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ (thus each $R \in S$ is a relation $R \subseteq (I × \allhist) × P$).
+Assume that $\cup S$ is total and right-unique and is not in $C$.
+    % Let us show that $C$ is not falsifiable.
+    % Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
+    % Let us show that $\exists R \in S \suchthat \theta \subseteq R$.
+    % Pick any triple $t \in \theta$. Thus, $t \in \cup S$. Thus, for some $R \in S$, $t \in R$. And $R \in C^\subseteq$.
+    % Pick any two triples $t, t' \in \theta$. Wlog, $\hist \subseteq \hist'$.
+  \end{proof}
+  \begin{conjecture}
+    Given a claim $C$, consider the sets $S \subseteq C^\subseteq$ such that $\set{s^{-1}(P) \suchthat s \in S} = \incr(\allhist)^I$ and such that $\cup S$, considered as a relation on $(I × \allhist) × P$, is right-unique (that is, $\cup S$ forms a new relation $\allleadstog$).
+    $C$ is falsifiable iff all such sets $S$ are in $C$.
+  \end{conjecture}
+  \begin{proof}
+    Consider such $S$.
+    Assume that $\cup S$ is right-unique and is not in $C$.
+    Let us show that $C$ is not falsifiable.
+    Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
+    Define $O \in (\incr(\allhist))^I \suchthat \theta^{-1}(P) \subseteq O$.
+Thus, $O \in \set{s^{-1}(P) \suchthat s \in S}$.
+Pick an $s \in S \suchthat s^{-1}(P) = O$.
+We have $s \in C^\subseteq$ and $\theta^{-1}(P) \subseteq s^{-1}(P)$.
+    Also, $\theta \subseteq \cup S$, and $\cup S$ is right-unique, so $\theta$ coincides with $s$ on its domain.
+It follows that $\theta \subseteq s$.
+As $C^\subseteq$ is downwards-closed, this concludes.
+
+    Now, Assume that $C$ is not falsifiable and pick any ${\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
+Let us exhibit a set $S$ such that $\cup S = {\allleadstog}$.
+    Pick any $O \in (\incr(\allhist))^I$ and complete it with values from $\allleadstog$ to obtain a $c$.
+Now, we know that $C^\subseteq$ contains all finite subsequences of $c$, but it does not follow that it contains the infinite sequence $O$, does it?
+    If $C ≠ \emptyset$, an element $c'$ has the same domain as $c$. We know that $c_1 \subseteq c_2 \subseteq …$, where each is a finite subset, is extensible to some function in $C$… ???
+  \end{proof}
 

### 2023-10-10 simple.tex
Equiv fals proven

@@
 Given an observation $\theta$, let $\theta^{-1}(P) \subseteq I × \allhist$ denote the pairs $(i, \hist)$ in $\theta$.
-Let $\incr(\allhist) = \cup_{N \subseteq \N} \set{A \in (\allhist)^N \suchthat \card{A_i} = i \land i < j \implies A_i \subsetneq A_j} \subseteq \powerset{\allhist}$ denote the possibly empty embedded sequences of paths.
+Let $\incr(\allhist) = \cup_{N \subseteq \N} \set{A \in (\allhist)^N \suchthat [\card{A_i} = i] \land [i < j \implies A_i \subsetneq A_j]} \subseteq \powerset{\allhist}$ denote the possibly empty embedded sequences of paths.
 An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhist)$, thus, a possibly empty embedded sequence of elements in $\allhist$.
@@
 Let also $\max\incr(\allhist) = \set{A \in \incr(\allhist) \suchthat \nexists A' \in \incr(\allhist) \suchthat A \subset A'} = \set{A \in \incr(\allhist) \cap (\allhist)^\N}$ denote the maximal elements of $\incr(\allhist)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\N$.
-Let a \emph{simple a priori observation} be defined as an element $O \in (\allhist)^I$.
+
+Let the \emph{simple a priori observations} be defined as $(\allhist)^I$.
 Given a simple a priori observation $O: I \mapsto \allhist$, we can define the a priori observation $O_O = \set{(i, \hist) \in I × \allhist \suchthat \forall i \in I: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.
@@
 \end{proof}
-  \begin{conjecture}
-    Given a claim $C$, consider the sets $S \subseteq C^\subseteq$ such that $\set{s^{-1}(P) \suchthat s \in S} = \incr(\allhist)^I$ and such that $\cup S$, considered as a relation on $(I × \allhist) × P$, is right-unique (that is, $\cup S$ forms a new relation $\allleadstog$).
-    $C$ is falsifiable iff all such sets $S$ are in $C$.
-  \end{conjecture}
+\begin{theorem}
+  Given a claim $C$, consider the sets $S \subseteq C^\subseteq$ such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and such that $\cup S$, considered as a relation on $(I × \allhist) × P$, is right-unique (that is, $\cup S$ forms a new relation $\allleadstog$).
+  $C$ is falsifiable iff all such sets $S$ satisfy $\cup S \in C$.
+\end{theorem}
 \begin{proof}
   Consider such $S$.
-    Assume that $\cup S$ is right-unique and is not in $C$.
+  Assume that $\cup S$ is not in $C$.
   Let us show that $C$ is not falsifiable.
@@
   Define $O \in (\incr(\allhist))^I \suchthat \theta^{-1}(P) \subseteq O$.
-Thus, $O \in \set{s^{-1}(P) \suchthat s \in S}$.
-Pick an $s \in S \suchthat s^{-1}(P) = O$.
-We have $s \in C^\subseteq$ and $\theta^{-1}(P) \subseteq s^{-1}(P)$.
-    Also, $\theta \subseteq \cup S$, and $\cup S$ is right-unique, so $\theta$ coincides with $s$ on its domain.
-It follows that $\theta \subseteq s$.
+Thus, $O \in \set{\theta^{-1}(P) \suchthat \theta \in S}$.
+Pick an element $\theta' \in S \suchthat (\theta')^{-1}(P) = O$.
+We have $\theta' \in C^\subseteq$ and $\theta^{-1}(P) \subseteq (\theta')^{-1}(P)$.
+  Also, $\theta \subseteq \cup S$, and $\cup S$ is right-unique, so $\theta$ coincides with $\theta'$ on its domain (meaning that $\theta = \restr{\theta'}{\theta^{-1}(P)}$).
+It follows that $\theta \subseteq \theta'$.
 As $C^\subseteq$ is downwards-closed, this concludes.
 
-    Now, Assume that $C$ is not falsifiable and pick any ${\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
-Let us exhibit a set $S$ such that $\cup S = {\allleadstog}$.
-    Pick any $O \in (\incr(\allhist))^I$ and complete it with values from $\allleadstog$ to obtain a $c$.
-Now, we know that $C^\subseteq$ contains all finite subsequences of $c$, but it does not follow that it contains the infinite sequence $O$, does it?
-    If $C ≠ \emptyset$, an element $c'$ has the same domain as $c$. We know that $c_1 \subseteq c_2 \subseteq …$, where each is a finite subset, is extensible to some function in $C$… ???
+  Now, assume that $C$ is not falsifiable and pick any ${\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
+  Given any $O \in (\incr(\allhist))^I$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
+  Define $S = \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I}$.
+  The set $S$ satisfies the required conditions and $\cup S = {\allleadstog}$, thus, $\cup S \notin C$.
+\end{proof}
+Here is another way (perhaps more illuminating) of stating the same thing.
+Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I}$.
+Conversely, any set $S$ such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
+Thus, there is a bijection between the set of such sets $S$ and the set of leads to relations.
+We can then rephrase the above theorem as follows.
+A claim $C$ is falsifiable iff $\forall S \in \mathcal{S}: S \subseteq C^\subseteq \implies \cup S \in C$.
+Equivalently, as follows.
+\begin{theorem}
+  A claim $C$ is falsifiable iff $\forall {\allleadstog} \in P^{I × \allhist}: \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I} \subseteq C^\subseteq \implies {\allleadstog} \in C$.
+\end{theorem}
+\begin{proof}
+  By definition, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: S_θ \cap C \neq \emptyset$;
+  equivalently, iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: θ \in C^\subseteq$;
+  equivalently, iff $\exists {\allleadstog} \notin C \suchthat \set{θ \subseteq {\allleadstog}} \subseteq C^\subseteq$.
+
+  The theorem holds because $\forall {\allleadstog} \in P^{I × \allhist}: \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I} = \set{θ \subseteq {\allleadstog}}$.
 \end{proof}

### 2023-10-20 simple.tex
Fals

@@
 \subsection{Form of theories}
-Given an exposure protocol $(I, \allargs, {\allleadsto})$, recall that ${\allleadsto} \in P^{I × \allhist}$.
-
-Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq P^{I × \allhist}$.
-Given a formula $\psi$, let the corresponding claim be $C_\psi = \set{{\allleadstog} \in P^{I × \allhist} \suchthat {\allleadstog} \text{ satisfies } \psi}$.
+Given an exposure protocol $(I, \allargs, {\allleadsto})$, recall that ${\allleadsto} \in \allallleadsto$.
+
+Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq \allallleadsto$.
+Given a formula $\psi$, let the corresponding claim be $C_\psi = \set{{\allleadstog} \in \allallleadsto \suchthat {\allleadstog} \text{ satisfies } \psi}$.
 A claim is finite iff its cardinal is finite (meaning that it is compatible with a finite number of possibilities).
@@
 The set $\Theta$ contains the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
-Let $S_θ = \set{{\allleadstog} \in P^{I × \allhist} \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
+Let $S_θ = \set{{\allleadstog} \in \allallleadsto \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
 We say that an observation $\theta$ is compatible with a claim $C$ iff $S_\theta \cap C ≠ \emptyset$, equivalently, iff $\theta \in C^\subseteq$.
@@
 Given an observation $\theta$, let $\theta^{-1}(P) \subseteq I × \allhist$ denote the pairs $(i, \hist)$ in $\theta$.
-Let $\incr(\allhist) = \cup_{N \subseteq \N} \set{A \in (\allhist)^N \suchthat [\card{A_i} = i] \land [i < j \implies A_i \subsetneq A_j]} \subseteq \powerset{\allhist}$ denote the possibly empty embedded sequences of paths.
-An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhist)$, thus, a possibly empty embedded sequence of elements in $\allhist$.
-Therefore, we let $\incr(\allhist)^I = \set{\theta^{-1}(P) \suchthat \theta \in \Theta}$ denote the set of possible observations restricted to $I × \allhist$, the elements of which being called \emph{a priori observation}.
-Note that $\incr(\allhist)^I$ is downwards closed, meaning that $\forall O \in \incr(\allhist)^I: O' \subseteq O \implies O' \in \incr(\allhist)^I$.
+Let $\incr(\allhist) = \set{\emptyset} \cup \cup_{\emptyset \neq N \subseteq \N} \set{A(N) \suchthat A \in (\allhist)^N \land [\card{A_i} = i] \land [i < j \implies A_i \subsetneq A_j]} \subseteq \powerset{\allhist}$ denote the possibly empty embedded sequences of paths.
+An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhist)$.
+Therefore, we let $\finite(\incr(\allhist)^I) = \set{\theta^{-1}(P) \suchthat \theta \in \Theta}$ denote the set of possible observations restricted to $I × \allhist$, the elements of which being called \emph{a priori observation}, where $\finite(\incr(\allhist)^I)$ denote the functions $f: I \mapsto \incr(\allhist)$ with finite support, thus $\card{f^{-1}(\incr(\allhist) \setminus \emptyset)} < \N$.
+Note that $\finite(\incr(\allhist)^I)$ and $\incr(\allhist)^I$ are downwards closed, meaning that $\forall O \in \finite(\incr(\allhist)^I): O' \subseteq O \implies O' \in \finite(\incr(\allhist)^I)$ and $\forall O \in \incr(\allhist)^I: O' \subseteq O \implies O' \in \incr(\allhist)^I$.
 Let also $\max\incr(\allhist) = \set{A \in \incr(\allhist) \suchthat \nexists A' \in \incr(\allhist) \suchthat A \subset A'} = \set{A \in \incr(\allhist) \cap (\allhist)^\N}$ denote the maximal elements of $\incr(\allhist)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\N$.
 
-Let the \emph{simple a priori observations} be defined as $(\allhist)^I$.
-Given a simple a priori observation $O: I \mapsto \allhist$, we can define the a priori observation $O_O = \set{(i, \hist) \in I × \allhist \suchthat \forall i \in I: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.
+Let the \emph{simple a priori observations} be defined as $\cup_{J \subseteq_\finite I} (\allhist)^J$, equivalently, as the right-unique finite relations over $I × \allhist$.
+Given a simple a priori observation $O: J \mapsto \allhist$, we can define the a priori observation $O_O = \set{(i, \hist) \in J × \allhist \suchthat \forall i \in J: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.
 Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.
@@
   We say that $C$ is \emph{syntactically falsifiable}, or just falsifiable, iff
-  %$\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
+  %$\forall {\allleadstog} \in \allallleadsto: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
   $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset$.
@@
 \begin{theorem}
-  A claim $C$ is falsifiable iff its complement $\Cbar$ satisfies:
+  A claim $C$ is falsifiable iff its complement $\Cbar = \allallleadsto \setminus C$ satisfies:
   $\forall {\allleadstog} \in \Cbar, \exists \theta \subseteq {\allleadstog} \suchthat S_\theta \subseteq \Cbar$, or equivalently:
@@
 \end{proof}
-\begin{theorem}
+\begin{theorem}[To check considering finiteness of observations]
   Given a claim $C$, consider the sets $S \subseteq C^\subseteq$ such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and such that $\cup S$, considered as a relation on $(I × \allhist) × P$, is right-unique (that is, $\cup S$ forms a new relation $\allleadstog$).
@@
 Here is another way (perhaps more illuminating) of stating the same thing.
-Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I}$.
-Conversely, any set $S$ such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
-Thus, there is a bijection between the set of such sets $S$ and the set of leads to relations.
-We can then rephrase the above theorem as follows.
-A claim $C$ is falsifiable iff $\forall S \in \mathcal{S}: S \subseteq C^\subseteq \implies \cup S \in C$.
-Equivalently, as follows.
+\begin{remark}
+  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\finite(\incr(\allhist))^I)}$.
+  (Also, any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in \cup_{J \subseteq_\finite I} (\allhist)^J}$.)
+  Conversely, any set $S$ of observations such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
+  Thus, there is a bijection between the set $\mathcal{S}$ of such sets $S$ and the set of leads to relations.
+
+  Therefore,
+  a claim $C$ is falsifiable iff $\forall S \in \mathcal{S}: S \subseteq C^\subseteq \implies \cup S \in C$.
+\end{remark}
+
 \begin{theorem}
-  A claim $C$ is falsifiable iff $\forall {\allleadstog} \in P^{I × \allhist}: \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I} \subseteq C^\subseteq \implies {\allleadstog} \in C$.
+  A claim $C$ is falsifiable iff \[\forall f \in C^{\finite(\incr(\allhist)^I)}: \cup_{O \in \finite(\incr(\allhist)^I)} \restr{f(O)}{O} \in C.\]
 \end{theorem}
@@
 
-  The theorem holds because $\forall {\allleadstog} \in P^{I × \allhist}: \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I} = \set{θ \subseteq {\allleadstog}}$.
+  The theorem states that a claim $C$ is falsifiable iff $\forall {\allleadstog} \in \allallleadsto: \set{\restr{\allleadstog}{O} \suchthat O \in \finite(\incr(\allhist)^I)} \subseteq C^\subseteq \implies {\allleadstog} \in C$.
+
+  This holds because $\forall {\allleadstog} \in \allallleadsto: \set{\restr{\allleadstog}{O} \suchthat O \in \finite(\incr(\allhist)^I)} = \set{θ \subseteq {\allleadstog}}$.
 \end{proof}
@@
 \begin{definition}[Anonymity]
-  Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in P^{I × \allhist}$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
+  Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in \allallleadsto$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
   A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
@@
     %	Its negation is $\forall k: (\ar^k) \nileadsto \phi$.
-    %	The claim represents the set $\set{{\allleadsto} \in P^{I × \allhist} \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
+    %	The claim represents the set $\set{{\allleadsto} \in \allallleadsto \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
     Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$.

### 2023-10-20 simple.tex
Rm redundant (less clear) thm

@@
 \end{proof}
-\begin{theorem}[To check considering finiteness of observations]
-  Given a claim $C$, consider the sets $S \subseteq C^\subseteq$ such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and such that $\cup S$, considered as a relation on $(I × \allhist) × P$, is right-unique (that is, $\cup S$ forms a new relation $\allleadstog$).
-  $C$ is falsifiable iff all such sets $S$ satisfy $\cup S \in C$.
-\end{theorem}
-\begin{proof}
-  Consider such $S$.
-  Assume that $\cup S$ is not in $C$.
-  Let us show that $C$ is not falsifiable.
-  Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
-  Define $O \in (\incr(\allhist))^I \suchthat \theta^{-1}(P) \subseteq O$.
-Thus, $O \in \set{\theta^{-1}(P) \suchthat \theta \in S}$.
-Pick an element $\theta' \in S \suchthat (\theta')^{-1}(P) = O$.
-We have $\theta' \in C^\subseteq$ and $\theta^{-1}(P) \subseteq (\theta')^{-1}(P)$.
-  Also, $\theta \subseteq \cup S$, and $\cup S$ is right-unique, so $\theta$ coincides with $\theta'$ on its domain (meaning that $\theta = \restr{\theta'}{\theta^{-1}(P)}$).
-It follows that $\theta \subseteq \theta'$.
-As $C^\subseteq$ is downwards-closed, this concludes.
-
-  Now, assume that $C$ is not falsifiable and pick any ${\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
-  Given any $O \in (\incr(\allhist))^I$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
-  Define $S = \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I}$.
-  The set $S$ satisfies the required conditions and $\cup S = {\allleadstog}$, thus, $\cup S \notin C$.
-\end{proof}
-Here is another way (perhaps more illuminating) of stating the same thing.
+
 \begin{remark}

### 2023-10-20 simple.tex
Rm more draft results less clear than caract fals

@@
   As $S_\theta \subseteq \Cbar$, we obtain $S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
-\end{proof}
-\begin{conjecture}
-  Test each $O$ of a given length.
-If find ${\allleadstog} \in \Cbar \suchthat S_{\restr{\allleadstog}{O_O}} \cap C \neq \emptyset$, and also the more lengthy $O'$ completing $O$ satisfy this, then $C$ is not falsifiable; otherwise, it is.
-  Equivalently, pick $k \in \N$, test each $O$ of that length; and proceed for each $k$. Nah.
-\end{conjecture}
-
-\begin{remark}
-  Let $E \subseteq I × \allhist$ denote an observable compatible set. It is downwards closed.
-  Let $M$ denote a maximal $E$.
-  Any $M$ maps each individual $i \in I$ to an increasing sequence.
-  Given ${\allleadsto}$, let $E_{\allleadsto} \subseteq {\allleadsto}$ denote the observable compatible sets (triples, not pairs, thus including values).
-These are the $E$ to which the value associated is the one given by $\allleadsto$.
-  Define similarly $M_{\allleadsto}$.
-  Let $X_C \subseteq I × \allhist × P$ denote a subset that is completable to some ${\allleadsto}$ in $C$. It is downwards closed.
-  Let $N_C$ denote a maximal such subset.
-  A claim is not falsifiable iff $\exists {\allleadsto} \notin C \suchthat$ each $E_{\allleadsto}$ equals some $X_C$.
-  A claim is not falsifiable iff $\exists {\allleadsto} \notin C \suchthat$ each $M_{\allleadsto}$ equals some $X_C$.
-  A claim is not falsifiable iff it is possible to pick some $M_{\allleadsto_1}$ from $C$ (that is, a mapping of each individual to an increasing sequence, together with the associated value from $\allleadsto_1$), some other $M_{\allleadsto_2}$ from $C$, and on their common entries (if any) these two relations agree (so their union is a right-unique relation), and so on for each possible mappings $M$, so as to form a complete $\allleadsto$ that is not in $C$.
-  A claim is falsifiable iff it is closed under the above picking operation.
-  Equivalently, a claim is not falsifiable iff this can be done for a given number of $M$ whose union is not an $X_C$.
-  We could need more than two such $M$'s, I suppose: for the theorem below, the number of such $M$'s is equal to the cardinal of the set on which they differ.
-  TODO what about finiteness of observables? Might fail falsifiability because only infinite obs would falsify.
-\end{remark}
-\begin{remark}
-  If $C$ is such that $\exists {\allleadsto} \notin C \suchthat$ each $M_{\allleadsto}$ equals some $X_C$, then $C$ is not falsifiable.
-  This looks correct:
-  our counter-example has the relation with some $M$ not equal to any $X_C$.
-
-  To obtain non fals, need to form a relation whose all decompositions into incr associations are in $C$, but itself not in $C$.
-\end{remark}
-\begin{conjecture}
-  Given a claim $C$, consider the subsets of $(\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ whose union, considered as a relation on $(I × \allhist) × P$, is total and right-unique (that is, the subsets that form a new relation $\allleadstog$).
-  $C$ is falsifiable iff these new elements are necessarily in $C$.
-\end{conjecture}
-\begin{proof}
-  This seems false.
-(Consider $I = \set{i_1, i_2}$ and $\args = \set{a, b}$ and $\psi$ is ${\ileadsto[i_1]} = {\ileadsto[i_2]}$ and $S = \set{R_1, R_2, …}$ with $R_1$ are all sequences starting with $a$ sent to $p$ and $R_2$ are all sequences starting with $b$ sent to $p' ≠ p$.)
-  % Consider $S \subseteq (\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ (thus each $R \in S$ is a relation $R \subseteq (I × \allhist) × P$).
-Assume that $\cup S$ is total and right-unique and is not in $C$.
-  % Let us show that $C$ is not falsifiable.
-  % Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
-  % Let us show that $\exists R \in S \suchthat \theta \subseteq R$.
-  % Pick any triple $t \in \theta$. Thus, $t \in \cup S$. Thus, for some $R \in S$, $t \in R$. And $R \in C^\subseteq$.
-  % Pick any two triples $t, t' \in \theta$. Wlog, $\hist \subseteq \hist'$.
 \end{proof}

### 2023-10-21 simple.tex
Fals caract and corol

@@
 Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \N^*: \intvl{j, 0} = \emptyset$).
-Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence.
-A generic element of $\allhist$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path.
+Define $\allhists = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence.
+A generic element of $\allhists$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path.
 Its length is denoted by $\card{\hist} \in \N$ and its elements, $\hist(k)$ or $\hist_k$.
-Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}: \hist(k) = \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
+Thus, given an argumentative path $\hist \in \allhists$, $\forall k \in \intvl{1, \card{\hist}}: \hist(k) = \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
 A path $\hist$ is a sub-path of another path $\histp$ whenever $\hist \subseteq \histp$, thus, $\forall k \in \intvl{1, \card{\hist}}: \hist_k = \histp_k$.
 
-The function ${\allleadsto}: I × \allhist → P$ associates to each individual and path an element of $P$, ${\allleadsto}(i, \alpha)$ representing the choice of $i$ following exposure to the arguments of $\alpha$, in order.
+The function ${\allleadsto}: I × \allhists → P$ associates to each individual and path an element of $P$, ${\allleadsto}(i, \alpha)$ representing the choice of $i$ following exposure to the arguments of $\alpha$, in order.
 That is, ${\allleadsto}(i, \alpha) = \phi$ denotes that $i$ chooses the first act after exposure to $\alpha$, ${\allleadsto}(i, \alpha) = ¬\phi$ denotes $i$ choosing the second act and ${\allleadsto}(i, \alpha) = 0$ is used to represent indifference of $i$.
-The notation $\alpha \ileadsto p$, pronounced “$\alpha$ leads $i$ to $p$”, will be used to mean ${\allleadsto}(i, \alpha) = p$, considering ${\ileadsto} \subseteq \allhist × P$ as a binary relation.
+The notation $\alpha \ileadsto p$, pronounced “$\alpha$ leads $i$ to $p$”, will be used to mean ${\allleadsto}(i, \alpha) = p$, considering ${\ileadsto} \subseteq \allhists × P$ as a binary relation.
 As usual with binary relations, $\hist \nileadsto p$ means ${\allleadsto}(i, \alpha) ≠ p$ or equivalently ${\allleadsto}(i, \alpha) \in P \setminus \set{p}$.
@@
 
-Given $\hist \in \allhist$, $\range(\hist) = \hist(\intvl{1, \card{\hist}})$ denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
+Given $\hist \in \allhists$, $\range(\hist) = \hist(\intvl{1, \card{\hist}})$ denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$.
 Let $\histend = \hist(\intvl{\max(1, \card{\hist} - 1), \card{\hist}})$ denote the set containing the last two arguments of the sequence $\hist$ if the sequence has at least two elements; the unique argument of the sequence if it has exactly one element; and the empty set if it is empty.
 
-Given $i \in I, p \in P, \ar \in \allargs$, define $\ar \ileadstost p$, pronounced “$a$ leads definitely $i$ to $p$”, iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadsto p$.
+Given $i \in I, p \in P, \ar \in \allargs$, define $\ar \ileadstost p$, pronounced “$a$ leads definitely $i$ to $p$”, iff $\forall \hist \in \allhists \suchthat \ar \in \histend: \hist \ileadsto p$.
 When $\ar \ileadstost p$, $\ar$ is said to be a decisive argument for $\prop$ from $i$’s point of view given the exposure protocol.
@@
 Accordingly, define $\ileadsto[e]$, representing the first kind of individuals, as follows.
-$\forall \hist \in \allhist: \hist \ileadsto[e] L_D ⇔ [\ar_e \in R(\hist)]$, and $\hist \ileadsto[e] L_P$ otherwise.
+$\forall \hist \in \allhists: \hist \ileadsto[e] L_D ⇔ [\ar_e \in R(\hist)]$, and $\hist \ileadsto[e] L_P$ otherwise.
 Note that in particular, if $\hist$ contains $\ar$ but not $\ar_e$, $\ar \ileadsto[e] L_P$, as we assume such individuals are confused by the longer argument $\ar$ referring to abstract notions and therefore opt for $L_P$, falling back to the common psychological bias.
-  The second kind of individuals is represented by $\ileadsto[u]$ defined as $\forall \hist \in \allhist: \hist \ileadsto[u] L_D ⇔ [\ar_u \notin R(\hist) \lor \ar \in R(\hist) \lor \set{\ar_u, \ar_l} \subseteq R(\hist)]$, and $\hist \ileadsto[u] L_P$ otherwise.
+  The second kind of individuals is represented by $\ileadsto[u]$ defined as $\forall \hist \in \allhists: \hist \ileadsto[u] L_D ⇔ [\ar_u \notin R(\hist) \lor \ar \in R(\hist) \lor \set{\ar_u, \ar_l} \subseteq R(\hist)]$, and $\hist \ileadsto[u] L_P$ otherwise.
   We assume here that such individuals think about $\ar_u$ as a correct argument in favor of $L_P$ until shown the rebuttal $\ar_l$ (or $\ar$, which contains a similar rebuttal).
@@
 \subsection{Form of theories}
-Given an exposure protocol $(I, \allargs, {\allleadsto})$, recall that ${\allleadsto} \in \allallleadsto$.
-
-Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq \allallleadsto$.
-Given a formula $\psi$, let the corresponding claim be $C_\psi = \set{{\allleadstog} \in \allallleadsto \suchthat {\allleadstog} \text{ satisfies } \psi}$.
+Given an exposure protocol $(I, \allargs, {\allleadsto})$, recall that ${\allleadsto} \in \allleadstos$.
+
+Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq \allleadstos$.
+Given a formula $\psi$, let the corresponding claim be $C_\psi = \set{{\allleadstog} \in \allleadstos \suchthat {\allleadstog} \text{ satisfies } \psi}$.
+A claim is trivial iff it is the trivial claim, defined as $C = \allleadstos$.
 A claim is finite iff its cardinal is finite (meaning that it is compatible with a finite number of possibilities).
-Let $C^\subseteq = \set{c \subseteq (I × \allhist) × P \suchthat \exists {\allleadstog} \in C \suchthat c \subseteq {\allleadstog}}$ denote the set of non necessarily complete possibilities compatible with $C$ (thus, each element $c \in C^\subseteq$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhist)$).
+Let $C^\subseteq = \set{c \subseteq (I × \allhists) × P \suchthat \exists {\allleadstog} \in C \suchthat c \subseteq {\allleadstog}}$ denote the set of non necessarily complete possibilities compatible with $C$ (thus, each element $c \in C^\subseteq$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhists)$).
 Note that $C^\subseteq$ is downwards closed, meaning that $\forall c \in C^\subseteq: c' \subseteq c \implies c' \in C^\subseteq$.
 
-Given a pair $(I, \allargs)$, an observation $θ \in \Theta$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
+Given a pair $(I, \allargs)$, an observation $θ \in \Theta$ is a right unique finite subset of $(I × \allhists) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
 The set $\Theta$ contains the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
-Let $S_θ = \set{{\allleadstog} \in \allallleadsto \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
+Let $S_θ = \set{{\allleadstog} \in \allleadstos \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
 We say that an observation $\theta$ is compatible with a claim $C$ iff $S_\theta \cap C ≠ \emptyset$, equivalently, iff $\theta \in C^\subseteq$.
 
-Given an observation $\theta$, let $\theta^{-1}(P) \subseteq I × \allhist$ denote the pairs $(i, \hist)$ in $\theta$.
-Let $\incr(\allhist) = \set{\emptyset} \cup \cup_{\emptyset \neq N \subseteq \N} \set{A(N) \suchthat A \in (\allhist)^N \land [\card{A_i} = i] \land [i < j \implies A_i \subsetneq A_j]} \subseteq \powerset{\allhist}$ denote the possibly empty embedded sequences of paths.
-An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhist)$.
-Therefore, we let $\finite(\incr(\allhist)^I) = \set{\theta^{-1}(P) \suchthat \theta \in \Theta}$ denote the set of possible observations restricted to $I × \allhist$, the elements of which being called \emph{a priori observation}, where $\finite(\incr(\allhist)^I)$ denote the functions $f: I \mapsto \incr(\allhist)$ with finite support, thus $\card{f^{-1}(\incr(\allhist) \setminus \emptyset)} < \N$.
-Note that $\finite(\incr(\allhist)^I)$ and $\incr(\allhist)^I$ are downwards closed, meaning that $\forall O \in \finite(\incr(\allhist)^I): O' \subseteq O \implies O' \in \finite(\incr(\allhist)^I)$ and $\forall O \in \incr(\allhist)^I: O' \subseteq O \implies O' \in \incr(\allhist)^I$.
-Let also $\max\incr(\allhist) = \set{A \in \incr(\allhist) \suchthat \nexists A' \in \incr(\allhist) \suchthat A \subset A'} = \set{A \in \incr(\allhist) \cap (\allhist)^\N}$ denote the maximal elements of $\incr(\allhist)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\N$.
-
-Let the \emph{simple a priori observations} be defined as $\cup_{J \subseteq_\finite I} (\allhist)^J$, equivalently, as the right-unique finite relations over $I × \allhist$.
-Given a simple a priori observation $O: J \mapsto \allhist$, we can define the a priori observation $O_O = \set{(i, \hist) \in J × \allhist \suchthat \forall i \in J: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.
+Given an observation $\theta$, let $\theta^{-1}(P) \subseteq I × \allhists$ denote the pairs $(i, \hist)$ in $\theta$.
+Let $\incr(\allhists) = \set{\emptyset} \cup \cup_{\emptyset \neq N \subseteq \N} \set{A(N) \suchthat A \in (\allhists)^N \land [\card{A_i} = i] \land [i < j \implies A_i \subsetneq A_j]} \subseteq \powerset{\allhists}$ denote the possibly empty embedded sequences of paths.
+An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhists)$.
+Therefore, we let $\finite(\incr(\allhists)^I) = \set{\theta^{-1}(P) \suchthat \theta \in \Theta}$ denote the set of possible observations restricted to $I × \allhists$, the elements of which being called \emph{a priori observation}, where $\finite(\incr(\allhists)^I)$ denote the functions $f: I \mapsto \incr(\allhists)$ with finite support, thus $\card{f^{-1}(\incr(\allhists) \setminus \emptyset)} < \N$.
+Note that $\allpriobss$ and $\incr(\allhists)^I$ are downwards closed, meaning that $\forall O \in \allpriobss: O' \subseteq O \implies O' \in \allpriobss$ and $\forall O \in \incr(\allhists)^I: O' \subseteq O \implies O' \in \incr(\allhists)^I$.
+Let also $\max\incr(\allhists) = \set{A \in \incr(\allhists) \suchthat \nexists A' \in \incr(\allhists) \suchthat A \subset A'} = \set{A \in \incr(\allhists) \cap (\allhists)^\N}$ denote the maximal elements of $\incr(\allhists)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\N$.
+
+Let the \emph{simple a priori observations} be defined as $\cup_{J \subseteq_\finite I} (\allhists)^J$, equivalently, as the right-unique finite relations over $I × \allhists$.
+Given a simple a priori observation $O: J \mapsto \allhists$, we can define the a priori observation $O_O = \set{(i, \hist) \in J × \allhists \suchthat \forall i \in J: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.
 Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.
 
-Similarly, we can view an observation $\theta$ as a function $\theta: I \mapsto \cup_{A \in \incr(\allhist)} P^A$ and thus $\Theta = \finite((\cup_{A \in \incr(\allhist)} P^A)^I)$, where $\finite$ designates the finite relations (considered as a set of triples).
-Note that $(\cup_{A \in \max \incr(\allhist)}P^A)^I$ is the set of functions that associate to each $I$ a maximal increasing sequence of paths, together with values from $P$.
+Similarly, we can view an observation $\theta$ as a function $\theta: I \mapsto \cup_{A \in \incr(\allhists)} P^A$ and thus $\Theta = \finite((\cup_{A \in \incr(\allhists)} P^A)^I)$, where $\finite$ designates the finite relations (considered as a set of triples).
+Note that $(\cup_{A \in \max \incr(\allhists)}P^A)^I$ is the set of functions that associate to each $I$ a maximal increasing sequence of paths, together with values from $P$.
 
@@
 
+\begin{remark}
+  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in \cup_{J \subseteq_\finite I} (\allhists)^J}$.
+\end{remark}
+
 \begin{definition}
   We say that $C$ is \emph{syntactically falsifiable}, or just falsifiable, iff
-  %$\forall {\allleadstog} \in \allallleadsto: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
+  %$\forall {\allleadstog} \in \allleadstos: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
   $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset$.
@@
 Equivalently, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
-\begin{example}
-  $(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
+
+\begin{remark}
+  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\finite(\incr(\allhists))^I)}$.
+  Conversely, any set $S$ of observations such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhists)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
+  Thus, there is a bijection between the set $\mathcal{S}$ of such sets $S$ and the set of leads to relations.
+
+  This is the intuitive reason that, as we will see,
+  a claim $C$ is falsifiable iff $\forall S \in \mathcal{S}: S \subseteq C^\subseteq \implies \cup S \in C$.
+\end{remark}
+
+\begin{example}
+  \label{ex:bigor}
+  $[\forall i: (\ar) \ileadstog \phi] \lor [\forall i: (\ar, \ar) \ileadstog \phi] \lor …$ is not falsifiable.
+  Here, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$.
+
   Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise.
@@
   \label{ex:unfals}
-  $(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
-  Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
+  Given $\ar \neq \ar' \in \allargs$,
+  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
+  Consider any ${\allleadstog} \notin C$, thus satisfying, for some $i$, $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
   Consider any $θ \subseteq {\allleadstog}$ and let us prove that $S_θ \cap C ≠ \emptyset$.
@@
 \begin{theorem}
-  A claim $C$ is falsifiable iff its complement $\Cbar = \allallleadsto \setminus C$ satisfies:
+  A claim $C$ is falsifiable iff its complement $\Cbar = \allleadstos \setminus C$ satisfies:
   $\forall {\allleadstog} \in \Cbar, \exists \theta \subseteq {\allleadstog} \suchthat S_\theta \subseteq \Cbar$, or equivalently:
-  $\forall {\allleadstog} \in \Cbar, \exists O \in (\allhist)^I \suchthat S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
+  $\forall {\allleadstog} \in \Cbar, \exists O \in (\allhists)^I \suchthat S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
 \end{theorem}
@@
 
-\begin{remark}
-  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\finite(\incr(\allhist))^I)}$.
-  (Also, any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in \cup_{J \subseteq_\finite I} (\allhist)^J}$.)
-  Conversely, any set $S$ of observations such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
-  Thus, there is a bijection between the set $\mathcal{S}$ of such sets $S$ and the set of leads to relations.
-
-  Therefore,
-  a claim $C$ is falsifiable iff $\forall S \in \mathcal{S}: S \subseteq C^\subseteq \implies \cup S \in C$.
-\end{remark}
-
 \begin{theorem}
-  A claim $C$ is falsifiable iff \[\forall f \in C^{\finite(\incr(\allhist)^I)}: \cup_{O \in \finite(\incr(\allhist)^I)} \restr{f(O)}{O} \in C.\]
+  \label{thm:caractFals}
+  A claim $C$ is falsifiable iff $\forall {\allleadstog} \in \allleadstos$:
+  \[\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq \implies {\allleadstog} \in C.\]
 \end{theorem}
@@
 
-  The theorem states that a claim $C$ is falsifiable iff $\forall {\allleadstog} \in \allallleadsto: \set{\restr{\allleadstog}{O} \suchthat O \in \finite(\incr(\allhist)^I)} \subseteq C^\subseteq \implies {\allleadstog} \in C$.
-
-  This holds because $\forall {\allleadstog} \in \allallleadsto: \set{\restr{\allleadstog}{O} \suchthat O \in \finite(\incr(\allhist)^I)} = \set{θ \subseteq {\allleadstog}}$.
-\end{proof}
+  To conclude, note that $\forall {\allleadstog} \in \allleadstos$: $\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} = \set{θ \subseteq {\allleadstog}}$.
+\end{proof}
+\begin{corollary}
+  A claim $C$ is falsifiable iff $\forall f \in C^{\allpriobss} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
+  \[\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C.\]
+\end{corollary}
+\begin{proof}
+  Consider a falsifiable claim $C$, consider such an $f$, and let us prove that $\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C$.
+  Define ${\allleadstog} \subseteq (I × \allhists) × P$ as $\cup_{O \in \allpriobss} \restr{f(O)}{O}$. Its domain equals $I × \allhists$, and it is right-unique thanks to the condition on $f$.
+  Thus, \cref{thm:caractFals} applies and ${\allleadstog} \in C$.
+
+  Conversely, assume that the statement about all $f$ holds and let us prove that $C$ is falsifiable.
+  Consider any ${\allleadstog} \in \allleadstos$ such that $\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq$.
+  Given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$ and therefore there is some $e_O \in C$ such that $\restr{\allleadstog}{O} = \restr{e_O}{O}$.
+  Define $f$ as $f(O) = e_O$.
+  As this $f$ satisfies the condition in the hypothesis, we obtain that $\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C$, hence, $\cup_{O \in \allpriobss} \restr{\allleadstog}{O} \in C$.
+  Therefore, ${\allleadstog} \in C$.
+  Apply \cref{thm:caractFals} to conclude that $C$ is falsifiable.
+\end{proof}
+
+\begin{corollary}
+  \label{th:corffals}
+  A claim $C$ is falsifiable iff $\forall f \in \left(C^\subseteq\right)^{\allpriobss} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
+  \[\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C.\]
+\end{corollary}
+\begin{corollary}
+  \label{th:corffalsdom}
+  A claim $C$ is falsifiable iff $\forall f \in \cup_{O \in \allpriobss} \set{\set{O} × (P^O \cap C^\subseteq)} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
+  \[\cup_{O \in \allpriobss} f(O) \in C.\]
+\end{corollary}
+\begin{corollary}
+  \label{th:veryunfals}
+  Any non-trivial claim $C$ satisfying $\forall O \in \allpriobss, {\allleadstog} \in \allleadstos: \restr{\allleadstog}{O} \in C^\subseteq$ is not falsifiable.
+\end{corollary}
+\begin{proof}
+  Pick any ${\allleadstog} \notin C$.
+  Define $f$ as $\forall O \in \allpriobss: f(O) = \restr{\allleadstog}{O}$.
+  Observe that $\cup_{O \in \allpriobss} f(O) = {\allleadstog}$ and hence $\cup_{O \in \allpriobss} f(O) \notin C$.
+  Apply \cref{th:corffalsdom}.
+\end{proof}
+
+\begin{example}
+  Considering again \cref{ex:bigor}, by \cref{th:veryunfals}, we see that $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$ is not falsifiable.
+\end{example}
 
@@
 \begin{example}
-  Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhist$ with $\hist$ and $\histp$ non prefix related.
+  Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhists$ with $\hist$ and $\histp$ non prefix related.
   The claim $\psi = (\hist \ileadstog p \lor \hist \ileadstog p') \land (\histp \ileadstog p \lor \histp \ileadstog p') \land (\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p)$ is falsifiable.
@@
 \begin{definition}[Anonymity]
-  Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in \allallleadsto$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
+  Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in \allleadstos$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
   A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
@@
 \subsection{Ideas for no suitable}
-Given $\histk \in \allhist$ and $\ar_l \in \allargs$, let $(\histk, …, \ar_l, ?)$ denote the set
+Given $\histk \in \allhists$ and $\ar_l \in \allargs$, let $(\histk, …, \ar_l, ?)$ denote the set
 $\set{\histl \suchthat \histk \subset \histl \land \ar_l \in \histlend}$.
-Given $\hist \in \allhist$, ${\ileadstog}$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set
+Given $\hist \in \allhists$, ${\ileadstog}$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set
 $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
@@
 $(…, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set
-$\cup_{\hist \in \allhist} (\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?) =
+$\cup_{\hist \in \allhists} (\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?) =
   \set{\histl \suchthat \exists \hist, \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend} =
@@
   We need to exhibit some ${\allleadstog} \notin C$ such that $\forall θ \subseteq {\allleadstog}: S_θ \cap C ≠ \emptyset$.
-  Define $\allleadstog$ as, $\forall i \in I$, $(\ar_k) \nileadstog p, (\ar_l) \nileadstog p, \forall \hist \in \allhist \setminus \set{(\ar_k), (\ar_l)}: \hist \ileadstog p$.
+  Define $\allleadstog$ as, $\forall i \in I$, $(\ar_k) \nileadstog p, (\ar_l) \nileadstog p, \forall \hist \in \allhists \setminus \set{(\ar_k), (\ar_l)}: \hist \ileadstog p$.
   It follows that $\ar_k \nileadstostg p \land \ar_l \nileadstostg p$. Thus, ${\allleadstog} \notin C$.
@@
   %	Then, intuitively, $\ar_k$ decisive is in $S_θ \cap C$.
-  Define $\allleadstog'$ as, $\forall i \in I: \forall \hist \in \allhist \setminus \set{(\ar_k), (\ar_l)}, \hist \ileadstog' p$
+  Define $\allleadstog'$ as, $\forall i \in I: \forall \hist \in \allhists \setminus \set{(\ar_k), (\ar_l)}, \hist \ileadstog' p$
   and $\forall \ar \in \set{\ar_k, \ar_l}$, $(\ar) \ileadstog' ({\allleadstog}(\ar, i))$ if $(\ar, i, {\allleadstog}(\ar, i)) \in O$, $(\ar) \ileadstog' p$ otherwise.
-  %Pick any $p' ≠ p$ and define $\allleadstog'$ as, $\forall i \in I: \forall \hist \in \allhist \setminus \set{(\ar_l)}, \hist \ileadstog' p \land (\ar_l) \ileadstog' p' ≠ p$.
+  %Pick any $p' ≠ p$ and define $\allleadstog'$ as, $\forall i \in I: \forall \hist \in \allhists \setminus \set{(\ar_l)}, \hist \ileadstog' p \land (\ar_l) \ileadstog' p' ≠ p$.
   The set $O$ can’t have both $(\ar_k) \nileadstog p$ and $(\ar_l) \nileadstog p$, thus, ${\allleadstog'} \in C$.
@@
   Now we need $C'$ to hold so it must contain ${\allleadsto}$ but not contain ${\allleadstog'}$.
-It does not contain ${\allleadstog'}$ iff it implies $¬(\land_{\hist \in \allhist \setminus \set{(\ar_l)}} \hist \ileadstog' p \land (\ar_l) \ileadstog' p')$.
+It does not contain ${\allleadstog'}$ iff it implies $¬(\land_{\hist \in \allhists \setminus \set{(\ar_l)}} \hist \ileadstog' p \land (\ar_l) \ileadstog' p')$.
   %So it must claim that $\ar_l$ is not decisive. Or something like, for some $\hist_1$: if $\ar_l \ileadstog' p'$, then $\hist_1 \ileadstog' ¬p$.
@@
     %	Its negation is $\forall k: (\ar^k) \nileadsto \phi$.
-    %	The claim represents the set $\set{{\allleadsto} \in \allallleadsto \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
+    %	The claim represents the set $\set{{\allleadsto} \in \allleadstos \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
     Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$.
@@
 
-  The defense relation $\dg \subseteq \allhist × \allargs$ defines the argumentation strategy of the theory.
+  The defense relation $\dg \subseteq \allhists × \allargs$ defines the argumentation strategy of the theory.
 Informally speaking, it defines the arguments that the theory claims will convince the individuals in $I$ to choose $\pga$.
@@
 
-  Formally speaking, a defense relation $\dg \subseteq \allhist × \allargs$ is a right-unique relation satisfying bounded depth (to be defined shortly).
-Right-unique means that given any $\hist \in \allhist$, $\dg(\hist) = \set{\ar \in \allargs \suchthat (\hist, \ar) \in \dg}$ is empty or is a singleton.
+  Formally speaking, a defense relation $\dg \subseteq \allhists × \allargs$ is a right-unique relation satisfying bounded depth (to be defined shortly).
+Right-unique means that given any $\hist \in \allhists$, $\dg(\hist) = \set{\ar \in \allargs \suchthat (\hist, \ar) \in \dg}$ is empty or is a singleton.
   As is usual for right-unique relations, we write $\dg(\hist) = \ar$ instead of $\dg(\hist) = \set{\ar}$ when $\dg(\hist)$ is a singleton (and $\dg(\hist) = \emptyset$ otherwise).
-  Given $H \subseteq \allhist$, define $\dg(H) = \set{\dg(\hist) \suchthat \alpha \in H} \subseteq \allargs$.
+  Given $H \subseteq \allhists$, define $\dg(H) = \set{\dg(\hist) \suchthat \alpha \in H} \subseteq \allargs$.
   Given $\ar_0, \ar_1 \in \allargs$, say that $\ar_1$ defends $\ar_0$
-  iff $\exists \hist \in \allhist \suchthat \ar_0 \in R(\hist) \land \dg(\hist) = \ar_1$, equivalently,
+  iff $\exists \hist \in \allhists \suchthat \ar_0 \in R(\hist) \land \dg(\hist) = \ar_1$, equivalently,
   iff $\ar_0 \in R(\dg^{-1}(\ar_1))$, equivalently,
@@
 
-  To define this formally, note that either $\arga$ is a decisive argument for $\pga$, or some paths challenge this claim, namely those $\hist \in \allhist$ such that $[\arga \in \histend \land \hist \nileadsto \pga]$.
+  To define this formally, note that either $\arga$ is a decisive argument for $\pga$, or some paths challenge this claim, namely those $\hist \in \allhists$ such that $[\arga \in \histend \land \hist \nileadsto \pga]$.
   Generalizing this observation, given $i \in I$, define $\dgi(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \in \histend \land \hist \nileadsto \pga} \subseteq \dg(\ar)$ as the subset of defenders of $\ar$ required for convincing $i$ of choosing $\pga$.
@@
     An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\allleadsto})$ is \emph{truthful} iff
-    $\forall i \in I, \hist \in \allhist, n \in \N, k \in \intvl{1, \card \hist}^n, \ar \in \allargs^n$:
+    $\forall i \in I, \hist \in \allhists, n \in \N, k \in \intvl{1, \card \hist}^n, \ar \in \allargs^n$:
     \begin{equation}
@@
     \label{ax:ans}
-    $\forall i \in I, \hist \in \allhist, \ar \in \gargsi$:
+    $\forall i \in I, \hist \in \allhists, \ar \in \gargsi$:
     \begin{equation}
@@
     \label{ax:ansn}
-    $\forall i \in I, \hist^j \in (\allhist)^n$:
+    $\forall i \in I, \hist^j \in (\allhists)^n$:
     \begin{equation}
@@
     \label{ax:r}
-    $\forall i \in I, \hist \in \allhist, \ar_1, \ar_2 \in \gargsi, \ar \in \allargs$:
+    $\forall i \in I, \hist \in \allhists, \ar_1, \ar_2 \in \gargsi, \ar \in \allargs$:
     \begin{equation}
@@
   \begin{axiom}[Self-sufficiency of positive arguments]
-    $\forall \ar_1, \ar_2 \in \gargsi, \ar \in \allargs, \hist \in \allhist$:
+    $\forall \ar_1, \ar_2 \in \gargsi, \ar \in \allargs, \hist \in \allhists$:
     \begin{equation}
@@
     \label{ax:omitting}
-    If the theory is truthful, then $\forall i \in I, k \in \N^*, l \in \intvl{2, k}, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist, \beta \in \allhist \suchthat [\ar_k \in \histend \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1})]:
+    If the theory is truthful, then $\forall i \in I, k \in \N^*, l \in \intvl{2, k}, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist, \beta \in \allhists \suchthat [\ar_k \in \histend \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1})]:
       (\beta, \ar_{l - 1}, \ar_l, \hist) \ileadsto \pga ⇒ (\beta, \ar_l, \hist) \ileadsto \pga$.

### 2023-10-22 simple.tex
Applying coro

@@
 \begin{example}
-  \label{ex:unfals}
+  \label{ex:disj}
   Given $\ar \neq \ar' \in \allargs$,
@@
 \begin{example}
-  $\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
+  \label{ex:partlyU}
+  Given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
+  $\hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
   Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
-  \Cref{ex:unfals} concludes.
+  \Cref{ex:disj} concludes.
 \end{example}
@@
   \label{th:veryunfals}
-  Any non-trivial claim $C$ satisfying $\forall O \in \allpriobss, {\allleadstog} \in \allleadstos: \restr{\allleadstog}{O} \in C^\subseteq$ is not falsifiable.
+  Any non-trivial claim $C$ satisfying $\Theta \subseteq C^\subseteq$ is not falsifiable.
 \end{corollary}
@@
   Pick any ${\allleadstog} \notin C$.
+  Per hypothesis, $\forall O \in \allpriobss$: $\restr{\allleadstog}{O} \in C^\subseteq$.
   Define $f$ as $\forall O \in \allpriobss: f(O) = \restr{\allleadstog}{O}$.
@@
   Considering again \cref{ex:bigor}, by \cref{th:veryunfals}, we see that $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$ is not falsifiable.
-\end{example}
+
+  Similarly, considering again \cref{ex:disj}, given $\ar \neq \ar' \in \allargs$,
+  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable, by \cref{th:veryunfals}.
+
+  Turning to \cref{ex:partlyU},
+  given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
+  $C = \set{{\allleadstog} \suchthat \hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ is not falsifiable but \cref{th:veryunfals} is not applicable.
+  Observe that $C^\subseteq = \set{R \in I × \allhists × P \suchthat [(j, \hist) \in R^{-1}(P) \implies (j, \hist, \phi) \in R] \land \forall i: [(i, (\ar)) \in R^{-1}(P) \land (i, (\ar')) \in R^{-1}(P)] \implies [(i, (\ar), \phi) \in R \land (i, (\ar'), \phi) \in R]}$.
+  Pick any $\allleadstog$ satisfying $\hist \ileadstog[j] \phi$ and $\exists i \suchthat (\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
+  The definition of non-falsifiability applies: pick any $\theta \subseteq {\allleadstog}$, we have $\theta \in C^\subseteq$ as $(j, \hist, \phi)$ is compatible with $\theta$ and the other condition excludes nothing in $\Theta$.
+  We can apply Thm 4 similarly: given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
+
+  We should be able to apply a corollary similarly.
+  Given any $O$, define $f(O) = \restr{\allleadstog}{O}$ and observe that $f(O) \in C^\subseteq$ although $\cup_{O \in \allpriobss} f(O) \notin C$.
+\end{example}
+
+TODO continue here (finish examples above).
 

### 2023-10-27 simple.tex
examples

@@
 \begin{example}
+  \label{ex:allParticular}
   Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
@@
 \begin{example}
+  \label{ex:existsParticular}
   Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
@@
 \end{example}
-\begin{example}
-  Consider any $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_1) \ileadstog^2 p'$.
-  The claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$ is unfalsifiable.
-
-  Consider … (seems redundant).
-\end{example}
+
 \begin{remark}
@@
 
+We thus reach a procedure to determine whether a claim is falsifiable.
+Given $C$, compute $C^\subseteq$. Find the set $R$ of relations $\allleadstog$ satisfying $\forall O: \restr{\allleadstog}{O} \in C^\subseteq$. The claim $C$ is falsifiable iff $R \subseteq C$.
+\begin{corollary}
+  A claim $C$ is falsifiable iff $\set{{\allleadstog} \in \allleadstos \suchthat \forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\subseteq} \subseteq C$.
+\end{corollary}
+A relation $\allleadstog$ is observably in $C$ iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)$.
+All relations in $C$ are observably in $C$. The question of falsifiability asks whether the converse holds.
+In other words, $C$ is falsifiable iff it includes the relations observably in $C$.
+Define that a relation ${\allleadstog} \in {\allleadstos}$ is \emph{obs-compatible} with a set $S$ iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S$.
+Then, the relations observably in $C$ are exactly those obs-compatible with $C^\subseteq \cap \Theta$.
+\begin{corollary}
+  A claim $C$ is falsifiable iff $\set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)} = C$.
+\end{corollary}
+\begin{remark}
+  The question of falsifiability is whether the set of relations $\allleadstog$ “compatible” with $C^\subseteq \cap \Theta$ equals $C$.
+  Compatibility needs to consider the observables, not a subset of it.
+  Define $\Theta_1 \subset \Theta$ as the observations that observe only one pair $(i, \hist)$.
+  Define $R_1 = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta_1: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)}$.
+  Note that $R \subseteq R_1$.
+  We know that $C$ is falsifiable iff $R \subseteq C$.
+Thus, $C$ is not falsifiable implies $C \subsetneq R \subseteq R_1$ thus $C \subsetneq R_1$.
+But we do not have that $C \subsetneq R_1$ implies $C$ not falsifiable: could have $C \subsetneq R_1$ but still $R = C$.
+\end{remark}
+
 \begin{example}
@@
   $C = \set{{\allleadstog} \suchthat \hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ is not falsifiable but \cref{th:veryunfals} is not applicable.
-  Observe that $C^\subseteq = \set{R \in I × \allhists × P \suchthat [(j, \hist) \in R^{-1}(P) \implies (j, \hist, \phi) \in R] \land \forall i: [(i, (\ar)) \in R^{-1}(P) \land (i, (\ar')) \in R^{-1}(P)] \implies [(i, (\ar), \phi) \in R \land (i, (\ar'), \phi) \in R]}$.
-  Pick any $\allleadstog$ satisfying $\hist \ileadstog[j] \phi$ and $\exists i \suchthat (\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
-  The definition of non-falsifiability applies: pick any $\theta \subseteq {\allleadstog}$, we have $\theta \in C^\subseteq$ as $(j, \hist, \phi)$ is compatible with $\theta$ and the other condition excludes nothing in $\Theta$.
-  We can apply Thm 4 similarly: given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
-
-  We should be able to apply a corollary similarly.
-  Given any $O$, define $f(O) = \restr{\allleadstog}{O}$ and observe that $f(O) \in C^\subseteq$ although $\cup_{O \in \allpriobss} f(O) \notin C$.
-\end{example}
-
-TODO continue here (finish examples above).
+  Observe that
+  $C^\subseteq = \set{R \in I × \allhists × P \suchthat [(j, \hist) \in R^{-1}(P) \implies (j, \hist, \phi) \in R] \land \forall i: [(i, (\ar)) \in R^{-1}(P) \land (i, (\ar')) \in R^{-1}(P)] \implies [(i, (\ar), \phi) \in R \land (i, (\ar'), \phi) \in R]}$ and
+  $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat (j, \hist) \in \theta^{-1}(P) \implies (j, \hist, \phi) \in \theta}$.
+  % Pick any $\allleadstog$ satisfying $\hist \ileadstog[j] \phi$ and $\exists i \suchthat (\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
+  % The definition of non-falsifiability applies: pick any $\theta \subseteq {\allleadstog}$, we have $\theta \in C^\subseteq$ as $(j, \hist, \phi)$ is compatible with $\theta$ and the other condition excludes nothing in $\Theta$.
+  % We can apply Thm 4 similarly: given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
+  % We should be able to apply a corollary similarly.
+  The relations obs-compatible with $C^\subseteq \cap \Theta$ are those satisfying $\hist \ileadstog[j] \phi$.
+  We conclude that $C$ is not falsifiable as $C$ is smaller than that set.
+
+  In \cref{ex:allParticular} we considered a given $\ar$ and $\phi$ and defined the falsifiable claim $C = \set{{\allleadstog} \suchthat \forall i: \ar \ileadstostg \phi}$.
+  Observe that $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat \forall \hist \suchthat \ar \in \histend: \theta(i, \hist) = \emptyset \lor \theta(i, \hist) = \phi}$.
+  The relations obs-compatible with $C^\subseteq \cap \Theta$ are exactly those in $C$.
+
+  \Cref{ex:existsParticular} assumed an infinite $I$, in which case the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
+  Observe that $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat \exists i \suchthat \forall \hist \suchthat \ar \in \histend: \theta(i, \hist) = \emptyset \lor \theta(i, \hist) = \phi}$.
+  Any relation ${\allleadstog}$ is obs-compatible with that set as $C^\subseteq \cap \Theta = \Theta$: given any $\theta \in \Theta$, there is an $i$ such that $\forall \hist: \theta(i, \hist) = \emptyset$ as $\theta$ must have a finite support.
+\end{example}
+
+\begin{remark}
+  Consider a set $S \wsub \Theta$.
+  We can define its border as follows.
+  Define a converging sequence in $\Theta$ as a sequence of strictly embedded elements $\Theta$, meaning increasing per strict inclusion (so $\theta_1 \ssub \theta_2 \ssub \theta_3…$), and which include every elements of $\hist × I$ (thus $\cup_i(\theta_i)^{-1}(P) = \hist × I$).
+  Such a sequence can be associated to a relation ${\allleadstog} \in \allleadstos$ in the natural way (${\allleadstog} = \cup_i(\theta_i)$).
+  Define $s_S$ as the set of such sequences.
+  The border of $S$ is the set $\set{\cup_i(\theta_i) \suchthat (\theta_i) \in s_S}$.
+  Nope, that’s not useful. That border is empty as soon as $\card{\allargs} ≥ 2$.
+\end{remark}
+\begin{conjecture}
+  Each element of $C$ is a forest (here, meaning, an association of each $i$ to a tree, whose nodes are all the triples in the element and related by “the pair in $\allhists × I$ is a close suffix of the pair in the parent”).
+  $C$ is falsifiable iff exists two compatible paths in two different such forests, for a given $i$, that are not in a single forest, for that $i$, of $C$.
+  % Given a claim $C$, define $S = C^\wsub \cap \Theta$.
+  % We have: $\set{\cup_i(\theta_i) \in \allleadstos \suchthat (\theta_i) \in s_S} = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S}$.
+\end{conjecture}
+\begin{proof}
+
+\end{proof}
+TODO continue here. Use example of constant to $p$ and constant to $p'$ with or without the empty argument and singleton $I$ (falsifiable VS not).
+\begin{example}
+  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p, p' \in P$.
+  The claim $C = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$ is falsifiable.
+
+  We have $C^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p) \land (\theta((\ar_2), i) = \emptyset \lor \theta((\ar_2), i) = p')}$.
+  The obs-compatible relations are $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$.
+\end{example}
+\begin{example}
+  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p, p' \in P$.
+  The claim $C = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \lor (\ar_2) \ileadstog p'}$ is unfalsifiable.
+
+  We have $C^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p) \lor (\theta((\ar_2), i) = \emptyset \lor \theta((\ar_2), i) = p')}$.
+  Observe that any $\theta \in \Theta$ satisfy $\theta((\ar_1), i) = \emptyset \lor \theta((\ar_2), i) = \emptyset$, thus, $C^\subseteq \cap \Theta = \Theta$.
+  It follows that the obs-compatible relations are $\allleadstos$, which is bigger than $C$.
+
+  The same holds if replacing $(\ar_1)$ and $(\ar_2)$ by any $\hist, \hist' \in \allhists$ that are not one a prefix of the other one.
+
+  Now consider the smaller claim $C' = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$ (thus $C' \ssub C$).
+  It yields a smaller set ${C'}^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p)}$.
+  The obs-compatible relations are the smaller set $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$.
+  Thus, $C'$ is falsifiable.
+
+  Note that any claim $C^{\prime\prime}$ bigger than $C$ is unfalsifiable as well (unless trivial):
+  from $C \wsub C^{\prime\prime}$, we deduce $\Theta = C^\subseteq \cap \Theta \wsub {C^{\prime\prime}}^\subseteq \cap \Theta$, thus ${C^{\prime\prime}}^\subseteq \cap \Theta = \Theta$ and the obs-compatible relations are $\allleadstos$, which equals $C^{\prime\prime}$ only if $C^{\prime\prime}$ is trivial.
+
+  Now consider the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the alternative smaller claim $C^{(2)} = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$ (thus $C^{(2)} \ssub C$).
+  It yields a smaller set ${C^{(2)}}^\subseteq \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
+  Consider any relation $\allleadstog$ that is obs-compatible with ${C^{(2)}}^\subseteq \cap \Theta$.
+Assume that for some $\hist, i$, $\hist \ileadstog p$.
+Then, pick any $j \neq i$, and observe that by obs-compatibility, for any $\hist'$, $\hist' \ileadstog[j] p$.
+  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and any $(\hist^{\prime\prime}, j)$).
+Conclude that $\allleadstog$ is constant to $p$.
+  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C^{(2)}$ is falsifiable.
+\end{example}
+\begin{remark}
+  Intuition (to be explored, TODO) is that when $C^\wsub \cap \Theta$ has the covering property, then the obs-compatible relations are easily deduced from the set (something like, just consider compatibility point per point, one singleton observation at a time).
+Covering is what is used above, something like $\exists i, \hist, \histp$ such that $\forall \hist^{\prime\prime}: [\forall j \neq i: \set{(\hist, i, .), (\histp, j, .)} \in C^\wsub \cap \Theta] \land [\exists j \neq i \suchthat \set{(\hist', i, .), (\hist^{\prime\prime}, j, .)} \in C^\wsub \cap \Theta]$.
+\end{remark}
+\begin{example}
+  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_2) \ileadstog^2 p'$.
+  Consider the claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$. When is it falsifiable considering these two relations?
+\end{example}
+
+TODO investigate claims that are non falsifiable but with $C^\wsub \cap \Theta \neq \Theta$.
+Then exhibit a claim such that a smaller one is not the same status and a bigger one is not the same status.
 

### 2023-10-27 simple.tex
Rm attempt with border (failed)

@@
 
-\begin{remark}
-  Consider a set $S \wsub \Theta$.
-  We can define its border as follows.
-  Define a converging sequence in $\Theta$ as a sequence of strictly embedded elements $\Theta$, meaning increasing per strict inclusion (so $\theta_1 \ssub \theta_2 \ssub \theta_3…$), and which include every elements of $\hist × I$ (thus $\cup_i(\theta_i)^{-1}(P) = \hist × I$).
-  Such a sequence can be associated to a relation ${\allleadstog} \in \allleadstos$ in the natural way (${\allleadstog} = \cup_i(\theta_i)$).
-  Define $s_S$ as the set of such sequences.
-  The border of $S$ is the set $\set{\cup_i(\theta_i) \suchthat (\theta_i) \in s_S}$.
-  Nope, that’s not useful. That border is empty as soon as $\card{\allargs} ≥ 2$.
-\end{remark}
 \begin{conjecture}

### 2023-11-06 simple.tex
Various draft conj about fals

@@
 \end{corollary}
-A relation $\allleadstog$ is observably in $C$ iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)$.
+A relation $\allleadstog$ is observably in $C$ iff $\forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\subseteq$, equivalently, iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)$.
 All relations in $C$ are observably in $C$. The question of falsifiability asks whether the converse holds.
@@
 \end{remark}
-
 \begin{example}
@@
 
-\begin{conjecture}
-  Each element of $C$ is a forest (here, meaning, an association of each $i$ to a tree, whose nodes are all the triples in the element and related by “the pair in $\allhists × I$ is a close suffix of the pair in the parent”).
-  $C$ is falsifiable iff exists two compatible paths in two different such forests, for a given $i$, that are not in a single forest, for that $i$, of $C$.
-  % Given a claim $C$, define $S = C^\wsub \cap \Theta$.
-  % We have: $\set{\cup_i(\theta_i) \in \allleadstos \suchthat (\theta_i) \in s_S} = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S}$.
-\end{conjecture}
-\begin{proof}
-
-\end{proof}
-TODO continue here. Use example of constant to $p$ and constant to $p'$ with or without the empty argument and singleton $I$ (falsifiable VS not).
+\begin{example}
+  \label{ex:cardPart}
+  Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhists$ with $\hist$ and $\histp$ non prefix related.
+  The claim $\psi = (\hist \ileadstog p \lor \hist \ileadstog p') \land (\histp \ileadstog p \lor \histp \ileadstog p') \land (\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p)$ is falsifiable.
+
+  Given $q, q' \in P$, let ${\allleadstog^{q, q'}}$ be defined as $\hist \ileadstog^{q, q'} q$, $\histp \ileadstog^{q, q'} q'$ and $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j]^{q, q'} p$.
+  Note that $C_\psi = \set{{\allleadstog^{p, p}}, {\allleadstog^{p, p'}}, {\allleadstog^{p', p}}, {\allleadstog^{p', p'}}}$.
+
+  Then, $C_\psi^\wsub \cap \Theta =
+    \set{\theta \in \Theta \suchthat \theta(\hist, i) \in \set{\emptyset, p, p'} \land \theta(\histp, i) \in \set{\emptyset, p, p'} \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
+  % and we see that $C_\psi^\wsub \cap \Theta =
+  % \set{\theta \in \Theta \suchthat [\theta(\hist, i) = \theta(\histp, i) = \emptyset \lor \theta(\hist, i) \in \set{p, p'} \lor \theta(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
+
+  Any obs-compatible relation has to satisfy $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p$.
+  It also must satisfy ${\allleadstog}(\hist, i) \in \set{p, p'}$, for otherwise, with $\theta = \set{(\hist, i, {\allleadstog}(\hist, i))}$, we get $({\allleadstog} \cap \theta) \notin C_\psi^\wsub \cap \Theta$.
+  Similarly, it must satisfy ${\allleadstog}(\histp, i) \in \set{p, p'}$.
+  % are $\set{{\allleadstog} \in \allleadstos \suchthat [{\allleadstog}(\hist, i) \in \set{p, p'} \lor {\allleadstog}(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p}$, which, given $p \neq p^{\prime\prime} \neq p'$, contains ${\allleadstog^{p, p^{\prime\prime}}}$, contrary to $C_\psi$.
+\end{example}
+
 \begin{example}
@@
 \begin{example}
-  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p, p' \in P$.
-  The claim $C = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \lor (\ar_2) \ileadstog p'}$ is unfalsifiable.
-
-  We have $C^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p) \lor (\theta((\ar_2), i) = \emptyset \lor \theta((\ar_2), i) = p')}$.
-  Observe that any $\theta \in \Theta$ satisfy $\theta((\ar_1), i) = \emptyset \lor \theta((\ar_2), i) = \emptyset$, thus, $C^\subseteq \cap \Theta = \Theta$.
-  It follows that the obs-compatible relations are $\allleadstos$, which is bigger than $C$.
-
-  The same holds if replacing $(\ar_1)$ and $(\ar_2)$ by any $\hist, \hist' \in \allhists$ that are not one a prefix of the other one.
-
-  Now consider the smaller claim $C' = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$ (thus $C' \ssub C$).
-  It yields a smaller set ${C'}^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p)}$.
-  The obs-compatible relations are the smaller set $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$.
-  Thus, $C'$ is falsifiable.
-
-  Note that any claim $C^{\prime\prime}$ bigger than $C$ is unfalsifiable as well (unless trivial):
-  from $C \wsub C^{\prime\prime}$, we deduce $\Theta = C^\subseteq \cap \Theta \wsub {C^{\prime\prime}}^\subseteq \cap \Theta$, thus ${C^{\prime\prime}}^\subseteq \cap \Theta = \Theta$ and the obs-compatible relations are $\allleadstos$, which equals $C^{\prime\prime}$ only if $C^{\prime\prime}$ is trivial.
-
-  Now consider the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the alternative smaller claim $C^{(2)} = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$ (thus $C^{(2)} \ssub C$).
-  It yields a smaller set ${C^{(2)}}^\subseteq \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
-  Consider any relation $\allleadstog$ that is obs-compatible with ${C^{(2)}}^\subseteq \cap \Theta$.
+  \label{ex:consti2}
+  Assume that $\card{I} ≥ 2$.
+  Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
+  We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
+  Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$.
 Assume that for some $\hist, i$, $\hist \ileadstog p$.
@@
 Conclude that $\allleadstog$ is constant to $p$.
-  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C^{(2)}$ is falsifiable.
-\end{example}
+  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
+\end{example}
+\begin{example}
+  \label{ex:consti1}
+  Assume that $\card{I} = 1$.
+  Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
+  We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
+  Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$.
+Assume that for some $\hist, i$, $\hist \ileadstog p$.
+Observe that by obs-compatibility, $\emptyset \ileadstog p$.
+  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and $(\emptyset, i)$).
+Conclude that $\allleadstog$ is constant to $p$.
+  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
+\end{example}
+\begin{example}
+  \label{ex:constwout0}
+  Consider any $p, p' \in P$ and the claim $C = \set{{\allleadstog} \suchthat (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p) \lor (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p')}$.
+That claim is falsifiable iff $\card I ≥ 2$ or $\card \allargs = 1$.
+The proof if so is similar to \cref{ex:consti2}; otherwise, pick any $\ar \in \allargs$ and note that any relation satisfying $(a.*) \ileadstog p$ and $\forall b \neq a: (b.*) \ileadstog p'$ is obs-compatible with $C^\wsub \cap \Theta$ but is not in $C$.
+\end{example}
+\begin{example}
+  \label{ex:unfor}
+  Consider any $i$, $\hist, \histp \in \allhists$, $p, p' \in P$ where $\hist$ and $\histp$ are not prefix related.
+  The claim $C = \set{{\allleadstog} \suchthat \hist \ileadstog p \lor \histp \ileadstog p'}$ is unfalsifiable.
+
+  We have $C^\wsub \cap \Theta = \set{\theta \suchthat (\theta(\hist, i) = \emptyset \lor \theta(\hist, i) = p) \lor (\theta(\histp, i) = \emptyset \lor \theta(\histp, i) = p')}$.
+  Observe that any $\theta \in \Theta$ satisfy $\theta(\hist, i) = \emptyset \lor \theta(\histp, i) = \emptyset$, thus, $C^\wsub \cap \Theta = \Theta$.
+  It follows that the obs-compatible relations are $\allleadstos$, which is bigger than $C$.
+\end{example}
+\begin{example}
+  Consider any $i$, $\ar \neq \ar' \in \allargs$, $p, p' \in P$.
+  The claim $C = \set{{\allleadstog} \suchthat (\ar) \ileadstog p \lor (\ar') \ileadstog p'}$ is unfalsifiable (per \cref{ex:unfor}).
+
+  Now consider the smaller claim $C' = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$ (thus $C' \ssub C$).
+  It yields a smaller set ${C'}^\wsub \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p)}$.
+  The obs-compatible relations are the smaller set $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$.
+  Thus, $C'$ is falsifiable.
+
+  Note that any claim $C^{\prime\prime}$ bigger than $C$ is unfalsifiable as well, unless trivial:
+  from $C \wsub C^{\prime\prime}$, we deduce $\Theta = C^\wsub \cap \Theta \wsub {C^{\prime\prime}}^\wsub \cap \Theta$, thus ${C^{\prime\prime}}^\wsub \cap \Theta = \Theta$ and the obs-compatible relations are $\allleadstos$, which equals $C^{\prime\prime}$ only if $C^{\prime\prime}$ is trivial.
+
+  Now consider the alternative smaller claim of \cref{ex:consti2}, $C^{(2)} = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$ (thus $C^{(2)} \ssub C$).
+  It yields a smaller set ${C^{(2)}}^\wsub \cap \Theta$.
+\end{example}
+\begin{example}
+  \label{ex:for}
+  Consider any $i$ and $p, p' \in P$.
+  The claim $C = \set{{\allleadstog} \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \hist \ileadstog p) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \hist \ileadstog p')}$, namely, all paths of even lengths lead $i$ to $p$ OR all paths of odd lengths or empty lead $i$ to $p'$, is falsifiable.
+
+  Note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \theta(\hist) \in \set{\emptyset, p}) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \theta(\hist) \in \set{\emptyset, p'})}$.
+  Consider any obs-compatible ${\allleadstog}$.
+  Assume that $\exists \hist \suchthat \card{\hist} \in 2\N \land \hist \nileadstog p$.
+  Pick $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\hist, i, {\ileadstog}(\hist))}$.
+We have $({\allleadstog} \cap \theta) \in C^\wsub \cap \Theta$, and ${\allleadstog} \cap \theta = \theta$, and from $\theta \in C^\wsub \cap \Theta$ we obtain ${\ileadstog}(\emptyset) = p'$.
+  Similarly, using $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\histp, j, {\ileadstog[j]}(\histp))}$, we obtain that $\allleadsto$ conforms to the relation in $C$.
+\end{example}
+
+\begin{remark}
+  \label{rq:closedcomb}
+  Being closed-under-combinations (where a combination forms a new relation by union of parts of relations in $C$) is sufficient to be falsifiable, but not necessary, as seen with \cref{ex:consti2}.
+\end{remark}
+
 \begin{remark}
@@
 \end{remark}
+
+Define the \emph{suffix} relation $R = \set{(\hist, \histp) \in \allhists × \allhists \suchthat \histp = (\hist, .)}$ as the (infinite) tree whose set of nodes is $\allhists$ and which links  argumentative paths to all of their direct suffixes.
+Note that a path in such a tree (an increasing sequence of elements in $\allhists$) corresponds to an argumentative path, that is, to an element of $\allhists$.
+
+Any function ${\ileadstog}: \allhists \mapsto P$ can be considered as having this tree as a domain.
+% Define a forest as an association of each $i \in I$ to such a tree.
+Any relation ${\allleadstog} \in \allleadstos$ can then be viewed as a forest associating each $i \in I$ to a tree labeled by the function ${\ileadstog}$ (see \cref{fig:forest}).
+
+\begin{figure}
+  \begin{tikzpicture}[level distance=0.7cm]
+
+    \tikzstyle{treenode}=[execute at begin node=$, execute at end node=$]
+    \tikzstyle{treelabel}=[treenode, anchor=west, inner sep=0]
+    \tikzstyle{bottomnode}=[execute at begin node=$\scriptstyle, execute at end node=$]
+    \tikzstyle{bottomlabel}=[bottomnode, anchor=west, inner sep=0]
+    \tikzstyle{tree}=[level 1/.style={sibling distance=3.4cm, every node/.style=treenode},
+    level 2/.style={sibling distance=1.6cm, every node/.style=bottomnode},
+    level 3/.style={sibling distance=0.7cm, every node/.style=treenode}
+    ]
+    \newlength{\lhi}
+    \setlength{\lhi}{3.5cm}
+    \newlength{\lvi}
+    \setlength{\lvi}{1.2cm}
+
+    \path node (all) {$\allleadstog$};
+
+    \path (-\lhi, -\lvi) node[anchor=north] (tree1) {\begin{tikzpicture}
+        \path[tree] node (root) {$\emptyset$}
+        child {
+            node (a) {(a)}
+            child {
+                node (aa) {(aa)}
+                child {
+                    node {…}
+                  }
+                child {
+                    node {…}
+                  }
+              }
+            child {
+                node (ab) {(ab)}
+                child {
+                    node {…}
+                  }
+                child {
+                    node {…}
+                  }
+              }
+          }
+        child {
+            node (b) {(b)}
+            child {
+                node (ba) {(ba)}
+                child {
+                    node {…}
+                  }
+                child {
+                    node {…}
+                  }
+              }
+            child {
+                node (bb) {(bb)}
+                child {
+                    node {…}
+                  }
+                child {
+                    node {…}
+                  }
+              }
+          }
+        ;
+        \begin{scope}[style=treelabel]
+          \path (root.east) node {\mapsto p};
+          \path (a.east) node {\mapsto p'};
+          \path (b.east) node {\mapsto p};
+        \end{scope}
+        \begin{scope}[style=bottomlabel]
+          \path (aa.east) node {\mapsto p'};
+          \path (ab.east) node {\mapsto p'};
+          \path (ba.east) node {\mapsto p'};
+          \path (bb.east) node {\mapsto p};
+        \end{scope}
+      \end{tikzpicture}};
+    \path[->] (all) edge node[midway, above] {$i_1$} (tree1.north);
+
+    \path (\lhi, -\lvi) node[anchor=north] (tree2) {\begin{tikzpicture}
+        \path[tree] node (root) {$\emptyset$}
+        child {
+            node (a) {(a)}
+            child {
+                node (aa) {(aa)}
+                child {
+                    node {…}
+                  }
+                child {
+                    node {…}
+                  }
+              }
+            child {
+                node (ab) {(ab)}
+                child {
+                    node {…}
+                  }
+                child {
+                    node {…}
+                  }
+              }
+          }
+        child {
+            node (b) {(b)}
+            child {
+                node (ba) {(ba)}
+                child {
+                    node {…}
+                  }
+                child {
+                    node {…}
+                  }
+              }
+            child {
+                node (bb) {(bb)}
+                child {
+                    node {…}
+                  }
+                child {
+                    node {…}
+                  }
+              }
+          }
+        ;
+        \begin{scope}[style=treelabel]
+          \path (root.east) node {\mapsto p};
+          \path (a.east) node {\mapsto p};
+          \path (b.east) node {\mapsto p'};
+        \end{scope}
+        \begin{scope}[style=bottomlabel]
+          \path (aa.east) node {\mapsto p};
+          \path (ab.east) node {\mapsto p'};
+          \path (ba.east) node {\mapsto p'};
+          \path (bb.east) node {\mapsto p};
+        \end{scope}
+      \end{tikzpicture}};
+    \path[->] (all) edge node[midway, above] {$i_2$} (tree2.north);
+  \end{tikzpicture}
+  \caption{A forest}
+  \label{fig:forest}
+\end{figure}
+
+\begin{conjecture}
+  $C$ is falsifiable iff exists two compatible paths in two different such forests, for a given $i$, that are not in a single forest, for that $i$, of $C$.
+  This seems incorrect; need to be able to build a union relation!
+  Prove that it is false with claim "i goes to phi OR i goes to not phi except for empty set going to phi"?
+  Actually I need to be able to merge two relations that agree on everything but some part of the tree, in such a way that all paths crossing the boundary must be in $C$, but not the merge.
+  TODO caract with singleton $I$.
+  % Given a claim $C$, define $S = C^\wsub \cap \Theta$.
+  % We have: $\set{\cup_i(\theta_i) \in \allleadstos \suchthat (\theta_i) \in s_S} = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S}$.
+\end{conjecture}
+\begin{remark}
+  Say that $(r1, o1)$ is determined in $C$ (to $p$) iff all relations in $C$ including $r1$ agree on ${\allleadstog}(o)$ (satisfy ${\allleadstog}(o) = p$).
+  Let $C(r, o)$ equal $\set{{\allleadstog}(o) \suchthat {\allleadstog} \in C \land r \in {\allleadstog}}$.
+
+  A claim satisfying, $\forall {\allleadstog} \in C$:
+  $\forall r1 = (o1, p1) \in {\allleadstog}$, $\exists o2$ with $o1$ and $o2$ obs-compatible and $(r1, o2)$ determined in $C$ such that $\forall o3: (o2, o3)$ is obs-compatible and $(r2 = (o2, C(r1, o2)), o3)$ is determined in $C$
+  %Perhaps can omit $(r1, o2)$ determined. In fact, has to satisfy that these determine only relations in $C$.
+  % \[\forall (\hist, i, p) \in {\allleadstog}, \exists (\histp, j, p) \in {\allleadstog} \suchthat \forall (\histpp, k) \in \allhists × I: \set{(\histp, j), (\histpp, k)} \in O\]
+  is falsifiable.
+
+  NOPE.
+  Need to say that $C$ is a union of disjoint subsets such that each subset $C'$ include all relations that are specified on a subset of observations (and left free on everything else) which satisfy something like the above condition: all points related to a point that is related to all others.
+\end{remark}
+\begin{theorem}
+  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
+  % $C = \set{\restr{\allleadstog}{R} \cup \restr{\allleadstog}{R'} \suchthat R' \in (I × \allhists) \setminus R}$.
+  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
+
+  If $\exists R \subseteq I × \allhists$ such that $C$ is determined on $R$ and satisfying $\exists o \in R \suchthat \forall o' \in R: (\set{o, o'} \in \allpriobss)$, then $C$ is falsifiable.
+\end{theorem}
+\begin{proof}
+  Note that as $C$ is closed-under-combinations, this follows from \cref{rq:closedcomb}, but let’s design a more direct proof in hope of weakening the condition.
+
+  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.
+
+  % Pick any $o_1 \in R$.
+  % Define $r_1 = (o_1, {\allleadstog}(o_1))$, thus with $r_1 \in {\allleadstog}$.
+  Pick some $o \in R$ as in the hypothesis.
+  Consider any $o' \in R$.
+  As $\set{o, o'} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
+  % $\exists {\allleadstog'} \suchthat \restr{\allleadstog}{\set{o, o'}} = \restr{\allleadstog'}{\set{o, o'}}$.
+  $\restr{\allleadstog}{\set{o, o'}} \in C^\wsub$.
+  Thus, ${\allleadstog}(o') = f(o')$.
+
+  We obtain that $\forall o' \in R: {\allleadstog}(o') = f(o')$, therefore, ${\allleadstog} \in C$.
+\end{proof}
+\begin{conjecture}[draft]
+  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
+  % $C = \set{\restr{\allleadstog}{R} \cup \restr{\allleadstog}{R'} \suchthat R' \in (I × \allhists) \setminus R}$.
+  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
+  Say that $R$ is coverable iff $\exists o_1, …, O_1, … \suchthat \forall o \in O_1: \set{o_1, o} \in \allpriobss \land \forall o \in O_2: \set{o_2, o} \in \allpriobss \land … \land \set{o_i, o_{i + 1}} \in \allpriobss \land \cup O_i = R \land o_i \in R$.
+
+  If $\exists R \subseteq I × \allhists$ coverable and such that $C$ is determined on $R$, then $C$ is falsifiable.
+\end{conjecture}
+\begin{proof}
+  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.
+
+  Pick some $o_1 \in R$ as in the hypothesis.
+  Consider any $o \in O_1 \cup \set{o_2}$.
+  As $\set{o_1, o} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
+  $\restr{\allleadstog}{\set{o_1, o}} \in C^\wsub$.
+  As also $o_1, o \in R$, ${\allleadstog}(o) = f(o)$.
+  In particular, ${\allleadstog}(o_2) = f(o_2)$.
+  Iterate with $o_2$ and $o \in O_2$, and so on.
+  We obtain that $\forall o \in R: {\allleadstog}(o) = f(o)$, therefore, ${\allleadstog} \in C$.
+\end{proof}
+\begin{example}
+  Pick $i \in I$ and
+  define $o_1 = ((a), i)$,
+  $o_2 = (\emptyset, i)$ and
+  $o_3 = ((b), i)$.
+  Define $R = \set{o_1, o_2, o_3}$.
+  Define $f_1, f_2, f_3 \in P^R$ as follows.
+  $f_1(o_1) = \phi$,
+  $f_1(o_2) = ¬\phi$,
+  $f_1(o_3) = \phi$.
+  $f_2(o_1) = \phi$,
+  $f_2(o_2) = \phi$,
+  $f_2(o_3) = ¬\phi$.
+  $f_3(o_1) = ¬\phi$,
+  $f_3(o_2) = \phi$,
+  $f_3(o_3) = \phi$.
+  Define $C = \set{f \cup g \suchthat f \in \set{f_1, f_2, f_3} \land g \in P^{(I × \allhists) \setminus R}}$.
+
+  Note that $R$ is covered by $O_1 = \set{o_1}, O_2 = \set{o_2}, O_3 = \set{o_3}$.
+  Note that $C$ is determined on $R$.
+  Yet, $C$ is not falsifiable.
+
+  Note that
+  \begin{equation}
+    C^\wsub \cap \Theta = \left\{\theta \in \Theta \suchthat
+    \begin{aligned}
+       & (\theta(o_1) \in \set{\emptyset, \phi} \land \theta(o_2) \in \set{\emptyset, ¬\phi} \land \theta(o_3) \in \set{\emptyset, \phi}) \lor \mbox{} \\
+       & (\theta(o_1) \in \set{\emptyset, \phi} \land \theta(o_2) \in \set{\emptyset, \phi} \land \theta(o_3) \in \set{\emptyset, ¬\phi}) \lor \mbox{} \\
+       & (\theta(o_1) \in \set{\emptyset, ¬\phi} \land \theta(o_2) \in \set{\emptyset, \phi} \land \theta(o_3) \in \set{\emptyset, \phi})
+    \end{aligned}\right\}.
+  \end{equation}
+  Also, $\theta(o_1) \neq \emptyset \implies \theta(o_3) = \emptyset$ (and equivalently, $\theta(o_3) \neq \emptyset \implies \theta(o_1) = \emptyset$),
+  whence:
+  \begin{equation}
+    C^\wsub \cap \Theta = \left\{\theta \in \Theta \suchthat
+    \begin{aligned}
+       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, ¬\phi}) \lor \mbox{} \\
+       & (\theta(o_1) = \phi \land \theta(o_2) \in \set{\emptyset, ¬\phi}) \lor \mbox{}                    \\
+       & (\theta(o_3) = \phi \land \theta(o_2) \in \set{\emptyset, ¬\phi}) \lor \mbox{}                    \\
+       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}  \\
+       & (\theta(o_1) = \phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                     \\
+       & (\theta(o_3) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                    \\
+       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}  \\
+       & (\theta(o_1) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                    \\
+       & (\theta(o_3) = \phi \land \theta(o_2) \in \set{\emptyset, \phi})
+    \end{aligned}\right\}.
+  \end{equation}
+  Factorizing:
+  \begin{equation}
+    C^\wsub \cap \Theta = \left\{\theta \in \Theta \suchthat
+    \begin{aligned}
+       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, \phi, ¬\phi})) \lor \mbox{} \\
+       & (\theta(o_1) = \phi \land \theta(o_2) \in \set{\emptyset, \phi, ¬\phi}) \lor \mbox{}                     \\
+       & (\theta(o_3) = \phi \land \theta(o_2) \in \set{\emptyset, \phi, ¬\phi}) \lor \mbox{}                     \\
+       & (\theta(o_3) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                           \\
+       & (\theta(o_1) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi})
+    \end{aligned}\right\}.
+  \end{equation}
+
+  Pick any $g \in P^{(I × \allhists) \setminus R}$ and define ${\allleadstog} = \set{(\emptyset, i, \phi), ((a), i, \phi), ((b), i, \phi)} \cup g$.
+  This relation is obs-compatible with $C^\wsub \cap \Theta$, but ${\allleadstog} \notin C$.
+\end{example}
+\begin{conjecture}
+  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
+  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
+  Say that $R$ is coverable iff $\exists k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}} \suchthat
+    \cup_{l \in \intvl{1, k}} O_l = R \land
+    \forall l \in \intvl{1, k}: o_l \in O_l \land
+    \forall o \in O_l: \set{o_l, o} \in \allpriobss \land
+    \forall l \in \intvl{1, k - 1}: \set{o_l, o_{l + 1}} \in \allpriobss$.
+
+  If $\exists R \subseteq I × \allhists$ coverable and such that $C$ is determined on $R$, then $C$ is falsifiable.
+\end{conjecture}
+\begin{proof}
+  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.
+
+  Pick some $k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}}$ as in the hypothesis.
+  Consider any $l \in \intvl{1, k - 1}$
+  and any $o \in O_l \cup \set{o_{l + 1}}$.
+  As $\set{o_l, o} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
+  $\restr{\allleadstog}{\set{o_l, o}} \in C^\wsub$.
+  As also $o_l, o \in R$ (per $\cup_{l' \in \intvl{1, k}} O_{l'} = R$), ${\allleadstog}(o) = f(o)$.
+  In particular, ${\allleadstog}(o_{l + 1}) = f(o_{l + 1})$.
+  Iterate with $o_2$ and $o \in O_2$, and so on.
+  We obtain that $\forall o \in R: {\allleadstog}(o) = f(o)$, therefore, ${\allleadstog} \in C$.
+\end{proof}
+\begin{conjecture}
+  Given $R \subseteq I × \allhists$, define ${\sim_R} \subseteq \allleadstos × \allleadstos$ as $f \sim_R f'$ iff $\restr{f}{R} = \restr{f'}{R}$. This is an equivalence relation.
+  Given $f \in \allleadstos$, define the equivalence class of $f$ for ${\sim_R}$ as ${\sim_R}(f) = \set{f' \in \allleadstos \suchthat f \sim_R f'} = \set{f' \in P^{(I × \allhists)} \suchthat \restr{f}{R} = \restr{f'}{R}}$.
+
+  Given $R \subseteq I × \allhists$, define the a priori observable subsets of $R$ as $Z_R = \allpriobss \cap \powerset{R}$.
+
+  Consider $R \subseteq I × \allhists$, $F \subseteq P^R$ and $C = \set{f \cup g \suchthat f \in F \land g \in P^{(I × \allhists) \setminus R}}$.
+  The claim $C$ is unfalsifiable iff $\exists {\allleadstog} \in \allleadstos \suchthat \bigcap_{O \in Z_R} {\sim_O}(f) \cap C = \emptyset$.
+
+    % Given $k \in \N$ and a family $(O_l)_{l \in \intvl{1, k}}$, consider $\exists f \in C \suchthat 
+    Say that $R$ is coverable iff $\exists k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}} \suchthat
+  \cup_{l \in \intvl{1, k}} O_l = R \land
+  \forall l \in \intvl{1, k}: o_l \in O_l \land
+  \forall o \in O_l: \set{o_l, o} \in \allpriobss \land
+  \forall l \in \intvl{1, k - 1}: \set{o_l, o_{l + 1}} \in \allpriobss$.
+
+    If $\exists R \subseteq I × \allhists$ coverable and such that $C$ is determined on $R$, then $C$ is falsifiable.
+\end{conjecture}
+TODO extend this so as to cover eg $C$ containing $f_1$ and $f_2$ constant functions as in example; but not covering when the domain is not suitable!
+Use proof similar to \cref{ex:for}, getting started with observing that any obs-compatible $\allleadstog$ failing every element but one of $C$ at least at one point must then satisfy the last element of $C$ at some point (?).
+\begin{conjecture}
+  If $\forall {\allleadstog} \in C: \exists R \suchthat {\allleadstog} = f \cup g$ with $f \in P^R, g \in P^{(I × \allhists) \setminus R}$ and $R$ converable, then $C$ is falsifiable.
+  Should be specified better, but also, not sure that this holds: consider C being a leads i to phi OR b leads i to phi (given i).
+  Perhaps something like $\exists F \suchthat C = \cup_{f \in F} \set{f \cup g}$ where $f^{-1}(P)$ being coverable.
+\end{conjecture}
+\begin{proof}
+  Problem is: how to get started?
+\end{proof}
+
 \begin{example}
@@
 \end{proof}
-The following example illustrates the need for the condition about the combination in the theorem.
-\begin{example}
-  Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhists$ with $\hist$ and $\histp$ non prefix related.
-  The claim $\psi = (\hist \ileadstog p \lor \hist \ileadstog p') \land (\histp \ileadstog p \lor \histp \ileadstog p') \land (\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p)$ is falsifiable.
-
-  Given $q, q' \in P$, let ${\allleadstog^{q, q'}}$ be defined as $\hist \ileadstog^{q, q'} q$, $\histp \ileadstog q'$ and $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p$.
-  Note that $C_\psi = \set{{\allleadstog^{p, p}}, {\allleadstog^{p, p'}}, {\allleadstog^{p', p}}, {\allleadstog^{p', p'}}}$.
-\end{example}
+\Cref{ex:cardPart} illustrates the need for the condition about the combination in the theorem.
 

### 2023-11-10 simple.tex
Cleaning fals

@@
 
-That the deliberated choice of any individual $i$ is well-defined may be doubtful, as it involves counterfactuals.
-To see this, let $\hist = (a_1, a_2, a_e)$ designate the argumentative path where the arguments are shown in the order they are described in \cref{ex:tutor}, and let $\hist' = (a_e, a_2, a_1)$ designate the reverse order.
+Now that deliberated choices are defined, we need to explore what one can learn about deliberated choices using our empirically available data.
+This requires to define claims about deliberated choices and to explore how to validate claims.
+
+\section{Claims about deliberated choice}
+Given an exposure protocol $(I, \allargs, {\allleadsto})$, consider a claim about $\allleadsto$, such as “every individuals in $I$ choose deliberately $\phi$”, or, in \cref{ex:tutor}, “$a_e$ is a decisive argument for $i$ in favor of $\phi_2$”.
+Validating claims about deliberated choice is no trivial matter, for two reasons.
+
+First,
+such claims must entail an infinity of constraints about $\allleadsto$:
+in order to deduce that $p \in P_i$ for some $p \in P, i \in I$, the claim must constrain $\ileadsto$ on every possible paths $\alpha \in \allhists$.
+It follows that a claim cannot be validated empirically exhaustively by observing the value of $\allleadsto$ on every points that it constraints.
+
+Second,
+our observations are limited in important ways: once we have shown some arguments to a given individual $i$, we cannot undo the effects of this action on $i$ and show to her a different argument as if starting from scratch (unless assuming $i$ forgets arguments after a while and waiting for sufficiently long, which would create practical and theoretical difficulties).
+In other words, once we have shown a path $\hist$ to $i$, we can only continue the protocol with $i$ by showing paths $\histp$ that are suffixes of $\hist$.
+
+To illustrate this point with \cref{ex:tutor}, let $\hist = (a_1, a_2, a_e)$ designate the argumentative path where the arguments are shown in the order they are described in \cref{ex:tutor}, and let $\hist' = (a_e, a_2, a_1)$ designate the reverse order.
 The deliberated choice concept is defined so as to not depend on the order of the arguments shown to $i$: for having $\prop \in P_i$, it must be that directing to $i$ the path $\hist$ or the path $\hist'$ both lead $i$ to choose $\prop$.
-However, once we have shown $\hist$ to $i$, we cannot show to her $\hist'$ (unless assuming $i$ forgets arguments after a while and waiting for sufficiently long, which would create practical and theoretical difficulties).
-
-This difficulty is resolved using falsifiable general theories, applicable to $I$ and not solely to a given $i$, so that $\hist$ can be tested on $i$ and $\hist'$ on some $i' ≠ i$.
-Indeed, we need a way to empirically test claims such as the one concluding \cref{ex:tutor}, according to which $a_e$ is a decisive argument.
-This is achieved in the next section thanks to theories of deliberated choice.
+But it is impossible to observe both the value of ${\allleadsto}(i, \hist)$ and the value of ${\allleadsto}(i, \hist')$.
+
+The first difficulty is familiar as it occurs in any endeavor to validate general claims in science: claims that cover a large (or infinite) spectrum cannot be validated by observing the system exhaustively.
+One must rather develop a falsification protocol, that is, a way to invalidate the claim, and then observe that the claim is not invalidated.
+This is the approach taken in the next section.
+
+This approach also permits to tackle the second difficulty, by letting us study theoretically the needs and limits of falsification given our observable basis.
 % Such theories contain an observable claim and a conclusion claim, so as to satisfy two properties.
@@
 
-\section{Theories of deliberated choice}
-This section assumes that an exposure protocol $(I, \allargs, {\allleadsto})$ is defined, and defines theories of deliberated choice associated with that exposure protocol.
-We will start with very simple theories (\cref{sec:static}) in order to build an intuition about the conditions required on theories of deliberated choice, then justify the need for more complex theories (\cref{sec:lichtenstein}) and finally define more general theories of deliberated choice (\cref{sec:dynamic}).
-
-\subsection{Theories using a static decisive argument}
-\label{sec:static}
-\Cref{ex:tutor} suggests a simple form for theories of deliberated choice: suffice to determine an argument $\ar \in \allargs$ and a preference $p \in P$ such that the theory claims that $\forall i \in I: \ar \ileadstost p$ and that $\forall i \in I: p \in P_i$.
-
-\begin{definition}[Static theory]
-  \label{def:static}
-  A static theory is a pair $(p, \ar)$ for some $p \in P$ and some $\ar \in \allargs$.
-\end{definition}
-A static theory $(p, \ar)$ is said to be truthful iff $\forall i \in I: \ar \ileadstost p$, and to be correct iff $\forall i \in I: p \in P_i$.
-We can then deduce that such theories are valid, meaning that their truthfulness implies their correctness.
-Let us make this (very simple) result stand out as a theorem, because a parallel will be usefully made with more complicated theories.
-%Note that this result immediately follows from \cref{ax:decisive}.
-\begin{theorem}[Static theories are valid]
-  Any truthful static theory is correct.
-\end{theorem}
-\begin{proof}
-  This follows immediately from \cref{def:decisive}.
-\end{proof}
-Importantly, truthfulness can indeed be checked using our observational basis, that is, if $\exists i \in I \suchthat \ar \nileadstost p$, then it is possible to exhibit this fact experimentally.
-
-Such theories have the merit of simplicity, but there is a need to design more adaptive theories: in many interesting cases, no single argument will be considered decisive by all individuals in $I$.
-We then need theories that argue with individuals by reacting to what they consider good arguments.
-The following section illustrates this need.
-
-\subsection{Some decision problems with no single decisive argument}
-\label{sec:lichtenstein}
-One ambition of the theories to be proposed here is to permit exhibiting the existence of a deliberated consensus among a large set of persons about issues that involve numerous arguments and counter-arguments.
-
-In many decision problems, individuals will not be attracted by the same set of arguments and counter-arguments, even though they may finally settle to the same preference.
-Imagine that some individual $i_1$ considers an argument $a_1$ for $\nprop$ relevant and some individual $i_2$ considers an argument $a_2$ for $\nprop$ relevant, but $i_1$ does not consider $a_2$ relevant and $i_2$ does not consider $a_1$ relevant (for example, because they already have some counter-arguments in mind to those arguments).
-Imagine further that there is some counter-argument $a'_1$ that can be given to $i_1$ to rebut $a_1$, and a different counter-argument $a'_2$ that can be given to $i_2$ to rebut $a_2$, so that they both have $\prop$ in their deliberated judgment when considering all these arguments.
-In such situation, static theories as defined in \cref{sec:static} are ill suited: these theories need to present the same argument to all individuals and would thus need to define a bigger argument $a$ containing both $a'_1$ and $a'_2$.
-Such an argument could be too long to be convincing to $i_1$ or $i_2$, as it needlessly spends efforts countering an argument that the individual considers irrelevant to start with.
-This  will become an important problem if there are not only two but many a priori possible arguments $a_k$ for $\nprop$, a small subset of which is considered relevant by any given individual, each with their own counter-argument $a'_k$ for $\prop$.
-This section is devoted to describing two examples to illustrate that point.
-Bear in mind that these examples may look somehow naïve on the aspect of the hypothesis they make about what convinces individuals.
-Real-world complex decision situations will require complex theories that do not fit the purpose of simple illustrative examples.
-Their goal is to argue that non-static theories are required, but not to fully describe such theories.
-
-%For a partial illustration about an ambitious setting, consider a decision to be taken about the relevance of some concrete action to help cope with climate change, and let $I$ be a set of citizens interested in the climate issue.
-The complete set of all arguments that will be considered relevant by at least one individual may well be very large.
-It may also be that, for each individual who considers relevant some arguments $A$ against the proposed concrete action, it is possible to give counter-arguments $A'$ that will convince the individual to opt for the proposal.
-One of the settings discussed by \citet{thaler_nudge_2009} permits such an illustration. %to illustrate this point more concretely.
-Let $I$ be a set of workers interested in establishing a savings plan.
-The authors claim that workers tend to not save enough because of psychological biases.
-It is therefore tempting to conjecture that the deliberated choice of those workers is to save more, in the sense defined here, than what their natural choice (the one revealed in absence of arguments) leads to.
-A difficulty related to this decision problem is that the complete set of all arguments that will be considered relevant by at least one individual for such a complex issue may well be very large.
-It may also be that, for each individual who considers relevant some arguments $A$ for saving not much (i.e., spending more in the short term), it is possible to give counter-arguments $A'$ that will convince the individual to opt for saving more.
-But no single argument could be decisive for each $i \in I$: it could be that only counter-arguments built specifically according to what a given individual considers relevant could convince her, given the complexity of the issue.
-This illustrates that the deliberated choice of each individuals in $I$ may be to save more even though no static theory (\cref{def:static}) may achieve showing it, as it could be that no such theory is truthful.
-
-%The above setting illustrates the ambition of this research program, but at the price of rendering impossible in the confines of this article to define fully the set of arguments and giving a complete account of a concrete theory of deliberated choice in such a complex setting, an endeavor of its own.
-
-The following example illustrates this same point in a constrained setting which permits a complete definition of $\allargs$ and $\allleadsto$.%, which permits defining the setting completely at the price of a reduced realism.
-\begin{example}[A decision problem about two lotteries]
-  \label{ex:lichtenstein}
-  In a famous article about preference reversals, \citet{lichtenstein_reversals_2006} discuss an example involving two lotteries.
-The lottery $L_P$ lets the subject win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $L_P = (.99, +\$4; .01, −\$0.1)$.
-The lottery $L_D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
-The letter $P$ stands for probability: one salient aspect of $L_P$ is the very high chance of winning.
-The letter $D$ stands for dollar: one salient aspect of $L_D$ is the high gain it gives (compared to $P$) in dollar amount if the subject is lucky.
-
-  This example is interesting because when asked to bid for lotteries, the theory discussed by the authors predicts, and their experiments confirm, that subjects tend to bid more for $L_D$ than for $L_P$, because the bidding question tend to make individuals focus on dollar amounts; whereas when asked to choose one lottery, the lotteries being presented in pairs, subjects tend to choose $L_P$ among the pair $\set{L_P, L_D}$, giving greater attention to probabilities.
-
-  Define $P = \set{L_P, L_D, 0}$.
-
-  Define $\ar_e$ as a text arguing that the choice between $L_P$ and $L_D$ should be determined by their expected revenue, namely, $\$3.959$ for $L_P$ and $\$4$ for $L_D$.%
-  \footnote{Here is a possible text for $\ar_e$.
-“Imagine you play $L_P$ 100 times.
-On average, you would win 99 times and lose once, which means gaining 99 × \$4 = \$396 and losing 1 × \$0.10 = \$0.10, hence a total net gain of \$395.90.
-Thus, your average net gain for the $L_P$ bet would be \$3.9590.
-[Similar text for $L_D$.] Therefore, we suggest you choose $L_D$ for a higher expected revenue.”}
-  Define $\ar_u$ as a text arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain.% 
-  \footnote{Here is a possible text for $\ar_u$.
-“$L_D$ is better than $L_P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
-For example, consider a choice between winning $10^6$ dollars with probability $0.8$ and winning $2 × 10^6$ dollars with probability $0.4$.
-These two lotteries have the same expected gain, but the first one is clearly preferrable.
-Therefore, we recommend to rather pick $L_P$ as it presents a much better chance of earning money”.}
-  Define a counter-argument $\ar_l$ to $\ar_u$, indicating that for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.%
-  \footnote{Here is a possible text for $\ar_l$.
-“The lottery $L_D$ has a higher expected revenue, and thus, a higher utility than $L_P$, because for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.”}
-  Define $\ar$ so as to include the contents of $\ar_e$, $\ar_u$ and $\ar_l$.%
-  \footnote{Here is a possible text for $\ar$.
-[Text of $\ar_e$] “Note that one could say that the utility of money should matter, but for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.”}
-  Define $\allargs = \set{\ar_e, \ar_u, \ar_l, \ar}$.
-
-  Define $I$ as a set of individuals facing a choice between $L_P$ and $L_D$ in a laboratory experiment.
-  Define $\ileadsto$ as exposing $i$ to $\alpha$ and observing the resulting choice by asking $i$ to indicate which lottery she prefers playing, or declare being indifferent.
-  %Given an argumentative path $\hist$, $\hist \ileadsto (P ≥ D)$ iff, in a situation of $i$ having been exposed, in order, to the arguments in $\hist$, letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$, or declare indifference.
-Here is a possible text presented to $i$ to ask for a choice: “Considering these arguments, would you please choose either to play $P$, or play $D$, or declare to be indifferent (in which case one will be picked randomly for you)”.
-  %Similarly, define $\hist \ileadsto (P > D)$ iff showing the arguments in $\hist$ to $i$ and letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$ and not $D$. 
-  %Define similarly $\hist \ileadsto \prop$ for $\prop \in \set{D ≥ P, D > P}$.
-
-  Assume that some individuals $i \in I$ do not see the point of argument $\ar_u$ and some do but are convinced by the counter-argument $\ar_l$.
-Accordingly, define $\ileadsto[e]$, representing the first kind of individuals, as follows.
-$\forall \hist \in \allhists: \hist \ileadsto[e] L_D ⇔ [\ar_e \in R(\hist)]$, and $\hist \ileadsto[e] L_P$ otherwise.
-Note that in particular, if $\hist$ contains $\ar$ but not $\ar_e$, $\ar \ileadsto[e] L_P$, as we assume such individuals are confused by the longer argument $\ar$ referring to abstract notions and therefore opt for $L_P$, falling back to the common psychological bias.
-  The second kind of individuals is represented by $\ileadsto[u]$ defined as $\forall \hist \in \allhists: \hist \ileadsto[u] L_D ⇔ [\ar_u \notin R(\hist) \lor \ar \in R(\hist) \lor \set{\ar_u, \ar_l} \subseteq R(\hist)]$, and $\hist \ileadsto[u] L_P$ otherwise.
-  We assume here that such individuals think about $\ar_u$ as a correct argument in favor of $L_P$ until shown the rebuttal $\ar_l$ (or $\ar$, which contains a similar rebuttal).
-  Assuming finally $\allleadsto$ as equal to $\ileadsto[e]$ for individuals of the first kind and $\ileadsto[u]$ otherwise concludes the definition of the exposure protocol $(I, \allargs, {\allleadsto})$.
-
-  It follows from this definition that $\forall i \in I: L_D \in P_i$, and that no static theory of that exposure protocol is truthful: only $\ar_e$ is a decisive argument for $L_D$ for the first kind of individuals whereas for the second kind, only $\ar$ is.
-\end{example}
-This example illustrates the need for theories that are able to react to arguments depending on what a given individual considers relevant. This is the object of the next section.
-
-\subsection{Form of theories (draft)}
-Given an exposure protocol $(I, \allargs, {\allleadsto})$, we want to phrase some claims under the form of a logical sentence $C$ such that:
-if $C$ holds, then it implies something about the dj of some $i$;
-if $C$ fails, it is possible to falsify it.
-
-We can observe set $O$ that forms a function $f(i) = \set{\alpha \ileadsto \phi, \alpha' \ileadsto ¬\phi, …}$, with $\alpha \subset \alpha \subset …$ and with finite $O$.
-Our second condition is that $¬C \implies \exists θ \suchthat θ \implies ¬C$.
-For example, if $C$ is $\alpha \ileadsto \phi \lor \beta \allleadsto[j] \phi$, $O$ is $\alpha \ileadsto ¬\phi \land \beta \allleadsto ¬\phi$, then $O$ implies $¬C$.
-As another example, $C$ being $\exists \alpha \suchthat \alpha \ileadsto \phi$ is unfalsifiable, as its negation is $\forall \alpha: \alpha \nileadsto \phi$, which requires infinite $O$.
-
-Consider $\allleadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadsto \phi$.
-Then some suitable $C$ exists.
-It is $\forall i: \ar \ileadstost \phi$.
-If false, it is falsifiable.
-Even though it is not provable by any $O$.
-
-Now consider $\allleadsto$ such that $\exists J, K \subset I \suchthat \ar \ileadstost[j] \phi, \ar' \ileadstost[k] \phi$.
-Then no suitable $C$ exists?
-
-If $C$ has the form, whenever $a$ fails, $a'$ is then decisive, it is falsifiable, but does not lead to a decisive argument.
-Want to show: $j \ileadstost \phi$. Need to show: $ar$ or $ar'$ is decisive.
-Assume we know who is a $j$. Then we can!
-Claim: $\ar \ileadsto \phi$.
-Now assume that our claim has to be anonymous.
-Also, assume the formulas involve one $i$ at a time (not needed, probably, but not much restrictive so okay for now).
-So it is of the form $(i, \alpha, \phi) \lor (i, \alpha, \phi') \land (i, \alpha', \phi)…$ implies something decisive.
-So it must be of the form: all $\alpha$ ending with $\ar$ do $\ileadsto \phi$. Or must imply this.
-Let’s make it very strong, as much as possible, thus equal to $\ileadsto \cap \ileadsto[j]$.
-That’s not strong enough!
-
-Escaping?
-Assume that we know that 50\% are J and 50\% are K.
-
-\subsection{Form of theories}
-Given an exposure protocol $(I, \allargs, {\allleadsto})$, recall that ${\allleadsto} \in \allleadstos$.
+\subsection{Claims and observable basis}
+% Such a deduction should use, as much as possible, the observational basis, that is, the propositions of the form $\alpha \ileadsto p$ that can be obtained experimentally.
+Note first that given a relation ${\allleadstog} \in \allleadstos$, $\powerset{\allleadstog}$ denotes the set of relations over $(I × \allhists) × P$ that refine $\allleadstog$ (thus, each element $f \in \powerset{\allleadstog}$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhists)$).
 
@@
 A claim is finite iff its cardinal is finite (meaning that it is compatible with a finite number of possibilities).
-Let $C^\subseteq = \set{c \subseteq (I × \allhists) × P \suchthat \exists {\allleadstog} \in C \suchthat c \subseteq {\allleadstog}}$ denote the set of non necessarily complete possibilities compatible with $C$ (thus, each element $c \in C^\subseteq$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhists)$).
+Let $C^\wsub = \cup_{{\allleadstog} \in C} \powerset{\allleadstog} = \set{c \subseteq (I × \allhists) × P \suchthat \exists {\allleadstog} \in C \suchthat c \in \powerset{\allleadstog}}$ denote the set of non necessarily complete possibilities compatible with $C$ (thus, each element $c \in C^\subseteq$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhists)$).
 Note that $C^\subseteq$ is downwards closed, meaning that $\forall c \in C^\subseteq: c' \subseteq c \implies c' \in C^\subseteq$.
@@
 The set $\Theta$ contains the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
-Let $S_θ = \set{{\allleadstog} \in \allleadstos \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
-We say that an observation $\theta$ is compatible with a claim $C$ iff $S_\theta \cap C ≠ \emptyset$, equivalently, iff $\theta \in C^\subseteq$.
+% Let $S_θ = \set{{\allleadstog} \in \allleadstos \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
+We say that an observation $\theta$ is compatible with a claim $C$ iff
+% $S_\theta \cap C ≠ \emptyset$, equivalently, iff 
+$\theta \in C^\subseteq$, equivalently, iff
+$\theta \in \cup_{{\allleadstog} \in C} \powerset{\allleadstog}$.
+Thus, given ${\allleadstog} \in \allleadstos$, the set $\Theta \cap \powerset{\allleadstog}$ is the set of observations compatible with ${\allleadstog}$.
 
@@
 
+\subsection{Rejection and falsification}
+Given an exposure protocol $(I, \allargs, {\allleadsto})$, and a claim about ${\allleadsto}$, we develop here a procedure to deduce that the claim is correct.
+
+Given an exposure protocol $\allleadsto$, we say that a claim $C$ \emph{holds} iff $C \ni {\allleadsto}$.
+
+At our disposal is the procedure of empirical rejection, that consists in directly invalidating a claim by observing something that contradicts it.
+\begin{definition}
+  Given an exposure protocol $\allleadsto$, we say that $C$ is \emph{rejectable} iff
+  % $\exists θ \in \Theta \cap \powerset{\allleadsto} \suchthat θ \notin C^\wsub$.
+  $\Theta \cap \powerset{\allleadsto} \nsubseteq C^\wsub$.
+\end{definition}
+
+The following theorem verifies that when $C$ holds, it is not rejectable.
+\begin{theorem}
+  \label{th:ex-post}
+  $\forall C \ni {\allleadsto}:
+    % \nexists θ \in \Theta \suchthat \theta \subseteq {\allleadsto} \land θ \notin C^\wsub$.
+  \Theta \cap \powerset{\allleadsto} \subseteq C^\wsub$.
+\end{theorem}
+\begin{proof}
+  This holds by definition of $C^\wsub = \cup_{{\allleadstog} \in C} \powerset{\allleadstog}$.
+  % Consider any claim $C$ with ${\allleadsto} \in C$.
+  % Consider any $\theta \in \Theta$ with $\theta \wsub {\allleadsto}$.
+  % We have $θ \subseteq {\allleadsto} \in C$, thus $θ \in C^\wsub$.
+\end{proof}
+
+The converse, however, does not hold.
+\begin{example}[Disjunct with incompatible paths, not rejectable]
+  \label{ex:disjR}
+  Given $\ar \neq \ar' \in \allargs$,
+  the claim $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not rejectable.
+  In fact, 
+  % $\nexists \theta \in \Theta \suchthat \theta \notin C^\wsub$.
+  $\Theta \wsub C^\wsub$.
+  % Consider any ${\allleadstog} \notin C$, thus satisfying, for some $i$, $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
+  Consider any $θ \in \Theta$ and let us prove that $\theta \in \cup_{{\allleadstog} \in C} \powerset{\allleadstog}$.
+  By definition of $\Theta$, $\theta^{-1}(P)$ may not contain both $((\ar), i)$ and $((\ar'), i)$, thus letting $t$ denote one of these pairs not in $\theta^{-1}(P)$ and defining $r = (t, \phi)$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$.
+We have $\theta \in \powerset{\allleadstog'}$ and ${\allleadstog'} \in C$.
+\end{example}
+\Cref{ex:disjR} shows a claim that is not rejectable, irrespective of the exposure protocol.
+In particular, the example applies when $C$ does not hold (that is, when ${\allleadsto} \notin C$). We conclude that a claim may fail to hold but still be not rejectable.
+It follows that non-rejection cannot be a sufficient condition for validating a claim.
+
 \begin{remark}
-  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in \cup_{J \subseteq_\finite I} (\allhists)^J}$.
+  \Cref{ex:threeFs} provides an example where, similarly, the claim may fail to hold but still be not rejectable; but where rejection depends on ${\allleadsto}$.
 \end{remark}
 
+\Cref{def:fals} fills the gap to obtain that $C$ holds iff it is not rejectable.
+The property demands that whatever the attitude of individuals, if the attitude is not according to the claim, then it is possible to observe that it is not.
 \begin{definition}
-  We say that $C$ is \emph{syntactically falsifiable}, or just falsifiable, iff
+  \label{def:fals}
+  A claim $C$ is \emph{falsifiable} iff
   %$\forall {\allleadstog} \in \allleadstos: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
-  $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset$.
+  $\forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
 \end{definition}
-Equivalently, iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$.
-Equivalently, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
-
-\begin{remark}
-  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\finite(\incr(\allhists))^I)}$.
-  Conversely, any set $S$ of observations such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhists)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
-  Thus, there is a bijection between the set $\mathcal{S}$ of such sets $S$ and the set of leads to relations.
-
-  This is the intuitive reason that, as we will see,
-  a claim $C$ is falsifiable iff $\forall S \in \mathcal{S}: S \subseteq C^\subseteq \implies \cup S \in C$.
-\end{remark}
-
-\begin{example}
+% A claim $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$,
+% equivalently iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
+
+It is important to note that falsifiability does not depend on $\allleadsto$: whether falsifiability holds can be determined analytically, meaning, by considering only the content of the claim, without considering the behavior of individuals.
+
+\Cref{th:holdsiff} shows that falsifiability indeed fills that gap:
+falsifiability guarantees that a claim holds if, and only if, it is not rejectable.
+\begin{theorem}
+  \label{th:holdsiff}
+  For any falsifiable claim $C$: $C \ni {\allleadsto}$ iff $\Theta \cap \powerset{\allleadsto} \wsub C^\wsub$.
+\end{theorem}
+\begin{proof}
+  Consider any falsifiable $C$.
+  Using the contrapositive of the definition of falsifiability, $\forall {\allleadstog} \in \allleadstos: \nexists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub \implies {\allleadstog} \in C$.
+  In particular,
+  $\nexists θ \in \Theta \cap \powerset{\allleadsto} \suchthat \theta \notin C^\wsub \implies {\allleadsto} \in C$.
+  The reverse implication is proven by \cref{th:ex-post}.
+\end{proof}
+
+\begin{example}[Big disjunct, not falsifiable]
   \label{ex:bigor}
@@
 Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
-We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
-\end{example}
-\begin{example}
+We have ${\allleadstog} \in \theta \in C^\wsub$.
+\end{example}
+\begin{example}[Disjunct with incompatible paths, not falsifiable]
   \label{ex:disj}
-  Given $\ar \neq \ar' \in \allargs$,
-  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
+  Given $\ar \neq \ar' \in \allargs$, the claim appearing in \cref{ex:disjR}, namely,
+  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$, is not falsifiable.
   Consider any ${\allleadstog} \notin C$, thus satisfying, for some $i$, $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
-  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $S_θ \cap C ≠ \emptyset$.
+  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $\theta \in C^\wsub$.
   By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$.
-We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
-\end{example}
-\begin{example}
+We have ${\allleadstog'} \in \theta \in C^\wsub$.
+\end{example}
+\begin{example}[Partly falsifiable is still unfalsifiable]
   \label{ex:partlyU}
@@
   Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
-  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_θ \cap C ≠ \emptyset$.
+  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $\theta \in C^\wsub$.
 \end{example}
@@
 \begin{proof}
-  By definition, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: S_θ \cap C \neq \emptyset$;
+  By definition, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: \theta \in C^\wsub$;
   equivalently, iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: θ \in C^\subseteq$;
@@
 \end{remark}
-\begin{example}
+\begin{example}[Come back]
   Considering again \cref{ex:bigor}, by \cref{th:veryunfals}, we see that $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$ is not falsifiable.
@@
   Define $C = \set{f \cup g \suchthat f \in \set{f_1, f_2, f_3} \land g \in P^{(I × \allhists) \setminus R}}$.
+  This is the claim of \cref{ex:threeFs}.
 
@@
 
+  Note that the complement is as follows.
+  \begin{equation}
+    \overline{C^\wsub \cap \Theta} = \left\{\theta \in \Theta \suchthat
+    \begin{aligned}
+       & \theta(o_2) = 0 \lor \mbox{}                                                                                \\
+       & \theta(o_2) = ¬\phi \land (\theta(o_1) \in \set{¬\phi, 0} \lor \theta(o_3) \in \set{¬\phi, 0}) \lor \mbox{} \\
+       & \theta(o_1) \in \set{¬\phi, 0} \land \theta(o_3) \neq ¬\phi \lor \mbox{}                                    \\
+       & \theta(o_1) = \emptyset \lor \mbox{}                                                                        \\
+       & \theta(o_3) = \emptyset \lor \mbox{}                                                                        \\
+       & \theta(o_3) \in \set{¬\phi, 0} \land \theta(o_1) \neq ¬\phi
+    \end{aligned}\right\}.
+  \end{equation}
+  This seems incorrect: if $\theta = \emptyset$, then it belongs, even though it satisfies $\theta(o_1) = \emptyset$.
+
+  The relations that are obs-compatible with $C^\wsub \cap \Theta$ are the ones that, for $(o_1, o_2, o_3)$, include two $\phi$ and one $¬\phi$, the one that equals all $\phi$, and the one that assigns $o_1$ and $o_3$ to $¬\phi$ and $o_2$ to $\phi$.
+
+  It follows that the relations that are obs-compatible with $C^\wsub \cap \Theta$ and that are in $C^\wsub \cap \Theta$ are the ones that, for $(o_1, o_2, o_3)$, include two $\phi$ and one $¬\phi$; and the relations that are obs-compatible with $C^\wsub \cap \Theta$ and that are not in $C^\wsub \cap \Theta$ are the one that equals all $\phi$ and the one that assign $o_1$ and $o_3$ to $\emptyset$ and $o_2$ to $\phi$.
+
   Pick any $g \in P^{(I × \allhists) \setminus R}$ and define ${\allleadstog} = \set{(\emptyset, i, \phi), ((a), i, \phi), ((b), i, \phi)} \cup g$.
@@
   Consider any $θ \subset {\allleadstog}$.
-  If $θ$ is fully compatible with ${\allleadstog^1}$, then ${\allleadstog^1} \in S_θ \cap C ≠ \emptyset$.
+  If $θ$ is fully compatible with ${\allleadstog^1}$, then ${\allleadstog^1} \in \theta \in C^\wsub$.
   Otherwise, $θ$ contains some element $(i, \hist, {\allleadstog^2}(i, \hist))$ with ${\allleadstog^2}(i, \hist) ≠ {\allleadstog^1}(i, \hist)$.
-Then, ${\allleadstog^2} \in S_θ \cap C ≠ \emptyset$, for otherwise, for at least one other element $(i', \histp)$, $θ$ contains $(i', \histp, {\allleadstog^1}(i', \histp))$ with ${\allleadstog^1}(i', \histp) ≠ {\allleadstog^2}(i', \histp)$, which violates the hypothesis.
+Then, ${\allleadstog^2} \in \theta \in C^\wsub$, for otherwise, for at least one other element $(i', \histp)$, $θ$ contains $(i', \histp, {\allleadstog^1}(i', \histp))$ with ${\allleadstog^1}(i', \histp) ≠ {\allleadstog^2}(i', \histp)$, which violates the hypothesis.
 \end{proof}
@@
 Actually, even if we can observe two among the three (using $i, a, p, i, aa, ¬p, i, b, 0$), we can’t falsifiy $four$.
-\end{proof}
-
-Given an exposure protocol $\allleadsto$, we say that a claim $C$ \emph{holds} iff $C \ni {\allleadsto}$.
-We say that $C$ is \emph{empirically falsifiable} iff $\exists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset$.
-
-The following theorem verifies that when $C$ holds, it is not empirically falsifiable (though it may be syntactically falsifiable).
-\begin{theorem}
-  \label{th:ex-post}
-  $\forall C \ni {\allleadsto}: \nexists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset$.
-\end{theorem}
-\begin{proof}
-  We have, $\forall C \suchthat C \ni {\allleadsto}, \forall θ \subseteq {\allleadsto}$: $θ \subseteq {\allleadsto} \in C$, equivalently, ${\allleadsto} \in S_θ \cap C$, thus $S_θ \cap C ≠ \emptyset$.
-\end{proof}
-Therefore, synctactic falsifiability guarantees that a claim holds if, and only if, it is not empirically falsifiable.
-\begin{theorem}
-  \label{th:holdsiff}
-  For all syntactically falsifiable $C$: ${\allleadsto} \in C$ iff $\nexists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset$.
-\end{theorem}
-\begin{proof}
-  Consider any syntactically falsifiable $C$.
-  By definition of falsifiability, $\forall {\allleadstog}: \nexists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset \implies {\allleadstog} \in C$.
-  In particular,
-  $\nexists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset \implies {\allleadsto} \in C$.
-  The reverse implication is proven by \cref{th:ex-post}.
 \end{proof}
@@
   %	Intuitively, because it might require (with $\hist = (\ar_1)$) to observe that for a given $i$, $(a_1) \nileadsto p \land (\ar_1, \ar_2) \ileadsto p$ and also $(\ar_2) \nileadsto p \land (\ar_2, \ar_1) \ileadsto p$.
-  We need to exhibit some ${\allleadstog} \notin C$ such that $\forall θ \subseteq {\allleadstog}: S_θ \cap C ≠ \emptyset$.
+  We need to exhibit some ${\allleadstog} \notin C$ such that $\forall θ \subseteq {\allleadstog}: \theta \in C^\wsub$.
   Define $\allleadstog$ as, $\forall i \in I$, $(\ar_k) \nileadstog p, (\ar_l) \nileadstog p, \forall \hist \in \allhists \setminus \set{(\ar_k), (\ar_l)}: \hist \ileadstog p$.
@@
   \subsection{Alternative definition of syntactic falsifiability}
-  A claim $C$ is attempt-falsifiable iff $\exists θ \suchthat θ \implies ¬C$, by which I mean $S_θ \cap C = \emptyset$.
+  A claim $C$ is attempt-falsifiable iff $\exists θ \suchthat θ \implies ¬C$, by which I mean $\theta \notin C^\wsub$.
   \begin{example}
@@
 Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
-We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
+We have ${\allleadstog} \in \theta \in C^\wsub$.
   \end{example}
@@
     Given any $O$, it may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land t \in {\allleadstog}$.
-We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
+We have ${\allleadstog} \in \theta \in C^\wsub$.
   \end{example}
@@
 
+  \appendix
+  \section{Supplementary material}
+  \label{sec:supplementary}
+  \begin{example}[Three functions, may be rejectable]
+    \label{ex:threeFs}
+    Consider $i \in I$, $ar \neq ar' \in \allargs$ and the three paths $\hists = \set{\emptyset, (\ar), (\ar')}$.
+    The claim “Exactly two of the three paths in $\hists$ lead $i$ to $\phi$ and the remaining one leads $i$ to $¬\phi$” is not rejectable iff ${\ileadsto}$ associates, in order, $(\emptyset, (\ar), (\ar'))$ to either
+    $(¬\phi, \phi, \phi)$,
+    $(\phi, ¬\phi, \phi)$,
+    $(\phi, \phi, ¬\phi)$,
+    $(\phi, \phi, \phi)$ or
+    $(\phi, ¬\phi, ¬\phi)$.
+
+    Indeed, if ${\ileadsto}$ satisfies this, then either it holds and by \cref{th:ex-post} it is not rejectable, or it associates this triplet to $(\phi, \phi, \phi)$ or
+    $(\phi, ¬\phi, ¬\phi)$ in which case, as $(\ar)$ and $(\ar')$ cannot be together in $\theta$, any $\theta \in \Theta$ with $\theta \sub {\allleadsto}$ satisfy $\theta \in C^\wsub$.
+
+    Conversely, if $C$ is not rejectable, then for any $\theta_1$ containing $\emptyset$ and $(\ar)$ and $\theta_2$ containing $\emptyset$ and $(\ar')$, with $\theta_1, \theta_2 \sub {\allleadsto}$, we have $\theta_1, \theta_2 \in C^\wsub$, which requires that ${\ileadsto}$ associates $(\emptyset, (\ar))$ to $(¬\phi, \phi)$, $(\phi, ¬\phi)$ or $(\phi, \phi)$ and $(\emptyset, (\ar'))$ to $(¬\phi, \phi)$, $(\phi, \phi)$ or $(\phi, ¬\phi)$.
+  \end{example}
+
+  \section{Theories of deliberated choice}
+  This section assumes that an exposure protocol $(I, \allargs, {\allleadsto})$ is defined, and defines theories of deliberated choice associated with that exposure protocol.
+We will start with very simple theories (\cref{sec:static}) in order to build an intuition about the conditions required on theories of deliberated choice, then justify the need for more complex theories (\cref{sec:lichtenstein}) and finally define more general theories of deliberated choice (\cref{sec:dynamic}).
+
+  \subsection{Theories using a static decisive argument}
+  \label{sec:static}
+  \Cref{ex:tutor} suggests a simple form for theories of deliberated choice: suffice to determine an argument $\ar \in \allargs$ and a preference $p \in P$ such that the theory claims that $\forall i \in I: \ar \ileadstost p$ and that $\forall i \in I: p \in P_i$.
+
+  \begin{definition}[Static theory]
+    \label{def:static}
+    A static theory is a pair $(p, \ar)$ for some $p \in P$ and some $\ar \in \allargs$.
+  \end{definition}
+  A static theory $(p, \ar)$ is said to be truthful iff $\forall i \in I: \ar \ileadstost p$, and to be correct iff $\forall i \in I: p \in P_i$.
+  We can then deduce that such theories are valid, meaning that their truthfulness implies their correctness.
+Let us make this (very simple) result stand out as a theorem, because a parallel will be usefully made with more complicated theories.
+  %Note that this result immediately follows from \cref{ax:decisive}.
+  \begin{theorem}[Static theories are valid]
+    Any truthful static theory is correct.
+  \end{theorem}
+  \begin{proof}
+    This follows immediately from \cref{def:decisive}.
+  \end{proof}
+  Importantly, truthfulness can indeed be checked using our observational basis, that is, if $\exists i \in I \suchthat \ar \nileadstost p$, then it is possible to exhibit this fact experimentally.
+
+  Such theories have the merit of simplicity, but there is a need to design more adaptive theories: in many interesting cases, no single argument will be considered decisive by all individuals in $I$.
+We then need theories that argue with individuals by reacting to what they consider good arguments.
+The following section illustrates this need.
+
+  \subsection{Some decision problems with no single decisive argument}
+  \label{sec:lichtenstein}
+  One ambition of the theories to be proposed here is to permit exhibiting the existence of a deliberated consensus among a large set of persons about issues that involve numerous arguments and counter-arguments.
+
+  In many decision problems, individuals will not be attracted by the same set of arguments and counter-arguments, even though they may finally settle to the same preference.
+Imagine that some individual $i_1$ considers an argument $a_1$ for $\nprop$ relevant and some individual $i_2$ considers an argument $a_2$ for $\nprop$ relevant, but $i_1$ does not consider $a_2$ relevant and $i_2$ does not consider $a_1$ relevant (for example, because they already have some counter-arguments in mind to those arguments).
+Imagine further that there is some counter-argument $a'_1$ that can be given to $i_1$ to rebut $a_1$, and a different counter-argument $a'_2$ that can be given to $i_2$ to rebut $a_2$, so that they both have $\prop$ in their deliberated judgment when considering all these arguments.
+  In such situation, static theories as defined in \cref{sec:static} are ill suited: these theories need to present the same argument to all individuals and would thus need to define a bigger argument $a$ containing both $a'_1$ and $a'_2$.
+Such an argument could be too long to be convincing to $i_1$ or $i_2$, as it needlessly spends efforts countering an argument that the individual considers irrelevant to start with.
+This  will become an important problem if there are not only two but many a priori possible arguments $a_k$ for $\nprop$, a small subset of which is considered relevant by any given individual, each with their own counter-argument $a'_k$ for $\prop$.
+  This section is devoted to describing two examples to illustrate that point.
+Bear in mind that these examples may look somehow naïve on the aspect of the hypothesis they make about what convinces individuals.
+Real-world complex decision situations will require complex theories that do not fit the purpose of simple illustrative examples.
+Their goal is to argue that non-static theories are required, but not to fully describe such theories.
+
+  %For a partial illustration about an ambitious setting, consider a decision to be taken about the relevance of some concrete action to help cope with climate change, and let $I$ be a set of citizens interested in the climate issue.
+The complete set of all arguments that will be considered relevant by at least one individual may well be very large.
+It may also be that, for each individual who considers relevant some arguments $A$ against the proposed concrete action, it is possible to give counter-arguments $A'$ that will convince the individual to opt for the proposal.
+  One of the settings discussed by \citet{thaler_nudge_2009} permits such an illustration. %to illustrate this point more concretely.
+  Let $I$ be a set of workers interested in establishing a savings plan.
+  The authors claim that workers tend to not save enough because of psychological biases.
+  It is therefore tempting to conjecture that the deliberated choice of those workers is to save more, in the sense defined here, than what their natural choice (the one revealed in absence of arguments) leads to.
+  A difficulty related to this decision problem is that the complete set of all arguments that will be considered relevant by at least one individual for such a complex issue may well be very large.
+It may also be that, for each individual who considers relevant some arguments $A$ for saving not much (i.e., spending more in the short term), it is possible to give counter-arguments $A'$ that will convince the individual to opt for saving more.
+  But no single argument could be decisive for each $i \in I$: it could be that only counter-arguments built specifically according to what a given individual considers relevant could convince her, given the complexity of the issue.
+  This illustrates that the deliberated choice of each individuals in $I$ may be to save more even though no static theory (\cref{def:static}) may achieve showing it, as it could be that no such theory is truthful.
+
+  %The above setting illustrates the ambition of this research program, but at the price of rendering impossible in the confines of this article to define fully the set of arguments and giving a complete account of a concrete theory of deliberated choice in such a complex setting, an endeavor of its own.
+
+  The following example illustrates this same point in a constrained setting which permits a complete definition of $\allargs$ and $\allleadsto$.%, which permits defining the setting completely at the price of a reduced realism.
+  \begin{example}[A decision problem about two lotteries]
+    \label{ex:lichtenstein}
+    In a famous article about preference reversals, \citet{lichtenstein_reversals_2006} discuss an example involving two lotteries.
+The lottery $L_P$ lets the subject win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $L_P = (.99, +\$4; .01, −\$0.1)$.
+The lottery $L_D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$.
+The letter $P$ stands for probability: one salient aspect of $L_P$ is the very high chance of winning.
+The letter $D$ stands for dollar: one salient aspect of $L_D$ is the high gain it gives (compared to $P$) in dollar amount if the subject is lucky.
+
+    This example is interesting because when asked to bid for lotteries, the theory discussed by the authors predicts, and their experiments confirm, that subjects tend to bid more for $L_D$ than for $L_P$, because the bidding question tend to make individuals focus on dollar amounts; whereas when asked to choose one lottery, the lotteries being presented in pairs, subjects tend to choose $L_P$ among the pair $\set{L_P, L_D}$, giving greater attention to probabilities.
+
+    Define $P = \set{L_P, L_D, 0}$.
+
+    Define $\ar_e$ as a text arguing that the choice between $L_P$ and $L_D$ should be determined by their expected revenue, namely, $\$3.959$ for $L_P$ and $\$4$ for $L_D$.%
+    \footnote{Here is a possible text for $\ar_e$.
+“Imagine you play $L_P$ 100 times.
+On average, you would win 99 times and lose once, which means gaining 99 × \$4 = \$396 and losing 1 × \$0.10 = \$0.10, hence a total net gain of \$395.90.
+Thus, your average net gain for the $L_P$ bet would be \$3.9590.
+[Similar text for $L_D$.] Therefore, we suggest you choose $L_D$ for a higher expected revenue.”}
+    Define $\ar_u$ as a text arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain.% 
+    \footnote{Here is a possible text for $\ar_u$.
+“$L_D$ is better than $L_P$ in terms of expected gain, but it is in general absurd to reason in terms of expected gain.
+For example, consider a choice between winning $10^6$ dollars with probability $0.8$ and winning $2 × 10^6$ dollars with probability $0.4$.
+These two lotteries have the same expected gain, but the first one is clearly preferrable.
+Therefore, we recommend to rather pick $L_P$ as it presents a much better chance of earning money”.}
+    Define a counter-argument $\ar_l$ to $\ar_u$, indicating that for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.%
+    \footnote{Here is a possible text for $\ar_l$.
+“The lottery $L_D$ has a higher expected revenue, and thus, a higher utility than $L_P$, because for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.”}
+    Define $\ar$ so as to include the contents of $\ar_e$, $\ar_u$ and $\ar_l$.%
+    \footnote{Here is a possible text for $\ar$.
+[Text of $\ar_e$] “Note that one could say that the utility of money should matter, but for small monetary amounts, it is perfectly reasonable to consider utility as linear, especially given that in this experiment, multiple lotteries will be played.”}
+    Define $\allargs = \set{\ar_e, \ar_u, \ar_l, \ar}$.
+
+    Define $I$ as a set of individuals facing a choice between $L_P$ and $L_D$ in a laboratory experiment.
+    Define $\ileadsto$ as exposing $i$ to $\alpha$ and observing the resulting choice by asking $i$ to indicate which lottery she prefers playing, or declare being indifferent.
+    %Given an argumentative path $\hist$, $\hist \ileadsto (P ≥ D)$ iff, in a situation of $i$ having been exposed, in order, to the arguments in $\hist$, letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$, or declare indifference.
+Here is a possible text presented to $i$ to ask for a choice: “Considering these arguments, would you please choose either to play $P$, or play $D$, or declare to be indifferent (in which case one will be picked randomly for you)”.
+    %Similarly, define $\hist \ileadsto (P > D)$ iff showing the arguments in $\hist$ to $i$ and letting $i$ choose between $P$ and $D$ or declare indifference leads $i$ to choose $P$ and not $D$. 
+    %Define similarly $\hist \ileadsto \prop$ for $\prop \in \set{D ≥ P, D > P}$.
+
+    Assume that some individuals $i \in I$ do not see the point of argument $\ar_u$ and some do but are convinced by the counter-argument $\ar_l$.
+Accordingly, define $\ileadsto[e]$, representing the first kind of individuals, as follows.
+$\forall \hist \in \allhists: \hist \ileadsto[e] L_D ⇔ [\ar_e \in R(\hist)]$, and $\hist \ileadsto[e] L_P$ otherwise.
+Note that in particular, if $\hist$ contains $\ar$ but not $\ar_e$, $\ar \ileadsto[e] L_P$, as we assume such individuals are confused by the longer argument $\ar$ referring to abstract notions and therefore opt for $L_P$, falling back to the common psychological bias.
+    The second kind of individuals is represented by $\ileadsto[u]$ defined as $\forall \hist \in \allhists: \hist \ileadsto[u] L_D ⇔ [\ar_u \notin R(\hist) \lor \ar \in R(\hist) \lor \set{\ar_u, \ar_l} \subseteq R(\hist)]$, and $\hist \ileadsto[u] L_P$ otherwise.
+    We assume here that such individuals think about $\ar_u$ as a correct argument in favor of $L_P$ until shown the rebuttal $\ar_l$ (or $\ar$, which contains a similar rebuttal).
+    Assuming finally $\allleadsto$ as equal to $\ileadsto[e]$ for individuals of the first kind and $\ileadsto[u]$ otherwise concludes the definition of the exposure protocol $(I, \allargs, {\allleadsto})$.
+
+    It follows from this definition that $\forall i \in I: L_D \in P_i$, and that no static theory of that exposure protocol is truthful: only $\ar_e$ is a decisive argument for $L_D$ for the first kind of individuals whereas for the second kind, only $\ar$ is.
+  \end{example}
+  This example illustrates the need for theories that are able to react to arguments depending on what a given individual considers relevant. This is the object of the next section.
+
+  \subsection{Form of theories (draft)}
+  Given an exposure protocol $(I, \allargs, {\allleadsto})$, we want to phrase some claims under the form of a logical sentence $C$ such that:
+  if $C$ holds, then it implies something about the dj of some $i$;
+  if $C$ fails, it is possible to falsify it.
+
+  We can observe set $O$ that forms a function $f(i) = \set{\alpha \ileadsto \phi, \alpha' \ileadsto ¬\phi, …}$, with $\alpha \subset \alpha \subset …$ and with finite $O$.
+  Our second condition is that $¬C \implies \exists θ \suchthat θ \implies ¬C$.
+  For example, if $C$ is $\alpha \ileadsto \phi \lor \beta \allleadsto[j] \phi$, $O$ is $\alpha \ileadsto ¬\phi \land \beta \allleadsto ¬\phi$, then $O$ implies $¬C$.
+  As another example, $C$ being $\exists \alpha \suchthat \alpha \ileadsto \phi$ is unfalsifiable, as its negation is $\forall \alpha: \alpha \nileadsto \phi$, which requires infinite $O$.
+
+  Consider $\allleadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadsto \phi$.
+  Then some suitable $C$ exists.
+  It is $\forall i: \ar \ileadstost \phi$.
+  If false, it is falsifiable.
+  Even though it is not provable by any $O$.
+
+  Now consider $\allleadsto$ such that $\exists J, K \subset I \suchthat \ar \ileadstost[j] \phi, \ar' \ileadstost[k] \phi$.
+  Then no suitable $C$ exists?
+
+  If $C$ has the form, whenever $a$ fails, $a'$ is then decisive, it is falsifiable, but does not lead to a decisive argument.
+  Want to show: $j \ileadstost \phi$. Need to show: $ar$ or $ar'$ is decisive.
+  Assume we know who is a $j$. Then we can!
+  Claim: $\ar \ileadsto \phi$.
+  Now assume that our claim has to be anonymous.
+  Also, assume the formulas involve one $i$ at a time (not needed, probably, but not much restrictive so okay for now).
+  So it is of the form $(i, \alpha, \phi) \lor (i, \alpha, \phi') \land (i, \alpha', \phi)…$ implies something decisive.
+  So it must be of the form: all $\alpha$ ending with $\ar$ do $\ileadsto \phi$. Or must imply this.
+  Let’s make it very strong, as much as possible, thus equal to $\ileadsto \cap \ileadsto[j]$.
+That’s not strong enough!
+
+Escaping?
+Assume that we know that 50\% are J and 50\% are K.
+
+\section{Technical notes about falsification}
+\begin{remark}
+  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in \cup_{J \subseteq_\finite I} (\allhists)^J}$.
+\end{remark}
+
+\begin{remark}
+  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\finite(\incr(\allhists))^I)}$.
+  Conversely, any set $S$ of observations such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhists)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
+  Thus, there is a bijection between the set $\mathcal{S}$ of such sets $S$ and the set of leads to relations.
+
+  This is the intuitive reason that, as we will see,
+  a claim $C$ is falsifiable iff $\forall S \in \mathcal{S}: S \subseteq C^\subseteq \implies \cup S \in C$.
+\end{remark}
+
 \hbadness=10000

### 2023-11-10 simple.tex
Str unfals

@@
   A claim $C$ is \emph{falsifiable} iff
-  %$\forall {\allleadstog} \in \allleadstos: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
   $\forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
+  %Actually we need to exclude trivial claims with an exists in supplement to forall; so that trivial claims are not falsifiable. Then the property that we seek is trivial-or-falsifiable.
 \end{definition}
-% A claim $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$,
-% equivalently iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
 
@@
 \end{proof}
+
+\begin{definition}
+  A claim is \emph{unfalsifiable} iff $\exists {\allleadstog} \notin C \suchthat \Theta \cap \powerset{\allleadstog} \wsub C^\wsub$.
+\end{definition} 
+\begin{definition}
+  A non-trivial claim is \emph{strongly unfalsifiable} iff $\Theta \wsub C^\wsub$.
+\end{definition}
 
@@
 \section{Technical notes about falsification}
+A claim $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$,
+equivalently iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
+
 \begin{remark}

### 2023-11-10 simple.tex
Restored unfortunate repl S_θ \cap C ≠ \emptyset

@@
 Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
-We have ${\allleadstog} \in \theta \in C^\wsub$.
+We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
 \end{example}
@@
   Consider any $θ \subset {\allleadstog}$.
-  If $θ$ is fully compatible with ${\allleadstog^1}$, then ${\allleadstog^1} \in \theta \in C^\wsub$.
+  If $θ$ is fully compatible with ${\allleadstog^1}$, then ${\allleadstog^1} \in S_θ \cap C ≠ \emptyset$.
   Otherwise, $θ$ contains some element $(i, \hist, {\allleadstog^2}(i, \hist))$ with ${\allleadstog^2}(i, \hist) ≠ {\allleadstog^1}(i, \hist)$.
-Then, ${\allleadstog^2} \in \theta \in C^\wsub$, for otherwise, for at least one other element $(i', \histp)$, $θ$ contains $(i', \histp, {\allleadstog^1}(i', \histp))$ with ${\allleadstog^1}(i', \histp) ≠ {\allleadstog^2}(i', \histp)$, which violates the hypothesis.
+Then, ${\allleadstog^2} \in S_θ \cap C ≠ \emptyset$, for otherwise, for at least one other element $(i', \histp)$, $θ$ contains $(i', \histp, {\allleadstog^1}(i', \histp))$ with ${\allleadstog^1}(i', \histp) ≠ {\allleadstog^2}(i', \histp)$, which violates the hypothesis.
 \end{proof}
@@
 Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
-We have ${\allleadstog} \in \theta \in C^\wsub$.
+We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
   \end{example}
@@
     Given any $O$, it may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land t \in {\allleadstog}$.
-We have ${\allleadstog} \in \theta \in C^\wsub$.
+We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
   \end{example}

### 2023-11-10 simple.tex
Some cleanup

@@
 
-\begin{example}[Big disjunct, not falsifiable]
+\begin{example}[Big disjunct, strongly unfalsifiable]
   \label{ex:bigor}
-  $[\forall i: (\ar) \ileadstog \phi] \lor [\forall i: (\ar, \ar) \ileadstog \phi] \lor …$ is not falsifiable.
-  Here, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$.
-
-  Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise.
+  Consider $\ar \in \allargs$.
+  The claim $[\forall i: (\ar) \ileadstog \phi] \lor [\forall i: (\ar, \ar) \ileadstog \phi] \lor …$,
+  thus, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$,
+  is strongly unfalsifiable.
+
+  Given any $θ \in \Theta$, define $l = \max_{\hist \suchthat \exists i \in I, p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise.
 Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
-We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
+We have
+  % ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
+  $\theta \in \powerset{\allleadstog}$ and ${\allleadstog} \in C$, thus, $\theta \in C^\wsub$.
 \end{example}
@@
   By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$.
-We have ${\allleadstog'} \in \theta \in C^\wsub$.
+We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
 \end{example}
@@
 
+\begin{example}[Bigger disjunct, strongly unfalsifiable]
+  \label{ex:biggeror}
+  Pick any $i \in I$ and $\ar \in \allargs$.
+  The claim $[(\ar) \ileadstog \phi] \lor [(\ar, \ar) \ileadstog \phi] \lor …$,
+  thus, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat (a)^n \ileadstog \phi}$,
+  is strongly unfalsifiable.
+
+  Let $C' = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall j: (a)^n \ileadstog[j] \phi}$ denote the claim of \cref{ex:bigor}.
+  We have $C' \subseteq C$.
+  It follows that ${C'}^\wsub \subseteq C^\wsub$.
+  We know from \cref{ex:bigor} that $\Theta \wsub {C'}^\wsub$, thus, $\Theta \wsub C^\wsub$.
+\end{example}
+
 \hbadness=10000

### 2023-11-10 simple.tex
Included trivial case

@@
 
-\Cref{def:fals} fills the gap to obtain that $C$ holds iff it is not rejectable.
+\Cref{def:falsw} fills the gap to obtain that $C$ holds iff it is not rejectable.
 The property demands that whatever the attitude of individuals, if the attitude is not according to the claim, then it is possible to observe that it is not.
 \begin{definition}
-  \label{def:fals}
-  A claim $C$ is \emph{falsifiable} iff
+  \label{def:falsw}
+  A claim $C$ is \emph{falsifiable or trivial} iff
   $\forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
-  %Actually we need to exclude trivial claims with an exists in supplement to forall; so that trivial claims are not falsifiable. Then the property that we seek is trivial-or-falsifiable.
 \end{definition}
@@
   \label{th:holdsiff}
-  For any falsifiable claim $C$: $C \ni {\allleadsto}$ iff $\Theta \cap \powerset{\allleadsto} \wsub C^\wsub$.
+  For any falsifiable or trivial claim $C$: $C \ni {\allleadsto}$ iff $\Theta \cap \powerset{\allleadsto} \wsub C^\wsub$.
 \end{theorem}
@@
   Consider any falsifiable $C$.
-  Using the contrapositive of the definition of falsifiability, $\forall {\allleadstog} \in \allleadstos: \nexists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub \implies {\allleadstog} \in C$.
+  Using the contrapositive of \cref{def:fals}, $\forall {\allleadstog} \in \allleadstos: \nexists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub \implies {\allleadstog} \in C$.
   In particular,
@@
 \begin{definition}
-  A claim is \emph{unfalsifiable} iff $\exists {\allleadstog} \notin C \suchthat \Theta \cap \powerset{\allleadstog} \wsub C^\wsub$.
-\end{definition}
-\begin{definition}
-  A non-trivial claim is \emph{strongly unfalsifiable} iff $\Theta \wsub C^\wsub$.
+  A claim is \emph{strongly unfalsifiable} iff 
+  $\Theta \wsub C^\wsub$.
 \end{definition}
@@
 \section{Technical notes about falsification}
+\begin{definition}
+  \label{def:fals}
+  A claim $C$ is \emph{falsifiable} iff
+  $C \neq {\allleadstos} \land
+  \forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
+\end{definition}
+\begin{definition}
+  A claim is \emph{unfalsifiable} iff 
+  $C = {\allleadstos} \lor
+  \exists {\allleadstog} \notin C \suchthat \Theta \cap \powerset{\allleadstog} \wsub C^\wsub$.
+\end{definition}
+
 A claim $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$,
 equivalently iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
+(To be corrected for the trivial claims.)
 

### 2023-11-10 simple.tex
Repl some Stheta

@@
 We say that an observation $\theta$ is compatible with a claim $C$ iff
-% $S_\theta \cap C ≠ \emptyset$, equivalently, iff 
+% $S_θ \cap C ≠ \emptyset$, equivalently, iff 
 $\theta \in C^\subseteq$, equivalently, iff
@@
   By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$.
-We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
+We have
+  $\theta \in \powerset{\allleadstog'}$ and ${\allleadstog'} \in C$, thus, $\theta \in C^\wsub$.
+  % ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
 \end{example}
@@
   A claim $C$ is falsifiable iff its complement $\Cbar = \allleadstos \setminus C$ satisfies:
-  $\forall {\allleadstog} \in \Cbar, \exists \theta \subseteq {\allleadstog} \suchthat S_\theta \subseteq \Cbar$, or equivalently:
+  $\forall {\allleadstog} \in \Cbar, \exists \theta \subseteq {\allleadstog} \suchthat S_θ \subseteq \Cbar$, or equivalently:
   $\forall {\allleadstog} \in \Cbar, \exists O \in (\allhists)^I \suchthat S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
@@
   It follows that $\theta \subseteq \restr{\allleadstog}{O_O}$.
-  Thus, $S_{\restr{\allleadstog}{O_O}} \subseteq S_\theta$.
-  As $S_\theta \subseteq \Cbar$, we obtain $S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
+  Thus, $S_{\restr{\allleadstog}{O_O}} \subseteq S_θ$.
+  As $S_θ \subseteq \Cbar$, we obtain $S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
 \end{proof}

### 2023-11-10 simple.tex
Rm outdated cmted

@@
 The set $\Theta$ contains the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
-% Let $S_θ = \set{{\allleadstog} \in \allleadstos \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
 We say that an observation $\theta$ is compatible with a claim $C$ iff
-% $S_θ \cap C ≠ \emptyset$, equivalently, iff 
 $\theta \in C^\subseteq$, equivalently, iff
@@
 Given a simple a priori observation $O: J \mapsto \allhists$, we can define the a priori observation $O_O = \set{(i, \hist) \in J × \allhists \suchthat \forall i \in J: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.
-Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.
 
@@
   Given an exposure protocol $\allleadsto$, we say that $C$ is \emph{rejectable} iff
-  % $\exists θ \in \Theta \cap \powerset{\allleadsto} \suchthat θ \notin C^\wsub$.
   $\Theta \cap \powerset{\allleadsto} \nsubseteq C^\wsub$.
@@
   $\forall C \ni {\allleadsto}:
-    % \nexists θ \in \Theta \suchthat \theta \subseteq {\allleadsto} \land θ \notin C^\wsub$.
     \Theta \cap \powerset{\allleadsto} \subseteq C^\wsub$.
@@
   This holds by definition of $C^\wsub = \cup_{{\allleadstog} \in C} \powerset{\allleadstog}$.
-  % Consider any claim $C$ with ${\allleadsto} \in C$.
-  % Consider any $\theta \in \Theta$ with $\theta \wsub {\allleadsto}$.
-  % We have $θ \subseteq {\allleadsto} \in C$, thus $θ \in C^\wsub$.
 \end{proof}
@@
   In fact,
-  % $\nexists \theta \in \Theta \suchthat \theta \notin C^\wsub$.
   $\Theta \wsub C^\wsub$.
-  % Consider any ${\allleadstog} \notin C$, thus satisfying, for some $i$, $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
   Consider any $θ \in \Theta$ and let us prove that $\theta \in \cup_{{\allleadstog} \in C} \powerset{\allleadstog}$.
@@
 We have
-  % ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
   $\theta \in \powerset{\allleadstog}$ and ${\allleadstog} \in C$, thus, $\theta \in C^\wsub$.
@@
   $\theta \in \powerset{\allleadstog'}$ and ${\allleadstog'} \in C$, thus, $\theta \in C^\wsub$.
-  % ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
 \end{example}
@@
 \end{remark}
+Let $S_θ = \set{{\allleadstog} \in \allleadstos \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
+Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.
 \begin{remark}

### 2023-11-23 simple.tex
Progress towards indicativeness

@@
 Let $\incr(\allhists) = \set{\emptyset} \cup \cup_{\emptyset \neq N \subseteq \N} \set{A(N) \suchthat A \in (\allhists)^N \land [\card{A_i} = i] \land [i < j \implies A_i \subsetneq A_j]} \subseteq \powerset{\allhists}$ denote the possibly empty embedded sequences of paths.
+\commentOC{TODO define $\incr(\allhists) = \set{H \wsub \allhists \suchthat \card(H) ≤ \card(H') \implies H \wsub H'}$.}
 An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhists)$.
@@
 \begin{remark}
-  \Cref{ex:threeFs} provides an example where, similarly, the claim may fail to hold but still be not rejectable; but where rejection depends on ${\allleadsto}$.
+  \Cref{ex:bigor,ex:threeFs} present situations where, similarly, the claim may fail to hold but still be not rejectable.
+  In \cref{ex:bigor}, non rejection is due to finiteness of observations.
+  In \cref{ex:threeFs}, rejection depends on ${\allleadsto}$.
 \end{remark}
@@
 \Cref{def:falsw} fills the gap to obtain that $C$ holds iff it is not rejectable.
-The property demands that whatever the attitude of individuals, if the attitude is not according to the claim, then it is possible to observe that it is not.
+The property demands that whatever the attitude of individuals, if the attitude is not compatible with the claim, then it is possible to observe that it is not.
 \begin{definition}
@@
   A claim $C$ is \emph{falsifiable or trivial} iff
-  $\forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
+  $\forall {\allleadstog} \notin C: \Theta \cap \powerset{\allleadstog} \nsubseteq C^\wsub$.
 \end{definition}
@@
 \end{definition}
-
-\begin{example}[Big disjunct, strongly unfalsifiable]
-  \label{ex:bigor}
-  Consider $\ar \in \allargs$.
-  The claim $[\forall i: (\ar) \ileadstog \phi] \lor [\forall i: (\ar, \ar) \ileadstog \phi] \lor …$,
-  thus, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$,
-  is strongly unfalsifiable.
-
-  Given any $θ \in \Theta$, define $l = \max_{\hist \suchthat \exists i \in I, p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise.
-Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
-We have
-  $\theta \in \powerset{\allleadstog}$ and ${\allleadstog} \in C$, thus, $\theta \in C^\wsub$.
-\end{example}
-\begin{example}[Disjunct with incompatible paths, not falsifiable]
-  \label{ex:disj}
-  Given $\ar \neq \ar' \in \allargs$, the claim appearing in \cref{ex:disjR}, namely,
-  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$, is not falsifiable.
-  Consider any ${\allleadstog} \notin C$, thus satisfying, for some $i$, $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
-  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $\theta \in C^\wsub$.
-  By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$.
-We have
-  $\theta \in \powerset{\allleadstog'}$ and ${\allleadstog'} \in C$, thus, $\theta \in C^\wsub$.
-\end{example}
-\begin{example}[Partly falsifiable is still unfalsifiable]
-  \label{ex:partlyU}
-  Given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
-  $\hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
-  Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
-  \Cref{ex:disj} concludes.
-\end{example}
+\Cref{ex:disjR,ex:bigor} illustrate, as well as \cref{ex:existsParticular} when $I$ is infinite.
+\begin{definition}
+  A claim is \emph{strictly unfalsifiable} iff
+  it is unfalsifiable and not strongly unfalsifiable.
+\end{definition}
+
+Making a strongly unfalsifiable claim more precise ($C = (C_1 \cap C_2) \sub C_1$ in \cref{th:strongUToStrictU}) can make it strictly unfalsifiable.
+Also, a strictly unfalsifiable claim can be made falsifiable by picking a single relation from the claim.
+
+But, it does not hold that more precise claims are always more falsifiable:
+making a falsifiable claim more precise ($C = (C_1 \cap C_2) \sub C_2$ in \cref{ex:partlyU}) can make it strictly unfalsifiable.
+(In fact, \cref{ex:partlyU} shows that the relation is not one-way: going from a strongly unfalsifiable ($C_1$), or from a falsifiable ($C_2$), claim, to a more precise one ($C = C_1 \cap C_2$) yields a strictly unfalsifiable claim.)
+
 \begin{example}
@@
 \end{example}
-\begin{example}
-  \label{ex:existsParticular}
-  Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
-  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $\theta \in C^\wsub$.
-\end{example}
-
-\begin{remark}
-  The claim “For each glass, it will not break on a monday or not break on a tuesday, whatever happens to it.” is not falsifiable.
-But one can make it stronger and falsify it, by giving a general theory of how glasses break, proving that it holds, and that it is not compatible with the claim.
-I should think about this.
-\end{remark}
+
+The following procedure permits to determine whether a claim is falsifiable.
+Given a set of observations $S \wsub \Theta$, define the relations that are observation-compatible with $S$ as $E(S) = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: {\allleadstog} \cap \theta \in S}$.
+Given a claim $C$, define the set of its observation-compatible relations as $E(C) = E(C^\wsub \cap \Theta)$ (reusing the letter $E$ by abuse of notation).
+Note that this set extends $C$, in the sense that $C \wsub E(C)$.
+The claim $C$ is falsifiable iff it is closed under extension to observation-compatible relations, that is, iff $E(C) \subseteq C$.
+\begin{theorem}
+  \label{thm:caractFals}
+  A claim $C$ is falsifiable or trivial iff $E(C) \wsub C$, or equivalently, iff 
+  $\forall {\allleadstog} \in \allleadstos$:
+  \[\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq \implies {\allleadstog} \in C.\]
+\end{theorem}
+\begin{proof}
+  Note that
+  $E(C) = E(C^\wsub \cap \Theta) = \set{{\allleadstog} \in \allleadstos \suchthat \forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\wsub}$.
+
+  The condition $E(C) \wsub C$ is equivalent to
+  $\forall {\allleadstog} \in \allleadstos: ({\allleadstog} \in E(C) \implies {\allleadstog} \in C)$.
+  Note that ${\allleadstog} \in E(C) \Leftrightarrow \set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq$.
+
+  By definition, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \Theta \cap \powerset{\allleadstog} \wsub C^\wsub$;
+  equivalently, iff $\exists {\allleadstog} \notin C \suchthat \set{θ \subseteq {\allleadstog}} \subseteq C^\subseteq$.
+  And, $\forall {\allleadstog} \in \allleadstos$: $\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} = \set{θ \subseteq {\allleadstog}}$.
+\end{proof}
+
 Let $S_θ = \set{{\allleadstog} \in \allleadstos \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
 Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.
-\begin{remark}
-  To be falsifiable, I need each time I exclude some relation $R$ to also exclude a subset $Cbar$ such that some $O \subseteq R$ satisfies $S_O$ is entirely in $Cbar$.
-\end{remark}
-\begin{theorem}
-  A claim $C$ is falsifiable iff its complement $\Cbar = \allleadstos \setminus C$ satisfies:
-  $\forall {\allleadstog} \in \Cbar, \exists \theta \subseteq {\allleadstog} \suchthat S_θ \subseteq \Cbar$, or equivalently:
-  $\forall {\allleadstog} \in \Cbar, \exists O \in (\allhists)^I \suchthat S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
-\end{theorem}
-\begin{proof}
-  The first phrasing follows from the definition of falsifiability.
-  Also, the second phrasing implies the first one: pick $\theta = \restr{\allleadstog}{O_O}$.
-
-  Let us prove that the first phrasing implies the second one.
-  Given $\theta$, define $O = \set{(i, \argmax_{\hist \in (\theta(i) \cup \emptyset)} \card{\hist})}$ as associating to each $i$ the longest corresponding $\hist$ from $\theta$, or the empty sequence if $\theta(i)$ is empty.
-  It follows that $\theta \subseteq \restr{\allleadstog}{O_O}$.
-  Thus, $S_{\restr{\allleadstog}{O_O}} \subseteq S_θ$.
-  As $S_θ \subseteq \Cbar$, we obtain $S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
-\end{proof}
-
-\begin{theorem}
-  \label{thm:caractFals}
-  A claim $C$ is falsifiable iff $\forall {\allleadstog} \in \allleadstos$:
-  \[\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq \implies {\allleadstog} \in C.\]
-\end{theorem}
-\begin{proof}
-  By definition, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: \theta \in C^\wsub$;
-  equivalently, iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: θ \in C^\subseteq$;
-  equivalently, iff $\exists {\allleadstog} \notin C \suchthat \set{θ \subseteq {\allleadstog}} \subseteq C^\subseteq$.
-
-  To conclude, note that $\forall {\allleadstog} \in \allleadstos$: $\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} = \set{θ \subseteq {\allleadstog}}$.
-\end{proof}
-\begin{corollary}
-  A claim $C$ is falsifiable iff $\forall f \in C^{\allpriobss} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
-  \[\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C.\]
-\end{corollary}
-\begin{proof}
-  Consider a falsifiable claim $C$, consider such an $f$, and let us prove that $\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C$.
-  Define ${\allleadstog} \subseteq (I × \allhists) × P$ as $\cup_{O \in \allpriobss} \restr{f(O)}{O}$. Its domain equals $I × \allhists$, and it is right-unique thanks to the condition on $f$.
-  Thus, \cref{thm:caractFals} applies and ${\allleadstog} \in C$.
-
-  Conversely, assume that the statement about all $f$ holds and let us prove that $C$ is falsifiable.
-  Consider any ${\allleadstog} \in \allleadstos$ such that $\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq$.
-  Given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$ and therefore there is some $e_O \in C$ such that $\restr{\allleadstog}{O} = \restr{e_O}{O}$.
-  Define $f$ as $f(O) = e_O$.
-  As this $f$ satisfies the condition in the hypothesis, we obtain that $\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C$, hence, $\cup_{O \in \allpriobss} \restr{\allleadstog}{O} \in C$.
-  Therefore, ${\allleadstog} \in C$.
-  Apply \cref{thm:caractFals} to conclude that $C$ is falsifiable.
-\end{proof}
-
-\begin{corollary}
-  \label{th:corffals}
-  A claim $C$ is falsifiable iff $\forall f \in \left(C^\subseteq\right)^{\allpriobss} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
-  \[\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C.\]
-\end{corollary}
-\begin{corollary}
-  \label{th:corffalsdom}
-  A claim $C$ is falsifiable iff $\forall f \in \cup_{O \in \allpriobss} \set{\set{O} × (P^O \cap C^\subseteq)} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
-  \[\cup_{O \in \allpriobss} f(O) \in C.\]
-\end{corollary}
-\begin{corollary}
-  \label{th:veryunfals}
-  Any non-trivial claim $C$ satisfying $\Theta \subseteq C^\subseteq$ is not falsifiable.
-\end{corollary}
-\begin{proof}
-  Pick any ${\allleadstog} \notin C$.
-  Per hypothesis, $\forall O \in \allpriobss$: $\restr{\allleadstog}{O} \in C^\subseteq$.
-  Define $f$ as $\forall O \in \allpriobss: f(O) = \restr{\allleadstog}{O}$.
-  Observe that $\cup_{O \in \allpriobss} f(O) = {\allleadstog}$ and hence $\cup_{O \in \allpriobss} f(O) \notin C$.
-  Apply \cref{th:corffalsdom}.
-\end{proof}
-
-We thus reach a procedure to determine whether a claim is falsifiable.
-Given $C$, compute $C^\subseteq$. Find the set $R$ of relations $\allleadstog$ satisfying $\forall O: \restr{\allleadstog}{O} \in C^\subseteq$. The claim $C$ is falsifiable iff $R \subseteq C$.
-\begin{corollary}
-  A claim $C$ is falsifiable iff $\set{{\allleadstog} \in \allleadstos \suchthat \forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\subseteq} \subseteq C$.
-\end{corollary}
-A relation $\allleadstog$ is observably in $C$ iff $\forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\subseteq$, equivalently, iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)$.
-All relations in $C$ are observably in $C$. The question of falsifiability asks whether the converse holds.
-In other words, $C$ is falsifiable iff it includes the relations observably in $C$.
 Define that a relation ${\allleadstog} \in {\allleadstos}$ is \emph{obs-compatible} with a set $S$ iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S$.
-Then, the relations observably in $C$ are exactly those obs-compatible with $C^\subseteq \cap \Theta$.
-\begin{corollary}
-  A claim $C$ is falsifiable iff $\set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)} = C$.
-\end{corollary}
-\begin{remark}
-  The question of falsifiability is whether the set of relations $\allleadstog$ “compatible” with $C^\subseteq \cap \Theta$ equals $C$.
-  Compatibility needs to consider the observables, not a subset of it.
-  Define $\Theta_1 \subset \Theta$ as the observations that observe only one pair $(i, \hist)$.
-  Define $R_1 = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta_1: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)}$.
-  Note that $R \subseteq R_1$.
-  We know that $C$ is falsifiable iff $R \subseteq C$.
-Thus, $C$ is not falsifiable implies $C \subsetneq R \subseteq R_1$ thus $C \subsetneq R_1$.
-But we do not have that $C \subsetneq R_1$ implies $C$ not falsifiable: could have $C \subsetneq R_1$ but still $R = C$.
-\end{remark}
-\begin{example}[Come back]
-  Considering again \cref{ex:bigor}, by \cref{th:veryunfals}, we see that $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$ is not falsifiable.
-
-  Similarly, considering again \cref{ex:disj}, given $\ar \neq \ar' \in \allargs$,
-  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable, by \cref{th:veryunfals}.
-
-  Turning to \cref{ex:partlyU},
-  given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
-  $C = \set{{\allleadstog} \suchthat \hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ is not falsifiable but \cref{th:veryunfals} is not applicable.
-  Observe that
-  $C^\subseteq = \set{R \in I × \allhists × P \suchthat [(j, \hist) \in R^{-1}(P) \implies (j, \hist, \phi) \in R] \land \forall i: [(i, (\ar)) \in R^{-1}(P) \land (i, (\ar')) \in R^{-1}(P)] \implies [(i, (\ar), \phi) \in R \land (i, (\ar'), \phi) \in R]}$ and
-  $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat (j, \hist) \in \theta^{-1}(P) \implies (j, \hist, \phi) \in \theta}$.
-  % Pick any $\allleadstog$ satisfying $\hist \ileadstog[j] \phi$ and $\exists i \suchthat (\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
-  % The definition of non-falsifiability applies: pick any $\theta \subseteq {\allleadstog}$, we have $\theta \in C^\subseteq$ as $(j, \hist, \phi)$ is compatible with $\theta$ and the other condition excludes nothing in $\Theta$.
-  % We can apply Thm 4 similarly: given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
-  % We should be able to apply a corollary similarly.
-  The relations obs-compatible with $C^\subseteq \cap \Theta$ are those satisfying $\hist \ileadstog[j] \phi$.
-  We conclude that $C$ is not falsifiable as $C$ is smaller than that set.
-
-  In \cref{ex:allParticular} we considered a given $\ar$ and $\phi$ and defined the falsifiable claim $C = \set{{\allleadstog} \suchthat \forall i: \ar \ileadstostg \phi}$.
-  Observe that $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat \forall \hist \suchthat \ar \in \histend: \theta(i, \hist) = \emptyset \lor \theta(i, \hist) = \phi}$.
-  The relations obs-compatible with $C^\subseteq \cap \Theta$ are exactly those in $C$.
-
-  \Cref{ex:existsParticular} assumed an infinite $I$, in which case the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
-  Observe that $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat \exists i \suchthat \forall \hist \suchthat \ar \in \histend: \theta(i, \hist) = \emptyset \lor \theta(i, \hist) = \phi}$.
-  Any relation ${\allleadstog}$ is obs-compatible with that set as $C^\subseteq \cap \Theta = \Theta$: given any $\theta \in \Theta$, there is an $i$ such that $\forall \hist: \theta(i, \hist) = \emptyset$ as $\theta$ must have a finite support.
-\end{example}
-
-\begin{example}
-  \label{ex:cardPart}
-  Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhists$ with $\hist$ and $\histp$ non prefix related.
-  The claim $\psi = (\hist \ileadstog p \lor \hist \ileadstog p') \land (\histp \ileadstog p \lor \histp \ileadstog p') \land (\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p)$ is falsifiable.
-
-  Given $q, q' \in P$, let ${\allleadstog^{q, q'}}$ be defined as $\hist \ileadstog^{q, q'} q$, $\histp \ileadstog^{q, q'} q'$ and $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j]^{q, q'} p$.
-  Note that $C_\psi = \set{{\allleadstog^{p, p}}, {\allleadstog^{p, p'}}, {\allleadstog^{p', p}}, {\allleadstog^{p', p'}}}$.
-
-  Then, $C_\psi^\wsub \cap \Theta =
-    \set{\theta \in \Theta \suchthat \theta(\hist, i) \in \set{\emptyset, p, p'} \land \theta(\histp, i) \in \set{\emptyset, p, p'} \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
-  % and we see that $C_\psi^\wsub \cap \Theta =
-  % \set{\theta \in \Theta \suchthat [\theta(\hist, i) = \theta(\histp, i) = \emptyset \lor \theta(\hist, i) \in \set{p, p'} \lor \theta(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
-
-  Any obs-compatible relation has to satisfy $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p$.
-  It also must satisfy ${\allleadstog}(\hist, i) \in \set{p, p'}$, for otherwise, with $\theta = \set{(\hist, i, {\allleadstog}(\hist, i))}$, we get $({\allleadstog} \cap \theta) \notin C_\psi^\wsub \cap \Theta$.
-  Similarly, it must satisfy ${\allleadstog}(\histp, i) \in \set{p, p'}$.
-  % are $\set{{\allleadstog} \in \allleadstos \suchthat [{\allleadstog}(\hist, i) \in \set{p, p'} \lor {\allleadstog}(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p}$, which, given $p \neq p^{\prime\prime} \neq p'$, contains ${\allleadstog^{p, p^{\prime\prime}}}$, contrary to $C_\psi$.
-\end{example}
-
-\begin{example}
-  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p, p' \in P$.
-  The claim $C = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$ is falsifiable.
-
-  We have $C^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p) \land (\theta((\ar_2), i) = \emptyset \lor \theta((\ar_2), i) = p')}$.
-  The obs-compatible relations are $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$.
-\end{example}
-\begin{example}
-  \label{ex:consti2}
-  Assume that $\card{I} ≥ 2$.
-  Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
-  We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
-  Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$.
-Assume that for some $\hist, i$, $\hist \ileadstog p$.
-Then, pick any $j \neq i$, and observe that by obs-compatibility, for any $\hist'$, $\hist' \ileadstog[j] p$.
-  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and any $(\hist^{\prime\prime}, j)$).
-Conclude that $\allleadstog$ is constant to $p$.
-  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
-\end{example}
-\begin{example}
-  \label{ex:consti1}
-  Assume that $\card{I} = 1$.
-  Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
-  We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
-  Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$.
-Assume that for some $\hist, i$, $\hist \ileadstog p$.
-Observe that by obs-compatibility, $\emptyset \ileadstog p$.
-  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and $(\emptyset, i)$).
-Conclude that $\allleadstog$ is constant to $p$.
-  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
-\end{example}
-\begin{example}
-  \label{ex:constwout0}
-  Consider any $p, p' \in P$ and the claim $C = \set{{\allleadstog} \suchthat (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p) \lor (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p')}$.
-That claim is falsifiable iff $\card I ≥ 2$ or $\card \allargs = 1$.
-The proof if so is similar to \cref{ex:consti2}; otherwise, pick any $\ar \in \allargs$ and note that any relation satisfying $(a.*) \ileadstog p$ and $\forall b \neq a: (b.*) \ileadstog p'$ is obs-compatible with $C^\wsub \cap \Theta$ but is not in $C$.
-\end{example}
-\begin{example}
-  \label{ex:unfor}
-  Consider any $i$, $\hist, \histp \in \allhists$, $p, p' \in P$ where $\hist$ and $\histp$ are not prefix related.
-  The claim $C = \set{{\allleadstog} \suchthat \hist \ileadstog p \lor \histp \ileadstog p'}$ is unfalsifiable.
-
-  We have $C^\wsub \cap \Theta = \set{\theta \suchthat (\theta(\hist, i) = \emptyset \lor \theta(\hist, i) = p) \lor (\theta(\histp, i) = \emptyset \lor \theta(\histp, i) = p')}$.
-  Observe that any $\theta \in \Theta$ satisfy $\theta(\hist, i) = \emptyset \lor \theta(\histp, i) = \emptyset$, thus, $C^\wsub \cap \Theta = \Theta$.
-  It follows that the obs-compatible relations are $\allleadstos$, which is bigger than $C$.
-\end{example}
-\begin{example}
-  Consider any $i$, $\ar \neq \ar' \in \allargs$, $p, p' \in P$.
-  The claim $C = \set{{\allleadstog} \suchthat (\ar) \ileadstog p \lor (\ar') \ileadstog p'}$ is unfalsifiable (per \cref{ex:unfor}).
-
-  Now consider the smaller claim $C' = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$ (thus $C' \ssub C$).
-  It yields a smaller set ${C'}^\wsub \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p)}$.
-  The obs-compatible relations are the smaller set $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$.
-  Thus, $C'$ is falsifiable.
-
-  Note that any claim $C^{\prime\prime}$ bigger than $C$ is unfalsifiable as well, unless trivial:
-  from $C \wsub C^{\prime\prime}$, we deduce $\Theta = C^\wsub \cap \Theta \wsub {C^{\prime\prime}}^\wsub \cap \Theta$, thus ${C^{\prime\prime}}^\wsub \cap \Theta = \Theta$ and the obs-compatible relations are $\allleadstos$, which equals $C^{\prime\prime}$ only if $C^{\prime\prime}$ is trivial.
-
-  Now consider the alternative smaller claim of \cref{ex:consti2}, $C^{(2)} = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$ (thus $C^{(2)} \ssub C$).
-  It yields a smaller set ${C^{(2)}}^\wsub \cap \Theta$.
-\end{example}
-\begin{example}
-  \label{ex:for}
-  Consider any $i$ and $p, p' \in P$.
-  The claim $C = \set{{\allleadstog} \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \hist \ileadstog p) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \hist \ileadstog p')}$, namely, all paths of even lengths lead $i$ to $p$ OR all paths of odd lengths or empty lead $i$ to $p'$, is falsifiable.
-
-  Note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \theta(\hist) \in \set{\emptyset, p}) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \theta(\hist) \in \set{\emptyset, p'})}$.
-  Consider any obs-compatible ${\allleadstog}$.
-  Assume that $\exists \hist \suchthat \card{\hist} \in 2\N \land \hist \nileadstog p$.
-  Pick $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\hist, i, {\ileadstog}(\hist))}$.
-We have $({\allleadstog} \cap \theta) \in C^\wsub \cap \Theta$, and ${\allleadstog} \cap \theta = \theta$, and from $\theta \in C^\wsub \cap \Theta$ we obtain ${\ileadstog}(\emptyset) = p'$.
-  Similarly, using $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\histp, j, {\ileadstog[j]}(\histp))}$, we obtain that $\allleadsto$ conforms to the relation in $C$.
-\end{example}
 
@@
   \label{rq:closedcomb}
-  Being closed-under-combinations (where a combination forms a new relation by union of parts of relations in $C$) is sufficient to be falsifiable, but not necessary, as seen with \cref{ex:consti2}.
-\end{remark}
-
-\begin{remark}
-  Intuition (to be explored, TODO) is that when $C^\wsub \cap \Theta$ has the covering property, then the obs-compatible relations are easily deduced from the set (something like, just consider compatibility point per point, one singleton observation at a time).
-Covering is what is used above, something like $\exists i, \hist, \histp$ such that $\forall \hist^{\prime\prime}: [\forall j \neq i: \set{(\hist, i, .), (\histp, j, .)} \in C^\wsub \cap \Theta] \land [\exists j \neq i \suchthat \set{(\hist', i, .), (\hist^{\prime\prime}, j, .)} \in C^\wsub \cap \Theta]$.
+  Define the closure under combinations of $C$ as the relations that can be formed by picking parts of relations in $C$, formally, $(\cup_{S \in C^\wsub \cap \Theta} S) \cap \allleadstos$.
+  We have $E(C) \wsub (\cup_{S \in C^\wsub \cap \Theta} S) \cap \allleadstos$.
+
+  Being closed under combinations is sufficient to be falsifiable, but not necessary, as seen with \cref{ex:consti2} (in other words, for some claims, $(\cup_{S \in C^\wsub \cap \Theta} S) \cap \allleadstos \wsub E(C)$ does not hold).
 \end{remark}
@@
 
-\begin{conjecture}
-  $C$ is falsifiable iff exists two compatible paths in two different such forests, for a given $i$, that are not in a single forest, for that $i$, of $C$.
-  This seems incorrect; need to be able to build a union relation!
-  Prove that it is false with claim "i goes to phi OR i goes to not phi except for empty set going to phi"?
-  Actually I need to be able to merge two relations that agree on everything but some part of the tree, in such a way that all paths crossing the boundary must be in $C$, but not the merge.
-  TODO caract with singleton $I$.
-  % Given a claim $C$, define $S = C^\wsub \cap \Theta$.
-  % We have: $\set{\cup_i(\theta_i) \in \allleadstos \suchthat (\theta_i) \in s_S} = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S}$.
-\end{conjecture}
+Given an attitude $\allleadsto$, deliberated choices are represented by an element $\pi({\allleadsto}) \subseteq I × P$ (thus with $\pi({\allleadsto})(i) = P_i$) which is right unique (meaning that $\forall i \in I: \card{\pi({\allleadsto})(i)} ≤ 1$).
+Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\allleadsto}) \in (P \cup \set{\emptyset})^I$.
+
+A claim $C$ is \emph{informative} iff $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.
+A claim $C$ is \emph{informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) ≠ P \cup \set{\emptyset}$.
+A claim $C$ is \emph{strongly informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) \ssub P$.
+% A claim $C$ is \emph{indicative} iff $\exists H \in \finite(\incr(\allhists)), i \in I \suchthat \pi(\set{{\allleadstog} \suchthat H \wsub \ileadstoinvg(P)} \cap C)(i) \ssub P$.
+Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
+A claim $C$ is \emph{indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \cap C^\wsub \suchthat \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
+Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
 \begin{remark}
-  Say that $(r1, o1)$ is determined in $C$ (to $p$) iff all relations in $C$ including $r1$ agree on ${\allleadstog}(o)$ (satisfy ${\allleadstog}(o) = p$).
-  Let $C(r, o)$ equal $\set{{\allleadstog}(o) \suchthat {\allleadstog} \in C \land r \in {\allleadstog}}$.
-
-  A claim satisfying, $\forall {\allleadstog} \in C$:
-  $\forall r1 = (o1, p1) \in {\allleadstog}$, $\exists o2$ with $o1$ and $o2$ obs-compatible and $(r1, o2)$ determined in $C$ such that $\forall o3: (o2, o3)$ is obs-compatible and $(r2 = (o2, C(r1, o2)), o3)$ is determined in $C$
-  %Perhaps can omit $(r1, o2)$ determined. In fact, has to satisfy that these determine only relations in $C$.
-  % \[\forall (\hist, i, p) \in {\allleadstog}, \exists (\histp, j, p) \in {\allleadstog} \suchthat \forall (\histpp, k) \in \allhists × I: \set{(\histp, j), (\histpp, k)} \in O\]
-  is falsifiable.
-
-  NOPE.
-  Need to say that $C$ is a union of disjoint subsets such that each subset $C'$ include all relations that are specified on a subset of observations (and left free on everything else) which satisfy something like the above condition: all points related to a point that is related to all others.
+  Informativeness permits mere counting: the claim that exactly two persons deliberately believe $\phi$ is informative.
+  Informativeness may be a desirable property (rather than informativeness beyond counting) as one may want to know whether a given proposition is believed by a majority of individuals, or whether a given proposition is believed by nobody.
+  Note also that strong informativeness beyond counting implies informativeness beyond counting and indicativeness.
+  Note also that informativeness beyond counting implies informativeness.
+  \Cref{th:infoBeyonCKO} (and extensions, \cref{th:infoBeyonCKOext,th:strinfoBeyonCKO}) shows that informativeness beyond counting (and variants) is too demanding if one wants to investigate situations where individuals have differing deliberate preferences.
 \end{remark}
-\begin{theorem}
-  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
-  % $C = \set{\restr{\allleadstog}{R} \cup \restr{\allleadstog}{R'} \suchthat R' \in (I × \allhists) \setminus R}$.
-  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
-
-  If $\exists R \subseteq I × \allhists$ such that $C$ is determined on $R$ and satisfying $\exists o \in R \suchthat \forall o' \in R: (\set{o, o'} \in \allpriobss)$, then $C$ is falsifiable.
-\end{theorem}
-\begin{proof}
-  Note that as $C$ is closed-under-combinations, this follows from \cref{rq:closedcomb}, but let’s design a more direct proof in hope of weakening the condition.
-
-  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.
-
-  % Pick any $o_1 \in R$.
-  % Define $r_1 = (o_1, {\allleadstog}(o_1))$, thus with $r_1 \in {\allleadstog}$.
-  Pick some $o \in R$ as in the hypothesis.
-  Consider any $o' \in R$.
-  As $\set{o, o'} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
-  % $\exists {\allleadstog'} \suchthat \restr{\allleadstog}{\set{o, o'}} = \restr{\allleadstog'}{\set{o, o'}}$.
-  $\restr{\allleadstog}{\set{o, o'}} \in C^\wsub$.
-  Thus, ${\allleadstog}(o') = f(o')$.
-
-  We obtain that $\forall o' \in R: {\allleadstog}(o') = f(o')$, therefore, ${\allleadstog} \in C$.
-\end{proof}
-\begin{conjecture}[draft]
-  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
-  % $C = \set{\restr{\allleadstog}{R} \cup \restr{\allleadstog}{R'} \suchthat R' \in (I × \allhists) \setminus R}$.
-  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
-  Say that $R$ is coverable iff $\exists o_1, …, O_1, … \suchthat \forall o \in O_1: \set{o_1, o} \in \allpriobss \land \forall o \in O_2: \set{o_2, o} \in \allpriobss \land … \land \set{o_i, o_{i + 1}} \in \allpriobss \land \cup O_i = R \land o_i \in R$.
-
-  If $\exists R \subseteq I × \allhists$ coverable and such that $C$ is determined on $R$, then $C$ is falsifiable.
-\end{conjecture}
-\begin{proof}
-  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.
-
-  Pick some $o_1 \in R$ as in the hypothesis.
-  Consider any $o \in O_1 \cup \set{o_2}$.
-  As $\set{o_1, o} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
-  $\restr{\allleadstog}{\set{o_1, o}} \in C^\wsub$.
-  As also $o_1, o \in R$, ${\allleadstog}(o) = f(o)$.
-  In particular, ${\allleadstog}(o_2) = f(o_2)$.
-  Iterate with $o_2$ and $o \in O_2$, and so on.
-  We obtain that $\forall o \in R: {\allleadstog}(o) = f(o)$, therefore, ${\allleadstog} \in C$.
-\end{proof}
-\begin{example}
-  Pick $i \in I$ and
-  define $o_1 = ((a), i)$,
-  $o_2 = (\emptyset, i)$ and
-  $o_3 = ((b), i)$.
-  Define $R = \set{o_1, o_2, o_3}$.
-  Define $f_1, f_2, f_3 \in P^R$ as follows.
-  $f_1(o_1) = \phi$,
-  $f_1(o_2) = ¬\phi$,
-  $f_1(o_3) = \phi$.
-  $f_2(o_1) = \phi$,
-  $f_2(o_2) = \phi$,
-  $f_2(o_3) = ¬\phi$.
-  $f_3(o_1) = ¬\phi$,
-  $f_3(o_2) = \phi$,
-  $f_3(o_3) = \phi$.
-  Define $C = \set{f \cup g \suchthat f \in \set{f_1, f_2, f_3} \land g \in P^{(I × \allhists) \setminus R}}$.
-  This is the claim of \cref{ex:threeFs}.
-
-  Note that $R$ is covered by $O_1 = \set{o_1}, O_2 = \set{o_2}, O_3 = \set{o_3}$.
-  Note that $C$ is determined on $R$.
-  Yet, $C$ is not falsifiable.
-
-  Note that
-  \begin{equation}
-    C^\wsub \cap \Theta = \left\{\theta \in \Theta \suchthat
-    \begin{aligned}
-       & (\theta(o_1) \in \set{\emptyset, \phi} \land \theta(o_2) \in \set{\emptyset, ¬\phi} \land \theta(o_3) \in \set{\emptyset, \phi}) \lor \mbox{} \\
-       & (\theta(o_1) \in \set{\emptyset, \phi} \land \theta(o_2) \in \set{\emptyset, \phi} \land \theta(o_3) \in \set{\emptyset, ¬\phi}) \lor \mbox{} \\
-       & (\theta(o_1) \in \set{\emptyset, ¬\phi} \land \theta(o_2) \in \set{\emptyset, \phi} \land \theta(o_3) \in \set{\emptyset, \phi})
-    \end{aligned}\right\}.
-  \end{equation}
-  Also, $\theta(o_1) \neq \emptyset \implies \theta(o_3) = \emptyset$ (and equivalently, $\theta(o_3) \neq \emptyset \implies \theta(o_1) = \emptyset$),
-  whence:
-  \begin{equation}
-    C^\wsub \cap \Theta = \left\{\theta \in \Theta \suchthat
-    \begin{aligned}
-       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, ¬\phi}) \lor \mbox{} \\
-       & (\theta(o_1) = \phi \land \theta(o_2) \in \set{\emptyset, ¬\phi}) \lor \mbox{}                    \\
-       & (\theta(o_3) = \phi \land \theta(o_2) \in \set{\emptyset, ¬\phi}) \lor \mbox{}                    \\
-       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}  \\
-       & (\theta(o_1) = \phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                     \\
-       & (\theta(o_3) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                    \\
-       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}  \\
-       & (\theta(o_1) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                    \\
-       & (\theta(o_3) = \phi \land \theta(o_2) \in \set{\emptyset, \phi})
-    \end{aligned}\right\}.
-  \end{equation}
-  Factorizing:
-  \begin{equation}
-    C^\wsub \cap \Theta = \left\{\theta \in \Theta \suchthat
-    \begin{aligned}
-       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, \phi, ¬\phi})) \lor \mbox{} \\
-       & (\theta(o_1) = \phi \land \theta(o_2) \in \set{\emptyset, \phi, ¬\phi}) \lor \mbox{}                     \\
-       & (\theta(o_3) = \phi \land \theta(o_2) \in \set{\emptyset, \phi, ¬\phi}) \lor \mbox{}                     \\
-       & (\theta(o_3) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                           \\
-       & (\theta(o_1) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi})
-    \end{aligned}\right\}.
-  \end{equation}
-
-  Note that the complement is as follows.
-  \begin{equation}
-    \overline{C^\wsub \cap \Theta} = \left\{\theta \in \Theta \suchthat
-    \begin{aligned}
-       & \theta(o_2) = 0 \lor \mbox{}                                                                                \\
-       & \theta(o_2) = ¬\phi \land (\theta(o_1) \in \set{¬\phi, 0} \lor \theta(o_3) \in \set{¬\phi, 0}) \lor \mbox{} \\
-       & \theta(o_1) \in \set{¬\phi, 0} \land \theta(o_3) \neq ¬\phi \lor \mbox{}                                    \\
-       & \theta(o_1) = \emptyset \lor \mbox{}                                                                        \\
-       & \theta(o_3) = \emptyset \lor \mbox{}                                                                        \\
-       & \theta(o_3) \in \set{¬\phi, 0} \land \theta(o_1) \neq ¬\phi
-    \end{aligned}\right\}.
-  \end{equation}
-  This seems incorrect: if $\theta = \emptyset$, then it belongs, even though it satisfies $\theta(o_1) = \emptyset$.
-
-  The relations that are obs-compatible with $C^\wsub \cap \Theta$ are the ones that, for $(o_1, o_2, o_3)$, include two $\phi$ and one $¬\phi$, the one that equals all $\phi$, and the one that assigns $o_1$ and $o_3$ to $¬\phi$ and $o_2$ to $\phi$.
-
-  It follows that the relations that are obs-compatible with $C^\wsub \cap \Theta$ and that are in $C^\wsub \cap \Theta$ are the ones that, for $(o_1, o_2, o_3)$, include two $\phi$ and one $¬\phi$; and the relations that are obs-compatible with $C^\wsub \cap \Theta$ and that are not in $C^\wsub \cap \Theta$ are the one that equals all $\phi$ and the one that assign $o_1$ and $o_3$ to $\emptyset$ and $o_2$ to $\phi$.
-
-  Pick any $g \in P^{(I × \allhists) \setminus R}$ and define ${\allleadstog} = \set{(\emptyset, i, \phi), ((a), i, \phi), ((b), i, \phi)} \cup g$.
-  This relation is obs-compatible with $C^\wsub \cap \Theta$, but ${\allleadstog} \notin C$.
-\end{example}
-\begin{conjecture}
-  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
-  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
-  Say that $R$ is coverable iff $\exists k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}} \suchthat
-    \cup_{l \in \intvl{1, k}} O_l = R \land
-    \forall l \in \intvl{1, k}: o_l \in O_l \land
-    \forall o \in O_l: \set{o_l, o} \in \allpriobss \land
-    \forall l \in \intvl{1, k - 1}: \set{o_l, o_{l + 1}} \in \allpriobss$.
-
-  If $\exists R \subseteq I × \allhists$ coverable and such that $C$ is determined on $R$, then $C$ is falsifiable.
-\end{conjecture}
-\begin{proof}
-  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.
-
-  Pick some $k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}}$ as in the hypothesis.
-  Consider any $l \in \intvl{1, k - 1}$
-  and any $o \in O_l \cup \set{o_{l + 1}}$.
-  As $\set{o_l, o} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
-  $\restr{\allleadstog}{\set{o_l, o}} \in C^\wsub$.
-  As also $o_l, o \in R$ (per $\cup_{l' \in \intvl{1, k}} O_{l'} = R$), ${\allleadstog}(o) = f(o)$.
-  In particular, ${\allleadstog}(o_{l + 1}) = f(o_{l + 1})$.
-  Iterate with $o_2$ and $o \in O_2$, and so on.
-  We obtain that $\forall o \in R: {\allleadstog}(o) = f(o)$, therefore, ${\allleadstog} \in C$.
-\end{proof}
-\begin{conjecture}
-  Given $R \subseteq I × \allhists$, define ${\sim_R} \subseteq \allleadstos × \allleadstos$ as $f \sim_R f'$ iff $\restr{f}{R} = \restr{f'}{R}$. This is an equivalence relation.
-  Given $f \in \allleadstos$, define the equivalence class of $f$ for ${\sim_R}$ as ${\sim_R}(f) = \set{f' \in \allleadstos \suchthat f \sim_R f'} = \set{f' \in P^{(I × \allhists)} \suchthat \restr{f}{R} = \restr{f'}{R}}$.
-
-  Given $R \subseteq I × \allhists$, define the a priori observable subsets of $R$ as $Z_R = \allpriobss \cap \powerset{R}$.
-
-  Consider $R \subseteq I × \allhists$, $F \subseteq P^R$ and $C = \set{f \cup g \suchthat f \in F \land g \in P^{(I × \allhists) \setminus R}}$.
-  The claim $C$ is unfalsifiable iff $\exists {\allleadstog} \in \allleadstos \suchthat \bigcap_{O \in Z_R} {\sim_O}(f) \cap C = \emptyset$.
-
-  % Given $k \in \N$ and a family $(O_l)_{l \in \intvl{1, k}}$, consider $\exists f \in C \suchthat 
-  Say that $R$ is coverable iff $\exists k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}} \suchthat
-    \cup_{l \in \intvl{1, k}} O_l = R \land
-    \forall l \in \intvl{1, k}: o_l \in O_l \land
-    \forall o \in O_l: \set{o_l, o} \in \allpriobss \land
-    \forall l \in \intvl{1, k - 1}: \set{o_l, o_{l + 1}} \in \allpriobss$.
-
-  If $\exists R \subseteq I × \allhists$ coverable and such that $C$ is determined on $R$, then $C$ is falsifiable.
-\end{conjecture}
-TODO extend this so as to cover eg $C$ containing $f_1$ and $f_2$ constant functions as in example; but not covering when the domain is not suitable!
-Use proof similar to \cref{ex:for}, getting started with observing that any obs-compatible $\allleadstog$ failing every element but one of $C$ at least at one point must then satisfy the last element of $C$ at some point (?).
-\begin{conjecture}
-  If $\forall {\allleadstog} \in C: \exists R \suchthat {\allleadstog} = f \cup g$ with $f \in P^R, g \in P^{(I × \allhists) \setminus R}$ and $R$ converable, then $C$ is falsifiable.
-  Should be specified better, but also, not sure that this holds: consider C being a leads i to phi OR b leads i to phi (given i).
-  Perhaps something like $\exists F \suchthat C = \cup_{f \in F} \set{f \cup g}$ where $f^{-1}(P)$ being coverable.
-\end{conjecture}
-\begin{proof}
-  Problem is: how to get started?
-\end{proof}
-
-\begin{example}
-  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_2) \ileadstog^2 p'$.
-  Consider the claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$. When is it falsifiable considering these two relations?
-\end{example}
-
-TODO investigate claims that are non falsifiable but with $C^\wsub \cap \Theta \neq \Theta$.
-Then exhibit a claim such that a smaller one is not the same status and a bigger one is not the same status.
-
-Any claim containing two relations that differ only on incompatible observations is not falsifiable.
-\begin{theorem}
-  Any $C$ such that $\exists {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$) and the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, does not contain two elements that are simultaneously observable (meaning that no $θ$ contains more than one of these elements), is not falsifiable.
-\end{theorem}
-\begin{proof}
-  Consider any $θ \subset {\allleadstog}$.
-  If $θ$ is fully compatible with ${\allleadstog^1}$, then ${\allleadstog^1} \in S_θ \cap C ≠ \emptyset$.
-  Otherwise, $θ$ contains some element $(i, \hist, {\allleadstog^2}(i, \hist))$ with ${\allleadstog^2}(i, \hist) ≠ {\allleadstog^1}(i, \hist)$.
-Then, ${\allleadstog^2} \in S_θ \cap C ≠ \emptyset$, for otherwise, for at least one other element $(i', \histp)$, $θ$ contains $(i', \histp, {\allleadstog^1}(i', \histp))$ with ${\allleadstog^1}(i', \histp) ≠ {\allleadstog^2}(i', \histp)$, which violates the hypothesis.
-\end{proof}
-\Cref{ex:cardPart} illustrates the need for the condition about the combination in the theorem.
-
-\begin{conjecture}
-  If a claim $C$ is not falsifiable, then $\exists {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$) and the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, does not contain two elements that are simultaneously observable (meaning that no $θ$ contains more than one of these elements).
-\end{conjecture}
-\begin{conjecture}
-  If $\forall {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$), the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, contains at least two elements that are simultaneously observable (meaning that some $θ$ contains more than one of these elements), then $C$ is falsifiable.
-\end{conjecture}
-\begin{proof}
-  We need a stronger hypothesis.
-  Consider $one$ and $two$ differ on $(i, (a))$, $(i, (b))$ and $(i, (a, a))$.
-And some $three$ not in $C$ has $(i, (a)), (i, (a, a))$ as in $one$ and $(i, (b))$ as in $two$.
-Then $C$ is not falsifiable.
-\end{proof}
-\begin{conjecture}
-  If $\forall {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$), the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, we can find some $(i, \hist) \in {\allleadstog^1}, (j, \hist') \in {\allleadstog^2}$ obs-compatible, then $C$ is falsifiable.
-\end{conjecture}
-\begin{proof}
-  This fails.
-Could have $one$, $two$, $three$, each sending everything to $p$, $¬p$ and $0$, respectively, and any combination of two of these in $C$, but no comb of three in $C$.
-Then $four$ a combination of the three ($i, a, p, i, b, ¬p, i, c, 0$), but $C$ not falsifiable.
-Actually, even if we can observe two among the three (using $i, a, p, i, aa, ¬p, i, b, 0$), we can’t falsifiy $four$.
-\end{proof}
-
-Given an exposure protocol $\allleadsto$, deliberated choices are represented by an element $\pi({\allleadsto}) \subseteq I × P$ which is right unique (meaning that $\forall i \in I: \card{\pi({\allleadsto})(i)} ≤ 1$).
-Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\allleadsto}) \in (P \cup \set{\emptyset})^I$.
-We say that $C$ is \emph{informative} iff $\exists {\allleadstog} \in (P \cup \set{\emptyset})^I \suchthat C \implies ¬{\allleadstog}$, meaning that $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.
 
@@
 
+\begin{theorem}
+  For all exposure protocols, there exists a claim that holds and is strongly informative beyond counting and falsifiable iff $\exists i \suchthat P_i \neq \emptyset$.
+\end{theorem}
+\begin{proof}
+  Define $C = \set{\allleadsto}$.
+\end{proof}
+\begin{theorem}
+  For all exposure protocols, there exists a claim that holds and is informative beyond counting and falsifiable.
+\end{theorem}
+\begin{proof}
+  Define $C = \set{\allleadsto}$.
+\end{proof}
+\begin{theorem}
+  For all exposure protocols, there exists a claim that is anonymous, strongly informative beyond counting and falsifiable.
+\end{theorem}
+\begin{proof}
+  Define the claim as $\forall i \in I, \hist \in \allhists: \hist \ileadstog \phi$.
+\end{proof}
+
+What about anonymous and holds?
+\begin{theorem}
+  For all exposure protocols, there exists a claim that holds and is anonymous.
+\end{theorem}
+\begin{proof}
+  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
+\end{proof}
+
+\begin{theorem}
+  Assume that $I = \set{i_1, i_2}$ and that $P_{i_1} = \phi$ and $P_{i_2} = ¬\phi$.
+
+  Then, there exists a claim that holds and is anonymous and indicative.
+\end{theorem}
+\begin{proof}
+  From $P_{i_1} = \phi$ we know that some $a_1$ is a decisive argument in favor of $\phi$ for $i_1$.
+  From $P_{i_2} = ¬\phi$ we know that for some $\hist \in \allhists \suchthat a_1 \in \histend$, $\hist \nileadsto[i_2] \phi$ whereas $\hist \ileadsto[i_1] \phi$.
+  Define $O = \set{(\hist, i_1)}$.
+  Define 
+  ${\allleadstog^1} = \set{(i_1, \ileadsto[i_1]), (i_2, \ileadsto[i_2])}$ and
+  ${\allleadstog^2} = \set{(i_1, \ileadsto[i_2]), (i_2, \ileadsto[i_1])}$.
+  Define the claim as $C = \set{{\allleadstog^1}, {\allleadstog^2}}$.
+\end{proof}
+
+\begin{theorem}
+  Assume that $I = \set{i_1, i_2, i_3}$ and that $P_{i_1} = \phi$ and $P_{i_2} = P_{i_3} = ¬\phi$.
+  Assume that all paths lead either to $\phi$ or to $¬\phi$.
+  Define $H_2$ as the set of paths that lead $i_2$ to $¬\phi$ and similarly $H_3$ for $i_3$.
+  In other words,
+  $\forall \hist \in \allhists \setminus H_2: \hist \ileadsto[i_2] \phi$,
+  $\forall \hist \in \allhists \setminus H_3: \hist \ileadsto[i_3] \phi$,
+  $\forall \hist \in H_2: \hist \ileadsto[i_2] ¬\phi$,
+  $\forall \hist \in H_3: \hist \ileadsto[i_3] ¬\phi$.
+  Also, define $H_{12}$ as the set of paths on which $i_1$ and $i_2$ differ.
+  Similarly for $H_{13}$.
+  We want small such sets, so let us assume that $i_1$ goes often to $¬\phi$ and only on some $H_1$ including all paths that ends with $a_1$ does it go to $\phi$.
+  We need to have suffix compatible observations from $H_{12}$ and $H_{13}$.
+  How to make none such?
+  Impossible: consider $(a_1, a_2)$ and $(a_1, a_2, a_1, a_3)$.
+
+  Thus with $H_2$ including all paths that ends with some $a_2$ decisive for $i_2$.
+  Thus, the path $(a_2, a_3)$ is in both $H_2$ and $H_3$.
+
+  Then, there exists a claim that holds and is anonymous and indicative?
+
+  But maybe $i_2$ always goes to $\phi$ except for the paths $H_2$, and $i_3$ always goes to $\phi$ except for the paths $H^3$ incompatible (not suffix or prefix) with $H_2$.
+  Then we can’t observe both that $i$ is not $i_2$ and not $i_3$: whatever $O$, if we fall upon $i_1$, this will leave $i_1$ and some other $i$ as possibilities.
+\end{theorem}
+\begin{theorem}
+  Assume that $I = \set{i_1, i_2, i_3}$ and that $P_{i_1} = \phi$ and $P_{i_2} = P_{i_3} = ¬\phi$.
+
+  Then, there exists a claim that holds and is anonymous and indicative.
+\end{theorem}
+\begin{proof}
+  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
+  In other words, for $k, l \in \intvl{1, 3}$, define
+  ${\allleadstog^{k, l}} = \set{(i_k, \ileadsto[i_1]), (i_l, \ileadsto[i_2]), (i_{\intvl{1, 3} \setminus \set{k, l}}, \ileadsto[i_3])}$.
+  Define the claim as $C = \set{{\allleadstog^{1, 2}}, {\allleadstog^{1, 3}}, {\allleadstog^{2, 1}}, {\allleadstog^{2, 3}}, {\allleadstog^{3, 1}}, {\allleadstog^{3, 2}}}$.
+
+  Define $a_1$ as an argument decisive in favor of $\phi$ for $i_1$ and $a_2, a_3$ as arguments decisive in favor of $¬\phi$ for $i_2, i_3$.
+
+  Define $\hist_{12} = (a_1, a_2)$ and $\hist_{13} = (\hist_{12}, a_1, a_3)$.
+  We know that 
+  $\hist_{12} \ileadsto[i_1] \phi$, 
+  $\hist_{12} \ileadsto[i_2] ¬\phi$, 
+  $\hist_{13} \ileadsto[i_1] \phi$, 
+  $\hist_{13} \ileadsto[i_3] ¬\phi$.
+  Define $\theta = \set{(\hist_{12}, i_1, \phi), (\hist_{13}, i_1, \phi)}$.
+  Finally, the attitudes in $C$ compatible with $\theta$ are only $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C = \set{{\allleadstog^{1, 2}}, {\allleadstog^{1, 3}}}$, and $\pi(\set{{\allleadstog^{1, 2}}, {\allleadstog^{1, 3}}})(i_1) = \phi$.
+\end{proof}
+
+\begin{theorem}
+  Assume that $P_{i_1} = \phi$ and $\forall i \in I \setminus \set{i_1}: P_i = ¬\phi$.
+
+  Then, there exists a claim that holds and is anonymous and indicative.
+\end{theorem}
+\begin{proof}
+  From $P_{i_1} = \phi$ we know that some $a_1$ is a decisive argument in favor of $\phi$ for $i_1$.
+  For $i_1 \neq i \in I$, from $P_i = ¬\phi$ we know that for some $\hist^i \in \allhists \suchthat a_1 \in \histend[i]$, $\hist^i \nileadsto \phi$ whereas $\hist^i \ileadsto[i_1] \phi$.
+  If $I$ is finite, define $O = \set{(\hist^i, i_1) \suchthat i_1 \neq i \in I}$.
+  TODO this fails because $O$ might not be an a priori observation.
+  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto} \suchthat i \in I}$.
+\end{proof}
+
+\begin{theorem}
+  \label{th:HAinformativeness}
+  Given any $Q \wsub P \cup \set{\emptyset}$,
+  the following two conditions on $\allleadsto$ are equivalent:
+  there exists a claim that holds and is anonymous and satisfies 
+  $\exists j \in I \suchthat \pi(C)(j) \ssub Q$;
+  and 
+  $\set{P_i, i \in I} \ssub Q$.
+\end{theorem}
+\begin{proof}
+  Consider any claim $C$ that holds and is anonymous, pick any $j \in I$, and let us show that $\set{P_i, i \in I} \wsub \pi(C)(j)$.
+  Pick any $p \in \set{P_i, i \in I}$. 
+  Pick any $i \in I$ such that $\pi({\allleadsto})(i) = p$.
+  Define $\sigma$ as the permutation exchanging $i$ and $j$.
+  As $C$ holds, it contains $\allleadsto$, and by anonymity, it contains ${\allleadsto} \circ \sigma$.
+Observing that $\pi({\allleadsto} \circ \sigma)(j) = \pi({\allleadsto})(i) = p$, we obtain $p \in \pi(C)(j)$.
+
+  It follows that for any claim $C$ that holds and is anonymous, if $\exists j \in I \suchthat \pi(C)(j) \ssub Q$ then $\set{P_i, i \in I} \wsub \pi(C)(j) \ssub Q$ thus $\set{P_i, i \in I} \ssub Q$.
+
+  Turning to the other direction, if $\set{P_i, i \in I} \ssub Q$, then pick any $p \in Q \setminus \set{P_i, i \in I}$; the claim $\forall i \in I: P_i \neq p$ satisfies the desired properties.
+\end{proof}
+
+\begin{theorem}
+  \label{th:infoBeyonCKO}
+  There exists a claim that holds and is anonymous and informative beyond counting iff $\set{P_i, i \in I} \neq P \cup \set{\emptyset}$.
+\end{theorem}
+\begin{proof}
+  From \cref{th:HAinformativeness} with $Q = P \cup \set{\emptyset}$, we have that 
+  there exists a claim that holds and is anonymous and satisfies 
+  $\exists j \in I \suchthat \pi(C)(j) \ssub P \cup \set{\emptyset}$ iff
+  $\set{P_i, i \in I} \ssub P \cup \set{\emptyset}$.
+\end{proof}
+
+\begin{theorem}
+  \label{th:strinfoBeyonCKO}
+  There exists a claim that holds and is anonymous and strongly informative beyond counting iff $\set{P_i, i \in I} \ssub P$.
+\end{theorem}
+\begin{proof}
+  From \cref{th:HAinformativeness} with $Q = P$, we have that 
+  there exists a claim that holds and is anonymous and satisfies 
+  $\exists j \in I \suchthat \pi(C)(j) \ssub P$ iff
+  $\set{P_i, i \in I} \ssub P$.
+\end{proof}
+
+\begin{theorem}
+  \label{th:infoBeyonCKOext}
+  Given $Q = \set{\phi, ¬\phi}$,
+  the following two conditions on $\allleadsto$ are equivalent:
+  there exists a claim that holds and is anonymous and satisfies 
+  $\exists j \in I \suchthat \pi(C)(j) \ssub Q$;
+  and 
+  $\set{P_i, i \in I} \ssub Q$.
+\end{theorem}
+\begin{proof}
+  From \cref{th:HAinformativeness} with $Q = \set{\phi, ¬\phi}$, we have that 
+  there exists a claim that holds and is anonymous and satisfies 
+  $\exists j \in I \suchthat \pi(C)(j) \ssub \set{\phi, ¬\phi}$ iff
+  $\set{P_i, i \in I} \ssub \set{\phi, ¬\phi}$.
+\end{proof}
+
 $C$ is \emph{suitable} iff it holds and is anonymous, informative and falsifiable.
@@
 Our goal now is to find an exposure protocol $\allleadsto$ with no suitable claim.
+
+Could we have that if it holds then it is not informative?
+$i_1$ thinks $p$ and $i_2$ thinks $¬p$.
+
+\subsection{Ideas for no suitable (new)}
+$C$ must contain the real one.
+Also, all the anonymously real ones.
 
@@
   \label{sec:supplementary}
+  The following example presents a situation where non rejection is due to finiteness of observations.
+  \begin{example}[Big disjunct, non rejectable]
+    \label{ex:bigor}
+    Consider $\ar \in \allargs$.
+    The claim $[\forall i: (\ar) \ileadstog \phi] \lor [\forall i: (\ar, \ar) \ileadstog \phi] \lor …$,
+    thus, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$,
+    is non rejectable: $\Theta \wsub C^\wsub$.
+
+    Given any $θ \in \Theta$, define $l = \max_{\hist \suchthat \exists i \in I, p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise.
+Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$.
+We have
+    $\theta \in \powerset{\allleadstog}$ and ${\allleadstog} \in C$, thus, $\theta \in C^\wsub$.
+  \end{example}
+  \begin{example}[Big disjunct unfals iff infinite]
+    \label{ex:existsParticular}
+    Given any $\ar \in \allargs$ and an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is strongly unfalsifiable: any $θ \in \Theta$ only has finitely many $i$ in its triples, thus, some $i$ is not reached by $\theta$, thus $\theta \in C^\wsub$.
+    If $I$ is finite, then the claim is falsifiable: if it is wrong, observe for each $i$ some adequate triple $(i, \hist_i, p ≠ \phi)$.
+  \end{example}
+
   \begin{example}[Three functions, may be rejectable]
@@
     Conversely, if $C$ is not rejectable, then for any $\theta_1$ containing $\emptyset$ and $(\ar)$ and $\theta_2$ containing $\emptyset$ and $(\ar')$, with $\theta_1, \theta_2 \sub {\allleadsto}$, we have $\theta_1, \theta_2 \in C^\wsub$, which requires that ${\ileadsto}$ associates $(\emptyset, (\ar))$ to $(¬\phi, \phi)$, $(\phi, ¬\phi)$ or $(\phi, \phi)$ and $(\emptyset, (\ar'))$ to $(¬\phi, \phi)$, $(\phi, \phi)$ or $(\phi, ¬\phi)$.
+  \end{example}
+
+  \begin{example}[Disjunct with incompatible paths, not falsifiable, to be deleted]
+    \label{ex:disj}
+    Given $\ar \neq \ar' \in \allargs$, the claim appearing in \cref{ex:disjR}, namely,
+    $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$, is not falsifiable.
+    Consider any ${\allleadstog} \notin C$, thus satisfying, for some $i$, $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
+    Consider any $θ \subseteq {\allleadstog}$ and let us prove that $\theta \in C^\wsub$.
+    (This is a consequence of \cref{ex:disjR} so this proof should not be useful.)
+    By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$.
+We have
+    $\theta \in \powerset{\allleadstog'}$ and ${\allleadstog'} \in C$, thus, $\theta \in C^\wsub$.
   \end{example}
@@
   \begin{definition}
+    \label{def:unfals}
     A claim is \emph{unfalsifiable} iff
@@
 
+  \subsection{Comparison with rejection}
+  The following theorem (whose condition is that $C$ may fail to hold and still be not rejectable) is a consequence of the contrapositive of \cref{th:holdsiff}.
+  \begin{corollary}
+    \label{th:holdsiffCorr}
+    A claim $C$ that satisfies $\exists {\allleadstog} \notin C$ such that $C$ is not rejectable given $\allleadstog$ is unfalsifiable and not trivial.
+  \end{corollary}
+  The following theorem (an immediate consequence of \cref{def:unfals}) is the converse of \cref{th:holdsiffCorr}.
+  It shows that falsifiability or triviality is exactly the property that we need to fill the gap.
+  \begin{theorem}
+    \label{th:holdsiffConv}
+    For any unfalsifiable and not trivial claim $C$:
+    $\exists {\allleadstog} \notin C$ such that $C$ is not rejectable given $\allleadstog$.
+  \end{theorem}
+  \begin{remark}
+    It is interesting to note that strong unfalsifiability entails necessary non rejection whereas strict unfalsifiability entails possible non rejection.
+Perhaps we should exploit this by showing that a given relation not in C entails non rejection using that relation, or something like that?
+  \end{remark}
+
+\subsection{Coverability}
+\begin{definition}
+  \label{def:covr}
+  A claim $C$ is \emph{coverable} iff $\forall \theta \in \Theta \cap C^\wsub: \exists \theta' \in \Theta \cap C^\wsub \suchthat \theta \wsub \theta' \land \set{{\allleadstog} \in \allleadstos \suchthat \theta' \in \powerset{\allleadstog}} \wsub C$.
+\end{definition}
+
+\begin{theorem}
+  \label{th:extStronglyU}
+  For any coverable claim $C$ and strongly unfalsifiable claim $C'$:
+  $\Theta \cap C^\wsub \wsub (C' \cap C)^\wsub$.
+\end{theorem}
+\begin{proof}
+  Consider any $\theta \in \Theta \cap C^\wsub$.
+  Let us show that $\theta \in \cup_{{\allleadstog} \in (C' \cap C)} \powerset{\allleadstog}$.
+
+  Consider any $\theta' \in \Theta \cap C^\wsub \suchthat \theta \wsub \theta' \land \set{{\allleadstog} \in \allleadstos \suchthat \theta' \in \powerset{\allleadstog}} \wsub C$.
+  As $\Theta \wsub {C'}^\wsub$, we have $\theta' \in \cup_{{\allleadstog} \in C'} \powerset{\allleadstog}$.
+  Pick any such $\allleadstog$ (thus with $\theta' \in \powerset{\allleadstog}$ and ${\allleadstog} \in C'$). Thus, $\theta \in \powerset{\allleadstog}$.
+  Also, as $\set{{\allleadstog} \in \allleadstos \suchthat \theta' \in \powerset{\allleadstog}} \wsub C$, we have ${\allleadstog} \in C$.
+\end{proof}
+A claim $C$ is not coverable iff $\exists \theta \in \Theta \cap C^\wsub \suchthat \forall \theta' \in \Theta \cap C^\wsub, \theta \wsub \theta': \exists {\allleadstog} \notin C \suchthat \theta' \in \powerset{\allleadstog}$.
+
+A claim $C$ is not coverable because of the empty set iff $\forall \theta \in \Theta \cap C^\wsub: \exists {\allleadstog} \notin C \suchthat \theta \in \powerset{\allleadstog}$.
+
+\begin{remark}
+  We do not have that when $C_1 \cap C_2 \neq \emptyset$, then $\theta \in C_1^\wsub \land \theta \in C_2^\wsub \implies \theta \in (C_1 \cap C_2)^\wsub$.
+  For a counter-example, consider $\hist, \hist_1, \hist_2 \in \allhists$, $i, i_1, i_2 \in I$ and $p \neq p', p_1, p_2 \in P$ and $C_1 = \set{{\allleadstog} \in \allleadstos \suchthat (\hist_1 \ileadstog[i_1] p_1 \implies \hist \ileadstog p) \land (\hist_2 \ileadstog[i_2] p_2 \implies \hist \ileadstog p')}$, $C_2 = \set{{\allleadstog} \in \allleadstos \suchthat (\hist \ileadstog p \implies \hist_2 \ileadstog[i_2] p_2)}$ and $\theta = \set{(\hist_1, i_1, p_1)}$.
+\end{remark}
+\begin{remark}
+  The above remark extends to the case where $C_1$ is strongly unfalsifiable.
+  For a counter-example, consider $C_1 = \set{{\allleadstog} \in \allleadstos \suchthat (\ar) \ileadstog \phi \lor (\ar' \ileadstog \phi)}$ and $C_2$ containing a condition requiring $(\ar) \nileadstog \phi \land (\ar' \nileadstog \phi)$.
+  Add implications if desired to make $C_1$ and $C_2$ partially compatible, for example, $C_1 = \set{{\allleadstog} \in \allleadstos \suchthat (\alpha \ileadstog[j] p) \implies [(\ar) \ileadstog \phi \lor (\ar' \ileadstog \phi)]}$, so that $C_1$ and $C_2$ require their condition only when some trigger holds.
+  Note that the $C_2$ condition may be arbitrarily complex so I see no hope of caracterizing these situations.
+\end{remark}
+\begin{remark}
+  Apparently (from \cref{ex:partlyU}) we can have $C_1 \cap C_2 \neq \emptyset$ and $\overline{C_1} \cap C_2 \neq \emptyset$ but still $C_1^\wsub \cap C_2^\wsub \wsub (C_1 \cap C_2)^\wsub$?
+  Though the above remark suggests that non inclusion will yield some similar incompatibility.
+\end{remark}
+
+\subsection{Extensions}
+\begin{theorem}
+  \label{th:struExt}
+  If $C$ is strongly unfalsifiable, then any wider claim $C' \supseteq C$ is strongly unfalsifiable.
+\end{theorem}
+\begin{proof}
+  $\Theta \wsub C^\wsub \wsub {C'}^\wsub$.
+\end{proof}
+
+\begin{theorem}
+  \label{th:partlyU}
+  If $C = C_1 \cap C_2$ with $C_1$ strongly unfalsifiable and $C_2$ coverable, then $C$ is unfalsifiable.
+\end{theorem}
+\begin{proof}
+  From $C_1$ being strongly unfalsifiable and $C_2$ being coverable, we obtain
+  $\Theta \cap C_2^\wsub \wsub (C_1 \cap C_2)^\wsub$ (\cref{th:extStronglyU}).
+
+  Pick any ${\allleadstog} \in C_2$ with ${\allleadstog} \notin C_1$ (thus ${\allleadstog} \notin C$) and any $\theta \in \Theta \cap \powerset{\allleadstog}$,
+  and let us show that $\theta \in C^\wsub$.
+
+  From $\theta \sub {\allleadstog}$ we have $\theta \in C_2^\wsub$.
+  Thus, $\theta \in (C_1 \cap C_2)^\wsub = C^\wsub$.
+\end{proof}
+\begin{theorem}
+  \label{th:strongUToStrictU}
+  If $C = C_1 \cap C_2$ with $C_1$ strongly unfalsifiable and $C_2$ falsifiable and coverable, then $C$ is unfalsifiable but not strongly unfalsifiable.
+\end{theorem}
+\begin{proof}
+  The claim $C_2$ is falsifiable, thus, is not strongly unfalsifiable.
+  Thus, the more precise claim $C$ is not strongly unfalsifiable (\cref{th:struExt}).
+  \Cref{th:partlyU} concludes.
+\end{proof}
+
+\subsection{More examples}
+\begin{example}[Partly falsifiable is still unfalsifiable]
+  \label{ex:partlyU}
+  Given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
+  the claim
+  $C = \set{{\allleadstog} \in \allleadstos \suchthat \hist \ileadstog[j] \phi \land \forall i \in I: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ is unfalsifiable but not strongly unfalsifiable.
+
+  Define
+  $C_1 = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ and
+  $C_2 = \set{{\allleadstog} \in \allleadstos \suchthat \hist \ileadstog[j] \phi}$,
+  so that $C = C_1 \cap C_2$.
+  Observe that $C_1$ is the claim of \cref{ex:disj} and $C_2$ is falsifiable and coverable. 
+  \Cref{th:strongUToStrictU} concludes.
+\end{example}
+
+\begin{example}[Partly again]
+  Considering again \cref{ex:partlyU},
+  given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
+  $C = \set{{\allleadstog} \suchthat \hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ is not falsifiable but \cref{th:veryunfals} is not applicable.
+  Observe that
+  $C^\subseteq = \set{R \in I × \allhists × P \suchthat [(j, \hist) \in R^{-1}(P) \implies (j, \hist, \phi) \in R] \land \forall i: [(i, (\ar)) \in R^{-1}(P) \land (i, (\ar')) \in R^{-1}(P)] \implies [(i, (\ar), \phi) \in R \land (i, (\ar'), \phi) \in R]}$ and
+  $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat (j, \hist) \in \theta^{-1}(P) \implies (j, \hist, \phi) \in \theta}$.
+  % Pick any $\allleadstog$ satisfying $\hist \ileadstog[j] \phi$ and $\exists i \suchthat (\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
+  % The definition of non-falsifiability applies: pick any $\theta \subseteq {\allleadstog}$, we have $\theta \in C^\subseteq$ as $(j, \hist, \phi)$ is compatible with $\theta$ and the other condition excludes nothing in $\Theta$.
+  % We can apply Thm 4 similarly: given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
+  % We should be able to apply a corollary similarly.
+  The relations obs-compatible with $C^\subseteq \cap \Theta$ are those satisfying $\hist \ileadstog[j] \phi$.
+  We conclude that $C$ is not falsifiable as $C$ is smaller than that set.
+\end{example}
+
+\begin{example}[Come back]
+  In \cref{ex:allParticular} we considered a given $\ar$ and $\phi$ and defined the falsifiable claim $C = \set{{\allleadstog} \suchthat \forall i: \ar \ileadstostg \phi}$.
+  Observe that $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat \forall \hist \suchthat \ar \in \histend: \theta(i, \hist) = \emptyset \lor \theta(i, \hist) = \phi}$.
+  The relations obs-compatible with $C^\subseteq \cap \Theta$ are exactly those in $C$.
+
+  \Cref{ex:existsParticular} assumed an infinite $I$, in which case the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
+  Observe that $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat \exists i \suchthat \forall \hist \suchthat \ar \in \histend: \theta(i, \hist) = \emptyset \lor \theta(i, \hist) = \phi}$.
+  Any relation ${\allleadstog}$ is obs-compatible with that set as $C^\subseteq \cap \Theta = \Theta$: given any $\theta \in \Theta$, there is an $i$ such that $\forall \hist: \theta(i, \hist) = \emptyset$ as $\theta$ must have a finite support.
+\end{example}
+
+\begin{example}
+  \label{ex:cardPart}
+  Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhists$ with $\hist$ and $\histp$ non prefix related.
+  The claim $\psi = (\hist \ileadstog p \lor \hist \ileadstog p') \land (\histp \ileadstog p \lor \histp \ileadstog p') \land (\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p)$ is falsifiable.
+
+  Given $q, q' \in P$, let ${\allleadstog^{q, q'}}$ be defined as $\hist \ileadstog^{q, q'} q$, $\histp \ileadstog^{q, q'} q'$ and $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j]^{q, q'} p$.
+  Note that $C_\psi = \set{{\allleadstog^{p, p}}, {\allleadstog^{p, p'}}, {\allleadstog^{p', p}}, {\allleadstog^{p', p'}}}$.
+
+  Then, $C_\psi^\wsub \cap \Theta =
+    \set{\theta \in \Theta \suchthat \theta(\hist, i) \in \set{\emptyset, p, p'} \land \theta(\histp, i) \in \set{\emptyset, p, p'} \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
+  % and we see that $C_\psi^\wsub \cap \Theta =
+  % \set{\theta \in \Theta \suchthat [\theta(\hist, i) = \theta(\histp, i) = \emptyset \lor \theta(\hist, i) \in \set{p, p'} \lor \theta(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
+
+  Any obs-compatible relation has to satisfy $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p$.
+  It also must satisfy ${\allleadstog}(\hist, i) \in \set{p, p'}$, for otherwise, with $\theta = \set{(\hist, i, {\allleadstog}(\hist, i))}$, we get $({\allleadstog} \cap \theta) \notin C_\psi^\wsub \cap \Theta$.
+  Similarly, it must satisfy ${\allleadstog}(\histp, i) \in \set{p, p'}$.
+  % are $\set{{\allleadstog} \in \allleadstos \suchthat [{\allleadstog}(\hist, i) \in \set{p, p'} \lor {\allleadstog}(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p}$, which, given $p \neq p^{\prime\prime} \neq p'$, contains ${\allleadstog^{p, p^{\prime\prime}}}$, contrary to $C_\psi$.
+\end{example}
+
+\begin{example}
+  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p, p' \in P$.
+  The claim $C = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$ is falsifiable.
+
+  We have $C^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p) \land (\theta((\ar_2), i) = \emptyset \lor \theta((\ar_2), i) = p')}$.
+  The obs-compatible relations are $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$.
+\end{example}
+\begin{example}
+  \label{ex:consti2}
+  Assume that $\card{I} ≥ 2$.
+  Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
+  We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
+  Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$.
+Assume that for some $\hist, i$, $\hist \ileadstog p$.
+Then, pick any $j \neq i$, and observe that by obs-compatibility, for any $\hist'$, $\hist' \ileadstog[j] p$.
+  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and any $(\hist^{\prime\prime}, j)$).
+Conclude that $\allleadstog$ is constant to $p$.
+  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
+\end{example}
+\begin{example}
+  \label{ex:consti1}
+  Assume that $\card{I} = 1$.
+  Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
+  We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
+  Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$.
+Assume that for some $\hist, i$, $\hist \ileadstog p$.
+Observe that by obs-compatibility, $\emptyset \ileadstog p$.
+  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and $(\emptyset, i)$).
+Conclude that $\allleadstog$ is constant to $p$.
+  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
+\end{example}
+\begin{example}
+  \label{ex:constwout0}
+  Consider any $p, p' \in P$ and the claim $C = \set{{\allleadstog} \suchthat (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p) \lor (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p')}$.
+That claim is falsifiable iff $\card I ≥ 2$ or $\card \allargs = 1$.
+The proof if so is similar to \cref{ex:consti2}; otherwise, pick any $\ar \in \allargs$ and note that any relation satisfying $(a.*) \ileadstog p$ and $\forall b \neq a: (b.*) \ileadstog p'$ is obs-compatible with $C^\wsub \cap \Theta$ but is not in $C$.
+\end{example}
+\begin{example}
+  \label{ex:unfor}
+  Consider any $i$, $\hist, \histp \in \allhists$, $p, p' \in P$ where $\hist$ and $\histp$ are not prefix related.
+  The claim $C = \set{{\allleadstog} \suchthat \hist \ileadstog p \lor \histp \ileadstog p'}$ is unfalsifiable.
+
+  We have $C^\wsub \cap \Theta = \set{\theta \suchthat (\theta(\hist, i) = \emptyset \lor \theta(\hist, i) = p) \lor (\theta(\histp, i) = \emptyset \lor \theta(\histp, i) = p')}$.
+  Observe that any $\theta \in \Theta$ satisfy $\theta(\hist, i) = \emptyset \lor \theta(\histp, i) = \emptyset$, thus, $C^\wsub \cap \Theta = \Theta$.
+  It follows that the obs-compatible relations are $\allleadstos$, which is bigger than $C$.
+\end{example}
+\begin{example}
+  Consider any $i$, $\ar \neq \ar' \in \allargs$, $p, p' \in P$.
+  The claim $C = \set{{\allleadstog} \suchthat (\ar) \ileadstog p \lor (\ar') \ileadstog p'}$ is unfalsifiable (per \cref{ex:unfor}).
+
+  Now consider the smaller claim $C' = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$ (thus $C' \ssub C$).
+  It yields a smaller set ${C'}^\wsub \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p)}$.
+  The obs-compatible relations are the smaller set $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$.
+  Thus, $C'$ is falsifiable.
+
+  Note that any claim $C^{\prime\prime}$ bigger than $C$ is unfalsifiable as well, unless trivial:
+  from $C \wsub C^{\prime\prime}$, we deduce $\Theta = C^\wsub \cap \Theta \wsub {C^{\prime\prime}}^\wsub \cap \Theta$, thus ${C^{\prime\prime}}^\wsub \cap \Theta = \Theta$ and the obs-compatible relations are $\allleadstos$, which equals $C^{\prime\prime}$ only if $C^{\prime\prime}$ is trivial.
+
+  Now consider the alternative smaller claim of \cref{ex:consti2}, $C^{(2)} = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$ (thus $C^{(2)} \ssub C$).
+  It yields a smaller set ${C^{(2)}}^\wsub \cap \Theta$.
+\end{example}
+\begin{example}
+  \label{ex:for}
+  Consider any $i$ and $p, p' \in P$.
+  The claim $C = \set{{\allleadstog} \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \hist \ileadstog p) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \hist \ileadstog p')}$, namely, all paths of even lengths lead $i$ to $p$ OR all paths of odd lengths or empty lead $i$ to $p'$, is falsifiable.
+
+  Note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \theta(\hist) \in \set{\emptyset, p}) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \theta(\hist) \in \set{\emptyset, p'})}$.
+  Consider any obs-compatible ${\allleadstog}$.
+  Assume that $\exists \hist \suchthat \card{\hist} \in 2\N \land \hist \nileadstog p$.
+  Pick $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\hist, i, {\ileadstog}(\hist))}$.
+We have $({\allleadstog} \cap \theta) \in C^\wsub \cap \Theta$, and ${\allleadstog} \cap \theta = \theta$, and from $\theta \in C^\wsub \cap \Theta$ we obtain ${\ileadstog}(\emptyset) = p'$.
+  Similarly, using $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\histp, j, {\ileadstog[j]}(\histp))}$, we obtain that $\allleadsto$ conforms to the relation in $C$.
+\end{example}
+
+\begin{remark}
+  Intuition (to be explored) is that when $C^\wsub \cap \Theta$ has the covering property, then the obs-compatible relations are easily deduced from the set (something like, just consider compatibility point per point, one singleton observation at a time).
+Covering is what is used above, something like $\exists i, \hist, \histp$ such that $\forall \hist^{\prime\prime}: [\forall j \neq i: \set{(\hist, i, .), (\histp, j, .)} \in C^\wsub \cap \Theta] \land [\exists j \neq i \suchthat \set{(\hist', i, .), (\hist^{\prime\prime}, j, .)} \in C^\wsub \cap \Theta]$.
+\end{remark}
+
+\subsection{Draft material about falsification}
 \begin{remark}
@@
 \end{remark}
+
+\begin{definition}
+  A claim $C$ is necessarily verifiable iff $\forall {\allleadstog} \in C$: $\exists \theta \in \Theta \cap \powerset{\allleadstog} \suchthat \set{{\allleadstog'} \in \allleadstos \suchthat \theta \in \powerset{\allleadstog'}} \wsub C$.
+\end{definition}
 
@@
 
+\begin{remark}
+  I think that \cref{th:extStronglyU} is not true when replacing the assumption that $C$ is easy with assuming that $C$ is necessarily verifiable.
+
+  Assume that $C$ is $\hist_1 \ileadstog p_1 \lor (\hist_2 \ileadstog p_2 \land \hist_3 \ileadstog p_3)$.
+  Say that $\theta = {(\hist_2 \ileadstog p_2), (\hist_4 \ileadstog p_4)}$.
+  Now we could have that together with $\hist_3$, this is not observable.
+  And together with $\hist_3$ it could be incompatible with $C'$: we only have guaranteed compatibility with observables.
+  % 
+  % From $C$ being verifiable we know that for some $\theta^\mathit{cover} \in \Theta: \set{{\allleadstog} \in \allleadstos \suchthat \theta^\mathit{cover} \in \powerset{\allleadstog}} \wsub C$.
+  % 
+  % From $\Theta \wsub {C'}^\wsub$
+  % we know that
+  % $\theta \in \cup_{{\allleadstog} \in C'} \powerset{\allleadstog}$.
+  % Pick any ${\allleadstog} \in C'$ such that $\theta \in \powerset{\allleadstog}$.
+  % 
+  % If $\theta^\mathit{cover} \wsub \theta$, then by $\theta \in \powerset{\allleadstog}$, $\theta^\mathit{cover} \in \powerset{\allleadstog}$,
+  % whence ${\allleadstog} \in C$.
+  % 
+  % If $\theta \wsub \theta^\mathit{cover}$, using $\Theta \wsub {C'}^\wsub$ whence $\theta^\mathit{cover} \in \cup_{{\allleadstog} \in C'} \powerset{\allleadstog}$, pick any ${\allleadstog} \in C'$ such that $\theta^\mathit{cover} \in \powerset{\allleadstog}$ (hence $\theta \in \powerset{\allleadstog}$) and get ${\allleadstog} \in C$ as previously.
+  % For the missing case (no inclusion relation), I probably need $C$ to be necessarily verifiable (and anyway the very notion of verifiability only makes sense for $\allleadsto$), but even that seems insufficient.
+  % Consider $C = \set{{\allleadstog} \in \allleadstos \suchthat \hist_1 \ileadstog p_1 \lor (…)}$.
+It is verifiable thanks to $\theta = \set{(\hist_1, i, p_1)}$ but this does not help with an observation that is compatible with $C$ using the other disjunct.
+\end{remark}
+
+Can I make a strictly unfalsifiable claim more precise and obtain a strongly unfalsifiable claim?
+
+\begin{remark}
+  The claim “For each glass, it will not break on a monday or not break on a tuesday, whatever happens to it.” is not falsifiable.
+But one can make it stronger and falsify it, by giving a general theory of how glasses break, proving that it holds, and that it is not compatible with the claim.
+I should think about this.
+\end{remark}
+
+\begin{conjecture}
+  $C$ is falsifiable iff exists two compatible paths in two different such forests, for a given $i$, that are not in a single forest, for that $i$, of $C$.
+  This seems incorrect; need to be able to build a union relation!
+  Prove that it is false with claim "i goes to phi OR i goes to not phi except for empty set going to phi"?
+  Actually I need to be able to merge two relations that agree on everything but some part of the tree, in such a way that all paths crossing the boundary must be in $C$, but not the merge.
+  TODO caract with singleton $I$.
+  % Given a claim $C$, define $S = C^\wsub \cap \Theta$.
+  % We have: $\set{\cup_i(\theta_i) \in \allleadstos \suchthat (\theta_i) \in s_S} = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S}$.
+\end{conjecture}
+\begin{remark}
+  Say that $(r1, o1)$ is determined in $C$ (to $p$) iff all relations in $C$ including $r1$ agree on ${\allleadstog}(o)$ (satisfy ${\allleadstog}(o) = p$).
+  Let $C(r, o)$ equal $\set{{\allleadstog}(o) \suchthat {\allleadstog} \in C \land r \in {\allleadstog}}$.
+
+  A claim satisfying, $\forall {\allleadstog} \in C$:
+  $\forall r1 = (o1, p1) \in {\allleadstog}$, $\exists o2$ with $o1$ and $o2$ obs-compatible and $(r1, o2)$ determined in $C$ such that $\forall o3: (o2, o3)$ is obs-compatible and $(r2 = (o2, C(r1, o2)), o3)$ is determined in $C$
+  %Perhaps can omit $(r1, o2)$ determined. In fact, has to satisfy that these determine only relations in $C$.
+  % \[\forall (\hist, i, p) \in {\allleadstog}, \exists (\histp, j, p) \in {\allleadstog} \suchthat \forall (\histpp, k) \in \allhists × I: \set{(\histp, j), (\histpp, k)} \in O\]
+  is falsifiable.
+
+  NOPE.
+  Need to say that $C$ is a union of disjoint subsets such that each subset $C'$ include all relations that are specified on a subset of observations (and left free on everything else) which satisfy something like the above condition: all points related to a point that is related to all others.
+\end{remark}
+\begin{theorem}
+  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
+  % $C = \set{\restr{\allleadstog}{R} \cup \restr{\allleadstog}{R'} \suchthat R' \in (I × \allhists) \setminus R}$.
+  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
+
+  If $\exists R \subseteq I × \allhists$ such that $C$ is determined on $R$ and satisfying $\exists o \in R \suchthat \forall o' \in R: (\set{o, o'} \in \allpriobss)$, then $C$ is falsifiable.
+\end{theorem}
+\begin{proof}
+  Note that as $C$ is closed-under-combinations, this follows from \cref{rq:closedcomb}, but let’s design a more direct proof in hope of weakening the condition.
+
+  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.
+
+  % Pick any $o_1 \in R$.
+  % Define $r_1 = (o_1, {\allleadstog}(o_1))$, thus with $r_1 \in {\allleadstog}$.
+  Pick some $o \in R$ as in the hypothesis.
+  Consider any $o' \in R$.
+  As $\set{o, o'} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
+  % $\exists {\allleadstog'} \suchthat \restr{\allleadstog}{\set{o, o'}} = \restr{\allleadstog'}{\set{o, o'}}$.
+  $\restr{\allleadstog}{\set{o, o'}} \in C^\wsub$.
+  Thus, ${\allleadstog}(o') = f(o')$.
+
+  We obtain that $\forall o' \in R: {\allleadstog}(o') = f(o')$, therefore, ${\allleadstog} \in C$.
+\end{proof}
+\begin{conjecture}[draft]
+  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
+  % $C = \set{\restr{\allleadstog}{R} \cup \restr{\allleadstog}{R'} \suchthat R' \in (I × \allhists) \setminus R}$.
+  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
+  Say that $R$ is coverable iff $\exists o_1, …, O_1, … \suchthat \forall o \in O_1: \set{o_1, o} \in \allpriobss \land \forall o \in O_2: \set{o_2, o} \in \allpriobss \land … \land \set{o_i, o_{i + 1}} \in \allpriobss \land \cup O_i = R \land o_i \in R$.
+
+  If $\exists R \subseteq I × \allhists$ coverable and such that $C$ is determined on $R$, then $C$ is falsifiable.
+\end{conjecture}
+\begin{proof}
+  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.
+
+  Pick some $o_1 \in R$ as in the hypothesis.
+  Consider any $o \in O_1 \cup \set{o_2}$.
+  As $\set{o_1, o} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
+  $\restr{\allleadstog}{\set{o_1, o}} \in C^\wsub$.
+  As also $o_1, o \in R$, ${\allleadstog}(o) = f(o)$.
+  In particular, ${\allleadstog}(o_2) = f(o_2)$.
+  Iterate with $o_2$ and $o \in O_2$, and so on.
+  We obtain that $\forall o \in R: {\allleadstog}(o) = f(o)$, therefore, ${\allleadstog} \in C$.
+\end{proof}
+\begin{example}
+  Pick $i \in I$ and
+  define $o_1 = ((a), i)$,
+  $o_2 = (\emptyset, i)$ and
+  $o_3 = ((b), i)$.
+  Define $R = \set{o_1, o_2, o_3}$.
+  Define $f_1, f_2, f_3 \in P^R$ as follows.
+  $f_1(o_1) = \phi$,
+  $f_1(o_2) = ¬\phi$,
+  $f_1(o_3) = \phi$.
+  $f_2(o_1) = \phi$,
+  $f_2(o_2) = \phi$,
+  $f_2(o_3) = ¬\phi$.
+  $f_3(o_1) = ¬\phi$,
+  $f_3(o_2) = \phi$,
+  $f_3(o_3) = \phi$.
+  Define $C = \set{f \cup g \suchthat f \in \set{f_1, f_2, f_3} \land g \in P^{(I × \allhists) \setminus R}}$.
+  This is the claim of \cref{ex:threeFs}.
+
+  Note that $R$ is covered by $O_1 = \set{o_1}, O_2 = \set{o_2}, O_3 = \set{o_3}$.
+  Note that $C$ is determined on $R$.
+  Yet, $C$ is not falsifiable.
+
+  Note that
+  \begin{equation}
+    C^\wsub \cap \Theta = \left\{\theta \in \Theta \suchthat
+    \begin{aligned}
+       & (\theta(o_1) \in \set{\emptyset, \phi} \land \theta(o_2) \in \set{\emptyset, ¬\phi} \land \theta(o_3) \in \set{\emptyset, \phi}) \lor \mbox{} \\
+       & (\theta(o_1) \in \set{\emptyset, \phi} \land \theta(o_2) \in \set{\emptyset, \phi} \land \theta(o_3) \in \set{\emptyset, ¬\phi}) \lor \mbox{} \\
+       & (\theta(o_1) \in \set{\emptyset, ¬\phi} \land \theta(o_2) \in \set{\emptyset, \phi} \land \theta(o_3) \in \set{\emptyset, \phi})
+    \end{aligned}\right\}.
+  \end{equation}
+  Also, $\theta(o_1) \neq \emptyset \implies \theta(o_3) = \emptyset$ (and equivalently, $\theta(o_3) \neq \emptyset \implies \theta(o_1) = \emptyset$),
+  whence:
+  \begin{equation}
+    C^\wsub \cap \Theta = \left\{\theta \in \Theta \suchthat
+    \begin{aligned}
+       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, ¬\phi}) \lor \mbox{} \\
+       & (\theta(o_1) = \phi \land \theta(o_2) \in \set{\emptyset, ¬\phi}) \lor \mbox{}                    \\
+       & (\theta(o_3) = \phi \land \theta(o_2) \in \set{\emptyset, ¬\phi}) \lor \mbox{}                    \\
+       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}  \\
+       & (\theta(o_1) = \phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                     \\
+       & (\theta(o_3) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                    \\
+       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}  \\
+       & (\theta(o_1) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                    \\
+       & (\theta(o_3) = \phi \land \theta(o_2) \in \set{\emptyset, \phi})
+    \end{aligned}\right\}.
+  \end{equation}
+  Factorizing:
+  \begin{equation}
+    C^\wsub \cap \Theta = \left\{\theta \in \Theta \suchthat
+    \begin{aligned}
+       & (\theta(o_1) = \theta(o_3) = \emptyset \land \theta(o_2) \in \set{\emptyset, \phi, ¬\phi})) \lor \mbox{} \\
+       & (\theta(o_1) = \phi \land \theta(o_2) \in \set{\emptyset, \phi, ¬\phi}) \lor \mbox{}                     \\
+       & (\theta(o_3) = \phi \land \theta(o_2) \in \set{\emptyset, \phi, ¬\phi}) \lor \mbox{}                     \\
+       & (\theta(o_3) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi}) \lor \mbox{}                           \\
+       & (\theta(o_1) = ¬\phi \land \theta(o_2) \in \set{\emptyset, \phi})
+    \end{aligned}\right\}.
+  \end{equation}
+
+  Note that the complement is as follows.
+  \begin{equation}
+    \overline{C^\wsub \cap \Theta} = \left\{\theta \in \Theta \suchthat
+    \begin{aligned}
+       & \theta(o_2) = 0 \lor \mbox{}                                                                                \\
+       & \theta(o_2) = ¬\phi \land (\theta(o_1) \in \set{¬\phi, 0} \lor \theta(o_3) \in \set{¬\phi, 0}) \lor \mbox{} \\
+       & \theta(o_1) \in \set{¬\phi, 0} \land \theta(o_3) \neq ¬\phi \lor \mbox{}                                    \\
+       & \theta(o_1) = \emptyset \lor \mbox{}                                                                        \\
+       & \theta(o_3) = \emptyset \lor \mbox{}                                                                        \\
+       & \theta(o_3) \in \set{¬\phi, 0} \land \theta(o_1) \neq ¬\phi
+    \end{aligned}\right\}.
+  \end{equation}
+  This seems incorrect: if $\theta = \emptyset$, then it belongs, even though it satisfies $\theta(o_1) = \emptyset$.
+
+  The relations that are obs-compatible with $C^\wsub \cap \Theta$ are the ones that, for $(o_1, o_2, o_3)$, include two $\phi$ and one $¬\phi$, the one that equals all $\phi$, and the one that assigns $o_1$ and $o_3$ to $¬\phi$ and $o_2$ to $\phi$.
+
+  It follows that the relations that are obs-compatible with $C^\wsub \cap \Theta$ and that are in $C^\wsub \cap \Theta$ are the ones that, for $(o_1, o_2, o_3)$, include two $\phi$ and one $¬\phi$; and the relations that are obs-compatible with $C^\wsub \cap \Theta$ and that are not in $C^\wsub \cap \Theta$ are the one that equals all $\phi$ and the one that assign $o_1$ and $o_3$ to $\emptyset$ and $o_2$ to $\phi$.
+
+  Pick any $g \in P^{(I × \allhists) \setminus R}$ and define ${\allleadstog} = \set{(\emptyset, i, \phi), ((a), i, \phi), ((b), i, \phi)} \cup g$.
+  This relation is obs-compatible with $C^\wsub \cap \Theta$, but ${\allleadstog} \notin C$.
+\end{example}
+\begin{conjecture}
+  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
+  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
+  Say that $R$ is coverable iff $\exists k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}} \suchthat
+    \cup_{l \in \intvl{1, k}} O_l = R \land
+    \forall l \in \intvl{1, k}: o_l \in O_l \land
+    \forall o \in O_l: \set{o_l, o} \in \allpriobss \land
+    \forall l \in \intvl{1, k - 1}: \set{o_l, o_{l + 1}} \in \allpriobss$.
+
+  If $\exists R \subseteq I × \allhists$ coverable and such that $C$ is determined on $R$, then $C$ is falsifiable.
+\end{conjecture}
+\begin{proof}
+  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.
+
+  Pick some $k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}}$ as in the hypothesis.
+  Consider any $l \in \intvl{1, k - 1}$
+  and any $o \in O_l \cup \set{o_{l + 1}}$.
+  As $\set{o_l, o} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
+  $\restr{\allleadstog}{\set{o_l, o}} \in C^\wsub$.
+  As also $o_l, o \in R$ (per $\cup_{l' \in \intvl{1, k}} O_{l'} = R$), ${\allleadstog}(o) = f(o)$.
+  In particular, ${\allleadstog}(o_{l + 1}) = f(o_{l + 1})$.
+  Iterate with $o_2$ and $o \in O_2$, and so on.
+  We obtain that $\forall o \in R: {\allleadstog}(o) = f(o)$, therefore, ${\allleadstog} \in C$.
+\end{proof}
+\begin{conjecture}
+  Given $R \subseteq I × \allhists$, define ${\sim_R} \subseteq \allleadstos × \allleadstos$ as $f \sim_R f'$ iff $\restr{f}{R} = \restr{f'}{R}$. This is an equivalence relation.
+  Given $f \in \allleadstos$, define the equivalence class of $f$ for ${\sim_R}$ as ${\sim_R}(f) = \set{f' \in \allleadstos \suchthat f \sim_R f'} = \set{f' \in P^{(I × \allhists)} \suchthat \restr{f}{R} = \restr{f'}{R}}$.
+
+  Given $R \subseteq I × \allhists$, define the a priori observable subsets of $R$ as $Z_R = \allpriobss \cap \powerset{R}$.
+
+  Consider $R \subseteq I × \allhists$, $F \subseteq P^R$ and $C = \set{f \cup g \suchthat f \in F \land g \in P^{(I × \allhists) \setminus R}}$.
+  The claim $C$ is unfalsifiable iff $\exists {\allleadstog} \in \allleadstos \suchthat \bigcap_{O \in Z_R} {\sim_O}(f) \cap C = \emptyset$.
+
+  % Given $k \in \N$ and a family $(O_l)_{l \in \intvl{1, k}}$, consider $\exists f \in C \suchthat 
+  Say that $R$ is coverable iff $\exists k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}} \suchthat
+    \cup_{l \in \intvl{1, k}} O_l = R \land
+    \forall l \in \intvl{1, k}: o_l \in O_l \land
+    \forall o \in O_l: \set{o_l, o} \in \allpriobss \land
+    \forall l \in \intvl{1, k - 1}: \set{o_l, o_{l + 1}} \in \allpriobss$.
+
+  If $\exists R \subseteq I × \allhists$ coverable and such that $C$ is determined on $R$, then $C$ is falsifiable.
+\end{conjecture}
+TODO extend this so as to cover eg $C$ containing $f_1$ and $f_2$ constant functions as in example; but not covering when the domain is not suitable!
+Use proof similar to \cref{ex:for}, getting started with observing that any obs-compatible $\allleadstog$ failing every element but one of $C$ at least at one point must then satisfy the last element of $C$ at some point (?).
+\begin{conjecture}
+  If $\forall {\allleadstog} \in C: \exists R \suchthat {\allleadstog} = f \cup g$ with $f \in P^R, g \in P^{(I × \allhists) \setminus R}$ and $R$ converable, then $C$ is falsifiable.
+  Should be specified better, but also, not sure that this holds: consider C being a leads i to phi OR b leads i to phi (given i).
+  Perhaps something like $\exists F \suchthat C = \cup_{f \in F} \set{f \cup g}$ where $f^{-1}(P)$ being coverable.
+\end{conjecture}
+\begin{proof}
+  Problem is: how to get started?
+\end{proof}
+
+\begin{example}
+  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_2) \ileadstog^2 p'$.
+  Consider the claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$. When is it falsifiable considering these two relations?
+\end{example}
+
+TODO investigate claims that are non falsifiable but with $C^\wsub \cap \Theta \neq \Theta$.
+Then exhibit a claim such that a smaller one is not the same status and a bigger one is not the same status.
+
+Any claim containing two relations that differ only on incompatible observations is not falsifiable.
+\begin{theorem}
+  Any $C$ such that $\exists {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$) and the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, does not contain two elements that are simultaneously observable (meaning that no $θ$ contains more than one of these elements), is not falsifiable.
+\end{theorem}
+\begin{proof}
+  Consider any $θ \subset {\allleadstog}$.
+  If $θ$ is fully compatible with ${\allleadstog^1}$, then ${\allleadstog^1} \in S_θ \cap C ≠ \emptyset$.
+  Otherwise, $θ$ contains some element $(i, \hist, {\allleadstog^2}(i, \hist))$ with ${\allleadstog^2}(i, \hist) ≠ {\allleadstog^1}(i, \hist)$.
+Then, ${\allleadstog^2} \in S_θ \cap C ≠ \emptyset$, for otherwise, for at least one other element $(i', \histp)$, $θ$ contains $(i', \histp, {\allleadstog^1}(i', \histp))$ with ${\allleadstog^1}(i', \histp) ≠ {\allleadstog^2}(i', \histp)$, which violates the hypothesis.
+\end{proof}
+\Cref{ex:cardPart} illustrates the need for the condition about the combination in the theorem.
+
+\begin{conjecture}
+  If a claim $C$ is not falsifiable, then $\exists {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$) and the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, does not contain two elements that are simultaneously observable (meaning that no $θ$ contains more than one of these elements).
+\end{conjecture}
+\begin{conjecture}
+  If $\forall {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$), the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, contains at least two elements that are simultaneously observable (meaning that some $θ$ contains more than one of these elements), then $C$ is falsifiable.
+\end{conjecture}
+\begin{proof}
+  We need a stronger hypothesis.
+  Consider $one$ and $two$ differ on $(i, (a))$, $(i, (b))$ and $(i, (a, a))$.
+And some $three$ not in $C$ has $(i, (a)), (i, (a, a))$ as in $one$ and $(i, (b))$ as in $two$.
+Then $C$ is not falsifiable.
+\end{proof}
+\begin{conjecture}
+  If $\forall {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$), the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, we can find some $(i, \hist) \in {\allleadstog^1}, (j, \hist') \in {\allleadstog^2}$ obs-compatible, then $C$ is falsifiable.
+\end{conjecture}
+\begin{proof}
+  This fails.
+Could have $one$, $two$, $three$, each sending everything to $p$, $¬p$ and $0$, respectively, and any combination of two of these in $C$, but no comb of three in $C$.
+Then $four$ a combination of the three ($i, a, p, i, b, ¬p, i, c, 0$), but $C$ not falsifiable.
+Actually, even if we can observe two among the three (using $i, a, p, i, aa, ¬p, i, b, 0$), we can’t falsifiy $four$.
+\end{proof}
+
+\begin{remark}
+  Odd length to $p$ and even length to $¬p$. Then we can know that $P_i = \emptyset$.
+Or, if $i$ finds $a_1 > a_2 > a_3 > a_1$ (more convincing relation), then $P_i = \emptyset$ and we can know it.
+\end{remark}
+
+\subsection{Probably redundant}
+NB the following results do not consider trivial claims.
+
+\begin{theorem}
+  A claim $C$ is falsifiable iff its complement $\Cbar = \allleadstos \setminus C$ satisfies:
+  $\forall {\allleadstog} \in \Cbar, \exists \theta \subseteq {\allleadstog} \suchthat S_θ \subseteq \Cbar$, or equivalently:
+  $\forall {\allleadstog} \in \Cbar, \exists O \in (\allhists)^I \suchthat S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
+\end{theorem}
+\begin{proof}
+  The first phrasing follows from the definition of falsifiability.
+  Also, the second phrasing implies the first one: pick $\theta = \restr{\allleadstog}{O_O}$.
+
+  Let us prove that the first phrasing implies the second one.
+  Given $\theta$, define $O = \set{(i, \argmax_{\hist \in (\theta(i) \cup \emptyset)} \card{\hist})}$ as associating to each $i$ the longest corresponding $\hist$ from $\theta$, or the empty sequence if $\theta(i)$ is empty.
+  It follows that $\theta \subseteq \restr{\allleadstog}{O_O}$.
+  Thus, $S_{\restr{\allleadstog}{O_O}} \subseteq S_θ$.
+  As $S_θ \subseteq \Cbar$, we obtain $S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
+\end{proof}
+
+\begin{corollary}
+  A claim $C$ is falsifiable iff $\forall f \in C^{\allpriobss} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
+  \[\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C.\]
+\end{corollary}
+\begin{proof}
+  Consider a falsifiable claim $C$, consider such an $f$, and let us prove that $\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C$.
+  Define ${\allleadstog} \subseteq (I × \allhists) × P$ as $\cup_{O \in \allpriobss} \restr{f(O)}{O}$. Its domain equals $I × \allhists$, and it is right-unique thanks to the condition on $f$.
+  Thus, \cref{thm:caractFals} applies and ${\allleadstog} \in C$.
+
+  Conversely, assume that the statement about all $f$ holds and let us prove that $C$ is falsifiable.
+  Consider any ${\allleadstog} \in \allleadstos$ such that $\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq$.
+  Given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$ and therefore there is some $e_O \in C$ such that $\restr{\allleadstog}{O} = \restr{e_O}{O}$.
+  Define $f$ as $f(O) = e_O$.
+  As this $f$ satisfies the condition in the hypothesis, we obtain that $\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C$, hence, $\cup_{O \in \allpriobss} \restr{\allleadstog}{O} \in C$.
+  Therefore, ${\allleadstog} \in C$.
+  Apply \cref{thm:caractFals} to conclude that $C$ is falsifiable.
+\end{proof}
+
+\begin{corollary}
+  \label{th:corffals}
+  A claim $C$ is falsifiable iff $\forall f \in \left(C^\subseteq\right)^{\allpriobss} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
+  \[\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C.\]
+\end{corollary}
+\begin{corollary}
+  \label{th:corffalsdom}
+  A claim $C$ is falsifiable iff $\forall f \in \cup_{O \in \allpriobss} \set{\set{O} × (P^O \cap C^\subseteq)} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
+  \[\cup_{O \in \allpriobss} f(O) \in C.\]
+\end{corollary}
+\begin{corollary}
+  \label{th:veryunfals}
+  Any non-trivial claim $C$ satisfying $\Theta \subseteq C^\subseteq$ is not falsifiable.
+\end{corollary}
+\begin{proof}
+  Pick any ${\allleadstog} \notin C$.
+  Per hypothesis, $\forall O \in \allpriobss$: $\restr{\allleadstog}{O} \in C^\subseteq$.
+  Define $f$ as $\forall O \in \allpriobss: f(O) = \restr{\allleadstog}{O}$.
+  Observe that $\cup_{O \in \allpriobss} f(O) = {\allleadstog}$ and hence $\cup_{O \in \allpriobss} f(O) \notin C$.
+  Apply \cref{th:corffalsdom}.
+\end{proof}
+
+\begin{corollary}
+  A claim $C$ is falsifiable iff $\set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)} = C$.
+\end{corollary}
+
+A relation $\allleadstog$ is obs-compatible with $C$ iff $\forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\subseteq$, equivalently, iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)$.
+
+\begin{remark}
+  The question of falsifiability is whether the set of relations $\allleadstog$ “compatible” with $C^\subseteq \cap \Theta$ equals $C$.
+  Compatibility needs to consider the observables, not a subset of it.
+  Define $\Theta_1 \subset \Theta$ as the observations that observe only one pair $(i, \hist)$.
+  Define $R_1 = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta_1: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)}$.
+  Note that $R \subseteq R_1$.
+  We know that $C$ is falsifiable iff $R \subseteq C$.
+Thus, $C$ is not falsifiable implies $C \subsetneq R \subseteq R_1$ thus $C \subsetneq R_1$.
+But we do not have that $C \subsetneq R_1$ implies $C$ not falsifiable: could have $C \subsetneq R_1$ but still $R = C$.
+\end{remark}
+
 \hbadness=10000

### 2023-11-23 simple.tex
Replaced and generalized arg about indicativeness

@@
   Assume that $I = \set{i_1, i_2, i_3}$ and that $P_{i_1} = \phi$ and $P_{i_2} = P_{i_3} = ¬\phi$.
-  Assume that all paths lead either to $\phi$ or to $¬\phi$.
-  Define $H_2$ as the set of paths that lead $i_2$ to $¬\phi$ and similarly $H_3$ for $i_3$.
-  In other words,
-  $\forall \hist \in \allhists \setminus H_2: \hist \ileadsto[i_2] \phi$,
-  $\forall \hist \in \allhists \setminus H_3: \hist \ileadsto[i_3] \phi$,
-  $\forall \hist \in H_2: \hist \ileadsto[i_2] ¬\phi$,
-  $\forall \hist \in H_3: \hist \ileadsto[i_3] ¬\phi$.
-  Also, define $H_{12}$ as the set of paths on which $i_1$ and $i_2$ differ.
-  Similarly for $H_{13}$.
-  We want small such sets, so let us assume that $i_1$ goes often to $¬\phi$ and only on some $H_1$ including all paths that ends with $a_1$ does it go to $\phi$.
-  We need to have suffix compatible observations from $H_{12}$ and $H_{13}$.
-  How to make none such?
-  Impossible: consider $(a_1, a_2)$ and $(a_1, a_2, a_1, a_3)$.
-
-  Thus with $H_2$ including all paths that ends with some $a_2$ decisive for $i_2$.
-  Thus, the path $(a_2, a_3)$ is in both $H_2$ and $H_3$.
-
-  Then, there exists a claim that holds and is anonymous and indicative?
-
-  But maybe $i_2$ always goes to $\phi$ except for the paths $H_2$, and $i_3$ always goes to $\phi$ except for the paths $H^3$ incompatible (not suffix or prefix) with $H_2$.
-  Then we can’t observe both that $i$ is not $i_2$ and not $i_3$: whatever $O$, if we fall upon $i_1$, this will leave $i_1$ and some other $i$ as possibilities.
-\end{theorem}
-\begin{theorem}
-  Assume that $I = \set{i_1, i_2, i_3}$ and that $P_{i_1} = \phi$ and $P_{i_2} = P_{i_3} = ¬\phi$.
 
@@
 \begin{theorem}
-  Assume that $P_{i_1} = \phi$ and $\forall i \in I \setminus \set{i_1}: P_i = ¬\phi$.
+  Assume that $I$ is finite and $P_{i_1} = \phi$ and $\forall i \in I \setminus \set{i_1}: P_i = ¬\phi$.
 
@@
 \begin{proof}
-  From $P_{i_1} = \phi$ we know that some $a_1$ is a decisive argument in favor of $\phi$ for $i_1$.
-  For $i_1 \neq i \in I$, from $P_i = ¬\phi$ we know that for some $\hist^i \in \allhists \suchthat a_1 \in \histend[i]$, $\hist^i \nileadsto \phi$ whereas $\hist^i \ileadsto[i_1] \phi$.
-  If $I$ is finite, define $O = \set{(\hist^i, i_1) \suchthat i_1 \neq i \in I}$.
-  TODO this fails because $O$ might not be an a priori observation.
-  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto} \suchthat i \in I}$.
+  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
+
+  Define $a_1$ as an argument decisive in favor of $\phi$ for $i_1$ and $a_i$ as arguments decisive in favor of $¬\phi$ for $i \in I \setminus \set{i_1}$.
+
+  Assume (wlog) that $I = \set{i_1, …, i_{\card{I}}}$.
+  Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{I}}$, $\hist_i = (\hist_{i - 1}, a_1, a_i)$.
+  We know that, $\forall i \in \intvl{2, \card{I}}$: $\hist_i \ileadsto[i_1] \phi$ and $\hist_i \ileadsto[i] ¬\phi$.
+  Define $\theta = \set{(\hist_i, i_1, \phi) \suchthat i \in \intvl{2, \card{I}}}$.
+
+  Finally, the attitudes in $C$ compatible with $\theta$ are only $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C = \set{{\allleadstog} \suchthat {\ileadstog[i_1]} = {\ileadsto[i_1]}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} = {\ileadsto[i_1]}})(i_1) = \phi$.
 \end{proof}

### 2023-11-23 simple.tex
Just finite for indicative

@@
   Finally, the attitudes in $C$ compatible with $\theta$ are only $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C = \set{{\allleadstog} \suchthat {\ileadstog[i_1]} = {\ileadsto[i_1]}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} = {\ileadsto[i_1]}})(i_1) = \phi$.
+\end{proof}
+
+\begin{theorem}
+  Assume that for some $I_1 \wsub I$, $\forall i_1 \in I_1: P_{i_1} = \phi$ and, defining $I_2 = I \setminus I_1$, that $I_2$ is finite and $\forall i_2 \in I_2: P_{i_2} = ¬\phi$.
+
+  Then, there exists a claim that holds and is anonymous and indicative.
+\end{theorem}
+\begin{proof}
+  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
+
+  Pick any $i_1 \in I_1$, define $a_1$ as an argument decisive in favor of $\phi$ for $i_1$ and $a_i$ as arguments decisive in favor of $¬\phi$ for $i \in I_2$.
+
+  Assume (wlog) that $I_2 = \set{2, …, \card{I_2} + 1}$.
+  Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{I_2} + 1}$, $\hist_i = (\hist_{i - 1}, a_1, a_i)$.
+  We know that, $\forall i \in \intvl{2, \card{I_2} + 1}$: $\hist_i \ileadsto[i_1] \phi$ and $\hist_i \ileadsto[i] ¬\phi$.
+  Define $\theta = \set{(\hist_i, i_1, \phi) \suchthat i \in \intvl{2, \card{I_2} + 1}}$.
+
+  Finally, the attitudes in $C$ compatible with $\theta$ are only $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat j \in I_1}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat j \in I_1}})(i_1) = \phi$.
 \end{proof}

### 2023-11-23 simple.tex
More about indicativeness

@@
 \end{remark}
+\begin{remark}
+  We could weaken indicativeness by allowing for disjuncts: observing either that $\hist \ileadsto \phi$ or that $\hist \ileadsto \psi$ permits to deduce something about $P_i$.
+  (Or more complex formulas under the form of a set of possible functions in $P^H$?)
+  (Actually I am not sure that this really weakens the condition.)
+\end{remark}
 
@@
 \begin{theorem}
-  Assume that $I$ is finite and $P_{i_1} = \phi$ and $\forall i \in I \setminus \set{i_1}: P_i = ¬\phi$.
-
-  Then, there exists a claim that holds and is anonymous and indicative.
-\end{theorem}
-\begin{proof}
-  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
-
-  Define $a_1$ as an argument decisive in favor of $\phi$ for $i_1$ and $a_i$ as arguments decisive in favor of $¬\phi$ for $i \in I \setminus \set{i_1}$.
-
-  Assume (wlog) that $I = \set{i_1, …, i_{\card{I}}}$.
-  Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{I}}$, $\hist_i = (\hist_{i - 1}, a_1, a_i)$.
-  We know that, $\forall i \in \intvl{2, \card{I}}$: $\hist_i \ileadsto[i_1] \phi$ and $\hist_i \ileadsto[i] ¬\phi$.
-  Define $\theta = \set{(\hist_i, i_1, \phi) \suchthat i \in \intvl{2, \card{I}}}$.
-
-  Finally, the attitudes in $C$ compatible with $\theta$ are only $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C = \set{{\allleadstog} \suchthat {\ileadstog[i_1]} = {\ileadsto[i_1]}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} = {\ileadsto[i_1]}})(i_1) = \phi$.
-\end{proof}
-
-\begin{theorem}
   Assume that for some $I_1 \wsub I$, $\forall i_1 \in I_1: P_{i_1} = \phi$ and, defining $I_2 = I \setminus I_1$, that $I_2$ is finite and $\forall i_2 \in I_2: P_{i_2} = ¬\phi$.
@@
 
-  Finally, the attitudes in $C$ compatible with $\theta$ are only $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat j \in I_1}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat j \in I_1}})(i_1) = \phi$.
+  Finally, the attitudes in $C$ compatible with $\theta$ are $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat j \in I_1}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat j \in I_1}})(i_1) = \phi$.
+\end{proof}
+
+\begin{theorem}
+  \label{th:suffIndic}
+  Define $I_1 = \set{i \in I \suchthat P_i = \phi}$ and $I_2 = \set{i \in I \suchthat P_i = ¬\phi}$. Assume that $I = I_1 \cup I_2$.
+  % Assume that for some $H \in \finite(\incr(\allhists)): [\exists i_1 \in I_1 \suchthat \forall \hist \in H: \hist \ileadsto[i_1] \phi] \land [\forall i \in I_2: \exists \hist \in H \suchthat \hist \ileadsto ¬\phi]$.
+  Assume that for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I_1$, we have $\forall i \in I_2$ that $\exists \hist \in H \suchthat {\allleadsto}(\hist, i_1) \neq {\allleadsto}(\hist, i_2)$.
+  Then, there exists a claim that holds and is anonymous and indicative.
+  \commentOC{In fact $I_2$ must include all those whose dj is not $\phi$.}
+\end{theorem}
+\begin{proof}
+  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$
+  and let us show that the claim is indicative for $i = i_1$ and $\theta = \set{(\hist, i_1, {\allleadsto}(\hist, i_1)) \suchthat \hist \in H}$.
+
+  Finally, the attitudes in $C$ compatible with $\theta$ are $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat j \in I_1}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat j \in I_1}})(i_1) = \phi$.
+\end{proof}
+\begin{corollary}
+  Define $I_1 = \set{i \in I \suchthat P_i = \phi}$ and $I_2 = \set{i \in I \suchthat P_i = ¬\phi}$. Assume that $I = I_1 \cup I_2$.
+  If $\exists A \in \finite(\allargs) \suchthat \forall i \in I_2, \exists a \in A \suchthat a \ileadstost ¬\phi$, then there exists a claim that holds and is anonymous and indicative.
+\end{corollary}
+\begin{proof}
+  We know that $i_1$ has some decisive argument $a_1$ in favor of $\phi$.
+  Assume (wlog) that $A = \set{2, …, \card{A} + 1}$.
+  Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{A} + 1}$, $\hist_i = (\hist_{i - 1}, a_1, i)$.
+  Define $H = \set{\hist_i \suchthat i \in \intvl{2, \card{A} + 1}}$.
+  Apply \cref{th:suffIndic}.
 \end{proof}

### 2023-11-30 simple.tex
Much new stuff

--- 2023-11-23 simple.tex
@@
 \begin{abstract}
-  TODO: abstract
+  To be written.
 \end{abstract}
@@
   Note also that informativeness beyond counting implies informativeness.
-  \Cref{th:infoBeyonCKO} (and extensions, \cref{th:infoBeyonCKOext,th:strinfoBeyonCKO}) shows that informativeness beyond counting (and variants) is too demanding if one wants to investigate situations where individuals have differing deliberate preferences.
+\end{remark}
+\begin{remark}
+  We could weaken indicativeness by allowing for disjuncts: observing either that $\hist \ileadsto \phi$ or that $\hist \ileadsto \psi$ permits to deduce something about $P_i$.
+  (Or more complex formulas under the form of a set of possible functions in $P^H$?)
+  (Actually I am not sure that this really weakens the condition.)
 \end{remark}
@@
 \end{definition}
-\begin{example}
-  Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$.
-Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
-\end{example}
-
-\begin{theorem}
-  For all exposure protocols, there exists a claim that holds and is strongly informative beyond counting and falsifiable iff $\exists i \suchthat P_i \neq \emptyset$.
-\end{theorem}
-\begin{proof}
-  Define $C = \set{\allleadsto}$.
-\end{proof}
-\begin{theorem}
-  For all exposure protocols, there exists a claim that holds and is informative beyond counting and falsifiable.
-\end{theorem}
-\begin{proof}
-  Define $C = \set{\allleadsto}$.
-\end{proof}
-\begin{theorem}
-  For all exposure protocols, there exists a claim that is anonymous, strongly informative beyond counting and falsifiable.
-\end{theorem}
-\begin{proof}
-  Define the claim as $\forall i \in I, \hist \in \allhists: \hist \ileadstog \phi$.
-\end{proof}
-
-What about anonymous and holds?
-\begin{theorem}
-  For all exposure protocols, there exists a claim that holds and is anonymous.
-\end{theorem}
-\begin{proof}
-  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
-\end{proof}
-
-\begin{theorem}
-  Assume that $I = \set{i_1, i_2}$ and that $P_{i_1} = \phi$ and $P_{i_2} = ¬\phi$.
-
-  Then, there exists a claim that holds and is anonymous and indicative.
-\end{theorem}
-\begin{proof}
-  From $P_{i_1} = \phi$ we know that some $a_1$ is a decisive argument in favor of $\phi$ for $i_1$.
-  From $P_{i_2} = ¬\phi$ we know that for some $\hist \in \allhists \suchthat a_1 \in \histend$, $\hist \nileadsto[i_2] \phi$ whereas $\hist \ileadsto[i_1] \phi$.
-  Define $O = \set{(\hist, i_1)}$.
-  Define 
-  ${\allleadstog^1} = \set{(i_1, \ileadsto[i_1]), (i_2, \ileadsto[i_2])}$ and
-  ${\allleadstog^2} = \set{(i_1, \ileadsto[i_2]), (i_2, \ileadsto[i_1])}$.
-  Define the claim as $C = \set{{\allleadstog^1}, {\allleadstog^2}}$.
-\end{proof}
-
-\begin{theorem}
-  Assume that $I = \set{i_1, i_2, i_3}$ and that $P_{i_1} = \phi$ and $P_{i_2} = P_{i_3} = ¬\phi$.
-
-  Then, there exists a claim that holds and is anonymous and indicative.
-\end{theorem}
-\begin{proof}
-  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
-  In other words, for $k, l \in \intvl{1, 3}$, define
-  ${\allleadstog^{k, l}} = \set{(i_k, \ileadsto[i_1]), (i_l, \ileadsto[i_2]), (i_{\intvl{1, 3} \setminus \set{k, l}}, \ileadsto[i_3])}$.
-  Define the claim as $C = \set{{\allleadstog^{1, 2}}, {\allleadstog^{1, 3}}, {\allleadstog^{2, 1}}, {\allleadstog^{2, 3}}, {\allleadstog^{3, 1}}, {\allleadstog^{3, 2}}}$.
-
-  Define $a_1$ as an argument decisive in favor of $\phi$ for $i_1$ and $a_2, a_3$ as arguments decisive in favor of $¬\phi$ for $i_2, i_3$.
-
-  Define $\hist_{12} = (a_1, a_2)$ and $\hist_{13} = (\hist_{12}, a_1, a_3)$.
-  We know that 
-  $\hist_{12} \ileadsto[i_1] \phi$, 
-  $\hist_{12} \ileadsto[i_2] ¬\phi$, 
-  $\hist_{13} \ileadsto[i_1] \phi$, 
-  $\hist_{13} \ileadsto[i_3] ¬\phi$.
-  Define $\theta = \set{(\hist_{12}, i_1, \phi), (\hist_{13}, i_1, \phi)}$.
-  Finally, the attitudes in $C$ compatible with $\theta$ are only $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C = \set{{\allleadstog^{1, 2}}, {\allleadstog^{1, 3}}}$, and $\pi(\set{{\allleadstog^{1, 2}}, {\allleadstog^{1, 3}}})(i_1) = \phi$.
-\end{proof}
-
-\begin{theorem}
-  Assume that $I$ is finite and $P_{i_1} = \phi$ and $\forall i \in I \setminus \set{i_1}: P_i = ¬\phi$.
-
-  Then, there exists a claim that holds and is anonymous and indicative.
-\end{theorem}
-\begin{proof}
-  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
-
-  Define $a_1$ as an argument decisive in favor of $\phi$ for $i_1$ and $a_i$ as arguments decisive in favor of $¬\phi$ for $i \in I \setminus \set{i_1}$.
-
-  Assume (wlog) that $I = \set{i_1, …, i_{\card{I}}}$.
-  Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{I}}$, $\hist_i = (\hist_{i - 1}, a_1, a_i)$.
-  We know that, $\forall i \in \intvl{2, \card{I}}$: $\hist_i \ileadsto[i_1] \phi$ and $\hist_i \ileadsto[i] ¬\phi$.
-  Define $\theta = \set{(\hist_i, i_1, \phi) \suchthat i \in \intvl{2, \card{I}}}$.
-
-  Finally, the attitudes in $C$ compatible with $\theta$ are only $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C = \set{{\allleadstog} \suchthat {\ileadstog[i_1]} = {\ileadsto[i_1]}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} = {\ileadsto[i_1]}})(i_1) = \phi$.
-\end{proof}
-
-\begin{theorem}
-  \label{th:HAinformativeness}
-  Given any $Q \wsub P \cup \set{\emptyset}$,
-  the following two conditions on $\allleadsto$ are equivalent:
-  there exists a claim that holds and is anonymous and satisfies 
-  $\exists j \in I \suchthat \pi(C)(j) \ssub Q$;
-  and 
-  $\set{P_i, i \in I} \ssub Q$.
-\end{theorem}
-\begin{proof}
-  Consider any claim $C$ that holds and is anonymous, pick any $j \in I$, and let us show that $\set{P_i, i \in I} \wsub \pi(C)(j)$.
-  Pick any $p \in \set{P_i, i \in I}$. 
-  Pick any $i \in I$ such that $\pi({\allleadsto})(i) = p$.
-  Define $\sigma$ as the permutation exchanging $i$ and $j$.
-  As $C$ holds, it contains $\allleadsto$, and by anonymity, it contains ${\allleadsto} \circ \sigma$.
-Observing that $\pi({\allleadsto} \circ \sigma)(j) = \pi({\allleadsto})(i) = p$, we obtain $p \in \pi(C)(j)$.
-
-  It follows that for any claim $C$ that holds and is anonymous, if $\exists j \in I \suchthat \pi(C)(j) \ssub Q$ then $\set{P_i, i \in I} \wsub \pi(C)(j) \ssub Q$ thus $\set{P_i, i \in I} \ssub Q$.
-
-  Turning to the other direction, if $\set{P_i, i \in I} \ssub Q$, then pick any $p \in Q \setminus \set{P_i, i \in I}$; the claim $\forall i \in I: P_i \neq p$ satisfies the desired properties.
-\end{proof}
-
-\begin{theorem}
-  \label{th:infoBeyonCKO}
-  There exists a claim that holds and is anonymous and informative beyond counting iff $\set{P_i, i \in I} \neq P \cup \set{\emptyset}$.
-\end{theorem}
-\begin{proof}
-  From \cref{th:HAinformativeness} with $Q = P \cup \set{\emptyset}$, we have that 
-  there exists a claim that holds and is anonymous and satisfies 
-  $\exists j \in I \suchthat \pi(C)(j) \ssub P \cup \set{\emptyset}$ iff
-  $\set{P_i, i \in I} \ssub P \cup \set{\emptyset}$.
-\end{proof}
-
-\begin{theorem}
-  \label{th:strinfoBeyonCKO}
-  There exists a claim that holds and is anonymous and strongly informative beyond counting iff $\set{P_i, i \in I} \ssub P$.
-\end{theorem}
-\begin{proof}
-  From \cref{th:HAinformativeness} with $Q = P$, we have that 
-  there exists a claim that holds and is anonymous and satisfies 
-  $\exists j \in I \suchthat \pi(C)(j) \ssub P$ iff
-  $\set{P_i, i \in I} \ssub P$.
-\end{proof}
-
-\begin{theorem}
-  \label{th:infoBeyonCKOext}
-  Given $Q = \set{\phi, ¬\phi}$,
-  the following two conditions on $\allleadsto$ are equivalent:
-  there exists a claim that holds and is anonymous and satisfies 
-  $\exists j \in I \suchthat \pi(C)(j) \ssub Q$;
-  and 
-  $\set{P_i, i \in I} \ssub Q$.
-\end{theorem}
-\begin{proof}
-  From \cref{th:HAinformativeness} with $Q = \set{\phi, ¬\phi}$, we have that 
-  there exists a claim that holds and is anonymous and satisfies 
-  $\exists j \in I \suchthat \pi(C)(j) \ssub \set{\phi, ¬\phi}$ iff
-  $\set{P_i, i \in I} \ssub \set{\phi, ¬\phi}$.
-\end{proof}
-
+\Cref{ex:anon} illustrates.
+
+We are now interested in the interplay between properties of holding, anonymity, (strong) informativeness beyond counting, and falsifiability.
+\Cref{th:hsif,th:hif,th:asif} show their compatibility when one of holding or anonymity is not required (except that informativeness beyond counting cannot be made strong in the edge case where $\forall i \in I: P_i = \emptyset$).
+
+We thus turn to requiring both anonymous and holding.
+They are always satisfiable when only these two are required (\cref{th:ha}).
+\Cref{th:infoBeyonCKO} (and extensions, \cref{th:infoBeyonCKOext,th:strinfoBeyonCKO}) shows that informativeness beyond counting (and variants) is too demanding if one wants to investigate situations where individuals have differing deliberate preferences.
+
+It is possible under reasonable conditions of regularity to satisfy anonymous and holding together with indicativeness.
+This happens for example when everybody has a deliberate judgment and a finite set of decisive arguments suffices to lead everybody to their deliberate judgment (\cref{th:suffIndicDec}).
+
+\begin{theorem}
+  \label{th:suffFals}
+  Assume that $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  Then, there exists a claim that holds and is anonymous and falsifiable.
+\end{theorem}
+\begin{proof}
+  Define $C = \set{{\allleadstog} \suchthat \forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}}$. It holds and is anonymous.
+  Pick any ${\allleadstog} \notin C$.
+  Then, $\exists i \in I \suchthat {{\ileadstog}} \notin \set{{\ileadsto[k]} \suchthat k \in I}$.
+  Pick any such $i$ and any $H$ such that $\forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  Define $\theta = \set{(\hist, i, {\ileadstog}(\hist)) \suchthat \hist \in H} \in \Theta \cap \powerset{\allleadstog}$.
+  Then, $\theta \notin C^\wsub$, because $\forall j \in I: \theta \nsubseteq {\ileadsto[j]}$.
+
+  For another proof, note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat \forall i \in I: \exists j \in I \suchthat \theta \cap (\allhists × \set{i} × P) \wsub {\ileadsto[j]}}$.
+  Pick any ${\allleadstog} \in E(C^\wsub \cap \Theta)$ and let us show that ${\allleadstog} \in C$.
+  Note that ${\allleadstog} \notin C \iff \exists i \in I \suchthat {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, in which case the consequent in the theorem holds.
+  We need to show that $\nexists i \in I, H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  In other words, given any $i \in I$, we need to show that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
+\end{proof}
+
+\begin{remark}
+  The opposite of \cref{th:suffFals} is NOT $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  Thus, for some ${\allleadstog} \in \allleadstos$ and some $i \in I$ with ${\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, we have that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
+
+  For example, $\allargs = \set{\ar_1, \ar_2}$ and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and the attitude contains only people constant to $\phi$ (except that they map $\emptyset$ to anything) and people constant to $¬\phi$ (except that they map $\emptyset$ to anything).
+\end{remark}
+\begin{theorem}
+  Consider the attitude above. Is there a claim that holds and is anonymous and falsifiable?
+  Check \cref{ex:falsAnonIfBig}.
+\end{theorem}
+
+\subsection{Ideas for no suitable}
 $C$ is \emph{suitable} iff it holds and is anonymous, informative and falsifiable.
@@
 
-\subsection{Ideas for no suitable (new)}
-$C$ must contain the real one.
-Also, all the anonymously real ones.
-
-\subsection{Ideas for no suitable}
 Given $\histk \in \allhists$ and $\ar_l \in \allargs$, let $(\histk, …, \ar_l, ?)$ denote the set
@@
   This definition of truthfulness is adopted because of our goal of distinguishing empirical claims.
-Truthfulness, so defined, can be falsified empirically: if it does not hold, it is possible to prove this empirically by exhibiting a counter-example in the form of a tuple $i, k, (a_j)_{j \in \intvl{1, k}}, \alpha$ such that TODO.
+Truthfulness, so defined, can be falsified empirically: if it does not hold, it is possible to prove this empirically by exhibiting a counter-example in the form of a tuple $i, k, (a_j)_{j \in \intvl{1, k}}, \alpha$ such that … (to be completed).
 
@@
   \end{example}
+
+  \begin{example}
+    \label{ex:anon}
+    Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$.
+Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
+  \end{example}
+
+  \begin{example}
+    Consider $I = \set{i}$ and $\ar_1 \neq \ar_2 \in \allargs$.
+    The claim $C = \set{{\allleadstog} \in \allleadstos \suchthat (\forall \hist \neq \emptyset: \hist \ileadstog \phi) \lor (\forall \hist \neq \emptyset: \hist \ileadstog ¬\phi)}$ is not falsifiable.
+
+    Consider ${\allleadstog}$ defined as $\hist \ileadstog \phi$ iff $\hist = \emptyset \lor \hist_1 = \ar_1$ and $\hist \ileadstog ¬\phi$ otherwise.
+    We have ${\allleadstog} \notin C$.
+    But any $θ \subseteq {\allleadstog}$ satisfies $\theta \in C^\wsub$.
+  \end{example}
+
+  \begin{example}
+    \label{ex:falsAnonIfBig}
+    Consider $I = \set{i_1, i_2}$ and $\ar_1 \neq \ar_2 \in \allargs$.
+    Given $p_0, p, p'_0, p' \in P$,
+    define ${\allleadstog^{i_1 \mapsto (p_0, p); i_2 \mapsto (p'_0, p')}}$ as $\emptyset \ileadstog[i_1] p_0 \land \emptyset \ileadstog[i_2] p'_0 \land \forall \hist \in \allhists \setminus \set{\emptyset}: \hist \ileadstog[i_1] p \land \hist \ileadstog[i_2] p'$.
+
+    The claim $C = \set{{\allleadstog^{i_1 \mapsto (p_0, p); i_2 \mapsto (p'_0, p')}} \suchthat p_0, p, p'_0, p' \in \set{\phi, ¬\phi}}$ is not falsifiable.
+    Consider ${\allleadstog}$ defined as, $\forall i \in I$, $\hist \ileadstog \phi$ iff $\hist = \emptyset \lor \hist_1 = \ar_1$ and $\hist \ileadstog ¬\phi$ otherwise.
+    We have ${\allleadstog} \notin C$.
+
+    Consider now any bigger claim $C'$, thus with $C \wsub C'$.
+    I believe that $C'$ is falsifiable iff it includes all relations that are constant on all paths starting with a given argument (thus all $\allleadstog$ such that $\forall \hist, \histp \in \allhists: \hist_1 = \histp_1 \implies {\ileadstog}(\hist) = {\ileadstog}(\histp)$).
+  \end{example}
+
+  \begin{example}
+    Consider $I = \set{i_{p_0, p} \suchthat p_0, p \in \set{\phi, ¬\phi}}$ (thus $\card{I} = 4$).
+    Given $p_0, p \in P$,
+    define $R^{(p_0, p)} = R^{\emptyset \mapsto p_0; p}: \allhists \rightarrow P$ as $R(\emptyset) = p_0 \land \forall \hist \in \allhists \setminus \set{\emptyset}: R(\hist) = p$.
+
+    Define ${\allleadsto}$ as $\forall p_0, p \in \set{\phi, ¬\phi}: {\ileadsto[i_{p_0, p}]} = R^{\emptyset \mapsto p_0; p}$.
+
+    Given $f: I \rightarrow \set{\phi, ¬\phi}^2$,
+    define ${\allleadstog^f}$ as $\forall i \in I: {\allleadstog^f_i} = R^{f(i)}$.
+    Note that any $f \in (\set{\phi, ¬\phi}^2)^I$ can be seen as a permutation $\sigma$ over $I$ and that ${\allleadstog^f} = {\allleadsto} \circ \sigma$.
+
+    The claim $C = \set{{\allleadstog^f} \suchthat f \in (\set{\phi, ¬\phi}^2)^I}$ is falsifiable: consider any ${\allleadstog}$ observably compatible with $C$; if there is $\hist^1, \hist^2, \hist^3 \in \allhists \setminus \set{\emptyset}$ and $i_1 \neq i_2 \neq i_3 \neq i_1 \in I$ with $\forall k \in \intvl{1, 3}: \hist^k \ileadstog[i_k] \phi$, then ${\allleadstog}$ is not observably compatible with $C$, so there must be at most 2 individuals mapping some non empty path to $\phi$ (thus at least 2 mapping all non empty paths to $¬\phi$) and for the same reason, at least 2 individuals mapping all non empty paths to $\phi$; thus (together with noting that two individuals mapping every paths to $\phi$ is not observably compatible with $C$ and adding the missing bits), ${\allleadstog} \in C$.
+  \end{example}
+
+  \begin{example}
+    Consider $I = \cup_{p_0, p \in \set{\phi, ¬\phi}} I_{p_0, p}$, with each $I_{p_0, p}$ infinite, and $\ar_1 \neq \ar_2 \in \allargs$.
+    Given $p_0, p \in P$,
+    define $R^{(p_0, p)} = R^{\emptyset \mapsto p_0; p}: \allhists \rightarrow P$ as $R(\emptyset) = p_0 \land \forall \hist \in \allhists \setminus \set{\emptyset}: R(\hist) = p$.
+    Define ${\allleadsto}$ as $\forall p_0, p \in \set{\phi, ¬\phi}, i \in I_{p_0, p}: {\ileadsto} = R^{\emptyset \mapsto p_0; p}$.
+
+    The claim $C = \set{{\allleadsto} \circ \sigma \suchthat \sigma: I \leftrightarrow I}$ is not falsifiable:
+    consider ${\allleadstog}$ defined as, $\forall i \in I$, $\hist \ileadstog \phi$ iff $\hist = \emptyset \lor \hist_1 = \ar_1$ and $\hist \ileadstog ¬\phi$ otherwise; we have ${\allleadstog} \notin C$
+    but any $θ \in \Theta, \theta \subseteq {\allleadstog}$ satisfies $\theta \in C^\wsub$.
+
+    Now consider $C' = \set{{\allleadstog} \suchthat \forall i \in I, \hist, \histp \in \allhists: \hist_1 = \histp_1 \implies {\ileadstog}(\hist) = {\ileadstog}(\histp)}$. (Thus $C \wsub C'$.)
+    This one is falsifiable: if ${\allleadstog} \notin C$, then $\exists i \in I, \hist, \histp \suchthat \hist_1 = \histp_1 \land {\ileadstog}(\hist) ≠ {\ileadstog}(\histp)$, now define $\histpp$ as the common prefix to $\hist$ and $\histp$; as ${\ileadstog}(\hist) ≠ {\ileadstog}(\histp)$, we have at least one of ${\ileadstog}(\hist) ≠ {\ileadstog}(\histpp)$ or ${\ileadstog}(\histp) ≠ {\ileadstog}(\histpp)$, and as $\histpp$ satisfies $\histpp_1 = \hist_1$ and $\histpp_1 = \histp_1$, observing the corresponding pair of paths for $i$ falsifies $C$.
+  \end{example}
+
+  \begin{example}
+    Imagine that the real relation is composed of individuals who map $(a_1, a_2)$ to $\phi$ and $(a_1, a_3)$ to $¬\phi$ and individuals converse (with both, say, mapping everything else to $0$).
+    Then the claim $C = \set{{\allleadstog} \suchthat \forall i \in I: {\ileadstog}(\ar_1, \ar_2) \in \set{\phi, ¬\phi} \land {\ileadstog}(\ar_1, \ar_3) \in \set{\phi, ¬\phi}}$ is falsifiable.
+
+    Imagine that the real relation is composed of individuals who map $(a_1, a_2)$ to $\phi$ and $(a_1, a_3)$ to $¬\phi$ and individuals converse (with both, say, mapping everything else to $0$) and individuals who map $(a_4, a_5)$ to $\phi$ and $(a_6)$ to $¬\phi$ and individuals converse, with both mapping everything else to $0$.
+    Then the claim $C = \set{{\allleadstog} \suchthat \forall i \in I: [{\ileadstog}(\ar_1, \ar_2) \in \set{\phi, ¬\phi} \land {\ileadstog}(\ar_1, \ar_3) \in \set{\phi, ¬\phi} \land {\ileadstog}(H) = 0] \lor [{\ileadstog}(\ar_4, \ar_5) \in \set{\phi, ¬\phi} \land {\ileadstog}(\ar_6) \in \set{\phi, ¬\phi} \land {\ileadstog}(H) = 0]}$, where $H$ designates all “other” paths (abusing notation), is falsifiable.
+
+    Imagine that the real relation is composed of individuals who map $(a_1, a_2)$ to $\phi$ and $(a_1, a_3)$ to $¬\phi$ and individuals converse (with both, say, mapping everything else to $0$) and individuals who map $(a_1, a_4)$ to $\phi$ and $(a_6)$ to $¬\phi$ and individuals converse, with both mapping everything else to $0$.
+    Then the claim $C = \set{{\allleadstog} \suchthat \forall i \in I: [{\ileadstog}(\ar_1, \ar_2) \in \set{\phi, ¬\phi} \land {\ileadstog}(\ar_1, \ar_3) \in \set{\phi, ¬\phi} \land {\ileadstog}(H) = 0] \lor [{\ileadstog}(\ar_1, \ar_4) \in \set{\phi, ¬\phi} \land {\ileadstog}(\ar_6) \in \set{\phi, ¬\phi} \land {\ileadstog}(H) = 0]}$, where $H$ designates all “other” paths (abusing notation), is falsifiable: could have an individual mapping both $(\ar_1, \ar_2)$ and $(\ar_1, \ar_4)$ to $0$ but then if she maps $\ar_6$ to $0$, observe both $(\ar_1, \ar_2)$ and $\ar_6$ and falsify $C$; if she maps $\ar_6$ in $\set{\phi, ¬\phi}$, both $(\ar_1, \ar_4)$ and $\ar_6$ and falsify $C$ (here assuming falsely in the whole example that $\ar_6$ can be observed together with $(\ar_1, .)$, so we probably should replace $\ar_6$ by $\emptyset$).
+  \end{example}
+
+  \subsection{More examples}
+  \begin{example}[Partly falsifiable is still unfalsifiable]
+    \label{ex:partlyU}
+    Given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
+    the claim
+    $C = \set{{\allleadstog} \in \allleadstos \suchthat \hist \ileadstog[j] \phi \land \forall i \in I: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ is unfalsifiable but not strongly unfalsifiable.
+
+    Define
+    $C_1 = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ and
+    $C_2 = \set{{\allleadstog} \in \allleadstos \suchthat \hist \ileadstog[j] \phi}$,
+    so that $C = C_1 \cap C_2$.
+    Observe that $C_1$ is the claim of \cref{ex:disj} and $C_2$ is falsifiable and coverable. 
+    \Cref{th:strongUToStrictU} concludes.
+  \end{example}
+
+  \begin{example}[Partly again]
+    Considering again \cref{ex:partlyU},
+    given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
+    $C = \set{{\allleadstog} \suchthat \hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ is not falsifiable but \cref{th:veryunfals} is not applicable.
+    Observe that
+    $C^\subseteq = \set{R \in I × \allhists × P \suchthat [(j, \hist) \in R^{-1}(P) \implies (j, \hist, \phi) \in R] \land \forall i: [(i, (\ar)) \in R^{-1}(P) \land (i, (\ar')) \in R^{-1}(P)] \implies [(i, (\ar), \phi) \in R \land (i, (\ar'), \phi) \in R]}$ and
+    $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat (j, \hist) \in \theta^{-1}(P) \implies (j, \hist, \phi) \in \theta}$.
+    % Pick any $\allleadstog$ satisfying $\hist \ileadstog[j] \phi$ and $\exists i \suchthat (\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
+    % The definition of non-falsifiability applies: pick any $\theta \subseteq {\allleadstog}$, we have $\theta \in C^\subseteq$ as $(j, \hist, \phi)$ is compatible with $\theta$ and the other condition excludes nothing in $\Theta$.
+    % We can apply Thm 4 similarly: given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
+    % We should be able to apply a corollary similarly.
+    The relations obs-compatible with $C^\subseteq \cap \Theta$ are those satisfying $\hist \ileadstog[j] \phi$.
+    We conclude that $C$ is not falsifiable as $C$ is smaller than that set.
+  \end{example}
+
+  \begin{example}[Come back]
+    In \cref{ex:allParticular} we considered a given $\ar$ and $\phi$ and defined the falsifiable claim $C = \set{{\allleadstog} \suchthat \forall i: \ar \ileadstostg \phi}$.
+    Observe that $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat \forall \hist \suchthat \ar \in \histend: \theta(i, \hist) = \emptyset \lor \theta(i, \hist) = \phi}$.
+    The relations obs-compatible with $C^\subseteq \cap \Theta$ are exactly those in $C$.
+
+    \Cref{ex:existsParticular} assumed an infinite $I$, in which case the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
+    Observe that $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat \exists i \suchthat \forall \hist \suchthat \ar \in \histend: \theta(i, \hist) = \emptyset \lor \theta(i, \hist) = \phi}$.
+    Any relation ${\allleadstog}$ is obs-compatible with that set as $C^\subseteq \cap \Theta = \Theta$: given any $\theta \in \Theta$, there is an $i$ such that $\forall \hist: \theta(i, \hist) = \emptyset$ as $\theta$ must have a finite support.
+  \end{example}
+
+  \begin{example}
+    \label{ex:cardPart}
+    Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhists$ with $\hist$ and $\histp$ non prefix related.
+    The claim $\psi = (\hist \ileadstog p \lor \hist \ileadstog p') \land (\histp \ileadstog p \lor \histp \ileadstog p') \land (\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p)$ is falsifiable.
+
+    Given $q, q' \in P$, let ${\allleadstog^{q, q'}}$ be defined as $\hist \ileadstog^{q, q'} q$, $\histp \ileadstog^{q, q'} q'$ and $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j]^{q, q'} p$.
+    Note that $C_\psi = \set{{\allleadstog^{p, p}}, {\allleadstog^{p, p'}}, {\allleadstog^{p', p}}, {\allleadstog^{p', p'}}}$.
+
+    Then, $C_\psi^\wsub \cap \Theta =
+      \set{\theta \in \Theta \suchthat \theta(\hist, i) \in \set{\emptyset, p, p'} \land \theta(\histp, i) \in \set{\emptyset, p, p'} \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
+    % and we see that $C_\psi^\wsub \cap \Theta =
+    % \set{\theta \in \Theta \suchthat [\theta(\hist, i) = \theta(\histp, i) = \emptyset \lor \theta(\hist, i) \in \set{p, p'} \lor \theta(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
+
+    Any obs-compatible relation has to satisfy $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p$.
+    It also must satisfy ${\allleadstog}(\hist, i) \in \set{p, p'}$, for otherwise, with $\theta = \set{(\hist, i, {\allleadstog}(\hist, i))}$, we get $({\allleadstog} \cap \theta) \notin C_\psi^\wsub \cap \Theta$.
+    Similarly, it must satisfy ${\allleadstog}(\histp, i) \in \set{p, p'}$.
+    % are $\set{{\allleadstog} \in \allleadstos \suchthat [{\allleadstog}(\hist, i) \in \set{p, p'} \lor {\allleadstog}(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p}$, which, given $p \neq p^{\prime\prime} \neq p'$, contains ${\allleadstog^{p, p^{\prime\prime}}}$, contrary to $C_\psi$.
+  \end{example}
+
+  \begin{example}
+    Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p, p' \in P$.
+    The claim $C = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$ is falsifiable.
+
+    We have $C^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p) \land (\theta((\ar_2), i) = \emptyset \lor \theta((\ar_2), i) = p')}$.
+    The obs-compatible relations are $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$.
+  \end{example}
+  \begin{example}
+    \label{ex:consti2}
+    Assume that $\card{I} ≥ 2$.
+    Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
+    We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
+    Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$.
+Assume that for some $\hist, i$, $\hist \ileadstog p$.
+Then, pick any $j \neq i$, and observe that by obs-compatibility, for any $\hist'$, $\hist' \ileadstog[j] p$.
+    It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and any $(\hist^{\prime\prime}, j)$).
+Conclude that $\allleadstog$ is constant to $p$.
+    It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
+  \end{example}
+  \begin{example}
+    \label{ex:consti1}
+    Assume that $\card{I} = 1$.
+    Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
+    We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
+    Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$.
+Assume that for some $\hist, i$, $\hist \ileadstog p$.
+Observe that by obs-compatibility, $\emptyset \ileadstog p$.
+    It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and $(\emptyset, i)$).
+Conclude that $\allleadstog$ is constant to $p$.
+    It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
+  \end{example}
+  \begin{example}
+    \label{ex:constwout0}
+    Consider any $p, p' \in P$ and the claim $C = \set{{\allleadstog} \suchthat (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p) \lor (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p')}$.
+That claim is falsifiable iff $\card I ≥ 2$ or $\card \allargs = 1$.
+The proof if so is similar to \cref{ex:consti2}; otherwise, pick any $\ar \in \allargs$ and note that any relation satisfying $(a.*) \ileadstog p$ and $\forall b \neq a: (b.*) \ileadstog p'$ is obs-compatible with $C^\wsub \cap \Theta$ but is not in $C$.
+  \end{example}
+  \begin{example}
+    \label{ex:unfor}
+    Consider any $i$, $\hist, \histp \in \allhists$, $p, p' \in P$ where $\hist$ and $\histp$ are not prefix related.
+    The claim $C = \set{{\allleadstog} \suchthat \hist \ileadstog p \lor \histp \ileadstog p'}$ is unfalsifiable.
+
+    We have $C^\wsub \cap \Theta = \set{\theta \suchthat (\theta(\hist, i) = \emptyset \lor \theta(\hist, i) = p) \lor (\theta(\histp, i) = \emptyset \lor \theta(\histp, i) = p')}$.
+    Observe that any $\theta \in \Theta$ satisfy $\theta(\hist, i) = \emptyset \lor \theta(\histp, i) = \emptyset$, thus, $C^\wsub \cap \Theta = \Theta$.
+    It follows that the obs-compatible relations are $\allleadstos$, which is bigger than $C$.
+  \end{example}
+  \begin{example}
+    Consider any $i$, $\ar \neq \ar' \in \allargs$, $p, p' \in P$.
+    The claim $C = \set{{\allleadstog} \suchthat (\ar) \ileadstog p \lor (\ar') \ileadstog p'}$ is unfalsifiable (per \cref{ex:unfor}).
+
+    Now consider the smaller claim $C' = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$ (thus $C' \ssub C$).
+    It yields a smaller set ${C'}^\wsub \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p)}$.
+    The obs-compatible relations are the smaller set $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$.
+    Thus, $C'$ is falsifiable.
+
+    Note that any claim $C^{\prime\prime}$ bigger than $C$ is unfalsifiable as well, unless trivial:
+    from $C \wsub C^{\prime\prime}$, we deduce $\Theta = C^\wsub \cap \Theta \wsub {C^{\prime\prime}}^\wsub \cap \Theta$, thus ${C^{\prime\prime}}^\wsub \cap \Theta = \Theta$ and the obs-compatible relations are $\allleadstos$, which equals $C^{\prime\prime}$ only if $C^{\prime\prime}$ is trivial.
+
+    Now consider the alternative smaller claim of \cref{ex:consti2}, $C^{(2)} = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$ (thus $C^{(2)} \ssub C$).
+    It yields a smaller set ${C^{(2)}}^\wsub \cap \Theta$.
+  \end{example}
+  \begin{example}
+    \label{ex:for}
+    Consider any $i$ and $p, p' \in P$.
+    The claim $C = \set{{\allleadstog} \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \hist \ileadstog p) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \hist \ileadstog p')}$, namely, all paths of even lengths lead $i$ to $p$ OR all paths of odd lengths or empty lead $i$ to $p'$, is falsifiable.
+
+    Note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \theta(\hist) \in \set{\emptyset, p}) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \theta(\hist) \in \set{\emptyset, p'})}$.
+    Consider any obs-compatible ${\allleadstog}$.
+    Assume that $\exists \hist \suchthat \card{\hist} \in 2\N \land \hist \nileadstog p$.
+    Pick $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\hist, i, {\ileadstog}(\hist))}$.
+We have $({\allleadstog} \cap \theta) \in C^\wsub \cap \Theta$, and ${\allleadstog} \cap \theta = \theta$, and from $\theta \in C^\wsub \cap \Theta$ we obtain ${\ileadstog}(\emptyset) = p'$.
+    Similarly, using $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\histp, j, {\ileadstog[j]}(\histp))}$, we obtain that $\allleadsto$ conforms to the relation in $C$.
+  \end{example}
+
+  \begin{remark}
+    Intuition (to be explored) is that when $C^\wsub \cap \Theta$ has the covering property, then the obs-compatible relations are easily deduced from the set (something like, just consider compatibility point per point, one singleton observation at a time).
+Covering is what is used above, something like $\exists i, \hist, \histp$ such that $\forall \hist^{\prime\prime}: [\forall j \neq i: \set{(\hist, i, .), (\histp, j, .)} \in C^\wsub \cap \Theta] \land [\exists j \neq i \suchthat \set{(\hist', i, .), (\hist^{\prime\prime}, j, .)} \in C^\wsub \cap \Theta]$.
+  \end{remark}
+
+  \subsection{Compatibility of claim properties}
+  \begin{theorem}
+    \label{th:hsif}
+    For all exposure protocols, there exists a claim that holds and is strongly informative beyond counting and falsifiable iff $\exists i \suchthat P_i \neq \emptyset$.
+  \end{theorem}
+  \begin{proof}
+    Define $C = \set{\allleadsto}$.
+  \end{proof}
+  \begin{theorem}
+    \label{th:hif}
+    For all exposure protocols, there exists a claim that holds and is informative beyond counting and falsifiable.
+  \end{theorem}
+  \begin{proof}
+    Define $C = \set{\allleadsto}$.
+  \end{proof}
+  \begin{theorem}
+    \label{th:asif}
+    For all exposure protocols, there exists a claim that is anonymous, strongly informative beyond counting and falsifiable.
+  \end{theorem}
+  \begin{proof}
+    Define the claim as $\forall i \in I, \hist \in \allhists: \hist \ileadstog \phi$.
+  \end{proof}
+
+  \begin{theorem}
+    \label{th:ha}
+    For all exposure protocols, there exists a claim that holds and is anonymous.
+  \end{theorem}
+  \begin{proof}
+    Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
+  \end{proof}
+
+  \begin{theorem}
+    \label{th:HAinformativeness}
+    Given any $Q \wsub P \cup \set{\emptyset}$,
+    the following two conditions on $\allleadsto$ are equivalent:
+    there exists a claim that holds and is anonymous and satisfies 
+    $\exists j \in I \suchthat \pi(C)(j) \ssub Q$;
+    and 
+    $\set{P_i, i \in I} \ssub Q$.
+  \end{theorem}
+  \begin{proof}
+    Consider any claim $C$ that holds and is anonymous, pick any $j \in I$, and let us show that $\set{P_i, i \in I} \wsub \pi(C)(j)$.
+    Pick any $p \in \set{P_i, i \in I}$. 
+    Pick any $i \in I$ such that $\pi({\allleadsto})(i) = p$.
+    Define $\sigma$ as the permutation exchanging $i$ and $j$.
+    As $C$ holds, it contains $\allleadsto$, and by anonymity, it contains ${\allleadsto} \circ \sigma$.
+Observing that $\pi({\allleadsto} \circ \sigma)(j) = \pi({\allleadsto})(i) = p$, we obtain $p \in \pi(C)(j)$.
+
+    It follows that for any claim $C$ that holds and is anonymous, if $\exists j \in I \suchthat \pi(C)(j) \ssub Q$ then $\set{P_i, i \in I} \wsub \pi(C)(j) \ssub Q$ thus $\set{P_i, i \in I} \ssub Q$.
+
+    Turning to the other direction, if $\set{P_i, i \in I} \ssub Q$, then pick any $p \in Q \setminus \set{P_i, i \in I}$; the claim $\forall i \in I: P_i \neq p$ satisfies the desired properties.
+  \end{proof}
+
+  \begin{theorem}
+    \label{th:infoBeyonCKO}
+    There exists a claim that holds and is anonymous and informative beyond counting iff $\set{P_i, i \in I} \neq P \cup \set{\emptyset}$.
+  \end{theorem}
+  \begin{proof}
+    From \cref{th:HAinformativeness} with $Q = P \cup \set{\emptyset}$, we have that 
+    there exists a claim that holds and is anonymous and satisfies 
+    $\exists j \in I \suchthat \pi(C)(j) \ssub P \cup \set{\emptyset}$ iff
+    $\set{P_i, i \in I} \ssub P \cup \set{\emptyset}$.
+  \end{proof}
+
+  \begin{theorem}
+    \label{th:strinfoBeyonCKO}
+    There exists a claim that holds and is anonymous and strongly informative beyond counting iff $\set{P_i, i \in I} \ssub P$.
+  \end{theorem}
+  \begin{proof}
+    From \cref{th:HAinformativeness} with $Q = P$, we have that 
+    there exists a claim that holds and is anonymous and satisfies 
+    $\exists j \in I \suchthat \pi(C)(j) \ssub P$ iff
+    $\set{P_i, i \in I} \ssub P$.
+  \end{proof}
+
+  \begin{theorem}
+    \label{th:infoBeyonCKOext}
+    Given $Q = \set{\phi, ¬\phi}$,
+    the following two conditions on $\allleadsto$ are equivalent:
+    there exists a claim that holds and is anonymous and satisfies 
+    $\exists j \in I \suchthat \pi(C)(j) \ssub Q$;
+    and 
+    $\set{P_i, i \in I} \ssub Q$.
+  \end{theorem}
+  \begin{proof}
+    From \cref{th:HAinformativeness} with $Q = \set{\phi, ¬\phi}$, we have that 
+    there exists a claim that holds and is anonymous and satisfies 
+    $\exists j \in I \suchthat \pi(C)(j) \ssub \set{\phi, ¬\phi}$ iff
+    $\set{P_i, i \in I} \ssub \set{\phi, ¬\phi}$.
+  \end{proof}
+
+  \begin{theorem}
+    \label{th:suffIndic}
+    Assume that for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\allleadsto}(\hist, i_1) \neq {\allleadsto}(\hist, i_2)$.
+    Then, there exists a claim that holds and is anonymous and indicative.
+  \end{theorem}
+  \begin{proof}
+    Define $p = P_{i_1}$.
+    Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
+    The claim is indicative for $i = i_1$ and $\theta = \set{(\hist, i_1, {\allleadsto}(\hist, i_1)) \suchthat \hist \in H}$ for the following reason.
+    The attitudes in $C$ compatible with $\theta$ are $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}})(i_1) = p$.
+  \end{proof}
+  \begin{corollary}
+    \label{th:suffIndicDec}
+    Assume that for some $p \in P$, we have $\exists i \in I \suchthat P_i = p$ and $\forall i_2 \suchthat P_{i_2} \neq p$ we have that $\exists A \in \finite(\allargs) \suchthat \forall i \in I \suchthat P_i \neq p, \exists a \in A \suchthat {\ileadstost}(a) \in P \setminus \set{p}$, then there exists a claim that holds and is anonymous and indicative.
+  \end{corollary}
+  \begin{proof}
+    We know that $i_1$ has some decisive argument $a_1$ in favor of $p$.
+    Assume (wlog) that $A = \set{2, …, \card{A} + 1}$.
+    Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{A} + 1}$, $\hist_i = (\hist_{i - 1}, a_1, i)$.
+    Define $H = \set{\hist_i \suchthat i \in \intvl{2, \card{A} + 1}}$.
+    Apply \cref{th:suffIndic}.
+  \end{proof}
 
@@
 \end{proof}
-
-\subsection{More examples}
-\begin{example}[Partly falsifiable is still unfalsifiable]
-  \label{ex:partlyU}
-  Given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
-  the claim
-  $C = \set{{\allleadstog} \in \allleadstos \suchthat \hist \ileadstog[j] \phi \land \forall i \in I: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ is unfalsifiable but not strongly unfalsifiable.
-
-  Define
-  $C_1 = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ and
-  $C_2 = \set{{\allleadstog} \in \allleadstos \suchthat \hist \ileadstog[j] \phi}$,
-  so that $C = C_1 \cap C_2$.
-  Observe that $C_1$ is the claim of \cref{ex:disj} and $C_2$ is falsifiable and coverable. 
-  \Cref{th:strongUToStrictU} concludes.
-\end{example}
-
-\begin{example}[Partly again]
-  Considering again \cref{ex:partlyU},
-  given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
-  $C = \set{{\allleadstog} \suchthat \hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ is not falsifiable but \cref{th:veryunfals} is not applicable.
-  Observe that
-  $C^\subseteq = \set{R \in I × \allhists × P \suchthat [(j, \hist) \in R^{-1}(P) \implies (j, \hist, \phi) \in R] \land \forall i: [(i, (\ar)) \in R^{-1}(P) \land (i, (\ar')) \in R^{-1}(P)] \implies [(i, (\ar), \phi) \in R \land (i, (\ar'), \phi) \in R]}$ and
-  $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat (j, \hist) \in \theta^{-1}(P) \implies (j, \hist, \phi) \in \theta}$.
-  % Pick any $\allleadstog$ satisfying $\hist \ileadstog[j] \phi$ and $\exists i \suchthat (\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
-  % The definition of non-falsifiability applies: pick any $\theta \subseteq {\allleadstog}$, we have $\theta \in C^\subseteq$ as $(j, \hist, \phi)$ is compatible with $\theta$ and the other condition excludes nothing in $\Theta$.
-  % We can apply Thm 4 similarly: given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
-  % We should be able to apply a corollary similarly.
-  The relations obs-compatible with $C^\subseteq \cap \Theta$ are those satisfying $\hist \ileadstog[j] \phi$.
-  We conclude that $C$ is not falsifiable as $C$ is smaller than that set.
-\end{example}
-
-\begin{example}[Come back]
-  In \cref{ex:allParticular} we considered a given $\ar$ and $\phi$ and defined the falsifiable claim $C = \set{{\allleadstog} \suchthat \forall i: \ar \ileadstostg \phi}$.
-  Observe that $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat \forall \hist \suchthat \ar \in \histend: \theta(i, \hist) = \emptyset \lor \theta(i, \hist) = \phi}$.
-  The relations obs-compatible with $C^\subseteq \cap \Theta$ are exactly those in $C$.
-
-  \Cref{ex:existsParticular} assumed an infinite $I$, in which case the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
-  Observe that $C^\subseteq \cap \Theta = \set{\theta \in \Theta \suchthat \exists i \suchthat \forall \hist \suchthat \ar \in \histend: \theta(i, \hist) = \emptyset \lor \theta(i, \hist) = \phi}$.
-  Any relation ${\allleadstog}$ is obs-compatible with that set as $C^\subseteq \cap \Theta = \Theta$: given any $\theta \in \Theta$, there is an $i$ such that $\forall \hist: \theta(i, \hist) = \emptyset$ as $\theta$ must have a finite support.
-\end{example}
-
-\begin{example}
-  \label{ex:cardPart}
-  Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhists$ with $\hist$ and $\histp$ non prefix related.
-  The claim $\psi = (\hist \ileadstog p \lor \hist \ileadstog p') \land (\histp \ileadstog p \lor \histp \ileadstog p') \land (\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p)$ is falsifiable.
-
-  Given $q, q' \in P$, let ${\allleadstog^{q, q'}}$ be defined as $\hist \ileadstog^{q, q'} q$, $\histp \ileadstog^{q, q'} q'$ and $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j]^{q, q'} p$.
-  Note that $C_\psi = \set{{\allleadstog^{p, p}}, {\allleadstog^{p, p'}}, {\allleadstog^{p', p}}, {\allleadstog^{p', p'}}}$.
-
-  Then, $C_\psi^\wsub \cap \Theta =
-    \set{\theta \in \Theta \suchthat \theta(\hist, i) \in \set{\emptyset, p, p'} \land \theta(\histp, i) \in \set{\emptyset, p, p'} \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
-  % and we see that $C_\psi^\wsub \cap \Theta =
-  % \set{\theta \in \Theta \suchthat [\theta(\hist, i) = \theta(\histp, i) = \emptyset \lor \theta(\hist, i) \in \set{p, p'} \lor \theta(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
-
-  Any obs-compatible relation has to satisfy $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p$.
-  It also must satisfy ${\allleadstog}(\hist, i) \in \set{p, p'}$, for otherwise, with $\theta = \set{(\hist, i, {\allleadstog}(\hist, i))}$, we get $({\allleadstog} \cap \theta) \notin C_\psi^\wsub \cap \Theta$.
-  Similarly, it must satisfy ${\allleadstog}(\histp, i) \in \set{p, p'}$.
-  % are $\set{{\allleadstog} \in \allleadstos \suchthat [{\allleadstog}(\hist, i) \in \set{p, p'} \lor {\allleadstog}(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p}$, which, given $p \neq p^{\prime\prime} \neq p'$, contains ${\allleadstog^{p, p^{\prime\prime}}}$, contrary to $C_\psi$.
-\end{example}
-
-\begin{example}
-  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p, p' \in P$.
-  The claim $C = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$ is falsifiable.
-
-  We have $C^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p) \land (\theta((\ar_2), i) = \emptyset \lor \theta((\ar_2), i) = p')}$.
-  The obs-compatible relations are $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$.
-\end{example}
-\begin{example}
-  \label{ex:consti2}
-  Assume that $\card{I} ≥ 2$.
-  Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
-  We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
-  Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$.
-Assume that for some $\hist, i$, $\hist \ileadstog p$.
-Then, pick any $j \neq i$, and observe that by obs-compatibility, for any $\hist'$, $\hist' \ileadstog[j] p$.
-  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and any $(\hist^{\prime\prime}, j)$).
-Conclude that $\allleadstog$ is constant to $p$.
-  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
-\end{example}
-\begin{example}
-  \label{ex:consti1}
-  Assume that $\card{I} = 1$.
-  Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
-  We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
-  Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$.
-Assume that for some $\hist, i$, $\hist \ileadstog p$.
-Observe that by obs-compatibility, $\emptyset \ileadstog p$.
-  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and $(\emptyset, i)$).
-Conclude that $\allleadstog$ is constant to $p$.
-  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
-\end{example}
-\begin{example}
-  \label{ex:constwout0}
-  Consider any $p, p' \in P$ and the claim $C = \set{{\allleadstog} \suchthat (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p) \lor (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p')}$.
-That claim is falsifiable iff $\card I ≥ 2$ or $\card \allargs = 1$.
-The proof if so is similar to \cref{ex:consti2}; otherwise, pick any $\ar \in \allargs$ and note that any relation satisfying $(a.*) \ileadstog p$ and $\forall b \neq a: (b.*) \ileadstog p'$ is obs-compatible with $C^\wsub \cap \Theta$ but is not in $C$.
-\end{example}
-\begin{example}
-  \label{ex:unfor}
-  Consider any $i$, $\hist, \histp \in \allhists$, $p, p' \in P$ where $\hist$ and $\histp$ are not prefix related.
-  The claim $C = \set{{\allleadstog} \suchthat \hist \ileadstog p \lor \histp \ileadstog p'}$ is unfalsifiable.
-
-  We have $C^\wsub \cap \Theta = \set{\theta \suchthat (\theta(\hist, i) = \emptyset \lor \theta(\hist, i) = p) \lor (\theta(\histp, i) = \emptyset \lor \theta(\histp, i) = p')}$.
-  Observe that any $\theta \in \Theta$ satisfy $\theta(\hist, i) = \emptyset \lor \theta(\histp, i) = \emptyset$, thus, $C^\wsub \cap \Theta = \Theta$.
-  It follows that the obs-compatible relations are $\allleadstos$, which is bigger than $C$.
-\end{example}
-\begin{example}
-  Consider any $i$, $\ar \neq \ar' \in \allargs$, $p, p' \in P$.
-  The claim $C = \set{{\allleadstog} \suchthat (\ar) \ileadstog p \lor (\ar') \ileadstog p'}$ is unfalsifiable (per \cref{ex:unfor}).
-
-  Now consider the smaller claim $C' = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$ (thus $C' \ssub C$).
-  It yields a smaller set ${C'}^\wsub \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p)}$.
-  The obs-compatible relations are the smaller set $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$.
-  Thus, $C'$ is falsifiable.
-
-  Note that any claim $C^{\prime\prime}$ bigger than $C$ is unfalsifiable as well, unless trivial:
-  from $C \wsub C^{\prime\prime}$, we deduce $\Theta = C^\wsub \cap \Theta \wsub {C^{\prime\prime}}^\wsub \cap \Theta$, thus ${C^{\prime\prime}}^\wsub \cap \Theta = \Theta$ and the obs-compatible relations are $\allleadstos$, which equals $C^{\prime\prime}$ only if $C^{\prime\prime}$ is trivial.
-
-  Now consider the alternative smaller claim of \cref{ex:consti2}, $C^{(2)} = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$ (thus $C^{(2)} \ssub C$).
-  It yields a smaller set ${C^{(2)}}^\wsub \cap \Theta$.
-\end{example}
-\begin{example}
-  \label{ex:for}
-  Consider any $i$ and $p, p' \in P$.
-  The claim $C = \set{{\allleadstog} \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \hist \ileadstog p) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \hist \ileadstog p')}$, namely, all paths of even lengths lead $i$ to $p$ OR all paths of odd lengths or empty lead $i$ to $p'$, is falsifiable.
-
-  Note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \theta(\hist) \in \set{\emptyset, p}) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \theta(\hist) \in \set{\emptyset, p'})}$.
-  Consider any obs-compatible ${\allleadstog}$.
-  Assume that $\exists \hist \suchthat \card{\hist} \in 2\N \land \hist \nileadstog p$.
-  Pick $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\hist, i, {\ileadstog}(\hist))}$.
-We have $({\allleadstog} \cap \theta) \in C^\wsub \cap \Theta$, and ${\allleadstog} \cap \theta = \theta$, and from $\theta \in C^\wsub \cap \Theta$ we obtain ${\ileadstog}(\emptyset) = p'$.
-  Similarly, using $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\histp, j, {\ileadstog[j]}(\histp))}$, we obtain that $\allleadsto$ conforms to the relation in $C$.
-\end{example}
-
-\begin{remark}
-  Intuition (to be explored) is that when $C^\wsub \cap \Theta$ has the covering property, then the obs-compatible relations are easily deduced from the set (something like, just consider compatibility point per point, one singleton observation at a time).
-Covering is what is used above, something like $\exists i, \hist, \histp$ such that $\forall \hist^{\prime\prime}: [\forall j \neq i: \set{(\hist, i, .), (\histp, j, .)} \in C^\wsub \cap \Theta] \land [\exists j \neq i \suchthat \set{(\hist', i, .), (\hist^{\prime\prime}, j, .)} \in C^\wsub \cap \Theta]$.
-\end{remark}
 
@@
   Actually I need to be able to merge two relations that agree on everything but some part of the tree, in such a way that all paths crossing the boundary must be in $C$, but not the merge.
-  TODO caract with singleton $I$.
+  TOo be done: caract with singleton $I$.
   % Given a claim $C$, define $S = C^\wsub \cap \Theta$.
@@
 \end{conjecture}
-TODO extend this so as to cover eg $C$ containing $f_1$ and $f_2$ constant functions as in example; but not covering when the domain is not suitable!
+Consider: extend this so as to cover eg $C$ containing $f_1$ and $f_2$ constant functions as in example; but not covering when the domain is not suitable!
 Use proof similar to \cref{ex:for}, getting started with observing that any obs-compatible $\allleadstog$ failing every element but one of $C$ at least at one point must then satisfy the last element of $C$ at some point (?).
@@
 
-TODO investigate claims that are non falsifiable but with $C^\wsub \cap \Theta \neq \Theta$.
+Consider: investigate claims that are non falsifiable but with $C^\wsub \cap \Theta \neq \Theta$.
 Then exhibit a claim such that a smaller one is not the same status and a bigger one is not the same status.

### 2024-01-15 simple.tex
C^HA

@@
 
+  Define the claim $C^\text{HA} = \set{{\allleadsto} \circ \sigma \suchthat \sigma: I \Leftrightarrow I}$, or equivalently, $C^\text{HA} = \set{{\allleadstog} \in \allleadstos \suchthat \forall f \in P^{\allhists}: \card({\allleadstoginv}(f)) = \card({\allleadstoinv}(f))}$.
+  Under anonymity, requesting that a claim holds is the same as requesting that it includes $C^\text{HA}$.
+  \begin{theorem}
+    \label{th:claim_ha}
+    A claim holds and is anonymous iff it includes $C^\text{HA}$ and is anonymous.
+    In particular, $C^\text{HA}$ holds and is anonymous.
+  \end{theorem}
+\begin{remark}
+  Define $C^\text{A} = \set{{\allleadstog} \in \allleadstos \suchthat {\allleadstog}(I) \wsub {\allleadsto}(I)}$.
+Observe that $C^\text{A}$ is anonymous, that $C^\text{HA} \wsub C^\text{A}$, and that $C^\text{HA} \neq C^\text{A}$ iff $\forall i, j \in I: {\ileadsto} \neq {\ileadsto[j]}$.
+\end{remark}
+
   \begin{theorem}
@@
     Define $p = P_{i_1}$.
-    Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
+    Consider any claim $C$ such that $C^\text{HA} \wsub C \wsub C^\text{A}$ and $C$ is anonymous.
+    % Define the claim $C$ as $\set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}}$ (or as anything included in it that includes $C^\text{HA}$ and is anonymous).
     The claim is indicative for $i = i_1$ and $\theta = \set{(\hist, i_1, {\allleadsto}(\hist, i_1)) \suchthat \hist \in H}$ for the following reason.
@@
     Apply \cref{th:suffIndic}.
+  \end{proof}
+
+\begin{conjecture}
+  The converse of \cref{th:suffIndic} holds.
+\end{conjecture}
+\begin{proof}
+  HA requires that the claim includes at least $C^\text{HA}$.
+  Indicativenes requires a $\theta$ that keeps a single type $i_1$ and rejects all $i_2$ (those with a deliberated judgment different from $i_1$).
+  Can we build a suitable $H$ with that $\theta$?
+  The question is: can we have $\theta$ about two individuals but still single out a single type?
+  Yes: claim is that all individuals reason in the same way about a given $\hist$.
+  In such a case, the observations about $i_2$, $i_3$ permit to know that the world is such that my observations about $i_1$ (if any) permit to single it out. 
+  In such a case, I conjecture that as the claim holds, adding those observations about $i_2$, $i_3$, we obtain a set of possible worlds which contain the real one; out of this we can build $H$ using the observations in $\theta$.
+  In other words, from $\theta$, consider only the observations about $i_1$ and define $H$ using those.
+Prove that this singles out $i_1$, from the fact that the world conforms to the remaining observations (about $i_2$, $i_3$) in $\theta$.
 \end{proof}

### 2024-01-15 simple.tex
Rm complex HAIndicative caract draft: it’s much simpler than that

@@
 
-\begin{conjecture}
-  The converse of \cref{th:suffIndic} holds.
-\end{conjecture}
-\begin{proof}
-  HA requires that the claim includes at least $C^\text{HA}$.
-  Indicativenes requires a $\theta$ that keeps a single type $i_1$ and rejects all $i_2$ (those with a deliberated judgment different from $i_1$).
-  Can we build a suitable $H$ with that $\theta$?
-  The question is: can we have $\theta$ about two individuals but still single out a single type?
-  Yes: claim is that all individuals reason in the same way about a given $\hist$.
-  In such a case, the observations about $i_2$, $i_3$ permit to know that the world is such that my observations about $i_1$ (if any) permit to single it out. 
-  In such a case, I conjecture that as the claim holds, adding those observations about $i_2$, $i_3$, we obtain a set of possible worlds which contain the real one; out of this we can build $H$ using the observations in $\theta$.
-  In other words, from $\theta$, consider only the observations about $i_1$ and define $H$ using those.
-Prove that this singles out $i_1$, from the fact that the world conforms to the remaining observations (about $i_2$, $i_3$) in $\theta$.
-\end{proof}
-
   \section{Theories of deliberated choice}

### 2024-01-15 simple.tex
2 sit for cond HAI

@@
     \label{th:suffIndic}
-    Assume that for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\allleadsto}(\hist, i_1) \neq {\allleadsto}(\hist, i_2)$.
-    Then, there exists a claim that holds and is anonymous and indicative.
-  \end{theorem}
-  \begin{proof}
-    Define $p = P_{i_1}$.
+    The following two conditions on $\allleadsto$ are equivalent:
+    \begin{enumerate}
+      \item \label{it:condHAI} for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\allleadsto}(\hist, i_1) \neq {\allleadsto}(\hist, i_2)$;
+      \item \label{it:HAI} there exists a claim that holds and is anonymous and indicative.
+    \end{enumerate}
+  \end{theorem}
+  \begin{proof}
+    For \cref{it:condHAI} $\implies$ \cref{it:HAI},
+    define $p = P_{i_1}$.
     Consider any claim $C$ such that $C^\text{HA} \wsub C \wsub C^\text{A}$ and $C$ is anonymous.
@@
     The attitudes in $C$ compatible with $\theta$ are $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}})(i_1) = p$.
+
+    For \cref{it:HAI} $\implies$ \cref{it:condHAI},
+    pick an indicative claim $C$ and consider $i \in I$ and $\theta \in \Theta \cap (\allhists × \set{i} × P) \cap C^\wsub$ such that $\pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
+    Define $H = \theta^{-1}(i, P)$.
   \end{proof}
@@
   \end{proof}
+
+  \begin{remark}
+    If there are only two types each with a DJ not empty, then the condition of \cref{it:condHAI} is satisfied.
+More formally, if ${\allleadsto}(I) = \set{{\ileadsto[i_1]}, {\ileadsto[i_2]}}$ and $\emptyset \notin \pi({\allleadsto})(I)$, then \cref{it:condHAI} is satisfied: define $\ar_1, \ar_2$ as some decisive arguments for $i_1, i_2$, respectively, and define $H = \set{(\ar_1, \ar_2)}$.
+  \end{remark}
+
+\begin{remark}
+  Given $p \in P$, define $I_p = \set{i \in I \suchthat \pi(i) = p}$.
+  If $I \setminus I_p$ all have $\ar$ as a decisive argument, then \cref{it:condHAI} is satisfied: if $I_p \neq \emptyset$, pick $i \in I_p$, let $\ar'$ be a decisive argument for $i$, and define $H = \set{(\ar, \ar')}$; otherwise, define $H = \set{(\ar)}$.
+\end{remark}
 

### 2024-01-15 simple.tex
Rm one sit for cond HAI, implied by the other one.

@@
 \begin{remark}
-    If there are only two types each with a DJ not empty, then the condition of \cref{it:condHAI} is satisfied.
-More formally, if ${\allleadsto}(I) = \set{{\ileadsto[i_1]}, {\ileadsto[i_2]}}$ and $\emptyset \notin \pi({\allleadsto})(I)$, then \cref{it:condHAI} is satisfied: define $\ar_1, \ar_2$ as some decisive arguments for $i_1, i_2$, respectively, and define $H = \set{(\ar_1, \ar_2)}$.
-  \end{remark}
-
-\begin{remark}
   Given $p \in P$, define $I_p = \set{i \in I \suchthat \pi(i) = p}$.

### 2024-01-18 simple.tex
Caract HAI seems to work

@@
 Define $\allhists = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence.
-A generic element of $\allhists$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path.
+A generic element of $\allhists$ (a possibly empty finite sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path.
 Its length is denoted by $\card{\hist} \in \N$ and its elements, $\hist(k)$ or $\hist_k$.
@@
     The following two conditions on $\allleadsto$ are equivalent:
-    \begin{enumerate}
-      \item \label{it:condHAI} for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\allleadsto}(\hist, i_1) \neq {\allleadsto}(\hist, i_2)$;
+    \begin{enumerate}[label=T\ref{th:suffIndic}-{\arabic*}]
+      \item \label{it:condHAI} for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\ileadsto[i_1]}(\hist) \neq {\ileadsto[i_2]}(\hist)$;
       \item \label{it:HAI} there exists a claim that holds and is anonymous and indicative.
@@
   \begin{proof}
-    For \cref{it:condHAI} $\implies$ \cref{it:HAI},
+    For \ref{it:condHAI} $\implies$ \ref{it:HAI},
     define $p = P_{i_1}$.
@@
     % Define the claim $C$ as $\set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}}$ (or as anything included in it that includes $C^\text{HA}$ and is anonymous).
-    The claim is indicative for $i = i_1$ and $\theta = \set{(\hist, i_1, {\allleadsto}(\hist, i_1)) \suchthat \hist \in H}$ for the following reason.
+    The claim is indicative for $i = i_1$ and $\theta = \set{(\hist, i_1, {\ileadsto[i_1]}(\hist)) \suchthat \hist \in H}$ for the following reason.
     The attitudes in $C$ compatible with $\theta$ are $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}})(i_1) = p$.
@@
   \end{proof}
-
-\begin{remark}
-  Given $p \in P$, define $I_p = \set{i \in I \suchthat \pi(i) = p}$.
-  If $I \setminus I_p$ all have $\ar$ as a decisive argument, then \cref{it:condHAI} is satisfied: if $I_p \neq \emptyset$, pick $i \in I_p$, let $\ar'$ be a decisive argument for $i$, and define $H = \set{(\ar, \ar')}$; otherwise, define $H = \set{(\ar)}$.
+\begin{example}
+  Consider $I_p$ such that $\forall i \in I_p$: $i$ constantly says $p$.
+  Consider $J = I \setminus I_p$ whose DJ is $p' \neq p$, and such that each $j \in J$ has a single decisive argument $\ar_j$ for $p'$, and when $\ar_j$ is not in $\hist$, $\hist \ileadsto[j] p$.
+  Then, the condition is not satisfied.
+\end{example}
+\begin{conjecture}
+  \label{th:caractNotIndicWrong}
+  The following two conditions on $\allleadsto$ are equivalent:
+  \begin{enumerate}[label=T\ref{th:caractNotIndic}-{\arabic*}]
+    \item \label{it:NotHAIWrong} there exists no claim that holds and is anonymous and indicative;
+    \item \label{it:condNotHAIWrong} either all individuals have an empty deliberated preference, or all paths are such that at least two individuals with different deliberated judgements behave identically on the whole path (formally: either $\pi(I) = \emptyset$ or $\forall \hist \in \allhists, \exists i_1, i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$);
+    \item \label{it:condNotHAIInfWrong} [To be adjusted for the zero case] all paths are such that infinitely many individuals with different deliberated judgements behave identically on the whole path (formally: $\forall \hist \in \allhists, \exists I_1 \wsub I, i_2 \in I \suchthat \card{I_1} = \infty \land \forall i_1 \in I_1: \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$).
+  \end{enumerate}
+
+  This is WRONG because could have $i$ that says $\phi$ on $H$ and has $\phi$ as DJ, and $i$ can be isolated (nobody with DJ different than $\phi$ says $\phi$ on $H$) but still some $i_1, i_2$ with different DJ behave identically on $H$, say they both say $¬\phi$ on $H$.
+\end{conjecture}
+\begin{proof}
+  Let us show that NOT \ref{it:condNotHAIWrong} implies \ref{it:condHAI}.
+  Consider: at least one individual $i$ has a non-empty DP, and some path is such that
+  $\forall i_1, i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2): \exists \histp \wsub \hist \suchthat {\ileadsto[i_1]}(\histp) \neq {\ileadsto[i_2]}(\histp)$.
+  Define $H = \set{\histp \wsub \hist}$ and $i_1 = i$.
+
+  Conversely, \ref{it:condHAI} implies NOT \ref{it:condNotHAIWrong}.
+  Consider: for some $H \in \finite(\incr(\allhists))$ and $i \in I \suchthat P_{i} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_i$ that $\exists \histp \in H \suchthat {\ileadsto}(\histp) \neq {\ileadsto[i_2]}(\histp)$.
+  Define $\hist$ as the maximal path (in cardinal) in $H$.
+  Consider any $i_1, i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2)$.
+  Remains to show that for some $\histp \wsub \hist$: ${\ileadsto[i_1]}(\histp) \neq {\ileadsto[i_2]}(\histp)$.
+  Assume, on the contrary, that for all $\histp \wsub \hist$: ${\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$.
+\end{proof}
+\begin{conjecture}
+  \label{th:caractNotIndic}
+  The following conditions on $\allleadsto$ are equivalent:
+  \begin{enumerate}[label=T\ref{th:caractNotIndic}-{\arabic*}]
+    \item \label{it:NotHAI} there exists no claim that holds and is anonymous and indicative;
+    \item \label{it:condNotHAI} all paths are such that for all $i_1$ having a DJ, there is an $i_2$ with another deliberated judgement that behaves identically on the whole path (formally: $\forall \hist \in \allhists, i_1 \in I \suchthat \pi(i_1) \neq \emptyset: \exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$);
+    % \item \label{it:condNotHAIAll} either all individuals have an empty deliberated preference, or all paths are such that for all $i_1$, there is an $i_2$ with another deliberated judgement that behaves identically on the whole path (formally: either $\pi(I) = \emptyset$ or $\forall \hist \in \allhists, i_1 \in I: \exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$).
+    \item \label{it:condNotHAIInf} all paths are such that for all $i_1$, either at least one individual without a DJ, or infinitely many individuals $i_2$ with another deliberated judgement than $i_1$, behave identically to $i_1$ on the whole path (formally: $\forall \hist \in \allhists, i_1 \in I: [\exists i_2 \in I \suchthat \pi(i_2) = \emptyset \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)] \lor [\card(\set{i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)}) = \infty]$)
+  \end{enumerate}
+\end{conjecture}
+\begin{proof}
+  Let us show that NOT \ref{it:condNotHAI} implies \ref{it:condHAI}.
+  Consider: some individual $i$ and some path $\hist$ are such that $\pi(i) \neq \emptyset$ and
+  $\forall i_2 \in I \suchthat \pi(i) \neq \pi(i_2): \exists \histp \wsub \hist \suchthat {\ileadsto[i]}(\histp) \neq {\ileadsto[i_2]}(\histp)$.
+  Define $H = \set{\histp \wsub \hist}$ and $i_1 = i$.
+
+  Conversely, \ref{it:condHAI} implies NOT \ref{it:condNotHAI}.
+  Consider: for some $H \in \finite(\incr(\allhists))$ and $i \in I \suchthat P_{i} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_i$ that $\exists \histp \in H \suchthat {\ileadsto}(\histp) \neq {\ileadsto[i_2]}(\histp)$.
+  Define $\hist$ as the maximal path (in cardinal) in $H$.
+
+  % Let us show that \ref{it:condNotHAI} implies \ref{it:condNotHAIAll}.
+  % Assume that at least one individual $i$ has a non-empty deliberated preference (otherwise, the first disjunct of \ref{it:condNotHAIAll} holds).
+  % Consider any path $\hist$ and $i_1$ with $\pi(i_1) = \emptyset$.
+  % Apply \ref{it:condNotHAI} on $i$, obtaining that $\exists i_2 \in I \suchthat \emptyset \neq \pi(i) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$.
+  % NOPE, that’s wrong.
+
+  TODO prove that \ref{it:condNotHAI} implies \ref{it:condNotHAIInf}.
+\end{proof}
+\begin{example}
+  I believe that we can’t remove the $\pi(i_1) \neq \emptyset$ in \ref{it:condNotHAI}.
+  We could have \ref{it:condNotHAI} satisfied, but not the part with $\pi(i_1) \neq \emptyset$.
+  Consider $i_1$ with empty DJ on some path has only individuals with identical behavior on the path that have an empty DJ (though for normal $i$’s, the condition is satisfied, thus there are collisions, meaning some individuals with different DJ having identical behavior on the path).
+  TODO check.
+\end{example}
+\begin{remark}
+  Given $J \wsub I$, say that a set of paths discriminates $J$ iff some function associating each path to an answer is compatible with some $j \in J$ (meaning that $f \wsub {\ileadsto[j]}$) and is compatible with no $i \notin J$.
+  The condition says that there must be some $p$ and some increasing set of paths $H$ such that $H$ discriminates $J = \pi^{-1}(p)$.
+\end{remark}
+\begin{remark}
+  For failing the condition, I need an infinity of $j$’s (and at least one $i$) who agree on any branch of the history tree? (Meaning relations $\ileadsto[j]$, we don’t care about individuals.)
+  No: on any finite branch in the tree, I need that remains one $j$ and one $i$ such that infinite prolongation of the branch will never discriminate them.
+
+  That’s it: any finite branch of the tree (meaning, any $H$) is compatible with two DJs, meaning at least one relation having a given DJ and at least one relation having another DJ.
+
+  That means (still mandating that everybody has a DJ), that the condition mandates that any finite branch of the tree be compatible with infinitely many different relations having one DJ and at least one having another DJ.
+(Otherwise when there’s only finitely many we can just exclude them by testing all decisive arguments.)
 \end{remark}

### 2024-01-22 simple.tex
Caract no HAI

@@
     \item \label{it:condNotHAI} all paths are such that for all $i_1$ having a DJ, there is an $i_2$ with another deliberated judgement that behaves identically on the whole path (formally: $\forall \hist \in \allhists, i_1 \in I \suchthat \pi(i_1) \neq \emptyset: \exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$);
-    % \item \label{it:condNotHAIAll} either all individuals have an empty deliberated preference, or all paths are such that for all $i_1$, there is an $i_2$ with another deliberated judgement that behaves identically on the whole path (formally: either $\pi(I) = \emptyset$ or $\forall \hist \in \allhists, i_1 \in I: \exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$).
     \item \label{it:condNotHAIInf} all paths are such that for all $i_1$, either at least one individual without a DJ, or infinitely many individuals $i_2$ with another deliberated judgement than $i_1$, behave identically to $i_1$ on the whole path (formally: $\forall \hist \in \allhists, i_1 \in I: [\exists i_2 \in I \suchthat \pi(i_2) = \emptyset \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)] \lor [\card(\set{i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)}) = \infty]$)
@@
 
-  % Let us show that \ref{it:condNotHAI} implies \ref{it:condNotHAIAll}.
-  % Assume that at least one individual $i$ has a non-empty deliberated preference (otherwise, the first disjunct of \ref{it:condNotHAIAll} holds).
-  % Consider any path $\hist$ and $i_1$ with $\pi(i_1) = \emptyset$.
-  % Apply \ref{it:condNotHAI} on $i$, obtaining that $\exists i_2 \in I \suchthat \emptyset \neq \pi(i) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$.
-  % NOPE, that’s wrong.
-
-  TODO prove that \ref{it:condNotHAI} implies \ref{it:condNotHAIInf}.
-\end{proof}
-\begin{example}
-  I believe that we can’t remove the $\pi(i_1) \neq \emptyset$ in \ref{it:condNotHAI}.
+  Let us now prove that \ref{it:condNotHAI} implies \ref{it:condNotHAIInf}.
+  Consider any $\hist \in \allhists, i_1 \in I$.
+  Define $J = \set{i_2 \in I \suchthat \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)}$.
+  Assume that $\forall i_2 \in J: \pi(i_2) \neq \emptyset$ (otherwise, the first disjunct of \ref{it:condNotHAIInf} holds), and let us show that $\card\set{i_2 \in J \suchthat \pi(i_1) \neq \pi(i_2)} = \infty$.
+  From $\forall i_2 \in J: \pi(i_2) \neq \emptyset$, we obtain $\pi(i_1) \neq \emptyset$, thus, $\exists a_{i_1} \in \allargs \suchthat a_{i_1} \ileadstost[i_1] \pi(i_1)$.
+  Apply \ref{it:condNotHAI} to obtain some $i_2 \in J$ such that $\pi(i_1) \neq \pi(i_2)$.
+  Also, by our assumption, $\pi(i_2) \neq \emptyset$, thus, $\exists a_{i_2} \in \allargs \suchthat a_{i_2} \ileadstost[i_2] \pi(i_2)$.
+  Consider the path $\histp = (\hist, a_{i_1}, a_{i_2})$. We have $\histp \ileadsto[i_1] \pi(i_1) \neq \histp \ileadsto[i_2] \pi(i_2)$, thus ${\ileadsto[i_1]}(\histp) \neq {\ileadsto[i_2]}(\histp)$. 
+  Apply \ref{it:condNotHAI} on $\histp, i_1$. We obtain some $i_3 \in I$ such that $\pi(i_1) \neq \pi(i_3)$ and $\forall \histpp \wsub \histp: {\ileadsto[i_1]}(\histpp) = {\ileadsto[i_3]}(\histpp)$.
+  In particular, ${\ileadsto[i_1]}(\histp) = {\ileadsto[i_3]}(\histp)$, thus, $i_3 \neq i_2$.
+  Also, $i_3 \in J$.
+  Iterating this process, we obtain an infinite sequence of distinct individuals in $J$.
+  In other words, we have shown that if some $i_2 \in J, \hist^{(2)} \in \allhists$ with $\pi(i_2) \neq \emptyset$ and $i_1$ and $i_2$ agree everywhere on $\hist^{(2)}$, then there exists $i_3 \in J, \hist^{(3)} \in \allhists$ with $\pi(i_3) \neq \emptyset$ and $\hist^{(2)} \ssub \hist^{(3)}$ and $i_1$ and $i_2$ disagree somewhere on $\hist^{(3)}$ and $i_1$ and $i_2$ agree everywhere on $\hist^{(3)}$.
+(Should check this summary.)
+  Could also use the following probably simpler proof.
+Consider any finite subset of $j$ individuals, build a $H'$ with all the test paths containing decisive arguments, namely $\hist^{(2)} = (\hist, a_1, a_2)$, $\hist^{(3)} = (\hist^{(2)}, a_1, a_3)$, …, and show that there’s another $j$ in fact.
+\end{proof}
+\begin{example}
+  TODO find example where Per \cref{th:caractNotIndic}, there is no claim that holds and is anonymous and indicative.
+
+  % Given $\ar \in \allargs$ and $p, p' \in P$, define ${\ileadsto[i^{(\ar, p, p')}]}$ as $\hist \ileadsto[i^{(\ar, p, p')}] p$ iff $\ar \in \histend$ and $\hist \ileadsto[i^{(\ar, p, p')}] p'$ otherwise.
+  % It follows that $\pi(i^{(\ar, p, p')}) = p$.
+
+  % Pick any two $p \neq p' \in P$ and consider infinitely many arguments $\allargs = \set{\ar_1, …, }$ and infinitely many individuals $I = \set{i^{(\ar, p, p')} \suchthat \ar \in \allargs} \cup \set{i^{(\ar, p', p)} \suchthat \ar \in \allargs}$.
+  % Per \cref{th:caractNotIndic}, there is no claim that holds and is anonymous and indicative:
+  % consider any $\hist, i_1$, if $\ar_1$. NOPE, that’s wrong, I think.
+
+  % Define ${\ileadsto[i^{(\ar, \phi)}]}$ as $\hist \ileadsto[i^{(\ar, \phi)}] \phi$ iff $\hist_0 = \ar$ and $\hist \ileadsto[i^{(\ar, \phi)}] ¬\phi$ otherwise.
+  % It follows that $\pi(i^{(\ar, \phi)}) = \emptyset$.
+
+  The condition $\pi(i_1) \neq \emptyset$ in \ref{it:condNotHAI} is required, as seen by this example where \ref{it:condNotHAI} is satisfied, even though
+  $[\forall \hist \in \allhists, i_1 \in I: \exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)]$ is not.
 We could have \ref{it:condNotHAI} satisfied, but not the part with $\pi(i_1) \neq \emptyset$.

### 2024-01-22 simple.tex
Rm wrong conjecture about (not) HAI

@@
 \begin{conjecture}
-  \label{th:caractNotIndicWrong}
-  The following two conditions on $\allleadsto$ are equivalent:
-  \begin{enumerate}[label=T\ref{th:caractNotIndic}-{\arabic*}]
-    \item \label{it:NotHAIWrong} there exists no claim that holds and is anonymous and indicative;
-    \item \label{it:condNotHAIWrong} either all individuals have an empty deliberated preference, or all paths are such that at least two individuals with different deliberated judgements behave identically on the whole path (formally: either $\pi(I) = \emptyset$ or $\forall \hist \in \allhists, \exists i_1, i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$);
-    \item \label{it:condNotHAIInfWrong} [To be adjusted for the zero case] all paths are such that infinitely many individuals with different deliberated judgements behave identically on the whole path (formally: $\forall \hist \in \allhists, \exists I_1 \wsub I, i_2 \in I \suchthat \card{I_1} = \infty \land \forall i_1 \in I_1: \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$).
-  \end{enumerate}
-
-  This is WRONG because could have $i$ that says $\phi$ on $H$ and has $\phi$ as DJ, and $i$ can be isolated (nobody with DJ different than $\phi$ says $\phi$ on $H$) but still some $i_1, i_2$ with different DJ behave identically on $H$, say they both say $¬\phi$ on $H$.
-\end{conjecture}
-\begin{proof}
-  Let us show that NOT \ref{it:condNotHAIWrong} implies \ref{it:condHAI}.
-  Consider: at least one individual $i$ has a non-empty DP, and some path is such that
-  $\forall i_1, i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2): \exists \histp \wsub \hist \suchthat {\ileadsto[i_1]}(\histp) \neq {\ileadsto[i_2]}(\histp)$.
-  Define $H = \set{\histp \wsub \hist}$ and $i_1 = i$.
-
-  Conversely, \ref{it:condHAI} implies NOT \ref{it:condNotHAIWrong}.
-  Consider: for some $H \in \finite(\incr(\allhists))$ and $i \in I \suchthat P_{i} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_i$ that $\exists \histp \in H \suchthat {\ileadsto}(\histp) \neq {\ileadsto[i_2]}(\histp)$.
-  Define $\hist$ as the maximal path (in cardinal) in $H$.
-  Consider any $i_1, i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2)$.
-  Remains to show that for some $\histp \wsub \hist$: ${\ileadsto[i_1]}(\histp) \neq {\ileadsto[i_2]}(\histp)$.
-  Assume, on the contrary, that for all $\histp \wsub \hist$: ${\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$.
-\end{proof}
-\begin{conjecture}
   \label{th:caractNotIndic}

### 2024-01-23 simple.tex
Thm promotion
Notation hist
Attempts concrete not HAI

@@
     Assume (wlog) that $A = \set{2, …, \card{A} + 1}$.
-    Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{A} + 1}$, $\hist_i = (\hist_{i - 1}, a_1, i)$.
-    Define $H = \set{\hist_i \suchthat i \in \intvl{2, \card{A} + 1}}$.
+    Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{A} + 1}$, $\hist^{(i)} = (\hist_{i - 1}, a_1, i)$.
+    Define $H = \set{\hist^{(i)} \suchthat i \in \intvl{2, \card{A} + 1}}$.
     Apply \cref{th:suffIndic}.
@@
 \end{example}
-\begin{conjecture}
+\begin{theorem}
   \label{th:caractNotIndic}
@@
   \end{enumerate}
-\end{conjecture}
+\end{theorem}
 \begin{proof}
@@
 \begin{example}
+  Given $\hist \in \allhists$, $\ar \in \allargs$ and $p \in P$, define ${\ileadsto[i^{(\hist, p)}]}$ as $\histp \ileadsto[i^{(\hist, p)}] \phi$ if $\histp \wsub \hist$ and $\histp \ileadsto[i^{(\hist, p)}] p$ otherwise.
+  It follows that $\forall \ar \notin \hist(\N)$, then $\ar \ileadstost[i^{(\hist, \ar)}] p$.
+
+  Given any infinite set $\allargs$, define $I = \set{i^{(\hist, p)} \suchthat \hist \in \allhists, p \in P}$.
+  Considering any $\hist \in \finite(\allhists)$ and $i^{(\histp, p)} \in I$, pick any $p' \neq p$ and consider $j = i^{(\histp, p')}$.
+
+  NOPE
+
+  Given $H_\phi$, $H_{¬\phi}$ and $p \in P$ with $H_\phi \cap H_{¬\phi} = \emptyset$, define ${\ileadsto[i^{(H_\phi, H_{¬\phi}, p)}]}$ as $\hist \ileadsto[i^{(H_\phi, H_{¬\phi}, p)}] \phi$ if $\hist \in H_\phi$, $\hist \ileadsto[i^{(H_\phi, H_{¬\phi}, p)}] ¬\phi$ if $\hist \in H_{¬\phi}$ and $\hist \ileadsto[i^{(H_\phi, H_{¬\phi}, p)}] p$ if $\hist \notin H_\phi \cup H_{¬\phi}$.
+
+  Given any infinite set $\allargs$, define $I = \set{i^{(H_\phi, H_{¬\phi}, p)} \suchthat H_\phi \cap H_{¬\phi} = \emptyset, p \in P}$.
+  Considering any $\hist \in \finite(\allhists)$ and $i^{(H_\phi, H_{¬\phi}, p)} \in I$, pick any $p' \neq p$ and consider $j = i^{(\histp, p')}$.
+
+  NOPE
+
+  Given any infinite set $\allargs$, define $I = \set{f \in P^{\allhists} \suchthat \pi(f) \neq \emptyset}$ and $\forall i \in I: {\ileadsto} = i$.
+  Considering any $\hist \in \finite(\allhists)$ and ${\ileadsto} \in I$, pick another relation that coincides on $\hist$ but with another DJ than ${\ileadsto}$.
+This is possible because $\hist$ is finite, thus there is an argument that is not involved in any of its elements, which can serve as decisive one.
+
+  SEEMS OKAY!
+
+  $p' \neq p$ and consider $j = i^{(\histp, p')}$.
+
   TODO find example where Per \cref{th:caractNotIndic}, there is no claim that holds and is anonymous and indicative.
+  For each path we need two individuals $i^{(\hist, \ar, p)}$ and $i^{(\hist, \ar, p')}$ that have the same behavior all along $\hist$ but different DJs.
+  Defining individuals systematically in such a way should produce a suitable situation.
+
+  If using empty DJs, it’s easier.
+Define $.* \ileadsto[i_1] \phi$, $\emptyset \ileadsto[i_2] \phi$, $a.* \ileadsto[i_2] \phi$, $b.* \ileadsto[i_2] ¬\phi$, $\emptyset \ileadsto[i_3] \phi$, $a.* \ileadsto[i_3] ¬\phi$, $b.* \ileadsto[i_3] \phi$.
+  Then $\pi(i_1) = \phi$ and $\pi(i_2) = \pi(i_3) = \emptyset$.
+  Also, for any path, if it is only $\emptyset$, everybody agree; if it starts with $a$ then $i_1$ and $i_2$ agree on it; if it starts with $b$ then $i_1$ and $i_3$ agree on it.
+
+  % All individuals always go to $\phi$ except for their own decisive argument, leading them, for $i_1, …$, to $\phi$, and for $j_1, …$, to $¬\phi$.
+  % So that when observing someone going always to $\phi$ except for a given argument,
 
@@
   Consider $i_1$ with empty DJ on some path has only individuals with identical behavior on the path that have an empty DJ (though for normal $i$’s, the condition is satisfied, thus there are collisions, meaning some individuals with different DJ having identical behavior on the path).
-  TODO check.
 \end{example}

### 2024-01-23 simple.tex
Cleaned some ¬HAI

--- 2024-01-22 simple.tex
@@
 \end{proof}
-\begin{example}
-  TODO find example where Per \cref{th:caractNotIndic}, there is no claim that holds and is anonymous and indicative.
-
-  % Given $\ar \in \allargs$ and $p, p' \in P$, define ${\ileadsto[i^{(\ar, p, p')}]}$ as $\hist \ileadsto[i^{(\ar, p, p')}] p$ iff $\ar \in \histend$ and $\hist \ileadsto[i^{(\ar, p, p')}] p'$ otherwise.
-  % It follows that $\pi(i^{(\ar, p, p')}) = p$.
-
-  % Pick any two $p \neq p' \in P$ and consider infinitely many arguments $\allargs = \set{\ar_1, …, }$ and infinitely many individuals $I = \set{i^{(\ar, p, p')} \suchthat \ar \in \allargs} \cup \set{i^{(\ar, p', p)} \suchthat \ar \in \allargs}$.
-  % Per \cref{th:caractNotIndic}, there is no claim that holds and is anonymous and indicative:
-  % consider any $\hist, i_1$, if $\ar_1$. NOPE, that’s wrong, I think.
-
-  % Define ${\ileadsto[i^{(\ar, \phi)}]}$ as $\hist \ileadsto[i^{(\ar, \phi)}] \phi$ iff $\hist_0 = \ar$ and $\hist \ileadsto[i^{(\ar, \phi)}] ¬\phi$ otherwise.
-  % It follows that $\pi(i^{(\ar, \phi)}) = \emptyset$.
+\begin{example}[no HAI]
+  Given any infinite set $\allargs$, define $I = \set{f \in P^{\allhists} \suchthat \pi(f) \neq \emptyset}$ and $\forall i \in I: {\ileadsto} = i$.
+  Considering any $\hist \in \finite(\allhists)$ and ${\ileadsto} \in I$, pick another relation that coincides on $\hist$ but with another DJ than ${\ileadsto}$.
+This is possible because $\hist$ is finite, thus there is an argument that is not involved in any of its elements, which can serve as decisive one.
+  Per \cref{th:caractNotIndic}, there is no claim that holds and is anonymous and indicative.
+
+  If using empty DJs, it’s easier.
+Define $.* \ileadsto[i_1] \phi$, $\emptyset \ileadsto[i_2] \phi$, $a.* \ileadsto[i_2] \phi$, $b.* \ileadsto[i_2] ¬\phi$, $\emptyset \ileadsto[i_3] \phi$, $a.* \ileadsto[i_3] ¬\phi$, $b.* \ileadsto[i_3] \phi$.
+  Then $\pi(i_1) = \phi$ and $\pi(i_2) = \pi(i_3) = \emptyset$.
+  Also, for any path, if it is only $\emptyset$, everybody agree; if it starts with $a$ then $i_1$ and $i_2$ agree on it; if it starts with $b$ then $i_1$ and $i_3$ agree on it.
 
@@
   $[\forall \hist \in \allhists, i_1 \in I: \exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)]$ is not.
-We could have \ref{it:condNotHAI} satisfied, but not the part with $\pi(i_1) \neq \emptyset$.
-  Consider $i_1$ with empty DJ on some path has only individuals with identical behavior on the path that have an empty DJ (though for normal $i$’s, the condition is satisfied, thus there are collisions, meaning some individuals with different DJ having identical behavior on the path).
-  TODO check.
+  TODO reuse the example here above to satisfy the condition, but add some $i_1$ with empty DJ who on some path has only individuals with identical behavior on the path that have an empty DJ.
 \end{example}

### 2024-01-24 simple.tex
Exmpls no HAI

@@
 \end{proof}
-\begin{example}[no HAI]
-  Given any infinite set $\allargs$, define $I = \set{f \in P^{\allhists} \suchthat \pi(f) \neq \emptyset}$ and $\forall i \in I: {\ileadsto} = i$.
+\begin{example}[no HAI, with DJ]
+  \label{ex:noHAIwithDJ}
+  The following situation illustrates \cref{th:caractNotIndic} and involve only individuals with a DJ.
+
+  Given any infinite set $\allargs$, define $I = I^\text{DJ} = \set{f \in P^{\allhists} \suchthat \pi(f) \neq \emptyset}$ and $\forall i \in I: {\ileadsto} = i$.
   Considering any $\hist \in \finite(\allhists)$ and ${\ileadsto} \in I$, pick another relation that coincides on $\hist$ but with another DJ than ${\ileadsto}$.
@@
   Per \cref{th:caractNotIndic}, there is no claim that holds and is anonymous and indicative.
-
-  If using empty DJs, it’s easier.
-Define $.* \ileadsto[i_1] \phi$, $\emptyset \ileadsto[i_2] \phi$, $a.* \ileadsto[i_2] \phi$, $b.* \ileadsto[i_2] ¬\phi$, $\emptyset \ileadsto[i_3] \phi$, $a.* \ileadsto[i_3] ¬\phi$, $b.* \ileadsto[i_3] \phi$.
+\end{example}  
+\begin{example}[no HAI]
+  \label{ex:noHAI}
+  Define $I = \set{i_1, i_2, i_3}$ and $\allleadsto$ as follows: $.* \ileadsto[i_1] \phi$, $\emptyset \ileadsto[i_2] \phi$, $a.* \ileadsto[i_2] \phi$, $b.* \ileadsto[i_2] ¬\phi$, $\emptyset \ileadsto[i_3] \phi$, $a.* \ileadsto[i_3] ¬\phi$, $b.* \ileadsto[i_3] \phi$.
   Then $\pi(i_1) = \phi$ and $\pi(i_2) = \pi(i_3) = \emptyset$.
-  Also, for any path, if it is only $\emptyset$, everybody agree; if it starts with $a$ then $i_1$ and $i_2$ agree on it; if it starts with $b$ then $i_1$ and $i_3$ agree on it.
-
-  The condition $\pi(i_1) \neq \emptyset$ in \ref{it:condNotHAI} is required, as seen by this example where \ref{it:condNotHAI} is satisfied, even though
-  $[\forall \hist \in \allhists, i_1 \in I: \exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)]$ is not.
-  TODO reuse the example here above to satisfy the condition, but add some $i_1$ with empty DJ who on some path has only individuals with identical behavior on the path that have an empty DJ.
-\end{example}
+  This satisfies \ref{it:condNotHAI}: considering any $\hist \in \allhists$, if $(1, a) \in \hist$, then $i_2$ collides with $i_1$ on $\hist$, and otherwise, $i_3$ does.
+\end{example}  
+\begin{remark}[no HAI thanks to condition]
+  Whether the condition $\pi(i_1) \neq \emptyset$ in \ref{it:condNotHAI} is required remains an open question. Showing that it is required requires an example where,
+  defining $Q(\hist, i_1)$ as $\exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$,
+  the condition
+  $\forall \hist \in \allhists, i_1 \in I \suchthat \pi(i_1) \neq \emptyset: Q(\hist, i_1)$ is satisfied, even though
+  $[\forall \hist \in \allhists, i_1 \in I: Q(\hist, i_1)]$ is not, thus satisfying $\exists \hist, i_0 \suchthat \pi(i_0) = \emptyset \land ¬Q(\hist, i_0)$.
+
+  Define $I = \set{i_1, …, i_5}$, $\ileadsto[i_1], \ileadsto[i_2], \ileadsto[i_3]$ as in \cref{ex:noHAI} and $\ileadsto[i_4]$ and $\ileadsto[i_5]$ as: $.* \ileadsto[i_4] ¬\phi$, $\emptyset \ileadsto[i_4] ¬\phi$, $a.* \ileadsto[i_4] \phi$, $b.* \ileadsto[i_4] ¬\phi$, $\emptyset \ileadsto[i_5] ¬\phi$, $a.* \ileadsto[i_5] ¬\phi$, $b.* \ileadsto[i_5] \phi$.
+  This satisfies \ref{it:condNotHAI} for the reason given in \cref{ex:noHAI}, and fails $Q(\emptyset, i_4)$.
+  This is not possible by starting from \cref{ex:noHAIwithDJ}: given any infinite set $\allargs$, defining some adequate $J = \set{i_0, …}$ and $I = I^\text{DJ} \cup J$ and $\forall i \in I: {\ileadsto} = i$, we get that $i_0$ conflicts on every paths with some individuals in $I^\text{DJ}$.
+\end{remark}
 \begin{remark}

### 2024-01-24 simple.tex
No HAI, condition required (reworded)

@@
 \end{example}  
-\begin{remark}[no HAI thanks to condition]
-  Whether the condition $\pi(i_1) \neq \emptyset$ in \ref{it:condNotHAI} is required remains an open question. Showing that it is required requires an example where,
-  defining $Q(\hist, i_1)$ as $\exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$,
-  the condition
-  $\forall \hist \in \allhists, i_1 \in I \suchthat \pi(i_1) \neq \emptyset: Q(\hist, i_1)$ is satisfied, even though
-  $[\forall \hist \in \allhists, i_1 \in I: Q(\hist, i_1)]$ is not, thus satisfying $\exists \hist, i_0 \suchthat \pi(i_0) = \emptyset \land ¬Q(\hist, i_0)$.
-
-  Define $I = \set{i_1, …, i_5}$, $\ileadsto[i_1], \ileadsto[i_2], \ileadsto[i_3]$ as in \cref{ex:noHAI} and $\ileadsto[i_4]$ and $\ileadsto[i_5]$ as: $.* \ileadsto[i_4] ¬\phi$, $\emptyset \ileadsto[i_4] ¬\phi$, $a.* \ileadsto[i_4] \phi$, $b.* \ileadsto[i_4] ¬\phi$, $\emptyset \ileadsto[i_5] ¬\phi$, $a.* \ileadsto[i_5] ¬\phi$, $b.* \ileadsto[i_5] \phi$.
+\begin{remark}[no HAI condition required]
+  The condition $\pi(i_1) \neq \emptyset$ in \ref{it:condNotHAI} is required:
+  the following example satisfies \ref{it:condNotHAI} but fails the extended version of that condition without that condition.
+  In other words, defining $Q(\hist, i_1)$ as $\exists i_2 \in I \suchthat \pi(i_1) \neq \pi(i_2) \land \forall \histp \wsub \hist: {\ileadsto[i_1]}(\histp) = {\ileadsto[i_2]}(\histp)$,
+  the example satisfies
+  $\forall \hist \in \allhists, i_1 \in I \suchthat \pi(i_1) \neq \emptyset: Q(\hist, i_1)$,
+  but does not satisfy
+  $[\forall \hist \in \allhists, i_1 \in I: Q(\hist, i_1)]$, thus, satisfies 
+  $\exists \hist, i_0 \suchthat \pi(i_0) = \emptyset \land ¬Q(\hist, i_0)$.
+
+  Define $I = \set{i_1, …, i_4}$, $\ileadsto[i_1], \ileadsto[i_2], \ileadsto[i_3]$ as in \cref{ex:noHAI} and $\ileadsto[i_4]$ as: $.* \ileadsto[i_4] ¬\phi$, $\emptyset \ileadsto[i_4] ¬\phi$, $a.* \ileadsto[i_4] \phi$, $b.* \ileadsto[i_4] ¬\phi$.
   This satisfies \ref{it:condNotHAI} for the reason given in \cref{ex:noHAI}, and fails $Q(\emptyset, i_4)$.
-  This is not possible by starting from \cref{ex:noHAIwithDJ}: given any infinite set $\allargs$, defining some adequate $J = \set{i_0, …}$ and $I = I^\text{DJ} \cup J$ and $\forall i \in I: {\ileadsto} = i$, we get that $i_0$ conflicts on every paths with some individuals in $I^\text{DJ}$.
 \end{remark}

### 2024-04-15 simple.tex
Mv around?

@@
 This happens for example when everybody has a deliberate judgment and a finite set of decisive arguments suffices to lead everybody to their deliberate judgment (\cref{th:suffIndicDec}).
-
-\begin{theorem}
-  \label{th:suffFals}
-  Assume that $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  Then, there exists a claim that holds and is anonymous and falsifiable.
-\end{theorem}
-\begin{proof}
-  Define $C = \set{{\allleadstog} \suchthat \forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}}$. It holds and is anonymous.
-  Pick any ${\allleadstog} \notin C$.
-  Then, $\exists i \in I \suchthat {{\ileadstog}} \notin \set{{\ileadsto[k]} \suchthat k \in I}$.
-  Pick any such $i$ and any $H$ such that $\forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  Define $\theta = \set{(\hist, i, {\ileadstog}(\hist)) \suchthat \hist \in H} \in \Theta \cap \powerset{\allleadstog}$.
-  Then, $\theta \notin C^\wsub$, because $\forall j \in I: \theta \nsubseteq {\ileadsto[j]}$.
-
-  For another proof, note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat \forall i \in I: \exists j \in I \suchthat \theta \cap (\allhists × \set{i} × P) \wsub {\ileadsto[j]}}$.
-  Pick any ${\allleadstog} \in E(C^\wsub \cap \Theta)$ and let us show that ${\allleadstog} \in C$.
-  Note that ${\allleadstog} \notin C \iff \exists i \in I \suchthat {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, in which case the consequent in the theorem holds.
-  We need to show that $\nexists i \in I, H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  In other words, given any $i \in I$, we need to show that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
-\end{proof}
-
-\begin{remark}
-  The opposite of \cref{th:suffFals} is NOT $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  Thus, for some ${\allleadstog} \in \allleadstos$ and some $i \in I$ with ${\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, we have that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
-
-  For example, $\allargs = \set{\ar_1, \ar_2}$ and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and the attitude contains only people constant to $\phi$ (except that they map $\emptyset$ to anything) and people constant to $¬\phi$ (except that they map $\emptyset$ to anything).
-\end{remark}
-\begin{theorem}
-  Consider the attitude above. Is there a claim that holds and is anonymous and falsifiable?
-  Check \cref{ex:falsAnonIfBig}.
-\end{theorem}
 
@@
 \end{remark}
+
+A claim about types of individuals is a set $C^\text{types} \wsub P^{\allhists}$.
+Given such a set, define the associated claim $C \wsub \allleadstos$ as $C = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in C^\text{types}}$.
+\begin{lemma}
+  \label{th:typesfalsifiable}
+  A claim about types of individuals $C^\text{types} \wsub P^{\allhists}$ 
+  satisfies $\forall {\ileadstog} \in P^{\allhists} \setminus C^\text{types}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall {\ileadstog[j]} \in C^\text{types}: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadstog[j]}(\hist)$,
+  iff its associated claim is falsifiable or trivial.
+\end{lemma}
+\begin{proof}
+  Pick any ${\allleadstog} \notin C$.
+  By definition of $C$,
+  $\exists i \in I \suchthat {{\ileadstog}} \notin C^\text{types}$.
+  As $C$ holds, ${\ileadstog} \notin \set{{\ileadsto[j]} \suchthat j \in I}$ (\cref{th:typesholds}).
+  Pick any $H$ such that $\forall {\ileadstog[j]} \in C^\text{types}: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadstog[j]}(\hist)$.
+  Define $\theta = \set{(\hist, i, {\ileadstog}(\hist)) \suchthat \hist \in H} \in \Theta \cap \powerset{\allleadstog}$.
+  Then, $\theta \notin C^\wsub$, because $\forall {\ileadstog[j]} \in C^\text{types}: \theta \nsubseteq {\ileadstog[j]}$.
+
+  Conversely, assume that for some ${\ileadstog} \in P^{\allhists} \setminus C^\text{types}$, no $H \in \finite(\incr(\allhists))$ satisfies the indicated condition.
+  Define ${\allleadstog}$ as including ${\ileadstog}$ and for all other individiduals, relations from $C^\text{types}$.
+  Then, ${\allleadstog} \notin C$, but any observation will be in $C$, thus the claim is not falsifiable and not trivial.
+\end{proof}
+\begin{lemma}
+  \label{th:typesholds}
+  Consider a claim about types of individuals $C^\text{types} \wsub P^{\allhists}$. Its associated claim holds iff $\set{{\ileadsto[j]} \suchthat j \in I} \wsub C^\text{types}$.
+\end{lemma}
+\begin{lemma}
+  \label{th:typesanonymous}
+  Given any claim about types of individuals $C^\text{types} \wsub P^{\allhists}$, its associated claim is anonymous.
+\end{lemma}
+The following result follows from \cref{th:typesfalsifiable,th:typesholds,th:typesanonymous}.
+\begin{theorem}
+  \label{th:suffFals}
+  Assume that $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  Then, the claim $C$ associated to the claim about types of individuals $C^\text{types} = \set{{\ileadsto[j]} \suchthat j \in I}$ holds and is anonymous and falsifiable.
+\end{theorem}
+\begin{proof}
+  For another proof, note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat \forall i \in I: \exists j \in I \suchthat \theta \cap (\allhists × \set{i} × P) \wsub {\ileadsto[j]}}$.
+  Pick any ${\allleadstog} \in E(C^\wsub \cap \Theta)$ and let us show that ${\allleadstog} \in C$.
+  Note that ${\allleadstog} \notin C \iff \exists i \in I \suchthat {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, in which case the consequent in the theorem holds.
+  We need to show that $\nexists i \in I, H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  In other words, given any $i \in I$, we need to show that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
+\end{proof}
+
 \begin{remark}
-  Given $J \wsub I$, say that a set of paths discriminates $J$ iff some function associating each path to an answer is compatible with some $j \in J$ (meaning that $f \wsub {\ileadsto[j]}$) and is compatible with no $i \notin J$.
-  The condition says that there must be some $p$ and some increasing set of paths $H$ such that $H$ discriminates $J = \pi^{-1}(p)$.
+  The opposite of \cref{th:suffFals} is the negation of $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  Thus, for some ${\allleadstog} \in \allleadstos$ and some $i \in I$ with ${\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, we have that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
+
+  For example, $\allargs = \set{\ar_1, \ar_2}$ and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and the attitude contains only people constant to $\phi$ (except that they map $\emptyset$ to anything) and people constant to $¬\phi$ (except that they map $\emptyset$ to anything).
+
+  TODO
+  In that case, if restricting our focus to claims about types of individuals, we need to include the real types, then close under suitable indistinguishability relation, so as to include for example $i$.
+
+  Define $S$ as the relations in the claim. Define $R(S)$ as the adequate closure: those that we can’t reject.
+  Does $S$ include $R(S)$? If so, it is falsifiable. Otherwise, there is in $R(S)$ a relation that we can’t reject.
+  Let $Impl$ be all impliciations in $S$, of the form: if $\hist$ goes to $p$, then $\hist'$ goes to $p'$ (in the above example: if $a$ goes to $\phi$ then $aa$ goes to $\phi$).
+Any relation that breaks one of these implications is rejectable.
+For example, sending $a$ to $\phi$ and $ab$ to $¬\phi$ is rejectable.We need to include all relations that break no implication.
+  TODO check all this. 
 \end{remark}
-\begin{remark}
-  For failing the condition, I need an infinity of $j$’s (and at least one $i$) who agree on any branch of the history tree? (Meaning relations $\ileadsto[j]$, we don’t care about individuals.)
-  No: on any finite branch in the tree, I need that remains one $j$ and one $i$ such that infinite prolongation of the branch will never discriminate them.
-
-  That’s it: any finite branch of the tree (meaning, any $H$) is compatible with two DJs, meaning at least one relation having a given DJ and at least one relation having another DJ.
-
-  That means (still mandating that everybody has a DJ), that the condition mandates that any finite branch of the tree be compatible with infinitely many different relations having one DJ and at least one having another DJ.
-(Otherwise when there’s only finitely many we can just exclude them by testing all decisive arguments.)
-\end{remark}
+\begin{theorem}
+  Consider the attitude above. Is there a claim that holds and is anonymous and falsifiable?
+  Check \cref{ex:falsAnonIfBig}.
+\end{theorem}
 

### 2024-04-23 simple.tex
Indistinguishability

@@
 In particular, such an “argument” need not have the logical structure of what is considered a proper argument in argumentation theory.
-This important feature of this proposal permits to avoid taking a position on what is a correct argument, and permits to study wide enough conceptions of deliberated judgment, including those involving no paternalism \citep{cailloux_formal_2020}: anything that influences the judgment of a subject, as judged by the subject herself and not by any external standard, may a priori be considered worth including in at least some conceptions of deliberated judgment, thus including whatever some could consider as “incorrect reasoning” or “bad reasons”.
+This important feature of this proposal permits to avoid taking a position on what is a correct argument, and permits to study wide enough conceptions of deliberated judgment, including those involving no paternalism \citep{cailloux_formal_2020}: anything that influences the judgment of a subject, as judged by the subject herself and not by any external standard, may a priori be considered worth including in at least some conceptions of deliberated judgment, thus including whatever some could consider as “incorrect reasoning”, “fallacies” or “bad reasons”.
 
@@
 While it is indeed a long-term goal of this research program to yield a normatively relevant conception of preference (appropriate, for example, for recommendation), it is not a claim of this article that anything that corresponds to deliberated judgments as defined here qualify as being appropriate for any normative use: much depends on the chosen exposure protocol.
-The goal of this article is one of a conceptual and practical clarification.
+The goal of this article is rather one of a conceptual and practical clarification.
 It proposes a sharp distinction between the empirical content and the normative content of the concept of deliberated judgments: the definition proposed here transfers the full normative weight on the choice of the exposure protocol; and leaves the rest of the disagreements to empirical settling.
@@
 A claim about types of individuals is a set $C^\text{types} \wsub P^{\allhists}$.
-Given such a set, define the associated claim $C \wsub \allleadstos$ as $C = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in C^\text{types}}$.
+Given such a set, define the associated claim $C \wsub \allleadstos$ as $C = (C^\text{types})^I = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in C^\text{types}}$.
 \begin{lemma}
@@
   Conversely, assume that for some ${\ileadstog} \in P^{\allhists} \setminus C^\text{types}$, no $H \in \finite(\incr(\allhists))$ satisfies the indicated condition.
-  Define ${\allleadstog}$ as including ${\ileadstog}$ and for all other individiduals, relations from $C^\text{types}$.
+  Define ${\allleadstog}$ as including ${\ileadstog}$ and for all other individuals, relations from $C^\text{types}$.
   Then, ${\allleadstog} \notin C$, but any observation will be in $C$, thus the claim is not falsifiable and not trivial.
@@
   Assume that $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  Then, the claim $C$ associated to the claim about types of individuals $C^\text{types} = \set{{\ileadsto[j]} \suchthat j \in I}$ holds and is anonymous and falsifiable.
+  Then, the claim $C$ associated to the claim about types of individuals $C^\text{types} = \set{{\ileadsto[j]} \suchthat j \in I}$ holds, is anonymous, and is falsifiable or trivial.
 \end{theorem}
@@
 \end{remark}
+\begin{definition}
+  Say that an attitude $g \in P^{\allhists}$ is indistinguishable from a set of attitudes $S \wsub P^{\allhists}$ iff $\forall H \in \finite(\incr(\allhists)): \exists f \in S \suchthat \restr{g}{H} = \restr{f}{H}$.
+
+  Define the extension of a claim about types $C^\text{types} \wsub P^{\allhists}$ to its indistiguishible attitudes as the the claim about types $R(C^\text{types}) = \set{g \in P^{\allhists} \suchthat \forall H \in \finite(\incr(\allhists)): \exists f \in C^\text{types} \suchthat \restr{g}{H} = \restr{f}{H}}$.
+  Note that $C^\text{types} \wsub R(C^\text{types})$. 
+  Also note that $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$.
+
+  Define the closure under indistinguishability of a claim about types $C^\text{types}$ as $R^\infty(C^\text{types})$, equivalently, as the smallest set $C^\text{types}_\text{ind}$ such that $R(C^\text{types}_\text{ind}) \wsub C^\text{types}_\text{ind}$.
+\end{definition}
+The following result follows from \cref{th:typesfalsifiable}.
+\begin{theorem}
+  If a claim about types of individuals $C^\text{types} \wsub P^{\allhists}$ is not closed under indistinguishability, then it is not falsifiable and not trivial.
+\end{theorem}
+\begin{theorem}
+  Given any situation, if the claim related to the claim about types of individuals $R^\infty({\allleadsto}(I))$ is trivial, then there exists no claim related to a claim about types of individuals that holds and is falsifiable.
+\end{theorem}
+\begin{proof}
+  Consider a claim related to a claim about types of individuals $S$ that holds and that is falsifiable or trivial.
+  For it to hold, we need ${\allleadsto}(I) \wsub S$.
+  From \cref{th:typesfalsifiable}, for it to be falsifiable or trivial, we need that $\forall g \in P^{\allhists} \setminus S: \exists H \in \finite(\incr(\allhists)) \suchthat \forall f \in S: \restr{g}{H} \neq \restr{f}{H}$.
+In other words, all $g$ must be distinguishable from $S$.
+In other words, $S$ must be closed under indistinguishability.
+Thus, we need $R^\infty(S) \wsub S$.
+  Also, because $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$, we need
+  $R^\infty({\allleadsto}(I)) \wsub R^\infty(S) \wsub S$.
+  It follows that $S$ is trivial.
+\end{proof}
+
+\begin{conjecture}
+  Given any situation, the claim about types of individuals $R^\infty({\allleadsto}(I))$ holds, is anonymous, and is falsifiable or trivial.
+\end{conjecture}
+
+\begin{theorem}[To be deleted, probably]
+  Consider the attitude where all individuals are either constant to $\phi$ except that they map $\emptyset$ to anything, or constant to $¬\phi$ except that they map $\emptyset$ to anything, say, $(\phi, \phi)$, $(¬\phi, \phi)$, $(\phi, ¬\phi)$, $(¬\phi, ¬\phi)$.
+  Consider a claim about types of individuals containing all those ones.
+Assume that for some attitude $i$ not in the claim, no $H$ permit to distinguish $i$ from the claim.
+Then from the lemma above, the claim is not falsifiable.
+So, we need to include all attitudes that no $H$ permit to distinguish from the claim.
+Iterating, this is the closure under the indistinguishability relation.
+  So, the claim about types must include the real ones and be closed under the indistinguishability relation.
+\end{theorem}
 \begin{theorem}

### 2024-04-30 simple.tex
observably closed

@@
 Given such a set, define the associated claim $C \wsub \allleadstos$ as $C = (C^\text{types})^I = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in C^\text{types}}$.
+\begin{definition}
+  Say that an attitude $g \in P^{\allhists}$ is observably included in a set of attitudes $S \wsub P^{\allhists}$ iff $\forall H \in \finite(\incr(\allhists)): \exists f \in S \suchthat \restr{g}{H} = \restr{f}{H}$.
+
+  Define the extension of a claim about types $C^\text{types} \wsub P^{\allhists}$ to its observably included attitudes as the the claim about types $R(C^\text{types}) = \set{g \in P^{\allhists} \suchthat \forall H \in \finite(\incr(\allhists)): \exists f \in C^\text{types} \suchthat \restr{g}{H} = \restr{f}{H}}$.
+  Note that $C^\text{types} \wsub R(C^\text{types})$. 
+  Also note that $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$.
+
+  Define the closure under observable inclusion of a claim about types $C^\text{types}$ as $R^\infty(C^\text{types})$, equivalently, as the smallest set $C^\text{types}_\text{ind}$ such that $R(C^\text{types}_\text{ind}) \wsub C^\text{types}_\text{ind}$.
+
+  Given a set of attitudes $S$ and $\hist \in \allhists$, define the equivalence relation $=_\hist$ on $S$ as $f =_\hist g$ iff $f(\hist) = g(\hist)$.
+This also defines the quotient set $S / =_\hist$.
+(For the readers used to that terminology: if defining $\beta_\hist \in P^S$ as $\beta_\hist(f) = f(\hist)$, then $=_\hist$ is the equivalence kernel of $\beta_\hist$ and $S / =_\hist$ is the coimage of $\beta_\hist$.)
+  Similarly, given $S$ and $H \in \finite(\incr(\allhists))$, define the equivalence relation $=_H$ on $S$ as $f =_H g$ iff $\restr{f}{H} = \restr{g}{H}$. This also defines the quotient set $S / =_H$.
+\end{definition}
+\begin{remark}
+  A few more, maybe not useful, definitions.
+  A function $l: \allhists \to \powerset{P^{\allhists}}$ is decreasing iff $\forall \hist \wsub \histp: l(\histp) \wsub l(\hist)$.
+  Let $S \wsub P^{\allhists}$ be a set of attitudes.
+  Say that a function $l: \allhists \to \powerset{P^{\allhists}}$ is an $S$-point-labeling function iff $\forall \hist \in \allhists: l(\hist) \in S / =_\hist$.
+  Say that a function $l: \allhists \to \powerset{P^{\allhists}}$ is an $S$-sequence-labeling function iff $\forall \hist \in \allhists: l(\hist) \in S / =_{\intvl{\hist}}$.
+\end{remark}
+Let $\intvl{\hist} = (\hist_i)_{i \in \intvl{0, \card{\hist}}} \in \finite(\incr(\allhists))$ denote the increasing sequence of paths from $\emptyset$ to $\hist$.
+\begin{conjecture}
+  The $S$-labeling function associated to an attitude $f \in P^{\allhists}$ is the function $l^S_f: \allhists \to \powerset{P^{\allhists}}$ defined as $l^S_f(\hist) = \set{g \in S \suchthat g(\hist) = f(\hist)}$.
+
+  An attitude is observably included in a set of attitudes $S$ iff $\forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$.
+\end{conjecture}
+\begin{proof}
+  Consider $f$ with $\forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$.
+  Consider any $H \in \finite(\incr(\allhists))$.
+  We know that $\cap_{\histp \wsub \hist}{l^S_f(\histp)} \neq \emptyset$, thus in particular, defining $\hist = \max H$ and observing that $H \wsub \set{\histp \suchthat \histp \wsub \hist}$, we have that $\cap_{\histp \in H} l^S_f(\histp) \neq \emptyset$.
+  Pick any $g \in \cap_{\histp \in H} l^S_f(\histp)$. Thus, $g \in S$.
+  Also, $\forall \hist \in H: g \in l^S_f(\hist)$, thus,
+  $\forall \hist \in H: g(\hist) = f(\hist)$.
+
+  First observe that given any $S \wsub P^{\allhists}$, $f \in P^{\allhists}$ and $\hist \in \allhists$, as $\histp \wsub \hist$ iff $\histp \in \intvl{\hist}$, we have that $\cap_{\histp \wsub \hist} l^S_f(\histp) = \set{g \in S \suchthat \forall \histp \in \intvl{\hist}: g(\histp) = f(\histp)}$.
+
+  It follows that if $\forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$, then $\forall H \in \finite(\incr(\allhists))$: $\emptyset \neq \set{g \in S \suchthat \forall \histp \in \intvl{\max H}: g(\histp) = f(\histp)} \wsub \set{g \in S \suchthat \forall \histp \in H: g(\histp) = f(\histp)}$.
+
+  Conversely, if $\forall H \in \finite(\incr(\allhists)): \set{g \in S \suchthat \forall \histp \in H: g(\histp) = f(\histp)} \neq \emptyset$, then $\forall \hist \in \allhists$, defining $H = \intvl{\hist}$, we have that $\cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$.
+\end{proof}
+\begin{remark}
+  The opposite of \cref{th:suffFals} is the negation of $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  Thus, for some ${\allleadstog} \in \allleadstos$ and some $i \in I$ with ${\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, we have that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
+
+  For example, $\allargs = \set{\ar_1, \ar_2}$ and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and the attitude contains only people constant to $\phi$ (except that they map $\emptyset$ to anything) and people constant to $¬\phi$ (except that they map $\emptyset$ to anything).
+
+  TODO
+  In that case, if restricting our focus to claims about types of individuals, we need to include the real types, then close under suitable indistinguishability relation (observable inclusion), so as to include for example $i$.
+
+  Define $S$ as the relations in the claim. Define $R(S)$ as the adequate closure: those that we can’t reject.
+  Does $S$ include $R(S)$? If so, it is falsifiable. Otherwise, there is in $R(S)$ a relation that we can’t reject.
+  Let $Impl$ be all impliciations in $S$, of the form: if $\hist$ goes to $p$, then $\hist'$ goes to $p'$ (in the above example: if $a$ goes to $\phi$ then $aa$ goes to $\phi$).
+Any relation that breaks one of these implications is rejectable.
+For example, sending $a$ to $\phi$ and $ab$ to $¬\phi$ is rejectable.We need to include all relations that break no implication.
+  TODO check all this. 
+\end{remark}
 \begin{lemma}
@@
   A claim about types of individuals $C^\text{types} \wsub P^{\allhists}$ 
-  satisfies $\forall {\ileadstog} \in P^{\allhists} \setminus C^\text{types}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall {\ileadstog[j]} \in C^\text{types}: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadstog[j]}(\hist)$,
+  satisfies $\forall g \in P^{\allhists} \setminus C^\text{types}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall f \in C^\text{types}: \restr{g}{H} \neq \restr{f}{H}$,
   iff its associated claim is falsifiable or trivial.
@@
 
-\begin{remark}
-  The opposite of \cref{th:suffFals} is the negation of $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  Thus, for some ${\allleadstog} \in \allleadstos$ and some $i \in I$ with ${\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, we have that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
-
-  For example, $\allargs = \set{\ar_1, \ar_2}$ and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and the attitude contains only people constant to $\phi$ (except that they map $\emptyset$ to anything) and people constant to $¬\phi$ (except that they map $\emptyset$ to anything).
-
-  TODO
-  In that case, if restricting our focus to claims about types of individuals, we need to include the real types, then close under suitable indistinguishability relation, so as to include for example $i$.
-
-  Define $S$ as the relations in the claim. Define $R(S)$ as the adequate closure: those that we can’t reject.
-  Does $S$ include $R(S)$? If so, it is falsifiable. Otherwise, there is in $R(S)$ a relation that we can’t reject.
-  Let $Impl$ be all impliciations in $S$, of the form: if $\hist$ goes to $p$, then $\hist'$ goes to $p'$ (in the above example: if $a$ goes to $\phi$ then $aa$ goes to $\phi$).
-Any relation that breaks one of these implications is rejectable.
-For example, sending $a$ to $\phi$ and $ab$ to $¬\phi$ is rejectable.We need to include all relations that break no implication.
-  TODO check all this. 
-\end{remark}
-\begin{definition}
-  Say that an attitude $g \in P^{\allhists}$ is indistinguishable from a set of attitudes $S \wsub P^{\allhists}$ iff $\forall H \in \finite(\incr(\allhists)): \exists f \in S \suchthat \restr{g}{H} = \restr{f}{H}$.
-
-  Define the extension of a claim about types $C^\text{types} \wsub P^{\allhists}$ to its indistiguishible attitudes as the the claim about types $R(C^\text{types}) = \set{g \in P^{\allhists} \suchthat \forall H \in \finite(\incr(\allhists)): \exists f \in C^\text{types} \suchthat \restr{g}{H} = \restr{f}{H}}$.
-  Note that $C^\text{types} \wsub R(C^\text{types})$. 
-  Also note that $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$.
-
-  Define the closure under indistinguishability of a claim about types $C^\text{types}$ as $R^\infty(C^\text{types})$, equivalently, as the smallest set $C^\text{types}_\text{ind}$ such that $R(C^\text{types}_\text{ind}) \wsub C^\text{types}_\text{ind}$.
-\end{definition}
 The following result follows from \cref{th:typesfalsifiable}.
 \begin{theorem}
-  If a claim about types of individuals $C^\text{types} \wsub P^{\allhists}$ is not closed under indistinguishability, then it is not falsifiable and not trivial.
+  If a claim about types of individuals $C^\text{types} \wsub P^{\allhists}$ is not closed under observable inclusion, then it is not falsifiable and not trivial.
 \end{theorem}
@@
   From \cref{th:typesfalsifiable}, for it to be falsifiable or trivial, we need that $\forall g \in P^{\allhists} \setminus S: \exists H \in \finite(\incr(\allhists)) \suchthat \forall f \in S: \restr{g}{H} \neq \restr{f}{H}$.
-In other words, all $g$ must be distinguishable from $S$.
-In other words, $S$ must be closed under indistinguishability.
+In other words, all $g$ must be observably excludable from $S$.
+In other words, $S$ must be closed under observable inclusion.
 Thus, we need $R^\infty(S) \wsub S$.
@@
 \end{proof}
-
-\begin{conjecture}
+\begin{theorem}
   Given any situation, the claim about types of individuals $R^\infty({\allleadsto}(I))$ holds, is anonymous, and is falsifiable or trivial.
-\end{conjecture}
+\end{theorem}
 
@@
   Consider a claim about types of individuals containing all those ones.
-Assume that for some attitude $i$ not in the claim, no $H$ permit to distinguish $i$ from the claim.
+Assume that for some attitude $i$ not in the claim, no $H$ permit to observably exclude $i$ from the claim.
 Then from the lemma above, the claim is not falsifiable.
-So, we need to include all attitudes that no $H$ permit to distinguish from the claim.
-Iterating, this is the closure under the indistinguishability relation.
-  So, the claim about types must include the real ones and be closed under the indistinguishability relation.
+So, we need to include all attitudes that no $H$ permit to observably exclude from the claim.
+Iterating, this is the closure under the observable inclusion relation.
+  So, the claim about types must include the real ones and be closed under observable inclusion.
 \end{theorem}

### 2024-04-30 simple.tex
Reordered

@@
 Let $\intvl{\hist} = (\hist_i)_{i \in \intvl{0, \card{\hist}}} \in \finite(\incr(\allhists))$ denote the increasing sequence of paths from $\emptyset$ to $\hist$.
-\begin{conjecture}
+\begin{theorem}
   The $S$-labeling function associated to an attitude $f \in P^{\allhists}$ is the function $l^S_f: \allhists \to \powerset{P^{\allhists}}$ defined as $l^S_f(\hist) = \set{g \in S \suchthat g(\hist) = f(\hist)}$.
 
-  An attitude is observably included in a set of attitudes $S$ iff $\forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$.
-\end{conjecture}
+  An attitude $f$ is observably included in a set of attitudes $S$ iff $\forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$.
+\end{theorem}
 \begin{proof}
@@
 \end{proof}
-\begin{remark}
-  The opposite of \cref{th:suffFals} is the negation of $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  Thus, for some ${\allleadstog} \in \allleadstos$ and some $i \in I$ with ${\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, we have that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
-
-  For example, $\allargs = \set{\ar_1, \ar_2}$ and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and the attitude contains only people constant to $\phi$ (except that they map $\emptyset$ to anything) and people constant to $¬\phi$ (except that they map $\emptyset$ to anything).
-
-  TODO
-  In that case, if restricting our focus to claims about types of individuals, we need to include the real types, then close under suitable indistinguishability relation (observable inclusion), so as to include for example $i$.
-
-  Define $S$ as the relations in the claim. Define $R(S)$ as the adequate closure: those that we can’t reject.
-  Does $S$ include $R(S)$? If so, it is falsifiable. Otherwise, there is in $R(S)$ a relation that we can’t reject.
-  Let $Impl$ be all impliciations in $S$, of the form: if $\hist$ goes to $p$, then $\hist'$ goes to $p'$ (in the above example: if $a$ goes to $\phi$ then $aa$ goes to $\phi$).
-Any relation that breaks one of these implications is rejectable.
-For example, sending $a$ to $\phi$ and $ab$ to $¬\phi$ is rejectable.We need to include all relations that break no implication.
-  TODO check all this. 
-\end{remark}
+
 \begin{lemma}
@@
 
-\begin{theorem}[To be deleted, probably]
-  Consider the attitude where all individuals are either constant to $\phi$ except that they map $\emptyset$ to anything, or constant to $¬\phi$ except that they map $\emptyset$ to anything, say, $(\phi, \phi)$, $(¬\phi, \phi)$, $(\phi, ¬\phi)$, $(¬\phi, ¬\phi)$.
-  Consider a claim about types of individuals containing all those ones.
-Assume that for some attitude $i$ not in the claim, no $H$ permit to observably exclude $i$ from the claim.
-Then from the lemma above, the claim is not falsifiable.
-So, we need to include all attitudes that no $H$ permit to observably exclude from the claim.
-Iterating, this is the closure under the observable inclusion relation.
-  So, the claim about types must include the real ones and be closed under observable inclusion.
-\end{theorem}
+\begin{remark}
+  The opposite of \cref{th:suffFals} is the negation of $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  Thus, for some ${\allleadstog} \in \allleadstos$ and some $i \in I$ with ${\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, we have that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
+
+  For example, $\allargs = \set{\ar_1, \ar_2}$ and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and the attitude contains only people constant to $\phi$ (except that they map $\emptyset$ to anything) and people constant to $¬\phi$ (except that they map $\emptyset$ to anything), say, $(\phi, \phi)$, $(¬\phi, \phi)$, $(\phi, ¬\phi)$, $(¬\phi, ¬\phi)$.
+
+  In that case, if restricting our focus to claims about types of individuals, we need to include the real types, then close under suitable indistinguishability relation (observable inclusion), so as to include for example $i$.
+
+  Define $S$ as the relations in the claim. Define $R(S)$ as the adequate closure: those that we can’t reject.
+  Does $S$ include $R(S)$? If so, it is falsifiable. Otherwise, there is in $R(S)$ a relation that we can’t reject.
+  Let $Impl$ be all impliciations in $S$, of the form: if $\hist$ goes to $p$, then $\hist'$ goes to $p'$ (in the above example: if $a$ goes to $\phi$ then $aa$ goes to $\phi$).
+Any relation that breaks one of these implications is rejectable.
+For example, sending $a$ to $\phi$ and $ab$ to $¬\phi$ is rejectable.We need to include all relations that break no implication.
+  TODO check all this. 
+\end{remark}
+
 \begin{theorem}

### 2024-04-30 simple.tex
rm claim about types

@@
 
-A claim about types of individuals is a set $C^\text{types} \wsub P^{\allhists}$.
-Given such a set, define the associated claim $C \wsub \allleadstos$ as $C = (C^\text{types})^I = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in C^\text{types}}$.
+Given a set of attitudes $S \wsub P^{\allhists}$, the claim associated to it designates the claim $S^I = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in S}$.
+Say that a claim $C$ is a claim about types iff $\exists S \wsub P^{\allhists} \suchthat C = S^I$.
 \begin{definition}
@@
 
-  Define the extension of a claim about types $C^\text{types} \wsub P^{\allhists}$ to its observably included attitudes as the the claim about types $R(C^\text{types}) = \set{g \in P^{\allhists} \suchthat \forall H \in \finite(\incr(\allhists)): \exists f \in C^\text{types} \suchthat \restr{g}{H} = \restr{f}{H}}$.
-  Note that $C^\text{types} \wsub R(C^\text{types})$. 
+  Define the extension of a set of attitudes $S \wsub P^{\allhists}$ to its observably included attitudes as the set of attitudes $R(S) = \set{g \in P^{\allhists} \suchthat \forall H \in \finite(\incr(\allhists)): \exists f \in S \suchthat \restr{g}{H} = \restr{f}{H}}$.
+  Note that $S \wsub R(S)$. 
   Also note that $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$.
 
-  Define the closure under observable inclusion of a claim about types $C^\text{types}$ as $R^\infty(C^\text{types})$, equivalently, as the smallest set $C^\text{types}_\text{ind}$ such that $R(C^\text{types}_\text{ind}) \wsub C^\text{types}_\text{ind}$.
+  Define the closure under observable inclusion of a claim about types $S$ as $R^\infty(S)$, equivalently, as the smallest set $S_\text{ind}$ such that $R(S_\text{ind}) \wsub S_\text{ind}$.
 
@@
   \label{th:typesfalsifiable}
-  A claim about types of individuals $C^\text{types} \wsub P^{\allhists}$ 
-  satisfies $\forall g \in P^{\allhists} \setminus C^\text{types}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall f \in C^\text{types}: \restr{g}{H} \neq \restr{f}{H}$,
+  A set of attitudes $S \wsub P^{\allhists}$ 
+  satisfies $\forall g \in P^{\allhists} \setminus S: \exists H \in \finite(\incr(\allhists)) \suchthat \forall f \in S: \restr{g}{H} \neq \restr{f}{H}$,
   iff its associated claim is falsifiable or trivial.
@@
   By definition of $C$,
-  $\exists i \in I \suchthat {{\ileadstog}} \notin C^\text{types}$.
+  $\exists i \in I \suchthat {{\ileadstog}} \notin S$.
   As $C$ holds, ${\ileadstog} \notin \set{{\ileadsto[j]} \suchthat j \in I}$ (\cref{th:typesholds}).
-  Pick any $H$ such that $\forall {\ileadstog[j]} \in C^\text{types}: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadstog[j]}(\hist)$.
+  Pick any $H$ such that $\forall {\ileadstog[j]} \in S: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadstog[j]}(\hist)$.
   Define $\theta = \set{(\hist, i, {\ileadstog}(\hist)) \suchthat \hist \in H} \in \Theta \cap \powerset{\allleadstog}$.
-  Then, $\theta \notin C^\wsub$, because $\forall {\ileadstog[j]} \in C^\text{types}: \theta \nsubseteq {\ileadstog[j]}$.
-
-  Conversely, assume that for some ${\ileadstog} \in P^{\allhists} \setminus C^\text{types}$, no $H \in \finite(\incr(\allhists))$ satisfies the indicated condition.
-  Define ${\allleadstog}$ as including ${\ileadstog}$ and for all other individuals, relations from $C^\text{types}$.
+  Then, $\theta \notin C^\wsub$, because $\forall {\ileadstog[j]} \in S: \theta \nsubseteq {\ileadstog[j]}$.
+
+  Conversely, assume that for some ${\ileadstog} \in P^{\allhists} \setminus S$, no $H \in \finite(\incr(\allhists))$ satisfies the indicated condition.
+  Define ${\allleadstog}$ as including ${\ileadstog}$ and for all other individuals, relations from $S$.
   Then, ${\allleadstog} \notin C$, but any observation will be in $C$, thus the claim is not falsifiable and not trivial.
@@
   \label{th:typesholds}
-  Consider a claim about types of individuals $C^\text{types} \wsub P^{\allhists}$. Its associated claim holds iff $\set{{\ileadsto[j]} \suchthat j \in I} \wsub C^\text{types}$.
+  Consider a set of attitudes $S \wsub P^{\allhists}$. Its associated claim holds iff $\set{{\ileadsto[j]} \suchthat j \in I} \wsub S$.
 \end{lemma}
@@
   \label{th:typesanonymous}
-  Given any claim about types of individuals $C^\text{types} \wsub P^{\allhists}$, its associated claim is anonymous.
+  Given any set of attitudes $S \wsub P^{\allhists}$, its associated claim is anonymous.
 \end{lemma}
@@
   Assume that $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  Then, the claim $C$ associated to the claim about types of individuals $C^\text{types} = \set{{\ileadsto[j]} \suchthat j \in I}$ holds, is anonymous, and is falsifiable or trivial.
+  Then, the claim $C$ associated to the set of attitudes $S = \set{{\ileadsto[j]} \suchthat j \in I}$ holds, is anonymous, and is falsifiable or trivial.
 \end{theorem}
@@
 \begin{theorem}
-  If a claim about types of individuals $C^\text{types} \wsub P^{\allhists}$ is not closed under observable inclusion, then it is not falsifiable and not trivial.
-\end{theorem}
-\begin{theorem}
-  Given any situation, if the claim related to the claim about types of individuals $R^\infty({\allleadsto}(I))$ is trivial, then there exists no claim related to a claim about types of individuals that holds and is falsifiable.
-\end{theorem}
-\begin{proof}
-  Consider a claim related to a claim about types of individuals $S$ that holds and that is falsifiable or trivial.
+  If a set of attitudes $S \wsub P^{\allhists}$ is not closed under observable inclusion, then it is not falsifiable and not trivial.
+\end{theorem}
+\begin{theorem}
+  Given any situation, if the claim associated to the set of attitudes $R^\infty({\allleadsto}(I))$ is trivial, then there exists no claim associated to a set of attitudes that holds and is falsifiable.
+\end{theorem}
+\begin{proof}
+  Consider a claim related to a set of attitudes $S$ that holds and that is falsifiable or trivial.
   For it to hold, we need ${\allleadsto}(I) \wsub S$.
@@
 \begin{theorem}
-  Given any situation, the claim about types of individuals $R^\infty({\allleadsto}(I))$ holds, is anonymous, and is falsifiable or trivial.
+  Given any situation, the claim associated to the set of attitudes $R^\infty({\allleadsto}(I))$ holds, is anonymous, and is falsifiable or trivial.
 \end{theorem}

### 2024-04-30 simple.tex
Proof by LLM

@@
   Also note that $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$.
-
-  Define the closure under observable inclusion of a claim about types $S$ as $R^\infty(S)$, equivalently, as the smallest set $S_\text{ind}$ such that $R(S_\text{ind}) \wsub S_\text{ind}$.
+\end{definition}
+\begin{theorem}
+  \label{th:RR}
+  $\forall S \wsub P^{\allhists}: R(R(S)) \wsub R(S)$.
+\end{theorem}
+\begin{proof}
+  Consider any $g \in R(R(S))$.
+  Consider any $H \in \finite(\incr(\allhists))$.
+  There exists $f \in R(S)$ such that $\restr{g}{H} = \restr{f}{H}$.
+  There exists $f' \in S$ such that $\restr{f}{H} = \restr{f'}{H}$.
+  Thus, $\restr{g}{H} = \restr{f'}{H}$.
+  Thus, $g \in R(S)$.
+\end{proof}
+Define the closure under observable inclusion of a claim about types $S$ as $R^\infty(S)$, equivalently, as the smallest set $S'$ such that $S \wsub S'$ and $R(S') \wsub S'$, equivalently, as indicated by \cref{th:RR}, as $R(S)$.
+\begin{remark}
+  A few more, maybe not useful, definitions.
 
@@
   Similarly, given $S$ and $H \in \finite(\incr(\allhists))$, define the equivalence relation $=_H$ on $S$ as $f =_H g$ iff $\restr{f}{H} = \restr{g}{H}$. This also defines the quotient set $S / =_H$.
-\end{definition}
-\begin{remark}
-  A few more, maybe not useful, definitions.
+
   A function $l: \allhists \to \powerset{P^{\allhists}}$ is decreasing iff $\forall \hist \wsub \histp: l(\histp) \wsub l(\hist)$.

### 2024-05-03 simple.tex
Conj closing

@@
 \end{proof}
-Define the closure under observable inclusion of a claim about types $S$ as $R^\infty(S)$, equivalently, as the smallest set $S'$ such that $S \wsub S'$ and $R(S') \wsub S'$, equivalently, as indicated by \cref{th:RR}, as $R(S)$.
-\begin{remark}
-  A few more, maybe not useful, definitions.
-
-  Given a set of attitudes $S$ and $\hist \in \allhists$, define the equivalence relation $=_\hist$ on $S$ as $f =_\hist g$ iff $f(\hist) = g(\hist)$.
-This also defines the quotient set $S / =_\hist$.
-(For the readers used to that terminology: if defining $\beta_\hist \in P^S$ as $\beta_\hist(f) = f(\hist)$, then $=_\hist$ is the equivalence kernel of $\beta_\hist$ and $S / =_\hist$ is the coimage of $\beta_\hist$.)
-  Similarly, given $S$ and $H \in \finite(\incr(\allhists))$, define the equivalence relation $=_H$ on $S$ as $f =_H g$ iff $\restr{f}{H} = \restr{g}{H}$. This also defines the quotient set $S / =_H$.
-
-  A function $l: \allhists \to \powerset{P^{\allhists}}$ is decreasing iff $\forall \hist \wsub \histp: l(\histp) \wsub l(\hist)$.
-  Let $S \wsub P^{\allhists}$ be a set of attitudes.
-  Say that a function $l: \allhists \to \powerset{P^{\allhists}}$ is an $S$-point-labeling function iff $\forall \hist \in \allhists: l(\hist) \in S / =_\hist$.
-  Say that a function $l: \allhists \to \powerset{P^{\allhists}}$ is an $S$-sequence-labeling function iff $\forall \hist \in \allhists: l(\hist) \in S / =_{\intvl{\hist}}$.
-\end{remark}
+Define the closure under observable inclusion of a claim about types $S$ as $R^\infty(S)$, equivalently, as the smallest set $S'$ such that $S \wsub S' = R(S')$, equivalently, as indicated by \cref{th:RR}, as $R(S)$.
+
 Let $\intvl{\hist} = (\hist_i)_{i \in \intvl{0, \card{\hist}}} \in \finite(\incr(\allhists))$ denote the increasing sequence of paths from $\emptyset$ to $\hist$.
 \begin{theorem}
+  \label{th:caractR}
   The $S$-labeling function associated to an attitude $f \in P^{\allhists}$ is the function $l^S_f: \allhists \to \powerset{P^{\allhists}}$ defined as $l^S_f(\hist) = \set{g \in S \suchthat g(\hist) = f(\hist)}$.
 
-  An attitude $f$ is observably included in a set of attitudes $S$ iff $\forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$.
+  We have: $R(S) = \set{f \suchthat \forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset}$.
 \end{theorem}
@@
 \begin{theorem}
-  Given any situation, if the claim associated to the set of attitudes $R^\infty({\allleadsto}(I))$ is trivial, then there exists no claim associated to a set of attitudes that holds and is falsifiable.
+  Given any situation, if the claim associated to the set of attitudes $R({\allleadsto}(I))$ is trivial, then there exists no claim associated to a set of attitudes that holds and is falsifiable.
 \end{theorem}
@@
 In other words, $S$ must be closed under observable inclusion.
-Thus, we need $R^\infty(S) \wsub S$.
+Thus, we need $R(S) \wsub S$.
   Also, because $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$, we need
-  $R^\infty({\allleadsto}(I)) \wsub R^\infty(S) \wsub S$.
+  $R({\allleadsto}(I)) \wsub R(S) \wsub S$.
   It follows that $S$ is trivial.
@@
 \begin{theorem}
-  Given any situation, the claim associated to the set of attitudes $R^\infty({\allleadsto}(I))$ holds, is anonymous, and is falsifiable or trivial.
-\end{theorem}
+  Given any situation, the claim associated to the set of attitudes $R({\allleadsto}(I))$ holds, is anonymous, and is falsifiable or trivial.
+\end{theorem}
+\begin{example}
+  Define $f^{(p, p')} \in P^{\allhists}$ as follows: $f^{(p, p')}(\emptyset) = p$ and $\forall \hist \in \allhists: \hist ≠ \emptyset \implies f^{(p, p')}(\hist) = p'$.
+
+  Consider a situation such that ${\allleadsto}(I) = \set{f^{(p, p')} \suchthat p, p' \in \set{\phi, ¬\phi}}$, thus, containing only people constant to $\phi$ and people constant to $¬\phi$, except that they map $\emptyset$ to anything in $\set{\phi, ¬\phi}$.
+  Define $F^p = \set{f^{(p, p')} \suchthat p' \in \set{\phi, ¬\phi}}$.
+
+  \Cref{th:caractR} indicates that $R({\allleadsto}(I)) = \set{f \suchthat l^S_f(\emptyset) \in \set{F^\phi, F^{¬\phi}} \land \forall \ar \in \allargs: [\forall \hist \suchthat \hist_1 = \ar: l^S_f(\hist) \in l^S_f(\emptyset)] \land [\forall \hist, \histp \suchthat \hist_1 = \histp_1 = \ar: l^S_f(\hist) = l^S_f(\histp)]}$.
+
+  Thus, $R({\allleadsto}(I))$ contains, for each mapping $m: \allargs \rightarrow \set{\phi, ¬\phi}$, the two functions $f_m^\phi, f_m^{¬\phi}$ defined as $f_m^\phi(\emptyset) = \phi$ and $\forall \ar \in \allargs: f_m^\phi((\ar, …)) = m(\ar)$, and similarly for $f_m^{¬\phi}$.
+
+  The claim associated to $R({\allleadsto}(I))$ is not trivial: $\forall f \suchthat [\exists \hist, \histp ≠ \emptyset \suchthat \hist_1 = \histp_1 \land f(\hist) ≠ f(\histp)]: f \notin R({\allleadsto}(I))$.
+\end{example}
+\begin{example}
+  Consider $\allargs = \set{\ar_1, \ar_2}$ and ${\allleadsto}(I) = \set{f \suchthat f(\ar_1) ≠ \phi \lor f(\ar_2) ≠ \phi}$, thus, $f \notin {\allleadsto}(I)$ iff $f(\ar_1) = f(\ar_2) = \phi$.
+
+  Consider any $f \notin {\allleadsto}(I)$.
+  We have $f \in R({\allleadsto}(I))$.
+  Indeed, define $g_1 \in P^{\allhists}$ as $g_1 = f$ except that $g_1(\ar_2) = ¬\phi$, and $g_2 \in P^{\allhists}$ as $g_2 = f$ except that $g_2(\ar_1) = ¬\phi$.
+  Then, $g_1, g_2 \in {\allleadsto}(I)$.
+  Now consider any $H \in \finite(\incr(\allhists))$.
+  If $(\ar_2) \notin H$, then $\restr{f}{H} = \restr{g_1}{H}$; otherwise, $\restr{f}{H} = \restr{g_2}{H}$.
+
+  It follows that the claim associated to $R({\allleadsto}(I))$ is trivial.
+\end{example}
+\begin{remark}
+  A few more, maybe not useful, definitions.
+
+  Given a set of attitudes $S$ and $\hist \in \allhists$, define the equivalence relation $=_\hist$ on $S$ as $f =_\hist g$ iff $f(\hist) = g(\hist)$.
+This also defines the quotient set $S / =_\hist$.
+(For the readers used to that terminology: if defining $\beta_\hist \in P^S$ as $\beta_\hist(f) = f(\hist)$, then $=_\hist$ is the equivalence kernel of $\beta_\hist$ and $S / =_\hist$ is the coimage of $\beta_\hist$.)
+  Similarly, given $S$ and $H \in \finite(\incr(\allhists))$, define the equivalence relation $=_H$ on $S$ as $f =_H g$ iff $\restr{f}{H} = \restr{g}{H}$. This also defines the quotient set $S / =_H$.
+
+  A function $l: \allhists \to \powerset{P^{\allhists}}$ is decreasing iff $\forall \hist \wsub \histp: l(\histp) \wsub l(\hist)$.
+  Let $S \wsub P^{\allhists}$ be a set of attitudes.
+  Say that a function $l: \allhists \to \powerset{P^{\allhists}}$ is an $S$-point-labeling function iff $\forall \hist \in \allhists: l(\hist) \in S / =_\hist$.
+  Say that a function $l: \allhists \to \powerset{P^{\allhists}}$ is an $S$-sequence-labeling function iff $\forall \hist \in \allhists: l(\hist) \in S / =_{\intvl{\hist}}$.
+\end{remark}
+\begin{conjecture}
+  Given a non empty set of attitudes $S \wsub P^{\allhists}$, the claim associated to $R(S)$ is not trivial iff [there exists some $H \in \finite(\incr(\allhists))$ such that some non empty equivalence class $S_H \in S / =_H$ on $S$ over $H$ does not permit all continuations, meaning that $\exists \ar, p \suchthat \forall f \in S_H: f(\max H, \ar) ≠ p$]; or $\exists p \suchthat \forall f \in S: f(\emptyset) ≠ p$.
+\end{conjecture}
+\begin{proof}
+  We want to show that $\exists f \in P^{\allhists}, \hist \in \allhists \suchthat \cap_{\histp \wsub \hist} l^S_f(\histp) = \emptyset$ is equivalent to the stated consequent.
+
+  Assuming that the consequent holds, consider any $f$ such that $\restr{f}{H} = \restr{g}{H}$ for some (equivalently, for all) $g \in S$ and such that $f(\max H, \ar) = p$ (or pick $H = \ar = \emptyset$).
+  We have $\cap_{\histp \wsub (\max H, \ar)} l^S_f(\histp) = \emptyset$.
+
+  Consider any $f, \hist \suchthat \cap_{\histp \wsub \hist} l^S_f(\histp) = \emptyset$ and let’s prove that the consequent holds.
+  As $S ≠ \emptyset$, $l^S_f(\hist) ≠ \emptyset$.
+  Consider the longest subsequence of $\hist$ such that $l^S_f(\histp) ≠ \emptyset$.
+\end{proof}
+
+Generally,
+define $S^p = \set{f \in P^{\allhists} \suchthat f(\emptyset) = p}$.
+Then \cref{th:caractR} indicates that $R({\allleadsto}(I)) = \set{f \suchthat l^S_f(\emptyset) \in \set{S^p \suchthat p \in P} \land \forall \ar \in \allargs: [\forall \hist \suchthat \hist_1 = \ar: l^S_f(\hist) \in l^S_f(\emptyset)] \land [\forall \hist, \histp \suchthat \hist_1 = \histp_1 = \ar: l^S_f(\hist) = l^S_f(\histp)]}$.
+TODO correct this.
 
@@
 
-  For example, $\allargs = \set{\ar_1, \ar_2}$ and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and the attitude contains only people constant to $\phi$ (except that they map $\emptyset$ to anything) and people constant to $¬\phi$ (except that they map $\emptyset$ to anything), say, $(\phi, \phi)$, $(¬\phi, \phi)$, $(\phi, ¬\phi)$, $(¬\phi, ¬\phi)$.
+  For example,  and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and
 

### 2024-05-03 simple.tex
Simple conf R(S)

@@
 \begin{conjecture}
-  Given a non empty set of attitudes $S \wsub P^{\allhists}$, the claim associated to $R(S)$ is not trivial iff [there exists some $H \in \finite(\incr(\allhists))$ such that some non empty equivalence class $S_H \in S / =_H$ on $S$ over $H$ does not permit all continuations, meaning that $\exists \ar, p \suchthat \forall f \in S_H: f(\max H, \ar) ≠ p$]; or $\exists p \suchthat \forall f \in S: f(\emptyset) ≠ p$.
+  Given a non empty set of attitudes $S \wsub P^{\allhists}$, the claim associated to $R(S)$ is not trivial iff $\exists \hist \in \allhists, f \in P^{\intvl{\hist}} \suchthat \forall g \in S: \restr{g}{\intvl{hist}} ≠ f$.
 \end{conjecture}
 \begin{proof}
-  We want to show that $\exists f \in P^{\allhists}, \hist \in \allhists \suchthat \cap_{\histp \wsub \hist} l^S_f(\histp) = \emptyset$ is equivalent to the stated consequent.
-
-  Assuming that the consequent holds, consider any $f$ such that $\restr{f}{H} = \restr{g}{H}$ for some (equivalently, for all) $g \in S$ and such that $f(\max H, \ar) = p$ (or pick $H = \ar = \emptyset$).
-  We have $\cap_{\histp \wsub (\max H, \ar)} l^S_f(\histp) = \emptyset$.
-
-  Consider any $f, \hist \suchthat \cap_{\histp \wsub \hist} l^S_f(\histp) = \emptyset$ and let’s prove that the consequent holds.
-  As $S ≠ \emptyset$, $l^S_f(\hist) ≠ \emptyset$.
-  Consider the longest subsequence of $\hist$ such that $l^S_f(\histp) ≠ \emptyset$.
-\end{proof}
+  This follows from the equivalence of the antecedent with $\exists f \in P^{\allhists}, \hist \in \allhists \suchthat \cap_{\histp \wsub \hist} l^S_f(\histp) = \emptyset$.
+\end{proof}
+Thus, a situation $S$ does not admit falsifiable theories (meaning that $R(S)$ is associated to the trivial claim) iff $\forall \hist, f, \exists g \in S \suchthat \restr{g}{\intvl{\hist}} = f$.
 

### 2024-05-06 simple.tex
False conj about strict claims about types instead of weak ones

@@
 Say that a claim $C$ is a claim about types iff $\exists S \wsub P^{\allhists} \suchthat C = S^I$.
+Informally, such a claim claims that the set of attitudes in $I$ is contained in $S$ (though might be a strict subset of $S$), or equivalently, that no attitude out of $S$ exists among $I$.
 \begin{definition}
@@
 
-  The claim associated to $R({\allleadsto}(I))$ is not trivial: $\forall f \suchthat [\exists \hist, \histp ≠ \emptyset \suchthat \hist_1 = \histp_1 \land f(\hist) ≠ f(\histp)]: f \notin R({\allleadsto}(I))$.
+  The claim associated to $R({\allleadsto}(I))$ is not trivial: $\forall f \suchthat [\exists \hist, \histp \ssub \hist \suchthat f(\histp) ≠ f(\hist)]: f \notin R({\allleadsto}(I))$.
 \end{example}
@@
 \end{remark}
+\begin{theorem}
+  Given $\hist \in \allhists$, define $\restr{S}{\intvl{\hist}} = \set{\restr{f}{\intvl{\hist}} \suchthat f \in S}$.
+  Given a non empty set of attitudes $S \wsub P^{\allhists}$, the following statements are equivalent.
+  \begin{itemize}
+    \item The claim associated to $R(S)$ is not trivial 
+    \item $R(S) ≠ P^{\allhists}$
+    \item $\exists \hist \in \allhists, f \in P^{\intvl{\hist}} \suchthat \forall g \in S: \restr{g}{\intvl{hist}} ≠ f$
+    \item $\exists \hist, f \in P^{\intvl{\hist}} \suchthat f \notin \restr{S}{\intvl{\hist}}$
+    \item $\exists \hist \suchthat P^{\intvl{\hist}} \not\wsub \restr{S}{\intvl{\hist}}$.
+  \end{itemize}
+  Also, the following statements are equivalent.
+  \begin{itemize}
+    \item The claim associated to $R(S)$ is trivial
+    \item $R(S) = P^{\allhists}$
+    \item $\forall \hist, f, \exists g \in S \suchthat \restr{g}{\intvl{\hist}} = f$
+    \item $\forall \hist: P^{\intvl{\hist}} \wsub \restr{S}{\intvl{\hist}}$.
+  \end{itemize}
+  Furthermore, $\forall \hist: P^{\intvl{\hist}} \wsub \restr{S}{\intvl{\hist}} \implies \card{S} \notin \N$.
+\end{theorem}
+\begin{proof}
+  This follows from $R(S) ≠ P^{\allhists} \iff \exists f \in P^{\allhists}, \hist \in \allhists \suchthat \cap_{\histp \wsub \hist} l^S_f(\histp) = \emptyset$.
+\end{proof}
+
+To recap, we now know that with $S = {\allleadsto}(I)$, when $R(S) ≠ P^{\allhists}$, there is a claim that holds and is anonymous and falsifiable.
+This includes all situations with finite behaviors ($\card{S} \in \N$), thus includes all situations with finite $I$.
+Consider now situations such that $R({\allleadsto}(I)) = P^{\allhists}$.
+
+Define $I = P^\N$ and ${\ileadsto} = i \circ \card$, so that $S = {\allleadsto}(I) = \set{l \circ \card \in P^{\allhists} \suchthat l \in P^\N}$.
+We have $R(S) = P^{\allhists}$.
+The function $f(\ar) ≠ f(\ar')$, for example, is not in $S$.
+
 \begin{conjecture}
-  Given a non empty set of attitudes $S \wsub P^{\allhists}$, the claim associated to $R(S)$ is not trivial iff $\exists \hist \in \allhists, f \in P^{\intvl{\hist}} \suchthat \forall g \in S: \restr{g}{\intvl{hist}} ≠ f$.
+  Consider a mapping ${\allleadstog} \in (P^{\allhists})^I$. Define $E$ as the equivalence classes in $I$ that considers as equivalent all $i$ mapped to the same element of $P^{\allhists}$.
+  A wide-shuffling over $I$ is a mapping $\sigma_{\allleadstog} \in I^I$ that reaches any equivalence class in $E$, thus $\forall e \in E: \exists i \suchthat \sigma_{\allleadstog}(i) \in e$.
+  The bijections over $I^I$ are a subset of the wide-shufflings (those that also are bijections per $e \in E$, thus $\forall e \in E: \restr{\sigma_{\allleadstog}}{e}$ bijects with its image).
+
+  A claim $C$ is not about types iff $\exists {\allleadstog} \in C$ and $\sigma_{\allleadstog}$, a wide-shuffling, such that $({\allleadstog} \circ \sigma_{\allleadstog}) \notin C$.
 \end{conjecture}
 \begin{proof}
-  This follows from the equivalence of the antecedent with $\exists f \in P^{\allhists}, \hist \in \allhists \suchthat \cap_{\histp \wsub \hist} l^S_f(\histp) = \emptyset$.
-\end{proof}
-Thus, a situation $S$ does not admit falsifiable theories (meaning that $R(S)$ is associated to the trivial claim) iff $\forall \hist, f, \exists g \in S \suchthat \restr{g}{\intvl{\hist}} = f$.
-
-Generally,
-define $S^p = \set{f \in P^{\allhists} \suchthat f(\emptyset) = p}$.
-Then \cref{th:caractR} indicates that $R({\allleadsto}(I)) = \set{f \suchthat l^S_f(\emptyset) \in \set{S^p \suchthat p \in P} \land \forall \ar \in \allargs: [\forall \hist \suchthat \hist_1 = \ar: l^S_f(\hist) \in l^S_f(\emptyset)] \land [\forall \hist, \histp \suchthat \hist_1 = \histp_1 = \ar: l^S_f(\hist) = l^S_f(\histp)]}$.
-TODO correct this.
-
-\begin{remark}
-  The opposite of \cref{th:suffFals} is the negation of $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  Thus, for some ${\allleadstog} \in \allleadstos$ and some $i \in I$ with ${\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, we have that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
-
-  For example,  and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and
-
-  In that case, if restricting our focus to claims about types of individuals, we need to include the real types, then close under suitable indistinguishability relation (observable inclusion), so as to include for example $i$.
-
-  Define $S$ as the relations in the claim. Define $R(S)$ as the adequate closure: those that we can’t reject.
-  Does $S$ include $R(S)$? If so, it is falsifiable. Otherwise, there is in $R(S)$ a relation that we can’t reject.
-  Let $Impl$ be all impliciations in $S$, of the form: if $\hist$ goes to $p$, then $\hist'$ goes to $p'$ (in the above example: if $a$ goes to $\phi$ then $aa$ goes to $\phi$).
-Any relation that breaks one of these implications is rejectable.
-For example, sending $a$ to $\phi$ and $ab$ to $¬\phi$ is rejectable.We need to include all relations that break no implication.
-  TODO check all this. 
-\end{remark}
-
+  % Consider that $\exists {\allleadstog} \in C$ and $\sigma_{\allleadstog}$, a wide-shuffling, such that $({\allleadstog} \circ \sigma_{\allleadstog}) \notin C$.
+  Consider a claim $C$ about types $S$.
+  Consider any ${\allleadstog} \in C$ and $\sigma_{\allleadstog}$, a wide-shuffling.
+  As ${\allleadstog} \in C$, we have ${\allleadstog}(I) \wsub S$.
+  Also, ${\allleadstog}(\sigma_{\allleadstog}(I)) = {\allleadstog}(I)$. 
+  Thus, ${\allleadstog}(\sigma_{\allleadstog}(I)) \wsub S$.
+  Thus, $({\allleadstog} \circ \sigma_{\allleadstog}) \in C$.
+
+  About the converse, given $C$, 
+  define $S = \bigcup_{{\allleadstog} \in C}({\allleadstog}(I))$,
+  and assuming that 
+  $[\forall {\allleadstog} \in C, \sigma_{\allleadstog}: ({\allleadstog} \circ \sigma_{\allleadstog}) \in C]$, let us show that 
+  $C = S^I$, equivalently, that $C = \set{{\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \wsub S}$.
+  First, considering any ${\allleadstog} \in C$, we have ${\allleadstog}(I) \wsub S$ by definition of $S$.
+  Second, considering any ${\allleadstog} \notin C$, 
+\end{proof}
+\begin{conjecture}
+  Consider a claim that is not about types but is anonymous. What’s that?
+  Example: the claim “everyone has the same behavior”.
+
+  Example 2, with $\card{I} = 3$: “exactly two individuals have behavior 1”.
+
+  Is there an example with infinitely many behaviors?
+  The claim must be not about types.
+If non empty, the claim includes some mapping in $(P^{\allhists})^I$.
+If not about types, some such mapping has not all correspondances shuffling $I$ in any number but keeping the same range?
+
+  Is it that if there is a claim anonymous, holding, and fals., then there is a claim about types that is anonymous, holds, and fals?
+\end{conjecture}
 \begin{theorem}

### 2024-05-06 simple.tex
Second attempt about claims about (strict) types also seems to fail

@@
 \begin{conjecture}
-  Consider a mapping ${\allleadstog} \in (P^{\allhists})^I$. Define $E$ as the equivalence classes in $I$ that considers as equivalent all $i$ mapped to the same element of $P^{\allhists}$.
-  A wide-shuffling over $I$ is a mapping $\sigma_{\allleadstog} \in I^I$ that reaches any equivalence class in $E$, thus $\forall e \in E: \exists i \suchthat \sigma_{\allleadstog}(i) \in e$.
-  The bijections over $I^I$ are a subset of the wide-shufflings (those that also are bijections per $e \in E$, thus $\forall e \in E: \restr{\sigma_{\allleadstog}}{e}$ bijects with its image).
-
-  A claim $C$ is not about types iff $\exists {\allleadstog} \in C$ and $\sigma_{\allleadstog}$, a wide-shuffling, such that $({\allleadstog} \circ \sigma_{\allleadstog}) \notin C$.
+  Consider a mapping ${\allleadstog} \in (P^{\allhists})^I$. 
+  Define $E$ as the equivalence classes in $I$ that considers as equivalent all $i$ mapped to the same element of $P^{\allhists}$.
+  Recall that the bijections over $I$ are the subset of $I^I$ that are bijections per $e \in E$, thus $s \in I^I$ is a bijection over $I$ iff $\forall e \in E: \restr{s}{e}$ bijects with its image.
+
+  A claim $C$ is not about types iff $\exists {\allleadstog} \in C, s \in I^I \suchthat ({\allleadstog} \circ s) \notin C$.
 \end{conjecture}
 \begin{proof}
-  % Consider that $\exists {\allleadstog} \in C$ and $\sigma_{\allleadstog}$, a wide-shuffling, such that $({\allleadstog} \circ \sigma_{\allleadstog}) \notin C$.
-  Consider a claim $C$ about types $S$.
-  Consider any ${\allleadstog} \in C$ and $\sigma_{\allleadstog}$, a wide-shuffling.
+  Consider a claim $C$ about types $S$,
+  thus,
+  $C = S^I = \set{{\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \wsub S}$.
+  Consider any ${\allleadstog} \in C$ and $s \in I^I$.
   As ${\allleadstog} \in C$, we have ${\allleadstog}(I) \wsub S$.
-  Also, ${\allleadstog}(\sigma_{\allleadstog}(I)) = {\allleadstog}(I)$. 
-  Thus, ${\allleadstog}(\sigma_{\allleadstog}(I)) \wsub S$.
-  Thus, $({\allleadstog} \circ \sigma_{\allleadstog}) \in C$.
+  Also, ${\allleadstog}(s(I)) \wsub {\allleadstog}(I)$. 
+  Thus, ${\allleadstog}(s(I)) \wsub S$.
+  Thus, $({\allleadstog} \circ s) \in C$.
 
@@
   and assuming that 
-  $[\forall {\allleadstog} \in C, \sigma_{\allleadstog}: ({\allleadstog} \circ \sigma_{\allleadstog}) \in C]$, let us show that 
-  $C = S^I$, equivalently, that $C = \set{{\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \wsub S}$.
+  $[\forall {\allleadstog} \in C, s: ({\allleadstog} \circ s) \in C]$, let us show that 
+  $C = \set{{\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \wsub S}$.
   First, considering any ${\allleadstog} \in C$, we have ${\allleadstog}(I) \wsub S$ by definition of $S$.
-  Second, considering any ${\allleadstog} \notin C$, 
+  Second, considering any ${\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \in S$,
+
 \end{proof}

### 2024-05-13 simple.tex
Pbl stated
some attempts at counter-examples

@@
 
+\begin{theorem}
+  Given a claim $C$, define $S_C \wsub P^{\allhists}$ as $S_C = \bigcup_{{\allleadstog} \in C}({\allleadstog}(I))$.
+  A claim $C$ is about types iff $C = (S_C)^I$.
+\end{theorem}
+\begin{proof}
+  If the consequent holds, then $C$ is about types, by definition.
+  If a claim is about types $S$, then consider any $f \in S$, we have $C = S^I$ thus for ${\allleadstog}$ defined as ${\allleadstog}(I) = \set{f}$ we have ${\allleadstog} \in C$, thus $f \in S_C$; and consider any $f \in S_C$, consider any ${\allleadstog} \in C \suchthat f \in {\allleadstog}(I)$, we have ${\allleadstog} \in S^I$, thus $f \in S$.
+\end{proof}
+
+\begin{theorem}
+  Consider a falsifiable and anonymous claim $C$ such that $\exists {\allleadstog} \in C, f_1, f_2 \suchthat {\allleadstog}(I) = \set{f_1, f_2} \land \card{\set{i \in I \suchthat {\allleadstog}(i) = f_1}} \notin \N \land \card{\set{i \in I \suchthat {\allleadstog}(i) = f_2}} \notin \N$.
+  Then, $\forall {\allleadstog} \suchthat {\allleadstog}(I) \wsub \set{f_1, f_2}: {\allleadstog} \in C$.
+\end{theorem}
+\begin{proof}
+  Consider any anonymous claim $C$ satisfying the antecedent and any ${\allleadstog'} \suchthat {\allleadstog'}(I) \wsub \set{f_1, f_2} \land {\allleadstog'} \notin C$. 
+  To show that $C$ is not falsifiable,
+  consider any observable subset of $\allleadstog'$ and let us show that it is completable in $C$.
+
+  From the antecedent we see that $I$ is infinite.
+  Define $I_k$ as the individuals that the observable interrogates and satisfying ${\allleadstog'}(i) = f_k$.
+  Consider sets of same sizes $I'_1$ and $I'_2$ among the non observed individuals (meaning those in $I \setminus I_1 \setminus I_2$) and with corresponding types in ${\allleadstog}$ (so that $\forall i \in I'_k: {\allleadstog}(i) = f_k$).
+  Define a bijection $\sigma$ that sends $I_1$ to $I'_1$ and $I_2$ to $I'_2$, and conversely, and that sends the elements of $I \setminus (\cup_k I_k) \setminus (\cup_k I'_k)$ to themselves.
+  The resulting relation ${\allleadstog} \circ \sigma$ is in $C$ and is compatible with the observable.
+\end{proof}
+
 \begin{conjecture}
-  Consider a mapping ${\allleadstog} \in (P^{\allhists})^I$. 
-  Define $E$ as the equivalence classes in $I$ that considers as equivalent all $i$ mapped to the same element of $P^{\allhists}$.
-  Recall that the bijections over $I$ are the subset of $I^I$ that are bijections per $e \in E$, thus $s \in I^I$ is a bijection over $I$ iff $\forall e \in E: \restr{s}{e}$ bijects with its image.
-
-  A claim $C$ is not about types iff $\exists {\allleadstog} \in C, s \in I^I \suchthat ({\allleadstog} \circ s) \notin C$.
+  If there is a claim anonymous, holding, and fals., then there is a claim about types that holds and is falsifiable.
 \end{conjecture}
 \begin{proof}
-  Consider a claim $C$ about types $S$,
-  thus,
-  $C = S^I = \set{{\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \wsub S}$.
-  Consider any ${\allleadstog} \in C$ and $s \in I^I$.
-  As ${\allleadstog} \in C$, we have ${\allleadstog}(I) \wsub S$.
-  Also, ${\allleadstog}(s(I)) \wsub {\allleadstog}(I)$. 
-  Thus, ${\allleadstog}(s(I)) \wsub S$.
-  Thus, $({\allleadstog} \circ s) \in C$.
-
-  About the converse, given $C$, 
-  define $S = \bigcup_{{\allleadstog} \in C}({\allleadstog}(I))$,
-  and assuming that 
-  $[\forall {\allleadstog} \in C, s: ({\allleadstog} \circ s) \in C]$, let us show that 
-  $C = \set{{\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \wsub S}$.
-  First, considering any ${\allleadstog} \in C$, we have ${\allleadstog}(I) \wsub S$ by definition of $S$.
-  Second, considering any ${\allleadstog} \in (P^{\allhists})^I \suchthat {\allleadstog}(I) \in S$,
-
-\end{proof}
-\begin{conjecture}
-  Consider a claim that is not about types but is anonymous. What’s that?
-  Example: the claim “everyone has the same behavior”.
-
-  Example 2, with $\card{I} = 3$: “exactly two individuals have behavior 1”.
-
-  Is there an example with infinitely many behaviors?
+  For a counter-example, we need a situation such that the closure for falsifiability of $\set{{\allleadsto} \circ \sigma}$ is not the whole of $\allleadstos$ and $R({\allleadsto}(I)) = P^{\allhists}$.
+  Equivalently, we need a situation such that the closure for falsifiability of $\set{{\allleadsto} \circ \sigma}$ is not the whole of $\allleadstos$ and $\forall \hist \in \allhists: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$.
+
+  A counter-example could be a situation where exactly one individual given $\emptyset$ chooses $\phi$, with the claim: “there is at most one individual who given $\emptyset$ chooses $\phi$”.
+  Nope, this seems to admit a claim about types, as then there is finitely many individuals satisfying $\emptyset$ to $\phi$ and hence some of these functions can be excluded.
+
+  The interesting case is a situation including infinitely many behaviors (not necessarily all), otherwise a claim about types exists.
+  In such a case, can we find a true claim that is anonymous and fals but not about types?
+
+  Consider a true claim $C$. It contains the true situation, thus involving $f_1, …$. Say it includes infinitely many $f_1$ and exactly one $f_2$.
+  A hypothetical situation with infinitely many $f_1$ and exactly two $f_2$ can be distinguished.
+
+  Consider the claim “there is exactly one behavior of each kind”.
+That is not fals because excludes the possibility that $f_1$ is not there (and if it’s not, impossible to observe).
+Even if $C$ admits that any finite number of behaviors may miss, it’s still not fals: if all odd $f$ miss (we have all even $f$ and no more), we will never prove it.
+  In fact, if an infinite subset of the support is there, it is not empirically distinguishable from all the subset is there; thus the claim must admit for all infinite strict subsets as well.
+  Thus, the claim could be “there is at most one behavior of each kind”.
+  “Kind” here must be: satisfying a given function in $P^{\intvl{\hist}}$ (more is not counter-observable).
+
+  Thus, consider the claim that $\forall \hist, f \in P^{\intvl{\hist}}: $ there is at one one behavior satisfying $f$. Well, that is self-contradicting.
+
   The claim must be not about types.
 If non empty, the claim includes some mapping in $(P^{\allhists})^I$.
-If not about types, some such mapping has not all correspondances shuffling $I$ in any number but keeping the same range?
-
-  Is it that if there is a claim anonymous, holding, and fals., then there is a claim about types that is anonymous, holds, and fals?
-\end{conjecture}
-\begin{theorem}
-  Consider the attitude above. Is there a claim that holds and is anonymous and falsifiable?
-  Check \cref{ex:falsAnonIfBig}.
-\end{theorem}
+If not about types, some such mapping has not all correspondances picking from various elements in $C$.
+But it is also not simply a bijection over $I$: either it picks from multiple elements of $C$, or it picks in different numbers.
+
+  In fact, if an anonymous and falsifiable claim includes a relation that includes an infinite number of $f_1$ and an infinite number of $f_2$ and so on, then I believe that the claim must also include the relations that include any finite number of $f_1$, because that case is impossible to distinguish empirically.
+
+  Check also \cref{ex:falsAnonIfBig}.
+\end{proof}
 

### 2024-05-13 simple.tex
Conj seems okay

@@
 
-  A counter-example could be a situation where exactly one individual given $\emptyset$ chooses $\phi$, with the claim: “there is at most one individual who given $\emptyset$ chooses $\phi$”.
-  Nope, this seems to admit a claim about types, as then there is finitely many individuals satisfying $\emptyset$ to $\phi$ and hence some of these functions can be excluded.
+  In other words, we look for, given $\allleadsto$ satisfying $\forall \hist \in \allhists: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$, a possible observable that is not compatible with any ${\allleadsto} \circ \sigma$.
+
+  To prove the conjecture, given $\allleadsto$ satisfying $\forall \hist \in \allhists: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$, consider any observable whatsoever, $O \in \allpriobss$, and let us show that for some bijection $\sigma$ over $I$, $O \wsub ({\allleadsto} \circ \sigma)$.
+
+  A counter-example could be a situation “at most one of each possible behavior”.
+  Nope: if there’s twice the same behavior, we cannot observe it for sure.
 

### 2024-05-13 simple.tex
Conjecture is now a theorem

@@
 
+\begin{theorem}
+  The two following statements are equivalent. 
+  \begin{itemize}
+    \item $\forall \hist: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$
+    \item There exists no anonymous claim that holds and is falsifiable.
+  \end{itemize}
+\end{theorem}
+\begin{proof}
+  If the first one is false, then the claim $R({\allleadsto}(I))$ is not trivial, thus is falsifiable.
+
+  If the first one holds, let us show that starting from $C^\text{HA}$ and integrating all relations that are not observably distinguishable, we obtain the trivial claim.
+
+  Consider any observable whatsoever, $O \in \allpriobss$, and let us show that for some bijection $\sigma$ over $I$, $O \wsub ({\allleadsto} \circ \sigma)$.
+
+  For each of the (finitely many) individuals that $O$ contains, we can find a different behavior $f_i$ that is in $\restr{{\allleadsto}(I)}{\intvl{\hist}}$, thus, with some $j_i \in I \suchthat {\allleadsto}(j_i) = f_i$, and that is compatible with what $O$ sees of $i$.
+We define $\sigma$ so that it maps each of those individuals $i$ to the individual $j_i$ with the corresponding behavior.
+  The resulting relation ${\allleadsto} \circ \sigma$ is compatible with the observable.
+
+  It follows that if the claim is not trivial, it is not falsifiable: pick any relation missing in the claim; it cannot be rejected by any observable.
+\end{proof}
+
 \begin{conjecture}

### 2024-05-20 simple.tex
Defs indicative (truly, newly)

@@
 While $I$ and $\allargs$ are fundamental sets whose elements are considered elementary, a few notations and concepts are required to define ${\allleadsto}$.
-Throughout the article, $\N$ includes zero and $\N^* = \N \setminus \set{0}$.
-Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \N^*: \intvl{j, 0} = \emptyset$).
-Define $\allhists = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence.
+Throughout the article, $\Z$ designates the integers (including $0$) and $\Zp = \Z \setminus \set{0}$ designates the positive numbers.
+Given $j, l \in \Z$, the notation $\intvl{j, l}$ represents $\set{k \in \Z \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \Zp: \intvl{j, 0} = \emptyset$).
+Define $\allhists = \bigcup_{k \in \Z} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence.
 A generic element of $\allhists$ (a possibly empty finite sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path.
-Its length is denoted by $\card{\hist} \in \N$ and its elements, $\hist(k)$ or $\hist_k$.
+Its length is denoted by $\card{\hist} \in \Z$ and its elements, $\hist(k)$ or $\hist_k$.
 Thus, given an argumentative path $\hist \in \allhists$, $\forall k \in \intvl{1, \card{\hist}}: \hist(k) = \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$.
-A path $\hist$ is a sub-path of another path $\histp$ whenever $\hist \subseteq \histp$, thus, $\forall k \in \intvl{1, \card{\hist}}: \hist_k = \histp_k$.
+A path $\hist \in \allhists$ is a prefix of a path $\histp \in \allhists$ whenever $\hist \subseteq \histp$, thus, $\forall k \in \intvl{1, \card{\hist}}: \hist_k = \histp_k$.
+Given any $\hist \in \allhists$, $\intvl{\hist} = \set{\restr{\hist}{\intvl{1, k}} \suchthat k \in \intvl{0, \card{\hist}}}$ denotes the set of prefixes of $\hist$.
 
@@
 
+Given an behavior function $\allleadstog$, deliberated choices are represented by an element $\pi({\allleadstog}) \subseteq I × P$ (thus with $\pi({\allleadsto})(i) = P_i$) which is right unique (meaning that $\forall i \in I: \card{\pi({\allleadstog})(i)} ≤ 1$).
+Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\allleadstog}) \in (P \cup \set{\emptyset})^I$.
+
 \subsection{An example and a discussion about observability}
-The following toy example is inspired by an argument from \citet[p.~59]{railton_facts_2003}. Here is his argument.
+The following toy example is inspired by the following argument from \citet[p.~59]{railton_facts_2003}.
 \begin{quote}
@@
 
-  If the prediction described in the quote applies to $i$, the relation $\ileadsto$ is as follows, $\forall k \in \N^*$ (recall that for $\args \subseteq \allargs$, $\args^k$ represents the set of sequences of length $k$ using arguments from $\args$): $\forall \hist \in \set{a_e}^k, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_1, a_2}^k, \hist \ileadsto \prop_1$; $\forall \hist \in \set{a_1, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_2, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \allargs^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$.
+  If the prediction described in the quote applies to $i$, the relation $\ileadsto$ is as follows, $\forall k \in \Zp$ (recall that for $\args \subseteq \allargs$, $\args^k$ represents the set of sequences of length $k$ using arguments from $\args$): $\forall \hist \in \set{a_e}^k, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_1, a_2}^k, \hist \ileadsto \prop_1$; $\forall \hist \in \set{a_1, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_2, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \allargs^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$.
 The values of ${\allleadsto}(i, \hist)$ for $\hist = \emptyset$ and for $\hist \in \allargs^k \suchthat a_e \notin \histend$ are undetermined by the prediction, but whatever they are, $a_e$ is a decisive argument for $\prop_2$, hence, $i$’s deliberated choice is $\prop_2$.
@@
 % Such a deduction should use, as much as possible, the observational basis, that is, the propositions of the form $\alpha \ileadsto p$ that can be obtained experimentally.
-Note first that given a relation ${\allleadstog} \in \allleadstos$, $\powerset{\allleadstog}$ denotes the set of relations over $(I × \allhists) × P$ that refine $\allleadstog$ (thus, each element $f \in \powerset{\allleadstog}$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhists)$).
+Note first that given a relation ${\allleadstog} \in \allleadstos$, $\powerset{\allleadstog}$ denotes the set of relations over $(I × \allhists) × P$ that refine $\allleadstog$ (thus, each element $f \in \powerset{\allleadstog}$ is right-unique but non necessarily total, meaning that it does not necessarily cover $I × \allhists$).
 
@@
 
-Given a pair $(I, \allargs)$, an observation $θ \in \Theta$ is a right unique finite subset of $(I × \allhists) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
-The set $\Theta$ contains the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
-We say that an observation $\theta$ is compatible with a claim $C$ iff
-$\theta \in C^\subseteq$, equivalently, iff
-$\theta \in \cup_{{\allleadstog} \in C} \powerset{\allleadstog}$.
+Define the increasing sets of paths as the set $\incr(\allhists) = \set{H \fsub \allhists \suchthat \card(H) ≤ \card(H') \implies H \wsub H'} \wsub \powerset{\allhists}$.
+A set of paths $H \in \incr(\allhists)$ can be strictly ordered by the lengths of the paths in $H$ and can thus also be considered as a sequence of paths.
+Note that $\incr(\allhists)$ includes both the empty set of paths $\emptyset$ and the set of paths $\set{\emptyset}$ containing only the empty path.
+A non empty set of paths $H \in \incr(\allhists)$ has a unique maximal element $\set{\max H} = \set{\hist \in H \suchthat \forall \histp \in H: \histp \wsub \hist}$.
+A non empty set of paths $H \in \incr(\allhists)$ contains all its prefixes (meaning, $\forall \hist \in H: \set{\histp \wsub \hist} \wsub H$) iff $H = \intvl{\max H}$.
+Let $\finite(\incr(\allhists)^I)$ denote the functions $f: I \mapsto \incr(\allhists)$ with finite support, thus, satisfying $\card{f^{-1}(\incr(\allhists) \setminus \emptyset)} \in \N$.
+An element $Q \in \allpriobss$ \commentOC{previously denoted $O$ and called a priori observation} is called a query.
+\commentOC[Note that $\incr(\allhists)^I$ and $\allpriobss$ are downwards closed, meaning that $\forall O \in \incr(\allhists)^I: \set{O' \subseteq O} \wsub \incr(\allhists)^I$ and $\forall O \in \allpriobss: \set{O' \subseteq O} \wsub \allpriobss$.]{To be deleted.}
+
+An observation associates to a query an element of $P$ per queried element, thus, the set of possible observations is $\Theta = \cup_{Q \in \allpriobss} P^Q$.
+In other words, an observation $θ \in \Theta$ is a right unique finite subset of $(I × \allhists) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
+Given an observation $\theta$, let $\theta^{-1}(P) \in \allpriobss$ denote the queried elements in $\theta$, which can also be considered as $\theta^{-1}(P) \subseteq I × \allhists$, the pairs $(i, \hist)$ in $\theta$.
+Similarly, we can view an observation $\theta$ as a function $\theta: I \mapsto \cup_{H \in \incr(\allhists)} P^H$ and thus $\Theta = \finite((\cup_{H \in \incr(\allhists)} P^H)^I)$, where $\finite$ designates the finite relations (considered as a set of triples).
+\commentOC[Note that $(\cup_{H \in \max \incr(\allhists)}P^H)^I$ is the set of functions that associate to each $I$ a maximal increasing sequence of paths, together with values from $P$.]{To be deleted.}
+
+\commentOC[Let also $\max\incr(\allhists) = \set{A \in \incr(\allhists) \suchthat \nexists A' \in \incr(\allhists) \suchthat A \subset A'}$ being equal to $\set{A \in \incr(\allhists) \cap (\allhists)^\Z}$ denote the maximal elements of $\incr(\allhists)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\Z$.]{To be deleted.}
+
+We say that an observation $\theta$ is compatible with a behavior ${\allleadstog} \in \allleadstos$ iff $\theta \subseteq \powerset{\allleadstog}$, that is, $\forall (i, \hist, p) \in \theta: (i, \hist, p) \in \powerset{\allleadstog}$.
 Thus, given ${\allleadstog} \in \allleadstos$, the set $\Theta \cap \powerset{\allleadstog}$ is the set of observations compatible with ${\allleadstog}$.
-
-Given an observation $\theta$, let $\theta^{-1}(P) \subseteq I × \allhists$ denote the pairs $(i, \hist)$ in $\theta$.
-Let $\incr(\allhists) = \set{\emptyset} \cup \cup_{\emptyset \neq N \subseteq \N} \set{A(N) \suchthat A \in (\allhists)^N \land [\card{A_i} = i] \land [i < j \implies A_i \subsetneq A_j]} \subseteq \powerset{\allhists}$ denote the possibly empty embedded sequences of paths.
-\commentOC{TODO define $\incr(\allhists) = \set{H \wsub \allhists \suchthat \card(H) ≤ \card(H') \implies H \wsub H'}$.}
-An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhists)$.
-Therefore, we let $\finite(\incr(\allhists)^I) = \set{\theta^{-1}(P) \suchthat \theta \in \Theta}$ denote the set of possible observations restricted to $I × \allhists$, the elements of which being called \emph{a priori observation}, where $\finite(\incr(\allhists)^I)$ denote the functions $f: I \mapsto \incr(\allhists)$ with finite support, thus $\card{f^{-1}(\incr(\allhists) \setminus \emptyset)} < \N$.
-Note that $\allpriobss$ and $\incr(\allhists)^I$ are downwards closed, meaning that $\forall O \in \allpriobss: O' \subseteq O \implies O' \in \allpriobss$ and $\forall O \in \incr(\allhists)^I: O' \subseteq O \implies O' \in \incr(\allhists)^I$.
-Let also $\max\incr(\allhists) = \set{A \in \incr(\allhists) \suchthat \nexists A' \in \incr(\allhists) \suchthat A \subset A'} = \set{A \in \incr(\allhists) \cap (\allhists)^\N}$ denote the maximal elements of $\incr(\allhists)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\N$.
-
-Let the \emph{simple a priori observations} be defined as $\cup_{J \subseteq_\finite I} (\allhists)^J$, equivalently, as the right-unique finite relations over $I × \allhists$.
-Given a simple a priori observation $O: J \mapsto \allhists$, we can define the a priori observation $O_O = \set{(i, \hist) \in J × \allhists \suchthat \forall i \in J: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.
-
-Similarly, we can view an observation $\theta$ as a function $\theta: I \mapsto \cup_{A \in \incr(\allhists)} P^A$ and thus $\Theta = \finite((\cup_{A \in \incr(\allhists)} P^A)^I)$, where $\finite$ designates the finite relations (considered as a set of triples).
-Note that $(\cup_{A \in \max \incr(\allhists)}P^A)^I$ is the set of functions that associate to each $I$ a maximal increasing sequence of paths, together with values from $P$.
-
-Given a claim $C$, we can also define the set $\Theta \cap C^\subseteq$ of possibilities for increasing sequences corresponding to the claim.
+Similarly, an observation $\theta$ is compatible with a claim $C$ iff
+$\theta \in \cup_{{\allleadstog} \in C} \powerset{\allleadstog}$, equivalently, iff
+$\theta \in C^\subseteq$.
+The set $\Theta \cap C^\subseteq$ is the set of observations compatible with the claim.
 This set is downwards-closed, as both $\Theta$ and $C^\subseteq$ are.
+
+\commentOC[Let the \emph{simple a priori observations} be defined as $\cup_{J \subseteq_\finite I} (\allhists)^J$, equivalently, as the right-unique finite relations over $I × \allhists$.
+  Given a simple a priori observation $O: J \mapsto \allhists$, we can define the a priori observation $O_O = \set{(i, \hist) \in J × \allhists \suchthat \forall i \in J: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.]{To be deleted.}
+
+It is important to realize that $\Theta$ is the set of \emph{a priori} possible observations, meaning, those that are conceivable, possibly counter-factually.
+The set of observations that can result from actually observing the behavior ${\allleadsto}$ is
+$\Theta \cap \powerset{\allleadsto} = \set*{\restr{{\allleadsto}}{Q} \suchthat Q \in \allpriobss}$.
 
@@
 \begin{definition}
-  Given an exposure protocol $\allleadsto$, we say that $C$ is \emph{rejectable} iff
+  Given a behavior $\allleadsto$, we say that $C$ is \emph{rejectable} iff
   $\Theta \cap \powerset{\allleadsto} \nsubseteq C^\wsub$.
@@
 
-\Cref{def:falsw} fills the gap to obtain that $C$ holds iff it is not rejectable.
-The property demands that whatever the attitude of individuals, if the attitude is not compatible with the claim, then it is possible to observe that it is not.
+\Cref{def:fals} fills the gap by defining a condition that ensures that $C$ holds iff it is not rejectable.
+The property demands that whatever the behavior of individuals, if their behavior is not compatible with the claim, then it is possible to observe that it is not.
 \begin{definition}
-  \label{def:falsw}
-  A claim $C$ is \emph{falsifiable or trivial} iff
-  $\forall {\allleadstog} \notin C: \Theta \cap \powerset{\allleadstog} \nsubseteq C^\wsub$.
+  \label{def:fals}
+  A claim $C$ is \emph{falsifiable} iff $C \neq {\allleadstos} \land
+  \forall {\allleadstog} \notin C: \Theta \cap \powerset{\allleadstog} \nsubseteq C^\wsub$.
 \end{definition}
@@
 \begin{proof}
-  Consider any falsifiable $C$.
-  Using the contrapositive of \cref{def:fals}, $\forall {\allleadstog} \in \allleadstos: \nexists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub \implies {\allleadstog} \in C$.
+  Consider any falsifiable claim $C$, thus, 
+  $\forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
+  Using the contrapositive, $\forall {\allleadstog} \in \allleadstos: \nexists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub \implies {\allleadstog} \in C$.
   In particular,
@@
 
-\begin{definition}
-  A claim is \emph{strongly unfalsifiable} iff
-  $\Theta \wsub C^\wsub$.
-\end{definition}
-\Cref{ex:disjR,ex:bigor} illustrate, as well as \cref{ex:existsParticular} when $I$ is infinite.
-\begin{definition}
-  A claim is \emph{strictly unfalsifiable} iff
-  it is unfalsifiable and not strongly unfalsifiable.
-\end{definition}
-
-Making a strongly unfalsifiable claim more precise ($C = (C_1 \cap C_2) \sub C_1$ in \cref{th:strongUToStrictU}) can make it strictly unfalsifiable.
-Also, a strictly unfalsifiable claim can be made falsifiable by picking a single relation from the claim.
-
-But, it does not hold that more precise claims are always more falsifiable:
-making a falsifiable claim more precise ($C = (C_1 \cap C_2) \sub C_2$ in \cref{ex:partlyU}) can make it strictly unfalsifiable.
-(In fact, \cref{ex:partlyU} shows that the relation is not one-way: going from a strongly unfalsifiable ($C_1$), or from a falsifiable ($C_2$), claim, to a more precise one ($C = C_1 \cap C_2$) yields a strictly unfalsifiable claim.)
-
 \begin{example}
   \label{ex:allParticular}
-  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
-  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
-\end{example}
-
-The following procedure permits to determine whether a claim is falsifiable.
-Given a set of observations $S \wsub \Theta$, define the relations that are observation-compatible with $S$ as $E(S) = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: {\allleadstog} \cap \theta \in S}$.
-Given a claim $C$, define the set of its observation-compatible relations as $E(C) = E(C^\wsub \cap \Theta)$ (reusing the letter $E$ by abuse of notation).
-Note that this set extends $C$, in the sense that $C \wsub E(C)$.
-The claim $C$ is falsifiable iff it is closed under extension to observation-compatible relations, that is, iff $E(C) \subseteq C$.
-\begin{theorem}
-  \label{thm:caractFals}
-  A claim $C$ is falsifiable or trivial iff $E(C) \wsub C$, or equivalently, iff 
-  $\forall {\allleadstog} \in \allleadstos$:
-  \[\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq \implies {\allleadstog} \in C.\]
-\end{theorem}
-\begin{proof}
-  Note that
-  $E(C) = E(C^\wsub \cap \Theta) = \set{{\allleadstog} \in \allleadstos \suchthat \forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\wsub}$.
-
-  The condition $E(C) \wsub C$ is equivalent to
-  $\forall {\allleadstog} \in \allleadstos: ({\allleadstog} \in E(C) \implies {\allleadstog} \in C)$.
-  Note that ${\allleadstog} \in E(C) \Leftrightarrow \set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq$.
-
-  By definition, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \Theta \cap \powerset{\allleadstog} \wsub C^\wsub$;
-  equivalently, iff $\exists {\allleadstog} \notin C \suchthat \set{θ \subseteq {\allleadstog}} \subseteq C^\subseteq$.
-  And, $\forall {\allleadstog} \in \allleadstos$: $\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} = \set{θ \subseteq {\allleadstog}}$.
-\end{proof}
-
-Let $S_θ = \set{{\allleadstog} \in \allleadstos \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
-Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.
-Define that a relation ${\allleadstog} \in {\allleadstos}$ is \emph{obs-compatible} with a set $S$ iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S$.
+  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable:
+  given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
+\end{example}
 
 \begin{remark}
-  \label{rq:closedcomb}
-  Define the closure under combinations of $C$ as the relations that can be formed by picking parts of relations in $C$, formally, $(\cup_{S \in C^\wsub \cap \Theta} S) \cap \allleadstos$.
-  We have $E(C) \wsub (\cup_{S \in C^\wsub \cap \Theta} S) \cap \allleadstos$.
-
-  Being closed under combinations is sufficient to be falsifiable, but not necessary, as seen with \cref{ex:consti2} (in other words, for some claims, $(\cup_{S \in C^\wsub \cap \Theta} S) \cap \allleadstos \wsub E(C)$ does not hold).
+  Making a claim more precise (meaning going from a claim $C$ to $C' \ssub C$) can make it falsifiable, or conversely, can make it unfalsifiable.
+  Given $\hist, i$, consider the claim $C_2 = \hist \ileadstog \phi$. It is falsifiable.
+  Now consider the claim $C = C_1 \cap C_2$ with $C_1$ being the claim “every individual chooses $\phi$ after seeing solely either $\ar$ or $\ar'$”. It is more precise but unfalsifiable.
+ But we can make it falsifiable again by making it even more precise (picking any single relation).
+ (See \cref{rq:precise}.)
 \end{remark}
 
-Define the \emph{suffix} relation $R = \set{(\hist, \histp) \in \allhists × \allhists \suchthat \histp = (\hist, .)}$ as the (infinite) tree whose set of nodes is $\allhists$ and which links  argumentative paths to all of their direct suffixes.
-Note that a path in such a tree (an increasing sequence of elements in $\allhists$) corresponds to an argumentative path, that is, to an element of $\allhists$.
-
-Any function ${\ileadstog}: \allhists \mapsto P$ can be considered as having this tree as a domain.
-% Define a forest as an association of each $i \in I$ to such a tree.
-Any relation ${\allleadstog} \in \allleadstos$ can then be viewed as a forest associating each $i \in I$ to a tree labeled by the function ${\ileadstog}$ (see \cref{fig:forest}).
-
-\begin{figure}
-  \begin{tikzpicture}[level distance=0.7cm]
-
-    \tikzstyle{treenode}=[execute at begin node=$, execute at end node=$]
-    \tikzstyle{treelabel}=[treenode, anchor=west, inner sep=0]
-    \tikzstyle{bottomnode}=[execute at begin node=$\scriptstyle, execute at end node=$]
-    \tikzstyle{bottomlabel}=[bottomnode, anchor=west, inner sep=0]
-    \tikzstyle{tree}=[level 1/.style={sibling distance=3.4cm, every node/.style=treenode},
-    level 2/.style={sibling distance=1.6cm, every node/.style=bottomnode},
-    level 3/.style={sibling distance=0.7cm, every node/.style=treenode}
-    ]
-    \newlength{\lhi}
-    \setlength{\lhi}{3.5cm}
-    \newlength{\lvi}
-    \setlength{\lvi}{1.2cm}
-
-    \path node (all) {$\allleadstog$};
-
-    \path (-\lhi, -\lvi) node[anchor=north] (tree1) {\begin{tikzpicture}
-        \path[tree] node (root) {$\emptyset$}
-        child {
-            node (a) {(a)}
-            child {
-                node (aa) {(aa)}
-                child {
-                    node {…}
-                  }
-                child {
-                    node {…}
-                  }
-              }
-            child {
-                node (ab) {(ab)}
-                child {
-                    node {…}
-                  }
-                child {
-                    node {…}
-                  }
-              }
-          }
-        child {
-            node (b) {(b)}
-            child {
-                node (ba) {(ba)}
-                child {
-                    node {…}
-                  }
-                child {
-                    node {…}
-                  }
-              }
-            child {
-                node (bb) {(bb)}
-                child {
-                    node {…}
-                  }
-                child {
-                    node {…}
-                  }
-              }
-          }
-        ;
-        \begin{scope}[style=treelabel]
-          \path (root.east) node {\mapsto p};
-          \path (a.east) node {\mapsto p'};
-          \path (b.east) node {\mapsto p};
-        \end{scope}
-        \begin{scope}[style=bottomlabel]
-          \path (aa.east) node {\mapsto p'};
-          \path (ab.east) node {\mapsto p'};
-          \path (ba.east) node {\mapsto p'};
-          \path (bb.east) node {\mapsto p};
-        \end{scope}
-      \end{tikzpicture}};
-    \path[->] (all) edge node[midway, above] {$i_1$} (tree1.north);
-
-    \path (\lhi, -\lvi) node[anchor=north] (tree2) {\begin{tikzpicture}
-        \path[tree] node (root) {$\emptyset$}
-        child {
-            node (a) {(a)}
-            child {
-                node (aa) {(aa)}
-                child {
-                    node {…}
-                  }
-                child {
-                    node {…}
-                  }
-              }
-            child {
-                node (ab) {(ab)}
-                child {
-                    node {…}
-                  }
-                child {
-                    node {…}
-                  }
-              }
-          }
-        child {
-            node (b) {(b)}
-            child {
-                node (ba) {(ba)}
-                child {
-                    node {…}
-                  }
-                child {
-                    node {…}
-                  }
-              }
-            child {
-                node (bb) {(bb)}
-                child {
-                    node {…}
-                  }
-                child {
-                    node {…}
-                  }
-              }
-          }
-        ;
-        \begin{scope}[style=treelabel]
-          \path (root.east) node {\mapsto p};
-          \path (a.east) node {\mapsto p};
-          \path (b.east) node {\mapsto p'};
-        \end{scope}
-        \begin{scope}[style=bottomlabel]
-          \path (aa.east) node {\mapsto p};
-          \path (ab.east) node {\mapsto p'};
-          \path (ba.east) node {\mapsto p'};
-          \path (bb.east) node {\mapsto p};
-        \end{scope}
-      \end{tikzpicture}};
-    \path[->] (all) edge node[midway, above] {$i_2$} (tree2.north);
-  \end{tikzpicture}
-  \caption{A forest}
-  \label{fig:forest}
-\end{figure}
-
-Given an attitude $\allleadsto$, deliberated choices are represented by an element $\pi({\allleadsto}) \subseteq I × P$ (thus with $\pi({\allleadsto})(i) = P_i$) which is right unique (meaning that $\forall i \in I: \card{\pi({\allleadsto})(i)} ≤ 1$).
-Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\allleadsto}) \in (P \cup \set{\emptyset})^I$.
-
+\subsection{More properties}
 A claim $C$ is \emph{informative} iff $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.
@@
 Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
-A claim $C$ is \emph{indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \cap C^\wsub \suchthat \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
-Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
+A claim $C$ is \emph{indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \cap C^\wsub \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
+Indicativity mandates that when knowing a finite number of observations about a given $i$ compatible with any (possibly counter-factual) world in $C$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
+A claim $C$ is \emph{truly indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \wsub {\allleadsto} \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
+A claim $C$ is \emph{newly indicative} iff $\forall {\allleadstog} \in C: \exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \wsub {\allleadstog} \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
+Indicativity mandates that when knowing a finite number of observations about a given $i$ compatible with any (possibly counter-factual) world in $C$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
+
 \begin{remark}
   Informativeness permits mere counting: the claim that exactly two persons deliberately believe $\phi$ is informative.
-  Informativeness may be a desirable property (rather than informativeness beyond counting) as one may want to know whether a given proposition is believed by a majority of individuals, or whether a given proposition is believed by nobody.
-  Note also that strong informativeness beyond counting implies informativeness beyond counting and indicativeness.
-  Note also that informativeness beyond counting implies informativeness.
-\end{remark}
-\begin{remark}
-  We could weaken indicativeness by allowing for disjuncts: observing either that $\hist \ileadsto \phi$ or that $\hist \ileadsto \psi$ permits to deduce something about $P_i$.
-  (Or more complex formulas under the form of a set of possible functions in $P^H$?)
-  (Actually I am not sure that this really weakens the condition.)
+  Informativeness may be a desirable property (rather than informativeness beyond counting) as one may, for example, want to know whether a given proposition is believed by a majority of individuals.
+  Note also that strong informativeness beyond counting implies informativeness beyond counting and indicativeness; and
+  that informativeness beyond counting implies informativeness.
 \end{remark}
@@
 
-We are now interested in the interplay between properties of holding, anonymity, (strong) informativeness beyond counting, and falsifiability.
-\Cref{th:hsif,th:hif,th:asif} show their compatibility when one of holding or anonymity is not required (except that informativeness beyond counting cannot be made strong in the edge case where $\forall i \in I: P_i = \emptyset$).
-
-We thus turn to requiring both anonymous and holding.
-They are always satisfiable when only these two are required (\cref{th:ha}).
-\Cref{th:infoBeyonCKO} (and extensions, \cref{th:infoBeyonCKOext,th:strinfoBeyonCKO}) shows that informativeness beyond counting (and variants) is too demanding if one wants to investigate situations where individuals have differing deliberate preferences.
-
-It is possible under reasonable conditions of regularity to satisfy anonymous and holding together with indicativeness.
-This happens for example when everybody has a deliberate judgment and a finite set of decisive arguments suffices to lead everybody to their deliberate judgment (\cref{th:suffIndicDec}).
+\Cref{th:AHFimpl} and related show that anonymous and falsifiable claims that hold exist iff the situation does not satisfy $\forall \hist: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$.
+
+Let us determine which situations admit anonymous and falsifiable claims that hold and are indicative (or other?).
 
@@
 \begin{example}[To be completed]
-  Assume that $\exists \ar_j ≠ \ar_k, J, K \subset I \suchthat J \cup K = I \land \card{J} \notin \N \land \card{K} \notin \N \land \forall j \in J: \ar_j \ileadstost[j] \phi \land \forall k \in K: \ar_k \ileadstost[k] \phi \land \forall \ar \in \allargs \setminus \set{\ar_j, \ar_k}, i \in I: \ar \nileadstost \phi$.
+  Assume that $\exists \ar_j ≠ \ar_k, J, K \subset I \suchthat J \cup K = I \land \card{J} \notin \Z \land \card{K} \notin \Z \land \forall j \in J: \ar_j \ileadstost[j] \phi \land \forall k \in K: \ar_k \ileadstost[k] \phi \land \forall \ar \in \allargs \setminus \set{\ar_j, \ar_k}, i \in I: \ar \nileadstost \phi$.
   Then no suitable $C$ exists?
@@
 
-  Say that $\gamma$ has depth at least $k \in \N^*$ iff $\exists (\alpha_i, 1 ≤ i ≤ k) \suchthat \forall 1 ≤ i ≤ k, \dg(\set{\alpha_j \suchthat 1 ≤ j ≤ i - 1}) \subsetneq \dg(\set{\alpha_j \suchthat 1 ≤ j ≤ i}) \land \forall 1 ≤ i ≤ k - 1, \alpha_i \cup \dg(\alpha_i) \subseteq \alpha_{i + 1}$.
-  The bounded depth condition on the defense relation imposes that for some $k \in \N^*$, $\gamma$ does not have depth at least $k$.
-  The depth of a theory is defined as the smallest value $k \in \N$ such that it does not have depth at least $k + 1$.
+  Say that $\gamma$ has depth at least $k \in \Zp$ iff $\exists (\alpha_i, 1 ≤ i ≤ k) \suchthat \forall 1 ≤ i ≤ k, \dg(\set{\alpha_j \suchthat 1 ≤ j ≤ i - 1}) \subsetneq \dg(\set{\alpha_j \suchthat 1 ≤ j ≤ i}) \land \forall 1 ≤ i ≤ k - 1, \alpha_i \cup \dg(\alpha_i) \subseteq \alpha_{i + 1}$.
+  The bounded depth condition on the defense relation imposes that for some $k \in \Zp$, $\gamma$ does not have depth at least $k$.
+  The depth of a theory is defined as the smallest value $k \in \Z$ such that it does not have depth at least $k + 1$.
   For example, $\gamma$ has depth $0$ iff $\dg = \emptyset$; and $\gamma$ has depth $1$ iff $[\exists \alpha_1 \suchthat \dg(\alpha_1) ≠ \emptyset] \land [\forall \alpha_1, \alpha_2 \suchthat \dg(\alpha_1) ≠ \emptyset \land \alpha_1 \cup \dg(\alpha_1) \subseteq \alpha_2: \dg(\alpha_2) \subseteq \dg(\alpha_1)]$.
@@
   Generalizing this observation, given $i \in I$, define $\dgi(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \in \histend \land \hist \nileadsto \pga} \subseteq \dg(\ar)$ as the subset of defenders of $\ar$ required for convincing $i$ of choosing $\pga$.
-  Define $\gargsi \subseteq \allargs$ as the transitive closure of $\arga$ under $\dgi$: $\gargsi = \cup_{k \in \N} (\dgi)^k(\arga)$.
+  Define $\gargsi \subseteq \allargs$ as the transitive closure of $\arga$ under $\dgi$: $\gargsi = \cup_{k \in \Z} (\dgi)^k(\arga)$.
 The set $\gargsi$ is the set of arguments required to convince $i$ of choosing $\pga$.
@@
     An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\allleadsto})$ is \emph{truthful} iff
-    $\forall i \in I, \hist \in \allhists, n \in \N, k \in \intvl{1, \card \hist}^n, \ar \in \allargs^n$:
+    $\forall i \in I, \hist \in \allhists, n \in \Z, k \in \intvl{1, \card \hist}^n, \ar \in \allargs^n$:
     \begin{equation}
@@
 
-  A path can be shortened to its first $k \in \intvl{0, \card{\hist}}$ elements, which is denoted by $\restr{\hist}{\intvl{1, k}}$, and “shortening” a path beyond its length yields the same path again, thus given $k \in \N$, $\restr{\hist}{\intvl{1, k}} = \restr{\hist}{\intvl{1, \min\set{\card{\hist}, k}}}$.
+  A path can be shortened to its first $k \in \intvl{0, \card{\hist}}$ elements, which is denoted by $\restr{\hist}{\intvl{1, k}}$, and “shortening” a path beyond its length yields the same path again, thus given $k \in \Z$, $\restr{\hist}{\intvl{1, k}} = \restr{\hist}{\intvl{1, \min\set{\card{\hist}, k}}}$.
   Define a path as being decisive for $p$, $\hist \ileadstost p$, iff $\hist \ileadsto p \land \forall \ar \in \allargs: (\hist, \ar) \ileadsto p$, or equivalently, iff $\forall \hist' \suchthat \card{\hist} ≤ \card{\hist'} ≤ \card{\hist} + 1 \land \restr{\hist'}{\intvl{1, \card{\hist}}} = \hist: \hist' \ileadsto p$.
@@
     \label{ax:omitting}
-    If the theory is truthful, then $\forall i \in I, k \in \N^*, l \in \intvl{2, k}, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist, \beta \in \allhists \suchthat [\ar_k \in \histend \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1})]:
+    If the theory is truthful, then $\forall i \in I, k \in \Zp, l \in \intvl{2, k}, (\ar_j)_{j \in \intvl{1, k}} \in \allargs^k, \hist, \beta \in \allhists \suchthat [\ar_k \in \histend \land \forall j \in \intvl{2, k}: \ar_j \in \dgi(\ar_{j - 1})]:
       (\beta, \ar_{l - 1}, \ar_l, \hist) \ileadsto \pga ⇒ (\beta, \ar_l, \hist) \ileadsto \pga$.
@@
     The claim $[\forall i: (\ar) \ileadstog \phi] \lor [\forall i: (\ar, \ar) \ileadstog \phi] \lor …$,
-    thus, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$,
+    thus, $C = \set{{\allleadstog} \suchthat \exists n \in \Zp \suchthat \forall i: (a)^n \ileadstog \phi}$,
     is non rejectable: $\Theta \wsub C^\wsub$.
@@
     Indeed, if ${\ileadsto}$ satisfies this, then either it holds and by \cref{th:ex-post} it is not rejectable, or it associates this triplet to $(\phi, \phi, \phi)$ or
-    $(\phi, ¬\phi, ¬\phi)$ in which case, as $(\ar)$ and $(\ar')$ cannot be together in $\theta$, any $\theta \in \Theta$ with $\theta \sub {\allleadsto}$ satisfy $\theta \in C^\wsub$.
-
-    Conversely, if $C$ is not rejectable, then for any $\theta_1$ containing $\emptyset$ and $(\ar)$ and $\theta_2$ containing $\emptyset$ and $(\ar')$, with $\theta_1, \theta_2 \sub {\allleadsto}$, we have $\theta_1, \theta_2 \in C^\wsub$, which requires that ${\ileadsto}$ associates $(\emptyset, (\ar))$ to $(¬\phi, \phi)$, $(\phi, ¬\phi)$ or $(\phi, \phi)$ and $(\emptyset, (\ar'))$ to $(¬\phi, \phi)$, $(\phi, \phi)$ or $(\phi, ¬\phi)$.
+    $(\phi, ¬\phi, ¬\phi)$ in which case, as $(\ar)$ and $(\ar')$ cannot be together in $\theta$, any $\theta \in \Theta$ with $\theta \wsub {\allleadsto}$ satisfy $\theta \in C^\wsub$.
+
+    Conversely, if $C$ is not rejectable, then for any $\theta_1$ containing $\emptyset$ and $(\ar)$ and $\theta_2$ containing $\emptyset$ and $(\ar')$, with $\theta_1, \theta_2 \wsub {\allleadsto}$, we have $\theta_1, \theta_2 \in C^\wsub$, which requires that ${\ileadsto}$ associates $(\emptyset, (\ar))$ to $(¬\phi, \phi)$, $(\phi, ¬\phi)$ or $(\phi, \phi)$ and $(\emptyset, (\ar'))$ to $(¬\phi, \phi)$, $(\phi, \phi)$ or $(\phi, ¬\phi)$.
   \end{example}
@@
     Consider any $i$ and $p, p' \in P$.
-    The claim $C = \set{{\allleadstog} \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \hist \ileadstog p) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \hist \ileadstog p')}$, namely, all paths of even lengths lead $i$ to $p$ OR all paths of odd lengths or empty lead $i$ to $p'$, is falsifiable.
-
-    Note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \theta(\hist) \in \set{\emptyset, p}) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \theta(\hist) \in \set{\emptyset, p'})}$.
+    The claim $C = \set{{\allleadstog} \suchthat (\forall \hist: \card{\hist} \in 2\Z \implies \hist \ileadstog p) \lor (\forall \hist: (\card{\hist} \in 2\Z + 1 \lor \hist = \emptyset) \implies \hist \ileadstog p')}$, namely, all paths of even lengths lead $i$ to $p$ OR all paths of odd lengths or empty lead $i$ to $p'$, is falsifiable.
+
+    Note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat (\forall \hist: \card{\hist} \in 2\Z \implies \theta(\hist) \in \set{\emptyset, p}) \lor (\forall \hist: (\card{\hist} \in 2\Z + 1 \lor \hist = \emptyset) \implies \theta(\hist) \in \set{\emptyset, p'})}$.
     Consider any obs-compatible ${\allleadstog}$.
-    Assume that $\exists \hist \suchthat \card{\hist} \in 2\N \land \hist \nileadstog p$.
+    Assume that $\exists \hist \suchthat \card{\hist} \in 2\Z \land \hist \nileadstog p$.
     Pick $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\hist, i, {\ileadstog}(\hist))}$.
@@
 
+  \subsection{Behavior function as a forest}
+  Define the \emph{suffix} relation $R = \set{(\hist, \histp) \in \allhists × \allhists \suchthat \histp = (\hist, .)}$ as the (infinite) tree whose set of nodes is $\allhists$ and which links  argumentative paths to all of their direct suffixes.
+  Note that a path in such a tree (an increasing sequence of elements in $\allhists$) corresponds to an argumentative path, that is, to an element of $\allhists$.
+
+  Any function ${\ileadstog}: \allhists \mapsto P$ can be considered as having this tree as a domain.
+  % Define a forest as an association of each $i \in I$ to such a tree.
+  Any relation ${\allleadstog} \in \allleadstos$ can then be viewed as a forest associating each $i \in I$ to a tree labeled by the function ${\ileadstog}$ (see \cref{fig:forest}).
+
+  \begin{figure}
+    \begin{tikzpicture}[level distance=0.7cm]
+
+      \tikzstyle{treenode}=[execute at begin node=$, execute at end node=$]
+      \tikzstyle{treelabel}=[treenode, anchor=west, inner sep=0]
+      \tikzstyle{bottomnode}=[execute at begin node=$\scriptstyle, execute at end node=$]
+      \tikzstyle{bottomlabel}=[bottomnode, anchor=west, inner sep=0]
+      \tikzstyle{tree}=[level 1/.style={sibling distance=3.4cm, every node/.style=treenode},
+      level 2/.style={sibling distance=1.6cm, every node/.style=bottomnode},
+      level 3/.style={sibling distance=0.7cm, every node/.style=treenode}
+      ]
+      \newlength{\lhi}
+      \setlength{\lhi}{3.5cm}
+      \newlength{\lvi}
+      \setlength{\lvi}{1.2cm}
+
+      \path node (all) {$\allleadstog$};
+
+      \path (-\lhi, -\lvi) node[anchor=north] (tree1) {\begin{tikzpicture}
+          \path[tree] node (root) {$\emptyset$}
+          child {
+              node (a) {(a)}
+              child {
+                  node (aa) {(aa)}
+                  child {
+                      node {…}
+                    }
+                  child {
+                      node {…}
+                    }
+                }
+              child {
+                  node (ab) {(ab)}
+                  child {
+                      node {…}
+                    }
+                  child {
+                      node {…}
+                    }
+                }
+            }
+          child {
+              node (b) {(b)}
+              child {
+                  node (ba) {(ba)}
+                  child {
+                      node {…}
+                    }
+                  child {
+                      node {…}
+                    }
+                }
+              child {
+                  node (bb) {(bb)}
+                  child {
+                      node {…}
+                    }
+                  child {
+                      node {…}
+                    }
+                }
+            }
+          ;
+          \begin{scope}[style=treelabel]
+            \path (root.east) node {\mapsto p};
+            \path (a.east) node {\mapsto p'};
+            \path (b.east) node {\mapsto p};
+          \end{scope}
+          \begin{scope}[style=bottomlabel]
+            \path (aa.east) node {\mapsto p'};
+            \path (ab.east) node {\mapsto p'};
+            \path (ba.east) node {\mapsto p'};
+            \path (bb.east) node {\mapsto p};
+          \end{scope}
+        \end{tikzpicture}};
+      \path[->] (all) edge node[midway, above] {$i_1$} (tree1.north);
+
+      \path (\lhi, -\lvi) node[anchor=north] (tree2) {\begin{tikzpicture}
+          \path[tree] node (root) {$\emptyset$}
+          child {
+              node (a) {(a)}
+              child {
+                  node (aa) {(aa)}
+                  child {
+                      node {…}
+                    }
+                  child {
+                      node {…}
+                    }
+                }
+              child {
+                  node (ab) {(ab)}
+                  child {
+                      node {…}
+                    }
+                  child {
+                      node {…}
+                    }
+                }
+            }
+          child {
+              node (b) {(b)}
+              child {
+                  node (ba) {(ba)}
+                  child {
+                      node {…}
+                    }
+                  child {
+                      node {…}
+                    }
+                }
+              child {
+                  node (bb) {(bb)}
+                  child {
+                      node {…}
+                    }
+                  child {
+                      node {…}
+                    }
+                }
+            }
+          ;
+          \begin{scope}[style=treelabel]
+            \path (root.east) node {\mapsto p};
+            \path (a.east) node {\mapsto p};
+            \path (b.east) node {\mapsto p'};
+          \end{scope}
+          \begin{scope}[style=bottomlabel]
+            \path (aa.east) node {\mapsto p};
+            \path (ab.east) node {\mapsto p'};
+            \path (ba.east) node {\mapsto p'};
+            \path (bb.east) node {\mapsto p};
+          \end{scope}
+        \end{tikzpicture}};
+      \path[->] (all) edge node[midway, above] {$i_2$} (tree2.north);
+    \end{tikzpicture}
+    \caption{A forest}
+    \label{fig:forest}
+  \end{figure}
+
 \subsection{Compatibility of claim properties}
+We are here interested in the interplay between properties of holding, anonymity, (strong) informativeness beyond counting, and falsifiability.
+\Cref{th:hsif,th:hif,th:asif} show their compatibility when one of holding or anonymity is not required (except that informativeness beyond counting cannot be made strong in the edge case where $\forall i \in I: P_i = \emptyset$).
+
+We thus turn to requiring both anonymous and holding.
+They are always satisfiable when only these two are required (\cref{th:ha}).
+\Cref{th:infoBeyonCKO} (and extensions, \cref{th:infoBeyonCKOext,th:strinfoBeyonCKO}) shows that informativeness beyond counting (and variants) is too demanding if one wants to investigate situations where individuals have differing deliberate preferences.
+
+It is possible under reasonable conditions of regularity to satisfy anonymous and holding together with indicativeness.
+This happens for example when everybody has a deliberate judgment and a finite set of decisive arguments suffices to lead everybody to their deliberate judgment (\cref{th:suffIndicDec}).
+
   \begin{theorem}
@@
 
-Given a set of attitudes $S \wsub P^{\allhists}$, the claim associated to it designates the claim $S^I = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in S}$.
-Say that a claim $C$ is a claim about types iff $\exists S \wsub P^{\allhists} \suchthat C = S^I$.
-Informally, such a claim claims that the set of attitudes in $I$ is contained in $S$ (though might be a strict subset of $S$), or equivalently, that no attitude out of $S$ exists among $I$.
-\begin{definition}
-  Say that an attitude $g \in P^{\allhists}$ is observably included in a set of attitudes $S \wsub P^{\allhists}$ iff $\forall H \in \finite(\incr(\allhists)): \exists f \in S \suchthat \restr{g}{H} = \restr{f}{H}$.
-
-  Define the extension of a set of attitudes $S \wsub P^{\allhists}$ to its observably included attitudes as the set of attitudes $R(S) = \set{g \in P^{\allhists} \suchthat \forall H \in \finite(\incr(\allhists)): \exists f \in S \suchthat \restr{g}{H} = \restr{f}{H}}$.
-  Note that $S \wsub R(S)$. 
-  Also note that $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$.
-\end{definition}
-\begin{theorem}
-  \label{th:RR}
-  $\forall S \wsub P^{\allhists}: R(R(S)) \wsub R(S)$.
-\end{theorem}
-\begin{proof}
-  Consider any $g \in R(R(S))$.
-  Consider any $H \in \finite(\incr(\allhists))$.
-  There exists $f \in R(S)$ such that $\restr{g}{H} = \restr{f}{H}$.
-  There exists $f' \in S$ such that $\restr{f}{H} = \restr{f'}{H}$.
-  Thus, $\restr{g}{H} = \restr{f'}{H}$.
-  Thus, $g \in R(S)$.
-\end{proof}
-Define the closure under observable inclusion of a claim about types $S$ as $R^\infty(S)$, equivalently, as the smallest set $S'$ such that $S \wsub S' = R(S')$, equivalently, as indicated by \cref{th:RR}, as $R(S)$.
-
-Let $\intvl{\hist} = (\hist_i)_{i \in \intvl{0, \card{\hist}}} \in \finite(\incr(\allhists))$ denote the increasing sequence of paths from $\emptyset$ to $\hist$.
-\begin{theorem}
-  \label{th:caractR}
-  The $S$-labeling function associated to an attitude $f \in P^{\allhists}$ is the function $l^S_f: \allhists \to \powerset{P^{\allhists}}$ defined as $l^S_f(\hist) = \set{g \in S \suchthat g(\hist) = f(\hist)}$.
-
-  We have: $R(S) = \set{f \suchthat \forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset}$.
-\end{theorem}
-\begin{proof}
-  Consider $f$ with $\forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$.
-  Consider any $H \in \finite(\incr(\allhists))$.
-  We know that $\cap_{\histp \wsub \hist}{l^S_f(\histp)} \neq \emptyset$, thus in particular, defining $\hist = \max H$ and observing that $H \wsub \set{\histp \suchthat \histp \wsub \hist}$, we have that $\cap_{\histp \in H} l^S_f(\histp) \neq \emptyset$.
-  Pick any $g \in \cap_{\histp \in H} l^S_f(\histp)$. Thus, $g \in S$.
-  Also, $\forall \hist \in H: g \in l^S_f(\hist)$, thus,
-  $\forall \hist \in H: g(\hist) = f(\hist)$.
-
-  First observe that given any $S \wsub P^{\allhists}$, $f \in P^{\allhists}$ and $\hist \in \allhists$, as $\histp \wsub \hist$ iff $\histp \in \intvl{\hist}$, we have that $\cap_{\histp \wsub \hist} l^S_f(\histp) = \set{g \in S \suchthat \forall \histp \in \intvl{\hist}: g(\histp) = f(\histp)}$.
-
-  It follows that if $\forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$, then $\forall H \in \finite(\incr(\allhists))$: $\emptyset \neq \set{g \in S \suchthat \forall \histp \in \intvl{\max H}: g(\histp) = f(\histp)} \wsub \set{g \in S \suchthat \forall \histp \in H: g(\histp) = f(\histp)}$.
-
-  Conversely, if $\forall H \in \finite(\incr(\allhists)): \set{g \in S \suchthat \forall \histp \in H: g(\histp) = f(\histp)} \neq \emptyset$, then $\forall \hist \in \allhists$, defining $H = \intvl{\hist}$, we have that $\cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$.
-\end{proof}
-
-\begin{lemma}
-  \label{th:typesfalsifiable}
-  A set of attitudes $S \wsub P^{\allhists}$ 
-  satisfies $\forall g \in P^{\allhists} \setminus S: \exists H \in \finite(\incr(\allhists)) \suchthat \forall f \in S: \restr{g}{H} \neq \restr{f}{H}$,
-  iff its associated claim is falsifiable or trivial.
-\end{lemma}
-\begin{proof}
-  Pick any ${\allleadstog} \notin C$.
-  By definition of $C$,
-  $\exists i \in I \suchthat {{\ileadstog}} \notin S$.
-  As $C$ holds, ${\ileadstog} \notin \set{{\ileadsto[j]} \suchthat j \in I}$ (\cref{th:typesholds}).
-  Pick any $H$ such that $\forall {\ileadstog[j]} \in S: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadstog[j]}(\hist)$.
-  Define $\theta = \set{(\hist, i, {\ileadstog}(\hist)) \suchthat \hist \in H} \in \Theta \cap \powerset{\allleadstog}$.
-  Then, $\theta \notin C^\wsub$, because $\forall {\ileadstog[j]} \in S: \theta \nsubseteq {\ileadstog[j]}$.
-
-  Conversely, assume that for some ${\ileadstog} \in P^{\allhists} \setminus S$, no $H \in \finite(\incr(\allhists))$ satisfies the indicated condition.
-  Define ${\allleadstog}$ as including ${\ileadstog}$ and for all other individuals, relations from $S$.
-  Then, ${\allleadstog} \notin C$, but any observation will be in $C$, thus the claim is not falsifiable and not trivial.
-\end{proof}
-\begin{lemma}
-  \label{th:typesholds}
-  Consider a set of attitudes $S \wsub P^{\allhists}$. Its associated claim holds iff $\set{{\ileadsto[j]} \suchthat j \in I} \wsub S$.
-\end{lemma}
-\begin{lemma}
-  \label{th:typesanonymous}
-  Given any set of attitudes $S \wsub P^{\allhists}$, its associated claim is anonymous.
-\end{lemma}
-The following result follows from \cref{th:typesfalsifiable,th:typesholds,th:typesanonymous}.
-\begin{theorem}
-  \label{th:suffFals}
-  Assume that $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  Then, the claim $C$ associated to the set of attitudes $S = \set{{\ileadsto[j]} \suchthat j \in I}$ holds, is anonymous, and is falsifiable or trivial.
-\end{theorem}
-\begin{proof}
-  For another proof, note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat \forall i \in I: \exists j \in I \suchthat \theta \cap (\allhists × \set{i} × P) \wsub {\ileadsto[j]}}$.
-  Pick any ${\allleadstog} \in E(C^\wsub \cap \Theta)$ and let us show that ${\allleadstog} \in C$.
-  Note that ${\allleadstog} \notin C \iff \exists i \in I \suchthat {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, in which case the consequent in the theorem holds.
-  We need to show that $\nexists i \in I, H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
-  In other words, given any $i \in I$, we need to show that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
-\end{proof}
-
-The following result follows from \cref{th:typesfalsifiable}.
-\begin{theorem}
-  If a set of attitudes $S \wsub P^{\allhists}$ is not closed under observable inclusion, then it is not falsifiable and not trivial.
-\end{theorem}
-\begin{theorem}
-  Given any situation, if the claim associated to the set of attitudes $R({\allleadsto}(I))$ is trivial, then there exists no claim associated to a set of attitudes that holds and is falsifiable.
-\end{theorem}
-\begin{proof}
-  Consider a claim related to a set of attitudes $S$ that holds and that is falsifiable or trivial.
-  For it to hold, we need ${\allleadsto}(I) \wsub S$.
-  From \cref{th:typesfalsifiable}, for it to be falsifiable or trivial, we need that $\forall g \in P^{\allhists} \setminus S: \exists H \in \finite(\incr(\allhists)) \suchthat \forall f \in S: \restr{g}{H} \neq \restr{f}{H}$.
-In other words, all $g$ must be observably excludable from $S$.
-In other words, $S$ must be closed under observable inclusion.
-Thus, we need $R(S) \wsub S$.
-  Also, because $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$, we need
-  $R({\allleadsto}(I)) \wsub R(S) \wsub S$.
-  It follows that $S$ is trivial.
-\end{proof}
-\begin{theorem}
-  Given any situation, the claim associated to the set of attitudes $R({\allleadsto}(I))$ holds, is anonymous, and is falsifiable or trivial.
-\end{theorem}
-\begin{example}
-  Define $f^{(p, p')} \in P^{\allhists}$ as follows: $f^{(p, p')}(\emptyset) = p$ and $\forall \hist \in \allhists: \hist ≠ \emptyset \implies f^{(p, p')}(\hist) = p'$.
-
-  Consider a situation such that ${\allleadsto}(I) = \set{f^{(p, p')} \suchthat p, p' \in \set{\phi, ¬\phi}}$, thus, containing only people constant to $\phi$ and people constant to $¬\phi$, except that they map $\emptyset$ to anything in $\set{\phi, ¬\phi}$.
-  Define $F^p = \set{f^{(p, p')} \suchthat p' \in \set{\phi, ¬\phi}}$.
-
-  \Cref{th:caractR} indicates that $R({\allleadsto}(I)) = \set{f \suchthat l^S_f(\emptyset) \in \set{F^\phi, F^{¬\phi}} \land \forall \ar \in \allargs: [\forall \hist \suchthat \hist_1 = \ar: l^S_f(\hist) \in l^S_f(\emptyset)] \land [\forall \hist, \histp \suchthat \hist_1 = \histp_1 = \ar: l^S_f(\hist) = l^S_f(\histp)]}$.
-
-  Thus, $R({\allleadsto}(I))$ contains, for each mapping $m: \allargs \rightarrow \set{\phi, ¬\phi}$, the two functions $f_m^\phi, f_m^{¬\phi}$ defined as $f_m^\phi(\emptyset) = \phi$ and $\forall \ar \in \allargs: f_m^\phi((\ar, …)) = m(\ar)$, and similarly for $f_m^{¬\phi}$.
-
-  The claim associated to $R({\allleadsto}(I))$ is not trivial: $\forall f \suchthat [\exists \hist, \histp \ssub \hist \suchthat f(\histp) ≠ f(\hist)]: f \notin R({\allleadsto}(I))$.
-\end{example}
-\begin{example}
-  Consider $\allargs = \set{\ar_1, \ar_2}$ and ${\allleadsto}(I) = \set{f \suchthat f(\ar_1) ≠ \phi \lor f(\ar_2) ≠ \phi}$, thus, $f \notin {\allleadsto}(I)$ iff $f(\ar_1) = f(\ar_2) = \phi$.
-
-  Consider any $f \notin {\allleadsto}(I)$.
-  We have $f \in R({\allleadsto}(I))$.
-  Indeed, define $g_1 \in P^{\allhists}$ as $g_1 = f$ except that $g_1(\ar_2) = ¬\phi$, and $g_2 \in P^{\allhists}$ as $g_2 = f$ except that $g_2(\ar_1) = ¬\phi$.
-  Then, $g_1, g_2 \in {\allleadsto}(I)$.
-  Now consider any $H \in \finite(\incr(\allhists))$.
-  If $(\ar_2) \notin H$, then $\restr{f}{H} = \restr{g_1}{H}$; otherwise, $\restr{f}{H} = \restr{g_2}{H}$.
-
-  It follows that the claim associated to $R({\allleadsto}(I))$ is trivial.
-\end{example}
-\begin{remark}
-  A few more, maybe not useful, definitions.
-
-  Given a set of attitudes $S$ and $\hist \in \allhists$, define the equivalence relation $=_\hist$ on $S$ as $f =_\hist g$ iff $f(\hist) = g(\hist)$.
-This also defines the quotient set $S / =_\hist$.
-(For the readers used to that terminology: if defining $\beta_\hist \in P^S$ as $\beta_\hist(f) = f(\hist)$, then $=_\hist$ is the equivalence kernel of $\beta_\hist$ and $S / =_\hist$ is the coimage of $\beta_\hist$.)
-  Similarly, given $S$ and $H \in \finite(\incr(\allhists))$, define the equivalence relation $=_H$ on $S$ as $f =_H g$ iff $\restr{f}{H} = \restr{g}{H}$. This also defines the quotient set $S / =_H$.
-
-  A function $l: \allhists \to \powerset{P^{\allhists}}$ is decreasing iff $\forall \hist \wsub \histp: l(\histp) \wsub l(\hist)$.
-  Let $S \wsub P^{\allhists}$ be a set of attitudes.
-  Say that a function $l: \allhists \to \powerset{P^{\allhists}}$ is an $S$-point-labeling function iff $\forall \hist \in \allhists: l(\hist) \in S / =_\hist$.
-  Say that a function $l: \allhists \to \powerset{P^{\allhists}}$ is an $S$-sequence-labeling function iff $\forall \hist \in \allhists: l(\hist) \in S / =_{\intvl{\hist}}$.
-\end{remark}
-\begin{theorem}
-  Given $\hist \in \allhists$, define $\restr{S}{\intvl{\hist}} = \set{\restr{f}{\intvl{\hist}} \suchthat f \in S}$.
-  Given a non empty set of attitudes $S \wsub P^{\allhists}$, the following statements are equivalent.
-  \begin{itemize}
-    \item The claim associated to $R(S)$ is not trivial 
-    \item $R(S) ≠ P^{\allhists}$
-    \item $\exists \hist \in \allhists, f \in P^{\intvl{\hist}} \suchthat \forall g \in S: \restr{g}{\intvl{hist}} ≠ f$
-    \item $\exists \hist, f \in P^{\intvl{\hist}} \suchthat f \notin \restr{S}{\intvl{\hist}}$
-    \item $\exists \hist \suchthat P^{\intvl{\hist}} \not\wsub \restr{S}{\intvl{\hist}}$.
-  \end{itemize}
-  Also, the following statements are equivalent.
-  \begin{itemize}
-    \item The claim associated to $R(S)$ is trivial
-    \item $R(S) = P^{\allhists}$
-    \item $\forall \hist, f, \exists g \in S \suchthat \restr{g}{\intvl{\hist}} = f$
-    \item $\forall \hist: P^{\intvl{\hist}} \wsub \restr{S}{\intvl{\hist}}$.
-  \end{itemize}
-  Furthermore, $\forall \hist: P^{\intvl{\hist}} \wsub \restr{S}{\intvl{\hist}} \implies \card{S} \notin \N$.
-\end{theorem}
-\begin{proof}
-  This follows from $R(S) ≠ P^{\allhists} \iff \exists f \in P^{\allhists}, \hist \in \allhists \suchthat \cap_{\histp \wsub \hist} l^S_f(\histp) = \emptyset$.
-\end{proof}
-
-To recap, we now know that with $S = {\allleadsto}(I)$, when $R(S) ≠ P^{\allhists}$, there is a claim that holds and is anonymous and falsifiable.
-This includes all situations with finite behaviors ($\card{S} \in \N$), thus includes all situations with finite $I$.
-Consider now situations such that $R({\allleadsto}(I)) = P^{\allhists}$.
-
-Define $I = P^\N$ and ${\ileadsto} = i \circ \card$, so that $S = {\allleadsto}(I) = \set{l \circ \card \in P^{\allhists} \suchthat l \in P^\N}$.
-We have $R(S) = P^{\allhists}$.
-The function $f(\ar) ≠ f(\ar')$, for example, is not in $S$.
-
-\begin{theorem}
-  Given a claim $C$, define $S_C \wsub P^{\allhists}$ as $S_C = \bigcup_{{\allleadstog} \in C}({\allleadstog}(I))$.
-  A claim $C$ is about types iff $C = (S_C)^I$.
-\end{theorem}
-\begin{proof}
-  If the consequent holds, then $C$ is about types, by definition.
-  If a claim is about types $S$, then consider any $f \in S$, we have $C = S^I$ thus for ${\allleadstog}$ defined as ${\allleadstog}(I) = \set{f}$ we have ${\allleadstog} \in C$, thus $f \in S_C$; and consider any $f \in S_C$, consider any ${\allleadstog} \in C \suchthat f \in {\allleadstog}(I)$, we have ${\allleadstog} \in S^I$, thus $f \in S$.
-\end{proof}
-
-\begin{theorem}
-  Consider a falsifiable and anonymous claim $C$ such that $\exists {\allleadstog} \in C, f_1, f_2 \suchthat {\allleadstog}(I) = \set{f_1, f_2} \land \card{\set{i \in I \suchthat {\allleadstog}(i) = f_1}} \notin \N \land \card{\set{i \in I \suchthat {\allleadstog}(i) = f_2}} \notin \N$.
-  Then, $\forall {\allleadstog} \suchthat {\allleadstog}(I) \wsub \set{f_1, f_2}: {\allleadstog} \in C$.
-\end{theorem}
-\begin{proof}
-  Consider any anonymous claim $C$ satisfying the antecedent and any ${\allleadstog'} \suchthat {\allleadstog'}(I) \wsub \set{f_1, f_2} \land {\allleadstog'} \notin C$. 
-  To show that $C$ is not falsifiable,
-  consider any observable subset of $\allleadstog'$ and let us show that it is completable in $C$.
-
-  From the antecedent we see that $I$ is infinite.
-  Define $I_k$ as the individuals that the observable interrogates and satisfying ${\allleadstog'}(i) = f_k$.
-  Consider sets of same sizes $I'_1$ and $I'_2$ among the non observed individuals (meaning those in $I \setminus I_1 \setminus I_2$) and with corresponding types in ${\allleadstog}$ (so that $\forall i \in I'_k: {\allleadstog}(i) = f_k$).
-  Define a bijection $\sigma$ that sends $I_1$ to $I'_1$ and $I_2$ to $I'_2$, and conversely, and that sends the elements of $I \setminus (\cup_k I_k) \setminus (\cup_k I'_k)$ to themselves.
-  The resulting relation ${\allleadstog} \circ \sigma$ is in $C$ and is compatible with the observable.
-\end{proof}
-
-\begin{theorem}
-  The two following statements are equivalent. 
-  \begin{itemize}
-    \item $\forall \hist: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$
-    \item There exists no anonymous claim that holds and is falsifiable.
-  \end{itemize}
-\end{theorem}
-\begin{proof}
-  If the first one is false, then the claim $R({\allleadsto}(I))$ is not trivial, thus is falsifiable.
-
-  If the first one holds, let us show that starting from $C^\text{HA}$ and integrating all relations that are not observably distinguishable, we obtain the trivial claim.
-
-  Consider any observable whatsoever, $O \in \allpriobss$, and let us show that for some bijection $\sigma$ over $I$, $O \wsub ({\allleadsto} \circ \sigma)$.
-
-  For each of the (finitely many) individuals that $O$ contains, we can find a different behavior $f_i$ that is in $\restr{{\allleadsto}(I)}{\intvl{\hist}}$, thus, with some $j_i \in I \suchthat {\allleadsto}(j_i) = f_i$, and that is compatible with what $O$ sees of $i$.
-We define $\sigma$ so that it maps each of those individuals $i$ to the individual $j_i$ with the corresponding behavior.
-  The resulting relation ${\allleadsto} \circ \sigma$ is compatible with the observable.
-
-  It follows that if the claim is not trivial, it is not falsifiable: pick any relation missing in the claim; it cannot be rejected by any observable.
-\end{proof}
-
-\begin{conjecture}
-  If there is a claim anonymous, holding, and fals., then there is a claim about types that holds and is falsifiable.
-\end{conjecture}
-\begin{proof}
-  For a counter-example, we need a situation such that the closure for falsifiability of $\set{{\allleadsto} \circ \sigma}$ is not the whole of $\allleadstos$ and $R({\allleadsto}(I)) = P^{\allhists}$.
-  Equivalently, we need a situation such that the closure for falsifiability of $\set{{\allleadsto} \circ \sigma}$ is not the whole of $\allleadstos$ and $\forall \hist \in \allhists: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$.
-
-  In other words, we look for, given $\allleadsto$ satisfying $\forall \hist \in \allhists: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$, a possible observable that is not compatible with any ${\allleadsto} \circ \sigma$.
-
-  To prove the conjecture, given $\allleadsto$ satisfying $\forall \hist \in \allhists: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$, consider any observable whatsoever, $O \in \allpriobss$, and let us show that for some bijection $\sigma$ over $I$, $O \wsub ({\allleadsto} \circ \sigma)$.
-
-  A counter-example could be a situation “at most one of each possible behavior”.
-  Nope: if there’s twice the same behavior, we cannot observe it for sure.
-
-  The interesting case is a situation including infinitely many behaviors (not necessarily all), otherwise a claim about types exists.
-  In such a case, can we find a true claim that is anonymous and fals but not about types?
-
-  Consider a true claim $C$. It contains the true situation, thus involving $f_1, …$. Say it includes infinitely many $f_1$ and exactly one $f_2$.
-  A hypothetical situation with infinitely many $f_1$ and exactly two $f_2$ can be distinguished.
-
-  Consider the claim “there is exactly one behavior of each kind”.
-That is not fals because excludes the possibility that $f_1$ is not there (and if it’s not, impossible to observe).
-Even if $C$ admits that any finite number of behaviors may miss, it’s still not fals: if all odd $f$ miss (we have all even $f$ and no more), we will never prove it.
-  In fact, if an infinite subset of the support is there, it is not empirically distinguishable from all the subset is there; thus the claim must admit for all infinite strict subsets as well.
-  Thus, the claim could be “there is at most one behavior of each kind”.
-  “Kind” here must be: satisfying a given function in $P^{\intvl{\hist}}$ (more is not counter-observable).
-
-  Thus, consider the claim that $\forall \hist, f \in P^{\intvl{\hist}}: $ there is at one one behavior satisfying $f$. Well, that is self-contradicting.
-
-  The claim must be not about types.
-If non empty, the claim includes some mapping in $(P^{\allhists})^I$.
-If not about types, some such mapping has not all correspondances picking from various elements in $C$.
-But it is also not simply a bijection over $I$: either it picks from multiple elements of $C$, or it picks in different numbers.
-
-  In fact, if an anonymous and falsifiable claim includes a relation that includes an infinite number of $f_1$ and an infinite number of $f_2$ and so on, then I believe that the claim must also include the relations that include any finite number of $f_1$, because that case is impossible to distinguish empirically.
-
-  Check also \cref{ex:falsAnonIfBig}.
-\end{proof}
+  TODO Check \cref{ex:falsAnonIfBig}. Check any example which seemed non admitting a falsifiable claim.
 
@@
 We will start with very simple theories (\cref{sec:static}) in order to build an intuition about the conditions required on theories of deliberated choice, then justify the need for more complex theories (\cref{sec:lichtenstein}) and finally define more general theories of deliberated choice (\cref{sec:dynamic}).
+
+\subsection{Future}
+\begin{remark}
+  We could weaken indicativeness by allowing for disjuncts: observing either that $\hist \ileadsto \phi$ or that $\hist \ileadsto \psi$ permits to deduce something about $P_i$.
+  (Or more complex formulas under the form of a set of possible functions in $P^H$?)
+  (Actually I am not sure that this really weakens the condition.)
+\end{remark}
 
@@
   \begin{definition}
-    \label{def:fals}
-    A claim $C$ is \emph{falsifiable} iff
-    $C \neq {\allleadstos} \land
-    \forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
-  \end{definition}
-  \begin{definition}
     \label{def:unfals}
@@
 Perhaps we should exploit this by showing that a given relation not in C entails non rejection using that relation, or something like that?
+  \end{remark}
+
+\subsection{Kinds}
+\begin{definition}
+  A claim is \emph{strongly unfalsifiable} iff
+  $\Theta \wsub C^\wsub$.
+\end{definition}
+\Cref{ex:disjR,ex:bigor} illustrate, as well as \cref{ex:existsParticular} when $I$ is infinite.
+\begin{definition}
+  A claim is \emph{strictly unfalsifiable} iff
+  it is unfalsifiable and not strongly unfalsifiable.
+\end{definition}
+\begin{remark}
+  \label{rq:precise}
+  Making a strongly unfalsifiable claim more precise ($C = (C_1 \cap C_2) \wsub C_1$ in \cref{th:strongUToStrictU}) can make it strictly unfalsifiable.
+  Also, a strictly unfalsifiable claim can be made falsifiable by picking a single relation from the claim.
+
+  But, it does not hold that more precise claims are always more falsifiable:
+  making a falsifiable claim more precise ($C = (C_1 \cap C_2) \wsub C_2$ in \cref{ex:partlyU}) can make it strictly unfalsifiable.
+  (In fact, \cref{ex:partlyU} shows that the relation is not one-way: going from a strongly unfalsifiable ($C_1$), or from a falsifiable ($C_2$), claim, to a more precise one ($C = C_1 \cap C_2$) yields a strictly unfalsifiable claim.)
 \end{remark}
@@
 
+  \subsection{Closure under undistinguishability}
+  The following procedure permits to determine whether a claim is falsifiable.
+  Given a set of observations $S \wsub \Theta$, define the relations that are observation-compatible with $S$ as $E(S) = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: {\allleadstog} \cap \theta \in S}$.
+  Given a claim $C$, define the set of its observation-compatible relations as $E(C) = E(C^\wsub \cap \Theta)$ (reusing the letter $E$ by abuse of notation).
+  Note that this set extends $C$, in the sense that $C \wsub E(C)$.
+  The claim $C$ is falsifiable iff it is closed under extension to observation-compatible relations, that is, iff $E(C) \subseteq C$.
+  \begin{theorem}
+    \label{thm:caractFals}
+    A claim $C$ is falsifiable or trivial iff $E(C) \wsub C$, or equivalently, iff
+    $\forall {\allleadstog} \in \allleadstos$:
+    \[\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq \implies {\allleadstog} \in C.\]
+  \end{theorem}
+  \begin{proof}
+    Note that
+    $E(C) = E(C^\wsub \cap \Theta) = \set{{\allleadstog} \in \allleadstos \suchthat \forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\wsub}$.
+
+    The condition $E(C) \wsub C$ is equivalent to
+    $\forall {\allleadstog} \in \allleadstos: ({\allleadstog} \in E(C) \implies {\allleadstog} \in C)$.
+    Note that ${\allleadstog} \in E(C) \Leftrightarrow \set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq$.
+
+    By definition, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \Theta \cap \powerset{\allleadstog} \wsub C^\wsub$;
+    equivalently, iff $\exists {\allleadstog} \notin C \suchthat \set{θ \subseteq {\allleadstog}} \subseteq C^\subseteq$.
+    And, $\forall {\allleadstog} \in \allleadstos$: $\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} = \set{θ \subseteq {\allleadstog}}$.
+  \end{proof}
+
+  Let $S_θ = \set{{\allleadstog} \in \allleadstos \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
+  Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.
+  Define that a relation ${\allleadstog} \in {\allleadstos}$ is \emph{obs-compatible} with a set $S$ iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S$.
+
+  \begin{remark}
+    \label{rq:closedcomb}
+    Define the closure under combinations of $C$ as the relations that can be formed by picking parts of relations in $C$, formally, $(\cup_{S \in C^\wsub \cap \Theta} S) \cap \allleadstos$.
+    We have $E(C) \wsub (\cup_{S \in C^\wsub \cap \Theta} S) \cap \allleadstos$.
+
+    Being closed under combinations is sufficient to be falsifiable, but not necessary, as seen with \cref{ex:consti2} (in other words, for some claims, $(\cup_{S \in C^\wsub \cap \Theta} S) \cap \allleadstos \wsub E(C)$ does not hold).
+  \end{remark}
+
+\subsection{Another closure}
+Given a set of attitudes $S \wsub P^{\allhists}$, the claim associated to it designates the claim $S^I = \set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in S}$.
+Say that a claim $C$ is a claim about types iff $\exists S \wsub P^{\allhists} \suchthat C = S^I$.
+Informally, such a claim claims that the set of attitudes in $I$ is contained in $S$ (though might be a strict subset of $S$), or equivalently, that no attitude out of $S$ exists among $I$.
+\begin{definition}
+  Say that an attitude $g \in P^{\allhists}$ is observably included in a set of attitudes $S \wsub P^{\allhists}$ iff $\forall H \in \finite(\incr(\allhists)): \exists f \in S \suchthat \restr{g}{H} = \restr{f}{H}$.
+
+  Define the extension of a set of attitudes $S \wsub P^{\allhists}$ to its observably included attitudes as the set of attitudes $R(S) = \set{g \in P^{\allhists} \suchthat \forall H \in \finite(\incr(\allhists)): \exists f \in S \suchthat \restr{g}{H} = \restr{f}{H}}$.
+  Note that $S \wsub R(S)$.
+  Also note that $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$.
+\end{definition}
+\begin{theorem}
+  \label{th:RR}
+  $\forall S \wsub P^{\allhists}: R(R(S)) \wsub R(S)$.
+\end{theorem}
+\begin{proof}
+  Consider any $g \in R(R(S))$.
+  Consider any $H \in \finite(\incr(\allhists))$.
+  There exists $f \in R(S)$ such that $\restr{g}{H} = \restr{f}{H}$.
+  There exists $f' \in S$ such that $\restr{f}{H} = \restr{f'}{H}$.
+  Thus, $\restr{g}{H} = \restr{f'}{H}$.
+  Thus, $g \in R(S)$.
+\end{proof}
+Define the closure under observable inclusion of a claim about types $S$ as $R^\infty(S)$, equivalently, as the smallest set $S'$ such that $S \wsub S' = R(S')$, equivalently, as indicated by \cref{th:RR}, as $R(S)$.
+
+Let $\intvl{\hist} = (\hist_i)_{i \in \intvl{0, \card{\hist}}} \in \finite(\incr(\allhists))$ denote the increasing sequence of paths from $\emptyset$ to $\hist$.
+\begin{theorem}
+  \label{th:caractR}
+  The $S$-labeling function associated to an attitude $f \in P^{\allhists}$ is the function $l^S_f: \allhists \to \powerset{P^{\allhists}}$ defined as $l^S_f(\hist) = \set{g \in S \suchthat g(\hist) = f(\hist)}$.
+
+  We have: $R(S) = \set{f \suchthat \forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset}$.
+\end{theorem}
+\begin{proof}
+  Consider $f$ with $\forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$.
+  Consider any $H \in \finite(\incr(\allhists))$.
+  We know that $\cap_{\histp \wsub \hist}{l^S_f(\histp)} \neq \emptyset$, thus in particular, defining $\hist = \max H$ and observing that $H \wsub \set{\histp \suchthat \histp \wsub \hist}$, we have that $\cap_{\histp \in H} l^S_f(\histp) \neq \emptyset$.
+  Pick any $g \in \cap_{\histp \in H} l^S_f(\histp)$. Thus, $g \in S$.
+  Also, $\forall \hist \in H: g \in l^S_f(\hist)$, thus,
+  $\forall \hist \in H: g(\hist) = f(\hist)$.
+
+  First observe that given any $S \wsub P^{\allhists}$, $f \in P^{\allhists}$ and $\hist \in \allhists$, as $\histp \wsub \hist$ iff $\histp \in \intvl{\hist}$, we have that $\cap_{\histp \wsub \hist} l^S_f(\histp) = \set{g \in S \suchthat \forall \histp \in \intvl{\hist}: g(\histp) = f(\histp)}$.
+
+  It follows that if $\forall \hist \in \allhists: \cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$, then $\forall H \in \finite(\incr(\allhists))$: $\emptyset \neq \set{g \in S \suchthat \forall \histp \in \intvl{\max H}: g(\histp) = f(\histp)} \wsub \set{g \in S \suchthat \forall \histp \in H: g(\histp) = f(\histp)}$.
+
+  Conversely, if $\forall H \in \finite(\incr(\allhists)): \set{g \in S \suchthat \forall \histp \in H: g(\histp) = f(\histp)} \neq \emptyset$, then $\forall \hist \in \allhists$, defining $H = \intvl{\hist}$, we have that $\cap_{\histp \wsub \hist} l^S_f(\histp) \neq \emptyset$.
+\end{proof}
+
+\begin{lemma}
+  \label{th:typesfalsifiable}
+  A set of attitudes $S \wsub P^{\allhists}$
+  satisfies $\forall g \in P^{\allhists} \setminus S: \exists H \in \finite(\incr(\allhists)) \suchthat \forall f \in S: \restr{g}{H} \neq \restr{f}{H}$,
+  iff its associated claim is falsifiable or trivial.
+\end{lemma}
+\begin{proof}
+  Pick any ${\allleadstog} \notin C$.
+  By definition of $C$,
+  $\exists i \in I \suchthat {{\ileadstog}} \notin S$.
+  As $C$ holds, ${\ileadstog} \notin \set{{\ileadsto[j]} \suchthat j \in I}$ (\cref{th:typesholds}).
+  Pick any $H$ such that $\forall {\ileadstog[j]} \in S: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadstog[j]}(\hist)$.
+  Define $\theta = \set{(\hist, i, {\ileadstog}(\hist)) \suchthat \hist \in H} \in \Theta \cap \powerset{\allleadstog}$.
+  Then, $\theta \notin C^\wsub$, because $\forall {\ileadstog[j]} \in S: \theta \nsubseteq {\ileadstog[j]}$.
+
+  Conversely, assume that for some ${\ileadstog} \in P^{\allhists} \setminus S$, no $H \in \finite(\incr(\allhists))$ satisfies the indicated condition.
+  Define ${\allleadstog}$ as including ${\ileadstog}$ and for all other individuals, relations from $S$.
+  Then, ${\allleadstog} \notin C$, but any observation will be in $C$, thus the claim is not falsifiable and not trivial.
+\end{proof}
+\begin{lemma}
+  \label{th:typesholds}
+  Consider a set of attitudes $S \wsub P^{\allhists}$. Its associated claim holds iff $\set{{\ileadsto[j]} \suchthat j \in I} \wsub S$.
+\end{lemma}
+\begin{lemma}
+  \label{th:typesanonymous}
+  Given any set of attitudes $S \wsub P^{\allhists}$, its associated claim is anonymous.
+\end{lemma}
+The following result follows from \cref{th:typesfalsifiable,th:typesholds,th:typesanonymous}.
+\begin{theorem}
+  \label{th:suffFals}
+  Assume that $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  Then, the claim $C$ associated to the set of attitudes $S = \set{{\ileadsto[j]} \suchthat j \in I}$ holds, is anonymous, and is falsifiable or trivial.
+\end{theorem}
+\begin{proof}
+  For another proof, note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat \forall i \in I: \exists j \in I \suchthat \theta \cap (\allhists × \set{i} × P) \wsub {\ileadsto[j]}}$.
+  Pick any ${\allleadstog} \in E(C^\wsub \cap \Theta)$ and let us show that ${\allleadstog} \in C$.
+  Note that ${\allleadstog} \notin C \iff \exists i \in I \suchthat {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, in which case the consequent in the theorem holds.
+  We need to show that $\nexists i \in I, H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
+  In other words, given any $i \in I$, we need to show that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
+\end{proof}
+
+The following result follows from \cref{th:typesfalsifiable}.
+\begin{theorem}
+  If a set of attitudes $S \wsub P^{\allhists}$ is not closed under observable inclusion, then it is not falsifiable and not trivial.
+\end{theorem}
+\begin{theorem}
+  Given any situation, if the claim associated to the set of attitudes $R({\allleadsto}(I))$ is trivial, then there exists no claim associated to a set of attitudes that holds and is falsifiable.
+\end{theorem}
+\begin{proof}
+  Consider a claim related to a set of attitudes $S$ that holds and that is falsifiable or trivial.
+  For it to hold, we need ${\allleadsto}(I) \wsub S$.
+  From \cref{th:typesfalsifiable}, for it to be falsifiable or trivial, we need that $\forall g \in P^{\allhists} \setminus S: \exists H \in \finite(\incr(\allhists)) \suchthat \forall f \in S: \restr{g}{H} \neq \restr{f}{H}$.
+In other words, all $g$ must be observably excludable from $S$.
+In other words, $S$ must be closed under observable inclusion.
+Thus, we need $R(S) \wsub S$.
+  Also, because $S_1 \wsub S_2 \implies R(S_1) \wsub R(S_2)$, we need
+  $R({\allleadsto}(I)) \wsub R(S) \wsub S$.
+  It follows that $S$ is trivial.
+\end{proof}
+\begin{theorem}
+  Given any situation, the claim associated to the set of attitudes $R({\allleadsto}(I))$ holds, is anonymous, and is falsifiable or trivial.
+\end{theorem}
+\begin{example}
+  Define $f^{(p, p')} \in P^{\allhists}$ as follows: $f^{(p, p')}(\emptyset) = p$ and $\forall \hist \in \allhists: \hist ≠ \emptyset \implies f^{(p, p')}(\hist) = p'$.
+
+  Consider a situation such that ${\allleadsto}(I) = \set{f^{(p, p')} \suchthat p, p' \in \set{\phi, ¬\phi}}$, thus, containing only people constant to $\phi$ and people constant to $¬\phi$, except that they map $\emptyset$ to anything in $\set{\phi, ¬\phi}$.
+  Define $F^p = \set{f^{(p, p')} \suchthat p' \in \set{\phi, ¬\phi}}$.
+
+  \Cref{th:caractR} indicates that $R({\allleadsto}(I)) = \set{f \suchthat l^S_f(\emptyset) \in \set{F^\phi, F^{¬\phi}} \land \forall \ar \in \allargs: [\forall \hist \suchthat \hist_1 = \ar: l^S_f(\hist) \in l^S_f(\emptyset)] \land [\forall \hist, \histp \suchthat \hist_1 = \histp_1 = \ar: l^S_f(\hist) = l^S_f(\histp)]}$.
+
+  Thus, $R({\allleadsto}(I))$ contains, for each mapping $m: \allargs \rightarrow \set{\phi, ¬\phi}$, the two functions $f_m^\phi, f_m^{¬\phi}$ defined as $f_m^\phi(\emptyset) = \phi$ and $\forall \ar \in \allargs: f_m^\phi((\ar, …)) = m(\ar)$, and similarly for $f_m^{¬\phi}$.
+
+  The claim associated to $R({\allleadsto}(I))$ is not trivial: $\forall f \suchthat [\exists \hist, \histp \ssub \hist \suchthat f(\histp) ≠ f(\hist)]: f \notin R({\allleadsto}(I))$.
+\end{example}
+\begin{example}
+  Consider $\allargs = \set{\ar_1, \ar_2}$ and ${\allleadsto}(I) = \set{f \suchthat f(\ar_1) ≠ \phi \lor f(\ar_2) ≠ \phi}$, thus, $f \notin {\allleadsto}(I)$ iff $f(\ar_1) = f(\ar_2) = \phi$.
+
+  Consider any $f \notin {\allleadsto}(I)$.
+  We have $f \in R({\allleadsto}(I))$.
+  Indeed, define $g_1 \in P^{\allhists}$ as $g_1 = f$ except that $g_1(\ar_2) = ¬\phi$, and $g_2 \in P^{\allhists}$ as $g_2 = f$ except that $g_2(\ar_1) = ¬\phi$.
+  Then, $g_1, g_2 \in {\allleadsto}(I)$.
+  Now consider any $H \in \finite(\incr(\allhists))$.
+  If $(\ar_2) \notin H$, then $\restr{f}{H} = \restr{g_1}{H}$; otherwise, $\restr{f}{H} = \restr{g_2}{H}$.
+
+  It follows that the claim associated to $R({\allleadsto}(I))$ is trivial.
+\end{example}
+\begin{remark}
+  A few more, maybe not useful, definitions.
+
+  Given a set of attitudes $S$ and $\hist \in \allhists$, define the equivalence relation $=_\hist$ on $S$ as $f =_\hist g$ iff $f(\hist) = g(\hist)$.
+This also defines the quotient set $S / =_\hist$.
+(For the readers used to that terminology: if defining $\beta_\hist \in P^S$ as $\beta_\hist(f) = f(\hist)$, then $=_\hist$ is the equivalence kernel of $\beta_\hist$ and $S / =_\hist$ is the coimage of $\beta_\hist$.)
+  Similarly, given $S$ and $H \in \finite(\incr(\allhists))$, define the equivalence relation $=_H$ on $S$ as $f =_H g$ iff $\restr{f}{H} = \restr{g}{H}$. This also defines the quotient set $S / =_H$.
+
+  A function $l: \allhists \to \powerset{P^{\allhists}}$ is decreasing iff $\forall \hist \wsub \histp: l(\histp) \wsub l(\hist)$.
+  Let $S \wsub P^{\allhists}$ be a set of attitudes.
+  Say that a function $l: \allhists \to \powerset{P^{\allhists}}$ is an $S$-point-labeling function iff $\forall \hist \in \allhists: l(\hist) \in S / =_\hist$.
+  Say that a function $l: \allhists \to \powerset{P^{\allhists}}$ is an $S$-sequence-labeling function iff $\forall \hist \in \allhists: l(\hist) \in S / =_{\intvl{\hist}}$.
+\end{remark}
+\begin{theorem}
+  Given $\hist \in \allhists$, define $\restr{S}{\intvl{\hist}} = \set{\restr{f}{\intvl{\hist}} \suchthat f \in S}$.
+  Given a non empty set of attitudes $S \wsub P^{\allhists}$, the following statements are equivalent.
+  \begin{itemize}
+    \item The claim associated to $R(S)$ is not trivial
+    \item $R(S) ≠ P^{\allhists}$
+    \item $\exists \hist \in \allhists, f \in P^{\intvl{\hist}} \suchthat \forall g \in S: \restr{g}{\intvl{hist}} ≠ f$
+    \item $\exists \hist, f \in P^{\intvl{\hist}} \suchthat f \notin \restr{S}{\intvl{\hist}}$
+    \item $\exists \hist \suchthat P^{\intvl{\hist}} \not\wsub \restr{S}{\intvl{\hist}}$.
+  \end{itemize}
+  Also, the following statements are equivalent.
+  \begin{itemize}
+    \item The claim associated to $R(S)$ is trivial
+    \item $R(S) = P^{\allhists}$
+    \item $\forall \hist, f, \exists g \in S \suchthat \restr{g}{\intvl{\hist}} = f$
+    \item $\forall \hist: P^{\intvl{\hist}} \wsub \restr{S}{\intvl{\hist}}$.
+  \end{itemize}
+  Furthermore, $\forall \hist: P^{\intvl{\hist}} \wsub \restr{S}{\intvl{\hist}} \implies \card{S} \notin \Z$.
+\end{theorem}
+\begin{proof}
+  This follows from $R(S) ≠ P^{\allhists} \iff \exists f \in P^{\allhists}, \hist \in \allhists \suchthat \cap_{\histp \wsub \hist} l^S_f(\histp) = \emptyset$.
+\end{proof}
+
+To recap, we now know that with $S = {\allleadsto}(I)$, when $R(S) ≠ P^{\allhists}$, there is a claim that holds and is anonymous and falsifiable.
+This includes all situations with finite behaviors ($\card{S} \in \Z$), thus includes all situations with finite $I$.
+Consider now situations such that $R({\allleadsto}(I)) = P^{\allhists}$.
+
+Define $I = P^\Z$ and ${\ileadsto} = i \circ \card$, so that $S = {\allleadsto}(I) = \set{l \circ \card \in P^{\allhists} \suchthat l \in P^\Z}$.
+We have $R(S) = P^{\allhists}$.
+The function $f(\ar) ≠ f(\ar')$, for example, is not in $S$.
+
+\begin{theorem}
+  Given a claim $C$, define $S_C \wsub P^{\allhists}$ as $S_C = \bigcup_{{\allleadstog} \in C}({\allleadstog}(I))$.
+  A claim $C$ is about types iff $C = (S_C)^I$.
+\end{theorem}
+\begin{proof}
+  If the consequent holds, then $C$ is about types, by definition.
+  If a claim is about types $S$, then consider any $f \in S$, we have $C = S^I$ thus for ${\allleadstog}$ defined as ${\allleadstog}(I) = \set{f}$ we have ${\allleadstog} \in C$, thus $f \in S_C$; and consider any $f \in S_C$, consider any ${\allleadstog} \in C \suchthat f \in {\allleadstog}(I)$, we have ${\allleadstog} \in S^I$, thus $f \in S$.
+\end{proof}
+
+\begin{theorem}
+  Consider a falsifiable and anonymous claim $C$ such that $\exists {\allleadstog} \in C, f_1, f_2 \suchthat {\allleadstog}(I) = \set{f_1, f_2} \land \card{\set{i \in I \suchthat {\allleadstog}(i) = f_1}} \notin \Z \land \card{\set{i \in I \suchthat {\allleadstog}(i) = f_2}} \notin \Z$.
+  Then, $\forall {\allleadstog} \suchthat {\allleadstog}(I) \wsub \set{f_1, f_2}: {\allleadstog} \in C$.
+\end{theorem}
+\begin{proof}
+  Consider any anonymous claim $C$ satisfying the antecedent and any ${\allleadstog'} \suchthat {\allleadstog'}(I) \wsub \set{f_1, f_2} \land {\allleadstog'} \notin C$.
+  To show that $C$ is not falsifiable,
+  consider any observable subset of $\allleadstog'$ and let us show that it is completable in $C$.
+
+  From the antecedent we see that $I$ is infinite.
+  Define $I_k$ as the individuals that the observable interrogates and satisfying ${\allleadstog'}(i) = f_k$.
+  Consider sets of same sizes $I'_1$ and $I'_2$ among the non observed individuals (meaning those in $I \setminus I_1 \setminus I_2$) and with corresponding types in ${\allleadstog}$ (so that $\forall i \in I'_k: {\allleadstog}(i) = f_k$).
+  Define a bijection $\sigma$ that sends $I_1$ to $I'_1$ and $I_2$ to $I'_2$, and conversely, and that sends the elements of $I \setminus (\cup_k I_k) \setminus (\cup_k I'_k)$ to themselves.
+  The resulting relation ${\allleadstog} \circ \sigma$ is in $C$ and is compatible with the observable.
+\end{proof}
+
+\begin{theorem}
+  \label{th:AHF}
+  The two following statements are equivalent.
+  \begin{itemize}
+    \item $\forall \hist: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$
+    \item There exists no anonymous claim that holds and is falsifiable.
+  \end{itemize}
+\end{theorem}
+\begin{proof}
+  If the first one is false, then the claim $R({\allleadsto}(I))$ is not trivial, thus is falsifiable.
+
+  If the first one holds, let us show that starting from $C^\text{HA}$ and integrating all relations that are not observably distinguishable, we obtain the trivial claim.
+
+  Consider any observable whatsoever, $O \in \allpriobss$, and let us show that for some bijection $\sigma$ over $I$, $O \wsub ({\allleadsto} \circ \sigma)$.
+
+  For each of the (finitely many) individuals that $O$ contains, we can find a different behavior $f_i$ that is in $\restr{{\allleadsto}(I)}{\intvl{\hist}}$, thus, with some $j_i \in I \suchthat {\allleadsto}(j_i) = f_i$, and that is compatible with what $O$ sees of $i$.
+We define $\sigma$ so that it maps each of those individuals $i$ to the individual $j_i$ with the corresponding behavior.
+  The resulting relation ${\allleadsto} \circ \sigma$ is compatible with the observable.
+
+  It follows that if the claim is not trivial, it is not falsifiable: pick any relation missing in the claim; it cannot be rejected by any observable.
+\end{proof}
+\begin{theorem}
+  The following statements are equivalent.
+  \begin{itemize}
+    \item $\exists \hist \in \allhists, f \in P^{\intvl{\hist}} \suchthat f \notin \restr{{\allleadsto}(I)}{\intvl{\hist}}$.
+    \item $\exists \emptyset ≠ H \in \incr(\allhists), f \in P^H \suchthat f \notin \restr{{\allleadsto}(I)}{H}$.
+    \item There exists an anonymous claim that holds and is falsifiable.
+  \end{itemize}
+\end{theorem}
+\begin{proof}
+  The first one is the complementary condition to \cref{th:AHF}.
+  It implies the second one.
+  The second one implies the first one as $f$ can be extended to $\intvl{\hist} = \intvl{\max H}$.
+\end{proof}
+
+\begin{theorem}[Direct proof]
+  \label{th:AHFimpl}
+  If $\forall \hist: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$,
+  then any anonymous claim that holds is trivial or strongly unfalsifiable.
+\end{theorem}
+\begin{proof}
+  To hold and be anonymous, we need $C$ includes $C^\text{HA}$ (\cref{th:claim_ha}).
+  Pick any such non trivial $C$ and let us show that $\Theta \wsub C^\wsub$.
+  Pick any $\theta \in \Theta$.
+
+  We define a bijection $\sigma$ over $I$ as follows.
+  For each of the (finitely many) individuals that $\theta$ contains, we can find a different behavior $f_i$ that is in $\restr{{\allleadsto}(I)}{\intvl{\hist}}$, thus, with some $j_i \in I \suchthat {\allleadsto}(j_i) = f_i$, and that is compatible with what $\theta$ sees of $i$.
+  We define $\sigma$ so that it maps each of those individuals $i$ to the individual $j_i$ with the corresponding behavior.
+
+  The resulting relation ${\allleadsto} \circ \sigma$ is compatible with the observable.
+\end{proof}
+
+\subsection{Indicativeness}
+\begin{theorem}
+  Indicativeness does not imply true indicativeness, even when considering only anonymous and falsifiable claims that hold.
+\end{theorem}
+\begin{proof}
+  Consider the situation where everybody is constant to $\phi$ except that emptyset to $¬\phi$.
+  The claim “C HA or everybody is constant to $\phi$” is anonymous and falsifiable and indicative and holds, but is not truly indicative.
+  Thus, the claim is “(everybody satisfies emptyset to $\phi$ or everybody satisfies emptyset to $¬\phi$) and (everybody satisfies every path but emptyset to $\phi$)”.
+  It is falsifiable: any behavior function not in the claim satisfies “(somebody fails emptyset to $\phi$ and somebody fails emptyset to $¬\phi$) or (somebody fails every path but emptyset to $\phi$)”, which is observable in either case.
+  It is indicative, as the behavior function “everybody constant to $\phi$” is what remains in the claim if assuming observing someone sending $\emptyset$ to $\phi$.
+
+  But it is not truly indicative: this would require some truthful observation that leaves only a subset of the claim with no $\pi({\allleadstog})(i) = \emptyset$, which requires excluding “everybody satisfies emptyset to $¬\phi$”.
+\end{proof}
+
+Let us determine which situations admit anonymous and falsifiable claims that hold and are truly indicative (or other?).
+
+From \cref{th:suffIndic} we know that we require at least
+for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\ileadsto[i_1]}(\hist) \neq {\ileadsto[i_2]}(\hist)$.
+
+\begin{theorem}
+  If an anonymous claim holds and is truly indicative, then $\exists i \in I \suchthat P_i ≠ \emptyset$.
+\end{theorem}
+\begin{proof}
+  By anon and holding, we have $C^\text{HA} \wsub C$.
+  By true indicativeness, for some $i$ and $\hist$ and $f \wsub {\ileadsto}$ on that $\intvl{\hist}$, all and some completion of $f$ in $C$ lead to $\pi({\allleadstog})(i) ≠ \emptyset$, thus, in particular,
+  ${\allleadsto}$ leads to $\pi({\allleadsto})(i) ≠ \emptyset$, 
+  whence 
+  $\exists i \in I \suchthat P_i ≠ \emptyset$.
+\end{proof}
+
+TODO: consider condition $\exists H \in \incr(\allhists), f \in P^H, \ar, p \suchthat \forall i: \restr{\ileadsto}{H} = f \implies \ar \ileadstost p$ (and someone satisfies the antecedent).
+Maybe this is equivalent to indicative claim exists?
+And implies the rest?
+
+\begin{conjecture}
+  If $P_{i_1} = \phi$ with a single decisive argument $\ar \ileadstost \phi$ and $i_2$ satisfies ${\ileadsto[i_2]} = {\ileadsto[i_1]}$ except that $(\ar) \ileadsto[i_2] ¬\phi$, then there is no anonymous and truly indicative claim that holds.
+\end{conjecture}
+\begin{proof}
+  True indicativeness requires that
+  $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \wsub {\allleadsto} \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
+  If $\theta$ observes $(\ar_1, \ar)$
+\end{proof}
+
 \subsection{Extensions}
@@
 
-  From $\theta \sub {\allleadstog}$ we have $\theta \in C_2^\wsub$.
+    From $\theta \wsub {\allleadstog}$ we have $\theta \in C_2^\wsub$.
     Thus, $\theta \in (C_1 \cap C_2)^\wsub = C^\wsub$.
@@
     The claim $[(\ar) \ileadstog \phi] \lor [(\ar, \ar) \ileadstog \phi] \lor …$,
-  thus, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat (a)^n \ileadstog \phi}$,
+    thus, $C = \set{{\allleadstog} \suchthat \exists n \in \Zp \suchthat (a)^n \ileadstog \phi}$,
     is strongly unfalsifiable.
 
-  Let $C' = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall j: (a)^n \ileadstog[j] \phi}$ denote the claim of \cref{ex:bigor}.
+    Let $C' = \set{{\allleadstog} \suchthat \exists n \in \Zp \suchthat \forall j: (a)^n \ileadstog[j] \phi}$ denote the claim of \cref{ex:bigor}.
     We have $C' \subseteq C$.
@@
     $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
-  Say that $R$ is coverable iff $\exists k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}} \suchthat
+    Say that $R$ is coverable iff $\exists k \in \Z, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}} \suchthat
       \cup_{l \in \intvl{1, k}} O_l = R \land
@@
 
-  Pick some $k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}}$ as in the hypothesis.
+    Pick some $k \in \Z, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}}$ as in the hypothesis.
     Consider any $l \in \intvl{1, k - 1}$
@@
 
-  % Given $k \in \N$ and a family $(O_l)_{l \in \intvl{1, k}}$, consider $\exists f \in C \suchthat 
-  Say that $R$ is coverable iff $\exists k \in \N, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}} \suchthat
+    % Given $k \in \Z$ and a family $(O_l)_{l \in \intvl{1, k}}$, consider $\exists f \in C \suchthat 
+    Say that $R$ is coverable iff $\exists k \in \Z, (O_l)_{l \in \intvl{1, k}}, (o_l)_{l \in \intvl{1, k}} \suchthat
       \cup_{l \in \intvl{1, k}} O_l = R \land

### 2024-05-20 simple.tex
Kept single def indicativeness

@@
 A claim $C$ is \emph{strongly informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) \ssub P$.
-% A claim $C$ is \emph{indicative} iff $\exists H \in \finite(\incr(\allhists)), i \in I \suchthat \pi(\set{{\allleadstog} \suchthat H \wsub \ileadstoinvg(P)} \cap C)(i) \ssub P$.
-Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
-A claim $C$ is \emph{indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \cap C^\wsub \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
-Indicativity mandates that when knowing a finite number of observations about a given $i$ compatible with any (possibly counter-factual) world in $C$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
-A claim $C$ is \emph{truly indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \wsub {\allleadsto} \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
-A claim $C$ is \emph{newly indicative} iff $\forall {\allleadstog} \in C: \exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \wsub {\allleadstog} \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
-Indicativity mandates that when knowing a finite number of observations about a given $i$ compatible with any (possibly counter-factual) world in $C$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
+A claim $C$ is \emph{indicative} iff $\forall {\allleadstog} \in C: \exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \wsub {\allleadstog} \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
+Indicativity mandates that for each (possibly counter-factual) world in $C$, when knowing a finite number of observations about a given $i$ compatible with, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
 
@@
   \begin{proof}
+    TODO check this, there is a problem with the definition and use of CA.
+
     For \ref{it:condHAI} $\implies$ \ref{it:HAI},
@@
 \subsection{Indicativeness}
-\begin{theorem}
-  Indicativeness does not imply true indicativeness, even when considering only anonymous and falsifiable claims that hold.
-\end{theorem}
-\begin{proof}
-  Consider the situation where everybody is constant to $\phi$ except that emptyset to $¬\phi$.
-  The claim “C HA or everybody is constant to $\phi$” is anonymous and falsifiable and indicative and holds, but is not truly indicative.
-  Thus, the claim is “(everybody satisfies emptyset to $\phi$ or everybody satisfies emptyset to $¬\phi$) and (everybody satisfies every path but emptyset to $\phi$)”.
-  It is falsifiable: any behavior function not in the claim satisfies “(somebody fails emptyset to $\phi$ and somebody fails emptyset to $¬\phi$) or (somebody fails every path but emptyset to $\phi$)”, which is observable in either case.
-  It is indicative, as the behavior function “everybody constant to $\phi$” is what remains in the claim if assuming observing someone sending $\emptyset$ to $\phi$.
-
-  But it is not truly indicative: this would require some truthful observation that leaves only a subset of the claim with no $\pi({\allleadstog})(i) = \emptyset$, which requires excluding “everybody satisfies emptyset to $¬\phi$”.
-\end{proof}
-
-Let us determine which situations admit anonymous and falsifiable claims that hold and are truly indicative (or other?).
+Let us determine which situations admit anonymous and falsifiable claims that hold and are indicative.
 
@@
 for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\ileadsto[i_1]}(\hist) \neq {\ileadsto[i_2]}(\hist)$.
-
-\begin{theorem}
-  If an anonymous claim holds and is truly indicative, then $\exists i \in I \suchthat P_i ≠ \emptyset$.
-\end{theorem}
-\begin{proof}
-  By anon and holding, we have $C^\text{HA} \wsub C$.
-  By true indicativeness, for some $i$ and $\hist$ and $f \wsub {\ileadsto}$ on that $\intvl{\hist}$, all and some completion of $f$ in $C$ lead to $\pi({\allleadstog})(i) ≠ \emptyset$, thus, in particular,
-  ${\allleadsto}$ leads to $\pi({\allleadsto})(i) ≠ \emptyset$, 
-  whence 
-  $\exists i \in I \suchthat P_i ≠ \emptyset$.
-\end{proof}
 
@@
 \begin{conjecture}
-  If $P_{i_1} = \phi$ with a single decisive argument $\ar \ileadstost \phi$ and $i_2$ satisfies ${\ileadsto[i_2]} = {\ileadsto[i_1]}$ except that $(\ar) \ileadsto[i_2] ¬\phi$, then there is no anonymous and truly indicative claim that holds.
+  If $P_{i_1} = \phi$ with a single decisive argument $\ar \ileadstost \phi$ and $i_2$ satisfies ${\ileadsto[i_2]} = {\ileadsto[i_1]}$ except that $(\ar) \ileadsto[i_2] ¬\phi$, then there is no anonymous and indicative claim that holds.
 \end{conjecture}
 \begin{proof}
-  True indicativeness requires that
+  Indicativeness requires that
   $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \wsub {\allleadsto} \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
